### 2022-07-22 src/paper/paper.tex
Initial commit

\documentclass[a4paper]{article}

\usepackage{microtype}
\usepackage{fullpage}
\usepackage{mathtools}
\usepackage{amsfonts}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{hyperref}
\usepackage{amsthm}
\usepackage{xcolor}
\usepackage[backend=biber,style=authoryear,maxbibnames=99,hyperref=true]{biblatex}

\addbibresource{references.bib}

\usepgfplotslibrary{fillbetween}
\usetikzlibrary{shapes}
\pgfplotsset{compat=1.17}

\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}

\newcommand{\dt}{\mathrm{d}t}
\newcommand{\ds}{\mathrm{d}s}
\newcommand{\E}{\mathbb{E}}

\title{The value of intermediation -- results so far}
\author{Martin Stancsics}

\begin{document}

\maketitle

\begin{abstract}
    This paper proposes a simplified model of two-sided markets aimed at analyzing the shares of total surplus various participants can achieve. Instead of explicitly modelling price structures and entry choices, I use a cooperative approach as a reduced-form model of bargaining outcomes. I show that this technique provides an analytically very tractable way of expressing the profits and surpluses of the agents.
\end{abstract}

\section{Motivation}

The use of solution concepts from cooperative game theory, such as the Shapley-value, to model the outcome of a bargaining process has been a feature of many papers in the industrial organization literature. It is particularly prevalent in articles dealing with issues related to integration and mergers \parencite[e.g.][]{hart1990property,segal2003collusion,inderst2003bargaining,montez2007downstream}. This is in part motivated by the appealing properties of the resulting distributions, their tractability, but also by the long line of studies showing that various bargaining procedures lead to such outcomes. For example, \textcite{gul1989bargaining,winter1994demand,hart1996bargaining,inderst2003bargaining,} or, perhaps most relevant to this paper, \textcite{stole1996intra} all propose various extensive-form bargaining games in which the expected outcomes correspond to players' Shapley-values.

A common feature of the aforementioned papers is that they involve models with a finite number of agents. However, as is often the case in economics, the infinite-player approximations might turn out to be more tractable while retaining the main conclusions of the finite models from which they arise. Indeed, in the case of cooperative games with non-atomic players, the axiomatic and asymptotic approaches both give rise to the same value\footnote{On the appropriate subspace of non-atomic games.} \parencite{aumann2015values}, which is furthermore analytically simple and readily interpretable. An economic application of this theory can be found in \textcite{billera1978internal}.

Beyond games with no atoms, economists are often interested in situations characterized by a relatively small number of large players and numerous individually rather insignificant ones. The continuous analogue of them are called oceanic games, in which the set of players consists of a finite number of atoms and an ocean made up of a continuum of fringe players. While the axiomatic characterization of the value on such games has not been particularly fruitful,\footnote{\textcite{hart1973values} shows that the usual axioms do not characterize a unique value in general.} \textcite{fogelman1980asymptotic} demonstrates that the asymptotic approach works well on a large subset of them.

Despite this positive result, and their analytical tractability, oceanic games are utilized by hardly any papers in economics. One of the few such examples is \textcite{levy1997individual}, applying it to the problem of wage bargaining. In the following, I propose an oceanic game with the main feature that the large player(s) is indispensable for creating value. Such a model can apply, for example, to upstream-downstream supply chains, or platforms connecting two sides of a market. I demonstrate that the values of the players in those models are described by easily interpretable and visualizable expressions. Furthermore, the results are simple enough that these games can be embedded into more complex models, for example, as the second stage of a sequential game \parencite[as in e.g.][]{montez2007downstream}. Just as importantly, the outcomes are in line with one's intuitive expectations of bargaining outcomes in such situations.

\section{One-sided case}

Imagine a cooperative game with two types of players: a major player $P$ and $n$ smaller players. I.e., $N = \{P, A_1, \dots, A_n\}$. Assume that (1) no coalition of players can achieve a positive value without the participation of $P$ and (2) players $A_i$ are identical. Let $n_T(S)$ denote the number of players of type $T$ in coalition $S$. Then, the value $S \subset N$ can achieve is the following:
\begin{align*}
    v(S) = \begin{cases}
        0                              & \text{if } P \notin S \\
        f\left(\frac{n_A(S)}{n}\right) & \text{otherwise}.
    \end{cases}
\end{align*}
One can think of this setting as a (one-sided) platform and a number of potential entrants.

\begin{proposition}
    The game $(N, v)$ is monotone and superadditive if and only if $f$ is increasing and $f(0) \geq 0$. % It is supermodular if and only if $f$ is convex.
\end{proposition}
\begin{proof}
    Monotonicity is evident. For superadditivity, note that for any $S, T$ such that $S \cap T = \emptyset$, $P \notin S$ or $P \notin T$. WLOG assume it is the latter, therefore $v(T) = 0$. As a result, $v(S) + v(T) = v(S) \leq v(S \cup T)$ holds if and only if $(N, v)$ is monotone.
\end{proof}
In the following, let us assume that the assumptions required for monotonicity are always satisfied. It ensures that the games are of bounded variation, and thus the main theorem in \textcite{fogelman1980asymptotic} applies: asymptotic value coincides with the axiomatic one using the uniform distribution for the latter. \textcolor{red}{Note: I realize that this paragraph is somewhat vague and needs explanation. However, for the current set of results, I do not rely on said theorem. If I end up using it later, I will expand on this part.}

Let $\varphi_P^n$ denote the Shapley-value of player $P$ in the case of $n$ players of type $A$. The following proposition demonstrates the main idea of this paper: even as the number of fringe players goes to infinity, the Shapley-value of the platform does not converge to $f(1)$. This in turn implies that the aggregated Shapley-values of the fringe remain positive even in the limit.
\begin{proposition}
    \label{prop:one_sided}
    Let $f$ be continuous on [0, 1]. Then
    \begin{align*}
        \varphi_P^\infty = \lim_{n \to \infty} \varphi_p^n = \int_0^1 f(t) \dt .
    \end{align*}
\end{proposition}
\begin{proof}
    For a permutation of players $R$, let us denote the players preceding $i$ by $\mathcal{P}_i^R$. The value of player $P$ is their expected marginal contribution averaged over all permutations of $N$:
    \begin{align*}
        \varphi_P^n = \frac{1}{(n+1)!} \sum_R v(\mathcal{P}_P^R \cup \{i\}) - v(\mathcal{P}_P^R)
    \end{align*}
    First, note that $v(\mathcal{P}_P^R) = 0$ for any permutation, as no coalition can achieve a positive value without player $P$. Furthermore, using the fact that all agents of type $A$ are identical implies that $v(\mathcal{P}_P^R \cup \{i\})$ only depends on the number of agents in the coalition. More precisely, 
    \begin{align*}
        v(\mathcal{P}_P^R \cup \{i\}) = f(n_A(\mathcal{P}_P^R \cup \{i\}) / n) = f(|\mathcal{P}_P^R| / n).
    \end{align*}
    Finally, the set of permutations in which the number of players preceding $P$ is $k$ is independent of $n$, i.e.
    \begin{align*}
        \{R \mid |\mathcal{P}_P^R| = k\} = n! \quad \forall\, k.
    \end{align*}
    Putting all the above together, the value of player $P$ can be expressed as
    \begin{align*}
        \varphi_P^n &= \frac{1}{(n+1)!} \sum_{k=0}^n n! f(k / n) \\
        &= \frac{1}{n+1} \sum_{k=0}^n f(k / n) \\
        &= \frac{n}{n+1} \underbrace{\frac{1}{n} \sum_{k=0}^{n-1} f(k / n)}_{=S_n} + \frac{1}{n+1} f(1).
    \end{align*}
    $S_n$ are just the left Riemann-sums of function $f$ on the interval $[0, 1]$. Therefore, if $f$ is continuous (and thus Riemann-integrable), then $S_n \to \int_0^1 f(t)$, and thus
    \begin{align*}
        \lim_{n \to \infty} \varphi_P^n &= \lim_{n \to \infty} \frac{1}{n+1} \sum_{k=1}^n f(k / n) \\
        &= \lim_{n \to \infty}\underbrace{\frac{n}{n+1}}_{\to 1} \frac{1}{n} \sum_{k=0}^{n-1} f(k / n) + \underbrace{\frac{1}{n+1} f(1)}_{\to 0} \\
        &= \int_0^1 f(t) \dt .
    \end{align*}
\end{proof}

The above proposition is not surprising in light of \textcite{fogelman1980asymptotic}: the limit is just the expected marginal contribution of the single atomic player, with said player being placed in the order according to the uniform distribution. Nevertheless, even this simple result has a compelling geometric interpretation, and gives rise to a couple of interesting corollaries, detailed below.

\begin{corollary}
    The aggregated Shapley-value of the fringe (alternatively, the per-unit Shapley-value of the fringe) is
    \begin{align*}
        \varphi_A^\infty = f(1) - \int_0^1 f(t) \dt.
    \end{align*}
    Furthermore, if $f$ is differentiable on $[0, 1]$, Then the value of the fringe can also be expressed as
    \begin{align*}
        \varphi_A^\infty = \int_0^1 t f'(t) \dt.
    \end{align*}
\end{corollary}
\begin{proof}
    The first equality comes from the efficiency of the Shapley-value. The values of all players sum up to $f(1)$ for all $n \in \mathbb{N}$, therefore
    \begin{align*}
        \lim_{n \to \infty} \sum_{i=1}^n \varphi_{A_i}^n = \lim_{n \to \infty} (1 - \varphi_P^n ) = 1 - \int_0^1 f(t).
    \end{align*}
    The second can be obtained by integration by parts:
    \begin{align*}
        \int_0^1 t f'(t) \dt = tf(t) \mid_0^1 - \int_0^1 f(t) \dt = f(1) - \int_0^1 f(t) \dt
    \end{align*}
\end{proof}

It is already apparent from Figure \ref{fig:one_sided} that (for fixed $f(0)$ and $f(1)$) player $P$ gets a larger share of the surplus when $f(t)$ is large even for small values of $t$. It corresponds to the case when only a small fraction of the fringe is needed to create most of the surplus (e.g. their products are substitutes of each other). This result aligns with our natural intuition that player $P$ has a better bargaining position in this case, than if only coalitions with most of the fringe firms could obtain high values.

\begin{figure}
    \centering
    \caption{Distribution of value between player $P$ and the fringe}
    \label{fig:one_sided}
    \begin{tikzpicture}
        \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick={0}, extra y ticks={1},  extra y tick style={yticklabel={$f(1)$}}]
            \addplot[name path=f, blue,ultra thick] {x^0.5};
            \node[anchor=north west] at (axis cs: .8, .8^0.5) {$f$};
            \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
            \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);

            \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
            \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];

            \node[anchor=north west] at (axis cs: .1, .9) {Fringe ($A$)};
            \node[anchor=south east] at (axis cs: .9, .1) {Player $P$};
        \end{axis}
    \end{tikzpicture}
\end{figure}

\begin{corollary}
    $\varphi_P^\infty < f(1)$ and $\varphi_A^\infty > 0$ for any $f$ that is not constant.
\end{corollary}
\begin{proof}
    If $f$ is monotone increasing, then $f(0) \leq \int_0^1 f(t) \dt \leq f(1)$. The inequalities become strict if $f$ is not constant on the whole interval.
\end{proof}

This proposition gives credence to using asymptotics to model situations with a finite, albeit large number of players. Even though the individual share of each $A_i$ vanishes as their number goes to infinity, their total value converges to a positive value.

\subsection{Weighted Shapley-values}

Imagine a general non-cooperative game $(N, v)$ with $N = \{1, \dots, n\}$. Assume that, in addition to the value function $v : 2^n \to \mathbb{R}$, the game is also endowed with a weight system $\lambda \in \mathbb{R}^n$. These weights can be thought of as measures of innate bargaining power \parencite{shapley1953additive}, not reflected in the value function. Further support for this interpretation can be found in \textcite{hart1996bargaining}, demonstrating that in a certain alternating offer bargaining game, weights are related to the probability of each player making the offer.\footnote{For example, only one player having a positive value corresponds to them making take it or leave it offers.}

For my purposes, it is sufficient to deal with the case of simple weights. I.e., assume that there is at most one player with zero weight. I make use of the fact that weighted Shapley values can be calculated by weighting the permutations by the probabilities arising from the following sequential entry procedure \parencite{kalai1987weighted}. Start adding players from the end. The probability of player $i$ being the last amongst the set of remaining players $R$ is $\lambda_i / \sum_{j \in R} \lambda_j$. This yields a well-defined probability for each permutation of players.

Getting back to the game at hand, let the weights of players of type $A$ and $P$ be 1 and $\lambda$, respectively. Let $X_n$ be a random variable representing the number of players before $P$ when players are ordered according to the above procedure. Then, the probability of player $P$ having at most $k$ players of type $A$ before themselves is simply
\begin{align*}
    \Pr{X_n \leq k} = \prod_{j=k+1}^n \frac{j}{j + \lambda} .
\end{align*}
The following lemma establishes the continuous analogue of this statement.
\begin{lemma}
     As $n \to \infty$, $X_n \xrightarrow[]{\mathrm{d}} X$ with the cdf $G_X(t) = \lambda^t$. Consequently, the corresponding probability density function is $g(t) = \lambda t^{\lambda - 1}$.
\end{lemma}
\begin{proof} \textcolor{red}{(Might have to fix sum indices)} \\
    The probability of $P$ having at most fraction $t$ of the other players before itself is
    \begin{align*}
        \Pr(X_n \leq nt) &= \Pr(X_n \leq nt ) \\
        &= \prod_{j = nt + 1}^n \frac{j}{j + \lambda} \\
        &= \exp \Bigg( \underbrace{\sum_{j = nt + 1}^n \log(j) - \log(j+\lambda)}_{\equiv S_n} \Bigg).
    \end{align*}
    Taking limits,
    \begin{align*}
        \lim_{n \to \infty} S_n &= \lim_{n \to \infty} \sum_{j = nt + 1}^n \log(j) - \log(j+\lambda) \\
        &= \lim_{n \to \infty} \sum_{i = 1}^{n - nt} \log(nt + i) - \log(nt + i + \lambda) \\
        &= \lim_{n \to \infty} \frac{1}{n - nt} \sum_{i = 1}^{n - nt} \frac{\log \left( t + \frac{i}{n - nt} \right) - \log \left( t + \frac{i}{n - nt} + \frac{\lambda}{n - nt} \right)}{1 / (n - nt)}
    \end{align*}
    Let
    \begin{align*}
        \Delta_n(s) = \frac{\log \left( s \right) - \log \left( s + \frac{\lambda}{n - nt} \right)}{1 / (n - nt)}
    \end{align*}
    By lemma \ref{lemma:log_convergence}, 
    \begin{align*}
        \Delta_n \xrightarrow[]{\mathrm{u}} \lambda \frac{\mathrm{d}}{\mathrm{d}s}log(s) = -\frac{\lambda}{s}
    \end{align*}
    on the compact interval $[t, 1]$ for any $t > 0$ ($\xrightarrow[]{\mathrm{u}}$ denotes uniform convergence).

    Then, by lemma \ref{lemma:integral_convergence}, we have that
    \begin{align*}
        \lim_{n \to \infty} S_n &= \lim_{n \to \infty} \frac{1}{n-nt} \sum_{i=1}^{n-nt} \Delta_n \left( t + \frac{i}{n - nt} \right) \\
        &= \int_t^1 (\lim_{n \to \infty} \Delta_n)(s) \ds \\
        &= \int_t^1 \lim_{n \to \infty} -\frac{\lambda}{s} \ds \\
        &= \lambda \log{t}
    \end{align*}

    Substituting $\lim_{n \to \infty} S_n$ into the original equation yields
    \begin{align*}
        \lim \Pr \left( \frac{X_n}{n} \leq t \right) &= \exp \Bigg( \lim_{n \to \infty} \sum_{j = nt + 1}^n \log(j) - \log(j+\lambda) \Bigg) \\
        &= \exp(\lambda \log(t)) \\
        &= t^\lambda.
    \end{align*}

    For $t=0$, simply observe that
    \begin{align*}
        \lim_{n \to \infty} \prod_{j = 1}^n \frac{j}{j + \lambda} = 0 = 0^\lambda.
    \end{align*}
\end{proof}

Finally, the weighted Shapley-value of player $i$ can be expressed as the expected marginal contribution of that player where the permutations are weighted according to the previous distribution.
\begin{proposition}
    \label{prop:one_sided_weighted}
    Let $f(t)$ be continuous on $[0, 1]$. Then
    \begin{align*}
        \varphi_P(\lambda, \infty) = \int_0^1 g(t) f(t) \dt
    \end{align*}
    where $g(t) = \lambda t^{\lambda - 1}$.
\end{proposition}
\begin{proof}
    The weighted value of player $P$ is its expected contribution across all permutations, with each permutation weighted by its probability of occurring.
    \begin{align*}
        \varphi_P^{n, \lambda} = \sum_R \Pr(R) [v(\mathcal{P}_P^R \cup \{i\}) - v(\mathcal{P}_P^R)]
    \end{align*}
    As before, using the fact that fringe players are identical, this can be rephrased as
    \begin{align*}
        \varphi_P^{n, \lambda} &= \sum_{k=0}^n \Pr(R) f(k/n) \\
        &= \E[f(X_n / n)]
    \end{align*}
    where $X_n$ is defined as above. $f$ is continuous, and therefore bounded on the compact set $[0, 1]$. As a consequence, $\frac{X_n}{n} \xrightarrow[]{\mathrm{d}} X$ implies $\E[f(X_n / n)] \to \E[f(X)]$, which in turn gives
    \begin{align*}
        \lim_{n \to \infty} \varphi_P^{n, \lambda} &= \lim_{n \to \infty} \E[f(X_n / n)] \\
        &= \E[f(X)] \\
        &= \int_0^1 f(t) \mathrm{d}G(t) \\
        &= \int_0^1 g(t)f(t) \dt
    \end{align*}
    where $G(t)$ and $g(t)$ are the cdf and pdf of X, respectively.
\end{proof}

\begin{corollary}
    $\varphi_P(\lambda, \infty)$ is increasing in $\lambda$ unless $f$ is constant.
\end{corollary}
\begin{proof}
    Let $X$ and $X'$ be random variables with cdfs $G_X = t^\lambda$ and $G_{X'}t^{\lambda'}$, respectively. For any $\lambda < \lambda'$, $t^\lambda > t^{\lambda'} \forall t \in [0, 1]$, meaning that $X'$ first-order stochastically dominates $X'$. As a result, for any monotonically increasing $f$,
    \begin{align*}
        \int_0^1 g_X(t)f(t) \dt = \E[f(X)] \leq \E[f(X')] = \int_0^1 g_{X'}(t)f(t)
    \end{align*}
    with strict inequality unless $f$ is constant almost everywhere. As $f$ is continuous, the latter is equivalent to $f$ being constant on the whole $[0, 1]$ interval.
\end{proof}

The following proposition supports the interpretation of weights as bargaining power, as a higher weight corresponds to a higher Shapley-value in this game.\footnote{This would not necessarily have to be the case, as demonstrated by \textcite{owen1968communications}.}

\begin{corollary}
    If the weight of player $P$ goes to infinity (zero), its weighted Shapley value converges to $f(1)$ ($f(0)$).
\end{corollary}
\begin{proof}
    As $\lambda \to 0$, $X$ converges to the degenerate random variable $X_0$ for which $\Pr(X_0 = 0) = 1$. As a consequence, the expected value of $f(X)$ converges to $\E[f(X_0)] = f(0)$. $\lim_{\lambda \to \infty} \varphi^{\infty, \lambda}_P = f(1)$ can be shown along the same lines.
\end{proof}

\subsection{Multiple platforms}

Imagine that there are $m$ players of type $P$ which are perfect substitutes of each other. That is, the fringe players still need a platform to achieve any value, but it does not matter which or how many platforms are available for them. Specifically, the value function for coalition $S$ is the following:
\begin{align*}
    v(S) = \begin{cases}
        0                              & \text{if } n_P(S) = 0 \\
        f\left(\frac{n_A(S)}{n}\right) & \text{otherwise}.
    \end{cases}
\end{align*}

% \begin{proposition}
%     The game is monotone, supermodular and convex if $f$ is increasing and convex
% \end{proposition}
\textcolor{red}{Note: I have to think more about how to describe this situation in the language of cooperative game theory. The issue is that, for example, the value of $\{P_1, A_1\}$ depends on whether $\{P_2, A_2\}$ also decides to form a coalition and enter the market.}

\begin{proposition}
    The limit of the Shapley-value (as $n \to \infty$) of each player of type $P$ is
    \begin{align*}
        \varphi_{P_i}^{\infty, m} = \int_0^1 (1-t) ^ {m-1} f(t) \dt .
    \end{align*}
\end{proposition}
\begin{proof}
    \label{prop:one_sided_multiple}
    First, let us rewrite the expected marginal contribution of player $P_i$ in the following way:
    \begin{align*}
        \varphi_{P_i}^{n, m} &= \frac{1}{(n+m)!} \sum_R v(\mathcal{P}_{P_i}^R \cup \{i\}) - v(\mathcal{P}_{P_i}^R) \\
        &= \frac{1}{(n+m)!} \left[ \sum_{\{R | n_P(\mathcal{P}_{P_i}^R = 0)\}} \left[v(\mathcal{P}_{P_i}^R \cup \{i\}) - v(\mathcal{P}_{P_i}^R)\right] + \sum_{\{R | n_P(\mathcal{P}_{P_i}^R > 0)\}} \left[v(\mathcal{P}_{P_i}^R \cup \{i\}) - v(\mathcal{P}_{P_i}^R)\right] \right]
    \end{align*}
    Next, make use of the fact that the marginal contribution of a platform is zero if another platform is already present, and only depends on the number of fringe firms otherwise.
    \begin{align*}
        \varphi_{P_i}^{n, m} &= \frac{1}{(n+m)!} \sum_{\{R | n_P(\mathcal{P}_{P_i}^R = 0)\}} f (\mathcal{P}_{A}^R / n) \\
        &= \frac{1}{(n+m)!} \sum_{k=0}^n |\{R | n_A(\mathcal{P}^R_{P_i} = k) \text{ and } n_P(\mathcal{P}^R_{P_i} = 0)\}| f(k/n)
    \end{align*}
    Finally, notice that, while the permutations with $k$ fringe agents before $P_i$ does not depend on $k$, amongst those, the number of permutations with no platform before $P_i$ does depend on it. In particular,
    \begin{align*}
        |\{R | n_A(\mathcal{P}^R_{P_i} = k) \text{ and } n_P(\mathcal{P}^R_{P_i} = 0)\}| &= \frac{n!(n+m-k-1)!}{(n-k)!}
    \end{align*}
    and
    \begin{align*}
        \varphi_{P_i}^{n, m} &= \sum_{k=0}^n \frac{n!(n+m-k-1)!}{(n+m)!(n-k)!} f(k/n) \\
        &= \sum_{k=0}^n \frac{(n-k+1)(n-k+2) \dots (n-k+m-1)}{(n+1)(n+2) \dots (n+m)} f(k/n) \\
        &= \frac{1}{n+1}\sum_{k=0}^n \underbrace{\frac{(n(1-k/n)+1)(n(1-k/n)+2) \dots (n(1-k/n)+m-1)}{(n+2) \dots (n+m)} f(k/n)}_{S_n}
    \end{align*}
    For any $t = k/n \in [0, 1]$, 
    \begin{align*}
        S_n(t) \to (1-t)^{m-1}f(t) \equiv S(t).
    \end{align*}
    Furthermore, it is simple to verify that this convergence is uniform, and that $S_n$ and $S$ are all continuous functions. By Dini's theorem, the former properties imply that $S_n \xrightarrow[]{\mathrm{u}} S$ uniformly on $[0, 1]$.

    The conclusion of the proof is similar to that of proposition \ref{prop:one_sided}:
    \begin{align*}
        \lim_{n \to \infty} \varphi_{P_i}^{n, m} &= \lim_{n \to \infty} \underbrace{\frac{n}{n+1}}_{\to 1} \sum_{k=0}^{n-1} S_k(k/n) + \underbrace{\frac{1}{1+n}S(1)}_{\to 0} \\
        &= \lim_{n \to \infty} \sum_{k=0}^{n-1} S_k(k/n) \\
        &= \int_0^1 (1-t)^{m-1} f(t) \dt
    \end{align*}
    with the last equality supported by lemma \ref{lemma:integral_convergence}.
\end{proof}

As with proposition \ref{prop:one_sided}, this result also has a probabilistic interpretation, and could have been obtained directly from the oceanic game. Let the location of the $m$ atoms be $t_1, \dots, t_m$, distributed independently and uniformly on the unit cube. The expected marginal contribution of $t_i$ is only positive whenever it is the first amongst the major players. That is, for any $t_i$, the probability if $P_i$ being the first is related to the cdf of the first order statistic from $n-1$ independent uniform distributions: $1 - (1-t)^{m-1}$.

\begin{corollary}
    The per-unit Shapley-value of the fringe is
    \begin{align*}
        \varphi_A(k, \infty) = 1 - m\int_0^1 (1-t) ^ {m-1} f(t) \dt = \int_0^1 [1 - (1-t)^m] f'(t) \dt .
    \end{align*}
\end{corollary}
\begin{proof}
    The allocation is efficient for all $n \in \mathbb{N}$, therefore efficient in the limit, as well. The second equality can be obtained by integration by parts.
\end{proof}

The following corollary again demonstrates that the predicted outcomes confirm intuitions. As the major players become more and more substitutable, the portion of the surplus they can capture decreases, and the aggregated value of the fringe increases.

\begin{corollary}
    Let $\varphi_{P}^{\infty, m} = m\varphi_{P_i}^{\infty, m}$ denote the aggregated values of players of type $P$. $\varphi_{P}^{\infty, m}$ is decreasing in $m$ and $\varphi_{A}^{\infty, m}$ is increasing in $m$ unless $f$ is constant.
\end{corollary}
\begin{proof} \textcolor{red}{(Assuming $f$ is continuously differentiable -- will have to relax this)}
    $f'(t)$ is non-negative, so $[1 - (1-t)^m] f'(t)$ is increasing in $m$ $\forall t \in [0, 1]$. As a consequence, $\varphi_A^{n, \infty}$ is also increasing in $m$ if $f'(t)$ is positive on some interval or, $f(t)$ is not constant. Conversely, $\varphi_{P}^{\infty, m} = 1 - \varphi_{A}^{\infty, m}$ is decreasing in $m$.
\end{proof}

\section{Two-sided case}

\textcolor{red}{\large No proofs or changes in this section. The next new results are in the appendix.}

Now imagine that, in addition to player $P$, there are two types of smaller players: $\{A_1, \dots, A_n\}$ and $\{B_1, \dots, B_n\}$. As before, $P$ is necessary for any coalition to have a positive value, and the small players are identical within their groups. I.e., the set of players and the characteristic function of the game are the following: $N = \{P, A_1, \dots, A_n, B_1, \dots, B_n\}$ and
\begin{align*}
    v(S) = \begin{cases}
        0                                                & \text{if } P \notin S \\
        f\left(\frac{n_A(S)}{n}, \frac{n_A(S)}{n}\right) & \text{otherwise}.
    \end{cases}
\end{align*}

\begin{proposition}
    The game $(N, v)$ is monotone and superadditive if and only if $f$ is increasing in both arguments.
\end{proposition}

Furthermore, the limits of the Shapley-values (as $n \to \infty$) of the various players turn out to be analytically tractable and nicely interpretable.

\begin{proposition}
    Let $f(a, b)$ be continuous everywhere on $[0, 1]^2$. Then,
    \begin{align*}
        \varphi_P^\infty & = \int_0^1 f(t, t) \dt                                 \\
        \varphi_A^\infty & = \int_0^1 t \frac{\partial f(t, t)}{\partial a} \dt   \\
        \varphi_B^\infty & = \int_0^1 t \frac{\partial f(t, t)}{\partial b} \dt .
    \end{align*}
\end{proposition}

That is, the value of the grand coalition can be decomposed into the Shapley-values of its members signifying their expected marginal contributions in the following way:
\begin{align*}
    f(1, 1) = \underbrace{\int_0^1 f(t, t) \dt}_{\text{ player } P} + \underbrace{\int_0^1 t \frac{\partial f(t, t)}{\partial a} \dt}_{\text{players } A} + \underbrace{\int_0^1 t \frac{\partial f(t, t)}{\partial b} \dt}_{\text{players } B}
\end{align*}

\subsection{Multiple platforms}

Again, assume that there are $k$ players of type $P$ which are perfect substitutes of each other.

\textbf{Note:} As in the previous case, I have to think more about how interpret the value function here. For now, let me just show the limit of the limits of the Shapley-values assuming that
\begin{align*}
    v(S) = \begin{cases}
        0                                                & \text{if } P_i \notin S \; \forall \, i = 1, \dots, k \\
        f\left(\frac{n_A(S)}{n}, \frac{n_B(S)}{n}\right) & \text{otherwise}.
    \end{cases}
\end{align*}

\begin{proposition}
    The unit Shapley-values of the various types of players are
    \begin{align*}
        \varphi_{P_i}(k, \infty) & = \int_0^1 (1-t)^{k-1} f(t, t) \dt                                 \\
        \varphi_A(k, \infty)     & = \int_0^1 [1 - (1-t)^k] \frac{\partial f(t, t)}{\partial a} \dt   \\
        \varphi_B(k, \infty)     & = \int_0^1 [1 - (1-t)^k] \frac{\partial f(t, t)}{\partial b} \dt .
    \end{align*}
\end{proposition}

\begin{corollary}
    Let $\varphi_{P}(k, \infty) = k\varphi_{P_i}(k, \infty)$ denote the aggregated Shapley-values of players of type $P$. Then $\varphi_{P}(k, \infty)$ is decreasing in $k$ and $\varphi_{A}(k, \infty)$, $\varphi_{B}(k, \infty)$ is increasing in $k$ unless $f$ is constant.
\end{corollary}

\appendix

\section{Miscellaneous lemmas}

\begin{lemma}
    \label{lemma:log_convergence}
    Let 
    \begin{align*}
        \Delta_n(s) &= \frac{\log(s + 1/n) - \log(\lambda)}{n}, \\
        \Delta(s) &= \frac{1}{s}.
    \end{align*}
    Then $\Delta_n \xrightarrow[]{\mathrm{u}} \Delta$ uniformly on $[t, 1]$ for any $t > 0, \lambda > 0$.
\end{lemma}
\begin{proof}
    First, note that $\Delta_n$ and $\Delta$ are all continuous functions. Then, following the standard proof for $\frac{\mathrm{d}}{\mathrm{d}s}log(s) = \frac{1}{s}$ rewrite $\Delta_n(s)$ as
    \begin{align*}
        \Delta_n(s) &= \frac{\log(s + 1/n) - \log(\lambda)}{n} \\
        &= \log \left( 1 + \frac{1}{sn} \right) ^ n .
    \end{align*}
    It is well known that $\left( 1 + \frac{1}{sn} \right) ^ n$ is monotone increasing in $n$ and converges to $\exp (1/s)$. Therefore, the pointwise convergence of $\Delta_n(s) \to \Delta(s)$ is also monotone.

    Finally, by Dini's theorem, the monotone pointwise convergence of a sequence of continuous functions to a continuous function on a compact set implies uniform convergence on that set.
\end{proof}

\begin{lemma}
    \label{lemma:integral_convergence}
    Let $f_n, f: [a, b] -> \mathbb{R}$ be Riemann-integrable functions with $f_n \xrightarrow[]{\mathrm{u}} f$ uniformly. Then,
    \begin{align*}
        \lim_{n \to \infty} \frac{b-a}{n} \sum_{k=1}^n f_n \left( a + \frac{b-a}{n} \right) = \int_0^1 f(t) \dt.
    \end{align*}
\end{lemma}
\begin{proof}
    \begin{align*}
        &\lim_{n \to \infty} \frac{b-a}{n} \sum_{k=1}^n f_n \left( a + \frac{b-a}{n} \right) \\
        &= \lim_{n \to \infty} \frac{b-a}{n} \left[ \sum_{k=1}^n f \left( a + \frac{b-a}{n} \right) + \sum_{k=1}^n \left( f_n \left( a + \frac{b-a}{n} \right) - f \left( a + \frac{b-a}{n} \right) \right) \right] \\
        &= \int_a^b f(t) \dt + \lim_{n \to \infty} \frac{b-a}{n}\sum_{k=1}^n \left( f_n \left( a + \frac{b-a}{n} \right) - f \left( a + \frac{b-a}{n} \right) \right) \\
        &\leq \int_a^b f(t) \dt + \lim_{n \to \infty} \frac{b-a}{n}\sum_{k=1}^n \left| f_n \left( a + \frac{b-a}{n} \right) - f \left( a + \frac{b-a}{n} \right) \right| \\
        &\leq \int_a^b f(t) \dt + \lim_{n \to \infty} \frac{b-a}{n}\sum_{k=1}^n \sup_{t \in [a, b]} \left| f_n(t) - f(t) \right| \\
        &= \int_a^b f(t) \dt + (b-a) \underbrace{\lim_{n \to \infty} \sup_{t \in [a, b]} \left| f_n(t) - f(t) \right|}_{=0 \text{ due to uniform convergence}} \\
        &= \int_a^b f(t) \dt
    \end{align*}
\end{proof}

\section{References}

\printbibliography

\end{document}

### 2022-07-22 src/paper/paper.tex
Add first version of the application section

@@
 
+\section{Application}
+
+Consider a market with a continuum of firms $a(t)$ ($t \in [0, 1]$), continuum of identical consumers and one platform $P$.
+The former two can only interact through the platform.
+Assume a measure $N \in (0, 1)$ of the firms are present on the platform.
+Then, consumers have the following quasilinear/CES utility function over money ($m$) and those firms' products:
+\begin{align*}
+    u(m, x(\cdot)) = m + \alpha \left[ \int_0^N x(t)^\rho \dt \right] ^ \frac{\gamma}{\rho}.
+\end{align*}
+
+\subsection{Timing of the game}
+
+The game proceeds as follows.
+In the first stage, firms decide whether to create a product or not.
+Doing this entails a fixed cost of $C$.
+Those firms that choose not to invest obtain a payoff of 0 and are excluded from the remainder of the game.
+Next, the firms that made an investment can decide to join the platform at the cost of some entry fee $F^f$.
+(Note that the entry fee can be negative, in which case it is a subsidy from the platform to the firm.) After that, consumers decide to join or not at an entry fee of $F^c$.
+Finally, firms post their product prices, and produce and sell to consumers at marginal cost $c$.
+
+The model heavily depends on how the entry fees are determined.
+The most widespread assumption in the literature is that they are unilaterally decided by the platform, and are essentially take it or leave it offers for the other players.
+The issue with this approach is that it generally leads to extreme conclusions.
+\textcolor{red}{(TODO: elaborate on this)} As opposed to this, in this paper I assume that firm entry fees are a result of some bargaining process between the firms and the platform, leading to an allocation in which the final profits of each player correspond to their Shapley values.
+User entry fees, on the other hand, are unilaterally decided by the platforms.
+
+The value (characteristic function) of a coalition of the platform and any set of firms is defined as follows.
+Assume that the firms in the coalition enter the platform, while the others do not.
+Then, taking that decision as fixed, platforms set a profit-maximizing entry price for the consumers and firms also set own-profit-maximizing prices.
+That is, there is no collusion between the coalition members in terms of pricing.
+All they contract on are entry fees and decisions.
+
+\subsection{Solution of the game}
+
+Let us start from the last stage, and assume that firms and consumers have already made their entry decisions: a measure $N$ of firms and measure $M$ of consumers are on the platform.
+Furthermore, firms have already set their prices $p(t)$, $t \in [0, N]$.
+Then consumers face the following utility maximization problem:
+\begin{align*}
+    &u(m, x(\cdot)) = m + \alpha \left[ \int_0^N x(t)^\rho \dt \right] ^ \frac{\gamma}{\rho} \\
+    &\text{s.t. } m + \int_0^N p(t) x(t) \dt = I.
+\end{align*}
+By following the usual solution method for CES utility functions, we obtain the following demand function:
+\begin{align*}
+    x(t) = M K p(t) ^ \frac{1}{\rho-1}
+\end{align*}
+where
+\begin{align*}
+    K = (\alpha \gamma) ^ {\frac{1}{1 - \rho} + \gamma - \rho} \left[ \int_0^N p(t) ^ \frac{\rho}{\rho - 1} \dt \right] ^ \frac{\rho - \gamma}{\rho (\gamma - 1)}.
+\end{align*}
+It implies that, as with the usual CES utility function, the optimal pricing strategy is independent on others' prices or the number of consumers, and is simply a constant markup over the marginal cost:
+\begin{align*}
+    p = \frac{c}{\rho}.
+\end{align*}
+The total profit each firm makes is then $\pi(N)$, while the total profit of all firms is $\Pi(n) = N\pi(N)$.
+
+Consumers utility is from buying the products is then $u(N)$, which is increasing in $N$.
+As all consumers are identical, the platform optimally sets a user entry price of $F^u = u(N)$, so that it extracts all surplus from the consumers.
+Therefore, the total profits that a coalition of firms and the platform can obtain (assuming they individually maximize profits after the entry decisions are made) is
+\begin{align*}
+    v(N) = \Pi(N) + U(N).
+\end{align*}
+$v(N)$ is increasing in $N$, and its shape depends on the parameters of the utility function of the consumers and the marginal cost of the producers.
+
+\subsection{Deciding firm entry fees}
+
+Let us look at the second stage of the game: firms have made their investment decisions, and are now negotiating with the platform over the entry price.
+Let us assume that $T \in [0, 1]$ measure of firms have made an investment.
+$C$ is a fixed cost, therefore does not influence the rest of the game.
+Remember that entry fees will be set such that the final profits correspond to Shapley values.
+Let us denote these values by $\varphi_f(v, T)$ and $\varphi_P(v, T)$ for firms and the platform, respectively.
+As shown in the main results,
+\begin{align*}
+    \varphi_P(v, T) &= \int_0^1 v(tT) \dt \\
+    \varphi_f(v, T) &= v(T) - \int_0^1 v(tT) \dt.
+\end{align*}
+In order to achieve these values, the firm entry fee will be set to $F^f = \varphi_P(v, T) - U(T)$.
+
+Finally, looking at the first stage, firms will make the initial investment if and only if $\varphi_f(v, T) / T \geq C$. Therefore, the equilibrium measure of entrants is given by
+\begin{align*}
+    v(T) - \int_0^1 v(tT) = CT.
+\end{align*}
+
 \appendix

### 2022-08-02 src/paper/paper.tex
Minor wording changes

@@
 A common feature of the aforementioned papers is that they involve models with a finite number of agents.
-However, as is often the case in economics, the infinite-player approximations might turn out to be more tractable while retaining the main conclusions of the finite models from which they arise.
+However, as is often the case in economics, infinite-player approximations might turn out to be more tractable while retaining the main conclusions of the finite models from which they arise.
 Indeed, in the case of cooperative games with non-atomic players, the axiomatic and asymptotic approaches both give rise to the same value\footnote{On the appropriate subspace of non-atomic games.} \parencite{aumann2015values}, which is furthermore analytically simple and readily interpretable.
@@
 Furthermore, the results are simple enough that these games can be embedded into more complex models, for example, as the second stage of a sequential game \parencite[as in e.g.][]{montez2007downstream}.
-Just as importantly, the outcomes are in line with one's intuitive expectations of bargaining outcomes in such situations.
+Furthermore, the outcomes are in line with one's intuitive expectations of bargaining outcomes in such situations.
 
@@
 Assume that (1) no coalition of players can achieve a positive value without the participation of $P$ and (2) players $A_i$ are identical.
-Let $n_T(S)$ denote the number of players of type $T$ in coalition $S$.
+Let $n_T(S)$ denote the number of players of type $T \in \{P, A\}$ in coalition $S$.
 Then, the value $S \subset N$ can achieve is the following:
@@
     Monotonicity is evident.
-For superadditivity, note that for any $S, T$ such that $S \cap T = \emptyset$, $P \notin S$ or $P \notin T$.
-WLOG assume it is the latter, therefore $v(T) = 0$.
-As a result, $v(S) + v(T) = v(S) \leq v(S \cup T)$ holds if and only if $(N, v)$ is monotone.
+For superadditivity, note that for any coalitions $S_1, s_2$ such that $S_1 \cap s_2 = \emptyset$, $P \notin S_1$ or $P \notin s_2$.
+WLOG assume it is the latter, therefore $v(S_2) = 0$.
+As a result, $v(S_1) + v(S_2) = v(S_1) \leq v(S_1 \cup S_2)$ holds if and only if $(N, v)$ is monotone.
 \end{proof}
@@
 \begin{proof}
-    For a permutation of players $R$, let us denote the players preceding $i$ by $\mathcal{P}_i^R$.
+    Let $R$ denote a permutation of the set of players ($N$).
+Additionally, let us denote the players preceding $i$ by $\mathcal{P}_i^R$.
 The value of player $P$ is their expected marginal contribution averaged over all permutations of $N$:
@@
     \end{align*}
-    Finally, the set of permutations in which the number of players preceding $P$ is $k$ is independent of $n$, i.e.
+    Finally, the set of permutations in which $k$ number of players precede $P$ is independent of $n$, i.e.
     \begin{align*}
@@
 \begin{corollary}
-    The aggregated Shapley-value of the fringe (alternatively, the per-unit Shapley-value of the fringe) is
+    The aggregated Shapley-value of the fringe is
     \begin{align*}
@@
 
-It is already apparent from Figure \ref{fig:one_sided} that (for fixed $f(0)$ and $f(1)$) player $P$ gets a larger share of the surplus when $f(t)$ is large even for small values of $t$.
+It is already apparent from Figure \ref{fig:one_sided} that (for fixed $f(0)$ and $f(1)$) player $P$ gets a larger share of the surplus when $f(t)$ is larger for every $t$.
 It corresponds to the case when only a small fraction of the fringe is needed to create most of the surplus (e.g.
@@
 
-This proposition gives credence to using asymptotics to model situations with a finite, albeit large number of players.
-Even though the individual share of each $A_i$ vanishes as their number goes to infinity, their total value converges to a positive value.
+This proposition implies that, even though the individual share of each $A_i$ vanishes as their number goes to infinity, their total value converges to a positive value.
 
@@
 I make use of the fact that weighted Shapley values can be calculated by weighting the permutations by the probabilities arising from the following sequential entry procedure \parencite{kalai1987weighted}.
-Start adding players from the end.
-The probability of player $i$ being the last amongst the set of remaining players $R$ is $\lambda_i / \sum_{j \in R} \lambda_j$.
+Start with the set of all players.
+Let the probability of player $i$ being the last amongst the set of remaining players $R$ be $\lambda_i / \sum_{j \in R} \lambda_j$.
 This yields a well-defined probability for each permutation of players.
+Continue until all players are exhausted.
 
@@
 
-    For $t=0$, simply observe that
+    For $t=0$, simply observe that \textcolor{red}{Have to elaborate on this}
     \begin{align*}

### 2022-08-02 src/paper/paper.tex
Rearrange paper (proofs at the end)

@@
 \begin{proposition}
+    \label{prop:monotone}
     The game $(N, v)$ is monotone and superadditive if and only if $f$ is increasing and $f(0) \geq 0$. % It is supermodular if and only if $f$ is convex.
 \end{proposition}
-\begin{proof}
-    Monotonicity is evident.
-For superadditivity, note that for any coalitions $S_1, s_2$ such that $S_1 \cap s_2 = \emptyset$, $P \notin S_1$ or $P \notin s_2$.
-WLOG assume it is the latter, therefore $v(S_2) = 0$.
-As a result, $v(S_1) + v(S_2) = v(S_1) \leq v(S_1 \cup S_2)$ holds if and only if $(N, v)$ is monotone.
-\end{proof}
+
 In the following, let us assume that the assumptions required for monotonicity are always satisfied.
@@
 \end{proposition}
-\begin{proof}
-    Let $R$ denote a permutation of the set of players ($N$).
-Additionally, let us denote the players preceding $i$ by $\mathcal{P}_i^R$.
-The value of player $P$ is their expected marginal contribution averaged over all permutations of $N$:
-    \begin{align*}
-        \varphi_P^n = \frac{1}{(n+1)!} \sum_R v(\mathcal{P}_P^R \cup \{i\}) - v(\mathcal{P}_P^R)
-    \end{align*}
-    First, note that $v(\mathcal{P}_P^R) = 0$ for any permutation, as no coalition can achieve a positive value without player $P$.
-Furthermore, using the fact that all agents of type $A$ are identical implies that $v(\mathcal{P}_P^R \cup \{i\})$ only depends on the number of agents in the coalition.
-More precisely,
-    \begin{align*}
-        v(\mathcal{P}_P^R \cup \{i\}) = f(n_A(\mathcal{P}_P^R \cup \{i\}) / n) = f(|\mathcal{P}_P^R| / n).
-    \end{align*}
-    Finally, the set of permutations in which $k$ number of players precede $P$ is independent of $n$, i.e.
-    \begin{align*}
-        \{R \mid |\mathcal{P}_P^R| = k\} = n! \quad \forall\, k.
-    \end{align*}
-    Putting all the above together, the value of player $P$ can be expressed as
-    \begin{align*}
-        \varphi_P^n &= \frac{1}{(n+1)!} \sum_{k=0}^n n! f(k / n) \\
-        &= \frac{1}{n+1} \sum_{k=0}^n f(k / n) \\
-        &= \frac{n}{n+1} \underbrace{\frac{1}{n} \sum_{k=0}^{n-1} f(k / n)}_{=S_n} + \frac{1}{n+1} f(1).
-    \end{align*}
-    $S_n$ are just the left Riemann-sums of function $f$ on the interval $[0, 1]$. Therefore, if $f$ is continuous (and thus Riemann-integrable), then $S_n \to \int_0^1 f(t)$, and thus
-    \begin{align*}
-        \lim_{n \to \infty} \varphi_P^n &= \lim_{n \to \infty} \frac{1}{n+1} \sum_{k=1}^n f(k / n) \\
-        &= \lim_{n \to \infty}\underbrace{\frac{n}{n+1}}_{\to 1} \frac{1}{n} \sum_{k=0}^{n-1} f(k / n) + \underbrace{\frac{1}{n+1} f(1)}_{\to 0} \\
-        &= \int_0^1 f(t) \dt .
-    \end{align*}
-\end{proof}
 
@@
 \begin{corollary}
+    \label{cor:fringe_value}
     The aggregated Shapley-value of the fringe is
@@
 \end{corollary}
-\begin{proof}
-    The first equality comes from the efficiency of the Shapley-value. The values of all players sum up to $f(1)$ for all $n \in \mathbb{N}$, therefore
-    \begin{align*}
-        \lim_{n \to \infty} \sum_{i=1}^n \varphi_{A_i}^n = \lim_{n \to \infty} (1 - \varphi_P^n ) = 1 - \int_0^1 f(t).
-    \end{align*}
-    The second can be obtained by integration by parts:
-    \begin{align*}
-        \int_0^1 t f'(t) \dt = tf(t) \mid_0^1 - \int_0^1 f(t) \dt = f(1) - \int_0^1 f(t) \dt
-    \end{align*}
-\end{proof}
 
@@
 \begin{corollary}
+    \label{cor:fringe_value_2}
     $\varphi_P^\infty < f(1)$ and $\varphi_A^\infty > 0$ for any $f$ that is not constant.
 \end{corollary}
-\begin{proof}
-    If $f$ is monotone increasing, then $f(0) \leq \int_0^1 f(t) \dt \leq f(1)$. The inequalities become strict if $f$ is not constant on the whole interval.
-\end{proof}
 
@@
 \begin{lemma}
+    \label{lem:entry_distr}
      As $n \to \infty$, $X_n \xrightarrow[]{\mathrm{d}} X$ with the cdf $G_X(t) = \lambda^t$. Consequently, the corresponding probability density function is $g(t) = \lambda t^{\lambda - 1}$.
 \end{lemma}
-\begin{proof} \textcolor{red}{(Might have to fix sum indices)} \\
-    The probability of $P$ having at most fraction $t$ of the other players before itself is
-    \begin{align*}
-        \Pr(X_n \leq nt) &= \Pr(X_n \leq nt ) \\
-        &= \prod_{j = nt + 1}^n \frac{j}{j + \lambda} \\
-        &= \exp \Bigg( \underbrace{\sum_{j = nt + 1}^n \log(j) - \log(j+\lambda)}_{\equiv S_n} \Bigg).
-    \end{align*}
-    Taking limits,
-    \begin{align*}
-        \lim_{n \to \infty} S_n &= \lim_{n \to \infty} \sum_{j = nt + 1}^n \log(j) - \log(j+\lambda) \\
-        &= \lim_{n \to \infty} \sum_{i = 1}^{n - nt} \log(nt + i) - \log(nt + i + \lambda) \\
-        &= \lim_{n \to \infty} \frac{1}{n - nt} \sum_{i = 1}^{n - nt} \frac{\log \left( t + \frac{i}{n - nt} \right) - \log \left( t + \frac{i}{n - nt} + \frac{\lambda}{n - nt} \right)}{1 / (n - nt)}
-    \end{align*}
-    Let
-    \begin{align*}
-        \Delta_n(s) = \frac{\log \left( s \right) - \log \left( s + \frac{\lambda}{n - nt} \right)}{1 / (n - nt)}
-    \end{align*}
-    By lemma \ref{lemma:log_convergence}, 
-    \begin{align*}
-        \Delta_n \xrightarrow[]{\mathrm{u}} \lambda \frac{\mathrm{d}}{\mathrm{d}s}log(s) = -\frac{\lambda}{s}
-    \end{align*}
-    on the compact interval $[t, 1]$ for any $t > 0$ ($\xrightarrow[]{\mathrm{u}}$ denotes uniform convergence).
-
-    Then, by lemma \ref{lemma:integral_convergence}, we have that
-    \begin{align*}
-        \lim_{n \to \infty} S_n &= \lim_{n \to \infty} \frac{1}{n-nt} \sum_{i=1}^{n-nt} \Delta_n \left( t + \frac{i}{n - nt} \right) \\
-        &= \int_t^1 (\lim_{n \to \infty} \Delta_n)(s) \ds \\
-        &= \int_t^1 \lim_{n \to \infty} -\frac{\lambda}{s} \ds \\
-        &= \lambda \log{t}
-    \end{align*}
-
-    Substituting $\lim_{n \to \infty} S_n$ into the original equation yields
-    \begin{align*}
-        \lim \Pr \left( \frac{X_n}{n} \leq t \right) &= \exp \Bigg( \lim_{n \to \infty} \sum_{j = nt + 1}^n \log(j) - \log(j+\lambda) \Bigg) \\
-        &= \exp(\lambda \log(t)) \\
-        &= t^\lambda.
-    \end{align*}
-
-    For $t=0$, simply observe that \textcolor{red}{Have to elaborate on this}
-    \begin{align*}
-        \lim_{n \to \infty} \prod_{j = 1}^n \frac{j}{j + \lambda} = 0 = 0^\lambda.
-    \end{align*}
-\end{proof}
 
@@
 \end{proposition}
-\begin{proof}
-    The weighted value of player $P$ is its expected contribution across all permutations, with each permutation weighted by its probability of occurring.
-    \begin{align*}
-        \varphi_P^{n, \lambda} = \sum_R \Pr(R) [v(\mathcal{P}_P^R \cup \{i\}) - v(\mathcal{P}_P^R)]
-    \end{align*}
-    As before, using the fact that fringe players are identical, this can be rephrased as
-    \begin{align*}
-        \varphi_P^{n, \lambda} &= \sum_{k=0}^n \Pr(R) f(k/n) \\
-        &= \E[f(X_n / n)]
-    \end{align*}
-    where $X_n$ is defined as above.
-$f$ is continuous, and therefore bounded on the compact set $[0, 1]$.
-As a consequence, $\frac{X_n}{n} \xrightarrow[]{\mathrm{d}} X$ implies $\E[f(X_n / n)] \to \E[f(X)]$, which in turn gives
-    \begin{align*}
-        \lim_{n \to \infty} \varphi_P^{n, \lambda} &= \lim_{n \to \infty} \E[f(X_n / n)] \\
-        &= \E[f(X)] \\
-        &= \int_0^1 f(t) \mathrm{d}G(t) \\
-        &= \int_0^1 g(t)f(t) \dt
-    \end{align*}
-    where $G(t)$ and $g(t)$ are the cdf and pdf of X, respectively.
-\end{proof}
 
 \begin{corollary}
+    \label{cor:platform_value_weighted}
     $\varphi_P(\lambda, \infty)$ is increasing in $\lambda$ unless $f$ is constant.
 \end{corollary}
-\begin{proof}
-    Let $X$ and $X'$ be random variables with cdfs $G_X = t^\lambda$ and $G_{X'}t^{\lambda'}$, respectively.
-For any $\lambda < \lambda'$, $t^\lambda > t^{\lambda'} \forall t \in [0, 1]$, meaning that $X'$ first-order stochastically dominates $X'$.
-As a result, for any monotonically increasing $f$,
-    \begin{align*}
-        \int_0^1 g_X(t)f(t) \dt = \E[f(X)] \leq \E[f(X')] = \int_0^1 g_{X'}(t)f(t)
-    \end{align*}
-    with strict inequality unless $f$ is constant almost everywhere. As $f$ is continuous, the latter is equivalent to $f$ being constant on the whole $[0, 1]$ interval.
-\end{proof}
 
@@
 \begin{corollary}
+    \label{cor:paltform_value_weighted_2}
     If the weight of player $P$ goes to infinity (zero), its weighted Shapley value converges to $f(1)$ ($f(0)$).
 \end{corollary}
-\begin{proof}
-    As $\lambda \to 0$, $X$ converges to the degenerate random variable $X_0$ for which $\Pr(X_0 = 0) = 1$.
-As a consequence, the expected value of $f(X)$ converges to $\E[f(X_0)] = f(0)$.
-$\lim_{\lambda \to \infty} \varphi^{\infty, \lambda}_P = f(1)$ can be shown along the same lines.
-\end{proof}
 
@@
 \begin{proposition}
+    \label{prop:multiple_platforms}
     The limit of the Shapley-value (as $n \to \infty$) of each player of type $P$ is
@@
 \end{proposition}
-\begin{proof}
-    \label{prop:one_sided_multiple}
-    First, let us rewrite the expected marginal contribution of player $P_i$ in the following way:
-    \begin{align*}
-        \varphi_{P_i}^{n, m} &= \frac{1}{(n+m)!} \sum_R v(\mathcal{P}_{P_i}^R \cup \{i\}) - v(\mathcal{P}_{P_i}^R) \\
-        &= \frac{1}{(n+m)!} \left[ \sum_{\{R | n_P(\mathcal{P}_{P_i}^R = 0)\}} \left[v(\mathcal{P}_{P_i}^R \cup \{i\}) - v(\mathcal{P}_{P_i}^R)\right] + \sum_{\{R | n_P(\mathcal{P}_{P_i}^R > 0)\}} \left[v(\mathcal{P}_{P_i}^R \cup \{i\}) - v(\mathcal{P}_{P_i}^R)\right] \right]
-    \end{align*}
-    Next, make use of the fact that the marginal contribution of a platform is zero if another platform is already present, and only depends on the number of fringe firms otherwise.
-    \begin{align*}
-        \varphi_{P_i}^{n, m} &= \frac{1}{(n+m)!} \sum_{\{R | n_P(\mathcal{P}_{P_i}^R = 0)\}} f (\mathcal{P}_{A}^R / n) \\
-        &= \frac{1}{(n+m)!} \sum_{k=0}^n |\{R | n_A(\mathcal{P}^R_{P_i} = k) \text{ and } n_P(\mathcal{P}^R_{P_i} = 0)\}| f(k/n)
-    \end{align*}
-    Finally, notice that, while the permutations with $k$ fringe agents before $P_i$ does not depend on $k$, amongst those, the number of permutations with no platform before $P_i$ does depend on it.
-In particular,
-    \begin{align*}
-        |\{R | n_A(\mathcal{P}^R_{P_i} = k) \text{ and } n_P(\mathcal{P}^R_{P_i} = 0)\}| &= \frac{n!(n+m-k-1)!}{(n-k)!}
-    \end{align*}
-    and
-    \begin{align*}
-        \varphi_{P_i}^{n, m} &= \sum_{k=0}^n \frac{n!(n+m-k-1)!}{(n+m)!(n-k)!} f(k/n) \\
-        &= \sum_{k=0}^n \frac{(n-k+1)(n-k+2) \dots (n-k+m-1)}{(n+1)(n+2) \dots (n+m)} f(k/n) \\
-        &= \frac{1}{n+1}\sum_{k=0}^n \underbrace{\frac{(n(1-k/n)+1)(n(1-k/n)+2) \dots (n(1-k/n)+m-1)}{(n+2) \dots (n+m)} f(k/n)}_{S_n}
-    \end{align*}
-    For any $t = k/n \in [0, 1]$, 
-    \begin{align*}
-        S_n(t) \to (1-t)^{m-1}f(t) \equiv S(t).
-    \end{align*}
-    Furthermore, it is simple to verify that this convergence is uniform, and that $S_n$ and $S$ are all continuous functions.
-By Dini's theorem, the former properties imply that $S_n \xrightarrow[]{\mathrm{u}} S$ uniformly on $[0, 1]$.
-
-    The conclusion of the proof is similar to that of proposition \ref{prop:one_sided}:
-    \begin{align*}
-        \lim_{n \to \infty} \varphi_{P_i}^{n, m} &= \lim_{n \to \infty} \underbrace{\frac{n}{n+1}}_{\to 1} \sum_{k=0}^{n-1} S_k(k/n) + \underbrace{\frac{1}{1+n}S(1)}_{\to 0} \\
-        &= \lim_{n \to \infty} \sum_{k=0}^{n-1} S_k(k/n) \\
-        &= \int_0^1 (1-t)^{m-1} f(t) \dt
-    \end{align*}
-    with the last equality supported by lemma \ref{lemma:integral_convergence}.
-\end{proof}
 
@@
 \begin{corollary}
+    \label{cor:multiple_platforms}
     The per-unit Shapley-value of the fringe is
@@
 \end{corollary}
-\begin{proof}
-    The allocation is efficient for all $n \in \mathbb{N}$, therefore efficient in the limit, as well. The second equality can be obtained by integration by parts.
-\end{proof}
 
@@
 \begin{corollary}
+    \label{cor:multiple_platforms_2}
     Let $\varphi_{P}^{\infty, m} = m\varphi_{P_i}^{\infty, m}$ denote the aggregated values of players of type $P$.
@@
 \end{corollary}
-\begin{proof} \textcolor{red}{(Assuming $f$ is continuously differentiable -- will have to relax this)}
-    $f'(t)$ is non-negative, so $[1 - (1-t)^m] f'(t)$ is increasing in $m$ $\forall t \in [0, 1]$.
-As a consequence, $\varphi_A^{n, \infty}$ is also increasing in $m$ if $f'(t)$ is positive on some interval or, $f(t)$ is not constant.
-Conversely, $\varphi_{P}^{\infty, m} = 1 - \varphi_{A}^{\infty, m}$ is decreasing in $m$.
-\end{proof}
 
 \section{Two-sided case}
-
-\textcolor{red}{\large No proofs or changes in this section. The next new results are in the appendix.}
 
@@
 
+\section{References}
+
+\printbibliography
+
 \section{Miscellaneous lemmas}
@@
 \end{lemma}
-\begin{proof}
+\begin{proof}[Proof of Lemma \ref{lemma:log_convergence}]
     First, note that $\Delta_n$ and $\Delta$ are all continuous functions. Then, following the standard proof for $\frac{\mathrm{d}}{\mathrm{d}s}log(s) = \frac{1}{s}$ rewrite $\Delta_n(s)$ as
@@
 \end{lemma}
-\begin{proof}
+\begin{proof}[Proof of Lemma \ref{lemma:integral_convergence}]
     \begin{align*}
@@
 
-\section{References}
+\section{Proofs of propositions and lemmas from the main text}
 
-\printbibliography
+\begin{proof}[Proof of Proposition \ref{prop:monotone}]
+    Monotonicity is evident.
+For superadditivity, note that for any coalitions $S_1, s_2$ such that $S_1 \cap s_2 = \emptyset$, $P \notin S_1$ or $P \notin s_2$.
+WLOG assume it is the latter, therefore $v(S_2) = 0$.
+As a result, $v(S_1) + v(S_2) = v(S_1) \leq v(S_1 \cup S_2)$ holds if and only if $(N, v)$ is monotone.
+\end{proof}
+
+\begin{proof}[Proof of Proposition \ref{prop:one_sided}]
+    Let $R$ denote a permutation of the set of players ($N$).
+Additionally, let us denote the players preceding $i$ by $\mathcal{P}_i^R$.
+The value of player $P$ is their expected marginal contribution averaged over all permutations of $N$:
+    \begin{align*}
+        \varphi_P^n = \frac{1}{(n+1)!} \sum_R v(\mathcal{P}_P^R \cup \{i\}) - v(\mathcal{P}_P^R)
+    \end{align*}
+    First, note that $v(\mathcal{P}_P^R) = 0$ for any permutation, as no coalition can achieve a positive value without player $P$.
+Furthermore, using the fact that all agents of type $A$ are identical implies that $v(\mathcal{P}_P^R \cup \{i\})$ only depends on the number of agents in the coalition.
+More precisely,
+    \begin{align*}
+        v(\mathcal{P}_P^R \cup \{i\}) = f(n_A(\mathcal{P}_P^R \cup \{i\}) / n) = f(|\mathcal{P}_P^R| / n).
+    \end{align*}
+    Finally, the set of permutations in which $k$ number of players precede $P$ is independent of $n$, i.e.
+    \begin{align*}
+        \{R \mid |\mathcal{P}_P^R| = k\} = n! \quad \forall\, k.
+    \end{align*}
+    Putting all the above together, the value of player $P$ can be expressed as
+    \begin{align*}
+        \varphi_P^n &= \frac{1}{(n+1)!} \sum_{k=0}^n n! f(k / n) \\
+        &= \frac{1}{n+1} \sum_{k=0}^n f(k / n) \\
+        &= \frac{n}{n+1} \underbrace{\frac{1}{n} \sum_{k=0}^{n-1} f(k / n)}_{=S_n} + \frac{1}{n+1} f(1).
+    \end{align*}
+    $S_n$ are just the left Riemann-sums of function $f$ on the interval $[0, 1]$. Therefore, if $f$ is continuous (and thus Riemann-integrable), then $S_n \to \int_0^1 f(t)$, and thus
+    \begin{align*}
+        \lim_{n \to \infty} \varphi_P^n &= \lim_{n \to \infty} \frac{1}{n+1} \sum_{k=1}^n f(k / n) \\
+        &= \lim_{n \to \infty}\underbrace{\frac{n}{n+1}}_{\to 1} \frac{1}{n} \sum_{k=0}^{n-1} f(k / n) + \underbrace{\frac{1}{n+1} f(1)}_{\to 0} \\
+        &= \int_0^1 f(t) \dt .
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of Corollary \ref{cor:fringe_value}]
+    The first equality comes from the efficiency of the Shapley-value. The values of all players sum up to $f(1)$ for all $n \in \mathbb{N}$, therefore
+    \begin{align*}
+        \lim_{n \to \infty} \sum_{i=1}^n \varphi_{A_i}^n = \lim_{n \to \infty} (1 - \varphi_P^n ) = 1 - \int_0^1 f(t).
+    \end{align*}
+    The second can be obtained by integration by parts:
+    \begin{align*}
+        \int_0^1 t f'(t) \dt = tf(t) \mid_0^1 - \int_0^1 f(t) \dt = f(1) - \int_0^1 f(t) \dt
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of Lemma \ref{lem:entry_distr}] \textcolor{red}{(Might have to fix sum indices)} \\
+    The probability of $P$ having at most fraction $t$ of the other players before itself is
+    \begin{align*}
+        \Pr(X_n \leq nt) &= \Pr(X_n \leq nt ) \\
+        &= \prod_{j = nt + 1}^n \frac{j}{j + \lambda} \\
+        &= \exp \Bigg( \underbrace{\sum_{j = nt + 1}^n \log(j) - \log(j+\lambda)}_{\equiv S_n} \Bigg).
+    \end{align*}
+    Taking limits,
+    \begin{align*}
+        \lim_{n \to \infty} S_n &= \lim_{n \to \infty} \sum_{j = nt + 1}^n \log(j) - \log(j+\lambda) \\
+        &= \lim_{n \to \infty} \sum_{i = 1}^{n - nt} \log(nt + i) - \log(nt + i + \lambda) \\
+        &= \lim_{n \to \infty} \frac{1}{n - nt} \sum_{i = 1}^{n - nt} \frac{\log \left( t + \frac{i}{n - nt} \right) - \log \left( t + \frac{i}{n - nt} + \frac{\lambda}{n - nt} \right)}{1 / (n - nt)}
+    \end{align*}
+    Let
+    \begin{align*}
+        \Delta_n(s) = \frac{\log \left( s \right) - \log \left( s + \frac{\lambda}{n - nt} \right)}{1 / (n - nt)}
+    \end{align*}
+    By lemma \ref{lemma:log_convergence}, 
+    \begin{align*}
+        \Delta_n \xrightarrow[]{\mathrm{u}} \lambda \frac{\mathrm{d}}{\mathrm{d}s}log(s) = -\frac{\lambda}{s}
+    \end{align*}
+    on the compact interval $[t, 1]$ for any $t > 0$ ($\xrightarrow[]{\mathrm{u}}$ denotes uniform convergence).
+
+    Then, by lemma \ref{lemma:integral_convergence}, we have that
+    \begin{align*}
+        \lim_{n \to \infty} S_n &= \lim_{n \to \infty} \frac{1}{n-nt} \sum_{i=1}^{n-nt} \Delta_n \left( t + \frac{i}{n - nt} \right) \\
+        &= \int_t^1 (\lim_{n \to \infty} \Delta_n)(s) \ds \\
+        &= \int_t^1 \lim_{n \to \infty} -\frac{\lambda}{s} \ds \\
+        &= \lambda \log{t}
+    \end{align*}
+
+    Substituting $\lim_{n \to \infty} S_n$ into the original equation yields
+    \begin{align*}
+        \lim \Pr \left( \frac{X_n}{n} \leq t \right) &= \exp \Bigg( \lim_{n \to \infty} \sum_{j = nt + 1}^n \log(j) - \log(j+\lambda) \Bigg) \\
+        &= \exp(\lambda \log(t)) \\
+        &= t^\lambda.
+    \end{align*}
+
+    For $t=0$, simply observe that \textcolor{red}{Have to elaborate on this}
+    \begin{align*}
+        \lim_{n \to \infty} \prod_{j = 1}^n \frac{j}{j + \lambda} = 0 = 0^\lambda.
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of Corollary \ref{cor:fringe_value_2}]
+    If $f$ is monotone increasing, then $f(0) \leq \int_0^1 f(t) \dt \leq f(1)$. The inequalities become strict if $f$ is not constant on the whole interval.
+\end{proof}
+
+\begin{proof}[Proof of Proposition \ref{prop:one_sided_weighted}]
+    The weighted value of player $P$ is its expected contribution across all permutations, with each permutation weighted by its probability of occurring.
+    \begin{align*}
+        \varphi_P^{n, \lambda} = \sum_R \Pr(R) [v(\mathcal{P}_P^R \cup \{i\}) - v(\mathcal{P}_P^R)]
+    \end{align*}
+    As before, using the fact that fringe players are identical, this can be rephrased as
+    \begin{align*}
+        \varphi_P^{n, \lambda} &= \sum_{k=0}^n \Pr(R) f(k/n) \\
+        &= \E[f(X_n / n)]
+    \end{align*}
+    where $X_n$ is defined as above.
+$f$ is continuous, and therefore bounded on the compact set $[0, 1]$.
+As a consequence, $\frac{X_n}{n} \xrightarrow[]{\mathrm{d}} X$ implies $\E[f(X_n / n)] \to \E[f(X)]$, which in turn gives
+    \begin{align*}
+        \lim_{n \to \infty} \varphi_P^{n, \lambda} &= \lim_{n \to \infty} \E[f(X_n / n)] \\
+        &= \E[f(X)] \\
+        &= \int_0^1 f(t) \mathrm{d}G(t) \\
+        &= \int_0^1 g(t)f(t) \dt
+    \end{align*}
+    where $G(t)$ and $g(t)$ are the cdf and pdf of X, respectively.
+\end{proof}
+
+\begin{proof}[Proof of Corollary \ref{cor:platform_value_weighted}]
+    Let $X$ and $X'$ be random variables with cdfs $G_X = t^\lambda$ and $G_{X'}t^{\lambda'}$, respectively.
+For any $\lambda < \lambda'$, $t^\lambda > t^{\lambda'} \forall t \in [0, 1]$, meaning that $X'$ first-order stochastically dominates $X'$.
+As a result, for any monotonically increasing $f$,
+    \begin{align*}
+        \int_0^1 g_X(t)f(t) \dt = \E[f(X)] \leq \E[f(X')] = \int_0^1 g_{X'}(t)f(t)
+    \end{align*}
+    with strict inequality unless $f$ is constant almost everywhere. As $f$ is continuous, the latter is equivalent to $f$ being constant on the whole $[0, 1]$ interval.
+\end{proof}
+
+\begin{proof}[Proof of Corollary \ref{cor:paltform_value_weighted_2}]
+    As $\lambda \to 0$, $X$ converges to the degenerate random variable $X_0$ for which $\Pr(X_0 = 0) = 1$.
+As a consequence, the expected value of $f(X)$ converges to $\E[f(X_0)] = f(0)$.
+$\lim_{\lambda \to \infty} \varphi^{\infty, \lambda}_P = f(1)$ can be shown along the same lines.
+\end{proof}
+
+\begin{proof}[Proof of Proposition \ref{prop:multiple_platforms}]
+    \label{prop:one_sided_multiple}
+    First, let us rewrite the expected marginal contribution of player $P_i$ in the following way:
+    \begin{align*}
+        \varphi_{P_i}^{n, m} &= \frac{1}{(n+m)!} \sum_R v(\mathcal{P}_{P_i}^R \cup \{i\}) - v(\mathcal{P}_{P_i}^R) \\
+        &= \frac{1}{(n+m)!} \left[ \sum_{\{R | n_P(\mathcal{P}_{P_i}^R = 0)\}} \left[v(\mathcal{P}_{P_i}^R \cup \{i\}) - v(\mathcal{P}_{P_i}^R)\right] + \sum_{\{R | n_P(\mathcal{P}_{P_i}^R > 0)\}} \left[v(\mathcal{P}_{P_i}^R \cup \{i\}) - v(\mathcal{P}_{P_i}^R)\right] \right]
+    \end{align*}
+    Next, make use of the fact that the marginal contribution of a platform is zero if another platform is already present, and only depends on the number of fringe firms otherwise.
+    \begin{align*}
+        \varphi_{P_i}^{n, m} &= \frac{1}{(n+m)!} \sum_{\{R | n_P(\mathcal{P}_{P_i}^R = 0)\}} f (\mathcal{P}_{A}^R / n) \\
+        &= \frac{1}{(n+m)!} \sum_{k=0}^n |\{R | n_A(\mathcal{P}^R_{P_i} = k) \text{ and } n_P(\mathcal{P}^R_{P_i} = 0)\}| f(k/n)
+    \end{align*}
+    Finally, notice that, while the permutations with $k$ fringe agents before $P_i$ does not depend on $k$, amongst those, the number of permutations with no platform before $P_i$ does depend on it.
+In particular,
+    \begin{align*}
+        |\{R | n_A(\mathcal{P}^R_{P_i} = k) \text{ and } n_P(\mathcal{P}^R_{P_i} = 0)\}| &= \frac{n!(n+m-k-1)!}{(n-k)!}
+    \end{align*}
+    and
+    \begin{align*}
+        \varphi_{P_i}^{n, m} &= \sum_{k=0}^n \frac{n!(n+m-k-1)!}{(n+m)!(n-k)!} f(k/n) \\
+        &= \sum_{k=0}^n \frac{(n-k+1)(n-k+2) \dots (n-k+m-1)}{(n+1)(n+2) \dots (n+m)} f(k/n) \\
+        &= \frac{1}{n+1}\sum_{k=0}^n \underbrace{\frac{(n(1-k/n)+1)(n(1-k/n)+2) \dots (n(1-k/n)+m-1)}{(n+2) \dots (n+m)} f(k/n)}_{S_n}
+    \end{align*}
+    For any $t = k/n \in [0, 1]$, 
+    \begin{align*}
+        S_n(t) \to (1-t)^{m-1}f(t) \equiv S(t).
+    \end{align*}
+    Furthermore, it is simple to verify that this convergence is uniform, and that $S_n$ and $S$ are all continuous functions.
+By Dini's theorem, the former properties imply that $S_n \xrightarrow[]{\mathrm{u}} S$ uniformly on $[0, 1]$.
+
+    The conclusion of the proof is similar to that of proposition \ref{prop:one_sided}:
+    \begin{align*}
+        \lim_{n \to \infty} \varphi_{P_i}^{n, m} &= \lim_{n \to \infty} \underbrace{\frac{n}{n+1}}_{\to 1} \sum_{k=0}^{n-1} S_k(k/n) + \underbrace{\frac{1}{1+n}S(1)}_{\to 0} \\
+        &= \lim_{n \to \infty} \sum_{k=0}^{n-1} S_k(k/n) \\
+        &= \int_0^1 (1-t)^{m-1} f(t) \dt
+    \end{align*}
+    with the last equality supported by lemma \ref{lemma:integral_convergence}.
+\end{proof}
+
+\begin{proof}[Proof of Corollary \ref{cor:multiple_platforms}]
+    The allocation is efficient for all $n \in \mathbb{N}$, therefore efficient in the limit, as well. The second equality can be obtained by integration by parts.
+\end{proof}
+
+\begin{proof}[Proof of Corollary \ref{cor:multiple_platforms_2}] \textcolor{red}{(Assuming $f$ is continuously differentiable -- will have to relax this)}
+    $f'(t)$ is non-negative, so $[1 - (1-t)^m] f'(t)$ is increasing in $m$ $\forall t \in [0, 1]$.
+As a consequence, $\varphi_A^{n, \infty}$ is also increasing in $m$ if $f'(t)$ is positive on some interval or, $f(t)$ is not constant.
+Conversely, $\varphi_{P}^{\infty, m} = 1 - \varphi_{A}^{\infty, m}$ is decreasing in $m$.
+\end{proof}
 

### 2022-09-01 src/paper/paper.tex
Slightly rewrite abstract and introduction

@@
 \newcommand{\ds}{\mathrm{d}s}
+\newcommand{\di}{\mathrm{d}i}
 \newcommand{\E}{\mathbb{E}}
@@
 \begin{abstract}
-    This paper proposes a simplified model of two-sided markets aimed at analyzing the shares of total surplus various participants can achieve.
-Instead of explicitly modelling price structures and entry choices, I use a cooperative approach as a reduced-form model of bargaining outcomes.
-I show that this technique provides an analytically very tractable way of expressing the profits and surpluses of the agents.
+    This paper investigates the idea of using concepts from cooperative game theory (in particular, the Shapley-value) to model bargaining outcomes in games with a few large and a continuum of small players.
+I show that the cooperative approach can be a tractable alternative of explicitly modelling price structures and entry choices in platform settings.
+This approach might be advantageous when one does not want to attribute all the bargaining power to one type of market participants, and at the same time would like to avoid having to deal with an explicit multi-stage bargaining game.
+I demonstrate the advantages of this approach in simple a model of hybrid platforms.
 \end{abstract}
@@
 
-The use of solution concepts from cooperative game theory, such as the Shapley-value, to model the outcome of a bargaining process has been a feature of many papers in the industrial organization literature.
+The use of solution concepts from cooperative game theory -- such as the Shapley-value -- to model the outcome of a bargaining process has been a feature of multiple papers in the industrial organization literature.
 It is particularly prevalent in articles dealing with issues related to integration and mergers \parencite[e.g.][]{hart1990property,segal2003collusion,inderst2003bargaining,montez2007downstream}.
-This is in part motivated by the appealing properties of the resulting distributions, their tractability, but also by the long line of studies showing that various bargaining procedures lead to such outcomes.
+This is in part motivated by the appealing properties of the resulting gain distributions, their tractability, but also by the long line of theoretical studies showing that various bargaining procedures lead to such outcomes.
 For example, \textcite{gul1989bargaining,winter1994demand,hart1996bargaining,inderst2003bargaining,} or, perhaps most relevant to this paper, \textcite{stole1996intra} all propose various extensive-form bargaining games in which the expected outcomes correspond to players' Shapley-values.
@@
 However, as is often the case in economics, infinite-player approximations might turn out to be more tractable while retaining the main conclusions of the finite models from which they arise.
-Indeed, in the case of cooperative games with non-atomic players, the axiomatic and asymptotic approaches both give rise to the same value\footnote{On the appropriate subspace of non-atomic games.} \parencite{aumann2015values}, which is furthermore analytically simple and readily interpretable.
+Indeed, in the case of cooperative games with non-atomic players, both the axiomatic approach to defining a value on infinite games and the asymptotic approach to calculate the limit of its finite counterparts lead to the same result \footnote{On the appropriate subspace of non-atomic games.} \parencite{aumann2015values}, which is furthermore analytically simple and readily interpretable.
 An economic application of this theory can be found in \textcite{billera1978internal}.
@@
 The continuous analogue of them are called oceanic games, in which the set of players consists of a finite number of atoms and an ocean made up of a continuum of fringe players.
-While the axiomatic characterization of the value on such games has not been particularly fruitful,\footnote{\textcite{hart1973values} shows that the usual axioms do not characterize a unique value in general.} \textcite{fogelman1980asymptotic} demonstrates that the asymptotic approach works well on a large subset of them.
+While the axiomatic characterization of the value on such games has not been particularly fruitful,\footnote{\textcite{hart1973values} shows that the usual axioms do not characterize a unique value in general.} \textcite{fogelman1980asymptotic} demonstrates that an asymptotic approach works well on a large subset of them.
+More specifically, the limit of the players' values converge to relatively simple and easy-to-interpret expressions as the number of small players goes towards infinity.
 
-Despite this positive result, and their analytical tractability, oceanic games are utilized by hardly any papers in economics.
-One of the few such examples is \textcite{levy1997individual}, applying it to the problem of wage bargaining.
-In the following, I propose an oceanic game with the main feature that the large player(s) is indispensable for creating value.
+Despite this positive result and their analytical tractability, oceanic games are extremely underutilized in economics.
+One of the few examples of papers employing them is \textcite{levy1997individual}, which applies it to the problem of wage bargaining.
+In the following sections, I propose an oceanic game with the main feature that the large player(s) is indispensable for creating value.
 Such a model can apply, for example, to upstream-downstream supply chains, or platforms connecting two sides of a market.
-I demonstrate that the values of the players in those models are described by easily interpretable and visualizable expressions.
+I demonstrate that the Shapley values of the players in those models are described by easily interpretable and visualizable expressions.
+Additionally, the outcomes are in line with one's intuitive expectations of bargaining outcomes in such situations.
 Furthermore, the results are simple enough that these games can be embedded into more complex models, for example, as the second stage of a sequential game \parencite[as in e.g.][]{montez2007downstream}.
-Furthermore, the outcomes are in line with one's intuitive expectations of bargaining outcomes in such situations.
+Finally, I demonstrate the usefulness of this approach by building a simple model of a platform that can choose to function in hybrid mode as opposed to just being a pure marketplace.
 
@@
 
-Consider a market with a continuum of firms $a(t)$ ($t \in [0, 1]$), continuum of identical consumers and one platform $P$.
+Consider a market with a continuum of firms $a(t)$ ($t \in \mathbb{R}^+$), continuum of identical consumers and one platform $P$.
 The former two can only interact through the platform.
-Assume a measure $N \in (0, 1)$ of the firms are present on the platform.
-Then, consumers have the following quasilinear/CES utility function over money ($m$) and those firms' products:
-\begin{align*}
-    u(m, x(\cdot)) = m + \alpha \left[ \int_0^N x(t)^\rho \dt \right] ^ \frac{\gamma}{\rho}.
-\end{align*}
+Each firm has its own differentiated product.
+In addition, the platform can decide to switch to hybrid mode, in which case it will also be able to sell a measure $N_P$ of differentiated products of its own.
+The consumers have a logit utility function over these products, and a set of outside options of measure 1.
 
@@
 The game proceeds as follows.
-In the first stage, firms decide whether to create a product or not.
-Doing this entails a fixed cost of $C$.
-Those firms that choose not to invest obtain a payoff of 0 and are excluded from the remainder of the game.
-Next, the firms that made an investment can decide to join the platform at the cost of some entry fee $F^f$.
-(Note that the entry fee can be negative, in which case it is a subsidy from the platform to the firm.) After that, consumers decide to join or not at an entry fee of $F^c$.
-Finally, firms post their product prices, and produce and sell to consumers at marginal cost $c$.
+In the first stage, the platform decides whether or not to function in hybrid mode by choosing the extent of its own product selection $N_P$.
+Afterwards, each firm decides whether to create a product or not.
+Creating a product (or, for the platform, a unit measure of products) incurs a development cost of C.
+Firms that that choose not to invest obtain a payoff of 0 and are excluded from the remainder of the game.
+
+Next, the firms that have a product decide whether they want to join the platform at the cost of some entry fee $F^f$.
+(Note that the entry fee can be negative, in which case it is a subsidy from the platform to the firm.) Consumers are assumed to be on the platform without a choice.
+Finally, the platform and the entering firms post their product prices, and produce and sell to consumers at marginal cost $c$.
 
@@
 The issue with this approach is that it generally leads to extreme conclusions.
-\textcolor{red}{(TODO: elaborate on this)} As opposed to this, in this paper I assume that firm entry fees are a result of some bargaining process between the firms and the platform, leading to an allocation in which the final profits of each player correspond to their Shapley values.
+\textcolor{red}{(TODO: elaborate on this)} As an alternative, in this paper I assume that firm entry fees are a result of some bargaining process between the firms and the platform, leading to an allocation in which the final profits of each player correspond to their Shapley values.
 User entry fees, on the other hand, are unilaterally decided by the platforms.
 
-The value (characteristic function) of a coalition of the platform and any set of firms is defined as follows.
-Assume that the firms in the coalition enter the platform, while the others do not.
-Then, taking that decision as fixed, platforms set a profit-maximizing entry price for the consumers and firms also set own-profit-maximizing prices.
-That is, there is no collusion between the coalition members in terms of pricing.
-All they contract on are entry fees and decisions.
+The value (characteristic function) of a coalition consisting of the platform and any set of firms is defined as follows.
+Take the members of any given coalition as fixed.
+Let firms and the platform set profit-maximizing prices for their products, irrespective of earlier decisions (as both development costs and entry fees are sunk cost at this point).
+The value of the coalition is the sum of the paltform's and the firms' profits.
 
-\subsection{Solution of the game}
+\subsection{The pricing subgame}
 
-Let us start from the last stage, and assume that firms and consumers have already made their entry decisions: a measure $N$ of firms and measure $M$ of consumers are on the platform.
-Furthermore, firms have already set their prices $p(t)$, $t \in [0, N]$.
-Then consumers face the following utility maximization problem:
+Let us start from the last stage, when firms have already made their entry decisions: a measure $N_f$ of firms is present on the platform.
+Assume that consumers have the same Logit-form demand system as in \textcite{anderson2021hybrid}.
+Each consumer buys precisely one product, the one giving her the highest net utility.
+The utility from choosing outside option $i$ is $\mu \epsilon_{0i}$.
+The net utility from buying platform's $i$th product at price $p_{Pi}$ is $v - p_{Pi} + \mu \epsilon_{Pi}$, while the net utility from choosing the $i$th fringe firm's product is $v - p_{Fi} + \epsilon_{Fi}$.
+$\epsilon_{Pi}, \epsilon_{Fi}$ and $\epsilon_{0i}$ come from identical, independent, standardized Gumbel-distributions.
+
+As shown in \textcite{anderson2021hybrid}, the demand for each of these three types of products is
 \begin{align*}
-    &u(m, x(\cdot)) = m + \alpha \left[ \int_0^N x(t)^\rho \dt \right] ^ \frac{\gamma}{\rho} \\
-    &\text{s.t. } m + \int_0^N p(t) x(t) \dt = I.
-\end{align*}
-By following the usual solution method for CES utility functions, we obtain the following demand function:
-\begin{align*}
-    x(t) = M K p(t) ^ \frac{1}{\rho-1}
+    q_{Pi} &= \frac{\int_0^{N_P}  e^\frac{v - p_{Pi} \di}{\mu}}{A} \\
+    q_{Fi} &= \frac{e^\frac{v - p_{Fi}}{\mu}}{A} \\
+    q_{0i} &= \frac{1}{A} .
 \end{align*}
@@
 \begin{align*}
-    K = (\alpha \gamma) ^ {\frac{1}{1 - \rho} + \gamma - \rho} \left[ \int_0^N p(t) ^ \frac{\rho}{\rho - 1} \dt \right] ^ \frac{\rho - \gamma}{\rho (\gamma - 1)}.
+    A = \int_0^{N_P} e^\frac{v - p_{Pi}}{\mu} \dt + \int_0^{N_F} e^\frac{v - p_{Fi}}{\mu} \dt + 1.
 \end{align*}
-It implies that, as with the usual CES utility function, the optimal pricing strategy is independent on others' prices or the number of consumers, and is simply a constant markup over the marginal cost:
+
+It can be shown that the optimal pricing strategy is a constant, additive markup over the unit cost.
+Moreover, the markup is the same for both the platform and the firms, and corresponds to the dispersion in tastes:
 \begin{align*}
-    p = \frac{c}{\rho}.
+    p_{Pi} = p_{Fi} = c + \mu.
 \end{align*}
-The total profit each firm makes is then $\pi(N)$, while the total profit of all firms is $\Pi(n) = N\pi(N)$.
+Conversely, the profit of the two types of players are
+\begin{align*}
+    \pi_{Fi} &= \frac{\mu}{A} e^\frac{v - c - \mu}{\mu} \\
+    \pi_{Pi} &= N_P \frac{\mu}{A} e^\frac{v - c - \mu}{\mu}
+\end{align*}
+and the total profits of all players together are
+\begin{align*}
+    v(N_f) = N_f \pi_{Fi} + \pi_{Pi} = \mu \frac{A - 1}{A}.
+\end{align*}
 
-Consumers utility is from buying the products is then $u(N)$, which is increasing in $N$.
-As all consumers are identical, the platform optimally sets a user entry price of $F^u = u(N)$, so that it extracts all surplus from the consumers.
-Therefore, the total profits that a coalition of firms and the platform can obtain (assuming they individually maximize profits after the entry decisions are made) is
+Let $B = e^\frac{v - c - \mu}{\mu}$. Then the total profits from sales (platform and the entering firms combined) can be expressed as
 \begin{align*}
-    v(N) = \Pi(N) + U(N).
+    v(N_f) = \frac{N_P B + N_f B}{N_P B + N_f B + 1}.
 \end{align*}
-$v(N)$ is increasing in $N$, and its shape depends on the parameters of the utility function of the consumers and the marginal cost of the producers.
 
@@
 Let us look at the second stage of the game: firms have made their investment decisions, and are now negotiating with the platform over the entry price.
-Let us assume that $T \in [0, 1]$ measure of firms have made an investment.
+Let us assume that $\bar{N}_f \in \mathbb{R}^+$ measure of firms have made an investment.
 $C$ is a fixed cost, therefore does not influence the rest of the game.
@@
 \begin{align*}
-    \varphi_P(v, T) &= \int_0^1 v(tT) \dt \\
-    \varphi_f(v, T) &= v(T) - \int_0^1 v(tT) \dt.
+    \varphi_P(v, \bar{N}_f) &= \int_0^1 v(t \bar{N}_f) \dt \\
+    &= 1 - \frac{\log(BN_p + BN_f + 1) - \log(BN_p + 1)}{BN_f}
 \end{align*}
-In order to achieve these values, the firm entry fee will be set to $F^f = \varphi_P(v, T) - U(T)$.
+and
+\begin{align*}
+    \varphi_f(v, \bar{N}_f) &= v(\bar{N}_f) - \int_0^1 v(t \bar{N}_f) \dt \\
+    &= \frac{N_P B + N_f B}{N_P B + N_f B + 1} - 1 + \frac{\log(BN_P + BN_f + 1) - \log(BN_P + 1)}{BN_f} \\
+    &= \frac{\log(BN_P + BN_f + 1) - \log(BN_P + 1)}{BN_f} - \frac{1}{N_P B + N_f B + 1}.
+\end{align*}
+In order to achieve these values, the firm entry fee will be set to $F^f = \varphi_P(v, T) - N_P\Pi_{P_i}$.
+However, these fees are not relevant for any of the participants -- only their net profits, which is their Shapley value, matter.
 
-Finally, looking at the first stage, firms will make the initial investment if and only if $\varphi_f(v, T) / T \geq C$. Therefore, the equilibrium measure of entrants is given by
+\subsection{Equilibrium entry}
+
+Finally, looking at the first stage, firms will make the initial investment if and only if $\varphi_{f_i}(v, \bar{N}_f) = \varphi_f(v, \bar{N}_f) / \bar{N}_f \geq C$.
+Therefore, because of the free entry condition, the equilibrium measure of entrants is given by
 \begin{align*}
-    v(T) - \int_0^1 v(tT) = CT.
+    \frac{\log(BN_P + BN_f + 1) - \log(BN_P + 1)}{BN_f} - \frac{1}{N_P B + N_f B + 1} = C \bar{N}_f.
 \end{align*}
+The left hand side of this expression is strictly concave \textcolor{red}{(show this explicitly!)}, therefore, for low enough values of $C$, the equilibrium measure of entrants as a function of $N_P$ is unique.
+
+Next steps:
+\begin{itemize}
+    \item Show how the equilibrium number of entrants depends on $N_P$
+    \item Show how consumer welfare (which is proportional to $\log(N_f + N_P)$) depends on $N_P$
+    \item Try to characterize the profit-maximizing $N_P$ and how it depends on the parameters
+\end{itemize}
+
+Why is it interesting?
+\begin{itemize}
+    \item In \textcite{anderson2021hybrid}, in the absence of a revenue-based fee, consumer welfare does not depend on the number/measure of the platform's products.
+(The idea is that a higher $N_P$ is offset by a lower $N_f$ and vice versa.) Consumer welfare effects materialize through the platform setting a different sales fee for different values of $N_P$.
+    \item In this model, however, $N_P$ also changes the bargaining power of the platform, which in turn changes the profits obtained by the fringe.
+Therefore, $N_P$ does have an effect on the equilibrium measure of entrants and consumer welfare, even without revenue-based fees.
+    \item Therefore, a paltform selling its own products is not only worriesome because of the ususal factors (possibility of steering, perverse incentives for setting sales fees, etc.), but also because it increases its bargaining power against the possible entrants.
+\end{itemize}
 
 \appendix
-
-\section{References}
 
@@
 
-\section{Proofs of propositions and lemmas from the main text}
+\section{Proofs of propositions and lemmas in the main text}
 

### 2022-09-01 src/paper/paper.tex
More explanation for the weighted value section

@@
 
-Imagine a cooperative game with two types of players: a major player $P$ and $n$ smaller players.
+Consider a cooperative game with two types of players: a major player $P$ and $n$ smaller players.
 I.e., $N = \{P, A_1, \dots, A_n\}$.
@@
 Let $n_T(S)$ denote the number of players of type $T \in \{P, A\}$ in coalition $S$.
-Then, the value $S \subset N$ can achieve is the following:
+Then, the value that any coalition $S \subset N$ can achieve is the following:
 \begin{align*}
@@
 \end{align*}
-One can think of this setting as a (one-sided) platform and a number of potential entrants.
+One can think of this setting as a (one-sided) platform and a number of potential entrants, if the entrants can only reach their prospective consumers through the platform.\footnote{While these assumptions might seem somewhat restrictive, they are relatively simple to relax.} First, let us characterize the conditions under which this game is superadditive.
+These features provide some theoretical support for using Shapley-values as bargaining outcomes, as papers creating a link between noncooperative bargaining and cooperative values often rely on such assumptions.\footnote{For example, the results in \textcite{gul1989bargaining} rely on superadditivity, while monotonicity suffices for \textcite[]{hart1996bargaining}.}
 
@@
 In the following, let us assume that the assumptions required for monotonicity are always satisfied.
-It ensures that the games are of bounded variation, and thus the main theorem in \textcite{fogelman1980asymptotic} applies: asymptotic value coincides with the axiomatic one using the uniform distribution for the latter.
-\textcolor{red}{Note: I realize that this paragraph is somewhat vague and needs explanation.
+In addition to the previous advantages, it also ensures that the games are of bounded variation, and thus the main theorem in \textcite{fogelman1980asymptotic} applies them, as well.
+Namely, the asymptotic value coincides with the axiomatic one using the uniform distribution, providing multiple ways of characterizing them.
+In practice, it means that there is no need to explicitly calculate the limits of finite-player cooperative games, as there is a more direct option for characterizing the value of the oceanic game.
+Nevertheless, in many of the following theorems, the asymptotic limit is preferred, as I believe that makes the proofs more instructive.
+%\textcolor{red}{Note: I realize that this paragraph is somewhat vague and needs explanation.
 However, for the current set of results, I do not rely on said theorem.
@@
 
-Let $\varphi_P^n$ denote the Shapley-value of player $P$ in the case of $n$ players of type $A$.
 The following proposition demonstrates the main idea of this paper: even as the number of fringe players goes to infinity, the Shapley-value of the platform does not converge to $f(1)$.
 This in turn implies that the aggregated Shapley-values of the fringe remain positive even in the limit.
+In the remainder of the paper, let us use the following notation: $\varphi_P^n$ denotes the Shapley-value of player $P$ in the case of $n$ players of type $A$.
 \begin{proposition}
@@
 
+Finally, the following corollary implies that, even though the individual share of each $A_i$ vanishes as their number goes to infinity, their total value still converges to a positive value.
 \begin{corollary}
@@
 
-This proposition implies that, even though the individual share of each $A_i$ vanishes as their number goes to infinity, their total value converges to a positive value.
+\subsection{Weighted Shapley-values}
 
-\subsection{Weighted Shapley-values}
+While the values of oceanic games (i.e.
+the limits of the Shapley values of their finite approximations in finite games) are well known in the relevant literature, there are no results about the limits of the weighted (Shapley) values.
+While providing very general results in the form of \textcite[]{fogelman1980asymptotic} is outside of the scope of the paper\footnote{They show that the (within some constraints) any discretization of an oceanic game converges to the same value.} the results in this section still provide some new insights into weighted values of oceanic games.
+In particular, I show that the weighted value of a game with one large and many small players converges to a rather simple and intuitive expression, if the size of the small players go to zero at the same rate.
 
@@
 I.e., assume that there is at most one player with zero weight.
-I make use of the fact that weighted Shapley values can be calculated by weighting the permutations by the probabilities arising from the following sequential entry procedure \parencite{kalai1987weighted}.
+For my main result, I make use of the fact that weighted Shapley values can be calculated by weighting the permutations by the probabilities arising from the following sequential ordering procedure \parencite{kalai1987weighted}.
 Start with the set of all players.
 Let the probability of player $i$ being the last amongst the set of remaining players $R$ be $\lambda_i / \sum_{j \in R} \lambda_j$.
+Continue until all players are exhausted.
 This yields a well-defined probability for each permutation of players.
-Continue until all players are exhausted.
 
-Getting back to the game at hand, let the weights of players of type $A$ and $P$ be 1 and $\lambda$, respectively.
+Consider the game described in the previous section, and let the weights of players of type $A$ and $P$ be 1 and $\lambda$, respectively.
 Let $X_n$ be a random variable representing the number of players before $P$ when players are ordered according to the above procedure.
@@
 
-Finally, the weighted Shapley-value of player $i$ can be expressed as the expected marginal contribution of that player where the permutations are weighted according to the previous distribution.
+The main proposition of this section shows that the weighted Shapley-value of player $i$ can be expressed as the expected marginal contribution of that player where the permutations are weighted according to the previous distribution.
 \begin{proposition}
@@
 
+Finally, the following corollaries support the interpretation of weights as bargaining power, as a higher weight corresponds to a higher Shapley-value in this game.\footnote{This would not necessarily have to be the case, as demonstrated by \textcite{owen1968communications}.} Furthermore, the limit of the weighted value of $P$, as their weight goes to zero (infinity) is precisely the payoffs $P$ would achieve if $P$ were making (facing) take-it-or-leave-it offers.
+
 \begin{corollary}
@@
 \end{corollary}
-
-The following proposition supports the interpretation of weights as bargaining power, as a higher weight corresponds to a higher Shapley-value in this game.\footnote{This would not necessarily have to be the case, as demonstrated by \textcite{owen1968communications}.}
 

### 2022-09-01 src/paper/paper.tex
Small additions to the multi-platform subsection

@@
 
-Imagine that there are $m$ players of type $P$ which are perfect substitutes of each other.
+Imagine that, instead of just one, there are $m$ players of type $P$, and they are perfect substitutes of each other.
 That is, the fringe players still need a platform to achieve any value, but it does not matter which or how many platforms are available for them.
-Specifically, the value function for coalition $S$ is the following:
+Formally, the value function for coalition $S$ is the following:
 \begin{align*}
@@
 
-% \begin{proposition}
-%     The game is monotone, supermodular and convex if $f$ is increasing and convex
-% \end{proposition}
-\textcolor{red}{Note: I have to think more about how to describe this situation in the language of cooperative game theory.
+Let us start by establishing monotonicity for this version of the model, too.
+\begin{proposition}
+    The game is monotone if $f$ is increasing and $f(0) \geq 0$.
+\end{proposition}
+% \textcolor{red}{Note: I have to think more about how to describe this situation in the language of cooperative game theory.
 The issue is that, for example, the value of $\{P_1, A_1\}$ depends on whether $\{P_2, A_2\}$ also decides to form a coalition and enter the market.}
 
+As before, the main proposition in this section provides us with an expression of the limit of the value for this variant of the game.
 \begin{proposition}
@@
 
-As with proposition \ref{prop:one_sided}, this result also has a probabilistic interpretation, and could have been obtained directly from the oceanic game.
+As with proposition \ref{prop:one_sided}, this result also has a probabilistic interpretation, and could have been obtained directly using the axiomatic approach.
 Let the location of the $m$ atoms be $t_1, \dots, t_m$, distributed independently and uniformly on the unit cube.

### 2022-09-01 src/paper/paper.tex
Add explanation to the two-sided models.

@@
 \end{align*}
+A prominent interpretation of this model would be a platform marketplace with a set of sellers and a set of buyers, where all three sides possess some amount of bargaining power.
+However, player $P$ does not have to be in the ``middle'' of the transactions for this framework to be applicable.
+For example, it also captures the situation of a single upstream producer, a large number of downstream firms, and a similarly large number of customers, as long as both the customers and the downstream firms can participate in the bargaining process.
+A setting where these assumptions might be plausible is, for example, the new car market with a car producer, a number of independent dealerships, and customers who might engage in negotiation.
 
+Let us follow the pattern from the previous sections. Start by characterizing conditions for superadditivity to support the bargaining interpretation.
 \begin{proposition}
@@
 
-Furthermore, the limits of the Shapley-values (as $n \to \infty$) of the various players turn out to be analytically tractable and nicely interpretable.
+Next, let us obtain formulas for the values of the three groups of players.
+It turns out that the limits of the Shapley-values (as $n \to \infty$) are still analytically tractable and they also have neat interpretations.
 
@@
 
-That is, the value of the grand coalition can be decomposed into the Shapley-values of its members signifying their expected marginal contributions in the following way:
+As the previous proposition shows, the value of each kind of player depends on their expected marginal contribution, i.e.
+the partial derivatives of $f$.
+Consequently, the value of the grand coalition can be decomposed into the Shapley-values of its members signifying their expected marginal contributions in the following way:
 \begin{align*}
-    f(1, 1) = \underbrace{\int_0^1 f(t, t) \dt}_{\text{ player } P} + \underbrace{\int_0^1 t \frac{\partial f(t, t)}{\partial a} \dt}_{\text{players } A} + \underbrace{\int_0^1 t \frac{\partial f(t, t)}{\partial b} \dt}_{\text{players } B}
+    f(1, 1) = \underbrace{\int_0^1 f(t, t) \dt}_{\text{ player } P} + \underbrace{\int_0^1 t \frac{\partial f(t, t)}{\partial a} \dt}_{\text{players } A} + \underbrace{\int_0^1 t \frac{\partial f(t, t)}{\partial b} \dt}_{\text{players } B}.
 \end{align*}
+
+One surprising element of the result is that one only has to integrate over the diagonal of the support  of $f$, and the value does not depend on the marginal contributions in the case of an unequal measure of $A$ and $B$ types.
+The intuition for that relies on a law-of-large-numbers-type reasoning.
+If the number of fringe players is large, then it is very unlikely that, after a random ordering, their proportion in any interval will be too different.
+Consequently, when taking the expectation over all orderings, ones with vary unequal numbers of the two types will have little impact on it.
 
@@
 
-Again, assume that there are $k$ players of type $P$ which are perfect substitutes of each other.
-
-\textbf{Note:} As in the previous case, I have to think more about how interpret the value function here. For now, let me just show the limit of the limits of the Shapley-values assuming that
+The two-sided case can also simply be extended to incorporate multiple platforms instead of just one.
+As before, assume that there are $k$ players of type $P$ which are perfect substitutes of each other:
 \begin{align*}
@@
 
+It can be shown that the values of each type of player are rather similar to the one-platform case.
 \begin{proposition}
@@
 
+Similarly, as the next corollary demonstrates, the combined value of platforms is still decreasing in their number.
 \begin{corollary}

### 2022-09-01 src/paper/paper.tex
Significantly expand the application section

@@
 
+This section demonstrates the usefulness of the cooperative approach via a model of a hybrid market, based on that in \textcite[]{anderson2021hybrid}.
 Consider a market with a continuum of firms $a(t)$ ($t \in \mathbb{R}^+$), continuum of identical consumers and one platform $P$.
-The former two can only interact through the platform.
-Each firm has its own differentiated product.
-In addition, the platform can decide to switch to hybrid mode, in which case it will also be able to sell a measure $N_P$ of differentiated products of its own.
+Assume former two can only interact through the platform.
+Let each firm have its own, differentiated product.
 The consumers have a logit utility function over these products, and a set of outside options of measure 1.
+I will examine the outcome in two situations: (1) the platform functions as a pure marketplace without having an own product, and (2) the platform operating in hybrid mode, selling a measure $N_P$ of differentiated products of its own.
 
@@
 The game proceeds as follows.
-In the first stage, the platform decides whether or not to function in hybrid mode by choosing the extent of its own product selection $N_P$.
-Afterwards, each firm decides whether to create a product or not.
-Creating a product (or, for the platform, a unit measure of products) incurs a development cost of C.
-Firms that that choose not to invest obtain a payoff of 0 and are excluded from the remainder of the game.
+In the first stage, each firm decides whether to invest in creating a product or not.
+Creating a product incurs a development cost of C.
+Firms that choose not to invest obtain a payoff of 0 and are excluded from the remainder of the game.
 
@@
 The most widespread assumption in the literature is that they are unilaterally decided by the platform, and are essentially take it or leave it offers for the other players.
-The issue with this approach is that it generally leads to extreme conclusions.
-\textcolor{red}{(TODO: elaborate on this)} As an alternative, in this paper I assume that firm entry fees are a result of some bargaining process between the firms and the platform, leading to an allocation in which the final profits of each player correspond to their Shapley values.
-User entry fees, on the other hand, are unilaterally decided by the platforms.
+The issue with this approach is that it generally leads to extreme conclusions (depending on the number of platforms, and assumptions about single-and-multi-homing, the platforms either act as monopolists or obtain zero profits).
+As an alternative to this, in this paper, I assume that firm entry fees are a result of some bargaining process between the firms and the platform.
+Furthermore, the bargaining process is such that it leads to an allocation in which the final profits of each player correspond to their Shapley values.
 
-The value (characteristic function) of a coalition consisting of the platform and any set of firms is defined as follows.
+The characteristic function (necessary for computing values) of a coalition consisting of the platform and any set of firms is defined as follows.
 Take the members of any given coalition as fixed.
-Let firms and the platform set profit-maximizing prices for their products, irrespective of earlier decisions (as both development costs and entry fees are sunk cost at this point).
-The value of the coalition is the sum of the paltform's and the firms' profits.
+Let firms and the platform set profit-maximizing prices for their products without collusion.
+Note that these prices will be irrespective irrespective of earlier decisions, as both development costs and entry fees are sunk cost at this point.
+The total profits of the coalition is then the sum of the platform's and the firms' profits from product sales.
+
+While the previous procedure might look somewhat peculiar at first glance, its elements would not be out of place in more traditional (noncooperative) models, either.
+Principally, the two main ideas it relies are the following.
+First, bargaining outcomes should not depend on which player actually obtains the money, all that matters is the total that a given set of players can obtain.\footnote{For example, imagine the following two situations with two players.
+In the first one, the first player obtains a playoff of two dollars if they both decide to cooperate and nothing otherwise.
+In the second scenario, both players receive one dollar in the case of cooperation.
+If they can transfer monay between each other, bargaining outcomes should be the same in both scenarios.} Second, players during the bargaining foresee the (unique) subgame perfect equilibrium in the following subgame, and negotiate based on them
 
@@
 
-Let us start from the last stage, when firms have already made their entry decisions: a measure $N_f$ of firms is present on the platform.
+Let us start from the last stage, when firms' entry to the platform is already decided: a measure $N_f$ of firms is present on the platform.
 Assume that consumers have the same Logit-form demand system as in \textcite{anderson2021hybrid}.
-Each consumer buys precisely one product, the one giving her the highest net utility.
+Each consumer buys precisely a measure one of products, those giving her the highest net utility.
 The utility from choosing outside option $i$ is $\mu \epsilon_{0i}$.
-The net utility from buying platform's $i$th product at price $p_{Pi}$ is $v - p_{Pi} + \mu \epsilon_{Pi}$, while the net utility from choosing the $i$th fringe firm's product is $v - p_{Fi} + \epsilon_{Fi}$.
+The net utility from buying the platform's $i$th product at price $p_{Pi}$ is $v - p_{Pi} + \mu \epsilon_{Pi}$, while the net utility from choosing the $i$th fringe firm's product is $v - p_{Fi} + \epsilon_{Fi}$.
 $\epsilon_{Pi}, \epsilon_{Fi}$ and $\epsilon_{0i}$ come from identical, independent, standardized Gumbel-distributions.
@@
 
-It can be shown that the optimal pricing strategy is a constant, additive markup over the unit cost.
+Furthermore, it can be shown that the optimal pricing strategy is a constant, additive markup over the unit cost.
 Moreover, the markup is the same for both the platform and the firms, and corresponds to the dispersion in tastes:
@@
 \end{align*}
+
 Conversely, the profit of the two types of players are
@@
 
-Let $B = e^\frac{v - c - \mu}{\mu}$. Then the total profits from sales (platform and the entering firms combined) can be expressed as
+Let $B = e^\frac{v - c - \mu}{\mu}$. Then the total profits from sales (platform and firms combined) can be expressed as
 \begin{align*}
@@
 \end{align*}
+This is the characteristic function that forms the basis of the profit allocation.
 
@@
 $C$ is a fixed cost, therefore does not influence the rest of the game.
-Remember that entry fees will be set such that the final profits correspond to Shapley values.
-Let us denote these values by $\varphi_f(v, T)$ and $\varphi_P(v, T)$ for firms and the platform, respectively.
-As shown in the main results,
+It is simpler to think about bargaining final net profits (entry fees can always be set to achieve any final allocation of profits), which are assumed to be equal to the players' Shapley values.
+Let us denote these values by $\varphi_f(v, T)$ and $\varphi_P(v, T)$ for the firms and the platform, respectively.
+As shown in proposition \ref{prop:one_sided},
 \begin{align*}
@@
 \end{align*}
-In order to achieve these values, the firm entry fee will be set to $F^f = \varphi_P(v, T) - N_P\Pi_{P_i}$.
-However, these fees are not relevant for any of the participants -- only their net profits, which is their Shapley value, matter.
 
@@
 Finally, looking at the first stage, firms will make the initial investment if and only if $\varphi_{f_i}(v, \bar{N}_f) = \varphi_f(v, \bar{N}_f) / \bar{N}_f \geq C$.
-Therefore, because of the free entry condition, the equilibrium measure of entrants is given by
+Therefore, because of the free entry condition, the equilibrium measure of entrants is given by the equation
 \begin{align*}
-    \frac{\log(BN_P + BN_f + 1) - \log(BN_P + 1)}{BN_f} - \frac{1}{N_P B + N_f B + 1} = C \bar{N}_f.
+    \underbrace{\frac{\log(BN_P + B\bar N_f + 1) - \log(BN_P + 1)}{B\bar N_f} - \frac{1}{N_P B + \bar N_f B + 1}}_{\equiv h(\bar N_f)} = C \bar{N}_f.
 \end{align*}
-The left hand side of this expression is strictly concave \textcolor{red}{(show this explicitly!)}, therefore, for low enough values of $C$, the equilibrium measure of entrants as a function of $N_P$ is unique.
+
+Let us examine the implications of this result through a numerical example.
+Let $B=1, C=0.2$, and let the product variety of the platform be $0$ and $0.2$ in the pure marketplace and the hybrid case, respectively.
+The equilibrium number of entrants is shown in figure \ref{fig:entry}.
+\begin{figure}
+    \centering
+    \includegraphics[width=4in]{../../out/figures/equilibrium_nf.png}
+    \caption{Equilibrium number of fringe entrants as a function of the platform's product variety.}
+    \label{fig:entry}
+\end{figure}
+
+It is immediately apparent from the figure, that a platform operating in hybrid mode discourages fringe entry, as a direct result of more competition and lower profits in the final stage of the game.
+However, a more subtle point is that the total number of products (platform's products plus measure of entrants) is also lower in the hybrid case.
+Because consumer surplus is proportional to the logarithm of the number of available products, this also corresponds to a decrease in that measure.
+
+ In the version of the model without bargaining, the platforms' product variety does not influence total product variety, as long as entry fees are fixed.
+An increase in the monopolist's product variety will lead to an identically sized decrease in fringe entry, leaving the total number of available products, and, conversely, consumer welfare, unchanged.
+Operating in hybrid mode only influences fringe entry through more indirect channels, e.g.
+self-preferencing \parencite[]{hagiu2022should} or distorted incentives when setting revenue-based fees \parencite[]{anderson2021hybrid}.
+This example application highlights another channel of distortion created by hybrid platforms: a platform having its own products has more bargaining power when entry fees are determined, leading to lower fringe profits.
+As a consequence, fewer firms enter than in the pure marketplace scenario, and this decrease is more significant than the addition of the platform's own products.
+
+\section{Conclusions}
 

### 2022-09-01 src/figures/equilibrium_nf.py

@@ -1,0 +1,26 @@
+import numpy as np
+import matplotlib. pyplot as plt
+
+
+def plot_equilibrium_nf(N_P_list, B, C, N_f_range=(0, 2), num_obs=500):
+    N_f = np.linspace(N_f_range[0], N_f_range[1], num_obs)
+    rhs = C * N_f
+    lhs_list = []
+    for N_P in N_P_list:
+        lhs = (np.log(B * N_P + B * N_f + 1) - np.log(B * N_P + 1)) / (B * N_f) - 1 / (N_P * B + N_f * B + 1)
+        lhs_list.append(lhs)
+    
+    fig, ax = plt.subplots()
+    ax.plot(N_f, rhs, label=r'$C\barN_f$', color='black')
+    for lhs, N_P in zip(lhs_list, N_P_list):
+        ax.plot(N_f, lhs, label=r'$h(\bar N_f) \mid N_P = {}$'.format(N_P))
+    
+    ax.set_xlabel(r'$\barN_f$')
+    ax.legend()
+
+    return fig, ax
+
+fig, ax = plot_equilibrium_nf([0, 0.2], B=1, C=0.2, N_f_range=(0, 1))
+fig.set_size_inches(5, 3.5)
+fig.set_facecolor("white")
+fig.savefig("../../out/figures/equilibrium_nf.png", dpi=300)

### 2022-09-01 src/paper/paper.tex
Minor formatting changes

@@
 
-\title{The value of intermediation -- results so far}
+\title{The value of intermediation}
 \author{Martin Stancsics}
@@
 One can think of this setting as a (one-sided) platform and a number of potential entrants, if the entrants can only reach their prospective consumers through the platform.\footnote{While these assumptions might seem somewhat restrictive, they are relatively simple to relax.} First, let us characterize the conditions under which this game is superadditive.
-These features provide some theoretical support for using Shapley-values as bargaining outcomes, as papers creating a link between noncooperative bargaining and cooperative values often rely on such assumptions.\footnote{For example, the results in \textcite{gul1989bargaining} rely on superadditivity, while monotonicity suffices for \textcite[]{hart1996bargaining}.}
+These features provide some theoretical support for using Shapley-values as bargaining outcomes, as papers creating a link between non-cooperative bargaining and cooperative values often rely on such assumptions.\footnote{For example, the results in \textcite{gul1989bargaining} rely on superadditivity, while monotonicity suffices for \textcite[]{hart1996bargaining}.}
 
@@
 
-While the previous procedure might look somewhat peculiar at first glance, its elements would not be out of place in more traditional (noncooperative) models, either.
+While the previous procedure might look somewhat peculiar at first glance, its elements would not be out of place in more traditional (non-cooperative) models, either.
 Principally, the two main ideas it relies are the following.
@@
 In the second scenario, both players receive one dollar in the case of cooperation.
-If they can transfer monay between each other, bargaining outcomes should be the same in both scenarios.} Second, players during the bargaining foresee the (unique) subgame perfect equilibrium in the following subgame, and negotiate based on them
+If they can transfer monay between each other, bargaining outcomes should be the same in both scenarios.} Second, players during the bargaining foresee the (unique) subgame perfect equilibrium in the following subgame, and negotiate based on them.
 
@@
 
-Next steps:
-\begin{itemize}
-    \item Show how the equilibrium number of entrants depends on $N_P$
-    \item Show how consumer welfare (which is proportional to $\log(N_f + N_P)$) depends on $N_P$
-    \item Try to characterize the profit-maximizing $N_P$ and how it depends on the parameters
-\end{itemize}
+This paper proposed a new framework to think about the profit allocation in situations concerning a few large and a continuum of smaller players.
+The results are especially relevant for upstream-downstream situations, platform settings, and two-sided markets.
+The outcomes of the Shapley-value-based gain sharing rule generally concur with intuitive expectations, and the resulting formulas are more tractable than most explicit non-cooperative approaches.
 
-Why is it interesting?
-\begin{itemize}
-    \item In \textcite{anderson2021hybrid}, in the absence of a revenue-based fee, consumer welfare does not depend on the number/measure of the platform's products.
-(The idea is that a higher $N_P$ is offset by a lower $N_f$ and vice versa.) Consumer welfare effects materialize through the platform setting a different sales fee for different values of $N_P$.
-    \item In this model, however, $N_P$ also changes the bargaining power of the platform, which in turn changes the profits obtained by the fringe.
-Therefore, $N_P$ does have an effect on the equilibrium measure of entrants and consumer welfare, even without revenue-based fees.
-    \item Therefore, a paltform selling its own products is not only worriesome because of the ususal factors (possibility of steering, perverse incentives for setting sales fees, etc.), but also because it increases its bargaining power against the possible entrants.
-\end{itemize}
+The illustrative hybrid platform model also highlights the strengths of this approach.
+Despite its simplicity, it highlights a novel channel through which platforms selling their own products might lead to welfare losses: hybrid platforms have more bargaining power against potential entrants than traditional ones.
+This mechanism should probably also be considered when competition authorities assess mergers between platforms and contents providers.
+
+There is a variety of ways through which this paper could be expanded or built upon.
+On the theoretical side, some of the stricter assumptions could be relaxed, such as fringe agents achieving a zero payoff without the platform.
+Besides, the convergence result for the weighted values could be strengthened if one could manage to show that any sequence along ever more refined partitions of the atomic players converges to the same limit \parencite[à la][]{fogelman1980asymptotic}.
+The possibilities for practical applications are no less interesting, either.
+As a first step, the majorly simplified example application could be expanded upon, so that it is a better description of certain real-life paltform markets.
+Finally, the cooperative approach to profit distribution could become an alternative for the more usual, but in some sense more extreme assumptions about the bargaining process widely used in industrial organization models.
+
+% Next steps:
+% \begin{itemize}
+%     \item Show how the equilibrium number of entrants depends on $N_P$
+%     \item Show how consumer welfare (which is proportional to $\log(N_f + N_P)$) depends on $N_P$
+%     \item Try to characterize the profit-maximizing $N_P$ and how it depends on the parameters
+% \end{itemize}
 
@@
 
-\begin{proof}[Proof of Lemma \ref{lem:entry_distr}] \textcolor{red}{(Might have to fix sum indices)} \\
+\begin{proof}[Proof of Lemma \ref{lem:entry_distr}] %\textcolor{red}{(Might have to fix sum indices)} \\
     The probability of $P$ having at most fraction $t$ of the other players before itself is
@@
 
-    For $t=0$, simply observe that \textcolor{red}{Have to elaborate on this}
+    For $t=0$, simply observe that %\textcolor{red}{Have to elaborate on this}
     \begin{align*}
@@
 
-\begin{proof}[Proof of Corollary \ref{cor:multiple_platforms_2}] \textcolor{red}{(Assuming $f$ is continuously differentiable -- will have to relax this)}
+\begin{proof}[Proof of Corollary \ref{cor:multiple_platforms_2}] (Assuming $f$ is continuously differentiable) %\textcolor{red}{(Assuming $f$ is continuously differentiable -- will have to relax this)}
     $f'(t)$ is non-negative, so $[1 - (1-t)^m] f'(t)$ is increasing in $m$ $\forall t \in [0, 1]$.

### 2022-09-01 src/figures/equilibrium_nf.py

@@ -9,16 +9,17 @@ def plot_equilibrium_nf(N_P_list, B, C, N_f_range=(0, 2), num_obs=500):
     for N_P in N_P_list:
         lhs = (np.log(B * N_P + B * N_f + 1) - np.log(B * N_P + 1)) / (B * N_f) - 1 / (N_P * B + N_f * B + 1)
         lhs_list.append(lhs)
-    
+
     fig, ax = plt.subplots()
     ax.plot(N_f, rhs, label=r'$C\barN_f$', color='black')
     for lhs, N_P in zip(lhs_list, N_P_list):
         ax.plot(N_f, lhs, label=r'$h(\bar N_f) \mid N_P = {}$'.format(N_P))
-    
+
     ax.set_xlabel(r'$\barN_f$')
     ax.legend()
 
     return fig, ax
+
 
 fig, ax = plot_equilibrium_nf([0, 0.2], B=1, C=0.2, N_f_range=(0, 1))
 fig.set_size_inches(5, 3.5)

### 2022-09-12 src/sympy/integrals.py
Add half-baked script for computing integrals

@@ -1,0 +1,17 @@
+from sympy import Symbol, integrate, init_printing, simplify, solve, Eq
+init_printing()
+
+mu = Symbol('mu')
+B = Symbol('B')
+C = Symbol('C')
+Nf = Symbol('N_f')
+Np = Symbol('N_P')
+Nfbar = Symbol('\\bar N_f')
+
+v = (Np * B + Nf * B) / (Np * B + Nf * B + 1)
+
+P_share = simplify(integrate(v, (Nf, 0, Nfbar)) / Nfbar)
+F_share = simplify(v.subs({Nf: Nfbar}) - P_share)
+
+Nfbar_eq = Eq(Nfbar * C, F_share)
+Nfbar_opt = solve(Nfbar_eq, Nfbar)

### 2022-09-12 src/utils/makeutils.py
Extend paper rule in snakefile
Also switch to root-dir-relative paths in the tex file.
Latex-workshop build rules have to be modified accordingly.

@@ -1,0 +1,28 @@
+import re
+import os
+
+
+def find_input_files(tex_file, add_tex_folder=False):
+    """Find all of the files that are included, inputted or includegraphics'
+    in a tex file.
+    Args:
+        tex_file: The path of the tex file.
+    Returns:
+        List[str]: the list of included files
+    """
+
+    with open(tex_file, 'r') as file:
+        tex_contents = file.read()
+
+    patterns = [
+        re.compile(r"\\input\{(.*)\}"),
+        re.compile(r"\\include\{(.*)\}"),
+        re.compile(r"\\includegraphics(?:\[.*\])?\{(.*)\}")
+    ]
+
+    paths = sum((pattern.findall(tex_contents) for pattern in patterns), [])
+    if add_tex_folder:
+        prefix = os.path.dirname(tex_file)
+        paths = [os.path.join(prefix, path) for path in paths]
+
+    return paths

### 2022-09-12 src/figures/equilibrium_nf.py
Add snakemake rule for creating figure

@@ -1,8 +1,9 @@
 import numpy as np
 import matplotlib. pyplot as plt
+import typer
 
 
-def plot_equilibrium_nf(N_P_list, B, C, N_f_range=(0, 2), num_obs=500):
+def plot_equilibrium_nf(N_P_list, B, C, N_f_range, num_obs=500):
     N_f = np.linspace(N_f_range[0], N_f_range[1], num_obs)
     rhs = C * N_f
     lhs_list = []
@@ -21,7 +22,20 @@ def plot_equilibrium_nf(N_P_list, B, C, N_f_range=(0, 2), num_obs=500):
     return fig, ax
 
 
-fig, ax = plot_equilibrium_nf([0, 0.2], B=1, C=0.2, N_f_range=(0, 1))
-fig.set_size_inches(5, 3.5)
-fig.set_facecolor("white")
-fig.savefig("../../out/figures/equilibrium_nf.png", dpi=300)
+def create_plot(out_path: str, B: float = 1, C: float = 0.2,
+                N_P: list[float] = [], N_f_range: tuple[float, float] = (0, 1),
+                num_obs: int = 500, width: float = 5, height: float = 3.5, dpi: int = 300):
+
+    if not N_P:
+        raise typer.BadParameter("At least one value for N_P must be provided")
+
+    fig, ax = plot_equilibrium_nf(N_P_list=N_P, B=B, C=C, N_f_range=N_f_range, num_obs=num_obs)
+
+    fig.set_size_inches(width, height)
+    fig.set_facecolor("white")
+
+    fig.savefig(out_path, dpi=dpi)
+
+
+if __name__ == "__main__":
+    typer.run(create_plot)

### 2022-09-12 src/presentation/presentation.qmd
Add presentation

---
title: "The value of intermediation"
author: "Martin Stancsics"
format: revealjs
bibliography: references.bib
---

<style>
    ul li li {
        font-size: 0.75em;
        line-height: 1.2em;
    }
</style>

# Intorduction

## Motivation

TODO

## Main ideas

 - Use the Shapley-value instead of an extensive-form bargaining model
    - Analytically more tractable
    - Has bargaining interpretation [e.g. @hart1996bargaining; @gul1989bargaining]
    - Has precedents in the IO literature [e.g. @hart1990property; @montez2007downstream]
 - Focus on the "few large players -- continuum of small players" case (oceanic games)
    - Good approximation of the finite player case even for not too many players
    - Results have a nice geometric interpretation
 - Balance generality and having useful results

## Preview of results

 - The Shapley-value seems to be a very tractable way of modeling bargaining in certain important contexts
    - One/two-sided platforms
    - Upstream-downstream setups
 - Comparative statistics give support to the bargaining interpretation
 - Extensions to include some important cases are relatively straightforward
 - Even a simple application yields interesting results about hybrid platforms

#

## The Shapley-value

Each player gets their expected marginal contribution

:::: {.columns}

::: {.column width="40%"}
contents...
:::

::: {.column width="60%"}
contents...
:::

::::

## Why do we care about it?

Same idea as with the Nash bargaining game/solution

 - Axiomatic reasoning
    - The Shapley-value is the only sharing rule that is efficient, symmetric, linear, and satisfies the null player axiom [@shapley1953additive]
 - Bargaining foundations
    - The value arises of the subgame-perfect equilibrium of various alternating-offer bargaining games [e.g. @gul1989bargaining; @winter1994demand; @hart1996bargaining; @stole1996intra; @inderst2003bargaining]
 - A tractable and sensible-looking gain-sharing rule
    - Comparative statics show that it behaves as one would expect

# The relevant setting

## Baseline model

# Thank you

## References

::: {#refs}
:::

### 2022-09-12 src/manim_figures/shapley_value_demo.py
Add manim video for Shapley-values

@@ -1,0 +1,143 @@
+from manim import *
+
+
+class Baseline(Scene):
+
+    def construct(self):
+
+        box_size = 2
+        label_size = 150
+        horiz_space = 7
+        up_shift = 3
+
+        self.camera.background_color = WHITE
+
+        Text.set_default(color=BLACK)
+        Line.set_default(color=BLACK)
+        Tex.set_default(color=BLACK)
+        Brace.set_default(color=BLACK)
+
+        self.next_section("draw objects")
+
+        P_text = Tex("$P$", color=BLACK, font_size=label_size)
+        P_text.bg = Rectangle(height=box_size, width=box_size, color=BLUE, fill_opacity=0.25)
+        P = VGroup(P_text, P_text.bg)
+
+        A1_text = Tex("$A_1$", color=BLACK, font_size=label_size)
+        A1_text.bg = Rectangle(height=box_size, width=box_size, color=RED, fill_opacity=0.25)
+        A1 = VGroup(A1_text, A1_text.bg)
+
+        A2_text = Tex("$A_2$", color=BLACK, font_size=label_size)
+        A2_text.bg = Rectangle(height=box_size, width=box_size, color=RED, fill_opacity=0.25)
+        A2 = VGroup(A2_text, A2_text.bg)
+
+        P.next_to(A1, horiz_space * LEFT)
+        A2.next_to(A1, horiz_space * RIGHT)
+
+        P.shift(up_shift * UP)
+        A1.shift(up_shift * UP)
+        A2.shift(up_shift * UP)
+
+        eq = Tex(
+            "$\\varphi_P$ = ", "$\\frac{1}{6}$", "$\\bigg($",
+            "$0$", "$+0$", "$+2$", "$+2$", "$+1$", "$+1$", "$\\bigg)$"
+            "$=1$"
+        )
+        eq.next_to(A1, up_shift * 6 * DOWN)
+        eq.font_size = 80
+
+        self.play(FadeIn(P, A1, A2))
+
+        left = P.get_center()
+        middle = A1.get_center()
+        right = A2.get_center()
+
+
+        pl0 = P.get_corner(DOWN + LEFT)
+        pl1 = P.get_corner(DOWN + RIGHT)
+        pm0 = A1.get_corner(DOWN + LEFT)
+        pm1 = A1.get_corner(DOWN + RIGHT)
+        pr1 = A2.get_corner(DOWN + LEFT)
[…]

### 2022-09-12 src/manim_figures/shapley_value_demo.py
Add snakemake rule for manim

@@ -1,7 +1,7 @@
 from manim import *
 
 
-class Baseline(Scene):
+class ShapleyDemo(Scene):
 
     def construct(self):
 
@@ -17,7 +17,7 @@ class Baseline(Scene):
         Tex.set_default(color=BLACK)
         Brace.set_default(color=BLACK)
 
-        self.next_section("draw objects")
+        self.next_section("draw_objects")
 
         P_text = Tex("$P$", color=BLACK, font_size=label_size)
         P_text.bg = Rectangle(height=box_size, width=box_size, color=BLUE, fill_opacity=0.25)

### 2022-09-12 src/utils/makeutils.py

@@ -1,12 +1,21 @@
 import re
 import os
+import json
+import glob
+import typer
 
 
-def find_input_files(tex_file, add_tex_folder=False):
+app = typer.Typer()
+
+
+@app.command()
+def find_input_files(tex_file: str, add_tex_folder: bool = False):
     """Find all of the files that are included, inputted or includegraphics'
     in a tex file.
     Args:
         tex_file: The path of the tex file.
+        add_tex_folder: Whether to add the folder of the tex file to the
+            paths of the included files.
     Returns:
         List[str]: the list of included files
     """
@@ -26,3 +35,46 @@ def find_input_files(tex_file, add_tex_folder=False):
         paths = [os.path.join(prefix, path) for path in paths]
 
     return paths
+
+
+@app.command()
+def find_manim_sections(manim_file: str):
+    """Find all of the section names in a manim scirpt.
+    Args:
+        tex_file: The path of the tex file.
+    Returns:
+        List[str]: the list of included files
+    """
+
+    with open(manim_file, 'r') as file:
+        manim_contents = file.read()
+
+    patterns = [
+        re.compile(r"self\.next_section\(\"(.*)\"\)"),
+    ]
+
+    sections = sum((pattern.findall(manim_contents) for pattern in patterns), [])
+    return sections
+
+
+@app.command()
+def rename_manim_sections(section_dir: str):
+    """Rename all of the section names in a manim sections folder.
+    Args:
+        section_dir: The path of the section directory.
+    Returns:
+        None
+    """
+
+    os.chdir(section_dir)
+    section_json = glob.glob("*.json")[0]
+    
+    with open(section_json, 'r') as file:
+        section_contents = json.load(file)
+
+    for section in section_contents:
+        os.rename(section["video"], section["name"] + ".mp4")
+
+
+if __name__ == "__main__":
+    app()

### 2022-09-13 src/utils/makeutils.py
Add snakemake rule for creating the presentation

@@ -9,13 +9,14 @@ app = typer.Typer()
 
 
 @app.command()
-def find_input_files(tex_file: str, add_tex_folder: bool = False):
+def find_input_files(tex_file: str, remove_prefix: str = "", print_console: bool = False):
     """Find all of the files that are included, inputted or includegraphics'
     in a tex file.
     Args:
         tex_file: The path of the tex file.
         add_tex_folder: Whether to add the folder of the tex file to the
             paths of the included files.
+        print_console: Whether to print the paths of the included files
     Returns:
         List[str]: the list of included files
     """
@@ -30,20 +31,25 @@ def find_input_files(tex_file: str, add_tex_folder: bool = False):
     ]
 
     paths = sum((pattern.findall(tex_contents) for pattern in patterns), [])
-    if add_tex_folder:
-        prefix = os.path.dirname(tex_file)
-        paths = [os.path.join(prefix, path) for path in paths]
+
+    if remove_prefix:
+        paths = [path.lstrip(remove_prefix) for path in paths]
+
+    if print_console:
+        for path in paths:
+            print(path)
 
     return paths
 
 
 @app.command()
-def find_manim_sections(manim_file: str):
+def find_manim_sections(manim_file: str, print_console: bool = False):
     """Find all of the section names in a manim scirpt.
     Args:
         tex_file: The path of the tex file.
+        print_console: Whether to print the paths of the manim sections
     Returns:
-        List[str]: the list of included files
+        List[str]: the list of manim sections
     """
 
     with open(manim_file, 'r') as file:
@@ -54,6 +60,11 @@ def find_manim_sections(manim_file: str):
     ]
 
     sections = sum((pattern.findall(manim_contents) for pattern in patterns), [])
+
+    if print_console:
+        for section in sections:
+            print(section)
+
     return sections
 
 
@@ -68,12 +79,41 @@ def rename_manim_sections(section_dir: str):
 
     os.chdir(section_dir)
     section_json = glob.glob("*.json")[0]
-    
+
     with open(section_json, 'r') as file:
         section_contents = json.load(file)
 
     for section in section_contents:
         os.rename(section["video"], section["name"] + ".mp4")
+
+
+@app.command()
+def find_videos(qmd_file: str, remove_prefix: str = "", print_console: bool = False):
+    """Find the video paths in a qmd file.
+    Args:
+        qmd_file: The path of the qmd file.
[…]

### 2022-09-13 src/manim_figures/shapley_value_demo.py
Minor fix in the shapley-value animation

@@ -136,8 +136,8 @@ class ShapleyDemo(Scene):
         A2.target.shift(left - middle)
 
         self.play(MoveToTarget(A1), MoveToTarget(A2))
-        self.play(Write(eq[7]))
+        self.play(Write(eq[8]))
 
         self.next_section("final")
         
-        self.play(Write(eq[1]), Write(eq[2]), Write(eq[8]), Write(eq[9]))
+        self.play(Write(eq[1]), Write(eq[2]), Write(eq[9]))

### 2022-09-13 src/presentation/presentation.qmd
Add first set of videos to the presentation

@@
 author: "Martin Stancsics"
-format: revealjs
+format:
+    revealjs:
+        embed-resources: true
+        transition: fade
 bibliography: references.bib
@@
 
+An example game in coalitional form
+
+:::: {.columns}
+
+::: {.column width="50%"}
+Imagine a game with three players:
+
+ - A wholesale producer: $P$
+ - Two downstream resellers: $A_1, A_2$
+
+:::
+
+::: {.column width="10%"}
+:::
+
+::: {.column width="40%"}
+And the following achievable profits:
+
+Coalition | Profits
+----------|---------
+$\{P\},  \{A_i\}$     |  0
+$\{A_1, A_2\}$  | 0  
+$\{P, A_i\}$  | 2 
+$\{P, A_1, A_2\}$  | 3
+:::
+
+::::
+
+## The Shapley-value
+
 Each player gets their expected marginal contribution
@@
 
-::: {.column width="40%"}
-contents...
+::: {.column width="50%"}
+::: {.r-stack}
+
+::: {.fragment}
+   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/draw_objects.mp4" />
+:::
+::: {.fragment}
+   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/value_P12.mp4" />
+:::
+::: {.fragment}
+   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/value_P21.mp4" />
+:::
+::: {.fragment}
+   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/value_2P1.mp4" />
+:::
+::: {.fragment}
+   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/value_1P2.mp4" />
+:::
+::: {.fragment}
+   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/value_12P.mp4" />
+:::
+::: {.fragment}
+   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/value_21P.mp4" />
+:::
+::: {.fragment}
+   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/final.mp4" />
 :::
 
-::: {.column width="60%"}
-contents...
+:::
+:::
+
+::: {.column width="10%"}
+:::
+
+::: {.column width="40%"}
+And the following achievable profits:
+
+Coalition | Profits
+----------|---------
+$\{P\},  \{A_i\}$     |  0
+$\{A_1, A_2\}$  | 0
+$\{P, A_i\}$  | 2 
+$\{P, A_1, A_2\}$  | 3
 :::

### 2022-09-13 src/presentation/presentation.qmd
Add manim figs for the main proposition

@@
 
+:::: {.columns}
+
+::: {.column width="100%"}
+
+Set of all players: $N = \{P, A_1, \dots, A_n\}$
+
+**Assumption**: the platform is the only way for firms to
+reach users and that all $n$ firms are identical
+$$
+v(C) = \begin{cases}
+   0                                           & \text{if } P \notin C \\
+   f\left(\frac{|C \setminus \{P\}|}{n}\right) & \text{otherwise}.
+\end{cases}
+$$
+$\forall\, C \subset N$.
+:::
+
+::::
+
+## Value of the platform
+
+:::: {.columns}
+
+::: {.column width="40%"}
+
+Characteristic function:
+$$
+\scriptsize
+v(C) = \begin{cases}
+   0 \;\text{ if } P \notin C \\
+   f\left(\frac{|C \setminus \{P\}|}{n}\right)
+\end{cases}
+$$
+
+Shapley value:
+$$
+\scriptsize
+\varphi_P^n(f) = \frac{1}{n+1} \sum_{k=0}^{n} f(k)
+$$
+::: {.fragment .fade-in fragment-index=4}
+$$
+\scriptsize
+\to \int_0^1 f(t) \, \mathrm{d}t
+$$
+:::
+
+:::
+
+::: {.column width="60%"}
+
+::: {.r-stack}
+
+::: {.fragment fragment-index=1}
+   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/draw_bars.mp4" />
+:::
+::: {.fragment fragment-index=2}
+   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/add_brace.mp4" />
+:::
+::: {.fragment fragment-index=3}
+   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/more_firms.mp4" />
+:::
+::: {.fragment fragment-index=4}
+   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/continuous_approximation.mp4" />
+:::
+::: {.fragment fragment-index=5}
+   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/surplus_division.mp4" />
+:::
+
+:::
+
+:::
+
+::::
+
+## Main proposition
+
+::: {#prp-baseline}
+Let $f$ be continuous on $[0, 1]$. Then
+
+$$
+\lim_{n \to \infty} \phi_P^n(f) = \int_0^1 f(t) \, \mathrm{d}t
+$$
+:::
+
+Even as firms become infinitesimally small, the platform cannot take all the created value
+
+## Simple comparative statics
+
+:::: {.columns}
+
+::: {.column width="40%"}
+
+Let $f_1, f_2$ continuous on $[0, 1]$. Then
+$$
+f_1(t) \leq f_2(t) \;\forall\, t
+$$
+$$
+\implies \phi_P^\infty(f_1) \leq \phi_P^\infty(f_2)
+$$
+
+In words: the platform gets a larger slice when
+
+  * the firms are substitutes to each other
+  * the platform has intrinsic value
+
+:::
+
+::: {.column width="60%"}
+
+::: {.r-stack}
+
+::: {.fragment fragment-index=1}
+   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/draw_bars.mp4" />
+:::
+::: {.fragment fragment-index=2}
+   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/add_brace.mp4" />
+:::
+::: {.fragment fragment-index=3}
+   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/more_firms.mp4" />
+:::
+::: {.fragment fragment-index=4}
+   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/continuous_approximation.mp4" />
+:::
+::: {.fragment fragment-index=5}
+   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/surplus_division.mp4" />
+:::
+
+:::
+
+:::
+
+::::
+
 # Thank you

### 2022-09-13 src/manim_figures/proposition_main.py

@@ -1,0 +1,77 @@
+from manim import *
+from numpy import sqrt
+
+
+class Baseline(Scene):
+
+    def construct(self):
+
+        self.next_section("draw_bars")
+
+        self.camera.background_color = WHITE
+        Text.set_default(color=BLACK)
+        Line.set_default(color=BLACK)
+        Tex.set_default(color=BLACK)
+        Brace.set_default(color=BLACK)
+        ParametricFunction.set_default(color=BLACK)
+
+        # Create plane
+        ax = plane = Axes(
+            x_range=[0, 1, 0.05],
+            y_range=[0, 1, 0.05],
+            x_length=10,
+            y_length=10
+        )
+        self.play(Create(plane))
+
+        f = plane.plot(lambda x: sqrt(x))
+        area = ax.get_area(f, (0, 1), opacity=0.5, color=BLUE)
+
+        # Discrete number of firms
+        rects = ax.get_riemann_rectangles(f, (0.2, 1), dx=0.2, input_sample_type="right")
+        self.play(DrawBorderThenFill(rects))
+
+        self.next_section("add_brace")
+
+        # Brace
+        brace = BraceBetweenPoints(ax.c2p(0.2, 0), ax.c2p(0.4, 0))
+        label = Tex(r"$\Pr[P \text{ is second}] = \frac{1}{5}$")
+        label.next_to(brace, DOWN)
+        self.play(Create(brace), Write(label))
+
+        self.next_section("more_firms")
+
+        # More firms
+        rects2 = ax.get_riemann_rectangles(f, (0.05, 1), dx=0.05, input_sample_type="right")
+
+        # Brace again
+        brace2 = BraceBetweenPoints(ax.c2p(0.05, 0), ax.c2p(0.1, 0))
+        label2 = Tex(r"$\Pr[P \text{ is second}] = \frac{1}{20}$")
+        label2.next_to(brace2, DOWN)
+
+        self.play(
+            ReplacementTransform(rects, rects2),
+            ReplacementTransform(brace, brace2),
+            ReplacementTransform(label, label2)
+        )
+
+        self.next_section("continuous_approximation")
+
+        # Continuous approximation
+
+        self.play(FadeOut(brace), FadeOut(label), FadeOut(brace2), FadeOut(label2))
+        f_label = ax.get_graph_label(f, "f(t)", direction=RIGHT)
+        self.wait(1)
+        self.play(Create(f), Create(f_label))
[…]

### 2022-09-13 src/presentation/presentation.qmd
Add slides and figs for corollaries

@@
 
-Let $f_1, f_2$ continuous on $[0, 1]$. Then
-$$
-f_1(t) \leq f_2(t) \;\forall\, t
-$$
-$$
-\implies \phi_P^\infty(f_1) \leq \phi_P^\infty(f_2)
-$$
-
-In words: the platform gets a larger slice when
-
-  * the firms are substitutes to each other
-  * the platform has intrinsic value
+::: {.fragment fragment-index=1}
+The platform gets a larger slice when
+:::
+::: {.fragment fragment-index=2}
+  1. the firms are substitutes to each other
+:::
+::: {.fragment fragment-index=3}
+  2. the platform has intrinsic value
+:::
+::: {.fragment fragment-index=4}
+  3. the fringe firms have no outside option
+:::
 
@@
 ::: {.fragment fragment-index=1}
-   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/draw_bars.mp4" />
+   <video data-autoplay src="../../out/manim_figures/videos/corollary_comparative/800p60/sections/draw_graph.mp4" />
 :::
 ::: {.fragment fragment-index=2}
-   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/add_brace.mp4" />
+   <video data-autoplay src="../../out/manim_figures/videos/corollary_comparative/800p60/sections/complements.mp4" />
 :::
 ::: {.fragment fragment-index=3}
-   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/more_firms.mp4" />
+   <video data-autoplay src="../../out/manim_figures/videos/corollary_comparative/800p60/sections/intrinsic_value.mp4" />
 :::
 ::: {.fragment fragment-index=4}
-   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/continuous_approximation.mp4" />
-:::
-::: {.fragment fragment-index=5}
-   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/surplus_division.mp4" />
+   <video data-autoplay src="../../out/manim_figures/videos/corollary_comparative/800p60/sections/outside_option.mp4" />
 :::

### 2022-09-13 src/manim_figures/corollary_comparative.py

@@ -24,22 +24,30 @@ class Baseline(Scene):
         )
         self.play(Create(plane))
 
-        f = plane.plot(lambda x: sqrt(x))
-        area = ax.get_area(f, (0, 1), opacity=0.5, color=BLUE)
+        f = plane.plot(lambda x: x**2)
         f_label = ax.get_graph_label(f, "f(t)", direction=RIGHT)
         self.play(Create(f), Create(f_label))
         self.wait(0.5)
-        self.play(FadeIn(area))
+
+        area = ax.get_area(f, (0, 1), opacity=0.5, color=BLUE)
+        top = ax.plot(lambda x: 1)
+        area_fringe = ax.get_area(f, (0, 1), bounded_graph=top, opacity=0.5, color=RED)
+
+        self.play(Create(top))
+
+        self.play(FadeIn(area), FadeIn(area_fringe))
 
         # Convex function
         self.next_section("complements")
 
-        f2 = ax.plot(lambda x: x**2)
+        f2 = ax.plot(lambda x: sqrt(x))
+        f2_label = ax.get_graph_label(f2, "f(t)", direction=RIGHT)
         area2 = ax.get_area(f2, (0, 1), opacity=0.5, color=BLUE)
         area_fringe2 = ax.get_area(f2, (0, 1), bounded_graph=top, opacity=0.5, color=RED)
 
         self.play(
             ReplacementTransform(f, f2),
+            ReplacementTransform(f_label, f2_label),
             ReplacementTransform(area, area2),
             ReplacementTransform(area_fringe, area_fringe2)
         )
@@ -62,13 +70,14 @@ class Baseline(Scene):
 
         f4 = ax.plot(lambda x: sqrt(0.1 + 0.9*x))
         fo4 = ax.plot(lambda x: sqrt(x) / 2)
+        fo4_label = ax.get_graph_label(fo4, "f_0(t)", direction=DOWN)
         area4 = ax.get_area(f4, (0, 1), bounded_graph=fo4, opacity=0.5, color=BLUE)
         areao4 = ax.get_area(fo4, (0, 1), opacity=0.5, color=RED)
         area_fringe4 = ax.get_area(f4, (0, 1), bounded_graph=top, opacity=0.5, color=RED)
 
         self.play(
             ReplacementTransform(f3, f4),
-            Create(fo4)
+            Create(fo4), Create(fo4_label)
         )
 
         self.play(

### 2022-09-13 src/presentation/presentation.qmd
Update the skeleton of the presentation

@@
         transition: fade
+        toc: true
+        toc-depth: 1
+        toc-title: Agenda
 bibliography: references.bib
 ---
+
+# Intorduction
 
@@
 </style>
-
-# Intorduction
 
@@
 
-#
+# The Shapley-value
 
@@
 
-# The relevant setting
+# Main results
 
@@
 
+::: {.fragment .fade-in fragment-index=2}
 Shapley value:
@@
 $$
+:::
 ::: {.fragment .fade-in fragment-index=4}
@@
 $$
-\lim_{n \to \infty} \phi_P^n(f) = \int_0^1 f(t) \, \mathrm{d}t
+\lim_{n \to \infty} \varphi_P^n(f) = \int_0^1 f(t) \, \mathrm{d}t
 $$
@@
 
-# Thank you
+# Extensions
+
+## Multiple platforms
+
+## Weighted value
+
+# Example application
+
+## Market setup
+
+## Timing of the game
+
+## Results
+
+# Conclusion
+
+## Conclusions
+
+ - Proposed a very tractable way of modeling bargaining applicable to certain important contexts
+ - The results are for upstream-downstream situations, platform settings, and two-sided markets
+ - The outcomes generally concur with intuitive expectations
+ - Even the simple example application provides some interesting insights into hybrid platforms
+
+## Future work
+
+- There is a variety of ways in which the model could be extended (e.g. additional platforms provide some value)
+- The example application could be turned into a proper, full-fledged model
+- A lab experiment about the outcomes of group bargaining could be conducted
+- The model could be applied to other contexts
+
+# Thank you {.unnumbered .unlisted}
 

### 2022-09-13 src/presentation/presentation.qmd
Add multiple platforms extension

@@
 
+:::: {.columns}
+
+::: {.column width="45%"}
+Imagine that
+
+  - There are $m$ platforms
+  - They are perfect substitutes
+:::
+
+::: {.column .fragment width="5%"}
+:::
+
+::: {.column .fragment width="45%"}
+That is, 
+$$
+   v(S) = \begin{cases}
+      0  \; \text{ if } P_i \notin S \; \forall i \\
+      f\left(\frac{\#_A(S)}{n}\right)
+   \end{cases}
+$$
+:::
+
+::::
+
+::: {.notes}
+ - Probabilistic interpretation: the platform has to be the first one in order to have any additional value
+ - As the number of platforms increases, the *total value* they obtain decreases, and the total value firms obtain increases
+:::
+
+::: {#prp-multiple-platforms .fragment}
+## Multiple platforms
+The limit of the Shapley-value (as $n \to \infty$) of each player of type $P$ is
+$$
+\begin{aligned}
+   \varphi_{P_i}^{\infty, m} = \int_0^1 (1-t) ^ {m-1} f(t) \mathrm{d}t .
+\end{aligned}
+$$
+:::
+
 ## Weighted value

### 2022-09-13 src/presentation/presentation.qmd
Add weighted value extension

@@
 
+::: {.fragment}
+ - Endow the game with a weight system
+   - The platform has weight $\lambda$
+   - The firms have weight $1$
+ - Weights can thoughts of as innate bargaining power [@shapley1953additive; @hart1973values]
+:::
+
+::: {#prp-weighted .fragment}
+## Weighted values
+Let $f(t)$ be continuous on $[0, 1]$. Then
+$$
+   \varphi_P^\infty(f, \lambda) = \int_0^1 \underbrace{\lambda t^{\lambda - 1}}_{g(t)} f(t) \mathrm{d}t
+$$
+:::
+
+::: {.notes}
+ - The limit of weighted values is *new*
+ - Corollaries give credence to the bargaining power interpretation
+ - Probabilistic interpretation (weighting permutations)
+:::
+
 # Example application

### 2022-09-13 src/presentation/presentation.qmd
Add notes to most slides

@@
 
+::: {.notes}
+ - Just the intuition in a few words
+:::
+
 ## The Shapley-value
@@
 ::::
+
+::: {.notes}
+ - Two ingredients: players (left) and characteristic function (right)
+ - We don't care about strategies, only about value achieved by coalitions
+:::
 
@@
 
+::: {.notes}
+ - Most direct definition of Shapley value
+ - Closed-form expression
+ - Generally computationally expensive, but not in this case
+:::
+
 ## Why do we care about it?
@@
 
+::: {.notes}
+ - You don't need to think about cooperative game theory in the following part
+ - Think of it as a convenient gain sharing rule with some (cooperative and non-cooperative) microfoundations
+:::
+
 # Main results
+
+::: {.notes}
+ - Very simple setting
+ - Conveys the intuition behind the results
+:::
 
@@
 ::::
+
+::: {.notes}
+ - Not only platforms. Also describes
+   - upstream-downstream setups
+   - generally any setting with an important large palyers and many identical small ones
+:::
 
@@
 
+::: {.notes}
+ - Think of the previous figure with the orderings
+ - Main insight: each ordering with the platform at position $k$ has the same probability
+:::
+
 ## Main proposition
@@
 Even as firms become infinitesimally small, the platform cannot take all the created value
+
+::: {.notes}
+ - The bargaining problem is reduced to a simple integral
+:::
 
@@
 
+::: {.notes}
+ - The comparative statics seem to coincide with one's intuition about bargaining
+:::
+
 # Extensions
+
+::: {.notes}
+ - Skippable if don't have time
+:::
 
@@
 
-::: {.column .fragment width="5%"}
+::: {.column width="5%"}
 :::
@@
 
+::: {.notes}
+ - Intentionally simple model
+ - Most elemnts borrowed from [@anderson2021hybrid]
+:::
+
 ## Market setup
@@
 
+::: {.notes}
+My contributions
+ - Shapley-value is a good fit for platform settings
+ - The continuous case is vary tractable in this speciific setting
+ - Results about the weighted value are mine
+ - Insight that hybrid platforms have higher bargaining power, leading to more distortion
+:::
+
 ## Future work
@@
 
+::: {.notes}
+ - Some extensions are straightforward
+ - However, some situations just don't fit the model
+ - Essentially a plug-and-play approach when one some middle ground between one side taking all the gains
+:::
+
 # Thank you {.unnumbered .unlisted}

### 2022-09-13 src/presentation/presentation.qmd
Add two-sided extension

@@
 TODO
+
+::: {.notes}
+ - Relevance to competition policy
+ - However: today's presentation is mostly theory but if I have time I'll say a few words about applications
+:::
 
@@
 
-::: {.notes}
- - Probabilistic interpretation: the platform has to be the first one in order to have any additional value
- - As the number of platforms increases, the *total value* they obtain decreases, and the total value firms obtain increases
-:::
-
 ::: {#prp-multiple-platforms .fragment}
@@
 $$
-\begin{aligned}
 \varphi_{P_i}^{\infty, m} = \int_0^1 (1-t) ^ {m-1} f(t) \mathrm{d}t .
-\end{aligned}
 $$
+:::
+
+::: {.notes}
+ - Probabilistic interpretation: the platform has to be the first one in order to have any additional value
+ - As the number of platforms increases, the *total value* they obtain decreases, and the total value firms obtain increases
 :::
@@
  - Probabilistic interpretation (weighting permutations)
+:::
+
+## Two-sided bargaining
+
+:::: {.columns}
+
+::: {.column width="45%"}
+Imagine that there are two fringe types ($A_i$ and $B_i$)
+:::
+
+::: {.column width="5%"}
+:::
+
+::: {.column .fragment width="45%"}
+$$
+    v(S) = \begin{cases}
+        0 \; \text{ if } P \notin S \\
+        f\left(\frac{\#_A(S)}{n}, \frac{\#_B(S)}{n}\right).
+    \end{cases}
+$$
+:::
+
+::: {#prp-multiple-platforms .fragment}
+## Two-sided bargaining
+Let $f(a, b)$ continuous on $[0, 1] \times [0, 1]$. Then
+$$
+f(1, 1) = \underbrace{\int_0^1 f(t, t) \mathrm{d}t}_{\varphi_P^\infty(f)} + \underbrace{\int_0^1 t \frac{\partial f(t, t)}{\partial a} \mathrm{d}t}_{\varphi_A^\infty(f)} + \underbrace{\int_0^1 t \frac{\partial f(t, t)}{\partial b} \mathrm{d}t}_{\varphi_B^\infty(f)}
+$$
+:::
+
+::::
+
+::: {.notes}
+ - The other side (e.g. consumers) also participates in the bargaining process
+ - Values are weighted marginal contributions
+ - $P$ does not have to be in the "middle" of the transactions
 :::

### 2022-09-13 src/presentation/presentation.qmd
Add application section to presentation

@@
 
+ - Measure 1 of consumers [à la @anderson2021hybrid]
+   - Each of them buy a unit of products
+   - Logit-type utility function ($u_i = v_i - p_i + \mu \epsilon_i$)
+ - Continuum of firms ($a(t), t \in \mathbb{R}$) with one differentiated product each
+ - Measure 1 of outside options
+ - A platform
+   - necessary for the firms to sell their products
+   - May or may not have its own products
+
+::: {.notes}
+ - Each consumer chooses the products giving them the highest net utility
+ - I don't want to go into the details of the model
+:::
+
 ## Timing of the game
 
+:::: {.columns}
+
+::: {.column width="45%"}
+ 1. Firms decide whether to invest at cost $c$
+ 2. Platform entry fees and decisions are negotiated
+ 3. Firms and platforms set product prices
+ 4. Consumers choose products
+
+**Idea:** 2. stage bargaining is over *final allocations*
+:::
+
+::::
+
+::: {.notes}
+ - Investment decisions are sunk costs
+ - Entry fees are lump sum, do not influence pricing
+ - All players foresee the outcome of the pricing subgame
+:::
+
 ## Results
+
+ - Assuming no collusion in the pricing game, total profits as a function of entering firms are
+$$
+v(N_f) = \frac{N_P B + N_F B}{N_P B + N_F B + 1} \quad \text{ where } B = e^\frac{v - c - \mu}{\mu}
+$$
+ - If entry fees were fixed, $N_P$ would not influence product variety / consumer welfare
+ - However, a higher $N_P$ leads to a better bargaining position for the platform and lower number of entrants
+
+::: {.notes}
+ - Constant, additive markup over marginal cost
+ - Consumer welfare is a function of product variety
+:::
+
+## Results graphically
 

### 2022-09-13 src/manim_figures/corollary_comparative.py
Add manim figures for application
Figure for equilibrium entry

@@ -16,15 +16,15 @@ class Baseline(Scene):
         ParametricFunction.set_default(color=BLACK)
 
         # Create plane
-        ax = plane = Axes(
+        ax = Axes(
             x_range=[0, 1, 0.05],
             y_range=[0, 1, 0.05],
             x_length=10,
             y_length=10
         )
-        self.play(Create(plane))
+        self.play(Create(ax))
 
-        f = plane.plot(lambda x: x**2)
+        f = ax.plot(lambda x: x**2)
         f_label = ax.get_graph_label(f, "f(t)", direction=RIGHT)
         self.play(Create(f), Create(f_label))
         self.wait(0.5)

### 2022-09-13 src/manim_figures/equilibrium_entry.py

@@ -1,0 +1,205 @@
+from manim import *
+from numpy import log
+from scipy.optimize import root_scalar
+
+
+B = 1
+C = 0.2
+
+
+def v(N_F, N_P):
+    return (N_F * B + N_P * B) / (N_F * B + N_P * B + 1)
+
+
+def phi_P(N_F, N_P):
+    return 1 - (log(B * N_P + B * N_F + 1) - log(B * N_P + 1)) / (B * N_F)
+
+
+def phi_F(N_F, N_P):
+    return v(N_F, N_P) - phi_P(N_F, N_P)
+
+
+
+class Equilibrium(Scene):
+
+    def construct(self):
+
+        self.next_section("draw_axes")
+
+        self.camera.background_color = WHITE
+        Text.set_default(color=BLACK)
+        Line.set_default(color=BLACK)
+        Tex.set_default(color=BLACK)
+        Brace.set_default(color=BLACK)
+        ParametricFunction.set_default(color=BLACK)
+
+        # Create plane
+        ax = Axes(
+            x_range=[0, 1.2, 0.05],
+            y_range=[0, 0.7, 0.05],
+            x_length=12,
+            y_length=6
+        )
+        ax.shift(UP * 0.5)
+        self.play(Create(ax))
+
+        # Non-hybrid
+        N_F_bar_val = 0.8
+        N_P_val = 0
+
+        self.next_section("char_func")
+        v_fun = ax.plot(lambda N_f: v(N_f, N_P_val), color=BLUE)
+        v_label = ax.get_graph_label(v_fun, "v(t)", direction=DOWN)
+        self.play(Create(v_fun), Write(v_label))
+
+        # Profit shares
+        self.next_section("fix_players")
+
+        pie_to_share = ax.c2p(N_F_bar_val, v(N_F_bar_val, N_P_val))
+        N_F_bar = ax.get_vertical_line(ax.c2p(N_F_bar_val, 1), color=BLACK)
+        self.play(Create(N_F_bar))
+
+        self.next_section("fix_players")
+        area = ax.get_area(v_fun, (0, N_F_bar_val), opacity=0.5, color=BLUE)
+        self.play(FadeIn(area))
+
+        self.next_section("profit_share_point")
+        div_point = Dot(color=BLUE)
+        div_point.move_to(ax.c2p(N_F_bar_val, phi_P(N_F_bar_val, N_P_val)))
[…]

### 2022-09-13 src/manim_figures/proposition_main.py

@@ -16,15 +16,15 @@ class Baseline(Scene):
         ParametricFunction.set_default(color=BLACK)
 
         # Create plane
-        ax = plane = Axes(
+        ax = Axes(
             x_range=[0, 1, 0.05],
             y_range=[0, 1, 0.05],
             x_length=10,
             y_length=10
         )
-        self.play(Create(plane))
+        self.play(Create(ax))
 
-        f = plane.plot(lambda x: sqrt(x))
+        f = ax.plot(lambda x: sqrt(x))
         area = ax.get_area(f, (0, 1), opacity=0.5, color=BLUE)
 
         # Discrete number of firms

### 2022-09-14 src/presentation/presentation.qmd
Include equilibrium entry graph in presentation

@@
 
+::: {.r-stack}
+::: {.fragment}
+<video data-autoplay src="../../out/manim_figures/videos/equilibrium_entry/800p60/sections/draw_axes.mp4" />
+:::
+::: {.fragment}
+<video data-autoplay src="../../out/manim_figures/videos/equilibrium_entry/800p60/sections/char_func.mp4" />
+:::
+::: {.fragment}
+<video data-autoplay src="../../out/manim_figures/videos/equilibrium_entry/800p60/sections/fix_players.mp4" />
+:::
+::: {.fragment}
+<video data-autoplay src="../../out/manim_figures/videos/equilibrium_entry/800p60/sections/P_profit_share.mp4" />
+:::
+::: {.fragment}
+<video data-autoplay src="../../out/manim_figures/videos/equilibrium_entry/800p60/sections/profit_share_point.mp4" />
+:::
+::: {.fragment}
+<video data-autoplay src="../../out/manim_figures/videos/equilibrium_entry/800p60/sections/hybrid_case.mp4" />
+:::
+::: {.fragment}
+<video data-autoplay src="../../out/manim_figures/videos/equilibrium_entry/800p60/sections/switch_to_phi_F.mp4" />
+:::
+::: {.fragment}
+<video data-autoplay src="../../out/manim_figures/videos/equilibrium_entry/800p60/sections/phi_F_functions.mp4" />
+:::
+::: {.fragment}
+<video data-autoplay src="../../out/manim_figures/videos/equilibrium_entry/800p60/sections/cost_function.mp4" />
+:::
+::: {.fragment}
+<video data-autoplay src="../../out/manim_figures/videos/equilibrium_entry/800p60/sections/equilibrium.mp4" />
+:::
+::: {.fragment}
+<video data-autoplay src="../../out/manim_figures/videos/equilibrium_entry/800p60/sections/N_F_loss.mp4" />
+:::
+
+:::
+
 # Conclusion

### 2022-09-14 src/manim_figures/corollary_comparative.py
Slightly improve manim figures

@@ -22,7 +22,9 @@ class Baseline(Scene):
             x_length=10,
             y_length=10
         )
-        self.play(Create(ax))
+        ax_label = ax.get_axis_labels(x_label=r"t")
+
+        self.play(Create(ax), Write(ax_label))
 
         f = ax.plot(lambda x: x**2)
         f_label = ax.get_graph_label(f, "f(t)", direction=RIGHT)

### 2022-09-14 src/manim_figures/equilibrium_entry.py

@@ -41,14 +41,16 @@ class Equilibrium(Scene):
             y_length=6
         )
         ax.shift(UP * 0.5)
-        self.play(Create(ax))
+        ax_label = ax.get_axis_labels(x_label=r"N_F")
+
+        self.play(Create(ax), Write(ax_label))
 
         # Non-hybrid
         N_F_bar_val = 0.8
         N_P_val = 0
 
         self.next_section("char_func")
-        v_fun = ax.plot(lambda N_f: v(N_f, N_P_val), color=BLUE)
+        v_fun = ax.plot(lambda N_f: v(N_f, N_P_val), color=BLUE_D)
         v_label = ax.get_graph_label(v_fun, "v(t)", direction=DOWN)
         self.play(Create(v_fun), Write(v_label))
 
@@ -56,15 +58,18 @@ class Equilibrium(Scene):
         self.next_section("fix_players")
 
         pie_to_share = ax.c2p(N_F_bar_val, v(N_F_bar_val, N_P_val))
-        N_F_bar = ax.get_vertical_line(ax.c2p(N_F_bar_val, 1), color=BLACK)
-        self.play(Create(N_F_bar))
+        N_F_bar = ax.get_vertical_line(ax.c2p(N_F_bar_val, 0.7), color=BLACK)
+        N_F_bar_label = MathTex(r"\bar{N}_F")
+        N_F_bar_label.next_to(N_F_bar, DOWN)
 
-        self.next_section("fix_players")
-        area = ax.get_area(v_fun, (0, N_F_bar_val), opacity=0.5, color=BLUE)
+        self.play(Create(N_F_bar), Write(N_F_bar_label))
+
+        self.next_section("P_profit_share")
+        area = ax.get_area(v_fun, (0, N_F_bar_val), opacity=0.5, color=BLUE_D)
         self.play(FadeIn(area))
 
         self.next_section("profit_share_point")
-        div_point = Dot(color=BLUE)
+        div_point = Dot(color=BLUE_D)
         div_point.move_to(ax.c2p(N_F_bar_val, phi_P(N_F_bar_val, N_P_val)))
         self.play(ReplacementTransform(area, div_point))
 
@@ -85,15 +90,15 @@ class Equilibrium(Scene):
         self.next_section("hybrid_case")
         N_P_val_h = 0.2
 
[…]

### 2022-09-14 src/manim_figures/proposition_main.py

@@ -22,7 +22,9 @@ class Baseline(Scene):
             x_length=10,
             y_length=10
         )
-        self.play(Create(ax))
+        ax_label = ax.get_axis_labels(x_label=r"t")
+
+        self.play(Create(ax), Write(ax_label))
 
         f = ax.plot(lambda x: sqrt(x))
         area = ax.get_area(f, (0, 1), opacity=0.5, color=BLUE)

### 2022-09-14 src/manim_figures/shapley_value_demo.py

@@ -20,7 +20,7 @@ class ShapleyDemo(Scene):
         self.next_section("draw_objects")
 
         P_text = Tex("$P$", color=BLACK, font_size=label_size)
-        P_text.bg = Rectangle(height=box_size, width=box_size, color=BLUE, fill_opacity=0.25)
+        P_text.bg = Rectangle(height=box_size, width=box_size, color=BLUE_D, fill_opacity=0.25)
         P = VGroup(P_text, P_text.bg)
 
         A1_text = Tex("$A_1$", color=BLACK, font_size=label_size)

### 2022-09-14 src/presentation/presentation.qmd
Add motivation and fix typos

@@
 
-TODO
+ - Bargaining between participants is rather overlooked in platform settings
+   - Most papers implicitly assume take-it-or-leave-it offers
+ - The use of cooperative bargaining concepts is not widespread in IO
+   - Although they are well established in certain subfields, such as upstream-downstream markets
+ - Most papers only consider finite-player games
+   - Modeling the small players as a continuum simplifies analysis
 
@@
  - You don't need to think about cooperative game theory in the following part
- - Think of it as a convenient gain sharing rule with some (cooperative and non-cooperative) microfoundations
+ - Think of it as a convenient gain sharing rule with some (cooperative and non-cooperative) micro-foundations
 :::
@@
    - upstream-downstream setups
-   - generally any setting with an important large palyers and many identical small ones
+   - generally any setting with an important large players and many identical small ones
 :::
@@
 ::: {.notes}
- - Skippable if don't have time
+ - Can be skipped if don't have time
 :::
@@
  - Intentionally simple model
- - Most elemnts borrowed from [@anderson2021hybrid]
+ - Most elements borrowed from [@anderson2021hybrid]
 :::
@@
  - Shapley-value is a good fit for platform settings
- - The continuous case is vary tractable in this speciific setting
+ - The continuous case is vary tractable in this specific setting
  - Results about the weighted value are mine

### 2022-09-14 src/presentation/presentation.qmd
Add manim figure about the timing of the game

@@
 ::: {.column width="45%"}
+::: {.fragment .fade-in fragment-index=2}
  1. Firms decide whether to invest at cost $c$
+:::
+::: {.fragment .fade-in fragment-index=3}
  2. Platform entry fees and decisions are negotiated
- 3. Firms and platforms set product prices
- 4. Consumers choose products
+:::
+::: {.fragment .fade-in fragment-index=4}
+ 3. Firms and platform set product prices, consumers buy products
+:::
 
+::: {.fragment .fade-in fragment-index=6}
 **Idea:** 2. stage bargaining is over *final allocations*
+:::
+:::
+
+::: {.column width="55%"}
+::: {.r-stack}
+
+::: {.fragment fragment-index=1}
+<video data-autoplay src="../../out/manim_figures/videos/market_structure/800p60/sections/draw_objects.mp4" />
+:::
+::: {.fragment fragment-index=2}
+<video data-autoplay src="../../out/manim_figures/videos/market_structure/800p60/sections/investment.mp4" />
+:::
+::: {.fragment fragment-index=3}
+<video data-autoplay src="../../out/manim_figures/videos/market_structure/800p60/sections/platform_entry.mp4" />
+:::
+::: {.fragment fragment-index=4}
+<video data-autoplay src="../../out/manim_figures/videos/market_structure/800p60/sections/pricing_game.mp4" />
+:::
+::: {.fragment fragment-index=5}
+<video data-autoplay src="../../out/manim_figures/videos/market_structure/800p60/sections/everyone_enters.mp4" />
+:::
+::: {.fragment fragment-index=6}
+<video data-autoplay src="../../out/manim_figures/videos/market_structure/800p60/sections/shapley_values.mp4" />
+:::
+
+:::
 :::

### 2022-09-14 src/manim_figures/market_structure.py

@@ -1,0 +1,117 @@
+from manim import *
+
+
+NUM_FIRMS = 4
+
+
+class MarketStructure(Scene):
+
+    def construct(self):
+
+        self.camera.background_color = WHITE
+
+        self.next_section("draw_objects")
+
+        firms = []
+        for i in range(NUM_FIRMS):
+            firm_text = Tex(f"$A_{i + 1}$", color=BLACK, font_size=80)
+            firm_text.bg = Rectangle(height=1.5, width=1.5, color=RED, fill_opacity=0.25)
+            firm = VGroup(firm_text, firm_text.bg)
+            firms.append(firm)
+
+        platform_text = Tex("$P$", color=BLACK, font_size=80)
+        platform_text.bg = Rectangle(height=2.5, width=2.5, color=BLUE_D, fill_opacity=0.25)
+        platform = VGroup(platform_text, platform_text.bg)
+
+        consumers = Tex("Consumers", color=BLACK, font_size=80)
+        consumers.bg = Rectangle(height=1.5, width=5, color=GREEN, fill_opacity=0.25)
+        consumers = VGroup(consumers, consumers.bg)
+
+        firms_group = VGroup(*firms)
+
+        all_players = VGroup(firms_group, platform, consumers)
+
+        firms_group.arrange(RIGHT, buff=2)
+        all_players.arrange(DOWN, buff=2)
+
+        self.play(FadeIn(all_players))
+
+        # Equations
+        consumer_eq = MathTex(r"-\sum p_i", color=BLACK)
+        consumer_eq.next_to(consumers, DOWN)
+
+        platform_eq = MathTex(r"\sum F_j", r"+ \pi_P", color=BLACK)
+        platform_eq.next_to(platform, LEFT)
+        platform_brace = Brace(platform_eq, UP, color=BLACK)
+        platform_brace_label = platform_brace.get_text(r"$\varphi_{P}$")
+        platform_brace_label.set_color(BLACK)
+        platform_brace_gr = VGroup(platform_brace, platform_brace_label)
+
+        firm_eqs = []
+        firm_shapleys = []
+        for j, firm in enumerate(firms):
+            firm_eq = MathTex(r"-c", f"-F_{j+1}", f"+ \\pi_{j+1}", color=BLACK)
+            firm_eq.next_to(firm, UP)
+            firm_eqs.append(firm_eq)
+            brace = Brace(firm_eq[1:], UP, color=BLACK)
[…]

### 2022-09-14 src/presentation/presentation.qmd
Add literature review

@@
  - Balance generality and having useful results
+
+## Related literature
+
+ - Shapley-value as a bargaining outcome
+   - [@gul1989bargaining; @winter1994demand; @hart1996bargaining; @stole1996intra]
+ - Cooperative bargaining in IO models
+   - [@billera1978internal; @hart1990property; @levy1997individual; @segal2003collusion; @inderst2003bargaining; @montez2007downstream]
+ - Values of oceanic games
+   - [@hart1973values; @fogelman1980asymptotic]
+ - Hybrid platforms
+   - [@anderson2021hybrid; @hagiu2022should]
 

### 2022-09-14 src/manim_figures/equilibrium_entry.py
Improve manim figure

@@ -41,7 +41,8 @@ class Equilibrium(Scene):
             y_length=6
         )
         ax.shift(UP * 0.5)
-        ax_label = ax.get_axis_labels(x_label=r"N_F")
+        ax_label = MathTex("N_f", color=BLACK)
+        ax_label.next_to(ax.get_corner(DOWN + RIGHT), DOWN)
 
         self.play(Create(ax), Write(ax_label))
 
@@ -144,10 +145,10 @@ class Equilibrium(Scene):
         # phi_F functions
         self.next_section("phi_F_functions")
 
-        phi_F_fun = ax.plot(lambda N_f: phi_F(N_f, N_P_val), color=BLUE_D, x_range=(0.05, 2))
+        phi_F_fun = ax.plot(lambda N_f: phi_F(N_f, N_P_val), color=BLUE_D, x_range=(0.02, 1.2))
         phi_F_fun_label = ax.get_graph_label(phi_F_fun, r"\varphi_F(v)", direction=UP)
 
-        phi_F_h_fun = ax.plot(lambda N_f: phi_F(N_f, N_P_val_h), color=RED_D, x_range=(0.05, 2))
+        phi_F_h_fun = ax.plot(lambda N_f: phi_F(N_f, N_P_val_h), color=RED_D, x_range=(0.02, 1.2))
         phi_F_h_fun_label = ax.get_graph_label(phi_F_h_fun, r"\varphi_F^h(v)", direction=DOWN)
 
         self.play(
@@ -155,15 +156,14 @@ class Equilibrium(Scene):
         )
         self.play(
             ReplacementTransform(phi_F_point, phi_F_fun), ReplacementTransform(phi_F_point_h, phi_F_h_fun),
-            ReplacementTransform(label_phi_F, phi_F_fun_label), ReplacementTransform(label_phi_F_h, phi_F_h_fun_label),
-            FadeOut(ax_label)
+            ReplacementTransform(label_phi_F, phi_F_fun_label), ReplacementTransform(label_phi_F_h, phi_F_h_fun_label)
         )
 
         # Cost function
         self.next_section("cost_function")
 
         cost_fun = ax.plot(lambda N_F: C * N_F, color=BLACK)
-        cost_fun_label = ax.get_graph_label(cost_fun, "C * N_F", direction=UP)
+        cost_fun_label = ax.get_graph_label(cost_fun, "C * N_F", direction=LEFT+UP)
 
         self.play(
             Create(cost_fun), Write(cost_fun_label)

### 2022-09-14 src/presentation/presentation.qmd
Add notes to the related literature

@@
 
+::: {.notes}
+ - Further evidence that the Shapley-value is a good bargaining outcome
+ - Cooperative bargaining solutions in IO models are finite-player
+ - The asymptotics of the weighted value are unknown
+ - The literature on hybrid platforms is very recent
+ - Shapley-value in a platform setting is new
+:::
+
 ## Preview of results
@@
 
-::: {.column width="50%"}
+::: {.column .fragment width="50%"}
 Imagine a game with three players:
@@
 
-::: {.column width="40%"}
+::: {.column .fragment width="40%"}
 And the following achievable profits:

### 2022-09-15 src/manim_figures/shapley_value_demo.py
Fix Shapley-value example

@@ -40,8 +40,8 @@ class ShapleyDemo(Scene):
 
         eq = Tex(
             "$\\varphi_P$ = ", "$\\frac{1}{6}$", "$\\bigg($",
-            "$0$", "$+0$", "$+2$", "$+2$", "$+1$", "$+1$", "$\\bigg)$"
-            "$=1$"
+            "$0$", "$+0$", "$+2$", "$+2$", "$+4$", "$+4$", "$\\bigg)$"
+            "$=2$"
         )
         eq.next_to(A1, up_shift * 6 * DOWN)
         eq.font_size = 80
@@ -88,11 +88,17 @@ class ShapleyDemo(Scene):
 
         brace_2 = BraceBetweenPoints(pl0, pm1)
         brace_2.shift(DOWN)
-        brace_2_text = brace_2.get_text("2")
+        brace_2_text = brace_2.get_text("3")
         brace_2_text.font_size = 80
 
+        brace_1_text_new = brace_1.get_text("1")
+        brace_1_text_new.font_size = 80
+
         self.play(MoveToTarget(P), MoveToTarget(A2))
-        self.play(FadeIn(brace_2), FadeIn(brace_2_text))
+        self.play(
+            ReplacementTransform(brace_1_text, brace_1_text_new),
+            FadeIn(brace_2), FadeIn(brace_2_text)
+        )
         self.play(Write(eq[5]))
 
         self.next_section("value_1P2")
@@ -118,13 +124,13 @@ class ShapleyDemo(Scene):
 
         brace_3 = BraceBetweenPoints(pl0, pr1)
         brace_3.shift(DOWN)
-        brace_3_text = brace_3.get_text("3")
+        brace_3_text = brace_3.get_text("6")
         brace_3_text.font_size = 80
 
         self.play(
             MoveToTarget(P), MoveToTarget(A2),
             Transform(brace_1, brace_2_up), Transform(brace_2, brace_3),
-            Transform(brace_1_text, brace_2_up_text), Transform(brace_2_text, brace_3_text)
+            Transform(brace_1_text_new, brace_2_up_text), Transform(brace_2_text, brace_3_text)
         )
         self.play(Write(eq[7]))
 

### 2022-09-15 src/presentation/presentation.qmd
Fix Shapley-value example
Speed up main proposition figure

@@
 
- - A wholesale producer: $P$
- - Two downstream resellers: $A_1, A_2$
+ - Two producers: $A_1, A_2$
+   - can each make \$1 on their own
+ - A platform: $P$
+   - Triples the firms' profits
 
@@
 ::: {.column .fragment width="40%"}
-And the following achievable profits:
-
 Coalition | Profits
 ----------|---------
-$\{P\},  \{A_i\}$     |  0
-$\{A_1, A_2\}$  | 0  
-$\{P, A_i\}$  | 2 
-$\{P, A_1, A_2\}$  | 3
+$\{P\}$     |  0
+$\{A_i\}$   | 1
+$\{A_1, A_2\}$  | 2
+$\{P, A_i\}$  | 3
+$\{P, A_1, A_2\}$  | 6
 :::
@@
 ::: {.column width="40%"}
-And the following achievable profits:
-
 Coalition | Profits
 ----------|---------
-$\{P\},  \{A_i\}$     |  0
-$\{A_1, A_2\}$  | 0
-$\{P, A_i\}$  | 2 
-$\{P, A_1, A_2\}$  | 3
+$\{P\}$     |  0
+$\{A_i\}$   | 1
+$\{A_1, A_2\}$  | 2
+$\{P, A_i\}$  | 3
+$\{P, A_1, A_2\}$  | 6
 :::
@@
 :::
-::: {.fragment .fade-in fragment-index=4}
+::: {.fragment .fade-in fragment-index=5}
 $$
@@
 :::
-::: {.fragment fragment-index=5}
+::: {.fragment fragment-index=6}
    <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/surplus_division.mp4" />

### 2022-09-15 src/manim_figures/proposition_main.py

@@ -63,7 +63,6 @@ class Baseline(Scene):
 
         self.play(FadeOut(brace), FadeOut(label), FadeOut(brace2), FadeOut(label2))
         f_label = ax.get_graph_label(f, "f(t)", direction=RIGHT)
-        self.wait(1)
         self.play(Create(f), Create(f_label))
         self.play(FadeOut(rects2), FadeIn(area))
 

### 2022-09-15 src/presentation/presentation.qmd
Switch to mathjax 3 for better output

@@
         embed-resources: true
+        html-math-method: mathjax
         transition: fade

### 2022-09-15 src/presentation/presentation.qmd
Add mathjax setup to header

--- 2022-09-15 src/presentation/presentation.qmd
@@
         toc-title: Agenda
+        header-includes: |
+          <script>
+            MathJax = {
+                loader: {load: ["input/tex", "output/svg"]}
+                svg: {
+                  scale: 0.9
+                },
+                chtml: {
+                  scale: 0.9
+                }
+            };
+          </script>
 bibliography: references.bib
@@
 
-# Intorduction
+# Introduction
 
@@
 ::: {.fragment .fade-in fragment-index=6}
-**Idea:** 2. stage bargaining is over *final allocations*
+**Idea:** stage 2 bargaining is over *final allocations*
 :::

### 2022-11-16 src/presentation/presentation.qmd
Fix v(N_F) in presentation

@@
 $$
-v(N_f) = \frac{N_P B + N_F B}{N_P B + N_F B + 1} \quad \text{ where } B = e^\frac{v - c - \mu}{\mu}
+v(N_F) = \mu \frac{N_P B + N_F B}{N_P B + N_F B + 1} \quad \text{ where } B = e^\frac{v - c - \mu}{\mu}
 $$

### 2022-11-17 src/presentation/micro_seminar_talk.qmd
Highlight differences compared to Anderson-Bedre

--- 2022-11-16 src/presentation/presentation.qmd
@@
  - Axiomatic reasoning
-    - The Shapley-value is the only sharing rule that is efficient, symmetric, linear, and satisfies the null player axiom [@shapley1953additive]
+    - The Shapley-value is the only sharing rule that satisfies a nice set of axioms (efficiency, symmetry, linearity, dummy player axiom) [@shapley1953additive]
  - Bargaining foundations
-    - The value arises of the subgame-perfect equilibrium of various alternating-offer bargaining games [e.g.
+    - The value arises as the subgame-perfect equilibrium of various alternating-offer bargaining games [e.g.
 @gul1989bargaining; @winter1994demand; @hart1996bargaining; @stole1996intra; @inderst2003bargaining]
@@
 
-# Extensions
-
-::: {.notes}
- - Can be skipped if don't have time
-:::
-
-## Multiple platforms
-
-:::: {.columns}
-
-::: {.column width="45%"}
-Imagine that
-
-  - There are $m$ platforms
-  - They are perfect substitutes
-:::
-
-::: {.column width="5%"}
-:::
-
-::: {.column .fragment width="45%"}
-That is, 
-$$
-   v(S) = \begin{cases}
-      0  \; \text{ if } P_i \notin S \; \forall i \\
-      f\left(\frac{\#_A(S)}{n}\right)
-   \end{cases}
-$$
-:::
-
-::::
-
-::: {#prp-multiple-platforms .fragment}
-## Multiple platforms
-The limit of the Shapley-value (as $n \to \infty$) of each player of type $P$ is
-$$
-\varphi_{P_i}^{\infty, m} = \int_0^1 (1-t) ^ {m-1} f(t) \mathrm{d}t .
-$$
-:::
-
-::: {.notes}
- - Probabilistic interpretation: the platform has to be the first one in order to have any additional value
- - As the number of platforms increases, the *total value* they obtain decreases, and the total value firms obtain increases
-:::
-
-## Weighted value
-
-::: {.fragment}
- - Endow the game with a weight system
-   - The platform has weight $\lambda$
-   - The firms have weight $1$
- - Weights can thoughts of as innate bargaining power [@shapley1953additive; @hart1973values]
-:::
-
-::: {#prp-weighted .fragment}
-## Weighted values
-Let $f(t)$ be continuous on $[0, 1]$. Then
-$$
-\varphi_P^\infty(f, \lambda) = \int_0^1 \underbrace{\lambda t^{\lambda - 1}}_{g(t)} f(t) \mathrm{d}t
-$$
-:::
-
-::: {.notes}
- - The limit of weighted values is *new*
- - Corollaries give credence to the bargaining power interpretation
- - Probabilistic interpretation (weighting permutations)
-:::
-
-## Two-sided bargaining
-
-:::: {.columns}
-
-::: {.column width="45%"}
-Imagine that there are two fringe types ($A_i$ and $B_i$)
-:::
-
-::: {.column width="5%"}
-:::
-
-::: {.column .fragment width="45%"}
-$$
-    v(S) = \begin{cases}
-        0 \; \text{ if } P \notin S \\
-        f\left(\frac{\#_A(S)}{n}, \frac{\#_B(S)}{n}\right).
-    \end{cases}
-$$
-:::
-
-::: {#prp-multiple-platforms .fragment}
-## Two-sided bargaining
-Let $f(a, b)$ continuous on $[0, 1] \times [0, 1]$. Then
-$$
-f(1, 1) = \underbrace{\int_0^1 f(t, t) \mathrm{d}t}_{\varphi_P^\infty(f)} + \underbrace{\int_0^1 t \frac{\partial f(t, t)}{\partial a} \mathrm{d}t}_{\varphi_A^\infty(f)} + \underbrace{\int_0^1 t \frac{\partial f(t, t)}{\partial b} \mathrm{d}t}_{\varphi_B^\infty(f)}
-$$
-:::
-
-::::
-
-::: {.notes}
- - The other side (e.g. consumers) also participates in the bargaining process
- - Values are weighted marginal contributions
- - $P$ does not have to be in the "middle" of the transactions
-:::
-
 # Example application
 
-::: {.notes}
+## The model
+
  - Intentionally simple model
  - Most elements borrowed from [@anderson2021hybrid]
-:::
+ - Main changes:
 
@@
 
-## Timing of the game
+## Hybrid platforms with lump-sum fees
+
+:::: {.columns}
+
+::: {.column width="45%"}
+::: {.fragment .fade-in fragment-index=2}
+ 1. Platforms set lump-sum fee $F$
+:::
+::: {.fragment .fade-in fragment-index=3}
+ 2. Firms decide whether to enter at cost $c + F$
+:::
+::: {.fragment .fade-in fragment-index=4}
+ 3. Firms and platform set product prices, consumers buy products
+:::
+:::
+
+::: {.column width="55%"}
+::: {.r-stack}
+
+::: {.fragment fragment-index=1}
+<video data-autoplay src="../../out/manim_figures/videos/market_structure_benchmark/800p60/sections/draw_objects.mp4" />
+:::
+::: {.fragment fragment-index=3}
+<video data-autoplay src="../../out/manim_figures/videos/market_structure_benchmark/800p60/sections/platform_entry.mp4" />
+:::
+::: {.fragment fragment-index=4}
+<video data-autoplay src="../../out/manim_figures/videos/market_structure_benchmark/800p60/sections/pricing_game.mp4" />
+:::
+
+:::
+:::
+
+::::
+
+## Outcomes
+
+ - Constant additive markup $\implies$ profit $\propto$ market share
+ - Per unit fringe profit
+     $$ \frac{\mu B}{N_P B + N_F B + 1} \quad \text{where } B = \frac{v - c - \mu}{\mu} $$
+ - Free entry
+     $$ N_F^* = \frac{\mu B}{F + c} - N_P - \frac{1}{B} $$
+
+## Outcomes - the platform's decision
+
+ - Platform's profit: own sales plus entry fees
+     $$ \pi_P = F N_F^* + \frac{\mu N_P B}{N_P B + N_F^* B + 1} $$
+ - In a pure marketplace the second term is zero
+ - Here, second term is increasing in $N_P$
+ - $\implies$ higher fee and lower entry in the hybrid case
+
+## Model with bargaining
 
@@
 
- - Proposed a very tractable way of modeling bargaining applicable to certain important contexts
- - The results are for upstream-downstream situations, platform settings, and two-sided markets
- - The outcomes generally concur with intuitive expectations
- - Even the simple example application provides some interesting insights into hybrid platforms
+Contributions
+
+ - A tractable way of modeling bargaining applicable to important contexts
+ - Interesting insights into hybrid platforms
+
+Future work
+
+- The example application could be turned into a proper, full-fledged model
+- A lab experiment about the outcomes of group bargaining
 
@@
  - Insight that hybrid platforms have higher bargaining power, leading to more distortion
-:::
-
-## Future work
-
-- There is a variety of ways in which the model could be extended (e.g. additional platforms provide some value)
-- The example application could be turned into a proper, full-fledged model
-- A lab experiment about the outcomes of group bargaining could be conducted
-- The model could be applied to other contexts
-
-::: {.notes}
- - Some extensions are straightforward
- - However, some situations just don't fit the model
+ - Some extensions are straightforward, but some situations just don't fit the model
  - Essentially a plug-and-play approach when one some middle ground between one side taking all the gains
 :::
-
-# Thank you {.unnumbered .unlisted}
 
@@
 :::
+
+# Appendix
+
+::: {.notes}
+ - Can be skipped if don't have time
+:::
+
+## Multiple platforms
+
+:::: {.columns}
+
+::: {.column width="45%"}
+Imagine that
+
+  - There are $m$ platforms
+  - They are perfect substitutes
+:::
+
+::: {.column width="5%"}
+:::
+
+::: {.column .fragment width="45%"}
+That is, 
+$$
+   v(S) = \begin{cases}
+      0  \; \text{ if } P_i \notin S \; \forall i \\
+      f\left(\frac{\#_A(S)}{n}\right)
+   \end{cases}
+$$
+:::
+
+::::
+
+::: {#prp-multiple-platforms .fragment}
+## Multiple platforms
+The limit of the Shapley-value (as $n \to \infty$) of each player of type $P$ is
+$$
+\varphi_{P_i}^{\infty, m} = \int_0^1 (1-t) ^ {m-1} f(t) \mathrm{d}t .
+$$
+:::
+
+::: {.notes}
+ - Probabilistic interpretation: the platform has to be the first one in order to have any additional value
+ - As the number of platforms increases, the *total value* they obtain decreases, and the total value firms obtain increases
+:::
+
+## Weighted value
+
+::: {.fragment}
+ - Endow the game with a weight system
+   - The platform has weight $\lambda$
+   - The firms have weight $1$
+ - Weights can thoughts of as innate bargaining power [@shapley1953additive; @hart1973values]
+:::
+
+::: {#prp-weighted .fragment}
+## Weighted values
+Let $f(t)$ be continuous on $[0, 1]$. Then
+$$
+\varphi_P^\infty(f, \lambda) = \int_0^1 \underbrace{\lambda t^{\lambda - 1}}_{g(t)} f(t) \mathrm{d}t
+$$
+:::
+
+::: {.notes}
+ - The limit of weighted values is *new*
+ - Corollaries give credence to the bargaining power interpretation
+ - Probabilistic interpretation (weighting permutations)
+:::
+
+## Two-sided bargaining
+
+:::: {.columns}
+
+::: {.column width="45%"}
+Imagine that there are two fringe types ($A_i$ and $B_i$)
+:::
+
+::: {.column width="5%"}
+:::
+
+::: {.column .fragment width="45%"}
+$$
+    v(S) = \begin{cases}
+        0 \; \text{ if } P \notin S \\
+        f\left(\frac{\#_A(S)}{n}, \frac{\#_B(S)}{n}\right).
+    \end{cases}
+$$
+:::
+
+::: {#prp-multiple-platforms .fragment}
+## Two-sided bargaining
+Let $f(a, b)$ continuous on $[0, 1] \times [0, 1]$. Then
+$$
+f(1, 1) = \underbrace{\int_0^1 f(t, t) \mathrm{d}t}_{\varphi_P^\infty(f)} + \underbrace{\int_0^1 t \frac{\partial f(t, t)}{\partial a} \mathrm{d}t}_{\varphi_A^\infty(f)} + \underbrace{\int_0^1 t \frac{\partial f(t, t)}{\partial b} \mathrm{d}t}_{\varphi_B^\infty(f)}
+$$
+:::
+
+::::
+
+::: {.notes}
+ - The other side (e.g. consumers) also participates in the bargaining process
+ - Values are weighted marginal contributions
+ - $P$ does not have to be in the "middle" of the transactions
+:::

### 2022-11-17 src/manim_figures/market_structure_benchmark.py

@@ -1,0 +1,99 @@
+from manim import *
+
+
+NUM_FIRMS = 4
+
+
+class MarketStructure(Scene):
+
+    def construct(self):
+
+        self.camera.background_color = WHITE
+
+        self.next_section("draw_objects")
+
+        firms = []
+        for i in range(NUM_FIRMS):
+            firm_text = Tex(f"$A_{i + 1}$", color=BLACK, font_size=80)
+            firm_text.bg = Rectangle(height=1.5, width=1.5, color=RED, fill_opacity=0.25)
+            firm = VGroup(firm_text, firm_text.bg)
+            firms.append(firm)
+
+        platform_text = Tex("$P$", color=BLACK, font_size=80)
+        platform_text.bg = Rectangle(height=2.5, width=2.5, color=BLUE_D, fill_opacity=0.25)
+        platform = VGroup(platform_text, platform_text.bg)
+
+        consumers = Tex("Consumers", color=BLACK, font_size=80)
+        consumers.bg = Rectangle(height=1.5, width=5, color=GREEN, fill_opacity=0.25)
+        consumers = VGroup(consumers, consumers.bg)
+
+        firms_group = VGroup(*firms)
+
+        all_players = VGroup(firms_group, platform, consumers)
+
+        firms_group.arrange(RIGHT, buff=2)
+        all_players.arrange(DOWN, buff=2)
+
+        self.play(FadeIn(all_players))
+
+        # Equations
+        consumer_eq = MathTex(r"-\sum p_i", color=BLACK)
+        consumer_eq.next_to(consumers, DOWN)
+
+        platform_eq = MathTex(r"\sum F_j", r"+ \pi_P", color=BLACK)
+        platform_eq.next_to(platform, LEFT)
+        platform_brace = Brace(platform_eq, UP, color=BLACK)
+        platform_brace_label = platform_brace.get_text(r"$\varphi_{P}$")
+        platform_brace_label.set_color(BLACK)
+        platform_brace_gr = VGroup(platform_brace, platform_brace_label)
+
+        firm_eqs = []
+        firm_shapleys = []
+        for j, firm in enumerate(firms):
+            firm_eq = MathTex(r"-c", f"-F_{j+1}", f"+ \\pi_{j+1}", color=BLACK)
+            firm_eq.next_to(firm, UP)
+            firm_eqs.append(firm_eq)
+            brace = Brace(firm_eq[1:], UP, color=BLACK)
[…]

### 2022-11-17 src/manim_figures/equilibrium_entry.py
Improve the application animation

@@ -66,13 +66,16 @@ class Equilibrium(Scene):
         self.play(Create(N_F_bar), Write(N_F_bar_label))
 
         self.next_section("P_profit_share")
+        top_line = ax.get_horizontal_line(pie_to_share, color=BLACK)
+        top_graph = ax.plot(lambda x: v(N_F_bar_val, N_P_val))
+        area_f = ax.get_area(v_fun, (0, N_F_bar_val), bounded_graph=top_graph, opacity=0.5, color=YELLOW_D)
         area = ax.get_area(v_fun, (0, N_F_bar_val), opacity=0.5, color=BLUE_D)
-        self.play(FadeIn(area))
+        self.play(Create(top_line))
+        self.play(FadeIn(area), FadeIn(area_f))
 
         self.next_section("profit_share_point")
         div_point = Dot(color=BLUE_D)
         div_point.move_to(ax.c2p(N_F_bar_val, phi_P(N_F_bar_val, N_P_val)))
-        self.play(ReplacementTransform(area, div_point))
 
         brace_P = BraceBetweenPoints(ax.c2p(N_F_bar_val, 0), div_point.get_bottom())
         label_P = Tex(r"$\varphi_P(v)$")
@@ -83,9 +86,15 @@ class Equilibrium(Scene):
         label_F.next_to(brace_F, RIGHT)
 
         self.play(
-            FadeIn(brace_P), FadeIn(brace_F),
+            ReplacementTransform(area, brace_P),
+            ReplacementTransform(area_f, brace_F)
+        )
+
+        self.play(
+            FadeIn(div_point),
             Write(label_P), Write(label_F)
         )
+        self.play(FadeOut(top_line))
 
         # Hybrid
         self.next_section("hybrid_case")
@@ -96,12 +105,16 @@ class Equilibrium(Scene):
         self.play(Create(v_h_fun), Write(v_h_label))
 
         pie_to_share_h = ax.c2p(N_F_bar_val, v(N_F_bar_val, N_P_val_h))
+        top_line_h = ax.get_horizontal_line(pie_to_share_h, color=BLACK)
+        top_graph_h = ax.plot(lambda x: v(N_F_bar_val, N_P_val_h))
+        area_f_h = ax.get_area(v_h_fun, (0, N_F_bar_val), bounded_graph=top_graph_h, opacity=0.5, color=YELLOW_D)
[…]

### 2022-11-17 src/presentation/micro_seminar_talk.qmd
Change investment cost notation (c -> i)

@@
  - Main changes:
+   - Lump-sum entry fees
+   - Entry fees are not set bilaterally (bargaining)
 
@@
 ::: {.fragment .fade-in fragment-index=3}
- 2. Firms decide whether to enter at cost $c + F$
+ 2. Firms decide whether to enter at cost $i + F$
 :::
@@
 ::: {.fragment .fade-in fragment-index=2}
- 1. Firms decide whether to invest at cost $c$
+ 1. Firms decide whether to invest at cost $i$
 :::

### 2022-11-17 src/manim_figures/equilibrium_entry.py

@@ -189,7 +189,7 @@ class Equilibrium(Scene):
         # Equilibrium
         self.next_section("equilibrium")
 
-        eq = root_scalar(lambda N_F: phi_F(N_F, N_P_val) - c * N_F, bracket=[0.4, 1.2], method='brentq')
+        eq = root_scalar(lambda N_F: phi_F(N_F, N_P_val) - C * N_F, bracket=[0.4, 1.2], method='brentq')
         eq_point = Dot(color=BLUE_D)
         eq_point.move_to(ax.c2p(eq.root, phi_F(eq.root, N_P_val)))
 
@@ -197,7 +197,7 @@ class Equilibrium(Scene):
         eq_line_label = MathTex("N_F^*", color=BLUE_D)
         eq_line_label.next_to(eq_line, DOWN)
 
-        eq_h = root_scalar(lambda N_F: phi_F(N_F, N_P_val_h) - c * N_F, bracket=[0.4, 1.2], method='brentq')
+        eq_h = root_scalar(lambda N_F: phi_F(N_F, N_P_val_h) - C * N_F, bracket=[0.4, 1.2], method='brentq')
         eq_point_h = Dot(color=RED_D)
         eq_point_h.move_to(ax.c2p(eq_h.root, phi_F(eq_h.root, N_P_val_h)))
 

### 2022-11-17 src/manim_figures/market_structure.py

@@ -50,7 +50,7 @@ class MarketStructure(Scene):
         firm_eqs = []
         firm_shapleys = []
         for j, firm in enumerate(firms):
-            firm_eq = MathTex(r"-c", f"-F_{j+1}", f"+ \\pi_{j+1}", color=BLACK)
+            firm_eq = MathTex(r"-i", f"-F_{j+1}", f"+ \\pi_{j+1}", color=BLACK)
             firm_eq.next_to(firm, UP)
             firm_eqs.append(firm_eq)
             brace = Brace(firm_eq[1:], UP, color=BLACK)

### 2022-12-13 src/paper/application.tex
Start working on application paper

\documentclass[a4paper]{article}

\usepackage{microtype}
\usepackage{fullpage}
\usepackage{mathtools}
\usepackage{amsfonts}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{hyperref}
\usepackage{amsthm}
\usepackage{xcolor}
\usepackage[backend=biber,style=authoryear,maxbibnames=99,hyperref=true]{biblatex}

\addbibresource{src/paper/references.bib}

\usepgfplotslibrary{fillbetween}
\usetikzlibrary{shapes}
\pgfplotsset{compat=1.17}

\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}

\newcommand{\dt}{\mathrm{d}t}
\newcommand{\ds}{\mathrm{d}s}
\newcommand{\di}{\mathrm{d}i}
\newcommand{\E}{\mathbb{E}}

\title{Hybrid platforms and bargaining power}
\author{Martin Stancsics}

\begin{document}

\maketitle

\begin{abstract}
\end{abstract}

\section{Motivation}

\section{Model}

This section introduces the modeling framework used throughout the paper.
I start by describing the demand system of a continuum of consumers and differentiated, monopolistically competitive sellers \parencite[]{anderson2021hybrid}.
After that, I describe the role of the (potentially hybrid) platform on this market.

\subsection{Demand}

Imagine that there is a unit mass of consumers, looking to buy one product each.
They choose from a continuum of products, indexed by $i$.
Customer $j$ derives the following utility from buying product $i$:
\begin{align*}
    u^F_{ij} = v^F_i - p^F_i + \mu\epsilon^F_{ij},
\end{align*}
where $v^F_i$ is the value of product $i$, $p^F_i$ is its price, and $\epsilon^F_{ij}$ is an idiosyncratic taste shock.
Throughout this paper I assume that the value of each product is the same: $v^F_i = v^F$.
This is to simplify the analysis, but is not crucial for getting the results.  % TODO: look into relaxing this assumption

Additionally, customers can also choose from a unit mass of outside options, yielding utility $u^0_ij = \mu\epsilon^0_{ij}$

$\epsilon^F_{ij}$ and $\epsilon^0_{ij}$ are assumed to be independent and identically distributed (i.i.d.) across consumers and products, and follow a standardized Type I Extreme Value distribution. This distributional assumption, along with the fact that each consumer consumes only one product, will lead to a tractable, logit-form demand function.

\subsection{Production}

Each (horizontally differentiated) product is produced by a single, monopolistically competitive (fringe) seller.
The production entails a constant marginal cost $c^F_i$.
As with the value, I assume that the marginal cost is the same for all products: $c^F_i = c^F$.
Facing the demand described in the previous paragraphs, the sellers choose their price $p^F_i$ to maximize profits.

Additionally, the platform itself can also offer mass $N_P$ of its own products.
The value and marginal cost of these products are denoted by $v^P$ and $c^P$, respectively.
Furthermore, consumers have the same i.i.d. taste shocks ($\epsilon^P_{ij}$) for platform products as for the products offered by the other sellers.
Finally, I assume that the product prices its products as if they were produced by separate, monopolistically competitive sellers.
That is, it does not take into account the fact that it can affect a non-zero measure of the prices, and therefore the aggregate demand.\footnote{
    As I show in section TODO the appendix, this assumption is more innocuous than it seems.
    If the platform can commit to the price of its products before the entry of the fringe firms, then the results are the same regardless if the platform behaves as a continuum of atomic firms or one single firm with many products.
    If the platform cannot make this commitment, and determines its prices after entry decisions are made, the results change quantitatively, but the main ideas carry over.  % TODO: check this!!!!!!!!!!
}

\subsection{Intermediation}

Assume that the sellers and the consumers can only interact through an intermediary platform, denoted by $P$.
Without the platform, the fringe firms are not able to sell their products, and thus make no profits.
For this service, the platform can charge a lump-sum entry fee $F_F$ to each fringe firm.\footnote{
    This is a critical difference from \textcite[]{anderson2021hybrid}, where the platform charges a per-unit royalty.
    % TODO: elaborate on this
}
In the baseline model, I assume that entry is free for the consumers, and they are always present on the platform, no matter the other players' entry and pricing decisions.\footnote{
    This essentially means that I assume a one-sided platform, without the usual strong network effects.
    % TODO: see if I can relax this assumption
}

As mentioned above, instead of operating as a pure marketplace, the platform can also produce and offer its own products.
In case it does, it is called a hybrid platform.
Additionally, the platform can choose to exclude all the fringe firms from the market (e.g. by setting a sufficiently high entry fee), and only offer its own products.  % TODO: should I allow it in the baseline case, or only after a policy intervention?

\subsection{Entry and timing}

There is an infinite measure of fringe firms, who are deciding whether to enter the market.
Entering has two, separate costs: an exogenous investment cost $I_F$, and the platform entry fee $F_F$.
One can conceptualize the first as usual fixed costs, such as the cost of setting up production, or designing a product.
Meanwhile, the second is a payment for using the platform's services.

The game starts by the platform announcing its entry fee $F_F$.
Next, each fringe firm decides whether to create a product at cost $I_F$ and enter the market.
After that, the firms that have made the investment decide if they also want to enter the platform for the announced fee $F_F$.\footnote{
    In the benchmark model, separating these two decisions is redundant, as, in any subgame perfect equilibrium, any firm that makes the investment will also enter the platform.
    However, in the model with bargaining, this distinction is crucial.
}
Finally, the platform and the fringe firms simultaneously choose the prices for their products.
Each consumer then chooses the one maximizing their utility, and profits are realized.

\subsection{Bargaining}

The main difference between the benchmark and the bargaining model is in determining the entry fee $F_F$.
In the former, the platform unilaterally sets the fee, and the fringe treats it as a take it or leave it offer.
On the other hand, in the bargaining model, I assume that the entry fee is the result of a negotiation between the platform and those firms that have made the investment.
% TODO: entry fee cap?

Instead of modeling the bargaining process in detail, choose a reduced form approach. I assume that the final, net profits (after paying and receiving entry fees) correspond to the Shapley value of the participants in the following, cooperative game.\footnote{
    This way of modeling bargaining has precedents in the industrial organization literature \parencite[e.g.][]{hart1990property,segal2003collusion,inderst2003bargaining,montez2007downstream}.
    Furthermore, a number of papers show that various extensive-form bargaining games result in this outcome \parencite{gul1989bargaining,winter1994demand,hart1996bargaining,inderst2003bargaining,stole1996intra}.
}
Assume that the value of a coalition consisting of the platform and a measure $N_F$ of fringe firms is the total profits that they can achieve by selling their products in the last stage \emph{using monopolistic pricing}.\footnote{
    Note that lump-sum entry fees do not influence this value, as they are just transfers between coalition members.
}
The value of a coalition without a platform is simply zero.
% TODO: elaborate on how entry fees are not too important.

\section{Equilibrium}

\subsection{Producer profits}

\subsection{The benchmark model}

\subsection{Bargaining outcomes}

%\section{Extensions}

\section{Conclusion}

\appendix

\printbibliography

\section{Shapley value in the platform game}

Consider a cooperative game with two types of players: a major player $P$ and $n$ smaller players.
I.e., $N = \{P, F_1, \dots, F_n\}$.
Assume that (1) no coalition of players can achieve a positive value without the participation of $P$ and (2) players $F_i$ are identical.
Let $n_T(S)$ denote the number of players of type $T \in \{P, F\}$ in coalition $S$. Then, the value that any coalition $S \subset N$ can achieve is the following:
\begin{align*}
    v(S) = \begin{cases}
        0                              & \text{if } P \notin S \\
        f\left(\frac{n_F(S)}{n}\right) & \text{otherwise}.
    \end{cases}
\end{align*}
This coalition-form game corresponds to the setting in this paper with a (one-sided) platform and a number of potential entrants.

I start by characterizing the case when the game is superadditive to provide some support for using the Shapley value as he bargaining outcome.\footnote{For example, the results in \textcite{gul1989bargaining} rely on superadditivity, while monotonicity suffices for \textcite[]{hart1996bargaining}.}

\begin{proposition}
    \label{prop:monotone}
    The game $(N, v)$ is monotone and superadditive if and only if $f$ is increasing and $f(0) \geq 0$. % It is supermodular if and only if $f$ is convex.
\end{proposition}

\begin{proof}[Proof% of Proposition \ref{prop:monotone}
    ]
    Monotonicity is evident. For superadditivity, note that for any coalitions $S_1, s_2$ such that $S_1 \cap s_2 = \emptyset$, $P \notin S_1$ or $P \notin s_2$. WLOG assume it is the latter, therefore $v(S_2) = 0$. As a result, $v(S_1) + v(S_2) = v(S_1) \leq v(S_1 \cup S_2)$ holds if and only if $(N, v)$ is monotone.
\end{proof}

Now let us look at the limit of the Shapley-values as the number of fringe firms goes to infinity.\footnote{
    As this game is of bounded variation, this result can also be obtained in a more direct way using the main theorem from \textcite{fogelman1980asymptotic}.
    However, I believe the following proof is instructive, and drives home the idea that the continuous approximation is rather accurate even in the case of a relatively small number of players.
}
I use the following notation: $\varphi_P^n$ denotes the Shapley-value of player $P$ if there exist $n$ players of type $F$.
The next proposition shows that the Shapley value of the platform can be described by a simple integral.

\begin{proposition}
    \label{prop:one_sided}
    Let $f$ be continuous on [0, 1]. Then
    \begin{align*}
        \varphi_P^\infty = \lim_{n \to \infty} \varphi_p^n = \int_0^1 f(t) \dt .
    \end{align*}
\end{proposition}

\begin{proof}[Proof% of Proposition \ref{prop:one_sided}
    ]
    Let $R$ denote a permutation of the set of players ($N$). Additionally, let us denote the players preceding $i$ by $\mathcal{P}_i^R$. The value of player $P$ is their expected marginal contribution averaged over all permutations of $N$:
    \begin{align*}
        \varphi_P^n = \frac{1}{(n+1)!} \sum_R v(\mathcal{P}_P^R \cup \{i\}) - v(\mathcal{P}_P^R)
    \end{align*}
    First, note that $v(\mathcal{P}_P^R) = 0$ for any permutation, as no coalition can achieve a positive value without player $P$. Furthermore, using the fact that all agents of type $A$ are identical implies that $v(\mathcal{P}_P^R \cup \{i\})$ only depends on the number of agents in the coalition. More precisely, 
    \begin{align*}
        v(\mathcal{P}_P^R \cup \{i\}) = f(n_A(\mathcal{P}_P^R \cup \{i\}) / n) = f(|\mathcal{P}_P^R| / n).
    \end{align*}
    Finally, the set of permutations in which $k$ number of players precede $P$ is independent of $n$, i.e.
    \begin{align*}
        \{R \mid |\mathcal{P}_P^R| = k\} = n! \quad \forall\, k.
    \end{align*}
    Putting all the above together, the value of player $P$ can be expressed as
    \begin{align*}
        \varphi_P^n &= \frac{1}{(n+1)!} \sum_{k=0}^n n! f(k / n) \\
        &= \frac{1}{n+1} \sum_{k=0}^n f(k / n) \\
        &= \frac{n}{n+1} \underbrace{\frac{1}{n} \sum_{k=0}^{n-1} f(k / n)}_{=S_n} + \frac{1}{n+1} f(1).
    \end{align*}
    $S_n$ are just the left Riemann-sums of function $f$ on the interval $[0, 1]$. Therefore, if $f$ is continuous (and thus Riemann-integrable), then $S_n \to \int_0^1 f(t)$, and thus
    \begin{align*}
        \lim_{n \to \infty} \varphi_P^n &= \lim_{n \to \infty} \frac{1}{n+1} \sum_{k=1}^n f(k / n) \\
        &= \lim_{n \to \infty}\underbrace{\frac{n}{n+1}}_{\to 1} \frac{1}{n} \sum_{k=0}^{n-1} f(k / n) + \underbrace{\frac{1}{n+1} f(1)}_{\to 0} \\
        &= \int_0^1 f(t) \dt .
    \end{align*}
\end{proof}

Finally, the aggregated value of the fringe can be obtained using the efficiency of the Shapley value.

\begin{corollary}
    \label{cor:fringe_value}
    The aggregated Shapley-value of the fringe is
    \begin{align*}
        \varphi_F^\infty = f(1) - \int_0^1 f(t) \dt.
    \end{align*}
    Furthermore, if $f$ is differentiable on $[0, 1]$, Then the value of the fringe can also be expressed as
    \begin{align*}
        \varphi_F^\infty = \int_0^1 t f'(t) \dt.
    \end{align*}
\end{corollary}

\begin{proof}[Proof% of Corollary \ref{cor:fringe_value}
    ]
    The first equality comes from the efficiency of the Shapley-value. The values of all players sum up to $f(1)$ for all $n \in \mathbb{N}$, therefore
    \begin{align*}
        \lim_{n \to \infty} \sum_{i=1}^n \varphi_{F_i}^n = \lim_{n \to \infty} (1 - \varphi_P^n ) = 1 - \int_0^1 f(t).
    \end{align*}
    The second can be obtained by integration by parts:
    \begin{align*}
        \int_0^1 t f'(t) \dt = tf(t) \mid_0^1 - \int_0^1 f(t) \dt = f(1) - \int_0^1 f(t) \dt
    \end{align*}
\end{proof}

\end{document}

### 2022-12-13 src/paper/application.tex
Add benchmark model equilibrium

@@
 \section{Model}
+\label{sec:model}
 
@@
 
+As shown in \textcite[]{anderson2021hybrid}, the utility functions described in section \ref{sec:model} give rise to a logit-type demand function.
+Specifically, the demand for product $i$ of producer $T \in \{P, F\}$ is given by:
+\begin{align*}
+    x_{Ti} = \frac{\exp\left( \frac{v_T - p_{Ti}}{\mu} \right)}{A}
+\end{align*}
+where
+\begin{align}
+    A = \int_0^{N_F} \exp\left( \frac{v_F - p_{Fi}}{\mu} \right) \di + \int_0^{N_P} \exp\left( \frac{v_P - p_{Pi}}{\mu} \right) \di + 1.
+    \label{eq:aggregate}
+\end{align}
+The producers' variable profit function is then given by
+\begin{align}
+    \pi^v_{Ti} = ( p_{Ti} - c_T ) \frac{\exp\left( \frac{v_T - p_{Ti}}{\mu} \right)}{A}.
+    \label{eq:variable_profit}
+\end{align}
+
+Notice that, as each producer is infinitesimal, its pricing decision does not affect the aggregate $A$.
+It follows that the profit maximizing price is a simple additive markup over marginal cost
+\begin{align*}
+    p^*_{Ti} = c_T + \mu,
+\end{align*}
+and the optimal profit is
+\begin{align*}
+    \pi^{v*}_{Ti} = \mu \frac{\exp \left( \frac{v_T - c_T - \mu}{\mu} \right)}{A}.
+\end{align*}
+
+For fringe firms, their total profit (including the investment cost $I_F$ and the entry fee $F_F$) is given by
+\begin{align}
+    \pi^{t*}_F = \mu \frac{\exp \left( \frac{v_F - c_F - \mu}{\mu} \right)}{A} - I_F - F_F.
+    \label{eq:fringe_profit}
+\end{align}
+
+\subsection{Fringe entry}
+
+Recall that there is an infinity of potential fringe entrants looking to enter the market.
+Therefore, total profits in equilibrium must be zero.
+Let us for the moment assume that fixed fees are low enough for some fringe firms to enter the market.
+In this case, setting $\pi^{t*}_F$, equation \eqref{eq:fringe_profit} implies that the size of the aggregate is
+\begin{align}
+    A = \mu \frac{\exp \left( \frac{v_F - c_F - \mu}{\mu} \right)}{F_F + I_F}.
+    \label{eq:aggregate_eq}
+\end{align}
+Substituting this into equation \eqref{eq:aggregate} and rearranging gives the number of fringe firms that enter the market:
+\begin{align*}
+    N_F = \frac{\mu}{F_F + I_F} - I_F N_P \exp \left( \frac{(v_P - v_F) - (v_F - c_F)}{\mu} \right) - \frac{1}{\exp \left( \frac{v_F - c_F - \mu}{\mu} \right)}.
+\end{align*}
+
+If, on the other hand, entry costs are too high, no fringe firms enter the market ($N_F = 0$).
+In that case, the aggregate demand is just
+\begin{align*}
+    A = N_P \exp\left( \frac{v_P - c_P - \mu}{\mu} \right) + 1.
+\end{align*}
+
 \subsection{The benchmark model}
+
+In the first period of the game, the platform chooses an entry fee to maximize its total profit, consisting of revenue from its own sales and the collected entry fees.
+First, let us examine the case when the fees are low enough for the fringe to be feasible.
+Profits from sales can be obtained by combining equations \eqref{eq:variable_profit} and \eqref{eq:aggregate_eq}:
+\begin{align*}
+    \pi_P^{v} = N_P (F_F + I_F) \exp \left( \frac{(v_P - v_F) - (c_P - c_F)}{\mu} \right).
+\end{align*}
+% TODO: other cases
+It is increasing in the (1) number of the platform's products, (2) the platform's product advantage (larger market share) and (3) the entry costs for fringe firms (less competition).
+The other component of the platform's profit, entry fees collected from the fringe, are given by
+\begin{align*}
+    \pi_P^{f} = N_F F_F = F_F \left[ \frac{\mu}{F_F + i} - N_P \exp \left( \frac{(v_P - v_F) - (v_F - c_F)}{\mu} \right) - \frac{1}{\exp \left( \frac{v_F - c_F - \mu}{\mu} \right)} \right].
+\end{align*}
+
+Combining these two, the platform's total profit as a function of the entry fee can be expressed as
+\begin{align*}
+    \pi_P^{t} = \mu\frac{F_F}{F_F + I_F} + N_P I_F \exp \left( \frac{(v_P - v_F) - (v_F - c_F)}{\mu} \right) - \frac{F_F}{\exp \left( \frac{v_F - c_F - \mu}{\mu} \right)}
+\end{align*}
+
+Now let us consider the case when the fringe is not present in the market.
+In this case, the collected entry fees are obviously zero, and the platform's profit is simply given by
+\begin{align*}
+    \pi_P^{t} = \pi_P^{v} = \mu \frac{ N_P \exp \left( \frac{v_P - c_P - \mu}{\mu} \right)}{N_P \exp\left( \frac{v_P - c_P - \mu}{\mu} \right) + 1}.
+\end{align*}
+
+% Note that, although the platform's profit is increasing in the number of its products, the optimal entry fee does not depend on it.
+% TODO: intuition
 

### 2022-12-14 src/paper/application.tex
Start working on bargaining outcomes

@@
 and the optimal profit is
-\begin{align*}
+\begin{align}
     \pi^{v*}_{Ti} = \mu \frac{\exp \left( \frac{v_T - c_T - \mu}{\mu} \right)}{A}.
-\end{align*}
+    \label{eq:optimal_profit}
+\end{align}
 
@@
 
-% Note that, although the platform's profit is increasing in the number of its products, the optimal entry fee does not depend on it.
+Note, that even though the platform's profit is increasing in the number of its products, the optimal entry fee does not depend on it.
+As a consequence, the size of the aggregate, and hence consumer welfare is also unaffected by the platform operating in hybrid mode.
 % TODO: intuition
+% TODO: when does switching to retail mode occur?
 
 \subsection{Bargaining outcomes}
+
+Now consider the case when instead of the platform setting take it or leave it entry fees, it must negotiate with the fringe about the division of profits.
+In this case, the timing is slightly different, as the platform cannot commit to an entry fee in the first period.
+Instead, the game starts by fringe firms' investment decisions.
+After that, in the second period, bargaining takes place between the platform and the fringe firms that have entered the market.
+
+The participants negotiate over the aggregate profits that they can achieve in the subsequent period (assuming non-collusive, monopolistic pricing, as before).
+I assume that bargaining outcomes are the Shapley values of the participants, where the value of a coalition is defined as the total profits that the coalition can achieve by selling their products.
+As the platform is necessary to reach the customers, the value of any coalition that does not include the platform is zero.
+Furthermore, using equation \eqref{eq:variable_profit}, the value of a coalition with $n$ fringe firms and the platform is
+\begin{align*}
+    v(n) = \mu \frac{n \exp \left( \frac{v_F - c_F - \mu}{\mu} \right) + N_P \exp \left( \frac{v_P - c_P - \mu}{\mu} \right)}{n \exp \left( \frac{v_F - c_F - \mu}{\mu} \right) + N_P \exp \left( \frac{v_P - c_P - \mu}{\mu} \right) + 1}.
+\end{align*}
+
+Proposition \ref{prop:one_sided} gives a simple formula for the Shapley value of the platform in case $N_F$ fringe firms made the initial investment:
+\begin{align*}
+    \pi^t_P &= \varphi_P = \int_0^1 v(tN_F) \dt \\
+            &= TODO.
+\end{align*}
+Subsequently, the fringe gets the remainder of the profits, therefore
+\begin{align*}
+    \pi^t_F &= \varphi_F =  1 - \int_0^1 v(tN_F) \dt \\
+            &= TODO.
+\end{align*}
 

### 2022-12-14 src/sympy/bargaining_case.py
Compute profit shares in the bargaining case

@@ -1,0 +1,23 @@
+from sympy import Symbol, integrate, init_printing, simplify
+
+init_printing()
+
+mu = Symbol('mu')
+V_F = Symbol('V_F')
+V_P = Symbol('V_P')
+
+I_F = Symbol('I_F')
+
+N_F = Symbol('N_f')
+N_P = Symbol('N_P')
+n = Symbol('n')
+
+v = mu * (n * V_F + N_P * V_P) / (n * V_F + N_P * V_P + 1)
+
+pi_P = simplify(integrate(v, (n, 0, N_F)) / N_F)
+pi_F = simplify(v.subs({n: N_F}) - pi_P)
+
+pi_P
+pi_F
+
+simplify(pi_F.diff(N_P))

### 2022-12-14 src/sympy/benchmark_case.py
Calculate stuff for the benchmark case

@@ -1,0 +1,25 @@
+from sympy import Symbol, init_printing, simplify, solve, Eq
+
+init_printing()
+
+mu = Symbol('mu')
+V_F = Symbol('V_F')
+V_P = Symbol('V_P')
+
+I_F = Symbol('I_F')
+F_F = Symbol('F_F')
+
+N_F = Symbol('N_F')
+N_P = Symbol('N_P')
+n = Symbol('n')
+
+A_eq = mu * V_F / (F_F + I_F)
+A_def = N_F * V_F + N_P * V_P + 1
+
+N_F_eq = simplify(solve(Eq(A_eq, A_def), N_F)[0])
+
+pi_P = simplify(F_F * N_F_eq + N_P * mu * V_P / A_eq)
+
+F_F_opt = simplify(solve(Eq(pi_P.diff(F_F), 0), F_F)[1])
+
+pi_P_opt = simplify(pi_P.subs(F_F, F_F_opt))

### 2022-12-15 src/paper/application.tex
Switch to simpler notation

@@
 \end{align}
-
 For fringe firms, their total profit (including the investment cost $I_F$ and the entry fee $F_F$) is given by
@@
 \end{align}
+
+For ease of notation, let us define the following:
+\begin{align*}
+    V_T = \exp \left( \frac{v_T - c_T - \mu}{\mu} \right).
+\end{align*}
+Then, equilibrium per-product demand and variable profit can be expressed as $V_T/ A$ and $\mu V_T/ A$, respectively.
 
@@
 \begin{align}
-    A = \mu \frac{\exp \left( \frac{v_F - c_F - \mu}{\mu} \right)}{F_F + I_F}.
+    A = \mu \frac{V_F}{F_F + I_F}.
     \label{eq:aggregate_eq}
@@
 \begin{align*}
-    N_F = \frac{\mu}{F_F + I_F} - I_F N_P \exp \left( \frac{(v_P - v_F) - (v_F - c_F)}{\mu} \right) - \frac{1}{\exp \left( \frac{v_F - c_F - \mu}{\mu} \right)}.
+    N_F = \frac{\mu}{F_F + I_F} - I_F N_P \frac{V_P}{V_F} - \frac{1}{V_F}.
 \end{align*}
@@
 \begin{align*}
-    A = N_P \exp\left( \frac{v_P - c_P - \mu}{\mu} \right) + 1.
+    A = N_P V_P + 1.
 \end{align*}
@@
 \begin{align*}
-    \pi_P^{v} = N_P (F_F + I_F) \exp \left( \frac{(v_P - v_F) - (c_P - c_F)}{\mu} \right).
+    \pi_P^{v} = N_P (F_F + I_F) \frac{V_P}{V_F}.
 \end{align*}
@@
 \begin{align*}
-    \pi_P^{f} = N_F F_F = F_F \left[ \frac{\mu}{F_F + i} - N_P \exp \left( \frac{(v_P - v_F) - (v_F - c_F)}{\mu} \right) - \frac{1}{\exp \left( \frac{v_F - c_F - \mu}{\mu} \right)} \right].
+    \pi_P^{f} = N_F F_F = F_F \left[ \frac{\mu}{F_F + i} - N_P \frac{V_P}{V_F} - \frac{1}{V_F} \right].
 \end{align*}
@@
 \begin{align*}
-    \pi_P^{t} = \mu\frac{F_F}{F_F + I_F} + N_P I_F \exp \left( \frac{(v_P - v_F) - (v_F - c_F)}{\mu} \right) - \frac{F_F}{\exp \left( \frac{v_F - c_F - \mu}{\mu} \right)}
+    \pi_P^{t} = \mu\frac{F_F}{F_F + I_F} + N_P I_F \frac{V_P}{V_F} - \frac{F_F}{V_F}
 \end{align*}
@@
 \begin{align*}
-    \pi_P^{t} = \pi_P^{v} = \mu \frac{ N_P \exp \left( \frac{v_P - c_P - \mu}{\mu} \right)}{N_P \exp\left( \frac{v_P - c_P - \mu}{\mu} \right) + 1}.
+    \pi_P^{t} = \pi_P^{v} = \mu \frac{ N_P V_P}{N_P V_P + 1}.
 \end{align*}
@@
 \begin{align*}
-    v(n) = \mu \frac{n \exp \left( \frac{v_F - c_F - \mu}{\mu} \right) + N_P \exp \left( \frac{v_P - c_P - \mu}{\mu} \right)}{n \exp \left( \frac{v_F - c_F - \mu}{\mu} \right) + N_P \exp \left( \frac{v_P - c_P - \mu}{\mu} \right) + 1}.
+    v(n) = \mu \frac{n V_F + N_P V_P}{n V_F + N_P V_P + 1}.
 \end{align*}
@@
     \pi^t_P &= \varphi_P = \int_0^1 v(tN_F) \dt \\
-            &= TODO.
+            &= \mu \left[ 1 + \frac{\log \left( \frac{N_P V_P + 1}{N_P V_P + N_F V_F + 1} \right)}{N_F V_F} \right]
 \end{align*}
@@
     \pi^t_F &= \varphi_F =  1 - \int_0^1 v(tN_F) \dt \\
-            &= TODO.
+            &= \mu \left[ \frac{N_P V_P + N_F V_F}{N_P V_P + N_F V_F + 1} - 1 - \frac{\log \left( \frac{N_P V_P + 1}{N_P V_P + N_F V_F + 1} \right)}{N_F V_F} \right]
 \end{align*}
@@
 
-\section{Conclusion}
+%\section{Conclusion}
 

### 2022-12-15 src/paper/application.tex
Fix equation for equilibrium entry
Flesh out the benchmark case a bit more

@@
 \end{align*}
-Then, equilibrium per-product demand and variable profit can be expressed as $V_T/ A$ and $\mu V_T/ A$, respectively.
+Then, equilibrium per-product demand and variable profit can be expressed as $V_T/ A$ and $\mu V_T/ A$, respectively, and the total aggregate is simply
+\begin{align*}
+    A = N_P V_P + N_F V_F + 1.
+\end{align*}
 
@@
 \begin{align*}
-    N_F = \frac{\mu}{F_F + I_F} - I_F N_P \frac{V_P}{V_F} - \frac{1}{V_F}.
+    N_F = \frac{\mu}{F_F + I_F} - N_P \frac{V_P}{V_F} - \frac{1}{V_F}.
 \end{align*}
@@
 Combining these two, the platform's total profit as a function of the entry fee can be expressed as
+\begin{align}
+    \pi_P^{t} = \mu\frac{F_F}{F_F + I_F} + N_P I_F \frac{V_P}{V_F} - \frac{F_F}{V_F}
+    \label{eq:hybrid_profit}
+\end{align}
+Note, that even though the platform's profit is increasing in the number of its products, the optimal entry fee does not depend on it.
+In particular, the optimal entry fee is given by
 \begin{align*}
-    \pi_P^{t} = \mu\frac{F_F}{F_F + I_F} + N_P I_F \frac{V_P}{V_F} - \frac{F_F}{V_F}
+    F_F^* = \sqrt{\mu I_F V_F} - I_F.
+\end{align*}
+As a consequence, as long as the fringe is feasible at the optimal entry fee, the size of the aggregate, and hence consumer welfare is also unaffected by the platform operating in hybrid mode.
+Substituting it into the profit function, the maximized profit is
+\begin{align*}
+    \pi_P^{t} = \mu - 2\sqrt{\frac{I_F \mu}{V_F}} + \frac{I_F}{V_F} (N_P V_P + 1).
 \end{align*}
@@
 \end{align*}
+In this regime, total aggregate, and hence consumer welfare are increasing in the number of the platform's products.
+This is mechanical: more variety leads to higher welfare.
 
-Note, that even though the platform's profit is increasing in the number of its products, the optimal entry fee does not depend on it.
-As a consequence, the size of the aggregate, and hence consumer welfare is also unaffected by the platform operating in hybrid mode.
+Finally, note that the profit of the platform in the hybrid regime is higher than in the retail regime, when the former is feasible.
+This is a consequence of the fact that equation \eqref{eq:hybrid_profit} is strictly concave in $F_F$, therefore $F_F^*$ is a global maximum.
+It implies that there is no jump in no point where the fringe would be feasible under optimal entry fees, but the platform would prefer to operate in retail mode.
+Therefore, in the benchmark model, a platform becomes a hybrid platform, or increasing the number of its own products, always has a weakly positive effect on the aggregate, and thus consumer welfare.
+This is in contrast to \textcite{anderson2021hybrid}, where a platform operating in hybrid mode sets a higher entry fee to advantage its own products, which in turn leads to a smaller aggregate.
+
 % TODO: intuition
-% TODO: when does switching to retail mode occur?
 

### 2022-12-15 src/sympy/bargaining_case.py

@@ -1,3 +1,4 @@
+import sympy
 from sympy import Symbol, integrate, init_printing, simplify
 
 init_printing()

### 2022-12-15 src/sympy/benchmark_case.py

@@ -1,4 +1,6 @@
 from sympy import Symbol, init_printing, simplify, solve, Eq
+from sympy import sqrt
+import sympy.plotting as sp
 
 init_printing()
 
@@ -23,3 +25,50 @@ pi_P = simplify(F_F * N_F_eq + N_P * mu * V_P / A_eq)
 F_F_opt = simplify(solve(Eq(pi_P.diff(F_F), 0), F_F)[1])
 
 pi_P_opt = simplify(pi_P.subs(F_F, F_F_opt))
+pi_P_ret = mu * (N_P * V_P) / (N_P * V_P + 1)
+
+N_P_bar = (sqrt(mu * V_F / I_F) - 1) / V_P
+
+# Plotting
+params_1 = {
+    mu: 3,
+    V_F: 1,
+    V_P: 1,
+    I_F: 0.5,
+}
+params_2 = {
+    mu: 3,
+    V_F: 1,
+    V_P: 2,
+    I_F: 0.5,
+}
+
+plot_single = sp.plot(
+    pi_P_opt.subs(params_1),
+    pi_P_ret.subs(params_1),
+    (N_P, 0, 5),
+    ylim=(0, 4),
+    show=False
+)
+plot_single.append(
+    sp.plot_implicit(Eq(N_P, N_P_bar.subs(params_1)), show=False)[0]
+)
+plot_single.show()
+
+plot_multi = sp.plot(
+    pi_P_opt.subs(params_1),
+    pi_P_ret.subs(params_1),
+    pi_P_opt.subs(params_2),
+    pi_P_ret.subs(params_2),
+    (N_P, 0, 5),
+    ylim=(0, 4),
+    show=False
+)
+plot_multi.append(
+    sp.plot_implicit(Eq(N_P, N_P_bar.subs(params_1)), show=False)[0]
+)
+plot_multi.append(
+    sp.plot_implicit(Eq(N_P, N_P_bar.subs(params_2)), show=False)[0]
+)
+plot_multi.show()
+

### 2022-12-16 src/figures/equilibrium_nf.py
Switch to new notation

@@ -3,33 +3,37 @@ import matplotlib. pyplot as plt
 import typer
 
 
-def plot_equilibrium_nf(N_P_list, B, C, N_f_range, num_obs=500):
-    N_f = np.linspace(N_f_range[0], N_f_range[1], num_obs)
-    rhs = C * N_f
+def plot_equilibrium_nf(N_P_list, mu, V_P, V_F, I_F, N_F_range, num_obs=500):
+    N_F = np.linspace(N_F_range[0], N_F_range[1], num_obs)
+    rhs = I_F * N_F
     lhs_list = []
     for N_P in N_P_list:
-        lhs = (np.log(B * N_P + B * N_f + 1) - np.log(B * N_P + 1)) / (B * N_f) - 1 / (N_P * B + N_f * B + 1)
+        lhs = mu * (
+            (N_P * V_P + N_F * V_F) / (N_P * V_P + N_F * V_F + 1)
+            - 1
+            - (np.log((N_P * V_P + 1) / (N_P * V_P + N_F * V_F + 1))) / (N_F * V_F)
+        )
         lhs_list.append(lhs)
 
     fig, ax = plt.subplots()
-    ax.plot(N_f, rhs, label=r'$C\barN_f$', color='black')
+    ax.plot(N_F, rhs, label=r'$N_F$', color='black')
     for lhs, N_P in zip(lhs_list, N_P_list):
-        ax.plot(N_f, lhs, label=r'$h(\bar N_f) \mid N_P = {}$'.format(N_P))
+        ax.plot(N_F, lhs, label=r'$\phi_F(N_F) \mid N_P = {}$'.format(N_P))
 
-    ax.set_xlabel(r'$\barN_f$')
+    ax.set_xlabel(r'$\bar N_F$')
     ax.legend()
 
     return fig, ax
 
 
-def create_plot(out_path: str, B: float = 1, C: float = 0.2,
-                N_P: list[float] = [], N_f_range: tuple[float, float] = (0, 1),
+def create_plot(out_path: str, mu: float = 1, V_P: float = 1, V_F: float = 1, I_F: float = 0.2,
+                N_P: list[float] = [], N_F_range: tuple[float, float] = (0, 1),
                 num_obs: int = 500, width: float = 5, height: float = 3.5, dpi: int = 300):
 
     if not N_P:
         raise typer.BadParameter("At least one value for N_P must be provided")
 
[…]

### 2022-12-16 src/sympy/bargaining_case.py
Try IFT

@@ -1,5 +1,4 @@
-import sympy
-from sympy import Symbol, integrate, init_printing, simplify
+from sympy import Symbol, integrate, init_printing, simplify, factor, solve
 
 init_printing()
 
@@ -21,4 +20,20 @@ pi_F = simplify(v.subs({n: N_F}) - pi_P)
 pi_P
 pi_F
 
-simplify(pi_F.diff(N_P))
+pi_F_t = pi_F - I_F * N_F
+solve(pi_F_t, N_F)  # :(
+
+d_N_F = simplify(pi_F_t.diff(N_F))
+d_N_P = simplify(pi_F_t.diff(N_P))
+
+d_N_F_N_P = factor(simplify(d_N_F / d_N_P))
+d_N_F_N_P
+
+pi_F_simplified = mu * (
+    (N_P * V_P + N_F * V_F) / (N_P * V_P + N_F * V_F + 1)
+    - 1
+    - 1 / (N_F * V_F)
+) - I_F * N_F
+d_N_F_N_P_simplified = simplify(
+    pi_F_simplified.diff(N_F) / pi_F_simplified.diff(N_P)
+)

### 2022-12-16 src/paper/application.tex
Simplify formulas for the bargaining case
Continue the bargaining case

@@
 % TODO: intuition
+% Figure
 
@@
     \pi^t_P &= \varphi_P = \int_0^1 v(tN_F) \dt \\
-            &= \mu \left[ 1 + \frac{\log \left( \frac{N_P V_P + 1}{N_P V_P + N_F V_F + 1} \right)}{N_F V_F} \right]
+            &= \mu \left[ 1 - \frac{\log \left(1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} \right]
 \end{align*}
@@
 \begin{align*}
-    \pi^t_F &= \varphi_F =  1 - \int_0^1 v(tN_F) \dt \\
-            &= \mu \left[ \frac{N_P V_P + N_F V_F}{N_P V_P + N_F V_F + 1} - 1 - \frac{\log \left( \frac{N_P V_P + 1}{N_P V_P + N_F V_F + 1} \right)}{N_F V_F} \right]
+    \pi^v_F &= \varphi_F =  1 - \int_0^1 v(tN_F) \dt \\
+            &= \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right]
 \end{align*}
+and the total profits of the whole fringe are
+\begin{align*}
+    \pi^v_F = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F N_F
+\end{align*}
+The free entry condition implies that fringe profits are zero, therefore the number of fringe entrants is given by the implicit equation
+\begin{align}
+    \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F N_F = 0
+    \label{eq:free_entry_bargaining}
+\end{align}
+
+\textcolor{red}{
+    What I really want to show at this point is that if $N_F$ is determined by equation \eqref{eq:free_entry_bargaining}, then the total aggregate is decreasing in $N_P$.
+    Unfortunately, I don't have a closed form for $N_F^*$, and the IFT does not seem to lead to useful results, either.
+    Therefore, at this point, all I can do is show it through some numerical examples.
+    That won't guarantee of course that it holds in general.
+}
+
+\textcolor{red}{
+    I have a graphical reasoning in mind though, that I might be able to make precise in the future.
+    For the moment, I'd rather not include it as it might be completely wrong.
+}
 

### 2022-12-16 src/sympy/bargaining_case.py

@@ -1,4 +1,4 @@
-from sympy import Symbol, integrate, init_printing, simplify, factor, solve
+from sympy import Symbol, integrate, init_printing, simplify, factor, solve, log
 
 init_printing()
 
@@ -23,17 +23,11 @@ pi_F
 pi_F_t = pi_F - I_F * N_F
 solve(pi_F_t, N_F)  # :(
 
-d_N_F = simplify(pi_F_t.diff(N_F))
-d_N_P = simplify(pi_F_t.diff(N_P))
-
-d_N_F_N_P = factor(simplify(d_N_F / d_N_P))
-d_N_F_N_P
-
-pi_F_simplified = mu * (
-    (N_P * V_P + N_F * V_F) / (N_P * V_P + N_F * V_F + 1)
-    - 1
-    - 1 / (N_F * V_F)
+pi_F_t_alt = mu * (
+    log(1 + (N_F * V_F) / (N_P * V_P + 1)) / (N_F * V_F)
+    - 1 / (N_P * V_P + N_F * V_F + 1)
 ) - I_F * N_F
-d_N_F_N_P_simplified = simplify(
-    pi_F_simplified.diff(N_F) / pi_F_simplified.diff(N_P)
+d_N_F_N_P = simplify(
+    pi_F_t_alt.diff(N_F) / pi_F_t_alt.diff(N_P)
 )
+

### 2022-12-16 src/paper/application.tex
Minor structure enhancements

@@
 
-Additionally, customers can also choose from a unit mass of outside options, yielding utility $u^0_ij = \mu\epsilon^0_{ij}$
-
+Additionally, customers can also choose from a unit mass of outside options, yielding utility $u^0_ij = \mu\epsilon^0_{ij}$.
 $\epsilon^F_{ij}$ and $\epsilon^0_{ij}$ are assumed to be independent and identically distributed (i.i.d.) across consumers and products, and follow a standardized Type I Extreme Value distribution.
@@
 
-The game starts by the platform announcing its entry fee $F_F$.
+In the benchmark model, the game starts by the platform announcing its entry fee $F_F$.
+In the bargaining case, the platform cannot commit to entry fees, so this step is skipped.
 Next, each fringe firm decides whether to create a product at cost $I_F$ and enter the market.
+In the bargaining model, the entry fee is decided at this point, as a result of a negotiation between the platform and the firms that have made the investment.
 After that, the firms that have made the investment decide if they also want to enter the platform for the announced fee $F_F$.\footnote{
@@
 In the former, the platform unilaterally sets the fee, and the fringe treats it as a take it or leave it offer.
-On the other hand, in the bargaining model, I assume that the entry fee is the result of a negotiation between the platform and those firms that have made the investment.
+On the other hand, in the bargaining model, I assume that the entry fee is the result of a negotiation between the parties.
 % TODO: entry fee cap?
@@
 
-\subsection{Fringe entry}
+\subsection{The benchmark model}
 
@@
 \end{align*}
-
-\subsection{The benchmark model}
 

### 2022-12-16 src/sympy/bargaining_case.py
Add some notes about proving decreasing welfare

@@ -8,7 +8,7 @@ V_P = Symbol('V_P')
 
 I_F = Symbol('I_F')
 
-N_F = Symbol('N_f')
+N_F = Symbol('N_F')
 N_P = Symbol('N_P')
 n = Symbol('n')
 
@@ -21,13 +21,19 @@ pi_P
 pi_F
 
 pi_F_t = pi_F - I_F * N_F
-solve(pi_F_t, N_F)  # :(
+# solve(pi_F_t, N_F)  # :(
 
-pi_F_t_alt = mu * (
+pi_F_alt = mu * (
     log(1 + (N_F * V_F) / (N_P * V_P + 1)) / (N_F * V_F)
     - 1 / (N_P * V_P + N_F * V_F + 1)
-) - I_F * N_F
+)
+pi_F_t_alt = pi_F_alt + I_F * N_F
 d_N_F_N_P = simplify(
     pi_F_t_alt.diff(N_F) / pi_F_t_alt.diff(N_P)
 )
 
+simplify((pi_F_alt).diff(N_F))
+simplify((pi_F_alt).diff(N_F).diff(N_F))
+simplify((pi_F_alt).diff(N_F).diff(N_F).diff(N_F))
+
+(2 * log((N_F * V_F) / (N_P * V_P + 1) + 1)).diff(N_F)  # type: ignore

### 2023-02-03 src/paper/application.tex
Add some lemmas

@@
 
-\section{Model}
+\section{Example}
 \label{sec:model}
@@
 Subsequently, the fringe gets the remainder of the profits, therefore
-\begin{align*}
+\begin{align}
     \pi^v_F &= \varphi_F =  1 - \int_0^1 v(tN_F) \dt \\
             &= \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right]
-\end{align*}
+            \label{eq:fringe_variable_profit}
+\end{align}
 and the total profits of the whole fringe are
 \begin{align*}
-    \pi^v_F = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F N_F
+    \pi^t_F = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F N_F
 \end{align*}
@@
 
+\section{Miscellaneous lemmas and proofs}
+
+The following proposition shows that, if the platform is operating in a more hybrid mode (meaning it has more or better products), then, for a given aggregate size, the fringe obtains a lower share of the profits.
+This is due to the increased bargaining power of the platform.
+
+\begin{proposition}
+    \label{prop:fringe_profit_decreasing_in_N_P}
+    For a fixed aggregate size $A$, fringe profit is decreasing in $N_P$ and $V_P$.
+\end{proposition}
+\begin{proof}
+    Let $N_P' V_P' > N_P V_P$.
+    Furthermore, let $N_F V_F = A - N_P V_P - 1$ and $N_F' V_F' = A - N_P' V_P' - 1$ for some $A > 1$.
+    Finally, let
+    \begin{align*}
+        v(n) &= \mu \frac{n V_F + N_P V_P}{n V_F + N_P V_P + 1}, \\
+        v'(n) &= \mu \frac{n V_F + N_P' V_P'}{n V_F + N_P' V_P' + 1}.
+    \end{align*}
+
+    Observe that for any $t \in [0, 1)$,
+    \begin{align*}
+        v(tN_F) &= \frac{t N_F V_F + N_P V_P}{t N_F V_F + N_P V_P + 1} \\
+                &= \frac{tA - t + (1 - t) N_P V_P}{tA - t + (1 - t) N_P V_P + 1} \\
+                &< \frac{tA - t + (1 - t) N_P' V_P'}{tA - t + (1 - t) N_P' V_P' + 1} \\
+                &= \frac{t N_F' V_F' + N_P' V_P'}{t N_F' V_F + N_P V_P + 1} \\
+                &= v'(tN_F').
+    \end{align*}
+    This in turn implies that
+    \begin{align*}
+        \pi_F^v = \int_0^1 v(t) \dt < \int_0^1 v'(t) \dt = (\pi_F^v)',
+    \end{align*}
+    which is what we wanted to show.
+
+\end{proof}
+
+\begin{lemma}
+    \label{lem:shape_of_pi_F}
+    For any $V_F, N_P, V_P, \mu$, the function $\pi^v_F$ is either concave in $N_F$ or decreasing in $N_F$.
+\end{lemma}
+\begin{proof}
+    Did not manage to prove it yet.
+\end{proof}
+
+\begin{corollary}
+    \label{cor:unique_eq}
+    There is at most one equilibrium with $N_F > 0$.
+\end{corollary}
+
+\begin{proposition}
+    \label{prop:A_decreasing_in_N_P}
+    The equilibrium aggregate size $A$ is monotonically decreasing in $N_P$ and $V_P$. When the fringe is feasible to begin with, the decrease is strict.
+\end{proposition}
+\begin{proof}
+    From proposition \ref{prop:fringe_profit_decreasing_in_N_P}, we know that the fringe profit is decreasing in $N_P$ and $V_P$.
+    Furthermore, lemma \ref{lem:shape_of_pi_F}
+\end{proof}
+
+\begin{corollary}
+    \label{consumer_welfare_decreasing_in_N_P}
+\end{corollary}
+\begin{proof}
+
+\end{proof}
+
 \end{document}

### 2023-02-03 src/sympy/bargaining_case.py
Add plots to the sympy calculations

@@ -1,4 +1,4 @@
-from sympy import Symbol, integrate, init_printing, simplify, factor, solve, log
+from sympy import Symbol, integrate, init_printing, simplify, expand, factor, solve, log, plot
 
 init_printing()
 
@@ -27,7 +27,7 @@ pi_F_alt = mu * (
     log(1 + (N_F * V_F) / (N_P * V_P + 1)) / (N_F * V_F)
     - 1 / (N_P * V_P + N_F * V_F + 1)
 )
-pi_F_t_alt = pi_F_alt + I_F * N_F
+pi_F_t_alt = pi_F_alt - I_F * N_F
 d_N_F_N_P = simplify(
     pi_F_t_alt.diff(N_F) / pi_F_t_alt.diff(N_P)
 )
@@ -37,3 +37,31 @@ simplify((pi_F_alt).diff(N_F).diff(N_F))
 simplify((pi_F_alt).diff(N_F).diff(N_F).diff(N_F))
 
 (2 * log((N_F * V_F) / (N_P * V_P + 1) + 1)).diff(N_F)  # type: ignore
+
+plot_params = {
+    V_F: 1,
+    N_P: 0.5,
+    V_P: 1,
+    mu: 1
+}
+plot(
+    pi_F_alt.subs(plot_params),
+    (N_F, 0, 10),
+)
+plot(
+    simplify((pi_F_alt).diff(N_F)).subs(plot_params),
+    simplify((pi_F_alt).diff(N_F).diff(N_F)).subs(plot_params),
+    (N_F, 3, 5),
+)
+
+# unfortunately the result of this has an ambiguous sign:
+simplify(
+    simplify((pi_F_alt).diff(N_F).diff(N_F) * N_F**3 * V_F * (N_F * V_F + N_P * V_P + 1) ** 3)
+    + simplify(2 * (pi_F_alt).diff(N_F) * N_F**2 * V_F * (N_F * V_F + N_P * V_P + 1) ** 3)
+)
+
+simplify(
+    simplify((pi_F_alt).diff(N_F).diff(N_F) * N_F**3 * V_F * (N_F * V_F + N_P * V_P + 1) ** 3)
+    + simplify(2 * (pi_F_alt).diff(N_F) * N_F**2 * V_F * (N_F * V_F + N_P * V_P + 1) ** 2 * N_F * V_F)
+)
+

### 2023-02-03 src/paper/application.tex
Start working on more general model

@@
 \newtheorem{lemma}{Lemma}
+\newtheorem{assumption}{Assumption}
 
@@
 \section{Motivation}
+
+\section{Model}
+
+This section introduces the model used throughout the paper.
+I use the terms ``platform'' and ``fringe sellers'', and present my ideas in the context of an intermediated market, such as an online marketplace or an application store.
+However, the model is more general, and the results apply to a broader class of settings.
+Chief among these is an upstream-downstream setting, with a single upstream producer and a continuum of downstream sellers.
+
+\subsection{Production}
+
+I make use of a reduced-form, but quite general approach to model production and demand.
+Assume that the total profits obtained by the platform and the fringe sellers are described by the function $f(n_P, n_F)$.
+Here, $n_F$ is the mass of fringe sellers, and $n_P$ measures the degree to which the platform sells its own products.
+In case the platform operates as a pure intermediary, $n_P = 0$.
+For example, in a setting with differentiated products and monopolistic competition, $n_F$ and $n_P$ represents the product variety of the fringe and the platform, respectively.
+
+I will assume that total profits are increasing in both arguments.
+\begin{assumption}
+    \label{ass:monotone_profits}
+    $f(n_P, n_F)$ is increasing in both $n_P$ and $n_F$.
+\end{assumption}
+Such profit functions arise in a variety of settings in which the profit reduction from increased competition is dominated by extra sales due to increased variety.
+One such example is \textcite{anderson2020aggregative}, where the demand exhibits love for variety, while consumers have access to an outside option.
+Alternatively, indirect network effects, such as in two-sided markets, can also result in such profit functions.
+
+\subsection{Profit sharing}
+
+Let us assume that the fringe firms are unable to sell their products directly to consumers.
+Instead, they must sell through the platform.
+For this service, the platform may charge a fee, and obtain a share of the fringe's profits.
+
+Let us assume that the platform and the fringe shares their total profits according to the following rule.
+\begin{assumption}
+    \label{ass:profit_sharing}
+    Let $w: [0, 1] \to \mathbb{R}^+$ such that $\int_0^1 w(s) \ds = 1$. 
+    \begin{align*}
+        \pi_P(N_P, N_F) &= \int_0^1 w(s) f(N_P, s N_F) \ds, \\
+        \pi_F(N_P, N_F) &= f(N_P, N_F) - \int_0^1 w(s) f(N_P, s N_F) \ds.
+    \end{align*}
+\end{assumption}
+
+While at first it might seem rather arbitrary, and much more convoluted than a simple percentage split, it has quite a few nice properties compared to the latter, and can also be microfounded.
+
+\subsection{Entry}
+
+\subsection{Equilibrium}
+
+\begin{assumption}
+    \label{ass:single_crossing}
+    Let $f(n_P, n_F)$ and $w(s)$ be such that the following holds for all $N_F, N_P \geq 0$:
+    \begin{gather*}
+        f'_{n_F} (N_P, N_F) < \int_0^1 s w(s) f'_{n_F} (N_P, s N_F) \ds \\
+        \text{or} \\
+        f''_{n_F} (N_P, N_F) < \int_0^1 s^2 w(s) f''_{n_F} (N_P, s N_F) \ds.
+    \end{gather*}
+\end{assumption}
 

### 2023-02-03 src/paper/application.tex
Add profit sharing section

@@
 \usepackage{hyperref}
+\usepackage[nameinlink]{cleveref}
 \usepackage{amsthm}
@@
     \label{ass:profit_sharing}
-    Let $w: [0, 1] \to \mathbb{R}^+$ such that $\int_0^1 w(s) \ds = 1$. 
+    Let $w: [0, 1] \to \mathbb{R}_0^+$ such that $\int_0^1 w(s) \ds = 1$. 
     \begin{align*}
@@
 \end{assumption}
+While at first it might seem rather arbitrary, and much more convoluted than a simple percentage split, it has quite a few nice properties compared to the latter.
+Furthermore, \cref{sec:profit_sharing} provides some cooperative and non-cooperative microfoundations for this rule.
+Let us start by examining the various parts of this rule, and then discuss how they impact the platform's profit share.
 
-While at first it might seem rather arbitrary, and much more convoluted than a simple percentage split, it has quite a few nice properties compared to the latter, and can also be microfounded.
+The main feature of this rule is that the platform's bargaining power depends on the substitutability of the fringe firms.
+The following proposition demonstrates this idea.
+\begin{proposition}
+    \label{prop:outcome_based_bargaining_power}
+    Let $f, \tilde{f}: \mathbb{R}^+_0 \times \mathbb{R}^+_0 \to \mathbb{R}^+_0$ two different total profit functions such that $f(N_P, N_F) = \tilde{f}(N_P, N_F)$ for some $N_P, N_F$ and $f(n_P, n_F) \leq \tilde{f}(n_P, n_F)$ for all $n_P < N_P, n_F < N_F$.
+    Furthermore, let us denote the corresponding platform profit shares by $\pi_P$ and $\tilde{\pi}_P$.
 
-\subsection{Entry}
+    Then, $\pi_P \leq \tilde{\pi}_P$.
+\end{proposition}
+In words, when comparing two different total profit functions (i.e., demand systems, production functions), even if the total profits are the same under some pair $N_P, N_F$, profit shares might differ.
+In particular, the platform's profits are higher when it needs fewer firms to achieve a certain total profit level (i.e., when the fringe firms are more substitutable).
+\textcolor{red}{GRAPH HERE}
+This coincides with the intuitive idea that the platform's bargaining power is higher when it does not really mind loosing a few fringe sellers.
+
+The other main ingredient of the sharing rule, $w(s)$, captures the platform's \emph{innate} bargaining power.
+It is independent of the production function, demand, or the fringe firms' substitutability, and might represent, for example, that the platform and the fringe firms have different power to propose allocations during the (not explicitly modeled) negotiation process.\footnote{
+    For a more thorough exploration of this idea, see \cref{app:profit_sharing} and \textcite{hart1996bargaining}.
+}
+One way to think about it is that the platform's share is randomly drawn from the total profit according to some distribution, and $w$ is the probability density function of this distribution.
+When the distribution $W_1$ first order stochastically dominates another distribution $W_2$, the platform is more likely to draw a value from with a higher mass of fringe firms, and therefore obtain a higher profit share in case of $W_1$ than in the case of $W_2$.
+The next proposition formalizes this idea.
+\begin{proposition}
+    \label{prop:innate_bargaining_power}
+    Let $w, \tilde{w}: [0, 1] \to \mathbb{R}_0^+$ be two different weight functions such that $\int_0^x w_1(s) \ds \leq \int_0^x w_2(s) \ds$ for all $x \in [0, 1]$.
+    As before, let us denote the corresponding platform profit shares by $\pi_P$ and $\tilde{\pi}_P$.
+
+    Then, $\pi_P(N_P, N_F) \leq \tilde{\pi}_P(N_P, N_F) \; \forall\, N_P \geq 0, N_F > 0$.
+    Furthermore, this inequality is strict if $\int_0^x w_1(s) \ds < \int_0^x w_2(s) \ds$ on some non-zero measure set.
+\end{proposition}
+
+\subsection{Entry and equilibrium}
 
@@
 
-As shown in \textcite[]{anderson2021hybrid}, the utility functions described in section \ref{sec:model} give rise to a logit-type demand function.
+As shown in \textcite[]{anderson2021hybrid}, the utility functions described in \cref{sec:model} give rise to a logit-type demand function.
 Specifically, the demand for product $i$ of producer $T \in \{P, F\}$ is given by:
@@
 
-Proposition \ref{prop:one_sided} gives a simple formula for the Shapley value of the platform in case $N_F$ fringe firms made the initial investment:
+\Cref{prop:one_sided} gives a simple formula for the Shapley value of the platform in case $N_F$ fringe firms made the initial investment:
 \begin{align*}
@@
 \begin{proof}
-    From proposition \ref{prop:fringe_profit_decreasing_in_N_P}, we know that the fringe profit is decreasing in $N_P$ and $V_P$.
-    Furthermore, lemma \ref{lem:shape_of_pi_F}
+    From \cref{prop:fringe_profit_decreasing_in_N_P}, we know that the fringe profit is decreasing in $N_P$ and $V_P$.
+    Furthermore, \cref{lem:shape_of_pi_F}
 \end{proof}

### 2023-02-03 src/paper/application.tex
Add equilibrium subsection

@@
 
+Assume that there are two types of players in the market: a platform $P$ and a continuum of fringe sellers $F_i$.
+
 \subsection{Production}
@@
 I make use of a reduced-form, but quite general approach to model production and demand.
-Assume that the total profits obtained by the platform and the fringe sellers are described by the function $f(n_P, n_F)$.
+First, I assume that all fringe firms are ex-ante identical.
+This implies that the total profits of the platform and the fringe taken together have a simple functional form $f(n_P, n_F)$.
+\begin{assumption}
+    \label{ass:identical_fringe}
+    The total profits of the platform and the fringe are described by some function $f: \mathbb{R}^+_0 \times \mathbb{R}^+_0 \to \mathbb{R}^+_0$.
+\end{assumption}
 Here, $n_F$ is the mass of fringe sellers, and $n_P$ measures the degree to which the platform sells its own products.
+For example, in a setting with differentiated products and monopolistic competition, $n_F$ and $n_P$ represents the product variety of the fringe and the platform, respectively.
 In case the platform operates as a pure intermediary, $n_P = 0$.
-For example, in a setting with differentiated products and monopolistic competition, $n_F$ and $n_P$ represents the product variety of the fringe and the platform, respectively.
 
@@
 
-\subsection{Equilibrium}
+Let us now turn to the determination of the equilibrium number of fringe firms.
+Assume that there is an unlimited number of potential fringe entrants, indexed by $i \in \mathbb{R}^+_0$.
+In the first stage of the game, each fringe firm must create a viable product at the investment cost $I_F > 0$.
+In the second stage, firms that made this investment plus the platform engage in producing and selling their respective products.
+If there are $N_F$ fringe entrants and $N_P$ platform products, then, as discussed previously, the total profit they make together is given by $f(N_P, N_F)$.
+Finally, the platform and the entrants share this profit according to the profit sharing rule from \cref{ass:profit_sharing}.
 
+The equilibrium number of entrants is determined by a free entry condition: in the end, the fringe firms' profits should be equal to the investment cost.
+\begin{assumption}
+    \label{ass:free_entry}
+    In equilibrium, $\pi_F(N_P, N_F) = I_F N_F$.
+\end{assumption}
+
+In order to guarantee a unique equilibrium, let us make the following, additional assumption about the profit and bargaining weight functions.
 \begin{assumption}
     \label{ass:single_crossing}
-    Let $f(n_P, n_F)$ and $w(s)$ be such that the following holds for all $N_F, N_P \geq 0$:
+    Let $f$ and $w$ be such that the following holds for all $N_F, N_P \geq 0$:
     \begin{gather*}
@@
 \end{assumption}
+\textcolor{red}{TODO: Find interpretable sufficient conditions for this assumption.}
+
+\section{Results}
+
+\begin{proposition}
+
+\end{proposition}
 
 \section{Example}
-\label{sec:model}
+\label{sec:example}
 

### 2023-02-06 src/paper/application.tex
Add preliminary results

@@
 
+Some preliminary (hand-wavily proven) results about equilibrium profits and entry.
+
 \begin{proposition}
+    \label{prop:share_of_platform}
+    Assume that $f, w$ are continuously differentiable and that $w$ has a non-zero measure support.
+    Then $\pi_P$ is also differentiable and
+    $$\frac{\partial \pi_P(N_P, n_F)}{\partial N_P} > 0$$.
+\end{proposition}
 
+\begin{proposition}
+    \label{prop:share_of_fringe}
+    Assume that $f, w$ are twice continuously differentiable and that $w$ has a non-zero measure support.
+    Then $\pi_F$ is also differentiable. Let $N_F > 0$.
+    \begin{align*}
+        &\text{If } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} > 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} < 0, \\
+        &\text{if } \frac{\partial^2 f(N_P, N_F)}{\partial n_P \partial n_F} > 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} > 0
+    \end{align*}
+    for all $N_P \geq 0$.
 \end{proposition}
+
+\begin{corollary}
+    \label{fringe_entry}
+    Assume that $f, w$ are twice continuously differentiable and that $w$ has a non-zero measure support.
+    Let $N_F^*$ denote the equilibrium number of fringe firms.
+    \begin{align*}
+        &\text{If } \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} > 0 \forall n_P \leq N_P, \text{ then } \frac{\partial N_F^*}{\partial N_P} < 0. \\
+        &\text{If } \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} > 0 \forall n_P \leq N_P, \text{ then } \frac{\partial N_F^*}{\partial N_P} > 0.
+    \end{align*}
+\end{corollary}
 
@@
 
-This section introduces the modeling framework used throughout the paper.
-I start by describing the demand system of a continuum of consumers and differentiated, monopolistically competitive sellers \parencite[]{anderson2021hybrid}.
-After that, I describe the role of the (potentially hybrid) platform on this market.
+This section presents an example application of the model, based on \parencite[]{anderson2021hybrid}.
+The setting is a (possibly hybrid) platform market with monopolistically competing fringe firms.
 

### 2023-02-06 src/paper/application.tex
Rewrite the example section

@@
 While at first it might seem rather arbitrary, and much more convoluted than a simple percentage split, it has quite a few nice properties compared to the latter.
-Furthermore, \cref{sec:profit_sharing} provides some cooperative and non-cooperative microfoundations for this rule.
+Furthermore, \cref{sec:profit_sharing} provides some cooperative and non-cooperative microfoundations for this rule.\footnote{
+    This way of modeling bargaining has precedents in the industrial organization literature \parencite[e.g.][]{hart1990property,segal2003collusion,inderst2003bargaining,montez2007downstream}.
+    Furthermore, a number of papers show that various extensive-form bargaining games result in this outcome \parencite{gul1989bargaining,winter1994demand,hart1996bargaining,inderst2003bargaining,stole1996intra}.
+}
 Let us start by examining the various parts of this rule, and then discuss how they impact the platform's profit share.
@@
 \begin{proposition}
+    \label{prop:unique_equilibrium}
+    Under the conditions in assumption \ref{ass:single_crossing}, the equilibrium is unique.
+\end{proposition}
+
+\begin{proposition}
     \label{prop:share_of_platform}
@@
     \begin{align*}
-        &\text{If } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} > 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} < 0, \\
+        &\text{If } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} < 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} < 0, \\
         &\text{if } \frac{\partial^2 f(N_P, N_F)}{\partial n_P \partial n_F} > 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} > 0
@@
     \begin{align*}
-        &\text{If } \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} > 0 \forall n_P \leq N_P, \text{ then } \frac{\partial N_F^*}{\partial N_P} < 0. \\
-        &\text{If } \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} > 0 \forall n_P \leq N_P, \text{ then } \frac{\partial N_F^*}{\partial N_P} > 0.
+        &\text{If } \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} < 0 \;\forall n_P \leq N_P, \text{ then } \frac{\partial N_F^*}{\partial N_P} < 0. \\
+        &\text{If } \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} > 0 \;\forall n_P \leq N_P, \text{ then } \frac{\partial N_F^*}{\partial N_P} > 0.
     \end{align*}
@@
 
-\subsection{Demand}
+\subsection{Setup}
+
+\subsubsection{Demand}
 
@@
 where $v^F_i$ is the value of product $i$, $p^F_i$ is its price, and $\epsilon^F_{ij}$ is an idiosyncratic taste shock.
-Throughout this paper I assume that the value of each product is the same: $v^F_i = v^F$.
+Throughout this section I assume that the value of each product is the same: $v^F_i = v^F$.
 This is to simplify the analysis, but is not crucial for getting the results.  % TODO: look into relaxing this assumption
@@
 
-\subsection{Production}
+\subsubsection{Production}
 
@@
 Finally, I assume that the product prices its products as if they were produced by separate, monopolistically competitive sellers.
-That is, it does not take into account the fact that it can affect a non-zero measure of the prices, and therefore the aggregate demand.\footnote{
-    As I show in section TODO the appendix, this assumption is more innocuous than it seems.
-    If the platform can commit to the price of its products before the entry of the fringe firms, then the results are the same regardless if the platform behaves as a continuum of atomic firms or one single firm with many products.
-    If the platform cannot make this commitment, and determines its prices after entry decisions are made, the results change quantitatively, but the main ideas carry over.
-% TODO: check this!!!!!!!!!!
-}
+That is, it does not take into account the fact that it can affect a non-zero measure of the prices, and therefore the aggregate demand.
+This is to simplify the example, but I expect that it does not affect the main results qualitatively
 
-\subsection{Intermediation}
+\subsubsection{Intermediation}
 
-Assume that the sellers and the consumers can only interact through an intermediary platform, denoted by $P$.
+As in \cref{sec:model}, assume that the sellers and the consumers can only interact through an intermediary platform, denoted by $P$.
 Without the platform, the fringe firms are not able to sell their products, and thus make no profits.
@@
 
-As mentioned above, instead of operating as a pure marketplace, the platform can also produce and offer its own products.
+As mentioned above, instead of operating as a pure marketplace, the platform may also produce and offer its own products.
 In case it does, it is called a hybrid platform.
-Additionally, the platform can choose to exclude all the fringe firms from the market (e.g.
+% Additionally, the platform can choose to exclude all the fringe firms from the market (e.g.
 by setting a sufficiently high entry fee), and only offer its own products.
@@
 
-\subsection{Entry and timing}
+\subsubsection{Entry and timing}
 
+The structure of the game follows closely that of the more general model in \cref{sec:model}.
+In addition, a benchmark model without bargaining is presented, for comparison.
 There is an infinite measure of fringe firms, who are deciding whether to enter the market.
@@
 
-\subsection{Bargaining}
-
 The main difference between the benchmark and the bargaining model is in determining the entry fee $F_F$.
@@
 On the other hand, in the bargaining model, I assume that the entry fee is the result of a negotiation between the parties.
-% TODO: entry fee cap?
+In particular, I use the profit sharing rule from \cref{ass:profit_sharing} with $w(s) \equiv 1$.
 
-Instead of modeling the bargaining process in detail, choose a reduced form approach.
-I assume that the final, net profits (after paying and receiving entry fees) correspond to the Shapley value of the participants in the following, cooperative game.\footnote{
-    This way of modeling bargaining has precedents in the industrial organization literature \parencite[e.g.][]{hart1990property,segal2003collusion,inderst2003bargaining,montez2007downstream}.
-    Furthermore, a number of papers show that various extensive-form bargaining games result in this outcome \parencite{gul1989bargaining,winter1994demand,hart1996bargaining,inderst2003bargaining,stole1996intra}.
-}
-Assume that the value of a coalition consisting of the platform and a measure $N_F$ of fringe firms is the total profits that they can achieve by selling their products in the last stage \emph{using monopolistic pricing}.\footnote{
-    Note that lump-sum entry fees do not influence this value, as they are just transfers between coalition members.
-}
-The value of a coalition without a platform is simply zero.
-% TODO: elaborate on how entry fees are not too important.
+\subsection{Equilibrium}
 
-\section{Equilibrium}
-
-\subsection{Producer profits}
+\subsubsection{Demand and producer profits}
 
 As shown in \textcite[]{anderson2021hybrid}, the utility functions described in \cref{sec:model} give rise to a logit-type demand function.
-Specifically, the demand for product $i$ of producer $T \in \{P, F\}$ is given by:
+\begin{proposition}
+    The demand for product $i$ of producer $T \in \{P, F\}$ is given by:
     \begin{align*}
@@
     \end{align}
-The producers' variable profit function is then given by
-\begin{align}
-    \pi^v_{Ti} = ( p_{Ti} - c_T ) \frac{\exp\left( \frac{v_T - p_{Ti}}{\mu} \right)}{A}.
-    \label{eq:variable_profit}
-\end{align}
+\end{proposition}
 
-Notice that, as each producer is infinitesimal, its pricing decision does not affect the aggregate $A$.
-It follows that the profit maximizing price is a simple additive markup over marginal cost
+Let us call $p_{Ti}$ the net value of product $i$.
+As one would expect, demand is increasing in this net vale, and decreasing in the competitors' net 
+Furthermore, demand for each product is increasing in $\mu$, which can be thought of as the degree of product differentiation or the importance of taste shocks.
+Finally, notice that, as each producer is infinitesimal, its pricing decision does not affect the aggregate $A$.
+This last property makes the optimal prices and profits of the producers very simple, as shown in the next proposition.
+% \begin{align}
+%     \pi^v_{Ti} = ( p_{Ti} - c_T ) \frac{\exp\left( \frac{v_T - p_{Ti}}{\mu} \right)}{A}.
+%     \label{eq:variable_profit}
+% \end{align}
+\begin{proposition}
+    The profit maximizing price for prouct $Ti$ is
     \begin{align*}
@@
     \end{align*}
-and the optimal profit is
+    and the profit from selling that product is
     \begin{align}
@@
     \end{align}
-For fringe firms, their total profit (including the investment cost $I_F$ and the entry fee $F_F$) is given by
-\begin{align}
-    \pi^{t*}_F = \mu \frac{\exp \left( \frac{v_F - c_F - \mu}{\mu} \right)}{A} - I_F - F_F.
-    \label{eq:fringe_profit}
-\end{align}
+\end{proposition}
 
+% For fringe firms, their total profit (including the investment cost $I_F$ and the entry fee $F_F$) is given by
+% \begin{align}
+%     \pi^{t*}_F = \mu \frac{\exp \left( \frac{v_F - c_F - \mu}{\mu} \right)}{A} - I_F - F_F.
+%     \label{eq:fringe_profit}
+% \end{align}
 For ease of notation, let us define the following:
@@
 
-\subsection{The benchmark model}
+Finally, another important feature of this demand system is that, assuming optimal pricing, consumer welfare only depends on the size of the aggregate \parencite{anderson2020aggregative}.
+In particular, consumer surplus is proportional to the logarithm of the aggregate:
+\begin{align*}
+    CS \propto \log(A).
+\end{align*}
+This fact makes welfare analysis rather simple in this setting.
+
+\subsubsection{The benchmark model}
 
@@
 Therefore, total profits in equilibrium must be zero.
-Let us for the moment assume that fixed fees are low enough for some fringe firms to enter the market.
-In this case, setting $\pi^{t*}_F$, equation \eqref{eq:fringe_profit} implies that the size of the aggregate is
+Combined with the simple profit function, this gives the following expressions for the equilibrium number of fringe firms and the equilibrium size of the aggregate.
+\begin{proposition}
+    If entry costs $I_F$ and $F_F$ are low enough, the equilibrium size of the aggregate is
     \begin{align}
@@
     \end{align}
-Substituting this into equation \eqref{eq:aggregate} and rearranging gives the number of fringe firms that enter the market:
+    and the equilibrium number of fringe firms is
     \begin{align*}
@@
 
-If, on the other hand, entry costs are too high, no fringe firms enter the market ($N_F = 0$).
-In that case, the aggregate demand is just
+    Otherwise, the equilibrium size of the aggregate is
     \begin{align*}
@@
     \end{align*}
+\end{proposition}
+Note that in the first case, the size of the aggregate does not depend on the platforms' product variety or the platform's product advantage.
 
-In the first period of the game, the platform chooses an entry fee to maximize its total profit, consisting of revenue from its own sales and the collected entry fees.
+Now let us turn to the optimal entry fee set by the platform, and its total profits, consisting of revenue from its own sales and the collected entry fees.
 First, let us examine the case when the fees are low enough for the fringe to be feasible.
-Profits from sales can be obtained by combining equations \eqref{eq:variable_profit} and \eqref{eq:aggregate_eq}:
-\begin{align*}
-    \pi_P^{v} = N_P (F_F + I_F) \frac{V_P}{V_F}.
-\end{align*}
-% TODO: other cases
-It is increasing in the (1) number of the platform's products, (2) the platform's product advantage (larger market share) and (3) the entry costs for fringe firms (less competition).
-The other component of the platform's profit, entry fees collected from the fringe, are given by
-\begin{align*}
-    \pi_P^{f} = N_F F_F = F_F \left[ \frac{\mu}{F_F + i} - N_P \frac{V_P}{V_F} - \frac{1}{V_F} \right].
-\end{align*}
 
-Combining these two, the platform's total profit as a function of the entry fee can be expressed as
-\begin{align}
-    \pi_P^{t} = \mu\frac{F_F}{F_F + I_F} + N_P I_F \frac{V_P}{V_F} - \frac{F_F}{V_F}
-    \label{eq:hybrid_profit}
-\end{align}
-Note, that even though the platform's profit is increasing in the number of its products, the optimal entry fee does not depend on it.
-In particular, the optimal entry fee is given by
+\begin{proposition}
+    The optimal entry fee is
     \begin{align*}
@@
     \end{align*}
+    The platform's total profit is
+    \begin{align*}
+        \pi_P^{t} = \mu - 2\sqrt{\frac{I_F \mu}{V_F}} + \frac{I_F}{V_F} (N_P V_P + 1)
+    \end{align*}
+    in the hybrid regime, and
+    \begin{align*}
+        \pi_P^{t} = \pi_P^{v} = \mu \frac{ N_P V_P}{N_P V_P + 1}
+    \end{align*}
+    in the retail regime.
+\end{proposition}
+Note, that even though the platform's profit is increasing in the number of its products, the optimal entry fee does not depend on it.
 As a consequence, as long as the fringe is feasible at the optimal entry fee, the size of the aggregate, and hence consumer welfare is also unaffected by the platform operating in hybrid mode.
-Substituting it into the profit function, the maximized profit is
-\begin{align*}
-    \pi_P^{t} = \mu - 2\sqrt{\frac{I_F \mu}{V_F}} + \frac{I_F}{V_F} (N_P V_P + 1).
-\end{align*}
+In contrast, when the fringe is not present in the market, total aggregate, and hence consumer welfare are increasing in the number of the platform's products.
+This is purely mechanical: more variety leads to higher welfare.
 
-Now let us consider the case when the fringe is not present in the market.
-In this case, the collected entry fees are obviously zero, and the platform's profit is simply given by
-\begin{align*}
-    \pi_P^{t} = \pi_P^{v} = \mu \frac{ N_P V_P}{N_P V_P + 1}.
-\end{align*}
-In this regime, total aggregate, and hence consumer welfare are increasing in the number of the platform's products.
-This is mechanical: more variety leads to higher welfare.
-
-Finally, note that the profit of the platform in the hybrid regime is higher than in the retail regime, when the former is feasible.
+Finally, note that the profit of the platform in the hybrid regime is higher than in the retail regime, whenever the former is feasible.
 This is a consequence of the fact that equation \eqref{eq:hybrid_profit} is strictly concave in $F_F$, therefore $F_F^*$ is a global maximum.
-It implies that there is no jump in no point where the fringe would be feasible under optimal entry fees, but the platform would prefer to operate in retail mode.
-Therefore, in the benchmark model, a platform becomes a hybrid platform, or increasing the number of its own products, always has a weakly positive effect on the aggregate, and thus consumer welfare.
+It implies that there is no point where the fringe would be feasible under optimal entry fees, but the platform would prefer to operate in retail mode.
+Therefore, in the benchmark model, a platform becoming a hybrid platform, or increasing the number of its own products, always has a weakly positive effect on the aggregate, and thus consumer welfare.
 This is in contrast to \textcite{anderson2021hybrid}, where a platform operating in hybrid mode sets a higher entry fee to advantage its own products, which in turn leads to a smaller aggregate.
@@
 
-\subsection{Bargaining outcomes}
+\subsubsection{The bargaining model}
 
@@
 The participants negotiate over the aggregate profits that they can achieve in the subsequent period (assuming non-collusive, monopolistic pricing, as before).
-I assume that bargaining outcomes are the Shapley values of the participants, where the value of a coalition is defined as the total profits that the coalition can achieve by selling their products.
-As the platform is necessary to reach the customers, the value of any coalition that does not include the platform is zero.
-Furthermore, using equation \eqref{eq:variable_profit}, the value of a coalition with $n$ fringe firms and the platform is
+I assume that bargaining outcomes are determined according to \cref{ass:profit_sharing}, where $f(N_P, N_F)$ is defined as the total profits that the platform and the entrants can achieve by selling their products.
+From \cref{eq:optimal_profit}, the total profit achieved by the platform and $N_F$ fringe firms is given by
 \begin{align*}
-    v(n) = \mu \frac{n V_F + N_P V_P}{n V_F + N_P V_P + 1}.
+    f(N_P, N_F) = \mu \frac{n V_F + N_P V_P}{n V_F + N_P V_P + 1}.
 \end{align*}
-
-\Cref{prop:one_sided} gives a simple formula for the Shapley value of the platform in case $N_F$ fringe firms made the initial investment:
+This yields the following closed-form expressions for the total profits of the partcipants.
+\begin{proposition}
+    The platform's total profits are
     \begin{align*}
-    \pi^t_P &= \varphi_P = \int_0^1 v(tN_F) \dt \\
-            &= \mu \left[ 1 - \frac{\log \left(1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} \right]
+        \pi^t_P &= \varphi_P = \int_0^1 f(N_P, sN_F) \ds \\
+                &= \mu \left[ 1 - \frac{\log \left(1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} \right].
     \end{align*}
-Subsequently, the fringe gets the remainder of the profits, therefore
-\begin{align}
-    \pi^v_F &= \varphi_F =  1 - \int_0^1 v(tN_F) \dt \\
-            &= \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right]
-            \label{eq:fringe_variable_profit}
-\end{align}
-and the total profits of the whole fringe are
+    The total profits of the whole fringe is given by
     \begin{align*}
-    \pi^t_F = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F N_F
+        \pi^t_F = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F N_F.
     \end{align*}
-The free entry condition implies that fringe profits are zero, therefore the number of fringe entrants is given by the implicit equation
-\begin{align}
-    \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F N_F = 0
-    \label{eq:free_entry_bargaining}
-\end{align}
+\end{proposition}
+\textcolor{red}{TODO: add an example figure}
 
 \textcolor{red}{
-    What I really want to show at this point is that if $N_F$ is determined by equation \eqref{eq:free_entry_bargaining}, then the total aggregate is decreasing in $N_P$.
-    Unfortunately, I don't have a closed form for $N_F^*$, and the IFT does not seem to lead to useful results, either.
-    Therefore, at this point, all I can do is show it through some numerical examples.
-    That won't guarantee of course that it holds in general.
+    Note: I have not managed to prove lemma \ref{lem:profit_assumptions} yet, but I'm pretty sure it's true.
+    In case I'm not able to come up with a proof, I'll just use some results based on numerical simulations using the closed form expressions above.
 }
 
-\textcolor{red}{
-    I have a graphical reasoning in mind though, that I might be able to make precise in the future.
-    For the moment, I'd rather not include it as it might be completely wrong.
-}
+Now let us turn to how the platform's hybridness affects product variety and consumer welfare.
+Let us start by establishing some properties of the toral profit function $f(n_P, n_F)$.
+\begin{lemma}
+    \label{lem:profit_assumptions}
+    $f(n_P, n_F)$ satisfies assumption \ref{ass:single_crossing}.
+    Furthermore,
+    \begin{align*}
+        \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} < 0.
+    \end{align*}
+\end{lemma}
 
-%\section{Extensions}
+% \section{Extensions}
 
-%\section{Conclusion}
+\section{Conclusion}
 
@@
 
-\begin{lemma}
-    \label{lem:shape_of_pi_F}
-    For any $V_F, N_P, V_P, \mu$, the function $\pi^v_F$ is either concave in $N_F$ or decreasing in $N_F$.
-\end{lemma}
-\begin{proof}
-    Did not manage to prove it yet.
-\end{proof}
-
-\begin{corollary}
-    \label{cor:unique_eq}
-    There is at most one equilibrium with $N_F > 0$.
-\end{corollary}
-
 \begin{proposition}

### 2023-02-06 src/paper/application.tex
Finish first draft of examples section

@@
 \newtheorem{assumption}{Assumption}
+\crefname{assumption}{assumption}{assumptions}
 
@@
 Assume that there are two types of players in the market: a platform $P$ and a continuum of fringe sellers $F_i$.
+The fringe firms each have one product, which they can only sell through the platform.
+The platform itself may also have its own products in addition to acting as an intermediary between the fringe and the consumers.
+In that case it is referred to as a hybrid platform.
+The main feature of the model is, instead of assuming that entry fees or royalties are set by the platform and the fringe treat it as take it or leave it offers, I assume that the platform and the fringe engage in some kind of bargaining over their total profits.
+The bargaining rule, as well as other details of the morel, are described in the rest of this section.
 
@@
 
-Some preliminary (hand-wavily proven) results about equilibrium profits and entry.
+These are some preliminary (hand-wavily proven) results about equilibrium profits and entry.
 
+First, a technical, but important result.
 \begin{proposition}
     \label{prop:unique_equilibrium}
-    Under the conditions in assumption \ref{ass:single_crossing}, the equilibrium is unique.
+    Under the conditions in \cref{ass:single_crossing}, the equilibrium is unique.
 \end{proposition}
 
-\begin{proposition}
-    \label{prop:share_of_platform}
-    Assume that $f, w$ are continuously differentiable and that $w$ has a non-zero measure support.
-    Then $\pi_P$ is also differentiable and
-    $$\frac{\partial \pi_P(N_P, n_F)}{\partial N_P} > 0$$.
-\end{proposition}
+The following statements provide some comparative statics for equilibrium profits and entry.
+% \begin{proposition}
+%     \label{prop:share_of_platform}
+%     Assume that $f, w$ are continuously differentiable and that $w$ has a non-zero measure support.
+%     Then $\pi_P$ is also differentiable and
+%     $$\frac{\partial \pi_P(N_P, n_F)}{\partial N_P} > 0$$.
+% \end{proposition}
 
@@
 \begin{corollary}
-    \label{fringe_entry}
+    \label{cor:fringe_entry}
     Assume that $f, w$ are twice continuously differentiable and that $w$ has a non-zero measure support.
@@
 \end{corollary}
+
+The following proposition establishes a stronger result for a particular class of profit functions.
+\begin{proposition}
+    \label{prop:aggregate_size_additive}
+    Let $f$ have the following, additive form:
+    \begin{align*}
+        f(N_P, N_F) = g(\alpha N_P + \beta N_F)
+    \end{align*}
+    where $\alpha, \beta > 0$.
+    Furthermore, assume that $g$ is twice differentiable and that $g'' < 0$.
+    Then
+    \begin{align*}
+        \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}.
+    \end{align*}
+\end{proposition}
 
@@
     \begin{align*}
-        \pi^t_P &= \varphi_P = \int_0^1 f(N_P, sN_F) \ds \\
+        \pi^t_P &\int_0^1 f(N_P, sN_F) \ds \\
                 &= \mu \left[ 1 - \frac{\log \left(1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} \right].
@@
 \textcolor{red}{
-    Note: I have not managed to prove lemma \ref{lem:profit_assumptions} yet, but I'm pretty sure it's true.
+    Note: I have not managed to prove \cref{lem:profit_assumptions} yet, but I'm pretty sure it's true.
     In case I'm not able to come up with a proof, I'll just use some results based on numerical simulations using the closed form expressions above.
@@
     \label{lem:profit_assumptions}
-    $f(n_P, n_F)$ satisfies assumption \ref{ass:single_crossing}.
+    $f(n_P, n_F)$ satisfies \cref{ass:single_crossing}.
     Furthermore,
@@
 \end{lemma}
+Using this, \cref{prop:unique_equilibrium} gives that the equilibrium is unique.
+Furthermore, \cref{cor:fringe_entry} implies that an increase in the hybridness of the platform leads to a reduction in the number of fringe firms that enter the market.
+
+Owing to the additive nature of the total profit function, an even stronger result can be established.
+Notice that $f$ has the functional form required for proposition \ref{prop:aggregate_size_additive} with $g(x) = \frac{x}{1+x}, \alpha = V_P, \beta = V_F$.
+Therefore, the same proposition implies that
+\begin{align*}
+    \frac{\partial N_F^*}{\partial N_P} < -\frac{V_P}{V_F},
+\end{align*}
+and in turn, equilibrium total aggregate is also decreasing in $N_P$.\footnote{
+    The same result can also easily be shown for an increase in $V_P$.
+}
+As in this model consumer welfare is monotone in the total aggregate, this implies that consumer welfare is decreasing in the number of the platform's products.
+Therefore, as opposed to the benchmark model, the platform becoming more hybrid leads to a reduction in consumer welfare.\footnote{
+    Unless $V_P N_P$ is high enough that the platform would operate in the benchmark model, too.
+}
+
+\textcolor{red}{TODO: add figure showing consumer welfare in the benchmark and bargaining models as a function of $N_P$}
 
@@
 
-\section{Miscellaneous lemmas and proofs}
-
-The following proposition shows that, if the platform is operating in a more hybrid mode (meaning it has more or better products), then, for a given aggregate size, the fringe obtains a lower share of the profits.
-This is due to the increased bargaining power of the platform.
-
-\begin{proposition}
-    \label{prop:fringe_profit_decreasing_in_N_P}
-    For a fixed aggregate size $A$, fringe profit is decreasing in $N_P$ and $V_P$.
-\end{proposition}
-\begin{proof}
-    Let $N_P' V_P' > N_P V_P$.
-    Furthermore, let $N_F V_F = A - N_P V_P - 1$ and $N_F' V_F' = A - N_P' V_P' - 1$ for some $A > 1$.
-    Finally, let
-    \begin{align*}
-        v(n) &= \mu \frac{n V_F + N_P V_P}{n V_F + N_P V_P + 1}, \\
-        v'(n) &= \mu \frac{n V_F + N_P' V_P'}{n V_F + N_P' V_P' + 1}.
-    \end{align*}
-
-    Observe that for any $t \in [0, 1)$,
-    \begin{align*}
-        v(tN_F) &= \frac{t N_F V_F + N_P V_P}{t N_F V_F + N_P V_P + 1} \\
-                &= \frac{tA - t + (1 - t) N_P V_P}{tA - t + (1 - t) N_P V_P + 1} \\
-                &< \frac{tA - t + (1 - t) N_P' V_P'}{tA - t + (1 - t) N_P' V_P' + 1} \\
-                &= \frac{t N_F' V_F' + N_P' V_P'}{t N_F' V_F + N_P V_P + 1} \\
-                &= v'(tN_F').
-    \end{align*}
-    This in turn implies that
-    \begin{align*}
-        \pi_F^v = \int_0^1 v(t) \dt < \int_0^1 v'(t) \dt = (\pi_F^v)',
-    \end{align*}
-    which is what we wanted to show.
-
-\end{proof}
-
-\begin{proposition}
-    \label{prop:A_decreasing_in_N_P}
-    The equilibrium aggregate size $A$ is monotonically decreasing in $N_P$ and $V_P$. When the fringe is feasible to begin with, the decrease is strict.
-\end{proposition}
-\begin{proof}
-    From \cref{prop:fringe_profit_decreasing_in_N_P}, we know that the fringe profit is decreasing in $N_P$ and $V_P$.
-    Furthermore, \cref{lem:shape_of_pi_F}
-\end{proof}
-
-\begin{corollary}
-    \label{consumer_welfare_decreasing_in_N_P}
-\end{corollary}
-\begin{proof}
-
-\end{proof}
-
 \end{document}

### 2023-03-24 src/paper/application.tex
Expand profit sharing rule section

@@
 \usepackage{xcolor}
+\usepackage{caption}
+\usepackage{subcaption}
 \usepackage[backend=biber,style=authoryear,maxbibnames=99,hyperref=true]{biblatex}
@@
 However, the model is more general, and the results apply to a broader class of settings.
-Chief among these is an upstream-downstream setting, with a single upstream producer and a continuum of downstream sellers.
+An important example of those is an upstream-downstream setting with a single upstream producer and a continuum of downstream sellers.
 
@@
 In that case it is referred to as a hybrid platform.
-The main feature of the model is, instead of assuming that entry fees or royalties are set by the platform and the fringe treat it as take it or leave it offers, I assume that the platform and the fringe engage in some kind of bargaining over their total profits.
-The bargaining rule, as well as other details of the morel, are described in the rest of this section.
+The main feature of the model is that, instead of assuming that entry fees or royalties are set by the platform and the fringe treat it as take it or leave it offers, I assume that the platform and the fringe engage in some kind of bargaining over their total profits.
+The bargaining rule, as well as other details of the model, are described in the rest of this section.
 
@@
 \end{assumption}
-While at first it might seem rather arbitrary, and much more convoluted than a simple percentage split, it has quite a few nice properties compared to the latter.
-Furthermore, \cref{sec:profit_sharing} provides some cooperative and non-cooperative microfoundations for this rule.\footnote{
+While somewhat more complex than a simple percentage split, it has quite a few adventages compared to the latter.\footnote{
     This way of modeling bargaining has precedents in the industrial organization literature \parencite[e.g.][]{hart1990property,segal2003collusion,inderst2003bargaining,montez2007downstream}.
@@
 }
-Let us start by examining the various parts of this rule, and then discuss how they impact the platform's profit share.
+On the theoretical side, the main argument in favor of this particular rule is its relation to the Shapley-value.\footnote{
+    \cref{sec:profit_sharing} shows that in the case of $w(s) \equiv 1$, $\pi_P(N_P, N_F)$ and $\pi_F(N_P, N_F)$ are the Shapley values of the platform and the fringe, respectively.
+}
+Shapley-value in turn has deep connections to bargaining theory.
+\textcite{gul1989bargaining,stole1996intra,hart1996bargaining,inderst2003bargaining}, along with a number of other papers, show that in various extensive-form bargaining games in the players' expected payoffs in the subgame perfect equilibrium correspond to their Shapley values.
 
-The main feature of this rule is that the platform's bargaining power depends on the substitutability of the fringe firms.
+The other main justification for this rule its intuitive behavior in terms of comparative statistics when varying $f$ and $w$.
+To illustrate this, let us examine the various parts of this rule, and then discuss how they impact the platform's profit share.
+
+The main feature of this rule is that the platform's bargaining power depends on the degree to which the fringe firms are complements or substitutes of each other.
 The following proposition demonstrates this idea.
@@
     \label{prop:outcome_based_bargaining_power}
-    Let $f, \tilde{f}: \mathbb{R}^+_0 \times \mathbb{R}^+_0 \to \mathbb{R}^+_0$ two different total profit functions such that $f(N_P, N_F) = \tilde{f}(N_P, N_F)$ for some $N_P, N_F$ and $f(n_P, n_F) \leq \tilde{f}(n_P, n_F)$ for all $n_P < N_P, n_F < N_F$.
+    Fix some $N_P \geq 0$.
+Let $f, \tilde{f}: \mathbb{R}^+_0 \times \mathbb{R}^+_0 \to \mathbb{R}^+_0$ two different total profit functions such that $f(N_P, N_F) = \tilde{f}(N_P, N_F)$ for some $N_P, N_F$ and $f(N_P, n_F) \leq \tilde{f}(N_P, n_F)$ for all $n_F < N_F$.
     Furthermore, let us denote the corresponding platform profit shares by $\pi_P$ and $\tilde{\pi}_P$.
@@
 \end{proposition}
-In words, when comparing two different total profit functions (i.e., demand systems, production functions), even if the total profits are the same under some pair $N_P, N_F$, profit shares might differ.
-In particular, the platform's profits are higher when it needs fewer firms to achieve a certain total profit level (i.e., when the fringe firms are more substitutable).
-\textcolor{red}{GRAPH HERE}
+
+In words, \cref{prop:outcome_based_bargaining_power} describes two alternative profit functions, under which $N_F$ fringe firms (along with the platform and it's $N_P$ products) are able to achieve the same total profit level.
+However, in one of these cases, the fringe firms are more substitutable to each other, in the sense that fewer of them are needed to achieve a given level of profit (see \cref{fig:outcome_based_bargaining_power}).
+The observation is that, in this situation, the platform's share is indeed higher when the fringe firms are more substitutable.
 This coincides with the intuitive idea that the platform's bargaining power is higher when it does not really mind loosing a few fringe sellers.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \begin{tikzpicture}[scale=0.8]
+            \centering
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
+                    xtick={0, 1}, ytick={0}, extra y ticks={1},  extra y tick style={yticklabel={$f(1)$}}]
+                \addplot[name path=f, blue,ultra thick] {x^2};
+                \node[anchor=north west] at (axis cs: .8, .8^0.5) {$f$};
+                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);
+
+                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
+
+                \node[anchor=north west] at (axis cs: .1, .9) {Fringe ($A$)};
+                \node[anchor=south east] at (axis cs: .9, .1) {Player $P$};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Fringe firms are complements}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
+                    xtick={0, 1}, ytick={0}, extra y ticks={1},  extra y tick style={yticklabel={$f(1)$}}]
+                \addplot[name path=f, blue,ultra thick] {x^0.5};
+                \node[anchor=north west] at (axis cs: .8, .8^0.5) {$\tilde{f}$};
+                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);
+
+                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
+
+                \node[anchor=north west] at (axis cs: .1, .9) {Fringe ($A$)};
+                \node[anchor=south east] at (axis cs: .9, .1) {Player $P$};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Fringe firms are substitutes}
+    \end{subfigure}
+    \caption{Distribution of value between player $P$ and the fringe}
+    \label{fig:outcome_based_bargaining_power}
+\end{figure}
 
@@
 }
-One way to think about it is that the platform's share is randomly drawn from the total profit according to some distribution, and $w$ is the probability density function of this distribution.
+
+One way to think about the weighting is that the platform's share is the expectation of the total profit, when the number of fringe firms is drawn from $[0, N_F]$ according to some distribution.\footnote{
+    In fact, this is exactly the idea behind the Shapley value: the platform (and other players, too) gets its expected marginal contribution to the total profit.
+    As the fringe cannot create any value without the platform, the latter's marginal contribution to a coalition of $n_F$ fringe firms is simply $f(n_F)$.
+}
+An obvious choice is to use the uniform distribution, in which case the shares correspond to the Shapley value.
+However, this is not the only possible choice.
+If, for example, we want to assume that the platform has a higher innate bargaining power, we can use a distribution with a higher mass on the right tail.\footnote{
+    Specific choices for $w$ can also be motivated by cooperative game theoretical concepts.
+    For example using, $w(s) = \lambda t^{\lambda - 1}$ leads to the weighted Shapley value, with weights $\lambda$ and $1$ for the platform and the fringe firms, respectively.
+}
 When the distribution $W_1$ first order stochastically dominates another distribution $W_2$, the platform is more likely to draw a value from with a higher mass of fringe firms, and therefore obtain a higher profit share in case of $W_1$ than in the case of $W_2$.
@@
 \end{proposition}
+
+Although the proposition is straightforward, it establishes that $w$ can indeed be used to represent some form of innate bargaining power.
+For example, if one has reason to believe that the platform has a stronger voice in the negotiation process, one can use a weight function with a higher mass on larger values.
 

### 2023-03-24 src/sympy/proof_of_lemma.py
Add calculations for proving the main lemma

@@ -1,0 +1,25 @@
+from sympy import Symbol, integrate, solve, Eq, init_printing, log, plot
+
+init_printing()
+
+x = Symbol('x')
+N_F = Symbol('N_F')
+f = x / (x + 1)
+
+int_f_sN = integrate(f, (x, 0, N_F)) / N_F
+
+int_1st = f.subs({x: N_F}) / N_F - int_f_sN / N_F
+int_2nd = f.diff(x).subs({x: N_F}) / N_F - 2 * f.subs({x: N_F}) / N_F**2 + 2 * int_f_sN / N_F**2
+
+eq_1 = Eq(f.diff(x).subs({x: N_F}), int_1st)
+eq_2 = Eq(f.diff(x, 2).subs({x: N_F}), int_2nd)
+
+plot(eq_1.lhs, eq_1.rhs, (N_F, 2, 5))
+plot(eq_2.lhs, eq_2.rhs, (N_F, 2, 5))
+
+
+sol_1 = solve(eq_1, log(1 + N_F))
+sol_2 = solve(eq_2, log(1 + N_F))
+
+plot(sol_1[0], sol_2[0], log(1+N_F), (N_F, 0, 5))
+

### 2023-03-24 src/paper/application.tex
Slightly rewrite entry and equilibrium section

@@
 
+\newtheorem{definition}{Definition}
 \newtheorem{proposition}{Proposition}
@@
     \end{subfigure}
-    \caption{Distribution of value between player $P$ and the fringe}
+    \caption{Distribution of value between the platform and the fringe (with $w(s) \equiv 1$)}
     \label{fig:outcome_based_bargaining_power}
@@
 The equilibrium number of entrants is determined by a free entry condition: in the end, the fringe firms' profits should be equal to the investment cost.
-\begin{assumption}
+\begin{definition}
     \label{ass:free_entry}
-    In equilibrium, $\pi_F(N_P, N_F) = I_F N_F$.
-\end{assumption}
+    Let us define a free entry equilibrium by the following conditions:
+    \begin{itemize}
+        \item Profits are shared according to \cref{ass:profit_sharing}.
+        \item Entrants make zero profits: $\pi_F(N_P, N_F) = I_F N_F$ after accounting for entry costs.
+    \end{itemize}
+\end{definition}
 
-In order to guarantee a unique equilibrium, let us make the following, additional assumption about the profit and bargaining weight functions.
+Finally, in order to guarantee a unique equilibrium, let us make the following, an additional assumption about the profit and bargaining weight functions.
 \begin{assumption}
@@
 \end{assumption}
-\textcolor{red}{TODO: Find interpretable sufficient conditions for this assumption.}
+The above assumption essentially guarantees that the profit of the fringe (as a function of the number of entrants) has at most a single crossing with the total entry cost (apart from the obvious $N_F=0$ intersection).
+While the conditions is not very simple to interpret, they can be verified once a specific choice for $f$ and $w$ is made.
+In particular, this assumption will be satisfied in the example in \cref{sec:example}.
 

### 2023-03-25 src/paper/application.tex
Set line spacing
Flesh out general results section

@@
 \usepackage{subcaption}
+\usepackage{setspace}
 \usepackage[backend=biber,style=authoryear,maxbibnames=99,hyperref=true]{biblatex}
+
+\setstretch{1.15}
 
@@
 \usetikzlibrary{shapes}
+\usetikzlibrary{intersections}
 \pgfplotsset{compat=1.17}
@@
 \newtheorem{definition}{Definition}
+\newtheorem{observation}{Observation}
 \newtheorem{proposition}{Proposition}
@@
 \newtheorem{assumption}{Assumption}
+
 \crefname{assumption}{assumption}{assumptions}
+\crefname{assumption}{Assumption}{Assumptions}
+\crefname{observation}{observation}{observations}
+\Crefname{observation}{Observation}{Observations}
 
@@
 The main feature of this rule is that the platform's bargaining power depends on the degree to which the fringe firms are complements or substitutes of each other.
-The following proposition demonstrates this idea.
-\begin{proposition}
+The following observation demonstrates this idea.
+\begin{observation}
     \label{prop:outcome_based_bargaining_power}
@@
     Then, $\pi_P \leq \tilde{\pi}_P$.
-\end{proposition}
+\end{observation}
 
@@
             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-                    xtick={0, 1}, ytick={0}, extra y ticks={1},  extra y tick style={yticklabel={$f(1)$}}]
+                    xtick={0, 1}, ytick={0}, extra y ticks={1}, extra y tick style={yticklabel={$f(1)$}},
+                    xlabel={$s$}]
                 \addplot[name path=f, blue,ultra thick] {x^2};
-                \node[anchor=north west] at (axis cs: .8, .8^0.5) {$f$};
+                \node[anchor= east] at (axis cs: .9, .9^2) {$f(N_P, sN_F)$};
                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
@@
             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-                    xtick={0, 1}, ytick={0}, extra y ticks={1},  extra y tick style={yticklabel={$f(1)$}}]
+                xtick={0, 1}, ytick={0}, extra y ticks={1}, extra y tick style={yticklabel={$f(1)$}},
+                xlabel={$s$}]
                 \addplot[name path=f, blue,ultra thick] {x^0.5};
-                \node[anchor=north west] at (axis cs: .8, .8^0.5) {$\tilde{f}$};
+                \node[anchor=north west] at (axis cs: .6, .6^0.5) {$\tilde{f}(N_P, sN_F)$};
                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
@@
 When the distribution $W_1$ first order stochastically dominates another distribution $W_2$, the platform is more likely to draw a value from with a higher mass of fringe firms, and therefore obtain a higher profit share in case of $W_1$ than in the case of $W_2$.
-The next proposition formalizes this idea.
-\begin{proposition}
+The next observation formalizes this idea.
+\begin{observation}
     \label{prop:innate_bargaining_power}
@@
     Furthermore, this inequality is strict if $\int_0^x w_1(s) \ds < \int_0^x w_2(s) \ds$ on some non-zero measure set.
-\end{proposition}
+\end{observation}
 
-Although the proposition is straightforward, it establishes that $w$ can indeed be used to represent some form of innate bargaining power.
+Although the reasoning is straightforward, it establishes that $w$ can indeed be used to represent some form of innate bargaining power.
 For example, if one has reason to believe that the platform has a stronger voice in the negotiation process, one can use a weight function with a higher mass on larger values.
@@
 
-\section{Results}
+\section{General results}
 
-These are some preliminary (hand-wavily proven) results about equilibrium profits and entry.
+This section presents some general result that only depend on the abstract model structure described in the previous section, and the assumptions therein.
+It is remarkable that even within such astylized setting and simple model, one can derive some interesting and non-trivial results.
+\Cref{sec:example} will then build on these results to derive some stronger implications in a more specific model.
 
-First, a technical, but important result.
+Let us start by a technical, but highly useful result.
 \begin{proposition}
     \label{prop:unique_equilibrium}
-    Under the conditions in \cref{ass:single_crossing}, the equilibrium is unique.
+    Under the conditions in \cref{ass:single_crossing}, the equilibrium is unique if it exists.
 \end{proposition}
+The intuition behind this result is that \cref{ass:single_crossing} ensures that the total profits achieved by the fringe is either concave or hump-shaped.
+Consequently, it has at most one crossing with the linear total entry cost (for $n_F > 0$).
+An example for this is shown in \cref{fig:equilibrium}.
+This particular shape is also the main driver for the following results about the comparative statics of equilibrium profits and entry.
 
-The following statements provide some comparative statics for equilibrium profits and entry.
-% \begin{proposition}
-%     \label{prop:share_of_platform}
-%     Assume that $f, w$ are continuously differentiable and that $w$ has a non-zero measure support.
-%     Then $\pi_P$ is also differentiable and
-%     $$\frac{\partial \pi_P(N_P, n_F)}{\partial N_P} > 0$$.
-% \end{proposition}
+\begin{figure}[ht]
+    \centering
+    \begin{tikzpicture}[xscale=2,yscale=2,samples=200]
+        \draw[->] (0,0) -- (0,2);
+        \draw[->] (0,0) -- (5.5,0) node[below] {$n_F$};
 
+        \draw[name path=piF,domain=0.01:5.5,variable=\x,blue,ultra thick] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
+        \draw[name path=IF,domain=0.01:5.5,variable=\x,red,ultra thick] plot ({\x},{(\x)/3});
+        \node[anchor=north east] at (5,1) {$\pi_F(N_P, n_F)$};
+        \node[anchor=south east] at (5,5/3) {$I_F n_F$};
+
+        \fill [name intersections={of=piF and IF, name=i, total=\t}]
+            [black] (i-2) circle (1pt);
+        \draw[dashed] (i-2) -- (i-2 |- 0,0) node[below] {$N_F^*$};
+    \end{tikzpicture}
+    \caption{An example free entry equilibrium under \cref{ass:single_crossing}}
+    \label{fig:equilibrium}
+\end{figure}
+
+For the following two propositions, let us ignore free entry and equilibrium behavior, and consider the number of fringe entrants $N_F$ as fixed.
+The following statement says that the platform's profit is increasing in its own product variety.
+\begin{proposition}
+    \label{prop:share_of_platform}
+    Assume that $f, w$ are continuously differentiable and that $w$ has a non-zero measure support.
+    Let $N_F \geq 0$.
+    Then $\pi_P$ is also differentiable and
+    $$\frac{\partial \pi_P(N_P, N_F)}{\partial N_P} > 0$$.
+\end{proposition}
+While it might seem obvious, let us still examine what this result does and does not mean.
+First, remember that $f$ is increasing in both arguments, and $N_F$ is fixed.
+Therefore, an increase in $N_P$ also increases the size of the pie the participants bargain over.
+This result states that the size of the pie that the platform gets increases in this case, too.
+It does not mean, however, that the \emph{relative share} of the pie that the platform gets is also bigger -- increase is also guaranteed in absolute terms.
+For example, it is possible that for the new, higher value of $N_P$, the complementarities between the fringe firms become stronger, and the platform's bargaining power decreases.
+This decrease cannot be so strong, however, to decrease the platform's profits in absolute terms.
+\cref{fig:increase_N_P_platform} shows an example of this situation.
+
+\begin{figure}[ht]
+    \centering
+    \caption{Illustration of \cref{prop:share_of_platform}}
+    \label{fig:increase_N_P_platform}
+\end{figure}
+
+Next, let us look at an analogous result for the fringe firms.
+As the next proposition demonstrates, in this case, the direction of the change depends on the complementarities between the fringe firms.
 \begin{proposition}
@@
     Assume that $f, w$ are twice continuously differentiable and that $w$ has a non-zero measure support.
-    Then $\pi_F$ is also differentiable. Let $N_F > 0$.
+    Let $N_F > 0$.
+    Then $\pi_F$ is also differentiable.
     \begin{align*}
         &\text{If } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} < 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} < 0, \\
-        &\text{if } \frac{\partial^2 f(N_P, N_F)}{\partial n_P \partial n_F} > 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} > 0
+        &\text{if } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} > 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} > 0
     \end{align*}
@@
 \end{proposition}
+In summary, when they are mostly substitutes (the cross-derivatives of $f$ are negative), the fringe's profits decrease as a result of an increase in $N_F$.
+The intuition is that, even though the total size of the pie increases, the bargaining power of the fringe deteriorates so much that its share decreases not only in relative, but also in absolute terms.
+On the other hand, when the fringe firms are mostly complements the fringe's profits increase.
 
+Now let us turn to equilibrium entry as a function of the platform's product variety.
+The previous proposition implies an almost immediate corollary regarding the equilibrium number of fringe entrants.
 \begin{corollary}
@@
     Let $N_F^*$ denote the equilibrium number of fringe firms.
+    Let us also assume that $N_F^* > 0$.
+    Then the equilibrium number of fringe firms is also differentiable and
     \begin{align*}
-        &\text{If } \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} < 0 \;\forall n_P \leq N_P, \text{ then } \frac{\partial N_F^*}{\partial N_P} < 0. \\
-        &\text{If } \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} > 0 \;\forall n_P \leq N_P, \text{ then } \frac{\partial N_F^*}{\partial N_P} > 0.
+        &\text{If } \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} < 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial N_F^*}{\partial N_P} < 0. \\
+        &\text{If } \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} > 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial N_F^*}{\partial N_P} > 0.
     \end{align*}
 \end{corollary}
+That is, the equilibrium number of entrants increases as a response to an increase in $N_P$ if the fringe firms are mostly complements, and decreases if they are mostly substitutes.
+The reason simply lies in the concave or hump-shaped fringe profit function.
+If $N_F^*$ is an equilibrium, then fringe profits minus entry costs are strictly positive for all $N_F \leq N_F^*$ and strictly negative for all $N_F > N_F^*$.
+Therefore, if an increase in $N_P$ decreases the fringe's profits for every $N_F \geq 0$, equilibrium can be restored by decreasing the number of fringe entrants, and vice versa for the other case (\cref{fig:comparative_N_F}).
 
-The following proposition establishes a stronger result for a particular class of profit functions.
+Finally, let us conclude this section by establishing a stronger result for a more restrictive class of profit functions.
+In the following, I assume that the profit function has a specific, additive form.
+Intuitively, this means that -- in terms of total profits generated -- the platform's and the fringe firms' products are substitutable to each other according to some constant ratio.\footnote{
+    Note that it does not mean that their products are \emph{substitutes} in the usual, demand theory sense.
+    They still might be complements to each other.
+}
 \begin{proposition}
@@
 \end{proposition}
+As opposed to the previous results, this proposition tells us something about the total profits generated by the platform and the fringe firms as a function of the platform's product variety, and under equilibrium entry behavior by the fringe firms.
+In particular, it states that total profits increase if the total profit function is convex (products are substitutes), and decreases otherwise.
+This result has particularly strong implications in models where total profits (or total product variety) has a monotone relationship with consumer welfare, such as those in \textcite{anderson2020aggregative}.
+\Cref{sec:example} also presents a model in which this is the case.
 
-\section{Example}
+\section{Example application}
 \label{sec:example}
 
-This section presents an example application of the model, based on \parencite[]{anderson2021hybrid}.
+Let us now turn to an example application of the somewhat abstract model presented in the previous sections.
+The model in this section is heavily inspired by the logit-like demand structur and hybrid platform setting in  \textcite{anderson2021hybrid}.
 The setting is a (possibly hybrid) platform market with monopolistically competing fringe firms.
@@
 Let us call $p_{Ti}$ the net value of product $i$.
-As one would expect, demand is increasing in this net vale, and decreasing in the competitors' net 
+As one would expect, demand is increasing in this net value, and decreasing in the competitors' net 
 Furthermore, demand for each product is increasing in $\mu$, which can be thought of as the degree of product differentiation or the importance of taste shocks.
@@
 \textcolor{red}{TODO: add an example figure}
-
-\textcolor{red}{
-    Note: I have not managed to prove \cref{lem:profit_assumptions} yet, but I'm pretty sure it's true.
-    In case I'm not able to come up with a proof, I'll just use some results based on numerical simulations using the closed form expressions above.
-}
 

### 2023-03-25 src/paper/application.tex
Add more graphs

@@
             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-                    xtick={0, 1}, ytick={0}, extra y ticks={1}, extra y tick style={yticklabel={$f(1)$}},
-                    xlabel={$s$}]
+                    xtick={0, 1}, ytick={0}, xlabel={$s$}]
                 \addplot[name path=f, blue,ultra thick] {x^2};
@@
                 \node[anchor=north west] at (axis cs: .1, .9) {Fringe ($A$)};
-                \node[anchor=south east] at (axis cs: .9, .1) {Player $P$};
+                \node[anchor=south east] at (axis cs: .9, .1) {Platform ($P$)};
             \end{axis}
@@
             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-                xtick={0, 1}, ytick={0}, extra y ticks={1}, extra y tick style={yticklabel={$f(1)$}},
-                xlabel={$s$}]
+                xtick={0, 1}, ytick={0}, xlabel={$s$}]
                 \addplot[name path=f, blue,ultra thick] {x^0.5};
@@
     \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
+                xtick={0, 1}, ytick={0}, axis lines=left, xlabel={$s$}]
+                \addplot[name path=f, blue,ultra thick] {ln(1+x)};
+                \addplot[name path=tildef, dashed, black] {x};
+                \node[anchor=north west] at (axis cs: .6, 0.5) {$f(N_P, sN_F)$};
+                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+                \draw[name path=top] (axis cs:0,0.693) -- (axis cs:1,0.693);
+                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,0.693);
+
+                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
+
+                \node[anchor=north west] at (axis cs: .05, .65) {Fringe ($A$)};
+                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Profit shares with $f$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
+                xtick={0, 1}, ytick={0}, axis lines=left, xlabel={$s$}]
+                \addplot[name path=f, dashed, black] {ln(1+x)};
+                \addplot[name path=tildef, blue,ultra thick] {x};
+                \node[anchor=south east] at (axis cs: 0.6, 0.6) {$\tilde{f}(N_P, sN_F)$};
+                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+                \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
+                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);
+
+                \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];
+
+                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($A$)};
+                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Profit shares with $\tilde{f}$}
+    \end{subfigure}
     \caption{Illustration of \cref{prop:share_of_platform}}
@@
 
+\begin{figure}[ht]
+    \centering
+    \begin{tikzpicture}[xscale=2,yscale=2,samples=200]
+        \draw[->] (0,0) -- (0,2);
+        \draw[->] (0,0) -- (5.5,0) node[below] {$n_F$};
+
+        \draw[name path=piF,domain=0.01:5.5,variable=\x,blue,ultra thick] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
+        \draw[name path=piF2,domain=0.01:5.5,variable=\x,blue,ultra thick] plot ({\x},{6*((\x)/(0.3+\x))-6*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
+        \draw[name path=IF,domain=0.01:5.5,variable=\x,red,ultra thick] plot ({\x},{(\x)/3});
+
+        \node[anchor=south] at (5,1) {$\pi_F(N_P, n_F)$};
+        \node[anchor=north] at (5,0.6) {$\pi_F(N_P', n_F)$};
+        \node[anchor=south east] at (5,5/3) {$I_F n_F$};
+
+        \fill [name intersections={of=piF and IF, name=i, total=\t}]
+            [black] (i-2) circle (1pt);
+        \draw[dashed] (i-2) -- (i-2 |- 0,0) node[below] {$N_F^*$};
+        \fill [name intersections={of=piF2 and IF, name=i2, total=\t}]
+            [black] (i2-2) circle (1pt);
+        \draw[dashed] (i2-2) -- (i2-2 |- 0,0) node[below] {$N_F^{*'}$};
+
+        \draw[->] (i-2 |- 0,0.5) -- (i2-2 |- 0,0.5);
+    \end{tikzpicture}
+    \caption{Comparative statistics for equilibrium entry (fringe are substitutes)}
+    \label{fig:comparative_N_F}
+\end{figure}
+
 Finally, let us conclude this section by establishing a stronger result for a more restrictive class of profit functions.
@@
 Intuitively, this means that -- in terms of total profits generated -- the platform's and the fringe firms' products are substitutable to each other according to some constant ratio.\footnote{
-    Note that it does not mean that their products are \emph{substitutes} in the usual, demand theory sense.
+    Note that it does not mean that their products are substitutes in the usual, demand theory sense.
     They still might be complements to each other.

### 2023-03-25 src/paper/application.tex
Even more figures in the model section

@@
 
-                \node[anchor=north west] at (axis cs: .1, .9) {Fringe ($A$)};
-                \node[anchor=south east] at (axis cs: .9, .1) {Platform ($P$)};
+                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($A$)};
+                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
             \end{axis}
@@
         \end{tikzpicture}
-        \caption{Profit shares with $f$}
+        \caption{Profit shares with $N_P$}
     \end{subfigure}
@@
                 \addplot[name path=tildef, blue,ultra thick] {x};
-                \node[anchor=south east] at (axis cs: 0.6, 0.6) {$\tilde{f}(N_P, sN_F)$};
+                \node[anchor=south east] at (axis cs: 0.6, 0.6) {$f(N_P', sN_F)$};
                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
@@
         \end{tikzpicture}
-        \caption{Profit shares with $\tilde{f}$}
+        \caption{Profit shares with $N_P'$}
     \end{subfigure}
-    \caption{Illustration of \cref{prop:share_of_platform}}
+    \caption{Illustration of \cref{prop:share_of_platform} ($N_P < N_P'$)}
     \label{fig:increase_N_P_platform}
@@
 In summary, when they are mostly substitutes (the cross-derivatives of $f$ are negative), the fringe's profits decrease as a result of an increase in $N_F$.
-The intuition is that, even though the total size of the pie increases, the bargaining power of the fringe deteriorates so much that its share decreases not only in relative, but also in absolute terms.
+The intuition is that, even though the total size of the pie increases, the bargaining power of the fringe deteriorates so much that its share decreases not only in relative, but also in absolute terms (as illustrated in \cref{fig:increase_N_P_fringe}).
 On the other hand, when the fringe firms are mostly complements the fringe's profits increase.
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.225, samples at={0, 0.02, ..., 0.98, 1},
+                xtick={0, 1}, ytick={0}, axis lines=left, xlabel={$s$}]
+                \addplot[name path=f, blue,ultra thick] {sqrt(x)};
+                \addplot[name path=tildef, dashed, black] {sqrt(0.5+x)};
+                \node[anchor=north west] at (axis cs: .6, 0.77) {$f(0, sN_F)$};
+                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+                \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
+                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);
+
+                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
+
+                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($A$)};
+                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Profit shares with $N_P = 0$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.225, samples at={0, 0.02, ..., 0.98, 1},
+                xtick={0, 1}, ytick={0}, axis lines=left, xlabel={$s$}]
+                \addplot[name path=f, dashed, black] {sqrt(x)};
+                \addplot[name path=tildef, blue,ultra thick] {sqrt(0.5+x)};
+                \node[anchor=north west] at (axis cs: 0, 0.7) {$f(0.5, sN_F)$};
+                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+                \draw[name path=top] (axis cs:0,1.225) -- (axis cs:1,1.225);
+                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1.225);
+
+                \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];
+
+                \node[anchor=north west] at (axis cs: .05, 1.17) {Fringe ($A$)};
+                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Profit shares with $N_P = 0.5$}
+    \end{subfigure}
+    \caption{Illustration of \cref{prop:share_of_fringe} (fringe firms are substitutes, $f(N_P, N_F) = \sqrt{N_P + N_F}$)}
+    \label{fig:increase_N_P_fringe}
+\end{figure}
 

### 2023-03-25 src/paper/application.tex
Do not ebbreviate references
Add figure to application section

@@
 \usepackage{pgfplots}
+\usepackage{pgfplotstable}
 \usepackage{hyperref}
-\usepackage[nameinlink]{cleveref}
+\usepackage[noabbrev,nameinlink]{cleveref}
 \usepackage{amsthm}
@@
 \crefname{assumption}{assumption}{assumptions}
-\crefname{assumption}{Assumption}{Assumptions}
+\Crefname{assumption}{Assumption}{Assumptions}
 \crefname{observation}{observation}{observations}
@@
 \newcommand{\E}{\mathbb{E}}
+
+\pgfplotstableread[col sep=comma]{out/figures/equilibrium.csv}\equilibrium
 
@@
 In the baseline model, I assume that entry is free for the consumers, and they are always present on the platform, no matter the other players' entry and pricing decisions.\footnote{
-    This essentially means that I assume a one-sided platform, without the usual strong network effects.
+    This essentially means that I assume a one-sided platform, without the usual network effects.
     % TODO: see if I can relax this assumption
@@
 
-Let us call $p_{Ti}$ the net value of product $i$.
-As one would expect, demand is increasing in this net value, and decreasing in the competitors' net 
+Let us call $v_T - p_{Ti}$ the net value of product $i$.
+As one would expect, demand is increasing in this net value, and decreasing in the competitors' net values.
 Furthermore, demand for each product is increasing in $\mu$, which can be thought of as the degree of product differentiation or the importance of taste shocks.
@@
 
-    Otherwise, the equilibrium size of the aggregate is
+    Otherwise, if they are sufficiently high, $N_F = 0$ and the equilibrium size of the aggregate is
     \begin{align*}
@@
 \end{align*}
-This yields the following closed-form expressions for the total profits of the partcipants.
+This yields the following closed-form expressions for the total profits of the participants.
 \begin{proposition}
@@
     \begin{align*}
-        \pi^t_P &\int_0^1 f(N_P, sN_F) \ds \\
+        \pi^t_P &=\int_0^1 f(N_P, sN_F) \ds \\
                 &= \mu \left[ 1 - \frac{\log \left(1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} \right].
@@
 Now let us turn to how the platform's hybridness affects product variety and consumer welfare.
-Let us start by establishing some properties of the toral profit function $f(n_P, n_F)$.
+Let us start by establishing some properties of the total profit function $f(n_P, n_F)$.
 \begin{lemma}
@@
 \textcolor{red}{TODO: add figure showing consumer welfare in the benchmark and bargaining models as a function of $N_P$}
+
+\begin{figure}
+    \centering
+    \begin{tikzpicture}
+        \begin{axis}[
+                xlabel={$N_P$},
+                ylabel={$N_F^*$},
+                xmin=0, xmax=1, % adjust these values as needed
+                ymin=0, ymax=1, % adjust these values as needed
+                % grid=major,
+                % grid style={dashed,gray!30},
+                width=6cm, % adjust the width of the plot
+                height=6cm, % adjust the height of the plot
+                axis lines=left,
+                xtick=\empty, ytick=\empty
+            ]
+            \addplot[color=blue,mark=none,very thick] table[x=N_P,y=N_F]{\equilibrium};
+            \addplot[color=black,mark=none,dashed] table[x=N_P,y=N_F_cf]{\equilibrium};
+        \end{axis}
+    \end{tikzpicture}
+    \caption{The equilibrium number of fringe firms as a function of the number of platform products.}
+    \label{fig:fringe_entry_eq}
+\end{figure}
 

### 2023-03-25 src/figures/equilibrium.py

@@ -1,0 +1,60 @@
+import pandas as pd
+import numpy as np
+from scipy.optimize import fsolve
+from collections.abc import Iterable
+import typer
+
+
+def create_plot_data(
+    out_path: str,
+    mu: float = 1,
+    V_P: float = 1,
+    V_F: float = 1,
+    I_F: float = 0.2,
+    N_P_range: tuple[float, float] = (0, 1),
+    num_obs: int = 500,
+):
+    def pi_P(N_P, N_F):
+        inner_part = np.log(1 + (N_F * V_F) / (N_P * V_P + 1)) / (N_F * V_F)
+        return mu * (1 - inner_part)
+
+    def pi_F(N_P, N_F):
+        first_part = np.log(1 + (N_F * V_F) / (N_P * V_P + 1)) / (N_F * V_F)
+        second_part = 1 / (N_P * V_P + N_F * V_F + 1)
+        return mu * (first_part - second_part)
+
+    def pi_F_t(N_P, N_F):
+        return pi_F(N_P, N_F) - I_F * N_F
+
+    def N_F_opt(N_P):
+        if isinstance(N_P, Iterable):
+            return np.array([N_F_opt(n) for n in N_P])
+        else:
+            return fsolve(lambda N_F: pi_F_t(N_P, N_F), 1)[0]
+
+    N_P_vec = np.linspace(N_P_range[0], N_P_range[1], num_obs)
+    N_F_vec = N_F_opt(N_P_vec)
+    N_F_cf_vec = np.maximum(N_F_vec[0] * V_F - N_P_vec * V_P, 0)
+
+    pi_F_vec = pi_F(N_P_vec, N_F_vec)
+    pi_P_vec = pi_P(N_P_vec, N_F_vec)
+    A_vec = N_P_vec * V_P + N_F_vec * V_F + 1
+    CS_vec = np.log(A_vec)
+
+    data = pd.DataFrame(
+        {
+            "N_P": N_P_vec,
+            "N_F": N_F_vec,
+            "pi_F": pi_F_vec,
+            "pi_P": pi_P_vec,
+            "A": A_vec,
+            "CS": CS_vec,
+            "N_F_cf": N_F_cf_vec,
+        }
+    )
+
+    data.to_csv(out_path, index=False)
+
+
+if __name__ == "__main__":
+    typer.run(create_plot_data)

### 2023-03-25 src/utils/makeutils.py

@@ -27,7 +27,8 @@ def find_input_files(tex_file: str, remove_prefix: str = "", print_console: bool
     patterns = [
         re.compile(r"\\input\{(.*)\}"),
         re.compile(r"\\include\{(.*)\}"),
-        re.compile(r"\\includegraphics(?:\[.*\])?\{(.*)\}")
+        re.compile(r"\\includegraphics(?:\[.*\])?\{(.*)\}"),
+        re.compile(r"\\pgfplotstableread(?:\[.*\])\{(.*)\}"),
     ]
 
     paths = sum((pattern.findall(tex_contents) for pattern in patterns), [])

### 2023-03-26 src/paper/application.tex
Add more graphs to results section

@@
 
+\begin{figure}
+    \centering
+    \begin{tikzpicture}
+        \begin{axis}[
+                xlabel={$N_P$},
+                ylabel={$A^*$},
+                xmin=0, xmax=1.5, % adjust these values as needed
+                ymin=0, ymax=2.6, % adjust these values as needed
+                width=10cm, % adjust the width of the plot
+                height=6cm, % adjust the height of the plot
+                axis lines=left,
+                xtick=\empty, ytick=\empty,
+                legend pos=south east
+            ]
+            \addplot[color=blue,mark=none,very thick] table[x=N_P,y=A_bench]{\equilibrium};
+            \addplot[color=red,mark=none,very thick] table[x=N_P,y=A]{\equilibrium};
+            \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=A_noF]{\equilibrium};
+            \legend{Benchmark, Bargaining, Pure retail}
+        \end{axis}
+    \end{tikzpicture}
+    \caption{Equilibrium aggregate as a function of the number of platform products.}
+    \label{fig:aggregate_eq}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \begin{tikzpicture}
+        \begin{axis}[
+                xlabel={$N_P$},
+                ylabel={$\pi_P^{t*}$},
+                xmin=0, xmax=1.5, % adjust these values as needed
+                ymin=0, ymax=0.65, % adjust these values as needed
+                width=10cm, % adjust the width of the plot
+                height=6cm, % adjust the height of the plot
+                axis lines=left,
+                xtick=\empty, ytick=\empty,
+                legend pos=south east
+            ]
+            \addplot[color=blue,mark=none,very thick] table[x=N_P,y=pi_P_bench]{\equilibrium};
+            \addplot[color=red,mark=none,very thick] table[x=N_P,y=pi_P]{\equilibrium};
+            \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=pi_P_noF]{\equilibrium};
+            \legend{Benchmark, Bargaining, Pure retail}
+        \end{axis}
+    \end{tikzpicture}
+    \caption{Equilibrium platform profit as a function of the number of platform products.}
+    \label{fig:pi_P_eq}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \begin{tikzpicture}
+        \begin{axis}[
+                xlabel={$N_P$},
+                ylabel={$F_F$},
+                xmin=0, xmax=1.5, % adjust these values as needed
+                ymin=0, ymax=0.65, % adjust these values as needed
+                width=10cm, % adjust the width of the plot
+                height=6cm, % adjust the height of the plot
+                axis lines=left,
+                xtick=\empty, ytick=\empty,
+                legend pos=north east
+            ]
+            \addplot[color=blue,mark=none,very thick] table[x=N_P,y=F_F_opt]{\equilibrium};
+            \addplot[color=red,mark=none,very thick] table[x=N_P,y=F_F_implied]{\equilibrium};
+            \legend{Benchmark (optimal), Bargaining (implied)}
+        \end{axis}
+    \end{tikzpicture}
+    \caption{Optimal/implied entry fee as a function of the number of platform products.}
+    \label{fig:F_F_eq}
+\end{figure}
+
 % \section{Extensions}

### 2023-03-26 src/figures/equilibrium.py

@@ -14,6 +14,9 @@ def create_plot_data(
     N_P_range: tuple[float, float] = (0, 1),
     num_obs: int = 500,
 ):
+    def f(N_P, N_F):
+        return mu * (N_F * V_F + N_P * V_P) / (N_F * V_F + N_P * V_P + 1)
+
     def pi_P(N_P, N_F):
         inner_part = np.log(1 + (N_F * V_F) / (N_P * V_P + 1)) / (N_F * V_F)
         return mu * (1 - inner_part)
@@ -31,15 +34,48 @@ def create_plot_data(
             return np.array([N_F_opt(n) for n in N_P])
         else:
             return fsolve(lambda N_F: pi_F_t(N_P, N_F), 1)[0]
+        
+    def F_F_opt():
+        return np.sqrt(mu * I_F * V_F) - I_F
+        
+    def N_F_opt_bench(N_P):
+        F_F = F_F_opt()
+        N_F_candidate = mu / (F_F + I_F) - N_P * V_P / V_F - 1 / V_F
+        return np.maximum(N_F_candidate, 0)
 
     N_P_vec = np.linspace(N_P_range[0], N_P_range[1], num_obs)
     N_F_vec = N_F_opt(N_P_vec)
-    N_F_cf_vec = np.maximum(N_F_vec[0] * V_F - N_P_vec * V_P, 0)
 
     pi_F_vec = pi_F(N_P_vec, N_F_vec)
     pi_P_vec = pi_P(N_P_vec, N_F_vec)
     A_vec = N_P_vec * V_P + N_F_vec * V_F + 1
     CS_vec = np.log(A_vec)
+
+    N_F_cf = np.maximum(N_F_vec[0] * V_F - N_P_vec * V_P, 0)
+    A_cf = N_P_vec * V_P + N_F_cf * V_F + 1
+    CS_cf = np.log(A_cf)
+
+    N_F_bench = N_F_opt_bench(N_P_vec)
+    A_bench = N_P_vec * V_P + N_F_bench * V_F + 1
+    CS_bench = np.log(A_bench)
+    pi_P_bench = F_F_opt() * N_F_bench + mu * N_P_vec * V_P / A_bench
+
+    A_noF = N_P_vec * V_P + 1
+    CS_noF = np.log(A_noF)
+    pi_P_noF = mu * N_P_vec * V_P / A_noF
+
+    pi_P_var_vec = mu * N_P_vec * V_P / A_vec
[…]

### 2023-03-26 src/paper/application.tex
Add some proofs

@@
     \label{prop:share_of_platform}
-    Assume that $f, w$ are continuously differentiable and that $w$ has a non-zero measure support.
+    Assume that $f$ is continuously differentiable with respect to $N_P$ and also twice differentiable.
     Let $N_F \geq 0$.
@@
     \label{prop:share_of_fringe}
-    Assume that $f, w$ are twice continuously differentiable and that $w$ has a non-zero measure support.
+    Assume that $f, w$ are twice continuously differentiable.
     Let $N_F > 0$.
@@
     \label{cor:fringe_entry}
-    Assume that $f, w$ are twice continuously differentiable and that $w$ has a non-zero measure support.
+    Assume that $f, w$ are twice continuously differentiable.
     Let $N_F^*$ denote the equilibrium number of fringe firms.
     Let us also assume that $N_F^* > 0$.
+    Furthermore, let us assume that
+    \begin{align*}
+        \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} < 0 \quad \forall n_F \leq N_F \\
+        \frac{\partial^2 f(n_P, n_F)}{\partial n_F^2} < 0 \quad \forall n_F \leq N_F.
+    \end{align*}
     Then the equilibrium number of fringe firms is also differentiable and
     \begin{align*}
-        &\text{If } \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} < 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial N_F^*}{\partial N_P} < 0. \\
-        &\text{If } \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} > 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial N_F^*}{\partial N_P} > 0.
+        \frac{\partial N_F^*}{\partial N_P} < 0.
     \end{align*}
@@
     \end{tikzpicture}
-    \caption{Comparative statistics for equilibrium entry (fringe are substitutes)}
+    \caption{Illustration of comparative statics for equilibrium entry}
     \label{fig:comparative_N_F}
@@
                 ylabel={$N_F^*$},
-                xmin=0, xmax=1, % adjust these values as needed
-                ymin=0, ymax=1, % adjust these values as needed
-                % grid=major,
-                % grid style={dashed,gray!30},
-                width=6cm, % adjust the width of the plot
+                xmin=0, xmax=1.5, % adjust these values as needed
+                ymin=0, ymax=1.4, % adjust these values as needed
+                width=10cm, % adjust the width of the plot
                 height=6cm, % adjust the height of the plot
@@
             ]
+            \addplot[color=red,mark=none,very thick] table[x=N_P,y=N_F_bench]{\equilibrium};
             \addplot[color=blue,mark=none,very thick] table[x=N_P,y=N_F]{\equilibrium};
-            \addplot[color=black,mark=none,dashed] table[x=N_P,y=N_F_cf]{\equilibrium};
+            \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=N_F_cf]{\equilibrium};
+            \legend{Benchmark, Bargaining, Fixed aggregate}
         \end{axis}
     \end{tikzpicture}
-    \caption{The equilibrium number of fringe firms as a function of the number of platform products.}
+    \caption{Equilibrium number of fringe firms as a function of the number of platform products.}
     \label{fig:fringe_entry_eq}
@@
 
+\section{Proofs and additional lemmas}
+
+\begin{lemma}
+    \label{lem:slope_at_eq}
+    Let the conditions in \cref{ass:single_crossing} hold.
+Then for any $N_F^* > 0$ for which $\pi_F(N_P, N_F^*) = I_F$, the partial derivative with respect to the number of fringe firms is smaller than the investment cost:
+    \begin{align*}
+        \left. \frac{\partial \pi_F(N_P, N_F)}{\partial N_F} \right|_{N_F = N_F^*} < I_F.
+    \end{align*}
+\end{lemma}
+\begin{proof}[Proof of \cref{lem:slope_at_eq}]
+    Let us use Leibniz' rule to obtain the first two derivatives of the fringe's profit with respect to the number of fringe firms:
+    \begin{align*}
+        \frac{\partial f(N_P, sN_F)}{\partial N_F} &= \frac{\partial}{\partial N_F} \left[ f(N_P, N_F) - \int_0^1 w(s) f(N_P, sN_F) \ds \right] \\
+        &= \frac{\partial f(N_P, N_F)}{\partial N_F} - \int_0^1 s w(s) \frac{\partial f(N_P, sN_F)}{\partial N_F} \ds, \\
+        \frac{\partial^2 f(N_P, sN_F)}{\partial N_F^2} &= \frac{\partial^2}{\partial N_F^2} \left[ f(N_P, N_F) - \int_0^1 w(s) f(N_P, sN_F) \ds \right] \\
+        &= \frac{\partial^2 f(N_P, N_F)}{\partial N_F^2} - \int_0^1 s^2 w(s) \frac{\partial f(N_P, sN_F)}{\partial N_F^2} \ds.
+    \end{align*}
+    Therefore, \cref{ass:single_crossing} implies that at any $N_F$, $\pi_F(N_P, N_F)$ is either concave or decreasing.
+
+    In the remainder, for ease of notation, let us denote partial derivatives as follows:
+    \begin{align*}
+        \partial_F \pi_F(N_P^*, N_F^*) := \left. \frac{\partial \pi_F(N_P, N_F)}{\partial N_F} \right|_{N_P = N_P*, N_F = N_F^*}.
+    \end{align*}
+
+    Notice that the fact that $\pi_F$ is concave or decreasing in $N_F$ implies that if $\partial_F \pi_F(N_P, N_F')$ for some $N_F' \geq 0$, then $\partial_F \pi_F(N_P, N_F'') < \partial_F \pi_F(N_P, N_F')$ for any $\tilde{N_F} < \bar{N_F}$.
+
+    Next, observe that if $\partial_F \pi_F(N_P, 0) < I_F$, then there is no equilibrium with $N_F > 0$.
+    To show this, assume by contradiction that $\exists N_F^* > 0$ such that $\pi_F(N_P, N_F^*) = I_F N_F^*$.
+    Then the mean value theorem implies that there is a $\bar{N}_F \in (0, N_F^*)$ such that $\partial_F \pi_F(N_P, \bar{N}_F) = I_F$.
+    However, this clearly cannot be the case as $\partial_F \pi_F(N_P, N_F) < I_F$ for all $N_F > 0$.
+
+    Now let $N_F^*$ be a positive number for which $f(N_P, N_F^*) = I_F N_F^*$, if it exists.
+    It is easy to see that $\partial \pi(N_P, N_F^*) < I_F$.
+    The reason is that if it exists, then $\partial_F \pi_F(N_P, 0) > I_F$.
+    Now if $\partial_F \pi_F(N_P, N_F^*) \geq I_F \forall N_F > 0$, then $f(N_P, N_F) > I_F N_F$, and the two functions do not intersect.
+    Therefore, there must exist some $\bar{N}_F > 0$ for which $\partial_F \pi_F(N_P, \bar{N}_F) < I_F$.
+    This in turn implies that $\partial_F \pi_F(N_P, N_F) \leq \partial_F \pi_F(N_P, \bar{N}_F) < I_F$ for all $N_F > \bar{N}_F$.
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:unique_equilibrium}]
+    \Cref{lem:slope_at_eq} states that for any positive $N_F^*$ for which $\pi_F(N_P, N_F^*)$, the partial derivative with respect to the number of fringe firms is negative.
+    Now assume by contradiction that $\exists 0 < N_F^* < N_F^{**}$ such that $\pi_F(N_P, N_F^*) = I_F N_F^*$ and $\pi_F(N_P, N_F^{**}) = I_F N_F^{**}$.
+    But then the mean value theorem implies that there is a $\bar{N}_F \in (N_F^*, N_F^{**})$ such that $\partial_F \pi_F(N_P, \bar{N}_F) = I_F$.
+    This is a contradiction, as $\partial_F \pi_F(N_P, N_F) < I_F$ for all $N_F^* < N_F$.
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:share_of_platform}]
+    $f(N_P, N_F)$ is continuously differentiable in $N_P$, therefore the Leibniz rule can be applied to obtain
+    \begin{align*}
+        \frac{\partial \pi_P(N_P, N_F)}{\partial N_P} &= \frac{\partial}{\partial N_P} \int_0^1 w(s) f(N_P, N_F) \ds \\
+        &= \int_0^1 w(s) \underbrace{\frac{\partial f(N_P, sN_F)}{\partial N_P}}_{> 0} \ds > 0.
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:share_of_fringe}]
+    Remember that
+    \begin{align*}
+        \pi_F(N_P, N_F) = f(N_P, N_F) - \int_0^1 w(s) f(N_P, N_F) \ds.
+    \end{align*}
+    $f(N_P, N_F)$ is continuously differentiable in $N_P$, therefore the Leibniz rule can be applied to obtain
+    \begin{align*}
+        \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} &= \frac{\partial}{\partial N_P} \left[ f(N_P, N_F) - \int_0^1 w(s) f(N_P, N_F) \ds \right]\\
+        &= \frac{\partial f(N_P, N_F)}{\partial N_P} - \int_0^1 w(s) \frac{\partial f(N_P, sN_F)}{\partial N_P} \ds \\
+        &= \underbrace{h(N_F)}_{(*)} - \underbrace{\int_0^1 w(s) h(s N_F)}_{(**)}
+    \end{align*}
+    where $h(N_F) = \frac{\partial h(N_F)}{\partial N_P}$.
+
+    Notice that $(*)$ and $(**)$ are both positive.
+    Furthermore, $(**)$ is the weighed average of $(*)$ over the interval $[0, N_F]$.
+    Therefore, if $h(N_F)$ is strictly increasing, then $(*) > (**)$, and the whole expression is positive.
+    Conversely, it is negative if $h(N_F)$ is strictly decreasing.
+
+    If $h(N_F)$ is differentiable, then it is equivalent to saying that
+    \begin{align*}
+        \frac{\mathrm{d}h(N_F)}{\mathrm{d}N_F} = \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} < 0 &\implies \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} < 0 \\
+        \frac{\mathrm{d}h(N_F)}{\mathrm{d}N_F} = \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} > 0 &\implies \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} > 0
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of \cref{cor:fringe_entry}]
+    \Cref{prop:unique_equilibrium} establishes that if an equilibrium with $N_F > 0$ exists, it is unique.
+    Use the implicit function theorem on the equation from \cref{ass:free_entry} to obtain
+    \begin{align*}
+        \frac{\partial N_F}{\partial N_P} = \frac{\frac{\partial \pi_F(N_P, N_F)}{\partial N_P}}{I_F - \frac{\partial \pi_F (N_P, N_F)}{\partial N_F}}
+    \end{align*}
+
+    Remember from \cref{prop:share_of_fringe} that the numerator of this expression is negative under the condition $\frac{\partial^2 f(N_P, N_F)}{\partial N_P \partial N_F}$.
+    All we need to show to conclude the proof is that
+    \begin{align*}
+        \frac{\partial \pi_F (N_P, N_F)}{\partial N_F} < I_F,
+    \end{align*}
+    which is the statement of \cref{lem:slope_at_eq}.
+\end{proof}
+
 \end{document}

### 2023-03-27 src/paper/application.tex
Expand results section

@@
 In case it does, it is called a hybrid platform.
-% Additionally, the platform can choose to exclude all the fringe firms from the market (e.g.
-by setting a sufficiently high entry fee), and only offer its own products.
-% TODO: should I allow it in the baseline case, or only after a policy intervention?
 
@@
 \end{proposition}
-Note that in the first case, the size of the aggregate does not depend on the platforms' product variety or the platform's product advantage.
+Note that in the first case, the size of the aggregate does not depend on the platforms' product variety or the platform's product advantage (\cref{eq:aggregate_eq}).
 
@@
 \end{proposition}
-Note, that even though the platform's profit is increasing in the number of its products, the optimal entry fee does not depend on it.
+Note, that even though the platform's profit is increasing in the number of its products, the optimal entry fee does not depend on it (\cref{fig:F_F_eq,fig:pi_P_eq}).\footnote{
+    This is only due to the fact that the platform's product does not reqire any investment cost.
+    If the platform is operating in the hybrid regime, less fringe firms are needed to achieve the (fixed) equilibrium aggregate, therefore there is less expenditure on investment costs, which is essentially wasted.
+    If the platform's products also require investment, and their cost is proportional to the platform's product advantage, then $N_P$ has no effect on platform profits within the hybrid regime.
+}
 As a consequence, as long as the fringe is feasible at the optimal entry fee, the size of the aggregate, and hence consumer welfare is also unaffected by the platform operating in hybrid mode.
@@
 Finally, note that the profit of the platform in the hybrid regime is higher than in the retail regime, whenever the former is feasible.
+Therefore, the platform prefers to operate in hybrid mode, and does not want to exclude fringe firms from the market.
 This is a consequence of the fact that equation \eqref{eq:hybrid_profit} is strictly concave in $F_F$, therefore $F_F^*$ is a global maximum.
 It implies that there is no point where the fringe would be feasible under optimal entry fees, but the platform would prefer to operate in retail mode.
-Therefore, in the benchmark model, a platform becoming a hybrid platform, or increasing the number of its own products, always has a weakly positive effect on the aggregate, and thus consumer welfare.
+Therefore, in the benchmark model, a platform becoming a hybrid platform, or increasing the number of its own products, always has a weakly positive effect on the aggregate, and thus consumer welfare.\footnote{
     This is in contrast to \textcite{anderson2021hybrid}, where a platform operating in hybrid mode sets a higher entry fee to advantage its own products, which in turn leads to a smaller aggregate.
-
-% TODO: intuition
-% Figure
-
+    The reason for this difference lies in the type of entry fee: they assume a revenue-based, proportional fee, which distorts prices.
+    In contrast, in this paper, I assume a non-distortive lump sum fee.
+}
 \subsubsection{The bargaining model}
@@
 \end{proposition}
-\textcolor{red}{TODO: add an example figure}
 
@@
 \end{align*}
-and in turn, equilibrium total aggregate is also decreasing in $N_P$.\footnote{
-    The same result can also easily be shown for an increase in $V_P$.
-}
-As in this model consumer welfare is monotone in the total aggregate, this implies that consumer welfare is decreasing in the number of the platform's products.
+that is, an increase in the platform's products leads to a more than proportional reduction in the number of fringe products (\cref{fig:fringe_entry_eq}).\footnote{
+    The intuition behind this is demonstrated in \cref{fig:F_F_eq}.
+    As the platform's product variety grows, its bargaining power also increases.
+    This can be thought of as an increase in (implied) entry fees, which in turn discourages fringe entry.
+}
+Conversely, equilibrium total aggregate is also decreasing in $N_P$.\footnote{
+    The same result also holds true for an increase in $V_P$.
+}
+As, in this model, consumer welfare is monotone in the total aggregate, this implies that consumer welfare is decreasing in the number of the platform's products (\cref{fig:aggregate_eq}).
 Therefore, as opposed to the benchmark model, the platform becoming more hybrid leads to a reduction in consumer welfare.\footnote{
-    Unless $V_P N_P$ is high enough that the platform would operate in the benchmark model, too.
-}
-
-\textcolor{red}{TODO: add figure showing consumer welfare in the benchmark and bargaining models as a function of $N_P$}
-
+    Unless $V_P N_P$ is high enough that the platform would operate in pure retial mode in the benchmark model, too.
+}
 \begin{figure}
@@
     \end{tikzpicture}
-    \caption{Equilibrium aggregate as a function of the number of platform products.}
+    \caption{Equilibrium aggregate as a function of the number of platform products.
+Note, that consumer surplus is monotone in the aggregate, therefore this figure also shows ordinal changes in the equilibrium consumer surplus.}
     \label{fig:aggregate_eq}

### 2023-03-27 src/paper/application.tex
Add an intro

@@
 \section{Motivation}
+
+Even though the economics literature offers no unambiguous definition for what a platform is, there seems to be a consensus that they are of key importance for the modern economy, and are getting even more so in the future.
+Although market structures resembling various aspects of what we call platforms have existed for some time, the term has only gained widespread usage in the 2000s, with the advent of digitization, and a number of behemoth technology companies playing matchmakers on the internet.
+Since then, platforms have become a buzzword in the business world, the subject of increasing regulatory scrutiny, and also a topic of intense academic interest.
+
+While it is hard to define what a platform is, there are a number of features commonly associated with platforms.\footnote{
+    I thank the participants of the Third Year Seminar at the University of Zurich for their lively discussion on this topic.
+    The conclusion was that, although platforms are hard to define, "You know one when you see one".
+}
+An organization does not have to exhibit all of these features to be considered a platform, but they are often present, and are also the main areas of interest when studying platforms.
+First, platforms are often characterized by multi-sidedness.
+Their most prominent examples are large internet companies, such as Google connecting advertisers and consumers, Amazon connecting sellers and consumers, or Uber connecting drivers and passengers.
+Second, a frequent feature of platforms is the presence of network effects.
+More buyers on Amazon mean more value for the sellers, and vice versa.
+These network effects often lead to increasing returns to scale, which in turn leads to consolidation in the industry.
+Third, another important aspect of platforms is the disparity between the various market participants.
+While there is usually just a few, large platforms in an industry, there is a much larger number of participants who use the platforms' services to connect to each other.
+Furthermore, the platform is often indispensable for the participants to make business, but the participants themselves are more easily replaceable.
+This power imbalance naturally leads to antitrust concerns, with regulators taking an increasingly close look at such markets as of late \parencite[see e.g. ][]{fletcher2021consumer}.
+Finally, a somewhat more recent, but slightly alarming feature of platforms is operating in a so-called hybrid mode.
+They act as an intermediary (deciding the rules) and a market participant (competing with the other entrants) at the same time.
+This paper focuses on the latter two aspects (bargaining power and hybridness), while mostly abstracting away the first two in the form of a rather reduced-form approach of modeling the production function.
+
+Various models have been proposed to study the economics of platforms, focusing on different aspects of the phenomenon.
+One of the larger and earlier strands of literature focus on the multi-sidedeness of platforms, the resulting implications.
+These papers investigate how various market features, such as the possibility of multi-homing, the magnitude of network-effects, or the number of platforms influence market outcomes.
+In addition to welfare, they are often interested in the transfers between the various sides facilitated by the platforms' desire to exploit network effects.
+Examples of such studies include the seminal papers \textcite{rochet2003platform} and \textcite{armstrong2006competition}, as well as a number of insightful papers examining the effects of various market attributes \parencite[e.g.][]{hagiu2004optimal,choi2010tying,evans2011platform,lee2014competing}.
+
+Hybrid platforms also received increasing attention in the literature.
+While not explicitly phrased in terms of hybridness, the literature on the importance of exclusive content can be seen as adjacent to this topic \parencite[]{hagiu2011exclusivity,lee2013vertical,dou2014sell,weeds2016tv}.
+These papers mostly focus on competition between platforms, and not on the impact on the platform-participant relationship.
+On the other hand, more recent papers, such as \textcite{hagiu2020should}, \textcite{anderson2021hybrid} and \textcite{gutierrez2021welfare} have started to address the issue of hybrid platforms, and how platforms having their own products affect competition between the platform and the entrants, and ultimately consumer welfare and producer surplus.
+The results are mixed: while some of them find that hybrid platforms can be beneficial if certain anti-competitive behavior, such as self-preferencing, is prevented \parencite[]{anderson2021hybrid}, others are more critical of this hybrid form \parencite[]{anderson2021hybrid}.
+This paper provides some additional insights into this topic, by looking at the impact of dual mode operation on bargaining power.
+
+Many results and concepts of this paper are also applicable outside the context of (multi-sided) platforms.
+Certain structures, such as vertical relationships, or even traditional retail stores share a number of features with platforms (notably, the presence of a dominant, indispensable entity), and can be modeled in much the same way.
+Therefore, the results of this paper also contributes to the literature on those settings, such as retailers having their own private labels \parencite{steiner2004nature}, or vertical integration in upstream-downstream markets \parencite{hart1990vertical,aghion2006vertical}.
+It is particularly closely related to \textcite{de2005vertical} and \textcite{montez2007downstream} in which bargaining between the upstream and downstream firms take the center stage.
+
+Finally, this also belongs to the not too large set of papers using concepts from cooperative game theory in an industrial organization setting.
+Such examples include the aforementioned \textcite{montez2007downstream}, as well as \textcite{hart1990property}, \textcite{levy1997individual}, \textcite{inderst2003bargaining} and \textcite{brugemann2019intra} among others.
 
@@
 
-\section{Conclusion}
+\section{Conclusion and future work}
+
+This paper has introduced a new model of hybrid platforms in which bargaining between the platform and the entrant firms plays a key role.
+It has been demonstrated that platforms operating in hybrid mode can have serious consequences in such an environment.
+In particular, when a platform has a large number of its own products, then its bargaining power is also higher compared to the fringe entrants.
+This, in certain situations, such as the one described in this paper, this can lead to fewer fringe firms entering the market, reduced product variety, and ultimately, lower consumer welfare.
+
+In addition to the specific platform model, this paper also provides a simple, tractable, yet quite general framework in which one can study the effects of bargaining between one large and a continuum of small players.
+Such environments might, in addition to platforms, include upstream-downstream settings with one upstream supplier, or franchises with one franchisor and a continuum of franchisees, or wage bargaining.
+The quite general results of this paper give some intuition on what happens in such settings, without needing to delve into the details of a specific model.
+This also highlights certain similarities between those markets.
+Furthermore, many of the results from this paper can be applied in a plug-and-play fashion to other models of large-player-small-player interactions.
+
+There is a number of avenues for future research in this direction.
+First, I suspect that many of the assumptions made in section \cref{sec:example} can be relaxed, and one can still obtain similar results.
+An additional step I am planning to take is to endogenize the number of the platform's products, and the parameters of the profit sharing (bargaining rule).
+The latter would provide important insights into what kind of demand structures might lead to the evolution of hybrid platforms.
+
+I also hope that others will find this framework useful in their own research, and incorporate it in more complex and more applied models.
+In general, I believe this approach for modeling bargaining is a rather good compromise between assuming that one party has all the bargaining power, and modeling the bargaining process in detail, and might be a good fit for a number of different economic applications.
 

### 2023-03-27 src/paper/application.tex
Spelling

@@
 They act as an intermediary (deciding the rules) and a market participant (competing with the other entrants) at the same time.
-This paper focuses on the latter two aspects (bargaining power and hybridness), while mostly abstracting away the first two in the form of a rather reduced-form approach of modeling the production function.
+This paper focuses on the latter two aspects (the interplay between bargaining power and hybrid operation), while mostly abstracting away the first two in the form of a rather reduced-form approach of modeling the production function.
 
@@
 Hybrid platforms also received increasing attention in the literature.
-While not explicitly phrased in terms of hybridness, the literature on the importance of exclusive content can be seen as adjacent to this topic \parencite[]{hagiu2011exclusivity,lee2013vertical,dou2014sell,weeds2016tv}.
+While not explicitly phrased in terms of hybrid operation, the literature on the importance of exclusive content can be seen as adjacent to this topic \parencite[]{hagiu2011exclusivity,lee2013vertical,dou2014sell,weeds2016tv}.
 These papers mostly focus on competition between platforms, and not on the impact on the platform-participant relationship.
@@
 \end{assumption}
-While somewhat more complex than a simple percentage split, it has quite a few adventages compared to the latter.\footnote{
+While somewhat more complex than a simple percentage split, it has quite a few advantages compared to the latter.\footnote{
     This way of modeling bargaining has precedents in the industrial organization literature \parencite[e.g.][]{hart1990property,segal2003collusion,inderst2003bargaining,montez2007downstream}.
@@
 On the theoretical side, the main argument in favor of this particular rule is its relation to the Shapley-value.\footnote{
-    \cref{sec:profit_sharing} shows that in the case of $w(s) \equiv 1$, $\pi_P(N_P, N_F)$ and $\pi_F(N_P, N_F)$ are the Shapley values of the platform and the fringe, respectively.
+    \cref{sec:profit_sharing} shows that in the case of $w(s) \equiv 1$, $\pi_P(N_P, N_F)$ and $\pi_F(N_P, N_F)$ are the Shapely values of the platform and the fringe, respectively.
 }
@@
 This section presents some general result that only depend on the abstract model structure described in the previous section, and the assumptions therein.
-It is remarkable that even within such astylized setting and simple model, one can derive some interesting and non-trivial results.
+It is remarkable that even within such a stylized setting and simple model, one can derive some interesting and non-trivial results.
 \Cref{sec:example} will then build on these results to derive some stronger implications in a more specific model.
@@
 Let us now turn to an example application of the somewhat abstract model presented in the previous sections.
-The model in this section is heavily inspired by the logit-like demand structur and hybrid platform setting in  \textcite{anderson2021hybrid}.
+The model in this section is heavily inspired by the logit-like demand structure and hybrid platform setting in  \textcite{anderson2021hybrid}.
 The setting is a (possibly hybrid) platform market with monopolistically competing fringe firms.
@@
 \begin{proposition}
-    The profit maximizing price for prouct $Ti$ is
+    The profit maximizing price for product $Ti$ is
     \begin{align*}
@@
 Note, that even though the platform's profit is increasing in the number of its products, the optimal entry fee does not depend on it (\cref{fig:F_F_eq,fig:pi_P_eq}).\footnote{
-    This is only due to the fact that the platform's product does not reqire any investment cost.
+    This is only due to the fact that the platform's product does not require any investment cost.
     If the platform is operating in the hybrid regime, less fringe firms are needed to achieve the (fixed) equilibrium aggregate, therefore there is less expenditure on investment costs, which is essentially wasted.
@@
 
-Now let us turn to how the platform's hybridness affects product variety and consumer welfare.
+Now let us turn to how the platform's dual mode operation affects product variety and consumer welfare.
 Let us start by establishing some properties of the total profit function $f(n_P, n_F)$.
@@
 Using this, \cref{prop:unique_equilibrium} gives that the equilibrium is unique.
-Furthermore, \cref{cor:fringe_entry} implies that an increase in the hybridness of the platform leads to a reduction in the number of fringe firms that enter the market.
+Furthermore, \cref{cor:fringe_entry} implies that an increase in the number of the platform's products leads to a reduction in the number of fringe firms that enter the market.
 
@@
 Therefore, as opposed to the benchmark model, the platform becoming more hybrid leads to a reduction in consumer welfare.\footnote{
-    Unless $V_P N_P$ is high enough that the platform would operate in pure retial mode in the benchmark model, too.
+    Unless $V_P N_P$ is high enough that the platform would operate in pure retail mode in the benchmark model, too.
 }
@@
 
-I start by characterizing the case when the game is superadditive to provide some support for using the Shapley value as he bargaining outcome.\footnote{For example, the results in \textcite{gul1989bargaining} rely on superadditivity, while monotonicity suffices for \textcite[]{hart1996bargaining}.}
+I start by characterizing the case when the game is superadditive to provide some support for using the Shapley value as the bargaining outcome.\footnote{For example, the results in \textcite{gul1989bargaining} rely on superadditivity, while monotonicity suffices for \textcite[]{hart1996bargaining}.}
 

### 2023-03-28 src/paper/paper.tex
Extend paper rule in snakefile
Also switch to root-dir-relative paths in the tex file.
Latex-workshop build rules have to be modified accordingly.
Add snakemake rule for creating figure
Add some graphs

@@
 \usepackage{xcolor}
+\usepackage[noabbrev,nameinlink]{cleveref}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{setspace}
 \usepackage[backend=biber,style=authoryear,maxbibnames=99,hyperref=true]{biblatex}
 
-\addbibresource{references.bib}
+\setstretch{1.15}
+
+\addbibresource{src/paper/references.bib}
 
@@
         \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-                xtick={0, 1}, ytick={0}, extra y ticks={1},  extra y tick style={yticklabel={$f(1)$}}]
-            \addplot[name path=f, blue,ultra thick] {x^0.5};
+                xtick={0, 1}, ytick={0}, xlabel={$s$}]
+            \addplot[name path=f, ultra thick] {x^0.5};
             \node[anchor=north west] at (axis cs: .8, .8^0.5) {$f$};
@@
             \node[anchor=north west] at (axis cs: .1, .9) {Fringe ($A$)};
-            \node[anchor=south east] at (axis cs: .9, .1) {Player $P$};
+            \node[anchor=south east] at (axis cs: .9, .1) {Platform ($P$)};
         \end{axis}
@@
 \begin{align*}
-    \Pr{X_n \leq k} = \prod_{j=k+1}^n \frac{j}{j + \lambda} .
+    \Pr(X_n \leq k) = \prod_{j=k+1}^n \frac{j}{j + \lambda} .
 \end{align*}
@@
 \end{proposition}
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=3, samples at={0.02, 0.04, ..., 0.98, 1},
+                xtick={0, 1}, ytick={0, 1, 2, 3}, axis lines=left, xlabel={$t$}, legend pos=south east]
+                \addplot[ultra thick] {0.5 * x ^ (-0.5)};
+                \addplot[ultra thick, dashed] {1};
+                \addplot[ultra thick, dotted] {1.5 * x ^ (0.5)};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{$g(t)$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.1, samples at={0, 0.02, ..., 0.98, 1},
+                xtick={0, 1}, ytick={0, 1}, axis lines=left, xlabel={$t$}, legend pos=south east]
+                \addplot[ultra thick] {x ^ (0.5)};
+                \addplot[ultra thick, dashed] {x};
+                \addplot[ultra thick, dotted] {x ^ (1.5)};
+                \legend{$\lambda = 0.5$, $\lambda = 1$, $\lambda = 1.5$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{$\int_0^t g(s) \ds$}
+    \end{subfigure}
+    \caption{Illustration of the weighting function for various values of $\lambda$ in the weighted Shapley-value.}
+    \label{fig:weigh_function}
+\end{figure}
 
@@
 \end{proposition}
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.1, samples at={0, 0.02, 0.04, ..., 0.98, 1},
+                xtick={0, 1}, ytick={0, 1}, axis lines=left, xlabel={$t$}, legend pos=north west]
+                \addplot[ultra thick] {1};
+                \addplot[ultra thick, dashed] {1-x};
+                \addplot[ultra thick, dotted] {(1-x)^2};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{$(1 - t) ^ {m - 1}$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.1, samples at={0, 0.02, ..., 0.98, 1},
+                xtick={0, 1}, ytick={0, 1}, axis lines=left, xlabel={$t$}, legend pos=north west]
+                \addplot[ultra thick] {x};
+                \addplot[ultra thick, dashed] {x - x^2/2};
+                \addplot[ultra thick, dotted] {x - x^2 + x^3/3};
+                \legend{$m = 1$, $m = 2$, $m = 3$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{$\int_0^t (1 - s) ^ {m - 1} \ds$}
+    \end{subfigure}
+    \caption{Illustration of the weighting function for various values of $m$ in the multiple platform case.}
+    \label{fig:multiple_platforms}
+\end{figure}
 
@@
     \centering
-    \includegraphics[width=4in]{../../out/figures/equilibrium_nf.png}
+    \includegraphics[width=4in]{out/figures/equilibrium_entry.pdf}
     \caption{Equilibrium number of fringe entrants as a function of the platform's product variety.}

### 2023-04-03 src/deploy/deploy_to_github.sh
Refactor github pages deployment

@@ -1,18 +1,0 @@
-set -e
-set -u
-
-source=$1
-target=$2
-target_folder=$(dirname "$target")
-
-cp $source $target
-
-rm -rf "$target_folder/.git"
-cd $target_folder
-
-git init --initial-branch=main
-git add -A
-git commit -m 'Deploy to GH pages'
-git push -f git@github.com:stanmart/ValueOfIntermediation.git main:gh-pages
-
-rm -rf .git

### 2023-04-05 src/paper/theory.tex
Switch to one line per sentence

--- 2023-03-28 src/paper/paper.tex
@@
 However, as is often the case in economics, infinite-player approximations might turn out to be more tractable while retaining the main conclusions of the finite models from which they arise.
-Indeed, in the case of cooperative games with non-atomic players, both the axiomatic approach to defining a value on infinite games and the asymptotic approach to calculate the limit of its finite counterparts lead to the same result \footnote{On the appropriate subspace of non-atomic games.} \parencite{aumann2015values}, which is furthermore analytically simple and readily interpretable.
-An economic application of this theory can be found in \textcite{billera1978internal}.
+Indeed, in the case of cooperative games with non-atomic players, both the axiomatic approach to defining a value on infinite games and the asymptotic approach to calculate the limit of its finite counterparts lead to the same result \footnote{
+    On the appropriate subspace of non-atomic games.
+} \parencite{aumann2015values}, which is furthermore analytically simple and readily interpretable. An economic application of this theory can be found in \textcite{billera1978internal}.
 
@@
 The continuous analogue of them are called oceanic games, in which the set of players consists of a finite number of atoms and an ocean made up of a continuum of fringe players.
-While the axiomatic characterization of the value on such games has not been particularly fruitful,\footnote{\textcite{hart1973values} shows that the usual axioms do not characterize a unique value in general.} \textcite{fogelman1980asymptotic} demonstrates that an asymptotic approach works well on a large subset of them.
+While the axiomatic characterization of the value on such games has not been particularly fruitful,\footnote{
+    \textcite{hart1973values} shows that the usual axioms do not characterize a unique value in general.
+} \textcite{fogelman1980asymptotic} demonstrates that an asymptotic approach works well on a large subset of them.
 More specifically, the limit of the players' values converge to relatively simple and easy-to-interpret expressions as the number of small players goes towards infinity.
@@
 \end{align*}
-One can think of this setting as a (one-sided) platform and a number of potential entrants, if the entrants can only reach their prospective consumers through the platform.\footnote{While these assumptions might seem somewhat restrictive, they are relatively simple to relax.} First, let us characterize the conditions under which this game is superadditive.
-These features provide some theoretical support for using Shapley-values as bargaining outcomes, as papers creating a link between non-cooperative bargaining and cooperative values often rely on such assumptions.\footnote{For example, the results in \textcite{gul1989bargaining} rely on superadditivity, while monotonicity suffices for \textcite[]{hart1996bargaining}.}
+One can think of this setting as a (one-sided) platform and a number of potential entrants, if the entrants can only reach their prospective consumers through the platform.\footnote{
+    While these assumptions might seem somewhat restrictive, they are relatively simple to relax.
+}
+First, let us characterize the conditions under which this game is superadditive.
+These features provide some theoretical support for using Shapley-values as bargaining outcomes, as papers creating a link between non-cooperative bargaining and cooperative values often rely on such assumptions.\footnote{
+    For example, the results in \textcite{gul1989bargaining} rely on superadditivity, while monotonicity suffices for \textcite[]{hart1996bargaining}.
+}
 
@@
 Nevertheless, in many of the following theorems, the asymptotic limit is preferred, as I believe that makes the proofs more instructive.
-%\textcolor{red}{Note: I realize that this paragraph is somewhat vague and needs explanation.
-However, for the current set of results, I do not rely on said theorem.
-If I end up using it later, I will expand on this part.}
 
@@
     \end{align*}
-    Furthermore, if $f$ is differentiable on $[0, 1]$, Then the value of the fringe can also be expressed as
+    Furthermore, if $f$ is differentiable on $[0, 1]$, then the value of the fringe can also be expressed as
     \begin{align*}
@@
 It is already apparent from Figure \ref{fig:one_sided} that (for fixed $f(0)$ and $f(1)$) player $P$ gets a larger share of the surplus when $f(t)$ is larger for every $t$.
-It corresponds to the case when only a small fraction of the fringe is needed to create most of the surplus (e.g.
-their products are substitutes of each other).
+It corresponds to the case when only a small fraction of the fringe is needed to create most of the surplus (e.g. their products are substitutes of each other).
 This result aligns with our natural intuition that player $P$ has a better bargaining position in this case, than if only coalitions with most of the fringe firms could obtain high values.
@@
 the limits of the Shapley values of their finite approximations in finite games) are well known in the relevant literature, there are no results about the limits of the weighted (Shapley) values.
-While providing very general results in the form of \textcite[]{fogelman1980asymptotic} is outside of the scope of the paper\footnote{They show that the (within some constraints) any discretization of an oceanic game converges to the same value.} the results in this section still provide some new insights into weighted values of oceanic games.
+While providing very general results in the form of \textcite[]{fogelman1980asymptotic} is outside the scope of the paper\footnote{
+    They show that the (within some constraints) any discretization of an oceanic game converges to the same value.
+} the results in this section still provide some new insights into weighted values of oceanic games.
 In particular, I show that the weighted value of a game with one large and many small players converges to a rather simple and intuitive expression, if the size of the small players go to zero at the same rate.
@@
 These weights can be thought of as measures of innate bargaining power \parencite{shapley1953additive}, not reflected in the value function.
-Further support for this interpretation can be found in \textcite{hart1996bargaining}, demonstrating that in a certain alternating offer bargaining game, weights are related to the probability of each player making the offer.\footnote{For example, only one player having a positive value corresponds to them making take it or leave it offers.}
+Further support for this interpretation can be found in \textcite{hart1996bargaining}, demonstrating that in a certain alternating offer bargaining game, weights are related to the probability of each player making the offer.\footnote{
+    For example, only one player having a positive value corresponds to them making take it or leave it offers.
+}
 
-For my purposes, it is sufficient to deal with the case of simple weights.
-I.e., assume that there is at most one player with zero weight.
+For my purposes, it is sufficient to deal with the case of simple weights. I.e., assume that there is at most one player with zero weight.
 For my main result, I make use of the fact that weighted Shapley values can be calculated by weighting the permutations by the probabilities arising from the following sequential ordering procedure \parencite{kalai1987weighted}.
@@
     \label{lem:entry_distr}
-     As $n \to \infty$, $X_n \xrightarrow[]{\mathrm{d}} X$ with the cdf $G_X(t) = \lambda^t$. Consequently, the corresponding probability density function is $g(t) = \lambda t^{\lambda - 1}$.
+     As $n \to \infty$, $X_n \xrightarrow[]{\mathrm{d}} X$ with the cdf $G_X(t) = \lambda^t$.
+     Consequently, the corresponding probability density function is $g(t) = \lambda t^{\lambda - 1}$.
 \end{lemma}
@@
 
-Finally, the following corollaries support the interpretation of weights as bargaining power, as a higher weight corresponds to a higher Shapley-value in this game.\footnote{This would not necessarily have to be the case, as demonstrated by \textcite{owen1968communications}.} Furthermore, the limit of the weighted value of $P$, as their weight goes to zero (infinity) is precisely the payoffs $P$ would achieve if $P$ were making (facing) take-it-or-leave-it offers.
+Finally, the following corollaries support the interpretation of weights as bargaining power, as a higher weight corresponds to a higher Shapley-value in this game.\footnote{
+    This would not necessarily have to be the case, as demonstrated by \textcite{owen1968communications}.
+}
+Furthermore, the limit of the weighted value of $P$, as their weight goes to zero (infinity) is precisely the payoffs $P$ would achieve if $P$ were making (facing) take-it-or-leave-it offers.
 
@@
 
-Let us follow the pattern from the previous sections. Start by characterizing conditions for superadditivity to support the bargaining interpretation.
+Let us follow the pattern from the previous sections.
+Start by characterizing conditions for superadditivity to support the bargaining interpretation.
 \begin{proposition}
@@
 \begin{proposition}
-    Let $f(a, b)$ be continuous everywhere on $[0, 1]^2$. Then,
+    Let $f(a, b)$ be continuous everywhere on $[0, 1]^2$.
+    Then,
     \begin{align*}
@@
 
-As the previous proposition shows, the value of each kind of player depends on their expected marginal contribution, i.e.
-the partial derivatives of $f$.
+As the previous proposition shows, the value of each kind of player depends on their expected marginal contribution, i.e. the partial derivatives of $f$.
 Consequently, the value of the grand coalition can be decomposed into the Shapley-values of its members signifying their expected marginal contributions in the following way:
@@
 
-\section{Application}
+\section{Example Application}
+
+\section{Old example application}
 
@@
 The game proceeds as follows.
-In the first stage, each firm decides whether to invest in creating a product or not.
-Creating a product incurs a development cost of C.
+In the first stage, each firm decides whether to invest in creating a product or not. Creating a product incurs a development cost of C.
 Firms that choose not to invest obtain a payoff of 0 and are excluded from the remainder of the game.
@@
 Next, the firms that have a product decide whether they want to join the platform at the cost of some entry fee $F^f$.
-(Note that the entry fee can be negative, in which case it is a subsidy from the platform to the firm.) Consumers are assumed to be on the platform without a choice.
+(Note that the entry fee can be negative, in which case it is a subsidy from the platform to the firm.)
+Consumers are assumed to be on the platform without a choice.
 Finally, the platform and the entering firms post their product prices, and produce and sell to consumers at marginal cost $c$.
@@
 Principally, the two main ideas it relies are the following.
-First, bargaining outcomes should not depend on which player actually obtains the money, all that matters is the total that a given set of players can obtain.\footnote{For example, imagine the following two situations with two players.
+First, bargaining outcomes should not depend on which player actually obtains the money, all that matters is the total that a given set of players can obtain.\footnote{
+    For example, imagine the following two situations with two players.
     In the first one, the first player obtains a playoff of two dollars if they both decide to cooperate and nothing otherwise.
     In the second scenario, both players receive one dollar in the case of cooperation.
-If they can transfer monay between each other, bargaining outcomes should be the same in both scenarios.} Second, players during the bargaining foresee the (unique) subgame perfect equilibrium in the following subgame, and negotiate based on them.
+    If they can transfer monay between each other, bargaining outcomes should be the same in both scenarios.
+} Second, players during the bargaining foresee the (unique) subgame perfect equilibrium in the following subgame, and negotiate based on them.
 
@@
 
-Let $B = e^\frac{v - c - \mu}{\mu}$. Then the total profits from sales (platform and firms combined) can be expressed as
+Let $B = e^\frac{v - c - \mu}{\mu}$.
+Then the total profits from sales (platform and firms combined) can be expressed as
 \begin{align*}
@@
 The possibilities for practical applications are no less interesting, either.
-As a first step, the majorly simplified example application could be expanded upon, so that it is a better description of certain real-life paltform markets.
+As a first step, the majorly simplified example application could be expanded upon, so that it is a better description of certain real-life pLAtform markets.
 Finally, the cooperative approach to profit distribution could become an alternative for the more usual, but in some sense more extreme assumptions about the bargaining process widely used in industrial organization models.
-
-% Next steps:
-% \begin{itemize}
-%     \item Show how the equilibrium number of entrants depends on $N_P$
-%     \item Show how consumer welfare (which is proportional to $\log(N_f + N_P)$) depends on $N_P$
-%     \item Try to characterize the profit-maximizing $N_P$ and how it depends on the parameters
-% \end{itemize}
 
@@
 \begin{proof}[Proof of Lemma \ref{lemma:log_convergence}]
-    First, note that $\Delta_n$ and $\Delta$ are all continuous functions. Then, following the standard proof for $\frac{\mathrm{d}}{\mathrm{d}s}log(s) = \frac{1}{s}$ rewrite $\Delta_n(s)$ as
+    First, note that $\Delta_n$ and $\Delta$ are all continuous functions.
+    Then, following the standard proof for $\frac{\mathrm{d}}{\mathrm{d}s}log(s) = \frac{1}{s}$ rewrite $\Delta_n(s)$ as
     \begin{align*}
@@
     \label{lemma:integral_convergence}
-    Let $f_n, f: [a, b] -> \mathbb{R}$ be Riemann-integrable functions with $f_n \xrightarrow[]{\mathrm{u}} f$ uniformly. Then,
+    Let $f_n, f: [a, b] -> \mathbb{R}$ be Riemann-integrable functions with $f_n \xrightarrow[]{\mathrm{u}} f$ uniformly.
+    Then,
     \begin{align*}
@@
     \end{align*}
-    $S_n$ are just the left Riemann-sums of function $f$ on the interval $[0, 1]$. Therefore, if $f$ is continuous (and thus Riemann-integrable), then $S_n \to \int_0^1 f(t)$, and thus
+    $S_n$ are just the left Riemann-sums of function $f$ on the interval $[0, 1]$.
+    Therefore, if $f$ is continuous (and thus Riemann-integrable), then $S_n \to \int_0^1 f(t)$, and thus
     \begin{align*}
@@
 \begin{proof}[Proof of Corollary \ref{cor:fringe_value}]
-    The first equality comes from the efficiency of the Shapley-value. The values of all players sum up to $f(1)$ for all $n \in \mathbb{N}$, therefore
+    The first equality comes from the efficiency of the Shapley-value.
+    The values of all players sum up to $f(1)$ for all $n \in \mathbb{N}$, therefore
     \begin{align*}
@@
 \begin{proof}[Proof of Corollary \ref{cor:fringe_value_2}]
-    If $f$ is monotone increasing, then $f(0) \leq \int_0^1 f(t) \dt \leq f(1)$. The inequalities become strict if $f$ is not constant on the whole interval.
+    If $f$ is monotone increasing, then $f(0) \leq \int_0^1 f(t) \dt \leq f(1)$.
+    The inequalities become strict if $f$ is not constant on the whole interval.
 \end{proof}
@@
     \end{align*}
-    with strict inequality unless $f$ is constant almost everywhere. As $f$ is continuous, the latter is equivalent to $f$ being constant on the whole $[0, 1]$ interval.
+    with strict inequality unless $f$ is constant almost everywhere.
+    As $f$ is continuous, the latter is equivalent to $f$ being constant on the whole $[0, 1]$ interval.
 \end{proof}
@@
 \begin{proof}[Proof of Corollary \ref{cor:multiple_platforms}]
-    The allocation is efficient for all $n \in \mathbb{N}$, therefore efficient in the limit, as well. The second equality can be obtained by integration by parts.
+    The allocation is efficient for all $n \in \mathbb{N}$, therefore efficient in the limit, as well.
+    The second equality can be obtained by integration by parts.
 \end{proof}

### 2023-04-05 src/paper/application.tex
Update graph x limits

@@
             \addplot[color=blue,mark=none,very thick] table[x=N_P,y=N_F]{\equilibrium};
-            \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=N_F_cf]{\equilibrium};
+            \addplot[color=black,mark=none,thick,dotted] table[x=N_P,y=N_F_cf]{\equilibrium};
             \legend{Benchmark, Bargaining, Fixed aggregate}
@@
                 xmin=0, xmax=1.5, % adjust these values as needed
-                ymin=0, ymax=2.6, % adjust these values as needed
+                ymin=0, ymax=3, % adjust these values as needed
                 width=10cm, % adjust the width of the plot

### 2023-04-05 src/paper/application.tex
Remove ticks from y axes

@@
             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-                    xtick={0, 1}, ytick={0}, xlabel={$s$}]
+                    xtick={0, 1}, ytick=\empty, xlabel={$s$}]
                 \addplot[name path=f, blue,ultra thick] {x^2};
@@
             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-                xtick={0, 1}, ytick={0}, xlabel={$s$}]
+                xtick={0, 1}, ytick=\empty, xlabel={$s$}]
                 \addplot[name path=f, blue,ultra thick] {x^0.5};
@@
             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-                xtick={0, 1}, ytick={0}, axis lines=left, xlabel={$s$}]
+                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
                 \addplot[name path=f, blue,ultra thick] {ln(1+x)};
@@
             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-                xtick={0, 1}, ytick={0}, axis lines=left, xlabel={$s$}]
+                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
                 \addplot[name path=f, dashed, black] {ln(1+x)};
@@
             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.225, samples at={0, 0.02, ..., 0.98, 1},
-                xtick={0, 1}, ytick={0}, axis lines=left, xlabel={$s$}]
+                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
                 \addplot[name path=f, blue,ultra thick] {sqrt(x)};
@@
             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.225, samples at={0, 0.02, ..., 0.98, 1},
-                xtick={0, 1}, ytick={0}, axis lines=left, xlabel={$s$}]
+                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
                 \addplot[name path=f, dashed, black] {sqrt(x)};

### 2023-04-07 src/paper/theory.tex
Start rewriting the application section

@@
     \begin{align*}
-        \varphi_P^\infty = \lim_{n \to \infty} \varphi_p^n = \int_0^1 f(t) \dt .
+        \varphi_P^\infty = \lim_{n \to \infty} \varphi_P^n = \int_0^1 f(t) \dt .
     \end{align*}
@@
         0                                                & \text{if } P \notin S \\
-        f\left(\frac{n_A(S)}{n}, \frac{n_A(S)}{n}\right) & \text{otherwise}.
+        f\left(\frac{n_A(S)}{n}, \frac{n_B(S)}{n}\right) & \text{otherwise}.
     \end{cases}
@@
 
-\section{Old example application}
+This section demonstrates the proposed cooperative approach via a model of a vertical market.
+Note, that this is not a full-fledged model, and many factors are exogenous.
+However, it is sufficient to illustrate the advantages of the framework presented in this paper: most notably, its analytical tractability and that it captures what intuitively feels like bargaining power.
 
-This section demonstrates the usefulness of the cooperative approach via a model of a hybrid market, based on that in \textcite[]{anderson2021hybrid}.
-Consider a market with a continuum of firms $a(t)$ ($t \in \mathbb{R}^+$), continuum of identical consumers and one platform $P$.
-Assume former two can only interact through the platform.
-Let each firm have its own, differentiated product.
-The consumers have a logit utility function over these products, and a set of outside options of measure 1.
-I will examine the outcome in two situations: (1) the platform functions as a pure marketplace without having an own product, and (2) the platform operating in hybrid mode, selling a measure $N_P$ of differentiated products of its own.
+Consider a market in the vein of \textcite{hart1990property}, but with a finite number of upstream and a continuum of downstream firms.
+Furthermore, let us model production and sales in a reduced form, without going into the micro-foundations of the profit functions.
+Finally, let us assume that profits are shared according to players' Shapley-values.
 
-\subsection{Timing of the game}
+In the rest of this section, I will examine the effect of various market structures on the profit distribution.
+I start by looking at the case of a single upstream producer, with no direct acces to the downstream market.
+I then contrast this with two scenarios in which the upstream producer acquires a way to directly sell to the final consumers: either by vertical integration (merging with some share of the downstream firms), or by creating a completely new, downstream division within itself.
+Finally, I look at the case of multiple upstream producers, and how their presence changes the incentives for merging with downstream firms.
 
-The game proceeds as follows.
-In the first stage, each firm decides whether to invest in creating a product or not. Creating a product incurs a development cost of C.
-Firms that choose not to invest obtain a payoff of 0 and are excluded from the remainder of the game.
-
-Next, the firms that have a product decide whether they want to join the platform at the cost of some entry fee $F^f$.
-(Note that the entry fee can be negative, in which case it is a subsidy from the platform to the firm.)
-Consumers are assumed to be on the platform without a choice.
-Finally, the platform and the entering firms post their product prices, and produce and sell to consumers at marginal cost $c$.
-
-The model heavily depends on how the entry fees are determined.
-The most widespread assumption in the literature is that they are unilaterally decided by the platform, and are essentially take it or leave it offers for the other players.
-The issue with this approach is that it generally leads to extreme conclusions (depending on the number of platforms, and assumptions about single-and-multi-homing, the platforms either act as monopolists or obtain zero profits).
-As an alternative to this, in this paper, I assume that firm entry fees are a result of some bargaining process between the firms and the platform.
-Furthermore, the bargaining process is such that it leads to an allocation in which the final profits of each player correspond to their Shapley values.
-
-The characteristic function (necessary for computing values) of a coalition consisting of the platform and any set of firms is defined as follows.
-Take the members of any given coalition as fixed.
-Let firms and the platform set profit-maximizing prices for their products without collusion.
-Note that these prices will be irrespective irrespective of earlier decisions, as both development costs and entry fees are sunk cost at this point.
-The total profits of the coalition is then the sum of the platform's and the firms' profits from product sales.
-
-While the previous procedure might look somewhat peculiar at first glance, its elements would not be out of place in more traditional (non-cooperative) models, either.
-Principally, the two main ideas it relies are the following.
-First, bargaining outcomes should not depend on which player actually obtains the money, all that matters is the total that a given set of players can obtain.\footnote{
-    For example, imagine the following two situations with two players.
-    In the first one, the first player obtains a playoff of two dollars if they both decide to cooperate and nothing otherwise.
-    In the second scenario, both players receive one dollar in the case of cooperation.
-    If they can transfer monay between each other, bargaining outcomes should be the same in both scenarios.
-} Second, players during the bargaining foresee the (unique) subgame perfect equilibrium in the following subgame, and negotiate based on them.
-
-\subsection{The pricing subgame}
-
-Let us start from the last stage, when firms' entry to the platform is already decided: a measure $N_f$ of firms is present on the platform.
-Assume that consumers have the same Logit-form demand system as in \textcite{anderson2021hybrid}.
-Each consumer buys precisely a measure one of products, those giving her the highest net utility.
-The utility from choosing outside option $i$ is $\mu \epsilon_{0i}$.
-The net utility from buying the platform's $i$th product at price $p_{Pi}$ is $v - p_{Pi} + \mu \epsilon_{Pi}$, while the net utility from choosing the $i$th fringe firm's product is $v - p_{Fi} + \epsilon_{Fi}$.
-$\epsilon_{Pi}, \epsilon_{Fi}$ and $\epsilon_{0i}$ come from identical, independent, standardized Gumbel-distributions.
-
-As shown in \textcite{anderson2021hybrid}, the demand for each of these three types of products is
-\begin{align*}
-    q_{Pi} &= \frac{\int_0^{N_P}  e^\frac{v - p_{Pi} \di}{\mu}}{A} \\
-    q_{Fi} &= \frac{e^\frac{v - p_{Fi}}{\mu}}{A} \\
-    q_{0i} &= \frac{1}{A} .
-\end{align*}
-where
-\begin{align*}
-    A = \int_0^{N_P} e^\frac{v - p_{Pi}}{\mu} \dt + \int_0^{N_F} e^\frac{v - p_{Fi}}{\mu} \dt + 1.
-\end{align*}
-
-Furthermore, it can be shown that the optimal pricing strategy is a constant, additive markup over the unit cost.
-Moreover, the markup is the same for both the platform and the firms, and corresponds to the dispersion in tastes:
-\begin{align*}
-    p_{Pi} = p_{Fi} = c + \mu.
-\end{align*}
-
-Conversely, the profit of the two types of players are
-\begin{align*}
-    \pi_{Fi} &= \frac{\mu}{A} e^\frac{v - c - \mu}{\mu} \\
-    \pi_{Pi} &= N_P \frac{\mu}{A} e^\frac{v - c - \mu}{\mu}
-\end{align*}
-and the total profits of all players together are
-\begin{align*}
-    v(N_f) = N_f \pi_{Fi} + \pi_{Pi} = \mu \frac{A - 1}{A}.
-\end{align*}
-
-Let $B = e^\frac{v - c - \mu}{\mu}$.
-Then the total profits from sales (platform and firms combined) can be expressed as
-\begin{align*}
-    v(N_f) = \frac{N_P B + N_f B}{N_P B + N_f B + 1}.
-\end{align*}
-This is the characteristic function that forms the basis of the profit allocation.
-
-\subsection{Deciding firm entry fees}
-
-Let us look at the second stage of the game: firms have made their investment decisions, and are now negotiating with the platform over the entry price.
-Let us assume that $\bar{N}_f \in \mathbb{R}^+$ measure of firms have made an investment.
-$C$ is a fixed cost, therefore does not influence the rest of the game.
-It is simpler to think about bargaining final net profits (entry fees can always be set to achieve any final allocation of profits), which are assumed to be equal to the players' Shapley values.
-Let us denote these values by $\varphi_f(v, T)$ and $\varphi_P(v, T)$ for the firms and the platform, respectively.
-As shown in proposition \ref{prop:one_sided},
-\begin{align*}
-    \varphi_P(v, \bar{N}_f) &= \int_0^1 v(t \bar{N}_f) \dt \\
-    &= 1 - \frac{\log(BN_p + BN_f + 1) - \log(BN_p + 1)}{BN_f}
-\end{align*}
-and
-\begin{align*}
-    \varphi_f(v, \bar{N}_f) &= v(\bar{N}_f) - \int_0^1 v(t \bar{N}_f) \dt \\
-    &= \frac{N_P B + N_f B}{N_P B + N_f B + 1} - 1 + \frac{\log(BN_P + BN_f + 1) - \log(BN_P + 1)}{BN_f} \\
-    &= \frac{\log(BN_P + BN_f + 1) - \log(BN_P + 1)}{BN_f} - \frac{1}{N_P B + N_f B + 1}.
-\end{align*}
-
-\subsection{Equilibrium entry}
-
-Finally, looking at the first stage, firms will make the initial investment if and only if $\varphi_{f_i}(v, \bar{N}_f) = \varphi_f(v, \bar{N}_f) / \bar{N}_f \geq C$.
-Therefore, because of the free entry condition, the equilibrium measure of entrants is given by the equation
-\begin{align*}
-    \underbrace{\frac{\log(BN_P + B\bar N_f + 1) - \log(BN_P + 1)}{B\bar N_f} - \frac{1}{N_P B + \bar N_f B + 1}}_{\equiv h(\bar N_f)} = C \bar{N}_f.
-\end{align*}
-
-Let us examine the implications of this result through a numerical example.
-Let $B=1, C=0.2$, and let the product variety of the platform be $0$ and $0.2$ in the pure marketplace and the hybrid case, respectively.
-The equilibrium number of entrants is shown in figure \ref{fig:entry}.
-\begin{figure}
-    \centering
-    \includegraphics[width=4in]{out/figures/equilibrium_entry.pdf}
-    \caption{Equilibrium number of fringe entrants as a function of the platform's product variety.}
-    \label{fig:entry}
-\end{figure}
-
-It is immediately apparent from the figure, that a platform operating in hybrid mode discourages fringe entry, as a direct result of more competition and lower profits in the final stage of the game.
-However, a more subtle point is that the total number of products (platform's products plus measure of entrants) is also lower in the hybrid case.
-Because consumer surplus is proportional to the logarithm of the number of available products, this also corresponds to a decrease in that measure.
-
- In the version of the model without bargaining, the platforms' product variety does not influence total product variety, as long as entry fees are fixed.
- An increase in the monopolist's product variety will lead to an identically sized decrease in fringe entry, leaving the total number of available products, and, conversely, consumer welfare, unchanged.
- Operating in hybrid mode only influences fringe entry through more indirect channels, e.g.
-self-preferencing \parencite[]{hagiu2022should} or distorted incentives when setting revenue-based fees \parencite[]{anderson2021hybrid}.
- This example application highlights another channel of distortion created by hybrid platforms: a platform having its own products has more bargaining power when entry fees are determined, leading to lower fringe profits.
- As a consequence, fewer firms enter than in the pure marketplace scenario, and this decrease is more significant than the addition of the platform's own products.
+As this model is only supposed to be an illustration, I will focus on simplicity rather than realism.
+Furthermore, I will not endogenize certain choices, such as entry, or the actual merger decisions.
+Nevertheless, some of the results are suggestive of what might happen in an applied, more fully specified model.
 

### 2023-04-07 src/paper/theory.tex
Switch from two-sided to many-sided

@@
 
-\section{Two-sided case}
+\section{Many-sided case}
 
-Now imagine that, in addition to player $P$, there are two types of smaller players: $\{A_1, \dots, A_n\}$ and $\{B_1, \dots, B_n\}$.
+Now imagine that, in addition to player $P$, there are $L$ types of $n$ smaller players: $\{A^l_1, \dots, A^l_n\}$ where $1 \leq l \leq L$.
 As before, $P$ is necessary for any coalition to have a positive value, and the small players are identical within their groups.
-I.e., the set of players and the characteristic function of the game are the following: $N = \{P, A_1, \dots, A_n, B_1, \dots, B_n\}$ and
+I.e., the set of players and the characteristic function of the game are the following: $N = \{P, A^1_1, \dots, A^1_n, \dots, A^L_1, \dots, A^L_n\}$ and
 \begin{align*}
@@
         0                                                & \text{if } P \notin S \\
-        f\left(\frac{n_A(S)}{n}, \frac{n_B(S)}{n}\right) & \text{otherwise}.
+        f\left(\frac{n_{A_1}(S)}{n}, \dots, \frac{n_{A_L}(S)}{n}\right) & \text{otherwise}.
     \end{cases}
 \end{align*}
-A prominent interpretation of this model would be a platform marketplace with a set of sellers and a set of buyers, where all three sides possess some amount of bargaining power.
+A prominent interpretation of the two-sided version this model would be a platform marketplace with a set of sellers and a set of buyers, where all three sides possess some amount of bargaining power.
 However, player $P$ does not have to be in the ``middle'' of the transactions for this framework to be applicable.
@@
 \begin{proposition}
-    The game $(N, v)$ is monotone and superadditive if and only if $f$ is increasing in both arguments.
+    The game $(N, v)$ is monotone and superadditive if and only if $f$ is increasing in all of its arguments.
 \end{proposition}
@@
 It turns out that the limits of the Shapley-values (as $n \to \infty$) are still analytically tractable and they also have neat interpretations.
+For ease of notation, let us define the following function:
 
 \begin{proposition}
-    Let $f(a, b)$ be continuous everywhere on $[0, 1]^2$.
+    Let $f$ be continuous everywhere on $[0, 1]^L$.
     Then,
     \begin{align*}
-        \varphi_P^\infty & = \int_0^1 f(t, t) \dt                                 \\
-        \varphi_A^\infty & = \int_0^1 t \frac{\partial f(t, t)}{\partial a} \dt   \\
-        \varphi_B^\infty & = \int_0^1 t \frac{\partial f(t, t)}{\partial b} \dt .
+        \varphi_P^\infty & = \int_0^1 f(t, \dots, t) \dt                                 \\
+        \varphi_{A_l}^\infty & = \int_0^1 t \partial_l f(t, \dots, t) \dt.
     \end{align*}
@@
 \begin{align*}
-    f(1, 1) = \underbrace{\int_0^1 f(t, t) \dt}_{\text{ player } P} + \underbrace{\int_0^1 t \frac{\partial f(t, t)}{\partial a} \dt}_{\text{players } A} + \underbrace{\int_0^1 t \frac{\partial f(t, t)}{\partial b} \dt}_{\text{players } B}.
+    f(1, \dots, 1) = \underbrace{\int_0^1 f(t, \dots, t) \dt}_{\text{ player } P} + \sum_{l=1}^L \underbrace{\int_0^1 t \partial_l f(t, \dots, t) \dt}_{\text{players } A_l}.
 \end{align*}
@@
 
-The two-sided case can also simply be extended to incorporate multiple platforms instead of just one.
+The many-sided case can also simply be extended to incorporate multiple platforms instead of just one.
 As before, assume that there are $k$ players of type $P$ which are perfect substitutes of each other:
@@
         0                                                & \text{if } P_i \notin S \; \forall \, i = 1, \dots, k \\
-        f\left(\frac{n_A(S)}{n}, \frac{n_B(S)}{n}\right) & \text{otherwise}.
+        f\left(\frac{n_{A_1}(S)}{n}, \dots, \frac{n_{A_L}(S)}{n}\right) & \text{otherwise}.
     \end{cases}
@@
     \begin{align*}
-        \varphi_{P_i}(k, \infty) & = \int_0^1 (1-t)^{k-1} f(t, t) \dt                                 \\
-        \varphi_A(k, \infty)     & = \int_0^1 [1 - (1-t)^k] \frac{\partial f(t, t)}{\partial a} \dt   \\
-        \varphi_B(k, \infty)     & = \int_0^1 [1 - (1-t)^k] \frac{\partial f(t, t)}{\partial b} \dt .
+        \varphi_{P_i}(k, \infty) & = \int_0^1 (1-t)^{k-1} f(t, \dots, t) \dt                                 \\
+        \varphi_{A_l}(k, \infty)     & = \int_0^1 [1 - (1-t)^k] \partial_l f(t, \dots, t) \dt.
     \end{align*}
@@
     Let $\varphi_{P}(k, \infty) = k\varphi_{P_i}(k, \infty)$ denote the aggregated Shapley-values of players of type $P$.
-    Then $\varphi_{P}(k, \infty)$ is decreasing in $k$ and $\varphi_{A}(k, \infty)$, $\varphi_{B}(k, \infty)$ is increasing in $k$ unless $f$ is constant.
+    Then $\varphi_{P}(k, \infty)$ is decreasing in $k$ and $\varphi_{A_l}(k, \infty)$ are increasing in $k$ unless $f$ is constant.
 \end{corollary}

### 2023-04-07 src/paper/theory.tex
Add benchmark case for example application

@@
 
+\subsection{Benchmark case}
+
+Let us start by looking at the simplest case: one upstream producer, no direct access to the downstream market.
+Assume that without the upstream producer, the downstream firms cannot produce anything, and thus total industry profits are zero.
+On the other hand, if the upstream producer and $t$ fraction of the downstream firms create an agreement, then total industry profits are given by the function $f(t)$.\footnote{
+    This reduced-form profit function can be given microfoundations in many ways.
+    For an example, see TODO!!!!
+}
+Furthermore, the following assumption guarantees ensures that the game is superadditive, therefore it actually makes sense to have every downstream firm in the coalition.\footnote{
+    TODO: elaborate on what this assumption entails.
+}
+\begin{assumption}
+    Let us assume that $f$ is continuous and increasing in $t$.
+\end{assumption}
+
+As noted before, profits are distributed according to players' Shapley values.
+Consequently, it follows from \cref{prop:one_sided} that the profits of the upstream producer and the downstream mass of firms are
+\begin{align*}
+    \pi_P & = \int_0^1 f(t) \dt, \\
+    \pi_A & = f(1) - \int_0^1 f(t) \dt,
+\end{align*}
+respectively.
+
+\subsection{Vertical integration}
+
+\subsection{Additional downstream division}
+
+\subsection{Multiple upstream producers}
+
 \section{Conclusions}

### 2023-04-09 src/paper/theory.tex
Expand example application section

@@
 I then contrast this with two scenarios in which the upstream producer acquires a way to directly sell to the final consumers: either by vertical integration (merging with some share of the downstream firms), or by creating a completely new, downstream division within itself.
-Finally, I look at the case of multiple upstream producers, and how their presence changes the incentives for merging with downstream firms.
 
@@
 \begin{align*}
-    \pi_P & = \int_0^1 f(t) \dt, \\
-    \pi_A & = f(1) - \int_0^1 f(t) \dt,
+    \pi_P^b & = \int_0^1 f(t) \dt, \\
+    \pi_A^b & = f(1) - \int_0^1 f(t) \dt,
 \end{align*}
@@
 
-\subsection{Additional downstream division}
+Let us now consider the case in which the upstream producer merges with some fraction $\alpha$ of the downstream firms.
+The total profits are the same as before, namely, $f(1)$.\footnote{
+    TODO: do I need a footnote here?
+}
+However, the profit distribution is now different.
+New shares can be calculated as follows:
+\begin{align}
+    \pi_{P}^m & = \frac{1}{1 - \alpha} \int_\alpha^1 f(t) \dt, \\
+    \pi_{A}^m & = f(1) - \frac{1}{1 - \alpha} \int_\alpha^1 f(t) \dt .
+\end{align}
 
-\subsection{Multiple upstream producers}
+Clearly, the upstream producer gets a larger share than before, while the remaining downstream firms capture a smaller share.
+This is intuitive, as the upstream producer now depends on the remaining downstream sellers to a lesser extent.
+However, it's worth examining whether this increase is large enough in the sense that the now hybrid upstream producer's profit is higher than the sum of its profit and $\alpha$ fraction of the downstream firms' profit from the benchmark case.
+The participants only have an incentive to merge if this is the case.
+It turns out that this depends on the shape of the profit function.
+
+\begin{proposition}
+    \label{prop:vertical_integration}
+    If $f$ is concave (convex) on $[0, 1]$, then $\pi_P^m \geq \pi_P^b + \alpha \pi_A^b$ ($\pi_P^m \leq \pi_P^b + \alpha \pi_A^b$). 
+\end{proposition}
+
+The intuition is that when $f$ is concave, then obtaining some fraction of the firms lets it create a (comparatively) large share of the total possible profits by itself, and its bargaining position is considerably strengthened.
+In comparison, when $f$ is convex, then the upstream producer still has a large need for the rest of the downstream firms, even when it acquires some of them.
+The bottom line is that industries which are characterized by the downstream firms being relatively substitutable are more susceptible to consolidation.
+
+\subsection{Upstream firm builds downstream capacity}
+
+Now let us consider another way of getting direct downstream access: instead of acquiring some of the existing downstream firms, the upstream producer creates new downstream capacity from scratch.
+In contrast to the previous case, the total size of the pie also changes.
+Let's assume that the upstream firm's downstream capacity is equal to that of $\alpha$ measure of the downstream firms.
+Then, the total profits when everyone agrees to participate is given by $f(1 + \alpha)$, which is larger than $f(1)$ before.
+
+As before, let us examine the distribution of the profits in this case as well:
+\begin{align*}
+    \pi_{P}^c & = \int_0^1 f(t + \alpha) \dt, \\
+    \pi_{A}^c & = f(1 + \alpha) - \int_0^1 f(t + \alpha) \dt .
+\end{align*}
+Similarly to the vertical merger case, the now hybrid upstream producer's profits increase with the size of its downstream capacity.
+However, it is not obvious how the downstream's profit changes.
+The next proposition shows that it, again, depends on the shape of the profit function.
+\begin{proposition}
+    \label{prop:downstream_capacity}
+    If $f$ is concave (convex) on $[0, 1+\alpha]$, then $\pi_A^m \geq \pi_A^b$ ($\pi_A^m \leq \pi_A^b$). 
+\end{proposition}
+
+The results are similar to the previous case.
+When the downstream firms are more substitutable, the upstream firms' newly created capacity strongly reduces their bargaining power, and even though the total size of the pie increases, the downstream firms' share decreases not only in relative terms, but also in absolute terms.
+In a model with endogenous entry and exit on the part of the downstream firms, this would most likely lead to a reduction in their number.
+The implication then also resembles the one in the vertical merger case: industries when downstream firms are easily substitutable should be strongly scrutinized when an upstream firm seeks to build its own downstream capacity.
 

### 2023-04-09 src/paper/theory.tex
Rewrite conclusions

@@
     This approach might be advantageous when one does not want to attribute all the bargaining power to one type of market participants, and at the same time would like to avoid having to deal with an explicit multi-stage bargaining game.
-    I demonstrate the advantages of this approach in simple a model of hybrid platforms.
+    I demonstrate the advantages of this approach in a stylized model of a vertical market.
 \end{abstract}
@@
 Furthermore, the results are simple enough that these games can be embedded into more complex models, for example, as the second stage of a sequential game \parencite[as in e.g.][]{montez2007downstream}.
-Finally, I demonstrate the usefulness of this approach by building a simple model of a platform that can choose to function in hybrid mode as opposed to just being a pure marketplace.
+Finally, I demonstrate the usefulness of this approach by building a simple model of a vertical market that obtains the capability of bypassing the downstream firms and selling directly to final consumers.
 
@@
 
-The illustrative hybrid platform model also highlights the strengths of this approach.
-Despite its simplicity, it highlights a novel channel through which platforms selling their own products might lead to welfare losses: hybrid platforms have more bargaining power against potential entrants than traditional ones.
-This mechanism should probably also be considered when competition authorities assess mergers between platforms and contents providers.
+The illustrative model also highlights the strengths of this approach.
+Despite its simplicity, it highlights that the effects of vertical integration strongly depends on the substitutability of the downstream firms.
+In a time when upstream firms and platforms are increasingly seeking to sell directly to the consumers\footnote{
+    As some recent examples, consider the recent acquisition of Whole Foods by Amazon, Microsoft's ongoing efforts to buy Activision/Blizzard (a major video game publisher), or Tesla's or BMW's plans to sell cars directly without the help of dealerships.
+}
+, such results can be important for competition authorities.
 
 There is a variety of ways through which this paper could be expanded or built upon.
-On the theoretical side, some of the stricter assumptions could be relaxed, such as fringe agents achieving a zero payoff without the platform.
-Besides, the convergence result for the weighted values could be strengthened if one could manage to show that any sequence along ever more refined partitions of the atomic players converges to the same limit \parencite[à la][]{fogelman1980asymptotic}.
-The possibilities for practical applications are no less interesting, either.
-As a first step, the majorly simplified example application could be expanded upon, so that it is a better description of certain real-life pLAtform markets.
-Finally, the cooperative approach to profit distribution could become an alternative for the more usual, but in some sense more extreme assumptions about the bargaining process widely used in industrial organization models.
+On the theoretical side, a number of the assumptions, such as fringe agents achieving a zero payoff without the platform, could be relaxed,
+Besides this, the convergence result for the weighted values could be strengthened if one could manage to show that any sequence along ever more refined partitions of the atomic players converges to the same limit \parencite[à la][]{fogelman1980asymptotic}.
+
+A slightly different direction would be to consider other solution concepts from cooperative game theory in this specific setting.
+One obvious candidate is the nucleolus, which shares many of the useful properties of the Shapley-value (it always exists and is unique).
+Furthermore, it also has connections to bargaining theory due to it being contained in the core when the latter exists.
+
+The possibilities for practical applications are no less interesting.
+The proposed profit sharing framework could be embedded in a more applied model of some real-life setting.
+For a step in this direction, see \textcite{stancsics2023hybrid}.
+
+Finally, with time, the cooperative approach to profit distribution could become an almost drop-in alternative of the more usual, but in some sense more extreme assumptions about the bargaining process widely used in industrial organization models.
 

### 2023-04-09 src/paper/theory.tex
Minor additions

@@
     \label{prop:monotone}
-    The game $(N, v)$ is monotone and superadditive if and only if $f$ is increasing and $f(0) \geq 0$. % It is supermodular if and only if $f$ is convex.
+    The game $(N, v)$ is monotone and superadditive if and only if $f$ is increasing and $f(0) \geq 0$.
 \end{proposition}
@@
     This reduced-form profit function can be given microfoundations in many ways.
-    For an example, see TODO!!!!
+    For an example, see \textcite{stancsics2023hybrid}.
 }
@@
 The participants only have an incentive to merge if this is the case.
-It turns out that this depends on the shape of the profit function.
+It turns out that this depends on the shape of the profit function.\footnote{
+    This way of modeling vertical integration assumes that the upstream firm's innate bargaining power is not affected by the merger.
+    In the terms of some non-cooperative bargaining model, such as \textcite{hart1996bargaining}, it means that the non-acquired downstream firms get a higher probability of proposing allocations.
+    It could be interesting to see how the results change when the upstream firm's also obtains the acquired downstream firms' innate bargaining power, and profits are distributed according to weighted Shapley values.
+}
 

### 2023-04-09 src/paper/theory.tex
Add figures

@@
 
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
+                xtick={0, 1}, 
+                axis lines=left, xlabel={$s$}]
+                \addplot[name path=f, dashed, black] {sqrt(x)};
+                \addplot[name path=tildef, black, ultra thick] {sqrt(0.3+0.7*x)};
+                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+                \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
+                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);
+
+                \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];
+
+                \node[anchor=north west] at (axis cs: .05, .95) {Downstream};
+                \node[anchor=south east] at (axis cs: .95, .05) {Upstream};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Concave case}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
+                xtick={0, 1}, ytick={0, 1}, yticklabels={0, f(1)},
+                axis lines=left, xlabel={$s$}]
+                \addplot[name path=f, dashed, black] {(x)^1.5};
+                \addplot[name path=tildef, black, ultra thick] {(0.3+0.7*x)^1.5};
+                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+                \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
+                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);
+
+                \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];
+
+                \node[anchor=north west] at (axis cs: .05, .95) {Downstream};
+                \node[anchor=south east] at (axis cs: .95, .05) {Upstream};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Convex case}
+    \end{subfigure}
+    \caption{Illustration of \cref{prop:vertical_integration}}
+    \label{fig:vertical_intergration}
+\end{figure}
+
 The intuition is that when $f$ is concave, then obtaining some fraction of the firms lets it create a (comparatively) large share of the total possible profits by itself, and its bargaining position is considerably strengthened.
@@
 \end{proposition}
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.14, samples at={0, 0.02, ..., 0.98, 1},
+                xtick={0, 1}, ytick={0, 1, 1.14}, yticklabels={$0$, $f(1)$, $f(1 + \alpha)$},
+                axis lines=left, xlabel={$s$}]
+                \addplot[name path=f, dashed, black] {sqrt(x)};
+                \addplot[name path=tildef, black, ultra thick] {sqrt(0.3+x)};
+                \draw[dashed] (axis cs:0,1) -- (axis cs:1,1);
+                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+                \draw[name path=top] (axis cs:0,1.14) -- (axis cs:1,1.14);
+                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1.14);
+
+                \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];
+
+                \node[anchor=north west] at (axis cs: .05, 1.09) {Downstream};
+                \node[anchor=south east] at (axis cs: .95, .05) {Upstream};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Concave case}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.482, samples at={0, 0.02, ..., 0.98, 1},
+                xtick={0, 1}, ytick={0, 1, 1.482}, yticklabels={$0$, $f(1)$, $f(1 + \alpha)$},
+                axis lines=left, xlabel={$s$}]
+                \addplot[name path=f, dashed, black] {(x)^1.5};
+                \addplot[name path=tildef, black, ultra thick] {(0.3+x)^1.5};
+                \draw[dashed] (axis cs:0,1) -- (axis cs:1,1);
+                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+                \draw[name path=top] (axis cs:0,1.482) -- (axis cs:1,1.482);
+                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1.482);
+
+                \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];
+
+                \node[anchor=north west] at (axis cs: .05, 1.43) {Downstream};
+                \node[anchor=south east] at (axis cs: .95, .05) {Upstream};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Convex case}
+    \end{subfigure}
+    \caption{Illustration of \cref{prop:downstream_capacity}}
+    \label{fig:upstream_capacity}
+\end{figure}
 

### 2023-04-09 src/paper/theory.tex
Improve main figure

@@
 
-Consider a cooperative game with two types of players: a major player $P$ and $n$ smaller players.
-I.e., $N = \{P, A_1, \dots, A_n\}$.
+Consider a cooperative game with two types of players: a major player $P$ and $n$ smaller players $A_i$, $1 \leq i \leq n$.
+Formally, let us denote the set of all players as $N = \{P, A_1, \dots, A_n\}$.
 Assume that (1) no coalition of players can achieve a positive value without the participation of $P$ and (2) players $A_i$ are identical.
@@
     \centering
-    \caption{Distribution of value between player $P$ and the fringe}
-    \label{fig:one_sided}
-    \begin{tikzpicture}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
@@
 
-            \node[anchor=north west] at (axis cs: .1, .9) {Fringe ($A$)};
-            \node[anchor=south east] at (axis cs: .9, .1) {Platform ($P$)};
+                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($A$)};
+                \node[anchor=south east] at (axis cs: .95, .05) {Big player ($P$)};
             \end{axis}
         \end{tikzpicture}
+        \caption{Fringe players are each other's substitutes}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
+                    xtick={0, 1}, ytick={0}, xlabel={$s$}]
+                \addplot[name path=f, ultra thick] {x^1.5};
+                \node[anchor=south east] at (axis cs: .8, .8^1.5) {$f$};
+                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);
+
+                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
+
+                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($A$)};
+                \node[anchor=south east] at (axis cs: .95, .05) {Big player ($P$)};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Fringe players are each other's complements}
+    \end{subfigure}
+    \caption{Distribution of value between player $P$ and the fringe}
+    \label{fig:one_sided}
 \end{figure}
@@
         0                                                & \text{if } P \notin S \\
-        f\left(\frac{n_{A_1}(S)}{n}, \dots, \frac{n_{A_L}(S)}{n}\right) & \text{otherwise}.
+        f\left(\frac{n_{A^1}(S)}{n}, \dots, \frac{n_{A^L}(S)}{n}\right) & \text{otherwise}.
     \end{cases}
@@
             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-                xtick={0, 1}, 
+                xtick={0, 1}, ytick={0, 1}, yticklabels={0, f(1)},
                 axis lines=left, xlabel={$s$}]

### 2023-04-09 src/paper/application.tex
Fix hagiu reference

@@
 These papers mostly focus on competition between platforms, and not on the impact on the platform-participant relationship.
-On the other hand, more recent papers, such as \textcite{hagiu2020should}, \textcite{anderson2021hybrid} and \textcite{gutierrez2021welfare} have started to address the issue of hybrid platforms, and how platforms having their own products affect competition between the platform and the entrants, and ultimately consumer welfare and producer surplus.
+On the other hand, more recent papers, such as \textcite{hagiu2022should}, \textcite{anderson2021hybrid} and \textcite{gutierrez2021welfare} have started to address the issue of hybrid platforms, and how platforms having their own products affect competition between the platform and the entrants, and ultimately consumer welfare and producer surplus.
 The results are mixed: while some of them find that hybrid platforms can be beneficial if certain anti-competitive behavior, such as self-preferencing, is prevented \parencite[]{anderson2021hybrid}, others are more critical of this hybrid form \parencite[]{anderson2021hybrid}.

### 2023-04-09 src/paper/theory.tex
improve info and basic, one-sided case

@@
 Let $n_T(S)$ denote the number of players of type $T \in \{P, A\}$ in coalition $S$.
-Then, the value that any coalition $S \subset N$ can achieve is the following:
+Under these assumptions, the characteristic function of the game (the value that any coalition $S \subset N$ can achieve) is the following:
 \begin{align*}
@@
 \end{align*}
-One can think of this setting as a (one-sided) platform and a number of potential entrants, if the entrants can only reach their prospective consumers through the platform.\footnote{
-    While these assumptions might seem somewhat restrictive, they are relatively simple to relax.
-}
-First, let us characterize the conditions under which this game is superadditive.
-These features provide some theoretical support for using Shapley-values as bargaining outcomes, as papers creating a link between non-cooperative bargaining and cooperative values often rely on such assumptions.\footnote{
+One can think of this setting as a (one-sided) platform and a number of potential entrants, if the entrants can only reach their prospective consumers through the platform, or as a vertical supply chain with one upstream producer and a number of downstream firms.
+
+First, let us characterize the conditions under which this game is monotone and superadditive.
+Superadditivity is a key property of cooperative games, as it ensures that it always pays off to form the grand coalition (i.e., the coalition that includes all players).
+Furthermore, in the context of bargaining, these properties provide some theoretical support for using Shapley-values as bargaining outcomes, as many results creating a link between non-cooperative bargaining and cooperative values often rely on these assumptions.\footnote{
     For example, the results in \textcite{gul1989bargaining} rely on superadditivity, while monotonicity suffices for \textcite[]{hart1996bargaining}.
 }
-
+Fortunately, in this specific setting, characterizing monotonicity and superadditivity is extremely straightforward.
 \begin{proposition}
@@
 
-In the following, let us assume that the assumptions required for monotonicity are always satisfied.
-In addition to the previous advantages, it also ensures that the games are of bounded variation, and thus the main theorem in \textcite{fogelman1980asymptotic} applies them, as well.
-Namely, the asymptotic value coincides with the axiomatic one using the uniform distribution, providing multiple ways of characterizing them.
+In the following, let us assume that the assumptions required for monotonicity are always satisfied (i.e., $f$ is monotone increasing).\footnote{
+    This assumption is not entirely innocuous.
+    For example, having more small firms could in theory lead to stronger competition, decreasing total profits.
+    However, it often holds in models with network effects \parencite{rochet2003platform} or with consumers having taste for variety \parencite{anderson2020aggregative}.
+}
+In addition to this, it also ensures that the games are of bounded variation, and thus the main theorem in \textcite{fogelman1980asymptotic} applies.
+Namely, various approaches of defining the value of an oceanic game (one with a finite number of atomic and a continuum of non-atomic players) lead to the same result\footnote{
+    More rpecisely, the asymptotic value coincides with the axiomatic one using the uniform distribution.
+    For a more detailed discussion, see \textcite{fogelman1980asymptotic}.
+}, providing multiple ways of characterizing it.
 In practice, it means that there is no need to explicitly calculate the limits of finite-player cooperative games, as there is a more direct option for characterizing the value of the oceanic game.
-Nevertheless, in many of the following theorems, the asymptotic limit is preferred, as I believe that makes the proofs more instructive.
+Nevertheless, in many of the following theorems, the asymptotic limit is explicitly derived, as I believe that makes the results more explanatory.
 
-The following proposition demonstrates the main idea of this paper: even as the number of fringe players goes to infinity, the Shapley-value of the platform does not converge to $f(1)$.
+The following proposition demonstrates the main idea of this paper: even as the number of fringe players goes to infinity, the Shapley-value of the big player does not converge to the worth of the grand coalition, $f(1)$.
 This in turn implies that the aggregated Shapley-values of the fringe remain positive even in the limit.
-In the remainder of the paper, let us use the following notation: $\varphi_P^n$ denotes the Shapley-value of player $P$ in the case of $n$ players of type $A$.
+In other words, even though the fringe players become smaller and more numerous, they do not lose all of their bargaining power, and still end up with a positive payoff in the end.
+
+In the remainder of the paper, let us use the following notation: $\varphi_P^n$ denotes the Shapley-value of player $P$ in the game with players $N = \{P, A_1, \dots, A_n\}$.
 \begin{proposition}
@@
 
-It is already apparent from Figure \ref{fig:one_sided} that (for fixed $f(0)$ and $f(1)$) player $P$ gets a larger share of the surplus when $f(t)$ is larger for every $t$.
-It corresponds to the case when only a small fraction of the fringe is needed to create most of the surplus (e.g. their products are substitutes of each other).
-This result aligns with our natural intuition that player $P$ has a better bargaining position in this case, than if only coalitions with most of the fringe firms could obtain high values.
+It is already apparent from Figure \ref{fig:one_sided} that (for a fixed total pie size $f(1)$) player $P$ gets a larger share when $f(t)$ is larger for every $t$.
+It corresponds to the case when only a relatively small fraction of the fringe is needed to create a large part of the total potential surplus (e.g.
+fringe players products are substitutes of each other).
+This result aligns with our natural intuition that player $P$ has a better bargaining position in this case, than if only coalitions with most of the fringe firms on board could obtain high values.
+In contrast, when fringe players are more complementary to each other, the big player can only obtain a smaller share, as its bargaining power is more limited.
 
@@
 
-Finally, the following corollary implies that, even though the individual share of each $A_i$ vanishes as their number goes to infinity, their total value still converges to a positive value.
+Finally, the following corollary highlights that, even though the individual share of each $A_i$ vanishes as their number goes to infinity, their total value still remains positive.
 \begin{corollary}

### 2023-04-09 src/paper/theory.tex
Improve section about weighted values

@@
 
-\subsection{Weighted Shapley-values}
+\subsection{Weighted values}
 
-While the values of oceanic games (i.e.
-the limits of the Shapley values of their finite approximations in finite games) are well known in the relevant literature, there are no results about the limits of the weighted (Shapley) values.
-While providing very general results in the form of \textcite[]{fogelman1980asymptotic} is outside the scope of the paper\footnote{
-    They show that the (within some constraints) any discretization of an oceanic game converges to the same value.
-} the results in this section still provide some new insights into weighted values of oceanic games.
-In particular, I show that the weighted value of a game with one large and many small players converges to a rather simple and intuitive expression, if the size of the small players go to zero at the same rate.
+Now let us turn to an extension of the Shapley-value, where the symmetry of the players is relaxed: the weighted value.
+Imagine a general non-cooperative game $(N, v)$ with $N = \{1, \dots, n\}$.
+Assume that, in addition to the value function $v : 2^n \to \mathbb{R}$, the game is now also endowed with a weight system $\lambda \in \mathbb{R}^n$.
+The main idea behind the weighted value is that, in contrast to the Shapley-value, even players that have the same contribution to each possible coalition do not necessarily get the same value.
 
-Imagine a general non-cooperative game $(N, v)$ with $N = \{1, \dots, n\}$.
-Assume that, in addition to the value function $v : 2^n \to \mathbb{R}$, the game is also endowed with a weight system $\lambda \in \mathbb{R}^n$.
 These weights can be thought of as measures of innate bargaining power \parencite{shapley1953additive}, not reflected in the value function.
@@
 
-For my purposes, it is sufficient to deal with the case of simple weights. I.e., assume that there is at most one player with zero weight.
-For my main result, I make use of the fact that weighted Shapley values can be calculated by weighting the permutations by the probabilities arising from the following sequential ordering procedure \parencite{kalai1987weighted}.
+Although the values of oceanic games (i.e.
+the limits of the Shapley values of their finite approximations in finite games) are well known in the relevant literature, there are no similar results for weighted (Shapley) values.
+While providing very general results in the form of \textcite[]{fogelman1980asymptotic} is outside the scope of the paper\footnote{
+    They show that the (within some constraints) any discretization of an oceanic game converges to the same value.
+} the results in this section still provide some new insights into the weighted values of oceanic games.
+In particular, I show that the weighted value of a game with one large and many small players converges to a rather simple and intuitive expression, if the size of the small players go to zero at the same rate.
+
+For my purposes, it is sufficient to deal with the case of simple weights.
+I.e., assume that there is at most one player with zero weight.
+For my main result, I make use of the fact that weighted values can be calculated by weighting the permutations by the probabilities arising from the following sequential ordering procedure \parencite{kalai1987weighted}.
 Start with the set of all players.
@@
 Consider the game described in the previous section, and let the weights of players of type $A$ and $P$ be 1 and $\lambda$, respectively.
-Let $X_n$ be a random variable representing the number of players before $P$ when players are ordered according to the above procedure.
+Let $X_n$ be a random variable representing the number of players before $P$ when players are ordered according to the previously described procedure.
 Then, the probability of player $P$ having at most $k$ players of type $A$ before themselves is simply
@@
 
-The main proposition of this section shows that the weighted Shapley-value of player $i$ can be expressed as the expected marginal contribution of that player where the permutations are weighted according to the previous distribution.
+Now let us turn to the main proposition of this section: the weighted value of player $P$ can again be expressed as an integral over the share of fringe players, but now it is weighted according to the previous probability distribution.
+Depending on the shape of this distribution (which in turn depends on the weight $\lambda$), regions corresponding to different masses of fringe firms can be over or underweighted in this integral, leading to different values.
 \begin{proposition}
@@
 
-Finally, the following corollaries support the interpretation of weights as bargaining power, as a higher weight corresponds to a higher Shapley-value in this game.\footnote{
+Now, let us examine how this weighting impacts the shares of the various players.
+It turns out, that a higher weight corresponds to a higher Shapley-value in this game.\footnote{
     This would not necessarily have to be the case, as demonstrated by \textcite{owen1968communications}.
-}
-Furthermore, the limit of the weighted value of $P$, as their weight goes to zero (infinity) is precisely the payoffs $P$ would achieve if $P$ were making (facing) take-it-or-leave-it offers.
-
+},
+supporting the interpretation of weights as some kind of innate bargaining power.
 \begin{corollary}
@@
 
+Furthermore, the following corollary shows that the limit of the weighted value of $P$, as their weight goes to zero (infinity) is precisely the payoffs $P$ would achieve if $P$ were making (facing) take-it-or-leave-it offers.
+This set of results highlights that utilizing (weighted) Shapley values to model bargaining outcomes provides an intermediate solution between inscribing all the bargaining power to one or the other player.
 \begin{corollary}

### 2023-04-09 src/paper/theory.tex
Improve multiple platforms section

@@
 
-\subsection{Multiple platforms}
+\subsection{Multiple big players}
 
-Imagine that, instead of just one, there are $m$ players of type $P$, and they are perfect substitutes of each other.
-That is, the fringe players still need a platform to achieve any value, but it does not matter which or how many platforms are available for them.
-Formally, the value function for coalition $S$ is the following:
+Now imagine that, instead of just one, there are $m$ players of type $P$, and they are perfect substitutes of each other.
+That is, the fringe players still need one at least of them to achieve any value, but it does not matter which and how many of them are present.
+Formally, the value function for coalition $S$ becomes the following:
 \begin{align*}
@@
 \end{proposition}
-% \textcolor{red}{Note: I have to think more about how to describe this situation in the language of cooperative game theory.
-The issue is that, for example, the value of $\{P_1, A_1\}$ depends on whether $\{P_2, A_2\}$ also decides to form a coalition and enter the market.}
+On the other hand, superadditivity is not as simple in this case, as before.
+For example, when $f$ is concave, then $m$ coalitions with one platform each and the fringe divided equally among them clearly achieve a higher total payoff than the grand coalition.
+Therefore, the results of this section are most applicable to settings when multiple coalitions cannot be formed at the same time for some reason.
+For example, \textcite{hart1996bargaining} propose an interpretation when there is a single, indivisible, non-replicable resource or technology (not captured in the value function) necessary to produce any value.
 
 As before, the main proposition in this section provides us with an expression of the limit of the value for this variant of the game.
+Notably, as in the case of the weighted value, the share of player $P$ can again be expressed as an integral of $f$ and some weighting\footnote{
+    Weighting is not a completely precise term, as $h(t)$ does not integrate to one, and is therefore not a probability distribution in this case.
+    Nevertheless, it highlights the parallel between multiple big players and weighted values.
+} function $h(t)$, with the latter depending only on the number of big players.
 \begin{proposition}
@@
     \begin{align*}
-        \varphi_{P_i}^{\infty, m} = \int_0^1 (1-t) ^ {m-1} f(t) \dt .
+        \varphi_{P_i}^{\infty, m} = \int_0^1 h(t) f(t) \dt,
     \end{align*}
+    where $h(t) = (1-t) ^ {m-1}$.
 \end{proposition}
+
+\begin{corollary}
+    \label{cor:multiple_platforms}
+    The per-unit Shapley-value of the fringe is
+    \begin{align*}
+        \varphi_A(k, \infty) = 1 - m\int_0^1 (1-t) ^ {m-1} f(t) \dt = \int_0^1 [1 - (1-t)^m] f'(t) \dt .
+    \end{align*}
+\end{corollary}
 
@@
         \end{tikzpicture}
-        \caption{$(1 - t) ^ {m - 1}$}
+        \caption{$h(t)$}
     \end{subfigure}
@@
         \end{tikzpicture}
-        \caption{$\int_0^t (1 - s) ^ {m - 1} \ds$}
+        \caption{$\int_0^t h(s) \ds$}
     \end{subfigure}
-    \caption{Illustration of the weighting function for various values of $m$ in the multiple platform case.}
+    \caption{Illustration of the weighting function for various values of $m$ in the multiple big player case.}
     \label{fig:multiple_platforms}
@@
 
-\begin{corollary}
-    \label{cor:multiple_platforms}
-    The per-unit Shapley-value of the fringe is
-    \begin{align*}
-        \varphi_A(k, \infty) = 1 - m\int_0^1 (1-t) ^ {m-1} f(t) \dt = \int_0^1 [1 - (1-t)^m] f'(t) \dt .
-    \end{align*}
-\end{corollary}
-
-The following corollary again demonstrates that the predicted outcomes confirm intuitions.
-As the major players become more and more substitutable, the portion of the surplus they can capture decreases, and the aggregated value of the fringe increases.
+The next corollary again demonstrates that the predicted outcomes confirm intuition.
+As the major players become more and more substitutable, the portion of the surplus they can capture decreases, and the aggregated value of the fringe increases (\cref{fig:multiple_platforms}).
 
@@
 
-\subsection{Multiple platforms}
+\subsection{Multiple big players}
 
@@
 
-It can be shown that the values of each type of player are rather similar to the one-platform case.
+It can be shown that the values of each type of player are rather similar to the single big player case.
 \begin{proposition}
@@
 
-Similarly, as the next corollary demonstrates, the combined value of platforms is still decreasing in their number.
+Similarly, as the next corollary demonstrates, the combined value of the big palyers is still decreasing in their number.
 \begin{corollary}

### 2023-04-09 src/paper/theory.tex
Improve multiple sides section

@@
     \begin{align*}
-        \varphi_A(k, \infty) = 1 - m\int_0^1 (1-t) ^ {m-1} f(t) \dt = \int_0^1 [1 - (1-t)^m] f'(t) \dt .
+        \varphi_A^{\infty, m} = 1 - m\int_0^1 (1-t) ^ {m-1} f(t) \dt = \int_0^1 [1 - (1-t)^m] f'(t) \dt .
     \end{align*}
@@
 
-Now imagine that, in addition to player $P$, there are $L$ types of $n$ smaller players: $\{A^l_1, \dots, A^l_n\}$ where $1 \leq l \leq L$.
-As before, $P$ is necessary for any coalition to have a positive value, and the small players are identical within their groups.
-I.e., the set of players and the characteristic function of the game are the following: $N = \{P, A^1_1, \dots, A^1_n, \dots, A^L_1, \dots, A^L_n\}$ and
+Up until this point, we have considered games with a single type of small players.
+Now imagine that, in addition to player $P$, there are $L$ types of smaller players: $\{A^l_1, \dots, A^l_n\}$ where $1 \leq l \leq L$.
+As before, assume that $P$ is necessary for any coalition to have a positive value, and the small players are identical to each other within their types.
+Formally, the game in coalitional form is now the following: the set of players is $N = \{P, A^1_1, \dots, A^1_n, \dots, A^L_1, \dots, A^L_n\}$ and the characteristic function is
 \begin{align*}
@@
 \end{align*}
-A prominent interpretation of the two-sided version this model would be a platform marketplace with a set of sellers and a set of buyers, where all three sides possess some amount of bargaining power.
+
+A prominent interpretation of the two-sided version of this model would be a platform marketplace with a set of sellers and a set of buyers, where all three sides possess some amount of bargaining power.
 However, player $P$ does not have to be in the ``middle'' of the transactions for this framework to be applicable.
 For example, it also captures the situation of a single upstream producer, a large number of downstream firms, and a similarly large number of customers, as long as both the customers and the downstream firms can participate in the bargaining process.
-A setting where these assumptions might be plausible is, for example, the new car market with a car producer, a number of independent dealerships, and customers who might engage in negotiation.
+A setting where these assumptions might be plausible is, for example, the new car market with a car producer, a number of independent dealerships, and customers who might engage in some form of negotiation.
 
 Let us follow the pattern from the previous sections.
-Start by characterizing conditions for superadditivity to support the bargaining interpretation.
+Start by characterizing conditions for monotonicity and superadditivity to support the bargaining interpretation and the formation of the grand coalition.
+The conditions are the straightforward analogues of those from the one-sided case.
 \begin{proposition}
@@
 
-Next, let us obtain formulas for the values of the three groups of players.
-It turns out that the limits of the Shapley-values (as $n \to \infty$) are still analytically tractable and they also have neat interpretations.
-For ease of notation, let us define the following function:
-
+Next, let us obtain formulas for the values of the three types of players.
+It turns out that the limits of the Shapley-values (as $n \to \infty$) are still analytically tractable, and they also have a neat interpretation.
 \begin{proposition}
@@
         \varphi_P^\infty & = \int_0^1 f(t, \dots, t) \dt                                 \\
-        \varphi_{A_l}^\infty & = \int_0^1 t \partial_l f(t, \dots, t) \dt.
+        \varphi_{A^l}^\infty & = \int_0^1 t \partial_l f(t, \dots, t) \dt.
     \end{align*}
@@
 As the previous proposition shows, the value of each kind of player depends on their expected marginal contribution, i.e. the partial derivatives of $f$.
-Consequently, the value of the grand coalition can be decomposed into the Shapley-values of its members signifying their expected marginal contributions in the following way:
+Consequently, the value of the grand coalition can be decomposed into the Shapley-values of its members the following way:
 \begin{align*}
-    f(1, \dots, 1) = \underbrace{\int_0^1 f(t, \dots, t) \dt}_{\text{ player } P} + \sum_{l=1}^L \underbrace{\int_0^1 t \partial_l f(t, \dots, t) \dt}_{\text{players } A_l}.
+    f(1, \dots, 1) = \underbrace{\int_0^1 f(t, \dots, t) \dt}_{\text{ player } P} + \sum_{l=1}^L \underbrace{\int_0^1 t \partial_l f(t, \dots, t) \dt}_{\text{players } A^ll}.
 \end{align*}
+This formulation makes it clear that values are intimately related to the marginal contributions of the players, captured by the partial derivatives of $f$ in the case of the various fringe players.
 
-One surprising element of the result is that one only has to integrate over the diagonal of the support  of $f$, and the value does not depend on the marginal contributions in the case of an unequal measure of $A$ and $B$ types.
+One surprising element of the result is that one only has to integrate over the diagonal of the support  of $f$, and the value does not depend on off-diagonal parts of the $f$ fucntion.
 The intuition for that relies on a law-of-large-numbers-type reasoning.
-If the number of fringe players is large, then it is very unlikely that, after a random ordering, their proportion in any interval will be too different.
-Consequently, when taking the expectation over all orderings, ones with vary unequal numbers of the two types will have little impact on it.
+If the number of fringe players is large, then it is very unlikely that, after a random ordering, their proportion is too different on any interval.
+Consequently, when taking the expectation over all orderings, those with very unequal numbers of the various types have little impact on it.
 
@@
 
-The many-sided case can also simply be extended to incorporate multiple platforms instead of just one.
-As before, assume that there are $k$ players of type $P$ which are perfect substitutes of each other:
+The many-sided case can also simply be extended to incorporate multiple big players instead of just one.
+As before, assume that there are $m$ players of type $P$ which are perfect substitutes of each other:
 \begin{align*}
     v(S) = \begin{cases}
-        0                                                & \text{if } P_i \notin S \; \forall \, i = 1, \dots, k \\
-        f\left(\frac{n_{A_1}(S)}{n}, \dots, \frac{n_{A_L}(S)}{n}\right) & \text{otherwise}.
+        0                                                & \text{if } P_i \notin S \; \forall \, i = 1, \dots, m \\
+        f\left(\frac{n_{A^1}(S)}{n}, \dots, \frac{n_{A^L}(S)}{n}\right) & \text{otherwise}.
     \end{cases}
@@
 \begin{proposition}
-    The unit Shapley-values of the various types of players are
+    The Shapley-values of the various types of players are
     \begin{align*}
-        \varphi_{P_i}(k, \infty) & = \int_0^1 (1-t)^{k-1} f(t, \dots, t) \dt                                 \\
-        \varphi_{A_l}(k, \infty)     & = \int_0^1 [1 - (1-t)^k] \partial_l f(t, \dots, t) \dt.
+        \varphi_{P_i}^{\infty, m} & = \int_0^1 (1-t)^{m-1} f(t, \dots, t) \dt                                 \\
+        \varphi_{A^l}^{\infty, m}     & = \int_0^1 [1 - (1-t)^m] \partial_l f(t, \dots, t) \dt.
     \end{align*}
@@
 
-Similarly, as the next corollary demonstrates, the combined value of the big palyers is still decreasing in their number.
+Similarly, as the next corollary demonstrates, the combined value of the big players is still decreasing in their number.
 \begin{corollary}
-    Let $\varphi_{P}(k, \infty) = k\varphi_{P_i}(k, \infty)$ denote the aggregated Shapley-values of players of type $P$.
-    Then $\varphi_{P}(k, \infty)$ is decreasing in $k$ and $\varphi_{A_l}(k, \infty)$ are increasing in $k$ unless $f$ is constant.
+    Let $\varphi_{P}^{\infty, m} = k\varphi_{P_i}^{\infty, m}$ denote the aggregated Shapley-values of players of type $P$.
+    Then $\varphi_{P}^{\infty, m}$ is decreasing in $k$ and $\varphi_{A^l}^{\infty, m}$ are increasing in $k$ unless $f$ is constant.
 \end{corollary}

### 2023-04-10 src/paper/application.tex
Add abstract

@@
 \begin{abstract}
+    This paper studies the effects of a platform selling their own products in addition to acting as intermediaries (hybrid platforms) in a setting when bargaining takes place between the platform and the potential entrants.
+    It highlights a so-far underexplored aspect of hybrid platforms: having their own products increases their bargaining power over the other sellers.
+    As shown through a more concrete example, this change in bargaining power can have negative welfare consequences for the consumers.
+    The results and methods described in this paper are also applicable to other similar settings, such as vertical integration with a monopolistic upstream supplier.
 \end{abstract}

### 2023-04-10 src/paper/application.tex
Improve intro and some minor changes

@@
 
+In the last couple of decades, a considerable amount of research has been devoted to the study of platforms.
+This paper aims to contribute to this literature by examining an important, but somewhat underexplored aspect of platforms: the bargaining power disparity between them and the other market participants, and how this disparity is affected by the platforms' hybrid operation.
+In particular, this paper proposes an analytically tractable framework which captures many important aspects of bargaining between one large and a continuum of small players, and applies it to the setting of a hybrid platform facing a continuum of potential entrants.
+The results show that when a platform operating in hybrid mode can increase its profits at the cost of decreased seller entry consumer welfare in comparison to the case when the platform is a pure intermediary.
+Before an overview of the relevant literature is given, it is useful to briefly discuss the most prominent features of platforms, as that will be useful to understand the relation of this paper to the existing body of research.
+
 While it is hard to define what a platform is, there are a number of features commonly associated with platforms.\footnote{
@@
 An organization does not have to exhibit all of these features to be considered a platform, but they are often present, and are also the main areas of interest when studying platforms.
-First, platforms are often characterized by multi-sidedness.
-Their most prominent examples are large internet companies, such as Google connecting advertisers and consumers, Amazon connecting sellers and consumers, or Uber connecting drivers and passengers.
-Second, a frequent feature of platforms is the presence of network effects.
+First, platforms are often characterized by multi-sidedness.\footnote{
+    The most prominent examples are large internet companies, such as Google connecting advertisers and consumers, Amazon connecting sellers and consumers, or Uber connecting drivers and passengers.
+}
+Second, a frequent feature of platforms is the presence of network effects.\footnote{
     More buyers on Amazon mean more value for the sellers, and vice versa.
     These network effects often lead to increasing returns to scale, which in turn leads to consolidation in the industry.
-Third, another important aspect of platforms is the disparity between the various market participants.
+}
+A third important aspect of platforms is the disparity between the various market participants.
 While there is usually just a few, large platforms in an industry, there is a much larger number of participants who use the platforms' services to connect to each other.
@@
 
-Various models have been proposed to study the economics of platforms, focusing on different aspects of the phenomenon.
-One of the larger and earlier strands of literature focus on the multi-sidedeness of platforms, the resulting implications.
+Most of the earlier literature on platform economics focuses on the multi-sidedeness of platforms and the related network effects.
 These papers investigate how various market features, such as the possibility of multi-homing, the magnitude of network-effects, or the number of platforms influence market outcomes.
@@
 
-Hybrid platforms also received increasing attention in the literature.
+More recently, hybrid platforms also received increasing attention in the literature.
 While not explicitly phrased in terms of hybrid operation, the literature on the importance of exclusive content can be seen as adjacent to this topic \parencite[]{hagiu2011exclusivity,lee2013vertical,dou2014sell,weeds2016tv}.
@@
 
-Finally, this also belongs to the not too large set of papers using concepts from cooperative game theory in an industrial organization setting.
+Finally, this paper also belongs to the not too large set of models using concepts from cooperative game theory in an industrial organization setting.
 Such examples include the aforementioned \textcite{montez2007downstream}, as well as \textcite{hart1990property}, \textcite{levy1997individual}, \textcite{inderst2003bargaining} and \textcite{brugemann2019intra} among others.
+In contrast to the majority of those, I utilize an oceanic game (a continuum of small players instead of a finite number), and demonstrate that this can considerably simplify the analysis in certain cases.
 
@@
 
-                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($A$)};
+                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
                 \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
@@
 It is independent of the production function, demand, or the fringe firms' substitutability, and might represent, for example, that the platform and the fringe firms have different power to propose allocations during the (not explicitly modeled) negotiation process.\footnote{
-    For a more thorough exploration of this idea, see \cref{app:profit_sharing} and \textcite{hart1996bargaining}.
+    For a more thorough exploration of this idea, see \textcite{hart1996bargaining}.
 }
@@
 
-                \node[anchor=north west] at (axis cs: .05, .65) {Fringe ($A$)};
+                \node[anchor=north west] at (axis cs: .05, .65) {Fringe ($F$)};
                 \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
@@
 
-                \node[anchor=north west] at (axis cs: .05, 1.17) {Fringe ($A$)};
+                \node[anchor=north west] at (axis cs: .05, 1.17) {Fringe ($F$)};
                 \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
@@
 \section{Shapley value in the platform game}
+\label{app:shapley_value}
 

### 2023-04-11 src/paper/application.tex
Rewrite introduction

@@
 
-Even though the economics literature offers no unambiguous definition for what a platform is, there seems to be a consensus that they are of key importance for the modern economy, and are getting even more so in the future.
+Even though the economics literature offers no unambiguous definition for what platforms are, there seems to be a consensus that they are of key importance for the modern economy, and are getting even more so in the future.
 Although market structures resembling various aspects of what we call platforms have existed for some time, the term has only gained widespread usage in the 2000s, with the advent of digitization, and a number of behemoth technology companies playing matchmakers on the internet.
@@
 
-In the last couple of decades, a considerable amount of research has been devoted to the study of platforms.
-This paper aims to contribute to this literature by examining an important, but somewhat underexplored aspect of platforms: the bargaining power disparity between them and the other market participants, and how this disparity is affected by the platforms' hybrid operation.
-In particular, this paper proposes an analytically tractable framework which captures many important aspects of bargaining between one large and a continuum of small players, and applies it to the setting of a hybrid platform facing a continuum of potential entrants.
-The results show that when a platform operating in hybrid mode can increase its profits at the cost of decreased seller entry consumer welfare in comparison to the case when the platform is a pure intermediary.
-Before an overview of the relevant literature is given, it is useful to briefly discuss the most prominent features of platforms, as that will be useful to understand the relation of this paper to the existing body of research.
-
-While it is hard to define what a platform is, there are a number of features commonly associated with platforms.\footnote{
-    I thank the participants of the Third Year Seminar at the University of Zurich for their lively discussion on this topic.
-    The conclusion was that, although platforms are hard to define, "You know one when you see one".
-}
-An organization does not have to exhibit all of these features to be considered a platform, but they are often present, and are also the main areas of interest when studying platforms.
-First, platforms are often characterized by multi-sidedness.\footnote{
-    The most prominent examples are large internet companies, such as Google connecting advertisers and consumers, Amazon connecting sellers and consumers, or Uber connecting drivers and passengers.
-}
-Second, a frequent feature of platforms is the presence of network effects.\footnote{
-    More buyers on Amazon mean more value for the sellers, and vice versa.
-    These network effects often lead to increasing returns to scale, which in turn leads to consolidation in the industry.
-}
-A third important aspect of platforms is the disparity between the various market participants.
-While there is usually just a few, large platforms in an industry, there is a much larger number of participants who use the platforms' services to connect to each other.
-Furthermore, the platform is often indispensable for the participants to make business, but the participants themselves are more easily replaceable.
-This power imbalance naturally leads to antitrust concerns, with regulators taking an increasingly close look at such markets as of late \parencite[see e.g. ][]{fletcher2021consumer}.
-Finally, a somewhat more recent, but slightly alarming feature of platforms is operating in a so-called hybrid mode.
-They act as an intermediary (deciding the rules) and a market participant (competing with the other entrants) at the same time.
-This paper focuses on the latter two aspects (the interplay between bargaining power and hybrid operation), while mostly abstracting away the first two in the form of a rather reduced-form approach of modeling the production function.
-
-Most of the earlier literature on platform economics focuses on the multi-sidedeness of platforms and the related network effects.
-These papers investigate how various market features, such as the possibility of multi-homing, the magnitude of network-effects, or the number of platforms influence market outcomes.
-In addition to welfare, they are often interested in the transfers between the various sides facilitated by the platforms' desire to exploit network effects.
-Examples of such studies include the seminal papers \textcite{rochet2003platform} and \textcite{armstrong2006competition}, as well as a number of insightful papers examining the effects of various market attributes \parencite[e.g.][]{hagiu2004optimal,choi2010tying,evans2011platform,lee2014competing}.
-
-More recently, hybrid platforms also received increasing attention in the literature.
-While not explicitly phrased in terms of hybrid operation, the literature on the importance of exclusive content can be seen as adjacent to this topic \parencite[]{hagiu2011exclusivity,lee2013vertical,dou2014sell,weeds2016tv}.
-These papers mostly focus on competition between platforms, and not on the impact on the platform-participant relationship.
-On the other hand, more recent papers, such as \textcite{hagiu2022should}, \textcite{anderson2021hybrid} and \textcite{gutierrez2021welfare} have started to address the issue of hybrid platforms, and how platforms having their own products affect competition between the platform and the entrants, and ultimately consumer welfare and producer surplus.
-The results are mixed: while some of them find that hybrid platforms can be beneficial if certain anti-competitive behavior, such as self-preferencing, is prevented \parencite[]{anderson2021hybrid}, others are more critical of this hybrid form \parencite[]{anderson2021hybrid}.
-This paper provides some additional insights into this topic, by looking at the impact of dual mode operation on bargaining power.
-
-Many results and concepts of this paper are also applicable outside the context of (multi-sided) platforms.
+Platforms have a number of unique features, which make them different from more traditional market structures.
+The most prominent of those are multi-sidedness and network effects, which most of the early literature \parencite[for an overview, see][]{rochet2006two} and policy debate \parencite[e.g.][]{fletcher2021consumer,calvano2021market} has focused on.
+However, in the more recent years, another important and potentially concerning behavior has been getting more attention: the hybrid operation of platforms.
+Essentially, this means that platforms act as an intermediary (deciding the rules) and a market participant (competing with other entrants) at the same time.
+
+While hybrid platforms are not a completely new phenomenon, they are becoming more and more common in various industries.
+Perhaps the most prominent example is Amazon, which on the one hand selling its own products, and at the same time is hosting  large number of third-party sellers.
+Examples abound in other industries, as well.
+For example, all of the largest digital distribution platforms for computer and smartphone applications (such as Google Play, Apple App Store or Microsoft Store) sell applications products by the platform owner itself besides their third party offerings.
+In the video game industry, platform owners owning their own game studios is the standard.
+Many video streaming services (e.g. Netflix, Amazon Prime Video, Hulu) offer a mix of their own and licensed content.
+One can also find examples of similar behavior outside the platform setting, too.
+For example BMW is preparing to offer cars directly to consumers in the US, competing with its own dealership network.
+
+As deciding the rules of the game and competing in it at the same time gives rise to some obvious concerns, policymakers have been paying a closer look at these platforms in the recent years.
+Various pieces of legislation have been proposed to regulate, or even ban e-commerce platforms from selling their own products \parencite[][]{phartiyal_2019,reynolds_2022,eu-2022}.
+Furthermore, one of the most prominent ongoing antitrust cases (in 2022--2023), Microsoft attempting to acquire the video game publisher Activision/Blizzard for a sum of 69 billion USD, is also a case of a platform becoming increasingly more hybrid.
+This merger would not only increase market concentration on the software side of the video game industry, but might also have further implications for bargaining power between Microsoft and the other game developers.
+The deal currently is investigated by multiple antitrust authorities, including the US Federal Trade Commission, the European Commission, and the UK Competition and Markets Authority \parencite{livni_merced_2023}.
+
+In parallel to the increased regulatory interest, the academic literature has also been steadily growing on the topic of hybrid platforms.
+\textcite{hagiu2022should} investigates how practices, such as self-preferencing and steering can distort competition on hybrid platforms.
+They argue that when such behavior is regulated, the platform selling its own products can be beneficial for consumers.
+On the contrary, \textcite[]{anderson2021hybrid} find that even in the absence of such behavior, allowing hybrid operation might have negative consequences due to platforms having an incentive to exclude competitors from the market.
+\textcite[postnote]{gutierrez2021welfare} shows that general conclusions are hard to draw, and welfare effects are platform and product specific.
+
+This paper aims to contribute to this discussion by examining an important, but so far underexplored aspect of platforms: the bargaining power disparity between them and the other market participants, and how this disparity is affected by the platforms' hybrid operation.
+In particular, I propose an analytically tractable framework which captures many important aspects of bargaining between one large and a continuum of small players, and apply it to the setting of a hybrid platform facing a continuum of potential entrants.
+The results show that, in the presence of bargaining, hybrid operation can indeed have negative welfare consequences for consumers.
+This result is particularly striking in this otherwise distortion-free\footnote{
+    In the benchmark model without bargaining, the platform's extent of hybrid operation does not affect consumer welfare.
+} setting. 
+The intuition is that hybrid operation increases the platform's bargaining power due to having its own products.
+This in turn leads to a higher entry fee, leading to fewer entrants, which in turn leads to lower consumer surplus.
+These observations highlight a so-far overlooked aspect of hybrid platforms that policymakers should be aware of.
+
+The closest paper to this one is \textcite{anderson2021hybrid}, which utilizes a similar model and reaches similar conclusions.
+I adapt many of the main features of thir model with a couple of crucial differences.
+Instead of the platform setting a percentage entry fee and being able to commit to it, I assume that (1) platforms charge a lump-sum entry fee and that (2) this entry fee is the result of a negotiation process\footnote{
+    The bargaining process is modeled using a concept from cooperative game theory, namely the Shapley-value.
+    This allows for a tractable analysis while at the same time capturing many of the important features of bargaining.
+    Examples of this approach in the industrial organization literature include \textcite{montez2007downstream}, as well as \textcite{hart1990property}, \textcite{levy1997individual}, \textcite{inderst2003bargaining} and \textcite{brugemann2019intra} among others.
+}
+between the platform and the entrants.
+The second point is a novelty not only compared to \textcite{anderson2021hybrid}, but also to the existing literature on hybrid platforms.
+Furthermore, in contrast to \textcite{hagiu2022should}, this model is free from any distortive behavior, such as self-preferencing or steering, and the negative results are purely driven by the platform's bargaining position.
+
+This paper is also related to various other strands of the industrial organization literature.
+In broad terms, it belongs to research agenda on understanding platforms and their role in the economy \parencite[e.g.][]{rochet2003platform,hagiu2004optimal,armstrong2006competition,evans2011platform,lee2014competing}.
+Furthermore, it is somewhat adjacent to the literature on the importance of exclusive content \parencite[e.g.][]{hagiu2011exclusivity,lee2013vertical,dou2014sell,weeds2016tv}, with the difference that instead of exclusive content giving an advantage against competing platforms, in this paper, own products provide an advantage over entrants.
+Somewhat more generally, many results and concepts of this paper are also applicable outside the context of (multi-sided) platforms.
 Certain structures, such as vertical relationships, or even traditional retail stores share a number of features with platforms (notably, the presence of a dominant, indispensable entity), and can be modeled in much the same way.
-Therefore, the results of this paper also contributes to the literature on those settings, such as retailers having their own private labels \parencite{steiner2004nature}, or vertical integration in upstream-downstream markets \parencite{hart1990vertical,aghion2006vertical}.
-It is particularly closely related to \textcite{de2005vertical} and \textcite{montez2007downstream} in which bargaining between the upstream and downstream firms take the center stage.
+Therefore, the methodology and results in this paper may also be of interest to researchers studying questions such as retailers having their own private labels \parencite{steiner2004nature} or vertical integration in upstream-downstream markets \parencite{hart1990vertical,aghion2006vertical}.
+\textcite{de2005vertical} and \textcite{montez2007downstream}, in which bargaining between the upstream and downstream firms take the center stage, are particularly closely related.
 
@@
 Such examples include the aforementioned \textcite{montez2007downstream}, as well as \textcite{hart1990property}, \textcite{levy1997individual}, \textcite{inderst2003bargaining} and \textcite{brugemann2019intra} among others.
-In contrast to the majority of those, I utilize an oceanic game (a continuum of small players instead of a finite number), and demonstrate that this can considerably simplify the analysis in certain cases.
+In contrast to the majority of those, which focus on games with a finite number of players, I utilize an oceanic game (a continuum of small players instead of a finite number), and demonstrate that this can considerably simplify the analysis in certain cases.
+Therefore, the modeling approach presented in this paper may be of use in other settings as well.
 

### 2023-04-11 src/paper/application.tex
Fix stuff in intro

@@
 
-Platforms have a number of unique features, which make them different from more traditional market structures.
+Platforms have a number of unique features that make them different from more traditional market structures.
 The most prominent of those are multi-sidedness and network effects, which most of the early literature \parencite[for an overview, see][]{rochet2006two} and policy debate \parencite[e.g.][]{fletcher2021consumer,calvano2021market} has focused on.
-However, in the more recent years, another important and potentially concerning behavior has been getting more attention: the hybrid operation of platforms.
+However, in the more recent years, another important and potentially concerning aspect has been getting more attention: the hybrid operation of certain platforms.
 Essentially, this means that platforms act as an intermediary (deciding the rules) and a market participant (competing with other entrants) at the same time.
@@
 While hybrid platforms are not a completely new phenomenon, they are becoming more and more common in various industries.
-Perhaps the most prominent example is Amazon, which on the one hand selling its own products, and at the same time is hosting  large number of third-party sellers.
-Examples abound in other industries, as well.
-For example, all of the largest digital distribution platforms for computer and smartphone applications (such as Google Play, Apple App Store or Microsoft Store) sell applications products by the platform owner itself besides their third party offerings.
-In the video game industry, platform owners owning their own game studios is the standard.
+Perhaps the most prominent example is Amazon, which, on the one hand sells its own products, and at the same time hosts ax large number of third-party sellers.
+However, examples abound in other industries, as well.
+For example, each of the largest digital distribution platforms for computer and smartphone applications (Google Play, Apple App Store and Microsoft Store) sell their own applications besides their third party offerings.
+In the video game industry, platform owners studios and publishing games under their own brand is the standard.
 Many video streaming services (e.g. Netflix, Amazon Prime Video, Hulu) offer a mix of their own and licensed content.
 One can also find examples of similar behavior outside the platform setting, too.
-For example BMW is preparing to offer cars directly to consumers in the US, competing with its own dealership network.
-
-As deciding the rules of the game and competing in it at the same time gives rise to some obvious concerns, policymakers have been paying a closer look at these platforms in the recent years.
+For example BMW is preparing to sell cars directly to consumers in the US, competing with its dealership network.
+
+As deciding the rules of the game and competing in it at the same time gives rise to some obvious concerns, policymakers have been paying increasingly close attention to these platforms in the recent years.
 Various pieces of legislation have been proposed to regulate, or even ban e-commerce platforms from selling their own products \parencite[][]{phartiyal_2019,reynolds_2022,eu-2022}.
-Furthermore, one of the most prominent ongoing antitrust cases (in 2022--2023), Microsoft attempting to acquire the video game publisher Activision/Blizzard for a sum of 69 billion USD, is also a case of a platform becoming increasingly more hybrid.
-This merger would not only increase market concentration on the software side of the video game industry, but might also have further implications for bargaining power between Microsoft and the other game developers.
-The deal currently is investigated by multiple antitrust authorities, including the US Federal Trade Commission, the European Commission, and the UK Competition and Markets Authority \parencite{livni_merced_2023}.
-
-In parallel to the increased regulatory interest, the academic literature has also been steadily growing on the topic of hybrid platforms.
-\textcite{hagiu2022should} investigates how practices, such as self-preferencing and steering can distort competition on hybrid platforms.
-They argue that when such behavior is regulated, the platform selling its own products can be beneficial for consumers.
-On the contrary, \textcite[]{anderson2021hybrid} find that even in the absence of such behavior, allowing hybrid operation might have negative consequences due to platforms having an incentive to exclude competitors from the market.
-\textcite[postnote]{gutierrez2021welfare} shows that general conclusions are hard to draw, and welfare effects are platform and product specific.
+Furthermore, one of the most prominent ongoing antitrust cases, Microsoft attempting to acquire the video game publisher Activision/Blizzard for a sum of 69 billion USD, is also a case of a platform becoming increasingly hybrid.
+This merger would not only increase market concentration on the software side of the video game industry, but might also have further implications for the competition between Microsoft as a platform owner and the other game developers.
+The deal is currently under investigation by multiple antitrust authorities, including the US Federal Trade Commission, the European Commission, and the UK Competition and Markets Authority \parencite{livni_merced_2023}.
+
+In parallel to the increasing regulatory interest, the academic literature has also been steadily growing on the topic of hybrid platforms.
+\textcite{hagiu2022should} investigate how practices, such as self-preferencing and steering can distort competition on hybrid platforms.
+They argue, however, that if such behavior is regulated, the platform selling its own products can be beneficial for consumers.
+In contrast to this positive result, \textcite[]{anderson2021hybrid} find that even in the absence of such behavior, allowing hybrid operation might have negative consequences due to platforms having an incentive to exclude competitors from the market.
+\textcite[]{gutierrez2021welfare} shows that general conclusions are hard to draw, and welfare effects are platform and product specific.
 
@@
 This result is particularly striking in this otherwise distortion-free\footnote{
-    In the benchmark model without bargaining, the platform's extent of hybrid operation does not affect consumer welfare.
+    In the benchmark model without bargaining, the platform's hybrid operation does not affect consumer welfare.
 } setting. 
-The intuition is that hybrid operation increases the platform's bargaining power due to having its own products.
-This in turn leads to a higher entry fee, leading to fewer entrants, which in turn leads to lower consumer surplus.
-These observations highlight a so-far overlooked aspect of hybrid platforms that policymakers should be aware of.
-
-The closest paper to this one is \textcite{anderson2021hybrid}, which utilizes a similar model and reaches similar conclusions.
-I adapt many of the main features of thir model with a couple of crucial differences.
+The intuition is that hybrid operation increases the platform's bargaining power against the sntrant sellers.
+This in turn leads to a higher entry fee, fewer entrants, then results in lower consumer surplus.
+These observations constitute a so-far overlooked aspect of hybrid platforms that policymakers should be aware of.
+
+The closest paper to this one is \textcite{anderson2021hybrid}, which utilizes a similar model and reaches similar conclusions, although through a different mechanism.
+I adapt many of the main features of their model with a couple of crucial differences.
 Instead of the platform setting a percentage entry fee and being able to commit to it, I assume that (1) platforms charge a lump-sum entry fee and that (2) this entry fee is the result of a negotiation process\footnote{
-    The bargaining process is modeled using a concept from cooperative game theory, namely the Shapley-value.
+    The bargaining process is modeled using a solution concept from cooperative game theory, namely the Shapley-value.
     This allows for a tractable analysis while at the same time capturing many of the important features of bargaining.
@@
 The second point is a novelty not only compared to \textcite{anderson2021hybrid}, but also to the existing literature on hybrid platforms.
-Furthermore, in contrast to \textcite{hagiu2022should}, this model is free from any distortive behavior, such as self-preferencing or steering, and the negative results are purely driven by the platform's bargaining position.
+Furthermore, in contrast to \textcite{hagiu2022should}, this model is free from any distortive behavior, such as self-preferencing or steering, and the negative results are purely driven by changes in the platform's bargaining position.
 
 This paper is also related to various other strands of the industrial organization literature.
-In broad terms, it belongs to research agenda on understanding platforms and their role in the economy \parencite[e.g.][]{rochet2003platform,hagiu2004optimal,armstrong2006competition,evans2011platform,lee2014competing}.
+For one, it belongs to the research agenda on understanding platforms and their role in the economy \parencite[e.g.][]{rochet2003platform,hagiu2004optimal,armstrong2006competition,evans2011platform,lee2014competing}.
 Furthermore, it is somewhat adjacent to the literature on the importance of exclusive content \parencite[e.g.][]{hagiu2011exclusivity,lee2013vertical,dou2014sell,weeds2016tv}, with the difference that instead of exclusive content giving an advantage against competing platforms, in this paper, own products provide an advantage over entrants.
-Somewhat more generally, many results and concepts of this paper are also applicable outside the context of (multi-sided) platforms.
+More generally, many results and concepts of this paper are also applicable outside the context of (multi-sided) platforms.
 Certain structures, such as vertical relationships, or even traditional retail stores share a number of features with platforms (notably, the presence of a dominant, indispensable entity), and can be modeled in much the same way.
@@
 Finally, this paper also belongs to the not too large set of models using concepts from cooperative game theory in an industrial organization setting.
-Such examples include the aforementioned \textcite{montez2007downstream}, as well as \textcite{hart1990property}, \textcite{levy1997individual}, \textcite{inderst2003bargaining} and \textcite{brugemann2019intra} among others.
+Such examples include the aforementioned \textcite{montez2007downstream}, as well as \textcite{hart1990property}, \textcite{levy1997individual}, \textcite{inderst2003bargaining} and \textcite{brugemann2019intra}, among others.
 In contrast to the majority of those, which focus on games with a finite number of players, I utilize an oceanic game (a continuum of small players instead of a finite number), and demonstrate that this can considerably simplify the analysis in certain cases.
 Therefore, the modeling approach presented in this paper may be of use in other settings as well.
+
+The rest of the paper is organized as follows.
+In \cref{sec:model}, I introduce a general version of the model.
+After that, \cref{sec:results} demonstrates results about bargaining outcomes one can derive even in this rather abstract setting.
+\Cref{sec:example} concretizes the model by assuming a specific demand system, and also presents a corresponding benchmark model without bargaining.
+Finally, \cref{sec:conclusion} summarizes the results and discusses possible future work.
 
@@
 \section{General results}
+\label{sec:results}
 
@@
 \section{Conclusion and future work}
+\label{sec:conclusion}
 

### 2023-04-14 src/paper/application.tex
Add a hard proof

@@
     \label{prop:aggregate_size_additive}
-    Let $f$ have the following, additive form:
+    Let the weight function be constant ($w(t) \equiv 1$).
+    % TODO: I think the weight function assumption is not necessary.
+    Furthermore, let $f$ have the following, additive form:
     \begin{align*}
@@
     where $\alpha, \beta > 0$.
-    Furthermore, assume that $g$ is twice differentiable and that $g'' < 0$.
+    Also assume that $g$ is twice differentiable and that $g'' < 0$.
     Then
@@
     \end{align*}
-
+    The derivative exists if the above expression is well-defined, i.e. $\frac{\partial \pi_F (N_P, N_F)}{\partial N_F} \neq I_F$.
     Remember from \cref{prop:share_of_fringe} that the numerator of this expression is negative under the condition $\frac{\partial^2 f(N_P, N_F)}{\partial N_P \partial N_F}$.
-    All we need to show to conclude the proof is that
+    Now all we need to show to conclude the proof is that
     \begin{align*}
@@
 
+\begin{proof}[Proof of \cref{prop:aggregate_size_additive}]
+    Assume by contradiction that $\frac{\partial N_F^*}{\partial N_P} \geq -\frac{\alpha}{\beta}$ for some $N_P'$.
+    Then, for $\forall K > 0$, $\exists \Delta \in (0, K)$ such that $N_F^*(N_P' + \Delta) \geq N_F^*(N_P') - \frac{\alpha}{\beta}\Delta$.
+For ease of notation, let us denote $N_P'' = N_P' + \Delta$, $N_F' = N_F^*(N_P')$ and $N_F'' = N_F^*(N_P'')$.
+
+    First, let us show that fringe profits are lower than total investment costs if $\bar N_F = N_F^*(N_P') - \frac{\alpha}{\beta}\Delta$.
+    In order to do this, consider this formulation of fringe profits:
+    \begin{align*}
+        \pi_F(N_P', N_F') &= f(N_P', N_F') - \int_0^1 w(s) f(N_P', t N_F') \dt \\
+        &= \int_0^1 t \frac{\partial f(N_P', n_F')}{\partial n_F} \bigg|_{n_F = t N_F'},
+    \end{align*}
+    which can be obtained by integration by parts.
+    Now let us use the functional form assumption $f(N_P, N_F) = g(\alpha N_P + \beta N_F)$ to obtain
+    \begin{align*}
+        \pi_F(N_P, N_F) = \int_0^1 t \underbrace{\frac{\partial}{\partial t}g(\alpha N_P + \beta t N_F)}_{\coloneq D(N_P, N_F)} \dt.
+    \end{align*}
+
+    Let us focus on the term $D(N_P, N_F)$.
+    First, calculate
+    \begin{align*}
+        D(N_P', N_F') = \beta N_F' g'(\alpha N_P' + \beta t N_F').
+    \end{align*}
+    Let us do the same for $D(N_P'', \bar{N}_F) = D(N_P' + \Delta, N_F - \frac{\alpha}{\beta} \Delta)$ to get
+    \begin{align*}
+        D(N_P'', \bar{N}_F) = \beta \bar{N}_F g'(\alpha N_P' + \beta t N_F' + \underbrace{\Delta \alpha (1-t)}_{> 0}).
+    \end{align*}
+    Substitute these expressions into $\pi_F$ to get
+    \begin{align*}
+        \pi_F(N_P', N_F') &= N_F' \beta \int_0^1 t g'(\alpha N_P' + \beta t N_F') \dt, \\
+        \pi_F(N_P'', \bar{N}_F) &= \bar{N}_F \beta \int_0^1 t g'(\alpha N_P' + \beta t N_F' + \Delta \alpha (1-t)) \dt.
+    \end{align*}
+    Finally, let the following hold:
+    \begin{align*}
+        \pi_F(N_P'', \bar{N}_F) - I_F \bar{N}_F &= \frac{\bar{N}_F}{N_F'}\left[\beta \int_0^1 t g'(\alpha N_P' + \beta t N_F' + \Delta \alpha (1-t)) \dt - I_F N_F' \right] \\
+        &< \frac{\bar{N}_F}{N_F'}\left[\beta \int_0^1 t g'(\alpha N_P' + \beta t N_F') \dt - I_F N_F' \right] \\
+        &= \frac{\bar{N}_F}{N_F'}\left[ \pi_F(N_P', N_F') - I_F N_F \right] \\
+        &= 0.
+    \end{align*}
+    The inequality is due to the concavity of $g$, and the final equality is the result of profits being zero in the equilibrium $(N_P', N_F')$.
+
+    All that remains to be shown is that $\pi_F(N_P'', N_F'') < N_F'' I_F$.
+    This is a consequence of the fact that, under \cref{ass:single_crossing}, $\pi_F$ is either concave or decreasing in $N_F$.
+    As a consequence, if it at some point ($\bar{N}_F$) dips below the linear function $N_F \mapsto I_F N_F$, it can never reach it again for any $N_F'' > \bar{N}_F$.
+    With this we arrive at a contradiction, as $(N_P'', N_F'')$ cannot be an equilibrium.
+
+    Therefore, the initial assumption that $\frac{\partial N_F^*}{\partial N_P} \geq -\frac{\alpha}{\beta}$ was wrong.
+    As we have from \cref{cor:fringe_entry} that $\frac{\partial N_F^*}{\partial N_P}$ exists, it must be the case that
+    \begin{align*}
+        \frac{\partial N_F^*}{\partial N_P} < \frac{\alpha}{\beta}
+    \end{align*}
+\end{proof}
+
 \end{document}

### 2023-04-14 src/paper/application.tex
Add proofs for remaining propositions (not lemma)

@@
 \begin{proposition}
+    \label{prop:demand_function}
     The demand for product $i$ of producer $T \in \{P, F\}$ is given by:
@@
 \begin{proposition}
+    \label{prop:optimal_profit}
     The profit maximizing price for product $Ti$ is
@@
 \begin{proposition}
+    \label{prop:equilibrium_aggregate}
     If entry costs $I_F$ and $F_F$ are low enough, the equilibrium size of the aggregate is
@@
 \begin{proposition}
+    \label{prop:optimal_entry_fee}
     The optimal entry fee is
@@
 \begin{proposition}
+    \label{prop:platform_profits_bargaining}
     The platform's total profits are
@@
 
+\begin{proof}[Proof of \cref{prop:demand_function}]
+    See Theorem 1 in \textcite{anderson2021hybrid}.
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:optimal_profit}]
+    The profit function for product $Ti$ is the following:
+    \begin{align*}
+        \pi^v_{Ti}(p_{Ti}) &= (p_{Ti} - c_T) x_{T_i}(p_{Ti}) \\
+        &= (p_{Ti} - c_T) \frac{\exp\left( \frac{v_T - p_{Ti}}{\mu} \right)}{A}.
+    \end{align*}
+    Note that $A$ is not influenced by changes in $p_{Ti}$, as $A$ is an integral and $p_T$ is only changed on a zero-measure (singleton) set.
+    Therefore, let calculate the first order condition while treating $A$ as a constant:
+    \begin{align}
+        \label{eq:foc_profit}
+        \mu \frac{\exp\left( \frac{v_T - p_{Ti}}{\mu} \right)}{A} \left[ \frac{p_T - c_T}{\mu} - 1 \right] = 0.
+    \end{align}
+    Also note that $\pi_{Ti}(p_{Ti})$ is strictly concave, so the FOC is sufficient for optimality.
+
+    Now simply rearrange \cref{eq:foc_profit} to obtain
+    \begin{align*}
+        p_{Ti}^* = c_T + \mu
+    \end{align*}
+    and substitute it into the profit function to get
+    \begin{align*}
+        \pi_{Ti}^{v*} = \mu \frac{\exp \left( \frac{v_T - c_T - \mu}{\mu} \right)}{A}.
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:equilibrium_aggregate}]
+    From \cref{prop:optimal_profit}, the variable profit of each fringe firm is $\pi_{Fi}^{v*} = \mu V_F / A$.
+    Total profit after entry fees and investment costs is therefore $\pi_{Fi}^{t*} = \mu V_F / A - I_F - F_F$.
+    Under free entry, total profits are zero:
+    \begin{align*}
+        0 = \pi_{Fi}^{t*} = \mu V_F / A - F_F - I_F.
+    \end{align*}
+    Simple rearrangement gives the formula we are looking for,
+    \begin{align*}
+        A = \mu \frac{V_F}{F_F + I_F},
+    \end{align*}
+    and substituting in $A = N_P V_P + N_F V_F + 1$ yields the equilibrium number of fringe firms,
+    \begin{align*}
+        N_F = \frac{\mu}{F_F + I_F} - N_P \frac{V_P}{V_F} - \frac{1}{V_F}.
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:optimal_entry_fee}]
+    The total profit function of the platform is the following:
+    \begin{align*}
+        \pi_P^t &= \pi_P^v + I_F N_F \\
+        &= \mu \frac{N_P V_P}{F_F + I_F} + F_F \left[ \frac{\mu}{F_F + I_F} - N_P \frac{V_P}{V_F} - \frac{1}{V_F} \right].
+    \end{align*}
+    The function is strictly concave in $F_F$, so the first order condition is sufficient for optimality in the case of an interior solution.
+    Assume that $N_F$ is high enough that the optimum is indeed interior.
+    Then the FOC is
+    \begin{align*}
+        \frac{\mu I_F V_F - (F_F + I_F)^2}{V_F (F_F + I_F)^2} = 0.
+    \end{align*}
+    Rearranging it gives the optimal entry fee
+    \begin{align*}
+        F_F^* = \sqrt{\mu I_F V_F} - I_F,
+    \end{align*}
+    and substituting it into the profit function leads to
+    \begin{align*}
+        \pi_P^{*t} = \mu - 2\sqrt{\frac{I_F \mu}{V_F}} + \frac{I_F}{V_F} (N_P V_P + 1).
+    \end{align*}
+    Finally, note that
+    \begin{align*}
+        \pi_P^{*t} \geq \mu \frac{N_P V_P}{N_P V_P + 1},
+    \end{align*}
+    i.e., the profit that the platform could achieve by excluding the fringe completely.
+    Therefore, the optimum is indeed interior whenever $F_F$ is low enough
+
+    Now consider the case when $F_F$ is so large that $F_F^*$ would lead to no fringe entry.
+    In that case, the platform's only source of profit is selling its own products, and thus
+    \begin{align*}
+        \pi_P^{t} = \pi_P^{v} = \mu \frac{ N_P V_P}{N_P V_P + 1}.
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:platform_profits_bargaining}]
+    Simply integrate the total industry profit function with respect to the mass of fringe entrants obtain the platform's share of the pie:
+    \begin{align*}
+        \pi^t_P &= \int_0^1 f(N_P, sN_F) \ds \\
+        &= \mu \int_0^1 \frac{N_P V_P + s N_F V_F}{N_P V_P + s N_F V_F + 1} \ds \\
+        &= \mu \left[ 1 - \frac{\log \left(1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} \right].
+    \end{align*}
+    The fringe's share is just the remainder,
+    \begin{align*}
+        f(N_P, N_F) - \int_0^1 f(N_P, sN_F) \ds = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right]
+    \end{align*}
+    Finally, remember that the investment cost of the fringe is fixed at the bargaining stage, and is therefore not included in the bargaining outcome.
+    Therefore, the total profits of the complete fringe are
+    \begin{align*}
+        \pi^t_P = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F N_F.
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of \cref{lem:profit_assumptions}]
+
+\end{proof}
+
 \end{document}

### 2023-04-16 src/presentation/topics_talk.qmd
Start working on topics presentation

---
title: "Hybrid platforms and bargaining"
author: "Martin Stancsics"
format:
    revealjs:
        embed-resources: true
        html-math-method: mathjax
        transition: fade
        touch: true
        toc: true
        toc-depth: 1
        toc-title: Agenda
        slide-number: c
        progress: true
        controls: false
        theme:
         - default
         - css/custom.scss
        include-in-header:
         - js/mathjax-settings.html
bibliography: references.bib
---

# Introduction

<style>
    ul li li {
        font-size: 0.75em;
        line-height: 1.2em;
    }
</style>

### 2023-04-16 src/presentation/topics_talk.qmd
Add motivation

@@
 </style>
+
+## Motivation
+
+::: {.highlight-block}
+Examine the bargaining power implications of hybrid platforms and its welfare consequences
+:::
+
+::: {.fragment}
+ - Hybrid platform
+    - Getting more and more common
+    - Seemingly obvious concerns and high-profire competition policy cases
+    - Comparatively little reserach
+:::
+::: {.fragment}
+ - Bargaining between participants is rather overlooked in platform settings
+   - Most papers assume take-it-or-leave-it offers
+:::
+
+::: {.notes}
+
+:::
+
+## Main ideas
+
+ - Use the Shapley-value instead of an extensive-form bargaining model
+    - Analytically more tractable
+    - Has bargaining interpretation [e.g. @hart1996bargaining; @gul1989bargaining]
+    - Has precedents in the IO literature [e.g. @hart1990property; @montez2007downstream]
+ - Abstract away from all frictions
+    - Allows me to focus on the bargaining channel
+    - Offers a good benchmark model
+ - Focus on continuum of small players case for tractability
+    - Good approximation of the finite player case even for not too many players
+    - Results have a nice geometric interpretation
+
+## References
+
+::: {#refs}
+:::

### 2023-04-16 src/presentation/topics_talk.qmd
Add a preview of results to the introduction

@@
 
+## Preview of results
+
+::: {.fragment}
+ - The effects of hybrid platforms depend on the substitutability of the products
+   - When they are substitutes, it increases the platform's profit share and decreases the fringe's profits
+   - In the presence of an investment cost, it leads to lower fringe entry
+   - With Logit-demand, hybrid operation leads to welfare losses
+:::
+::: {.fragment}
+ - This modeling strategy seems promising
+   - The model is surprisingly tractable
+   - Quite general results can be obtained
+:::
+
 ## References

### 2023-04-19 src/presentation/topics_talk.qmd
Add model section to the topics talk

@@
 
+# Model
+
+## Players
+
+::: {.fragment}
+ - One platform: $P$
+   - Without the platform, no value can be created
+   - Might have its own products (hybrid mdoe)
+:::
+::: {.fragment}
+ - A continuum of potential fringe entrants: $F_i, i \in \mathbb{R}_0^+$
+   - Infinitesimal size
+   - Have one product each
+   - Can only sell through the platform
+:::
+
+## Production
+
+Reduced-form approach: assume some function for total profit:
+
+::: {.fragment}
+$$
+f(N_P, N_F)
+$$
+:::
+
+::: {.fragment}
+ - $N_P$ is the number of platform products
+ - $N_F$ is the number of fringe products/firms
+ - Assume that $f$ is increasing in both arguments
+:::
+
+## Profit sharing
+
+ - Platform gets $$ \pi_P(N_P, N_F) = \int_0^1 w(s) f(N_P, sN_F) \mathrm{d}s $$
+ - Fringe gets the rest
+
+::: {.fragment}
+ - Based on the Shapley-value 
+   - Bargaining interpretation [e.g. @hart1996bargaining; @gul1989bargaining]
+   - Precedents in the IO literature [e.g. @hart1990property; @montez2007downstream]
+ - $w(s)$ is a weighting function with $\int_0^1 w(s) \mathrm{d}s = 1$
+   - Related to the weighted value for a certain class of functions
+:::
+
+## Some simple comparative statics
+
+::::: {.columns}
+
+:::: {.column width="40%"}
+
+::: {.fragment fragment-index=1}
+ - The platform likes being hybrid
+$$
+\small
+\frac{\partial \pi_P(N_P, N_F)}{\partial N_P} > 0
+$$
+:::
+::: {.fragment fragment-index=2}
+ - It depends™ for the fringe
+$$
+\begin{align*}
+\small\mathrm{sign} \left( \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} \right) = \\
+\small\mathrm{sign} \left( \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} \right)
+\end{align*}
+$$
+:::
+
+::::
+
+:::: {.column width="60%"}
+
+::: {.r-stack}
+
+::: {.fragment fragment-index=1}
+
+:::
+::: {.fragment fragment-index=2}
+
+:::
+
+:::
+
+::::
+
+:::::
+
+## Entry and equilibrium
+
+Now let us endogeneize the number of fringe entrants!
+
+::: {.fragment}
+ - Unlimited number of potential entrants
+:::
+::: {.incremental}
+ - Timing
+    - Hybrid mode is exogeneously determined $\to N_P$
+    - Each fringe firm decides whether to invest at cost $I_F$ $\to N_F$
+    - Platform and firms produce and sell products $\to f(N_P, N_F)$
+    - Profits are shared according to previous rule $\to \pi_P(N_P, N_F), \pi_F(N_P, N_F)$
+:::
+
+## Equilibrium
+
+::: {.incremental}
+ - Free entry equilibrium: fringe firms make zero net profits
+   $$ \pi_F(N_P, N_F^*) = I_F N_F^* $$
+ - In order to guarantee uniqueness, let us assume
+   $$
+   \scriptsize
+   \begin{gather*}
+       f'_{n_F} (N_P, N_F) < \int_0^1 s w(s) f'_{n_F} (N_P, s N_F) \mathrm{d}s \\
+       \text{or} \\
+       f''_{n_F} (N_P, N_F) < \int_0^1 s^2 w(s) f''_{n_F} (N_P, s N_F) \mathrm{d}s.
+   \end{gather*}
+   $$
+     - Holds for certain interesting cases, such as the example application
+:::
+
+## Equilibrium comparative statics
+
+::::: {.columns}
+
+:::: {.column width="40%"}
+
+::: {.fragment fragment-index=1}
+ - Hybrid mode reduces fringe entry
+$$
+\small
+\frac{\partial N_F^*}{\partial N_P} < 0
+$$
+:::
+::: {.fragment fragment-index=2}
+ - And, under certain conditions, total profits
+$$
+\small\text{Let } f(N_P, N_F) = g(\alpha N_P + \beta N_F)
+$$
+$$
+\small\text{Then } \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}
+$$
+:::
+
+::::
+
+:::: {.column width="60%"}
+
+::: {.r-stack}
+
+::: {.fragment fragment-index=1}
+
+:::
+::: {.fragment fragment-index=2}
+
+:::
+
+:::
+
+::::
+
+:::::
+
+# More concrete example
+
+# Summary
+
 ## References

### 2023-04-19 src/presentation/topics_talk.qmd
Add example with benchmark case

@@
 
+## Demand
+
+::: {.incremental}
+ - Follow @anderson2021hybrid
+ - Unit mass of customers, each choosing one product maximizing $$u_{ij}^T = v^T - p_i^T + \mu \epsilon_{ij}^T$$
+   - $T \in \{P, F, 0\}$
+   - Unit mass of outside options at price $p_i^0 = 0$
+   - $v_T$: value of the product
+   - $\mu$: degree of horizontal differentiation
+   - $\epsilon_{ij}^T \sim \mathrm{Gumbel}(0, 1)$: taste shocks
+:::
+
+## Demand
+
+::: {.fragment}
+Logit-like demand:
+$$
+x_{Ti} = \frac{\exp\left( \frac{v_T - p_{Ti}}{\mu} \right)}{A}
+$$
+:::
+::: {.fragment}
+where
+$$
+A = \int_0^{N_F} \exp\left( \frac{v_F - p_{Fi}}{\mu} \right) \mathrm{d}i + \int_0^{N_P} \exp\left( \frac{v_P - p_{Pi}}{\mu} \right) \mathrm{d}i + 1
+$$
+:::
+
+## Production
+::: {.fragment}
+ - Assume that the platform prices its products as if they were made by seperate, competitive sellers
+   - Possible interpretation: profit-maximizing subsidiaries
+   - More importantly: provides a nice benchmark
+:::
+::: {.fragment}
+ - The optimal price is an additive markup rule:
+ $$
+ \begin{align*}
+ p^*_{Ti} &= c_T + \mu \\
+ \pi^{v*}_{Ti} &= \mu \frac{\exp \left( \frac{v_T - c_T - \mu}{\mu} \right)}{A}
+ \end{align*}
+ $$
+:::
+::: {.fragment}
+ - The optimal price is an additive markup rule:
+ $$
+ \begin{align*}
+ p^*_{Ti} &= c_T + \mu \\
+ \pi^{v*}_{Ti} &= \mu \frac{\exp \left( \frac{v_T - c_T - \mu}{\mu} \right)}{A}
+ \end{align*}
+ $$
+:::
+
+## Entry and equilibrium
+
+I consider two cases:
+
+::: {.incremental}
+ - **Benchmark**<br>platform can commit to any lump-sum fee $F_F$
+ - **Bargaining**<br>total profits are shared according to the Shapley-value-based rule
+:::
+
+## Benchmark equilibrium
+
+::: {.incremental}
+ - Optimal entry fee is independent of $N_P$:
+   $$ F_F^* = \sqrt{\mu I_F V_F} - I_F $$
+ - Size of the aggregate is independent* of $N_P$:
+   $$ A^* = \sqrt{\frac{\mu V_F}{I_F}} $$
+ - Consumer welfare is also independent* of $N_P$:
+   $$ CS^* \propto \log(A^*) $$
+:::
+
 # Summary

### 2023-04-19 src/presentation/topics_talk.qmd
Add bargaining equilibrium

@@
 ::: {.fragment fragment-index=2}
- - And, under certain conditions, total profits
-$$
-\small\text{Let } f(N_P, N_F) = g(\alpha N_P + \beta N_F)
-$$
+ - And, under certain conditions, total profits: if $\small f(N_P, N_F) = g(\alpha N_P + \beta N_F)$ and $g'' < 0$
 $$
@@
    $$ A^* = \sqrt{\frac{\mu V_F}{I_F}} $$
- - Consumer welfare is also independent* of $N_P$:
+ - **Consumer surplus** is also **independent*** of $N_P$:
    $$ CS^* \propto \log(A^*) $$
 :::
+
+## Bargaining equilibrium
+
+::: {.incremental}
+ - Total profits as a function of entrants have a simple form:
+ $$
+ f(N_P, N_F) = \mu \frac{n V_F + N_P V_P}{n V_F + N_P V_P + 1}
+ $$
+   - Satisfies the assumption for unique equilibrium
+   - Has the form $f(N_P, N_F) = g(\alpha N_P + \beta N_F)$
+   - $g$ is concave
+ - Therefore,
+ $$
+ \frac{\partial N_F^*}{\partial N_P} < -\frac{V_P}{V_F}
+ $$
+:::
+
+## Bargaining equilibrium
+
+::: {.incremental}
+ - Equilibrium aggregate and total profits are decreasing in $N_P$
+ $$
+ \frac{\partial A^*}{\partial N_P} < 0
+ $$
+   - Platform profits are increasing in $N_P$, though
+ - **Consumer surplus** is also **decreasing** in $N_P$
+ $$
+ \frac{\partial CS^*}{\partial N_P} < 0
+ $$
+:::
+
+## Results graphically
 

### 2023-04-19 src/presentation/topics_talk.qmd
Add summary

@@
 ::: {.fragment fragment-index=2}
- - And, under certain conditions, total profits: if $\small f(N_P, N_F) = g(\alpha N_P + \beta N_F)$ and $g'' < 0$
+ - And, under certain conditions, total profits: if $\small f(N_P, N_F) = g(\alpha N_P + \beta N_F)$, $w(s) \equiv 1$ and $g'' < 0$
 $$
@@
 
+## Summary
+
+::: {.fragment}
+ - **Tractable model** of hybrid platforms in which **bargaining** plays a key role
+   - Applicable to other settings, too (e.g. vertical markets, franchises)
+:::
+::: {.fragment}
+ - Highlight an important aspect if hybrid platforms
+   - **Hybridness increases bargaining power** against entrants
+   - This can have **negative welfare consequences**
+:::
+::: {.fragment}
+ - Policy implications for such markets
+   - Amazon operating in hybrid mode
+   - Microsoft acquiring Activision/Blizzard for $68bn
+:::
+
+## Future directions
+
+::: {.fragment}
+ - In this paper
+   - Endogenenize hybridness ($N_P$)
+   - Relax separate pricing assumption
+   - Alternative benchmarks (e.g. exogeneous split)
+:::
+::: {.fragment}
+ - Longer term
+   - Endogeneize consumer entry (possibly with them engaging in the negotiation)
+   - Apply this bargaining model to other, similar settings
+:::
+
+# Thank you {.unnumbered .unlisted}
+
 ## References

### 2023-04-19 src/presentation/topics_talk.qmd
Add related literature slide

@@
    - Quite general results can be obtained
+:::
+
+## Related literature
+
+::: {.incremental}
+ - **Hybrid platform markets**<br>
+ @anderson2021hybrid, @gutierrez2021welfare, @hagiu2022should
+ - Similarly structured markets
+   - Private labels in retail [@steiner2004nature]
+   - Vertical integration [@hart1990vertical; @de2005vertical; @montez2007downstream]
+ - Cooperative games in IO<br>
+ @hart1990property, @levy1997individual, @inderst2003bargaining, @montez2007downstream
+
 :::

### 2023-04-19 src/presentation/topics_talk.qmd
Add manim grraph with simple comparative stats

@@
 
-::: {.fragment fragment-index=1}
+::: {.fragment fragment-index=2}
  - The platform likes being hybrid
@@
 :::
-::: {.fragment fragment-index=2}
+::: {.fragment fragment-index=4}
  - It depends™ for the fringe
@@
 ::: {.fragment fragment-index=1}
-
+  <video data-autoplay src="../../out/manim_figures/videos/comparative_n_p_on_shares/800p60/sections/draw_graph.mp4" />
 :::
 ::: {.fragment fragment-index=2}
-
+  <video data-autoplay src="../../out/manim_figures/videos/comparative_n_p_on_shares/800p60/sections/cross_derivative_positive.mp4" />
+:::
+::: {.fragment fragment-index=3}
+  <video data-autoplay src="../../out/manim_figures/videos/comparative_n_p_on_shares/800p60/sections/back_to_original.mp4" />
+:::
+::: {.fragment fragment-index=4}
+  <video data-autoplay src="../../out/manim_figures/videos/comparative_n_p_on_shares/800p60/sections/cross_derivative_negative.mp4" />
 :::

### 2023-04-19 src/manim_figures/comparative_n_p_on_shares.py

@@ -1,0 +1,112 @@
+from manim import *
+from numpy import sqrt, log1p, exp
+
+
+class Baseline(Scene):
+
+    def construct(self):
+
+        self.next_section("draw_graph")
+
+        self.camera.background_color = WHITE
+        Text.set_default(color=BLACK)
+        Line.set_default(color=BLACK)
+        Tex.set_default(color=BLACK)
+        Brace.set_default(color=BLACK)
+        ParametricFunction.set_default(color=BLACK)
+
+        # Create plane
+        ax = Axes(
+            x_range=[0, 1, 0.05],
+            y_range=[0, 1, 0.05],
+            x_length=10,
+            y_length=10
+        )
+        ax_label = ax.get_axis_labels(x_label=r"t")
+
+        # Destinations
+        f_orig = ax.plot(lambda x: log1p(x))
+        f_positive = ax.plot(lambda x: x)
+        f_negative = ax.plot(lambda x: log1p(exp(1) - 2 + x))
+
+        f_orig_label = ax.get_graph_label(f_orig, "f(N_P, N_F)", direction=RIGHT)
+        f_positive_label = ax.get_graph_label(f_positive, "f(N_P', N_F)", direction=RIGHT)
+        f_negative_label = ax.get_graph_label(f_negative, "f(N_P', N_F)", direction=RIGHT)
+
+        top_orig = ax.plot(lambda x: log1p(1))
+        top_alt = ax.plot(lambda x: 1)
+
+        area_orig = ax.get_area(f_orig, (0, 1), opacity=0.5, color=BLUE)
+        area_fringe_orig = ax.get_area(f_orig, (0, 1), bounded_graph=top_orig, opacity=0.5, color=RED)
+        area_positive = ax.get_area(f_positive, (0, 1), opacity=0.5, color=BLUE)
+        area_fringe_positive = ax.get_area(f_positive, (0, 1), bounded_graph=top_alt, opacity=0.5, color=RED)
+        area_negative = ax.get_area(f_negative, (0, 1), opacity=0.5, color=BLUE)
+        area_fringe_negative = ax.get_area(f_negative, (0, 1), bounded_graph=top_alt, opacity=0.5, color=RED)
+
+        # Dashed placeholders
+        def get_dashed_version(obj):
+            dashed = obj.copy()
+            dashed.set_stroke(width=1, color=BLACK)
+            return DashedVMobject(dashed)
+        f_orig_dashed = get_dashed_version(f_orig)
[…]

### 2023-04-19 src/presentation/topics_talk.qmd
Add manim figure for equilibrium entry

@@
 
-::: {.fragment fragment-index=1}
- - Hybrid mode reduces fringe entry
+::: {.fragment fragment-index=3}
+ - If $\frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} < 0$, hybrid mode reduces fringe entry
+
+:::
+::: {.fragment fragment-index=4}
+ - And sometimes total profits, too
  $$
-\small
-\frac{\partial N_F^*}{\partial N_P} < 0
+ \begin{gather*}
+   g(\alpha N_P + \beta N_F), \\
+   g'' < 0, w(s) \equiv 1
+ \end{gather*}
  $$
-:::
-::: {.fragment fragment-index=2}
- - And, under certain conditions, total profits: if $\small f(N_P, N_F) = g(\alpha N_P + \beta N_F)$, $w(s) \equiv 1$ and $g'' < 0$
  $$
-\small\text{Then } \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}
+ \implies \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}
  $$
@@
 ::: {.fragment fragment-index=1}
-
+  <video data-autoplay src="../../out/manim_figures/videos/comparative_equilibrium_entry/800p60/sections/draw_graph.mp4" />
 :::
 ::: {.fragment fragment-index=2}
-
+  <video data-autoplay src="../../out/manim_figures/videos/comparative_equilibrium_entry/800p60/sections/mark_equilibrium.mp4" />
+:::
+::: {.fragment fragment-index=3}
+  <video data-autoplay src="../../out/manim_figures/videos/comparative_equilibrium_entry/800p60/sections/alternate_equilibrium.mp4" />
+:::
+::: {.fragment fragment-index=4}
+  <video data-autoplay src="../../out/manim_figures/videos/comparative_equilibrium_entry/800p60/sections/show_loss.mp4" />
 :::
@@
    - More importantly: provides a nice benchmark
-:::
-::: {.fragment}
- - The optimal price is an additive markup rule:
- $$
- \begin{align*}
- p^*_{Ti} &= c_T + \mu \\
- \pi^{v*}_{Ti} &= \mu \frac{\exp \left( \frac{v_T - c_T - \mu}{\mu} \right)}{A}
- \end{align*}
- $$
 :::

### 2023-04-19 src/manim_figures/comparative_equilibrium_entry.py

@@ -1,0 +1,103 @@
+from manim import *
+from numpy import log
+from scipy.optimize import fsolve
+
+
+def pi_F(N_P, N_F):
+    numerator = N_F * (N_F + N_P) - (N_F + N_P + 1) * (N_F + log(N_P + 1) - log(N_F + N_P + 1))
+    denominator = N_F * (N_F + N_P + 1)
+    return numerator / denominator
+
+
+class Baseline(Scene):
+
+    def construct(self):
+
+        self.next_section("draw_graph")
+
+        self.camera.background_color = WHITE
+        Text.set_default(color=BLACK)
+        Line.set_default(color=BLACK)
+        Tex.set_default(color=BLACK)
+        Brace.set_default(color=BLACK)
+        ParametricFunction.set_default(color=BLACK)
+
+        # Create plane
+        ax = Axes(
+            x_range=[0.005, 30, 0.1],
+            y_range=[0, 0.25, 0.01],
+            x_length=12,
+            y_length=8,
+            x_axis_config={"include_ticks": False},
+            y_axis_config={"include_ticks": False}
+        )
+        ax_label = ax.get_axis_labels(x_label=r"t")
+
+        N_P_0 = 0
+        N_P_1 = 0.5
+        I_F = 0.005
+
+        # Intersections
+        N_F_opt_0 = fsolve(lambda N_F: pi_F(N_P_0, N_F) - I_F * N_F, 20)[0]
+        N_F_opt_0_val = pi_F(N_P_0, N_F_opt_0)
+        N_F_opt_point_0 = ax.c2p(N_F_opt_0, N_F_opt_0_val)
+        N_F_opt_1 = fsolve(lambda N_F: pi_F(N_P_1, N_F) - I_F * N_F, 20)[0]
+        N_F_opt_1_val = pi_F(N_P_1, N_F_opt_1)
+        N_F_opt_point_1 = ax.c2p(N_F_opt_1, N_F_opt_1_val)
+
+        # Destinations
+        pi_F_orig = ax.plot(lambda x: pi_F(N_P_0, x), color=BLUE_D)
+        pi_F_alt = ax.plot(lambda x: pi_F(N_P_1, x), color=RED_D)
+        pi_F_orig_label = ax.get_graph_label(pi_F_orig, r"\pi_F(0, N_F)", direction=UP)
+        pi_F_alt_label = ax.get_graph_label(pi_F_alt, r"\pi_F(0.5, N_F)", direction=DOWN)
+
[…]

### 2023-04-19 src/manim_figures/comparative_n_p_on_shares.py

@@ -18,7 +18,7 @@ class Baseline(Scene):
         # Create plane
         ax = Axes(
             x_range=[0, 1, 0.05],
-            y_range=[0, 1, 0.05],
+            y_range=[0, 1.1, 0.05],
             x_length=10,
             y_length=10
         )
@@ -29,9 +29,9 @@ class Baseline(Scene):
         f_positive = ax.plot(lambda x: x)
         f_negative = ax.plot(lambda x: log1p(exp(1) - 2 + x))
 
-        f_orig_label = ax.get_graph_label(f_orig, "f(N_P, N_F)", direction=RIGHT)
-        f_positive_label = ax.get_graph_label(f_positive, "f(N_P', N_F)", direction=RIGHT)
-        f_negative_label = ax.get_graph_label(f_negative, "f(N_P', N_F)", direction=RIGHT)
+        f_orig_label = ax.get_graph_label(f_orig, "f(N_P, N_F)", direction=UP)
+        f_positive_label = ax.get_graph_label(f_positive, "f(N_P', N_F)", direction=UP)
+        f_negative_label = ax.get_graph_label(f_negative, "f(N_P', N_F)", direction=UP)
 
         top_orig = ax.plot(lambda x: log1p(1))
         top_alt = ax.plot(lambda x: 1)

### 2023-04-20 src/presentation/topics_talk.qmd
Add manim figure for results and appendix

@@
 
+::: {.r-stack}
+
+::: {.fragment fragment-index=1}
+  <video height="500" data-autoplay src="../../out/manim_figures/videos/equilibrium_outcomes/800p60/sections/draw_graph.mp4" />
+:::
+::: {.fragment fragment-index=1}
+  <video height="500" data-autoplay src="../../out/manim_figures/videos/equilibrium_outcomes/800p60/sections/draw_graph.mp4" />
+:::
+::: {.fragment fragment-index=1}
+  <video height="500" data-autoplay src="../../out/manim_figures/videos/equilibrium_outcomes/800p60/sections/draw_graph.mp4" />
+:::
+::: {.fragment fragment-index=1}
+  <video height="500" data-autoplay src="../../out/manim_figures/videos/equilibrium_outcomes/800p60/sections/draw_graph.mp4" />
+:::
+::: {.fragment fragment-index=1}
+  <video height="500" data-autoplay src="../../out/manim_figures/videos/equilibrium_outcomes/800p60/sections/draw_graph.mp4" />
+:::
+
+:::
+
 # Summary
@@
 :::
+
+# Appendix
+
+## Baseline model
+
+:::: {.columns}
+
+::: {.column width="100%"}
+
+Set of all players: $N = \{P, A_1, \dots, A_n\}$
+
+**Assumption**: the platform is the only way for firms to
+reach users and that all $n$ firms are identical
+$$
+v(C) = \begin{cases}
+   0                                           & \text{if } P \notin C \\
+   f\left(\frac{|C \setminus \{P\}|}{n}\right) & \text{otherwise}.
+\end{cases}
+$$
+$\forall\, C \subset N$.
+:::
+
+::::
+
+::: {.notes}
+ - Not only platforms. Also describes
+   - upstream-downstream setups
+   - generally any setting with an important large players and many identical small ones
+:::
+
+## Value of the platform
+
+:::: {.columns}
+
+::: {.column width="40%"}
+
+Characteristic function:
+$$
+\scriptsize
+v(C) = \begin{cases}
+   0 \;\text{ if } P \notin C \\
+   f\left(\frac{|C \setminus \{P\}|}{n}\right)
+\end{cases}
+$$
+
+::: {.fragment .fade-in fragment-index=2}
+Shapley value:
+$$
+\scriptsize
+\varphi_P^n(f) = \frac{1}{n+1} \sum_{k=0}^{n} f(k)
+$$
+:::
+::: {.fragment .fade-in fragment-index=5}
+$$
+\scriptsize
+\to \int_0^1 f(t) \, \mathrm{d}t
+$$
+:::
+
+:::
+
+::: {.column width="60%"}
+
+::: {.r-stack}
+
+::: {.fragment fragment-index=1}
+   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/draw_bars.mp4" />
+:::
+::: {.fragment fragment-index=2}
+   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/a_nof.mp4" />
+:::
+::: {.fragment fragment-index=3}
+   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/a_bench.mp4" />
+:::
+::: {.fragment fragment-index=4}
+   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/a_barg.mp4" />
+:::
+::: {.fragment fragment-index=6}
+   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/pi_p_all.mp4" />
+:::
+
+:::
+
+:::
+
+::::
+
+::: {.notes}
+ - Think of the previous figure with the orderings
+ - Main insight: each ordering with the platform at position $k$ has the same probability
+:::

### 2023-04-20 src/manim_figures/comparative_equilibrium_entry.py

@@ -19,6 +19,7 @@ class Baseline(Scene):
         Text.set_default(color=BLACK)
         Line.set_default(color=BLACK)
         Tex.set_default(color=BLACK)
+        MathTex.set_default(color=BLACK)
         Brace.set_default(color=BLACK)
         ParametricFunction.set_default(color=BLACK)
 
@@ -26,7 +27,7 @@ class Baseline(Scene):
         ax = Axes(
             x_range=[0.005, 30, 0.1],
             y_range=[0, 0.25, 0.01],
-            x_length=12,
+            x_length=14,
             y_length=8,
             x_axis_config={"include_ticks": False},
             y_axis_config={"include_ticks": False}

### 2023-04-20 src/manim_figures/equilibrium_entry.py

@@ -30,6 +30,7 @@ class Equilibrium(Scene):
         Text.set_default(color=BLACK)
         Line.set_default(color=BLACK)
         Tex.set_default(color=BLACK)
+        MathTex.set_default(color=BLACK)
         Brace.set_default(color=BLACK)
         ParametricFunction.set_default(color=BLACK)
 
@@ -37,7 +38,7 @@ class Equilibrium(Scene):
         ax = Axes(
             x_range=[0, 1.2, 0.05],
             y_range=[0, 0.7, 0.05],
-            x_length=12,
+            x_length=11,
             y_length=6
         )
         ax.shift(UP * 0.5)

### 2023-04-20 src/manim_figures/equilibrium_outcomes.py

@@ -1,0 +1,106 @@
+from manim import *
+import pandas as pd
+
+
+class Baseline(Scene):
+
+    def construct(self):
+
+        data = pd.read_csv("out/figures/equilibrium.csv")
+
+        self.next_section("draw_graph")
+
+        self.camera.background_color = WHITE
+        Text.set_default(color=BLACK)
+        Line.set_default(color=BLACK)
+        Tex.set_default(color=BLACK)
+        MathTex.set_default(color=BLACK)
+        Brace.set_default(color=BLACK)
+        ParametricFunction.set_default(color=BLACK)
+
+        # Create plane
+        ax = Axes(
+            x_range=[0, 1.5, 0.015],
+            y_range=[0, 2.5, 0.02],
+            x_length=11,
+            y_length=7,
+            x_axis_config={"include_ticks": False},
+            y_axis_config={"include_ticks": False},
+
+        )
+        x_ax_label, y_ax_label = ax.get_axis_labels(x_label=r"N_P", y_label=r"A^*(N_P)")
+
+        # Destiniations
+        A_noF =  (ax.plot_line_graph(
+            x_values=data["N_P"], y_values=data["A_noF"],
+            line_color=BLACK, add_vertex_dots=False
+        ))
+        A_bench = ax.plot_line_graph(
+            data["N_P"], data["A_bench"],
+            line_color=BLUE_D, add_vertex_dots=False
+        )
+        A_barg = ax.plot_line_graph(
+            data["N_P"], data["A"],
+            line_color=RED_D, add_vertex_dots=False
+        )
+
+        pi_P_noF = (ax.plot_line_graph(
+            data["N_P"], data["pi_P_noF"],
+            line_color=BLACK, add_vertex_dots=False
+        ))
+        pi_P_bench = ax.plot_line_graph(
+            data["N_P"], data["pi_P_bench"],
+            line_color=BLUE_D, add_vertex_dots=False
+        )
+        pi_P_barg = ax.plot_line_graph(
+            data["N_P"], data["pi_P"],
+            line_color=RED_D, add_vertex_dots=False
+        )
+
+        pi_P_noF_scaled = (ax.plot_line_graph(
+            data["N_P"], data["pi_P_noF"] * 3,
+            line_color=BLACK, add_vertex_dots=False
+        ))
+        pi_P_bench_scaled = ax.plot_line_graph(
+            data["N_P"], data["pi_P_bench"] * 3,
[…]

### 2023-04-20 src/presentation/topics_talk.qmd
Fix video placement

--- 2023-04-19 src/presentation/topics_talk.qmd
@@
 
+::: {.r-stack}
+
+::: {.fragment fragment-index=1}
+  <video height="500" data-autoplay src="../../out/manim_figures/videos/equilibrium_outcomes/800p60/sections/draw_graph.mp4" />
+:::
+::: {.fragment fragment-index=2}
+  <video height="500" data-autoplay src="../../out/manim_figures/videos/equilibrium_outcomes/800p60/sections/a_nof.mp4" />
+:::
+::: {.fragment fragment-index=3}
+  <video height="500" data-autoplay src="../../out/manim_figures/videos/equilibrium_outcomes/800p60/sections/a_bench.mp4" />
+:::
+::: {.fragment fragment-index=4}
+  <video height="500" data-autoplay src="../../out/manim_figures/videos/equilibrium_outcomes/800p60/sections/a_barg.mp4" />
+:::
+::: {.fragment fragment-index=5}
+  <video height="500" data-autoplay src="../../out/manim_figures/videos/equilibrium_outcomes/800p60/sections/pi_p_all.mp4" />
+:::
+
+:::
+
 # Summary
@@
 :::
+
+# Appendix
+
+## Baseline model
+
+:::: {.columns}
+
+::: {.column width="100%"}
+
+Set of all players: $N = \{P, A_1, \dots, A_n\}$
+
+**Assumption**: the platform is the only way for firms to
+reach users and that all $n$ firms are identical
+$$
+v(C) = \begin{cases}
+   0                                           & \text{if } P \notin C \\
+   f\left(\frac{|C \setminus \{P\}|}{n}\right) & \text{otherwise}.
+\end{cases}
+$$
+$\forall\, C \subset N$.
+:::
+
+::::
+
+::: {.notes}
+ - Not only platforms. Also describes
+   - upstream-downstream setups
+   - generally any setting with an important large players and many identical small ones
+:::
+
+## Value of the platform
+
+:::: {.columns}
+
+::: {.column width="40%"}
+
+Characteristic function:
+$$
+\scriptsize
+v(C) = \begin{cases}
+   0 \;\text{ if } P \notin C \\
+   f\left(\frac{|C \setminus \{P\}|}{n}\right)
+\end{cases}
+$$
+
+::: {.fragment .fade-in fragment-index=2}
+Shapley value:
+$$l 
+\scriptsize
+\varphi_P^n(f) = \frac{1}{n+1} \sum_{k=0}^{n} f(k)
+$$
+:::
+::: {.fragment .fade-in fragment-index=5}
+$$
+\scriptsize
+\to \int_0^1 f(t) \, \mathrm{d}t
+$$
+:::
+
+:::
+
+::: {.column width="60%"}
+
+::: {.r-stack}
+
+::: {.fragment fragment-index=1}
+   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/draw_bars.mp4" />
+:::
+::: {.fragment fragment-index=2}
+   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/add_brace.mp4" />
+:::
+::: {.fragment fragment-index=3}
+   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/more_firms.mp4" />
+:::
+::: {.fragment fragment-index=4}
+   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/continuous_approximation.mp4" />
+:::
+::: {.fragment fragment-index=6}
+   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/surplus_division.mp4" />
+:::
+
+:::
+
+:::
+
+::::
+
+::: {.notes}
+ - Think of the previous figure with the orderings
+ - Main insight: each ordering with the platform at position $k$ has the same probability
+:::

### 2023-04-20 src/presentation/topics_talk.qmd
Extend appendix

@@
 
+## The Shapley-value
+
+Each player gets their expected marginal contribution
+
+:::: {.columns}
+
+::: {.column width="50%"}
+::: {.r-stack}
+
+::: {.fragment}
+   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/draw_objects.mp4" />
+:::
+::: {.fragment}
+   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/value_P12.mp4" />
+:::
+::: {.fragment}
+   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/value_P21.mp4" />
+:::
+::: {.fragment}
+   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/value_2P1.mp4" />
+:::
+::: {.fragment}
+   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/value_1P2.mp4" />
+:::
+::: {.fragment}
+   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/value_12P.mp4" />
+:::
+::: {.fragment}
+   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/value_21P.mp4" />
+:::
+::: {.fragment}
+   <video data-autoplay src="../../out/manim_figures/videos/shapley_value_demo/800p60/sections/final.mp4" />
+:::
+
+:::
+:::
+
+::: {.column width="10%"}
+:::
+
+::: {.column width="40%"}
+Coalition | Profits
+----------|---------
+$\{P\}$     |  0
+$\{A_i\}$   | 1
+$\{A_1, A_2\}$  | 2
+$\{P, A_i\}$  | 3
+$\{P, A_1, A_2\}$  | 6
+:::
+
+::::
+
+::: {.notes}
+ - Most direct definition of Shapley value
+ - Closed-form expression
+ - Generally computationally expensive, but not in this case
+:::
+
 ## Baseline model

### 2023-04-20 src/manim_figures/comparative_equilibrium_entry.py
Fix axis labels

@@ -27,12 +27,12 @@ class Baseline(Scene):
         ax = Axes(
             x_range=[0.005, 30, 0.1],
             y_range=[0, 0.25, 0.01],
-            x_length=14,
+            x_length=12,
             y_length=8,
             x_axis_config={"include_ticks": False},
             y_axis_config={"include_ticks": False}
         )
-        ax_label = ax.get_axis_labels(x_label=r"t")
+        ax_label = ax.get_x_axis_label(r"t")
 
         N_P_0 = 0
         N_P_1 = 0.5

### 2023-04-20 src/manim_figures/corollary_comparative.py

@@ -12,6 +12,7 @@ class Baseline(Scene):
         Text.set_default(color=BLACK)
         Line.set_default(color=BLACK)
         Tex.set_default(color=BLACK)
+        MathTex.set_default(color=BLACK)
         Brace.set_default(color=BLACK)
         ParametricFunction.set_default(color=BLACK)
 
@@ -22,7 +23,7 @@ class Baseline(Scene):
             x_length=10,
             y_length=10
         )
-        ax_label = ax.get_axis_labels(x_label=r"t")
+        ax_label = ax.get_x_axis_label(r"t")
 
         self.play(Create(ax), Write(ax_label))
 

### 2023-04-20 src/presentation/topics_talk.qmd
Fix minor things

@@
     - Getting more and more common
-    - Seemingly obvious concerns and high-profire competition policy cases
+    - Seemingly obvious concerns and high-profile competition policy cases
     - Comparatively little reserach
@@
 ::: {.fragment}
- - Bargaining between participants is rather overlooked in platform settings
-   - Most papers assume take-it-or-leave-it offers
+ - Bargaining between participants is understudied in the platform setting
+   - Authors generally assume take-it-or-leave-it offers
 :::
@@
 
- - Use the Shapley-value instead of an extensive-form bargaining model
+::: {.fragment}
+ - Shapley-value based bargaining rule
     - Analytically more tractable
@@
     - Has precedents in the IO literature [e.g. @hart1990property; @montez2007downstream]
- - Abstract away from all frictions
+:::
+::: {.fragment}
+ - Abstract away all frictions
     - Allows me to focus on the bargaining channel
     - Offers a good benchmark model
- - Focus on continuum of small players case for tractability
+:::
+::: {.fragment}
+ - Focus on a continuum of small players case for tractability
     - Good approximation of the finite player case even for not too many players
     - Results have a nice geometric interpretation
+:::
 
@@
 ::: {.fragment}
- - The effects of hybrid platforms depend on the substitutability of the products
+ - The impacts of hybrid platforms depend on the substitutability of the products
    - When they are substitutes, it increases the platform's profit share and decreases the fringe's profits
-   - In the presence of an investment cost, it leads to lower fringe entry
-   - With Logit-demand, hybrid operation leads to welfare losses
+   - In the presence of investment costs, it can lead to lower fringe entry
+   - With Logit demand, hybrid operation leads to welfare losses
 :::
@@
 ::: {.fragment}
- - One platform: $P$
+ - One **platform**: $P$
    - Without the platform, no value can be created
@@
 ::: {.fragment}
- - A continuum of potential fringe entrants: $F_i, i \in \mathbb{R}_0^+$
-   - Infinitesimal size
+ - A continuum of potential **fringe entrants**: $F_i, i \in \mathbb{R}_0^+$
+   - Infinitesimally small
    - Have one product each
@@
 
-Reduced-form approach: assume some function for total profit:
+Reduced-form approach: assume some function for **total profit**:
 
@@
 
+::: {.fragment}
  - Platform gets $$ \pi_P(N_P, N_F) = \int_0^1 w(s) f(N_P, sN_F) \mathrm{d}s $$
  - Fringe gets the rest
-
+:::
 ::: {.fragment}
@@
 
-# More concrete example
+# Microfounding the profit function
 
@@
  - Follow @anderson2021hybrid
- - Unit mass of customers, each choosing one product maximizing $$u_{ij}^T = v^T - p_i^T + \mu \epsilon_{ij}^T$$
+ - Unit mass of customers, each choosing one product maximizing $$u_{ij}^T = v^T - p_i^T + \mu \varepsilon_{ij}^T$$
    - $T \in \{P, F, 0\}$
@@
    - $\mu$: degree of horizontal differentiation
-   - $\epsilon_{ij}^T \sim \mathrm{Gumbel}(0, 1)$: taste shocks
+   - $\varepsilon_{ij}^T \sim \mathrm{Gumbel}(0, 1)$: taste shocks
 :::
@@
    - Possible interpretation: profit-maximizing subsidiaries
-   - More importantly: provides a nice benchmark
+   - More importantly: "best case scenario"
 :::
@@
 ::: {.incremental}
- - **Benchmark**<br>platform can commit to any lump-sum fee $F_F$
+ - **Benchmark**<br>platform can commit to any lump-sum entry fee $F_F$
  - **Bargaining**<br>total profits are shared according to the Shapley-value-based rule
@@
  $$
- f(N_P, N_F) = \mu \frac{n V_F + N_P V_P}{n V_F + N_P V_P + 1}
+ f(N_P, N_F) = \mu \frac{N_F V_F + N_P V_P}{N_F V_F + N_P V_P + 1}
  $$
@@
 
-# Summary
+# Conclusion
 
@@
    - Endogeneize consumer entry (possibly with them engaging in the negotiation)
-   - Apply this bargaining model to other, similar settings
+   - Apply this bargaining rule to other, similar settings
 :::

### 2023-04-20 src/manim_figures/comparative_n_p_on_shares.py

@@ -12,6 +12,7 @@ class Baseline(Scene):
         Text.set_default(color=BLACK)
         Line.set_default(color=BLACK)
         Tex.set_default(color=BLACK)
+        MathTex.set_default(color=BLACK)
         Brace.set_default(color=BLACK)
         ParametricFunction.set_default(color=BLACK)
 
@@ -22,16 +23,16 @@ class Baseline(Scene):
             x_length=10,
             y_length=10
         )
-        ax_label = ax.get_axis_labels(x_label=r"t")
+        ax_label = ax.get_x_axis_label(r"s")
 
         # Destinations
         f_orig = ax.plot(lambda x: log1p(x))
         f_positive = ax.plot(lambda x: x)
         f_negative = ax.plot(lambda x: log1p(exp(1) - 2 + x))
 
-        f_orig_label = ax.get_graph_label(f_orig, "f(N_P, N_F)", direction=UP)
-        f_positive_label = ax.get_graph_label(f_positive, "f(N_P', N_F)", direction=UP)
-        f_negative_label = ax.get_graph_label(f_negative, "f(N_P', N_F)", direction=UP)
+        f_orig_label = ax.get_graph_label(f_orig, "f(N_P, sN_F)", direction=UP)
+        f_positive_label = ax.get_graph_label(f_positive, "f(N_P', sN_F)", direction=UP)
+        f_negative_label = ax.get_graph_label(f_negative, "f(N_P', sN_F)", direction=UP)
 
         top_orig = ax.plot(lambda x: log1p(1))
         top_alt = ax.plot(lambda x: 1)

### 2023-06-11 src/presentation/io_day.qmd
Add IO day presentation

--- 2023-04-20 src/presentation/topics_talk.qmd
@@
 title: "Hybrid platforms and bargaining"
-author: "Martin Stancsics"
+subtitle: "Swiss IO day 2023"
+author:
+  - name: Martin Stancsics
+    email: martin.stancsics@econ.uzh.ch
+    affiliations:
+      - name: University of Zürich
+date: 2023-06-16
+date-format: long
 format:

### 2023-06-11 src/presentation/io_day.qmd
Remove weighing

@@
 ::: {.incremental}
- - **Hybrid platform markets**<br>
- @anderson2021hybrid, @gutierrez2021welfare, @hagiu2022should
+ - Hybrid platform markets<br>
+ **@anderson2021hybrid**, @gutierrez2021welfare, @hagiu2022should
  - Similarly structured markets
@@
  - Cooperative games in IO<br>
- @hart1990property, @levy1997individual, @inderst2003bargaining, @montez2007downstream
+ @hart1990property, **@levy1997individual**, @inderst2003bargaining, **@montez2007downstream**
 
@@
 ::: {.fragment}
- - Platform gets $$ \pi_P(N_P, N_F) = \int_0^1 w(s) f(N_P, sN_F) \mathrm{d}s $$
+ - Players get their Shapley-values 
+   - Bargaining interpretation [e.g. @hart1996bargaining; @gul1989bargaining]
+   - Precedents in the IO literature [e.g. @hart1990property; @montez2007downstream]
+:::
+::: {.fragment}
+ - Platform gets $$ \pi_P(N_P, N_F) = \int_0^1f(N_P, sN_F) \mathrm{d}s $$
  - Fringe gets the rest
@@
 ::: {.fragment}
- - Based on the Shapley-value 
-   - Bargaining interpretation [e.g. @hart1996bargaining; @gul1989bargaining]
-   - Precedents in the IO literature [e.g. @hart1990property; @montez2007downstream]
- - $w(s)$ is a weighting function with $\int_0^1 w(s) \mathrm{d}s = 1$
-   - Related to the weighted value for a certain class of functions
+ - Can be extended with weighting (innate bargaining power)
 :::
@@
    \begin{gather*}
-       f'_{n_F} (N_P, N_F) < \int_0^1 s w(s) f'_{n_F} (N_P, s N_F) \mathrm{d}s \\
+       f'_{n_F} (N_P, N_F) < \int_0^1 s f'_{n_F} (N_P, s N_F) \mathrm{d}s \\
        \text{or} \\
-       f''_{n_F} (N_P, N_F) < \int_0^1 s^2 w(s) f''_{n_F} (N_P, s N_F) \mathrm{d}s.
+       f''_{n_F} (N_P, N_F) < \int_0^1 s^2 f''_{n_F} (N_P, s N_F) \mathrm{d}s.
    \end{gather*}
@@
  \begin{gather*}
-   g(\alpha N_P + \beta N_F), \\
-   g'' < 0, w(s) \equiv 1
+   g(\alpha N_P + \beta N_F), g'' < 0
  \end{gather*}

### 2023-06-11 src/presentation/io_day.qmd
Reorganize slides

@@
    $$ \pi_F(N_P, N_F^*) = I_F N_F^* $$
- - In order to guarantee uniqueness, let us assume
-   $$
-   \scriptsize
-   \begin{gather*}
-       f'_{n_F} (N_P, N_F) < \int_0^1 s f'_{n_F} (N_P, s N_F) \mathrm{d}s \\
-       \text{or} \\
-       f''_{n_F} (N_P, N_F) < \int_0^1 s^2 f''_{n_F} (N_P, s N_F) \mathrm{d}s.
-   \end{gather*}
-   $$
-     - Holds for certain interesting cases, such as the example application
+ - An extra assumption on $f$ is needed for uniqueness.
+   - It guarantees a concave or hump-shaped $\pi_F(N_P, N_F^*)$
+   - It is satisfied in the example application
 :::
@@
 
-::: {.incremental}
- - Follow @anderson2021hybrid
- - Unit mass of customers, each choosing one product maximizing $$u_{ij}^T = v^T - p_i^T + \mu \varepsilon_{ij}^T$$
-   - $T \in \{P, F, 0\}$
-   - Unit mass of outside options at price $p_i^0 = 0$
-   - $v_T$: value of the product
-   - $\mu$: degree of horizontal differentiation
-   - $\varepsilon_{ij}^T \sim \mathrm{Gumbel}(0, 1)$: taste shocks
-:::
-
-## Demand
-
 ::: {.fragment}
@@
 $$
+:::
+
+::: {.crossref .fragment}
+Microfoundations: @sec-utility-function
 :::
@@
  - **Bargaining**<br>total profits are shared according to the Shapley-value-based rule
-:::
-
-## Benchmark equilibrium
-
-::: {.incremental}
- - Optimal entry fee is independent of $N_P$:
-   $$ F_F^* = \sqrt{\mu I_F V_F} - I_F $$
- - Size of the aggregate is independent* of $N_P$:
-   $$ A^* = \sqrt{\frac{\mu V_F}{I_F}} $$
- - **Consumer surplus** is also **independent*** of $N_P$:
-   $$ CS^* \propto \log(A^*) $$
 :::
@@
 
+## Benchmark equilibrium
+
+::: {.incremental}
+ - Optimal entry fee is independent of $N_P$:
+   $$ F_F^* = \sqrt{\mu I_F V_F} - I_F $$
+ - Size of the aggregate is independent* of $N_P$:
+   $$ A^* = \sqrt{\frac{\mu V_F}{I_F}} $$
+ - **Consumer surplus** is also **independent*** of $N_P$:
+   $$ CS^* \propto \log(A^*) $$
+:::
+
 ## Results graphically
+
+<!-- TODO: CS instead of A, labels -->
 
@@
 :::
+
+## Utility function {#sec-utility-function}
+
+::: {.incremental}
+ - Follow @anderson2021hybrid
+ - Unit mass of customers, each choosing one product maximizing $$u_{ij}^T = v^T - p_i^T + \mu \varepsilon_{ij}^T$$
+   - $T \in \{P, F, 0\}$
+   - Unit mass of outside options at price $p_i^0 = 0$
+   - $v_T$: value of the product
+   - $\mu$: degree of horizontal differentiation
+   - $\varepsilon_{ij}^T \sim \mathrm{Gumbel}(0, 1)$: taste shocks
+:::

### 2023-06-11 src/presentation/io_day.qmd
Minor improvements

@@
  - The platform likes being hybrid
-$$
-\small
-\frac{\partial \pi_P(N_P, N_F)}{\partial N_P} > 0
-$$
+   - It's profits increase in $N_P$
 :::
@@
  - It depends™ for the fringe
-$$
-\begin{align*}
-\small\mathrm{sign} \left( \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} \right) = \\
-\small\mathrm{sign} \left( \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} \right)
-\end{align*}
-$$
+   - It's profits increase if and only if platform and fringe products are complements:
+     $$ \scriptsize \frac{\partial f^2}{N_P N_F} > 0 $$
 :::
@@
 ::: {.crossref .fragment}
-Microfoundations: @sec-utility-function
+Utility function: @sec-utility-function
 :::
@@
 ::: {.incremental}
- - Total profits as a function of entrants have a simple form:
+ - Total profits as a function of number of entrants have a simple form:
  $$
@@
  $$
-   - Satisfies the assumption for unique equilibrium
+   - Satisfies the assumption for a unique equilibrium
    - Has the form $f(N_P, N_F) = g(\alpha N_P + \beta N_F)$
@@
  - Longer term
-   - Endogeneize consumer entry (possibly with them engaging in the negotiation)
+   - Endogeneize consumer entry (possibly with consumers also engaging in the negotiation)
    - Apply this bargaining rule to other, similar settings

### 2023-06-11 src/presentation/io_day.qmd
Add crossrefs

@@
 
-## Profit sharing
+## Profit sharing {#sec-profit-sharing}
 
@@
 :::
-::: {.fragment}
- - Can be extended with weighting (innate bargaining power)
+
+::: {.crossref}
+Shapley-value: @sec-shapley-value
+
+Value of the platform: @sec-platform-value
 :::
@@
 
-## Demand
+## Demand {#sec-demand}
 
@@
  - Optimal entry fee is independent of $N_P$:
-   $$ F_F^* = \sqrt{\mu I_F V_F} - I_F $$
  - Size of the aggregate is independent* of $N_P$:
@@
 
-## The Shapley-value
+## The Shapley-value {#sec-shapley-value}
 
@@
 
+::: {.crossref}
+Back: @sec-profit-sharing
+:::
+
 ::::
@@
 
-## Value of the platform
+## Value of the platform {#sec-platform-value}
 
@@
 Shapley value:
-$$l 
+$$
 \scriptsize
@@
 $$
+:::
+
+::: {.crossref}
+Back: @sec-profit-sharing
 :::
@@
 :::
+
+::: {.crossref}
+Back: @sec-demand
+:::

### 2023-06-15 src/manim_figures/equilibrium_outcomes.py
Add legend and switch to CS

@@ -28,32 +28,19 @@ class Baseline(Scene):
             y_axis_config={"include_ticks": False},
 
         )
-        x_ax_label, y_ax_label = ax.get_axis_labels(x_label=r"N_P", y_label=r"A^*(N_P)")
+        x_ax_label, y_ax_label = ax.get_axis_labels(x_label=r"N_P", y_label=r"CS^*(N_P)")
 
         # Destiniations
         A_noF =  (ax.plot_line_graph(
-            x_values=data["N_P"], y_values=data["A_noF"],
+            x_values=data["N_P"], y_values=data["CS_noF"],
             line_color=BLACK, add_vertex_dots=False
         ))
         A_bench = ax.plot_line_graph(
-            data["N_P"], data["A_bench"],
+            data["N_P"], data["CS_bench"],
             line_color=BLUE_D, add_vertex_dots=False
         )
         A_barg = ax.plot_line_graph(
-            data["N_P"], data["A"],
-            line_color=RED_D, add_vertex_dots=False
-        )
-
-        pi_P_noF = (ax.plot_line_graph(
-            data["N_P"], data["pi_P_noF"],
-            line_color=BLACK, add_vertex_dots=False
-        ))
-        pi_P_bench = ax.plot_line_graph(
-            data["N_P"], data["pi_P_bench"],
-            line_color=BLUE_D, add_vertex_dots=False
-        )
-        pi_P_barg = ax.plot_line_graph(
-            data["N_P"], data["pi_P"],
+            data["N_P"], data["CS"],
             line_color=RED_D, add_vertex_dots=False
         )
 
@@ -78,21 +65,29 @@ class Baseline(Scene):
         f_bench = A_bench.copy()
         f_barg = A_barg.copy()
 
+        # Legend
+        legend_noF = MathTex(r"\text{No Fringe}", color=BLACK)
+        legend_bench = MathTex(r"\text{Benchmark}", color=BLUE_D)
+        legend_barg = MathTex(r"\text{Bargaining}", color=RED_D)
+
+        legend_noF.next_to(ax.c2p(1, 2.3), RIGHT)
+        legend_bench.next_to(ax.c2p(1, 2.1), RIGHT)
+        legend_barg.next_to(ax.c2p(1, 1.9), RIGHT)
 
         # First phase: draw axes
         self.play(Create(ax), Write(x_ax_label), Write(y_ax_label))
 
         # Second phase: no fringe
         self.next_section("a_nof")
-        self.play(Create(f_noF))
[…]

### 2023-06-15 src/presentation/io_day.qmd
Minor improvements to presentation

@@
 
-# Microfounding the profit function
+# A concrete example
 
@@
 $$
+\scriptsize
 A = \int_0^{N_F} \exp\left( \frac{v_F - p_{Fi}}{\mu} \right) \mathrm{d}i + \int_0^{N_P} \exp\left( \frac{v_P - p_{Pi}}{\mu} \right) \mathrm{d}i + 1
@@
 
-::: {.crossref .fragment}
+::: {.crossref}
 Utility function: @sec-utility-function
@@
  $$
- \begin{align*}
- p^*_{Ti} &= c_T + \mu \\
- \pi^{v*}_{Ti} &= \mu \frac{\exp \left( \frac{v_T - c_T - \mu}{\mu} \right)}{A}
- \end{align*}
+ p^*_{Ti} &= c_T + \mu
  $$
@@
 ::: {.incremental}
+ - **Bargaining**<br>total profits are shared according to the Shapley-value-based rule
  - **Benchmark**<br>platform can commit to any lump-sum entry fee $F_F$
- - **Bargaining**<br>total profits are shared according to the Shapley-value-based rule
 :::
@@
 ::: {.incremental}
- - Optimal entry fee is independent of $N_P$:
+ - Optimal entry fee is independent of $N_P$
  - Size of the aggregate is independent* of $N_P$:
-   $$ A^* = \sqrt{\frac{\mu V_F}{I_F}} $$
+   $$ A^* = \sqrt{\frac{\mu V_F}{I_F}} = \text{constant} $$
  - **Consumer surplus** is also **independent*** of $N_P$:
-   $$ CS^* \propto \log(A^*) $$
+   $$ CS^* \propto \log(A^*) = \text{constant}$$
 :::
@@
  - In this paper
-   - Endogenenize hybridness ($N_P$)
-   - Relax separate pricing assumption
+   - Endogenenize "hybridness" ($N_P$)
+   - Relax separate product pricing assumption
    - Alternative benchmarks (e.g. exogeneous split)
@@
  - Longer term
-   - Endogeneize consumer entry (possibly with consumers also engaging in the negotiation)
-   - Apply this bargaining rule to other, similar settings
+   - Endogeneize consumer entry
+   - Three-sided negotiation (platform, firms, consumers)
+   - Test bargaining through lab experiment
 :::

### 2023-06-15 src/manim_figures/equilibrium_outcomes.py

@@ -57,7 +57,7 @@ class Baseline(Scene):
             line_color=RED_D, add_vertex_dots=False
         )
 
-        y_ax_label_pi = MathTex(r"\pi_P")
+        y_ax_label_pi = MathTex(r"\pi_P^*(N_P)")
         y_ax_label_pi.move_to(y_ax_label.get_center())
 
         # Plotted objects
@@ -70,9 +70,9 @@ class Baseline(Scene):
         legend_bench = MathTex(r"\text{Benchmark}", color=BLUE_D)
         legend_barg = MathTex(r"\text{Bargaining}", color=RED_D)
 
-        legend_noF.next_to(ax.c2p(1, 2.3), RIGHT)
-        legend_bench.next_to(ax.c2p(1, 2.1), RIGHT)
-        legend_barg.next_to(ax.c2p(1, 1.9), RIGHT)
+        legend_noF.next_to(ax.c2p(1, 2.5), RIGHT + DOWN)
+        legend_bench.next_to(ax.c2p(1, 2.3), RIGHT + DOWN)
+        legend_barg.next_to(ax.c2p(1, 2.1), RIGHT + DOWN)
 
         # First phase: draw axes
         self.play(Create(ax), Write(x_ax_label), Write(y_ax_label))

### 2023-06-15 src/presentation/io_day.qmd
Even more last-minute improvements

@@
  $$
- p^*_{Ti} &= c_T + \mu
+ p^*_{Ti} = c_T + \mu
  $$
@@
 ::: {.incremental}
- - **Bargaining**<br>total profits are shared according to the Shapley-value-based rule
- - **Benchmark**<br>platform can commit to any lump-sum entry fee $F_F$
+ - **Bargaining**<br>Total profits are shared according to the Shapley-value-based rule
+ - **Benchmark**<br>The platform can commit to any lump-sum entry fee $F_F$
 :::
@@
    - $g$ is concave
- - Therefore,
+:::
+::: {.fragment}
 $$
- \frac{\partial N_F^*}{\partial N_P} < -\frac{V_P}{V_F}
+\implies \quad \frac{\partial N_F^*}{\partial N_P} < -\frac{V_P}{V_F}
 $$
@@
  - Highlight an important aspect if hybrid platforms
-   - **Hybridness increases bargaining power** against entrants
+   - **Hybrid mode increases bargaining power** against entrants
    - This can have **negative welfare consequences**
@@
 ::: {.fragment}
- - In this paper
-   - Endogenenize "hybridness" ($N_P$)
+ - Low-hanging fruit
+   - Endogenenize hybrid mode ($N_P$)
    - Relax separate product pricing assumption

### 2023-06-15 src/manim_figures/comparative_equilibrium_entry.py

@@ -49,8 +49,8 @@ class Baseline(Scene):
         # Destinations
         pi_F_orig = ax.plot(lambda x: pi_F(N_P_0, x), color=BLUE_D)
         pi_F_alt = ax.plot(lambda x: pi_F(N_P_1, x), color=RED_D)
-        pi_F_orig_label = ax.get_graph_label(pi_F_orig, r"\pi_F(0, N_F)", direction=UP)
-        pi_F_alt_label = ax.get_graph_label(pi_F_alt, r"\pi_F(0.5, N_F)", direction=DOWN)
+        pi_F_orig_label = ax.get_graph_label(pi_F_orig, r"\pi_F(N_P, N_F)", direction=UP)
+        pi_F_alt_label = ax.get_graph_label(pi_F_alt, r"\pi_F(N_P', N_F)", direction=DOWN)
 
         N_F_opt_0_bar = ax.get_vertical_line(N_F_opt_point_0, color=BLACK)
         N_F_opt_1_bar = ax.get_vertical_line(N_F_opt_point_1, color=BLACK)

### 2023-06-16 src/presentation/io_day.qmd
Even more last-minute changes

@@
  - It depends™ for the fringe
-   - It's profits increase if and only if platform and fringe products are complements:
-     $$ \scriptsize \frac{\partial f^2}{N_P N_F} > 0 $$
+   - It's profits decrease if platform and fringe products are substitutes:
+     $$ \scriptsize \frac{\partial f^2}{N_P N_F} < 0 $$
 :::
@@
 ::: {.fragment fragment-index=3}
- - If $\frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} < 0$, hybrid mode reduces fringe entry
+ - If $\frac{\partial^2 f(N_P, N_F)}{\partial N_P \partial N_F} < 0$, hybrid mode reduces fringe entry
 
@@
  $$
- \frac{\partial CS^*}{\partial N_P} < 0
+ CS^* \propto \log(A^*) \implies \frac{\partial CS^*}{\partial N_P} < 0
  $$
@@
 ::: {.fragment}
- - Highlight an important aspect if hybrid platforms
+ - Highlight an important aspect of hybrid platforms
    - **Hybrid mode increases bargaining power** against entrants

### 2023-11-14 src/paper/theory.tex
Add new, general random order value results

@@
 \end{corollary}
+
+% TODO: find a better place for this
+Let us now turn to the case of more general random order values.
+For any finite number of fringe players, the random order value can be expressed as follows:
+\begin{align*}
+    \varphi_P^n = \frac{1}{(n+1)!} \sum_{R} \Pr(R) [ v(\mathcal{P}_P^R \cup \{i\}) - v(\mathcal{P}_P^R) ]
+\end{align*}
+where $R$ is a permutation of all players, and $\mathcal{P}_P^R$ is the set of players before $P$ in the permutation $R$. \footnote{
+    For example, if $R = \{A_1, P, A_2\}$, then $\mathcal{P}_P^R = \{A_1\}$.
+}
+Utilizing the fact that the value of any coalition is zero without $P$, and that -- conditional on player $P$ being in a coalition -- a coalition's value only depends on the number of fringe firms in it, the above expression can be simplified to the following:
+\begin{align*}
+    \varphi_P^n = \frac{1}{n+1} \sum_{k=0}^n \Pr(|\mathcal{P}_P| = k) f(k/n),
+\end{align*}
+where $\Pr(|\mathcal{P}_P| = k)$ is determined by the probability distribution over the permutations.
+
+Now let us look at the asymptotic limit of this expression, as the number of fringe players goes to infinity.
+
+\begin{proposition}
+    \label{prop:one_sided_general}
+    Let $f$ be continuous on [0, 1].
+Furthermore, let us denote the random variable $\frac{|\mathcal{P}_P|}{n}$ as $X_n$.
+Assume that $X_n \xrightarrow[]{\mathrm{d}} X$ with cdf $G_X(t)$ and (if exists) pdf $g(t)$.
+    Then
+    \begin{align*}
+        \varphi_P^\infty = \lim_{n \to \infty} \varphi_P^n = \int_0^1 f(t) \mathrm{d}G(t) = \int_0^1 g(t) f(t) \dt,
+    \end{align*}
+    with the last equality holding if $X$ is a continuous random variable.
+\end{proposition}
+
+\begin{proof}[Proof of Proposition \ref{prop:one_sided_general}]
+    First, observe that $f$ is continuous on the compact set $[0, 1]$, and is therefore also bounded.
+    Furthermore,
+    \begin{align*}
+        \varphi_P^n = \frac{1}{n+1} \sum_{k=0}^n \Pr(|\mathcal{P}_P| / n = k) f(k/n) = \E[X_n].
+    \end{align*}
+    As $f$ is continuous and bounded, and $X_n \xrightarrow[]{\mathrm{d}} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
+    Putting it together,
+    \begin{align*}
+        \lim_{n \to \infty} \varphi_P^n &= \frac{1}{n+1} \sum_{k=0}^n \Pr(|\mathcal{P}_P| / n = k) f(k/n) \\
+        &= \lim_{n \to \infty} \E[X_n] \\
+        &= \E[X] \\
+        &= \int_0^1 f(t) \mathrm{d}G(t).
+    \end{align*}
+    Furthermore, if $G$ is differentiable, then
+    \begin{align*}
+        \int_0^1 f(t) \mathrm{d}G(t) = \int_0^1 g(t) f(t) \dt.
+    \end{align*}
+\end{proof}
 
@@
 Consequently, when taking the expectation over all orderings, those with very unequal numbers of the various types have little impact on it.
+
+\subsection{Random order values}
+
+Let us start by establishing the analog of \cref{prop:one_sided_general} for the many-sided case.
+\begin{proposition}
+    \label{prop:many_sided_general}
+    Let $f$ be continuous on $[0, 1]^L$. Furthermore, let us denote the random vector of the proportions of the various types of fringe players before $P$ as $X_n$:
+    \begin{align*}
+        X_n = \left( \frac{n_{A_1}(\mathcal{P}_P)}{n}, \dots, \frac{n_{A_L}(\mathcal{P}_P)}{n} \right).
+    \end{align*}
+    Assume that $X_n \xrightarrow[]{\mathrm{d}} X$ with cdf $G_X(t_1, \dots, t_L)$ and (if exists) pdf $g(t_1, \dots, t_L)$.
+    Then
+    \begin{align*}
+        \varphi_P^\infty = \lim_{n \to \infty} \varphi_P^n &= \int_0^1 \dots \int_0^1 f(t_1, \dots, t_L) \mathrm{d}G(t_1, \dots t_L) \\
+        &= \int_0^1\dots \int_0^1 g(t) f(t_1, \dots, t_L) \dt_1 \dots \dt_L,
+    \end{align*}
+    with the last equality holding if $X$ is a continuous random variable.
+\end{proposition}
+
+\begin{proof}[Proof of Proposition \ref{prop:many_sided_general}]
+    The proof mirrors that of \cref{prop:one_sided_general}.
+    First, note that the random order value can be expressed as follows:
+    \begin{align*}
+        \varphi_P^n &= \sum_{k_1=0}^n \dots \sum_{k_L=0}^n \Pr(n_{A_1}(\mathcal{P}_P) = k_1, \dots, n_{A_L}(\mathcal{P}_P) = k_L) f\left(\frac{k_1}{n}, \dots, \frac{k_L}{n}\right) \\
+        &= \sum_{k_1=0}^n \dots \sum_{k_L=0}^n \Pr(n X_n = (k_1, \dots, k_L)) f\left(\frac{k_1}{n}, \dots, \frac{k_L}{n}\right) \\
+        &= \sum_{k_1=0}^n \dots \sum_{k_L=0}^n \Pr \left( X_n = \left(\frac{k_1}{n}, \dots, \frac{k_L}{n}\right) \right) f \left(\frac{k_1}{n}, \dots, \frac{k_L}{n}\right) \\
+        &= \E[f(X_n)].
+    \end{align*}
+    Furthermore, as $f$ is continuous (and therefore bounded on $[0, 1]^L$), and $X_n \xrightarrow[]{\mathrm{d}} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
+    Putting it together,
+    \begin{align*}
+        \lim_{n \to \infty} \varphi_P^n &= \lim_{n \to \infty} \E[f(X_n)] \\
+        &= \E[f(X)] \\
+        &= \int_0^1 \dots \int_0^1 f(t_1, \dots, t_L) \mathrm{d}G(t_1, \dots t_L).
+    \end{align*}
+    Finally, if $X$ is a continuous random variable, then
+    \begin{align*}
+        \int_0^1 \dots \int_0^1 f(t_1, \dots, t_L) \mathrm{d}G(t_1, \dots t_L) = \int_0^1\dots \int_0^1 g(t_1, \dots, t_L) f(t_1, \dots, t_L) \dt_1 \dots \dt_L.
+    \end{align*}
+\end{proof}
 

### 2023-11-15 src/paper/theory.tex
Finished (?) proof of multi-sided SV

@@
 \newcommand{\E}{\mathbb{E}}
+\newcommand{\Var}{\mathrm{Var}}
+
+\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
 
@@
 Furthermore, let us denote the random variable $\frac{|\mathcal{P}_P|}{n}$ as $X_n$.
-Assume that $X_n \xrightarrow[]{\mathrm{d}} X$ with cdf $G_X(t)$ and (if exists) pdf $g(t)$.
+Assume that $X_n \xrightarrow[]{d} X$ with cdf $G_X(t)$ and (if exists) pdf $g(t)$.
     Then
@@
     \end{align*}
-    As $f$ is continuous and bounded, and $X_n \xrightarrow[]{\mathrm{d}} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
+    As $f$ is continuous and bounded, and $X_n \xrightarrow[]{d} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
     Putting it together,
@@
     \label{lem:entry_distr}
-     As $n \to \infty$, $X_n \xrightarrow[]{\mathrm{d}} X$ with the cdf $G_X(t) = \lambda^t$.
+     As $n \to \infty$, $X_n \xrightarrow[]{d} X$ with the cdf $G_X(t) = \lambda^t$.
      Consequently, the corresponding probability density function is $g(t) = \lambda t^{\lambda - 1}$.
@@
     \end{align*}
-    Assume that $X_n \xrightarrow[]{\mathrm{d}} X$ with cdf $G_X(t_1, \dots, t_L)$ and (if exists) pdf $g(t_1, \dots, t_L)$.
+    Assume that $X_n \xrightarrow[]{d} X$ with cdf $G_X(t_1, \dots, t_L)$ and (if exists) pdf $g(t_1, \dots, t_L)$.
     Then
@@
     \end{align*}
-    Furthermore, as $f$ is continuous (and therefore bounded on $[0, 1]^L$), and $X_n \xrightarrow[]{\mathrm{d}} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
+    Furthermore, as $f$ is continuous (and therefore bounded on $[0, 1]^L$), and $X_n \xrightarrow[]{d} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
     Putting it together,
@@
     \end{align*}
+\end{proof}
+
+While the above proposition is very general in terms of requirements on the permutation probabilities, it is not very tractable in practice, as one has to integrate over the entire unit hypercube.
+It would be much more convenient, if one only had to be concerned with a one-dimensional manifold within the hypercube instead.
+It turns out, that for a couple of important cases (namely, the Shapley-value and the weighted value) it is indeed the case.
+
+Let us start by establishing a general result, after which I will show that the Shapley-value and the weighted value are special cases of it.
+
+\begin{lemma}
+    % TODO: check notation!
+    \label{lem:many_sided_manifold}
+    Assume that $X_n \xrightarrow[]{d} X$ where $X$ is a degenerate distribution in the following sense: $\exists \, a_l: [0, 1] \to [0, 1], l = 1, \dots, L$, such that
+    \begin{align*}
+        X = (a_1(\xi), \dots, a_L(\xi)),
+    \end{align*}
+    where $\xi$ is a random variable on $[0, 1]$ with cdf $H(s)$.
+    In words, the whole probability mass is concentrated on the manifold $(a_1(s), \dots a_L(s)), t \in [0, 1]$.
+    Then
+    \begin{align*}
+        \varphi_P^\infty = \lim_{n \to \infty} \varphi_P^n &= \int_0^1 f(a_1(s), \dots a_L(s)) \mathrm{d}H(s).
+    \end{align*}
+\end{lemma}
+
+\begin{proof}[Proof of Lemma \ref{lem:many_sided_manifold}]
+    Just like in the proof of \cref{prop:many_sided_general}, the random order value can be expressed as follows:
+    \begin{align*}
+        \varphi_P^n &= \E[f(X_n)].
+    \end{align*}
+    Furthermore, as $f$ is continuous and bounded on $[0, 1]^L$, and $X_n \xrightarrow[]{d} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
+    Therefore,
+    \begin{align*}
+        \lim_{n \to \infty} \varphi_P^n &= \lim_{n \to \infty} \E[f(X_n)] \\
+        &= \E[f(X)] \\
+        &= \E[f(a_1(\xi), \dots, a_L(\xi))] \\
+        &= \int_0^1 f(a_1(s), \dots a_L(s)) \mathrm{d}H(s).
+    \end{align*}
+\end{proof}
+
+The Shapley-value:
+
+\begin{proposition}
+    \label{prop:many_sided_shapley}
+    Let $f$ be continuous on $[0, 1]^L$.
+    Then,
+    \begin{align*}
+        \varphi_P^\infty & = \int_0^1 f(t, \dots, t) \dt
+    \end{align*}
+\end{proposition}
+
+\begin{proof}[Proof of Proposition \ref{prop:many_sided_shapley}]
+    Let us show than $X_n$ converges in distribution to the degenerate random variable $X = (U, \dots, U)$, where $U$ is uniformly distributed on $[0, 1]$.
+
+    Let us first define the random variable $S_n = \sum_l[X_n]_l / L$, the total number of small players placed before $P$.
+    Also, define $h(s) = (s, \dots, s)$.
+    Now let us look at the conditional distribution $n X_n | n L S_n = k$.
+    As all permutations have equal probability, this is the same as picking $kL$ firms from the set $N \setminus \{P\}$ without replacement.
+    The numbers of each type in this sample will follow a multinomial distribution with $kL$ trials, $L$ events and probabilities $1/L$.
+
+    Let us now show that $\Pr(X_n < x \mid S_n = s) \xrightarrow[]{\mathrm{u}} \mathbf{1}[(s, \dots, s) \leq x]$ on $s \in \mathrm{supp}(S_n)$.
+
+    First, observe that
+    \begin{align*}
+        [\E(n X_n | nS_n = \lfloor ns \rfloor)]_l &= \lfloor ns \rfloor, \\
+        [\Var(n X_n | nS_n = \lfloor ns \rfloor)]_l &= \lfloor ns \rfloor \frac{L-1}{L}
+    \end{align*}
+    for all $\quad l = 1, \dots, L$.
+    Consequently,
+    \begin{align*}
+        [\E(X_n | nS_n = \lfloor ns \rfloor)]_l &= \frac{\lfloor ns \rfloor}{n}, \\
+        [\Var(X_n | nS_n = \lfloor ns \rfloor)]_l &= \frac{\lfloor ns \rfloor}{n^2} \frac{L-1}{L}
+    \end{align*}
+    for all $\quad l = 1, \dots, L$.
+
+    Notice that, as $n \to \infty$, $[\Var(X_n | nS_n = \lfloor ns \rfloor)]_l \to 0$.
+    Furthermore, $\E(X_n | nS_n = \lfloor ns \rfloor) \to h(s)$.
+    Thus, for any $s \in [0, 1], X_n | nS_n = \lfloor ns \rfloor \xrightarrow[]{L^2} h(s)$.
+
+    % Notice that, regardless of $s$, the variance $\Var(X_n | S_n = s)$ is bounded by $\frac{1}{n}$.
+    % By Chebyshev's inequality,
+    % \begin{align*}
+    %     \Pr( \| X_n - (s, \dots, s) \| > \epsilon \mid S_n = s) \leq \frac{L}{n \epsilon^2}.
+    % \end{align*}
+
+    Let us now turn to the random variable $S_n$.
+    Observe that because the probability of each permutation is the same, player $P$ has the same probability of being in any position.
+    In other words, $S_n$ follows a uniform distribution on $0, \frac{1}{nL}, \frac{2}{nL} \dots, 1$.
+    Consequently, $S_n$ converges in distribution to the uniform distribution $U[0, 1]$.
+
+    I have now shown that the assumptions of \cref{lem:convergence_to_manifold} are satisfied.
+    % TODO
+
+    Then, by \cref{lem:many_sided_manifold}, the Shapley-value is
+    \begin{align*}
+        \varphi_P^\infty & = \int_0^1 f(t, \dots, t) \dt.
+    \end{align*}
+
+\end{proof}
+
+\begin{lemma}
+    \label{lem:convergence_to_manifold}
+    Consider the random vector $X_n$ with values from $[0, 1]^L$.
+    Let $S_n = \sum_l[X_n]_l / L$, with the cumulative distribution function $G_n(s)$.
+    Assume that for every $s \in [0, 1]$, $X_n \mid n S_n = \lfloor ns \rfloor \xrightarrow[]{L^2} h(s)$ where $h(s)$ is some continuous function.
+    Let $S_n \xrightarrow[]{d} S$.
+    Then $X_n \xrightarrow[]{d} h(S)$.
+\end{lemma}
+
+\begin{proof}[Proof of lemma \ref{lem:convergence_to_manifold}]
+    We have to show that
+    \begin{align*}
+        \lim_{n \to \infty} \Pr(X_n \leq x) = \Pr(h(S) \leq x).
+    \end{align*}
+    for any $x$ where the cdf of $h(S)$ is continuous.
+
+    Let us start by conditioning on $S_n$:
+    \begin{align*}
+        \Pr(X_n \leq x) = \int_0^1 \Pr(X_n \leq x \mid S_n = s) \mathrm{d}G_n(s).
+    \end{align*}
+    Now consider the following:
+    \begin{align*}
+        \lim_{n \to \infty} \left| \Pr(X_n \leq x) - \Pr(h(S) \leq x) \right| &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \mathrm{d}G_n(s) - \Pr(h(S) \leq x) \right| \\
+        &\leq \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \mathrm{d}G_n(s) - \Pr(h(S_n) \leq x) \right| \\
+        &+ \lim_{n \to \infty} \left| \Pr(h(S_n) \leq x) - \Pr(h(S) \leq x) \right|
+    \end{align*}
+    for all $x \in [0, 1]^L$.
+    I will show that both limits on the right-hand side are zero.
+
+    Let us start with the first term.
+    \begin{align*}
+        \lim_{n \to \infty} &\left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \mathrm{d}G_n(s) - \Pr(h(S_n) \leq x) \right| \\
+        &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \mathrm{d}G_n(s) - \int_0^1 \mathbf{1}[h(s) \leq s] \mathrm{d}G_n(s) \right| \\
+        &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) - \mathbf{1}[h(s) \leq x] \mathrm{d}G_n(s) \right| \\
+        &= \lim_{n \to \infty} \left| \int_0^1 \underbrace{\Pr(X_n \leq x \mid nS_n = \lfloor ns \rfloor) - \mathbf{1}[h(s) \leq x]}_{\coloneqq r(s)} \mathrm{d}G_n(s) \right| \\
+        &\leq \lim_{n \to \infty} \int_0^1 \left| \Pr(X_n \leq x \mid nS_n = \lfloor ns \rfloor) - \mathbf{1}[h(s) \leq x] \right| \mathrm{d}G(s) \\
+        &+ \lim_{n \to \infty} \left| \int_0^1 r(s) \mathrm{d}G_n(s) - \int_0^1 r(s) \mathrm{d}G(s) \right| \\
+        &= 0.
+    \end{align*}
+    The first limit is zero because $X_n \mid n S_n = \lfloor ns \rfloor \xrightarrow[]{L^2} h(s)$.
+    The second limit is zero because of the continuous mapping theorem, as $S_n \xrightarrow[]{p} S$ and $\Pr_S(s : r\text{ is not continuous at }s)= 0$.
+
+    All that remains is to show that the second term is also zero.
+    This simply follows from the continuous mapping theorem, as $f$ is continuous and $S_n \xrightarrow[]{d} S$.
 \end{proof}
@@
     $f$ is continuous, and therefore bounded on the compact set $[0, 1]$.
-    As a consequence, $\frac{X_n}{n} \xrightarrow[]{\mathrm{d}} X$ implies $\E[f(X_n / n)] \to \E[f(X)]$, which in turn gives
+    As a consequence, $\frac{X_n}{n} \xrightarrow[]{d} X$ implies $\E[f(X_n / n)] \to \E[f(X)]$, which in turn gives
     \begin{align*}

### 2023-11-15 src/paper/theory.tex
Remove multiple big players and sides

@@
 
-\subsection{Multiple big players}
-
-The many-sided case can also simply be extended to incorporate multiple big players instead of just one.
-As before, assume that there are $m$ players of type $P$ which are perfect substitutes of each other:
-\begin{align*}
-    v(S) = \begin{cases}
-        0                                                & \text{if } P_i \notin S \; \forall \, i = 1, \dots, m \\
-        f\left(\frac{n_{A^1}(S)}{n}, \dots, \frac{n_{A^L}(S)}{n}\right) & \text{otherwise}.
-    \end{cases}
-\end{align*}
-
-It can be shown that the values of each type of player are rather similar to the single big player case.
-\begin{proposition}
-    The Shapley-values of the various types of players are
-    \begin{align*}
-        \varphi_{P_i}^{\infty, m} & = \int_0^1 (1-t)^{m-1} f(t, \dots, t) \dt                                 \\
-        \varphi_{A^l}^{\infty, m}     & = \int_0^1 [1 - (1-t)^m] \partial_l f(t, \dots, t) \dt.
-    \end{align*}
-\end{proposition}
-
-Similarly, as the next corollary demonstrates, the combined value of the big players is still decreasing in their number.
-\begin{corollary}
-    Let $\varphi_{P}^{\infty, m} = k\varphi_{P_i}^{\infty, m}$ denote the aggregated Shapley-values of players of type $P$.
-    Then $\varphi_{P}^{\infty, m}$ is decreasing in $k$ and $\varphi_{A^l}^{\infty, m}$ are increasing in $k$ unless $f$ is constant.
-\end{corollary}
-
 \section{Example Application}

### 2023-11-20 src/paper/theory.tex
Start working on many-sided weighted value

@@
 
-\begin{proof}[Proof of Proposition \ref{prop:one_sided_general}]
+\begin{proof}[Proof of \cref{prop:one_sided_general}]
     First, observe that $f$ is continuous on the compact set $[0, 1]$, and is therefore also bounded.
@@
 
-\begin{proof}[Proof of Proposition \ref{prop:many_sided_general}]
+\begin{proof}[Proof of \cref{prop:many_sided_general}]
     The proof mirrors that of \cref{prop:one_sided_general}.
@@
 
-\begin{proof}[Proof of Lemma \ref{lem:many_sided_manifold}]
+\begin{proof}[Proof of \cref{lem:many_sided_manifold}]
     Just like in the proof of \cref{prop:many_sided_general}, the random order value can be expressed as follows:
@@
 
-The Shapley-value:
+\subsection{Shapley-value}
 
@@
 
-\begin{proof}[Proof of Proposition \ref{prop:many_sided_shapley}]
+\begin{proof}[Proof of \cref{prop:many_sided_shapley}]
     Let us show than $X_n$ converges in distribution to the degenerate random variable $X = (U, \dots, U)$, where $U$ is uniformly distributed on $[0, 1]$.
@@
     Let $S_n = \sum_l[X_n]_l / L$, with the cumulative distribution function $G_n(s)$.
-    Assume that for every $s \in [0, 1]$, $X_n \mid n S_n = \lfloor ns \rfloor \xrightarrow[]{L^2} h(s)$ where $h(s)$ is some continuous function.
+    Assume that for every $s \in [0, 1]$, $X_n \mid n S_n = \lfloor ns \rfloor \xrightarrow[]{L^1} h(s)$ where $h(s)$ is some continuous function.
     Let $S_n \xrightarrow[]{d} S$.
@@
 
-\begin{proof}[Proof of lemma \ref{lem:convergence_to_manifold}]
+\begin{proof}[Proof of \cref{lem:convergence_to_manifold}]
     We have to show that
@@
     \end{align*}
-    The first limit is zero because $X_n \mid n S_n = \lfloor ns \rfloor \xrightarrow[]{L^2} h(s)$.
+    The first limit is zero because $X_n \mid n S_n = \lfloor ns \rfloor \xrightarrow[]{L^1} h(s)$.
     The second limit is zero because of the continuous mapping theorem, as $S_n \xrightarrow[]{p} S$ and $\Pr_S(s : r\text{ is not continuous at }s)= 0$.
@@
     This simply follows from the continuous mapping theorem, as $f$ is continuous and $S_n \xrightarrow[]{d} S$.
+\end{proof}
+
+\subsection{Weighted value}
+
+Let us now examine the weighted value in the multi-sided case.
+The set of players and the characteristic function are the same as in the previous section, but players have the following weights: player $P$ has weight $\lambda_P$, while players $A^l_i$ have weight $\lambda_l$.
+I will show, that as with the Shapley-value, the limit of the weighted value can also be expressed as an integral over a one-dimensional path.
+However, this path is not the diagonal of the unit hypercube, and depends on the ratio of the fringe players' weights.
+
+\begin{proposition}
+    \label{prop:many_sided_weighted}
+    Let $f$ be continuous on $[0, 1]^L$.
+    Then,
+    \begin{align*}
+        \varphi_P^\infty & = \int_0^1 f(t^{\lambda_1}, \dots, t^{\lambda^L}) \lambda_P t^{\lambda_P} \dt.
+    \end{align*}
+\end{proposition}
+
+\begin{proof}[Proof of \cref{prop:many_sided_weighted}]
+    The proof uses the same approach as that of \cref{prop:many_sided_shapley}.
+    I will show that $X_n \xrightarrow[]{d} h(\xi)$, where $h(s) = (s^{\lambda_1}, \dots, s^{\lambda_L})$, and $\xi$ is a random variable with cdf $G(s) = s^{\lambda_P}$, and then rely on \cref{lem:many_sided_manifold}.
+
 \end{proof}
@@
 \end{lemma}
-\begin{proof}[Proof of Lemma \ref{lemma:log_convergence}]
+\begin{proof}[Proof of \cref{lemma:log_convergence}]
     First, note that $\Delta_n$ and $\Delta$ are all continuous functions.
@@
 \end{lemma}
-\begin{proof}[Proof of Lemma \ref{lemma:integral_convergence}]
+\begin{proof}[Proof of \cref{lemma:integral_convergence}]
     \begin{align*}
@@
 
-\begin{proof}[Proof of Proposition \ref{prop:monotone}]
+\begin{proof}[Proof of \cref{prop:monotone}]
     Monotonicity is evident.
@@
 
-\begin{proof}[Proof of Proposition \ref{prop:one_sided}]
+\begin{proof}[Proof of \cref{prop:one_sided}]
     Let $R$ denote a permutation of the set of players ($N$).
@@
 
-\begin{proof}[Proof of Lemma \ref{lem:entry_distr}] %\textcolor{red}{(Might have to fix sum indices)} \\
+\begin{proof}[Proof of \cref{lem:entry_distr}] %\textcolor{red}{(Might have to fix sum indices)} \\
     The probability of $P$ having at most fraction $t$ of the other players before itself is
@@
 
-\begin{proof}[Proof of Proposition \ref{prop:one_sided_weighted}]
+\begin{proof}[Proof of \cref{prop:one_sided_weighted}]
     The weighted value of player $P$ is its expected contribution across all permutations, with each permutation weighted by its probability of occurring.
@@
 
-\begin{proof}[Proof of Proposition \ref{prop:multiple_platforms}]
+\begin{proof}[Proof of \cref{prop:multiple_platforms}]
     \label{prop:one_sided_multiple}

### 2023-11-20 src/paper/theory.tex
Rewrite abstract and title

@@
 
-\title{The value of intermediation}
+\title{The value of being indispensable: a cooperative approach to bargaining with a continuum of players}
 \author{Martin Stancsics}
@@
 \begin{abstract}
-    This paper investigates the idea of using concepts from cooperative game theory (in particular, the Shapley-value) to model bargaining outcomes in games with a few large and a continuum of small players.
-    I show that the cooperative approach can be a tractable alternative of explicitly modelling price structures and entry choices in platform settings.
-    This approach might be advantageous when one does not want to attribute all the bargaining power to one type of market participants, and at the same time would like to avoid having to deal with an explicit multi-stage bargaining game.
-    I demonstrate the advantages of this approach in a stylized model of a vertical market.
+    This paper investigates the idea of using concepts random order values, a concept from cooperative game theory, to model bargaining outcomes in games with an indispensable player and a continuum of fringe players.
+    I show that this approach proves to be very tractable in a number of settings, and leads to results that are in line with one's intuitive expectations about bargaining outcomes.
+    Thus, it can be a useful tool in modelling situations where one does not want to attribute all the bargaining power to one type of market participants, and at the same time would like to avoid having to deal with an explicit multi-stage bargaining game.
+    On one hand, this paper serves as a taxonomization of various results found in some applied papers.
+    Furthermore, it introduces some new results pertaining to the case when participants have different levels of innate bargaining power, and weighted values are more appropriate.
+    The results in this paper is intended to be used as a tool-kit for embedding bargaining outcomes into more complex models.
 \end{abstract}
@@
 \section{Motivation}
+
+Using cooperative game theory to model bargaining outcomes in a tractable way has quite a few examples in the industrial organization literature.
+The case of one indispensable player and a large number of small ones is particularly important, for example, in the context of vertical markets or platforms.
 

### 2023-11-21 src/paper/theory.tex
Rewrite introduction

@@
     Thus, it can be a useful tool in modelling situations where one does not want to attribute all the bargaining power to one type of market participants, and at the same time would like to avoid having to deal with an explicit multi-stage bargaining game.
-    On one hand, this paper serves as a taxonomization of various results found in some applied papers.
+    On one hand, this paper provides a taxonomy of the various results found in some applied papers.
     Furthermore, it introduces some new results pertaining to the case when participants have different levels of innate bargaining power, and weighted values are more appropriate.
@@
 Using cooperative game theory to model bargaining outcomes in a tractable way has quite a few examples in the industrial organization literature.
-The case of one indispensable player and a large number of small ones is particularly important, for example, in the context of vertical markets or platforms.
-
-The use of solution concepts from cooperative game theory -- such as the Shapley-value -- to model the outcome of a bargaining process has been a feature of multiple papers in the industrial organization literature.
-It is particularly prevalent in articles dealing with issues related to integration and mergers \parencite[e.g.][]{hart1990property,segal2003collusion,inderst2003bargaining,montez2007downstream}.
 This is in part motivated by the appealing properties of the resulting gain distributions, their tractability, but also by the long line of theoretical studies showing that various bargaining procedures lead to such outcomes.
@@
 
-A common feature of the aforementioned papers is that they involve models with a finite number of agents.
-However, as is often the case in economics, infinite-player approximations might turn out to be more tractable while retaining the main conclusions of the finite models from which they arise.
-Indeed, in the case of cooperative games with non-atomic players, both the axiomatic approach to defining a value on infinite games and the asymptotic approach to calculate the limit of its finite counterparts lead to the same result \footnote{
-    On the appropriate subspace of non-atomic games.
-} \parencite{aumann2015values}, which is furthermore analytically simple and readily interpretable. An economic application of this theory can be found in \textcite{billera1978internal}.
-
-Beyond games with no atoms, economists are often interested in situations characterized by a relatively small number of large players and numerous individually rather insignificant ones.
-The continuous analogue of them are called oceanic games, in which the set of players consists of a finite number of atoms and an ocean made up of a continuum of fringe players.
-While the axiomatic characterization of the value on such games has not been particularly fruitful,\footnote{
-    \textcite{hart1973values} shows that the usual axioms do not characterize a unique value in general.
-} \textcite{fogelman1980asymptotic} demonstrates that an asymptotic approach works well on a large subset of them.
-More specifically, the limit of the players' values converge to relatively simple and easy-to-interpret expressions as the number of small players goes towards infinity.
-
-Despite this positive result and their analytical tractability, oceanic games are extremely underutilized in economics.
-One of the few examples of papers employing them is \textcite{levy1997individual}, which applies it to the problem of wage bargaining.
-In the following sections, I propose an oceanic game with the main feature that the large player(s) is indispensable for creating value.
-Such a model can apply, for example, to upstream-downstream supply chains, or platforms connecting two sides of a market.
-I demonstrate that the Shapley values of the players in those models are described by easily interpretable and visualizable expressions.
-Additionally, the outcomes are in line with one's intuitive expectations of bargaining outcomes in such situations.
-Furthermore, the results are simple enough that these games can be embedded into more complex models, for example, as the second stage of a sequential game \parencite[as in e.g.][]{montez2007downstream}.
-Finally, I demonstrate the usefulness of this approach by building a simple model of a vertical market that obtains the capability of bypassing the downstream firms and selling directly to final consumers.
+In terms of applications, the case of one indispensable player and a large number of small ones is particularly important in a number of settings.
+Examples include intra-firm ownership strutures \parencite{hart1990property}, wage bargaining \parencite{stole1996intra,stole1996organizational,levy1997individual}, collusion and mergers \parencite{segal2003collusion} and upstream-downstream supply chains \parencite{inderst2003bargaining,montez2007downstream}.
+The study of multi-sided markets (paltforms) is also a good fit for this modeling approach, as the platform is often indispensable for the fringe firms, but the latter are also numerous enough to be approximated by a continuum.\footnote{
+    \textcite{huang2022shapley} is one of the very few examples of using cooperative game theory in this setting.
+}
+
+A common feature of most of the aforementioned papers is that they assume a finite number of players.
+However, as is often the case in economics, infinite-player approximations turn out to be more tractable while retaining the main conclusions of the finite models from which they arise.
+Perhaps most importantly, the resulting profit shares become continuous and differentiable functions of the size of the fringe, which is particularly useful when embedding these results into more complex models.
+
+Cooperative games with a finite number of atomic players and a continuum of non-atomic ones are called mixed or oceanic games \parencite{milnor1978values}, and have been studied in the literature of cooperative game theory.
+Most papers in this line of research focus on questions such as for which games the Shapley-value exists and is unique \parencite{hart1973values}, and whether various approaches (namely, characterizing the value using a set of axioms, and taking the limit of the value of finite-player games) lead to the same result \parencite{fogelman1980asymptotic}.\footnote{
+    \textcite{hart1973values} shows that in the case of mixed games, the usual axioms do not characterize a unique value in general.
+    However, \textcite{fogelman1980asymptotic} demonstrates that, for a quite general subset of games, the asymptotic approach leads to one specific element from the set characterized by the axiomatic approach.
+}
+My aim with this paper is both more general and more specific in certain aspects.
+For one, I am only interested in the asymptotic approach, and withing that, a specific series of finite games.
+Furthermore, I restrict my attention to one specific type of games, namely those with an indispensable player, and a continuum of fringe players consisting of a finite number of types.
+This in turn allows me to go beyond the usual Shapley-value, and obtain results for a more general set of solution concepts: random order values.
+A specific example of those, for which I provide a number of new results, is the weighted value \parencite{shapley1953additive}.
+Additionally, due to more structure in the model, I am able to provide more concrete results, investigate some comparative statics, as well.
+
+Despite their theoretical appeal and their tractability, oceanic games saw very little use in the industrial organization, and, more generally, applied economics literature.
+The two most prominent examples are \textcite{stole1996intra, stole1996organizational} and \textcite{levy1997individual}, all of which use the Shapley-value to model wage bargaining, and consider the case of divisible labor (continuum of workers).
+The first two of these paper also provides microfoundations for the Shapley value and the weighted value in the intra-firm bargaining setting.
+
+In the following sections, I propose an oceanic game with the main feature that the large player is indispensable for creating value.\footnote{
+    This assumption will be somewhat relaxed throughout some of the generalizations.
+}
+Such a model applies to all the settings mentioned above, such as intra-firm bargaining, vertical supply chains, or multi-sided markets.
+I demonstrate that the Shapley values of the players in those models are described by very tractable expressions that have nice geometric interpretations.
+Additionally, the outcomes are in line with one's intuitive expectations of bargaining power in such situations.
+Finally, I demonstrate the usefulness of this approach by building a simple model of TODO.
 

### 2023-11-21 src/paper/theory.tex
Rewrite one-sided shapley

@@
 \newcommand{\di}{\mathrm{d}i}
+\newcommand{\dG}{\mathrm{d}G}
 \newcommand{\E}{\mathbb{E}}
@@
 
-Consider a cooperative game with two types of players: a major player $P$ and $n$ smaller players $A_i$, $1 \leq i \leq n$.
+In this section I examine the case of identical fringe players.
+I will first look at the simplest setting (one large player, which is completely indispensable), but in the subsequent sections I will somewhat relax this assumption.
+Let us start by defining the cooperative game that describes this situation.
+
+Consider a game with two types of players: a major player $P$ and $n$ smaller players $A_i$, $1 \leq i \leq n$.
 Formally, let us denote the set of all players as $N = \{P, A_1, \dots, A_n\}$.
@@
 }
-Fortunately, in this specific setting, characterizing monotonicity and superadditivity is extremely straightforward.
+In this specific setting, characterizing monotonicity and superadditivity is extremely straightforward.
 \begin{proposition}
@@
 }
-In addition to this, it also ensures that the games are of bounded variation, and thus the main theorem in \textcite{fogelman1980asymptotic} applies.
-Namely, various approaches of defining the value of an oceanic game (one with a finite number of atomic and a continuum of non-atomic players) lead to the same result\footnote{
-    More rpecisely, the asymptotic value coincides with the axiomatic one using the uniform distribution.
+As a side note, it also ensures that the games are of bounded variation, and thus the main theorem in \textcite{fogelman1980asymptotic} applies.
+Namely, both the asymptotic and axiomatic approach of characterizing the Shapley-value of the game lead to the same result\footnote{
+    More precisely, the asymptotic value coincides with the axiomatic one derived using the uniform distribution.
     For a more detailed discussion, see \textcite{fogelman1980asymptotic}.
-}, providing multiple ways of characterizing it.
-In practice, it means that there is no need to explicitly calculate the limits of finite-player cooperative games, as there is a more direct option for characterizing the value of the oceanic game.
-Nevertheless, in many of the following theorems, the asymptotic limit is explicitly derived, as I believe that makes the results more explanatory.
-
-The following proposition demonstrates the main idea of this paper: even as the number of fringe players goes to infinity, the Shapley-value of the big player does not converge to the worth of the grand coalition, $f(1)$.
-This in turn implies that the aggregated Shapley-values of the fringe remain positive even in the limit.
+}.
+
+\subsection{Random order values}
+
+For any finite number of fringe players, the random order value of a player \parencite{weber1988probabilistic} is simply its average marginal contribution to the value of all possible coalitions.
+More precisely, take all permutations of the players, and assign a probability to each of them.
+Then, the random order value of player $P$ is the expected marginal contribution of $P$ to the value of the coalition preceding it in these permutations.
+
+For the remainder of the paper, let us use the following notation: $\varphi_P^n$ denotes the (depending on section, Shapley, weighted or random order) value of player $P$ in the game with players $N = \{P, A_1, \dots, A_n\}$.
+Then, formally,
+\begin{align*}
+    \varphi_P^n = \frac{1}{(n+1)!} \sum_{R} \Pr(R) [ v(\mathcal{P}_P^R \cup \{i\}) - v(\mathcal{P}_P^R) ]
+\end{align*}
+where $R$ is a permutation of all players, and $\mathcal{P}_P^R$ is the set of players before $P$ in the permutation $R$. \footnote{
+    For example, if $R = \{A_1, P, A_2\}$, then $\mathcal{P}_P^R = \{A_1\}$.
+}
+
+Random order values are of interest to us for a number of reasons.
+First, they are a natural extension to the Shapley value, where the axiom of symmetry is relaxed.
+Furthermore, they provide a convenient framework, of which all subsequent results (Shapley value, weighted value, multiple big players) are special cases.
+
+Utilizing the fact that the value of any coalition is zero without $P$, and that -- conditional on player $P$ being in a coalition -- a coalition's value only depends on the number of fringe firms in it, the above expression can be simplified to the following:
+\begin{align*}
+    \varphi_P^n = \frac{1}{n+1} \sum_{k=0}^n \Pr(|\mathcal{P}_P| = k) f(k/n),
+\end{align*}
+where $\Pr(|\mathcal{P}_P| = k)$ is determined by the probability distribution over the permutations.
+
+Now let us look at the asymptotic limit of this expression, as the number of fringe players goes to infinity.
+The following proposition demonstrates the main idea of this paper: even as the number of fringe players goes to infinity, the value of the big player does not converge to the worth of the grand coalition, $f(1)$.
+
+\begin{proposition}
+    \label{prop:one_sided_general}
+    Let $f$ be continuous on [0, 1].
+Furthermore, let us denote the random variable $\frac{|\mathcal{P}_P|}{n}$ as $X_n$.
+Assume that $X_n \xrightarrow[]{d} X$ with cdf $G_X(t)$ and (if exists) pdf $g(t)$.
+    Then
+    \begin{align*}
+        \varphi_P^\infty = \lim_{n \to \infty} \varphi_P^n = \int_0^1 f(t) \dG(t) = \int_0^1 g(t) f(t) \dt,
+    \end{align*}
+    with the last equality holding if $X$ is a continuous random variable.
+\end{proposition}
+
+Now let us turn to the value of the fringe.
+The following corollary shows that the aggregated value of the fringe remains positive even in the limit.
 In other words, even though the fringe players become smaller and more numerous, they do not lose all of their bargaining power, and still end up with a positive payoff in the end.
-
-In the remainder of the paper, let us use the following notation: $\varphi_P^n$ denotes the Shapley-value of player $P$ in the game with players $N = \{P, A_1, \dots, A_n\}$.
-\begin{proposition}
-    \label{prop:one_sided}
-    Let $f$ be continuous on [0, 1]. Then
-    \begin{align*}
-        \varphi_P^\infty = \lim_{n \to \infty} \varphi_P^n = \int_0^1 f(t) \dt .
-    \end{align*}
-\end{proposition}
-
-The above proposition is not surprising in light of \textcite{fogelman1980asymptotic}: the limit is just the expected marginal contribution of the single atomic player, with said player being placed in the order according to the uniform distribution.
-Nevertheless, even this simple result has a compelling geometric interpretation, and gives rise to a couple of interesting corollaries, detailed below.
-
 \begin{corollary}
-    \label{cor:fringe_value}
-    The aggregated Shapley-value of the fringe is
-    \begin{align*}
-        \varphi_A^\infty = f(1) - \int_0^1 f(t) \dt.
+    \label{cor:fringe_value_general}
+    The aggregated value of the fringe is
+    \begin{align*}
+        \varphi_A^\infty = f(1) - \int_0^1 f(t) \dG(t).
     \end{align*}
@@
     \begin{align*}
-        \varphi_A^\infty = \int_0^1 t f'(t) \dt.
+        \varphi_A^\infty = \int_0^1 t G(t) f'(t) \dt.
     \end{align*}
@@
 
+It also provides us with two ways of thinking about the value of the fringe.
+First, due to random order values being efficient, it can be thought of as the leftover from the total value after subtracting the value of the big player.
+Alternatively, as the second part of the corollary demonstrates, it is also related to the marginal contributions to the fringe agents.
+The only difference from the big player's value is that we have to weight this marginal contribution by the probability of the big player appearing before the fringe firm in question, as otherwise its marginal contribution is zero.
+The latter interpretation will be particularly useful when thinking about the value of the fringe in the multi-sided setting.
+
+It is immediately follows from the proposition above that (for a fixed total pie size $f(1)$) player $P$ gets a larger share when $f(t)$ is larger for every $t$.
 It is already apparent from Figure \ref{fig:one_sided} that (for a fixed total pie size $f(1)$) player $P$ gets a larger share when $f(t)$ is larger for every $t$.
@@
 In contrast, when fringe players are more complementary to each other, the big player can only obtain a smaller share, as its bargaining power is more limited.
+
+\subsection{Shapley value}
+
+Now let us turn our attention to an important special case of random order values: the Shapley value.
+It can be characterized by being the random order value that additionally also satisfies the axiom of symmetry.
+This axiom requires that if two players are identical in terms of the characteristic function, then they should receive the same value.
+Equivalently, it is the same as requiring that all permutations have an equal probability.
+
+The following proposition and corollary derives the Shapley value of the big player and the fringe, respectively.
+
+\begin{proposition}
+    \label{prop:one_sided}
+    Let $f$ be continuous on [0, 1]. Then
+    \begin{align*}
+        \varphi_P^\infty = \lim_{n \to \infty} \varphi_P^n = \int_0^1 f(t) \dt .
+    \end{align*}
+\end{proposition}
+
+\begin{corollary}
+    \label{cor:fringe_value}
+    The aggregated Shapley-value of the fringe is
+    \begin{align*}
+        \varphi_A^\infty = f(1) - \int_0^1 f(t) \dt.
+    \end{align*}
+    Furthermore, if $f$ is differentiable on $[0, 1]$, then the value of the fringe can also be expressed as
+    \begin{align*}
+        \varphi_A^\infty = \int_0^1 t f'(t) \dt.
+    \end{align*}
+\end{corollary}
+
+Because the Shapley value is a special case of the random order value, these results follows quite straightforwardly from \cref{prop:one_sided_general} and \cref{cor:fringe_value_general}.
+One only has to notice that each permutation having an equal probability implies that the number of firms coming before $P$ is uniformly distributed on $1, \dots, n$, and thus the share of firms before $P$ converges in distribution to the uniform distribution on $[0, 1]$.
+Alternatively, a more direct proof is provided in \cref{sec:proofs}, or a probabilistic justification can be found in \textcite{levy1997individual}.
+
+The resulting Shapley values also have a nice geometric interpretation \cref{fig:one_sided}.
+Consider a rectangle with sides of length 1 and $f(1)$, respectively.
+Then, due to superadditivity, the grand coalition forms and achieves the value $f(1)$, which is the area of the rectangle.
+The value of the big player is then $\int_0^1 f(t) \dt$, which is simply the part of the rectangle below the graph of $f$, while the fringe gets the rest.
+Thus, the graph of $f$ partitions the area (total value) into what the big player and the fringe obtain.
 
@@
 
-                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($A$)};
-                \node[anchor=south east] at (axis cs: .95, .05) {Big player ($P$)};
+                \node[anchor=north west, align=left] at (axis cs: .05, .95) {Value of the \\ fringe ($\varphi_A^\infty$)};
+                \node[anchor=south east, align=right] at (axis cs: .95, .05) {Value of the \\ big player ($\varphi_P^\infty$)};
             \end{axis}
@@
 \end{corollary}
-
-% TODO: find a better place for this
-Let us now turn to the case of more general random order values.
-For any finite number of fringe players, the random order value can be expressed as follows:
-\begin{align*}
-    \varphi_P^n = \frac{1}{(n+1)!} \sum_{R} \Pr(R) [ v(\mathcal{P}_P^R \cup \{i\}) - v(\mathcal{P}_P^R) ]
-\end{align*}
-where $R$ is a permutation of all players, and $\mathcal{P}_P^R$ is the set of players before $P$ in the permutation $R$. \footnote{
-    For example, if $R = \{A_1, P, A_2\}$, then $\mathcal{P}_P^R = \{A_1\}$.
-}
-Utilizing the fact that the value of any coalition is zero without $P$, and that -- conditional on player $P$ being in a coalition -- a coalition's value only depends on the number of fringe firms in it, the above expression can be simplified to the following:
-\begin{align*}
-    \varphi_P^n = \frac{1}{n+1} \sum_{k=0}^n \Pr(|\mathcal{P}_P| = k) f(k/n),
-\end{align*}
-where $\Pr(|\mathcal{P}_P| = k)$ is determined by the probability distribution over the permutations.
-
-Now let us look at the asymptotic limit of this expression, as the number of fringe players goes to infinity.
-
-\begin{proposition}
-    \label{prop:one_sided_general}
-    Let $f$ be continuous on [0, 1].
-Furthermore, let us denote the random variable $\frac{|\mathcal{P}_P|}{n}$ as $X_n$.
-Assume that $X_n \xrightarrow[]{d} X$ with cdf $G_X(t)$ and (if exists) pdf $g(t)$.
-    Then
-    \begin{align*}
-        \varphi_P^\infty = \lim_{n \to \infty} \varphi_P^n = \int_0^1 f(t) \mathrm{d}G(t) = \int_0^1 g(t) f(t) \dt,
-    \end{align*}
-    with the last equality holding if $X$ is a continuous random variable.
-\end{proposition}
-
-\begin{proof}[Proof of \cref{prop:one_sided_general}]
-    First, observe that $f$ is continuous on the compact set $[0, 1]$, and is therefore also bounded.
-    Furthermore,
-    \begin{align*}
-        \varphi_P^n = \frac{1}{n+1} \sum_{k=0}^n \Pr(|\mathcal{P}_P| / n = k) f(k/n) = \E[X_n].
-    \end{align*}
-    As $f$ is continuous and bounded, and $X_n \xrightarrow[]{d} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
-    Putting it together,
-    \begin{align*}
-        \lim_{n \to \infty} \varphi_P^n &= \frac{1}{n+1} \sum_{k=0}^n \Pr(|\mathcal{P}_P| / n = k) f(k/n) \\
-        &= \lim_{n \to \infty} \E[X_n] \\
-        &= \E[X] \\
-        &= \int_0^1 f(t) \mathrm{d}G(t).
-    \end{align*}
-    Furthermore, if $G$ is differentiable, then
-    \begin{align*}
-        \int_0^1 f(t) \mathrm{d}G(t) = \int_0^1 g(t) f(t) \dt.
-    \end{align*}
-\end{proof}
 
@@
 On the other hand, superadditivity is not as simple in this case, as before.
-For example, when $f$ is concave, then $m$ coalitions with one platform each and the fringe divided equally among them clearly achieve a higher total payoff than the grand coalition.
+For example, when $f$ is concave, then $m$ coalitions with one platform each and the fringe divided equally amongst them clearly achieve a higher total payoff than the grand coalition.
 Therefore, the results of this section are most applicable to settings when multiple coalitions cannot be formed at the same time for some reason.
@@
     \begin{align*}
-        \varphi_P^\infty = \lim_{n \to \infty} \varphi_P^n &= \int_0^1 \dots \int_0^1 f(t_1, \dots, t_L) \mathrm{d}G(t_1, \dots t_L) \\
+        \varphi_P^\infty = \lim_{n \to \infty} \varphi_P^n &= \int_0^1 \dots \int_0^1 f(t_1, \dots, t_L) \dG(t_1, \dots t_L) \\
         &= \int_0^1\dots \int_0^1 g(t) f(t_1, \dots, t_L) \dt_1 \dots \dt_L,
@@
         &= \E[f(X)] \\
-        &= \int_0^1 \dots \int_0^1 f(t_1, \dots, t_L) \mathrm{d}G(t_1, \dots t_L).
+        &= \int_0^1 \dots \int_0^1 f(t_1, \dots, t_L) \dG(t_1, \dots t_L).
     \end{align*}
@@
     \begin{align*}
-        \int_0^1 \dots \int_0^1 f(t_1, \dots, t_L) \mathrm{d}G(t_1, \dots t_L) = \int_0^1\dots \int_0^1 g(t_1, \dots, t_L) f(t_1, \dots, t_L) \dt_1 \dots \dt_L.
+        \int_0^1 \dots \int_0^1 f(t_1, \dots, t_L) \dG(t_1, \dots t_L) = \int_0^1\dots \int_0^1 g(t_1, \dots, t_L) f(t_1, \dots, t_L) \dt_1 \dots \dt_L.
     \end{align*}
@@
     \begin{align*}
-        \Pr(X_n \leq x) = \int_0^1 \Pr(X_n \leq x \mid S_n = s) \mathrm{d}G_n(s).
+        \Pr(X_n \leq x) = \int_0^1 \Pr(X_n \leq x \mid S_n = s) \dG_n(s).
     \end{align*}
@@
     \begin{align*}
-        \lim_{n \to \infty} \left| \Pr(X_n \leq x) - \Pr(h(S) \leq x) \right| &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \mathrm{d}G_n(s) - \Pr(h(S) \leq x) \right| \\
-        &\leq \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \mathrm{d}G_n(s) - \Pr(h(S_n) \leq x) \right| \\
+        \lim_{n \to \infty} \left| \Pr(X_n \leq x) - \Pr(h(S) \leq x) \right| &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \dG_n(s) - \Pr(h(S) \leq x) \right| \\
+        &\leq \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \dG_n(s) - \Pr(h(S_n) \leq x) \right| \\
         &+ \lim_{n \to \infty} \left| \Pr(h(S_n) \leq x) - \Pr(h(S) \leq x) \right|
@@
     \begin{align*}
-        \lim_{n \to \infty} &\left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \mathrm{d}G_n(s) - \Pr(h(S_n) \leq x) \right| \\
-        &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \mathrm{d}G_n(s) - \int_0^1 \mathbf{1}[h(s) \leq s] \mathrm{d}G_n(s) \right| \\
-        &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) - \mathbf{1}[h(s) \leq x] \mathrm{d}G_n(s) \right| \\
-        &= \lim_{n \to \infty} \left| \int_0^1 \underbrace{\Pr(X_n \leq x \mid nS_n = \lfloor ns \rfloor) - \mathbf{1}[h(s) \leq x]}_{\coloneqq r(s)} \mathrm{d}G_n(s) \right| \\
-        &\leq \lim_{n \to \infty} \int_0^1 \left| \Pr(X_n \leq x \mid nS_n = \lfloor ns \rfloor) - \mathbf{1}[h(s) \leq x] \right| \mathrm{d}G(s) \\
-        &+ \lim_{n \to \infty} \left| \int_0^1 r(s) \mathrm{d}G_n(s) - \int_0^1 r(s) \mathrm{d}G(s) \right| \\
+        \lim_{n \to \infty} &\left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \dG_n(s) - \Pr(h(S_n) \leq x) \right| \\
+        &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \dG_n(s) - \int_0^1 \mathbf{1}[h(s) \leq s] \dG_n(s) \right| \\
+        &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) - \mathbf{1}[h(s) \leq x] \dG_n(s) \right| \\
+        &= \lim_{n \to \infty} \left| \int_0^1 \underbrace{\Pr(X_n \leq x \mid nS_n = \lfloor ns \rfloor) - \mathbf{1}[h(s) \leq x]}_{\coloneqq r(s)} \dG_n(s) \right| \\
+        &\leq \lim_{n \to \infty} \int_0^1 \left| \Pr(X_n \leq x \mid nS_n = \lfloor ns \rfloor) - \mathbf{1}[h(s) \leq x] \right| \dG(s) \\
+        &+ \lim_{n \to \infty} \left| \int_0^1 r(s) \dG_n(s) - \int_0^1 r(s) \dG(s) \right| \\
         &= 0.
@@
 \section{Proofs of propositions and lemmas in the main text}
+\label{sec:proofs}
 
@@
 
+\begin{proof}[Proof of \cref{prop:one_sided_general}]
+    First, observe that $f$ is continuous on the compact set $[0, 1]$, and is therefore also bounded.
+    Furthermore,
+    \begin{align*}
+        \varphi_P^n = \frac{1}{n+1} \sum_{k=0}^n \Pr(|\mathcal{P}_P| / n = k) f(k/n) = \E[X_n].
+    \end{align*}
+    As $f$ is continuous and bounded, and $X_n \xrightarrow[]{d} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
+    Putting it together,
+    \begin{align*}
+        \lim_{n \to \infty} \varphi_P^n &= \frac{1}{n+1} \sum_{k=0}^n \Pr(|\mathcal{P}_P| / n = k) f(k/n) \\
+        &= \lim_{n \to \infty} \E[X_n] \\
+        &= \E[X] \\
+        &= \int_0^1 f(t) \dG(t).
+    \end{align*}
+    Furthermore, if $G$ is differentiable, then
+    \begin{align*}
+        \int_0^1 f(t) \dG(t) = \int_0^1 g(t) f(t) \dt.
+    \end{align*}
+\end{proof}
+
 \begin{proof}[Proof of \cref{prop:one_sided}]
@@
         &= \E[f(X)] \\
-        &= \int_0^1 f(t) \mathrm{d}G(t) \\
+        &= \int_0^1 f(t) \dG(t) \\
         &= \int_0^1 g(t)f(t) \dt

### 2023-11-21 src/paper/theory.tex
Rewrite rest of one-sided case

@@
     \begin{align*}
-        \varphi_A^\infty = \int_0^1 t G(t) f'(t) \dt.
+        \varphi_A^\infty = \int_0^1 G(t) f'(t) \dt.
     \end{align*}
@@
     \end{subfigure}
-    \caption{Distribution of value between player $P$ and the fringe}
+    \caption{Distribution of value between player $P$ (red) and the fringe (blue)}
     \label{fig:one_sided}
@@
 
-Now let us turn to an extension of the Shapley-value, where the symmetry of the players is relaxed: the weighted value.
-Imagine a general non-cooperative game $(N, v)$ with $N = \{1, \dots, n\}$.
-Assume that, in addition to the value function $v : 2^n \to \mathbb{R}$, the game is now also endowed with a weight system $\lambda \in \mathbb{R}^n$.
-The main idea behind the weighted value is that, in contrast to the Shapley-value, even players that have the same contribution to each possible coalition do not necessarily get the same value.
-
-These weights can be thought of as measures of innate bargaining power \parencite{shapley1953additive}, not reflected in the value function.
-Further support for this interpretation can be found in \textcite{hart1996bargaining}, demonstrating that in a certain alternating offer bargaining game, weights are related to the probability of each player making the offer.\footnote{
+This section investigates the case when players have different levels of innate bargaining power.
+One way to model this is by using weighted values \parencite{shapley1953additive}, which are a generalization of the Shapley value.
+The idea behind them is that, in addition to the set of players and the characteristic function, the game is also endowed with a weight system, which is a vector of non-negative numbers, one for each player.
+These weights determine how the value of a coalition is distributed amongst its members in the case when they are all equally important for the coalition.
+This is a way to relax the symmetry axiom of Shapley values, while retaining more structure than in the case of the more general random order values.
+
+These weights can be thought of as the measure of some innate bargaining power, not reflected in the value function.\footnote{
+    Although, this interpretation is not always appropriate.
+    As \textcite{owen1968communications} demonstrates, there are games where the weighted value is not monotone increasing in a player's weight.
+}
+Further support for this interpretation in certain games can be found in \textcite{hart1996bargaining}, demonstrating that in a certain alternating offer bargaining game, weights are related to the probability of each player making the offer.\footnote{
     For example, only one player having a positive value corresponds to them making take it or leave it offers.
 }
-
-Although the values of oceanic games (i.e.
-the limits of the Shapley values of their finite approximations in finite games) are well known in the relevant literature, there are no similar results for weighted (Shapley) values.
-While providing very general results in the form of \textcite[]{fogelman1980asymptotic} is outside the scope of the paper\footnote{
-    They show that the (within some constraints) any discretization of an oceanic game converges to the same value.
-} the results in this section still provide some new insights into the weighted values of oceanic games.
-In particular, I show that the weighted value of a game with one large and many small players converges to a rather simple and intuitive expression, if the size of the small players go to zero at the same rate.
+Additionally, \textcite{stole1996intra} provides an alternative microfoundation for the weighted value in the case of non-binding contracts.
 
@@
 Then, the probability of player $P$ having at most $k$ players of type $A$ before themselves is simply
-\begin{align*}
-    \Pr(X_n \leq k) = \prod_{j=k+1}^n \frac{j}{j + \lambda} .
-\end{align*}
+\begin{align}
+    \label{eq:entry_distr_discrete}
+    \Pr(X_n \leq k) = \prod_{j=k+1}^n \frac{j}{j + \lambda}.
+\end{align}
 The following lemma establishes the continuous analogue of this statement.
@@
 
-Now let us turn to the main proposition of this section: the weighted value of player $P$ can again be expressed as an integral over the share of fringe players, but now it is weighted according to the previous probability distribution.
-Depending on the shape of this distribution (which in turn depends on the weight $\lambda$), regions corresponding to different masses of fringe firms can be over or underweighted in this integral, leading to different values.
+Now we have everything we need to derive the weighted value of both types of players.
+Having \cref{eq:entry_distr_discrete} and \cref{lem:entry_distr} allows us to invoke \cref{prop:one_sided_general} to obtain the following proposition.\footnote{
+    \textcite{stole1996intra} also derives essentially the same expression for the equilibrium outcome of their bargaining game with unequal profit distribution, and assert that it is equal to the weighted value.
+}
+
 \begin{proposition}
@@
     where $g(t) = \lambda t^{\lambda - 1}$.
-\end{proposition}
+
+    Furthermore,
+    \begin{align*}
+        \varphi_A(\lambda, \infty) &= 1 - \int_0^1 g(t) f(t) \dt \\
+                                   &= \int_0^1 G(t) f'(t) \dt,
+    \end{align*}
+    where $G(t) = t^\lambda$.
+\end{proposition}
+
+Depending on the shape of this distribution (which in turn depends on the weight $\lambda$), regions corresponding to different masses of fringe firms can be over or underweighted in this integral, leading to different values.
 
@@
 
-\subsection{Multiple big players}
+\subsection{Shapley value with multiple big players}
 
@@
 Notably, as in the case of the weighted value, the share of player $P$ can again be expressed as an integral of $f$ and some weighting\footnote{
-    Weighting is not a completely precise term, as $h(t)$ does not integrate to one, and is therefore not a probability distribution in this case.
-    Nevertheless, it highlights the parallel between multiple big players and weighted values.
+    Weighting is not a completely precise term, as $h(t)$ does not integrate to one, and is therefore not a probability distribution in this case (\cref{fig:multiple_platforms}).
 } function $h(t)$, with the latter depending only on the number of big players.
@@
 
-\begin{corollary}
-    \label{cor:multiple_platforms}
-    The per-unit Shapley-value of the fringe is
-    \begin{align*}
-        \varphi_A^{\infty, m} = 1 - m\int_0^1 (1-t) ^ {m-1} f(t) \dt = \int_0^1 [1 - (1-t)^m] f'(t) \dt .
-    \end{align*}
-\end{corollary}
+As with proposition \ref{prop:one_sided}, this result also has a probabilistic interpretation.
+Let the location of the $m$ atoms be $t_1, \dots, t_m$, distributed independently and uniformly on the unit interval.
+The expected marginal contribution of $t_i$ is only positive whenever it is the first amongst the major players.
+That is, for any $t_i$, the probability if $P_i$ being the first is related to the cdf of the first order statistic from $n-1$ independent uniform distributions: $1 - (1-t)^{m-1}$.
 
@@
     \end{subfigure}
-    \caption{Illustration of the weighting function for various values of $m$ in the multiple big player case.}
+    \caption{Illustration of the weighting function for various values of $m$ in the multiple big player case -- individual big player.}
     \label{fig:multiple_platforms}
@@
 
-As with proposition \ref{prop:one_sided}, this result also has a probabilistic interpretation, and could have been obtained directly using the axiomatic approach.
-Let the location of the $m$ atoms be $t_1, \dots, t_m$, distributed independently and uniformly on the unit cube.
-The expected marginal contribution of $t_i$ is only positive whenever it is the first amongst the major players.
-That is, for any $t_i$, the probability if $P_i$ being the first is related to the cdf of the first order statistic from $n-1$ independent uniform distributions: $1 - (1-t)^{m-1}$.
-
-The next corollary again demonstrates that the predicted outcomes confirm intuition.
-As the major players become more and more substitutable, the portion of the surplus they can capture decreases, and the aggregated value of the fringe increases (\cref{fig:multiple_platforms}).
+Let us examine the total value of all the big players.
+Denote the aggregated value of players of type $P$ as $\varphi_{P}^{\infty, m} \coloneqq \sum_{j=1}^m\varphi_{P_j}^{\infty, m} = m\varphi_{P_i}^{\infty, m}$.
+It immediately follows from the previous proposition that
+\begin{align*}
+    \varphi_{P}^{\infty, m} = \int_0^1 g(t) f(t) \dt,
+\end{align*}
+where $g(t) = m (1-t) ^ {m-1}$.
+Notice that $g(t)$ now integrates to one, and is thus a probability distribution (\cref{fig:multiple_platforms_total}).
+Therefore, the Shapley value in the case of multiple, substitutable big players can be interpreted as a random order value with a single big player.
+The probability distribution for the corresponding random order value has a specific form, and its only parameter is the number of big players.
+Thus, all the results from the previous section apply to this case as well.
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=3.1, samples at={0, 0.02, 0.04, ..., 0.98, 1},
+                xtick={0, 1}, ytick={0, 1, 2, 3}, axis lines=left, xlabel={$t$}, legend pos=north west]
+                \addplot[ultra thick] {1};
+                \addplot[ultra thick, dashed] {2 * (1-x)};
+                \addplot[ultra thick, dotted] {3 * ((1-x)^2)};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{$g(t)$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.1, samples at={0, 0.02, ..., 0.98, 1},
+                xtick={0, 1}, ytick={0, 1}, axis lines=left, xlabel={$t$}, legend pos=north west]
+                \addplot[ultra thick] {x};
+                \addplot[ultra thick, dashed] {2 * (x - x^2/2)};
+                \addplot[ultra thick, dotted] {3 * (x - x^2 + x^3/3)};
+                \legend{$m = 1$, $m = 2$, $m = 3$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{$\int_0^t g(s) \ds$}
+    \end{subfigure}
+    \caption{Illustration of the weighting function for various values of $m$ in the multiple big player case -- total of big players.}
+    \label{fig:multiple_platforms_total}
+\end{figure}
+
+Now let us look at how the value of the big players and the fringe changes as a function of the number of the big players.
+Proposition \cref{cor:multiple_platforms_2} again confirms our intuition: more players means that they become more substitutable, and thus their bargaining power decreases.
+This not only means that the value of each individual big player decreases, but also that their total value goes down.
 
@@
 \end{corollary}
+
+Finally, let us show that the value of the fringe has a similar, marginal contribution-based interpretation as in the case of a single big player.
+
+\begin{corollary}
+    \label{cor:multiple_platforms}
+    The per-unit Shapley-value of the fringe is
+    \begin{align*}
+        \varphi_A^{\infty, m} = 1 - \int_0^1 f(t) \dG(t) = \int_0^1 G(t) f'(t) \dt ,
+    \end{align*}
+    where $G(t) = 1 - (1-t)^m$.
+\end{corollary}
+
+\subsection{Non-indispensable big player}
+
+As a final extension for the one-sided case, let us examine what happens when the big player is not indispensable.
+Assume that it provides some value to any coalition, but a coalition of fringe players can achieve a positive value without it.
+Formally, the value function is the following:
+\begin{align*}
+    v(S) = \begin{cases}
+        f_0\left(\frac{n_A(S)}{n}\right) & P \notin S \\
+        f\left(\frac{n_A(S)}{n}\right)   & \text{otherwise}.
+    \end{cases}
+\end{align*}
+
+As in the case of multiple big players, monotonicity is straightforward to establish.
+\begin{proposition}
+    The game is monotone if $f$ is increasing and $f(t) \geq f_0(t) \geq 0 \forall t$.
+\end{proposition}
+Also similarly, superadditivity is not straightforward in general.
+Therefore, the simultaneous formation of multiple coalitions must be excluded in this setting as well.
+
+On the other hand, the random order values and their limits are very straightforward to characterize.
+The value of the big player is still its average marginal contribution.
+The only difference is that this marginal contribution (conditional on $s$ share of the fringe coming before $P$) is not simply $f(s)$, but rather $f(s) - f_0(s)$.
+This is because the big player is not indispensable, and thus the fringe can achieve some value without it.
+
+\begin{proposition}
+    \label{prop:one_sided_non_indispensable}
+    Let $f$ be continuous on [0, 1].
+Furthermore, let us denote the random variable $\frac{|\mathcal{P}_P|}{n}$ as $X_n$.
+Assume that $X_n \xrightarrow[]{d} X$ with cdf $G_X(t)$ and (if exists) pdf $g(t)$.
+    Then
+    \begin{align*}
+        \varphi_P^\infty = \lim_{n \to \infty} \varphi_P^n = \int_0^1 f(t) \dG(t) = \int_0^1 g(t) [f(t) - f_0(t)] \dt,
+    \end{align*}
+    with the last equality holding if $X$ is a continuous random variable.
+\end{proposition}
+
+The value of the fringe is also similar to the baseline case, except now fringe players have a non-zero marginal contribution even when $P$ is not present.
+Therefore, there is an additional term in the integral, corresponding to the marginal value of the fringe when $P$ is not present.
+
+\begin{corollary}
+    \label{cor:fringe_value_non_indispensable}
+    The aggregated value of the fringe is
+    \begin{align*}
+        \varphi_A^\infty = f(1) - \int_0^1 f(t) - f_0(t) \dG(t).
+    \end{align*}
+    Furthermore, if $f$ and $f_0$ are differentiable on $[0, 1]$, then the value of the fringe can also be expressed as
+    \begin{align*}
+        \varphi_A^\infty = \int_0^1 G(t) f'(t) + (1 - G(t)) f'_0(t) \dt.
+    \end{align*}
+\end{corollary}
+
+It is clear that the value of the big player is decreasing in $f_0$ (\cref{fig:non_indispensable}).
+Consequently, the value of the fringe is increasing in $f_0$, which is essentially its outside option (what it can achieve without the big player).
+This is a natural result, and again, it is in line with what one would expect from bargaining theory.
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
+                    xtick={0, 1}, ytick={0}, xlabel={$s$}]
+                \addplot[name path=f, ultra thick] {x^0.5};
+                \addplot[name path=f0, ultra thick] {0.3 * x^0.5};
+                \node[anchor=north west] at (axis cs: .8, .8^0.5) {$f$};
+                \node[anchor=south west] at (axis cs: .8, .3*.8^0.5) {$f_0$};
+                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);
+
+                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and f0];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=f0 and bottom];
+
+                \node[anchor=north west, align=left] at (axis cs: .05, .95) {$\varphi_A^\infty$};
+                \node[anchor=south east, align=left] at (axis cs: .95, .05) {$\varphi_A^\infty$};
+                \node[anchor=north west, align=right] at (axis cs: .5, .5) {$\varphi_P^\infty$};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Fringe can achieve relatively little without $P$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
+                    xtick={0, 1}, ytick={0}, xlabel={$s$}]
+                \addplot[name path=f, ultra thick] {x^0.5};
+                \addplot[name path=f0, ultra thick] {0.7 * x^0.5};
+                \node[anchor=north west] at (axis cs: .8, .8^0.5) {$f$};
+                \node[anchor=north west] at (axis cs: .8, .7*.8^0.5) {$f_0$};
+                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);
+
+                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and f0];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=f0 and bottom];
+
+                \node[anchor=north west, align=left] at (axis cs: .05, .95) {$\varphi_A^\infty$};
+                \node[anchor=south east, align=left] at (axis cs: .95, .05) {$\varphi_A^\infty$};
+                \node[anchor=north west, align=right] at (axis cs: .5, .7) {$\varphi_P^\infty$};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Fringe can achieve relatively more without $P$}
+    \end{subfigure}
+    \caption{Distribution of value between player $P$ (blue) and the fringe (red)}
+    \label{fig:non_indispensable}
+\end{figure}
 

### 2023-11-21 src/paper/theory.tex
Reorganize many-sided case

@@
 
-Up until this point, we have considered games with a single type of small players.
+Up until this point, we have only considered games with a single type of small player.
 Now imagine that, in addition to player $P$, there are $L$ types of smaller players: $\{A^l_1, \dots, A^l_n\}$ where $1 \leq l \leq L$.
-As before, assume that $P$ is necessary for any coalition to have a positive value, and the small players are identical to each other within their types.
+As before, assume that $P$ is necessary for any coalition to have a positive value, and the small players are identical to each other \emph{within their types}.
 Formally, the game in coalitional form is now the following: the set of players is $N = \{P, A^1_1, \dots, A^1_n, \dots, A^L_1, \dots, A^L_n\}$ and the characteristic function is
@@
 However, player $P$ does not have to be in the ``middle'' of the transactions for this framework to be applicable.
-For example, it also captures the situation of a single upstream producer, a large number of downstream firms, and a similarly large number of customers, as long as both the customers and the downstream firms can participate in the bargaining process.
+For example, it also captures the situation of a single upstream producer, a large number of downstream firms, and a similarly large number of customers, as long as both the customers and the downstream firms can participate in the bargaining process.\footnote{
     A setting where these assumptions might be plausible is, for example, the new car market with a car producer, a number of independent dealerships, and customers who might engage in some form of negotiation.
+}
+Or, following \textcite{stole1996intra}, it could also be used to model bargaining between a firm and multiple types of workers.
 
@@
 Start by characterizing conditions for monotonicity and superadditivity to support the bargaining interpretation and the formation of the grand coalition.
-The conditions are the straightforward analogues of those from the one-sided case.
+It is easy to see that the conditions are the straightforward analogues of those from the one-sided case.
 \begin{proposition}
@@
 
-Next, let us obtain formulas for the values of the three types of players.
-It turns out that the limits of the Shapley-values (as $n \to \infty$) are still analytically tractable, and they also have a neat interpretation.
-\begin{proposition}
-    Let $f$ be continuous everywhere on $[0, 1]^L$.
-    Then,
-    \begin{align*}
-        \varphi_P^\infty & = \int_0^1 f(t, \dots, t) \dt                                 \\
-        \varphi_{A^l}^\infty & = \int_0^1 t \partial_l f(t, \dots, t) \dt.
-    \end{align*}
-\end{proposition}
-
-As the previous proposition shows, the value of each kind of player depends on their expected marginal contribution, i.e. the partial derivatives of $f$.
-Consequently, the value of the grand coalition can be decomposed into the Shapley-values of its members the following way:
-\begin{align*}
-    f(1, \dots, 1) = \underbrace{\int_0^1 f(t, \dots, t) \dt}_{\text{ player } P} + \sum_{l=1}^L \underbrace{\int_0^1 t \partial_l f(t, \dots, t) \dt}_{\text{players } A^ll}.
-\end{align*}
-This formulation makes it clear that values are intimately related to the marginal contributions of the players, captured by the partial derivatives of $f$ in the case of the various fringe players.
-
-One surprising element of the result is that one only has to integrate over the diagonal of the support  of $f$, and the value does not depend on off-diagonal parts of the $f$ fucntion.
-The intuition for that relies on a law-of-large-numbers-type reasoning.
-If the number of fringe players is large, then it is very unlikely that, after a random ordering, their proportion is too different on any interval.
-Consequently, when taking the expectation over all orderings, those with very unequal numbers of the various types have little impact on it.
+In the next subsections, I will first examine random order values, and then two important special cases: the Shapley value and the weighted value.
+
+% \subsection{Shapley value}
+
+% Let us obtain formulas for the values of the three types of players.
+% It turns out that the limits of the Shapley-values (as $n \to \infty$) are still analytically tractable, and they also have a neat interpretation.
+% \begin{proposition}
+%     Let $f$ be continuous everywhere on $[0, 1]^L$.
+%     Then,
+%     \begin{align*}
+%         \varphi_P^\infty & = \int_0^1 f(t, \dots, t) \dt                                 \\
+%         \varphi_{A^l}^\infty & = \int_0^1 t \partial_l f(t, \dots, t) \dt.
+%     \end{align*}
+% \end{proposition}
+
+% As the previous proposition shows, the value of each kind of player depends on their expected marginal contribution, i.e. the partial derivatives of $f$.
+% Consequently, the value of the grand coalition can be decomposed into the Shapley-values of its members the following way:
+% \begin{align*}
+%     f(1, \dots, 1) = \underbrace{\int_0^1 f(t, \dots, t) \dt}_{\text{ player } P} + \sum_{l=1}^L \underbrace{\int_0^1 t \partial_l f(t, \dots, t) \dt}_{\text{players } A^ll}.
+% \end{align*}
+% This formulation makes it clear that values are intimately related to the marginal contributions of the players, captured by the partial derivatives of $f$ in the case of the various fringe players.
+
+% One surprising element of the result is that one only has to integrate over the diagonal of the support  of $f$, and the value does not depend on off-diagonal parts of the $f$ fucntion.
+% The intuition for that relies on a law-of-large-numbers-type reasoning.
+% If the number of fringe players is large, then it is very unlikely that, after a random ordering, their proportion is too different on any interval.
+% Consequently, when taking the expectation over all orderings, those with very unequal numbers of the various types have little impact on it.
 
@@
 
-\begin{proof}[Proof of \cref{prop:many_sided_general}]
-    The proof mirrors that of \cref{prop:one_sided_general}.
-    First, note that the random order value can be expressed as follows:
-    \begin{align*}
-        \varphi_P^n &= \sum_{k_1=0}^n \dots \sum_{k_L=0}^n \Pr(n_{A_1}(\mathcal{P}_P) = k_1, \dots, n_{A_L}(\mathcal{P}_P) = k_L) f\left(\frac{k_1}{n}, \dots, \frac{k_L}{n}\right) \\
-        &= \sum_{k_1=0}^n \dots \sum_{k_L=0}^n \Pr(n X_n = (k_1, \dots, k_L)) f\left(\frac{k_1}{n}, \dots, \frac{k_L}{n}\right) \\
-        &= \sum_{k_1=0}^n \dots \sum_{k_L=0}^n \Pr \left( X_n = \left(\frac{k_1}{n}, \dots, \frac{k_L}{n}\right) \right) f \left(\frac{k_1}{n}, \dots, \frac{k_L}{n}\right) \\
-        &= \E[f(X_n)].
-    \end{align*}
-    Furthermore, as $f$ is continuous (and therefore bounded on $[0, 1]^L$), and $X_n \xrightarrow[]{d} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
-    Putting it together,
-    \begin{align*}
-        \lim_{n \to \infty} \varphi_P^n &= \lim_{n \to \infty} \E[f(X_n)] \\
-        &= \E[f(X)] \\
-        &= \int_0^1 \dots \int_0^1 f(t_1, \dots, t_L) \dG(t_1, \dots t_L).
-    \end{align*}
-    Finally, if $X$ is a continuous random variable, then
-    \begin{align*}
-        \int_0^1 \dots \int_0^1 f(t_1, \dots, t_L) \dG(t_1, \dots t_L) = \int_0^1\dots \int_0^1 g(t_1, \dots, t_L) f(t_1, \dots, t_L) \dt_1 \dots \dt_L.
-    \end{align*}
-\end{proof}
-
 While the above proposition is very general in terms of requirements on the permutation probabilities, it is not very tractable in practice, as one has to integrate over the entire unit hypercube.
@@
 
-\begin{proof}[Proof of \cref{lem:many_sided_manifold}]
-    Just like in the proof of \cref{prop:many_sided_general}, the random order value can be expressed as follows:
-    \begin{align*}
-        \varphi_P^n &= \E[f(X_n)].
-    \end{align*}
-    Furthermore, as $f$ is continuous and bounded on $[0, 1]^L$, and $X_n \xrightarrow[]{d} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
-    Therefore,
-    \begin{align*}
-        \lim_{n \to \infty} \varphi_P^n &= \lim_{n \to \infty} \E[f(X_n)] \\
-        &= \E[f(X)] \\
-        &= \E[f(a_1(\xi), \dots, a_L(\xi))] \\
-        &= \int_0^1 f(a_1(s), \dots a_L(s)) \mathrm{d}H(s).
-    \end{align*}
-\end{proof}
-
 \subsection{Shapley-value}
@@
 \end{proposition}
-
-\begin{proof}[Proof of \cref{prop:many_sided_shapley}]
-    Let us show than $X_n$ converges in distribution to the degenerate random variable $X = (U, \dots, U)$, where $U$ is uniformly distributed on $[0, 1]$.
-
-    Let us first define the random variable $S_n = \sum_l[X_n]_l / L$, the total number of small players placed before $P$.
-    Also, define $h(s) = (s, \dots, s)$.
-    Now let us look at the conditional distribution $n X_n | n L S_n = k$.
-    As all permutations have equal probability, this is the same as picking $kL$ firms from the set $N \setminus \{P\}$ without replacement.
-    The numbers of each type in this sample will follow a multinomial distribution with $kL$ trials, $L$ events and probabilities $1/L$.
-
-    Let us now show that $\Pr(X_n < x \mid S_n = s) \xrightarrow[]{\mathrm{u}} \mathbf{1}[(s, \dots, s) \leq x]$ on $s \in \mathrm{supp}(S_n)$.
-
-    First, observe that
-    \begin{align*}
-        [\E(n X_n | nS_n = \lfloor ns \rfloor)]_l &= \lfloor ns \rfloor, \\
-        [\Var(n X_n | nS_n = \lfloor ns \rfloor)]_l &= \lfloor ns \rfloor \frac{L-1}{L}
-    \end{align*}
-    for all $\quad l = 1, \dots, L$.
-    Consequently,
-    \begin{align*}
-        [\E(X_n | nS_n = \lfloor ns \rfloor)]_l &= \frac{\lfloor ns \rfloor}{n}, \\
-        [\Var(X_n | nS_n = \lfloor ns \rfloor)]_l &= \frac{\lfloor ns \rfloor}{n^2} \frac{L-1}{L}
-    \end{align*}
-    for all $\quad l = 1, \dots, L$.
-
-    Notice that, as $n \to \infty$, $[\Var(X_n | nS_n = \lfloor ns \rfloor)]_l \to 0$.
-    Furthermore, $\E(X_n | nS_n = \lfloor ns \rfloor) \to h(s)$.
-    Thus, for any $s \in [0, 1], X_n | nS_n = \lfloor ns \rfloor \xrightarrow[]{L^2} h(s)$.
-
-    % Notice that, regardless of $s$, the variance $\Var(X_n | S_n = s)$ is bounded by $\frac{1}{n}$.
-    % By Chebyshev's inequality,
-    % \begin{align*}
-    %     \Pr( \| X_n - (s, \dots, s) \| > \epsilon \mid S_n = s) \leq \frac{L}{n \epsilon^2}.
-    % \end{align*}
-
-    Let us now turn to the random variable $S_n$.
-    Observe that because the probability of each permutation is the same, player $P$ has the same probability of being in any position.
-    In other words, $S_n$ follows a uniform distribution on $0, \frac{1}{nL}, \frac{2}{nL} \dots, 1$.
-    Consequently, $S_n$ converges in distribution to the uniform distribution $U[0, 1]$.
-
-    I have now shown that the assumptions of \cref{lem:convergence_to_manifold} are satisfied.
-    % TODO
-
-    Then, by \cref{lem:many_sided_manifold}, the Shapley-value is
-    \begin{align*}
-        \varphi_P^\infty & = \int_0^1 f(t, \dots, t) \dt.
-    \end{align*}
-
-\end{proof}
-
-\begin{lemma}
-    \label{lem:convergence_to_manifold}
-    Consider the random vector $X_n$ with values from $[0, 1]^L$.
-    Let $S_n = \sum_l[X_n]_l / L$, with the cumulative distribution function $G_n(s)$.
-    Assume that for every $s \in [0, 1]$, $X_n \mid n S_n = \lfloor ns \rfloor \xrightarrow[]{L^1} h(s)$ where $h(s)$ is some continuous function.
-    Let $S_n \xrightarrow[]{d} S$.
-    Then $X_n \xrightarrow[]{d} h(S)$.
-\end{lemma}
-
-\begin{proof}[Proof of \cref{lem:convergence_to_manifold}]
-    We have to show that
-    \begin{align*}
-        \lim_{n \to \infty} \Pr(X_n \leq x) = \Pr(h(S) \leq x).
-    \end{align*}
-    for any $x$ where the cdf of $h(S)$ is continuous.
-
-    Let us start by conditioning on $S_n$:
-    \begin{align*}
-        \Pr(X_n \leq x) = \int_0^1 \Pr(X_n \leq x \mid S_n = s) \dG_n(s).
-    \end{align*}
-    Now consider the following:
-    \begin{align*}
-        \lim_{n \to \infty} \left| \Pr(X_n \leq x) - \Pr(h(S) \leq x) \right| &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \dG_n(s) - \Pr(h(S) \leq x) \right| \\
-        &\leq \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \dG_n(s) - \Pr(h(S_n) \leq x) \right| \\
-        &+ \lim_{n \to \infty} \left| \Pr(h(S_n) \leq x) - \Pr(h(S) \leq x) \right|
-    \end{align*}
-    for all $x \in [0, 1]^L$.
-    I will show that both limits on the right-hand side are zero.
-
-    Let us start with the first term.
-    \begin{align*}
-        \lim_{n \to \infty} &\left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \dG_n(s) - \Pr(h(S_n) \leq x) \right| \\
-        &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \dG_n(s) - \int_0^1 \mathbf{1}[h(s) \leq s] \dG_n(s) \right| \\
-        &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) - \mathbf{1}[h(s) \leq x] \dG_n(s) \right| \\
-        &= \lim_{n \to \infty} \left| \int_0^1 \underbrace{\Pr(X_n \leq x \mid nS_n = \lfloor ns \rfloor) - \mathbf{1}[h(s) \leq x]}_{\coloneqq r(s)} \dG_n(s) \right| \\
-        &\leq \lim_{n \to \infty} \int_0^1 \left| \Pr(X_n \leq x \mid nS_n = \lfloor ns \rfloor) - \mathbf{1}[h(s) \leq x] \right| \dG(s) \\
-        &+ \lim_{n \to \infty} \left| \int_0^1 r(s) \dG_n(s) - \int_0^1 r(s) \dG(s) \right| \\
-        &= 0.
-    \end{align*}
-    The first limit is zero because $X_n \mid n S_n = \lfloor ns \rfloor \xrightarrow[]{L^1} h(s)$.
-    The second limit is zero because of the continuous mapping theorem, as $S_n \xrightarrow[]{p} S$ and $\Pr_S(s : r\text{ is not continuous at }s)= 0$.
-
-    All that remains is to show that the second term is also zero.
-    This simply follows from the continuous mapping theorem, as $f$ is continuous and $S_n \xrightarrow[]{d} S$.
-\end{proof}
 
@@
 
-\section{Proofs of propositions and lemmas in the main text}
+\begin{lemma}
+    \label{lem:convergence_to_manifold}
+    Consider the random vector $X_n$ with values from $[0, 1]^L$.
+    Let $S_n = \sum_l[X_n]_l / L$, with the cumulative distribution function $G_n(s)$.
+    Assume that for every $s \in [0, 1]$, $X_n \mid n S_n = \lfloor ns \rfloor \xrightarrow[]{L^1} h(s)$ where $h(s)$ is some continuous function.
+    Let $S_n \xrightarrow[]{d} S$.
+    Then $X_n \xrightarrow[]{d} h(S)$.
+\end{lemma}
+
+\begin{proof}[Proof of \cref{lem:convergence_to_manifold}]
+    We have to show that
+    \begin{align*}
+        \lim_{n \to \infty} \Pr(X_n \leq x) = \Pr(h(S) \leq x).
+    \end{align*}
+    for any $x$ where the cdf of $h(S)$ is continuous.
+
+    Let us start by conditioning on $S_n$:
+    \begin{align*}
+        \Pr(X_n \leq x) = \int_0^1 \Pr(X_n \leq x \mid S_n = s) \dG_n(s).
+    \end{align*}
+    Now consider the following:
+    \begin{align*}
+        \lim_{n \to \infty} \left| \Pr(X_n \leq x) - \Pr(h(S) \leq x) \right| &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \dG_n(s) - \Pr(h(S) \leq x) \right| \\
+        &\leq \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \dG_n(s) - \Pr(h(S_n) \leq x) \right| \\
+        &+ \lim_{n \to \infty} \left| \Pr(h(S_n) \leq x) - \Pr(h(S) \leq x) \right|
+    \end{align*}
+    for all $x \in [0, 1]^L$.
+    I will show that both limits on the right-hand side are zero.
+
+    Let us start with the first term.
+    \begin{align*}
+        \lim_{n \to \infty} &\left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \dG_n(s) - \Pr(h(S_n) \leq x) \right| \\
+        &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \dG_n(s) - \int_0^1 \mathbf{1}[h(s) \leq s] \dG_n(s) \right| \\
+        &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) - \mathbf{1}[h(s) \leq x] \dG_n(s) \right| \\
+        &= \lim_{n \to \infty} \left| \int_0^1 \underbrace{\Pr(X_n \leq x \mid nS_n = \lfloor ns \rfloor) - \mathbf{1}[h(s) \leq x]}_{\coloneqq r(s)} \dG_n(s) \right| \\
+        &\leq \lim_{n \to \infty} \int_0^1 \left| \Pr(X_n \leq x \mid nS_n = \lfloor ns \rfloor) - \mathbf{1}[h(s) \leq x] \right| \dG(s) \\
+        &+ \lim_{n \to \infty} \left| \int_0^1 r(s) \dG_n(s) - \int_0^1 r(s) \dG(s) \right| \\
+        &= 0.
+    \end{align*}
+    The first limit is zero because $X_n \mid n S_n = \lfloor ns \rfloor \xrightarrow[]{L^1} h(s)$.
+    The second limit is zero because of the continuous mapping theorem, as $S_n \xrightarrow[]{p} S$ and $\Pr_S(s : r\text{ is not continuous at }s)= 0$.
+
+    All that remains is to show that the second term is also zero.
+    This simply follows from the continuous mapping theorem, as $f$ is continuous and $S_n \xrightarrow[]{d} S$.
+\end{proof}
+
+\section{Proofs of propositions in the main text}
 \label{sec:proofs}
@@
 
+\begin{proof}[Proof of \cref{prop:many_sided_general}]
+    The proof mirrors that of \cref{prop:one_sided_general}.
+    First, note that the random order value can be expressed as follows:
+    \begin{align*}
+        \varphi_P^n &= \sum_{k_1=0}^n \dots \sum_{k_L=0}^n \Pr(n_{A_1}(\mathcal{P}_P) = k_1, \dots, n_{A_L}(\mathcal{P}_P) = k_L) f\left(\frac{k_1}{n}, \dots, \frac{k_L}{n}\right) \\
+        &= \sum_{k_1=0}^n \dots \sum_{k_L=0}^n \Pr(n X_n = (k_1, \dots, k_L)) f\left(\frac{k_1}{n}, \dots, \frac{k_L}{n}\right) \\
+        &= \sum_{k_1=0}^n \dots \sum_{k_L=0}^n \Pr \left( X_n = \left(\frac{k_1}{n}, \dots, \frac{k_L}{n}\right) \right) f \left(\frac{k_1}{n}, \dots, \frac{k_L}{n}\right) \\
+        &= \E[f(X_n)].
+    \end{align*}
+    Furthermore, as $f$ is continuous (and therefore bounded on $[0, 1]^L$), and $X_n \xrightarrow[]{d} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
+    Putting it together,
+    \begin{align*}
+        \lim_{n \to \infty} \varphi_P^n &= \lim_{n \to \infty} \E[f(X_n)] \\
+        &= \E[f(X)] \\
+        &= \int_0^1 \dots \int_0^1 f(t_1, \dots, t_L) \dG(t_1, \dots t_L).
+    \end{align*}
+    Finally, if $X$ is a continuous random variable, then
+    \begin{align*}
+        \int_0^1 \dots \int_0^1 f(t_1, \dots, t_L) \dG(t_1, \dots t_L) = \int_0^1\dots \int_0^1 g(t_1, \dots, t_L) f(t_1, \dots, t_L) \dt_1 \dots \dt_L.
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of \cref{lem:many_sided_manifold}]
+    Just like in the proof of \cref{prop:many_sided_general}, the random order value can be expressed as follows:
+    \begin{align*}
+        \varphi_P^n &= \E[f(X_n)].
+    \end{align*}
+    Furthermore, as $f$ is continuous and bounded on $[0, 1]^L$, and $X_n \xrightarrow[]{d} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
+    Therefore,
+    \begin{align*}
+        \lim_{n \to \infty} \varphi_P^n &= \lim_{n \to \infty} \E[f(X_n)] \\
+        &= \E[f(X)] \\
+        &= \E[f(a_1(\xi), \dots, a_L(\xi))] \\
+        &= \int_0^1 f(a_1(s), \dots a_L(s)) \mathrm{d}H(s).
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:many_sided_shapley}]
+    Let us show than $X_n$ converges in distribution to the degenerate random variable $X = (U, \dots, U)$, where $U$ is uniformly distributed on $[0, 1]$.
+
+    Let us first define the random variable $S_n = \sum_l[X_n]_l / L$, the total number of small players placed before $P$.
+    Also, define $h(s) = (s, \dots, s)$.
+    Now let us look at the conditional distribution $n X_n | n L S_n = k$.
+    As all permutations have equal probability, this is the same as picking $kL$ firms from the set $N \setminus \{P\}$ without replacement.
+    The numbers of each type in this sample will follow a multinomial distribution with $kL$ trials, $L$ events and probabilities $1/L$.
+
+    Let us now show that $\Pr(X_n < x \mid S_n = s) \xrightarrow[]{\mathrm{u}} \mathbf{1}[(s, \dots, s) \leq x]$ on $s \in \mathrm{supp}(S_n)$.
+
+    First, observe that
+    \begin{align*}
+        [\E(n X_n | nS_n = \lfloor ns \rfloor)]_l &= \lfloor ns \rfloor, \\
+        [\Var(n X_n | nS_n = \lfloor ns \rfloor)]_l &= \lfloor ns \rfloor \frac{L-1}{L}
+    \end{align*}
+    for all $\quad l = 1, \dots, L$.
+    Consequently,
+    \begin{align*}
+        [\E(X_n | nS_n = \lfloor ns \rfloor)]_l &= \frac{\lfloor ns \rfloor}{n}, \\
+        [\Var(X_n | nS_n = \lfloor ns \rfloor)]_l &= \frac{\lfloor ns \rfloor}{n^2} \frac{L-1}{L}
+    \end{align*}
+    for all $\quad l = 1, \dots, L$.
+
+    Notice that, as $n \to \infty$, $[\Var(X_n | nS_n = \lfloor ns \rfloor)]_l \to 0$.
+    Furthermore, $\E(X_n | nS_n = \lfloor ns \rfloor) \to h(s)$.
+    Thus, for any $s \in [0, 1], X_n | nS_n = \lfloor ns \rfloor \xrightarrow[]{L^2} h(s)$.
+
+    Let us now turn to the random variable $S_n$.
+    Observe that because the probability of each permutation is the same, player $P$ has the same probability of being in any position.
+    In other words, $S_n$ follows a uniform distribution on $0, \frac{1}{nL}, \frac{2}{nL} \dots, 1$.
+    Consequently, $S_n$ converges in distribution to the uniform distribution $U[0, 1]$.
+
+    I have now shown that the assumptions of \cref{lem:convergence_to_manifold} are satisfied.
+    % TODO
+
+    Then, by \cref{lem:many_sided_manifold}, the Shapley-value is
+    \begin{align*}
+        \varphi_P^\infty & = \int_0^1 f(t, \dots, t) \dt.
+    \end{align*}
+
+\end{proof}
+
 \end{document}

### 2023-11-22 src/paper/theory.tex
Add one-sided shapley example

@@
 
+\paragraph{Example: power function.}
+
+Let us illustrate the results of this section with a simple example.
+Consider the case when $f(n) = n^\alpha$, for some $\alpha > 0$.
+Assume that the bargaining takes place between player $P$ and a measure $\bar{n}$ of fringe players.
+Thus, the value that the grand coalition can achieve is $\bar{n}^\alpha$.
+
+\Cref{prop:many_sided_shapley} shows that the value of player $P$ in this case is
+\begin{align*}
+    \varphi_P^\infty(\bar{n}) = \int_0^1 (s \bar{n})^\alpha = \frac{1}{\alpha + 1} \bar{n}^\alpha,
+\end{align*}
+while the fringe gets the rest, i.e.,
+\begin{align*}
+    \varphi_A^\infty(\bar{n}) = \bar{n}^\alpha - \frac{1}{\alpha + 1} \bar{n}^\alpha = \frac{\alpha}{\alpha + 1} \bar{n}^\alpha.
+\end{align*}
+
+In words, regardless of the value of $\bar{n}$, the two types of players share the total value in the same proportion.
+This proportion depends on the parameter $\alpha$ (\cref{fig:power_function_example}), which can be interpreted as the degree of substitutability between the fringe players.
+More specifically, the higher $\alpha$ is, the more complementary the fringe players are to each other, and the larger the share they obtain.
+In the limit, when $\alpha \to \infty$, the fringe obtains all the value, as essentially all players become indispensable, and share the total value equally.
+On the other hand, when $\alpha \to 0$, the big players can appropriate all the value.
+
+\begin{figure}
+    \centering
+    \begin{tikzpicture}[scale=0.8]
+        \begin{axis}[xmin=0, xmax=5, ymin=0, ymax=1, samples at={0, 0.05, ..., 4.95, 5},
+                xtick={0, 1, 2, 3, 4, 5}, ytick={0, 1},
+                xlabel={Complementarity between fringe players ($\alpha$)}, ylabel={Share of the fringe}]
+            \addplot[name path=f, ultra thick] {x / (1 + x)};
+            \node[anchor=north west] at (axis cs: 3, 3/4) {$\frac{\varphi_A^\infty(\bar{n})}{f(\bar{n})}$};
+            \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+            \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);
+        \end{axis}
+    \end{tikzpicture}
+    \caption{Example: share of the fringe as a function of $\alpha$ (degree of complementarity between fringe players)}
+    \label{fig:power_function_example}
+\end{figure}
+
 \subsection{Weighted values}
@@
     \end{align*}
+    Furthermore, the value of fringe $l$ has the following limit:
+    \begin{align*}
+        \varphi_{A^l}^\infty = \lim_{n \to \infty} \varphi_{A^l}^n &= \int_0^1 H(s) \partial_l f(a_1(s), \dots a_L(s)) \ds.        
+    \end{align*}
 \end{lemma}
@@
     \end{align*}
+    and
+    \begin{align*}
+        \varphi_{A^l}^\infty = \int_0^1 t \partial_l f(t, \dots, t) \dt.
+    \end{align*}
 \end{proposition}
@@
     \begin{align*}
-        \varphi_P^\infty & = \int_0^1 f(t^{\lambda_1}, \dots, t^{\lambda^L}) \lambda_P t^{\lambda_P} \dt.
+        \varphi_P^\infty & = \int_0^1 \lambda_P t^{\lambda_P - 1} f(t^{\lambda_1}, \dots, t^{\lambda^L}) \dt
+    \end{align*}
+    and
+    \begin{align*}
+        \varphi_{A^l}^\infty & = \int_0^1 t^{\lambda_P} \partial_l f(t^{\lambda_1}, \dots, t^{\lambda^L}) \dt.
     \end{align*}
 \end{proposition}
-
-\begin{proof}[Proof of \cref{prop:many_sided_weighted}]
-    The proof uses the same approach as that of \cref{prop:many_sided_shapley}.
-    I will show that $X_n \xrightarrow[]{d} h(\xi)$, where $h(s) = (s^{\lambda_1}, \dots, s^{\lambda_L})$, and $\xi$ is a random variable with cdf $G(s) = s^{\lambda_P}$, and then rely on \cref{lem:many_sided_manifold}.
-
-\end{proof}
 
@@
 
+\begin{proof}[Proof of \cref{prop:many_sided_weighted}]
+    The proof uses the same approach as that of \cref{prop:many_sided_shapley}.
+    I will show that $X_n \xrightarrow[]{d} h(\xi)$, where $h(s) = (s^{\lambda_1}, \dots, s^{\lambda_L})$, and $\xi$ is a random variable with cdf $G(s) = s^{\lambda_P}$, and then rely on \cref{lem:many_sided_manifold}.
+
+\end{proof}
+
 \end{document}

### 2023-11-22 src/paper/theory.tex
Rewrite multi-sided case

@@
 
-While the above proposition is very general in terms of requirements on the permutation probabilities, it is not very tractable in practice, as one has to integrate over the entire unit hypercube.
+While the above proposition is very general in terms of permutation probabilities, it is not very tractable in practice, as one has to integrate over the entire unit hypercube.
 It would be much more convenient, if one only had to be concerned with a one-dimensional manifold within the hypercube instead.
-It turns out, that for a couple of important cases (namely, the Shapley-value and the weighted value) it is indeed the case.
-
-Let us start by establishing a general result, after which I will show that the Shapley-value and the weighted value are special cases of it.
+It turns out, that for a couple of important cases (namely, the Shapley value and the weighted value) it is indeed the case.
+
+Let us start by establishing a general result, after which I will show that the Shapley value and the weighted value are special cases of it.
 
@@
     \end{align*}
-    Furthermore, the value of fringe $l$ has the following limit:
+    Furthermore, if $f$'s partial derivatives exist on $\{(a_1(t), \dots, a_L(t)) : t \in [0, 1]\}$ the value of fringe $l$ has the following limit:
     \begin{align*}
@@
 
+The lemma above states, that -- if its assumptions are satisfied -- one only has to be concerned with just a tiny fraction of the production function $f$.
+Namely, we only need to know how the function behaves on the set $\{(a_1(t), \dots, a_L(t)) : t \in [0, 1]\} \subset [0, 1]^L$.\footnote{
+    For the fringe players, we also need the partial derivatives.
+    Therefore, technically, the behavior of $f$ on some arbitrarily small neighborhood of the set also matters.
+}
+This result is essentially a generalization of the diagonal formula from \textcite{aumann2015values} or \textcite{stole1996intra} to the case where permutation probabilities are not uniform.
+The intuition behind it is the same: if the number of fringe players is large, then it is very unlikely that, after a random ordering, their proportion is very different from \emph{what it should be}.
+The main difference is that, in this case, the ``what it should be'' part is not uniform, but rather given by the $a_l$ functions.
+
+In the remainder of this section, I will show that the Shapley value satisfy the assumptions of the above lemma, and thus the limit of those values can be expressed as an integral over a one-dimensional path.
+
 \subsection{Shapley-value}
+
+Now let us turn our attention to the Shapley-value.
+As mentioned before, due to the uniformity of the permutation probabilities, we get a diagonal formula in this case.
+\Cref{prop:many_sided_shapley} establishes this result formally.
 
@@
 
+As displayed on \cref{fig:many_sided_shapley}, The value of player $P$ is the integral of $f$ over the diagonal of the unit hypercube.\footnote{
+    \textcite{stole1996intra} also obtain this expression for the limiting case of their bargaining game.
+    The proof of this proposition demonstrates a way to obtain it as a limit of the Shapley value of the finite games.
+}
+Furthermore, this result also demonstrates how the rest of the value is divided amongst the fringe players.
+Namely, those having higher marginal contributions along the diagonal get a larger share of the value.
+
+\begin{figure}
+    \centering
+    \begin{tikzpicture}
+        \begin{axis}[
+            xlabel={$a_1$}, ylabel={$a_2$}, zlabel={$f(a_1,, a_2)$},
+            domain=0:1, y domain=0:1,
+            zmin=0, zmax=1,
+            xtick={0, 1}, ytick={0, 1}, ztick={0, 1},
+            zticklabels={0, {$f(1, 1)$}}, % use the literal expression as a label
+            view={60}{30}
+        ]
+            % plot the function
+            \addplot3[surf, shader=flat, draw=none, name path=f, fill opacity=0] {x*y};
+            % highlight the diagonal
+            \addplot3[black, name path=diagonal, ultra thick, domain=0:1, samples=100, samples y=0] ({x}, {x}, {0});
+            \addplot3[black, name path=f_diagonal, ultra thick, domain=0:1, samples=100, samples y=0] ({x}, {x}, {x^2});
+            \addplot[blue, fill opacity=0.5] fill between[of=diagonal and f_diagonal];
+        \end{axis}
+    \end{tikzpicture}
+    \caption{Illustration of the Shapley value in the case of two types of fringe players.
+The blue area corresponds to the value of the platform (with a scaling factor of $\sqrt{2}$ to account for the length of the diagonal)}
+    \label{fig:many_sided_shapley}
+\end{figure}
+
 \subsection{Weighted value}
@@
 \end{proposition}
+
+The intuition is the following.
+A higher weight for a player means that it has a higher chance of being relatively late in a random permutation.
+Therefore, conditional on $s$ proportion of the fringe coming before $P$, the various types' proportions do not reflect their population shares ($1/L$).
+For any $s \in (0, 1)$, the proportion of fringe players with a higher weight is lower than their population share, while the proportion of fringe players with a lower weight is higher than their population share.
+\Cref{fig:many_sided_weighted} illustrates this phenomenon in the case of two types of fringe players.
+
+Finally, player $P$'s probability of coming after $s$ proportion of the fringe is also not uniform, but rather influenced by the relationship between its own and the fringe players' weights.
+Therefore, the integral is not taken with respect to the uniform distribution, but rather one resembling that of \cref{prop:one_sided_weighted}.
+The result is the following: when the big player has a higher weight, its chances of being relatively late in the ordering are higher, and thus -- due to $f$ being monotone increasing -- its value is higher.
+The following, simple corollary formalizes this idea.
+
+\begin{figure}
+    \centering
+    \begin{tikzpicture}
+        \begin{axis}[
+            xlabel={$a_1$}, ylabel={$a_2$}, zlabel={$f(a_1,, a_2)$},
+            domain=0:1, y domain=0:1,
+            zmin=0, zmax=1,
+            xtick={0, 1}, ytick={0, 1}, ztick={0, 1},
+            zticklabels={0, {$f(1, 1)$}}, % use the literal expression as a label
+            view={60}{30}
+        ]
+            % plot the function
+            \addplot3[surf, shader=flat, draw=none, name path=f, fill opacity=0] {x*y};
+            % highlight the diagonal
+            \addplot3[black, name path=diagonal, ultra thick, domain=0:1, samples=100, samples y=0] ({x}, {x^3}, {0});
+            \addplot3[black, name path=f_diagonal, ultra thick, domain=0:1, samples=100, samples y=0] ({x}, {x^3}, {x^4});
+            \addplot[blue, fill opacity=0.5] fill between[of=diagonal and f_diagonal];
+        \end{axis}
+    \end{tikzpicture}
+    \caption{Illustration of the weighted value in the case of two types of fringe players.
+Players of type $A^2$ have a higher weight than those of type $A^1$, thus the integral is not taken over the diagonal.
+The blue area corresponds to the value of the platform (the area have to be scaled so that the length of the path integrated over is one)}
+    \label{fig:many_sided_weighted}
+\end{figure}
+
+\begin{corollary}
+    \label{cor:platform_value_multiple_sides_weighted}
+    $\varphi_P^\infty$ is increasing in $\lambda_P$ unless $f$ is constant.
+\end{corollary}
 

### 2023-11-22 src/paper/theory.tex
Remove example application

@@
 
-\section{Example Application}
-
-This section demonstrates the proposed cooperative approach via a model of a vertical market.
-Note, that this is not a full-fledged model, and many factors are exogenous.
-However, it is sufficient to illustrate the advantages of the framework presented in this paper: most notably, its analytical tractability and that it captures what intuitively feels like bargaining power.
-
-Consider a market in the vein of \textcite{hart1990property}, but with a finite number of upstream and a continuum of downstream firms.
-Furthermore, let us model production and sales in a reduced form, without going into the micro-foundations of the profit functions.
-Finally, let us assume that profits are shared according to players' Shapley-values.
-
-In the rest of this section, I will examine the effect of various market structures on the profit distribution.
-I start by looking at the case of a single upstream producer, with no direct acces to the downstream market.
-I then contrast this with two scenarios in which the upstream producer acquires a way to directly sell to the final consumers: either by vertical integration (merging with some share of the downstream firms), or by creating a completely new, downstream division within itself.
-
-As this model is only supposed to be an illustration, I will focus on simplicity rather than realism.
-Furthermore, I will not endogenize certain choices, such as entry, or the actual merger decisions.
-Nevertheless, some of the results are suggestive of what might happen in an applied, more fully specified model.
-
-\subsection{Benchmark case}
-
-Let us start by looking at the simplest case: one upstream producer, no direct access to the downstream market.
-Assume that without the upstream producer, the downstream firms cannot produce anything, and thus total industry profits are zero.
-On the other hand, if the upstream producer and $t$ fraction of the downstream firms create an agreement, then total industry profits are given by the function $f(t)$.\footnote{
-    This reduced-form profit function can be given microfoundations in many ways.
-    For an example, see \textcite{stancsics2023hybrid}.
-}
-Furthermore, the following assumption guarantees ensures that the game is superadditive, therefore it actually makes sense to have every downstream firm in the coalition.\footnote{
-    TODO: elaborate on what this assumption entails.
-}
-\begin{assumption}
-    Let us assume that $f$ is continuous and increasing in $t$.
-\end{assumption}
-
-As noted before, profits are distributed according to players' Shapley values.
-Consequently, it follows from \cref{prop:one_sided} that the profits of the upstream producer and the downstream mass of firms are
-\begin{align*}
-    \pi_P^b & = \int_0^1 f(t) \dt, \\
-    \pi_A^b & = f(1) - \int_0^1 f(t) \dt,
-\end{align*}
-respectively.
-
-\subsection{Vertical integration}
-
-Let us now consider the case in which the upstream producer merges with some fraction $\alpha$ of the downstream firms.
-The total profits are the same as before, namely, $f(1)$.\footnote{
-    TODO: do I need a footnote here?
-}
-However, the profit distribution is now different.
-New shares can be calculated as follows:
-\begin{align}
-    \pi_{P}^m & = \frac{1}{1 - \alpha} \int_\alpha^1 f(t) \dt, \\
-    \pi_{A}^m & = f(1) - \frac{1}{1 - \alpha} \int_\alpha^1 f(t) \dt .
-\end{align}
-
-Clearly, the upstream producer gets a larger share than before, while the remaining downstream firms capture a smaller share.
-This is intuitive, as the upstream producer now depends on the remaining downstream sellers to a lesser extent.
-However, it's worth examining whether this increase is large enough in the sense that the now hybrid upstream producer's profit is higher than the sum of its profit and $\alpha$ fraction of the downstream firms' profit from the benchmark case.
-The participants only have an incentive to merge if this is the case.
-It turns out that this depends on the shape of the profit function.\footnote{
-    This way of modeling vertical integration assumes that the upstream firm's innate bargaining power is not affected by the merger.
-    In the terms of some non-cooperative bargaining model, such as \textcite{hart1996bargaining}, it means that the non-acquired downstream firms get a higher probability of proposing allocations.
-    It could be interesting to see how the results change when the upstream firm's also obtains the acquired downstream firms' innate bargaining power, and profits are distributed according to weighted Shapley values.
-}
-
-\begin{proposition}
-    \label{prop:vertical_integration}
-    If $f$ is concave (convex) on $[0, 1]$, then $\pi_P^m \geq \pi_P^b + \alpha \pi_A^b$ ($\pi_P^m \leq \pi_P^b + \alpha \pi_A^b$). 
-\end{proposition}
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.8]
-            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-                xtick={0, 1}, ytick={0, 1}, yticklabels={0, f(1)},
-                axis lines=left, xlabel={$s$}]
-                \addplot[name path=f, dashed, black] {sqrt(x)};
-                \addplot[name path=tildef, black, ultra thick] {sqrt(0.3+0.7*x)};
-                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
-                \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
-                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);
-
-                \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
-                \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];
-
-                \node[anchor=north west] at (axis cs: .05, .95) {Downstream};
-                \node[anchor=south east] at (axis cs: .95, .05) {Upstream};
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Concave case}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.8]
-            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-                xtick={0, 1}, ytick={0, 1}, yticklabels={0, f(1)},
-                axis lines=left, xlabel={$s$}]
-                \addplot[name path=f, dashed, black] {(x)^1.5};
-                \addplot[name path=tildef, black, ultra thick] {(0.3+0.7*x)^1.5};
-                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
-                \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
-                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);
-
-                \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
-                \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];
-
-                \node[anchor=north west] at (axis cs: .05, .95) {Downstream};
-                \node[anchor=south east] at (axis cs: .95, .05) {Upstream};
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Convex case}
-    \end{subfigure}
-    \caption{Illustration of \cref{prop:vertical_integration}}
-    \label{fig:vertical_intergration}
-\end{figure}
-
-The intuition is that when $f$ is concave, then obtaining some fraction of the firms lets it create a (comparatively) large share of the total possible profits by itself, and its bargaining position is considerably strengthened.
-In comparison, when $f$ is convex, then the upstream producer still has a large need for the rest of the downstream firms, even when it acquires some of them.
-The bottom line is that industries which are characterized by the downstream firms being relatively substitutable are more susceptible to consolidation.
-
-\subsection{Upstream firm builds downstream capacity}
-
-Now let us consider another way of getting direct downstream access: instead of acquiring some of the existing downstream firms, the upstream producer creates new downstream capacity from scratch.
-In contrast to the previous case, the total size of the pie also changes.
-Let's assume that the upstream firm's downstream capacity is equal to that of $\alpha$ measure of the downstream firms.
-Then, the total profits when everyone agrees to participate is given by $f(1 + \alpha)$, which is larger than $f(1)$ before.
-
-As before, let us examine the distribution of the profits in this case as well:
-\begin{align*}
-    \pi_{P}^c & = \int_0^1 f(t + \alpha) \dt, \\
-    \pi_{A}^c & = f(1 + \alpha) - \int_0^1 f(t + \alpha) \dt .
-\end{align*}
-Similarly to the vertical merger case, the now hybrid upstream producer's profits increase with the size of its downstream capacity.
-However, it is not obvious how the downstream's profit changes.
-The next proposition shows that it, again, depends on the shape of the profit function.
-\begin{proposition}
-    \label{prop:downstream_capacity}
-    If $f$ is concave (convex) on $[0, 1+\alpha]$, then $\pi_A^m \geq \pi_A^b$ ($\pi_A^m \leq \pi_A^b$). 
-\end{proposition}
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.8]
-            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.14, samples at={0, 0.02, ..., 0.98, 1},
-                xtick={0, 1}, ytick={0, 1, 1.14}, yticklabels={$0$, $f(1)$, $f(1 + \alpha)$},
-                axis lines=left, xlabel={$s$}]
-                \addplot[name path=f, dashed, black] {sqrt(x)};
-                \addplot[name path=tildef, black, ultra thick] {sqrt(0.3+x)};
-                \draw[dashed] (axis cs:0,1) -- (axis cs:1,1);
-                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
-                \draw[name path=top] (axis cs:0,1.14) -- (axis cs:1,1.14);
-                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1.14);
-
-                \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
-                \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];
-
-                \node[anchor=north west] at (axis cs: .05, 1.09) {Downstream};
-                \node[anchor=south east] at (axis cs: .95, .05) {Upstream};
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Concave case}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.8]
-            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.482, samples at={0, 0.02, ..., 0.98, 1},
-                xtick={0, 1}, ytick={0, 1, 1.482}, yticklabels={$0$, $f(1)$, $f(1 + \alpha)$},
-                axis lines=left, xlabel={$s$}]
-                \addplot[name path=f, dashed, black] {(x)^1.5};
-                \addplot[name path=tildef, black, ultra thick] {(0.3+x)^1.5};
-                \draw[dashed] (axis cs:0,1) -- (axis cs:1,1);
-                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
-                \draw[name path=top] (axis cs:0,1.482) -- (axis cs:1,1.482);
-                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1.482);
-
-                \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
-                \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];
-
-                \node[anchor=north west] at (axis cs: .05, 1.43) {Downstream};
-                \node[anchor=south east] at (axis cs: .95, .05) {Upstream};
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Convex case}
-    \end{subfigure}
-    \caption{Illustration of \cref{prop:downstream_capacity}}
-    \label{fig:upstream_capacity}
-\end{figure}
-
-The results are similar to the previous case.
-When the downstream firms are more substitutable, the upstream firms' newly created capacity strongly reduces their bargaining power, and even though the total size of the pie increases, the downstream firms' share decreases not only in relative terms, but also in absolute terms.
-In a model with endogenous entry and exit on the part of the downstream firms, this would most likely lead to a reduction in their number.
-The implication then also resembles the one in the vertical merger case: industries when downstream firms are easily substitutable should be strongly scrutinized when an upstream firm seeks to build its own downstream capacity.
-
 \section{Conclusions}
@@
 
-The illustrative model also highlights the strengths of this approach.
-Despite its simplicity, it highlights that the effects of vertical integration strongly depends on the substitutability of the downstream firms.
-In a time when upstream firms and platforms are increasingly seeking to sell directly to the consumers\footnote{
-    As some recent examples, consider the recent acquisition of Whole Foods by Amazon, Microsoft's ongoing efforts to buy Activision/Blizzard (a major video game publisher), or Tesla's or BMW's plans to sell cars directly without the help of dealerships.
-}
-, such results can be important for competition authorities.
-
-There is a variety of ways through which this paper could be expanded or built upon.
+% The illustrative model also highlights the strengths of this approach.
+% Despite its simplicity, it highlights that the effects of vertical integration strongly depends on the substitutability of the downstream firms.
+% In a time when upstream firms and platforms are increasingly seeking to sell directly to the consumers\footnote{
+%     As some recent examples, consider the recent acquisition of Whole Foods by Amazon, Microsoft's ongoing efforts to buy Activision/Blizzard (a major video game publisher), or Tesla's or BMW's plans to sell cars directly without the help of dealerships.
+% }
+% , such results can be important for competition authorities.
+
+There is a variety of ways in which this paper could be expanded or built upon.
 On the theoretical side, a number of the assumptions, such as fringe agents achieving a zero payoff without the platform, could be relaxed,

### 2023-11-22 src/paper/theory.tex
Start working on example application

@@
 \section{Many-sided case}
+\label{sec:many_sided}
 
@@
 
+\section{Example application}
+
+In this section I will apply the results of the previous sections to a simple model of two-sided platforms.
+I follow the modelling approach of the monopoly platform case in \textcite{armstrong2006competition}, with a few extensions.
+There are two major departures from the original model.
+First, and most importantly, instead of letting the platform choose entry fees, I assume that they are the result of a bargaining process, and the outcomes are described by the weighted value.
+Second, instead of assuming that each player's utility is linear in the number of the other side's players, I allow for more general (power) functions, which lets me capture the substitutability of the two sides.
+
+\subsection{Model}
+
+Imagine a two-sided market with a continuum of players on both sides.
+Furthermore, assume that there is a single platform that connects the two sides.
+The utility that a player on side $i$ derives from participating in the market is an increasing function\footnote{
+    \textcite{armstrong2006competition} -- along with much of the literature on two-sided markets \parencite[e.g.][]{rochet2003platform,hagiu2006pricing} -- assumes that the utility of a player is linear in the number of players on the other side.
+    Using a more general function allows me to model different degrees of network effects.
+} of the number of players on the other side ($n_j$), minus the entry fee charged by the platform ($p_i$):
+\begin{align*}
+    u_i = \alpha_i n_j ^ {\gamma_i} - p_i,
+\end{align*}
+where $\alpha \geq 0$ and $\gamma > 0$ determine the strength and shape of the network effects, respectively.
+
+Following \textcite{armstrong2006competition}, let us also model player entry in a reduced form manner.
+Assume that there is a continuum of potential entrants on both sides, and the number of actual entrants is an increasing function of the utility achieved after entering\footnote{
+    One possible microfoundation of this is assuming some idiosyncratic entry cost for the players.
+    Then, the number of entrants is the number of players for whom the utility of entering is higher than the entry cost.
+}:
+\begin{align*}
+    n_i = \phi_i(u_i).
+\end{align*}
+
+Finally, let us assume that the platform can charge lump-sum entry fees to both sides.
+These fees can also be negative, in which case they are interpreted as subsidies.
+The platform's profit is the sum of entry fees, minus the cost of serving the entrants ($F_i$ for each entrant):
+\begin{align*}
+    \pi(n_1, n_2) = n_1 p_1 + n_2 p_2 - F_1 n_1 - F_2 n_2.
+\end{align*}
+
+I will consider two cases as to the timing and nature of the price-setting process, as well as a welfare-maximizing benchmark.
+For the latter, I derive the entry fees that maximize social welfare, i.e. the sum of the utilities of the two sides plus the platform's profit.
+After that, I will first consider a model analogous to that in \textcite{armstrong2006competition}, where the platform can unilaterally commit to any entry fees it wishes.
+Finally, I consider a model in which entry fees are the result of a bargaining process in such a way that the resulting utilities and profits correspond to the various players' weighted values.
+
+\subsection{Benchmark: welfare-maximizing entry fees}
+
+Let us consider first what entry fees would maximize social welfare.
+Instead of approaching this problem directly, let us rely on the following observation: if entry fees correspond to the externality that a player's entry imposes on the other side, then the resulting choices are welfare-maximizing.
+In this specific case, there are two externalities to consider.
+First, it costs the platform $F_i$ to serve an additional player on side $i$.
+Second, the entry of a player on side $i$ increases the utility on side $j$ due to positive network effects.
+Welfare is maximized when the price reflects the balance of these two  factors:
+\begin{align*}
+    p_i^* &= F_i - n_j \frac{\partial u_j}{\partial n_i} \\
+          &= F_i - \alpha_j \gamma_j n_j n_i^{\gamma_j - 1}.
+\end{align*}
+As in \textcite{armstrong2006competition}, for any $\alpha_j > 0$ welfare-maximizing $F_i$ is below the platform's cost of serving player $i$.
+Thus, the platform's profit would necessarily be negative.
+It naturally cannot happen in the case when the platform sets the entry fees, or even the bargaining case.
+
+As an immediate corollary, utilities in this case are given by
+\begin{align*}
+    u_i^* = \alpha_i n_j ^ {\gamma_i} + \alpha_j \gamma_j n_j n_i^{\gamma_j - 1} - F_i.
+\end{align*}
+Furthermore, the utility of type $i$ depends positively on both $\alpha_i$ (mechanically) and $\alpha_j$ (a stronger positive externality on the other players implies a lower entry fee and thus higher utility).
+Finally, if $n_i \geq e^{-\frac{1}{\gamma_j}}$, then $u_i$ is also increasing in $\gamma_j$.
+Both of the latter two effects are related to player $i$ being compensated for the positive externality it imposes on the other side.
+
+\subsection{Platform sets prices unilaterally}
+
+Now let us examine what happens when the platform sets the entry fees unilaterally.
+First, rewrite the platform's profit as a function of utilities, rather than the number of entrants:
+\begin{align*}
+    \pi(u_1, u_2) = \phi_1(u_1) [\alpha_1 \phi_2(u_2) ^ {\gamma_1} - u_1 - F_1] + \phi_2(u_2) [\alpha_2 \phi_1(u_1) ^ {\gamma_2} - u_2 - F_2].
+\end{align*}
+
+Let us assume that the above expression is concave, and thus the first order conditions characterize its maximum.
+Then, simply taking the partial derivatives with respect to $u_i$ yields the following condition for the optimal entry fees.
+\begin{proposition}
+    \label{prop:platform_unilateral}
+    If the platform can set entry fees unilaterally, then optimal entry fees for side $i$ are characterized by
+    \begin{align*}
+        p_i^u &= F_i - \alpha_j \gamma_j n_j n_i^{\gamma_j - 1} + \frac{\phi_1(u_1)}{\phi'_1(u_1)} \\
+              &= p_i^* + \frac{\phi_1(u_1)}{\phi'_1(u_1)}.
+    \end{align*}
+\end{proposition}
+
+As one would expect, profit-maximizing entry fees are higher than welfare-maximizing ones.
+In addition to the comparative statics of the welfare-maximizing case, the platform's entry fees also depend on the elasticity of entry.
+When it is low, the platform will set a high entry fee, as the loss of entrants is small.
+
+For ease of comparison with the bargaining case, let us also derive the utilities in this case:
+\begin{align*}
+    u_i^u = \alpha_i n_j ^ {\gamma_i} + \alpha_j \gamma_j n_j n_i^{\gamma_j - 1} - F_i - \frac{\phi_1(u_1)}{\phi'_1(u_1)}.
+\end{align*}
+Clearly, as equilibrium utilities must be smaller than in the welfare-maximizing case, due to $\phi_i$ being increasing, the number of entrants is also lower.
+
+\subsection{Bargaining}
+
+Finally, let us consider the case when the platform and the players bargain over the entry fees.
+To do this, let us impose some structure on the timing of the game.
+The idea is that even though the platform cannot commit to a specific entry fee structure anymore, it can commit to a bargaining process.
+Specifically, it is able to commit to a bargaining weight for each side and itself: $\lambda_P, \lambda_1, \lambda_2$.
+
+Then, the game proceeds as follows.
+In the first period, the platform chooses $\lambda_P, \lambda_1$ and $\lambda_2$.
+After that, potential antrants on both sides simultaneously decide whether to enter or not.
+Finally, in the last period, the platform and the entrants bargain over the entry fees, and utilities are realized according to their weighted values.
+
+Let us start by looking at the last period.
+Assume that $n_1$ and $n_2$ players have decided to enter on sides $1$ and $2$, respectively.
+Furthermore, assume that bargaining weights are $\lambda_1, \lambda_2$ and $\lambda_P$.
+
+The characteristic function of the game takes a similar form to that in \cref{sec:many_sided}.
+If the platform is not part of the coalition, then the value is zero.
+Otherwise, it is simply the sum of the utilities of the two sides minus the cost of serving them.\footnote{
+    The entry fees do not matter, as they are simply payments between coalition members, and thus do not affect the total value.
+}
+This value, as a function of the number of entrants, is
+\begin{align*}
+    f(n_1, n_2) = n_1 \alpha_1 n_2^{\gamma_1} + n_2 \alpha_2 n_1^{\gamma_2} - F_1 n_1 - F_2 n_2.
+\end{align*}
+
+The share received by each type of player is then easily established using \cref{prop:many_sided_weighted}.
+\begin{proposition}
+    \label{prop:platform_bargaining_last_period}
+    \begin{align*}
+        \pi_P(n_1, n_2) &= \int_0^1 \lambda_P t^{\lambda_P - 1} f(t_1^{\lambda_1} n_1, t_1^{\lambda_2} n_2) \dt \\
+        u_i(n_1, n_2) &= \int_0^1 t^{\lambda_P} \partial_i f(t_1^{\lambda_1} n_1, t_1^{\lambda_2} n_2) \dt
+    \end{align*}
+\end{proposition}
+
 \section{Conclusions}

### 2023-11-28 src/paper/theory.tex
Add proposition for weighted values in the example
Add idiosyncratic utilities

@@
 \paragraph{Example: power function.}
+\label{sec:power_function_example}
 
@@
     \begin{align*}
-        \varphi_{A^l}^\infty = \lim_{n \to \infty} \varphi_{A^l}^n &= \int_0^1 H(s) \partial_l f(a_1(s), \dots a_L(s)) \ds.        
+        \varphi_{A^l}^\infty = \lim_{n \to \infty} \varphi_{A^l}^n &= \int_0^1 H(s) a_l'(s) \partial_l f(a_1(s), \dots a_L(s)) \ds.        
     \end{align*}
@@
     \begin{align*}
-        \varphi_{A^l}^\infty & = \int_0^1 t^{\lambda_P} \partial_l f(t^{\lambda_1}, \dots, t^{\lambda^L}) \dt.
+        \varphi_{A^l}^\infty & = \int_0^1 t^{\lambda_P} \lambda_l t^{\lambda_l - 1} \partial_l f(t^{\lambda_1}, \dots, t^{\lambda^L}) \dt.
     \end{align*}
@@
 Following \textcite{armstrong2006competition}, let us also model player entry in a reduced form manner.
-Assume that there is a continuum of potential entrants on both sides, and the number of actual entrants is an increasing function of the utility achieved after entering\footnote{
-    One possible microfoundation of this is assuming some idiosyncratic entry cost for the players.
-    Then, the number of entrants is the number of players for whom the utility of entering is higher than the entry cost.
-}:
-\begin{align*}
-    n_i = \phi_i(u_i).
-\end{align*}
+There is a continuum of potential entrants on both sides of the market.
+Assume that the total utility of a player on side $i$ also includes an idiosyncratic component.
+Let us order the players on side $i$ by this idiosyncratic utility in a decreasing manner.
+That is, if we denote the idiosyncratic utility of player $n$ on side $i$ as $\epsilon_i(n)$, then $\epsilon_i$ is strictly decreasing in $n$.
+Also assume that $\lim_{n \to \infty} \epsilon_i(n) = -\infty$.
+
+Entry is given by the usual assumption that a player enters if and only if the total utility of entering is non-negative.
+
+Due to the properties of $\epsilon_i$, this implies that there is a well-defined, finite number of entrants on each side.
+Let us denote the number of entrants as a function of their non-idiosyncratic utility as $\phi_i(u_i)$.
+Then, the total number of players on side $i$ is 
+\begin{align*}
+    n_i = \phi_i(u_i) = \epsilon_i^{-1}(u_i),
+\end{align*}
+where $\phi_i$ has the same role as in \textcite{armstrong2006competition}.
 
@@
 \begin{align*}
-    u_i^* = \alpha_i n_j ^ {\gamma_i} + \alpha_j \gamma_j n_j n_i^{\gamma_j - 1} - F_i.
-\end{align*}
+    u_i^*(n_i, n_j) = \alpha_i n_j ^ {\gamma_i} + \alpha_j \gamma_j n_j n_i^{\gamma_j - 1} - F_i
+\end{align*}
+for an individual player on side $i$.
+That is, side $i$ obtains the total utility generated by its players minus the cost of serving them, plus $\gamma_j$ times the total utility generated by the other side, too.
+This is due to the positive externality that side $i$ imposes on side $j$.
+
 Furthermore, the utility of type $i$ depends positively on both $\alpha_i$ (mechanically) and $\alpha_j$ (a stronger positive externality on the other players implies a lower entry fee and thus higher utility).
@@
 Both of the latter two effects are related to player $i$ being compensated for the positive externality it imposes on the other side.
+
+One can also obtain the total welfare of side $i$, as it is simply the number of entrants plus the non-idiosyncratic utility of its players, plus the sum (integral) of the idiosyncratic utilities.
+\begin{align*}
+    w_i^*(n_i, n_j) = \alpha_i n_i n_j ^ {\gamma_i} + \gamma_j \alpha_j n_j n_i^{\gamma_j} - n_i F_i + \int_0^{n_i} \epsilon_i(s) \ds.
+\end{align*}
 
@@
 \begin{align*}
-    u_i^u = \alpha_i n_j ^ {\gamma_i} + \alpha_j \gamma_j n_j n_i^{\gamma_j - 1} - F_i - \frac{\phi_1(u_1)}{\phi'_1(u_1)}.
-\end{align*}
-Clearly, as equilibrium utilities must be smaller than in the welfare-maximizing case, due to $\phi_i$ being increasing, the number of entrants is also lower.
+    u_i^u(n_1, n_2) &= \alpha_i n_j ^ {\gamma_i} + \alpha_j \gamma_j n_j n_i^{\gamma_j - 1} - F_i - \frac{\phi_1(u_i)}{\phi'_1(u_i)} \\
+    &= \alpha_i n_j ^ {\gamma_i} + \alpha_j \gamma_j n_j n_i^{\gamma_j - 1} - F_i - n_i \epsilon'_i(n_i).
+\end{align*}
+Welfare of side $i$ immediately follows in this case, too:
+\begin{align*}
+    U_i^u(n_1, n_2) = \alpha_i n_i n_j ^ {\gamma_i} + \gamma_j \alpha_j n_j n_i^{\gamma_j} - n_i F_i - n_i^2 \epsilon'_i(n_i) + \int_0^{n_i} \epsilon_i(s) \ds.
+\end{align*}
+Clearly, equilibrium utilities must be smaller than in the welfare-maximizing case, due to $\phi_i$ being increasing, the number of entrants is also lower.
 
@@
 
-Finally, let us consider the case when the platform and the players bargain over the entry fees.
+Finally, let us consider the case when the platform and the players bargain over the value they generate.
 To do this, let us impose some structure on the timing of the game.
@@
 \begin{align*}
-    f(n_1, n_2) = n_1 \alpha_1 n_2^{\gamma_1} + n_2 \alpha_2 n_1^{\gamma_2} - F_1 n_1 - F_2 n_2.
+    w(n_1, n_2) = n_1 \alpha_1 n_2^{\gamma_1} + n_2 \alpha_2 n_1^{\gamma_2} - F_1 n_1 - F_2 n_2.
 \end{align*}
@@
     \label{prop:platform_bargaining_last_period}
-    \begin{align*}
-        \pi_P(n_1, n_2) &= \int_0^1 \lambda_P t^{\lambda_P - 1} f(t_1^{\lambda_1} n_1, t_1^{\lambda_2} n_2) \dt \\
-        u_i(n_1, n_2) &= \int_0^1 t^{\lambda_P} \partial_i f(t_1^{\lambda_1} n_1, t_1^{\lambda_2} n_2) \dt
-    \end{align*}
+    Let $f(t_1, t_2) = w(t_1 n_1, t_2 n_2)$. Then the weighted values of the various sides are
+    \begin{alignat*}{4}
+        \pi_P^b(n_1, n_2) &= \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_P^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_P^{b_2}} \alpha_2 n_2 n_1^{\gamma_2} &&- \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_1}}_{\coloneqq S_P^{c_1}} n_1 F_1 &&- \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_2}}_{\coloneqq S_P^{c_2}} n_2 F_2 \\
+        U_1^b(n_1, n_2) &= \underbracket{\frac{\lambda_1}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_1^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_1 \gamma_2}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_1^{b_2}}  \alpha_2 n_2 n_1^{\gamma_2} &&- \underbracket{\frac{\lambda_1}{\lambda_P + \lambda_1}}_{\coloneqq S_1^{c_1}} n_1 F_1 && \\
+        U_2^b(n_1, n_2) &= \underbracket{\frac{\lambda_2\gamma_1}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_2^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_2}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_2^{b_1}} \alpha_2 n_2 n_1^{\gamma_2} && &&- \underbracket{\frac{\lambda_2}{\lambda_P + \lambda_2}}_{\coloneqq S_2^{c_2}} n_2 F_2.
+    \end{alignat*}
 \end{proposition}
+
+There are four parts that the total welfare $w(n_1, n_2)$ is divided into: utility generated by side $1$ and $2$, and cost of serving side $1$ and $2$.
+Each side's share of these parts is given by $S_i^{b_1}, S_i^{b_2}, S_i^{c_1}$ and $S_i^{c_2}$, respectively.
+As it turns out, these shares only depend on the bargaining weights ($\lambda_P, \lambda_1, \lambda_2$) and the network effects ($\gamma_1, \gamma_2$), but not on the actual number of entrants.\footnote{
+    This is due to the characteristic function being a polynomial in the number of entrants.
+    Just like in \cref{sec:power_function_example}, the parts of the polynomial are divided in a constant proportion.
+}
+Furthermore, all of these shares are increasing in one's own bargaining weight, and decreasing in the others' weights.
+Finally, the share of side $i$ from the value generated on side $j$ is also increasing in $\gamma_j$.
+This means that if players on side $i$ are less substitutable / more complementary in terms of generating utility on side $j$, then they will receive a larger share of the value generated on that side.
+
+Let us look at the per-player utilities to
 

### 2023-11-29 src/paper/theory.tex
More or less finish example application

@@
 There is a continuum of potential entrants on both sides of the market.
-Assume that the total utility of a player on side $i$ also includes an idiosyncratic component.
-Let us order the players on side $i$ by this idiosyncratic utility in a decreasing manner.
-That is, if we denote the idiosyncratic utility of player $n$ on side $i$ as $\epsilon_i(n)$, then $\epsilon_i$ is strictly decreasing in $n$.
-Also assume that $\lim_{n \to \infty} \epsilon_i(n) = -\infty$.
+Assume that the total utility of an entrant on side $i$ also includes an idiosyncratic cost component.
+Let us order the players on side $i$ by this idiosyncratic cost in an increasing manner.
+That is, if we denote the idiosyncratic utility of player $n$ on side $i$ as $\kappa_i(n)$, then $\kappa_i$ is strictly increasing in $n$.
+Also assume that $\lim_{n \to \infty} \kappa_i(n) = \infty$.
 
@@
 
-Due to the properties of $\epsilon_i$, this implies that there is a well-defined, finite number of entrants on each side.
+Due to the properties of $\kappa_i$, this implies that there is a well-defined, finite number of entrants on each side.
 Let us denote the number of entrants as a function of their non-idiosyncratic utility as $\phi_i(u_i)$.
@@
 \begin{align*}
-    n_i = \phi_i(u_i) = \epsilon_i^{-1}(u_i),
+    n_i = \phi_i(u_i) = \kappa_i^{-1}(u_i),
 \end{align*}
@@
 One can also obtain the total welfare of side $i$, as it is simply the number of entrants plus the non-idiosyncratic utility of its players, plus the sum (integral) of the idiosyncratic utilities.
-\begin{align*}
-    w_i^*(n_i, n_j) = \alpha_i n_i n_j ^ {\gamma_i} + \gamma_j \alpha_j n_j n_i^{\gamma_j} - n_i F_i + \int_0^{n_i} \epsilon_i(s) \ds.
-\end{align*}
+\begin{align}
+    \label{eq:W_star}
+    W_i^*(n_i, n_j) = \alpha_i n_i n_j ^ {\gamma_i} + \gamma_j \alpha_j n_j n_i^{\gamma_j} - n_i F_i - \int_0^{n_i} \kappa_i(s) \ds.
+\end{align}
 
@@
     u_i^u(n_1, n_2) &= \alpha_i n_j ^ {\gamma_i} + \alpha_j \gamma_j n_j n_i^{\gamma_j - 1} - F_i - \frac{\phi_1(u_i)}{\phi'_1(u_i)} \\
-    &= \alpha_i n_j ^ {\gamma_i} + \alpha_j \gamma_j n_j n_i^{\gamma_j - 1} - F_i - n_i \epsilon'_i(n_i).
+    &= \alpha_i n_j ^ {\gamma_i} + \alpha_j \gamma_j n_j n_i^{\gamma_j - 1} - F_i - n_i \kappa'_i(n_i).
 \end{align*}
@@
 \begin{align*}
-    U_i^u(n_1, n_2) = \alpha_i n_i n_j ^ {\gamma_i} + \gamma_j \alpha_j n_j n_i^{\gamma_j} - n_i F_i - n_i^2 \epsilon'_i(n_i) + \int_0^{n_i} \epsilon_i(s) \ds.
+    \label{eq:W_u}
+    W_i^u(n_1, n_2) = \alpha_i n_i n_j ^ {\gamma_i} + \gamma_j \alpha_j n_j n_i^{\gamma_j} - n_i F_i - n_i^2 \kappa'_i(n_i) - \int_0^{n_i} \kappa_i(s) \ds.
 \end{align*}
@@
 Finally, let us consider the case when the platform and the players bargain over the value they generate.
-To do this, let us impose some structure on the timing of the game.
-The idea is that even though the platform cannot commit to a specific entry fee structure anymore, it can commit to a bargaining process.
-Specifically, it is able to commit to a bargaining weight for each side and itself: $\lambda_P, \lambda_1, \lambda_2$.
-
-Then, the game proceeds as follows.
-In the first period, the platform chooses $\lambda_P, \lambda_1$ and $\lambda_2$.
-After that, potential antrants on both sides simultaneously decide whether to enter or not.
-Finally, in the last period, the platform and the entrants bargain over the entry fees, and utilities are realized according to their weighted values.
-
-Let us start by looking at the last period.
+I will approach this problem in two steps.
+First, I will examine the distribution of the value generated in the case of no idiosyncratic cost.
+I do this because this partial result has a neat interpretation, and is very tractable.
+After that, I derive how the total idiosyncratic cost is distributed between the players.
+Because of the linearity of random order values, the total welfare in the general case is simply the sum of these two building blocks.
+
+Let us start by examining the case when there is no idiosyncratic cost.
 Assume that $n_1$ and $n_2$ players have decided to enter on sides $1$ and $2$, respectively.
@@
     \label{prop:platform_bargaining_last_period}
-    Let $f(t_1, t_2) = w(t_1 n_1, t_2 n_2)$. Then the weighted values of the various sides are
+    The weighted values of the various sides without idiosyncratic costs are
     \begin{alignat*}{4}
         \pi_P^b(n_1, n_2) &= \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_P^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_P^{b_2}} \alpha_2 n_2 n_1^{\gamma_2} &&- \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_1}}_{\coloneqq S_P^{c_1}} n_1 F_1 &&- \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_2}}_{\coloneqq S_P^{c_2}} n_2 F_2 \\
-        U_1^b(n_1, n_2) &= \underbracket{\frac{\lambda_1}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_1^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_1 \gamma_2}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_1^{b_2}}  \alpha_2 n_2 n_1^{\gamma_2} &&- \underbracket{\frac{\lambda_1}{\lambda_P + \lambda_1}}_{\coloneqq S_1^{c_1}} n_1 F_1 && \\
-        U_2^b(n_1, n_2) &= \underbracket{\frac{\lambda_2\gamma_1}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_2^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_2}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_2^{b_1}} \alpha_2 n_2 n_1^{\gamma_2} && &&- \underbracket{\frac{\lambda_2}{\lambda_P + \lambda_2}}_{\coloneqq S_2^{c_2}} n_2 F_2.
+        w_1^b(n_1, n_2) &= \underbracket{\frac{\lambda_1}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_1^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_1 \gamma_2}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_1^{b_2}}  \alpha_2 n_2 n_1^{\gamma_2} &&- \underbracket{\frac{\lambda_1}{\lambda_P + \lambda_1}}_{\coloneqq S_1^{c_1}} n_1 F_1 && \\
+        w_2^b(n_1, n_2) &= \underbracket{\frac{\lambda_2\gamma_1}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_2^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_2}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_2^{b_1}} \alpha_2 n_2 n_1^{\gamma_2} && &&- \underbracket{\frac{\lambda_2}{\lambda_P + \lambda_2}}_{\coloneqq S_2^{c_2}} n_2 F_2.
     \end{alignat*}
@@
 
-Let us look at the per-player utilities to
+Let us now turn our attention to the idiosyncratic cost component.
+Assume that, even though entrants with different costs have different contribution to the total value, there can be no discrimination between them.
+That is, they each must share the same fraction of the total idiosyncratic cost (e.g. have the same value).
+
+Let us denote the total idiosyncratic cost incurred by all players on both sides as $K(n_1, n_2)$.
+Also, suppose that if $n_i$ players enter on side $i$, then they are the ones with the lowest idiosyncratic cost.
+Then, the total idiosyncratic cost is simply the sum of the idiosyncratic costs of the entrants on both sides:
+\begin{align*}
+    K(n_1, n_2) = \int_0^{n_1} \kappa_1(s) \ds + \int_0^{n_2} \kappa_2(s) \ds.
+\end{align*}
+Again, one can obtain the weighted values of all sides using \cref{prop:many_sided_weighted}.
+\begin{proposition}
+    \label{prop:platform_bargaining_idiosyncratic}
+    The weighted values of the idiosyncratic cost component are
+    \begin{align*}
+        K_P(n_1, n_2) &= \sum_{i \in \{1, 2\}} \int_0^{n_1} \left[ 1 - \lambda_i \left( \frac{s}{n_i} \right)^{\lambda_P + \lambda_i - 1} \right] \kappa_i(s) \ds, \\
+        K_i(n_1, n_2) &= \lambda_i \int_0^{n_1} \left( \frac{s}{n_i} \right)^{\lambda_P + \lambda_i - 1} \kappa_i(s) \ds.
+    \end{align*}
+\end{proposition}
+
+That is, each side only has to bear some part of the total idiosyncratic cost, and the rest is shared with the platform.
+As with the rest of the value, the share of the idiosyncratic cost is increasing in one's own bargaining weight.
+This might seem counterintuitive at first, as one may expect that a player with a higher bargaining weight would be able to shift more of the cost to the other side.
+However, in the case of random order values, this intuition is only correct for monotonic games, which it is not in this case.
+One has to keep in mind though that this is just part of the final payoffs, and the other parts are increasing in one's own bargaining weight.
+Therefore, as long as the combined game is monotonic, the final payoffs will be increasing in one's own bargaining weight.
+
+Let us finally consider total welfare.
+As mentioned before, it is simply the sum of the value generated and the idiosyncratic cost.
+That is, the welfare of side $i \in \{1, 2\}$ is
+\begin{align*}
+    W_i^b(n_1, n_2) &= \frac{\lambda_i}{\lambda_P + \lambda_i + \lambda_j\gamma_i} \alpha_i n_i n_j^{\gamma_i} + \frac{\lambda_i \gamma_j}{\lambda_P + \lambda_j + \lambda_i\gamma_j} \alpha_j n_j n_i^{\gamma_j} - \frac{\lambda_i}{\lambda_P + \lambda_i} n_i F_i \\
+    &- \lambda_i \int_0^{n_1} \left( \frac{s}{n_i} \right)^{\lambda_P + \lambda_i - 1} \kappa_i(s) \ds.
+\end{align*}
+It is remarkably similar in structure to the welfare maximizing case in \cref{eq:W_star}.
+The main difference is that each part (both costs and positive utilities) is reweighted, and side $i$ only receives a fraction of it.
+It is also worth noting that $W_i^b(n_1, n_2) < W_i^*(n_1, n_2)$, and, as a consequence, entry is lower than what would be socially optimal.\footnote{
+    The easiest way to see it is that in the welfare-maximizing case the platform's profit is negative, while in the bargaining case it is positive.
+    Therefore, fringe utilities must be lower in the latter case.
+}
+
+For better comparison, let us also examine implied entry fees and non-idiosyncratic utilities.
+The latter is the difference between the average welfare and the average idiosyncratic cost:
+\begin{align*}
+    u_i^b(n_1, n_2) &= \frac{\lambda_i}{\lambda_P + \lambda_i + \lambda_j\gamma_i} \alpha_i n_j^{\gamma_i} + \frac{\lambda_i \gamma_j}{\lambda_P + \lambda_j + \lambda_i\gamma_j} \alpha_j n_j n_i^{\gamma_j - 1} - \frac{\lambda_i}{\lambda_P + \lambda_i} F_i \\
+    &+ \int_0^{n_1} \left[ 1 - \lambda_i \left( \frac{s}{n_i} \right)^{\lambda_P + \lambda_i - 1} \right] \kappa_i(s) \ds.
+\end{align*}
+If one wished to close the model, the number of entrants in equilibrium could be obtained by solving the system of equations $\kappa_i(n_i) = u_i(n_1, n_2), n \in \{1, 2\}$.
+Finally, the implied entry fees can be calculated from the equation $u_i = \alpha_i n_j^{\gamma_i} - p_i$, yielding
+\begin{align*}
+    p_i^b(n_1, n_2) &= \frac{\lambda_i}{\lambda_P + \lambda_i} F_i - \frac{\lambda_i \gamma_j}{\lambda_P + \lambda_j + \lambda_i\gamma_j} \alpha_j n_j n_i^{\gamma_j - 1} + \frac{\lambda_P + \lambda_j\gamma_i}{\lambda_P + \lambda_i + \lambda_j\gamma_i} \alpha_i n_j^{\gamma_i} \\
+    &- \int_0^{n_1} \left[ 1 - \lambda_i \left( \frac{s}{n_i} \right)^{\lambda_P + \lambda_i - 1} \right] \kappa_i(s) \ds.
+\end{align*}
 

### 2023-11-29 src/paper/theory.tex
Finish example application

@@
 
+\subsection{Comparison}
+
+Let us now compare the outcomes at the three cases by looking at the entry fees for side $i$.
+From the previous results, they are
+\begin{align*}
+    p_i^* &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j \gamma_j n_j n_i^{\gamma_j - 1}}_{(2)}, \\
+    p_i^u &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j \gamma_j n_j n_i^{\gamma_j - 1}}_{(2)} + \underbracket{n_i \kappa'_i(n_i)}_{(3)} \\
+    p_i^b &= \underbracket{\frac{\lambda_i}{\lambda_P + \lambda_i} F_i}_{(1)} - \underbracket{\frac{\lambda_i \gamma_j}{\lambda_P + \lambda_j + \lambda_i\gamma_j} \alpha_j n_j n_i^{\gamma_j - 1}}_{(2)} \\
+    &+ \underbracket{\frac{\lambda_P + \lambda_j\gamma_i}{\lambda_P + \lambda_i + \lambda_j\gamma_i} \alpha_i n_j^{\gamma_i} +
+    - \int_0^{n_1} \left[ 1 - \lambda_i \left( \frac{s}{n_i} \right)^{\lambda_P + \lambda_i - 1} \right] \kappa_i(s) \ds}_{(4)},
+\end{align*}
+for the welfare-maximizing, unilateral price setting and bargaining cases, respectively.
+
+All of these expressions bear some similarities to each other, in that the price is somehow related to the externalities that an entrant imposes on the other players.
+In fact, the welfare-maximizing price is just that: the cost of serving one additional player (1) and the positive externality imposed on the other side (2).
+The unilateral pricing case also includes these two factors in full, but also adds a third factor, related to the elasticity of entry (3).
+Namely, the platform extracts some of the surplus generated by the entrants, and the surplus it can extract depends on $\phi'_i(u_i)$ (or, equivalently, $\kappa'_i(u_i)$).
+It is the same mechanism that leads to the markup in the simple monopolistic pricing model.
+
+The bargaining case also has the first two factors, albeit they are somewhat different.
+As opposed to the first two cases, the price only contains some fraction of the externalities, and the rest is shared with the platform and the other side.
+Furthermore, some part of the welfare generated on side $i$ is also shared with the other players, and thus appears in the price (4).
+Therefore, bargaining introduces some interesting departures from both the welfare-maximizing and unilateral pricing cases.
+
+Whether these departures lead to a higher or lower total welfare depends on the specific parameters of the model.
+For example, if $\lambda_P$ is very high, then $p_i^b > p_i^u > p_i^*$, leading to lower entry and total surplus than not only the welfare-maximizing case, but also the unilateral pricing case.
+That is, everybody looses from bargaining.\footnote{
+    In such a case, the platform would like to set lower entry fees that what it can achieve via bargaining.
+    While in some settings it is very plausible that it can do it, in others commitment problems might prevent it from doing so.
+}
+
+On the other hand, if $\lambda_P$ is sufficiently low, then one can find weights $\lambda_1, \lambda_2$, such that $p_i^u > p_i^b > p_i^*$.
+In such a case, the platform would like to set higher entry fees than what it can achieve via bargaining.
+The total welfare is also between the welfare-maximizing and unilateral pricing cases, therefore bargaining can be beneficial as an alternative of unilateral pricing.
+The platform, however, achieves a lower profit than if it could set the entry fees unilaterally.
+
+Finally, it is always true that $p_1^b < p_1^*$ or $p_2^b < p_2^*$.\footnote{
+    Given that $\alpha_i > 0, i \in \{1, 2\}$.
+}
+The reason is that the platform's profit is always non-negative in the bargaining case, while it is negative in the welfare-maximizing case.
+This also implies that the total welfare is strictly lower than in the welfare-maximizing case.
+Therefore, while bargaining can be welfare-increasing compared to unilateral price setting, it can not achieve the maximum possible welfare.\footnote{
+    One could argue that the welfare maximizing case is not a realistic benchmark anyway, as it assumes that the platform is making a loss.
+}
+
 \section{Conclusions}

### 2023-11-29 src/paper/theory.tex
Rewrite conclusion

@@
 
-This paper proposed a new framework to think about the profit allocation in situations concerning a few large and a continuum of smaller players.
-The results are especially relevant for upstream-downstream situations, platform settings, and two-sided markets.
-The outcomes of the Shapley-value-based gain sharing rule generally concur with intuitive expectations, and the resulting formulas are more tractable than most explicit non-cooperative approaches.
-
-% The illustrative model also highlights the strengths of this approach.
-% Despite its simplicity, it highlights that the effects of vertical integration strongly depends on the substitutability of the downstream firms.
-% In a time when upstream firms and platforms are increasingly seeking to sell directly to the consumers\footnote{
-%     As some recent examples, consider the recent acquisition of Whole Foods by Amazon, Microsoft's ongoing efforts to buy Activision/Blizzard (a major video game publisher), or Tesla's or BMW's plans to sell cars directly without the help of dealerships.
-% }
-% , such results can be important for competition authorities.
+In this paper, I examined the problem of bargaining between one indispensable player and a continuum of fringe players.
+I did so using the concept of random order values from cooperative game theory.
+I showed that random-order-value-based bargaining has some desirable properties, and that it coincides with intuitive expectations in terms of certain comparative statics.
+Furthermore, the resulting distributions of the value are also analytically tractable, and has neat geometric interpretations.
+
+I use random order values to provide a comprehensive framework for a number of important special cases.
+Some of those, such as the Shapley-value, or the weighted value in the one-sided case, is already known in the literature.\footnote{
+    Aside from looking at it in an abstract manner, my contribution to those cases mostly lie in showing how the fringe's value can be expressed as a kind of expected marginal contribution.
+    This is especially relevant in the multi-sided case, where it is important to know how the value not obtained by the indispensible player is distributed among the various sides.
+}
+Others, such as the weighted value in the multi-sided case, or the interpretation of substitutable "indispensible" players, are, to the best of my knowledge, new.
+As I demonstrate, they retain the simplicity and interpretability of the simpler cases, while making the model more general.
+Finally, I demonstrate how the proposed framework can be applied in practice by
+examining the two-sided platform model of \textcite{armstrong2006competition} with a small extension and a bargaining process over entry fees.
+I show that the resulting entry fees have a simple structure, but they also differ from the welfare-maximizing and unilateral price-setting cases in number of interesting ways.
+Therefore, in situations where bargaining between players is plausible, certain effects might be missed if one assumes unilateral price-setting.
 
 There is a variety of ways in which this paper could be expanded or built upon.
-On the theoretical side, a number of the assumptions, such as fringe agents achieving a zero payoff without the platform, could be relaxed,
-Besides this, the convergence result for the weighted values could be strengthened if one could manage to show that any sequence along ever more refined partitions of the atomic players converges to the same limit \parencite[à la][]{fogelman1980asymptotic}.
-
-A slightly different direction would be to consider other solution concepts from cooperative game theory in this specific setting.
-One obvious candidate is the nucleolus, which shares many of the useful properties of the Shapley-value (it always exists and is unique).
-Furthermore, it also has connections to bargaining theory due to it being contained in the core when the latter exists.
-
-The possibilities for practical applications are no less interesting.
-The proposed profit sharing framework could be embedded in a more applied model of some real-life setting.
-For a step in this direction, see \textcite{stancsics2023hybrid}.
-
-Finally, with time, the cooperative approach to profit distribution could become an almost drop-in alternative of the more usual, but in some sense more extreme assumptions about the bargaining process widely used in industrial organization models.
+One obvious direction is to consider other solution concepts from cooperative game theory, such as the nuclelous\footnote{
+    It retains many of the desirable properties of the Shapley-value, such as existence and uniqueness, but it is contained in the core when the latter exists, and thus has a more immediate connection to non-cooperative bargaining theory.
+}.
+Another way to go is to build non-cooperative microfoundations for the random-order-value-based bargaining outcomes.
+Many such results exist for the Shapley value, and some also exist for the weighted value, but it might be interesting to see if some of the more general random order values can be motivated in a similar manner.
+
+Besides those theoretical directions, the practical applications are no less interesting.
+The proposed profit sharing framework could be embedded in more realistic models of various settings.
+The example application in this paper is a small example of that, while \textcite{stancsics2023hybrid} provides a more detailed model involving hybrid platforms.
+Due to the simplicity of the results, this approach might be a viable replacement of unilateral price setting in cases where one does not wish to ascribe all the bargaining power to one player.
 

### 2023-12-06 src/paper/application.tex
Fix typo
Rewrite general part for application

@@
 I make use of a reduced-form, but quite general approach to model production and demand.
-First, I assume that all fringe firms are ex-ante identical.
-This implies that the total profits of the platform and the fringe taken together have a simple functional form $f(n_P, n_F)$.
+First, I assume that all fringe firms and consumers are ex-ante identical.
+This implies that the total profits of the platform and the fringe taken together have a simple functional form $n_C f(n_P, n_F)$.
 \begin{assumption}
     \label{ass:identical_fringe}
-    The total profits of the platform and the fringe are described by some function $f: \mathbb{R}^+_0 \times \mathbb{R}^+_0 \to \mathbb{R}^+_0$.
+    The total profits of the platform and the fringe are described by 
+    \begin{align*}
+        \Pi(n_P, n_F, n_C) = n_C f(n_P, n_F),
+    \end{align*}
+    where $f: \mathbb{R}^+_0 \times \mathbb{R}^+_0 \to \mathbb{R}^+_0$.
 \end{assumption}
-Here, $n_F$ is the mass of fringe sellers, and $n_P$ measures the degree to which the platform sells its own products.
+Here, $n_F$ is the mass of fringe sellers, $n_C$ is the mass of consumers, and $n_P$ measures the degree to which the platform sells its own products.
 For example, in a setting with differentiated products and monopolistic competition, $n_F$ and $n_P$ represents the product variety of the fringe and the platform, respectively.
 In case the platform operates as a pure intermediary, $n_P = 0$.
-
-I will assume that total profits are increasing in both arguments.
+This formulation also assumes that total profits are linear in the number of consumers.\footnote{
+    While normally this would exclude fixed production costs, this is not the case here.
+    $\Pi$ only describes profits conditional on $N_C$ and $N_F$ players entering the platform.
+    Fixed costs can be incorporated into the first stage of the game, where fringe firms decide whether to enter or not.
+}
+
+I will assume that, in addition to being increasing in the number of consumers, total profits are also increasing in both the number of fringe firms and the platform' products.
 \begin{assumption}
@@
 \end{assumption}
-Such profit functions arise in a variety of settings in which the profit reduction from increased competition is dominated by extra sales due to increased variety.
+Such profit functions arise in a variety of settings in which the profit reduction from increased competition is dominated by extra sales due to increased product variety.
 One such example is \textcite{anderson2020aggregative}, where the demand exhibits love for variety, while consumers have access to an outside option.
-Alternatively, indirect network effects, such as in two-sided markets, can also result in such profit functions.
+Alternatively, indirect network effects, such as in two-sided markets, can also result in such increasing profits.
 
@@
 
-Let us assume that the platform and the fringe shares their total profits according to the following rule.
+In the benchmark model, the platform will be able to set and commit to any lump-sum entry fee it wishes to.\footnote{
+    The focus is on fees and entry of fringe producers, but I will also consider the case when the platform can set an entry fee for consumers, as well.
+}
+The main contribution of this paper is to deviate this usual assumption, and instead consider a setting in which the platform and the fringe engage in some form of bargaining over the entry fee.
+To model this bargaining in a theoretically sound, but still tractable way, I will borrow a solution concept from cooperative game theory.
+Similarly to a number of other papers in the industrial organization literature \parencite[e.g.][]{montez2007downstream,hart1990property,levy1997individual,inderst2003bargaining,brugemann2019intra}, I will assume that the resulting allocation for each player is given by their Shapley value.
+This value (and the game itself) depends on who is assumed to participate in the bargaining process.
+I will consider two different cases.
+
+\paragraph{One-sided case} In the first setting, the platform and the fringe firms bargain over the total profits of the platform and the fringe taken together, and the consumers are not included in the negotiations.
+The following assumption describes this case.
 \begin{assumption}
     \label{ass:profit_sharing}
-    Let $w: [0, 1] \to \mathbb{R}_0^+$ such that $\int_0^1 w(s) \ds = 1$. 
-    \begin{align*}
-        \pi_P(N_P, N_F) &= \int_0^1 w(s) f(N_P, s N_F) \ds, \\
-        \pi_F(N_P, N_F) &= f(N_P, N_F) - \int_0^1 w(s) f(N_P, s N_F) \ds.
+    Consider the following cooperative game $\mathcal{G} = (\mathcal{N}, v)$.
+    The set of players consists of the platform plus the fringe firms: $\mathcal{N} = \{P, F_i\}, i \in [0, N_F]$.
+    The value of a coalition $S$ is zero without the platform, and depends on the number of fringe firms otherwise:
+    \begin{align*}
+        v(S) = \begin{cases}
+            0 & \text{if } P \notin S \\
+            N_C f(N_P, n_F(S)) & \text{if } P \in S
+        \end{cases},
+    \end{align*}
+    where $n_F(S)$ is the measure of fringe firms in $S$.
+    Each type of player gets their Shapley value in this game:
+    \begin{align*}
+        \pi_P(N_P, N_F, N_C) &= \varphi_P(\mathcal{G}), \\
+        \pi_F(N_P, N_F, N_C) &= \varphi_F(\mathcal{G}).
     \end{align*}
 \end{assumption}
-While somewhat more complex than a simple percentage split, it has quite a few advantages compared to the latter.\footnote{
-    This way of modeling bargaining has precedents in the industrial organization literature \parencite[e.g.][]{hart1990property,segal2003collusion,inderst2003bargaining,montez2007downstream}.
-    Furthermore, a number of papers show that various extensive-form bargaining games result in this outcome \parencite{gul1989bargaining,winter1994demand,hart1996bargaining,inderst2003bargaining,stole1996intra}.
-}
-On the theoretical side, the main argument in favor of this particular rule is its relation to the Shapley-value.\footnote{
-    \cref{sec:profit_sharing} shows that in the case of $w(s) \equiv 1$, $\pi_P(N_P, N_F)$ and $\pi_F(N_P, N_F)$ are the Shapely values of the platform and the fringe, respectively.
-}
-Shapley-value in turn has deep connections to bargaining theory.
-\textcite{gul1989bargaining,stole1996intra,hart1996bargaining,inderst2003bargaining}, along with a number of other papers, show that in various extensive-form bargaining games in the players' expected payoffs in the subgame perfect equilibrium correspond to their Shapley values.
-
-The other main justification for this rule its intuitive behavior in terms of comparative statistics when varying $f$ and $w$.
-To illustrate this, let us examine the various parts of this rule, and then discuss how they impact the platform's profit share.
-
-The main feature of this rule is that the platform's bargaining power depends on the degree to which the fringe firms are complements or substitutes of each other.
+
+While this assumption might seem somewhat abstract, the resulting profit allocations are remarkably simple, and can be expressed as integrals (expectations) over the marginal contributions of the players.
+\begin{proposition}
+    \label{prop:profit_sharing}
+    Consider the case when only the platform and the fringe firms participate in the bargaining process.
+    Then, the resulting profit shares are given by
+    \begin{align*}
+        \pi_P(N_P, N_F, N_C) &= N_C \int_0^1 f(N_P, s N_F) \ds, \\
+        \pi_F(N_P, N_F, N_C) &= N_C \int_0^1 s N_F \partial_2 f(N_P, s N_F) \ds.
+    \end{align*}
+\end{proposition}
+
+\begin{proof}[proof of \cref{prop:profit_sharing}]
+    This result is a direct application of Proposition 3 and Corollary 2 in \textcite{stancsics2023value}.
+\end{proof}
+
+As mentioned before, one main justification for this profit allocation rule its intuitive behavior in terms of comparative statistics.
+To illustrate this, let us examine what happens when one varies the substitutability between the fringe firms.
+As it turns out, the platform's share increases if the fringe firms are more substitutable.
 The following observation demonstrates this idea.
@@
     \label{prop:outcome_based_bargaining_power}
-    Fix some $N_P \geq 0$.
-Let $f, \tilde{f}: \mathbb{R}^+_0 \times \mathbb{R}^+_0 \to \mathbb{R}^+_0$ two different total profit functions such that $f(N_P, N_F) = \tilde{f}(N_P, N_F)$ for some $N_P, N_F$ and $f(N_P, n_F) \leq \tilde{f}(N_P, n_F)$ for all $n_F < N_F$.
+    Fix some $N_P, N_C \geq 0$.
+Let $f, \tilde{f}: \mathbb{R}^+_0 \times \mathbb{R}^+_0 \to \mathbb{R}^+_0$ two different profit functions such that $f(N_P, N_F) = \tilde{f}(N_P, N_F)$ for some $N_P, N_F$ and $f(N_P, n_F) \leq \tilde{f}(N_P, n_F)$ for all $n_F < N_F$.
     Furthermore, let us denote the corresponding platform profit shares by $\pi_P$ and $\tilde{\pi}_P$.
@@
 
-In words, \cref{prop:outcome_based_bargaining_power} describes two alternative profit functions, under which $N_F$ fringe firms (along with the platform and it's $N_P$ products) are able to achieve the same total profit level.
-However, in one of these cases, the fringe firms are more substitutable to each other, in the sense that fewer of them are needed to achieve a given level of profit (see \cref{fig:outcome_based_bargaining_power}).
+In words, \cref{prop:outcome_based_bargaining_power} describes two alternative worlds, in which $N_F$ fringe firms (assuming a platform with $N_P$ product variety and $N_C$ consumers) are able to achieve the same total profit level.
+However, in one of these cases, the fringe firms are more substitutable to each other in the sense that fewer of them are needed to achieve a given level of profit (see \cref{fig:outcome_based_bargaining_power}).
 The observation is that, in this situation, the platform's share is indeed higher when the fringe firms are more substitutable.
@@
                 \addplot[name path=f, blue,ultra thick] {x^2};
-                \node[anchor= east] at (axis cs: .9, .9^2) {$f(N_P, sN_F)$};
+                \node[anchor= east] at (axis cs: .9, .9^2) {$N_C f(N_P, sN_F)$};
                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
@@
                 \addplot[name path=f, blue,ultra thick] {x^0.5};
-                \node[anchor=north west] at (axis cs: .6, .6^0.5) {$\tilde{f}(N_P, sN_F)$};
+                \node[anchor=north west] at (axis cs: .6, .6^0.5) {$N_C \tilde{f}(N_P, sN_F)$};
                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
@@
     \end{subfigure}
-    \caption{Distribution of value between the platform and the fringe (with $w(s) \equiv 1$)}
-    \label{fig:outcome_based_bargaining_power}
+    \caption{Distribution of value between the platform and the fringe.
+Profit shares correspond to the shaded areas.
+The platform's profit share is higher when the fringe firms are more substitutable.}
 \end{figure}
 
-The other main ingredient of the sharing rule, $w(s)$, captures the platform's \emph{innate} bargaining power.
-It is independent of the production function, demand, or the fringe firms' substitutability, and might represent, for example, that the platform and the fringe firms have different power to propose allocations during the (not explicitly modeled) negotiation process.\footnote{
-    For a more thorough exploration of this idea, see \textcite{hart1996bargaining}.
-}
-
-One way to think about the weighting is that the platform's share is the expectation of the total profit, when the number of fringe firms is drawn from $[0, N_F]$ according to some distribution.\footnote{
-    In fact, this is exactly the idea behind the Shapley value: the platform (and other players, too) gets its expected marginal contribution to the total profit.
-    As the fringe cannot create any value without the platform, the latter's marginal contribution to a coalition of $n_F$ fringe firms is simply $f(n_F)$.
-}
-An obvious choice is to use the uniform distribution, in which case the shares correspond to the Shapley value.
-However, this is not the only possible choice.
-If, for example, we want to assume that the platform has a higher innate bargaining power, we can use a distribution with a higher mass on the right tail.\footnote{
-    Specific choices for $w$ can also be motivated by cooperative game theoretical concepts.
-    For example using, $w(s) = \lambda t^{\lambda - 1}$ leads to the weighted Shapley value, with weights $\lambda$ and $1$ for the platform and the fringe firms, respectively.
-}
-When the distribution $W_1$ first order stochastically dominates another distribution $W_2$, the platform is more likely to draw a value from with a higher mass of fringe firms, and therefore obtain a higher profit share in case of $W_1$ than in the case of $W_2$.
-The next observation formalizes this idea.
-\begin{observation}
-    \label{prop:innate_bargaining_power}
-    Let $w, \tilde{w}: [0, 1] \to \mathbb{R}_0^+$ be two different weight functions such that $\int_0^x w_1(s) \ds \leq \int_0^x w_2(s) \ds$ for all $x \in [0, 1]$.
-    As before, let us denote the corresponding platform profit shares by $\pi_P$ and $\tilde{\pi}_P$.
-
-    Then, $\pi_P(N_P, N_F) \leq \tilde{\pi}_P(N_P, N_F) \; \forall\, N_P \geq 0, N_F > 0$.
-    Furthermore, this inequality is strict if $\int_0^x w_1(s) \ds < \int_0^x w_2(s) \ds$ on some non-zero measure set.
-\end{observation}
-
-Although the reasoning is straightforward, it establishes that $w$ can indeed be used to represent some form of innate bargaining power.
-For example, if one has reason to believe that the platform has a stronger voice in the negotiation process, one can use a weight function with a higher mass on larger values.
+\paragraph{Two-sided case} Alternatively, in certain settings, it might be appropriate to assume that the consumers (or, more generally, the entities on the other side of the market) also engage in the bargaining process.
+The cooperative game describing this situation is formalized in \cref{ass:profit_sharing_two_sided}.
+\begin{assumption}
+    \label{ass:profit_sharing_two_sided}
+    Consider the following cooperative game $\mathcal{G} = (\mathcal{N}, v)$.
+    The set of players consists of the platform plus the fringe firms: $\mathcal{N} = \{P, F_i, C_j\}, i \in [0, N_F], j \in [0, N_C]$.
+    The value of a coalition $S$ is zero without the platform, and depends on the number of fringe firms otherwise:
+    \begin{align*}
+        v(S) = \begin{cases}
+            0 & \text{if } P \notin S \\
+            n_C(S) f(N_P, n_F(S)) & \text{if } P \in S
+        \end{cases},
+    \end{align*}
+    where $n_F(S)$ and $n_C(S)$ is the measure of fringe firms and consumers, respectively, in $S$.
+    Each type of player gets their Shapley value in this game:
+    \begin{align*}
+        \pi_P(N_P, N_F, N_C) &= \varphi_P(\mathcal{G}), \\
+        \pi_F(N_P, N_F, N_C) &= \varphi_F(\mathcal{G}), \\
+        \pi_C(N_P, N_F, N_C) &= \varphi_F(\mathcal{G}).
+    \end{align*}
+\end{assumption}
+
+As in the one-sided case, simple expressions exist for these various shares.
+\begin{proposition}
+    \label{prop:profit_sharing_two_sided}
+    Consider the case when only the platform and the fringe firms participate in the bargaining process.
+    Then, the resulting profit shares are given by
+    \begin{align*}
+        \pi_P(N_P, N_F, N_C) &= N_C \int_0^1 s f(N_P, s N_F) \ds, \\
+        \pi_F(N_P, N_F, N_C) &= N_C \int_0^1 s^2 N_F \partial_2 f(N_P, s N_F) \ds \\
+        \pi_C(N_P, N_F, N_C) &= N_C \int_0^1 s f(N_P, s N_F) \ds.
+    \end{align*}
+\end{proposition}
+\begin{proof}[proof of \cref{prop:profit_sharing}]
+    This result is a direct application of Proposition 11 in \textcite{stancsics2023value}.
+\end{proof}
+One thing to note is that the platform's and fringe firms' shares are lower than in the one-sided case.
+This is due to the fact of needing to share the pie with the consumers, too.
+Additionally, the platform's share is identical to the consumers' (aggregated) share.\footnote{
+    This stems from the linearity of the profit function in the number of consumers.
+}
+This foreshadows the idea that -- even though it might not be welfare-maximizing -- what's good for the platform might also good for the consumers in the two-sided case.
 
 \subsection{Entry and equilibrium}
+
+Throughout the paper, I will assume that the number of consumers is fixed and exogenous.
+They are thus passive in the sense that they do not make a decision about whether to enter the market or not.
+However, when developing microfoundations for $f$ in \cref{sec:example}, consumers will make consumption choices, and their welfare will be of interest.
+The product variety of the platform is also exogeneous.
 
@@
 Assume that there is an unlimited number of potential fringe entrants, indexed by $i \in \mathbb{R}^+_0$.
-In the first stage of the game, each fringe firm must create a viable product at the investment cost $I_F > 0$.
+In the first stage of the game, each fringe firm must create a viable product at an investment cost $I_F > 0$.
 In the second stage, firms that made this investment plus the platform engage in producing and selling their respective products.
-If there are $N_F$ fringe entrants and $N_P$ platform products, then, as discussed previously, the total profit they make together is given by $f(N_P, N_F)$.
-Finally, the platform and the entrants share this profit according to the profit sharing rule from \cref{ass:profit_sharing}.
-
-The equilibrium number of entrants is determined by a free entry condition: in the end, the fringe firms' profits should be equal to the investment cost.
+If there are $N_F$ fringe entrants along with $N_P$ platform products and $N_C$ consumers, then, as discussed previously, the total value they create together is given by $\Pi(N_P, N_F, N_C) = N_C f(N_P, N_F)$.
+Finally, the platform and the entrants share this profit according to the profit sharing rule from \cref{ass:profit_sharing} or \cref{ass:profit_sharing_two_sided}, and the fringe gets $\pi_F(N_P, N_F, N_C)$.
+
+The equilibrium number of entrants is determined by a free entry condition: in the end, the fringe firms' total profits should be equal to the aggregated investment cost.
 \begin{definition}
@@
     \begin{itemize}
-        \item Profits are shared according to \cref{ass:profit_sharing}.
+        \item Profits are shared according to \cref{ass:profit_sharing} or \cref{ass:profit_sharing}.
         \item Entrants make zero profits: $\pi_F(N_P, N_F) = I_F N_F$ after accounting for entry costs.
@@
 
-Finally, in order to guarantee a unique equilibrium, let us make the following, an additional assumption about the profit and bargaining weight functions.
+Finally, in order to guarantee a unique equilibrium, let us make the following, an additional assumption about the profit function.
 \begin{assumption}
     \label{ass:single_crossing}
-    Let $f$ and $w$ be such that the following holds for all $N_F, N_P \geq 0$:
-    \begin{gather*}
-        f'_{n_F} (N_P, N_F) < \int_0^1 s w(s) f'_{n_F} (N_P, s N_F) \ds \\
-        \text{or} \\
-        f''_{n_F} (N_P, N_F) < \int_0^1 s^2 w(s) f''_{n_F} (N_P, s N_F) \ds.
-    \end{gather*}
+    Let $f$ be such that the following holds for all $N_F, N_P, N_C \geq 0$:
+    \begin{align*}
+        \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_F} < 0 \text{ or } \frac{\partial^2 \pi_F(N_P, N_F, N_C)}{\partial N_F^2} < 0
+    \end{align*}
 \end{assumption}
-The above assumption essentially guarantees that the profit of the fringe (as a function of the number of entrants) has at most a single crossing with the total entry cost (apart from the obvious $N_F=0$ intersection).
-While the conditions is not very simple to interpret, they can be verified once a specific choice for $f$ and $w$ is made.
-In particular, this assumption will be satisfied in the example in \cref{sec:example}.
+This assumption essentially guarantees that the profit of the fringe (as a function of the number of entrants) has at most a single crossing with the --linear -- total entry cost (apart from the obvious $N_F=0$ intersection).
+The interpretation of the assumption itself is simple: total fringe profits, as a function of the number of fringe firms, must be either concave or hump-shaped.\footnote{
+    As it turns out, even though total industry profits are assumed to be increasing in $n_f$, it is not necessarily true for fringe profits.
+    For certain profit functions, it happens that even though the size of the pie increases, the bargaining position of the fringe deteriorates so much that they get a smaller share even in absolute value.
+}
+What it requires of $f$, however, is not so obvious, and also depends on whether one assumes one-sided or two-sided bargaining.
+Nevertheless, when microfounding the profit function, one can simply check whether this assumption holds or not.
+In particular, it will be satisfied for the logit-type demand in \cref{sec:example}.
 
@@
 
-\section{Example application}
+\section{Logit demand}
 \label{sec:example}
 
-Let us now turn to an example application of the somewhat abstract model presented in the previous sections.
+Let us now add more structure to the model, and microfound the profit function $\Pi$.
 The model in this section is heavily inspired by the logit-like demand structure and hybrid platform setting in  \textcite{anderson2021hybrid}.
@@
 Furthermore, consumers have the same i.i.d. taste shocks ($\epsilon^P_{ij}$) for platform products as for the products offered by the other sellers.
-Finally, I assume that the product prices its products as if they were produced by separate, monopolistically competitive sellers.
+Finally, I assume that the platform prices its products as if they were produced by separate, monopolistically competitive sellers.
 That is, it does not take into account the fact that it can affect a non-zero measure of the prices, and therefore the aggregate demand.
@@
     \begin{align*}
-        \partial_F \pi_F(N_P^*, N_F^*) := \left. \frac{\partial \pi_F(N_P, N_F)}{\partial N_F} \right|_{N_P = N_P*, N_F = N_F^*}.
+        \partial_F \pi_F(N_P^*, N_F^*) \coloneqq \left. \frac{\partial \pi_F(N_P, N_F)}{\partial N_F} \right|_{N_P = N_P*, N_F = N_F^*}.
     \end{align*}
@@
     \end{align*}
-    Finally, let the following hold:
+    Finally, let us bound the difference between $\pi_F(N''_Pm \bar{N}_F) - I_F \bar{N}_F$ from above:
     \begin{align*}

### 2023-12-06 src/paper/application.tex
Start rewriting general results

@@
 This section presents some general result that only depend on the abstract model structure described in the previous section, and the assumptions therein.
-It is remarkable that even within such a stylized setting and simple model, one can derive some interesting and non-trivial results.
-\Cref{sec:example} will then build on these results to derive some stronger implications in a more specific model.
+It turns out that even within such a general setting, one can derive some interesting and non-trivial results.
+\Cref{sec:example} will then build on these results to derive stronger results in a more fully specific model.
 
@@
 For the following two propositions, let us ignore free entry and equilibrium behavior, and consider the number of fringe entrants $N_F$ as fixed.
-The following statement says that the platform's profit is increasing in its own product variety.
+The following statement claims that -- in both the one-sided and two-sided bargaining cases -- the platform's profits are increasing in its own product variety.
 \begin{proposition}
@@
     Then $\pi_P$ is also differentiable and
-    $$\frac{\partial \pi_P(N_P, N_F)}{\partial N_P} > 0$$.
+    \begin{align*}
+        \frac{\partial \pi_P(N_P, N_F)}{\partial N_P} > 0.
+    \end{align*}
 \end{proposition}
@@
 Therefore, an increase in $N_P$ also increases the size of the pie the participants bargain over.
-This result states that the size of the pie that the platform gets increases in this case, too.
-It does not mean, however, that the \emph{relative share} of the pie that the platform gets is also bigger -- increase is also guaranteed in absolute terms.
-For example, it is possible that for the new, higher value of $N_P$, the complementarities between the fringe firms become stronger, and the platform's bargaining power decreases.
-This decrease cannot be so strong, however, to decrease the platform's profits in absolute terms.
+This result states that the slice of the pie that the platform gets increases in this case, too.
+It does not mean, however, that the \emph{relative share} of the pie that the platform gets is also bigger -- increase is only guaranteed in absolute terms.
+For example, it is possible that for the new, higher value of $N_P$, the complementarities between the fringe firms become stronger, and the platform's bargaining power decreases.\footnote{
+    In fact, one can show that this is the case if the cross-derivatives of $f$ are negative.
+}
+As this result shows, this decrease cannot be large enough to decrease the platform's profits in absolute terms.
 \cref{fig:increase_N_P_platform} shows an example of this situation.
@@
                 \addplot[name path=tildef, dashed, black] {x};
-                \node[anchor=north west] at (axis cs: .6, 0.5) {$f(N_P, sN_F)$};
+                \node[anchor=north west] at (axis cs: .5, .4) {$N_C f(N_P, sN_F)$};
                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
@@
                 \addplot[name path=tildef, blue,ultra thick] {x};
-                \node[anchor=south east] at (axis cs: 0.6, 0.6) {$f(N_P', sN_F)$};
+                \node[anchor=south east] at (axis cs: 0.6, 0.6) {$N_C f(N_P', sN_F)$};
                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
@@
     \end{subfigure}
-    \caption{Illustration of \cref{prop:share_of_platform} ($N_P < N_P'$)}
+    \caption{Illustration of \cref{prop:share_of_platform} in the one-sided bargaining case.
+The right hand side figure shows a world with larger platform product variety ($N_P < N_P'$).
+Even though the platform's share of the total profits is smaller in relative terms in that case, it is still larger in absolute terms.}
     \label{fig:increase_N_P_platform}
@@
 \begin{proof}[Proof of \cref{lem:slope_at_eq}]
-    Let us use Leibniz' rule to obtain the first two derivatives of the fringe's profit with respect to the number of fringe firms:
-    \begin{align*}
-        \frac{\partial f(N_P, sN_F)}{\partial N_F} &= \frac{\partial}{\partial N_F} \left[ f(N_P, N_F) - \int_0^1 w(s) f(N_P, sN_F) \ds \right] \\
-        &= \frac{\partial f(N_P, N_F)}{\partial N_F} - \int_0^1 s w(s) \frac{\partial f(N_P, sN_F)}{\partial N_F} \ds, \\
-        \frac{\partial^2 f(N_P, sN_F)}{\partial N_F^2} &= \frac{\partial^2}{\partial N_F^2} \left[ f(N_P, N_F) - \int_0^1 w(s) f(N_P, sN_F) \ds \right] \\
-        &= \frac{\partial^2 f(N_P, N_F)}{\partial N_F^2} - \int_0^1 s^2 w(s) \frac{\partial f(N_P, sN_F)}{\partial N_F^2} \ds.
-    \end{align*}
-    Therefore, \cref{ass:single_crossing} implies that at any $N_F$, $\pi_F(N_P, N_F)$ is either concave or decreasing.
-
-    In the remainder, for ease of notation, let us denote partial derivatives as follows:
+    \cref{ass:single_crossing} states that at any $N_F \geq 0$, $\pi_F(N_P, N_F)$ is either concave or decreasing.
+    In the remainder, for ease of notation drop $N_C$ from the arguments of $\pi_F$ profit function as it is simply a multiplicative constant, and let us denote partial derivatives as follows:
     \begin{align*}
@@
     \begin{align*}
-        \frac{\partial \pi_P(N_P, N_F)}{\partial N_P} &= \frac{\partial}{\partial N_P} \int_0^1 w(s) f(N_P, N_F) \ds \\
-        &= \int_0^1 w(s) \underbrace{\frac{\partial f(N_P, sN_F)}{\partial N_P}}_{> 0} \ds > 0.
-    \end{align*}
+        \frac{\partial \pi_P(N_P, N_F, N_C)}{\partial N_P} &= N_C \frac{\partial}{\partial N_P} \int_0^1 w(s) f(N_P, N_F) \ds \\
+        &= \int_0^1 w(s) \underbrace{\frac{\partial f(N_P, sN_F)}{\partial N_P}}_{> 0} \ds > 0
+    \end{align*}
+    for any continuous $w(s)$.
+    In particular, this holds for $w(s) = 1$ and $w(s) = s$, which correspond to assumptions \cref{ass:profit_sharing} and \cref{ass:profit_sharing_two_sided}, respectively.
 \end{proof}

### 2023-12-06 src/paper/application.tex
Make figures nicer

@@
 
+\definecolor{myblue}{rgb}{0.3, 0.45, 0.69}
+\definecolor{myred}{rgb}{0.87, 0.52, 0.32}
+
 \pgfplotstableread[col sep=comma]{out/figures/equilibrium.csv}\equilibrium
@@
                     xtick={0, 1}, ytick=\empty, xlabel={$s$}]
-                \addplot[name path=f, blue,ultra thick] {x^2};
+                \addplot[name path=f, black, thick] {x^2};
                 \node[anchor= east] at (axis cs: .9, .9^2) {$N_C f(N_P, sN_F)$};
@@
                 xtick={0, 1}, ytick=\empty, xlabel={$s$}]
-                \addplot[name path=f, blue,ultra thick] {x^0.5};
+                \addplot[name path=f, black, thick] {x^0.5};
                 \node[anchor=north west] at (axis cs: .6, .6^0.5) {$N_C \tilde{f}(N_P, sN_F)$};
@@
 
-        \draw[name path=piF,domain=0.01:5.5,variable=\x,blue,ultra thick] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
-        \draw[name path=IF,domain=0.01:5.5,variable=\x,red,ultra thick] plot ({\x},{(\x)/3});
-        \node[anchor=north east] at (5,1) {$\pi_F(N_P, n_F)$};
-        \node[anchor=south east] at (5,5/3) {$I_F n_F$};
+        \draw[name path=piF,domain=0.01:5.5,variable=\x,black,thick] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
+        \draw[name path=IF,domain=0.01:5.5,variable=\x,black,dashed,thick] plot ({\x},{(\x)/3});
+        \node[anchor=north east] at (5,1) {$\pi_F(N_P, N_F)$};
+        \node[anchor=south east] at (5,5/3) {$I_F N_F$};
 
@@
                 xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
-                \addplot[name path=f, blue,ultra thick] {ln(1+x)};
-                \addplot[name path=tildef, dashed, black] {x};
+                \addplot[name path=f, black, thick] {ln(1+x)};
+                % \addplot[name path=tildef, dashed, black] {x};
                 \node[anchor=north west] at (axis cs: .5, .4) {$N_C f(N_P, sN_F)$};
@@
                 \addplot[name path=f, dashed, black] {ln(1+x)};
-                \addplot[name path=tildef, blue,ultra thick] {x};
+                \addplot[name path=tildef, black, thick] {x};
                 \node[anchor=south east] at (axis cs: 0.6, 0.6) {$N_C f(N_P', sN_F)$};
@@
                 xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
-                \addplot[name path=f, blue,ultra thick] {sqrt(x)};
-                \addplot[name path=tildef, dashed, black] {sqrt(0.5+x)};
-                \node[anchor=north west] at (axis cs: .6, 0.77) {$f(0, sN_F)$};
+                \addplot[name path=f, black, thick] {sqrt(x)};
+                % \addplot[name path=tildef, dashed, black] {sqrt(0.5+x)};
+                \node[anchor=north west] at (axis cs: .6, 0.77) {$N_C f(0, sN_F)$};
                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
@@
                 \addplot[name path=f, dashed, black] {sqrt(x)};
-                \addplot[name path=tildef, blue,ultra thick] {sqrt(0.5+x)};
-                \node[anchor=north west] at (axis cs: 0, 0.7) {$f(0.5, sN_F)$};
+                \addplot[name path=tildef, black, thick] {sqrt(0.5+x)};
+                \node[anchor=north west] at (axis cs: 0.05, 0.75) {$N_C f(N_P', sN_F)$};
                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                 \draw[name path=top] (axis cs:0,1.225) -- (axis cs:1,1.225);
+                \draw[name path=top_old, dashed] (axis cs:0,1) -- (axis cs:1,1);
                 \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1.225);
@@
 
-        \draw[name path=piF,domain=0.01:5.5,variable=\x,blue,ultra thick] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
-        \draw[name path=piF2,domain=0.01:5.5,variable=\x,blue,ultra thick] plot ({\x},{6*((\x)/(0.3+\x))-6*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
-        \draw[name path=IF,domain=0.01:5.5,variable=\x,red,ultra thick] plot ({\x},{(\x)/3});
+        \draw[name path=piF,domain=0.01:5.5,variable=\x,black, thick] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
+        \draw[name path=piF2,domain=0.01:5.5,variable=\x,black, thick] plot ({\x},{6*((\x)/(0.3+\x))-6*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
+        \draw[name path=IF,domain=0.01:5.5,variable=\x,black,dashed,thick] plot ({\x},{(\x)/3});
 
@@
             ]
-            \addplot[color=red,mark=none,very thick] table[x=N_P,y=N_F_bench]{\equilibrium};
-            \addplot[color=blue,mark=none,very thick] table[x=N_P,y=N_F]{\equilibrium};
+            \addplot[color=myred,mark=none,thick] table[x=N_P,y=N_F_bench]{\equilibrium};
+            \addplot[color=myblue,mark=none,thick] table[x=N_P,y=N_F]{\equilibrium};
             \addplot[color=black,mark=none,thick,dotted] table[x=N_P,y=N_F_cf]{\equilibrium};
@@
             ]
-            \addplot[color=blue,mark=none,very thick] table[x=N_P,y=A_bench]{\equilibrium};
-            \addplot[color=red,mark=none,very thick] table[x=N_P,y=A]{\equilibrium};
+            \addplot[color=myblue,mark=none,thick] table[x=N_P,y=A_bench]{\equilibrium};
+            \addplot[color=myred,mark=none,thick] table[x=N_P,y=A]{\equilibrium};
             \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=A_noF]{\equilibrium};
@@
             ]
-            \addplot[color=blue,mark=none,very thick] table[x=N_P,y=pi_P_bench]{\equilibrium};
-            \addplot[color=red,mark=none,very thick] table[x=N_P,y=pi_P]{\equilibrium};
+            \addplot[color=myblue,mark=none,thick] table[x=N_P,y=pi_P_bench]{\equilibrium};
+            \addplot[color=myred,mark=none,thick] table[x=N_P,y=pi_P]{\equilibrium};
             \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=pi_P_noF]{\equilibrium};
@@
             ]
-            \addplot[color=blue,mark=none,very thick] table[x=N_P,y=F_F_opt]{\equilibrium};
-            \addplot[color=red,mark=none,very thick] table[x=N_P,y=F_F_implied]{\equilibrium};
+            \addplot[color=myblue,mark=none,thick] table[x=N_P,y=F_F_opt]{\equilibrium};
+            \addplot[color=myred,mark=none,thick] table[x=N_P,y=F_F_implied]{\equilibrium};
             \legend{Benchmark (optimal), Bargaining (implied)}

### 2023-12-06 src/paper/theory.tex
Make figures nicer

@@
                     xtick={0, 1}, ytick={0}, xlabel={$s$}]
-                \addplot[name path=f, ultra thick] {x^0.5};
+                \addplot[name path=f, thick] {x^0.5};
                 \node[anchor=north west] at (axis cs: .8, .8^0.5) {$f$};
@@
                     xtick={0, 1}, ytick={0}, xlabel={$s$}]
-                \addplot[name path=f, ultra thick] {x^1.5};
+                \addplot[name path=f, thick] {x^1.5};
                 \node[anchor=south east] at (axis cs: .8, .8^1.5) {$f$};
@@
                 xlabel={Complementarity between fringe players ($\alpha$)}, ylabel={Share of the fringe}]
-            \addplot[name path=f, ultra thick] {x / (1 + x)};
+            \addplot[name path=f, thick] {x / (1 + x)};
             \node[anchor=north west] at (axis cs: 3, 3/4) {$\frac{\varphi_A^\infty(\bar{n})}{f(\bar{n})}$};
@@
                 xtick={0, 1}, ytick={0, 1, 2, 3}, axis lines=left, xlabel={$t$}, legend pos=south east]
-                \addplot[ultra thick] {0.5 * x ^ (-0.5)};
-                \addplot[ultra thick, dashed] {1};
-                \addplot[ultra thick, dotted] {1.5 * x ^ (0.5)};
+                \addplot[thick] {0.5 * x ^ (-0.5)};
+                \addplot[thick, dashed] {1};
+                \addplot[thick, dotted] {1.5 * x ^ (0.5)};
             \end{axis}
@@
                 xtick={0, 1}, ytick={0, 1}, axis lines=left, xlabel={$t$}, legend pos=south east]
-                \addplot[ultra thick] {x ^ (0.5)};
-                \addplot[ultra thick, dashed] {x};
-                \addplot[ultra thick, dotted] {x ^ (1.5)};
+                \addplot[thick] {x ^ (0.5)};
+                \addplot[thick, dashed] {x};
+                \addplot[thick, dotted] {x ^ (1.5)};
                 \legend{$\lambda = 0.5$, $\lambda = 1$, $\lambda = 1.5$}
@@
                 xtick={0, 1}, ytick={0, 1}, axis lines=left, xlabel={$t$}, legend pos=north west]
-                \addplot[ultra thick] {1};
-                \addplot[ultra thick, dashed] {1-x};
-                \addplot[ultra thick, dotted] {(1-x)^2};
+                \addplot[thick] {1};
+                \addplot[thick, dashed] {1-x};
+                \addplot[thick, dotted] {(1-x)^2};
             \end{axis}
@@
                 xtick={0, 1}, ytick={0, 1}, axis lines=left, xlabel={$t$}, legend pos=north west]
-                \addplot[ultra thick] {x};
-                \addplot[ultra thick, dashed] {x - x^2/2};
-                \addplot[ultra thick, dotted] {x - x^2 + x^3/3};
+                \addplot[thick] {x};
+                \addplot[thick, dashed] {x - x^2/2};
+                \addplot[thick, dotted] {x - x^2 + x^3/3};
                 \legend{$m = 1$, $m = 2$, $m = 3$}
@@
                 xtick={0, 1}, ytick={0, 1, 2, 3}, axis lines=left, xlabel={$t$}, legend pos=north west]
-                \addplot[ultra thick] {1};
-                \addplot[ultra thick, dashed] {2 * (1-x)};
-                \addplot[ultra thick, dotted] {3 * ((1-x)^2)};
+                \addplot[thick] {1};
+                \addplot[thick, dashed] {2 * (1-x)};
+                \addplot[thick, dotted] {3 * ((1-x)^2)};
             \end{axis}
@@
                 xtick={0, 1}, ytick={0, 1}, axis lines=left, xlabel={$t$}, legend pos=north west]
-                \addplot[ultra thick] {x};
-                \addplot[ultra thick, dashed] {2 * (x - x^2/2)};
-                \addplot[ultra thick, dotted] {3 * (x - x^2 + x^3/3)};
+                \addplot[thick] {x};
+                \addplot[thick, dashed] {2 * (x - x^2/2)};
+                \addplot[thick, dotted] {3 * (x - x^2 + x^3/3)};
                 \legend{$m = 1$, $m = 2$, $m = 3$}
@@
                     xtick={0, 1}, ytick={0}, xlabel={$s$}]
-                \addplot[name path=f, ultra thick] {x^0.5};
-                \addplot[name path=f0, ultra thick] {0.3 * x^0.5};
+                \addplot[name path=f, thick] {x^0.5};
+                \addplot[name path=f0, thick] {0.3 * x^0.5};
                 \node[anchor=north west] at (axis cs: .8, .8^0.5) {$f$};
@@
                     xtick={0, 1}, ytick={0}, xlabel={$s$}]
-                \addplot[name path=f, ultra thick] {x^0.5};
-                \addplot[name path=f0, ultra thick] {0.7 * x^0.5};
+                \addplot[name path=f, thick] {x^0.5};
+                \addplot[name path=f0, thick] {0.7 * x^0.5};
                 \node[anchor=north west] at (axis cs: .8, .8^0.5) {$f$};
@@
             % highlight the diagonal
-            \addplot3[black, name path=diagonal, ultra thick, domain=0:1, samples=100, samples y=0] ({x}, {x}, {0});
-            \addplot3[black, name path=f_diagonal, ultra thick, domain=0:1, samples=100, samples y=0] ({x}, {x}, {x^2});
+            \addplot3[black, name path=diagonal, very thick, domain=0:1, samples=100, samples y=0] ({x}, {x}, {0});
+            \addplot3[black, name path=f_diagonal, very thick, domain=0:1, samples=100, samples y=0] ({x}, {x}, {x^2});
             \addplot[blue, fill opacity=0.5] fill between[of=diagonal and f_diagonal];
@@
             % highlight the diagonal
-            \addplot3[black, name path=diagonal, ultra thick, domain=0:1, samples=100, samples y=0] ({x}, {x^3}, {0});
-            \addplot3[black, name path=f_diagonal, ultra thick, domain=0:1, samples=100, samples y=0] ({x}, {x^3}, {x^4});
+            \addplot3[black, name path=diagonal, very thick, domain=0:1, samples=100, samples y=0] ({x}, {x^3}, {0});
+            \addplot3[black, name path=f_diagonal, very thick, domain=0:1, samples=100, samples y=0] ({x}, {x^3}, {x^4});
             \addplot[blue, fill opacity=0.5] fill between[of=diagonal and f_diagonal];

### 2023-12-06 src/paper/application.tex
Update proofs and propositions for general case

@@
     \label{prop:aggregate_size_additive}
-    Let the weight function be constant ($w(t) \equiv 1$).
-    % TODO: I think the weight function assumption is not necessary.
-    Furthermore, let $f$ have the following, additive form:
+    Let $f$ have the following, additive form:
     \begin{align*}
@@
     \begin{align*}
-        \pi_F(N_P, N_F) = f(N_P, N_F) - \int_0^1 w(s) f(N_P, N_F) \ds.
-    \end{align*}
-    $f(N_P, N_F)$ is continuously differentiable in $N_P$, therefore the Leibniz rule can be applied to obtain
-    \begin{align*}
-        \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} &= \frac{\partial}{\partial N_P} \left[ f(N_P, N_F) - \int_0^1 w(s) f(N_P, N_F) \ds \right]\\
-        &= \frac{\partial f(N_P, N_F)}{\partial N_P} - \int_0^1 w(s) \frac{\partial f(N_P, sN_F)}{\partial N_P} \ds \\
-        &= \underbrace{h(N_F)}_{(*)} - \underbrace{\int_0^1 w(s) h(s N_F)}_{(**)}
-    \end{align*}
-    where $h(N_F) = \frac{\partial h(N_F)}{\partial N_P}$.
-
-    Notice that $(*)$ and $(**)$ are both positive.
-    Furthermore, $(**)$ is the weighed average of $(*)$ over the interval $[0, N_F]$.
-    Therefore, if $h(N_F)$ is strictly increasing, then $(*) > (**)$, and the whole expression is positive.
-    Conversely, it is negative if $h(N_F)$ is strictly decreasing.
-
-    If $h(N_F)$ is differentiable, then it is equivalent to saying that
-    \begin{align*}
-        \frac{\mathrm{d}h(N_F)}{\mathrm{d}N_F} = \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} < 0 &\implies \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} < 0 \\
-        \frac{\mathrm{d}h(N_F)}{\mathrm{d}N_F} = \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} > 0 &\implies \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} > 0
+        \pi_F(N_P, N_F, N_C) = N_C \int_0^1 w(s) N_F \partial_2 f(N_P, s N_F) \ds,
+    \end{align*}
+    where $w(s)$ is either $s$ or $s^2$, depending on whether one assumes one or two-sided bargaining.
+    By assumption, $f$ is twice continuously differentiable, therefore $\partial_2$ is also continuously differentiable in $N_P$.
+    Thus the Leibniz rule can be applied to obtain
+    \begin{align*}
+        \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P} &= \frac{\partial}{\partial N_P} N_C \int_0^1 w(s) N_F \partial_2 f(N_P, s N_F) \ds \\
+        &= N_C \int_0^1 w(s) N_F \frac{\partial}{\partial N_P} \partial_2 f(N_P, s N_F) \ds \\
+        &= N_C \int_0^1 w(s) N_F \partial^2_{12} f(N_P, s N_F) \ds.
+    \end{align*}
+
+    As $w(s) > 0$ for $s > 0$, if $\partial_2 f(N_P, s N_F)$ has the same sign over $[0, N_F]$, then the integral also has the same sign.
+    Formally,
+    \begin{align*}
+        \forall n_F \in [0, N_F] \enspace \frac{\partial^2 f(N_P, n_F)}{\partial N_P \partial n_F} < 0 &\implies \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P} < 0 \\
+        \forall n_F \in [0, N_F] \enspace \frac{\partial^2 f(N_P, n_F)}{\partial N_P \partial n_F} > 0 &\implies \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P} > 0
     \end{align*}
@@
     \begin{align*}
-        \frac{\partial N_F}{\partial N_P} = \frac{\frac{\partial \pi_F(N_P, N_F)}{\partial N_P}}{I_F - \frac{\partial \pi_F (N_P, N_F)}{\partial N_F}}
-    \end{align*}
-    The derivative exists if the above expression is well-defined, i.e. $\frac{\partial \pi_F (N_P, N_F)}{\partial N_F} \neq I_F$.
-    Remember from \cref{prop:share_of_fringe} that the numerator of this expression is negative under the condition $\frac{\partial^2 f(N_P, N_F)}{\partial N_P \partial N_F}$.
+        \frac{\partial N_F}{\partial N_P} = \frac{\frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P}}{I_F - \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F}}
+    \end{align*}
+    The derivative exists if the above expression is well-defined, i.e. $\frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} \neq I_F$.
+    Remember from \cref{prop:share_of_fringe} that the numerator of this expression is negative under the condition $\frac{\partial^2 f(N_P, N_F, N_C)}{\partial N_P \partial N_F}$.
     Now all we need to show to conclude the proof is that
     \begin{align*}
-        \frac{\partial \pi_F (N_P, N_F)}{\partial N_F} < I_F,
+        \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} < I_F,
     \end{align*}
@@
     First, let us show that fringe profits are lower than total investment costs if $\bar N_F = N_F^*(N_P') - \frac{\alpha}{\beta}\Delta$.
-    In order to do this, consider this formulation of fringe profits:
-    \begin{align*}
-        \pi_F(N_P', N_F') &= f(N_P', N_F') - \int_0^1 w(s) f(N_P', t N_F') \dt \\
-        &= \int_0^1 t \frac{\partial f(N_P', n_F')}{\partial n_F} \bigg|_{n_F = t N_F'},
-    \end{align*}
-    which can be obtained by integration by parts.
-    Now let us use the functional form assumption $f(N_P, N_F) = g(\alpha N_P + \beta N_F)$ to obtain
-    \begin{align*}
-        \pi_F(N_P, N_F) = \int_0^1 t \underbrace{\frac{\partial}{\partial t}g(\alpha N_P + \beta t N_F)}_{\coloneq D(N_P, N_F)} \dt.
-    \end{align*}
+    In order to do this, consider the following formulation of the fringe profit function:
+    \begin{align*}
+        \pi_F(N_P', N_F', N_C) &= \int_0^1 w(t) \frac{\Pi(N_P, t N_F, N_C)}{\partial t} \dt \\
+        &= N_C \int_0^1 w(t) \underbrace{\frac{\partial}{\partial t}g(\alpha N_P + \beta t N_F)}_{\coloneq D(N_P, N_F)} \dt,
+    \end{align*}
+    where $w(t) = t$ or $w(t) = t^2$ in the one-sided and two-sided bargaining cases, respectively.
 
@@
     \begin{align*}
-        \pi_F(N_P', N_F') &= N_F' \beta \int_0^1 t g'(\alpha N_P' + \beta t N_F') \dt, \\
-        \pi_F(N_P'', \bar{N}_F) &= \bar{N}_F \beta \int_0^1 t g'(\alpha N_P' + \beta t N_F' + \Delta \alpha (1-t)) \dt.
+        \pi_F(N_P', N_F', N_C) &= N_C N_F' \beta \int_0^1 w(t) g'(\alpha N_P' + \beta t N_F') \dt, \\
+        \pi_F(N_P'', \bar{N}_F, N_C) &= N_C \bar{N}_F \beta \int_0^1 w(t) g'(\alpha N_P' + \beta t N_F' + \Delta \alpha (1-t)) \dt.
     \end{align*}
@@
     \begin{align*}
-        \pi_F(N_P'', \bar{N}_F) - I_F \bar{N}_F &= \frac{\bar{N}_F}{N_F'}\left[\beta \int_0^1 t g'(\alpha N_P' + \beta t N_F' + \Delta \alpha (1-t)) \dt - I_F N_F' \right] \\
-        &< \frac{\bar{N}_F}{N_F'}\left[\beta \int_0^1 t g'(\alpha N_P' + \beta t N_F') \dt - I_F N_F' \right] \\
-        &= \frac{\bar{N}_F}{N_F'}\left[ \pi_F(N_P', N_F') - I_F N_F \right] \\
+        \pi_F(N_P'', \bar{N}_F, N_C) - I_F \bar{N}_F &= \frac{\bar{N}_F}{N_F'}\left[\beta N_C \int_0^1 w(t) g'(\alpha N_P' + \beta t N_F' + \Delta \alpha (1-t)) \dt - I_F N_F' \right] \\
+        &< \frac{\bar{N}_F}{N_F'}\left[\beta N_C \int_0^1 w(t) g'(\alpha N_P' + \beta t N_F') \dt - I_F N_F' \right] \\
+        &= \frac{\bar{N}_F}{N_F'}\left[ \pi_F(N_P', N_F', N_C) - I_F N_F \right] \\
         &= 0.
     \end{align*}
-    The inequality is due to the concavity of $g$, and the final equality is the result of profits being zero in the equilibrium $(N_P', N_F')$.
-
-    All that remains to be shown is that $\pi_F(N_P'', N_F'') < N_F'' I_F$.
+    The inequality is due to the concavity of $g$, and the final equality is the result of profits being zero in the equilibrium $(N_P', N_F', N_C)$.
+
+    All that remains to be shown is that $\pi_F(N_P'', N_F'', N_C) < N_F'' I_F$.
     This is a consequence of the fact that, under \cref{ass:single_crossing}, $\pi_F$ is either concave or decreasing in $N_F$.
-    As a consequence, if it at some point ($\bar{N}_F$) dips below the linear function $N_F \mapsto I_F N_F$, it can never reach it again for any $N_F'' > \bar{N}_F$.
-    With this we arrive at a contradiction, as $(N_P'', N_F'')$ cannot be an equilibrium.
+    Therefore, if it at some point ($\bar{N}_F$) dips below the linear function $N_F \mapsto I_F N_F$, it can never reach it again for any $N_F'' > \bar{N}_F$.
+    With this we arrive at a contradiction, as $(N_P'', N_F'', N_C)$ cannot be an equilibrium.
 

### 2023-12-06 src/paper/application.tex
Add a useful lemma

@@
         \pi_P(N_P, N_F, N_C) &= \varphi_P(\mathcal{G}), \\
-        \pi_F(N_P, N_F, N_C) &= \varphi_F(\mathcal{G}).
-    \end{align*}
+        \pi_F(N_P, N_F, N_C) &= \varphi_F(\mathcal{G}),
+    \end{align*}
+    where $\varphi_i(\mathcal{G})$ denotes the Shapley value of player(s) $i$ in game $\mathcal{G}$.
 \end{assumption}
@@
                 \addplot[name path=f, black, thick] {x^2};
-                \node[anchor= east] at (axis cs: .9, .9^2) {$N_C f(N_P, sN_F)$};
+                \node[anchor= east] at (axis cs: .5, .5^2) {$N_C f(N_P, sN_F)$};
                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
@@
                 \addplot[name path=f, black, thick] {x^0.5};
-                \node[anchor=north west] at (axis cs: .6, .6^0.5) {$N_C \tilde{f}(N_P, sN_F)$};
+                \node[anchor=north west] at (axis cs: .5, .5^0.5) {$N_C \tilde{f}(N_P, sN_F)$};
                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
@@
         \pi_F(N_P, N_F, N_C) &= \varphi_F(\mathcal{G}), \\
-        \pi_C(N_P, N_F, N_C) &= \varphi_F(\mathcal{G}).
-    \end{align*}
+        \pi_C(N_P, N_F, N_C) &= \varphi_F(\mathcal{G}),
+    \end{align*}
+    where $\varphi_i(\mathcal{G})$ denotes the Shapley value of player(s) $i$ in game $\mathcal{G}$.
 \end{assumption}
@@
         \draw[->] (0,0) -- (0,2);
-        \draw[->] (0,0) -- (5.5,0) node[below] {$n_F$};
+        \draw[->] (0,0) -- (5.5,0) node[below] {$N_F$};
 
@@
         \draw[name path=IF,domain=0.01:5.5,variable=\x,black,dashed,thick] plot ({\x},{(\x)/3});
-        \node[anchor=north east] at (5,1) {$\pi_F(N_P, N_F)$};
+        \node[anchor=north east] at (5,1) {$\pi_F(N_P, N_F, N_C)$};
         \node[anchor=south east] at (5,5/3) {$I_F N_F$};
@@
     \end{tikzpicture}
-    \caption{An example free entry equilibrium under \cref{ass:single_crossing}}
+    \caption{An example free entry equilibrium.
+\Cref{ass:single_crossing} states that the fringe profit function is concave or hump-shaped in $N_F$, guaranteeing at most one intersection with the linear entry cost function.}
     \label{fig:equilibrium}
@@
     \end{subfigure}
-    \caption{Illustration of \cref{prop:share_of_fringe} (fringe firms are substitutes, $f(N_P, N_F) = \sqrt{N_P + N_F}$)}
+    \caption{Illustration of \cref{prop:share_of_fringe} when fringe and platforrm products are substitutes.
+An increase in the platform's product variety increases total profits, yet, the fringe's share decreases in absolute terms.}
     \label{fig:increase_N_P_fringe}
@@
 That is, the equilibrium number of entrants increases as a response to an increase in $N_P$ if the fringe firms are mostly complements, and decreases if they are mostly substitutes.
-The reason simply lies in the concave or hump-shaped fringe profit function.
+The underlyong reason is again the concave or hump-shaped fringe profit function.
 If $N_F^*$ is an equilibrium, then fringe profits minus entry costs are strictly positive for all $N_F \leq N_F^*$ and strictly negative for all $N_F > N_F^*$.
@@
 
-        \node[anchor=south] at (5,1) {$\pi_F(N_P, n_F)$};
-        \node[anchor=north] at (5,0.6) {$\pi_F(N_P', n_F)$};
+        \node[anchor=south] at (5,1) {$\pi_F(N_P, N_F, N_C)$};
+        \node[anchor=north] at (5,0.6) {$\pi_F(N_P', N_F, N_C)$};
         \node[anchor=south east] at (5,5/3) {$I_F n_F$};
@@
             [black] (i2-2) circle (1pt);
-        \draw[dashed] (i2-2) -- (i2-2 |- 0,0) node[below] {$N_F^{*'}$};
+        \draw[dashed] (i2-2) -- (i2-2 |- 0,0) node[below] {${N_F^*}'$};
 
@@
     \end{tikzpicture}
-    \caption{Illustration of comparative statics for equilibrium entry}
+    \caption{Illustration of comparative statics for equilibrium entry.
+If the change in $N_P$ decreases the fringe's profits for every $N_F \geq 0$, equilibrium can be restored by decreasing the number of fringe entrants, and vice versa for the other case.}
     \label{fig:comparative_N_F}
@@
     \end{align*}
+    Furthermore,
+    \begin{align*}
+        \frac{\partial \Pi(N_P, N_F^*(N_P), N_C)}{\partial N_P} < 0.
+    \end{align*}
 \end{proposition}
-As opposed to the previous results, this proposition tells us something about the total profits generated by the platform and the fringe firms as a function of the platform's product variety, and under equilibrium entry behavior by the fringe firms.
-In particular, it states that total profits increase if the total profit function is convex (products are substitutes), and decreases otherwise.
+
+The first part of this proposition is a stronger version of \cref{cor:fringe_entry}.
+It states that, not only does the equilibrium number of fringe firms decrease as a response to an increase in $N_P$, but it establishes a lower bound for this decrease.
+And, as the second part shows, this bound is sufficient to guarantee that the total size of the pie ($\Pi(N_P, N_F, N_C)$) also decreases in equilibrium.
+
 This result has particularly strong implications in models where total profits (or total product variety) has a monotone relationship with consumer welfare, such as those in \textcite{anderson2020aggregative}.
-\Cref{sec:example} also presents a model in which this is the case.
+\Cref{sec:example} also presents a demand system which satisfies this property.
 
@@
 The model in this section is heavily inspired by the logit-like demand structure and hybrid platform setting in \textcite{anderson2021hybrid}.
-The setting is a (possibly hybrid) platform market with monopolistically competing fringe firms.
+The setting can be thought of as a (possibly hybrid) platform market with monopolistically competing fringe firms.
 
@@
 \begin{lemma}
+    \label{lem:single_crossing_affine_transformation}
+    Let $g: \mathbb{R}^+ \to \mathbb{R}$ be a twice continuously differentiable function.
+    Define
+    \begin{align*}
+        G(x) = \int_0^x g(sx) \ds.
+    \end{align*}
+    Assume that for any $x \geq 0$, $G'(x) < 0$ or $G''(x) < 0$.
+
+    Let $h(x) = c g(a + bx)$ for some $a, c > 0$ and $b > 0$.
+    Then the function $H(x) = \int_0^1 h(sx) \ds$ satisfies the same conditions: for any $x \geq 0$, $h'(x) < 0$ or $h''(x) < 0$.
+\end{lemma}
+\begin{proof}[Proof of \cref{lem:single_crossing_affine_transformation}]
+    Differentiating $H$ yields
+    \begin{align*}
+        H'(x) &= \int_0^1 h'(sx) \ds \\
+              &= \int_0^1 c b g'(a + bsx) \ds \\
+              &= c b G'(a + bsx).
+    \end{align*}
+    Similarly, the second derivative is
+    \begin{align*}
+        H''(x) &= \int_0^1 h''(sx) \ds \\
+               &= \int_0^1 c b^2 g''(a + bsx) \ds \\
+               &= c b^2 G''(a + bsx).
+    \end{align*}
+    Now, for any $x \geq 0$, $y = a + bsx \geq 0$, therefore $G'(y) < 0$ or $G''(y) < 0$.
+    As $c, b > 0$, this implies that $H'(x) < 0$ or $H''(x) < 0$.
+\end{proof}
+
+\begin{lemma}
     \label{lem:slope_at_eq}
@@
     \begin{align*}
-        \frac{\partial N_F^*}{\partial N_P} < \frac{\alpha}{\beta}
+        \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}.
+    \end{align*}
+
+    To prove the second part of the proposition, differentiate total profits with respect to $N_P$:
+    \begin{align*}
+        \frac{\partial \Pi(N_P, N_F^*(N_P), N_C)}{\partial N_F} &= \frac{\partial}{\partial N_F} N_C g(\alpha N_P + \beta N_F^*(N_P)) \\
+        &= \underbrace{N_C g'(\alpha N_P + \beta N_F^*(N_P))}_{> 0} \left[ \alpha + \beta \frac{\partial N_F^*(N_P)}{\partial N_P} \right] \\
+        &< N_C g'(\alpha N_P + \beta N_F^*(N_P)) \left[ \alpha + \beta \left( -\frac{\alpha}{\beta} \right) \right] \\
+        &= 0.
     \end{align*}

### 2023-12-06 src/paper/application.tex
Expand intro of logit model

@@
 
-Let us now add more structure to the model, and microfound the profit function $\Pi$.
-The model in this section is heavily inspired by the logit-like demand structure and hybrid platform setting in \textcite{anderson2021hybrid}.
+Let us now add more structure to the model, place the function $\Pi$ on more solid microfoundations.
+The modeling strategy is heavily inspired by the logit-like demand structure and hybrid platform setting of \textcite{anderson2021hybrid}.
 The setting can be thought of as a (possibly hybrid) platform market with monopolistically competing fringe firms.
+
+In the main model, I consider the case when the total profit function only includes the sales of the platform's and fringe firms' products.
+That is, the platform does not charge any entry fees to the consumers.
+Here, I consider two variants of the model: a benchmark where the platform can unilaterally commit to any entry fee, and a bargaining model where the platform and the fringe firms negotiate over the distribution of profits.
+
+As an extension, I also examine what happens if the platform is able to extract consumer surplus by charging a flat entry fee, and the platform and the firms bargain over this larger sum.
+Furthermore, I also consider the case of two-sided bargaining, where the consumers also participate in the negotiation over the value produced.
+
+Throughout the analysis, I treat the product variety of the platform and the number of consumers as exogenous, and focus on the equilibrium number of fringe firms.
+Nevertheless, the results regarding equilibrium platform profits and consumer surplus are somewhat indicative of the potential general equilibrium behavior of the former two, as well.
 
@@
 Throughout this section I assume that the value of each product is the same: $v^F_i = v^F$.
-This is to simplify the analysis, but is not crucial for getting the results.  % TODO: look into relaxing this assumption
+This is to simplify the analysis, but is not crucial for the results.  % TODO: look into relaxing this assumption
 

### 2023-12-06 src/figures/equilibrium_symbolic.py
Add sympy-based plotting script

@@ -1,0 +1,115 @@
+import pandas as pd
+import numpy as np
+from scipy.optimize import fsolve
+from collections.abc import Iterable
+import typer
+from sympy import Symbol, integrate, simplify, log
+
+
+def create_plot_data(
+    out_path: str,
+    mu: float = 1,
+    V_P: float = 1,
+    V_F: float = 1,
+    I_F: float = 0.2,
+    N_P_range: tuple[float, float] = (0, 1),
+    num_obs: int = 500,
+    value_function: str = "profit",
+    bargaining: str = "one-sided",
+):
+    
+    N_P_sp, N_F_sp = Symbol("N_P"), Symbol("N_F")
+    s = Symbol("s")
+
+    f_profit = mu * (s * N_F_sp * V_F + N_P_sp * V_P) / (s * N_F_sp * V_F + N_P_sp * V_P + 1)
+    f_surplus = mu * log(s * N_F_sp * V_F + N_P_sp * V_P + 1)
+
+    if value_function == "profit":
+        f = f_profit
+    elif value_function == "welfare":
+        f = f_profit + f_surplus
+    else:
+        raise typer.BadParameter(f"Unknown value function: {value_function}")
+    
+    if bargaining == "onesided":
+        pi_P_symbolic = simplify(integrate(f, (s, 0, 1)))
+        pi_F_symbolic = simplify(integrate(s * f.diff(s), (s, 0, 1)))
+    elif bargaining == "twosided":
+        pi_P_symbolic = simplify(integrate(s * f, (s, 0, 1)))
+        pi_F_symbolic = simplify(integrate(s**2 * f.diff(s), (s, 0, 1)))
+    else:
+        raise typer.BadParameter(f"Unknown bargaining mode: {bargaining}")
+
+    def pi_P(N_P, N_F):
+        if not isinstance(N_P, Iterable):
+            N_P = [N_P]
+        return np.array(
+            [pi_P_symbolic.subs({N_P_sp: n_P, N_F_sp: n_F}) for n_P, n_F in zip(N_P, N_F)],
+            dtype=float
+        )
+
+    def pi_F(N_P, N_F):
+        if not isinstance(N_P, Iterable):
+            N_P = [N_P]
+        x = np.array(
[…]

### 2023-12-06 src/figures/equilibrium_symbolic.py
Speed up sympy-based plotting

@@ -3,7 +3,7 @@ import numpy as np
 from scipy.optimize import fsolve
 from collections.abc import Iterable
 import typer
-from sympy import Symbol, integrate, simplify, log
+from sympy import Symbol, integrate, simplify, log, lambdify
 
 
 def create_plot_data(
@@ -39,23 +39,9 @@ def create_plot_data(
         pi_F_symbolic = simplify(integrate(s**2 * f.diff(s), (s, 0, 1)))
     else:
         raise typer.BadParameter(f"Unknown bargaining mode: {bargaining}")
-
-    def pi_P(N_P, N_F):
-        if not isinstance(N_P, Iterable):
-            N_P = [N_P]
-        return np.array(
-            [pi_P_symbolic.subs({N_P_sp: n_P, N_F_sp: n_F}) for n_P, n_F in zip(N_P, N_F)],
-            dtype=float
-        )
-
-    def pi_F(N_P, N_F):
-        if not isinstance(N_P, Iterable):
-            N_P = [N_P]
-        x = np.array(
-            [pi_F_symbolic.subs({N_P_sp: n_P, N_F_sp: n_F}) for n_P, n_F in zip(N_P, N_F)],
-            dtype=float
-        )
-        return x
+    
+    pi_P = lambdify((N_P_sp, N_F_sp), pi_P_symbolic)
+    pi_F = lambdify((N_P_sp, N_F_sp), pi_F_symbolic)
 
     def pi_F_t(N_P, N_F):
         return pi_F(N_P, N_F) - I_F * N_F

### 2023-12-06 src/figures/equilibrium_symbolic.py
Parametrize plotting script further

@@ -12,6 +12,7 @@ def create_plot_data(
     V_P: float = 1,
     V_F: float = 1,
     I_F: float = 0.2,
+    N_C: float = 1,
     N_P_range: tuple[float, float] = (0, 1),
     num_obs: int = 500,
     value_function: str = "profit",
@@ -21,8 +22,8 @@ def create_plot_data(
     N_P_sp, N_F_sp = Symbol("N_P"), Symbol("N_F")
     s = Symbol("s")
 
-    f_profit = mu * (s * N_F_sp * V_F + N_P_sp * V_P) / (s * N_F_sp * V_F + N_P_sp * V_P + 1)
-    f_surplus = mu * log(s * N_F_sp * V_F + N_P_sp * V_P + 1)
+    f_profit = N_C * mu * (s * N_F_sp * V_F + N_P_sp * V_P) / (s * N_F_sp * V_F + N_P_sp * V_P + 1)
+    f_surplus = N_C * mu * log(s * N_F_sp * V_F + N_P_sp * V_P + 1)
 
     if value_function == "profit":
         f = f_profit

### 2023-12-06 src/paper/application.tex
Add sympy-based plotting script
Parametrize plotting script further
Finally add proof for lemma 1

@@
 \pgfplotstableread[col sep=comma]{out/figures/equilibrium.csv}\equilibrium
+% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_profit_onesided_scale-1.csv}\equilibriumProfitOneSided
+% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_onesided_scale-0.5.csv}\equilibriumFullSurplusOneSided
+% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_twosided_scale-1.csv}\equilibriumFullSurplusTwoSided
 
@@
 
-As in \cref{sec:model}, assume that the sellers and the consumers can only interact through an intermediary platform, denoted by $P$.
+The overall structure of the model comes from \cref{sec:model}: assume that the sellers and the consumers can only interact through an intermediary platform, denoted by $P$.
 Without the platform, the fringe firms are not able to sell their products, and thus make no profits.
@@
 }
+Later on, I look at the case of the platform obtaining consumer surplus, and also the case of consumers participating in the bargaining over the total surplus.
 
 As mentioned above, instead of operating as a pure marketplace, the platform may also produce and offer its own products.
-In case it does, it is called a hybrid platform.
+Therefore, there are three potential modes of operation.
+First, it can offer no product on its own ($N_P = 0$), and operate as a pure marketplace.
+Second, it can offer a selection of products alongside with a number of competing fringe firms also being present on the platform ($N_P, N_F > 0$).
+In this case, it is a hybrid platform.
+Finally, it can operate as a pure retailer, offering its own products, but no products from other sellers ($N_P > 0, N_F = 0$).
 
@@
 
-The structure of the game follows closely that of the more general model in \cref{sec:model}.
-In addition, a benchmark model without bargaining is presented, for comparison.
 There is an infinite measure of fringe firms, who are deciding whether to enter the market.
@@
 One can conceptualize the first as usual fixed costs, such as the cost of setting up production, or designing a product.
-Meanwhile, the second is a payment for using the platform's services.
-
-In the benchmark model, the game starts by the platform announcing its entry fee $F_F$.
+Meanwhile, the second is a payment to the platform for using its services.
+
+In the benchmark model, the game starts by the platform announcing and committing to an entry fee $F_F$.\footnote{
+    Without no commitment power, but the ability to set any prices after fringe firms make their investment decisions, the platform would charge an entry fee that would make the fringe profits zero \emph{sans the investment cost}.
+    This would lead to a trivial equilibrium, where no firm enters.
+}
 In the bargaining case, the platform cannot commit to entry fees, so this step is skipped.
 Next, each fringe firm decides whether to create a product at cost $I_F$ and enter the market.
-In the bargaining model, the entry fee is decided at this point, as a result of a negotiation between the platform and the firms that have made the investment.
+% In the bargaining model, the entry fee is decided at this point, as a result of a negotiation between the platform and the firms that have made the investment.
 After that, the firms that have made the investment decide if they also want to enter the platform for the announced fee $F_F$.\footnote{
@@
 
+In the baseline model, each player gets their profits from the sales of their products, plus the pre-agreed entry fees from the first period.
+In the model with bargaining, the platform and the fringe distribute total profits according to their Shapley values.
+One can also think of the latter as agreeing on an entry fee that makes final profits net entry fees equal to the Shapley value of the various players.
+
 The main difference between the benchmark and the bargaining model is in determining the entry fee $F_F$.
@@
 On the other hand, in the bargaining model, I assume that the entry fee is the result of a negotiation between the parties.
-In particular, I use the profit sharing rule from \cref{ass:profit_sharing} with $w(s) \equiv 1$.
 
@@
 \begin{proof}[Proof of \cref{lem:profit_assumptions}]
-
+    First, consider the function
+    \begin{align*}
+        g(x) = \frac{sx}{1 + sx}.
+    \end{align*}
+    Also, let us define
+    \begin{align*}
+        G(x) &= \int_0^1 s g(sx) \ds \\
+        &= \frac{\log(x+1)}{x} + \frac{1}{x(x+1)} - \frac{1}{x}.
+    \end{align*}
+
+    Differentiation with respect to $x$ yields that
+    \begin{align*}
+        G'(x) < 0 \iff \log(x+1) > \frac{x (2x+1)}{(x+1)^2}
+    \end{align*}
+    and
+    \begin{align*}
+        G''(x) < 0 \iff \log(x+1) < \frac{x (5x^2 + 5x + 2)}{2 (x+1)^3}.
+    \end{align*}
+    There exists $\bar{x} > 0$\footnote{
+        $\bar{x} = 3$ is such a number.
+    }, such that the first equality holds for all $x > \bar{x}$, and the second for all $x < \bar{x}$.
+    Therefore, $G$ is either concave or decreasing for all $x > 0$.
+
+    Now let us consider the function $h(x) = N_C \mu g(N_P V_P + V_F x)$.
+    By \cref{lem:single_crossing_affine_transformation}, $H(x) = \int_0^1 s h'(sx) \ds$ is also either concave or decreasing for any $x > 0$.
+    Finally, notice that $H(x)$ is exactly the profit function of the fringe:
+    \begin{align*}
+        \pi_F(N_P, N_F, N_C) = \int_0^1 N_F h'(s N_F) \ds,
+    \end{align*}
+    and thus the lemma is proven.
 \end{proof}

### 2023-12-13 src/paper/application.tex
Relax investment cost assumption (make it weakly convex)

@@
 Assume that there is an unlimited number of potential fringe entrants, indexed by $i \in \mathbb{R}^+_0$.
-In the first stage of the game, each fringe firm must create a viable product at an investment cost $I_F > 0$.
+In the first stage of the game, each fringe firm must create a viable product at some investment cost.
+Let us denote the total investment costs of $N_F$ fringe firms by $I_F(N_F)$.
+\begin{assumption}
+    Assume that $I_F(N_F)$ is a strictly increasing, convex, twice differentiable function:
+    \begin{align*}
+        \frac{\partial I_F(N_F)}{\partial N_F} > 0, \quad \frac{\partial^2 I_F(N_F)}{\partial N_F^2} \geq 0.
+    \end{align*}
+\end{assumption}
+This assumption essentially states that the marginal investment cost of the fringe is increasing in the number of fringe firms.
+Notice that this only assumes weak convexity, and thus includes the case of constant marginal investment costs.
+
 In the second stage, firms that made this investment plus the platform engage in producing and selling their respective products.
@@
         \item Profits are shared according to \cref{ass:profit_sharing} or \cref{ass:profit_sharing}.
-        \item Entrants make zero profits: $\pi_F(N_P, N_F) = I_F N_F$ after accounting for entry costs.
+        \item Entrants make zero profits: $\pi_F(N_P, N_F) = I_F(N_F)$ after accounting for entry costs.
     \end{itemize}
@@
         \node[anchor=north east] at (5,1) {$\pi_F(N_P, N_F, N_C)$};
-        \node[anchor=south east] at (5,5/3) {$I_F N_F$};
+        \node[anchor=south east] at (5,5/3) {$I_F(N_F)$};
 
@@
         \node[anchor=north] at (5,0.6) {$\pi_F(N_P', N_F, N_C)$};
-        \node[anchor=south east] at (5,5/3) {$I_F n_F$};
+        \node[anchor=south east] at (5,5/3) {$I_F(N_F)$};
 
@@
     \begin{align*}
-        \pi^t_F = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F N_F.
+        \pi^t_F = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F(N_F).
     \end{align*}
@@
     Let the conditions in \cref{ass:single_crossing} hold.
-Then for any $N_F^* > 0$ for which $\pi_F(N_P, N_F^*) = I_F$, the partial derivative with respect to the number of fringe firms is smaller than the investment cost:
-    \begin{align*}
-        \left. \frac{\partial \pi_F(N_P, N_F)}{\partial N_F} \right|_{N_F = N_F^*} < I_F.
+Then for any $N_F^* > 0$ for which $\pi_F(N_P, N_F^*, N_C) = I_F(N_F)$, the partial derivative of fringe profits with respect to the number of fringe firms is smaller than the marginal investment cost:
+    \begin{align*}
+        \left. \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_F} \right|_{N_F = N_F^*} < I_F'(N_F).
     \end{align*}
@@
 \begin{proof}[Proof of \cref{lem:slope_at_eq}]
-    \cref{ass:single_crossing} states that at any $N_F \geq 0$, $\pi_F(N_P, N_F)$ is either concave or decreasing.
-    In the remainder, for ease of notation drop $N_C$ from the arguments of $\pi_F$ profit function as it is simply a multiplicative constant, and let us denote partial derivatives as follows:
-    \begin{align*}
-        \partial_F \pi_F(N_P^*, N_F^*) \coloneqq \left. \frac{\partial \pi_F(N_P, N_F)}{\partial N_F} \right|_{N_P = N_P*, N_F = N_F^*}.
-    \end{align*}
-
-    Notice that the fact that $\pi_F$ is concave or decreasing in $N_F$ implies that if $\partial_F \pi_F(N_P, N_F')$ for some $N_F' \geq 0$, then $\partial_F \pi_F(N_P, N_F'') < \partial_F \pi_F(N_P, N_F')$ for any $\tilde{N_F} < \bar{N_F}$.
-
-    Next, observe that if $\partial_F \pi_F(N_P, 0) < I_F$, then there is no equilibrium with $N_F > 0$.
-    To show this, assume by contradiction that $\exists N_F^* > 0$ such that $\pi_F(N_P, N_F^*) = I_F N_F^*$.
-    Then the mean value theorem implies that there is a $\bar{N}_F \in (0, N_F^*)$ such that $\partial_F \pi_F(N_P, \bar{N}_F) = I_F$.
-    However, this clearly cannot be the case as $\partial_F \pi_F(N_P, N_F) < I_F$ for all $N_F > 0$.
-
-    Now let $N_F^*$ be a positive number for which $f(N_P, N_F^*) = I_F N_F^*$, if it exists.
-    It is easy to see that $\partial \pi(N_P, N_F^*) < I_F$.
-    The reason is that if it exists, then $\partial_F \pi_F(N_P, 0) > I_F$.
-    Now if $\partial_F \pi_F(N_P, N_F^*) \geq I_F \forall N_F > 0$, then $f(N_P, N_F) > I_F N_F$, and the two functions do not intersect.
-    Therefore, there must exist some $\bar{N}_F > 0$ for which $\partial_F \pi_F(N_P, \bar{N}_F) < I_F$.
-    This in turn implies that $\partial_F \pi_F(N_P, N_F) \leq \partial_F \pi_F(N_P, \bar{N}_F) < I_F$ for all $N_F > \bar{N}_F$.
+    \cref{ass:single_crossing} states that at any $N_F \geq 0$, $\pi_F(N_P, N_F, N_C)$ is either concave or decreasing in $N_F$.
+    In the remainder, let us denote partial derivatives as follows:
+    \begin{align*}
+        \partial_F \pi_F(N_P^*, N_F^*, N_C^*) \coloneqq \left. \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_F} \right|_{N_P = N_P*, N_F = N_F^*, N_C = N_C^*}.
+    \end{align*}
+
+    Notice that the fact that $\pi_F$ is concave or decreasing in $N_F$ implies that if $\partial_F \pi_F(N_P, N_F', N_C)$ for some $N_F' \geq 0$, then $\partial_F \pi_F(N_P, N_F'', N_C) < \partial_F \pi_F(N_P, N_F', N_C)$ for any $\tilde{N_F} < \bar{N_F}$.
+
+    Next, observe that if $\partial_F \pi_F(N_P, 0, N_C) < I_F'(0)$, then there is no equilibrium with $N_F > 0$.
+    To show this, assume by contradiction that $\exists N_F^* > 0$ such that $\pi_F(N_P, N_F^*, N_C) = I_F(N_F^*)$.
+    Then the mean value theorem implies that there is a $\bar{N}_F \in (0, N_F^*)$ such that $\partial_F \pi_F(N_P, \bar{N}_F, N_C) = I_F'(\bar{N_F}) \geq I_F'(0)$.
+    However, this clearly cannot be the case as $\partial_F \pi_F(N_P, N_F, N_C) < I_F'(0)$ or $\pi_F(N_P, N_F, N_C) \leq 0$ for all $N_F > 0$.
+
+    Now let $N_F^*$ be a positive number for which $f(N_P, N_F^*, N_C) = I_F(N_F^*)$.
+    It is easy to see that $\partial \pi(N_P, N_F^*, N_C) < I_F'(N_F^*)$.
+    The reason is that if it exists, then $\partial_F \pi_F(N_P, 0, N_C) > I_F'(0)$.
+    Now if $\partial_F \pi_F(N_P, N_F, N_C) \geq I_F'(N_F) \forall N_F > 0$, then $f(N_P, N_F, N_F) > I_F(N_F)$, and the two functions do not intersect.
+    Therefore, there must exist some $\bar{N}_F > 0$ for which $\partial_F \pi_F(N_P, \bar{N}_F, N_C) < I_F'(\bar{N}_F)$.
+    This in turn implies that $\partial_F \pi_F(N_P, N_F, N_C) \leq \partial_F \pi_F(N_P, \bar{N}_F, N_C) < I_F'(\bar{N}_F) \leq I_F'(N_F)$ for all $N_F > \bar{N}_F$.
 \end{proof}
@@
 \begin{proof}[Proof of \cref{prop:unique_equilibrium}]
-    \Cref{lem:slope_at_eq} states that for any positive $N_F^*$ for which $\pi_F(N_P, N_F^*)$, the partial derivative with respect to the number of fringe firms is negative.
+    \Cref{lem:slope_at_eq} states that for any positive $N_F^*$ for which $\pi_F(N_P, N_F^*) - N_F I_F$, the partial derivative with respect to the number of fringe firms is negative.
     Now assume by contradiction that $\exists 0 < N_F^* < N_F^{**}$ such that $\pi_F(N_P, N_F^*) = I_F N_F^*$ and $\pi_F(N_P, N_F^{**}) = I_F N_F^{**}$.
@@
     \begin{align*}
-        \frac{\partial N_F}{\partial N_P} = \frac{\frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P}}{I_F - \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F}}
+        \frac{\partial N_F}{\partial N_P} = \frac{\frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P}}{I_F'(N_F) - \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F}}
     \end{align*}
@@
     \begin{align*}
-        \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} < I_F,
+        \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} < I_F'(N_F),
     \end{align*}
@@
 \begin{proof}[Proof of \cref{prop:aggregate_size_additive}]
-    Assume by contradiction that $\frac{\partial N_F^*}{\partial N_P} \geq -\frac{\alpha}{\beta}$ for some $N_P'$.
-    Then, for $\forall K > 0$, $\exists \Delta \in (0, K)$ such that $N_F^*(N_P' + \Delta) \geq N_F^*(N_P') - \frac{\alpha}{\beta}\Delta$.
-For ease of notation, let us denote $N_P'' = N_P' + \Delta$, $N_F' = N_F^*(N_P')$ and $N_F'' = N_F^*(N_P'')$.
-
-    First, let us show that fringe profits are lower than total investment costs if $\bar N_F = N_F^*(N_P') - \frac{\alpha}{\beta}\Delta$.
-    In order to do this, consider the following formulation of the fringe profit function:
-    \begin{align*}
-        \pi_F(N_P', N_F', N_C) &= \int_0^1 w(t) \frac{\Pi(N_P, t N_F, N_C)}{\partial t} \dt \\
-        &= N_C \int_0^1 w(t) \underbrace{\frac{\partial}{\partial t}g(\alpha N_P + \beta t N_F)}_{\coloneq D(N_P, N_F)} \dt,
-    \end{align*}
-    where $w(t) = t$ or $w(t) = t^2$ in the one-sided and two-sided bargaining cases, respectively.
-
-    Let us focus on the term $D(N_P, N_F)$.
-    First, calculate
-    \begin{align*}
-        D(N_P', N_F') = \beta N_F' g'(\alpha N_P' + \beta t N_F').
-    \end{align*}
-    Let us do the same for $D(N_P'', \bar{N}_F) = D(N_P' + \Delta, N_F - \frac{\alpha}{\beta} \Delta)$ to get
-    \begin{align*}
-        D(N_P'', \bar{N}_F) = \beta \bar{N}_F g'(\alpha N_P' + \beta t N_F' + \underbrace{\Delta \alpha (1-t)}_{> 0}).
-    \end{align*}
-    Substitute these expressions into $\pi_F$ to get
-    \begin{align*}
-        \pi_F(N_P', N_F', N_C) &= N_C N_F' \beta \int_0^1 w(t) g'(\alpha N_P' + \beta t N_F') \dt, \\
-        \pi_F(N_P'', \bar{N}_F, N_C) &= N_C \bar{N}_F \beta \int_0^1 w(t) g'(\alpha N_P' + \beta t N_F' + \Delta \alpha (1-t)) \dt.
-    \end{align*}
-    Finally, let us bound the difference between $\pi_F(N''_Pm \bar{N}_F) - I_F \bar{N}_F$ from above:
-    \begin{align*}
-        \pi_F(N_P'', \bar{N}_F, N_C) - I_F \bar{N}_F &= \frac{\bar{N}_F}{N_F'}\left[\beta N_C \int_0^1 w(t) g'(\alpha N_P' + \beta t N_F' + \Delta \alpha (1-t)) \dt - I_F N_F' \right] \\
-        &< \frac{\bar{N}_F}{N_F'}\left[\beta N_C \int_0^1 w(t) g'(\alpha N_P' + \beta t N_F') \dt - I_F N_F' \right] \\
-        &= \frac{\bar{N}_F}{N_F'}\left[ \pi_F(N_P', N_F', N_C) - I_F N_F \right] \\
-        &= 0.
-    \end{align*}
-    The inequality is due to the concavity of $g$, and the final equality is the result of profits being zero in the equilibrium $(N_P', N_F', N_C)$.
-
-    All that remains to be shown is that $\pi_F(N_P'', N_F'', N_C) < N_F'' I_F$.
-    This is a consequence of the fact that, under \cref{ass:single_crossing}, $\pi_F$ is either concave or decreasing in $N_F$.
-    Therefore, if it at some point ($\bar{N}_F$) dips below the linear function $N_F \mapsto I_F N_F$, it can never reach it again for any $N_F'' > \bar{N}_F$.
-    With this we arrive at a contradiction, as $(N_P'', N_F'', N_C)$ cannot be an equilibrium.
-
-    Therefore, the initial assumption that $\frac{\partial N_F^*}{\partial N_P} \geq -\frac{\alpha}{\beta}$ was wrong.
-    As we have from \cref{cor:fringe_entry} that $\frac{\partial N_F^*}{\partial N_P}$ exists, it must be the case that
-    \begin{align*}
-        \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}.
-    \end{align*}
+    Use the implicit function theorem to get the equilibrium number of fringe firms as a function of the platform's product variety:
+    \begin{align*}
+        \frac{\partial N_F}{\partial N_P} = \frac{\frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P}}{I_F'(N_F) - \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F}}.
+    \end{align*}
+    Remember, that from \cref{lem:slope_at_eq}, and the assumption on the investment cost function we have that $\frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} < I_F'(N_F)$.
+    Then, substitute $f(N_P, N_F) = g(\alpha N_P + \beta N_P)$ into $\pi_F$ to get the following fringe profit function:
+    \begin{align*}
+        \pi_F(N_P, N_F, N_C) = \beta N_C N_F \int_0^1 w_s s g'(\alpha N_P + s \beta N_F) \ds.
+    \end{align*}
+    Differentiate it with respect to $N_P$ and $N_F$ and substitute into the first expression to obtain
+    \begin{align*}
+        \frac{\partial N_F}{\partial N_P} = \frac{
+            \alpha \beta N_C N_P \int_0^1 w(s) g''(\alpha N_P + s \beta N_F) \ds
+        }{
+            \underbracket{I'_F(N_F) - \beta N_C \int_0^1 w(s) g'(\alpha N_P + s \beta N_F) \ds}_{(1)} - \underbracket{\beta^2 N_C N_F \int_0^1 w(s) s g''(\alpha N_P + s \beta N_F) \ds}_{(2)}.
+        }
+    \end{align*}
+    From \cref{lem:slope_at_eq}, we know that the denominator of this expression is positive.
+    Furthermore, the concavity of $g$ implies that expression (2) is also positive.
+    Finally, from \cref{prop:share_of_fringe}, we have that the whole expression must be negative.
+
+    First, let us show that (1) is non-negative, and, coupled with the fact that (2) is positive, omitting it increases the denominator in absolute value, thus making the whole expression larger.
+    To see this, observe that the second part of (1) is just the per-unit fringe profit, i.e.
+    \begin{align*}
+        (1) = I_F'(N_F) - \pi_F(N_P, N_F, N_C) / N_F \geq 0 \Leftrightarrow N_F I_F'(N_F) - \pi_F(N_P, N_F, N_C) \leq 0.
+    \end{align*}
+    Next, use the convexity of $I_F$ and the definition of the equilibrium to obtain
+    \begin{align*}
+        N_F I_F'(N_F) - \pi_F(N_P, N_F, N_C) \leq I_F(N_F) - \pi_F(N_P, N_F, N_C) = 0,
+    \end{align*}
+    thus proving that (1) is non-negative.
+
+    Next, observe that we can bound (2) from above using the fact that $s \in [0, 1]$:
+    \begin{align*}
+        (2) \leq \beta^2 N_C N_F \int_0^1 w(s) g''(\alpha N_P + s \beta N_F) \ds.
+    \end{align*}
+    For the same reason as before, it also bounds the whole expression from above.
+
+    Putting it all together, we have that
+    \begin{align*}
+        \frac{\partial N_F}{\partial N_P} \leq \frac{\alpha \beta N_C N_P \int_0^1 w(s) g''(\alpha N_P + s \beta N_F) \ds}{\beta^2 N_C N_F \int_0^1 w(s) g''(\alpha N_P + s \beta N_F) \ds} = -\frac{\alpha}{\beta},
+    \end{align*}
+    which is the first statement of the proposition.
 

### 2023-12-13 src/paper/application.tex
Add bargaining over total surplus extension

@@
 \begin{abstract}
-    This paper studies the effects of a platform selling their own products in addition to acting as intermediaries (hybrid platforms) in a setting when bargaining takes place between the platform and the potential entrants.
-    It highlights a so-far underexplored aspect of hybrid platforms: having their own products increases their bargaining power over the other sellers.
-    As shown through a more concrete example, this change in bargaining power can have negative welfare consequences for the consumers.
+    This paper explores the effects of a platform selling their own products in addition to acting as intermediaries (hybrid platforms) in a setting when bargaining takes place between the platform and the potential entrants.
+    It highlights a so-far underappreciated aspect of hybrid platforms: having their own products increases their bargaining power over the other sellers.
+    This change in bargaining might lead to lower entry, and thus reduced product variety which in turn can have negative welfare consequences for the consumers.
     The results and methods described in this paper are also applicable to other similar settings, such as vertical integration with a monopolistic upstream supplier.
@@
 I use the terms ``platform'' and ``fringe sellers'', and present my ideas in the context of an intermediated market, such as an online marketplace or an application store.
-However, the model is more general, and the results apply to a broader class of settings.
-An important example of those is an upstream-downstream setting with a single upstream producer and a continuum of downstream sellers.
-
-Assume that there are two types of players in the market: a platform $P$ and a continuum of fringe sellers $F_i$.
-The fringe firms each have one product, which they can only sell through the platform.
-The platform itself may also have its own products in addition to acting as an intermediary between the fringe and the consumers.
-In that case it is referred to as a hybrid platform.
-The main feature of the model is that, instead of assuming that entry fees or royalties are set by the platform and the fringe treat it as take it or leave it offers, I assume that the platform and the fringe engage in some kind of bargaining over their total profits.
+However, the model is quite general, and the results apply to a broader class of settings, such as vertical markets where the upstream firm can sell directly to consumers, or retail stores with their own private labels.
+
+Assume that there are three types of players in the market: a platform $P$, a continuum of fringe sellers $F_i$ ($i \in [0, N_C$) and a continuum of consumers $C_j$ ($j \in [0, N_C$]).
+The fringe firms have one product each, which they can only sell through the platform.
+Without the platform, they make zero profits.
+In addition to acting as an intermediary between the fringe and the consumers, the platform itself may also produce and sell a number of products directly to the consumers.
+If it does, it is referred to as a hybrid platform.
+
+The main distinguishing feature of this model is that, instead of assuming that entry fees or royalties are set by the platform and the fringe treat it as take it or leave it offers, I assume that the platform and the fringe engage in some kind of bargaining over their total profits.
 The bargaining rule, as well as other details of the model, are described in the rest of this section.
@@
 First, I assume that all fringe firms and consumers are ex-ante identical.
-This implies that the total profits of the platform and the fringe taken together have a simple functional form $n_C f(n_P, n_F)$.
+This implies two things: (1) per-consumer profits are just a function of the number of fringe and platform products, and (2) the platform's and the fringe's profits are linear in the number of consumers.\footnote{
+    While normally this would exclude fixed production costs, this is not the case here.
+    $\Pi$ only describes profits conditional on $N_C$ and $N_F$ players entering the platform.
+    Fixed costs can be incorporated into the first stage of the game, where fringe firms decide whether to enter or not.
+}
+Therefore, the total profits of the platform and the fringe taken together have a simple functional form $N_C f(N_P, N_F)$.\footnote{
+    Based on the same reasoning, it is easy to see that total welfare has a similar form.
+}
+Formally, this is described by the following assumption.
 \begin{assumption}
@@
     \begin{align*}
-        \Pi(n_P, n_F, n_C) = n_C f(n_P, n_F),
+        \Pi(N_P, N_F, N_C) = N_C f(N_P, N_F),
     \end{align*}
@@
 \end{assumption}
-Here, $n_F$ is the mass of fringe sellers, $n_C$ is the mass of consumers, and $n_P$ measures the degree to which the platform sells its own products.
-For example, in a setting with differentiated products and monopolistic competition, $n_F$ and $n_P$ represents the product variety of the fringe and the platform, respectively.
-In case the platform operates as a pure intermediary, $n_P = 0$.
-This formulation also assumes that total profits are linear in the number of consumers.\footnote{
-    While normally this would exclude fixed production costs, this is not the case here.
-    $\Pi$ only describes profits conditional on $N_C$ and $N_F$ players entering the platform.
-    Fixed costs can be incorporated into the first stage of the game, where fringe firms decide whether to enter or not.
-}
+Here, $N_F$ is the mass of fringe sellers, $N_C$ is the mass of consumers, and $N_P$ measures the degree to which the platform sells its own products.
+For example, in a setting with differentiated products and monopolistic competition, $N_F$ and $N_P$ represent the product variety of the fringe and the platform, respectively.
+$N_P = 0$ corresponds to the case when the platform is a pure intermediary, and $N_F = 0$ to the case then the platform is a pure retailer.
 
@@
 \end{assumption}
-Such profit functions arise in a variety of settings in which the profit reduction from increased competition is dominated by extra sales due to increased product variety.
+Such profit functions arise in settings in which the profit reduction from increased competition is dominated by extra sales due to increased product variety.
 One such example is \textcite{anderson2020aggregative}, where the demand exhibits love for variety, while consumers have access to an outside option.
-Alternatively, indirect network effects, such as in two-sided markets, can also result in such increasing profits.
+Alternatively, indirect network effects, such as those in two-sided markets, can also result in such increasing profits.
+Finally, if we assume that the platform can extract consumer surplus through entry fees or some similar mechanism, then this assumption will be true for any demand system in which total surplus is increasing in product variety.
 
@@
 
-Let us assume that the fringe firms are unable to sell their products directly to consumers.
+I assume that fringe firms are unable to sell their products directly to consumers.
 Instead, they must sell through the platform.
@@
 In the benchmark model, the platform will be able to set and commit to any lump-sum entry fee it wishes to.\footnote{
-    The focus is on fees and entry of fringe producers, but I will also consider the case when the platform can set an entry fee for consumers, as well.
-}
-The main contribution of this paper is to deviate this usual assumption, and instead consider a setting in which the platform and the fringe engage in some form of bargaining over the entry fee.
-To model this bargaining in a theoretically sound, but still tractable way, I will borrow a solution concept from cooperative game theory.
-Similarly to a number of other papers in the industrial organization literature \parencite[e.g.][]{montez2007downstream,hart1990property,levy1997individual,inderst2003bargaining,brugemann2019intra}, I will assume that the resulting allocation for each player is given by their Shapley value.
+    The focus of this paper is on fees paid and entry decisions made by fringe producers, but I will also consider the case when consumers might also face entry fees or subsidies.
+}
+The main contribution of this paper is to deviate from this usual assumption, and instead consider a setting in which the platform and the fringe engage in some form of bargaining over the total profits.
+To model this in a theoretically sound, but still tractable way, I borrow a solution concept from cooperative game theory.
+Similarly to a number of other papers in the industrial organization literature \parencite[e.g.][]{montez2007downstream,hart1990property,levy1997individual,inderst2003bargaining,brugemann2019intra}, I assume that the resulting allocation for each player is given by their Shapley value.
 This value (and the game itself) depends on who is assumed to participate in the bargaining process.
@@
     \begin{itemize}
-        \item Profits are shared according to \cref{ass:profit_sharing} or \cref{ass:profit_sharing}.
-        \item Entrants make zero profits: $\pi_F(N_P, N_F) = I_F(N_F)$ after accounting for entry costs.
+        \item Profits are shared according to \cref{ass:profit_sharing} (one-sided bargaining) or \cref{ass:profit_sharing_two_sided} (two-sided bargaining).
+        \item Entrants make zero profits after accounting for entry costs: $\pi_F(N_P, N_F) = I_F(N_F)$.
     \end{itemize}
@@
 It turns out that even within such a general setting, one can derive some interesting and non-trivial results.
-\Cref{sec:example} will then build on these results to derive stronger results in a more fully specific model.
-
-Let us start by a technical, but highly useful result.
+\Cref{sec:example} then builds on these results to derive stronger ones under a specific demand system.
+
+Let us start with a technical, but very useful result.
 \begin{proposition}
@@
 The intuition behind this result is that \cref{ass:single_crossing} ensures that the total profits achieved by the fringe is either concave or hump-shaped.
-Consequently, it has at most one crossing with the linear total entry cost (for $n_F > 0$).
+Consequently, it has at most one crossing with the -- convex and increasing -- total entry cost function (for $n_F > 0$).
 An example for this is shown in \cref{fig:equilibrium}.
-This particular shape is also the main driver for the following results about the comparative statics of equilibrium profits and entry.
+This particular shape (concave or hump-shaped) is also the main driver for the later results about the comparative statics of equilibrium profits and entry.
 
@@
     \end{align*}
-    The total profits of the whole fringe is given by
+    The total profits of the whole fringe are given by
     \begin{align*}
@@
 
+\section{Extensions}
+\label{sec:extensions}
+
+In this section, I look at a number of extensions of the model presented in \cref{sec:example}.
+The common theme of these extensions is that the consumer surplus is also included in the sum that is bargained over.
+That is, $\Pi(N_P, N_F, N_C)$ now represents total surplus.
+
+First, \cref{sec:total_welfare} looks at the case when consumer can be extracted by the platform, but consumers are still passive, and the bargaining is between the platform and the fringe.
+Then, \cref{sec:two_sided} explores what happens when all three sides engage in the negotiation over the same total surplus.
+I will only consider the bargaining outcomes under assumptions \cref{ass:profit_sharing} and \cref{ass:profit_sharing_two_sided}, respectively, and do not look at a benchmark with unilateraly set entry fees for the fringe.
+
+\subsection{Platform can extract consumer surplus}
+\label{sec:total_welfare}
+
+In this section, I assume that the platform can extract consumer surplus by charging a flat entry fee $F_C$.
+As consumers are identical, and the platform can set any entry fee, this implies that the platform can extract all consumer surplus in this case.\footnote{
+    Note, that I still assume that all $N_C$ consumers are present on the market by default, they do not have to pay any cost that would be analogous to the entry fee ($I_F$) of the fringe firms.
+    Therefore, they enter the market if and only if they are expected to have non-negative utility, which in turn means that the platform sets the entry fee to be equal to the consumer surplus.
+}
+
+Let us start by deriving total profits (which, in this case is the total surplus) as a function of $N_P, N_F$ and $N_C$.
+Under the logit-like demand structure described in \cref{sec:example}, the total surplus is given by
+\begin{proposition}
+    \label{prop:profits_total_surplus}
+    If the platform can extract consumer surplus, then the total profits that the platform and the fringe firms can achieve are given by
+    \begin{align*}
+        \Pi(N_P, N_F, N_C) = \mu N_C \left[ \frac{N_P V_P + N_F V_F}{N_P V_P + N_F V_F + 1} + \log(N_P V_P + N_F V_F + 1) \right].
+    \end{align*}
+\end{proposition}
+\begin{proof}[Proof of \cref{prop:profits_total_surplus}]
+    \textcite{small1981applied} show that the total surplus in a logit demand system is given by this expression.
+    As total consumer surplus is zero, the total profits are equal to the total surplus.
+\end{proof}
+Note, that this expression is of the form $\Pi(N_C, N_P, N_F) = N_C f(N_P, N_F)$.
+Furthermore, $f(N_P, N_F) = g(V_P N_P + V_F N_F)$ for an increasing, strictly concave $g$.
+
+Therefore, if we show that \cref{ass:single_crossing} holds, it in turn implies that all of the results in \cref{sec:results} apply here, as well.
+The following lemma establishes this result.
+\begin{lemma}
+    \label{lem:profit_assumptions_total_surplus}
+    $f(n_P, n_F)$ satisfies \cref{ass:single_crossing}.
+    Furthermore,
+    \begin{align*}
+        \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} < 0.
+    \end{align*}
+\end{lemma}
+
+With this proven, we can rely on \cref{prop:aggregate_size_additive} to see that, in equilibrium, an increase in $N_P$ decreases $N_F$.
+Furthermore, this decrease is so large that total product variety, and thus total surplus (which in turn is equal to total profits) also decreases.\footnote{
+    As long as the market is in the hybrid regime.
+    If $N_F^* = 0$, then an increase in $N_P$ mechanically increases total aggregate, and thus total surplus.
+}
+Thus, as in the case without consumer entry fees, a platform becoming increasingly hybrid has generally negative consequences.
+
+The difference is that, due to the platform appropriating all the consumer surplus, it does not hurt consumer welfare -- it is zero regardless of $N_P$.
+Coupled with the fact that fringe firms also make zero profits in equilibrium, this means that the outcome is not so negative, after all.
+In particular, the platform's profits are increasing in $N_P$, and thus it prefers to operate in hybrid mode, as long as it is feasible.
+So even though the total pie gets smaller, the platform gets a larger slice, while the consumers and the fringe are just as well off.
+
+\subsection{Consumers also engage in bargaining}
+\label{sec:two_sided}
+
 \section{Shapley value in the platform game}
@@
 
+\begin{proof}[Proof of \cref{lem:profit_assumptions_total_surplus}]
+    To show this, I go through the same steps as in the proof of \cref{lem:profit_assumptions}.
+    Consider the function
+    \begin{align*}
+        g(x) = \frac{sx}{1 + sx} + \log(1 + sx).
+    \end{align*}
+    Also, let us define
+    \begin{align*}
+        G(x) &= \int_0^1 s g(sx) \ds \\
+        &= \frac{1}{x + 1}.
+    \end{align*}
+    Clearly, $G$ is a strictly concave function of $x$.
+
+    Now let us consider $h(x) = N_C \mu g(N_P V_P + V_F x).$
+    By \cref{lem:single_crossing_affine_transformation}, $H(x) = \int_0^1 s h'(sx) \ds$ is also strictly concave in $x$.\footnote{
+        Technically, the lemma establishes concavity \emph{or} being monotone decreasing.
+        It does not matter for this application, but it is easy to see that $H$ is indeed strictly concave.
+    }
+    Finally, notice that $H(x)$ is exactly the profit function of the fringe:
+    \begin{align*}
+        \pi_F(N_P, N_F, N_C) = \int_0^1 N_F h'(s N_F) \ds,
+    \end{align*}
+    and thus the lemma is proven.
+\end{proof}
+
 \end{document}

### 2023-12-16 src/paper/application.tex
Switch to numeric integration

@@
 \pgfplotstableread[col sep=comma]{out/figures/equilibrium.csv}\equilibrium
-% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_profit_onesided_scale-1.csv}\equilibriumProfitOneSided
-% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_onesided_scale-0.5.csv}\equilibriumFullSurplusOneSided
-% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_twosided_scale-1.csv}\equilibriumFullSurplusTwoSided
+% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_profit_onesided_scale-1_lambda-0.3.csv}\equilibriumFullSurplusOneSided
+% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_onesided_scale-0.5_lambda-1.csv}\equilibriumFullSurplusOneSided
+% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_twosided_scale-1_lambda-1.csv}\equilibriumFullSurplusTwoSided
 
@@
 
+The catch is that, in this comparative statics exercise, the platforms' increased product variety came out of thin air.
+Specifically, when looking at the platform's profits, this increase in product variety is not associated with any increase in investment costs.
+If we were to include those at the same level of the fringe's investment costs, then the platform's profits would be decreasing in $N_P$, and it would not make the investment.
+Nevertheless, if it were to make it for some reason, it would not have the negative consequences that it had in \cref{sec:example}.
+
 \subsection{Consumers also engage in bargaining}

### 2023-12-16 src/figures/equilibrium_symbolic.py

@@ -1,5 +1,6 @@
 import pandas as pd
 import numpy as np
+from scipy.integrate import quad
 from scipy.optimize import fsolve
 from collections.abc import Iterable
 import typer
@@ -15,6 +16,7 @@ def create_plot_data(
     N_C: float = 1,
     N_P_range: tuple[float, float] = (0, 1),
     num_obs: int = 500,
+    lambda_P: float = 1,
     value_function: str = "profit",
     bargaining: str = "one-sided",
 ):
@@ -32,17 +34,20 @@ def create_plot_data(
     else:
         raise typer.BadParameter(f"Unknown value function: {value_function}")
     
+    f_num = lambdify((N_P_sp, N_F_sp, s), f)
+    f_diff_num = lambdify((N_P_sp, N_F_sp, s), f.diff(s))
+
     if bargaining == "onesided":
-        pi_P_symbolic = simplify(integrate(f, (s, 0, 1)))
-        pi_F_symbolic = simplify(integrate(s * f.diff(s), (s, 0, 1)))
+        pi_P_scalar = lambda N_P, N_F: quad(lambda s: f_num(N_P, N_F, s) * lambda_P * s  ** (lambda_P - 1), 0, 1)[0]
+        pi_F_scalar = lambda N_P, N_F: quad(lambda s: f_diff_num(N_P, N_F, s) * s ** lambda_P, 0, 1)[0]
     elif bargaining == "twosided":
-        pi_P_symbolic = simplify(integrate(s * f, (s, 0, 1)))
-        pi_F_symbolic = simplify(integrate(s**2 * f.diff(s), (s, 0, 1)))
+        pi_P_scalar = lambda N_P, N_F: quad(lambda s: f_num(N_P, N_F, s) * lambda_P * s ** lambda_P, 0, 1)[0]
+        pi_F_scalar = lambda N_P, N_F: quad(lambda s: f_diff_num(N_P, N_F, s) * s ** (lambda_P + 1), 0, 1)[0]
     else:
         raise typer.BadParameter(f"Unknown bargaining mode: {bargaining}")
     
-    pi_P = lambdify((N_P_sp, N_F_sp), pi_P_symbolic)
-    pi_F = lambdify((N_P_sp, N_F_sp), pi_F_symbolic)
+    pi_P = np.vectorize(pi_P_scalar)
+    pi_F = np.vectorize(pi_F_scalar)
 
     def pi_F_t(N_P, N_F):
         return pi_F(N_P, N_F) - I_F * N_F

### 2023-12-16 src/paper/application.tex
Add figure for extension - total welfare

@@
 \pgfplotstableread[col sep=comma]{out/figures/equilibrium.csv}\equilibrium
-% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_profit_onesided_scale-1_lambda-0.3.csv}\equilibriumFullSurplusOneSided
-% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_onesided_scale-0.5_lambda-1.csv}\equilibriumFullSurplusOneSided
+% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_profit_onesided_scale-1_lambda-1.csv}\equilibriumProfitOneSided
+\pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_onesided_scale-0.6_lambda-1.csv}\equilibriumFullSurplusOneSided
 % \pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_twosided_scale-1_lambda-1.csv}\equilibriumFullSurplusTwoSided
+% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_twosided_scale-1_lambda-0.5.csv}\equilibriumProfitOneSidedLowLambda
 
@@
 }
+\Cref{fig:equilibrium_full_surplus_one_sided} displays equilibrium outcomes for an example parametrization
 Thus, as in the case without consumer entry fees, a platform becoming increasingly hybrid has generally negative consequences.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                    ylabel={},
+                    xmin=0, xmax=1.5, % adjust these values as needed
+                    ymin=0, ymax=3.1, % adjust these values as needed
+                    axis lines=left,
+                    xtick=\empty, ytick=\empty,
+                    legend pos=south east,
+                    width=\textwidth,
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=N_P]{\equilibriumFullSurplusOneSided};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y=N_F]{\equilibriumFullSurplusOneSided};
+                \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=A]{\equilibriumFullSurplusOneSided};
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumFullSurplusOneSided};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+
+                \legend{$N_P$, $N_F$, $A$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Platform product variety and number of fringe entrants}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                    ylabel={},
+                    xmin=0, xmax=1.5, % adjust these values as needed
+                    ymin=0, ymax=1.2, % adjust these values as needed
+                    axis lines=left,
+                    xtick=\empty, ytick=\empty,
+                    legend pos=north west,
+                    width=\textwidth,
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=pi_P]{\equilibriumFullSurplusOneSided};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y=pi_F]{\equilibriumFullSurplusOneSided};
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumFullSurplusOneSided};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+
+                \legend{$\pi_P(N_P)$, $\pi_F(N_P)$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Platform and fringe profits}
+    \end{subfigure}
+    \caption{Equilibrium outcomes in the case when the whole surplus is bargained over ($N_C = 0.6, V_P = 1, V_F = 1, I_F = 0.2$).
+As in the case of bargaining over profits, the platform's profits are increasing in $N_P$, while the fringe's profits are decreasing.
+Consumer surplus does not matter in this case, as it is extracted by the platform.
+The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode.}
+    \label{fig:equilibrium_full_surplus_one_sided}
+\end{figure}
 

### 2023-12-16 src/figures/equilibrium_symbolic.py

@@ -81,6 +81,13 @@ def create_plot_data(
         np.nan
     )
 
+    hybrid_mode = np.where(
+        N_F_vec > 1e-5,
+        100,
+        0
+    )
+       
+
 
     data = pd.DataFrame(
         {
@@ -97,6 +104,7 @@ def create_plot_data(
             "CS_noF": CS_noF,
             "pi_P_noF": pi_P_noF,
             "F_F_implied": F_F_implied,
+            "hybrid": hybrid_mode,
         }
     )
 

### 2023-12-17 src/paper/application.tex
Add graphs for extensions

@@
 \definecolor{myred}{rgb}{0.87, 0.52, 0.32}
+\definecolor{mygreen}{rgb}{0.34, 0.68, 0.45}
 
@@
 \pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_onesided_scale-0.6_lambda-1.csv}\equilibriumFullSurplusOneSided
-% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_twosided_scale-1_lambda-1.csv}\equilibriumFullSurplusTwoSided
-% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_twosided_scale-1_lambda-0.5.csv}\equilibriumProfitOneSidedLowLambda
+\pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_twosided_scale-0.6_lambda-1.csv}\equilibriumFullSurplusTwoSided
+\pgfplotstableread[col sep=comma]{out/figures/equilibrium_profit_onesided_scale-1_lambda-0.5.csv}\equilibriumProfitOneSidedLowLambda
 
@@
                     axis lines=left,
-                    xtick=\empty, ytick=\empty,
+                    xtick={0, 1.5},
                     legend pos=south east,
@@
                 \addplot[color=myred,mark=none,thick] table[x=N_P,y=N_F]{\equilibriumFullSurplusOneSided};
-                \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=A]{\equilibriumFullSurplusOneSided};
+                \addplot[color=black,mark=none,thick] table[x=N_P,y=A]{\equilibriumFullSurplusOneSided};
 
@@
                     axis lines=left,
-                    xtick=\empty, ytick=\empty,
+                    xtick={0, 1.5},
                     legend pos=north west,
@@
 
-                \legend{$\pi_P(N_P)$, $\pi_F(N_P)$}
+                \legend{$\pi_P$, $\pi_F$}
             \end{axis}
@@
 
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                    ylabel={},
+                    xmin=0, xmax=1.5, % adjust these values as needed
+                    ymin=0, ymax=3.1, % adjust these values as needed
+                    axis lines=left,
+                    xtick={0, 1.5},
+                    legend pos=south east,
+                    width=\textwidth,
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=N_P]{\equilibriumFullSurplusTwoSided};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y=N_F]{\equilibriumFullSurplusTwoSided};
+                \addplot[color=black,mark=none,thick] table[x=N_P,y=A]{\equilibriumFullSurplusTwoSided};
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumFullSurplusTwoSided};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+
+                \legend{$N_P$, $N_F$, $A$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Platform product variety and number of fringe entrants}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                    ylabel={},
+                    xmin=0, xmax=1.5, % adjust these values as needed
+                    ymin=0, ymax=1.2, % adjust these values as needed
+                    axis lines=left,
+                    xtick={0, 1.5},
+                    legend pos=north west,
+                    width=\textwidth,
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=pi_P]{\equilibriumFullSurplusTwoSided};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y=pi_F]{\equilibriumFullSurplusTwoSided};
+                \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=pi_P]{\equilibriumFullSurplusTwoSided};
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumFullSurplusTwoSided};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+
+                \legend{$\pi_P$, $\pi_F$, $CS$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Platform and fringe profits}
+    \end{subfigure}
+    \caption{Equilibrium outcomes in the case when the whole surplus is bargained over ($N_C = 0.6, V_P = 1, V_F = 1, I_F = 0.2$), and both consumers and fringe firms participate in the bargaining.
+As before, the platform's profits are increasing in $N_P$, while the fringe's profits are decreasing.
+On the other hand, consumer welfare is equal to platform profits, therefore it is increasing in $N_P$.
+The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode.}
+    \label{fig:equilibrium_full_surplus_two_sided}
+\end{figure}
+
+\subsection{Platform has lower innate bargaining power}
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                    ylabel={},
+                    xmin=0, xmax=1.5, % adjust these values as needed
+                    ymin=0, ymax=3.1, % adjust these values as needed
+                    axis lines=left,
+                    xtick={0, 1.5},
+                    legend pos=south east,
+                    width=\textwidth,
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=N_P]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y=N_F]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[color=black,mark=none,thick] table[x=N_P,y=A]{\equilibriumProfitOneSidedLowLambda};
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+
+                \legend{$N_P$, $N_F$, $A$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Platform product variety and number of fringe entrants}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                    ylabel={},
+                    xmin=0, xmax=1.5, % adjust these values as needed
+                    ymin=0, ymax=1.2, % adjust these values as needed
+                    axis lines=left,
+                    xtick={0, 1.5},
+                    legend pos=north west,
+                    width=\textwidth,
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=pi_P]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y=pi_F]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[color=black,mark=none,thick] table[x=N_P,y=CS]{\equilibriumProfitOneSidedLowLambda};
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+
+                \legend{$\pi_P$, $\pi_F$, $CS$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Platform and fringe profits}
+    \end{subfigure}
+    \caption{Equilibrium outcomes in the case when the platform has lower innate bargaining power ($N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$).
+As in every other case, the platform's profits are increasing in $N_P$, while the fringe's profits are decreasing.
+Furthermore, consumer surplus is also decreasing as a result in a decrease in total product variety.
+The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode.}
+    \label{fig:equilibrium_low_lambda}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                    ylabel={},
+                    xmin=0, xmax=1.5, % adjust these values as needed
+                    ymin=0, ymax=0.4, % adjust these values as needed
+                    axis lines=left,
+                    xtick={0, 1.5},
+                    legend pos=south east,
+                    width=\textwidth,
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=F_F_implied]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=F_F_opt]{\equilibriumProfitOneSidedLowLambda};
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+
+                \legend{$F_F$, $F_F^{opt}$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Optimal and actual (implied) entry fees}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                    ylabel={},
+                    xmin=0, xmax=1.5, % adjust these values as needed
+                    ymin=0.25, ymax=0.35, % adjust these values as needed
+                    axis lines=left,
+                    xtick={0, 1.5},
+                    legend pos=north west,
+                    width=\textwidth,
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.18]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.2]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.22]{\equilibriumProfitOneSidedLowLambda};
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+
+                \legend{$I_P = 0.18$, $I_P = 0.2$, $I_P = 0.22$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Platform profits net of investment costs}
+    \end{subfigure}
+    \caption{Equilibrium outcomes in the case when the platform has lower innate bargaining power ($N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$).
+As in every other case, the platform's profits are increasing in $N_P$, while the fringe's profits are decreasing.
+Furthermore, consumer surplus is also decreasing as a result in a decrease in total product variety.
+The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode.}
+    \label{fig:equilibrium_low_lambda_entry_fees}
+\end{figure}
+
 \section{Shapley value in the platform game}

### 2023-12-17 src/figures/equilibrium_symbolic.py

@@ -57,6 +57,14 @@ def create_plot_data(
             return np.array([N_F_opt(n) for n in N_P])
         else:
             return fsolve(lambda N_F: pi_F_t(N_P, N_F), 3)[0]
+        
+    def F_F_opt():
+        return np.sqrt(mu * I_F * V_F) - I_F
+    
+    def N_F_opt_bench(N_P):
+        F_F = F_F_opt()
+        N_F_candidate = mu / (F_F + I_F) - N_P * V_P / V_F - 1 / V_F
+        return np.maximum(N_F_candidate, 0)
 
     N_P_vec = np.linspace(N_P_range[0], N_P_range[1], num_obs)
     N_F_vec = N_F_opt(N_P_vec)
@@ -75,6 +83,17 @@ def create_plot_data(
     pi_P_noF = mu * N_P_vec * V_P / A_noF
 
     pi_P_var_vec = mu * N_P_vec * V_P / A_vec
+
+    if bargaining == "onesided" and value_function == "profit":
+        N_F_bench = N_F_opt_bench(N_P_vec)
+        F_F_opt_vec = np.where(
+            N_F_bench > 1e-5,
+            F_F_opt(),
+            np.nan
+        )
+    else:
+        F_F_opt_vec = np.ones_like(N_P_vec, dtype=float) * np.nan
+
     F_F_implied = np.where(
         N_F_vec > 1e-5,
         (pi_P_vec - pi_P_var_vec) / N_F_vec,
@@ -83,10 +102,10 @@ def create_plot_data(
 
     hybrid_mode = np.where(
         N_F_vec > 1e-5,
-        100,
+        10,
         0
     )
-       
+
 
 
     data = pd.DataFrame(
@@ -104,6 +123,7 @@ def create_plot_data(
             "CS_noF": CS_noF,
             "pi_P_noF": pi_P_noF,
             "F_F_implied": F_F_implied,
+            "F_F_opt": F_F_opt_vec,
             "hybrid": hybrid_mode,
         }
     )

### 2023-12-19 src/paper/application.tex
Add a bunch of new graphs

@@
 
-\pgfplotstableread[col sep=comma]{out/figures/equilibrium.csv}\equilibrium
-% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_profit_onesided_scale-1_lambda-1.csv}\equilibriumProfitOneSided
+\pgfplotstableread[col sep=comma]{out/figures/equilibrium_profit_onesided_scale-1_lambda-1.csv}\equilibrium
 \pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_onesided_scale-0.6_lambda-1.csv}\equilibriumFullSurplusOneSided
@@
 \begin{align*}
-    CS \propto \log(A).
+    CS = \mu N_C \log(A).
 \end{align*}
@@
     \end{align*}
-
-    Otherwise, if they are sufficiently high, $N_F = 0$ and the equilibrium size of the aggregate is
+    Otherwise,  $N_F = 0$ and the equilibrium size of the aggregate is
     \begin{align*}
@@
 \end{proposition}
-Note that in the first case, the size of the aggregate does not depend on the platforms' product variety or the platform's product advantage (\cref{eq:aggregate_eq}).
-
-Now let us turn to the optimal entry fee set by the platform, and its total profits, consisting of revenue from its own sales and the collected entry fees.
-First, let us examine the case when the fees are low enough for the fringe to be feasible.
+Note that in the first case (\cref{eq:aggregate_eq})., the size of the aggregate does not depend on the platforms' product variety or the platform's product advantage.
+The intuition behind this is that per-firm fringe profits only depend on these factors indirectly, through the size of the aggregate.
+That is, unless the fringe is not feasible, an increase in $N_P$ will simply replace some fringe entrants, but the free entry condition will pin down the same aggregate, as before.
+
+Now let us turn to the optimal entry fee set by the platform, and its total profits (consisting of revenue from its own sales and the collected entry fees).
+The following proposition establishes these both for the hybrid and the pure retail regimes.
 
@@
 \end{proposition}
-Note, that even though the platform's profit is increasing in the number of its products, the optimal entry fee does not depend on it (\cref{fig:F_F_eq,fig:pi_P_eq}).\footnote{
+Note, that even though the platform's profit is increasing in the number of its products, the optimal entry fee does not depend on it (\cref{fig:F_F_eq,fig:pi_P_eq}).
 This is only due to the fact that the platform's product does not require any investment cost.
 If the platform is operating in the hybrid regime, less fringe firms are needed to achieve the (fixed) equilibrium aggregate, therefore there is less expenditure on investment costs, which is essentially wasted.
-    If the platform's products also require investment, and their cost is proportional to the platform's product advantage, then $N_P$ has no effect on platform profits within the hybrid regime.
-}
+Consequently, in the hybrid regime, the marginal derivative of optimal profits with respect to the platform's product variety is simply the fringe's investment cost, adjusted for the possible difference in product advantage:
+\begin{align*}
+    N_F > 0 \implies \frac{\partial \pi_P^t}{\partial N_P} = \frac{V_P}{V_F} I_F.
+\end{align*}
+Furthermore, if the platform does have to pay an investment cost $I_P$, then it will only have its own products if $\frac{I_P}{V_P} \leq \frac{I_F}{V_F}$, which is efficient from a welfare perspective.
+
 As a consequence, as long as the fringe is feasible at the optimal entry fee, the size of the aggregate, and hence consumer welfare is also unaffected by the platform operating in hybrid mode.
 In contrast, when the fringe is not present in the market, total aggregate, and hence consumer welfare are increasing in the number of the platform's products.
-This is purely mechanical: more variety leads to higher welfare.
+This effect is purely mechanical: more variety leads to higher welfare.
 
 Finally, note that the profit of the platform in the hybrid regime is higher than in the retail regime, whenever the former is feasible.
-Therefore, the platform prefers to operate in hybrid mode, and does not want to exclude fringe firms from the market.
+Therefore, the platform prefers to operate in hybrid mode, and does not want to exclude fringe firms from the market.\footnote{
     This is a consequence of the fact that equation \eqref{eq:hybrid_profit} is strictly concave in $F_F$, therefore $F_F^*$ is a global maximum.
     It implies that there is no point where the fringe would be feasible under optimal entry fees, but the platform would prefer to operate in retail mode.
+}
 Therefore, in the benchmark model, a platform becoming a hybrid platform, or increasing the number of its own products, always has a weakly positive effect on the aggregate, and thus consumer welfare.\footnote{
-    This is in contrast to \textcite{anderson2021hybrid}, where a platform operating in hybrid mode sets a higher entry fee to advantage its own products, which in turn leads to a smaller aggregate.
+    This is in contrast to \textcite{anderson2021hybrid}, where a platform operating in hybrid mode sets higher royalties to create a price advantage for its own products.
     The reason for this difference lies in the type of entry fee: they assume a revenue-based, proportional fee, which distorts prices.
@@
 
-Now consider the case when instead of the platform setting take it or leave it entry fees, it must negotiate with the fringe about the division of profits.
-In this case, the timing is slightly different, as the platform cannot commit to an entry fee in the first period.
+Now consider the case where, instead of the platform setting take it or leave it entry fees, it must negotiate with the fringe about the division of profits.
+As the platform cannot choose 
 Instead, the game starts by fringe firms' investment decisions.
@@
 that is, an increase in the platform's products leads to a more than proportional reduction in the number of fringe products (\cref{fig:fringe_entry_eq}).\footnote{
-    The intuition behind this is demonstrated in \cref{fig:F_F_eq}.
+    The intuition behind this is demonstrated in \cref{fig:entry_fee}.
     As the platform's product variety grows, its bargaining power also increases.
@@
 }
-As, in this model, consumer welfare is monotone in the total aggregate, this implies that consumer welfare is decreasing in the number of the platform's products (\cref{fig:aggregate_eq}).
+As, in this model, consumer welfare is monotone in the total aggregate, this implies that consumer welfare is decreasing in the number of the platform's products (\cref{fig:welfare}).
 Therefore, as opposed to the benchmark model, the platform becoming more hybrid leads to a reduction in consumer welfare.\footnote{
@@
 }
+
 \begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
         \centering
@@
                     xlabel={$N_P$},
-                ylabel={$N_F^*$},
                     xmin=0, xmax=1.5, % adjust these values as needed
                     ymin=0, ymax=1.4, % adjust these values as needed
-                width=10cm, % adjust the width of the plot
-                height=6cm, % adjust the height of the plot
+                    width=\linewidth, % adjust the width of the plot
                     axis lines=left,
-                xtick=\empty, ytick=\empty
+                    xtick={0, 1.5},
                 ]
@@
                 \addplot[color=myblue,mark=none,thick] table[x=N_P,y=N_F]{\equilibrium};
-            \addplot[color=black,mark=none,thick,dotted] table[x=N_P,y=N_F_cf]{\equilibrium};
-            \legend{Benchmark, Bargaining, Fixed aggregate}
-        \end{axis}
-    \end{tikzpicture}
-    \caption{Equilibrium number of fringe firms as a function of the number of platform products.}
+                \legend{Bargaining, Benchmark}
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibrium};
+                \addplot[draw=none,name path=hybrid_bench] table[x=N_P,y=hybrid_bench]{\equilibrium};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_bench and bottom];
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Equilibrium number of fringe firms ($N_F$)}
         \label{fig:fringe_entry_eq}
-\end{figure}
-
-\begin{figure}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.45\textwidth}
         \centering
@@
                     xlabel={$N_P$},
-                ylabel={$A^*$},
+                    ylabel={$F_F$},
+                    xmin=0, xmax=1.5, % adjust these values as needed
+                    ymin=0, ymax=0.65, % adjust these values as needed
+                    width=\linewidth, % adjust the width of the plot
+                    axis lines=left,
+                    xtick={0, 1.5},
+                    legend pos=north east
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=F_F_opt]{\equilibrium};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y=F_F_implied]{\equilibrium};
+                \legend{Benchmark, Bargaining (implied)}
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibrium};
+                \addplot[draw=none,name path=hybrid_bench] table[x=N_P,y=hybrid_bench]{\equilibrium};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_bench and bottom];
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Optimal/implied entry fee ($F_F$)}
+        \label{fig:entry_fee}
+    \end{subfigure}
+    \caption{Equilibrium number of fringe entrants and (implied) entry fees ($\mu = 1, N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$).
+In the benchmark model, the entry fee does not depend on the platform's product variety, and an increase in $N_P$ leads to a proportional reduction in $N_F$.
+In contrast, in the bargaining case, the entry fee is increasing in $N_P$, and the reduction in $N_F$ is more than proportional.
+Dark shaded area represents hybrid mode under the bargaining assumption, while light shaded area represents additional hybrid mode under the benchmark assumption.}
+    \label{fig:entry_and_fees}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \begin{tikzpicture}
+        \begin{axis}[
+                xlabel={$N_P$},
+                    xmin=0, xmax=1.5, % adjust these values as needed
+                    ymin=0, ymax=0.65, % adjust these values as needed
+                    width=0.5\linewidth, % adjust the width of the plot
+                    axis lines=left,
+                    xtick={0, 1.5},
+                    legend pos=south east
+                ]
+            \addplot[color=myblue,mark=none,thick] table[x=N_P,y=pi_P_bench]{\equilibrium};
+            \addplot[color=myred,mark=none,thick] table[x=N_P,y=pi_P]{\equilibrium};
+            \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=pi_P_noF]{\equilibrium};
+            \legend{Benchmark, Bargaining, Pure retail}
+
+            \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibrium};
+            \addplot[draw=none,name path=hybrid_bench] table[x=N_P,y=hybrid_bench]{\equilibrium};
+            \addplot[draw=none,name path=bottom] {0};
+            \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+            \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_bench and bottom];
+        \end{axis}
+    \end{tikzpicture}
+    \caption{Platform profits in equilibrium ($\mu = 1, N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$).
+In both cases, platform profits are increasing in $N_P$.
+However, in the case of the hybrid regime under bargaining, this increase is lower, due to the fact that prices deviate further from optimal.
+Dark shaded area represents hybrid mode under the bargaining assumption, while light shaded area represents additional hybrid mode under the benchmark assumption.}
+    \label{fig:platform_profits}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
                     xmin=0, xmax=1.5, % adjust these values as needed
                     ymin=0, ymax=3, % adjust these values as needed
-                width=10cm, % adjust the width of the plot
-                height=6cm, % adjust the height of the plot
+                    width=\linewidth, % adjust the width of the plot
                     axis lines=left,
-                xtick=\empty, ytick=\empty,
+                    xtick={0, 1.5},
                     legend pos=south east
@@
                 \legend{Benchmark, Bargaining, Pure retail}
-        \end{axis}
-    \end{tikzpicture}
-    \caption{Equilibrium aggregate as a function of the number of platform products.
-Note, that consumer surplus is monotone in the aggregate, therefore this figure also shows ordinal changes in the equilibrium consumer surplus.}
-    \label{fig:aggregate_eq}
-\end{figure}
-
-\begin{figure}
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibrium};
+                \addplot[draw=none,name path=hybrid_bench] table[x=N_P,y=hybrid_bench]{\equilibrium};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_bench and bottom];
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Aggregate ($A$)}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.45\textwidth}
         \centering
@@
                     xlabel={$N_P$},
-                ylabel={$\pi_P^{t*}$},
+                    xmin=0, xmax=1.5, % adjust these values as needed
+                    ymin=0, ymax=1.5, % adjust these values as needed
+                    width=\linewidth, % adjust the width of the plot
+                    axis lines=left,
+                    xtick={0, 1.5},
+                    legend pos=south east
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=CS_bench]{\equilibrium};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y=CS]{\equilibrium};
+                \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=CS_noF]{\equilibrium};
+                \legend{Benchmark, Bargaining, Pure retail}
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibrium};
+                \addplot[draw=none,name path=hybrid_bench] table[x=N_P,y=hybrid_bench]{\equilibrium};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_bench and bottom];
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Consumer surplus ($CS$)}
+    \end{subfigure}
+    \caption{Size of the aggregate and consumer surplus in equilibrium ($\mu = 1, N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$).
+In the benchmark model, an increase in platform product variety has no effect in the hybrid regime.
+Under bargaining, it does have a negative effect on total product variety, and, in turn, consumer surplus.
+The increase has a (mechanical) positive effect in the pure retail regime under both assumptions.
+Dark shaded area represents hybrid mode under the bargaining assumption, while light shaded area represents additional hybrid mode under the benchmark assumption.}
+    \label{fig:welfare}
+\end{figure}
+
+\section{Extensions}
+
+\subsection{Platform has lower innate bargaining power}
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                    ylabel={},
+                    xmin=0, xmax=1.5, % adjust these values as needed
+                    ymin=0, ymax=3.1, % adjust these values as needed
+                    axis lines=left,
+                    xtick={0, 1.5},
+                    legend pos=south east,
+                    width=\textwidth,
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=N_P]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y=N_F]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[color=black,mark=none,thick] table[x=N_P,y=A]{\equilibriumProfitOneSidedLowLambda};
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+
+                \legend{$N_P$, $N_F$, $A$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Platform product variety and number of entrants}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                    ylabel={},
+                    xmin=0, xmax=1.5, % adjust these values as needed
+                    ymin=0, ymax=1.2, % adjust these values as needed
+                    axis lines=left,
+                    xtick={0, 1.5},
+                    legend pos=north west,
+                    width=\textwidth,
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=pi_P]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y=pi_F]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[color=black,mark=none,thick] table[x=N_P,y=CS]{\equilibriumProfitOneSidedLowLambda};
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+
+                \legend{$\pi_P$, $\pi_F$, $CS$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Profits and consumer surplus}
+    \end{subfigure}
+    \caption{Equilibrium outcomes in the case when the platform has lower innate bargaining power ($N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$).
+As in every other case, the platform's profits are increasing in $N_P$, while the fringe's profits are decreasing.
+Furthermore, consumer surplus is also decreasing as a result in a decrease in total product variety.
+The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode.}
+    \label{fig:equilibrium_low_lambda}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                    ylabel={},
                     xmin=0, xmax=1.5, % adjust these values as needed
                     ymin=0, ymax=0.65, % adjust these values as needed
-                width=10cm, % adjust the width of the plot
-                height=6cm, % adjust the height of the plot
                     axis lines=left,
-                xtick=\empty, ytick=\empty,
-                legend pos=south east
+                    xtick={0, 1.5},
+                    legend pos=south east,
+                    width=\textwidth,
                 ]
@@
                 \addplot[color=myred,mark=none,thick] table[x=N_P,y=pi_P]{\equilibrium};
+                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=pi_P]{\equilibriumProfitOneSidedLowLambda};
                 \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=pi_P_noF]{\equilibrium};
-            \legend{Benchmark, Bargaining, Pure retail}
-        \end{axis}
-    \end{tikzpicture}
-    \caption{Equilibrium platform profit as a function of the number of platform products.}
-    \label{fig:pi_P_eq}
-\end{figure}
-
-\begin{figure}
+
+                \legend{Benchmark, Bargaining ($\lambda = 1$), Bargaining ($\lambda = 0.5$)}
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[draw=none,name path=hybrid_orig] table[x=N_P,y=hybrid]{\equilibrium};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_orig and bottom];
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Platform profits}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.45\textwidth}
         \centering
@@
                     xlabel={$N_P$},
-                ylabel={$F_F$},
+                    ylabel={},
                     xmin=0, xmax=1.5, % adjust these values as needed
-                ymin=0, ymax=0.65, % adjust these values as needed
-                width=10cm, % adjust the width of the plot
-                height=6cm, % adjust the height of the plot
+                    ymin=0, ymax=0.5, % adjust these values as needed
                     axis lines=left,
-                xtick=\empty, ytick=\empty,
-                legend pos=north east
+                    xtick={0, 1.5},
+                    legend pos=south east,
+                    width=\textwidth,
                 ]
@@
                 \addplot[color=myred,mark=none,thick] table[x=N_P,y=F_F_implied]{\equilibrium};
-            \legend{Benchmark (optimal), Bargaining (implied)}
-        \end{axis}
-    \end{tikzpicture}
-    \caption{Optimal/implied entry fee as a function of the number of platform products.}
-    \label{fig:F_F_eq}
+                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=F_F_implied]{\equilibriumProfitOneSidedLowLambda};
+
+                \legend{Benchmark, Bargaining ($\lambda = 1$), Bargaining ($\lambda = 0.5$)}
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[draw=none,name path=hybrid_orig] table[x=N_P,y=hybrid]{\equilibrium};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_orig and bottom];
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Optimal/implied entry fee}
+    \end{subfigure}
+    \caption{Platform profits and (implied) entry fees ($\mu = 0.2, N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$).
+Regardless of lambda, platform profits and entry fees are increasing in $N_P$.
+However, when the platform's innate bargaining power is higher, entry fees are above optimal levels already for $N_P = 0$, and the additional increase somewhat mitigates the benefits of the platform's increased product variety.
+When $\lambda$ is lower, the entry fees are below optimal for low $N_P$, therefore increasing $N_P$ has a larger positive effect on profits.
+Dark shaded area represents hybrid mode under $\lambda=1$, while light shaded area represents additional hybrid mode under $\lambda=0.5$.}
+    \label{fig:platform_profits_low_lambda}
 \end{figure}
 
-% \section{Extensions}
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                    ylabel={},
+                    xmin=0, xmax=1.5, % adjust these values as needed
+                    ymin=0.2, ymax=0.35, % adjust these values as needed
+                    axis lines=left,
+                    xtick={0, 1.5},
+                    legend pos=north west,
+                    width=\textwidth,
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.18]{\equilibrium};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.2]{\equilibrium};
+                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.22]{\equilibrium};
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibrium};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+
+                \legend{$I_P = 0.18$, $I_P = 0.2$, $I_P = 0.22$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{$\lambda = 1$}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                    ylabel={},
+                    xmin=0, xmax=1.5, % adjust these values as needed
+                    ymin=0.2, ymax=0.35, % adjust these values as needed
+                    axis lines=left,
+                    xtick={0, 1.5},
+                    legend pos=south west,
+                    width=\textwidth,
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.18]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.2]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.22]{\equilibriumProfitOneSidedLowLambda};
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+
+                \legend{$I_P = 0.18$, $I_P = 0.2$, $I_P = 0.22$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{$\lambda = 0.5$}
+    \end{subfigure}
+    \caption{Total platform profits if the platform incurs an investment cost for creating its own products ($\pi_P(N_P) - I_P N_P$).
+In the high bargaining power case (left), the platform never chooses to operate in hybrid mode.
+It either becomes a pure marketplace or a pure retailer.
+In the case of lower $\lambda_P$ (right), choosing the hybrid mode can be optimal depending on $I_P$.
+The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode ($\mu = 1, N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$).}
+    \label{fig:equilibrium_low_lambda_entry_fees}
+\end{figure}
 
@@
                     axis lines=left,
-                    xtick={0, 1.5},
+                    xtick={0, 0.6},
                     legend pos=north west,
@@
 
-\subsection{Platform has lower innate bargaining power}
-
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}
-            \begin{axis}[
-                    xlabel={$N_P$},
-                    ylabel={},
-                    xmin=0, xmax=1.5, % adjust these values as needed
-                    ymin=0, ymax=3.1, % adjust these values as needed
-                    axis lines=left,
-                    xtick={0, 1.5},
-                    legend pos=south east,
-                    width=\textwidth,
-                ]
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=N_P]{\equilibriumProfitOneSidedLowLambda};
-                \addplot[color=myred,mark=none,thick] table[x=N_P,y=N_F]{\equilibriumProfitOneSidedLowLambda};
-                \addplot[color=black,mark=none,thick] table[x=N_P,y=A]{\equilibriumProfitOneSidedLowLambda};
-
-                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
-                \addplot[draw=none,name path=bottom] {0};
-                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
-
-                \legend{$N_P$, $N_F$, $A$}
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Platform product variety and number of fringe entrants}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}
-            \begin{axis}[
-                    xlabel={$N_P$},
-                    ylabel={},
-                    xmin=0, xmax=1.5, % adjust these values as needed
-                    ymin=0, ymax=1.2, % adjust these values as needed
-                    axis lines=left,
-                    xtick={0, 1.5},
-                    legend pos=north west,
-                    width=\textwidth,
-                ]
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=pi_P]{\equilibriumProfitOneSidedLowLambda};
-                \addplot[color=myred,mark=none,thick] table[x=N_P,y=pi_F]{\equilibriumProfitOneSidedLowLambda};
-                \addplot[color=black,mark=none,thick] table[x=N_P,y=CS]{\equilibriumProfitOneSidedLowLambda};
-
-                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
-                \addplot[draw=none,name path=bottom] {0};
-                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
-
-                \legend{$\pi_P$, $\pi_F$, $CS$}
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Platform and fringe profits}
-    \end{subfigure}
-    \caption{Equilibrium outcomes in the case when the platform has lower innate bargaining power ($N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$).
-As in every other case, the platform's profits are increasing in $N_P$, while the fringe's profits are decreasing.
-Furthermore, consumer surplus is also decreasing as a result in a decrease in total product variety.
-The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode.}
-    \label{fig:equilibrium_low_lambda}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}
-            \begin{axis}[
-                    xlabel={$N_P$},
-                    ylabel={},
-                    xmin=0, xmax=1.5, % adjust these values as needed
-                    ymin=0, ymax=0.4, % adjust these values as needed
-                    axis lines=left,
-                    xtick={0, 1.5},
-                    legend pos=south east,
-                    width=\textwidth,
-                ]
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=F_F_implied]{\equilibriumProfitOneSidedLowLambda};
-                \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=F_F_opt]{\equilibriumProfitOneSidedLowLambda};
-
-                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
-                \addplot[draw=none,name path=bottom] {0};
-                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
-
-                \legend{$F_F$, $F_F^{opt}$}
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Optimal and actual (implied) entry fees}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}
-            \begin{axis}[
-                    xlabel={$N_P$},
-                    ylabel={},
-                    xmin=0, xmax=1.5, % adjust these values as needed
-                    ymin=0.25, ymax=0.35, % adjust these values as needed
-                    axis lines=left,
-                    xtick={0, 1.5},
-                    legend pos=north west,
-                    width=\textwidth,
-                ]
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.18]{\equilibriumProfitOneSidedLowLambda};
-                \addplot[color=myred,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.2]{\equilibriumProfitOneSidedLowLambda};
-                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.22]{\equilibriumProfitOneSidedLowLambda};
-
-                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
-                \addplot[draw=none,name path=bottom] {0};
-                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
-
-                \legend{$I_P = 0.18$, $I_P = 0.2$, $I_P = 0.22$}
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Platform profits net of investment costs}
-    \end{subfigure}
-    \caption{Equilibrium outcomes in the case when the platform has lower innate bargaining power ($N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$).
-As in every other case, the platform's profits are increasing in $N_P$, while the fringe's profits are decreasing.
-Furthermore, consumer surplus is also decreasing as a result in a decrease in total product variety.
-The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode.}
-    \label{fig:equilibrium_low_lambda_entry_fees}
-\end{figure}
-
 \section{Shapley value in the platform game}

### 2023-12-19 src/figures/equilibrium_baseline.py

@@ -76,6 +76,18 @@ def create_plot_data(
         np.nan
     )
 
+    hybrid = np.where(
+        N_F_vec > 1e-5,
+        10,
+        0
+    )
+
+    hybrid_bench = np.where(
+        N_F_bench_vec > 1e-5,
+        10,
+        0
+    )
+
 
     data = pd.DataFrame(
         {

### 2023-12-19 src/figures/equilibrium_symbolic.py

@@ -86,13 +86,26 @@ def create_plot_data(
 
     if bargaining == "onesided" and value_function == "profit":
         N_F_bench = N_F_opt_bench(N_P_vec)
+        A_bench = N_P_vec * V_P + N_F_bench * V_F + 1   
+        CS_bench = np.log(A_bench)
+        pi_P_bench = F_F_opt() * N_F_bench + mu * N_P_vec * V_P / A_bench
         F_F_opt_vec = np.where(
             N_F_bench > 1e-5,
             F_F_opt(),
             np.nan
         )
+        hybrid_mode_bench = np.where(
+            N_F_bench > 1e-5,
+            10,
+            0
+        )
     else:
+        N_F_bench = np.ones_like(N_P_vec, dtype=float) * np.nan
+        A_bench = np.ones_like(N_P_vec, dtype=float) * np.nan
+        CS_bench = np.ones_like(N_P_vec, dtype=float) * np.nan
+        pi_P_bench = np.ones_like(N_P_vec, dtype=float) * np.nan
         F_F_opt_vec = np.ones_like(N_P_vec, dtype=float) * np.nan
+        hybrid_mode_bench = np.ones_like(N_P_vec, dtype=float) * np.nan
 
     F_F_implied = np.where(
         N_F_vec > 1e-5,
@@ -106,7 +119,9 @@ def create_plot_data(
         0
     )
 
-
+    A_noF = N_P_vec * V_P + 1
+    CS_noF = np.log(A_noF)
+    pi_P_noF = mu * N_P_vec * V_P / A_noF
 
     data = pd.DataFrame(
         {
@@ -125,6 +140,11 @@ def create_plot_data(
             "F_F_implied": F_F_implied,
             "F_F_opt": F_F_opt_vec,
             "hybrid": hybrid_mode,
+            "N_F_bench": N_F_bench,
+            "A_bench": A_bench,
+            "CS_bench": CS_bench,
+            "pi_P_bench": pi_P_bench,
+            "hybrid_bench": hybrid_mode_bench,
         }
     )
 

### 2023-12-19 src/paper/application.tex
Flesh out bargaining results section

@@
 The platform's profit share is higher when the fringe firms are more substitutable.}
+    \label{fig:outcome_based_bargaining_power}
 \end{figure}
@@
 Throughout this section I assume that the value of each product is the same: $v^F_i = v^F$.
-This is to simplify the analysis, but is not crucial for the results.  % TODO: look into relaxing this assumption
+This is to simplify the analysis, but is not crucial for the results.
 
@@
     This essentially means that I assume a one-sided platform, without the usual network effects.
-    % TODO: see if I can relax this assumption
 }
@@
 Finally, another important feature of this demand system is that, assuming optimal pricing, consumer welfare only depends on the size of the aggregate \parencite{anderson2020aggregative}.
-In particular, consumer surplus is proportional to the logarithm of the aggregate:
-\begin{align*}
-    CS = \mu N_C \log(A).
-\end{align*}
-This fact makes welfare analysis rather simple in this setting.
-
-\subsubsection{The benchmark model}
+In particular, consumer surplus is proportional to the logarithm of the aggregate: $CS = \mu N_C \log(A)$. This fact makes welfare analysis rather simple in this setting.
+
+\subsubsection{Benchmark: platform sets entry fee unilaterally}
 
@@
 Therefore, total profits in equilibrium must be zero.
-Combined with the simple profit function, this gives the following expressions for the equilibrium number of fringe firms and the equilibrium size of the aggregate.
+Combined with the  profit function, this gives the following expressions for the equilibrium number of fringe firms and the equilibrium size of the aggregate.
 \begin{proposition}
@@
 \end{proposition}
-Note that in the first case (\cref{eq:aggregate_eq})., the size of the aggregate does not depend on the platforms' product variety or the platform's product advantage.
+Note that in the first case (\cref{eq:aggregate_eq}), the size of the aggregate does not depend on the platforms' product variety or the platform's product advantage.
 The intuition behind this is that per-firm fringe profits only depend on these factors indirectly, through the size of the aggregate.
@@
 Now let us turn to the optimal entry fee set by the platform, and its total profits (consisting of revenue from its own sales and the collected entry fees).
-The following proposition establishes these both for the hybrid and the pure retail regimes.
+The following proposition establishes these both for the hybrid and the pure retail regimes, and \cref{fig:entry_fee,fig:platform_profits} demonstrates them graphically.
 
@@
 \end{proposition}
-Note, that even though the platform's profit is increasing in the number of its products, the optimal entry fee does not depend on it (\cref{fig:F_F_eq,fig:pi_P_eq}).
+Note, that even though the platform's profit is increasing in the number of its products, the optimal entry fee does not depend on it (\cref{fig:platform_profits,fig:entry_fee}).
 This is only due to the fact that the platform's product does not require any investment cost.
@@
 This effect is purely mechanical: more variety leads to higher welfare.
-
-Finally, note that the profit of the platform in the hybrid regime is higher than in the retail regime, whenever the former is feasible.
-Therefore, the platform prefers to operate in hybrid mode, and does not want to exclude fringe firms from the market.\footnote{
-    This is a consequence of the fact that equation \eqref{eq:hybrid_profit} is strictly concave in $F_F$, therefore $F_F^*$ is a global maximum.
-    It implies that there is no point where the fringe would be feasible under optimal entry fees, but the platform would prefer to operate in retail mode.
-}
-Therefore, in the benchmark model, a platform becoming a hybrid platform, or increasing the number of its own products, always has a weakly positive effect on the aggregate, and thus consumer welfare.\footnote{
+\Cref{fig:fringe_entry_eq} illustrates this effect.
+
+Finally, note that the profit of the platform under the hybrid regime is higher than under the retail regime, whenever the former is feasible.
+Therefore, for a given $N_P$, the platform prefers to operate in hybrid mode, and does not want to exclude fringe firms from the market.
+As a corollary, in the benchmark model, a platform becoming a hybrid platform, or increasing the number of its own products, always has a weakly positive effect on the aggregate, and thus consumer welfare.\footnote{
     This is in contrast to \textcite{anderson2021hybrid}, where a platform operating in hybrid mode sets higher royalties to create a price advantage for its own products.
@@
 }
-\subsubsection{The bargaining model}
+\subsubsection{Main model: bargaining between platform and fringe}
 
 Now consider the case where, instead of the platform setting take it or leave it entry fees, it must negotiate with the fringe about the division of profits.
-As the platform cannot choose 
+As the platform cannot choose and commit to an entry fee, the first period from the benchmark model is skipped.
 Instead, the game starts by fringe firms' investment decisions.
@@
 
-The participants negotiate over the aggregate profits that they can achieve in the subsequent period (assuming non-collusive, monopolistic pricing, as before).
-I assume that bargaining outcomes are determined according to \cref{ass:profit_sharing}, where $f(N_P, N_F)$ is defined as the total profits that the platform and the entrants can achieve by selling their products.
+The participants negotiate over the aggregate profits that they expect to obtain in the subsequent period (assuming the same non-collusive, monopolistic pricing, as before).
+I assume that bargaining outcomes are determined according to \cref{ass:profit_sharing}, where $\Pi(N_P, N_F, N_C)$ is defined as the sum of profits that the platform and the entrants acquire by selling their products.
 From \cref{eq:optimal_profit}, the total profit achieved by the platform and $N_F$ fringe firms is given by
 \begin{align*}
-    f(N_P, N_F) = \mu \frac{n V_F + N_P V_P}{n V_F + N_P V_P + 1}.
-\end{align*}
-This yields the following closed-form expressions for the total profits of the participants.
+    \Pi(N_P, N_F, N_C) = N_C \underbracket{\mu \frac{n V_F + N_P V_P}{n V_F + N_P V_P + 1}}_{\coloneqq f(N_P, N_F)}.
+\end{align*}
+Based on \cref{prop:profit_sharing}, one can even obtain closed-form expressions for platform and fringe profit shares for this class of demand systems.
 \begin{proposition}
@@
     \begin{align*}
-        \pi^t_P &=\int_0^1 f(N_P, sN_F) \ds \\
-                &= \mu \left[ 1 - \frac{\log \left(1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} \right].
-    \end{align*}
-    The total profits of the whole fringe are given by
-    \begin{align*}
-        \pi^t_F = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F(N_F).
+        \pi^t_P &= N_C \int_0^1 f(N_P, sN_F) \ds \\
+                &= \mu N_C \left[ 1 - \frac{\log \left(1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} \right].
+    \end{align*}
+    The total profits of the whole fringe (including investment costs) are given by
+    \begin{align*}
+        \pi^t_F = \mu N_C \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F N_F .
     \end{align*}
@@
 Now let us turn to how the platform's dual mode operation affects product variety and consumer welfare.
-Let us start by establishing some properties of the total profit function $f(n_P, n_F)$.
+I will rely on results from \cref{sec:results} to establish comparative statics for the equilibrium aggregate.
+Let us start by showing that $f(n_P, n_F)$ satisfies the assumptions those results rely on.
 \begin{lemma}
@@
 
-Owing to the additive nature of the total profit function, an even stronger result can be established.
+Owing to the additive nature of the total profit function, an even stronger result can be obtained.
 Notice that $f$ has the functional form required for proposition \ref{prop:aggregate_size_additive} with $g(x) = \frac{x}{1+x}, \alpha = V_P, \beta = V_F$.
@@
 \end{align*}
-that is, an increase in the platform's products leads to a more than proportional reduction in the number of fringe products (\cref{fig:fringe_entry_eq}).\footnote{
-    The intuition behind this is demonstrated in \cref{fig:entry_fee}.
-    As the platform's product variety grows, its bargaining power also increases.
-    This can be thought of as an increase in (implied) entry fees, which in turn discourages fringe entry.
-}
-Conversely, equilibrium total aggregate is also decreasing in $N_P$.\footnote{
-    The same result also holds true for an increase in $V_P$.
+that is, an increase in the platform's products leads to a more than proportional reduction in the number of fringe products (\cref{fig:fringe_entry_eq}).
+
+As a consequence of this, equilibrium total aggregate is also decreasing in $N_P$.\footnote{
+    The same result also holds true for an increase in the paltform's product advantage $V_P$.
 }
@@
 }
+
+The intuition behind this is demonstrated in can be captured by looking at entry fees.
+First, define the implied entry fee in the bargaining case as the difference between the variable profit and the final, total profit of the fringe firms, less the investment cost:
+\begin{align*}
+    F_F^{\text{impl}} = \pi_F^v - \pi_F^t + I_F.
+\end{align*}
+As shown before, the platform's product variety grows, its bargaining power also increases.
+This can be thought of as an increase in (implied) entry fees $F_F^{\text{impl}}$, which in turn discourages fringe entry \cref{fig:entry_fee}.
+
+In this specific demand system and parametrization, the implied entry fee is higher than what the platform would prefer to set for any $N_P \geq 0$.
+If it could, it would commit to a lower entry fee to incentivize more fringe entry, and thus increase total profits.
+This is an example that bargaining instead of unilateral pricing does not necessarily lead to lower platform shares, or better welfare outcomes: it can be a lose-lose situation for both the platform and the consumers.
+\Cref{sec:lower_bargaining_power} explores an alternative model where the platform has less bargaining power, and thus -- for sufficiently low values of $N_P$ -- the implied entry fee it achieves in the bargaining model is lower than what it would set unilaterally.
+
+Finally, let us look at the platform's profits in equilibrium.
+As in the benchmark model, they are increasing in the number platform's product variety $N_P$ (\cref{fig:platform_profits}). % TODO: can I make it a proper proposition?
+However, in contrast to that case, there is an important difference in the hybrid regime.
+In the benchmark model, the entry fee was independent of the platform's product variety.
+On the other hand, with bargaining, it is increasing in $N_P$ (\cref{fig:entry_fee}).
+Therefore, if the entry fee is already higher than optimal for a given $N_P$, an additional increase will lead to an even more suboptimal (implied) entry fee, and thus a lower increase in platform profits than it would otherwise.
+This is the case in the example parametrization displayed on the figures for every $N_P \geq 0$.
+
+This means that, if the platform had to create its product variety at a per-unit investment cost of $I_P$, it would make different (inefficient) choices compared to the benchmark model.
+In particular, it might invest in some products even if it has a product disadvantage, and it might not invest in some products even if it has a product disadvantage.
+This phenomenon is more pronounced when the implied entry fee for $N_P = 0$ is lower than optimal, and is explored in more detail in \cref{sec:lower_bargaining_power}.
 
@@
                 ]
-                \addplot[color=myred,mark=none,thick] table[x=N_P,y=N_F_bench]{\equilibrium};
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=N_F]{\equilibrium};
-                \legend{Bargaining, Benchmark}
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=N_F_bench]{\equilibrium};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y=N_F]{\equilibrium};
+                \legend{Benchmark, Bargaining}
 
@@
 \subsection{Platform has lower innate bargaining power}
+\label{sec:lower_bargaining_power}
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                    xmin=0, xmax=1.5, % adjust these values as needed
+                    ymin=0, ymax=1.8, % adjust these values as needed
+                    width=\linewidth, % adjust the width of the plot
+                    axis lines=left,
+                    xtick={0, 1.5},
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=N_F_bench]{\equilibrium};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y=N_F]{\equilibrium};
+                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=N_F]{\equilibriumProfitOneSidedLowLambda};
+                \legend{Benchmark, Bargaining ($\lambda = 1$), Bargaining ($\lambda = 0.5$)}
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibrium};
+                \addplot[draw=none,name path=hybrid_alt] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_alt and bottom];
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Equilibrium number of fringe firms ($N_F$)}
+        \label{fig:fringe_entry_eq_low_lambda}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                    xmin=0, xmax=1.5, % adjust these values as needed
+                    ymin=0, ymax=3, % adjust these values as needed
+                    width=\linewidth, % adjust the width of the plot
+                    axis lines=left,
+                    xtick={0, 1.5},
+                    legend pos=south east,
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=A_bench]{\equilibrium};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y=A]{\equilibrium};
+                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=A]{\equilibriumProfitOneSidedLowLambda};
+                \legend{Benchmark, Bargaining ($\lambda = 1$), Bargaining ($\lambda = 0.5$)}
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibrium};
+                \addplot[draw=none,name path=hybrid_alt] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_alt and bottom];
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Equilibrium number of fringe firms ($N_F$)}
+    \end{subfigure}
+    \caption{Equilibrium outcomes in the case when the platform has lower innate bargaining power ($N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$).
+As in every other case, the platform's profits are increasing in $N_P$, while the fringe's profits are decreasing.
+Furthermore, consumer surplus is also decreasing as a result in a decrease in total product variety.
+The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode.}
+    \label{fig:equilibrium_low_lambda}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                    ylabel={},
+                    xmin=0, xmax=1.5, % adjust these values as needed
+                    ymin=0, ymax=0.65, % adjust these values as needed
+                    axis lines=left,
+                    xtick={0, 1.5},
+                    legend pos=south east,
+                    width=\linewidth,
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=pi_P_bench]{\equilibrium};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y=pi_P]{\equilibrium};
+                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=pi_P]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=pi_P_noF]{\equilibrium};
+
+                \legend{Benchmark, Bargaining ($\lambda = 1$), Bargaining ($\lambda = 0.5$)}
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[draw=none,name path=hybrid_orig] table[x=N_P,y=hybrid]{\equilibrium};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_orig and bottom];
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Platform profits}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                    ylabel={},
+                    xmin=0, xmax=1.5, % adjust these values as needed
+                    ymin=0, ymax=0.5, % adjust these values as needed
+                    axis lines=left,
+                    xtick={0, 1.5},
+                    legend pos=south east,
+                    width=\linewidth,
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=F_F_opt]{\equilibrium};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y=F_F_implied]{\equilibrium};
+                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=F_F_implied]{\equilibriumProfitOneSidedLowLambda};
+
+                \legend{Benchmark, Bargaining ($\lambda = 1$), Bargaining ($\lambda = 0.5$)}
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[draw=none,name path=hybrid_orig] table[x=N_P,y=hybrid]{\equilibrium};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_orig and bottom];
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Optimal/implied entry fee}
+    \end{subfigure}
+    \caption{Platform profits and (implied) entry fees ($\mu = 0.2, N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$).
+Regardless of lambda, platform profits and entry fees are increasing in $N_P$.
+However, when the platform's innate bargaining power is higher, entry fees are above optimal levels already for $N_P = 0$, and the additional increase somewhat mitigates the benefits of the platform's increased product variety.
+When $\lambda$ is lower, the entry fees are below optimal for low $N_P$, therefore increasing $N_P$ has a larger positive effect on profits.
+Dark shaded area represents hybrid mode under $\lambda=1$, while light shaded area represents additional hybrid mode under $\lambda=0.5$.}
+    \label{fig:platform_profits_low_lambda}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                    ylabel={},
+                    xmin=0, xmax=1.5, % adjust these values as needed
+                    ymin=0.2, ymax=0.35, % adjust these values as needed
+                    axis lines=left,
+                    xtick={0, 1.5},
+                    legend pos=north west,
+                    width=\linewidth,
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.18]{\equilibrium};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.2]{\equilibrium};
+                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.22]{\equilibrium};
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibrium};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+
+                \legend{$I_P = 0.18$, $I_P = 0.2$, $I_P = 0.22$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{$\lambda = 1$}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                    ylabel={},
+                    xmin=0, xmax=1.5, % adjust these values as needed
+                    ymin=0.2, ymax=0.35, % adjust these values as needed
+                    axis lines=left,
+                    xtick={0, 1.5},
+                    legend pos=south west,
+                    width=\linewidth,
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.18]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.2]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.22]{\equilibriumProfitOneSidedLowLambda};
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+
+                \legend{$I_P = 0.18$, $I_P = 0.2$, $I_P = 0.22$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{$\lambda = 0.5$}
+    \end{subfigure}
+    \caption{Total platform profits if the platform incurs an investment cost for creating its own products ($\pi_P(N_P) - I_P N_P$).
+In the high bargaining power case (left), the platform never chooses to operate in hybrid mode.
+It either becomes a pure marketplace or a pure retailer.
+In the case of lower $\lambda_P$ (right), choosing the hybrid mode can be optimal depending on $I_P$.
+The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode ($\mu = 1, N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$).}
+    \label{fig:equilibrium_low_lambda_entry_fees}
+\end{figure}
+
+\section{Conclusion and future work}
+\label{sec:conclusion}
+
+This paper has introduced a new model of hybrid platforms in which bargaining between the platform and the entrant firms plays a key role.
+It has been demonstrated that platforms operating in hybrid mode can have serious consequences in such an environment.
+In particular, when a platform has a large number of its own products, then its bargaining power is also higher compared to the fringe entrants.
+This, in certain situations, such as the one described in this paper, this can lead to fewer fringe firms entering the market, reduced product variety, and ultimately, lower consumer welfare.
+
+In addition to the specific platform model, this paper also provides a simple, tractable, yet quite general framework in which one can study the effects of bargaining between one large and a continuum of small players.
+Such environments might, in addition to platforms, include upstream-downstream settings with one upstream supplier, or franchises with one franchisor and a continuum of franchisees, or wage bargaining.
+The quite general results of this paper give some intuition on what happens in such settings, without needing to delve into the details of a specific model.
+This also highlights certain similarities between those markets.
+Furthermore, many of the results from this paper can be applied in a plug-and-play fashion to other models of large-player-small-player interactions.
+
+There is a number of avenues for future research in this direction.
+First, I suspect that many of the assumptions made in section \cref{sec:example} can be relaxed, and one can still obtain similar results.
+An additional step I am planning to take is to endogenize the number of the platform's products, and the parameters of the profit sharing (bargaining rule).
+The latter would provide important insights into what kind of demand structures might lead to the evolution of hybrid platforms.
+
+I also hope that others will find this framework useful in their own research, and incorporate it in more complex and more applied models.
+In general, I believe this approach for modeling bargaining is a rather good compromise between assuming that one party has all the bargaining power, and modeling the bargaining process in detail, and might be a good fit for a number of different economic applications.
+
+\appendix
+
+\printbibliography
+
+\section{Extensions}
+\label{sec:extensions}
+
+In this section, I look at a number of extensions of the model presented in \cref{sec:example}.
+The common theme of these extensions is that the consumer surplus is also included in the sum that is bargained over.
+That is, $\Pi(N_P, N_F, N_C)$ now represents total surplus.
+
+First, \cref{sec:total_welfare} looks at the case when consumer can be extracted by the platform, but consumers are still passive, and the bargaining is between the platform and the fringe.
+Then, \cref{sec:two_sided} explores what happens when all three sides engage in the negotiation over the same total surplus.
+I will only consider the bargaining outcomes under assumptions \cref{ass:profit_sharing} and \cref{ass:profit_sharing_two_sided}, respectively, and do not look at a benchmark with unilateraly set entry fees for the fringe.
+
+\subsection{Platform can extract consumer surplus}
+\label{sec:total_welfare}
+
+In this section, I assume that the platform can extract consumer surplus by charging a flat entry fee $F_C$.
+As consumers are identical, and the platform can set any entry fee, this implies that the platform can extract all consumer surplus in this case.\footnote{
+    Note, that I still assume that all $N_C$ consumers are present on the market by default, they do not have to pay any cost that would be analogous to the entry fee ($I_F$) of the fringe firms.
+    Therefore, they enter the market if and only if they are expected to have non-negative utility, which in turn means that the platform sets the entry fee to be equal to the consumer surplus.
+}
+
+Let us start by deriving total profits (which, in this case is the total surplus) as a function of $N_P, N_F$ and $N_C$.
+Under the logit-like demand structure described in \cref{sec:example}, the total surplus is given by
+\begin{proposition}
+    \label{prop:profits_total_surplus}
+    If the platform can extract consumer surplus, then the total profits that the platform and the fringe firms can achieve are given by
+    \begin{align*}
+        \Pi(N_P, N_F, N_C) = \mu N_C \left[ \frac{N_P V_P + N_F V_F}{N_P V_P + N_F V_F + 1} + \log(N_P V_P + N_F V_F + 1) \right].
+    \end{align*}
+\end{proposition}
+\begin{proof}[Proof of \cref{prop:profits_total_surplus}]
+    \textcite{small1981applied} show that the total surplus in a logit demand system is given by this expression.
+    As total consumer surplus is zero, the total profits are equal to the total surplus.
+\end{proof}
+Note, that this expression is of the form $\Pi(N_C, N_P, N_F) = N_C f(N_P, N_F)$.
+Furthermore, $f(N_P, N_F) = g(V_P N_P + V_F N_F)$ for an increasing, strictly concave $g$.
+
+Therefore, if we show that \cref{ass:single_crossing} holds, it in turn implies that all of the results in \cref{sec:results} apply here, as well.
+The following lemma establishes this result.
+\begin{lemma}
+    \label{lem:profit_assumptions_total_surplus}
+    $f(n_P, n_F)$ satisfies \cref{ass:single_crossing}.
+    Furthermore,
+    \begin{align*}
+        \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} < 0.
+    \end{align*}
+\end{lemma}
+
+With this proven, we can rely on \cref{prop:aggregate_size_additive} to see that, in equilibrium, an increase in $N_P$ decreases $N_F$.
+Furthermore, this decrease is so large that total product variety, and thus total surplus (which in turn is equal to total profits) also decreases.\footnote{
+    As long as the market is in the hybrid regime.
+    If $N_F^* = 0$, then an increase in $N_P$ mechanically increases total aggregate, and thus total surplus.
+}
+\Cref{fig:equilibrium_full_surplus_one_sided} displays equilibrium outcomes for an example parametrization
+Thus, as in the case without consumer entry fees, a platform becoming increasingly hybrid has generally negative consequences.
 
@@
                     legend pos=south east,
-                    width=\textwidth,
+                    width=\linewidth,
                 ]
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=N_P]{\equilibriumProfitOneSidedLowLambda};
-                \addplot[color=myred,mark=none,thick] table[x=N_P,y=N_F]{\equilibriumProfitOneSidedLowLambda};
-                \addplot[color=black,mark=none,thick] table[x=N_P,y=A]{\equilibriumProfitOneSidedLowLambda};
-
-                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=N_P]{\equilibriumFullSurplusOneSided};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y=N_F]{\equilibriumFullSurplusOneSided};
+                \addplot[color=black,mark=none,thick] table[x=N_P,y=A]{\equilibriumFullSurplusOneSided};
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumFullSurplusOneSided};
                 \addplot[draw=none,name path=bottom] {0};
@@
         \end{tikzpicture}
-        \caption{Platform product variety and number of entrants}
+        \caption{Platform product variety and number of fringe entrants}
     \end{subfigure}
@@
                     legend pos=north west,
-                    width=\textwidth,
+                    width=\linewidth,
                 ]
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=pi_P]{\equilibriumProfitOneSidedLowLambda};
-                \addplot[color=myred,mark=none,thick] table[x=N_P,y=pi_F]{\equilibriumProfitOneSidedLowLambda};
-                \addplot[color=black,mark=none,thick] table[x=N_P,y=CS]{\equilibriumProfitOneSidedLowLambda};
-
-                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=pi_P]{\equilibriumFullSurplusOneSided};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y=pi_F]{\equilibriumFullSurplusOneSided};
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumFullSurplusOneSided};
                 \addplot[draw=none,name path=bottom] {0};
@@
 
-                \legend{$\pi_P$, $\pi_F$, $CS$}
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Profits and consumer surplus}
-    \end{subfigure}
-    \caption{Equilibrium outcomes in the case when the platform has lower innate bargaining power ($N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$).
-As in every other case, the platform's profits are increasing in $N_P$, while the fringe's profits are decreasing.
-Furthermore, consumer surplus is also decreasing as a result in a decrease in total product variety.
+                \legend{$\pi_P$, $\pi_F$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Platform and fringe profits}
+    \end{subfigure}
+    \caption{Equilibrium outcomes in the case when the whole surplus is bargained over ($N_C = 0.6, V_P = 1, V_F = 1, I_F = 0.2$).
+As in the case of bargaining over profits, the platform's profits are increasing in $N_P$, while the fringe's profits are decreasing.
+Consumer surplus does not matter in this case, as it is extracted by the platform.
 The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode.}
-    \label{fig:equilibrium_low_lambda}
+    \label{fig:equilibrium_full_surplus_one_sided}
 \end{figure}
 
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}
-            \begin{axis}[
-                    xlabel={$N_P$},
-                    ylabel={},
-                    xmin=0, xmax=1.5, % adjust these values as needed
-                    ymin=0, ymax=0.65, % adjust these values as needed
-                    axis lines=left,
-                    xtick={0, 1.5},
-                    legend pos=south east,
-                    width=\textwidth,
-                ]
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=pi_P_bench]{\equilibrium};
-                \addplot[color=myred,mark=none,thick] table[x=N_P,y=pi_P]{\equilibrium};
-                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=pi_P]{\equilibriumProfitOneSidedLowLambda};
-                \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=pi_P_noF]{\equilibrium};
-
-                \legend{Benchmark, Bargaining ($\lambda = 1$), Bargaining ($\lambda = 0.5$)}
-
-                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
-                \addplot[draw=none,name path=hybrid_orig] table[x=N_P,y=hybrid]{\equilibrium};
-                \addplot[draw=none,name path=bottom] {0};
-                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
-                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_orig and bottom];
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Platform profits}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}
-            \begin{axis}[
-                    xlabel={$N_P$},
-                    ylabel={},
-                    xmin=0, xmax=1.5, % adjust these values as needed
-                    ymin=0, ymax=0.5, % adjust these values as needed
-                    axis lines=left,
-                    xtick={0, 1.5},
-                    legend pos=south east,
-                    width=\textwidth,
-                ]
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=F_F_opt]{\equilibrium};
-                \addplot[color=myred,mark=none,thick] table[x=N_P,y=F_F_implied]{\equilibrium};
-                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=F_F_implied]{\equilibriumProfitOneSidedLowLambda};
-
-                \legend{Benchmark, Bargaining ($\lambda = 1$), Bargaining ($\lambda = 0.5$)}
-
-                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
-                \addplot[draw=none,name path=hybrid_orig] table[x=N_P,y=hybrid]{\equilibrium};
-                \addplot[draw=none,name path=bottom] {0};
-                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
-                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_orig and bottom];
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Optimal/implied entry fee}
-    \end{subfigure}
-    \caption{Platform profits and (implied) entry fees ($\mu = 0.2, N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$).
-Regardless of lambda, platform profits and entry fees are increasing in $N_P$.
-However, when the platform's innate bargaining power is higher, entry fees are above optimal levels already for $N_P = 0$, and the additional increase somewhat mitigates the benefits of the platform's increased product variety.
-When $\lambda$ is lower, the entry fees are below optimal for low $N_P$, therefore increasing $N_P$ has a larger positive effect on profits.
-Dark shaded area represents hybrid mode under $\lambda=1$, while light shaded area represents additional hybrid mode under $\lambda=0.5$.}
-    \label{fig:platform_profits_low_lambda}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}
-            \begin{axis}[
-                    xlabel={$N_P$},
-                    ylabel={},
-                    xmin=0, xmax=1.5, % adjust these values as needed
-                    ymin=0.2, ymax=0.35, % adjust these values as needed
-                    axis lines=left,
-                    xtick={0, 1.5},
-                    legend pos=north west,
-                    width=\textwidth,
-                ]
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.18]{\equilibrium};
-                \addplot[color=myred,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.2]{\equilibrium};
-                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.22]{\equilibrium};
-
-                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibrium};
-                \addplot[draw=none,name path=bottom] {0};
-                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
-
-                \legend{$I_P = 0.18$, $I_P = 0.2$, $I_P = 0.22$}
-            \end{axis}
-        \end{tikzpicture}
-        \caption{$\lambda = 1$}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}
-            \begin{axis}[
-                    xlabel={$N_P$},
-                    ylabel={},
-                    xmin=0, xmax=1.5, % adjust these values as needed
-                    ymin=0.2, ymax=0.35, % adjust these values as needed
-                    axis lines=left,
-                    xtick={0, 1.5},
-                    legend pos=south west,
-                    width=\textwidth,
-                ]
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.18]{\equilibriumProfitOneSidedLowLambda};
-                \addplot[color=myred,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.2]{\equilibriumProfitOneSidedLowLambda};
-                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.22]{\equilibriumProfitOneSidedLowLambda};
-
-                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
-                \addplot[draw=none,name path=bottom] {0};
-                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
-
-                \legend{$I_P = 0.18$, $I_P = 0.2$, $I_P = 0.22$}
-            \end{axis}
-        \end{tikzpicture}
-        \caption{$\lambda = 0.5$}
-    \end{subfigure}
-    \caption{Total platform profits if the platform incurs an investment cost for creating its own products ($\pi_P(N_P) - I_P N_P$).
-In the high bargaining power case (left), the platform never chooses to operate in hybrid mode.
-It either becomes a pure marketplace or a pure retailer.
-In the case of lower $\lambda_P$ (right), choosing the hybrid mode can be optimal depending on $I_P$.
-The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode ($\mu = 1, N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$).}
-    \label{fig:equilibrium_low_lambda_entry_fees}
-\end{figure}
-
-\section{Conclusion and future work}
-\label{sec:conclusion}
-
-This paper has introduced a new model of hybrid platforms in which bargaining between the platform and the entrant firms plays a key role.
-It has been demonstrated that platforms operating in hybrid mode can have serious consequences in such an environment.
-In particular, when a platform has a large number of its own products, then its bargaining power is also higher compared to the fringe entrants.
-This, in certain situations, such as the one described in this paper, this can lead to fewer fringe firms entering the market, reduced product variety, and ultimately, lower consumer welfare.
-
-In addition to the specific platform model, this paper also provides a simple, tractable, yet quite general framework in which one can study the effects of bargaining between one large and a continuum of small players.
-Such environments might, in addition to platforms, include upstream-downstream settings with one upstream supplier, or franchises with one franchisor and a continuum of franchisees, or wage bargaining.
-The quite general results of this paper give some intuition on what happens in such settings, without needing to delve into the details of a specific model.
-This also highlights certain similarities between those markets.
-Furthermore, many of the results from this paper can be applied in a plug-and-play fashion to other models of large-player-small-player interactions.
-
-There is a number of avenues for future research in this direction.
-First, I suspect that many of the assumptions made in section \cref{sec:example} can be relaxed, and one can still obtain similar results.
-An additional step I am planning to take is to endogenize the number of the platform's products, and the parameters of the profit sharing (bargaining rule).
-The latter would provide important insights into what kind of demand structures might lead to the evolution of hybrid platforms.
-
-I also hope that others will find this framework useful in their own research, and incorporate it in more complex and more applied models.
-In general, I believe this approach for modeling bargaining is a rather good compromise between assuming that one party has all the bargaining power, and modeling the bargaining process in detail, and might be a good fit for a number of different economic applications.
-
-\appendix
-
-\printbibliography
-
-\section{Extensions}
-\label{sec:extensions}
-
-In this section, I look at a number of extensions of the model presented in \cref{sec:example}.
-The common theme of these extensions is that the consumer surplus is also included in the sum that is bargained over.
-That is, $\Pi(N_P, N_F, N_C)$ now represents total surplus.
-
-First, \cref{sec:total_welfare} looks at the case when consumer can be extracted by the platform, but consumers are still passive, and the bargaining is between the platform and the fringe.
-Then, \cref{sec:two_sided} explores what happens when all three sides engage in the negotiation over the same total surplus.
-I will only consider the bargaining outcomes under assumptions \cref{ass:profit_sharing} and \cref{ass:profit_sharing_two_sided}, respectively, and do not look at a benchmark with unilateraly set entry fees for the fringe.
-
-\subsection{Platform can extract consumer surplus}
-\label{sec:total_welfare}
-
-In this section, I assume that the platform can extract consumer surplus by charging a flat entry fee $F_C$.
-As consumers are identical, and the platform can set any entry fee, this implies that the platform can extract all consumer surplus in this case.\footnote{
-    Note, that I still assume that all $N_C$ consumers are present on the market by default, they do not have to pay any cost that would be analogous to the entry fee ($I_F$) of the fringe firms.
-    Therefore, they enter the market if and only if they are expected to have non-negative utility, which in turn means that the platform sets the entry fee to be equal to the consumer surplus.
-}
-
-Let us start by deriving total profits (which, in this case is the total surplus) as a function of $N_P, N_F$ and $N_C$.
-Under the logit-like demand structure described in \cref{sec:example}, the total surplus is given by
-\begin{proposition}
-    \label{prop:profits_total_surplus}
-    If the platform can extract consumer surplus, then the total profits that the platform and the fringe firms can achieve are given by
-    \begin{align*}
-        \Pi(N_P, N_F, N_C) = \mu N_C \left[ \frac{N_P V_P + N_F V_F}{N_P V_P + N_F V_F + 1} + \log(N_P V_P + N_F V_F + 1) \right].
-    \end{align*}
-\end{proposition}
-\begin{proof}[Proof of \cref{prop:profits_total_surplus}]
-    \textcite{small1981applied} show that the total surplus in a logit demand system is given by this expression.
-    As total consumer surplus is zero, the total profits are equal to the total surplus.
-\end{proof}
-Note, that this expression is of the form $\Pi(N_C, N_P, N_F) = N_C f(N_P, N_F)$.
-Furthermore, $f(N_P, N_F) = g(V_P N_P + V_F N_F)$ for an increasing, strictly concave $g$.
-
-Therefore, if we show that \cref{ass:single_crossing} holds, it in turn implies that all of the results in \cref{sec:results} apply here, as well.
-The following lemma establishes this result.
-\begin{lemma}
-    \label{lem:profit_assumptions_total_surplus}
-    $f(n_P, n_F)$ satisfies \cref{ass:single_crossing}.
-    Furthermore,
-    \begin{align*}
-        \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} < 0.
-    \end{align*}
-\end{lemma}
-
-With this proven, we can rely on \cref{prop:aggregate_size_additive} to see that, in equilibrium, an increase in $N_P$ decreases $N_F$.
-Furthermore, this decrease is so large that total product variety, and thus total surplus (which in turn is equal to total profits) also decreases.\footnote{
-    As long as the market is in the hybrid regime.
-    If $N_F^* = 0$, then an increase in $N_P$ mechanically increases total aggregate, and thus total surplus.
-}
-\Cref{fig:equilibrium_full_surplus_one_sided} displays equilibrium outcomes for an example parametrization
-Thus, as in the case without consumer entry fees, a platform becoming increasingly hybrid has generally negative consequences.
+The difference is that, due to the platform appropriating all the consumer surplus, it does not hurt consumer welfare -- it is zero regardless of $N_P$.
+Coupled with the fact that fringe firms also make zero profits in equilibrium, this means that the outcome is not so negative, after all.
+In particular, the platform's profits are increasing in $N_P$, and thus it prefers to operate in hybrid mode, as long as it is feasible.
+So even though the total pie gets smaller, the platform gets a larger slice, while the consumers and the fringe are just as well off.
+
+The catch is that, in this comparative statics exercise, the platforms' increased product variety came out of thin air.
+Specifically, when looking at the platform's profits, this increase in product variety is not associated with any increase in investment costs.
+If we were to include those at the same level of the fringe's investment costs, then the platform's profits would be decreasing in $N_P$, and it would not make the investment.
+Nevertheless, if it were to make it for some reason, it would not have the negative consequences that it had in \cref{sec:example}.
+
+\subsection{Consumers also engage in bargaining}
+\label{sec:two_sided}
 
@@
                     legend pos=south east,
-                    width=\textwidth,
-                ]
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=N_P]{\equilibriumFullSurplusOneSided};
-                \addplot[color=myred,mark=none,thick] table[x=N_P,y=N_F]{\equilibriumFullSurplusOneSided};
-                \addplot[color=black,mark=none,thick] table[x=N_P,y=A]{\equilibriumFullSurplusOneSided};
-
-                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumFullSurplusOneSided};
-                \addplot[draw=none,name path=bottom] {0};
-                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
-
-                \legend{$N_P$, $N_F$, $A$}
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Platform product variety and number of fringe entrants}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}
-            \begin{axis}[
-                    xlabel={$N_P$},
-                    ylabel={},
-                    xmin=0, xmax=1.5, % adjust these values as needed
-                    ymin=0, ymax=1.2, % adjust these values as needed
-                    axis lines=left,
-                    xtick={0, 1.5},
-                    legend pos=north west,
-                    width=\textwidth,
-                ]
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=pi_P]{\equilibriumFullSurplusOneSided};
-                \addplot[color=myred,mark=none,thick] table[x=N_P,y=pi_F]{\equilibriumFullSurplusOneSided};
-
-                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumFullSurplusOneSided};
-                \addplot[draw=none,name path=bottom] {0};
-                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
-
-                \legend{$\pi_P$, $\pi_F$}
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Platform and fringe profits}
-    \end{subfigure}
-    \caption{Equilibrium outcomes in the case when the whole surplus is bargained over ($N_C = 0.6, V_P = 1, V_F = 1, I_F = 0.2$).
-As in the case of bargaining over profits, the platform's profits are increasing in $N_P$, while the fringe's profits are decreasing.
-Consumer surplus does not matter in this case, as it is extracted by the platform.
-The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode.}
-    \label{fig:equilibrium_full_surplus_one_sided}
-\end{figure}
-
-The difference is that, due to the platform appropriating all the consumer surplus, it does not hurt consumer welfare -- it is zero regardless of $N_P$.
-Coupled with the fact that fringe firms also make zero profits in equilibrium, this means that the outcome is not so negative, after all.
-In particular, the platform's profits are increasing in $N_P$, and thus it prefers to operate in hybrid mode, as long as it is feasible.
-So even though the total pie gets smaller, the platform gets a larger slice, while the consumers and the fringe are just as well off.
-
-The catch is that, in this comparative statics exercise, the platforms' increased product variety came out of thin air.
-Specifically, when looking at the platform's profits, this increase in product variety is not associated with any increase in investment costs.
-If we were to include those at the same level of the fringe's investment costs, then the platform's profits would be decreasing in $N_P$, and it would not make the investment.
-Nevertheless, if it were to make it for some reason, it would not have the negative consequences that it had in \cref{sec:example}.
-
-\subsection{Consumers also engage in bargaining}
-\label{sec:two_sided}
-
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}
-            \begin{axis}[
-                    xlabel={$N_P$},
-                    ylabel={},
-                    xmin=0, xmax=1.5, % adjust these values as needed
-                    ymin=0, ymax=3.1, % adjust these values as needed
-                    axis lines=left,
-                    xtick={0, 1.5},
-                    legend pos=south east,
-                    width=\textwidth,
+                    width=\linewidth,
                 ]
@@
                     legend pos=north west,
-                    width=\textwidth,
+                    width=\linewidth,
                 ]
@@
 
-\section{Shapley value in the platform game}
-\label{app:shapley_value}
-
-Consider a cooperative game with two types of players: a major player $P$ and $n$ smaller players.
-I.e., $N = \{P, F_1, \dots, F_n\}$.
-Assume that (1) no coalition of players can achieve a positive value without the participation of $P$ and (2) players $F_i$ are identical.
-Let $n_T(S)$ denote the number of players of type $T \in \{P, F\}$ in coalition $S$. Then, the value that any coalition $S \subset N$ can achieve is the following:
-\begin{align*}
-    v(S) = \begin{cases}
-        0                              & \text{if } P \notin S \\
-        f\left(\frac{n_F(S)}{n}\right) & \text{otherwise}.
-    \end{cases}
-\end{align*}
-This coalition-form game corresponds to the setting in this paper with a (one-sided) platform and a number of potential entrants.
-
-I start by characterizing the case when the game is superadditive to provide some support for using the Shapley value as the bargaining outcome.\footnote{For example, the results in \textcite{gul1989bargaining} rely on superadditivity, while monotonicity suffices for \textcite[]{hart1996bargaining}.}
-
-\begin{proposition}
-    \label{prop:monotone}
-    The game $(N, v)$ is monotone and superadditive if and only if $f$ is increasing and $f(0) \geq 0$. % It is supermodular if and only if $f$ is convex.
-\end{proposition}
-
-\begin{proof}[Proof% of Proposition \ref{prop:monotone}
-    ]
-    Monotonicity is evident.
-For superadditivity, note that for any coalitions $S_1, s_2$ such that $S_1 \cap s_2 = \emptyset$, $P \notin S_1$ or $P \notin s_2$.
-WLOG assume it is the latter, therefore $v(S_2) = 0$.
-As a result, $v(S_1) + v(S_2) = v(S_1) \leq v(S_1 \cup S_2)$ holds if and only if $(N, v)$ is monotone.
-\end{proof}
-
-Now let us look at the limit of the Shapley-values as the number of fringe firms goes to infinity.\footnote{
-    As this game is of bounded variation, this result can also be obtained in a more direct way using the main theorem from \textcite{fogelman1980asymptotic}.
-    However, I believe the following proof is instructive, and drives home the idea that the continuous approximation is rather accurate even in the case of a relatively small number of players.
-}
-I use the following notation: $\varphi_P^n$ denotes the Shapley-value of player $P$ if there exist $n$ players of type $F$.
-The next proposition shows that the Shapley value of the platform can be described by a simple integral.
-
-\begin{proposition}
-    \label{prop:one_sided}
-    Let $f$ be continuous on [0, 1]. Then
-    \begin{align*}
-        \varphi_P^\infty = \lim_{n \to \infty} \varphi_p^n = \int_0^1 f(t) \dt .
-    \end{align*}
-\end{proposition}
-
-\begin{proof}[Proof% of Proposition \ref{prop:one_sided}
-    ]
-    Let $R$ denote a permutation of the set of players ($N$).
-Additionally, let us denote the players preceding $i$ by $\mathcal{P}_i^R$.
-The value of player $P$ is their expected marginal contribution averaged over all permutations of $N$:
-    \begin{align*}
-        \varphi_P^n = \frac{1}{(n+1)!} \sum_R v(\mathcal{P}_P^R \cup \{i\}) - v(\mathcal{P}_P^R)
-    \end{align*}
-    First, note that $v(\mathcal{P}_P^R) = 0$ for any permutation, as no coalition can achieve a positive value without player $P$.
-Furthermore, using the fact that all agents of type $A$ are identical implies that $v(\mathcal{P}_P^R \cup \{i\})$ only depends on the number of agents in the coalition.
-More precisely,
-    \begin{align*}
-        v(\mathcal{P}_P^R \cup \{i\}) = f(n_A(\mathcal{P}_P^R \cup \{i\}) / n) = f(|\mathcal{P}_P^R| / n).
-    \end{align*}
-    Finally, the set of permutations in which $k$ number of players precede $P$ is independent of $n$, i.e.
-    \begin{align*}
-        \{R \mid |\mathcal{P}_P^R| = k\} = n! \quad \forall\, k.
-    \end{align*}
-    Putting all the above together, the value of player $P$ can be expressed as
-    \begin{align*}
-        \varphi_P^n &= \frac{1}{(n+1)!} \sum_{k=0}^n n! f(k / n) \\
-        &= \frac{1}{n+1} \sum_{k=0}^n f(k / n) \\
-        &= \frac{n}{n+1} \underbrace{\frac{1}{n} \sum_{k=0}^{n-1} f(k / n)}_{=S_n} + \frac{1}{n+1} f(1).
-    \end{align*}
-    $S_n$ are just the left Riemann-sums of function $f$ on the interval $[0, 1]$. Therefore, if $f$ is continuous (and thus Riemann-integrable), then $S_n \to \int_0^1 f(t)$, and thus
-    \begin{align*}
-        \lim_{n \to \infty} \varphi_P^n &= \lim_{n \to \infty} \frac{1}{n+1} \sum_{k=1}^n f(k / n) \\
-        &= \lim_{n \to \infty}\underbrace{\frac{n}{n+1}}_{\to 1} \frac{1}{n} \sum_{k=0}^{n-1} f(k / n) + \underbrace{\frac{1}{n+1} f(1)}_{\to 0} \\
-        &= \int_0^1 f(t) \dt .
-    \end{align*}
-\end{proof}
-
-Finally, the aggregated value of the fringe can be obtained using the efficiency of the Shapley value.
-
-\begin{corollary}
-    \label{cor:fringe_value}
-    The aggregated Shapley-value of the fringe is
-    \begin{align*}
-        \varphi_F^\infty = f(1) - \int_0^1 f(t) \dt.
-    \end{align*}
-    Furthermore, if $f$ is differentiable on $[0, 1]$, Then the value of the fringe can also be expressed as
-    \begin{align*}
-        \varphi_F^\infty = \int_0^1 t f'(t) \dt.
-    \end{align*}
-\end{corollary}
-
-\begin{proof}[Proof% of Corollary \ref{cor:fringe_value}
-    ]
-    The first equality comes from the efficiency of the Shapley-value. The values of all players sum up to $f(1)$ for all $n \in \mathbb{N}$, therefore
-    \begin{align*}
-        \lim_{n \to \infty} \sum_{i=1}^n \varphi_{F_i}^n = \lim_{n \to \infty} (1 - \varphi_P^n ) = 1 - \int_0^1 f(t).
-    \end{align*}
-    The second can be obtained by integration by parts:
-    \begin{align*}
-        \int_0^1 t f'(t) \dt = tf(t) \mid_0^1 - \int_0^1 f(t) \dt = f(1) - \int_0^1 f(t) \dt
-    \end{align*}
-\end{proof}
+% TODO: do I want a section on Shapley-values, or move some cooperative stuff here?
 

### 2024-01-05 src/paper/application.tex
Reorganize paper

@@
 In the benchmark model, the platform will be able to set and commit to any lump-sum entry fee it wishes to.\footnote{
-    The focus of this paper is on fees paid and entry decisions made by fringe producers, but I will also consider the case when consumers might also face entry fees or subsidies.
+    The focus of this paper is on fees paid and entry decisions made by fringe producers, but I will also consider the case when consumers also face entry fees or subsidies.
 }
 The main contribution of this paper is to deviate from this usual assumption, and instead consider a setting in which the platform and the fringe engage in some form of bargaining over the total profits.
-To model this in a theoretically sound, but still tractable way, I borrow a solution concept from cooperative game theory.
-Similarly to a number of other papers in the industrial organization literature \parencite[e.g.][]{montez2007downstream,hart1990property,levy1997individual,inderst2003bargaining,brugemann2019intra}, I assume that the resulting allocation for each player is given by their Shapley value.
-This value (and the game itself) depends on who is assumed to participate in the bargaining process.
-I will consider two different cases.
-
-\paragraph{One-sided case} In the first setting, the platform and the fringe firms bargain over the total profits of the platform and the fringe taken together, and the consumers are not included in the negotiations.
-The following assumption describes this case.
+To model this in a tractable way, I propose a profit division rule that is based on the Shapley value \parencite{shapley1953additive}, or, more generally, random order values \parencite{weber1988probabilistic}.
+This way of modelling bargaining outcomes has many precedents in the industrial organization literature \parencite[e.g.][]{montez2007downstream,hart1990property,levy1997individual,inderst2003bargaining,brugemann2019intra}.
+In the main text, I simply propose a formula for the profit shares without going into the details of the underlying cooperative game.
+The interested reader can find a more detailed discussion of how it relates to random order values in \cref{sec:cooperative_game}.
+
 \begin{assumption}
     \label{ass:profit_sharing}
-    Consider the following cooperative game $\mathcal{G} = (\mathcal{N}, v)$.
-    The set of players consists of the platform plus the fringe firms: $\mathcal{N} = \{P, F_i\}, i \in [0, N_F]$.
-    The value of a coalition $S$ is zero without the platform, and depends on the number of fringe firms otherwise:
-    \begin{align*}
-        v(S) = \begin{cases}
-            0 & \text{if } P \notin S \\
-            N_C f(N_P, n_F(S)) & \text{if } P \in S
-        \end{cases},
-    \end{align*}
-    where $n_F(S)$ is the measure of fringe firms in $S$.
-    Each type of player gets their Shapley value in this game:
-    \begin{align*}
-        \pi_P(N_P, N_F, N_C) &= \varphi_P(\mathcal{G}), \\
-        \pi_F(N_P, N_F, N_C) &= \varphi_F(\mathcal{G}),
-    \end{align*}
-    where $\varphi_i(\mathcal{G})$ denotes the Shapley value of player(s) $i$ in game $\mathcal{G}$.
+    Let $N_P, N_F, N_C \geq 0$ be the number of platform products, fringe firms and consumers, respectively.
+    Thus, the value that players create together is given by $\Pi(N_P, N_F, N_C) = N_C f(N_P, N_F)$.
+    Let us denote the platform's and the fringe's profit shares by $\pi_P(N_P, N_F, N_C)$ and $\pi_F(N_P, N_F, N_C)$, respectively.
+    Then, the following holds:
+    \begin{align*}
+        \pi_P(N_P, N_F, N_C) &= N_C \int_0^1 w_P(s) f(N_P, s N_F) \ds, \\
+        \pi_F(N_P, N_F, N_C) &= N_C \int_0^1 w_F(s) N_F \partial_2 f(N_P, s N_F) \ds.
+    \end{align*}
+    Furthermore, $w_P \geq 0$ and $w_F \geq 0$ are such that $\pi_P(N_P, N_F, N_C) + \pi_F(N_P, N_F, N_C) \leq \Pi(N_P, N_F, N_C)$.
 \end{assumption}
 
-While this assumption might seem somewhat abstract, the resulting profit allocations are remarkably simple, and can be expressed as integrals (expectations) over the marginal contributions of the players.
-\begin{proposition}
-    \label{prop:profit_sharing}
-    Consider the case when only the platform and the fringe firms participate in the bargaining process.
-    Then, the resulting profit shares are given by
-    \begin{align*}
-        \pi_P(N_P, N_F, N_C) &= N_C \int_0^1 f(N_P, s N_F) \ds, \\
-        \pi_F(N_P, N_F, N_C) &= N_C \int_0^1 s N_F \partial_2 f(N_P, s N_F) \ds.
-    \end{align*}
-\end{proposition}
-
-\begin{proof}[proof of \cref{prop:profit_sharing}]
-    This result is a direct application of Proposition 3 and Corollary 2 in \textcite{stancsics2023value}.
-\end{proof}
+Although the reason behind choosing this particular form for profit shares is discussed in detail in the appendix, let me highlight some important observations.
+First, player's profit shares are closely related to their (weighted average) marginal contributions to the total value.
+In the case of the platform, its contribution is the total value, as it is indispensable, while the fringe firms' contribution is captured by the partial derivative of the total value with respect to the number of fringe firms.
+Second, the platform and the fringe do not necessarily get the entire value they create.
+This is due to the fact that I also want to allow for the possibility of consumers participating in the bargaining process and getting a share of the profits, too
+Finally, the profit shares depend on two types of factors: the production function $f$ and $w_P$ and $w_F$, which I will call bargaining weights.
+The former is determined by the technology and demand structure, while the latter can be thought of as some king of intrinsic bargaining power.
+
+In the later sections, I will consider specific examples for $f$ and $w_P$ and $w_F$, motivated by a Logit-like demand system, and (weighted) Shapley values, respectively.
+However, for a number of results, this level of detail is not necessary, and these quite general assumptions are sufficient.
 
@@
 The following observation demonstrates this idea.
-\begin{observation}
+\begin{proposition}
     \label{prop:outcome_based_bargaining_power}
@@
     Then, $\pi_P \leq \tilde{\pi}_P$.
-\end{observation}
+\end{proposition}
 
@@
 \end{figure}
-
-\paragraph{Two-sided case} Alternatively, in certain settings, it might be appropriate to assume that the consumers (or, more generally, the entities on the other side of the market) also engage in the bargaining process.
-The cooperative game describing this situation is formalized in \cref{ass:profit_sharing_two_sided}.
-\begin{assumption}
-    \label{ass:profit_sharing_two_sided}
-    Consider the following cooperative game $\mathcal{G} = (\mathcal{N}, v)$.
-    The set of players consists of the platform plus the fringe firms: $\mathcal{N} = \{P, F_i, C_j\}, i \in [0, N_F], j \in [0, N_C]$.
-    The value of a coalition $S$ is zero without the platform, and depends on the number of fringe firms otherwise:
-    \begin{align*}
-        v(S) = \begin{cases}
-            0 & \text{if } P \notin S \\
-            n_C(S) f(N_P, n_F(S)) & \text{if } P \in S
-        \end{cases},
-    \end{align*}
-    where $n_F(S)$ and $n_C(S)$ is the measure of fringe firms and consumers, respectively, in $S$.
-    Each type of player gets their Shapley value in this game:
-    \begin{align*}
-        \pi_P(N_P, N_F, N_C) &= \varphi_P(\mathcal{G}), \\
-        \pi_F(N_P, N_F, N_C) &= \varphi_F(\mathcal{G}), \\
-        \pi_C(N_P, N_F, N_C) &= \varphi_F(\mathcal{G}),
-    \end{align*}
-    where $\varphi_i(\mathcal{G})$ denotes the Shapley value of player(s) $i$ in game $\mathcal{G}$.
-\end{assumption}
-
-As in the one-sided case, simple expressions exist for these various shares.
-\begin{proposition}
-    \label{prop:profit_sharing_two_sided}
-    Consider the case when only the platform and the fringe firms participate in the bargaining process.
-    Then, the resulting profit shares are given by
-    \begin{align*}
-        \pi_P(N_P, N_F, N_C) &= N_C \int_0^1 s f(N_P, s N_F) \ds, \\
-        \pi_F(N_P, N_F, N_C) &= N_C \int_0^1 s^2 N_F \partial_2 f(N_P, s N_F) \ds \\
-        \pi_C(N_P, N_F, N_C) &= N_C \int_0^1 s f(N_P, s N_F) \ds.
-    \end{align*}
-\end{proposition}
-\begin{proof}[proof of \cref{prop:profit_sharing}]
-    This result is a direct application of Proposition 11 in \textcite{stancsics2023value}.
-\end{proof}
-One thing to note is that the platform's and fringe firms' shares are lower than in the one-sided case.
-This is due to the fact of needing to share the pie with the consumers, too.
-Additionally, the platform's share is identical to the consumers' (aggregated) share.\footnote{
-    This stems from the linearity of the profit function in the number of consumers.
-}
-This foreshadows the idea that -- even though it might not be welfare-maximizing -- what's good for the platform might also good for the consumers in the two-sided case.
 
@@
 }
-What it requires of $f$, however, is not so obvious, and also depends on whether one assumes one-sided or two-sided bargaining.
+What it requires of $f$, however, is not so obvious, and also depends on what one assumes about the innate bargaining weights $w_F$ and $w_P$.
 Nevertheless, when microfounding the profit function, one can simply check whether this assumption holds or not.
 In particular, it will be satisfied for the logit-type demand in \cref{sec:example}.
+% TODO: conjecture: it only has to hold for $f(N_P, N_F)$.
 
@@
 For the following two propositions, let us ignore free entry and equilibrium behavior, and consider the number of fringe entrants $N_F$ as fixed.
-The following statement claims that -- in both the one-sided and two-sided bargaining cases -- the platform's profits are increasing in its own product variety.
+The following statement claims that the platform's profits are increasing in its own product variety.
 \begin{proposition}
@@
 In the following, I assume that the profit function has a specific, additive form.
-Intuitively, this means that -- in terms of total profits generated -- the platform's and the fringe firms' products are substitutable to each other according to some constant ratio.\footnote{
-    Note that it does not mean that their products are substitutes in the usual, demand theory sense.
-    They still might be complements to each other.
-}
+Intuitively, this means that -- in terms of total profits generated -- the platform's and the fringe firms' products are substitutable to each other according to some constant ratio.
 \begin{proposition}
@@
 Here, I consider two variants of the model: a benchmark where the platform can unilaterally commit to any entry fee, and a bargaining model where the platform and the fringe firms negotiate over the distribution of profits.
-
-As an extension, I also examine what happens if the platform is able to extract consumer surplus by charging a flat entry fee, and the platform and the firms bargain over this larger sum.
+Furthermore, I focus on a particular set of weight functions $w_P$ and $w_F$, which correspont to the Shapley-values of the players in the case of one-sided bargaining.
+
+As an extension, I also examine what happens when the platform and the fringe firms have unequal bargaining weights, while still retaining more structure than the very general bargaining rule from \cref{ass:profit_sharing}.
+In particular, I look at the case of bargaining outcomes being describet by weighted values, with all fringe players sharing the same weight.
 Furthermore, I also consider the case of two-sided bargaining, where the consumers also participate in the negotiation over the value produced.
@@
 \end{align*}
-Based on \cref{prop:profit_sharing}, one can even obtain closed-form expressions for platform and fringe profit shares for this class of demand systems.
+
+Let us assume that the bargaining results in profits being shared according to players' Shapley values.
+These Shapley values satisfy \cref{ass:profit_sharing}, with $w_P(s) \equiv 1$ and $w_F(s) = s$.\footnote{
+    For a discussion and proof of this claim, see \cref{sec:cooperative_game}.
+}
+Based on these, one can even obtain closed-form expressions for platform and fringe profit shares for this class of demand systems.
 \begin{proposition}
@@
 \label{sec:lower_bargaining_power}
+
+In the previous sections, I assumed that the platform and the fringe firms split total profits according to their Shapley values.
+Because of the symmetry property of the Shapley value, this excludes the possibility of players having some kind of innate bargaining power, which is not related to the profit functions.
+In this extension, I will relax this assumption, and assume instead that profits are shared according to \emph{weighed} Shapley values.
+These are a generalization of the Shapley value, where each player has a weight $w_i$ that can, in certain settings, be thought of as a parameter describing bargaining power.\footnote{
+    \textcite{hart1996bargaining} and \textcite{stole1996intra} provide foundations for this interpretation.
+}
+Similarly to the standard Shapley value, one can show that outcomes based on weighted values also satisfy \cref{ass:profit_sharing}.
+Specifically, when the weight of the platform is $\lambda_P$, the functions $w_P$ and $w_F$ are given by
+\begin{align*}
+    w_P(s) &= \lambda_P s ^ {\lambda_P - 1} \\
+    w_F(s) &= s ^ {\lambda_P}.
+\end{align*}
+
+TODO: can I show that \cref{ass:single_crossing} still holds for any $\lambda_P$? If not, focus on a specific case, such as the one on the graphs.
 
@@
 
+\section{The platform game and the (weighted) Shapley value}
+\label{sec:cooperative_game}
+
+In this section, I describe how the profit sharing rule from \cref{sec:profit_sharing} can be derived from various cooperative games.
+In each of the following subsections, I formally define a cooperative game that models the platform setting, and derive the (weighted) Shapley values of the various players.
+I show that they correspond to the formulas given in \cref{sec:profit_sharing}, with a specific choice of weight functions $w_P$ and $w_F$ for each case.
+
+I start with the simplest case: one-sided bargaining and the usual Shapley value \parencite{shapley1953additive}.
+Then, I look at weighted values \parencite{weber1988probabilistic} in the same cooperative game.
+Finally, I consider the case when the consumers also participate in the bargaining process, and derive the corresponding Shapley values.
+
+\subsection{One-sided case}
+\label{sec:cooperative_game_one_sided}
+
+In the first setting, the platform and the fringe firms bargain over the total profits they generate together, and the consumers are not included in the negotiations.
+The following cooperative game describes this case.
+
+Consider the game $\mathcal{G} = (\mathcal{N}, v)$, characterized by the set of players $\mathcal{N}$ and its characteristic function $v$.
+The set of players consists of the platform plus the fringe firms: $\mathcal{N} = \{P, F_i\}, i \in [0, N_F]$.
+Because the platform is indispensible, the value of a coalition $S$ is zero without the platform, and depends on the number of fringe firms otherwise:
+\begin{align*}
+    v(S) = \begin{cases}
+        0 & \text{if } P \notin S \\
+        N_C f(N_P, n_F(S)) & \text{if } P \in S
+    \end{cases},
+\end{align*}
+where $n_F(S)$ is the measure of fringe firms in $S$.
+
+The following proposition describes the Shapley value of the platform ($\varphi_P(\mathcal{G})$) and the fringe firms ($\varphi_F(\mathcal{G})$) in this game.
+
+\begin{proposition}
+    \label{prop:profit_sharing_one_sided}
+    Consider the cooperative game above.
+    Then, the Shapley values of the platform and the fringe firms are given by
+    \begin{align*}
+        \varphi_P(\mathcal{G}) &= N_C \int_0^1 f(N_P, s N_F) \ds, \\
+        \varphi_P(\mathcal{F}) &= N_C \int_0^1 s N_F \partial_2 f(N_P, s N_F) \ds.
+    \end{align*}
+\end{proposition}
+
+\begin{proof}[proof of \cref{prop:profit_sharing_one_sided}]
+    This result is a direct application of Proposition 3 and Corollary 2 in \textcite{stancsics2023value}.
+\end{proof}
+
+As an immediate consequence, if bargaining outcomes are described by the Shapley value, then the resulting allocations satisfy \cref{ass:profit_sharing} with $w_P(s) \equiv 1$ and $w_F(s) = s$.
+
+\subsection{Weighted value}
+\label{sec:cooperative_game_weighted}
+
+Now let us generalize the previous result, and assume instead that players' shares are described by their weighted values,
+As before, let us start by formally describing the cooperative game.
+The set of players and the characteristic function are the same as in \cref{sec:cooperative_game_one_sided}, but now the game is additionally endowed with a weight system $\mathbf{\lambda} = \{\lambda_P, \lambda_{F}(i)\}$.
+Let us assume that all fringe players have the same weight $\lambda_{F}(i) \equiv 1$.
+
+Then, the weighted values of the players are described by the following proposition.
+
+\begin{proposition}
+    \label{prop:profit_sharing_weighted}
+    Consider the cooperative game above.
+    Then, the weighted values of the platform and the fringe firms are given by
+    \begin{align*}
+        \varphi_P(\mathcal{G}) &= N_C \int_0^1 \lambda_P s ^ {\lambda_P - 1} f(N_P, s N_F) \ds, \\
+        \varphi_F(\mathcal{G}) &= N_C \int_0^1 s ^ {\lambda_P} N_F \partial_2 f(N_P, s N_F) \ds.
+    \end{align*}
+\end{proposition}
+
+\begin{proof}[proof of \cref{prop:profit_sharing_weighted}]
+    This result is a direct application of Proposition 4 in \textcite{stancsics2023value}.
+\end{proof}
+
+As before, the resulting allocations satisfy \cref{ass:profit_sharing} with $w_P(s) \equiv \lambda_P s ^ {\lambda_P - 1}$ and $w_F(s) = s ^ {\lambda_P}$.
+
+\subsection{Two-sided case}
+\label{sec:cooperative_game_two_sided}
+
+Finally, in certain settings, it might be appropriate to assume that the consumers (or, more generally, the entities on the other side of the market) also engage in the bargaining process.
+The cooperative game describing can be formalized as follows.
+
+The set of players consists of the platform plus the fringe firms: $\mathcal{N} = \{P, F_i, C_j\}, i \in [0, N_F], j \in [0, N_C]$.
+The value of a coalition $S$ is zero without the platform, and depends on the number of fringe firms otherwise:
+\begin{align*}
+    v(S) = \begin{cases}
+        0 & \text{if } P \notin S \\
+        n_C(S) f(N_P, n_F(S)) & \text{if } P \in S
+    \end{cases},
+\end{align*}
+where $n_F(S)$ and $n_C(S)$ is the measure of fringe firms and consumers, respectively, in $S$.
+
+As in the one-sided case, simple expressions exist for the Shapley value of the platform ($\varphi_P(\mathcal{G})$), fringe firms ($\varphi_F(\mathcal{G})$) and consumers ($\varphi_C(\mathcal{G})$).
+
+\begin{proposition}
+    \label{prop:profit_sharing_two_sided}
+    Consider the case when only the platform and the fringe firms participate in the bargaining process.
+    Then, the resulting profit shares are given by
+    \begin{align*}
+        \varphi_P(\mathcal{G}) &= N_C \int_0^1 s f(N_P, s N_F) \ds, \\
+        \varphi_F(\mathcal{G}) &= N_C \int_0^1 s^2 N_F \partial_2 f(N_P, s N_F) \ds \\
+        \varphi_C(\mathcal{G}) &= N_C \int_0^1 s f(N_P, s N_F) \ds.
+    \end{align*}
+\end{proposition}
+\begin{proof}[proof of \cref{prop:profit_sharing_two_sided}]
+    This result is a direct application of Proposition 11 in \textcite{stancsics2023value}.
+\end{proof}
+
+One thing to note is that the platform's and fringe firms' shares are lower than in the one-sided case.
+This is due to the fact of needing to share the pie with the consumers, too.
+Additionally, the platform's share is identical to the consumers' (aggregated) share.\footnote{
+    This stems from the linearity of the profit function in the number of consumers.
+}
+This foreshadows the idea that -- even though it might not be welfare-maximizing -- what's good for the platform might also good for the consumers in the two-sided case.
+Finally, as in both examples before, these values satisfy \cref{ass:profit_sharing} with $w_P(s) = s$ and $w_F(s) = s^2$.
+
 \section{Extensions}
@@
 
-% TODO: do I want a section on Shapley-values, or move some cooperative stuff here?
-
 \section{Proofs and additional lemmas}
@@
     \begin{align*}
-        G(x) = \int_0^x g(sx) \ds.
+        G(x) = \int_0^1 g(sx) \ds.
     \end{align*}
@@
     \begin{align*}
-        \frac{\partial \pi_P(N_P, N_F, N_C)}{\partial N_P} &= N_C \frac{\partial}{\partial N_P} \int_0^1 w(s) f(N_P, N_F) \ds \\
-        &= \int_0^1 w(s) \underbrace{\frac{\partial f(N_P, sN_F)}{\partial N_P}}_{> 0} \ds > 0
-    \end{align*}
-    for any continuous $w(s)$.
-    In particular, this holds for $w(s) = 1$ and $w(s) = s$, which correspond to assumptions \cref{ass:profit_sharing} and \cref{ass:profit_sharing_two_sided}, respectively.
+        \frac{\partial \pi_P(N_P, N_F, N_C)}{\partial N_P} &= N_C \frac{\partial}{\partial N_P} \int_0^1 w_P(s) f(N_P, N_F) \ds \\
+        &= \int_0^1 w_P(s) \underbrace{\frac{\partial f(N_P, sN_F)}{\partial N_P}}_{> 0} \ds > 0
+    \end{align*}
+    for any non-negative, continuous $w_P(s)$.
 \end{proof}
@@
     \begin{align*}
-        \pi_F(N_P, N_F, N_C) = N_C \int_0^1 w(s) N_F \partial_2 f(N_P, s N_F) \ds,
-    \end{align*}
-    where $w(s)$ is either $s$ or $s^2$, depending on whether one assumes one or two-sided bargaining.
+        \pi_F(N_P, N_F, N_C) = N_C \int_0^1 w_F(s) N_F \partial_2 f(N_P, s N_F) \ds,
+    \end{align*}
     By assumption, $f$ is twice continuously differentiable, therefore $\partial_2$ is also continuously differentiable in $N_P$.
-    Thus the Leibniz rule can be applied to obtain
-    \begin{align*}
-        \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P} &= \frac{\partial}{\partial N_P} N_C \int_0^1 w(s) N_F \partial_2 f(N_P, s N_F) \ds \\
-        &= N_C \int_0^1 w(s) N_F \frac{\partial}{\partial N_P} \partial_2 f(N_P, s N_F) \ds \\
-        &= N_C \int_0^1 w(s) N_F \partial^2_{12} f(N_P, s N_F) \ds.
-    \end{align*}
-
-    As $w(s) > 0$ for $s > 0$, if $\partial_2 f(N_P, s N_F)$ has the same sign over $[0, N_F]$, then the integral also has the same sign.
+    Thus, the Leibniz rule can be applied to obtain
+    \begin{align*}
+        \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P} &= \frac{\partial}{\partial N_P} N_C \int_0^1 w_F(s) N_F \partial_2 f(N_P, s N_F) \ds \\
+        &= N_C \int_0^1 w_F(s) N_F \frac{\partial}{\partial N_P} \partial_2 f(N_P, s N_F) \ds \\
+        &= N_C \int_0^1 w_F(s) N_F \partial^2_{12} f(N_P, s N_F) \ds.
+    \end{align*}
+
+    As $w_F(s) \geq 0$ for $s > 0$, if $\partial_2 f(N_P, s N_F)$ has the same sign over $[0, N_F]$, then the integral also has the same sign.
     Formally,
@@
     \begin{align*}
-        \pi_F(N_P, N_F, N_C) = \beta N_C N_F \int_0^1 w_s s g'(\alpha N_P + s \beta N_F) \ds.
+        \pi_F(N_P, N_F, N_C) = \beta N_C N_F \int_0^1 w_F(s) g'(\alpha N_P + s \beta N_F) \ds.
     \end{align*}
@@
         \frac{\partial N_F}{\partial N_P} = \frac{
-            \alpha \beta N_C N_P \int_0^1 w(s) g''(\alpha N_P + s \beta N_F) \ds
+            \alpha \beta N_C N_P \int_0^1 w_F(s) g''(\alpha N_P + s \beta N_F) \ds
         }{
-            \underbracket{I'_F(N_F) - \beta N_C \int_0^1 w(s) g'(\alpha N_P + s \beta N_F) \ds}_{(1)} - \underbracket{\beta^2 N_C N_F \int_0^1 w(s) s g''(\alpha N_P + s \beta N_F) \ds}_{(2)}.
+            \underbracket{I'_F(N_F) - \beta N_C \int_0^1 w_F(s) g'(\alpha N_P + s \beta N_F) \ds}_{(1)} - \underbracket{\beta^2 N_C N_F \int_0^1 w_F(s) s g''(\alpha N_P + s \beta N_F) \ds}_{(2)}.
         }
@@
 
-    Next, observe that we can bound (2) from above using the fact that $s \in [0, 1]$:
-    \begin{align*}
-        (2) \leq \beta^2 N_C N_F \int_0^1 w(s) g''(\alpha N_P + s \beta N_F) \ds.
+    Next, observe that we can bound (2) from above using the fact that $0 \leq s \leq 1$:
+    \begin{align*}
+        (2) \leq \beta^2 N_C N_F \int_0^1 w_F(s) g''(\alpha N_P + s \beta N_F) \ds.
     \end{align*}
@@
     \begin{align*}
-        \frac{\partial N_F}{\partial N_P} \leq \frac{\alpha \beta N_C N_P \int_0^1 w(s) g''(\alpha N_P + s \beta N_F) \ds}{\beta^2 N_C N_F \int_0^1 w(s) g''(\alpha N_P + s \beta N_F) \ds} = -\frac{\alpha}{\beta},
+        \frac{\partial N_F}{\partial N_P} \leq \frac{\alpha \beta N_C N_P \int_0^1 w_F(s) g''(\alpha N_P + s \beta N_F) \ds}{\beta^2 N_C N_F \int_0^1 w_F(s) g''(\alpha N_P + s \beta N_F) \ds} = -\frac{\alpha}{\beta},
     \end{align*}

### 2024-01-12 src/paper/application.tex
Add low lambda extension

@@
 
-TODO: can I show that \cref{ass:single_crossing} still holds for any $\lambda_P$? If not, focus on a specific case, such as the one on the graphs.
+\textcolor{red}{TODO: can I show that \cref{ass:single_crossing} still holds for any $\lambda_P$? If not, focus on a specific case, such as the one on the graphs.}
+
+The example parametrizatrion is the same as in the main model, with the only difference that the platform has a lower innate bargaining power ($\lambda_P = 0.5$).
+As the conditions in \cref{ass:single_crossing} are also satisfied in this case, the main observations from \cref{sec:results} also apply.
+That is, as shown on \cref{fig:fringe_entry_eq_low_lambda}, total aggregate is decreasing in $N_P$ throughout the hybrid regime, due to the platform's products displacing more fringe products than their total number.
+
+The main difference is that, due to the lower bargaining power of the platform, the implied entry fee (\cref{fig:platform_profits_low_lambda}) is lower than the benchmark, unilaterally set one for low enough $N_P$.
+As a consequence, total aggregate, and thus consumer surplus, is also above the benchmark outcome in that case.
+Furthermore, there exists some $\bar{N}_P$ for which the unilateral price setting and bargaining outcomes coincide in terms of all variables, due to the implied entry fee being the same.
+
+Another major difference pertains to the total profits of the platform as a function of $N_P$.
+It is still true that they are increasing in the number of the platform's products, but now this increase is even more pronounced for low values of $N_P$.
+The reason is that for low $N_P$, the implied entry fee is lower than the optimal one.
+Furthermore, it increases in $N_P$ as a result of the platform's increased bargaining power.
+Therefore, the platform's profits are increasing in $N_P$ even more than in the benchmark case or the main model, up to the point where the implied entry fee is equal to the optimal one.
+After that, the same effect as in the main model kicks in, and the increase in profits is lower than in the benchmark case.
+
+\Cref{fig:equilibrium_low_lambda_entry_fees} demonstrates an important consequence of this phenomenon.
+Imagine that the platform can decide on the number of its products at time 0, at an investment cost of $I_P$ per product.
+In the main model, due to the implied entry fee being higher than optimal even for $N_P = 0$, hybrid operation is never optimal.
+The platform would always prefer either pure retail or pure marketplace operation.
+In contrast, when the platform has lower bargaining power, there exists a range of $I_P$ values (e.g. $I_P = 0.2$) for which the platform would prefer to operate in hybrid mode.
+Furthermore, if hybrid operation is not allowed, the platform might switch to become a pure marketplace, thereby increasing consumer surplus.
 
@@
         \caption{Platform profits}
+        \label{fig:platform_profits_low_lambda}
     \end{subfigure}
@@
         \caption{Optimal/implied entry fee}
+        \label{fig:entry_fee_low_lambda}
     \end{subfigure}
@@
 Dark shaded area represents hybrid mode under $\lambda=1$, while light shaded area represents additional hybrid mode under $\lambda=0.5$.}
-    \label{fig:platform_profits_low_lambda}
+    \label{fig:profits_and_entry_fees_low_lambda}
 \end{figure}

### 2024-01-12 src/paper/application.tex
Add extension for two-sided bargaining

@@
 
+\subsection{Consumers also participate in bargaining}
+
+In the second extension, I consider the case when the consumers also participate in the bargaining process.
+This entails two changes compared to the main model.
+First, the players bargain over the total surplus generated on all sides of the market, not just total profits.
+Second, the outcomes are assumed to be described by a cooperative game with three types of players: the platform, the fringe firms, and the consumers.
+
+Let us start by deriving total surplus as a function of $N_P, N_F$ and $N_C$.
+Under the logit-like demand structure described in \cref{sec:example}, the total surplus is given by
+\begin{proposition}
+    \label{prop:profits_total_surplus}
+    If the platform can extract consumer surplus, then the total surplus is given by
+    \begin{align*}
+        \Pi(N_P, N_F, N_C) = \mu N_C \left[ \frac{N_P V_P + N_F V_F}{N_P V_P + N_F V_F + 1} + \log(N_P V_P + N_F V_F + 1) \right].
+    \end{align*}
+\end{proposition}
+\begin{proof}[Proof of \cref{prop:profits_total_surplus}]
+    See \textcite{small1981applied} for a derivation for the discrete case.
+    The continuous case is analogous.
+\end{proof}
+Note, that this expression is of the form $\Pi(N_C, N_P, N_F) = N_C f(N_P, N_F)$.
+Furthermore, $f(N_P, N_F) = g(V_P N_P + V_F N_F)$ for an increasing, strictly concave $g$.
+
+Next, let us consider the bargaining outcomes in this three-sided setting.
+\Cref{sec:cooperative_game_two_sided} formally describes the corresponding cooperative game, and \cref{prop:profit_sharing_two_sided} establishes the resulting profit shares.
+To summarize, the shares of the various players are given by
+Then, the resulting profit shares are given by
+\begin{align*}
+    \pi_P(N_P, N_F, N_C) &= N_C \int_0^1 s f(N_P, s N_F) \ds, \\
+    \pi_F(N_P, N_F, N_C) &= N_C \int_0^1 s^2 N_F \partial_2 f(N_P, s N_F) \ds \\
+    CS(N_P, N_F, N_C) &= N_C \int_0^1 s f(N_P, s N_F) \ds.
+\end{align*}
+
+There are a number of things to note here.
+First, and most importantly, the consumers' share from total surplus is equal to the platform's.\footnote{
+    This is a consequence of the fact that the total surplus function is linear in the number of consumers.
+}
+As a consequence, what's good for the platform is also optimal for the consumers.
+Therefore, letting the platform choose the number of its products maximizes consumer welfare, as well (but not necessarily total surplus).
+
+Second, the expression for the fringe profits has the same structure as in \cref{ass:profit_sharing}.
+Therefore, if we show that \cref{ass:single_crossing} holds, it in turn implies that all of the results in \cref{sec:results} apply here, as well.
+The following lemma establishes this result.
+\begin{lemma}
+    \label{lem:profit_assumptions_total_surplus}
+    $f(n_P, n_F)$ satisfies \cref{ass:single_crossing}.
+    Furthermore,
+    \begin{align*}
+        \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} < 0.
+    \end{align*}
+\end{lemma}
+
+With this proven, we can again rely on \cref{prop:aggregate_size_additive} to see that, in equilibrium, an increase in $N_P$ decreases $N_F$.
+Furthermore, this decrease is so large that total product variety, and thus total surplus (which in turn is equal to total profits) also decreases (\cref{fig:fringe_entry_eq_full_surplus_two_sided}).\footnote{
+    As long as the market is in the hybrid regime.
+    If $N_F^* = 0$, then an increase in $N_P$ mechanically increases total aggregate, and thus total surplus.
+}
+
+Nevertheless, there is an important distinction compared to the previous results.
+As before, platform profits are again increasing in $N_P$.
+However, in this case, it also implies that consumers' share is also increasing in this case (\cref{fig:profits_full_surplus_two_sided}).
+Therefore, consumers do prefer hybrid operation to the the platform being a pure marketplace.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                    ylabel={},
+                    xmin=0, xmax=1.5, % adjust these values as needed
+                    ymin=0, ymax=3.1, % adjust these values as needed
+                    axis lines=left,
+                    xtick={0, 1.5},
+                    legend pos=south east,
+                    width=\linewidth,
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=N_P]{\equilibriumFullSurplusTwoSided};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y=N_F]{\equilibriumFullSurplusTwoSided};
+                \addplot[color=black,mark=none,thick] table[x=N_P,y=A]{\equilibriumFullSurplusTwoSided};
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumFullSurplusTwoSided};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+
+                \legend{$N_P$, $N_F$, $A$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Platform product variety and number of fringe entrants}
+        \label{fig:fringe_entry_eq_full_surplus_two_sided}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                    ylabel={},
+                    xmin=0, xmax=1.5, % adjust these values as needed
+                    ymin=0, ymax=1.2, % adjust these values as needed
+                    axis lines=left,
+                    xtick={0, 0.6},
+                    legend pos=north west,
+                    width=\linewidth,
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=pi_P]{\equilibriumFullSurplusTwoSided};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y=pi_F]{\equilibriumFullSurplusTwoSided};
+                \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=pi_P]{\equilibriumFullSurplusTwoSided};
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumFullSurplusTwoSided};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+
+                \legend{$\pi_P$, $\pi_F$, $CS$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Platform and fringe profits}
+        \label{fig:profits_full_surplus_two_sided}
+    \end{subfigure}
+    \caption{Equilibrium outcomes in the case when the whole surplus is bargained over ($N_C = 0.6, V_P = 1, V_F = 1, I_F = 0.2$), and both consumers and fringe firms participate in the bargaining.
+As before, the platform's profits are increasing in $N_P$, while the fringe's profits are decreasing.
+On the other hand, consumer welfare is equal to platform profits, therefore it is increasing in $N_P$.
+The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode.}
+    \label{fig:equilibrium_full_surplus_two_sided}
+\end{figure}
+
 \section{Conclusion and future work}
@@
 
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}
-            \begin{axis}[
-                    xlabel={$N_P$},
-                    ylabel={},
-                    xmin=0, xmax=1.5, % adjust these values as needed
-                    ymin=0, ymax=3.1, % adjust these values as needed
-                    axis lines=left,
-                    xtick={0, 1.5},
-                    legend pos=south east,
-                    width=\linewidth,
-                ]
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=N_P]{\equilibriumFullSurplusTwoSided};
-                \addplot[color=myred,mark=none,thick] table[x=N_P,y=N_F]{\equilibriumFullSurplusTwoSided};
-                \addplot[color=black,mark=none,thick] table[x=N_P,y=A]{\equilibriumFullSurplusTwoSided};
-
-                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumFullSurplusTwoSided};
-                \addplot[draw=none,name path=bottom] {0};
-                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
-
-                \legend{$N_P$, $N_F$, $A$}
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Platform product variety and number of fringe entrants}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}
-            \begin{axis}[
-                    xlabel={$N_P$},
-                    ylabel={},
-                    xmin=0, xmax=1.5, % adjust these values as needed
-                    ymin=0, ymax=1.2, % adjust these values as needed
-                    axis lines=left,
-                    xtick={0, 0.6},
-                    legend pos=north west,
-                    width=\linewidth,
-                ]
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=pi_P]{\equilibriumFullSurplusTwoSided};
-                \addplot[color=myred,mark=none,thick] table[x=N_P,y=pi_F]{\equilibriumFullSurplusTwoSided};
-                \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=pi_P]{\equilibriumFullSurplusTwoSided};
-
-                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumFullSurplusTwoSided};
-                \addplot[draw=none,name path=bottom] {0};
-                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
-
-                \legend{$\pi_P$, $\pi_F$, $CS$}
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Platform and fringe profits}
-    \end{subfigure}
-    \caption{Equilibrium outcomes in the case when the whole surplus is bargained over ($N_C = 0.6, V_P = 1, V_F = 1, I_F = 0.2$), and both consumers and fringe firms participate in the bargaining.
-As before, the platform's profits are increasing in $N_P$, while the fringe's profits are decreasing.
-On the other hand, consumer welfare is equal to platform profits, therefore it is increasing in $N_P$.
-The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode.}
-    \label{fig:equilibrium_full_surplus_two_sided}
-\end{figure}
-
 \section{Proofs and additional lemmas}

### 2024-01-12 src/paper/application.tex
Update extension in appendix

@@
 
-As an extension, I also examine what happens when the platform and the fringe firms have unequal bargaining weights, while still retaining more structure than the very general bargaining rule from \cref{ass:profit_sharing}.
-In particular, I look at the case of bargaining outcomes being describet by weighted values, with all fringe players sharing the same weight.
-Furthermore, I also consider the case of two-sided bargaining, where the consumers also participate in the negotiation over the value produced.
+As an extension, in \cref{sec:lower_bargaining_power} I also examine what happens when the platform and the fringe firms have unequal bargaining weights, while still retaining more structure than the very general bargaining rule from \cref{ass:profit_sharing}.
+In particular, I look at the case of bargaining outcomes being described by weighted values, with all fringe players sharing the same weight.
+Furthermore, in \cref{sec:two_sided}, I also consider the case of two-sided bargaining, where the consumers also participate in the negotiation over the value produced.
+Finally, \cref{sec:total_welfare_one_sided} explores the case of the platform being able to extract all of the consumer surplus through from consumers.
 
@@
 This last property makes the optimal prices and profits of the producers very simple, as shown in the next proposition.
-% \begin{align}
-%     \pi^v_{Ti} = ( p_{Ti} - c_T ) \frac{\exp\left( \frac{v_T - p_{Ti}}{\mu} \right)}{A}.
-%     \label{eq:variable_profit}
-% \end{align}
 \begin{proposition}
@@
 
-% For fringe firms, their total profit (including the investment cost $I_F$ and the entry fee $F_F$) is given by
-% \begin{align}
-%     \pi^{t*}_F = \mu \frac{\exp \left( \frac{v_F - c_F - \mu}{\mu} \right)}{A} - I_F - F_F.
-%     \label{eq:fringe_profit}
-% \end{align}
 For ease of notation, let us define the following:
@@
 Second, the expression for the fringe profits has the same structure as in \cref{ass:profit_sharing}.
-Therefore, if we show that \cref{ass:single_crossing} holds, it in turn implies that all of the results in \cref{sec:results} apply here, as well.
+Therefore, if we show that \cref{ass:single_crossing} holds, it in turn implies that all of the results in \cref{sec:example} apply here, as well.
 The following lemma establishes this result.
 \begin{lemma}
-    \label{lem:profit_assumptions_total_surplus}
+    \label{lem:profit_assumptions_two_sided}
     $f(n_P, n_F)$ satisfies \cref{ass:single_crossing}.
@@
 
-\section{Extensions}
-\label{sec:extensions}
-
-In this section, I look at a number of extensions of the model presented in \cref{sec:example}.
-The common theme of these extensions is that the consumer surplus is also included in the sum that is bargained over.
+\section{Two-sided bargaining over the full surplus}
+\label{sec:total_welfare_one_sided}
+
+In this section, I look at what happens if the paltform and the firms bargain over the total surplus, instead of just their total profits.
 That is, $\Pi(N_P, N_F, N_C)$ now represents total surplus.
-
-First, \cref{sec:total_welfare} looks at the case when consumer can be extracted by the platform, but consumers are still passive, and the bargaining is between the platform and the fringe.
-Then, \cref{sec:two_sided} explores what happens when all three sides engage in the negotiation over the same total surplus.
-I will only consider the bargaining outcomes under assumptions \cref{ass:profit_sharing} and \cref{ass:profit_sharing_two_sided}, respectively, and do not look at a benchmark with unilateraly set entry fees for the fringe.
-
-\subsection{Platform can extract consumer surplus}
-\label{sec:total_welfare}
-
-In this section, I assume that the platform can extract consumer surplus by charging a flat entry fee $F_C$.
-As consumers are identical, and the platform can set any entry fee, this implies that the platform can extract all consumer surplus in this case.\footnote{
-    Note, that I still assume that all $N_C$ consumers are present on the market by default, they do not have to pay any cost that would be analogous to the entry fee ($I_F$) of the fringe firms.
-    Therefore, they enter the market if and only if they are expected to have non-negative utility, which in turn means that the platform sets the entry fee to be equal to the consumer surplus.
-}
-
-Let us start by deriving total profits (which, in this case is the total surplus) as a function of $N_P, N_F$ and $N_C$.
-Under the logit-like demand structure described in \cref{sec:example}, the total surplus is given by
-\begin{proposition}
-    \label{prop:profits_total_surplus}
-    If the platform can extract consumer surplus, then the total profits that the platform and the fringe firms can achieve are given by
+One way to motivate this is to assume that the platform can extract consumer surplus by charging a flat entry fee $F_C$.
+As consumers are identical, and the platform can set any entry fee, this implies that the platform can extract all consumer surplus in this case.
+I will only consider the bargaining outcomes under assumptions \cref{ass:profit_sharing}, and do not look at a benchmark with unilateraly set entry fees for the fringe.
+
+As shown in \cref{prop:profits_total_surplus}, total surplus (which in case is also total profits) is given by
 \begin{align*}
@@
 \end{align*}
-\end{proposition}
-\begin{proof}[Proof of \cref{prop:profits_total_surplus}]
-    \textcite{small1981applied} show that the total surplus in a logit demand system is given by this expression.
-    As total consumer surplus is zero, the total profits are equal to the total surplus.
-\end{proof}
-Note, that this expression is of the form $\Pi(N_C, N_P, N_F) = N_C f(N_P, N_F)$.
-Furthermore, $f(N_P, N_F) = g(V_P N_P + V_F N_F)$ for an increasing, strictly concave $g$.
-
-Therefore, if we show that \cref{ass:single_crossing} holds, it in turn implies that all of the results in \cref{sec:results} apply here, as well.
-The following lemma establishes this result.
+
+The following lemma establishes that \cref{ass:single_crossing} is satisfied for this profit function as well, assuming two-sided bargaining with $\lambda_P = 1$ ($w_P(s) \equiv 1, w_F(s) = s$).
 \begin{lemma}
@@
 
-The difference is that, due to the platform appropriating all the consumer surplus, it does not hurt consumer welfare -- it is zero regardless of $N_P$.
+The difference is that, due to the platform appropriating all the consumer surplus, such an increase does not hurt consumer welfare -- it is zero regardless of $N_P$.
 Coupled with the fact that fringe firms also make zero profits in equilibrium, this means that the outcome is not so negative, after all.
@@
 Nevertheless, if it were to make it for some reason, it would not have the negative consequences that it had in \cref{sec:example}.
-
-\subsection{Consumers also engage in bargaining}
-\label{sec:two_sided}
 

### 2024-01-12 src/paper/application.tex
Fix some references

@@
 If there are $N_F$ fringe entrants along with $N_P$ platform products and $N_C$ consumers, then, as discussed previously, the total value they create together is given by $\Pi(N_P, N_F, N_C) = N_C f(N_P, N_F)$.
-Finally, the platform and the entrants share this profit according to the profit sharing rule from \cref{ass:profit_sharing} or \cref{ass:profit_sharing_two_sided}, and the fringe gets $\pi_F(N_P, N_F, N_C)$.
+Finally, the platform and the entrants share this profit according to the profit sharing rule from \cref{ass:profit_sharing}, and the fringe gets $\pi_F(N_P, N_F, N_C)$.
 
@@
     \begin{itemize}
-        \item Profits are shared according to \cref{ass:profit_sharing} (one-sided bargaining) or \cref{ass:profit_sharing_two_sided} (two-sided bargaining).
+        \item Profits are shared according to \cref{ass:profit_sharing}.
         \item Entrants make zero profits after accounting for entry costs: $\pi_F(N_P, N_F) = I_F(N_F)$.
@@
 \subsection{Consumers also participate in bargaining}
+\label{sec:two_sided}
 
@@
 
-In this section, I describe how the profit sharing rule from \cref{sec:profit_sharing} can be derived from various cooperative games.
+In this section, I describe how the profit sharing rule from \cref{ass:profit_sharing} can be derived from various cooperative games.
 In each of the following subsections, I formally define a cooperative game that models the platform setting, and derive the (weighted) Shapley values of the various players.
-I show that they correspond to the formulas given in \cref{sec:profit_sharing}, with a specific choice of weight functions $w_P$ and $w_F$ for each case.
+I show that they correspond to the formulas given in \cref{ass:profit_sharing}, with a specific choice of weight functions $w_P$ and $w_F$ for each case.
 

### 2024-01-12 src/paper/application.tex
Rewrite conclusions

@@
 
-This paper has introduced a new model of hybrid platforms in which bargaining between the platform and the entrant firms plays a key role.
-It has been demonstrated that platforms operating in hybrid mode can have serious consequences in such an environment.
-In particular, when a platform has a large number of its own products, then its bargaining power is also higher compared to the fringe entrants.
-This, in certain situations, such as the one described in this paper, this can lead to fewer fringe firms entering the market, reduced product variety, and ultimately, lower consumer welfare.
-
-In addition to the specific platform model, this paper also provides a simple, tractable, yet quite general framework in which one can study the effects of bargaining between one large and a continuum of small players.
-Such environments might, in addition to platforms, include upstream-downstream settings with one upstream supplier, or franchises with one franchisor and a continuum of franchisees, or wage bargaining.
-The quite general results of this paper give some intuition on what happens in such settings, without needing to delve into the details of a specific model.
-This also highlights certain similarities between those markets.
+This paper introduces a new model of hybrid platforms in which bargaining between the platform and the entrant firms plays a key role.
+It highlights the importance of a so far overlooked aspect of platforms having their own products: the fact that it increases their bargaining power compared to other players'.
+As a result, even in the absence of other frictions, hybrid platforms might have detrimental effects on fringe entry.
+This, in certain situations, such as the one described in this paper, this can lead to fewer fringe reduced product variety, and ultimately, lower consumer welfare.
+
+The contributions of this paper can be broken down into two categories.
+First, a simple, but quite general model of bargaining between one indispensable player and a continuum of potential market entrants is introduced.
+This model is applicable beyond the platform setting, and can describe other markets, such as upstream-downstream relations, or franchising, as well.
+The quite general results obtained from this model also highlight the similarities between those markets.
 Furthermore, many of the results from this paper can be applied in a plug-and-play fashion to other models of large-player-small-player interactions.
 
+The second set of contributions pertains to applying the aforementioned model to a setting with a hybrid platform.
+The demand structure is similar to the one in \textcite{anderson2021hybrid}, and the results convey the same general message: hybrid platforms can have detrimental welfare effects.
+However, the mechanism behind this result is quite different.
+This paper relies on the change in bargaing power, and shows that even in the case of lump-sum entry fees, hybrid platforms can be problematic from a welfare perspective.
+An extension of the main model also highlight the importance of the assumptions on who is participating in the bargaining process.
+
 There is a number of avenues for future research in this direction.
-First, I suspect that many of the assumptions made in section \cref{sec:example} can be relaxed, and one can still obtain similar results.
-An additional step I am planning to take is to endogenize the number of the platform's products, and the parameters of the profit sharing (bargaining rule).
-The latter would provide important insights into what kind of demand structures might lead to the evolution of hybrid platforms.
-
-I also hope that others will find this framework useful in their own research, and incorporate it in more complex and more applied models.
-In general, I believe this approach for modeling bargaining is a rather good compromise between assuming that one party has all the bargaining power, and modeling the bargaining process in detail, and might be a good fit for a number of different economic applications.
+First, although the results provide some suggestions about what endogenizing the number of the platform's products might entail, a more formal analysis is needed for a more complete picture.
+Second, applying the same bargaining framework, but using a different demand structure (e.g.
+CES utility) for microfounding the profit functions would have important implications for the robustness of the results.
+Finally, I believe this approach for modeling bargaining is a rather good compromise between assuming that one party has all the bargaining power, and modeling the bargaining process in detail, and some of the main ideas in this paper might be a good fit for different settings and and more applied models.
 

### 2024-01-12 src/paper/application.tex
Improve intro

@@
 \begin{abstract}
-    This paper explores the effects of a platform selling their own products in addition to acting as intermediaries (hybrid platforms) in a setting when bargaining takes place between the platform and the potential entrants.
+    This paper explores the effects of a platform selling their own products in addition to acting as intermediaries (hybrid platform) in a setting when bargaining takes place between the platform and the potential entrants.
     It highlights a so-far underappreciated aspect of hybrid platforms: having their own products increases their bargaining power over the other sellers.
@@
 
-Even though the economics literature offers no unambiguous definition for what platforms are, there seems to be a consensus that they are of key importance for the modern economy, and are getting even more so in the future.
 Although market structures resembling various aspects of what we call platforms have existed for some time, the term has only gained widespread usage in the 2000s, with the advent of digitization, and a number of behemoth technology companies playing matchmakers on the internet.
 Since then, platforms have become a buzzword in the business world, the subject of increasing regulatory scrutiny, and also a topic of intense academic interest.
-
 Platforms have a number of unique features that make them different from more traditional market structures.
@@
 \textcite[]{gutierrez2021welfare} shows that general conclusions are hard to draw, and welfare effects are platform and product specific.
+For example, using a mechanism design approach, \textcite{kang2022contracting} demonstrate that welfare consequences greatly depend on whether the platform faces competition in the upstream market.
 
@@
 \Cref{sec:example} concretizes the model by assuming a specific demand system, and also presents a corresponding benchmark model without bargaining.
+\Cref{sec:extensions} then examines the effect of different assumptions about the bargaining process.
 Finally, \cref{sec:conclusion} summarizes the results and discusses possible future work.
@@
 \section{Extensions}
+\label{sec:extensions}
 

### 2024-01-12 src/paper/application.tex
Expand intro

@@
 In particular, I propose an analytically tractable framework which captures many important aspects of bargaining between one large and a continuum of small players, and apply it to the setting of a hybrid platform facing a continuum of potential entrants.
-The results show that, in the presence of bargaining, hybrid operation can indeed have negative welfare consequences for consumers.
+The framework quite general, and does not depend on a specific demand structure, investment cost assumptions, and there is even some flexibility to the assumptions about bargaining outcomes.
+Nevertheless, even in this stylized setting, I can highlight certain factors which might cause a platform's hybrid operation to potentially have negative effects. 
+In particular, when the platform's and the potential entrants' products are substitutes, increasing the platform's product variety will lead to a decrease in the number of entrants.
+Under slightly more restrictive assumptions about the functional form of the profit functions, I show that this decrease in entry is so large as to cause a decrease in total profits, as well.
+Due to the generality of this model, these results are applicable not only to hybrid platform, but to other similar settings, such as upstream producers having their own downstream outlets, or retailers with private labels, as well.
+
+As a more specific example, I also examine this phenomenon in a more fully specified model, too.
+In particular, I provide some sharper results under the assumption of logit-like demand and a specific form of the bargaiing rule.
+I show that, in the presence of bargaining, hybrid operation can indeed have negative welfare consequences for consumers.
 This result is particularly striking in this otherwise distortion-free\footnote{
@@
 } setting. 
-The intuition is that hybrid operation increases the platform's bargaining power against the sntrant sellers.
+The intuition is that hybrid operation increases the platform's bargaining power against the entrant sellers.
 This in turn leads to a higher entry fee, fewer entrants, then results in lower consumer surplus.
@@
 
-The closest paper to this one is \textcite{anderson2021hybrid}, which utilizes a similar model and reaches similar conclusions, although through a different mechanism.
-I adapt many of the main features of their model with a couple of crucial differences.
-Instead of the platform setting a percentage entry fee and being able to commit to it, I assume that (1) platforms charge a lump-sum entry fee and that (2) this entry fee is the result of a negotiation process\footnote{
+The closest paper to this second, more applied part of this one is \textcite{anderson2021hybrid}.
+The main difference between the two boils down to how the entry fee is decided.
+In the former, of the platform setting a percentage entry fee and being able to commit to it, I assume that (1) platforms charge a lump-sum entry fee and that (2) this entry fee is the result of a negotiation process\footnote{
     The bargaining process is modeled using a solution concept from cooperative game theory, namely the Shapley-value.
@@
 
-This paper is also related to various other strands of the industrial organization literature.
-For one, it belongs to the research agenda on understanding platforms and their role in the economy \parencite[e.g.][]{rochet2003platform,hagiu2004optimal,armstrong2006competition,evans2011platform,lee2014competing}.
-Furthermore, it is somewhat adjacent to the literature on the importance of exclusive content \parencite[e.g.][]{hagiu2011exclusivity,lee2013vertical,dou2014sell,weeds2016tv}, with the difference that instead of exclusive content giving an advantage against competing platforms, in this paper, own products provide an advantage over entrants.
-More generally, many results and concepts of this paper are also applicable outside the context of (multi-sided) platforms.
+The first set of results in this paper go beyond the aforementined studies in the sense that they illuminate the effects of hybridness as a more abstract phenomenon, and thus also highlight the similarities between the hybrid platform literature and adjacent ones.
 Certain structures, such as vertical relationships, or even traditional retail stores share a number of features with platforms (notably, the presence of a dominant, indispensable entity), and can be modeled in much the same way.
@@
 \textcite{de2005vertical} and \textcite{montez2007downstream}, in which bargaining between the upstream and downstream firms take the center stage, are particularly closely related.
+Among empirical studies in related settings, \textcite{ho2017insurer} looks at the effect of insurer competition on health care prices, while \textcite{crawford2018welfare} explores the effects of vertical integration on television markets.
+
+This paper is also related to various other strands of the industrial organization literature.
+For one, it belongs to the research agenda on understanding platforms and their role in the economy \parencite[e.g.][]{rochet2003platform,hagiu2004optimal,armstrong2006competition,evans2011platform,lee2014competing}.
+Furthermore, it is somewhat adjacent to the literature on the importance of exclusive content \parencite[e.g.][]{hagiu2011exclusivity,lee2013vertical,dou2014sell,weeds2016tv}, with the difference that instead of exclusive content giving an advantage against competing platforms, in this paper, own products provide an advantage over potential entrants.
+More generally, many results and concepts of this paper are also applicable outside the context of (multi-sided) platforms.
 

### 2024-01-30 src/paper/theory.tex
Improve structure

@@
     On one hand, this paper provides a taxonomy of the various results found in some applied papers.
-    Furthermore, it introduces some new results pertaining to the case when participants have different levels of innate bargaining power, and weighted values are more appropriate.
-    The results in this paper is intended to be used as a tool-kit for embedding bargaining outcomes into more complex models.
+    Furthermore, it introduces some new results pertaining to the case of multiple types of fringe players.
+    The utility of this approach is demonstrated via a simple model of two-sided markets.
+    The results in this paper are intended to be used as a tool-kit for embedding bargaining outcomes into more complex models.
 \end{abstract}
@@
 This in turn allows me to go beyond the usual Shapley-value, and obtain results for a more general set of solution concepts: random order values.
-A specific example of those, for which I provide a number of new results, is the weighted value \parencite{shapley1953additive}.
-Additionally, due to more structure in the model, I am able to provide more concrete results, investigate some comparative statics, as well.
+In the case of multiple types of fringe players, I also present a number of new results for the Shapley value and the weighted value.
+In particular, I derive the value of the different types of fringe players in the multi-sided setting, and demonstrate how they are related to their marginal contributions.
+Additionally, due to having more structure in the model, I am able to provide more concrete results, investigate some comparative statics, as well.
 
 Despite their theoretical appeal and their tractability, oceanic games saw very little use in the industrial organization, and, more generally, applied economics literature.
-The two most prominent examples are \textcite{stole1996intra, stole1996organizational} and \textcite{levy1997individual}, all of which use the Shapley-value to model wage bargaining, and consider the case of divisible labor (continuum of workers).
+The most prominent examples are \textcite{stole1996intra, stole1996organizational} and \textcite{levy1997individual}, all of which use the Shapley-value to model wage bargaining, and consider the case of divisible labor (continuum of workers).
 The first two of these paper also provides microfoundations for the Shapley value and the weighted value in the intra-firm bargaining setting.
+To showcase the utility of this approach, I also build a simple model of two-sided markets.
+In addition to the aformentioned papers, this model includes two new features: (1) results about the distribution of the value between the various types of fringe players, and (2) using the weighted value in a multi-sided setting.
 
@@
 Such a model applies to all the settings mentioned above, such as intra-firm bargaining, vertical supply chains, or multi-sided markets.
-I demonstrate that the Shapley values of the players in those models are described by very tractable expressions that have nice geometric interpretations.
+I demonstrate that the random order values of the players in those models are described by very tractable expressions that have nice geometric interpretations.
 Additionally, the outcomes are in line with one's intuitive expectations of bargaining power in such situations.
-Finally, I demonstrate the usefulness of this approach by building a simple model of TODO.
+Finally, I demonstrate the usefulness of this approach by building a simple model of two-sided markets, where the various players' shares are determined by their (weighted) Shapley values.
 
@@
 In this section I examine the case of identical fringe players.
-I will first look at the simplest setting (one large player, which is completely indispensable), but in the subsequent sections I will somewhat relax this assumption.
+Many of these results are known in the literature, but I include them here to build intuition, and highlight the similarities with the multi-sided case.
+I will first look at the simplest setting (one large player, which is completely indispensable), but in \ref{sec:extensions} I will somewhat relax this assumption.
 Let us start by defining the cooperative game that describes this situation.
@@
 \end{corollary}
-
-\subsection{Shapley value with multiple big players}
-
-Now imagine that, instead of just one, there are $m$ players of type $P$, and they are perfect substitutes of each other.
-That is, the fringe players still need one at least of them to achieve any value, but it does not matter which and how many of them are present.
-Formally, the value function for coalition $S$ becomes the following:
-\begin{align*}
-    v(S) = \begin{cases}
-        0                              & \text{if } n_P(S) = 0 \\
-        f\left(\frac{n_A(S)}{n}\right) & \text{otherwise}.
-    \end{cases}
-\end{align*}
-
-Let us start by establishing monotonicity for this version of the model, too.
-\begin{proposition}
-    The game is monotone if $f$ is increasing and $f(0) \geq 0$.
-\end{proposition}
-On the other hand, superadditivity is not as simple in this case, as before.
-For example, when $f$ is concave, then $m$ coalitions with one platform each and the fringe divided equally amongst them clearly achieve a higher total payoff than the grand coalition.
-Therefore, the results of this section are most applicable to settings when multiple coalitions cannot be formed at the same time for some reason.
-For example, \textcite{hart1996bargaining} propose an interpretation when there is a single, indivisible, non-replicable resource or technology (not captured in the value function) necessary to produce any value.
-
-As before, the main proposition in this section provides us with an expression of the limit of the value for this variant of the game.
-Notably, as in the case of the weighted value, the share of player $P$ can again be expressed as an integral of $f$ and some weighting\footnote{
-    Weighting is not a completely precise term, as $h(t)$ does not integrate to one, and is therefore not a probability distribution in this case (\cref{fig:multiple_platforms}).
-} function $h(t)$, with the latter depending only on the number of big players.
-\begin{proposition}
-    \label{prop:multiple_platforms}
-    The limit of the Shapley-value (as $n \to \infty$) of each player of type $P$ is
-    \begin{align*}
-        \varphi_{P_i}^{\infty, m} = \int_0^1 h(t) f(t) \dt,
-    \end{align*}
-    where $h(t) = (1-t) ^ {m-1}$.
-\end{proposition}
-
-As with proposition \ref{prop:one_sided}, this result also has a probabilistic interpretation.
-Let the location of the $m$ atoms be $t_1, \dots, t_m$, distributed independently and uniformly on the unit interval.
-The expected marginal contribution of $t_i$ is only positive whenever it is the first amongst the major players.
-That is, for any $t_i$, the probability if $P_i$ being the first is related to the cdf of the first order statistic from $n-1$ independent uniform distributions: $1 - (1-t)^{m-1}$.
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.8]
-            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.1, samples at={0, 0.02, 0.04, ..., 0.98, 1},
-                xtick={0, 1}, ytick={0, 1}, axis lines=left, xlabel={$t$}, legend pos=north west]
-                \addplot[thick] {1};
-                \addplot[thick, dashed] {1-x};
-                \addplot[thick, dotted] {(1-x)^2};
-            \end{axis}
-        \end{tikzpicture}
-        \caption{$h(t)$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.8]
-            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.1, samples at={0, 0.02, ..., 0.98, 1},
-                xtick={0, 1}, ytick={0, 1}, axis lines=left, xlabel={$t$}, legend pos=north west]
-                \addplot[thick] {x};
-                \addplot[thick, dashed] {x - x^2/2};
-                \addplot[thick, dotted] {x - x^2 + x^3/3};
-                \legend{$m = 1$, $m = 2$, $m = 3$}
-            \end{axis}
-        \end{tikzpicture}
-        \caption{$\int_0^t h(s) \ds$}
-    \end{subfigure}
-    \caption{Illustration of the weighting function for various values of $m$ in the multiple big player case -- individual big player.}
-    \label{fig:multiple_platforms}
-\end{figure}
-
-Let us examine the total value of all the big players.
-Denote the aggregated value of players of type $P$ as $\varphi_{P}^{\infty, m} \coloneqq \sum_{j=1}^m\varphi_{P_j}^{\infty, m} = m\varphi_{P_i}^{\infty, m}$.
-It immediately follows from the previous proposition that
-\begin{align*}
-    \varphi_{P}^{\infty, m} = \int_0^1 g(t) f(t) \dt,
-\end{align*}
-where $g(t) = m (1-t) ^ {m-1}$.
-Notice that $g(t)$ now integrates to one, and is thus a probability distribution (\cref{fig:multiple_platforms_total}).
-Therefore, the Shapley value in the case of multiple, substitutable big players can be interpreted as a random order value with a single big player.
-The probability distribution for the corresponding random order value has a specific form, and its only parameter is the number of big players.
-Thus, all the results from the previous section apply to this case as well.
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.8]
-            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=3.1, samples at={0, 0.02, 0.04, ..., 0.98, 1},
-                xtick={0, 1}, ytick={0, 1, 2, 3}, axis lines=left, xlabel={$t$}, legend pos=north west]
-                \addplot[thick] {1};
-                \addplot[thick, dashed] {2 * (1-x)};
-                \addplot[thick, dotted] {3 * ((1-x)^2)};
-            \end{axis}
-        \end{tikzpicture}
-        \caption{$g(t)$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.8]
-            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.1, samples at={0, 0.02, ..., 0.98, 1},
-                xtick={0, 1}, ytick={0, 1}, axis lines=left, xlabel={$t$}, legend pos=north west]
-                \addplot[thick] {x};
-                \addplot[thick, dashed] {2 * (x - x^2/2)};
-                \addplot[thick, dotted] {3 * (x - x^2 + x^3/3)};
-                \legend{$m = 1$, $m = 2$, $m = 3$}
-            \end{axis}
-        \end{tikzpicture}
-        \caption{$\int_0^t g(s) \ds$}
-    \end{subfigure}
-    \caption{Illustration of the weighting function for various values of $m$ in the multiple big player case -- total of big players.}
-    \label{fig:multiple_platforms_total}
-\end{figure}
-
-Now let us look at how the value of the big players and the fringe changes as a function of the number of the big players.
-Proposition \cref{cor:multiple_platforms_2} again confirms our intuition: more players means that they become more substitutable, and thus their bargaining power decreases.
-This not only means that the value of each individual big player decreases, but also that their total value goes down.
-
-\begin{corollary}
-    \label{cor:multiple_platforms_2}
-    Let $\varphi_{P}^{\infty, m} = m\varphi_{P_i}^{\infty, m}$ denote the aggregated values of players of type $P$.
-$\varphi_{P}^{\infty, m}$ is decreasing in $m$ and $\varphi_{A}^{\infty, m}$ is increasing in $m$ unless $f$ is constant.
-\end{corollary}
-
-Finally, let us show that the value of the fringe has a similar, marginal contribution-based interpretation as in the case of a single big player.
-
-\begin{corollary}
-    \label{cor:multiple_platforms}
-    The per-unit Shapley-value of the fringe is
-    \begin{align*}
-        \varphi_A^{\infty, m} = 1 - \int_0^1 f(t) \dG(t) = \int_0^1 G(t) f'(t) \dt ,
-    \end{align*}
-    where $G(t) = 1 - (1-t)^m$.
-\end{corollary}
-
-\subsection{Non-indispensable big player}
-
-As a final extension for the one-sided case, let us examine what happens when the big player is not indispensable.
-Assume that it provides some value to any coalition, but a coalition of fringe players can achieve a positive value without it.
-Formally, the value function is the following:
-\begin{align*}
-    v(S) = \begin{cases}
-        f_0\left(\frac{n_A(S)}{n}\right) & P \notin S \\
-        f\left(\frac{n_A(S)}{n}\right)   & \text{otherwise}.
-    \end{cases}
-\end{align*}
-
-As in the case of multiple big players, monotonicity is straightforward to establish.
-\begin{proposition}
-    The game is monotone if $f$ is increasing and $f(t) \geq f_0(t) \geq 0 \forall t$.
-\end{proposition}
-Also similarly, superadditivity is not straightforward in general.
-Therefore, the simultaneous formation of multiple coalitions must be excluded in this setting as well.
-
-On the other hand, the random order values and their limits are very straightforward to characterize.
-The value of the big player is still its average marginal contribution.
-The only difference is that this marginal contribution (conditional on $s$ share of the fringe coming before $P$) is not simply $f(s)$, but rather $f(s) - f_0(s)$.
-This is because the big player is not indispensable, and thus the fringe can achieve some value without it.
-
-\begin{proposition}
-    \label{prop:one_sided_non_indispensable}
-    Let $f$ be continuous on [0, 1].
-Furthermore, let us denote the random variable $\frac{|\mathcal{P}_P|}{n}$ as $X_n$.
-Assume that $X_n \xrightarrow[]{d} X$ with cdf $G_X(t)$ and (if exists) pdf $g(t)$.
-    Then
-    \begin{align*}
-        \varphi_P^\infty = \lim_{n \to \infty} \varphi_P^n = \int_0^1 f(t) \dG(t) = \int_0^1 g(t) [f(t) - f_0(t)] \dt,
-    \end{align*}
-    with the last equality holding if $X$ is a continuous random variable.
-\end{proposition}
-
-The value of the fringe is also similar to the baseline case, except now fringe players have a non-zero marginal contribution even when $P$ is not present.
-Therefore, there is an additional term in the integral, corresponding to the marginal value of the fringe when $P$ is not present.
-
-\begin{corollary}
-    \label{cor:fringe_value_non_indispensable}
-    The aggregated value of the fringe is
-    \begin{align*}
-        \varphi_A^\infty = f(1) - \int_0^1 f(t) - f_0(t) \dG(t).
-    \end{align*}
-    Furthermore, if $f$ and $f_0$ are differentiable on $[0, 1]$, then the value of the fringe can also be expressed as
-    \begin{align*}
-        \varphi_A^\infty = \int_0^1 G(t) f'(t) + (1 - G(t)) f'_0(t) \dt.
-    \end{align*}
-\end{corollary}
-
-It is clear that the value of the big player is decreasing in $f_0$ (\cref{fig:non_indispensable}).
-Consequently, the value of the fringe is increasing in $f_0$, which is essentially its outside option (what it can achieve without the big player).
-This is a natural result, and again, it is in line with what one would expect from bargaining theory.
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.8]
-            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-                    xtick={0, 1}, ytick={0}, xlabel={$s$}]
-                \addplot[name path=f, thick] {x^0.5};
-                \addplot[name path=f0, thick] {0.3 * x^0.5};
-                \node[anchor=north west] at (axis cs: .8, .8^0.5) {$f$};
-                \node[anchor=south west] at (axis cs: .8, .3*.8^0.5) {$f_0$};
-                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
-                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);
-
-                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and f0];
-                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
-                \addplot [fill=red, fill opacity=0.05] fill between [of=f0 and bottom];
-
-                \node[anchor=north west, align=left] at (axis cs: .05, .95) {$\varphi_A^\infty$};
-                \node[anchor=south east, align=left] at (axis cs: .95, .05) {$\varphi_A^\infty$};
-                \node[anchor=north west, align=right] at (axis cs: .5, .5) {$\varphi_P^\infty$};
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Fringe can achieve relatively little without $P$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.8]
-            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-                    xtick={0, 1}, ytick={0}, xlabel={$s$}]
-                \addplot[name path=f, thick] {x^0.5};
-                \addplot[name path=f0, thick] {0.7 * x^0.5};
-                \node[anchor=north west] at (axis cs: .8, .8^0.5) {$f$};
-                \node[anchor=north west] at (axis cs: .8, .7*.8^0.5) {$f_0$};
-                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
-                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);
-
-                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and f0];
-                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
-                \addplot [fill=red, fill opacity=0.05] fill between [of=f0 and bottom];
-
-                \node[anchor=north west, align=left] at (axis cs: .05, .95) {$\varphi_A^\infty$};
-                \node[anchor=south east, align=left] at (axis cs: .95, .05) {$\varphi_A^\infty$};
-                \node[anchor=north west, align=right] at (axis cs: .5, .7) {$\varphi_P^\infty$};
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Fringe can achieve relatively more without $P$}
-    \end{subfigure}
-    \caption{Distribution of value between player $P$ (blue) and the fringe (red)}
-    \label{fig:non_indispensable}
-\end{figure}
 
@@
 The proposed profit sharing framework could be embedded in more realistic models of various settings.
-The example application in this paper is a small example of that, while \textcite{stancsics2023hybrid} provides a more detailed model involving hybrid platforms.
+The example application in this paper is a streamlined example of this, while \textcite{stancsics2023hybrid} provides a more detailed model involving hybrid platforms.
 Due to the simplicity of the results, this approach might be a viable replacement of unilateral price setting in cases where one does not wish to ascribe all the bargaining power to one player.
@@
 \printbibliography
+
+\section{Non-indispensable big player(s)}
+\label{sec:extensions}
+
+This section demonstrates two ways in which the model can be extended to include non-indispensable big players, while retaining the essential structure and the tractability of the results.
+In the first case, there are a number of big players, which are perfect substitutes of each other.
+In the second case, there is a single big player, the fringe is able to generate some value on its own, and the big player is only needed to generate the rest.
+In both cases, the value function is still a random order value, and thus results from the main text can be applied.
+
+\subsection{Shapley value with multiple big players}
+
+Now imagine that, instead of just one, there are $m$ players of type $P$, and they are perfect substitutes of each other.
+That is, the fringe players still need one at least of them to achieve any value, but it does not matter which and how many of them are present.
+Formally, the value function for coalition $S$ becomes the following:
+\begin{align*}
+    v(S) = \begin{cases}
+        0                              & \text{if } n_P(S) = 0 \\
+        f\left(\frac{n_A(S)}{n}\right) & \text{otherwise}.
+    \end{cases}
+\end{align*}
+
+Let us start by establishing monotonicity for this version of the model, too.
+\begin{proposition}
+    The game is monotone if $f$ is increasing and $f(0) \geq 0$.
+\end{proposition}
+On the other hand, superadditivity is not as simple in this case, as before.
+For example, when $f$ is concave, then $m$ coalitions with one platform each and the fringe divided equally amongst them clearly achieve a higher total payoff than the grand coalition.
+Therefore, the results of this section are most applicable to settings when multiple coalitions cannot be formed at the same time for some reason.
+For example, \textcite{hart1996bargaining} propose an interpretation when there is a single, indivisible, non-replicable resource or technology (not captured in the value function) necessary to produce any value.
+
+As before, the main proposition in this section provides us with an expression of the limit of the value for this variant of the game.
+Notably, as in the case of the weighted value, the share of player $P$ can again be expressed as an integral of $f$ and some weighting\footnote{
+    Weighting is not a completely precise term, as $h(t)$ does not integrate to one, and is therefore not a probability distribution in this case (\cref{fig:multiple_platforms}).
+} function $h(t)$, with the latter depending only on the number of big players.
+\begin{proposition}
+    \label{prop:multiple_platforms}
+    The limit of the Shapley-value (as $n \to \infty$) of each player of type $P$ is
+    \begin{align*}
+        \varphi_{P_i}^{\infty, m} = \int_0^1 h(t) f(t) \dt,
+    \end{align*}
+    where $h(t) = (1-t) ^ {m-1}$.
+\end{proposition}
+
+As with proposition \ref{prop:one_sided}, this result also has a probabilistic interpretation.
+Let the location of the $m$ atoms be $t_1, \dots, t_m$, distributed independently and uniformly on the unit interval.
+The expected marginal contribution of $t_i$ is only positive whenever it is the first amongst the major players.
+That is, for any $t_i$, the probability if $P_i$ being the first is related to the cdf of the first order statistic from $n-1$ independent uniform distributions: $1 - (1-t)^{m-1}$.
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.1, samples at={0, 0.02, 0.04, ..., 0.98, 1},
+                xtick={0, 1}, ytick={0, 1}, axis lines=left, xlabel={$t$}, legend pos=north west]
+                \addplot[thick] {1};
+                \addplot[thick, dashed] {1-x};
+                \addplot[thick, dotted] {(1-x)^2};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{$h(t)$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.1, samples at={0, 0.02, ..., 0.98, 1},
+                xtick={0, 1}, ytick={0, 1}, axis lines=left, xlabel={$t$}, legend pos=north west]
+                \addplot[thick] {x};
+                \addplot[thick, dashed] {x - x^2/2};
+                \addplot[thick, dotted] {x - x^2 + x^3/3};
+                \legend{$m = 1$, $m = 2$, $m = 3$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{$\int_0^t h(s) \ds$}
+    \end{subfigure}
+    \caption{Illustration of the weighting function for various values of $m$ in the multiple big player case -- individual big player.}
+    \label{fig:multiple_platforms}
+\end{figure}
+
+Let us examine the total value of all the big players.
+Denote the aggregated value of players of type $P$ as $\varphi_{P}^{\infty, m} \coloneqq \sum_{j=1}^m\varphi_{P_j}^{\infty, m} = m\varphi_{P_i}^{\infty, m}$.
+It immediately follows from the previous proposition that
+\begin{align*}
+    \varphi_{P}^{\infty, m} = \int_0^1 g(t) f(t) \dt,
+\end{align*}
+where $g(t) = m (1-t) ^ {m-1}$.
+Notice that $g(t)$ now integrates to one, and is thus a probability distribution (\cref{fig:multiple_platforms_total}).
+Therefore, the Shapley value in the case of multiple, substitutable big players can be interpreted as a random order value with a single big player.
+The probability distribution for the corresponding random order value has a specific form, and its only parameter is the number of big players.
+Thus, all the results from the previous section apply to this case as well.
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=3.1, samples at={0, 0.02, 0.04, ..., 0.98, 1},
+                xtick={0, 1}, ytick={0, 1, 2, 3}, axis lines=left, xlabel={$t$}, legend pos=north west]
+                \addplot[thick] {1};
+                \addplot[thick, dashed] {2 * (1-x)};
+                \addplot[thick, dotted] {3 * ((1-x)^2)};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{$g(t)$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.1, samples at={0, 0.02, ..., 0.98, 1},
+                xtick={0, 1}, ytick={0, 1}, axis lines=left, xlabel={$t$}, legend pos=north west]
+                \addplot[thick] {x};
+                \addplot[thick, dashed] {2 * (x - x^2/2)};
+                \addplot[thick, dotted] {3 * (x - x^2 + x^3/3)};
+                \legend{$m = 1$, $m = 2$, $m = 3$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{$\int_0^t g(s) \ds$}
+    \end{subfigure}
+    \caption{Illustration of the weighting function for various values of $m$ in the multiple big player case -- total of big players.}
+    \label{fig:multiple_platforms_total}
+\end{figure}
+
+Now let us look at how the value of the big players and the fringe changes as a function of the number of the big players.
+Proposition \cref{cor:multiple_platforms_2} again confirms our intuition: more players means that they become more substitutable, and thus their bargaining power decreases.
+This not only means that the value of each individual big player decreases, but also that their total value goes down.
+
+\begin{corollary}
+    \label{cor:multiple_platforms_2}
+    Let $\varphi_{P}^{\infty, m} = m\varphi_{P_i}^{\infty, m}$ denote the aggregated values of players of type $P$.
+$\varphi_{P}^{\infty, m}$ is decreasing in $m$ and $\varphi_{A}^{\infty, m}$ is increasing in $m$ unless $f$ is constant.
+\end{corollary}
+
+Finally, let us show that the value of the fringe has a similar, marginal contribution-based interpretation as in the case of a single big player.
+
+\begin{corollary}
+    \label{cor:multiple_platforms}
+    The per-unit Shapley-value of the fringe is
+    \begin{align*}
+        \varphi_A^{\infty, m} = 1 - \int_0^1 f(t) \dG(t) = \int_0^1 G(t) f'(t) \dt ,
+    \end{align*}
+    where $G(t) = 1 - (1-t)^m$.
+\end{corollary}
+
+\subsection{Non-indispensable big player}
+
+As a final extension for the one-sided case, let us examine what happens when the big player is not indispensable.
+Assume that it provides some value to any coalition, but a coalition of fringe players can achieve a positive value without it.
+Formally, the value function is the following:
+\begin{align*}
+    v(S) = \begin{cases}
+        f_0\left(\frac{n_A(S)}{n}\right) & P \notin S \\
+        f\left(\frac{n_A(S)}{n}\right)   & \text{otherwise}.
+    \end{cases}
+\end{align*}
+
+As in the case of multiple big players, monotonicity is straightforward to establish.
+\begin{proposition}
+    The game is monotone if $f$ is increasing and $f(t) \geq f_0(t) \geq 0 \forall t$.
+\end{proposition}
+Also similarly, superadditivity is not straightforward in general.
+Therefore, the simultaneous formation of multiple coalitions must be excluded in this setting as well.
+
+On the other hand, the random order values and their limits are very straightforward to characterize.
+The value of the big player is still its average marginal contribution.
+The only difference is that this marginal contribution (conditional on $s$ share of the fringe coming before $P$) is not simply $f(s)$, but rather $f(s) - f_0(s)$.
+This is because the big player is not indispensable, and thus the fringe can achieve some value without it.
+
+\begin{proposition}
+    \label{prop:one_sided_non_indispensable}
+    Let $f$ be continuous on [0, 1].
+Furthermore, let us denote the random variable $\frac{|\mathcal{P}_P|}{n}$ as $X_n$.
+Assume that $X_n \xrightarrow[]{d} X$ with cdf $G_X(t)$ and (if exists) pdf $g(t)$.
+    Then
+    \begin{align*}
+        \varphi_P^\infty = \lim_{n \to \infty} \varphi_P^n = \int_0^1 f(t) \dG(t) = \int_0^1 g(t) [f(t) - f_0(t)] \dt,
+    \end{align*}
+    with the last equality holding if $X$ is a continuous random variable.
+\end{proposition}
+
+The value of the fringe is also similar to the baseline case, except now fringe players have a non-zero marginal contribution even when $P$ is not present.
+Therefore, there is an additional term in the integral, corresponding to the marginal value of the fringe when $P$ is not present.
+
+\begin{corollary}
+    \label{cor:fringe_value_non_indispensable}
+    The aggregated value of the fringe is
+    \begin{align*}
+        \varphi_A^\infty = f(1) - \int_0^1 f(t) - f_0(t) \dG(t).
+    \end{align*}
+    Furthermore, if $f$ and $f_0$ are differentiable on $[0, 1]$, then the value of the fringe can also be expressed as
+    \begin{align*}
+        \varphi_A^\infty = \int_0^1 G(t) f'(t) + (1 - G(t)) f'_0(t) \dt.
+    \end{align*}
+\end{corollary}
+
+It is clear that the value of the big player is decreasing in $f_0$ (\cref{fig:non_indispensable}).
+Consequently, the value of the fringe is increasing in $f_0$, which is essentially its outside option (what it can achieve without the big player).
+This is a natural result, and again, it is in line with what one would expect from bargaining theory.
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
+                    xtick={0, 1}, ytick={0}, xlabel={$s$}]
+                \addplot[name path=f, thick] {x^0.5};
+                \addplot[name path=f0, thick] {0.3 * x^0.5};
+                \node[anchor=north west] at (axis cs: .8, .8^0.5) {$f$};
+                \node[anchor=south west] at (axis cs: .8, .3*.8^0.5) {$f_0$};
+                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);
+
+                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and f0];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=f0 and bottom];
+
+                \node[anchor=north west, align=left] at (axis cs: .05, .95) {$\varphi_A^\infty$};
+                \node[anchor=south east, align=left] at (axis cs: .95, .05) {$\varphi_A^\infty$};
+                \node[anchor=north west, align=right] at (axis cs: .5, .5) {$\varphi_P^\infty$};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Fringe can achieve relatively little without $P$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
+                    xtick={0, 1}, ytick={0}, xlabel={$s$}]
+                \addplot[name path=f, thick] {x^0.5};
+                \addplot[name path=f0, thick] {0.7 * x^0.5};
+                \node[anchor=north west] at (axis cs: .8, .8^0.5) {$f$};
+                \node[anchor=north west] at (axis cs: .8, .7*.8^0.5) {$f_0$};
+                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);
+
+                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and f0];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=f0 and bottom];
+
+                \node[anchor=north west, align=left] at (axis cs: .05, .95) {$\varphi_A^\infty$};
+                \node[anchor=south east, align=left] at (axis cs: .95, .05) {$\varphi_A^\infty$};
+                \node[anchor=north west, align=right] at (axis cs: .5, .7) {$\varphi_P^\infty$};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Fringe can achieve relatively more without $P$}
+    \end{subfigure}
+    \caption{Distribution of value between player $P$ (blue) and the fringe (red)}
+    \label{fig:non_indispensable}
+\end{figure}
 

### 2024-02-08 src/paper/theory.tex
More elegant proof for proposition 7

@@
 
+\newtheorem{theorem}{Theorem}
 \newtheorem{proposition}{Proposition}
@@
 
-\begin{proposition}
+\begin{theorem}
     \label{prop:many_sided_weighted}
@@
     \end{align*}
-\end{proposition}
+\end{theorem}
 
@@
     Consider the random vector $X_n$ with values from $[0, 1]^L$.
-    Let $S_n = \sum_l[X_n]_l / L$, with the cumulative distribution function $G_n(s)$.
-    Assume that for every $s \in [0, 1]$, $X_n \mid n S_n = \lfloor ns \rfloor \xrightarrow[]{L^1} h(s)$ where $h(s)$ is some continuous function.
-    Let $S_n \xrightarrow[]{d} S$.
+    Let $S$, be a random variable with support $[0, 1]$ and cumulative distribution function $G_n(s)$.
+    Assume that for every $s \in [0, 1]$, $X_n \mid S = s \xrightarrow[]{a.s.} h(s)$ where $h(s)$ is some continuous function.
     Then $X_n \xrightarrow[]{d} h(S)$.
@@
     \end{align*}
-    for any $x$ where the cdf of $h(S)$ is continuous.
-
-    Let us start by conditioning on $S_n$:
-    \begin{align*}
-        \Pr(X_n \leq x) = \int_0^1 \Pr(X_n \leq x \mid S_n = s) \dG_n(s).
+
+    First, note that
+
+    Let us start by conditioning on $S$:
+    \begin{align*}
+        \Pr(X_n \leq x) = \int_0^1 \Pr(X_n \leq x \mid S = s) \dG(s).
     \end{align*}
@@
     \begin{align*}
-        \lim_{n \to \infty} \left| \Pr(X_n \leq x) - \Pr(h(S) \leq x) \right| &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \dG_n(s) - \Pr(h(S) \leq x) \right| \\
-        &\leq \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \dG_n(s) - \Pr(h(S_n) \leq x) \right| \\
-        &+ \lim_{n \to \infty} \left| \Pr(h(S_n) \leq x) - \Pr(h(S) \leq x) \right|
+        \lim_{n \to \infty} \left| \Pr(X_n \leq x) - \Pr(h(S) \leq x) \right| &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S = s) \dG(s) - \Pr(h(S) \leq x)\right| \\
+        &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S = s) \dG(s) - \int_0^1 \mathbf{1}[h(s) \leq 1] \dG(s) \right| \\
+        &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S = s) - \mathbf{1}[h(s) \leq x] \dG(s) \right| \\
+        &\leq \lim_{n \to \infty} \int_0^1 \left| \Pr(X_n \leq x \mid S = s) - \mathbf{1}[h(s) \leq x] \right| \dG(s) \\
+        &= \int_0^1 \lim_{n \to \infty} \left| \Pr(X_n \leq x \mid S = s) - \mathbf{1}[h(s) \leq x] \right| \dG(s) \\
+        &= 0
     \end{align*}
     for all $x \in [0, 1]^L$.
-    I will show that both limits on the right-hand side are zero.
-
-    Let us start with the first term.
-    \begin{align*}
-        \lim_{n \to \infty} &\left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \dG_n(s) - \Pr(h(S_n) \leq x) \right| \\
-        &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \dG_n(s) - \int_0^1 \mathbf{1}[h(s) \leq s] \dG_n(s) \right| \\
-        &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) - \mathbf{1}[h(s) \leq x] \dG_n(s) \right| \\
-        &= \lim_{n \to \infty} \left| \int_0^1 \underbrace{\Pr(X_n \leq x \mid nS_n = \lfloor ns \rfloor) - \mathbf{1}[h(s) \leq x]}_{\coloneqq r(s)} \dG_n(s) \right| \\
-        &\leq \lim_{n \to \infty} \int_0^1 \left| \Pr(X_n \leq x \mid nS_n = \lfloor ns \rfloor) - \mathbf{1}[h(s) \leq x] \right| \dG(s) \\
-        &+ \lim_{n \to \infty} \left| \int_0^1 r(s) \dG_n(s) - \int_0^1 r(s) \dG(s) \right| \\
-        &= 0.
-    \end{align*}
-    The first limit is zero because $X_n \mid n S_n = \lfloor ns \rfloor \xrightarrow[]{L^1} h(s)$.
-    The second limit is zero because of the continuous mapping theorem, as $S_n \xrightarrow[]{p} S$ and $\Pr_S(s : r\text{ is not continuous at }s)= 0$.
-
-    All that remains is to show that the second term is also zero.
-    This simply follows from the continuous mapping theorem, as $f$ is continuous and $S_n \xrightarrow[]{d} S$.
+    The exchange of the limit and the integral is justified by the fact that the integrand is dominated by a constant function, and therefore the dominated convergence theorem applies.
+    The last equality follows from the fact that $X_n \mid S = s \xrightarrow[]{a.s.} h(s)$. 
 \end{proof}
@@
 
-    Let us first define the random variable $S_n = \sum_l[X_n]_l / L$, the total number of small players placed before $P$.
-    Also, define $h(s) = (s, \dots, s)$.
-    Now let us look at the conditional distribution $n X_n | n L S_n = k$.
-    As all permutations have equal probability, this is the same as picking $kL$ firms from the set $N \setminus \{P\}$ without replacement.
-    The numbers of each type in this sample will follow a multinomial distribution with $kL$ trials, $L$ events and probabilities $1/L$.
-
-    Let us now show that $\Pr(X_n < x \mid S_n = s) \xrightarrow[]{\mathrm{u}} \mathbf{1}[(s, \dots, s) \leq x]$ on $s \in \mathrm{supp}(S_n)$.
-
-    First, observe that
-    \begin{align*}
-        [\E(n X_n | nS_n = \lfloor ns \rfloor)]_l &= \lfloor ns \rfloor, \\
-        [\Var(n X_n | nS_n = \lfloor ns \rfloor)]_l &= \lfloor ns \rfloor \frac{L-1}{L}
-    \end{align*}
-    for all $\quad l = 1, \dots, L$.
-    Consequently,
-    \begin{align*}
-        [\E(X_n | nS_n = \lfloor ns \rfloor)]_l &= \frac{\lfloor ns \rfloor}{n}, \\
-        [\Var(X_n | nS_n = \lfloor ns \rfloor)]_l &= \frac{\lfloor ns \rfloor}{n^2} \frac{L-1}{L}
-    \end{align*}
-    for all $\quad l = 1, \dots, L$.
-
-    Notice that, as $n \to \infty$, $[\Var(X_n | nS_n = \lfloor ns \rfloor)]_l \to 0$.
-    Furthermore, $\E(X_n | nS_n = \lfloor ns \rfloor) \to h(s)$.
-    Thus, for any $s \in [0, 1], X_n | nS_n = \lfloor ns \rfloor \xrightarrow[]{L^2} h(s)$.
-
-    Let us now turn to the random variable $S_n$.
-    Observe that because the probability of each permutation is the same, player $P$ has the same probability of being in any position.
-    In other words, $S_n$ follows a uniform distribution on $0, \frac{1}{nL}, \frac{2}{nL} \dots, 1$.
-    Consequently, $S_n$ converges in distribution to the uniform distribution $U[0, 1]$.
-
-    I have now shown that the assumptions of \cref{lem:convergence_to_manifold} are satisfied.
-    % TODO
-
-    Then, by \cref{lem:many_sided_manifold}, the Shapley-value is
+    First, let us switch to an alternative formulation of the problem.
+    Remember, that the probability of each permutation is the same.
+    Therefore, the following procedure leads to the same distribution over permutations: (1) for each player, draw a random number from the uniform distribution on $[0, 1]$, then sort the players according to the drawn numbers.
+    This is equivalent to the original problem, as the probability of each permutation is the same.
+
+    Now let us characterize $X_n$ in terms of this procedure.
+    $[X_n]_l$ is the proportion of players of type $A_l$ that are placed before player $P$, or, equivalently, the number of players of type $A_l$ that have drawn a number less than player $P$.
+    I.e.,
+    \begin{align*}
+        [X_n]_l = \frac{1}{n}\sum_{i = 1}^n \mathbf{1}[U_{li} < U_P].
+    \end{align*}
+    For any finite $n$, we can disregard ties, as they have probability zero.
+
+    Now let us condition this probability distriibution on the draw of player $P$:
+    \begin{align*}
+        [X_n]_l < x \mid U_P = u = \frac{1}{n} \sum_{i=1}^n \mathbf{1}[U_{li} < u].
+    \end{align*}
+    As the draws are independent, by the strong law of large numbers,
+    \begin{align*}
+        [X_n]_l < x \mid U_P \xrightarrow[a.s.]{} \E[\mathbf{1}[U_{li} < u]] = u.
+    \end{align*}
+
+    Now we can use \cref{lem:convergence_to_manifold} to conclude that $X_n \xrightarrow[]{d} (U, \dots, U)$.
+    Finally, by \cref{lem:many_sided_manifold}, the Shapley-value is
     \begin{align*}

### 2024-02-09 src/paper/theory.tex
Prove the main theorem

@@
 \subsection{Weighted values}
+\label{sec:weighted_one_sided}
 
@@
 
-    Now let us condition this probability distriibution on the draw of player $P$:
+    Now let us condition this probability distribution on the draw of player $P$:
     \begin{align*}
@@
     \begin{align*}
-        [X_n]_l < x \mid U_P \xrightarrow[a.s.]{} \E[\mathbf{1}[U_{li} < u]] = u.
+        [X_n]_l < x \mid U_P \xrightarrow[]{a.s.} \E[\mathbf{1}[U_{li} < u]] = u.
     \end{align*}
@@
     \begin{align*}
-        \varphi_P^\infty & = \int_0^1 f(t, \dots, t) \dt.
+        \varphi_P^\infty & = \int_0^1 f(s, \dots, s) \dt
+    \end{align*}
+    and the value of fringe $l$ is
+    \begin{align*}
+        \varphi_{A_l}^\infty & = \int_0^1 \partial_l f(s, \dots, s) \ds
     \end{align*}
@@
     The proof uses the same approach as that of \cref{prop:many_sided_shapley}.
-    I will show that $X_n \xrightarrow[]{d} h(\xi)$, where $h(s) = (s^{\lambda_1}, \dots, s^{\lambda_L})$, and $\xi$ is a random variable with cdf $G(s) = s^{\lambda_P}$, and then rely on \cref{lem:many_sided_manifold}.
+    I will show that $X_n \xrightarrow[]{d} h(S)$, where $h(s) = (s^{\lambda_1}, \dots, s^{\lambda_L})$, and $S$ is a random variable with cdf $G(s) = s^{\lambda_P}$, and then rely on \cref{lem:many_sided_manifold}.
+
+    First, as before, let us characterize the probabilities of the various permutations.
+    The approach I am using relies on two main ideas.
+
+    First, as shown by \textcite{kalai1987weighted}, the probability of a permutation can be described by successively selecting the players with probabilities proportional to the weights of the players that have not been selected yet, and then reversing this ordering.\footnote{
+        For more details, see \cref{sec:weighted_one_sided}.
+    }
+
+    The other key result I rely on is the main proposition of \textcite{efraimidis2006weighted}.
+    It states that weighted random sampling without replacement can be also be achieved by the following procedure.
+    First, for each player $i$, draw a random number from the distribution $U^{\frac{1}{\lambda_i}}$, where $U$ is uniformly distributed on $[0, 1]$, and $\lambda_i$ is the sampling weight of player $i$.
+    Then, for a sample size of $m$, select the $m$ players with the largest numbers.
+
+    An immediate corollary of the latter result is that the procedure described by \textcite{kalai1987weighted} is equivalent to the following procedure.
+    First, for each player $i$, draw a random number from the distribution $V_i = U^{\frac{1}{\lambda_i}}$, where $U$ is uniformly distributed on $[0, 1]$.
+    Then, for each player $i$, sort the players according to the drawn numbers in ascending order.
+
+    Now let us characterize $X_n$ in terms of this procedure.
+    $[X_n]_l$ is the proportion of players of type $A_l$ that are placed before player $P$, or, equivalently, the number of players of type $A_l$ that have drawn a number less than player $P$.
+    I.e.,
+    \begin{align*}
+        [X_n]_l = \frac{1}{n}\sum_{i = 1}^n \mathbf{1}[V_{li} < V_P].
+    \end{align*}
+
+    Now let us condition this probability distribution on the draw of player $P$:
+    \begin{align*}
+        [X_n]_l < x \mid V_P = s = \frac{1}{n} \sum_{i=1}^n \mathbf{1}[V_{li} < u].
+    \end{align*}
+    Then use the strong law of large numbers to deduce that
+    \begin{align*}
+        [X_n]_l < x \mid V_P \xrightarrow[]{a.s.} \E[\mathbf{1}[V_{li} < u]] = u^{\lambda_l}.
+    \end{align*}
+    Then we can rely on \cref{lem:convergence_to_manifold} to conclude that $X_n \xrightarrow[]{d} (V_P^{\lambda_1}, \dots, V_P^{\lambda_L})$.
+
+    Finally, by \cref{lem:many_sided_manifold}, the weighted value of player $P$ is
+    \begin{align*}
+        \varphi_P^\infty &= \int_0^1 f(s_1^{\lambda_1}, \dots, s_L^{\lambda_L}) \mathrm{d} V_P(s) \\
+        &= \int_0^1 f(s_1^{\lambda_1}, \dots, s_L^{\lambda_L}) \lambda_P s^{\lambda_P - 1} \ds,
+    \end{align*}
+    and the value of fringe $l$ is
+    \begin{align*}
+        \varphi_{A_l}^\infty &= \int_0^1 t^{\lambda_P} \lambda_l s^{\lambda_l - 1} \partial_l f(s_1^{\lambda_1}, \dots, s_L^{\lambda_L}) \lambda_P s^{\lambda_P - 1} \ds.
+    \end{align*}
 

### 2024-02-09 src/paper/theory.tex
First sketch of proof for second part of lemma 2

@@
     \end{align*}
+
+    For the fringe value, the proof is similar, with a couple of additional steps.
+    First, fix some fringe player $A_{li}$.
+    Let $Y_n$ be the random variable describing the share of each type of fringe player that precede player $A_{li}$.
+    Also, let $Q_n$ be the random variable describing whether player $P$ precedes player $A_{li}$.
+    Then, the value of fringe player $A_{li}$ is
+    \begin{align*}
+        \varphi_{A_{li}}^n &= \E[ \mathbf{1}[Q_n = 1] (f(Y_1, \dots, Y_l + 1/n, \dots, Y_L) - f(Y_1, \dots, Y_l, \dots, Y_L)) ],
+    \end{align*}
+    and the value of the whole fringe of type $A_l$ is
+    \begin{align*}
+        \varphi_{A_{l}}^n = n \varphi_{A_{li}}^n = \E \bigg[ \underbrace{\mathbf{1}[Q_n = 1] \frac{f(Y_1, \dots, Y_l + 1/n, \dots, Y_L) - f(Y_1, \dots, Y_l, \dots, Y_L)}{1/n}}_{\coloneqq \Delta_n} \bigg].
+    \end{align*}
+
+    Now notice that, because the number of fringe players goes to infinity,
+    \begin{align*}
+        X_n \xrightarrow[]{d} (a_1(\xi), \dots, a_L(\xi)) &\implies Y_n \xrightarrow[]{d} (a_1(\xi), \dots, a_L(\xi)) \\
+        &\implies (Y_1, \dots, Y_n) | Y_l = a_l(s) \xrightarrow[]{d} (a_1(s), \dots, a_l(s)) .
+    \end{align*}
+    Furthermore,
+    \begin{align*}
+        \Pr(Q_n = 1 | [Y_n]_l = a_l(s)) \to H(s).
+    \end{align*}
+    Finally, for fixed $(Y_1, \dots, Y_L)$,
+    \begin{align*}
+        \Delta_n \to \partial_l f(Y_1, \dots, Y_l, \dots, Y_L).
+    \end{align*}
+
+    Putting it all together,
+    \begin{align*}
+        \lim_{n \to \infty} \varphi_{A_{l}}^n &= \lim_{n \to \infty} \E[\Delta_n (Y_n)] \\
+        &= \E[ H(s) \partial_l f(Y_1, \dots, Y_L) ] \\
+        &= \int_0^1 H(s) \partial_l f(a_1(s), \dots, a_L(s)) \mathrm{d} a_l(s) \\
+        &= \int_0^1 H(s) a_l'(s) \partial_l f(a_1(s), \dots, a_L(s)) \ds.
+    \end{align*}
+
 \end{proof}

### 2024-02-22 src/paper/theory.tex
Highlight main theorem
Compare example model in steps

@@
 The set of players and the characteristic function are the same as in the previous section, but players have the following weights: player $P$ has weight $\lambda_P$, while players $A^l_i$ have weight $\lambda_l$.
+This can be considered as the main theorem of the paper, as most of the propositions in the previous sections are special cases of it.
+
 I will show, that as with the Shapley-value, the limit of the weighted value can also be expressed as an integral over a one-dimensional path.
@@
 \end{align*}
-Clearly, equilibrium utilities must be smaller than in the welfare-maximizing case, due to $\phi_i$ being increasing, the number of entrants is also lower.
+Clearly, equilibrium utilities must be smaller than in the welfare-maximizing case.
+Due to $\phi_i$ being increasing, the number of entrants is also lower.
 
@@
 
-Let us now compare the outcomes at the three cases by looking at the entry fees for side $i$.
-From the previous results, they are
-\begin{align*}
-    p_i^* &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j \gamma_j n_j n_i^{\gamma_j - 1}}_{(2)}, \\
-    p_i^u &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j \gamma_j n_j n_i^{\gamma_j - 1}}_{(2)} + \underbracket{n_i \kappa'_i(n_i)}_{(3)} \\
-    p_i^b &= \underbracket{\frac{\lambda_i}{\lambda_P + \lambda_i} F_i}_{(1)} - \underbracket{\frac{\lambda_i \gamma_j}{\lambda_P + \lambda_j + \lambda_i\gamma_j} \alpha_j n_j n_i^{\gamma_j - 1}}_{(2)} \\
-    &+ \underbracket{\frac{\lambda_P + \lambda_j\gamma_i}{\lambda_P + \lambda_i + \lambda_j\gamma_i} \alpha_i n_j^{\gamma_i} +
-    - \int_0^{n_1} \left[ 1 - \lambda_i \left( \frac{s}{n_i} \right)^{\lambda_P + \lambda_i - 1} \right] \kappa_i(s) \ds}_{(4)},
+Let us now compare the outcomes of the three cases described in this section.
+To highlight the similarity to \textcite{armstrong2006competition}, I will first consider the case of linear network effects.
+Furthermore, for simplicity of exposition, I start by considering the non-weighted Shapley value before moving on to the weighted value.
+
+Assume that network effects are linear, i.e. $\gamma_i = 1$ for $i \in \{1, 2\}$.
+Also, focus on non-weighted Shapley values ($\lambda_P = \lambda_1 = \lambda_2 = 1$).
+From the previous results, the entry fees for side $i$ are
+\begin{align*}
+    p_i^* &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j n_j n_i}_{(2)}, \\
+    p_i^u &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j n_j n_i}_{(2)} + \underbracket{n_i \kappa'_i(n_i)}_{(3)} \\
+    p_i^b &= \underbracket{\frac{1}{2} F_i}_{(1)} - \underbracket{\frac{1}{3} \alpha_j n_j n_i}_{(2)} + \underbracket{\frac{2}{3} \alpha_i n_j - \int_0^{n_1} \left[ 1 - \frac{s}{n_i} \right] \kappa_i(s) \ds}_{(4)},
 \end{align*}
@@
 
-The bargaining case also has the first two factors, albeit they are somewhat different.
-As opposed to the first two cases, the price only contains some fraction of the externalities, and the rest is shared with the platform and the other side.
+The bargaining case also includes the first two factors, albeit they are somewhat different.
+As opposed to the first two cases, the price only contains some fraction of the externalities, and the rest is shared with the platform and the other side.\footnote{
+    Due to the linearity of the model, various parts of the value are shared equally between players who participate in producing them.
+    This is the reason why, for example, the platform and the firms share the cost of serving the entrants (1) equally, or that all three types of players share the value generated on a given side (2) equally.
+}
 Furthermore, some part of the welfare generated on side $i$ is also shared with the other players, and thus appears in the price (4).
@@
 
-Whether these departures lead to a higher or lower total welfare depends on the specific parameters of the model.
-For example, if $\lambda_P$ is very high, then $p_i^b > p_i^u > p_i^*$, leading to lower entry and total surplus than not only the welfare-maximizing case, but also the unilateral pricing case.
+Now let us consider the cases of non-linear network effects.
+The welfare-maximizing, unilateral pricing and bargaining entry fees are as follows:
+\begin{align*}
+    p_i^* &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j \gamma_j n_j n_i^{\gamma_j - 1}}_{(2)}, \\
+    p_i^u &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j \gamma_j n_j n_i^{\gamma_j - 1}}_{(2)} + \underbracket{n_i \kappa'_i(n_i)}_{(3)} \\
+    p_i^b &= \underbracket{\frac{1}{2} F_i}_{(1)} - \underbracket{\frac{\gamma_j}{2 + \gamma_j} \alpha_j n_j n_i^{\gamma_j - 1}}_{(2)} + \underbracket{\frac{1 + \gamma_i}{2 + \gamma_i} \alpha_i n_j^{\gamma_i} - \int_0^{n_1} \left[ 1 - \frac{s}{n_i} \right] \kappa_i(s) \ds}_{(4)}.
+\end{align*}
+For the most part, the intuition is the same as in the linear case.
+The welfare-maximizing price is still the cost of serving one additional player (1) and the positive externality imposed on the other side (2).
+In addition to those, the unilaterally set entry fee includes a markup related to the elasticity of entry (3).
+Finally, in the case of bargaining, these factors do not appear in full, but are shared with the platform and the other side.
+
+There is one important difference in the bargaining case, however.
+In the linear case, the terms related to the value generated on each side were shared between the players in a constant proportion, independent of the model parameters.
+In the non-linear case, however, these shares do depend on the shape of the network effects.
+In particular, when side $i$'s network externality on side $j$ is more convex (e.g. firms on side $i$ are less substitutable), then it receives a larger share of the value generated on the other side.
+This is signified by the fact that the coefficient of side $i$'s network externality, $\frac{\gamma_j}{2 + \gamma_j}$, is increasing in $\gamma_j$.
+This result shows that the bargaining outcomes are not just a trivial distribution of the value, but also take into account the shape of the network effects.
+
+Finally, for completeness, let us consider the case of weighted values.
+The following theorem summarizes the entry fees in this most general case.
+\begin{theorem}
+    Let $p_i^*$, $p_i^u$ and $p_i^b$ denote the welfare-maximizing, unilateral pricing and bargaining entry fees, respectively.
+    Then,
+    \begin{align*}
+        p_i^* &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j \gamma_j n_j n_i^{\gamma_j - 1}}_{(2)}, \\
+        p_i^u &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j \gamma_j n_j n_i^{\gamma_j - 1}}_{(2)} + \underbracket{n_i \kappa'_i(n_i)}_{(3)} \\
+        p_i^b &= \underbracket{\frac{\lambda_i}{\lambda_P + \lambda_i} F_i}_{(1)} - \underbracket{\frac{\lambda_i \gamma_j}{\lambda_P + \lambda_j + \lambda_i\gamma_j} \alpha_j n_j n_i^{\gamma_j - 1}}_{(2)} \\
+        &+ \underbracket{\frac{\lambda_P + \lambda_j\gamma_i}{\lambda_P + \lambda_i + \lambda_j\gamma_i} \alpha_i n_j^{\gamma_i} - \int_0^{n_1} \left[ 1 - \lambda_i \left( \frac{s}{n_i} \right)^{\lambda_P + \lambda_i - 1} \right] \kappa_i(s) \ds}_{(4)}.
+    \end{align*}
+\end{theorem}
+
+In the case of the linear terms, such as the cost of serving one additional player (1), the addition of bargaining weights simply leads to players shareing the cost in a constant proportion, according to their weights.
+The higher the weight, the larger the share for the player.
+While the latter is true for non-linear terms, as well, the influence of the weights is more complex, as it also depends on the shape of value function.
+For example, in term (2), $\lambda_i$ interacts with the parameter determining the shape of the network effects, $\gamma_j$
+Therefore, the weighted value is more than just a simple reweighting of the non-weighted value, and its effects can be quite complex depending on the assumptions on the value function.
+
+Whether bargaining leads to a higher or lower total welfare depends on the parameters of the model.
+For example, if $\lambda_P$ is very high, then $p_i^b > p_i^u > p_i^*$, leading to fewer firms entering and lower total surplus than not only the welfare-maximizing case, but also the unilateral pricing case.
 That is, everybody looses from bargaining.\footnote{
@@
 
-Finally, it is always true that $p_1^b < p_1^*$ or $p_2^b < p_2^*$.\footnote{
-    Given that $\alpha_i > 0, i \in \{1, 2\}$.
-}
+Finally, it is always true that $p_1^b < p_1^*$ or $p_2^b < p_2^*$.
 The reason is that the platform's profit is always non-negative in the bargaining case, while it is negative in the welfare-maximizing case.
 This also implies that the total welfare is strictly lower than in the welfare-maximizing case.
-Therefore, while bargaining can be welfare-increasing compared to unilateral price setting, it can not achieve the maximum possible welfare.\footnote{
+Therefore, while bargaining can be welfare-increasing compared to unilateral price setting, it can not achieve the highest possible total welfare.\footnote{
     One could argue that the welfare maximizing case is not a realistic benchmark anyway, as it assumes that the platform is making a loss.

### 2024-02-22 src/paper/theory.tex
Fix Typo

@@
 
-One can also obtain the total welfare of side $i$, as it is simply the number of entrants plus the non-idiosyncratic utility of its players, plus the sum (integral) of the idiosyncratic utilities.
+One can also obtain the total welfare of side $i$, as it is simply the number of entrants times the non-idiosyncratic utility of its players, plus the sum (integral) of the idiosyncratic utilities.
 \begin{align}

### 2024-02-22 src/paper/theory.tex
Move idiosyncratic entry costs to appendix

@@
 Following \textcite{armstrong2006competition}, let us also model player entry in a reduced form manner.
-There is a continuum of potential entrants on both sides of the market.
-Assume that the total utility of an entrant on side $i$ also includes an idiosyncratic cost component.
-Let us order the players on side $i$ by this idiosyncratic cost in an increasing manner.
-That is, if we denote the idiosyncratic utility of player $n$ on side $i$ as $\kappa_i(n)$, then $\kappa_i$ is strictly increasing in $n$.
-Also assume that $\lim_{n \to \infty} \kappa_i(n) = \infty$.
-
-Entry is given by the usual assumption that a player enters if and only if the total utility of entering is non-negative.
-
-Due to the properties of $\kappa_i$, this implies that there is a well-defined, finite number of entrants on each side.
-Let us denote the number of entrants as a function of their non-idiosyncratic utility as $\phi_i(u_i)$.
-Then, the total number of players on side $i$ is 
-\begin{align*}
-    n_i = \phi_i(u_i) = \kappa_i^{-1}(u_i),
-\end{align*}
-where $\phi_i$ has the same role as in \textcite{armstrong2006competition}.
+Assume that there is a continuum of potential entrants on both sides of the market.
+The number of actual entrants depends on the utility they would derive from participating in the market.\footnote{
+    Such assumptions are usually justified by some idiosyncratic cost of entry, the distribution of which determines the function $\phi$.
+    In the main text, for simplicity, I refrain from explicitly modeling this cost, but \cref{sec:explicit_entry_costs} provides a discussion of how to incorporate it into the model, and how it would affect bargaining outcomes.
+}
+Let us denote this relationship as $\phi_i(u_i)$, where $\phi_i$ is a strictly increasing, differentiable function.
+Then,
+\begin{align*}
+    n_i = \phi_i(u_i).
+\end{align*}
 
@@
     \label{eq:W_star}
-    W_i^*(n_i, n_j) = \alpha_i n_i n_j ^ {\gamma_i} + \gamma_j \alpha_j n_j n_i^{\gamma_j} - n_i F_i - \int_0^{n_i} \kappa_i(s) \ds.
+    W_i^*(n_i, n_j) = \alpha_i n_i n_j ^ {\gamma_i} + \gamma_j \alpha_j n_j n_i^{\gamma_j} - n_i F_i.
 \end{align}
@@
 \begin{align*}
-    u_i^u(n_1, n_2) &= \alpha_i n_j ^ {\gamma_i} + \alpha_j \gamma_j n_j n_i^{\gamma_j - 1} - F_i - \frac{\phi_1(u_i)}{\phi'_1(u_i)} \\
-    &= \alpha_i n_j ^ {\gamma_i} + \alpha_j \gamma_j n_j n_i^{\gamma_j - 1} - F_i - n_i \kappa'_i(n_i).
+    u_i^u(n_1, n_2) &= \alpha_i n_j ^ {\gamma_i} + \alpha_j \gamma_j n_j n_i^{\gamma_j - 1} - F_i - \frac{\phi_1(u_i)}{\phi'_1(u_i)}
 \end{align*}
@@
     \label{eq:W_u}
-    W_i^u(n_1, n_2) = \alpha_i n_i n_j ^ {\gamma_i} + \gamma_j \alpha_j n_j n_i^{\gamma_j} - n_i F_i - n_i^2 \kappa'_i(n_i) - \int_0^{n_i} \kappa_i(s) \ds.
+    W_i^u(n_1, n_2) = \alpha_i n_i n_j ^ {\gamma_i} + \gamma_j \alpha_j n_j n_i^{\gamma_j} - n_i F_i - n_i^2 (\phi_i^{-1})'(n_i).
 \end{align*}
@@
 Finally, let us consider the case when the platform and the players bargain over the value they generate.
-I will approach this problem in two steps.
-First, I will examine the distribution of the value generated in the case of no idiosyncratic cost.
-I do this because this partial result has a neat interpretation, and is very tractable.
-After that, I derive how the total idiosyncratic cost is distributed between the players.
-Because of the linearity of random order values, the total welfare in the general case is simply the sum of these two building blocks.
-
-Let us start by examining the case when there is no idiosyncratic cost.
 Assume that $n_1$ and $n_2$ players have decided to enter on sides $1$ and $2$, respectively.
-Furthermore, assume that bargaining weights are $\lambda_1, \lambda_2$ and $\lambda_P$.
+Furthermore, assume that players' bargaining weights are $\lambda_1, \lambda_2$ and $\lambda_P$.
 
 The characteristic function of the game takes a similar form to that in \cref{sec:many_sided}.
-If the platform is not part of the coalition, then the value is zero.
+If the platform is not part of the coalition, then the value the coalition can generate is zero.
 Otherwise, it is simply the sum of the utilities of the two sides minus the cost of serving them.\footnote{
-    The entry fees do not matter, as they are simply payments between coalition members, and thus do not affect the total value.
+    Entry fees do not matter, as they are within-coalition transfers, and thus do not affect the total value.
 }
@@
 
-Let us now turn our attention to the idiosyncratic cost component.
-Assume that, even though entrants with different costs have different contribution to the total value, there can be no discrimination between them.
-That is, they each must share the same fraction of the total idiosyncratic cost (e.g. have the same value).
-
-Let us denote the total idiosyncratic cost incurred by all players on both sides as $K(n_1, n_2)$.
-Also, suppose that if $n_i$ players enter on side $i$, then they are the ones with the lowest idiosyncratic cost.
-Then, the total idiosyncratic cost is simply the sum of the idiosyncratic costs of the entrants on both sides:
-\begin{align*}
-    K(n_1, n_2) = \int_0^{n_1} \kappa_1(s) \ds + \int_0^{n_2} \kappa_2(s) \ds.
-\end{align*}
-Again, one can obtain the weighted values of all sides using \cref{prop:many_sided_weighted}.
-\begin{proposition}
-    \label{prop:platform_bargaining_idiosyncratic}
-    The weighted values of the idiosyncratic cost component are
-    \begin{align*}
-        K_P(n_1, n_2) &= \sum_{i \in \{1, 2\}} \int_0^{n_1} \left[ 1 - \lambda_i \left( \frac{s}{n_i} \right)^{\lambda_P + \lambda_i - 1} \right] \kappa_i(s) \ds, \\
-        K_i(n_1, n_2) &= \lambda_i \int_0^{n_1} \left( \frac{s}{n_i} \right)^{\lambda_P + \lambda_i - 1} \kappa_i(s) \ds.
-    \end{align*}
-\end{proposition}
-
-That is, each side only has to bear some part of the total idiosyncratic cost, and the rest is shared with the platform.
-As with the rest of the value, the share of the idiosyncratic cost is increasing in one's own bargaining weight.
-This might seem counterintuitive at first, as one may expect that a player with a higher bargaining weight would be able to shift more of the cost to the other side.
-However, in the case of random order values, this intuition is only correct for monotonic games, which it is not in this case.
-One has to keep in mind though that this is just part of the final payoffs, and the other parts are increasing in one's own bargaining weight.
-Therefore, as long as the combined game is monotonic, the final payoffs will be increasing in one's own bargaining weight.
-
-Let us finally consider total welfare.
-As mentioned before, it is simply the sum of the value generated and the idiosyncratic cost.
-That is, the welfare of side $i \in \{1, 2\}$ is
-\begin{align*}
-    W_i^b(n_1, n_2) &= \frac{\lambda_i}{\lambda_P + \lambda_i + \lambda_j\gamma_i} \alpha_i n_i n_j^{\gamma_i} + \frac{\lambda_i \gamma_j}{\lambda_P + \lambda_j + \lambda_i\gamma_j} \alpha_j n_j n_i^{\gamma_j} - \frac{\lambda_i}{\lambda_P + \lambda_i} n_i F_i \\
-    &- \lambda_i \int_0^{n_1} \left( \frac{s}{n_i} \right)^{\lambda_P + \lambda_i - 1} \kappa_i(s) \ds.
-\end{align*}
-It is remarkably similar in structure to the welfare maximizing case in \cref{eq:W_star}.
+These utilities are remarkably similar in structure to the welfare maximizing case in \cref{eq:W_star}.
 The main difference is that each part (both costs and positive utilities) is reweighted, and side $i$ only receives a fraction of it.
@@
 \begin{align*}
-    u_i^b(n_1, n_2) &= \frac{\lambda_i}{\lambda_P + \lambda_i + \lambda_j\gamma_i} \alpha_i n_j^{\gamma_i} + \frac{\lambda_i \gamma_j}{\lambda_P + \lambda_j + \lambda_i\gamma_j} \alpha_j n_j n_i^{\gamma_j - 1} - \frac{\lambda_i}{\lambda_P + \lambda_i} F_i \\
-    &+ \int_0^{n_1} \left[ 1 - \lambda_i \left( \frac{s}{n_i} \right)^{\lambda_P + \lambda_i - 1} \right] \kappa_i(s) \ds.
-\end{align*}
-If one wished to close the model, the number of entrants in equilibrium could be obtained by solving the system of equations $\kappa_i(n_i) = u_i(n_1, n_2), n \in \{1, 2\}$.
+    u_i^b(n_1, n_2) &= \frac{\lambda_i}{\lambda_P + \lambda_i + \lambda_j\gamma_i} \alpha_i n_j^{\gamma_i} + \frac{\lambda_i \gamma_j}{\lambda_P + \lambda_j + \lambda_i\gamma_j} \alpha_j n_j n_i^{\gamma_j - 1} - \frac{\lambda_i}{\lambda_P + \lambda_i} F_i.
+\end{align*}
+If one wished to close the model, the number of entrants in equilibrium could be obtained by solving the system of equations $n_i = \phi_i(u_i(n_1, n_2)), n \in \{1, 2\}$.
 Finally, the implied entry fees can be calculated from the equation $u_i = \alpha_i n_j^{\gamma_i} - p_i$, yielding
 \begin{align*}
-    p_i^b(n_1, n_2) &= \frac{\lambda_i}{\lambda_P + \lambda_i} F_i - \frac{\lambda_i \gamma_j}{\lambda_P + \lambda_j + \lambda_i\gamma_j} \alpha_j n_j n_i^{\gamma_j - 1} + \frac{\lambda_P + \lambda_j\gamma_i}{\lambda_P + \lambda_i + \lambda_j\gamma_i} \alpha_i n_j^{\gamma_i} \\
-    &- \int_0^{n_1} \left[ 1 - \lambda_i \left( \frac{s}{n_i} \right)^{\lambda_P + \lambda_i - 1} \right] \kappa_i(s) \ds.
+    p_i^b(n_1, n_2) &= \frac{\lambda_i}{\lambda_P + \lambda_i} F_i - \frac{\lambda_i \gamma_j}{\lambda_P + \lambda_j + \lambda_i\gamma_j} \alpha_j n_j n_i^{\gamma_j - 1} + \frac{\lambda_P + \lambda_j\gamma_i}{\lambda_P + \lambda_i + \lambda_j\gamma_i} \alpha_i n_j^{\gamma_i}.
 \end{align*}
@@
     p_i^* &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j n_j n_i}_{(2)}, \\
-    p_i^u &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j n_j n_i}_{(2)} + \underbracket{n_i \kappa'_i(n_i)}_{(3)} \\
-    p_i^b &= \underbracket{\frac{1}{2} F_i}_{(1)} - \underbracket{\frac{1}{3} \alpha_j n_j n_i}_{(2)} + \underbracket{\frac{2}{3} \alpha_i n_j - \int_0^{n_1} \left[ 1 - \frac{s}{n_i} \right] \kappa_i(s) \ds}_{(4)},
+    p_i^u &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j n_j n_i}_{(2)} + \underbracket{n_i (\phi_i^{-1})'(n_i)}_{(3)} \\
+    p_i^b &= \underbracket{\frac{1}{2} F_i}_{(1)} - \underbracket{\frac{1}{3} \alpha_j n_j n_i}_{(2)} + \underbracket{\frac{2}{3} \alpha_i n_j}_{(4)},
 \end{align*}
@@
 The unilateral pricing case also includes these two factors in full, but also adds a third factor, related to the elasticity of entry (3).
-Namely, the platform extracts some of the surplus generated by the entrants, and the surplus it can extract depends on $\phi'_i(u_i)$ (or, equivalently, $\kappa'_i(u_i)$).
-It is the same mechanism that leads to the markup in the simple monopolistic pricing model.
+Namely, the platform extracts some of the surplus generated by the entrants, and the surplus it can extract depends on $\phi'_i(u_i)$.
+It is the same mechanism that leads to markups in a simple monopolistic pricing model.
 
@@
 Furthermore, some part of the welfare generated on side $i$ is also shared with the other players, and thus appears in the price (4).
+This is in contrast to both the welfare-maximizing and unilateral pricing cases, where the entry fee did not depend on the actual utility that was materialized on the given side.
 Therefore, bargaining introduces some interesting departures from both the welfare-maximizing and unilateral pricing cases.
 
-Now let us consider the cases of non-linear network effects.
+Now let us consider non-linear network effects.
 The welfare-maximizing, unilateral pricing and bargaining entry fees are as follows:
@@
     p_i^u &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j \gamma_j n_j n_i^{\gamma_j - 1}}_{(2)} + \underbracket{n_i \kappa'_i(n_i)}_{(3)} \\
-    p_i^b &= \underbracket{\frac{1}{2} F_i}_{(1)} - \underbracket{\frac{\gamma_j}{2 + \gamma_j} \alpha_j n_j n_i^{\gamma_j - 1}}_{(2)} + \underbracket{\frac{1 + \gamma_i}{2 + \gamma_i} \alpha_i n_j^{\gamma_i} - \int_0^{n_1} \left[ 1 - \frac{s}{n_i} \right] \kappa_i(s) \ds}_{(4)}.
+    p_i^b &= \underbracket{\frac{1}{2} F_i}_{(1)} - \underbracket{\frac{\gamma_j}{2 + \gamma_j} \alpha_j n_j n_i^{\gamma_j - 1}}_{(2)} + \underbracket{\frac{1 + \gamma_i}{2 + \gamma_i} \alpha_i n_j^{\gamma_i}}_{(4)}.
 \end{align*}
@@
         p_i^u &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j \gamma_j n_j n_i^{\gamma_j - 1}}_{(2)} + \underbracket{n_i \kappa'_i(n_i)}_{(3)} \\
-        p_i^b &= \underbracket{\frac{\lambda_i}{\lambda_P + \lambda_i} F_i}_{(1)} - \underbracket{\frac{\lambda_i \gamma_j}{\lambda_P + \lambda_j + \lambda_i\gamma_j} \alpha_j n_j n_i^{\gamma_j - 1}}_{(2)} \\
-        &+ \underbracket{\frac{\lambda_P + \lambda_j\gamma_i}{\lambda_P + \lambda_i + \lambda_j\gamma_i} \alpha_i n_j^{\gamma_i} - \int_0^{n_1} \left[ 1 - \lambda_i \left( \frac{s}{n_i} \right)^{\lambda_P + \lambda_i - 1} \right] \kappa_i(s) \ds}_{(4)}.
+        p_i^b &= \underbracket{\frac{\lambda_i}{\lambda_P + \lambda_i} F_i}_{(1)} - \underbracket{\frac{\lambda_i \gamma_j}{\lambda_P + \lambda_j + \lambda_i\gamma_j} \alpha_j n_j n_i^{\gamma_j - 1}}_{(2)} + \underbracket{\frac{\lambda_P + \lambda_j\gamma_i}{\lambda_P + \lambda_i + \lambda_j\gamma_i} \alpha_i n_j^{\gamma_i}}_{(4)}.
     \end{align*}
@@
 
-\subsection{Non-indispensable big player}
-
-As a final extension for the one-sided case, let us examine what happens when the big player is not indispensable.
-Assume that it provides some value to any coalition, but a coalition of fringe players can achieve a positive value without it.
+\subsection{Small players can generate some value on their own}
+
+As a final extension for the one-sided case, let us examine what happens when the small players can generate some value on their own.
+Assume that the big player still provides some value to any coalition, but a coalition of fringe players can achieve a positive value even without it.
 Formally, the value function is the following:
@@
 
+\section{Idiosyncratic entry costs are explicitly modeled}
+\label{sec:explicit_entry_costs}
+
+Assume that the total utility of an entrant on side $i$ also includes an idiosyncratic cost component.
+Let us order the players on side $i$ by this idiosyncratic cost in an increasing manner.
+That is, if we denote the idiosyncratic utility of player $n$ on side $i$ as $\kappa_i(n)$, then $\kappa_i$ is strictly increasing in $n$.
+Also assume that $\lim_{n \to \infty} \kappa_i(n) = \infty$.
+
+Entry is given by the usual assumption that a player enters if and only if the total utility of entering is non-negative.
+Due to the properties of $\kappa_i$, this implies that there is a well-defined, finite number of entrants on each side.
+Let us denote the number of entrants as a function of their non-idiosyncratic utility as $\phi_i(u_i)$.
+Then, the total number of players on side $i$ is 
+\begin{align*}
+    n_i = \kappa_i^{-1}(u_i) \coloneqq \phi_i(u_i).
+\end{align*}
+
+This microfoundation does not change the results of the welfare-maximizing and unilateral pricing cases in any fundamental way.
+Total welfare must be adjusted to include this idosyncratic cost, but entry fees do not change at all.
+The reason is that, in the welfare-maximizing case, optimal prices only depend on externalities, while in the unilateral pricing case, the only additional factor is the elasticity of entry\footnote{
+    With this microfoundation in mind, one also relate this entry elasticity as the marginal cost of entry.
+}.
+On the other hand, the bargaining case is more interesting.
+The reason is that this idiosyncratic cost becomes a part of the value that the players bargain over, and thus it affects the characteristic function and the resulting bargaining outcomes.
+
+I approach this problem by breaking it down into two parts: the bargaining over the idisyncratic and non-idiosyncratic parts of the value generated.
+Due to the linearity property of the Shapley value, the bargaining outcomes over the whole value are simply the sum of the bargaining outcomes over these two parts.
+Furthermore, the non-idiosyncratic part is simply the value function from the main text, and thus the resulting weighted values are the same as before.
+
+Let us continue by examining the idiosyncratic part of the value.
+Assume that, even though entrants with different costs have different contribution to the total value, there can be no discrimination between them in terms of the bargaining outcomes.
+That is, they each must share the same fraction of the total idiosyncratic cost (e.g. have the same value).
+
+Let us denote the total idiosyncratic cost incurred by all players on both sides as $K(n_1, n_2)$.
+Also, suppose that if $n_i$ players enter on side $i$, then they are the ones with the lowest idiosyncratic cost.
+Then, the total idiosyncratic cost is simply the sum of the idiosyncratic costs of the entrants on both sides:
+\begin{align*}
+    K(n_1, n_2) = \int_0^{n_1} \kappa_1(s) \ds + \int_0^{n_2} \kappa_2(s) \ds.
+\end{align*}
+One can obtain the weighted values of all sides using \cref{prop:many_sided_weighted}.
+\begin{proposition}
+    \label{prop:platform_bargaining_idiosyncratic}
+    The weighted values of the idiosyncratic cost component are
+    \begin{align*}
+        K_P(n_1, n_2) &= \sum_{i \in \{1, 2\}} \int_0^{n_1} \left[ 1 - \lambda_i \left( \frac{s}{n_i} \right)^{\lambda_P + \lambda_i - 1} \right] \kappa_i(s) \ds, \\
+        K_i(n_1, n_2) &= \lambda_i \int_0^{n_1} \left( \frac{s}{n_i} \right)^{\lambda_P + \lambda_i - 1} \kappa_i(s) \ds.
+    \end{align*}
+\end{proposition}
+
+That is, each side only has to bear some part of the total idiosyncratic cost, and the rest is shared with the platform.
+As with the rest of the value, the share of the idiosyncratic cost is increasing in one's own bargaining weight.
+This might seem counterintuitive at first, as one may expect that a player with a higher bargaining weight would be able to shift more of the cost to the other side.
+However, in the case of random order values, this intuition is only correct for monotonic games, which it is not.
+One has to keep in mind though that this is just part of the final payoffs, and the other parts are increasing in one's own bargaining weight.
+Therefore, as long as the game over the total value is monotonic, the final payoffs will be increasing in one's own bargaining weight.
+
+Let us finally consider total welfare.
+As mentioned before, it is simply the sum of the value generated and the idiosyncratic cost.
+That is, the welfare of side $i \in \{1, 2\}$ is
+\begin{align*}
+    W_i^b(n_1, n_2) &= \frac{\lambda_i}{\lambda_P + \lambda_i + \lambda_j\gamma_i} \alpha_i n_i n_j^{\gamma_i} + \frac{\lambda_i \gamma_j}{\lambda_P + \lambda_j + \lambda_i\gamma_j} \alpha_j n_j n_i^{\gamma_j} - \frac{\lambda_i}{\lambda_P + \lambda_i} n_i F_i \\
+    &- \underbracket{\lambda_i \int_0^{n_1} \left( \frac{s}{n_i} \right)^{\lambda_P + \lambda_i - 1} \kappa_i(s) \ds }_{(*)}.
+\end{align*}
+In turn, the implied entry fee for side $i$ is
+\begin{align*}
+    p_i^b &= \frac{\lambda_i}{\lambda_P + \lambda_i} F_i - \frac{\lambda_i \gamma_j}{\lambda_P + \lambda_j + \lambda_i\gamma_j} \alpha_j n_j n_i^{\gamma_j - 1} \\
+    &+ \frac{\lambda_P + \lambda_j\gamma_i}{\lambda_P + \lambda_i + \lambda_j\gamma_i} \alpha_i n_j^{\gamma_i} - \underbracket{\int_0^{n_1} \left[ 1 - \lambda_i \left( \frac{s}{n_i} \right)^{\lambda_P + \lambda_i - 1} \right] \kappa_i(s) \ds}_{(**)}.
+\end{align*}
+
+As with the other components of the value, the idiosyncratic entry cost is also shared between the platform and the entrants.
+Part of it $(*)$ is incurred on the side of the entrants, while the other part $(**)$ paid by the platform as a reduction of entry fees.
+How this cost is divided is not straightforward, though.
+As in the case of non-linear network effects, it depends on the bargaining weights and the shape of the idiosyncratic cost function, with the two also interacting in a non-trivial way.
+
 \section{Miscellaneous lemmas}

### 2024-02-22 src/paper/theory.tex
Improve one-sided case

@@
 In this section I examine the case of identical fringe players.
-Many of these results are known in the literature, but I include them here to build intuition, and highlight the similarities with the multi-sided case.
-I will first look at the simplest setting (one large player, which is completely indispensable), but in \ref{sec:extensions} I will somewhat relax this assumption.
+Many of these results are known in the literature, but I include them here for three reasons.
+First, to provide build intuition for the more general case later on.
+Second, to highlight the similarities to the multi-sided case, and to provide a bridge between the two.
+Finally, I also express the fringe's value in terms of its weighted marginal contributions, which is a useful result in its own right.
+In the main text, I only consider the most straightforward case (one large completely indispensable player), but in \ref{sec:extensions} I will somewhat relax these assumptions.
+
 Let us start by defining the cooperative game that describes this situation.
-
 Consider a game with two types of players: a major player $P$ and $n$ smaller players $A_i$, $1 \leq i \leq n$.
 Formally, let us denote the set of all players as $N = \{P, A_1, \dots, A_n\}$.
-Assume that (1) no coalition of players can achieve a positive value without the participation of $P$ and (2) players $A_i$ are identical.
+Assume that (1) no coalition of players can achieve a positive value without the participation of $P$ and (2) players $A_i$ are identical to each other.
 Let $n_T(S)$ denote the number of players of type $T \in \{P, A\}$ in coalition $S$.
-Under these assumptions, the characteristic function of the game (the value that any coalition $S \subset N$ can achieve) is the following:
+Under these assumptions, the characteristic function of this game (the value that a coalition $S \subset N$ can achieve) is the following:
 \begin{align*}
@@
 \end{align*}
-One can think of this setting as a (one-sided) platform and a number of potential entrants, if the entrants can only reach their prospective consumers through the platform, or as a vertical supply chain with one upstream producer and a number of downstream firms.
-
-First, let us characterize the conditions under which this game is monotone and superadditive.
-Superadditivity is a key property of cooperative games, as it ensures that it always pays off to form the grand coalition (i.e., the coalition that includes all players).
-Furthermore, in the context of bargaining, these properties provide some theoretical support for using Shapley-values as bargaining outcomes, as many results creating a link between non-cooperative bargaining and cooperative values often rely on these assumptions.\footnote{
+Such a game can represent, for example, a (one-sided) platform and a number of potential entrants, where the entrants can only reach their prospective consumers through the platform, or as a vertical supply chain with one upstream producer and a number of downstream sellers.
+
+Before delving into the various values, let us characterize the conditions under which this game is monotone and superadditive.
+Monotonicity requires that the value of any coalition is weakly higher than the value of any of its subsets.
+Superadditivity on the other hand requires that the value of the union of two disjoint coalitions is weakly higher than the sum of their values.
+The latter is a key property of cooperative games, as it ensures that it always pays off to form the grand coalition (i.e., the coalition that includes all players).
+Furthermore, in the context of bargaining, these properties provide some theoretical support for using the Shapley-value or the weighted value to represent bargaining outcomes, as many results creating a link between non-cooperative bargaining games and the values of cooperative games often rely on these assumptions.\footnote{
     For example, the results in \textcite{gul1989bargaining} rely on superadditivity, while monotonicity suffices for \textcite[]{hart1996bargaining}.
@@
 \end{proposition}
+The intuition behind this result is quite straightforward.
+As player $P$ is necessary to create any value, no two disjoint coalitions can both achieve a positive value.
+Therefore, superadditivity is equivalent to monotonicity in this case.
 
@@
 }
-As a side note, it also ensures that the games are of bounded variation, and thus the main theorem in \textcite{fogelman1980asymptotic} applies.
-Namely, both the asymptotic and axiomatic approach of characterizing the Shapley-value of the game lead to the same result\footnote{
+As a side note, it also ensures that the game is of bounded variation, and thus the main theorem in \textcite{fogelman1980asymptotic} applies.
+Namely, the asymptotic and the axiomatic approach of characterizing the Shapley-value of the game both lead to the same result\footnote{
     More precisely, the asymptotic value coincides with the axiomatic one derived using the uniform distribution.
@@
 }.
+This result could also be used to prove \cref{prop:one_sided} instead of the direct proof provided in \cref{sec:proofs}.
 
@@
 
-For any finite number of fringe players, the random order value of a player \parencite{weber1988probabilistic} is simply its average marginal contribution to the value of all possible coalitions.
-More precisely, take all permutations of the players, and assign a probability to each of them.
-Then, the random order value of player $P$ is the expected marginal contribution of $P$ to the value of the coalition preceding it in these permutations.
+Random order values are a class of cooperative solution concepts characterized by efficiency, monotonicity, linearity and the null-player axiom \parencite{weber1988probabilistic}.
+That is, they are a generalization of the Shapley value, where the axiom of symmetry is relaxed.
+Another way to think about them is that they are the average marginal contribution of a player to all possible coalitions, where the average is taken according to some probability distribution over the permutations of the players.
+
+In this specific game, a random order value can be obtained in the following way.
+First, take all permutations of the players, and assign a probability to each permutation.
+Then, the random order value of player $P$ is the expected marginal contribution of $P$ to the value of the coalition preceding it, where the expectation is taken according to said probability distribution.
 
@@
 
-Random order values are of interest to us for a number of reasons.
-First, they are a natural extension to the Shapley value, where the axiom of symmetry is relaxed.
+Random order values are of interest for a number of reasons.
+First, they are a natural extension to the Shapley value and the weighted value.
 Furthermore, they provide a convenient framework, of which all subsequent results (Shapley value, weighted value, multiple big players) are special cases.
@@
 The following proposition demonstrates the main idea of this paper: even as the number of fringe players goes to infinity, the value of the big player does not converge to the worth of the grand coalition, $f(1)$.
+Or, in other words, the fringe, even when its members are infinitesimally small, still retains some bargaining power.
+As a corollary, the continuous fringe model can be thought of as a more tractable approximation of bargaining between a finite number of fringe players, as it retains the latter's main features.
 
@@
 First, due to random order values being efficient, it can be thought of as the leftover from the total value after subtracting the value of the big player.
-Alternatively, as the second part of the corollary demonstrates, it is also related to the marginal contributions to the fringe agents.
-The only difference from the big player's value is that we have to weight this marginal contribution by the probability of the big player appearing before the fringe firm in question, as otherwise its marginal contribution is zero.
+Alternatively, as the second part of the corollary demonstrates, it is also related to the marginal contributions of the fringe agents.
+The only difference from the big player's value is that we have to multiply these marginal contributions by the probability of the big player appearing before the fringe firm in question, as otherwise they would be zero.
 The latter interpretation will be particularly useful when thinking about the value of the fringe in the multi-sided setting.
 
-It is immediately follows from the proposition above that (for a fixed total pie size $f(1)$) player $P$ gets a larger share when $f(t)$ is larger for every $t$.
-It is already apparent from Figure \ref{fig:one_sided} that (for a fixed total pie size $f(1)$) player $P$ gets a larger share when $f(t)$ is larger for every $t$.
-It corresponds to the case when only a relatively small fraction of the fringe is needed to create a large part of the total potential surplus (e.g.
-fringe players products are substitutes of each other).
+It also follows immediately from the previous proposition that (for a fixed total pie size $f(1)$) player $P$ gets a larger share when $f(t)$ is larger for every $t$.
+That is, when only a relatively small fraction of the fringe is needed to create a large part of the total potential surplus (e.g.
+fringe players' products are substitutes of each other), then player $P$ is able to appropriate a larger share of the total value.
 This result aligns with our natural intuition that player $P$ has a better bargaining position in this case, than if only coalitions with most of the fringe firms on board could obtain high values.
@@
 
-The following proposition and corollary derives the Shapley value of the big player and the fringe, respectively.
+The following proposition and corollary derives the limit of the Shapley value for the big player and the fringe, respectively.
 
@@
 
-Because the Shapley value is a special case of the random order value, these results follows quite straightforwardly from \cref{prop:one_sided_general} and \cref{cor:fringe_value_general}.
+Because the Shapley value is a special case of the random order value, these results are quite straightforward consequences of \cref{prop:one_sided_general} and \cref{cor:fringe_value_general}.
 One only has to notice that each permutation having an equal probability implies that the number of firms coming before $P$ is uniformly distributed on $1, \dots, n$, and thus the share of firms before $P$ converges in distribution to the uniform distribution on $[0, 1]$.
@@
 
-The resulting Shapley values also have a nice geometric interpretation \cref{fig:one_sided}.
+The resulting Shapley values also have a nice geometric interpretation shown on \cref{fig:one_sided}.
 Consider a rectangle with sides of length 1 and $f(1)$, respectively.
-Then, due to superadditivity, the grand coalition forms and achieves the value $f(1)$, which is the area of the rectangle.
+The grand coalition achieves the value $f(1)$, which is also the area of the rectangle.\footnote{
+    Due to superadditivity, the grand coalition can be expected to form, and the main question is how the value is distributed between the big player and the fringe.
+}
 The value of the big player is then $\int_0^1 f(t) \dt$, which is simply the part of the rectangle below the graph of $f$, while the fringe gets the rest.
-Thus, the graph of $f$ partitions the area (total value) into what the big player and the fringe obtain.
+Thus, the graph of $f$ partitions the area (total value) into what the big player and the fringe can obtain.
 
@@
 
-This section investigates the case when players have different levels of innate bargaining power.
+This section investigates the case of players having different levels of innate bargaining power.
 One way to model this is by using weighted values \parencite{shapley1953additive}, which are a generalization of the Shapley value.
+They are also a non-symmetric generalization of the Shapley value, albeit with more structure than random order values.
 The idea behind them is that, in addition to the set of players and the characteristic function, the game is also endowed with a weight system, which is a vector of non-negative numbers, one for each player.
 These weights determine how the value of a coalition is distributed amongst its members in the case when they are all equally important for the coalition.
-This is a way to relax the symmetry axiom of Shapley values, while retaining more structure than in the case of the more general random order values.
+Then, relying on the linearity of the value, this distribution can be extended to the case when the players are not equally important.
 
@@
 I.e., assume that there is at most one player with zero weight.
-For my main result, I make use of the fact that weighted values can be calculated by weighting the permutations by the probabilities arising from the following sequential ordering procedure \parencite{kalai1987weighted}.
+For my main result, I make use of an alternative, computational characterization of the weighted values. 
+\textcite{kalai1987weighted} demonstratesd that weighted values can be calculated by weighting the permutations by the probabilities arising from the following sequential ordering procedure.
 Start with the set of all players.
@@
 
+Now let us turn to deriving the weighted value and its limit for the big player and the fringe in this specific game.
+First, I propose a lemma that characterizes the distribution of the number of players before $P$ in the limit, and then use it to derive the weighted value of the big player and the fringe.
 Consider the game described in the previous section, and let the weights of players of type $A$ and $P$ be 1 and $\lambda$, respectively.
@@
 Having \cref{eq:entry_distr_discrete} and \cref{lem:entry_distr} allows us to invoke \cref{prop:one_sided_general} to obtain the following proposition.\footnote{
-    \textcite{stole1996intra} also derives essentially the same expression for the equilibrium outcome of their bargaining game with unequal profit distribution, and assert that it is equal to the weighted value.
+    \textcite{stole1996intra} also derive essentially the same expression for the equilibrium outcome of their bargaining game with unequal profit distribution, and assert that it is equal to the weighted value.
 }
@@
 
-Depending on the shape of this distribution (which in turn depends on the weight $\lambda$), regions corresponding to different masses of fringe firms can be over or underweighted in this integral, leading to different values.
+As before, the value of the big player can still be expressed as an integral of the value function, while the value of the fringe can be expressed as an integral of the marginal contributions of the fringe players.
+The only difference is that, as in the case of the general random order value, the integrands are weighted by some probability distribution.
+Depending on the shape of this distribution, regions corresponding to different masses of fringe firms can be over or underweighted in this integral, leading to different values.
+Contrary to \cref{prop:one_sided_general}, the probability distribution has a specific functional form, and is characterized by a single parameter, $\lambda$.
+\Cref{fig:weigh_function} illustrates the weighting function for various values of $\lambda$.
 
@@
         \end{tikzpicture}
-        \caption{$\int_0^t g(s) \ds$}
+        \caption{$G(t)$}
     \end{subfigure}
@@
 
-Now, let us examine how this weighting impacts the shares of the various players.
-It turns out, that a higher weight corresponds to a higher Shapley-value in this game.\footnote{
-    This would not necessarily have to be the case, as demonstrated by \textcite{owen1968communications}.
-},
-supporting the interpretation of weights as some kind of innate bargaining power.
+Now, let us examine how these weights impact the shares of the various players.
 \begin{corollary}
@@
 \end{corollary}
-
-Furthermore, the following corollary shows that the limit of the weighted value of $P$, as their weight goes to zero (infinity) is precisely the payoffs $P$ would achieve if $P$ were making (facing) take-it-or-leave-it offers.
-This set of results highlights that utilizing (weighted) Shapley values to model bargaining outcomes provides an intermediate solution between inscribing all the bargaining power to one or the other player.
+It turns out, that a higher weight corresponds to a higher Shapley-value in this game.\footnote{
+    This would not necessarily have to be the case, as demonstrated by \textcite{owen1968communications}.
+},
+supporting their interpretation as some kind of innate bargaining power.
+
+Furthermore, the next corollary shows that the limit of the weighted value of $P$, as their weight goes to zero (infinity) is precisely the payoffs $P$ would achieve if $P$ were making (facing) take-it-or-leave-it offers.
 \begin{corollary}
@@
 \end{corollary}
+This set of results highlights that utilizing (weighted) Shapley values to model bargaining outcomes provides an intermediate solution between inscribing all the bargaining power to one or the other player, and thus a generalization of take-it-or-leave-it offers.
 
@@
     \end{align*}
-    As $f$ is continuous and bounded, and $X_n \xrightarrow[]{d} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
+    As $f$ is continuous and bounded, and $X_n \xrightarrow[]{d} X$, by the portmanteau lemma, $\E[f(X_n)] \to \E[f(X)]$.
     Putting it together,
@@
     \end{align*}
-    The second can be obtained by integration by parts:
+    The second one can be obtained by integration by parts:
     \begin{align*}
@@
     \end{align*}
-    Furthermore, as $f$ is continuous (and therefore bounded on $[0, 1]^L$), and $X_n \xrightarrow[]{d} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
+    Furthermore, as $f$ is continuous (and therefore bounded on $[0, 1]^L$), and $X_n \xrightarrow[]{d} X$, by the portmanteau lemma, $\E[f(X_n)] \to \E[f(X)]$.
     Putting it together,
@@
     \end{align*}
-    Furthermore, as $f$ is continuous and bounded on $[0, 1]^L$, and $X_n \xrightarrow[]{d} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
+    Furthermore, as $f$ is continuous and bounded on $[0, 1]^L$, and $X_n \xrightarrow[]{d} X$, by the portmanteau lemma, $\E[f(X_n)] \to \E[f(X)]$.
     Therefore,

### 2024-02-27 src/paper/theory.tex
Improve many-sided section

@@
 Up until this point, we have only considered games with a single type of small player.
-Now imagine that, in addition to player $P$, there are $L$ types of smaller players: $\{A^l_1, \dots, A^l_n\}$ where $1 \leq l \leq L$.
-As before, assume that $P$ is necessary for any coalition to have a positive value, and the small players are identical to each other \emph{within their types}.
-Formally, the game in coalitional form is now the following: the set of players is $N = \{P, A^1_1, \dots, A^1_n, \dots, A^L_1, \dots, A^L_n\}$ and the characteristic function is
+Now imagine that, in addition to player $P$, there are $L$ different varieties of smaller players: $\{A^l_1, \dots, A^l_n\}$ where $1 \leq l \leq L$.
+The idea is the same as before: I assume that $P$ is necessary for any coalition to have a positive value, and the small players are identical to each other \emph{within their types}.
+The substitutability of the different types of small players will be captured by the -- now multivariate -- function $f$.
+
+Let us now turn to the formal definition of the game.
+For a finite number of fringe players, the coalitional form of the game $(N, v)$ is the following.
+The set of players is $N = \{P, A^1_1, \dots, A^1_n, \dots, A^L_1, \dots, A^L_n\}$, which in total contains $nL + 1$ players.\footnote{
+    In this formulation, we assume that the number of players of each type is the same.
+    However, this is not as restrictive as it might seem.
+    In the limit, each type of player will become infinitesimally small, and the exact number of players of each type will not matter.
+}
+The characteristic function is
 \begin{align*}
@@
         0                                                & \text{if } P \notin S \\
-        f\left(\frac{n_{A^1}(S)}{n}, \dots, \frac{n_{A^L}(S)}{n}\right) & \text{otherwise}.
+        f\left(\frac{n_{A^1}(S)}{n}, \dots, \frac{n_{A^L}(S)}{n}\right) & \text{otherwise},
     \end{cases}
 \end{align*}
+where $f$ is now a multivariate function from $[0, 1]^L$ to $\mathbb{R}$.
 
@@
 }
-Or, following \textcite{stole1996intra}, it could also be used to model bargaining between a firm and multiple types of workers.
-
-Let us follow the pattern from the previous sections.
-Start by characterizing conditions for monotonicity and superadditivity to support the bargaining interpretation and the formation of the grand coalition.
-It is easy to see that the conditions are the straightforward analogues of those from the one-sided case.
+More than two types of fringe players can be used to model a platform with more than two sides, such as a platform with both buyers and sellers, and a set of advertisers, or, following \textcite{stole1996intra}, bargaining between a firm and multiple types of input suppliers.
+
+For the subseuent discussion, let us follow the structure of the previous section.
+I start by characterizing conditions for monotonicity and superadditivity to support the bargaining interpretation and the formation of the grand coalition.
+It turns out that necessary and sufficient conditions for these properties are the straightforward analogues of those from the one-sided case.
 \begin{proposition}
@@
 \end{proposition}
+The intuition for this is the same as before: superadditivity is equivalent to monotonicity due to the fact that no coalition can have a positive value without $P$, and monotonicity boils down to $f$ being increasing in all of its arguments.
 
 In the next subsections, I will first examine random order values, and then two important special cases: the Shapley value and the weighted value.
-
-% \subsection{Shapley value}
-
-% Let us obtain formulas for the values of the three types of players.
-% It turns out that the limits of the Shapley-values (as $n \to \infty$) are still analytically tractable, and they also have a neat interpretation.
-% \begin{proposition}
-%     Let $f$ be continuous everywhere on $[0, 1]^L$.
-%     Then,
-%     \begin{align*}
-%         \varphi_P^\infty & = \int_0^1 f(t, \dots, t) \dt                                 \\
-%         \varphi_{A^l}^\infty & = \int_0^1 t \partial_l f(t, \dots, t) \dt.
-%     \end{align*}
-% \end{proposition}
-
-% As the previous proposition shows, the value of each kind of player depends on their expected marginal contribution, i.e. the partial derivatives of $f$.
-% Consequently, the value of the grand coalition can be decomposed into the Shapley-values of its members the following way:
-% \begin{align*}
-%     f(1, \dots, 1) = \underbrace{\int_0^1 f(t, \dots, t) \dt}_{\text{ player } P} + \sum_{l=1}^L \underbrace{\int_0^1 t \partial_l f(t, \dots, t) \dt}_{\text{players } A^ll}.
-% \end{align*}
-% This formulation makes it clear that values are intimately related to the marginal contributions of the players, captured by the partial derivatives of $f$ in the case of the various fringe players.
-
-% One surprising element of the result is that one only has to integrate over the diagonal of the support  of $f$, and the value does not depend on off-diagonal parts of the $f$ fucntion.
-% The intuition for that relies on a law-of-large-numbers-type reasoning.
-% If the number of fringe players is large, then it is very unlikely that, after a random ordering, their proportion is too different on any interval.
-% Consequently, when taking the expectation over all orderings, those with very unequal numbers of the various types have little impact on it.
+Many of the results will be similar to the one-sided case, including the marginal contribution interpretation of the value of the fringe, and the geometric interpretation of the Shapley value.
+Furthermore, it turns out that even though the number of fringe players is a multi-dimensional object in this case, for the limit of the Shapley and weighted values, one only has to integrate over a one-dimensional manifold within the unit hypercube, which makes the results more tractable.
 
@@
 
-Let us start by establishing the analog of \cref{prop:one_sided_general} for the many-sided case.
+First, let us examine the most general case: the random order value.
+Let us start by establishing the analog of \cref{prop:one_sided_general} for the many-sided case to obtain the limit of the value of the big player.
 \begin{proposition}
@@
         \varphi_P^\infty = \lim_{n \to \infty} \varphi_P^n &= \int_0^1 \dots \int_0^1 f(t_1, \dots, t_L) \dG(t_1, \dots t_L) \\
-        &= \int_0^1\dots \int_0^1 g(t) f(t_1, \dots, t_L) \dt_1 \dots \dt_L,
+        &= \int_0^1\dots \int_0^1 g(t_1, \dots, \t_n) f(t_1, \dots, t_L) \dt_1 \dots \dt_L,
     \end{align*}
@@
 \end{proposition}
-
-While the above proposition is very general in terms of permutation probabilities, it is not very tractable in practice, as one has to integrate over the entire unit hypercube.
+The proposition above is almost identical to \cref{prop:one_sided_general}, with the only difference being that the integral is now over the $L$-dimensional unit hypercube, due to $f$ being a function of $L$ variables.
+
+While the above proposition is very general in terms of permutation probabilities, it is not very tractable in practice, as one has to integrate over the entire, $L$-dimensional domain of $f$.
 It would be much more convenient, if one only had to be concerned with a one-dimensional manifold within the hypercube instead.
-It turns out, that for a couple of important cases (namely, the Shapley value and the weighted value) it is indeed the case.
+It turns out, that for a number of important cases (namely, the Shapley value and the weighted value) it is indeed the case.
 
 Let us start by establishing a general result, after which I will show that the Shapley value and the weighted value are special cases of it.
-
+The following lemma provides sufficient conditions, under which the limit of the value of the big player can be expressed as an integral over a one-dimensional path, even though the value for any finite number of players depends on the whole domain of $f$.
 \begin{lemma}
@@
 
-The lemma above states, that -- if its assumptions are satisfied -- one only has to be concerned with just a tiny fraction of the production function $f$.
+The lemma states, that if the permutation probabilities are such that the number of fringe players before $P$ converges to a degenerate distribution, then one only has to be concerned with just a tiny fraction of the production function $f$.
 Namely, we only need to know how the function behaves on the set $\{(a_1(t), \dots, a_L(t)) : t \in [0, 1]\} \subset [0, 1]^L$.\footnote{
@@
 This result is essentially a generalization of the diagonal formula from \textcite{aumann2015values} or \textcite{stole1996intra} to the case where permutation probabilities are not uniform.
-The intuition behind it is the same: if the number of fringe players is large, then it is very unlikely that, after a random ordering, their proportion is very different from \emph{what it should be}.
-The main difference is that, in this case, the ``what it should be'' part is not uniform, but rather given by the $a_l$ functions.
-
-In the remainder of this section, I will show that the Shapley value satisfy the assumptions of the above lemma, and thus the limit of those values can be expressed as an integral over a one-dimensional path.
+The intuition, however, is the same law-of-large-numbers-type argument: if the number of fringe players is large, then it is very unlikely that, after a random ordering, their proportion is very different from its expected value.
+The main difference is that, in this case, this conditional expectations are not linear, but rather given by the $a_l$ functions.
+
+In the remainder of this section, I will show that the Shapley value and the weighted value satisfy the assumptions of the above lemma, and thus the limit of those values can be expressed as an integral over a well-defined one-dimensional path.
 
@@
 
-Now let us turn our attention to the Shapley-value.
-As mentioned before, due to the uniformity of the permutation probabilities, we get a diagonal formula in this case.
+Let us now turn our attention to the Shapley value.
+As hinted before, due to the uniformity of the permutation probabilities, we get a diagonal formula in this case.
 \Cref{prop:many_sided_shapley} establishes this result formally.
@@
 \end{proposition}
-
-As displayed on \cref{fig:many_sided_shapley}, The value of player $P$ is the integral of $f$ over the diagonal of the unit hypercube.\footnote{
-    \textcite{stole1996intra} also obtain this expression for the limiting case of their bargaining game.
+That is, in the case of the Shapley value, one has to integrate over the diagonal of the unit hypercube to obtain the limit of the value of the big player.\footnote{
+    \textcite{stole1996intra} also obtain the expression for the big player's value for the limiting case of their bargaining game.
     The proof of this proposition demonstrates a way to obtain it as a limit of the Shapley value of the finite games.
 }
+\Cref{fig:many_sided_shapley} illustrates this result in the case of two types of fringe players: the value of player $P$ is the integral of $f$ over the diagonal of the unit square.
 Furthermore, this result also demonstrates how the rest of the value is divided amongst the fringe players.
@@
 
-Let us now examine the weighted value in the multi-sided case.
-The set of players and the characteristic function are the same as in the previous section, but players have the following weights: player $P$ has weight $\lambda_P$, while players $A^l_i$ have weight $\lambda_l$.
-This can be considered as the main theorem of the paper, as most of the propositions in the previous sections are special cases of it.
-
-I will show, that as with the Shapley-value, the limit of the weighted value can also be expressed as an integral over a one-dimensional path.
-However, this path is not the diagonal of the unit hypercube, and depends on the ratio of the fringe players' weights.
-
+The final part of this section is dedicated to the weighted value in the many-sided case.
+The set of players and the characteristic function are the same as in the previous section, but, as before, each player has a weight attached to them.
+I will assume that fringe players are identical to each other within their types also with respect to their weights.
+That is, the weight system for the game is the following: player $P$ has weight $\lambda_P$, while players $A^l_i$ have weight $\lambda_l$.
+
+I will show, that as with non-weighted Shapley value, the limit of the weighted value can be expressed as an integral over a one-dimensional path in the weighted case as well.
+However, now this path is not the diagonal of the unit hypercube, but a function of the fringe players' weights.
+The reason for this is that not all permutations have the same probability of occurring: those with players having higher weights ordered later are more likely to occur.
+
+The following statement is the central theorem of this paper.
+In fact, most of the propositions in the previous sections can be considered as special cases of it.
 \begin{theorem}
@@
 \end{theorem}
-
 The intuition is the following.
@@
 For any $s \in (0, 1)$, the proportion of fringe players with a higher weight is lower than their population share, while the proportion of fringe players with a lower weight is higher than their population share.
-\Cref{fig:many_sided_weighted} illustrates this phenomenon in the case of two types of fringe players.
-
-Finally, player $P$'s probability of coming after $s$ proportion of the fringe is also not uniform, but rather influenced by the relationship between its own and the fringe players' weights.
+
+Cref{fig:many_sided_weighted} illustrates this phenomenon in the case of two types of fringe players.
+Fringe players of type $A^2$ have a higher weight than those of type $A^1$, and thus the path the integral is taken over contains more of the latter than the former.
+
+Finally, player $P$'s probability of coming after $s$ proportion of the fringe is also not uniform, but rather influenced by the relationship between its own and the fringe players' weights.\footnote{
+    This is the same mechanism as in the case of the one-sided weighted value.
+}
 Therefore, the integral is not taken with respect to the uniform distribution, but rather one resembling that of \cref{prop:one_sided_weighted}.
@@
 \end{corollary}
+This result is analogous to \cref{cor:platform_value_weighted}, and demonstrates that a higher weight for player $P$ corresponds to a higher value in this game as well.
 

### 2024-02-27 src/paper/theory.tex
Add links to the latest draft
Add thanks section

@@
 
+\newcommand*{\thisdraft}{\normalsize{This draft: \today}} 
+\newcommand*{\firstdraft}{\normalsize{First draft: 2 August 2022}} 
+\newcommand*{\latestversion}{\normalsize{Latest version: \href{https://stanmart.github.io/ValueOfIntermediation/theory.pdf}{stanmart.github.io/ValueOfIntermediation/theory.pdf}}}
+
 \DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
 
-\title{The value of being indispensable: a cooperative approach to bargaining with a continuum of players}
-\author{Martin Stancsics}
+\title{%
+    The value of being indispensable: a cooperative approach to bargaining with a continuum of players%
+    \thanks{
+        I would like to thank my advisors, Armin Schmutzler and Marek Pycia, for their guidance, support and encouragement throughout the writing of this paper.
+        I am also grateful to the participants of the Topics in Microeconomic Theory and Market Design seminars at the University of Zurich for their helpful comments.
+    }
+}
+\author{Martin Stancsics \\ \normalsize{University of Zurich}}
+\date{\thisdraft \\ \firstdraft \\ \latestversion}
 
@@
         \varphi_P^\infty = \lim_{n \to \infty} \varphi_P^n &= \int_0^1 \dots \int_0^1 f(t_1, \dots, t_L) \dG(t_1, \dots t_L) \\
-        &= \int_0^1\dots \int_0^1 g(t_1, \dots, \t_n) f(t_1, \dots, t_L) \dt_1 \dots \dt_L,
+        &= \int_0^1\dots \int_0^1 g(t_1, \dots, t_n) f(t_1, \dots, t_L) \dt_1 \dots \dt_L,
     \end{align*}
@@
 
-Cref{fig:many_sided_weighted} illustrates this phenomenon in the case of two types of fringe players.
+\Cref{fig:many_sided_weighted} illustrates this phenomenon in the case of two types of fringe players.
 Fringe players of type $A^2$ have a higher weight than those of type $A^1$, and thus the path the integral is taken over contains more of the latter than the former.

### 2024-02-29 src/paper/theory.tex
Streamline abstract

@@
 \begin{abstract}
-    This paper investigates the idea of using concepts random order values, a concept from cooperative game theory, to model bargaining outcomes in games with an indispensable player and a continuum of fringe players.
-    I show that this approach proves to be very tractable in a number of settings, and leads to results that are in line with one's intuitive expectations about bargaining outcomes.
-    Thus, it can be a useful tool in modelling situations where one does not want to attribute all the bargaining power to one type of market participants, and at the same time would like to avoid having to deal with an explicit multi-stage bargaining game.
-    On one hand, this paper provides a taxonomy of the various results found in some applied papers.
-    Furthermore, it introduces some new results pertaining to the case of multiple types of fringe players.
-    The utility of this approach is demonstrated via a simple model of two-sided markets.
-    The results in this paper are intended to be used as a tool-kit for embedding bargaining outcomes into more complex models.
+    This paper investigates the idea of using random order values, a concept from cooperative game theory, to model bargaining outcomes in games with one indispensable player and a continuum of fringe players.
+    Two important special cases of random order values are discussed in detail: the Shapley value and the weighted value.
+    I show that this approach proves to be very tractable, and leads to results that are in line with one's intuitive expectations about bargaining outcomes.
+    Thus, it can be a useful tool in modelling situations where one does not want to attribute all the bargaining power to one side of the market, and at the same time would like to avoid having to deal with an explicit multi-stage bargaining game.
+    The utility of this approach is demonstrated via a simple model of a two-sided market.
 \end{abstract}

### 2024-02-29 src/paper/theory.tex
Rewrite intro

@@
 
-\section{Motivation}
-
-Using cooperative game theory to model bargaining outcomes in a tractable way has quite a few examples in the industrial organization literature.
-This is in part motivated by the appealing properties of the resulting gain distributions, their tractability, but also by the long line of theoretical studies showing that various bargaining procedures lead to such outcomes.
-For example, \textcite{gul1989bargaining,winter1994demand,hart1996bargaining,inderst2003bargaining,} or, perhaps most relevant to this paper, \textcite{stole1996intra} all propose various extensive-form bargaining games in which the expected outcomes correspond to players' Shapley-values.
-
-In terms of applications, the case of one indispensable player and a large number of small ones is particularly important in a number of settings.
+\section{Introduction}
+
+Using cooperative game theory to model bargaining outcomes has quite a few precedents in the industrial organization literature.
+This is in part motivated by the appealing properties of the resulting gain distributions and their tractability.
+Furthermore, this practice also has solid theoretical justifications thanks to the long line of studies showing that various cooperative solution concepts are related to certain dynamic, non-cooperative bargaining games.
+For example, \textcite{gul1989bargaining,winter1994demand,hart1996bargaining,inderst2003bargaining,} or, perhaps most relevant to this paper, \textcite{stole1996intra} all propose various extensive-form bargaining games in which the equilibrium corresponds to players' Shapley-values.
+
+For practical applications, the case of one indispensable player and a large number of small ones is particularly important in a number of settings.
 Examples include intra-firm ownership strutures \parencite{hart1990property}, wage bargaining \parencite{stole1996intra,stole1996organizational,levy1997individual}, collusion and mergers \parencite{segal2003collusion} and upstream-downstream supply chains \parencite{inderst2003bargaining,montez2007downstream}.
-The study of multi-sided markets (paltforms) is also a good fit for this modeling approach, as the platform is often indispensable for the fringe firms, but the latter are also numerous enough to be approximated by a continuum.\footnote{
-    \textcite{huang2022shapley} is one of the very few examples of using cooperative game theory in this setting.
+The study of multi-sided markets (or platforms) is also a good fit for this modeling approach, as the platform is often assumed to be indispensable for the various sides to interact.\footnote{
+    \textcite{huang2022shapley} is amongst the very few examples of using cooperative game theory in this setting.
 }
@@
 A common feature of most of the aforementioned papers is that they assume a finite number of players.
-However, as is often the case in economics, infinite-player approximations turn out to be more tractable while retaining the main conclusions of the finite models from which they arise.
-Perhaps most importantly, the resulting profit shares become continuous and differentiable functions of the size of the fringe, which is particularly useful when embedding these results into more complex models.
-
-Cooperative games with a finite number of atomic players and a continuum of non-atomic ones are called mixed or oceanic games \parencite{milnor1978values}, and have been studied in the literature of cooperative game theory.
-Most papers in this line of research focus on questions such as for which games the Shapley-value exists and is unique \parencite{hart1973values}, and whether various approaches (namely, characterizing the value using a set of axioms, and taking the limit of the value of finite-player games) lead to the same result \parencite{fogelman1980asymptotic}.\footnote{
-    \textcite{hart1973values} shows that in the case of mixed games, the usual axioms do not characterize a unique value in general.
-    However, \textcite{fogelman1980asymptotic} demonstrates that, for a quite general subset of games, the asymptotic approach leads to one specific element from the set characterized by the axiomatic approach.
-}
-My aim with this paper is both more general and more specific in certain aspects.
-For one, I am only interested in the asymptotic approach, and withing that, a specific series of finite games.
-Furthermore, I restrict my attention to one specific type of games, namely those with an indispensable player, and a continuum of fringe players consisting of a finite number of types.
-This in turn allows me to go beyond the usual Shapley-value, and obtain results for a more general set of solution concepts: random order values.
-In the case of multiple types of fringe players, I also present a number of new results for the Shapley value and the weighted value.
-In particular, I derive the value of the different types of fringe players in the multi-sided setting, and demonstrate how they are related to their marginal contributions.
-Additionally, due to having more structure in the model, I am able to provide more concrete results, investigate some comparative statics, as well.
-
-Despite their theoretical appeal and their tractability, oceanic games saw very little use in the industrial organization, and, more generally, applied economics literature.
-The most prominent examples are \textcite{stole1996intra, stole1996organizational} and \textcite{levy1997individual}, all of which use the Shapley-value to model wage bargaining, and consider the case of divisible labor (continuum of workers).
-The first two of these paper also provides microfoundations for the Shapley value and the weighted value in the intra-firm bargaining setting.
-To showcase the utility of this approach, I also build a simple model of two-sided markets.
-In addition to the aformentioned papers, this model includes two new features: (1) results about the distribution of the value between the various types of fringe players, and (2) using the weighted value in a multi-sided setting.
-
-In the following sections, I propose an oceanic game with the main feature that the large player is indispensable for creating value.\footnote{
+This paper explores the idea of using an infinite-player version of these models, where fringe players are represented as a continuum.
+As is often the case in economics, this infinite-player approximation turns out to be more tractable than the original, finite-player model, while retaining the main features of the latter.
+For example, the resulting profit shares depend on the production function similarly to the finite-player case, while becoming continuous and differentiable functions of the size of the fringe.
+This can be useful when embedding these results into more complex models.
+
+The main contribution of this paper is to provide a general framework for modeling bargaining outcomes in games with one indispensable player and a continuum of fringe players.
+I propose an oceanic game with the main feature that the large player is indispensable for creating value\footnote{
     This assumption will be somewhat relaxed throughout some of the generalizations.
-}
-Such a model applies to all the settings mentioned above, such as intra-firm bargaining, vertical supply chains, or multi-sided markets.
-I demonstrate that the random order values of the players in those models are described by very tractable expressions that have nice geometric interpretations.
-Additionally, the outcomes are in line with one's intuitive expectations of bargaining power in such situations.
-Finally, I demonstrate the usefulness of this approach by building a simple model of two-sided markets, where the various players' shares are determined by their (weighted) Shapley values.
+}, and examine the (Shapley, weighted and random order) values of the players in this game.
+I demonstrate that these values are described by very tractable expressions and have illuminating geometric interpretations.
+Just as importantly, I show that the outcomes are in line with one's intuitive expectations of bargaining power in such situations.
+
+On one hand, this paper provides a taxonomy of the various results found in some applied papers.
+Furthermore, it introduces some new results pertaining to the case of multiple types of fringe players.
+In particular, I highlight how the value of the fringe players can be expressed in terms of their marginal contributions, and how players' bargaining weights affect outcomes through changing the probability weights of orderings from which those marginal contributions are calculated.
+Finally, to showcase the utility of this approach, I also build a simple model of two-sided markets.
+My hope is that the results in this paper can be used as a tool-kit for embedding bargaining outcomes into more complex models.
+
+The present paper is closely related to two bodies of literature: a theoretical and an applied one.
+Cooperative games with a finite number of atomic players and a continuum of non-atomic ones are called mixed or oceanic games \parencite{milnor1978values}, and have been studied in the cooperative game theory literature.
+Most papers in this line of research focus on rather fundamental questions, such as for which games does the Shapley-value exist, when is it unique \parencite{hart1973values}, and whether the various ways of defining it\footnote{
+    One can characterize the value of the oceanic game directly, relying on a set of axioms (axiomatic approach).
+Alternatively the value of an infinite-player game can also be defined as the limit of the value of a series of finite-player games (asymptotic approach).
+} lead to the same result \parencite{fogelman1980asymptotic}.\footnote{
+    \textcite{hart1973values} shows that in the case of mixed games, the usual axioms do not in general characterize a unique value.
+    However, \textcite{fogelman1980asymptotic} demonstrates that, for a quite large subset of games, the asymptotic approach leads to one specific element from the set characterized by the axiomatic approach.
+}
+My aim with this paper is both somewhat more general and much more specific in certain aspects.
+For one, I focus on the asymptotic approach, and withing that, a specific way of approximating the infinite game of interest.
+This is motivated by the fact that I am not interested in the oceanic game per se, but rather in its ability to approximate finite-player games.
+Furthermore, I restrict my attention to a specific, but economically important subset of games: those with one indispensable player, and a continuum of fringe players consisting of a finite number of types.
+These two restrictions in turn allow me to go beyond the Shapley value, and obtain results for a more general set of solution concepts: random order values.
+Additionally, instead of looking at general results, such as existence, I can provide and interpret explicit expressions for the values of the various players.
+
+The other strand of research that is closely related to this paper belongs to the industrial organization literature.
+Despite the theoretical appeal and tractability of oceanic games, they, in general, saw remarkably little use in the industrial organization, and, more generally, applied economics.
+Nevertheless, there are a few prominent exceptions, such as \textcite{stole1996intra, stole1996organizational} and \textcite{levy1997individual}, which use the Shapley value to model wage bargaining under the assumption of divisible labor (continuum of workers).
+The first two of these paper also provides microfoundations for using the Shapley value and the weighted value in an intra-firm bargaining setting.
+The present paper contributes to this literature by generalizing some of its results, and an examinating some general properties of the various values in the context of such games.
+In particular, in addition to the aformentioned papers, the proposed model includes two new features: (1) results about the distribution of the value between the various types of fringe players, and (2) using random order values instead of the less general Shapley value or weighted value.
+Furthermore, I also provide results for the intersection of two important extensions in \textcite{stole1996intra}: the case of weighted values in the case of multiple types of fringe players.
+
+Finally, en example application is presented to demonstrate the usefulness of the proposed approach.
+This model is based on the seminal work of \textcite{armstrong2006competition} on multi-sided markets.
+Thus, although the present paper is mainly theoretical, it also has some minor contributions towards better understanding the functioning of multi-sided markets.
+
+The paper is organized as follows.
+In \cref{sec:one_sided}, I present the main results for the case of one indispensable player and a continuum of identical fringe players.
+\Cref{sec:many_sided} extends these results to the case of multiple types of fringe players.
+This is where the most novel results of the paper are presented.
+\Cref{sec:application} provides an example application of the results to a simple model of a two-sided market.
+Finally, \cref{sec:conclusion} concludes the paper.
 
 \section{One-sided case}
+\label{sec:one_sided}
 
@@
 \section{Example application}
+\label{sec:application}
 

### 2024-02-29 src/paper/theory.tex
Rewrite conclusions

@@
 \Cref{sec:application} provides an example application of the results to a simple model of a two-sided market.
-Finally, \cref{sec:conclusion} concludes the paper.
+Finally, \cref{sec:conclusions} concludes the paper.
 
@@
 \section{Conclusions}
-
-In this paper, I examined the problem of bargaining between one indispensable player and a continuum of fringe players.
-I did so using the concept of random order values from cooperative game theory.
-I showed that random-order-value-based bargaining has some desirable properties, and that it coincides with intuitive expectations in terms of certain comparative statics.
-Furthermore, the resulting distributions of the value are also analytically tractable, and has neat geometric interpretations.
-
-I use random order values to provide a comprehensive framework for a number of important special cases.
-Some of those, such as the Shapley-value, or the weighted value in the one-sided case, is already known in the literature.\footnote{
-    Aside from looking at it in an abstract manner, my contribution to those cases mostly lie in showing how the fringe's value can be expressed as a kind of expected marginal contribution.
-    This is especially relevant in the multi-sided case, where it is important to know how the value not obtained by the indispensible player is distributed among the various sides.
-}
-Others, such as the weighted value in the multi-sided case, or the interpretation of substitutable "indispensible" players, are, to the best of my knowledge, new.
-As I demonstrate, they retain the simplicity and interpretability of the simpler cases, while making the model more general.
+\label{sec:conclusions}
+
+In this paper, I examine the problem of bargaining between one indispensable player and a continuum of fringe players.
+I model this setting relying on the concept of random order values from cooperative game theory.
+I demonstrate that random-order-value-based outcomes have some desirable properties, and coincide with intuitive expectations in terms of comparative statics.
+Furthermore, the results are analytically tractable, and have neat interpretations both from a geometric perspective, and in terms of players' marginal contributions.
+
+Random order values offer a comprehensive framework for modeling bargaining outcomes, and also include important and well-known special cases, such as the Shapley value or the weighted value.
+Due to the former retaining many of the attractive properties of its more specialized counterparts, it might be a good candidate for modeling bargaining outcomes flexibly and in a tractable manner.
+Furthermore, as shown in \cref{sec:extensions}, the results can also be generalized to cases with not completely indispensable big players, while retaining the essential structure of the results.
+
+Another contribution of this paper is the derivation of the weighted value in the case of multiple types of fringe players.
+This provides a rather flexible model (one more general than the Shapley value) for modeling multi-sided markets.
+The proof of the corresponding theorem is also instructive in that it highlights how bargaining weights affect player's values through determining the probabilities of player orderings.
+
 Finally, I demonstrate how the proposed framework can be applied in practice by
-examining the two-sided platform model of \textcite{armstrong2006competition} with a small extension and a bargaining process over entry fees.
-I show that the resulting entry fees have a simple structure, but they also differ from the welfare-maximizing and unilateral price-setting cases in number of interesting ways.
-Therefore, in situations where bargaining between players is plausible, certain effects might be missed if one assumes unilateral price-setting.
+examining the two-sided platform model based on \textcite{armstrong2006competition}.
+I show that the resulting entry fees have some similarities to the welfare-maximizing and unilateral price setting benchmarks, but also differ in some important ways.
+In particular, the externalities that players entrants impose on the platform (cost of serving) and the other side (network externalities) are not fully incorporated into the entry fees, but shared across the affected players.
+Similarly, the value generated on each side also factors into the entry fee, contrary to the benchmark cases where it does not directly matter.
+This suggests, in situations where bargaining between players is plausible, certain effects might be overrepresented or missed if one assumes unilateral price-setting.
 
@@
 One obvious direction is to consider other solution concepts from cooperative game theory, such as the nuclelous\footnote{
-    It retains many of the desirable properties of the Shapley-value, such as existence and uniqueness, but it is contained in the core when the latter exists, and thus has a more immediate connection to non-cooperative bargaining theory.
+    It retains many of the desirable properties of the weighted values, such as existence and uniquenes while having a more immediate connection to non-cooperative bargaining theory.
 }.
-Another way to go is to build non-cooperative microfoundations for the random-order-value-based bargaining outcomes.
-Many such results exist for the Shapley value, and some also exist for the weighted value, but it might be interesting to see if some of the more general random order values can be motivated in a similar manner.
-
-Besides those theoretical directions, the practical applications are no less interesting.
-The proposed profit sharing framework could be embedded in more realistic models of various settings.
-The example application in this paper is a streamlined example of this, while \textcite{stancsics2023hybrid} provides a more detailed model involving hybrid platforms.
-Due to the simplicity of the results, this approach might be a viable replacement of unilateral price setting in cases where one does not wish to ascribe all the bargaining power to one player.
+Another is to consider either a wider, or different class of games, and see if the various values can be derived in a similar manner.
+A further direction is to consider is building non-cooperative microfoundations for the proposed random-order-value-based bargaining outcomes.
+Many such results exist for the Shapley value, and there are also a couple for the the weighted value, but motivating the more general random order value in a similar manner could be a significant step forward for bargaining theory.
+
+Besides these more theoretical directions, the practical applications are no less interesting.
+The proposed profit sharing framework could be embedded in more applied and detailed models describing various settings.
+The example application in this paper is a streamlined example of this, while \textcite{stancsics2023hybrid} is a further step in this direction, applying these ideas to a model of hybrid platforms.
+Due to the simplicity of the results, this approach might be a viable, almost drop-in replacement for unilateral price setting in cases where one does not wish to ascribe all the bargaining power to one player.
 

### 2024-03-01 src/paper/theory.tex
Improve example model

@@
     \begin{align*}
-        \varphi_P^\infty & = \int_0^1 \lambda_P t^{\lambda_P - 1} f(t^{\lambda_1}, \dots, t^{\lambda^L}) \dt
+        \varphi_P^\infty & = \int_0^1 \lambda_P t^{\lambda_P - 1} f(t^{\lambda_1}, \dots, t^{\lambda_L}) \dt
     \end{align*}
@@
     \begin{align*}
-        \varphi_{A^l}^\infty & = \int_0^1 t^{\lambda_P} \lambda_l t^{\lambda_l - 1} \partial_l f(t^{\lambda_1}, \dots, t^{\lambda^L}) \dt.
+        \varphi_{A^l}^\infty & = \int_0^1 t^{\lambda_P} \lambda_l t^{\lambda_l - 1} \partial_l f(t^{\lambda_1}, \dots, t^{\_L}) \dt.
     \end{align*}
@@
 
-In this section I will apply the results of the previous sections to a simple model of two-sided platforms.
-I follow the modelling approach of the monopoly platform case in \textcite{armstrong2006competition}, with a few extensions.
-There are two major departures from the original model.
-First, and most importantly, instead of letting the platform choose entry fees, I assume that they are the result of a bargaining process, and the outcomes are described by the weighted value.
-Second, instead of assuming that each player's utility is linear in the number of the other side's players, I allow for more general (power) functions, which lets me capture the substitutability of the two sides.
+In this section, I apply the ideas from the previous sections to a simple model of two-sided platforms.
+I follow the modelling approach of \textcite{armstrong2006competition}, focusing on the monopoly platform case.
+The model presented in this section expands on the original model in two main ways.
+First, instead of assuming that each player's utility is linear in the number of the other side's players, I allow for more general non-linear network effects. 
+This extension lets me capture and vary the substitutability of the two sides.
+Second, and most importantly, I add bargaining between the platform and the two sides.
+That is, besides the welfare-maximizing and unilateral price setting cases presented in \textcite{armstrong2006competition}, I also consider a case where the platform and the two sides bargain over the entry fees.
+I assume that the outcomes of this bargaining process are described by the weighted value.
 
@@
 
-Imagine a two-sided market with a continuum of players on both sides.
-Furthermore, assume that there is a single platform that connects the two sides.
-The utility that a player on side $i$ derives from participating in the market is an increasing function\footnote{
-    \textcite{armstrong2006competition} -- along with much of the literature on two-sided markets \parencite[e.g.][]{rochet2003platform,hagiu2006pricing} -- assumes that the utility of a player is linear in the number of players on the other side.
+Imagine a two-sided market with a continuum of players on both sides and a single platform connecting those two sides.
+Furthermore, assume that the utility that a player on side $i$ derives from participating in the market is an increasing function\footnote{
+    \textcite{armstrong2006competition} -- along with much of the early literature on two-sided markets \parencite[e.g.][]{rochet2003platform,hagiu2006pricing} -- assume that the utility of a player is linear in the number of players on the other side.
     Using a more general function allows me to model different degrees of network effects.
@@
 \begin{align*}
-    u_i = \alpha_i n_j ^ {\gamma_i} - p_i,
-\end{align*}
-where $\alpha \geq 0$ and $\gamma > 0$ determine the strength and shape of the network effects, respectively.
-
-Following \textcite{armstrong2006competition}, let us also model player entry in a reduced form manner.
+    u_i = \alpha_i n_j ^ {\gamma_i} - p_i.
+\end{align*}
+In this formulation, $\alpha \geq 0$ and $\gamma > 0$ determine the strength and shape of the network effects, respectively.
+
+Following \textcite{armstrong2006competition}, let us model player entry also in a reduced form manner.
 Assume that there is a continuum of potential entrants on both sides of the market.
@@
     Such assumptions are usually justified by some idiosyncratic cost of entry, the distribution of which determines the function $\phi$.
-    In the main text, for simplicity, I refrain from explicitly modeling this cost, but \cref{sec:explicit_entry_costs} provides a discussion of how to incorporate it into the model, and how it would affect bargaining outcomes.
+    For simplicity, I refrain from explicitly modeling this cost in the main text, but \cref{sec:explicit_entry_costs} provides a discussion of how one can incorporate it into the model, its impact on bargaining outcomes.
 }
@@
 
-I will consider two cases as to the timing and nature of the price-setting process, as well as a welfare-maximizing benchmark.
-For the latter, I derive the entry fees that maximize social welfare, i.e. the sum of the utilities of the two sides plus the platform's profit.
-After that, I will first consider a model analogous to that in \textcite{armstrong2006competition}, where the platform can unilaterally commit to any entry fees it wishes.
-Finally, I consider a model in which entry fees are the result of a bargaining process in such a way that the resulting utilities and profits correspond to the various players' weighted values.
-
-\subsection{Benchmark: welfare-maximizing entry fees}
-
-Let us consider first what entry fees would maximize social welfare.
-Instead of approaching this problem directly, let us rely on the following observation: if entry fees correspond to the externality that a player's entry imposes on the other side, then the resulting choices are welfare-maximizing.
+I consider two cases as to the determination of the entry fees, as well as a welfare-maximizing benchmark.
+By the latter, I mean the entry fees that maximize social welfare, i.e. the sum of the utilities of the two sides plus the platform's profit.
+After that, I first consider a model analogous to that in \textcite{armstrong2006competition}, where the platform can unilaterally commit to any entry fees it wishes.
+Finally, I examine and contrast the case where the entry fees the result of a bargaining process in such a way that the resulting utilities and profits correspond to the various players' (weighted) values.
+
+\subsection{Welfare-maximizing entry fees}
+
+Let us first consider what the entry fees would be if they were set to maximize social welfare.
+Instead of approaching this problem directly, I rely on the following observation: if entry fees correspond to the externality that a player's entry imposes on the other players, then the resulting entry decisions are welfare-maximizing.
+
 In this specific case, there are two externalities to consider.
 First, it costs the platform $F_i$ to serve an additional player on side $i$.
-Second, the entry of a player on side $i$ increases the utility on side $j$ due to positive network effects.
-Welfare is maximized when the price reflects the balance of these two  factors:
-\begin{align*}
-    p_i^* &= F_i - n_j \frac{\partial u_j}{\partial n_i} \\
-          &= F_i - \alpha_j \gamma_j n_j n_i^{\gamma_j - 1}.
-\end{align*}
+Second, the entry of a player on side $i$ increases the utility on side $j$ due to the presence of network effects.
+Welfare is maximized when the price reflects the balance of these two factors.
+\begin{proposition}
+    \label{prop:welfare_max_entry_fees}
+    The welfare-maximizing entry fees for side $i$ are characterized by
+    \begin{align*}
+        p_i^* = F_i - \alpha_j \gamma_j n_j n_i^{\gamma_j - 1}.
+    \end{align*}
+\end{proposition}
+
 As in \textcite{armstrong2006competition}, for any $\alpha_j > 0$ welfare-maximizing $F_i$ is below the platform's cost of serving player $i$.
 Thus, the platform's profit would necessarily be negative.
-It naturally cannot happen in the case when the platform sets the entry fees, or even the bargaining case.
+Therefore, while this case is useful as a benchmark, it is not particularly realistic when the platform has a say in determining entry fees, or even the possibility to exit the market.
 
@@
 \end{align*}
-for an individual player on side $i$.
-That is, side $i$ obtains the total utility generated by its players minus the cost of serving them, plus $\gamma_j$ times the total utility generated by the other side, too.
-This is due to the positive externality that side $i$ imposes on side $j$.
-
-Furthermore, the utility of type $i$ depends positively on both $\alpha_i$ (mechanically) and $\alpha_j$ (a stronger positive externality on the other players implies a lower entry fee and thus higher utility).
-Finally, if $n_i \geq e^{-\frac{1}{\gamma_j}}$, then $u_i$ is also increasing in $\gamma_j$.
-Both of the latter two effects are related to player $i$ being compensated for the positive externality it imposes on the other side.
-
-One can also obtain the total welfare of side $i$, as it is simply the number of entrants times the non-idiosyncratic utility of its players, plus the sum (integral) of the idiosyncratic utilities.
+for each individual player on side $i$.
+Consequently, the total welfare on side $i$, as it is simply the number of entrants times the non-idiosyncratic utility of its players, plus the sum (integral) of the idiosyncratic utilities.
 \begin{align}
-    \label{eq:W_star}
     W_i^*(n_i, n_j) = \alpha_i n_i n_j ^ {\gamma_i} + \gamma_j \alpha_j n_j n_i^{\gamma_j} - n_i F_i.
@@
 
+That is, players on side $i$ obtain the total generated by themselves, plus $\gamma_j$ times the total utility generated by the other side, net of the cost of serving them.
+The utility of side $i$ depends positively on both $\alpha_i$ (mechanically) and $\alpha_j$ (a stronger positive externality on the other players implies a lower entry fee and thus higher utility).
+Furthermore, it is increasing in the number of entrants on the other side through two channels: (1) entrants on the other side generate utility for side $i$ through network effects, and (2) players on side $i$ are compensated for the positive externality they impose on the other side.
+
+The effects of $\gamma_j$ are somewhat more complex, and are best understood through the dependence of the utility on side $i$ on $n_i$.
+Total welfare on side $i$ is always increasing in $n_i$, but individual utilities are not.
+If $\gamma_j > 1$ (i.e., network effects are convex), then $u_i$ is indeed increasing in $n_i$, as the positive externality each individual player imposes on the other side is increasing in the number of entrants.
+Conversely, when $\gamma_j < 1$, the positive externality of the whole side is still increasing in their number (therefore, $W_i$ is increasing in $n_i$), but the positive externality each individual player imposes is now a decreasing function of it (thus, $u_i$ is decreasing in $n_i$).
+
 \subsection{Platform sets prices unilaterally}
@@
 \begin{align*}
-    \pi(u_1, u_2) = \phi_1(u_1) [\alpha_1 \phi_2(u_2) ^ {\gamma_1} - u_1 - F_1] + \phi_2(u_2) [\alpha_2 \phi_1(u_1) ^ {\gamma_2} - u_2 - F_2].
-\end{align*}
-
-Let us assume that the above expression is concave, and thus the first order conditions characterize its maximum.
-Then, simply taking the partial derivatives with respect to $u_i$ yields the following condition for the optimal entry fees.
+    \pi_P(u_1, u_2) = \phi_1(u_1) [\alpha_1 \phi_2(u_2) ^ {\gamma_1} - u_1 - F_1] + \phi_2(u_2) [\alpha_2 \phi_1(u_1) ^ {\gamma_2} - u_2 - F_2].
+\end{align*}
+If the platform can set entry fees unilaterally, then it's problem is to choose $u_1$ and $u_2$ to maximize this expression.
+
 \begin{proposition}
-    \label{prop:platform_unilateral}
-    If the platform can set entry fees unilaterally, then optimal entry fees for side $i$ are characterized by
+    \label{prop:unilateral_entry_fees}
+    Assume that $\pi_P(u_1, u_2)$ is concave in $u_i$ and $u_2$.
+    Then, the profit-maximizing entry fees for side $i$ are characterized by
     \begin{align*}
@@
 As one would expect, profit-maximizing entry fees are higher than welfare-maximizing ones.
-In addition to the comparative statics of the welfare-maximizing case, the platform's entry fees also depend on the elasticity of entry.
-When it is low, the platform will set a high entry fee, as the loss of entrants is small.
-
-For ease of comparison with the bargaining case, let us also derive the utilities in this case:
-\begin{align*}
-    u_i^u(n_1, n_2) &= \alpha_i n_j ^ {\gamma_i} + \alpha_j \gamma_j n_j n_i^{\gamma_j - 1} - F_i - \frac{\phi_1(u_i)}{\phi'_1(u_i)}
-\end{align*}
-Welfare of side $i$ immediately follows in this case, too:
-\begin{align*}
-    \label{eq:W_u}
-    W_i^u(n_1, n_2) = \alpha_i n_i n_j ^ {\gamma_i} + \gamma_j \alpha_j n_j n_i^{\gamma_j} - n_i F_i - n_i^2 (\phi_i^{-1})'(n_i).
+In addition to the comparative statics of the welfare-maximizing case, the unilaterally chosen also depend on the elasticity of entry.
+When this elasticity is low, the can set high entry fees, as the reduction in the number of entrants is not relatively minor.
+
+For ease of comparison with the bargaining case, let us also derive the utilities and welfare on side $i$ in this case, too:
+\begin{align*}
+    u_i^u(n_1, n_2) &= \alpha_i n_j ^ {\gamma_i} + \alpha_j \gamma_j n_j n_i^{\gamma_j - 1} - F_i - \frac{\phi_1(u_i)}{\phi'_1(u_i)} \\
+    W_i^u(n_1, n_2) &= \alpha_i n_i n_j ^ {\gamma_i} + \gamma_j \alpha_j n_j n_i^{\gamma_j} - n_i F_i - n_i^2 (\phi_i^{-1})'(n_i).
 \end{align*}
@@
 
-Finally, let us consider the case when the platform and the players bargain over the value they generate.
+Finally, let us consider the case when the platform and the entrants bargain over the value they generate.
 Assume that $n_1$ and $n_2$ players have decided to enter on sides $1$ and $2$, respectively.
@@
 The characteristic function of the game takes a similar form to that in \cref{sec:many_sided}.
-If the platform is not part of the coalition, then the value the coalition can generate is zero.
+If the platform is not a member of a coalition, then the value that coalition can generate is zero.
 Otherwise, it is simply the sum of the utilities of the two sides minus the cost of serving them.\footnote{
-    Entry fees do not matter, as they are within-coalition transfers, and thus do not affect the total value.
+    Entry fees paid to the platform do not matter, as they are within-coalition transfers, and thus do not affect the total value.
 }
@@
 \begin{proposition}
-    \label{prop:platform_bargaining_last_period}
-    The weighted values of the various sides without idiosyncratic costs are
+    \label{prop:bargaining_entry_fees}
+    The weighted values of the various sides are
     \begin{alignat*}{4}
         \pi_P^b(n_1, n_2) &= \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_P^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_P^{b_2}} \alpha_2 n_2 n_1^{\gamma_2} &&- \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_1}}_{\coloneqq S_P^{c_1}} n_1 F_1 &&- \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_2}}_{\coloneqq S_P^{c_2}} n_2 F_2 \\
-        w_1^b(n_1, n_2) &= \underbracket{\frac{\lambda_1}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_1^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_1 \gamma_2}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_1^{b_2}}  \alpha_2 n_2 n_1^{\gamma_2} &&- \underbracket{\frac{\lambda_1}{\lambda_P + \lambda_1}}_{\coloneqq S_1^{c_1}} n_1 F_1 && \\
-        w_2^b(n_1, n_2) &= \underbracket{\frac{\lambda_2\gamma_1}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_2^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_2}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_2^{b_1}} \alpha_2 n_2 n_1^{\gamma_2} && &&- \underbracket{\frac{\lambda_2}{\lambda_P + \lambda_2}}_{\coloneqq S_2^{c_2}} n_2 F_2.
+        W_1^b(n_1, n_2) &= \underbracket{\frac{\lambda_1}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_1^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_1 \gamma_2}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_1^{b_2}}  \alpha_2 n_2 n_1^{\gamma_2} &&- \underbracket{\frac{\lambda_1}{\lambda_P + \lambda_1}}_{\coloneqq S_1^{c_1}} n_1 F_1 && \\
+        W_2^b(n_1, n_2) &= \underbracket{\frac{\lambda_2\gamma_1}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_2^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_2}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_2^{b_1}} \alpha_2 n_2 n_1^{\gamma_2} && &&- \underbracket{\frac{\lambda_2}{\lambda_P + \lambda_2}}_{\coloneqq S_2^{c_2}} n_2 F_2.
     \end{alignat*}
@@
 
-There are four parts that the total welfare $w(n_1, n_2)$ is divided into: utility generated by side $1$ and $2$, and cost of serving side $1$ and $2$.
+Total welfare $w(n_1, n_2)$ can be divided into four parts: utility generated by side $1$ and $2$, and the costs of serving side $1$ and $2$.
 Each side's share of these parts is given by $S_i^{b_1}, S_i^{b_2}, S_i^{c_1}$ and $S_i^{c_2}$, respectively.
 As it turns out, these shares only depend on the bargaining weights ($\lambda_P, \lambda_1, \lambda_2$) and the network effects ($\gamma_1, \gamma_2$), but not on the actual number of entrants.\footnote{
-    This is due to the characteristic function being a polynomial in the number of entrants.
-    Just like in \cref{sec:power_function_example}, the parts of the polynomial are divided in a constant proportion.
+    This is due to the characteristic function being a polynomial of the number of entrants.
+    Just like in \cref{sec:power_function_example}, each constituent of the polynomial are divided in a constant proportion.
 }
 Furthermore, all of these shares are increasing in one's own bargaining weight, and decreasing in the others' weights.
-Finally, the share of side $i$ from the value generated on side $j$ is also increasing in $\gamma_j$.
-This means that if players on side $i$ are less substitutable / more complementary in terms of generating utility on side $j$, then they will receive a larger share of the value generated on that side.
-
-These utilities are remarkably similar in structure to the welfare maximizing case in \cref{eq:W_star}.
+Finally, and perhaps most interestingly, the share of side $i$ from the value generated on side $j$ is also increasing in $\gamma_j$.
+This means that if players on side $i$ are less substitutable (or, equivalently, more complementary) in terms of contributing to the utility of the other side, then they will receive a larger share of the value generated there.
+
+These utilities are remarkably similar in structure to those obtained in the welfare maximizing case.
 The main difference is that each part (both costs and positive utilities) is reweighted, and side $i$ only receives a fraction of it.
@@
 }
-
-For better comparison, let us also examine implied entry fees and non-idiosyncratic utilities.
-The latter is the difference between the average welfare and the average idiosyncratic cost:
+These similarities and differences are examined in more detail in the next subsection.
+
+For better comparison, let us also derive implied entry fees and utilities.\footnote{
+    If one wished to close the model, the number of entrants in equilibrium could be obtained by solving the system of equations $n_i = \phi_i(u_i(n_1, n_2)), n \in \{1, 2\}$, just like in the other cases.
+}
+The latter is simply average welfare, i.e.:
 \begin{align*}
@@
 \end{align*}
-If one wished to close the model, the number of entrants in equilibrium could be obtained by solving the system of equations $n_i = \phi_i(u_i(n_1, n_2)), n \in \{1, 2\}$.
-Finally, the implied entry fees can be calculated from the equation $u_i = \alpha_i n_j^{\gamma_i} - p_i$, yielding
+Finally, the implied entry fees can be calculated from the equation $u_i = \alpha_i n_j^{\gamma_i} - p_i$, giving
 \begin{align*}
@@
 
-Let us now compare the outcomes of the three cases described in this section.
+Let us now compare the outcomes of the three cases described in the previous subsections.
 To highlight the similarity to \textcite{armstrong2006competition}, I will first consider the case of linear network effects.
-Furthermore, for simplicity of exposition, I start by considering the non-weighted Shapley value before moving on to the weighted value.
+Furthermore, for simplicity of exposition, I start by examining the non-weighted Shapley value before moving on to the weighted value.
 
@@
 
-All of these expressions bear some similarities to each other, in that the price is somehow related to the externalities that an entrant imposes on the other players.
+All of these expressions bear some similarities to each other in that the price is somehow related to the externalities that an entrant imposes on the other players.
 In fact, the welfare-maximizing price is just that: the cost of serving one additional player (1) and the positive externality imposed on the other side (2).
 The unilateral pricing case also includes these two factors in full, but also adds a third factor, related to the elasticity of entry (3).
-Namely, the platform extracts some of the surplus generated by the entrants, and the surplus it can extract depends on $\phi'_i(u_i)$.
+Namely, the platform extracts some of the surplus generated by the entrants, and the surplus it wants to extract depends on the elasticity of entry, $\phi'_i(u_i)$.
 It is the same mechanism that leads to markups in a simple monopolistic pricing model.
@@
 The bargaining case also includes the first two factors, albeit they are somewhat different.
-As opposed to the first two cases, the price only contains some fraction of the externalities, and the rest is shared with the platform and the other side.\footnote{
-    Due to the linearity of the model, various parts of the value are shared equally between players who participate in producing them.
-    This is the reason why, for example, the platform and the firms share the cost of serving the entrants (1) equally, or that all three types of players share the value generated on a given side (2) equally.
+As opposed to the first two cases, the price only contains some fraction of the externalities, while the rest is shared with the platform and the other side.\footnote{
+    Due to the linearity of the model and the symmetry of the Shapley value, each part of the value is shared equally between players who participate in producing them.
+    This is the reason why, for example, the platform and the firms share the cost of serving the entrants (1) equally, or why all three types of players share the value generated on a given side (2) equally.
 }
@@
 For the most part, the intuition is the same as in the linear case.
-The welfare-maximizing price is still the cost of serving one additional player (1) and the positive externality imposed on the other side (2).
-In addition to those, the unilaterally set entry fee includes a markup related to the elasticity of entry (3).
-Finally, in the case of bargaining, these factors do not appear in full, but are shared with the platform and the other side.
-
-There is one important difference in the bargaining case, however.
+In fact, in the welfare-maximizing and unilateral pricing cases, nothing changes apart from the marginal externality imposed on the other side (2) being slightly different.
+On the other hand, there is one important difference in the bargaining case.
 In the linear case, the terms related to the value generated on each side were shared between the players in a constant proportion, independent of the model parameters.
-In the non-linear case, however, these shares do depend on the shape of the network effects.
+In this non-linear case, however, these shares depend on the shape of the network effects.
 In particular, when side $i$'s network externality on side $j$ is more convex (e.g. firms on side $i$ are less substitutable), then it receives a larger share of the value generated on the other side.
 This is signified by the fact that the coefficient of side $i$'s network externality, $\frac{\gamma_j}{2 + \gamma_j}$, is increasing in $\gamma_j$.
-This result shows that the bargaining outcomes are not just a trivial distribution of the value, but also take into account the shape of the network effects.
-
-Finally, for completeness, let us consider the case of weighted values.
+This result demonstrates that bargaining outcomes are not just a split of the value, but also take into account the shape of the network effects.
+
+Finally, for completeness, let us also consider the case of weighted values.
 The following theorem summarizes the entry fees in this most general case.
 \begin{theorem}
+    \label{prop:all_entry_fees}
     Let $p_i^*$, $p_i^u$ and $p_i^b$ denote the welfare-maximizing, unilateral pricing and bargaining entry fees, respectively.
@@
 
-In the case of the linear terms, such as the cost of serving one additional player (1), the addition of bargaining weights simply leads to players shareing the cost in a constant proportion, according to their weights.
-The higher the weight, the larger the share for the player.
-While the latter is true for non-linear terms, as well, the influence of the weights is more complex, as it also depends on the shape of value function.
+In the case of the cost of serving one additional player (1), the addition of bargaining weights simply leads to players sharing the cost in a constant proportion, according to their weights.\footnote{
+    This is because this term is linear in the number of entrants.
+}
+The higher the weight, the larger the share for any given player.
+While the latter observation is true for non-linear terms, as well, the influence of the weights is more complex for those.
+Namely, it also depends on the shape of value function.
 For example, in term (2), $\lambda_i$ interacts with the parameter determining the shape of the network effects, $\gamma_j$
@@
 Whether bargaining leads to a higher or lower total welfare depends on the parameters of the model.
-For example, if $\lambda_P$ is very high, then $p_i^b > p_i^u > p_i^*$, leading to fewer firms entering and lower total surplus than not only the welfare-maximizing case, but also the unilateral pricing case.
-That is, everybody looses from bargaining.\footnote{
-    In such a case, the platform would like to set lower entry fees that what it can achieve via bargaining.
-    While in some settings it is very plausible that it can do it, in others commitment problems might prevent it from doing so.
-}
-
+For example, if $\lambda_P$ is very high, then $p_i^b > p_i^u > p_i^*$, leading to fewer firms entering and lower total surplus not only than the welfare-maximizing case, but also than the unilateral pricing case.
+That is, it can happen that everybody looses from bargaining.\footnote{
+    In such a case, the platform would like to set lower entry fees than what it can achieve via bargaining.
+    While in some settings it makes sense to assume that it can do that, in others, commitment issues might prevent it from doing so.
+}
 On the other hand, if $\lambda_P$ is sufficiently low, then one can find weights $\lambda_1, \lambda_2$, such that $p_i^u > p_i^b > p_i^*$.
-In such a case, the platform would like to set higher entry fees than what it can achieve via bargaining.
-The total welfare is also between the welfare-maximizing and unilateral pricing cases, therefore bargaining can be beneficial as an alternative of unilateral pricing.
-The platform, however, achieves a lower profit than if it could set the entry fees unilaterally.
+In such a case, the platform would like to set higher entry fees than what it can achieve via bargaining for both sides.
+Furthermore, the total welfare under bargaining is between the welfare-maximizing and unilateral pricing cases.
+Therefore, whether bargaining leads to higher or lower welfare than unilateral pricing depends on model parameters.
+The platform, however, always achieves a (weakly) lower profit than if it could set the entry fees unilaterally.
 
@@
 The reason is that the platform's profit is always non-negative in the bargaining case, while it is negative in the welfare-maximizing case.
-This also implies that the total welfare is strictly lower than in the welfare-maximizing case.
-Therefore, while bargaining can be welfare-increasing compared to unilateral price setting, it can not achieve the highest possible total welfare.\footnote{
+This also implies that the total welfare is strictly lower under bargaining than in the welfare maximizing benchmark.
+Therefore, while bargaining can be welfare-improving compared to unilateral price setting, it can not achieve the highest possible total utility.\footnote{
     One could argue that the welfare maximizing case is not a realistic benchmark anyway, as it assumes that the platform is making a loss.
@@
 
-\section{Idiosyncratic entry costs are explicitly modeled}
+\section{Idiosyncratic entry costs are modeled explicitly}
 \label{sec:explicit_entry_costs}
@@
 
+\begin{proof}[Proof of \cref{prop:welfare_max_entry_fees}]
+    The (marginal) cost of serving an entrant on side $i$ is $F_i$.
+    The marginal network externality it generates on the other side is
+    \begin{align*}
+        n_j \frac{\partial u_j}{\partial n_i} = \alpha_j \gamma_j n_j n_i^{\gamma_j - 1}.
+    \end{align*}
+    Welfare is maximized when the cost of entry equals the externality from entry, i.e.:
+    \begin{align*}
+        p_i^* &= F_i - \alpha_j \gamma_j n_j n_i^{\gamma_j - 1}
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:unilateral_entry_fees}]
+    By assumption, $\pi_P(u_1, u_2)$ is concave in $u_1$ and $u_2$, therefore the first-order conditions are necessary and sufficient for a maximum.
+    Simply taking the partial derivatives with respect to $u_i$ yields the following condition for the optimal entry fees:
+    \begin{align*}
+        p_i^u = F_i - \alpha_j \gamma_j n_j n_i^{\gamma_j - 1} + \frac{\phi_1(u_1)}{\phi'_1(u_1)}.
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:bargaining_entry_fees}]
+    From \cref{prop:many_sided_weighted}, the value of player $P$ is
+    \begin{align*}
+        \pi_P &= \int_0^1 \lambda_P t^{\lambda_P - 1} w(t^{\lambda_1} n_1, t^{\lambda_2} n_2) \dt \\
+        &= \int_0^1 \lambda_P t^{\lambda_P - 1} \left[ \alpha_1 t^{\lambda_1} n_1 t^{\lambda_2\gamma_1} n_2^{\gamma_1} + \alpha_2 t^{\lambda_2} n_2 t^{\lambda_1\gamma_2} n_1^{\gamma_2} + t^{\lambda_1} F_1 n_1 + t^{\lambda_2} F_2 n_2 \right] \dt \\
+        &= \frac{\lambda_P}{\lambda_P + \lambda_1 + \lambda_2\gamma_1} \alpha_1 n_1 n_2^{\gamma_1} + \frac{\lambda_P}{\lambda_P + \lambda_2 + \lambda_1\gamma_2} \alpha_2 n_2 n_1^{\gamma_2} - \frac{\lambda_P}{\lambda_P + \lambda_1} n_1 F_1 - \frac{\lambda_P}{\lambda_P + \lambda_2} n_2 F_2.
+    \end{align*}
+    Similarly, the value of side $i \in \{1, 2\}$ is
+    % TODO: improve formalism in the first line of formula below?
+    \begin{align*}
+        W_i &= \int_0^1 t^{\lambda_P} \lambda_i t^{\lambda_i - 1} \partial_i w(t^{\lambda_1} n_1, t^{\lambda_2} n_2) \dt \\
+        &= \int_0^1 t^{\lambda_P} \lambda_i t^{\lambda_i - 1} \left[ \alpha_i n_i t^{\lambda_j \gamma_i} n_j^{\gamma_i} + \alpha_j \lambda_i \gamma_j t^{\lambda_j} n_j t^{\lambda_i (\gamma_j - 1)} n_i^{\gamma_j} - n_i F_i \right] \dt \\
+        &= \frac{\lambda_i}{\lambda_P + \lambda_i + \lambda_j\gamma_i} \alpha_i n_i n_j^{\gamma_i} + \frac{\lambda_i \gamma_j}{\lambda_P + \lambda_j + \lambda_i\gamma_j} \alpha_j n_j n_i^{\gamma_j} - \frac{\lambda_i}{\lambda_P + \lambda_1} n_i F_i.
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:all_entry_fees}]
+    See the proof of \cref{prop:welfare_max_entry_fees,prop:unilateral_entry_fees,prop:bargaining_entry_fees}.
+\end{proof}
+
 \end{document}

### 2024-03-04 src/paper/application.tex
Add links to the latest draft
Fix latest version link
Minor corrections

@@
 
+\newcommand*{\thisdraft}{\normalsize{This draft: \today}} 
+\newcommand*{\firstdraft}{\normalsize{First draft: 27 March 2023}} 
+\newcommand*{\latestversion}{\normalsize{Latest version: \href{https://stanmart.github.io/ValueOfIntermediation/application.pdf}{stanmart.github.io/ValueOfIntermediation/application.pdf}}}
+
 \definecolor{myblue}{rgb}{0.3, 0.45, 0.69}
@@
 \title{Hybrid platforms and bargaining power}
-\author{Martin Stancsics}
+\author{Martin Stancsics \\ \normalsize{University of Zurich}}
+\date{\thisdraft \\ \firstdraft \\ \latestversion}
 
@@
 One can also find examples of similar behavior outside the platform setting, too.
-For example BMW is preparing to sell cars directly to consumers in the US, competing with its dealership network.
+For example, a number of car manufacturers are planning to sell directly to consumers in addition to selling through their dealership networks.
 
@@
 
-In parallel to the increasing regulatory interest, the academic literature has also been steadily growing on the topic of hybrid platforms.
+In parallel to the increasing regulatory interest, the academic literature on the topic of hybrid platforms has also been steadily growing.
 \textcite{hagiu2022should} investigate how practices, such as self-preferencing and steering can distort competition on hybrid platforms.
-They argue, however, that if such behavior is regulated, the platform selling its own products can be beneficial for consumers.
+They argue that -- while such practices are problematic and can have negative welfare effects -- with proper regulation the platform selling its own products can be beneficial for consumers.
 In contrast to this positive result, \textcite[]{anderson2021hybrid} find that even in the absence of such behavior, allowing hybrid operation might have negative consequences due to platforms having an incentive to exclude competitors from the market.
@@
 In particular, I propose an analytically tractable framework which captures many important aspects of bargaining between one large and a continuum of small players, and apply it to the setting of a hybrid platform facing a continuum of potential entrants.
-The framework quite general, and does not depend on a specific demand structure, investment cost assumptions, and there is even some flexibility to the assumptions about bargaining outcomes.
+The framework is quite general: it does not depend on a specific demand structure and investment cost assumptions, and there is even some flexibility to the assumptions about bargaining outcomes.
 Nevertheless, even in this stylized setting, I can highlight certain factors which might cause a platform's hybrid operation to potentially have negative effects. 
@@
 As a more specific example, I also examine this phenomenon in a more fully specified model, too.
-In particular, I provide some sharper results under the assumption of logit-like demand and a specific form of the bargaiing rule.
+In particular, I provide some sharper results under the assumption of logit-like demand and a specific form of the bargaining rule.
 I show that, in the presence of bargaining, hybrid operation can indeed have negative welfare consequences for consumers.
@@
 
-The closest paper to this second, more applied part of this one is \textcite{anderson2021hybrid}.
+The closest model to the second, more applied part of this paper one is the one proposed by \textcite{anderson2021hybrid}.
 The main difference between the two boils down to how the entry fee is decided.
-In the former, of the platform setting a percentage entry fee and being able to commit to it, I assume that (1) platforms charge a lump-sum entry fee and that (2) this entry fee is the result of a negotiation process\footnote{
+In \textcite{anderson2021hybrid}, the platform sets a percentage entry fee, and the entrants decide whether to enter or not.
+In contrast to this, I assume that (1) platforms charge a lump-sum entry fee and that (2) this entry fee is the result of a negotiation process\footnote{
     The bargaining process is modeled using a solution concept from cooperative game theory, namely the Shapley-value.
@@
 Certain structures, such as vertical relationships, or even traditional retail stores share a number of features with platforms (notably, the presence of a dominant, indispensable entity), and can be modeled in much the same way.
-Therefore, the methodology and results in this paper may also be of interest to researchers studying questions such as retailers having their own private labels \parencite{steiner2004nature} or vertical integration in upstream-downstream markets \parencite{hart1990vertical,aghion2006vertical}.
+Therefore, the methodology and results in this paper are also of interest to researchers studying questions such as retailers having their own private labels \parencite{steiner2004nature} or vertical integration in upstream-downstream markets \parencite{hart1990vertical,aghion2006vertical}.
 \textcite{de2005vertical} and \textcite{montez2007downstream}, in which bargaining between the upstream and downstream firms take the center stage, are particularly closely related.
@@
 
-Assume that there are three types of players in the market: a platform $P$, a continuum of fringe sellers $F_i$ ($i \in [0, N_C$) and a continuum of consumers $C_j$ ($j \in [0, N_C$]).
+Assume that there are three types of players in the market: a platform $P$, a continuum of fringe sellers $F_i$ ($i \in [0, N_C$]) and a continuum of consumers $C_j$ ($j \in [0, N_C$]).
 The fringe firms have one product each, which they can only sell through the platform.
@@
     \label{ass:profit_sharing}
-    Let $N_P, N_F, N_C \geq 0$ be the number of platform products, fringe firms and consumers, respectively.
-    Thus, the value that players create together is given by $\Pi(N_P, N_F, N_C) = N_C f(N_P, N_F)$.
-    Let us denote the platform's and the fringe's profit shares by $\pi_P(N_P, N_F, N_C)$ and $\pi_F(N_P, N_F, N_C)$, respectively.
-    Then, the following holds:
+    Let $w_P, w_F: \mathbb{R}^+_0 \to \mathbb{R}^+_0$ be non-negative functions such that the following condition holds: $\pi_P(N_P, N_F, N_C) + \pi_F(N_P, N_F, N_C) \leq \Pi(N_P, N_F, N_C)$.
+    %TODO: can I make this condition nicer?
+    Then, the platform's profit ($\pi_P(N_P, N_F, N_C)$) and the fringe's profit ($\pi_F(N_P, N_F, N_C)$) are given by:
     \begin{align*}
@@
     \end{align*}
-    Furthermore, $w_P \geq 0$ and $w_F \geq 0$ are such that $\pi_P(N_P, N_F, N_C) + \pi_F(N_P, N_F, N_C) \leq \Pi(N_P, N_F, N_C)$.
 \end{assumption}
@@
 Furthermore, in \cref{sec:two_sided}, I also consider the case of two-sided bargaining, where the consumers also participate in the negotiation over the value produced.
-Finally, \cref{sec:total_welfare_one_sided} explores the case of the platform being able to extract all of the consumer surplus through from consumers.
+Finally, \cref{sec:total_welfare_one_sided} explores the case of the platform being able to extract all of the consumer surplus from consumers.
 
 Throughout the analysis, I treat the product variety of the platform and the number of consumers as exogenous, and focus on the equilibrium number of fringe firms.
-Nevertheless, the results regarding equilibrium platform profits and consumer surplus are somewhat indicative of the potential general equilibrium behavior of the former two, as well.
+Nevertheless, the results regarding equilibrium platform profits and consumer surplus are indicative of the potential general equilibrium behavior of the former two, as well.
 
@@
 }
-Later on, I look at the case of the platform obtaining consumer surplus, and also the case of consumers participating in the bargaining over the total surplus.
+Later on, I look at the case of the platform appropriating consumer surplus, and also the case of consumers participating in the bargaining over the total surplus.
 
@@
 \end{align*}
-Then, equilibrium per-product demand and variable profit can be expressed as $V_T/ A$ and $\mu V_T/ A$, respectively, and the total aggregate is simply
-\begin{align*}
-    A = N_P V_P + N_F V_F + 1.
-\end{align*}
+$V_T$ can be thought of as the value of the product, also accounting for marginal costs and taste heterogeneity.
+In this logit demand system, the value of the product is the only parameter that matters for market shares and profits.
+In fact, equilibrium per-product demand and variable profit can simply be expressed as $V_T/ A$ and $\mu V_T/ A$, respectively, where
+\begin{align*}
+    A = N_P V_P + N_F V_F + 1
+\end{align*}
+denotes the total aggregate.
 
@@
 \end{proposition}
-Note that in the first case (\cref{eq:aggregate_eq}), the size of the aggregate does not depend on the platforms' product variety or the platform's product advantage.
+Note that in the first case (\cref{eq:aggregate_eq}), the size of the aggregate does not depend on the platforms' product variety or the platform's product value.
 The intuition behind this is that per-firm fringe profits only depend on these factors indirectly, through the size of the aggregate.
@@
 If the platform is operating in the hybrid regime, less fringe firms are needed to achieve the (fixed) equilibrium aggregate, therefore there is less expenditure on investment costs, which is essentially wasted.
-Consequently, in the hybrid regime, the marginal derivative of optimal profits with respect to the platform's product variety is simply the fringe's investment cost, adjusted for the possible difference in product advantage:
+Consequently, in the hybrid regime, the derivative of optimal profits with respect to the platform's product variety is simply the fringe's investment cost, adjusted for the possible difference in product value:
 \begin{align*}
@@
 As a consequence of this, equilibrium total aggregate is also decreasing in $N_P$.\footnote{
-    The same result also holds true for an increase in the paltform's product advantage $V_P$.
+    The same result also holds true for an increase in the platform's product advantage $V_P$.
 }
-As, in this model, consumer welfare is monotone in the total aggregate, this implies that consumer welfare is decreasing in the number of the platform's products (\cref{fig:welfare}).
+As, in this model, consumer welfare is monotone in the total aggregate, this implies that consumer welfare is decreasing in the number of the platform's products (\cref{fig:welfare_consumer_surplus}).
 Therefore, as opposed to the benchmark model, the platform becoming more hybrid leads to a reduction in consumer welfare.\footnote{
@@
         \caption{Consumer surplus ($CS$)}
+        \label{fig:welfare_consumer_surplus}
     \end{subfigure}

### 2024-04-06 src/paper/application.tex
Add timing figure

@@
 \usetikzlibrary{intersections}
+\usetikzlibrary{positioning}
 \pgfplotsset{compat=1.17}
@@
 In the benchmark model, the game starts by the platform announcing and committing to an entry fee $F_F$.\footnote{
-    Without no commitment power, but the ability to set any prices after fringe firms make their investment decisions, the platform would charge an entry fee that would make the fringe profits zero \emph{sans the investment cost}.
+    With no commitment power, but the ability to set any prices after fringe firms make their investment decisions, the platform would charge an entry fee that would make the fringe profits zero \emph{sans the investment cost}.
     This would lead to a trivial equilibrium, where no firm enters.
@@
 
-In the baseline model, each player gets their profits from the sales of their products, plus the pre-agreed entry fees from the first period.
 In the model with bargaining, the platform and the fringe distribute total profits according to their Shapley values.
@@
 On the other hand, in the bargaining model, I assume that the entry fee is the result of a negotiation between the parties.
+\cref{fig:timing} illustrates this difference.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[node distance=2cm, auto]
+            \node[align=center] (entry_fee) {Platform unilaterally sets the entry fee \\ $[F_F]$};
+            \node[align=center] (entry_decision) [below of=entry_fee] {Potential entrants decide to enter \\ at cost $I_F + F_F$ \\ $[N_F]$};
+            \node[align=center] (sales) [below of=entry_decision] {Platform and fringe sell products \\ $[\pi_{Fi}^v, \pi_P^v]$};
+            \node[align=center] (final) [below of=sales] {Final profits are realized \\ $[\pi_{Fi}^t, \pi_P^t]$};
+            \draw[->] (entry_fee) -- (entry_decision);
+            \draw[->] (entry_decision) -- (sales);
+            \draw[->] (sales) -- (final);
+        \end{tikzpicture}
+        \caption{Benchmark model (platform sets the entry fee unilaterally)}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[node distance=2cm, auto]
+            \node[align=center] (entry_decision) {Potential entrants decide to invest \\ at cost $I_F$ \\ $[N_F]$};
+            \node[align=center] (entry_fee) [below of=entry_decision] {Entry fees are negotiated \\ between platform and $N_F$ fringe firms \\ $[F_F]$};
+            \node[align=center] (sales) [below of=entry_fee] {Platform and fringe sell products \\ $[\pi_{Fi}^v, \pi_P^v]$};
+            \node[align=center] (final) [below of=sales] {Final profits are realized \\ $[\pi_{Fi}^t, \pi_P^t]$};
+            \draw[->] (entry_decision) -- (entry_fee);
+            \draw[->] (entry_fee) -- (sales);
+            \draw[->] (sales) -- (final);
+        \end{tikzpicture}
+        \caption{Bargaining model (platform and fringe negotiate over the entry fee)}
+    \end{subfigure}
+    \caption{Timing of the models}
+    \label{fig:timing}
+\end{figure}
 

### 2024-04-06 src/paper/application.tex
Add motivation for lump sum fees

@@
 There is an infinite measure of fringe firms, who are deciding whether to enter the market.
-Entering has two, separate costs: an exogenous investment cost $I_F$, and the platform entry fee $F_F$.
+Entering has two, separate costs: an exogenous investment cost $I_F$, and the lump-sum platform entry fee $F_F$.
 One can conceptualize the first as usual fixed costs, such as the cost of setting up production, or designing a product.
 Meanwhile, the second is a payment to the platform for using its services.
+While percentage fees are more common both in the literature and in practice, I assume a lump-sum fee for a few reasons.
+First, and most importantly, revenue-based fees enter the entrants' pricing decision, and thus create a channel through which platforms distort competition.
+I want to show that even in the absence such distortions, hybrid platforms can have a significant impact on competition.
+Furthermore, due to this distortion, the resulting game could not be represented as a transferable utility game, and the proposed solution concept would not be applicable.
+Finally, lump-sum fees do make sense in settings when individual negotiation takes place and contracts are not standardized.
 

### 2024-04-24 src/paper/application.tex
Minor text improvements

@@
 
-The first set of results in this paper go beyond the aforementined studies in the sense that they illuminate the effects of hybridness as a more abstract phenomenon, and thus also highlight the similarities between the hybrid platform literature and adjacent ones.
+The first set of results in this paper go beyond the aforementioned studies in the sense that they illuminate the effects of hybridness as a more abstract phenomenon, and thus also highlight the similarities between the hybrid platform literature and adjacent ones.
 Certain structures, such as vertical relationships, or even traditional retail stores share a number of features with platforms (notably, the presence of a dominant, indispensable entity), and can be modeled in much the same way.
@@
 This paper is also related to various other strands of the industrial organization literature.
-For one, it belongs to the research agenda on understanding platforms and their role in the economy \parencite[e.g.][]{rochet2003platform,hagiu2004optimal,armstrong2006competition,evans2011platform,lee2014competing}.
+Most generally, it is a contribution to the research agenda on understanding platforms and their role in the economy \parencite[e.g.][]{rochet2003platform,hagiu2004optimal,armstrong2006competition,evans2011platform,lee2014competing}.
 Furthermore, it is somewhat adjacent to the literature on the importance of exclusive content \parencite[e.g.][]{hagiu2011exclusivity,lee2013vertical,dou2014sell,weeds2016tv}, with the difference that instead of exclusive content giving an advantage against competing platforms, in this paper, own products provide an advantage over potential entrants.
@@
 }
-Therefore, the total profits of the platform and the fringe taken together have a simple functional form $N_C f(N_P, N_F)$.\footnote{
+
+As a consequence, the total profits of the platform and the fringe taken together have a simple functional form $N_C f(N_P, N_F)$.\footnote{
     Based on the same reasoning, it is easy to see that total welfare has a similar form.

### 2024-05-03 src/paper/application.tex
Rewrite model section in terms of the fully specified model

@@
 This section introduces the model used throughout the paper.
+% TODO: better motivation
 I use the terms ``platform'' and ``fringe sellers'', and present my ideas in the context of an intermediated market, such as an online marketplace or an application store.
@@
 
-\subsection{Production}
-
-I make use of a reduced-form, but quite general approach to model production and demand.
-First, I assume that all fringe firms and consumers are ex-ante identical.
-This implies two things: (1) per-consumer profits are just a function of the number of fringe and platform products, and (2) the platform's and the fringe's profits are linear in the number of consumers.\footnote{
-    While normally this would exclude fixed production costs, this is not the case here.
-    $\Pi$ only describes profits conditional on $N_C$ and $N_F$ players entering the platform.
-    Fixed costs can be incorporated into the first stage of the game, where fringe firms decide whether to enter or not.
+\subsection{Overview}
+
+There is an infinite measure of fringe firms, who are deciding whether to enter the market.
+Entering has two, separate costs: an exogenous investment cost $I_F$, and the lump-sum platform entry fee $F_F$.
+One can conceptualize the first as usual fixed costs, such as the cost of setting up production, or designing a product.
+Meanwhile, the second is a payment to the platform for using its services.
+While percentage fees are more common both in the literature and in practice, I assume a lump-sum fee for a few reasons.
+First, and most importantly, revenue-based fees enter the entrants' pricing decision, and thus create a channel through which platforms distort competition.
+I want to show that even in the absence such distortions, hybrid platforms can have a significant impact on competition.
+Furthermore, due to this distortion, the resulting game could not be represented as a transferable utility game, and the proposed solution concept would not be applicable.
+Finally, lump-sum fees do make sense in settings when individual negotiation takes place and contracts are not standardized.
+
+In the benchmark model, the game starts by the platform announcing and committing to an entry fee $F_F$.\footnote{
+    With no commitment power, but the ability to set any prices after fringe firms make their investment decisions, the platform would charge an entry fee that would make the fringe profits zero \emph{sans the investment cost}.
+    This would lead to a trivial equilibrium, where no firm enters.
 }
-
-As a consequence, the total profits of the platform and the fringe taken together have a simple functional form $N_C f(N_P, N_F)$.\footnote{
-    Based on the same reasoning, it is easy to see that total welfare has a similar form.
+In the bargaining case, the platform cannot commit to entry fees at this point.
+Next, each fringe firm decides whether to create a product at cost $I_F$ and enter the market.
+In the bargaining model, the entry fee is decided at this point as a result of some negotiation\footnote{
+    The negotiation process, or rather its outcome is described in detail in \cref{sec:cooperative_game}.
+} between the platform and the firms that have made the investment.
+After this, the firms that made the investment pay the platform entry fees, too.
+
+From this point on, the game proceeds in the same way in both models.
+The platform and the fringe firms simultaneously choose the prices for their products, engaging in monopolistic competition.
+Finally, consumers make their purchase decisions, and profits are realized.
+
+In the model with bargaining, the platform and the fringe distribute total profits according to their Shapley values.
+One can also think of the latter as agreeing on an entry fee that makes final profits net entry fees equal to the Shapley value of the various players.
+
+The main difference between the benchmark and the bargaining model is in determining the entry fee $F_F$.
+In the former, the platform unilaterally sets the fee, and the fringe treats it as a take it or leave it offer.
+On the other hand, in the bargaining model, I assume that the entry fee is the result of a negotiation between the parties.
+\Cref{fig:timing} illustrates this difference.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[node distance=2cm, auto]
+            \node[align=center] (entry_fee) {Platform unilaterally sets the entry fee \\ $[F_F]$};
+            \node[align=center] (entry_decision) [below of=entry_fee] {Potential entrants decide to enter \\ at cost $I_F + F_F$ \\ $[N_F]$};
+            \node[align=center] (sales) [below of=entry_decision] {Platform and fringe sell products \\ $[\pi_{Fi}^v, \pi_P^v]$};
+            \node[align=center] (final) [below of=sales] {Final profits are realized \\ $[\pi_{Fi}^t, \pi_P^t]$};
+            \draw[->] (entry_fee) -- (entry_decision);
+            \draw[->] (entry_decision) -- (sales);
+            \draw[->] (sales) -- (final);
+        \end{tikzpicture}
+        \caption{Benchmark model (platform sets the entry fee unilaterally)}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[node distance=2cm, auto]
+            \node[align=center] (entry_decision) {Potential entrants decide to invest \\ at cost $I_F$ \\ $[N_F]$};
+            \node[align=center] (entry_fee) [below of=entry_decision] {Entry fees are negotiated \\ between platform and $N_F$ fringe firms \\ $[F_F]$};
+            \node[align=center] (sales) [below of=entry_fee] {Platform and fringe sell products \\ $[\pi_{Fi}^v, \pi_P^v]$};
+            \node[align=center] (final) [below of=sales] {Final profits are realized \\ $[\pi_{Fi}^t, \pi_P^t]$};
+            \draw[->] (entry_decision) -- (entry_fee);
+            \draw[->] (entry_fee) -- (sales);
+            \draw[->] (sales) -- (final);
+        \end{tikzpicture}
+        \caption{Bargaining model (platform and fringe negotiate over the entry fee)}
+    \end{subfigure}
+    \caption{Timing of the models}
+    \label{fig:timing}
+\end{figure}
+
+In the rest of this section, I describe each step in detail, starting from the end of the game and working my way back to the beginning.
+
+\subsection{Demand}
+
+Imagine that there is an $N_C$ mass of consumers, looking to buy one product each.
+They choose from a continuum of products, which are either produced by the fringe (indexed by $F_i$), by the platform ($P_i$) and a unit mass of outside options ($0_i$).
+Customer $j$ derives the following utility from buying product $T_i$:
+\begin{align*}
+    u^F_{{T_i}j} = v^{T_i} - p^{T_i} + \mu\epsilon^{T_i}_j \quad \text{for } T_i \in \{F, P\},
+\end{align*}
+where $v^T_i$ is the value of product $T_i$, $p^{T_i}$ is its price, and $\epsilon^{T_i}_j$ is an idiosyncratic taste shock.
+Throughout this section I assume that the value of each product within its category is the same.
+I.e., $v^T_i = v^T \, \forall\,i$.
+This is to simplify the analysis, but is not crucial for the results.
+
+$\epsilon^{T_i}_j$ is assumed to be independent and identically distributed (i.i.d.) across consumers and products, and follow a standardized Type I Extreme Value distribution.
+This distributional assumption, along with the fact that each consumer consumes only one product, will lead to a tractable, logit-form demand function.
+
+\subsubsection{Production}
+
+Each (horizontally differentiated) product is produced by a single, monopolistically competitive (fringe) seller.
+The production entails a constant marginal cost $c^{T_i}$.
+As with the value, I assume that the marginal cost is the same for all products: $c^{T_i} = c^T$.
+Facing the demand described in the previous paragraphs, the sellers choose their price $p^{T_i}$ to maximize profits.
+The price of the outside option is normalized to zero.
+
+The pricing decision of the fringe sellers is rather straightforward, due to their infinitesimal market share: they do not have to take into account the effect of their prices on the aggregate demand.
+This normally is not the case for the platform, as it can affect a non-zero measure of the prices.
+Therefore, when setting the price for product $P_i$, it would optimally like to take into account how it affects demand on its other products $P_j$ $(j \neq i)$.
+Despite this, I assume that the platform prices its products as if they were produced by separate, monopolistically competitive sellers.
+
+I do this for a number of reasons.
+For one, it simplifies the analysis without affecting the main results qualitatively.
+More importantly, it lets me focus on the main question of this paper: how the platform's hybrid operation affects the bargaining power.
+If the platform priced its products strategically, there would be a quite mechanical effect that an increase in the number of products would lead to an increase in optimal prices, which would in fact decrease consumer surplus.
+This hard to disentangle the effects of hybrid operation from the effects of strategic pricing.
+Therefore, this assumption can be seen as a best-case scenario for consumers, and the results can be interpreted as a lower bound on the negative effects of hybrid operation.
+For a more thorough discussion of this assumption, see \cref{sec:separate_pricing}.
+
+Finally, this assumption is not as unrealistic as it might seem at first.
+For example, the platform might be producing its products through a number of subsidiaries, which are legally separate entities, thus having no control over operational decisions, but still getting the profits from the sales.
+Alternatively, there might be some kind of internal competition between the different product teams, which would lead to a similar outcome.
+
+\subsection{Fringe entry and platform fees}
+
+\subsubsection{Benchmark case}
+
+I assume that there is a continuum of potential fringe entrants, indexed by $i \in \mathbb{R}^+_0$.
+Each of them can create a product at an exogenous investment cost $I_F$.
+If they decide not to, they make zero profits and do not participate in the later stages of the game.
+Furthermore, these firms can only sell their products through the platform, for which the platform can charge a lump-sum entry fee $F_F$.
+The timing of these decisions is as follows: (1) the platform sets and commits to an entry fee $F_F$, (2) the fringe firms decide whether to enter the market, and (3) the firms that have entered pay the entry fee to the platform.
+
+\subsubsection{Bargaining case}
+
+In contrast to the benchmark model, in this case, the platform cannot commit to an entry fee: it is decided as a result of a negotiation between the platform and the fringe firms.
+For this reason, the timing of the model is also different.
+First, the fringe firms decide whether to invest in creating a product at cost $I_F$.
+After this, the platform and the firms that have made the investment negotiate the entry fee.
+Finally, the firms that have entered pay the entry fee to the platform.
+
+In order to keep the model tractable I model the negotiation process in a reduced form manner.
+In particular, I assume that the platform and the entrants agree on an entry fee $F_F$, which makes the total profits net entry fees equal to the Shapley value of the players.\footnote{
+    One simple extension would be to use the more general concept of random order values \parencite{weber1988probabilistic}.
+    \Cref{sec:cooperative_game_weighted} takes a step in this direction by introducing bargaining weights and utilizing the weighted value.
 }
-Formally, this is described by the following assumption.
-\begin{assumption}
-    \label{ass:identical_fringe}
-    The total profits of the platform and the fringe are described by 
-    \begin{align*}
-        \Pi(N_P, N_F, N_C) = N_C f(N_P, N_F),
-    \end{align*}
-    where $f: \mathbb{R}^+_0 \times \mathbb{R}^+_0 \to \mathbb{R}^+_0$.
-\end{assumption}
-Here, $N_F$ is the mass of fringe sellers, $N_C$ is the mass of consumers, and $N_P$ measures the degree to which the platform sells its own products.
-For example, in a setting with differentiated products and monopolistic competition, $N_F$ and $N_P$ represent the product variety of the fringe and the platform, respectively.
-$N_P = 0$ corresponds to the case when the platform is a pure intermediary, and $N_F = 0$ to the case then the platform is a pure retailer.
-
-I will assume that, in addition to being increasing in the number of consumers, total profits are also increasing in both the number of fringe firms and the platform' products.
-\begin{assumption}
-    \label{ass:monotone_profits}
-    $f(n_P, n_F)$ is increasing in both $n_P$ and $n_F$.
-\end{assumption}
-Such profit functions arise in settings in which the profit reduction from increased competition is dominated by extra sales due to increased product variety.
-One such example is \textcite{anderson2020aggregative}, where the demand exhibits love for variety, while consumers have access to an outside option.
-Alternatively, indirect network effects, such as those in two-sided markets, can also result in such increasing profits.
-Finally, if we assume that the platform can extract consumer surplus through entry fees or some similar mechanism, then this assumption will be true for any demand system in which total surplus is increasing in product variety.
-
-\subsection{Profit sharing}
-
-I assume that fringe firms are unable to sell their products directly to consumers.
-Instead, they must sell through the platform.
-For this service, the platform may charge a fee, and obtain a share of the fringe's profits.
-
-In the benchmark model, the platform will be able to set and commit to any lump-sum entry fee it wishes to.\footnote{
-    The focus of this paper is on fees paid and entry decisions made by fringe producers, but I will also consider the case when consumers also face entry fees or subsidies.
+This way of modelling bargaining outcomes has many precedents in the industrial organization literature \parencite[e.g.][]{montez2007downstream,hart1990property,levy1997individual,inderst2003bargaining,brugemann2019intra} and has a number of appealing properties.
+For example, it is closely related to the marginal contributions of the players to the total value, and, as it will be shown, it is also quite intuitive in terms of comparative statistics.
+Furthermore, and perhaps more importantly, there are a number of ways to place it on non-cooperative microfoundations by setting up non-cooperative games for which the Shapley value is a subgame perfect equilibrium \parencite[e.g.][]{gul1989bargaining,hart1996bargaining,stole1996organizational}.\footnote{
+    For a possible microfoundation of this specific model, see \cref{sec:bargaining_microfoundation}.
 }
-The main contribution of this paper is to deviate from this usual assumption, and instead consider a setting in which the platform and the fringe engage in some form of bargaining over the total profits.
-To model this in a tractable way, I propose a profit division rule that is based on the Shapley value \parencite{shapley1953additive}, or, more generally, random order values \parencite{weber1988probabilistic}.
-This way of modelling bargaining outcomes has many precedents in the industrial organization literature \parencite[e.g.][]{montez2007downstream,hart1990property,levy1997individual,inderst2003bargaining,brugemann2019intra}.
-In the main text, I simply propose a formula for the profit shares without going into the details of the underlying cooperative game.
-The interested reader can find a more detailed discussion of how it relates to random order values in \cref{sec:cooperative_game}.
-
-\begin{assumption}
-    \label{ass:profit_sharing}
-    Let $w_P, w_F: \mathbb{R}^+_0 \to \mathbb{R}^+_0$ be non-negative functions such that the following condition holds: $\pi_P(N_P, N_F, N_C) + \pi_F(N_P, N_F, N_C) \leq \Pi(N_P, N_F, N_C)$.
-    %TODO: can I make this condition nicer?
-    Then, the platform's profit ($\pi_P(N_P, N_F, N_C)$) and the fringe's profit ($\pi_F(N_P, N_F, N_C)$) are given by:
-    \begin{align*}
-        \pi_P(N_P, N_F, N_C) &= N_C \int_0^1 w_P(s) f(N_P, s N_F) \ds, \\
-        \pi_F(N_P, N_F, N_C) &= N_C \int_0^1 w_F(s) N_F \partial_2 f(N_P, s N_F) \ds.
-    \end{align*}
-\end{assumption}
-
-Although the reason behind choosing this particular form for profit shares is discussed in detail in the appendix, let me highlight some important observations.
-First, player's profit shares are closely related to their (weighted average) marginal contributions to the total value.
-In the case of the platform, its contribution is the total value, as it is indispensable, while the fringe firms' contribution is captured by the partial derivative of the total value with respect to the number of fringe firms.
-Second, the platform and the fringe do not necessarily get the entire value they create.
-This is due to the fact that I also want to allow for the possibility of consumers participating in the bargaining process and getting a share of the profits, too
-Finally, the profit shares depend on two types of factors: the production function $f$ and $w_P$ and $w_F$, which I will call bargaining weights.
-The former is determined by the technology and demand structure, while the latter can be thought of as some king of intrinsic bargaining power.
-
-In the later sections, I will consider specific examples for $f$ and $w_P$ and $w_F$, motivated by a Logit-like demand system, and (weighted) Shapley values, respectively.
-However, for a number of results, this level of detail is not necessary, and these quite general assumptions are sufficient.
-
-As mentioned before, one main justification for this profit allocation rule its intuitive behavior in terms of comparative statistics.
-To illustrate this, let us examine what happens when one varies the substitutability between the fringe firms.
-As it turns out, the platform's share increases if the fringe firms are more substitutable.
-The following observation demonstrates this idea.
+
+For the Shapley value (or any other cooperative solution concept) to be well-defined, the corresponding coalitional game must be specified.
+\Cref{sec:cooperative_game} describes it in detail, but in short, the idea is the following: given any subset of the players (coalition), players can predict total, industry-wide profits assuming the monopolistic competition described previously.
+This is taken as the value of that coalition, thus defining a characteristic function.
+Then, every firm (including the platform) will get their average marginal contribution this industry-wide profit (with the average taken over all possible orderings of the firms).
+
+In practice, it looks like the following.
+Assume that $N_F$ fringe firms choose to invest in creating a product in the first stage of the game.
+Now, for every $s N_F$ ($s \in [0, 1]$), calculate the total profits that would be realized if the platform and $n_f$ fringe firms were the only players in the market, and they engaged in monopolistic competition as described in the previous paragraph.
+Let us denote these profits by $\pi^v_{F}(N_C, N_P, s N_F)$ and $\pi^v_{P}(N_C, N_P, s N_F)$, and the corresponding industry-wide total profits by $\Pi$ and $\Pi(N_C, N_P, s N_F)$.
+
 \begin{proposition}
-    \label{prop:outcome_based_bargaining_power}
-    Fix some $N_P, N_C \geq 0$.
+    \label{prop:shapley_value}
+    The Shapley value of the platform and the fringe firms, and thus final total profits, are given by:
+    \begin{align*}
+        \pi^t_P(N_P, N_F, N_C) &= N_C \int_0^1 \Pi(N_C, N_P, s N_F) \ds, \\
+        \pi^t_F(N_P, N_F, N_C) &= N_C \int_0^1 \partial_3 N_F \Pi(N_C, N_P, s N_F) \ds.
+    \end{align*}
+\end{proposition}
+
+\subsection{Equilibrium}
+
+For both models, the previous sections describe a perfect-information extensive-form game.
+As a consequence, the solution concept I use is the subgame perfect equilibrium.
+As tha platform's product variety ($N_P$) is assumed to be exogenous, the only strategic variables are (1) the fringe players' entry decisions, (2) the platform's entry fee (only in the benchmark model), and (3) the prices of the products.
+
+Furthermore, the game can be solved via straightforward backward induction.
+In both models, the final subgame is simply a game of monopolistic competition with horizontally differentiated products.
+In the benchmark model, it is preceded by the platform setting the entry fee, while in the bargaining model the entry fee is set according to the previously described rule (which in turn can be motivated by an extensive form game).
+Finally, the first stage of the game is the fringe firms' investment decision.
+Due to the outside option being normalized to zero, the fringe firms will enter the market if and only if the expected profits from doing so are positive, leading to the usual free entry condition.
+
+% \subsection{Profit sharing}
+
+% I assume that fringe firms are unable to sell their products directly to consumers.
+% Instead, they must sell through the platform.
+% For this service, the platform may charge a fee, and obtain a share of the fringe's profits.
+
+% In the benchmark model, the platform will be able to set and commit to any lump-sum entry fee it wishes to.\footnote{
+%     The focus of this paper is on fees paid and entry decisions made by fringe producers, but I will also consider the case when consumers also face entry fees or subsidies.
+% }
+% The main contribution of this paper is to deviate from this usual assumption, and instead consider a setting in which the platform and the fringe engage in some form of bargaining over the total profits.
+% To model this in a tractable way, I propose a profit division rule that is based on the Shapley value \parencite{shapley1953additive}, or, more generally, random order values \parencite{weber1988probabilistic}.
+% This way of modelling bargaining outcomes has many precedents in the industrial organization literature \parencite[e.g.][]{montez2007downstream,hart1990property,levy1997individual,inderst2003bargaining,brugemann2019intra}.
+% In the main text, I simply propose a formula for the profit shares without going into the details of the underlying cooperative game.
+% The interested reader can find a more detailed discussion of how it relates to random order values in \cref{sec:cooperative_game}.
+
+% \begin{assumption}
+%     \label{ass:profit_sharing}
+%     Let $w_P, w_F: \mathbb{R}^+_0 \to \mathbb{R}^+_0$ be non-negative functions such that the following condition holds: $\pi_P(N_P, N_F, N_C) + \pi_F(N_P, N_F, N_C) \leq \Pi(N_P, N_F, N_C)$.
+%     %TODO: can I make this condition nicer?
+%     Then, the platform's profit ($\pi_P(N_P, N_F, N_C)$) and the fringe's profit ($\pi_F(N_P, N_F, N_C)$) are given by:
+%     \begin{align*}
+%         \pi_P(N_P, N_F, N_C) &= N_C \int_0^1 w_P(s) f(N_P, s N_F) \ds, \\
+%         \pi_F(N_P, N_F, N_C) &= N_C \int_0^1 w_F(s) N_F \partial_2 f(N_P, s N_F) \ds.
+%     \end{align*}
+% \end{assumption}
+
+% Although the reason behind choosing this particular form for profit shares is discussed in detail in the appendix, let me highlight some important observations.
+% First, player's profit shares are closely related to their (weighted average) marginal contributions to the total value.
+% In the case of the platform, its contribution is the total value, as it is indispensable, while the fringe firms' contribution is captured by the partial derivative of the total value with respect to the number of fringe firms.
+% Second, the platform and the fringe do not necessarily get the entire value they create.
+% This is due to the fact that I also want to allow for the possibility of consumers participating in the bargaining process and getting a share of the profits, too
+% Finally, the profit shares depend on two types of factors: the production function $f$ and $w_P$ and $w_F$, which I will call bargaining weights.
+% The former is determined by the technology and demand structure, while the latter can be thought of as some king of intrinsic bargaining power.
+
+% In the later sections, I will consider specific examples for $f$ and $w_P$ and $w_F$, motivated by a Logit-like demand system, and (weighted) Shapley values, respectively.
+% However, for a number of results, this level of detail is not necessary, and these quite general assumptions are sufficient.
+
+% As mentioned before, one main justification for this profit allocation rule its intuitive behavior in terms of comparative statistics.
+% To illustrate this, let us examine what happens when one varies the substitutability between the fringe firms.
+% As it turns out, the platform's share increases if the fringe firms are more substitutable.
+% The following observation demonstrates this idea.
+% \begin{proposition}
+%     \label{prop:outcome_based_bargaining_power}
+%     Fix some $N_P, N_C \geq 0$.
 Let $f, \tilde{f}: \mathbb{R}^+_0 \times \mathbb{R}^+_0 \to \mathbb{R}^+_0$ two different profit functions such that $f(N_P, N_F) = \tilde{f}(N_P, N_F)$ for some $N_P, N_F$ and $f(N_P, n_F) \leq \tilde{f}(N_P, n_F)$ for all $n_F < N_F$.
-    Furthermore, let us denote the corresponding platform profit shares by $\pi_P$ and $\tilde{\pi}_P$.
-
-    Then, $\pi_P \leq \tilde{\pi}_P$.
-\end{proposition}
-
-In words, \cref{prop:outcome_based_bargaining_power} describes two alternative worlds, in which $N_F$ fringe firms (assuming a platform with $N_P$ product variety and $N_C$ consumers) are able to achieve the same total profit level.
-However, in one of these cases, the fringe firms are more substitutable to each other in the sense that fewer of them are needed to achieve a given level of profit (see \cref{fig:outcome_based_bargaining_power}).
-The observation is that, in this situation, the platform's share is indeed higher when the fringe firms are more substitutable.
-This coincides with the intuitive idea that the platform's bargaining power is higher when it does not really mind loosing a few fringe sellers.
-
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \begin{tikzpicture}[scale=0.8]
-            \centering
-            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-                    xtick={0, 1}, ytick=\empty, xlabel={$s$}]
-                \addplot[name path=f, black, thick] {x^2};
-                \node[anchor= east] at (axis cs: .5, .5^2) {$N_C f(N_P, sN_F)$};
-                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
-                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);
-
-                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
-                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
-
-                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
-                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Fringe firms are complements}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.8]
-            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-                xtick={0, 1}, ytick=\empty, xlabel={$s$}]
-                \addplot[name path=f, black, thick] {x^0.5};
-                \node[anchor=north west] at (axis cs: .5, .5^0.5) {$N_C \tilde{f}(N_P, sN_F)$};
-                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
-                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);
-
-                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
-                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
-
-                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
-                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Fringe firms are substitutes}
-    \end{subfigure}
-    \caption{Distribution of value between the platform and the fringe.
+%     Furthermore, let us denote the corresponding platform profit shares by $\pi_P$ and $\tilde{\pi}_P$.
+
+%     Then, $\pi_P \leq \tilde{\pi}_P$.
+% \end{proposition}
+
+% In words, \cref{prop:outcome_based_bargaining_power} describes two alternative worlds, in which $N_F$ fringe firms (assuming a platform with $N_P$ product variety and $N_C$ consumers) are able to achieve the same total profit level.
+% However, in one of these cases, the fringe firms are more substitutable to each other in the sense that fewer of them are needed to achieve a given level of profit (see \cref{fig:outcome_based_bargaining_power}).
+% The observation is that, in this situation, the platform's share is indeed higher when the fringe firms are more substitutable.
+% This coincides with the intuitive idea that the platform's bargaining power is higher when it does not really mind loosing a few fringe sellers.
+
+% \begin{figure}
+%     \centering
+%     \begin{subfigure}[b]{0.45\textwidth}
+%         \begin{tikzpicture}[scale=0.8]
+%             \centering
+%             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
+%                     xtick={0, 1}, ytick=\empty, xlabel={$s$}]
+%                 \addplot[name path=f, black, thick] {x^2};
+%                 \node[anchor= east] at (axis cs: .5, .5^2) {$N_C f(N_P, sN_F)$};
+%                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+%                 \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);
+
+%                 \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
+%                 \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
+
+%                 \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
+%                 \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
+%             \end{axis}
+%         \end{tikzpicture}
+%         \caption{Fringe firms are complements}
+%     \end{subfigure}
+%     \begin{subfigure}[b]{0.45\textwidth}
+%         \centering
+%         \begin{tikzpicture}[scale=0.8]
+%             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
+%                 xtick={0, 1}, ytick=\empty, xlabel={$s$}]
+%                 \addplot[name path=f, black, thick] {x^0.5};
+%                 \node[anchor=north west] at (axis cs: .5, .5^0.5) {$N_C \tilde{f}(N_P, sN_F)$};
+%                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+%                 \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);
+
+%                 \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
+%                 \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
+
+%                 \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
+%                 \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
+%             \end{axis}
+%         \end{tikzpicture}
+%         \caption{Fringe firms are substitutes}
+%     \end{subfigure}
+%     \caption{Distribution of value between the platform and the fringe.
 Profit shares correspond to the shaded areas.
 The platform's profit share is higher when the fringe firms are more substitutable.}
-    \label{fig:outcome_based_bargaining_power}
-\end{figure}
-
-\subsection{Entry and equilibrium}
-
-Throughout the paper, I will assume that the number of consumers is fixed and exogenous.
-They are thus passive in the sense that they do not make a decision about whether to enter the market or not.
-However, when developing microfoundations for $f$ in \cref{sec:example}, consumers will make consumption choices, and their welfare will be of interest.
-The product variety of the platform is also exogeneous.
-
-Let us now turn to the determination of the equilibrium number of fringe firms.
-Assume that there is an unlimited number of potential fringe entrants, indexed by $i \in \mathbb{R}^+_0$.
-In the first stage of the game, each fringe firm must create a viable product at some investment cost.
-Let us denote the total investment costs of $N_F$ fringe firms by $I_F(N_F)$.
-\begin{assumption}
-    Assume that $I_F(N_F)$ is a strictly increasing, convex, twice differentiable function:
-    \begin{align*}
-        \frac{\partial I_F(N_F)}{\partial N_F} > 0, \quad \frac{\partial^2 I_F(N_F)}{\partial N_F^2} \geq 0.
-    \end{align*}
-\end{assumption}
-This assumption essentially states that the marginal investment cost of the fringe is increasing in the number of fringe firms.
-Notice that this only assumes weak convexity, and thus includes the case of constant marginal investment costs.
-
-In the second stage, firms that made this investment plus the platform engage in producing and selling their respective products.
-If there are $N_F$ fringe entrants along with $N_P$ platform products and $N_C$ consumers, then, as discussed previously, the total value they create together is given by $\Pi(N_P, N_F, N_C) = N_C f(N_P, N_F)$.
-Finally, the platform and the entrants share this profit according to the profit sharing rule from \cref{ass:profit_sharing}, and the fringe gets $\pi_F(N_P, N_F, N_C)$.
-
-The equilibrium number of entrants is determined by a free entry condition: in the end, the fringe firms' total profits should be equal to the aggregated investment cost.
-\begin{definition}
-    \label{ass:free_entry}
-    Let us define a free entry equilibrium by the following conditions:
-    \begin{itemize}
-        \item Profits are shared according to \cref{ass:profit_sharing}.
-        \item Entrants make zero profits after accounting for entry costs: $\pi_F(N_P, N_F) = I_F(N_F)$.
-    \end{itemize}
-\end{definition}
-
-Finally, in order to guarantee a unique equilibrium, let us make the following, an additional assumption about the profit function.
-\begin{assumption}
-    \label{ass:single_crossing}
-    Let $f$ be such that the following holds for all $N_F, N_P, N_C \geq 0$:
-    \begin{align*}
-        \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_F} < 0 \text{ or } \frac{\partial^2 \pi_F(N_P, N_F, N_C)}{\partial N_F^2} < 0
-    \end{align*}
-\end{assumption}
-This assumption essentially guarantees that the profit of the fringe (as a function of the number of entrants) has at most a single crossing with the --linear -- total entry cost (apart from the obvious $N_F=0$ intersection).
-The interpretation of the assumption itself is simple: total fringe profits, as a function of the number of fringe firms, must be either concave or hump-shaped.\footnote{
-    As it turns out, even though total industry profits are assumed to be increasing in $n_f$, it is not necessarily true for fringe profits.
-    For certain profit functions, it happens that even though the size of the pie increases, the bargaining position of the fringe deteriorates so much that they get a smaller share even in absolute value.
-}
-What it requires of $f$, however, is not so obvious, and also depends on what one assumes about the innate bargaining weights $w_F$ and $w_P$.
-Nevertheless, when microfounding the profit function, one can simply check whether this assumption holds or not.
-In particular, it will be satisfied for the logit-type demand in \cref{sec:example}.
+%     \label{fig:outcome_based_bargaining_power}
+% \end{figure}
+
+% \subsection{Entry and equilibrium}
+
+% Throughout the paper, I will assume that the number of consumers is fixed and exogenous.
+% They are thus passive in the sense that they do not make a decision about whether to enter the market or not.
+% However, when developing microfoundations for $f$ in \cref{sec:example}, consumers will make consumption choices, and their welfare will be of interest.
+% The product variety of the platform is also exogeneous.
+
+% Let us now turn to the determination of the equilibrium number of fringe firms.
+% Assume that there is an unlimited number of potential fringe entrants, indexed by $i \in \mathbb{R}^+_0$.
+% In the first stage of the game, each fringe firm must create a viable product at some investment cost.
+% Let us denote the total investment costs of $N_F$ fringe firms by $I_F(N_F)$.
+% \begin{assumption}
+%     Assume that $I_F(N_F)$ is a strictly increasing, convex, twice differentiable function:
+%     \begin{align*}
+%         \frac{\partial I_F(N_F)}{\partial N_F} > 0, \quad \frac{\partial^2 I_F(N_F)}{\partial N_F^2} \geq 0.
+%     \end{align*}
+% \end{assumption}
+% This assumption essentially states that the marginal investment cost of the fringe is increasing in the number of fringe firms.
+% Notice that this only assumes weak convexity, and thus includes the case of constant marginal investment costs.
+
+% In the second stage, firms that made this investment plus the platform engage in producing and selling their respective products.
+% If there are $N_F$ fringe entrants along with $N_P$ platform products and $N_C$ consumers, then, as discussed previously, the total value they create together is given by $\Pi(N_P, N_F, N_C) = N_C f(N_P, N_F)$.
+% Finally, the platform and the entrants share this profit according to the profit sharing rule from \cref{ass:profit_sharing}, and the fringe gets $\pi_F(N_P, N_F, N_C)$.
+
+% The equilibrium number of entrants is determined by a free entry condition: in the end, the fringe firms' total profits should be equal to the aggregated investment cost.
+% \begin{definition}
+%     \label{ass:free_entry}
+%     Let us define a free entry equilibrium by the following conditions:
+%     \begin{itemize}
+%         \item Profits are shared according to \cref{ass:profit_sharing}.
+%         \item Entrants make zero profits after accounting for entry costs: $\pi_F(N_P, N_F) = I_F(N_F)$.
+%     \end{itemize}
+% \end{definition}
+
+% Finally, in order to guarantee a unique equilibrium, let us make the following, an additional assumption about the profit function.
+% \begin{assumption}
+%     \label{ass:single_crossing}
+%     Let $f$ be such that the following holds for all $N_F, N_P, N_C \geq 0$:
+%     \begin{align*}
+%         \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_F} < 0 \text{ or } \frac{\partial^2 \pi_F(N_P, N_F, N_C)}{\partial N_F^2} < 0
+%     \end{align*}
+% \end{assumption}
+% This assumption essentially guarantees that the profit of the fringe (as a function of the number of entrants) has at most a single crossing with the --linear -- total entry cost (apart from the obvious $N_F=0$ intersection).
+% The interpretation of the assumption itself is simple: total fringe profits, as a function of the number of fringe firms, must be either concave or hump-shaped.\footnote{
+%     As it turns out, even though total industry profits are assumed to be increasing in $n_f$, it is not necessarily true for fringe profits.
+%     For certain profit functions, it happens that even though the size of the pie increases, the bargaining position of the fringe deteriorates so much that they get a smaller share even in absolute value.
+% }
+% What it requires of $f$, however, is not so obvious, and also depends on what one assumes about the innate bargaining weights $w_F$ and $w_P$.
+% Nevertheless, when microfounding the profit function, one can simply check whether this assumption holds or not.
+% In particular, it will be satisfied for the logit-type demand in \cref{sec:example}.
 % TODO: conjecture: it only has to hold for $f(N_P, N_F)$.
@@
 \subsubsection{Entry and timing}
-
-There is an infinite measure of fringe firms, who are deciding whether to enter the market.
-Entering has two, separate costs: an exogenous investment cost $I_F$, and the lump-sum platform entry fee $F_F$.
-One can conceptualize the first as usual fixed costs, such as the cost of setting up production, or designing a product.
-Meanwhile, the second is a payment to the platform for using its services.
-While percentage fees are more common both in the literature and in practice, I assume a lump-sum fee for a few reasons.
-First, and most importantly, revenue-based fees enter the entrants' pricing decision, and thus create a channel through which platforms distort competition.
-I want to show that even in the absence such distortions, hybrid platforms can have a significant impact on competition.
-Furthermore, due to this distortion, the resulting game could not be represented as a transferable utility game, and the proposed solution concept would not be applicable.
-Finally, lump-sum fees do make sense in settings when individual negotiation takes place and contracts are not standardized.
-
-In the benchmark model, the game starts by the platform announcing and committing to an entry fee $F_F$.\footnote{
-    With no commitment power, but the ability to set any prices after fringe firms make their investment decisions, the platform would charge an entry fee that would make the fringe profits zero \emph{sans the investment cost}.
-    This would lead to a trivial equilibrium, where no firm enters.
-}
-In the bargaining case, the platform cannot commit to entry fees, so this step is skipped.
-Next, each fringe firm decides whether to create a product at cost $I_F$ and enter the market.
-% In the bargaining model, the entry fee is decided at this point, as a result of a negotiation between the platform and the firms that have made the investment.
-After that, the firms that have made the investment decide if they also want to enter the platform for the announced fee $F_F$.\footnote{
-    In the benchmark model, separating these two decisions is redundant, as, in any subgame perfect equilibrium, any firm that makes the investment will also enter the platform.
-    However, in the model with bargaining, this distinction is crucial.
-}
-Finally, the platform and the fringe firms simultaneously choose the prices for their products.
-Each consumer then chooses the one maximizing their utility, and profits are realized.
-
-In the model with bargaining, the platform and the fringe distribute total profits according to their Shapley values.
-One can also think of the latter as agreeing on an entry fee that makes final profits net entry fees equal to the Shapley value of the various players.
-
-The main difference between the benchmark and the bargaining model is in determining the entry fee $F_F$.
-In the former, the platform unilaterally sets the fee, and the fringe treats it as a take it or leave it offer.
-On the other hand, in the bargaining model, I assume that the entry fee is the result of a negotiation between the parties.
-\cref{fig:timing} illustrates this difference.
-
-\begin{figure}
-    \centering
-    \begin{subfigure}{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[node distance=2cm, auto]
-            \node[align=center] (entry_fee) {Platform unilaterally sets the entry fee \\ $[F_F]$};
-            \node[align=center] (entry_decision) [below of=entry_fee] {Potential entrants decide to enter \\ at cost $I_F + F_F$ \\ $[N_F]$};
-            \node[align=center] (sales) [below of=entry_decision] {Platform and fringe sell products \\ $[\pi_{Fi}^v, \pi_P^v]$};
-            \node[align=center] (final) [below of=sales] {Final profits are realized \\ $[\pi_{Fi}^t, \pi_P^t]$};
-            \draw[->] (entry_fee) -- (entry_decision);
-            \draw[->] (entry_decision) -- (sales);
-            \draw[->] (sales) -- (final);
-        \end{tikzpicture}
-        \caption{Benchmark model (platform sets the entry fee unilaterally)}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[node distance=2cm, auto]
-            \node[align=center] (entry_decision) {Potential entrants decide to invest \\ at cost $I_F$ \\ $[N_F]$};
-            \node[align=center] (entry_fee) [below of=entry_decision] {Entry fees are negotiated \\ between platform and $N_F$ fringe firms \\ $[F_F]$};
-            \node[align=center] (sales) [below of=entry_fee] {Platform and fringe sell products \\ $[\pi_{Fi}^v, \pi_P^v]$};
-            \node[align=center] (final) [below of=sales] {Final profits are realized \\ $[\pi_{Fi}^t, \pi_P^t]$};
-            \draw[->] (entry_decision) -- (entry_fee);
-            \draw[->] (entry_fee) -- (sales);
-            \draw[->] (sales) -- (final);
-        \end{tikzpicture}
-        \caption{Bargaining model (platform and fringe negotiate over the entry fee)}
-    \end{subfigure}
-    \caption{Timing of the models}
-    \label{fig:timing}
-\end{figure}
 

### 2024-05-03 src/paper/application.tex
Rewrite and expand benchmark case

@@
 \newtheorem{proposition}{Proposition}
+\newtheorem{theorem}{Theorem}
 \newtheorem{corollary}{Corollary}
@@
 \subsection{Demand}
+\label{sec:demand}
 
@@
 \begin{align*}
-    u^F_{{T_i}j} = v^{T_i} - p^{T_i} + \mu\epsilon^{T_i}_j \quad \text{for } T_i \in \{F, P\},
-\end{align*}
-where $v^T_i$ is the value of product $T_i$, $p^{T_i}$ is its price, and $\epsilon^{T_i}_j$ is an idiosyncratic taste shock.
+    u_{T_i}^j = v_{T_i} - p_{T_i} + \mu\epsilon_{T_i}^j \quad \text{for } T_i \in \{F, P\},
+\end{align*}
+where $v_{T_i}$ is the value of product $T_i$, $p_{T_i}$ is its price, and $\epsilon_{T_i}^j$ is an idiosyncratic taste shock.
 Throughout this section I assume that the value of each product within its category is the same.
-I.e., $v^T_i = v^T \, \forall\,i$.
+I.e., $v_{T_i} = v_T \, \forall\,i$.
 This is to simplify the analysis, but is not crucial for the results.
 
-$\epsilon^{T_i}_j$ is assumed to be independent and identically distributed (i.i.d.) across consumers and products, and follow a standardized Type I Extreme Value distribution.
+$\epsilon_{T_i}^j$ is assumed to be independent and identically distributed (i.i.d.) across consumers and products, and follow a standardized Type I Extreme Value distribution.
 This distributional assumption, along with the fact that each consumer consumes only one product, will lead to a tractable, logit-form demand function.
@@
 Each (horizontally differentiated) product is produced by a single, monopolistically competitive (fringe) seller.
-The production entails a constant marginal cost $c^{T_i}$.
-As with the value, I assume that the marginal cost is the same for all products: $c^{T_i} = c^T$.
-Facing the demand described in the previous paragraphs, the sellers choose their price $p^{T_i}$ to maximize profits.
+The production entails a constant marginal cost $c_{T_i}$.
+As with the value, I assume that the marginal cost is the same for all products: $c_{T_i} = c_T$.
+Facing the demand described in the previous paragraphs, the sellers choose their price $p_{T_i}$ to maximize profits.
 The price of the outside option is normalized to zero.
@@
 As a consequence, the solution concept I use is the subgame perfect equilibrium.
-As tha platform's product variety ($N_P$) is assumed to be exogenous, the only strategic variables are (1) the fringe players' entry decisions, (2) the platform's entry fee (only in the benchmark model), and (3) the prices of the products.
+As the platform's product variety ($N_P$) is assumed to be exogenous, the only strategic variables are (1) the fringe players' entry decisions, (2) the platform's entry fee (only in the benchmark model), and (3) the prices of the products.
 
@@
 
-\section{General results}
-\label{sec:results}
-
-This section presents some general result that only depend on the abstract model structure described in the previous section, and the assumptions therein.
-It turns out that even within such a general setting, one can derive some interesting and non-trivial results.
-\Cref{sec:example} then builds on these results to derive stronger ones under a specific demand system.
-
-Let us start with a technical, but very useful result.
-\begin{proposition}
-    \label{prop:unique_equilibrium}
-    Under the conditions in \cref{ass:single_crossing}, the equilibrium is unique if it exists.
-\end{proposition}
-The intuition behind this result is that \cref{ass:single_crossing} ensures that the total profits achieved by the fringe is either concave or hump-shaped.
-Consequently, it has at most one crossing with the -- convex and increasing -- total entry cost function (for $n_F > 0$).
-An example for this is shown in \cref{fig:equilibrium}.
-This particular shape (concave or hump-shaped) is also the main driver for the later results about the comparative statics of equilibrium profits and entry.
-
-\begin{figure}[ht]
-    \centering
-    \begin{tikzpicture}[xscale=2,yscale=2,samples=200]
-        \draw[->] (0,0) -- (0,2);
-        \draw[->] (0,0) -- (5.5,0) node[below] {$N_F$};
-
-        \draw[name path=piF,domain=0.01:5.5,variable=\x,black,thick] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
-        \draw[name path=IF,domain=0.01:5.5,variable=\x,black,dashed,thick] plot ({\x},{(\x)/3});
-        \node[anchor=north east] at (5,1) {$\pi_F(N_P, N_F, N_C)$};
-        \node[anchor=south east] at (5,5/3) {$I_F(N_F)$};
-
-        \fill [name intersections={of=piF and IF, name=i, total=\t}]
-            [black] (i-2) circle (1pt);
-        \draw[dashed] (i-2) -- (i-2 |- 0,0) node[below] {$N_F^*$};
-    \end{tikzpicture}
-    \caption{An example free entry equilibrium.
+% \section{General results}
+% \label{sec:results}
+
+% This section presents some general result that only depend on the abstract model structure described in the previous section, and the assumptions therein.
+% It turns out that even within such a general setting, one can derive some interesting and non-trivial results.
+% \Cref{sec:example} then builds on these results to derive stronger ones under a specific demand system.
+
+% Let us start with a technical, but very useful result.
+% \begin{proposition}
+%     \label{prop:unique_equilibrium}
+%     Under the conditions in \cref{ass:single_crossing}, the equilibrium is unique if it exists.
+% \end{proposition}
+% The intuition behind this result is that \cref{ass:single_crossing} ensures that the total profits achieved by the fringe is either concave or hump-shaped.
+% Consequently, it has at most one crossing with the -- convex and increasing -- total entry cost function (for $n_F > 0$).
+% An example for this is shown in \cref{fig:equilibrium}.
+% This particular shape (concave or hump-shaped) is also the main driver for the later results about the comparative statics of equilibrium profits and entry.
+
+% \begin{figure}[ht]
+%     \centering
+%     \begin{tikzpicture}[xscale=2,yscale=2,samples=200]
+%         \draw[->] (0,0) -- (0,2);
+%         \draw[->] (0,0) -- (5.5,0) node[below] {$N_F$};
+
+%         \draw[name path=piF,domain=0.01:5.5,variable=\x,black,thick] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
+%         \draw[name path=IF,domain=0.01:5.5,variable=\x,black,dashed,thick] plot ({\x},{(\x)/3});
+%         \node[anchor=north east] at (5,1) {$\pi_F(N_P, N_F, N_C)$};
+%         \node[anchor=south east] at (5,5/3) {$I_F(N_F)$};
+
+%         \fill [name intersections={of=piF and IF, name=i, total=\t}]
+%             [black] (i-2) circle (1pt);
+%         \draw[dashed] (i-2) -- (i-2 |- 0,0) node[below] {$N_F^*$};
+%     \end{tikzpicture}
+%     \caption{An example free entry equilibrium.
 \Cref{ass:single_crossing} states that the fringe profit function is concave or hump-shaped in $N_F$, guaranteeing at most one intersection with the linear entry cost function.}
-    \label{fig:equilibrium}
-\end{figure}
-
-For the following two propositions, let us ignore free entry and equilibrium behavior, and consider the number of fringe entrants $N_F$ as fixed.
-The following statement claims that the platform's profits are increasing in its own product variety.
-\begin{proposition}
-    \label{prop:share_of_platform}
-    Assume that $f$ is continuously differentiable with respect to $N_P$ and also twice differentiable.
-    Let $N_F \geq 0$.
-    Then $\pi_P$ is also differentiable and
-    \begin{align*}
-        \frac{\partial \pi_P(N_P, N_F)}{\partial N_P} > 0.
-    \end{align*}
-\end{proposition}
-While it might seem obvious, let us still examine what this result does and does not mean.
-First, remember that $f$ is increasing in both arguments, and $N_F$ is fixed.
-Therefore, an increase in $N_P$ also increases the size of the pie the participants bargain over.
-This result states that the slice of the pie that the platform gets increases in this case, too.
-It does not mean, however, that the \emph{relative share} of the pie that the platform gets is also bigger -- increase is only guaranteed in absolute terms.
-For example, it is possible that for the new, higher value of $N_P$, the complementarities between the fringe firms become stronger, and the platform's bargaining power decreases.\footnote{
-    In fact, one can show that this is the case if the cross-derivatives of $f$ are negative.
-}
-As this result shows, this decrease cannot be large enough to decrease the platform's profits in absolute terms.
-\cref{fig:increase_N_P_platform} shows an example of this situation.
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.8]
-            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
-                \addplot[name path=f, black, thick] {ln(1+x)};
-                % \addplot[name path=tildef, dashed, black] {x};
-                \node[anchor=north west] at (axis cs: .5, .4) {$N_C f(N_P, sN_F)$};
-                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
-                \draw[name path=top] (axis cs:0,0.693) -- (axis cs:1,0.693);
-                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,0.693);
-
-                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
-                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
-
-                \node[anchor=north west] at (axis cs: .05, .65) {Fringe ($F$)};
-                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Profit shares with $N_P$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.8]
-            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
-                \addplot[name path=f, dashed, black] {ln(1+x)};
-                \addplot[name path=tildef, black, thick] {x};
-                \node[anchor=south east] at (axis cs: 0.6, 0.6) {$N_C f(N_P', sN_F)$};
-                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
-                \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
-                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);
-
-                \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
-                \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];
-
-                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
-                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Profit shares with $N_P'$}
-    \end{subfigure}
-    \caption{Illustration of \cref{prop:share_of_platform} in the one-sided bargaining case.
+%     \label{fig:equilibrium}
+% \end{figure}
+
+% For the following two propositions, let us ignore free entry and equilibrium behavior, and consider the number of fringe entrants $N_F$ as fixed.
+% The following statement claims that the platform's profits are increasing in its own product variety.
+% \begin{proposition}
+%     \label{prop:share_of_platform}
+%     Assume that $f$ is continuously differentiable with respect to $N_P$ and also twice differentiable.
+%     Let $N_F \geq 0$.
+%     Then $\pi_P$ is also differentiable and
+%     \begin{align*}
+%         \frac{\partial \pi_P(N_P, N_F)}{\partial N_P} > 0.
+%     \end{align*}
+% \end{proposition}
+% While it might seem obvious, let us still examine what this result does and does not mean.
+% First, remember that $f$ is increasing in both arguments, and $N_F$ is fixed.
+% Therefore, an increase in $N_P$ also increases the size of the pie the participants bargain over.
+% This result states that the slice of the pie that the platform gets increases in this case, too.
+% It does not mean, however, that the \emph{relative share} of the pie that the platform gets is also bigger -- increase is only guaranteed in absolute terms.
+% For example, it is possible that for the new, higher value of $N_P$, the complementarities between the fringe firms become stronger, and the platform's bargaining power decreases.\footnote{
+%     In fact, one can show that this is the case if the cross-derivatives of $f$ are negative.
+% }
+% As this result shows, this decrease cannot be large enough to decrease the platform's profits in absolute terms.
+% \cref{fig:increase_N_P_platform} shows an example of this situation.
+
+% \begin{figure}[ht]
+%     \centering
+%     \begin{subfigure}[b]{0.45\textwidth}
+%         \centering
+%         \begin{tikzpicture}[scale=0.8]
+%             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
+%                 xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
+%                 \addplot[name path=f, black, thick] {ln(1+x)};
+%                 % \addplot[name path=tildef, dashed, black] {x};
+%                 \node[anchor=north west] at (axis cs: .5, .4) {$N_C f(N_P, sN_F)$};
+%                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+%                 \draw[name path=top] (axis cs:0,0.693) -- (axis cs:1,0.693);
+%                 \draw[name path=right] (axis cs:1,0) -- (axis cs:1,0.693);
+
+%                 \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
+%                 \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
+
+%                 \node[anchor=north west] at (axis cs: .05, .65) {Fringe ($F$)};
+%                 \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
+%             \end{axis}
+%         \end{tikzpicture}
+%         \caption{Profit shares with $N_P$}
+%     \end{subfigure}
+%     \begin{subfigure}[b]{0.45\textwidth}
+%         \centering
+%         \begin{tikzpicture}[scale=0.8]
+%             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
+%                 xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
+%                 \addplot[name path=f, dashed, black] {ln(1+x)};
+%                 \addplot[name path=tildef, black, thick] {x};
+%                 \node[anchor=south east] at (axis cs: 0.6, 0.6) {$N_C f(N_P', sN_F)$};
+%                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+%                 \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
+%                 \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);
+
+%                 \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
+%                 \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];
+
+%                 \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
+%                 \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
+%             \end{axis}
+%         \end{tikzpicture}
+%         \caption{Profit shares with $N_P'$}
+%     \end{subfigure}
+%     \caption{Illustration of \cref{prop:share_of_platform} in the one-sided bargaining case.
 The right hand side figure shows a world with larger platform product variety ($N_P < N_P'$).
 Even though the platform's share of the total profits is smaller in relative terms in that case, it is still larger in absolute terms.}
-    \label{fig:increase_N_P_platform}
-\end{figure}
-
-Next, let us look at an analogous result for the fringe firms.
-As the next proposition demonstrates, in this case, the direction of the change depends on the complementarities between the fringe firms.
-\begin{proposition}
-    \label{prop:share_of_fringe}
-    Assume that $f, w$ are twice continuously differentiable.
-    Let $N_F > 0$.
-    Then $\pi_F$ is also differentiable.
-    \begin{align*}
-        &\text{If } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} < 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} < 0, \\
-        &\text{if } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} > 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} > 0
-    \end{align*}
-    for all $N_P \geq 0$.
-\end{proposition}
-In summary, when they are mostly substitutes (the cross-derivatives of $f$ are negative), the fringe's profits decrease as a result of an increase in $N_F$.
-The intuition is that, even though the total size of the pie increases, the bargaining power of the fringe deteriorates so much that its share decreases not only in relative, but also in absolute terms (as illustrated in \cref{fig:increase_N_P_fringe}).
-On the other hand, when the fringe firms are mostly complements the fringe's profits increase.
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.8]
-            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.225, samples at={0, 0.02, ..., 0.98, 1},
-                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
-                \addplot[name path=f, black, thick] {sqrt(x)};
-                % \addplot[name path=tildef, dashed, black] {sqrt(0.5+x)};
-                \node[anchor=north west] at (axis cs: .6, 0.77) {$N_C f(0, sN_F)$};
-                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
-                \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
-                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);
-
-                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
-                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
-
-                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
-                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Profit shares with $N_P = 0$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.8]
-            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.225, samples at={0, 0.02, ..., 0.98, 1},
-                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
-                \addplot[name path=f, dashed, black] {sqrt(x)};
-                \addplot[name path=tildef, black, thick] {sqrt(0.5+x)};
-                \node[anchor=north west] at (axis cs: 0.05, 0.75) {$N_C f(N_P', sN_F)$};
-                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
-                \draw[name path=top] (axis cs:0,1.225) -- (axis cs:1,1.225);
-                \draw[name path=top_old, dashed] (axis cs:0,1) -- (axis cs:1,1);
-                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1.225);
-
-                \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
-                \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];
-
-                \node[anchor=north west] at (axis cs: .05, 1.17) {Fringe ($F$)};
-                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Profit shares with $N_P = 0.5$}
-    \end{subfigure}
-    \caption{Illustration of \cref{prop:share_of_fringe} when fringe and platforrm products are substitutes.
+%     \label{fig:increase_N_P_platform}
+% \end{figure}
+
+% Next, let us look at an analogous result for the fringe firms.
+% As the next proposition demonstrates, in this case, the direction of the change depends on the complementarities between the fringe firms.
+% \begin{proposition}
+%     \label{prop:share_of_fringe}
+%     Assume that $f, w$ are twice continuously differentiable.
+%     Let $N_F > 0$.
+%     Then $\pi_F$ is also differentiable.
+%     \begin{align*}
+%         &\text{If } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} < 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} < 0, \\
+%         &\text{if } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} > 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} > 0
+%     \end{align*}
+%     for all $N_P \geq 0$.
+% \end{proposition}
+% In summary, when they are mostly substitutes (the cross-derivatives of $f$ are negative), the fringe's profits decrease as a result of an increase in $N_F$.
+% The intuition is that, even though the total size of the pie increases, the bargaining power of the fringe deteriorates so much that its share decreases not only in relative, but also in absolute terms (as illustrated in \cref{fig:increase_N_P_fringe}).
+% On the other hand, when the fringe firms are mostly complements the fringe's profits increase.
+
+% \begin{figure}[ht]
+%     \centering
+%     \begin{subfigure}[b]{0.45\textwidth}
+%         \centering
+%         \begin{tikzpicture}[scale=0.8]
+%             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.225, samples at={0, 0.02, ..., 0.98, 1},
+%                 xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
+%                 \addplot[name path=f, black, thick] {sqrt(x)};
+%                 % \addplot[name path=tildef, dashed, black] {sqrt(0.5+x)};
+%                 \node[anchor=north west] at (axis cs: .6, 0.77) {$N_C f(0, sN_F)$};
+%                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+%                 \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
+%                 \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);
+
+%                 \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
+%                 \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
+
+%                 \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
+%                 \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
+%             \end{axis}
+%         \end{tikzpicture}
+%         \caption{Profit shares with $N_P = 0$}
+%     \end{subfigure}
+%     \begin{subfigure}[b]{0.45\textwidth}
+%         \centering
+%         \begin{tikzpicture}[scale=0.8]
+%             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.225, samples at={0, 0.02, ..., 0.98, 1},
+%                 xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
+%                 \addplot[name path=f, dashed, black] {sqrt(x)};
+%                 \addplot[name path=tildef, black, thick] {sqrt(0.5+x)};
+%                 \node[anchor=north west] at (axis cs: 0.05, 0.75) {$N_C f(N_P', sN_F)$};
+%                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+%                 \draw[name path=top] (axis cs:0,1.225) -- (axis cs:1,1.225);
+%                 \draw[name path=top_old, dashed] (axis cs:0,1) -- (axis cs:1,1);
+%                 \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1.225);
+
+%                 \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
+%                 \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];
+
+%                 \node[anchor=north west] at (axis cs: .05, 1.17) {Fringe ($F$)};
+%                 \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
+%             \end{axis}
+%         \end{tikzpicture}
+%         \caption{Profit shares with $N_P = 0.5$}
+%     \end{subfigure}
+%     \caption{Illustration of \cref{prop:share_of_fringe} when fringe and platforrm products are substitutes.
 An increase in the platform's product variety increases total profits, yet, the fringe's share decreases in absolute terms.}
-    \label{fig:increase_N_P_fringe}
-\end{figure}
-
-Now let us turn to equilibrium entry as a function of the platform's product variety.
-The previous proposition implies an almost immediate corollary regarding the equilibrium number of fringe entrants.
-\begin{corollary}
-    \label{cor:fringe_entry}
-    Assume that $f, w$ are twice continuously differentiable.
-    Let $N_F^*$ denote the equilibrium number of fringe firms.
-    Let us also assume that $N_F^* > 0$.
-    Furthermore, let us assume that
-    \begin{align*}
-        \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} < 0 \quad \forall n_F \leq N_F \\
-        \frac{\partial^2 f(n_P, n_F)}{\partial n_F^2} < 0 \quad \forall n_F \leq N_F.
-    \end{align*}
-    Then the equilibrium number of fringe firms is also differentiable and
-    \begin{align*}
-        \frac{\partial N_F^*}{\partial N_P} < 0.
-    \end{align*}
-\end{corollary}
-That is, the equilibrium number of entrants increases as a response to an increase in $N_P$ if the fringe firms are mostly complements, and decreases if they are mostly substitutes.
-The underlyong reason is again the concave or hump-shaped fringe profit function.
-If $N_F^*$ is an equilibrium, then fringe profits minus entry costs are strictly positive for all $N_F \leq N_F^*$ and strictly negative for all $N_F > N_F^*$.
-Therefore, if an increase in $N_P$ decreases the fringe's profits for every $N_F \geq 0$, equilibrium can be restored by decreasing the number of fringe entrants, and vice versa for the other case (\cref{fig:comparative_N_F}).
-
-\begin{figure}[ht]
-    \centering
-    \begin{tikzpicture}[xscale=2,yscale=2,samples=200]
-        \draw[->] (0,0) -- (0,2);
-        \draw[->] (0,0) -- (5.5,0) node[below] {$N_F$};
-
-        \draw[name path=piF,domain=0.01:5.5,variable=\x,black, thick] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
-        \draw[name path=piF2,domain=0.01:5.5,variable=\x,black, thick] plot ({\x},{6*((\x)/(0.3+\x))-6*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
-        \draw[name path=IF,domain=0.01:5.5,variable=\x,black,dashed,thick] plot ({\x},{(\x)/3});
-
-        \node[anchor=south] at (5,1) {$\pi_F(N_P, N_F, N_C)$};
-        \node[anchor=north] at (5,0.6) {$\pi_F(N_P', N_F, N_C)$};
-        \node[anchor=south east] at (5,5/3) {$I_F(N_F)$};
-
-        \fill [name intersections={of=piF and IF, name=i, total=\t}]
-            [black] (i-2) circle (1pt);
-        \draw[dashed] (i-2) -- (i-2 |- 0,0) node[below] {$N_F^*$};
-        \fill [name intersections={of=piF2 and IF, name=i2, total=\t}]
-            [black] (i2-2) circle (1pt);
-        \draw[dashed] (i2-2) -- (i2-2 |- 0,0) node[below] {${N_F^*}'$};
-
-        \draw[->] (i-2 |- 0,0.5) -- (i2-2 |- 0,0.5);
-    \end{tikzpicture}
-    \caption{Illustration of comparative statics for equilibrium entry.
+%     \label{fig:increase_N_P_fringe}
+% \end{figure}
+
+% Now let us turn to equilibrium entry as a function of the platform's product variety.
+% The previous proposition implies an almost immediate corollary regarding the equilibrium number of fringe entrants.
+% \begin{corollary}
+%     \label{cor:fringe_entry}
+%     Assume that $f, w$ are twice continuously differentiable.
+%     Let $N_F^*$ denote the equilibrium number of fringe firms.
+%     Let us also assume that $N_F^* > 0$.
+%     Furthermore, let us assume that
+%     \begin{align*}
+%         \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} < 0 \quad \forall n_F \leq N_F \\
+%         \frac{\partial^2 f(n_P, n_F)}{\partial n_F^2} < 0 \quad \forall n_F \leq N_F.
+%     \end{align*}
+%     Then the equilibrium number of fringe firms is also differentiable and
+%     \begin{align*}
+%         \frac{\partial N_F^*}{\partial N_P} < 0.
+%     \end{align*}
+% \end{corollary}
+% That is, the equilibrium number of entrants increases as a response to an increase in $N_P$ if the fringe firms are mostly complements, and decreases if they are mostly substitutes.
+% The underlyong reason is again the concave or hump-shaped fringe profit function.
+% If $N_F^*$ is an equilibrium, then fringe profits minus entry costs are strictly positive for all $N_F \leq N_F^*$ and strictly negative for all $N_F > N_F^*$.
+% Therefore, if an increase in $N_P$ decreases the fringe's profits for every $N_F \geq 0$, equilibrium can be restored by decreasing the number of fringe entrants, and vice versa for the other case (\cref{fig:comparative_N_F}).
+
+% \begin{figure}[ht]
+%     \centering
+%     \begin{tikzpicture}[xscale=2,yscale=2,samples=200]
+%         \draw[->] (0,0) -- (0,2);
+%         \draw[->] (0,0) -- (5.5,0) node[below] {$N_F$};
+
+%         \draw[name path=piF,domain=0.01:5.5,variable=\x,black, thick] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
+%         \draw[name path=piF2,domain=0.01:5.5,variable=\x,black, thick] plot ({\x},{6*((\x)/(0.3+\x))-6*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
+%         \draw[name path=IF,domain=0.01:5.5,variable=\x,black,dashed,thick] plot ({\x},{(\x)/3});
+
+%         \node[anchor=south] at (5,1) {$\pi_F(N_P, N_F, N_C)$};
+%         \node[anchor=north] at (5,0.6) {$\pi_F(N_P', N_F, N_C)$};
+%         \node[anchor=south east] at (5,5/3) {$I_F(N_F)$};
+
+%         \fill [name intersections={of=piF and IF, name=i, total=\t}]
+%             [black] (i-2) circle (1pt);
+%         \draw[dashed] (i-2) -- (i-2 |- 0,0) node[below] {$N_F^*$};
+%         \fill [name intersections={of=piF2 and IF, name=i2, total=\t}]
+%             [black] (i2-2) circle (1pt);
+%         \draw[dashed] (i2-2) -- (i2-2 |- 0,0) node[below] {${N_F^*}'$};
+
+%         \draw[->] (i-2 |- 0,0.5) -- (i2-2 |- 0,0.5);
+%     \end{tikzpicture}
+%     \caption{Illustration of comparative statics for equilibrium entry.
 If the change in $N_P$ decreases the fringe's profits for every $N_F \geq 0$, equilibrium can be restored by decreasing the number of fringe entrants, and vice versa for the other case.}
-    \label{fig:comparative_N_F}
-\end{figure}
-
-Finally, let us conclude this section by establishing a stronger result for a more restrictive class of profit functions.
-In the following, I assume that the profit function has a specific, additive form.
-Intuitively, this means that -- in terms of total profits generated -- the platform's and the fringe firms' products are substitutable to each other according to some constant ratio.
-\begin{proposition}
-    \label{prop:aggregate_size_additive}
-    Let $f$ have the following, additive form:
-    \begin{align*}
-        f(N_P, N_F) = g(\alpha N_P + \beta N_F)
-    \end{align*}
-    where $\alpha, \beta > 0$.
-    Also assume that $g$ is twice differentiable and that $g'' < 0$.
-    Then
-    \begin{align*}
-        \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}.
-    \end{align*}
-    Furthermore,
-    \begin{align*}
-        \frac{\partial \Pi(N_P, N_F^*(N_P), N_C)}{\partial N_P} < 0.
-    \end{align*}
-\end{proposition}
-
-The first part of this proposition is a stronger version of \cref{cor:fringe_entry}.
-It states that, not only does the equilibrium number of fringe firms decrease as a response to an increase in $N_P$, but it establishes a lower bound for this decrease.
-And, as the second part shows, this bound is sufficient to guarantee that the total size of the pie ($\Pi(N_P, N_F, N_C)$) also decreases in equilibrium.
-
-This result has particularly strong implications in models where total profits (or total product variety) has a monotone relationship with consumer welfare, such as those in \textcite{anderson2020aggregative}.
-\Cref{sec:example} also presents a demand system which satisfies this property.
-
-\section{Logit demand}
-\label{sec:example}
-
-Let us now add more structure to the model, place the function $\Pi$ on more solid microfoundations.
-The modeling strategy is heavily inspired by the logit-like demand structure and hybrid platform setting of \textcite{anderson2021hybrid}.
-The setting can be thought of as a (possibly hybrid) platform market with monopolistically competing fringe firms.
-
-In the main model, I consider the case when the total profit function only includes the sales of the platform's and fringe firms' products.
-That is, the platform does not charge any entry fees to the consumers.
-Here, I consider two variants of the model: a benchmark where the platform can unilaterally commit to any entry fee, and a bargaining model where the platform and the fringe firms negotiate over the distribution of profits.
-Furthermore, I focus on a particular set of weight functions $w_P$ and $w_F$, which correspont to the Shapley-values of the players in the case of one-sided bargaining.
-
-As an extension, in \cref{sec:lower_bargaining_power} I also examine what happens when the platform and the fringe firms have unequal bargaining weights, while still retaining more structure than the very general bargaining rule from \cref{ass:profit_sharing}.
-In particular, I look at the case of bargaining outcomes being described by weighted values, with all fringe players sharing the same weight.
-Furthermore, in \cref{sec:two_sided}, I also consider the case of two-sided bargaining, where the consumers also participate in the negotiation over the value produced.
-Finally, \cref{sec:total_welfare_one_sided} explores the case of the platform being able to extract all of the consumer surplus from consumers.
-
-Throughout the analysis, I treat the product variety of the platform and the number of consumers as exogenous, and focus on the equilibrium number of fringe firms.
-Nevertheless, the results regarding equilibrium platform profits and consumer surplus are indicative of the potential general equilibrium behavior of the former two, as well.
-
-\subsection{Setup}
-
-\subsubsection{Demand}
-
-Imagine that there is a unit mass of consumers, looking to buy one product each.
-They choose from a continuum of products, indexed by $i$.
-Customer $j$ derives the following utility from buying product $i$:
-\begin{align*}
-    u^F_{ij} = v^F_i - p^F_i + \mu\epsilon^F_{ij},
-\end{align*}
-where $v^F_i$ is the value of product $i$, $p^F_i$ is its price, and $\epsilon^F_{ij}$ is an idiosyncratic taste shock.
-Throughout this section I assume that the value of each product is the same: $v^F_i = v^F$.
-This is to simplify the analysis, but is not crucial for the results.
-
-Additionally, customers can also choose from a unit mass of outside options, yielding utility $u^0_ij = \mu\epsilon^0_{ij}$.
+%     \label{fig:comparative_N_F}
+% \end{figure}
+
+% Finally, let us conclude this section by establishing a stronger result for a more restrictive class of profit functions.
+% In the following, I assume that the profit function has a specific, additive form.
+% Intuitively, this means that -- in terms of total profits generated -- the platform's and the fringe firms' products are substitutable to each other according to some constant ratio.
+% \begin{proposition}
+%     \label{prop:aggregate_size_additive}
+%     Let $f$ have the following, additive form:
+%     \begin{align*}
+%         f(N_P, N_F) = g(\alpha N_P + \beta N_F)
+%     \end{align*}
+%     where $\alpha, \beta > 0$.
+%     Also assume that $g$ is twice differentiable and that $g'' < 0$.
+%     Then
+%     \begin{align*}
+%         \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}.
+%     \end{align*}
+%     Furthermore,
+%     \begin{align*}
+%         \frac{\partial \Pi(N_P, N_F^*(N_P), N_C)}{\partial N_P} < 0.
+%     \end{align*}
+% \end{proposition}
+
+% The first part of this proposition is a stronger version of \cref{cor:fringe_entry}.
+% It states that, not only does the equilibrium number of fringe firms decrease as a response to an increase in $N_P$, but it establishes a lower bound for this decrease.
+% And, as the second part shows, this bound is sufficient to guarantee that the total size of the pie ($\Pi(N_P, N_F, N_C)$) also decreases in equilibrium.
+
+% This result has particularly strong implications in models where total profits (or total product variety) has a monotone relationship with consumer welfare, such as those in \textcite{anderson2020aggregative}.
+% \Cref{sec:example} also presents a demand system which satisfies this property.
+
+% \section{Logit demand}
+% \label{sec:example}
+
+% Let us now add more structure to the model, place the function $\Pi$ on more solid microfoundations.
+% The modeling strategy is heavily inspired by the logit-like demand structure and hybrid platform setting of \textcite{anderson2021hybrid}.
+% The setting can be thought of as a (possibly hybrid) platform market with monopolistically competing fringe firms.
+
+% In the main model, I consider the case when the total profit function only includes the sales of the platform's and fringe firms' products.
+% That is, the platform does not charge any entry fees to the consumers.
+% Here, I consider two variants of the model: a benchmark where the platform can unilaterally commit to any entry fee, and a bargaining model where the platform and the fringe firms negotiate over the distribution of profits.
+% Furthermore, I focus on a particular set of weight functions $w_P$ and $w_F$, which correspont to the Shapley-values of the players in the case of one-sided bargaining.
+
+% As an extension, in \cref{sec:lower_bargaining_power} I also examine what happens when the platform and the fringe firms have unequal bargaining weights, while still retaining more structure than the very general bargaining rule from \cref{ass:profit_sharing}.
+% In particular, I look at the case of bargaining outcomes being described by weighted values, with all fringe players sharing the same weight.
+% Furthermore, in \cref{sec:two_sided}, I also consider the case of two-sided bargaining, where the consumers also participate in the negotiation over the value produced.
+% Finally, \cref{sec:total_welfare_one_sided} explores the case of the platform being able to extract all of the consumer surplus from consumers.
+
+% Throughout the analysis, I treat the product variety of the platform and the number of consumers as exogenous, and focus on the equilibrium number of fringe firms.
+% Nevertheless, the results regarding equilibrium platform profits and consumer surplus are indicative of the potential general equilibrium behavior of the former two, as well.
+
+% \subsection{Setup}
+
+% \subsubsection{Demand}
+
+% Imagine that there is a unit mass of consumers, looking to buy one product each.
+% They choose from a continuum of products, indexed by $i$.
+% Customer $j$ derives the following utility from buying product $i$:
+% \begin{align*}
+%     u^F_{ij} = v^F_i - p^F_i + \mu\epsilon^F_{ij},
+% \end{align*}
+% where $v^F_i$ is the value of product $i$, $p^F_i$ is its price, and $\epsilon^F_{ij}$ is an idiosyncratic taste shock.
+% Throughout this section I assume that the value of each product is the same: $v^F_i = v^F$.
+% This is to simplify the analysis, but is not crucial for the results.
+
+% Additionally, customers can also choose from a unit mass of outside options, yielding utility $u^0_ij = \mu\epsilon^0_{ij}$.
 $\epsilon^F_{ij}$ and $\epsilon^0_{ij}$ are assumed to be independent and identically distributed (i.i.d.) across consumers and products, and follow a standardized Type I Extreme Value distribution.
@@
 
-\subsubsection{Production}
-
-Each (horizontally differentiated) product is produced by a single, monopolistically competitive (fringe) seller.
-The production entails a constant marginal cost $c^F_i$.
-As with the value, I assume that the marginal cost is the same for all products: $c^F_i = c^F$.
-Facing the demand described in the previous paragraphs, the sellers choose their price $p^F_i$ to maximize profits.
-
-Additionally, the platform itself can also offer mass $N_P$ of its own products.
-The value and marginal cost of these products are denoted by $v^P$ and $c^P$, respectively.
-Furthermore, consumers have the same i.i.d. taste shocks ($\epsilon^P_{ij}$) for platform products as for the products offered by the other sellers.
-Finally, I assume that the platform prices its products as if they were produced by separate, monopolistically competitive sellers.
-That is, it does not take into account the fact that it can affect a non-zero measure of the prices, and therefore the aggregate demand.
-This is to simplify the example, but I expect that it does not affect the main results qualitatively
-
-\subsubsection{Intermediation}
-
-The overall structure of the model comes from \cref{sec:model}: assume that the sellers and the consumers can only interact through an intermediary platform, denoted by $P$.
-Without the platform, the fringe firms are not able to sell their products, and thus make no profits.
-For this service, the platform can charge a lump-sum entry fee $F_F$ to each fringe firm.\footnote{
-    This is a critical difference from \textcite[]{anderson2021hybrid}, where the platform charges a per-unit royalty.
-    % TODO: elaborate on this
-}
-In the baseline model, I assume that entry is free for the consumers, and they are always present on the platform, no matter the other players' entry and pricing decisions.\footnote{
-    This essentially means that I assume a one-sided platform, without the usual network effects.
-}
-Later on, I look at the case of the platform appropriating consumer surplus, and also the case of consumers participating in the bargaining over the total surplus.
-
-As mentioned above, instead of operating as a pure marketplace, the platform may also produce and offer its own products.
-Therefore, there are three potential modes of operation.
-First, it can offer no product on its own ($N_P = 0$), and operate as a pure marketplace.
-Second, it can offer a selection of products alongside with a number of competing fringe firms also being present on the platform ($N_P, N_F > 0$).
-In this case, it is a hybrid platform.
-Finally, it can operate as a pure retailer, offering its own products, but no products from other sellers ($N_P > 0, N_F = 0$).
-
-\subsubsection{Entry and timing}
-
-\subsection{Equilibrium}
-
-\subsubsection{Demand and producer profits}
-
-As shown in \textcite[]{anderson2021hybrid}, the utility functions described in \cref{sec:model} give rise to a logit-type demand function.
+% \subsubsection{Production}
+
+% Each (horizontally differentiated) product is produced by a single, monopolistically competitive (fringe) seller.
+% The production entails a constant marginal cost $c^F_i$.
+% As with the value, I assume that the marginal cost is the same for all products: $c^F_i = c^F$.
+% Facing the demand described in the previous paragraphs, the sellers choose their price $p^F_i$ to maximize profits.
+
+% Additionally, the platform itself can also offer mass $N_P$ of its own products.
+% The value and marginal cost of these products are denoted by $v^P$ and $c^P$, respectively.
+% Furthermore, consumers have the same i.i.d. taste shocks ($\epsilon^P_{ij}$) for platform products as for the products offered by the other sellers.
+% Finally, I assume that the platform prices its products as if they were produced by separate, monopolistically competitive sellers.
+% That is, it does not take into account the fact that it can affect a non-zero measure of the prices, and therefore the aggregate demand.
+% This is to simplify the example, but I expect that it does not affect the main results qualitatively
+
+% \subsubsection{Intermediation}
+
+% The overall structure of the model comes from \cref{sec:model}: assume that the sellers and the consumers can only interact through an intermediary platform, denoted by $P$.
+% Without the platform, the fringe firms are not able to sell their products, and thus make no profits.
+% For this service, the platform can charge a lump-sum entry fee $F_F$ to each fringe firm.\footnote{
+%     This is a critical difference from \textcite[]{anderson2021hybrid}, where the platform charges a per-unit royalty.
+%     % TODO: elaborate on this
+% }
+% In the baseline model, I assume that entry is free for the consumers, and they are always present on the platform, no matter the other players' entry and pricing decisions.\footnote{
+%     This essentially means that I assume a one-sided platform, without the usual network effects.
+% }
+% Later on, I look at the case of the platform appropriating consumer surplus, and also the case of consumers participating in the bargaining over the total surplus.
+
+% As mentioned above, instead of operating as a pure marketplace, the platform may also produce and offer its own products.
+% Therefore, there are three potential modes of operation.
+% First, it can offer no product on its own ($N_P = 0$), and operate as a pure marketplace.
+% Second, it can offer a selection of products alongside with a number of competing fringe firms also being present on the platform ($N_P, N_F > 0$).
+% In this case, it is a hybrid platform.
+% Finally, it can operate as a pure retailer, offering its own products, but no products from other sellers ($N_P > 0, N_F = 0$).
+
+% \subsubsection{Entry and timing}
+
+\section{Results}
+
+I will now present the main results of the model, again, starting from the final subgame and working backwards.
+For each subgame, I also demonstrate that the equilibrium exists and is unique, and therefore the complete game also has a unique equilibrium.
+
+\subsection{Demand and producer profits}
+
+As the final, price-setting subgame is the same in both the benchmark and the bargaining model, the results in this subsection apply to both.
+Discrete choice models with type I Extreme Value errors give rise to a logit-type demand function \parencite[e.g.][]{small1981applied}.
+More specifically, \textcite[]{anderson2021hybrid} utilize the exact same utility structure as in \cref{sec:model}, and show that it gives rise to the following demand function.
 \begin{proposition}
@@
     \begin{align*}
-        x_{Ti} = \frac{\exp\left( \frac{v_T - p_{Ti}}{\mu} \right)}{A}
+        x_{T_i} = \frac{\exp\left( \frac{v_T - p_{T_i}}{\mu} \right)}{A}
     \end{align*}
@@
     \begin{align}
-        A = \int_0^{N_F} \exp\left( \frac{v_F - p_{Fi}}{\mu} \right) \di + \int_0^{N_P} \exp\left( \frac{v_P - p_{Pi}}{\mu} \right) \di + 1.
+        A = \int_0^{N_F} \exp\left( \frac{v_F - p_{F_i}}{\mu} \right) \di + \int_0^{N_P} \exp\left( \frac{v_P - p_{P_i}}{\mu} \right) \di + 1.
         \label{eq:aggregate}
@@
 As one would expect, demand is increasing in this net value, and decreasing in the competitors' net values.
-Furthermore, demand for each product is increasing in $\mu$, which can be thought of as the degree of product differentiation or the importance of taste shocks.
+Furthermore, demand for each product is increasing in $\mu$, which describes the degree of product differentiation or the importance of taste shocks.
 Finally, notice that, as each producer is infinitesimal, its pricing decision does not affect the aggregate $A$.
@@
     \label{prop:optimal_profit}
-    The profit maximizing price for product $Ti$ is
-    \begin{align*}
-        p^*_{Ti} = c_T + \mu,
+    The profit maximizing price for product $T_i$ is
+    \begin{align*}
+        p^*_{T_i} = c_T + \mu,
     \end{align*}
@@
     \begin{align}
-        \pi^{v*}_{Ti} = \mu \frac{\exp \left( \frac{v_T - c_T - \mu}{\mu} \right)}{A}.
+        \pi^{v*}_{T_i} = \mu \frac{\exp \left( \frac{v_T - c_T - \mu}{\mu} \right)}{A}.
         \label{eq:optimal_profit}
@@
 
-\subsubsection{Benchmark: platform sets entry fee unilaterally}
-
+\subsection{Benchmark: platform sets entry fee unilaterally}
+
+Let us now turn to platform entry fees and fringe entry decisions in the benchmark model.
 Recall that there is an infinity of potential fringe entrants looking to enter the market.
@@
 The intuition behind this is that per-firm fringe profits only depend on these factors indirectly, through the size of the aggregate.
-That is, unless the fringe is not feasible, an increase in $N_P$ will simply replace some fringe entrants, but the free entry condition will pin down the same aggregate, as before.
+Therefore, the zero profit condition for the fringe firms pins down the aggregate in equilibrium (as long as the fringe is feasible).
+That is, an increase in $N_P$ will simply replace some fringe entrants, but the free entry condition will pin down the same aggregate regardless of the number of platform products.
 
@@
 
-\begin{proposition}
+\begin{theorem}
     \label{prop:optimal_entry_fee}
-    The optimal entry fee is
+    The optimal entry fee when the platform is operating in the hybrid regime is unique and given by
     \begin{align*}
@@
     \end{align*}
-    The platform's total profit is
-    \begin{align*}
-        \pi_P^{t} = \mu - 2\sqrt{\frac{I_F \mu}{V_F}} + \frac{I_F}{V_F} (N_P V_P + 1)
-    \end{align*}
-    in the hybrid regime, and
-    \begin{align*}
-        \pi_P^{t} = \pi_P^{v} = \mu \frac{ N_P V_P}{N_P V_P + 1}
-    \end{align*}
-    in the retail regime.
-\end{proposition}
-Note, that even though the platform's profit is increasing in the number of its products, the optimal entry fee does not depend on it (\cref{fig:platform_profits,fig:entry_fee}).
-This is only due to the fact that the platform's product does not require any investment cost.
-If the platform is operating in the hybrid regime, less fringe firms are needed to achieve the (fixed) equilibrium aggregate, therefore there is less expenditure on investment costs, which is essentially wasted.
-Consequently, in the hybrid regime, the derivative of optimal profits with respect to the platform's product variety is simply the fringe's investment cost, adjusted for the possible difference in product value:
+    The platform's total profit in this case is
+    \begin{align*}
+        \pi_P^{t} = \mu - 2\sqrt{\frac{I_F \mu}{V_F}} + \frac{I_F}{V_F} (N_P V_P + 1).
+    \end{align*}
+    When the optimal mode of operation is retail, the platform's profit is
+    \begin{align*}
+        \pi_P^{t} = \pi_P^{v} = \mu \frac{ N_P V_P}{N_P V_P + 1}.
+    \end{align*}
+\end{theorem}
+
+First, let us look at the case when the platform finds it optimal to operate in the hybrid regime.
+Notice that the optimal entry fee does not depend on either the platform's product value or product variety (\cref{fig:entry_fee}).
+This is because due to the lump-sum nature of the entry fee, the platform can extract all the surplus from the fringe firms, and thus chooses $F_F$ to maximize total industry profits.
+The latter is essentially a function of the aggregate, minus the investment costs of the fringe firms.
+As I have shown in \cref{prop:equilibrium_aggregate}, the aggregate is independent of the platform's product variety in the hybrid regime, and therefore the optimal entry fee is also independent of it.
+
+On the other hand, the platform's profit is increasing in the number of its products (\cref{fig:platform_profits}).
+This is a rather mechanical result: the platform's product variety is exogenous, and therefore possible investment costs are not modeled.
+If the platform is operating in the hybrid regime, less fringe firms are needed to achieve the (fixed) equilibrium aggregate, therefore there is less expenditure on (essentially wasted) investment costs.
+Consequently, in the hybrid regime, the derivative of optimal profits with respect to the platform's product variety is simply the fringe's investment cost, adjusted for the possible difference in product value.
+\begin{corollary}
     \begin{align*}
@@
     \end{align*}
-Furthermore, if the platform does have to pay an investment cost $I_P$, then it will only have its own products if $\frac{I_P}{V_P} \leq \frac{I_F}{V_F}$, which is efficient from a welfare perspective.
-
-As a consequence, as long as the fringe is feasible at the optimal entry fee, the size of the aggregate, and hence consumer welfare is also unaffected by the platform operating in hybrid mode.
-In contrast, when the fringe is not present in the market, total aggregate, and hence consumer welfare are increasing in the number of the platform's products.
-This effect is purely mechanical: more variety leads to higher welfare.
-\Cref{fig:fringe_entry_eq} illustrates this effect.
+\end{corollary}
+This results also have implications for what would happen if the platform's product variety was an endogenous choice.
+It would only choose to operate in a hybrid mode if it had some advantage over the fringe firm's products (either in investment cost, production cost, or product value).
+Otherwise, it would simply operate as a pure intermediary, and the number of fringe firms would adjust to the equilibrium aggregate.
+
+Another important corollary of \cref{prop:optimal_entry_fee} is that consumer welfare is also unaffected by the platform's product variety in the hybrid regime.
+\begin{corollary}
+    \begin{align*}
+        N_F > 0 \implies \frac{\partial CS}{\partial N_P} = 0.
+    \end{align*}
+\end{corollary}
+This result is a direct consequence of the facts that the aggregate is independent of the platform's product variety in the hybrid regime, and that consumer surplus is a monotone increasing function of the aggregate.
+
+Next, let us turn to the case when the platform finds it optimal to operate as a pure retailer.
+In this case, the only products on the market are the platform's own products.
+Therefore, quite mechanically, the aggregate, and thus consumer surplus, are increasing in the number of the platform's products.
+\begin{corollary}
+    \begin{align*}
+        N_F = 0 \implies \frac{\partial CS}{\partial N_P} = \frac{V_P}{1 + N_P V_P} > 0.
+    \end{align*}
+\end{corollary}
 
@@
 Therefore, for a given $N_P$, the platform prefers to operate in hybrid mode, and does not want to exclude fringe firms from the market.
-As a corollary, in the benchmark model, a platform becoming a hybrid platform, or increasing the number of its own products, always has a weakly positive effect on the aggregate, and thus consumer welfare.\footnote{
+This fact, together with the previous corollaries, implies that the platform's product variety always has a weakly positive effect on consumer welfare.\footnote{
     This is in contrast to \textcite{anderson2021hybrid}, where a platform operating in hybrid mode sets higher royalties to create a price advantage for its own products.
     The reason for this difference lies in the type of entry fee: they assume a revenue-based, proportional fee, which distorts prices.
-    In contrast, in this paper, I assume a non-distortive lump sum fee.
+    In contrast, in this paper, I assume a non-distortive, lump sum fee.
 }
-\subsubsection{Main model: bargaining between platform and fringe}
+\begin{corollary}
+    \begin{align*}
+        \frac{\partial CS}{\partial N_P} \geq 0.
+    \end{align*}
+\end{corollary}
+It either has no effect (hybrid operation), or it increases the aggregate (pure retailer), and thus consumer surplus.
+\Cref{fig:fringe_entry_eq} illustrates this effect.
+
+Finally, these results also suggest that if the platform's product variety (and thus also the pure marketplace/ hybrid mode decision) was endogenous, an improvement in the platform's product (either higher value or lower cost) would also have a weakly positive effect on consumer welfare.
+Therefore, it suggests that platform's having their own products are always weakly beneficial for consumers.
+This surprising result depends on a number of -- admittedly unrealistic -- assumptions.
+Namely, the lump-sum nature of the entry fee, no entry fee for consumers, and the platform pricing its products as if they were produced by separate sellers.
+Therefore, one should not take this result as a conclusion applicable to the real world, but as a best-case benchmark.
+On the other hand, these assumptions are also why this model is so useful as a benchmark: as I show in the next subsection, even with these assumptions in place, the platform's product can have a negative effect on consumer welfare if the entry fee is set through bargaining.
+
+\subsection{Bargaining: platform and entrants negotiate over entry fees}
 
@@
     \begin{align*}
-        \pi^v_{Ti}(p_{Ti}) &= (p_{Ti} - c_T) x_{T_i}(p_{Ti}) \\
-        &= (p_{Ti} - c_T) \frac{\exp\left( \frac{v_T - p_{Ti}}{\mu} \right)}{A}.
-    \end{align*}
-    Note that $A$ is not influenced by changes in $p_{Ti}$, as $A$ is an integral and $p_T$ is only changed on a zero-measure (singleton) set.
+        \pi^v_{T_i}(p_{T_i}) &= (p_{T_i} - c_T) x_{T_i}(p_{Ti}) \\
+        &= (p_{T_i} - c_T) \frac{\exp\left( \frac{v_T - p_{T_i}}{\mu} \right)}{A}.
+    \end{align*}
+    Note that $A$ is not influenced by changes in $p_{T_i}$, as $A$ is an integral and $p_T$ is only changed on a zero-measure (singleton) set.
     Therefore, let calculate the first order condition while treating $A$ as a constant:
@@
         \label{eq:foc_profit}
-        \mu \frac{\exp\left( \frac{v_T - p_{Ti}}{\mu} \right)}{A} \left[ \frac{p_T - c_T}{\mu} - 1 \right] = 0.
+        \mu \frac{\exp\left( \frac{v_T - p_{T_i}}{\mu} \right)}{A} \left[ \frac{p_T - c_T}{\mu} - 1 \right] = 0.
     \end{align}
-    Also note that $\pi_{Ti}(p_{Ti})$ is strictly concave, so the FOC is sufficient for optimality.
+    Also note that $\pi_{T_i}(p_{T_i})$ is strictly concave, so the FOC is sufficient for optimality.
 
@@
     \begin{align*}
-        p_{Ti}^* = c_T + \mu
+        p_{T_i}^* = c_T + \mu
     \end{align*}
@@
     \begin{align*}
-        \pi_{Ti}^{v*} = \mu \frac{\exp \left( \frac{v_T - c_T - \mu}{\mu} \right)}{A}.
+        \pi_{T_i}^{v*} = \mu \frac{\exp \left( \frac{v_T - c_T - \mu}{\mu} \right)}{A}.
     \end{align*}
@@
 \begin{proof}[Proof of \cref{prop:equilibrium_aggregate}]
-    From \cref{prop:optimal_profit}, the variable profit of each fringe firm is $\pi_{Fi}^{v*} = \mu V_F / A$.
-    Total profit after entry fees and investment costs is therefore $\pi_{Fi}^{t*} = \mu V_F / A - I_F - F_F$.
+    From \cref{prop:optimal_profit}, the variable profit of each fringe firm is $\pi_{F_i}^{v*} = \mu V_F / A$.
+    Total profit after entry fees and investment costs is therefore $\pi_{F_i}^{t*} = \mu V_F / A - I_F - F_F$.
     Under free entry, total profits are zero:
     \begin{align*}
-        0 = \pi_{Fi}^{t*} = \mu V_F / A - F_F - I_F.
+        0 = \pi_{F_i}^{t*} = \mu V_F / A - F_F - I_F.
     \end{align*}
@@
     \begin{align*}
-        \pi_P^t &= \pi_P^v + I_F N_F \\
+        \pi_P^t &= \pi_P^v + F_F N_F \\
         &= \mu \frac{N_P V_P}{F_F + I_F} + F_F \left[ \frac{\mu}{F_F + I_F} - N_P \frac{V_P}{V_F} - \frac{1}{V_F} \right].
@@
     The function is strictly concave in $F_F$, so the first order condition is sufficient for optimality in the case of an interior solution.
-    Assume that $N_F$ is high enough that the optimum is indeed interior.
+    Assume that that the optimum is indeed interior.
     Then the FOC is
@@
 
-    Now consider the case when $F_F$ is so large that $F_F^*$ would lead to no fringe entry.
+    Now consider the case when $F_F^*$ is so large that it would lead to no fringe entry.
     In that case, the platform's only source of profit is selling its own products, and thus

### 2024-05-03 src/paper/application.tex
Rewrite bargaining part

@@
 
-Assume that there are three types of players in the market: a platform $P$, a continuum of fringe sellers $F_i$ ($i \in [0, N_C$]) and a continuum of consumers $C_j$ ($j \in [0, N_C$]).
+Assume that there are two types of players in the market: a platform $P$, a continuum of fringe sellers $F_i$ ($i \in [0, N_F$]) and a continuum of consumers $C_j$ ($j \in [0, 1]$).
 The fringe firms have one product each, which they can only sell through the platform.
@@
 
-Imagine that there is an $N_C$ mass of consumers, looking to buy one product each.
+Imagine that there is a unit mass of consumers, looking to buy one product each.
 They choose from a continuum of products, which are either produced by the fringe (indexed by $F_i$), by the platform ($P_i$) and a unit mass of outside options ($0_i$).
@@
 \subsubsection{Bargaining case}
+\label{sec:model_bargaining}
 
@@
 Now, for every $s N_F$ ($s \in [0, 1]$), calculate the total profits that would be realized if the platform and $n_f$ fringe firms were the only players in the market, and they engaged in monopolistic competition as described in the previous paragraph.
-Let us denote these profits by $\pi^v_{F}(N_C, N_P, s N_F)$ and $\pi^v_{P}(N_C, N_P, s N_F)$, and the corresponding industry-wide total profits by $\Pi$ and $\Pi(N_C, N_P, s N_F)$.
+Let us denote these profits by $\pi^v_{F}(N_P,s N_F)$ and $\pi^v_{P}(N_P,s N_F)$, and the corresponding industry-wide total profits by $\Pi$ and $\Pi(N_P,s N_F, N_C)$.
 
@@
     \begin{align*}
-        \pi^t_P(N_P, N_F, N_C) &= N_C \int_0^1 \Pi(N_C, N_P, s N_F) \ds, \\
-        \pi^t_F(N_P, N_F, N_C) &= N_C \int_0^1 \partial_3 N_F \Pi(N_C, N_P, s N_F) \ds.
+        \pi^t_P(N_P, N_F) &= N_C \int_0^1 \Pi(N_P,s N_F) \ds, \\
+        \pi^t_F(N_P, N_F) &= N_C \int_0^1 \partial_2 N_F \Pi(N_P,s N_F) \ds.
     \end{align*}
@@
 Finally, another important feature of this demand system is that, assuming optimal pricing, consumer welfare only depends on the size of the aggregate \parencite{anderson2020aggregative}.
-In particular, consumer surplus is proportional to the logarithm of the aggregate: $CS = \mu N_C \log(A)$. This fact makes welfare analysis rather simple in this setting.
+In particular, consumer surplus is proportional to the logarithm of the aggregate: $CS = \mu \log(A)$. This fact makes welfare analysis rather simple in this setting.
 
@@
 
-Let us now turn to platform entry fees and fringe entry decisions in the benchmark model.
+Let us now examine entry fees and fringe entry decisions in the benchmark model.
 Recall that there is an infinity of potential fringe entrants looking to enter the market.
@@
     \begin{align*}
-        N_F = 0 \implies \frac{\partial CS}{\partial N_P} = \frac{V_P}{1 + N_P V_P} > 0.
+        N_F = 0 \implies \frac{\partial CS}{\partial N_P} = \frac{\mu V_P}{1 + N_P V_P} > 0.
     \end{align*}
@@
 
-Now consider the case where, instead of the platform setting take it or leave it entry fees, it must negotiate with the fringe about the division of profits.
-As the platform cannot choose and commit to an entry fee, the first period from the benchmark model is skipped.
-Instead, the game starts by fringe firms' investment decisions.
-After that, in the second period, bargaining takes place between the platform and the fringe firms that have entered the market.
-
-The participants negotiate over the aggregate profits that they expect to obtain in the subsequent period (assuming the same non-collusive, monopolistic pricing, as before).
-I assume that bargaining outcomes are determined according to \cref{ass:profit_sharing}, where $\Pi(N_P, N_F, N_C)$ is defined as the sum of profits that the platform and the entrants acquire by selling their products.
+Let us now turn to the main contribution of this paper: the case where the platform and the fringe firms negotiate over the division of profits.
+As the platform cannot choose and commit to an entry fee, the first two periods are switched compared to the benchmark model.
+The game starts by fringe firms' investment decisions, after which, in the second period, bargaining takes place between the platform and the entrants to determine the entry fee.
+
+As described in \cref{sec:model_bargaining}, the participants negotiate over the aggregate profits that they expect to obtain in the subsequent period (assuming the same non-collusive, monopolistic pricing, as before).
 From \cref{eq:optimal_profit}, the total profit achieved by the platform and $N_F$ fringe firms is given by
 \begin{align*}
-    \Pi(N_P, N_F, N_C) = N_C \underbracket{\mu \frac{n V_F + N_P V_P}{n V_F + N_P V_P + 1}}_{\coloneqq f(N_P, N_F)}.
-\end{align*}
-
-Let us assume that the bargaining results in profits being shared according to players' Shapley values.
-These Shapley values satisfy \cref{ass:profit_sharing}, with $w_P(s) \equiv 1$ and $w_F(s) = s$.\footnote{
-    For a discussion and proof of this claim, see \cref{sec:cooperative_game}.
-}
+    \Pi(N_P, N_F) = \mu \frac{n V_F + N_P V_P}{n V_F + N_P V_P + 1}.
+\end{align*}
+Bargaining outcomes are determined according to Shapley values, given by \cref{prop:shapley_value}.
 Based on these, one can even obtain closed-form expressions for platform and fringe profit shares for this class of demand systems.
@@
     \begin{align*}
-        \pi^t_P &= N_C \int_0^1 f(N_P, sN_F) \ds \\
-                &= \mu N_C \left[ 1 - \frac{\log \left(1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} \right].
-    \end{align*}
-    The total profits of the whole fringe (including investment costs) are given by
-    \begin{align*}
-        \pi^t_F = \mu N_C \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F N_F .
+        \pi^t_P = \mu \left[ 1 - \frac{\log \left(1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} \right].
+    \end{align*}
+    The total profits of the whole fringe (excluding investment costs) are given by
+    \begin{align*}
+        \pi^t_F = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right].
     \end{align*}
@@
 Now let us turn to how the platform's dual mode operation affects product variety and consumer welfare.
-I will rely on results from \cref{sec:results} to establish comparative statics for the equilibrium aggregate.
-Let us start by showing that $f(n_P, n_F)$ satisfies the assumptions those results rely on.
+I start by showing that the equilibrium is unique in this case, as well.
+This, and a few other results in this section\footnote{
+    These results do not actually rely on the specific logit demand system.
+    As long as the fringe profit function has the property described in \cref{lem:shape_of_fringe_profit}, and the total profit function satisfies some assumptions, the results hold.
+    \Cref{sec:more_general_results} provides more detail on the necessary assumptions.
+}, rely on the following lemma.
 \begin{lemma}
-    \label{lem:profit_assumptions}
-    $f(n_P, n_F)$ satisfies \cref{ass:single_crossing}.
-    Furthermore,
-    \begin{align*}
-        \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} < 0.
+    \label{lem:shape_of_fringe_profit}
+    For any $N_P, N_F \geq 0$, the fringe profit function is either concave or decreasing in $N_F$:
+    \begin{align*}
+        \frac{\pi_F^t(N_P, N_F)}{\partial N_F} < 0 \text{ or } \frac{\partial^2 \pi_F^t(N_P, N_F)}{\partial N_F^2} < 0 \quad \forall\, N_P, N_F \geq 0.
     \end{align*}
 \end{lemma}
-Using this, \cref{prop:unique_equilibrium} gives that the equilibrium is unique.
-Furthermore, \cref{cor:fringe_entry} implies that an increase in the number of the platform's products leads to a reduction in the number of fringe firms that enter the market.
-
-Owing to the additive nature of the total profit function, an even stronger result can be obtained.
-Notice that $f$ has the functional form required for proposition \ref{prop:aggregate_size_additive} with $g(x) = \frac{x}{1+x}, \alpha = V_P, \beta = V_F$.
-Therefore, the same proposition implies that
-\begin{align*}
-    \frac{\partial N_F^*}{\partial N_P} < -\frac{V_P}{V_F},
-\end{align*}
-that is, an increase in the platform's products leads to a more than proportional reduction in the number of fringe products (\cref{fig:fringe_entry_eq}).
-
-As a consequence of this, equilibrium total aggregate is also decreasing in $N_P$.\footnote{
-    The same result also holds true for an increase in the platform's product advantage $V_P$.
+This lemma states that the fringe profit function is hump-shaped in the sense that it starts with an increasing, concave part, after which it may turn into a decreasing (but not necessarily concave or convex) function of $N_F$.
+\Cref{fig:equilibrium} illustrates this property.
+
+While this lemma's main purpose is to help establish the other, more interpretable results in this chapter, it is also interesting in its own right.
+It shows that the number of fringe firms have a non-monotonic effect on the total profits of the fringe.
+That is, even though industry-wide profits are increasing in $N_F$, the share that the fringe can obtain may decrease after a certain point, not only in relative terms, but also in absolute terms.
+The underlying reason is that as the number of fringe firms increases, due to their substitutability with each other, their bargaining power decreases.
+This decrease can be large enough to offset the total pie getting larger.
+
+\begin{figure}[ht]
+    \centering
+    \begin{tikzpicture}[xscale=2,yscale=2,samples=200]
+        \draw[->] (0,0) -- (0,2);
+        \draw[->] (0,0) -- (5.5,0) node[below] {$N_F$};
+
+        \draw[name path=piF,domain=0.01:5.5,variable=\x,black] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
+        \draw[name path=IF,domain=0.01:5.5,variable=\x,black,dashed] plot ({\x},{(\x)/3});
+        \node[anchor=north east] at (5,1) {$\pi_F(N_P, N_F)$};
+        \node[anchor=south east] at (5,5/3) {$I_F N_F$};
+
+        \fill [name intersections={of=piF and IF, name=i, total=\t}]
+            [black] (i-2) circle (1pt);
+        \draw[dashed] (i-2) -- (i-2 |- 0,0) node[below] {$N_F^*$};
+    \end{tikzpicture}
+    \caption{An example equilibrium.
+\Cref{lem:shape_of_fringe_profit} states that the fringe profit function is concave or hump-shaped in $N_F$, guaranteeing at most one intersection with the linear entry cost function.}
+    \label{fig:equilibrium}
+\end{figure}
+
+An almost immediate corollary is that such a function must have (apart from the trivial $N_F=0$ case) at most one crossing with total investment costs, which is a linear function of $N_F$.
+Let us denote this point as $N_F^*$.
+Furthermore, if there exists such a crossing, then it must be that $\pi_F^t(N_F) > I_F N_F \forall\, N_F \in [0, N_F^*)$, and $\pi_F^t(N_F) < I_F N_F \forall\, N_F \in (N_F^*, \infty)$ (see \cref{fig:equilibrium}).
+Therefore, $N_F^*$ must be the unique number of equilibrium entrants.
+The following proposition formalizes this idea.
+\begin{proposition}
+    \label{prop:unique_equilibrium}
+    The equilibrium number of entrants $N_F^*$ is unique in the bargaining case.
+\end{proposition}
+
+Now let us examine how the platform's product variety affects fringe profits and the equilibrium number of fringe firms.
+First, let us establish that fringe profits are decreasing in the number of the platform's products.
+Note, that this is a partial equilibrium result: $N_F$ is assumed to be fixed, and the platform's product variety is increased.
+Later on, 
+\begin{proposition}
+    \label{prop:fringe_profits_partial}
+    For any $N_P, N_F \geq 0$, the fringe profit function is decreasing in $N_P$:
+    \begin{align*}
+        \frac{\partial \pi_F^t(N_P, N_F)}{\partial N_P} < 0.
+    \end{align*}
+\end{proposition}
+
+Together with the hump-shaped fringe profit function, this implies that an increase in the platform's product variety leads to a reduction in the number of fringe firms.
+\Cref{fig:comparative_N_F} illustrates this idea.
+What is not immediately clear is how this affects the total size of the aggregate, and consumer welfare.
+In the benchmark case, the decrease in the number of fringe firms was exactly offset by an increase in the platform's product variety, and the aggregate remained constant.
+The following results shows that this is not the case in the bargaining model: as long as the platform is in the hybrid regime, the aggregate decreases in the number of the platform's products.\footnote{
+    Similar results hold for an increase in the platform's product value $V_P$.
 }
-As, in this model, consumer welfare is monotone in the total aggregate, this implies that consumer welfare is decreasing in the number of the platform's products (\cref{fig:welfare_consumer_surplus}).
-Therefore, as opposed to the benchmark model, the platform becoming more hybrid leads to a reduction in consumer welfare.\footnote{
-    Unless $V_P N_P$ is high enough that the platform would operate in pure retail mode in the benchmark model, too.
-}
+
+\begin{proposition}
+    Assume that the platform is operating in the hybrid regime.
+Then, the equilibrium number of fringe firms is decreasing in the number of the platform's products.
+Furthermore, this decrease is more than proportional to the increase in the platform's product variety (also taking into account product value).
+    \begin{align*}
+        N_F > 0 \implies \frac{\partial N_F}{\partial N_P} < -\frac{V_P}{V_F} < 0.
+    \end{align*}
+\end{proposition}
+
+\begin{corollary}
+    Assume that the platform is operating in the hybrid regime. Then the equilibrium aggregate and consumer surplus is decreasing in the number of the platform's products.
+    \begin{align*}
+        N_F > 0 \implies \frac{\partial A}{\partial N_P}, \frac{\partial CS}{\partial N_P} < 0.
+    \end{align*}
+\end{corollary}
+
+\begin{figure}[ht]
+    \centering
+    \begin{tikzpicture}[xscale=2,yscale=2,samples=200]
+        \draw[->] (0,0) -- (0,2);
+        \draw[->] (0,0) -- (5.5,0) node[below] {$N_F$};
+
+        \draw[name path=piF,domain=0.01:5.5,variable=\x,black] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
+        \draw[name path=piF2,domain=0.01:5.5,variable=\x,black] plot ({\x},{6*((\x)/(0.3+\x))-6*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
+        \draw[name path=IF,domain=0.01:5.5,variable=\x,black,dashed] plot ({\x},{(\x)/3});
+
+        \node[anchor=south] at (5,1) {$\pi_F(N_P, N_F)$};
+        \node[anchor=north] at (5,0.6) {$\pi_F(N_P', N_F)$};
+        \node[anchor=south east] at (5,5/3) {$I_F N_F$};
+
+        \fill [name intersections={of=piF and IF, name=i, total=\t}]
+            [black] (i-2) circle (1pt);
+        \draw[dashed] (i-2) -- (i-2 |- 0,0) node[below] {$N_F^*$};
+        \fill [name intersections={of=piF2 and IF, name=i2, total=\t}]
+            [black] (i2-2) circle (1pt);
+        \draw[dashed] (i2-2) -- (i2-2 |- 0,0) node[below] {${N_F^*}'$};
+
+        \draw[->] (i-2 |- 0,0.5) -- (i2-2 |- 0,0.5);
+    \end{tikzpicture}
+    \caption{Illustration of comparative statics for equilibrium entry.
+If the change in $N_P$ decreases the fringe's profits for every $N_F \geq 0$, then equilibrium can be restored by decreasing the number of fringe entrants.}
+    \label{fig:comparative_N_F}
+\end{figure}
+
+When the fringe is not viable, the platform's product variety has the same, mechanical effect on total aggregate and consumer surplus as in the benchmark model.
+\begin{proposition}
+    Assume that the platform is operating in the pure retail regime. Then the equilibrium aggregate and consumer surplus is increasing in the number of the platform's products.
+    \begin{align*}
+        N_F = 0 \implies \frac{\partial A}{\partial N_P}, \frac{\partial CS}{\partial N_P} > 0.
+    \end{align*}
+\end{proposition}
+This set of results is in stark contrast to the benchmark model.
+Instead of increased product variety weakly increasing consumer welfare, when entry fees are negotiated, it can actually decrease it if the platform stays in the hybrid regime.
+
+This conclusion is in line with many of the findings in the literature on hybrid platforms, such as \textcite{hagiu2022should} or \textcite{anderson2021hybrid}.
+The channel through which this happens, and thus the potential policy implications, are quite different, however.
+In \textcite{hagiu2022should}, the negative consequences are due to its incentives to engage in anti-competitive behavior, such as self-preferencing or imitation.
+In their model, in the absence of such behavior, hybrid platforms can actually increase consumer welfare.
+\textcite{anderson2021hybrid}, on the other hand, shows that even in the absence of such behavior, hybrid platforms can harm consumers, as platforms are inclined to set higher than optimal royalties to create a price advantage for their own products.
+This model goes one step further.
+Due to the lump-sum nature of the entry fee and platforms pricing their products as if they were produced by separate sellers, this inventive is no more present (as demonstrated by the benchmark model).
+However, the fact that the platform having its own products improves its bargaining position leads to a different distortion: the platform sets higher entry fees than it would if it had no products on its own.
+
+\subsection{Comparison and example}
+
+% TODO: theorem summarizing the most important results.
 
@@
 \end{proof}
-Note, that this expression is of the form $\Pi(N_C, N_P, N_F) = N_C f(N_P, N_F)$.
+Note, that this expression is of the form $\Pi(N_P, N_P, N_C) = N_C f(N_P, N_F)$.
 Furthermore, $f(N_P, N_F) = g(V_P N_P + V_F N_F)$ for an increasing, strictly concave $g$.

### 2024-05-08 src/paper/application.tex
Finish rearranging results section

@@
     \begin{align*}
-        N_F = 0 \implies \frac{\partial CS}{\partial N_P} = \frac{\mu V_P}{1 + N_P V_P} > 0.
+        N_F = 0 \implies \frac{\partial CS}{\partial N_P} = \frac{\mu V_P}{(1 + N_P V_P)^2} > 0.
     \end{align*}
@@
 
-\subsection{Comparison and example}
-
-% TODO: theorem summarizing the most important results.
-
-The intuition behind this is demonstrated in can be captured by looking at entry fees.
-First, define the implied entry fee in the bargaining case as the difference between the variable profit and the final, total profit of the fringe firms, less the investment cost:
-\begin{align*}
-    F_F^{\text{impl}} = \pi_F^v - \pi_F^t + I_F.
-\end{align*}
-As shown before, the platform's product variety grows, its bargaining power also increases.
-This can be thought of as an increase in (implied) entry fees $F_F^{\text{impl}}$, which in turn discourages fringe entry \cref{fig:entry_fee}.
-
-In this specific demand system and parametrization, the implied entry fee is higher than what the platform would prefer to set for any $N_P \geq 0$.
+\subsection{Example and comparison}
+
+In this section, I look a specific example to illustrate the main results and compare the benchmark and bargaining models.
+But first, let us collect and state the most important results from the previous sections in one theorem each for both models.
+
+In the benchmark model, the platform having its own product variety has a weakly positive effect.
+As long as the market is in the hybrid regime, and there is a non-zero number of fringe firms, it has no effect on the aggregate or consumer surplus.
+When the fringe is no longer feasible, and the platform is in the pure retail regime, the platform's product variety mechanically increases both.
+\begin{theorem}
+    In the benchmark model with unilateral price setting, in a hybrid regime equilibrium (with $N_F > 0$), the following results hold:
+    \begin{itemize}
+        \item The equilibrium number of fringe firms decreases in the number of the platform's products: $\frac{\partial N_F}{\partial N_P} = -\frac{V_P}{V_F} 0$.
+        \item The aggregate is independent of the platform's product variety: $\frac{\partial A}{\partial N_P} = 0$.
+        \item Consumer surplus is independent of the platform's product variety: $\frac{\partial CS}{\partial N_P} = 0$.
+        % \item The platform's profit is increasing in the number of its products: $\frac{\partial \pi_P^t}{\partial N_P} = \frac{V_P}{V_F} I_F$.
+    \end{itemize}
+\end{theorem}
+
+In contrast, in the bargaining model, increasing the platform's product variety can have a negative effect on consumer welfare.
+The reason for this is that the platform's product variety increases its bargaining power, and thus decreases the share that the fringe firms obtain.
+This in turn leads to a decrease in the number of fringe firms, and this decrease is large enough to offset the increase in the platform's product variety.
+\begin{theorem}
+    In the bargaining model, in a hybrid regime equilibrium (with $N_F > 0$), the following results hold:
+    \begin{itemize}
+        \item The equilibrium number of fringe firms decreases in the number of the platform's products more than in the benchmark case: $\frac{\partial N_F}{\partial N_P} < -\frac{V_P}{V_F} 0$.
+        \item The aggregate decreases in the platform's product variety: $\frac{\partial A}{\partial N_P} < 0$.
+        \item Consumer surplus decreases in the platform's product variety: $\frac{\partial CS}{\partial N_P} < 0$.
+    \end{itemize}
+\end{theorem}
+
+The statements of these theorems are illustrated in \cref{fig:comparative_N_F} and \cref{fig:welfare_aggregate} and \cref{fig:platform_profits}.
+The intuition behind these results can be demonstrated by looking at entry fees.
+First, define the implied entry fee in the bargaining case as the difference between the variable profit and the final, total profit of the fringe firms (bar the investment cost):
+\begin{align*}
+    F_F^{\text{impl}} = \pi_F^v - \pi_F^t.
+\end{align*}
+As shown before, as the platform's product variety grows, its bargaining power also increases.
+This can be thought of as an increase in (implied) entry fees $F_F^{\text{impl}}$, which in turn discourages fringe entry.
+This is not happening in the benchmark model, as the optimal entry fee does not depend on the platform's product variety.
+\Cref{fig:entry_fee} demonstrates this effect.
+
+In the example parametrization, the implied entry fee is higher than what the platform would prefer to set for any $N_P \geq 0$.
 If it could, it would commit to a lower entry fee to incentivize more fringe entry, and thus increase total profits.
@@
 
-This means that, if the platform had to create its product variety at a per-unit investment cost of $I_P$, it would make different (inefficient) choices compared to the benchmark model.
-In particular, it might invest in some products even if it has a product disadvantage, and it might not invest in some products even if it has a product disadvantage.
-This phenomenon is more pronounced when the implied entry fee for $N_P = 0$ is lower than optimal, and is explored in more detail in \cref{sec:lower_bargaining_power}.
+% This means that, if the platform had to create its product variety at a per-unit investment cost of $I_P$, it would make different (inefficient) choices compared to the benchmark model.
+% In particular, it might invest in some products even if it has a product disadvantage, and it might not invest in some products even if it has a product disadvantage.
+% This phenomenon is more pronounced when the implied entry fee for $N_P = 0$ is lower than optimal, and is explored in more detail in \cref{sec:lower_bargaining_power}.
 
@@
         \caption{Aggregate ($A$)}
+        \label{fig:welfare_aggregate}
     \end{subfigure}
@@
 In the previous sections, I assumed that the platform and the fringe firms split total profits according to their Shapley values.
-Because of the symmetry property of the Shapley value, this excludes the possibility of players having some kind of innate bargaining power, which is not related to the profit functions.
-In this extension, I will relax this assumption, and assume instead that profits are shared according to \emph{weighed} Shapley values.
+Because of the symmetry property of the Shapley value, this excludes the possibility of players having some kind of innate bargaining power, which is not related to their profit functions.
+In this extension, I will relax this assumption, and assume instead that profits are shared according to \emph{weighed} values.
 These are a generalization of the Shapley value, where each player has a weight $w_i$ that can, in certain settings, be thought of as a parameter describing bargaining power.\footnote{
@@
 }
-Similarly to the standard Shapley value, one can show that outcomes based on weighted values also satisfy \cref{ass:profit_sharing}.
-Specifically, when the weight of the platform is $\lambda_P$, the functions $w_P$ and $w_F$ are given by
-\begin{align*}
-    w_P(s) &= \lambda_P s ^ {\lambda_P - 1} \\
-    w_F(s) &= s ^ {\lambda_P}.
-\end{align*}
+TODO: rewrite this
+% Similarly to the standard Shapley value, one can show that outcomes based on weighted values also satisfy \cref{ass:profit_sharing}.
+% Specifically, when the weight of the platform is $\lambda_P$, the functions $w_P$ and $w_F$ are given by
+% \begin{align*}
+%     w_P(s) &= \lambda_P s ^ {\lambda_P - 1} \\
+%     w_F(s) &= s ^ {\lambda_P}.
+% \end{align*}
 

### 2024-05-09 src/paper/application.tex
Update extension 1

@@
 
-\subsection{Platform has lower innate bargaining power}
+\subsection{Playrs have different innate bargaining power}
 \label{sec:lower_bargaining_power}
@@
 }
-TODO: rewrite this
-% Similarly to the standard Shapley value, one can show that outcomes based on weighted values also satisfy \cref{ass:profit_sharing}.
-% Specifically, when the weight of the platform is $\lambda_P$, the functions $w_P$ and $w_F$ are given by
-% \begin{align*}
-%     w_P(s) &= \lambda_P s ^ {\lambda_P - 1} \\
-%     w_F(s) &= s ^ {\lambda_P}.
-% \end{align*}
-
-\textcolor{red}{TODO: can I show that \cref{ass:single_crossing} still holds for any $\lambda_P$? If not, focus on a specific case, such as the one on the graphs.}
+I still assume that fringe firms are identical, also in regard to their bargaining weights.
+Therefore, the only difference is between the platform and the fringe firms.
+Let us denote the platform's bargaining weight as $\lambda_P \in \mathbb{R}^+$, and without loss of generality, normalize the fringe firms' weights to 1.
+
+As shown in \cref{sec:cooperative_game_weighted}, the weighted Shapley value, and thus final profits in this setting is given by
+\begin{proposition}
+    \label{prop:weighted_shapley_value}
+    The Shapley value of the platform and the fringe firms, and thus final total profits, are given by:
+    \begin{align*}
+        \pi^t_P(N_P, N_F) &= N_C \int_0^1 \lambda_P s ^ {\lambda_P - 1} \Pi(N_P,s N_F) \ds, \\
+        \pi^t_F(N_P, N_F) &= N_C \int_0^1 s ^ {\lambda_P} \partial_2 N_F \Pi(N_P,s N_F) \ds.
+    \end{align*}
+\end{proposition}
+It is similar to the non-weighted value in that it is an average of marginal contributions, but now those averages are weighted, with the weight function depending on platform's bargaining weight.
+
+The interpretation of $\lambda_P$ as a bargaining weight for the platform is supported by the fact that the platform's profit function is increasing in it.
+\begin{proposition}
+    \label{prop:lambda_P_comparative}
+    For any fixed $N_F >0, N_P \geq 0$, the platform's total profits are increasing in its bargaining weight $\lambda_P$, while the fringe's profits are decreasing in it:
+    \begin{align*}
+        \frac{\partial \pi_P^t(N_P, N_F)}{\partial \lambda_P} &> 0, \\
+        \frac{\partial \pi_F^t(N_P, N_F)}{\partial \lambda_P} &< 0.
+    \end{align*}
+\end{proposition}
+In fact, the limits as $\lambda_P \to 0$ and $\lambda_P \to \infty$ are quite intuitive: in the former case, the platform's profits are zero, while in the latter case it is able to appropriate all profits.
+That is, these limits correspond to the platform either receiving or making take-it or leave-it offers.
+
+\textcolor{red}{TODO: can I show a result analogous to \cref{lem:shape_of_fringe_profit} still holds for any $\lambda_P$? If not, focus on a specific case, such as the one on the graphs.}
 
 The example parametrizatrion is the same as in the main model, with the only difference that the platform has a lower innate bargaining power ($\lambda_P = 0.5$).
-As the conditions in \cref{ass:single_crossing} are also satisfied in this case, the main observations from \cref{sec:results} also apply.
+The main result, namely that the platform's product variety has a negative effect on consumer welfare in the hybrid regime, still holds.
 That is, as shown on \cref{fig:fringe_entry_eq_low_lambda}, total aggregate is decreasing in $N_P$ throughout the hybrid regime, due to the platform's products displacing more fringe products than their total number.
 
-The main difference is that, due to the lower bargaining power of the platform, the implied entry fee (\cref{fig:platform_profits_low_lambda}) is lower than the benchmark, unilaterally set one for low enough $N_P$.
+The main difference is that, for low enough $N_P$, the implied entry fee (\cref{fig:platform_profits_low_lambda}) is lower than the benchmark, unilaterally set one,  due to the lower bargaining power of the platform.
 As a consequence, total aggregate, and thus consumer surplus, is also above the benchmark outcome in that case.
@@
 The reason is that for low $N_P$, the implied entry fee is lower than the optimal one.
-Furthermore, it increases in $N_P$ as a result of the platform's increased bargaining power.
+Furthermore, it is increasing in $N_P$ as a result of the platform's increased bargaining power.
 Therefore, the platform's profits are increasing in $N_P$ even more than in the benchmark case or the main model, up to the point where the implied entry fee is equal to the optimal one.
@@
 Imagine that the platform can decide on the number of its products at time 0, at an investment cost of $I_P$ per product.
-In the main model, due to the implied entry fee being higher than optimal even for $N_P = 0$, hybrid operation is never optimal.
+In the example for the main model, due to the implied entry fee being higher than optimal even for $N_P = 0$, hybrid operation is never optimal.
 The platform would always prefer either pure retail or pure marketplace operation.
-In contrast, when the platform has lower bargaining power, there exists a range of $I_P$ values (e.g. $I_P = 0.2$) for which the platform would prefer to operate in hybrid mode.
+In contrast, when the platform has lower bargaining power, there exists a range of values for $I_P$ (most notably, $I_P = I_F = 0.2$) for which the platform would prefer to operate in hybrid mode.
 Furthermore, if hybrid operation is not allowed, the platform might switch to become a pure marketplace, thereby increasing consumer surplus.
@@
                 ]
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=A_bench]{\equilibrium};
-                \addplot[color=myred,mark=none,thick] table[x=N_P,y=A]{\equilibrium};
-                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=A]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=CS_bench]{\equilibrium};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y=CS]{\equilibrium};
+                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=CS]{\equilibriumProfitOneSidedLowLambda};
                 \legend{Benchmark, Bargaining ($\lambda = 1$), Bargaining ($\lambda = 0.5$)}
@@
         \end{tikzpicture}
-        \caption{Equilibrium number of fringe firms ($N_F$)}
+        \caption{Equilibrium consumer surplus ($CS$)}
     \end{subfigure}

### 2024-05-09 src/paper/application.tex
Rewrite second extension

@@
 Let us start by deriving total surplus as a function of $N_P, N_F$ and $N_C$.
-Under the logit-like demand structure described in \cref{sec:example}, the total surplus is given by
+Under the logit-like demand structure described in \cref{sec:demand}, the total surplus is given by
 \begin{proposition}
     \label{prop:profits_total_surplus}
-    If the platform can extract consumer surplus, then the total surplus is given by
+    Assuming profit-maximizing prices from the platform and the fringe, total surplus as a function of $N_P, N_F$ and $N_C$ is given by
     \begin{align*}
@@
 \Cref{sec:cooperative_game_two_sided} formally describes the corresponding cooperative game, and \cref{prop:profit_sharing_two_sided} establishes the resulting profit shares.
-To summarize, the shares of the various players are given by
-Then, the resulting profit shares are given by
-\begin{align*}
-    \pi_P(N_P, N_F, N_C) &= N_C \int_0^1 s f(N_P, s N_F) \ds, \\
-    \pi_F(N_P, N_F, N_C) &= N_C \int_0^1 s^2 N_F \partial_2 f(N_P, s N_F) \ds \\
-    CS(N_P, N_F, N_C) &= N_C \int_0^1 s f(N_P, s N_F) \ds.
-\end{align*}
+To summarize, the shares of the various players are as follows.
+\begin{proposition}
+    \label{prop:profit_sharing_two_sided}
+    \begin{align*}
+        \pi_P(N_P, N_F, N_C) &= \int_0^1 s \Pi(N_P, s N_F) \ds, \\
+        \pi_F(N_P, N_F, N_C) &= \int_0^1 s^2 N_F \partial_2 \Pi(N_P, s N_F) \ds \\
+        CS(N_P, N_F, N_C) &= \int_0^1 s \Pi(N_P, s N_F) \ds.
+    \end{align*}
+\end{proposition}
 
@@
 As a consequence, what's good for the platform is also optimal for the consumers.
-Therefore, letting the platform choose the number of its products maximizes consumer welfare, as well (but not necessarily total surplus).
-
-Second, the expression for the fringe profits has the same structure as in \cref{ass:profit_sharing}.
-Therefore, if we show that \cref{ass:single_crossing} holds, it in turn implies that all of the results in \cref{sec:example} apply here, as well.
-The following lemma establishes this result.
-\begin{lemma}
-    \label{lem:profit_assumptions_two_sided}
-    $f(n_P, n_F)$ satisfies \cref{ass:single_crossing}.
-    Furthermore,
-    \begin{align*}
-        \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} < 0.
-    \end{align*}
-\end{lemma}
-
-With this proven, we can again rely on \cref{prop:aggregate_size_additive} to see that, in equilibrium, an increase in $N_P$ decreases $N_F$.
-Furthermore, this decrease is so large that total product variety, and thus total surplus (which in turn is equal to total profits) also decreases (\cref{fig:fringe_entry_eq_full_surplus_two_sided}).\footnote{
-    As long as the market is in the hybrid regime.
-    If $N_F^* = 0$, then an increase in $N_P$ mechanically increases total aggregate, and thus total surplus.
-}
+Therefore, if the platform can choose its mode of operation to maximize its profits, it maximizes consumer welfare, as well (but not necessarily total surplus).
+
+Second, it can be shown that due to the fringe firms' total profit function having a similar shape as in the main model, the same results hold in terms of the platform's product variety displacing fringe products.
+\begin{proposition}
+    In the hybrid regime under three-sided bargaining, the following holds:
+    \begin{align*}
+        N_F > 0 \implies \frac{\partial N_F}{\partial N_P} < -\frac{V_P}{V_F}.
+    \end{align*}
+\end{proposition}
+As a consequence, the aggregate is decreasing in $N_P$ in the hybrid regime (\cref{fig:fringe_entry_eq_full_surplus_two_sided}).
+\begin{corollary}
+    In the hybrid regime under three-sided bargaining, total aggregate is decreasing in the platform's product variety:
+    \begin{align*}
+        N_F > 0 \implies \frac{\partial A}{\partial N_P} < 0.
+    \end{align*}
+\end{corollary}
 
 Nevertheless, there is an important distinction compared to the previous results.
-As before, platform profits are again increasing in $N_P$.
-However, in this case, it also implies that consumers' share is also increasing in this case (\cref{fig:profits_full_surplus_two_sided}).
-Therefore, consumers do prefer hybrid operation to the the platform being a pure marketplace.
+While this does lead to a decrease in total surplus, in contrast to the two-sided bargaining case, this does not imply a decrese in consumer surplus.
+As mentioned before, the consumers' share of total surplus is equal to the platform's profits, and thus it is increasing in $N_P$ if and only if platform profits (\cref{fig:profits_full_surplus_two_sided}) are.
+Therefore, consumers might prefer hybrid operation to the platform being a pure marketplace.
 

### 2024-05-09 src/paper/application.tex
Remove uninteresting appendix section

@@
 
-\section{Two-sided bargaining over the full surplus}
-\label{sec:total_welfare_one_sided}
-
-In this section, I look at what happens if the paltform and the firms bargain over the total surplus, instead of just their total profits.
-That is, $\Pi(N_P, N_F, N_C)$ now represents total surplus.
-One way to motivate this is to assume that the platform can extract consumer surplus by charging a flat entry fee $F_C$.
-As consumers are identical, and the platform can set any entry fee, this implies that the platform can extract all consumer surplus in this case.
-I will only consider the bargaining outcomes under assumptions \cref{ass:profit_sharing}, and do not look at a benchmark with unilateraly set entry fees for the fringe.
-
-As shown in \cref{prop:profits_total_surplus}, total surplus (which in case is also total profits) is given by
-\begin{align*}
-    \Pi(N_P, N_F, N_C) = \mu N_C \left[ \frac{N_P V_P + N_F V_F}{N_P V_P + N_F V_F + 1} + \log(N_P V_P + N_F V_F + 1) \right].
-\end{align*}
-
-The following lemma establishes that \cref{ass:single_crossing} is satisfied for this profit function as well, assuming two-sided bargaining with $\lambda_P = 1$ ($w_P(s) \equiv 1, w_F(s) = s$).
-\begin{lemma}
-    \label{lem:profit_assumptions_total_surplus}
-    $f(n_P, n_F)$ satisfies \cref{ass:single_crossing}.
-    Furthermore,
-    \begin{align*}
-        \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} < 0.
-    \end{align*}
-\end{lemma}
-
-With this proven, we can rely on \cref{prop:aggregate_size_additive} to see that, in equilibrium, an increase in $N_P$ decreases $N_F$.
-Furthermore, this decrease is so large that total product variety, and thus total surplus (which in turn is equal to total profits) also decreases.\footnote{
-    As long as the market is in the hybrid regime.
-    If $N_F^* = 0$, then an increase in $N_P$ mechanically increases total aggregate, and thus total surplus.
-}
-\Cref{fig:equilibrium_full_surplus_one_sided} displays equilibrium outcomes for an example parametrization
-Thus, as in the case without consumer entry fees, a platform becoming increasingly hybrid has generally negative consequences.
-
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}
-            \begin{axis}[
-                    xlabel={$N_P$},
-                    ylabel={},
-                    xmin=0, xmax=1.5, % adjust these values as needed
-                    ymin=0, ymax=3.1, % adjust these values as needed
-                    axis lines=left,
-                    xtick={0, 1.5},
-                    legend pos=south east,
-                    width=\linewidth,
-                ]
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=N_P]{\equilibriumFullSurplusOneSided};
-                \addplot[color=myred,mark=none,thick] table[x=N_P,y=N_F]{\equilibriumFullSurplusOneSided};
-                \addplot[color=black,mark=none,thick] table[x=N_P,y=A]{\equilibriumFullSurplusOneSided};
-
-                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumFullSurplusOneSided};
-                \addplot[draw=none,name path=bottom] {0};
-                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
-
-                \legend{$N_P$, $N_F$, $A$}
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Platform product variety and number of fringe entrants}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}
-            \begin{axis}[
-                    xlabel={$N_P$},
-                    ylabel={},
-                    xmin=0, xmax=1.5, % adjust these values as needed
-                    ymin=0, ymax=1.2, % adjust these values as needed
-                    axis lines=left,
-                    xtick={0, 1.5},
-                    legend pos=north west,
-                    width=\linewidth,
-                ]
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=pi_P]{\equilibriumFullSurplusOneSided};
-                \addplot[color=myred,mark=none,thick] table[x=N_P,y=pi_F]{\equilibriumFullSurplusOneSided};
-
-                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumFullSurplusOneSided};
-                \addplot[draw=none,name path=bottom] {0};
-                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
-
-                \legend{$\pi_P$, $\pi_F$}
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Platform and fringe profits}
-    \end{subfigure}
-    \caption{Equilibrium outcomes in the case when the whole surplus is bargained over ($N_C = 0.6, V_P = 1, V_F = 1, I_F = 0.2$).
-As in the case of bargaining over profits, the platform's profits are increasing in $N_P$, while the fringe's profits are decreasing.
-Consumer surplus does not matter in this case, as it is extracted by the platform.
-The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode.}
-    \label{fig:equilibrium_full_surplus_one_sided}
-\end{figure}
-
-The difference is that, due to the platform appropriating all the consumer surplus, such an increase does not hurt consumer welfare -- it is zero regardless of $N_P$.
-Coupled with the fact that fringe firms also make zero profits in equilibrium, this means that the outcome is not so negative, after all.
-In particular, the platform's profits are increasing in $N_P$, and thus it prefers to operate in hybrid mode, as long as it is feasible.
-So even though the total pie gets smaller, the platform gets a larger slice, while the consumers and the fringe are just as well off.
-
-The catch is that, in this comparative statics exercise, the platforms' increased product variety came out of thin air.
-Specifically, when looking at the platform's profits, this increase in product variety is not associated with any increase in investment costs.
-If we were to include those at the same level of the fringe's investment costs, then the platform's profits would be decreasing in $N_P$, and it would not make the investment.
-Nevertheless, if it were to make it for some reason, it would not have the negative consequences that it had in \cref{sec:example}.
-
 \section{Proofs and additional lemmas}

### 2024-05-09 src/paper/application.tex
Add back general results into appendix

@@
 
-% \subsection{Profit sharing}
-
-% I assume that fringe firms are unable to sell their products directly to consumers.
-% Instead, they must sell through the platform.
-% For this service, the platform may charge a fee, and obtain a share of the fringe's profits.
-
-% In the benchmark model, the platform will be able to set and commit to any lump-sum entry fee it wishes to.\footnote{
-%     The focus of this paper is on fees paid and entry decisions made by fringe producers, but I will also consider the case when consumers also face entry fees or subsidies.
-% }
-% The main contribution of this paper is to deviate from this usual assumption, and instead consider a setting in which the platform and the fringe engage in some form of bargaining over the total profits.
-% To model this in a tractable way, I propose a profit division rule that is based on the Shapley value \parencite{shapley1953additive}, or, more generally, random order values \parencite{weber1988probabilistic}.
-% This way of modelling bargaining outcomes has many precedents in the industrial organization literature \parencite[e.g.][]{montez2007downstream,hart1990property,levy1997individual,inderst2003bargaining,brugemann2019intra}.
-% In the main text, I simply propose a formula for the profit shares without going into the details of the underlying cooperative game.
-% The interested reader can find a more detailed discussion of how it relates to random order values in \cref{sec:cooperative_game}.
-
-% \begin{assumption}
-%     \label{ass:profit_sharing}
-%     Let $w_P, w_F: \mathbb{R}^+_0 \to \mathbb{R}^+_0$ be non-negative functions such that the following condition holds: $\pi_P(N_P, N_F, N_C) + \pi_F(N_P, N_F, N_C) \leq \Pi(N_P, N_F, N_C)$.
-%     %TODO: can I make this condition nicer?
-%     Then, the platform's profit ($\pi_P(N_P, N_F, N_C)$) and the fringe's profit ($\pi_F(N_P, N_F, N_C)$) are given by:
-%     \begin{align*}
-%         \pi_P(N_P, N_F, N_C) &= N_C \int_0^1 w_P(s) f(N_P, s N_F) \ds, \\
-%         \pi_F(N_P, N_F, N_C) &= N_C \int_0^1 w_F(s) N_F \partial_2 f(N_P, s N_F) \ds.
-%     \end{align*}
-% \end{assumption}
-
-% Although the reason behind choosing this particular form for profit shares is discussed in detail in the appendix, let me highlight some important observations.
-% First, player's profit shares are closely related to their (weighted average) marginal contributions to the total value.
-% In the case of the platform, its contribution is the total value, as it is indispensable, while the fringe firms' contribution is captured by the partial derivative of the total value with respect to the number of fringe firms.
-% Second, the platform and the fringe do not necessarily get the entire value they create.
-% This is due to the fact that I also want to allow for the possibility of consumers participating in the bargaining process and getting a share of the profits, too
-% Finally, the profit shares depend on two types of factors: the production function $f$ and $w_P$ and $w_F$, which I will call bargaining weights.
-% The former is determined by the technology and demand structure, while the latter can be thought of as some king of intrinsic bargaining power.
-
-% In the later sections, I will consider specific examples for $f$ and $w_P$ and $w_F$, motivated by a Logit-like demand system, and (weighted) Shapley values, respectively.
-% However, for a number of results, this level of detail is not necessary, and these quite general assumptions are sufficient.
-
-% As mentioned before, one main justification for this profit allocation rule its intuitive behavior in terms of comparative statistics.
-% To illustrate this, let us examine what happens when one varies the substitutability between the fringe firms.
-% As it turns out, the platform's share increases if the fringe firms are more substitutable.
-% The following observation demonstrates this idea.
-% \begin{proposition}
-%     \label{prop:outcome_based_bargaining_power}
-%     Fix some $N_P, N_C \geq 0$.
-Let $f, \tilde{f}: \mathbb{R}^+_0 \times \mathbb{R}^+_0 \to \mathbb{R}^+_0$ two different profit functions such that $f(N_P, N_F) = \tilde{f}(N_P, N_F)$ for some $N_P, N_F$ and $f(N_P, n_F) \leq \tilde{f}(N_P, n_F)$ for all $n_F < N_F$.
-%     Furthermore, let us denote the corresponding platform profit shares by $\pi_P$ and $\tilde{\pi}_P$.
-
-%     Then, $\pi_P \leq \tilde{\pi}_P$.
-% \end{proposition}
-
-% In words, \cref{prop:outcome_based_bargaining_power} describes two alternative worlds, in which $N_F$ fringe firms (assuming a platform with $N_P$ product variety and $N_C$ consumers) are able to achieve the same total profit level.
-% However, in one of these cases, the fringe firms are more substitutable to each other in the sense that fewer of them are needed to achieve a given level of profit (see \cref{fig:outcome_based_bargaining_power}).
-% The observation is that, in this situation, the platform's share is indeed higher when the fringe firms are more substitutable.
-% This coincides with the intuitive idea that the platform's bargaining power is higher when it does not really mind loosing a few fringe sellers.
-
-% \begin{figure}
-%     \centering
-%     \begin{subfigure}[b]{0.45\textwidth}
-%         \begin{tikzpicture}[scale=0.8]
-%             \centering
-%             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-%                     xtick={0, 1}, ytick=\empty, xlabel={$s$}]
-%                 \addplot[name path=f, black, thick] {x^2};
-%                 \node[anchor= east] at (axis cs: .5, .5^2) {$N_C f(N_P, sN_F)$};
-%                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
-%                 \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);
-
-%                 \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
-%                 \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
-
-%                 \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
-%                 \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
-%             \end{axis}
-%         \end{tikzpicture}
-%         \caption{Fringe firms are complements}
-%     \end{subfigure}
-%     \begin{subfigure}[b]{0.45\textwidth}
-%         \centering
-%         \begin{tikzpicture}[scale=0.8]
-%             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-%                 xtick={0, 1}, ytick=\empty, xlabel={$s$}]
-%                 \addplot[name path=f, black, thick] {x^0.5};
-%                 \node[anchor=north west] at (axis cs: .5, .5^0.5) {$N_C \tilde{f}(N_P, sN_F)$};
-%                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
-%                 \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);
-
-%                 \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
-%                 \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
-
-%                 \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
-%                 \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
-%             \end{axis}
-%         \end{tikzpicture}
-%         \caption{Fringe firms are substitutes}
-%     \end{subfigure}
-%     \caption{Distribution of value between the platform and the fringe.
-Profit shares correspond to the shaded areas.
-The platform's profit share is higher when the fringe firms are more substitutable.}
-%     \label{fig:outcome_based_bargaining_power}
-% \end{figure}
-
-% \subsection{Entry and equilibrium}
-
-% Throughout the paper, I will assume that the number of consumers is fixed and exogenous.
-% They are thus passive in the sense that they do not make a decision about whether to enter the market or not.
-% However, when developing microfoundations for $f$ in \cref{sec:example}, consumers will make consumption choices, and their welfare will be of interest.
-% The product variety of the platform is also exogeneous.
-
-% Let us now turn to the determination of the equilibrium number of fringe firms.
-% Assume that there is an unlimited number of potential fringe entrants, indexed by $i \in \mathbb{R}^+_0$.
-% In the first stage of the game, each fringe firm must create a viable product at some investment cost.
-% Let us denote the total investment costs of $N_F$ fringe firms by $I_F(N_F)$.
-% \begin{assumption}
-%     Assume that $I_F(N_F)$ is a strictly increasing, convex, twice differentiable function:
-%     \begin{align*}
-%         \frac{\partial I_F(N_F)}{\partial N_F} > 0, \quad \frac{\partial^2 I_F(N_F)}{\partial N_F^2} \geq 0.
-%     \end{align*}
-% \end{assumption}
-% This assumption essentially states that the marginal investment cost of the fringe is increasing in the number of fringe firms.
-% Notice that this only assumes weak convexity, and thus includes the case of constant marginal investment costs.
-
-% In the second stage, firms that made this investment plus the platform engage in producing and selling their respective products.
-% If there are $N_F$ fringe entrants along with $N_P$ platform products and $N_C$ consumers, then, as discussed previously, the total value they create together is given by $\Pi(N_P, N_F, N_C) = N_C f(N_P, N_F)$.
-% Finally, the platform and the entrants share this profit according to the profit sharing rule from \cref{ass:profit_sharing}, and the fringe gets $\pi_F(N_P, N_F, N_C)$.
-
-% The equilibrium number of entrants is determined by a free entry condition: in the end, the fringe firms' total profits should be equal to the aggregated investment cost.
-% \begin{definition}
-%     \label{ass:free_entry}
-%     Let us define a free entry equilibrium by the following conditions:
-%     \begin{itemize}
-%         \item Profits are shared according to \cref{ass:profit_sharing}.
-%         \item Entrants make zero profits after accounting for entry costs: $\pi_F(N_P, N_F) = I_F(N_F)$.
-%     \end{itemize}
-% \end{definition}
-
-% Finally, in order to guarantee a unique equilibrium, let us make the following, an additional assumption about the profit function.
-% \begin{assumption}
-%     \label{ass:single_crossing}
-%     Let $f$ be such that the following holds for all $N_F, N_P, N_C \geq 0$:
-%     \begin{align*}
-%         \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_F} < 0 \text{ or } \frac{\partial^2 \pi_F(N_P, N_F, N_C)}{\partial N_F^2} < 0
-%     \end{align*}
-% \end{assumption}
-% This assumption essentially guarantees that the profit of the fringe (as a function of the number of entrants) has at most a single crossing with the --linear -- total entry cost (apart from the obvious $N_F=0$ intersection).
-% The interpretation of the assumption itself is simple: total fringe profits, as a function of the number of fringe firms, must be either concave or hump-shaped.\footnote{
-%     As it turns out, even though total industry profits are assumed to be increasing in $n_f$, it is not necessarily true for fringe profits.
-%     For certain profit functions, it happens that even though the size of the pie increases, the bargaining position of the fringe deteriorates so much that they get a smaller share even in absolute value.
-% }
-% What it requires of $f$, however, is not so obvious, and also depends on what one assumes about the innate bargaining weights $w_F$ and $w_P$.
-% Nevertheless, when microfounding the profit function, one can simply check whether this assumption holds or not.
-% In particular, it will be satisfied for the logit-type demand in \cref{sec:example}.
-% TODO: conjecture: it only has to hold for $f(N_P, N_F)$.
-
-% \section{General results}
-% \label{sec:results}
-
-% This section presents some general result that only depend on the abstract model structure described in the previous section, and the assumptions therein.
-% It turns out that even within such a general setting, one can derive some interesting and non-trivial results.
-% \Cref{sec:example} then builds on these results to derive stronger ones under a specific demand system.
-
-% Let us start with a technical, but very useful result.
-% \begin{proposition}
-%     \label{prop:unique_equilibrium}
-%     Under the conditions in \cref{ass:single_crossing}, the equilibrium is unique if it exists.
-% \end{proposition}
-% The intuition behind this result is that \cref{ass:single_crossing} ensures that the total profits achieved by the fringe is either concave or hump-shaped.
-% Consequently, it has at most one crossing with the -- convex and increasing -- total entry cost function (for $n_F > 0$).
-% An example for this is shown in \cref{fig:equilibrium}.
-% This particular shape (concave or hump-shaped) is also the main driver for the later results about the comparative statics of equilibrium profits and entry.
-
-% \begin{figure}[ht]
-%     \centering
-%     \begin{tikzpicture}[xscale=2,yscale=2,samples=200]
-%         \draw[->] (0,0) -- (0,2);
-%         \draw[->] (0,0) -- (5.5,0) node[below] {$N_F$};
-
-%         \draw[name path=piF,domain=0.01:5.5,variable=\x,black,thick] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
-%         \draw[name path=IF,domain=0.01:5.5,variable=\x,black,dashed,thick] plot ({\x},{(\x)/3});
-%         \node[anchor=north east] at (5,1) {$\pi_F(N_P, N_F, N_C)$};
-%         \node[anchor=south east] at (5,5/3) {$I_F(N_F)$};
-
-%         \fill [name intersections={of=piF and IF, name=i, total=\t}]
-%             [black] (i-2) circle (1pt);
-%         \draw[dashed] (i-2) -- (i-2 |- 0,0) node[below] {$N_F^*$};
-%     \end{tikzpicture}
-%     \caption{An example free entry equilibrium.
-\Cref{ass:single_crossing} states that the fringe profit function is concave or hump-shaped in $N_F$, guaranteeing at most one intersection with the linear entry cost function.}
-%     \label{fig:equilibrium}
-% \end{figure}
-
-% For the following two propositions, let us ignore free entry and equilibrium behavior, and consider the number of fringe entrants $N_F$ as fixed.
-% The following statement claims that the platform's profits are increasing in its own product variety.
-% \begin{proposition}
-%     \label{prop:share_of_platform}
-%     Assume that $f$ is continuously differentiable with respect to $N_P$ and also twice differentiable.
-%     Let $N_F \geq 0$.
-%     Then $\pi_P$ is also differentiable and
-%     \begin{align*}
-%         \frac{\partial \pi_P(N_P, N_F)}{\partial N_P} > 0.
-%     \end{align*}
-% \end{proposition}
-% While it might seem obvious, let us still examine what this result does and does not mean.
-% First, remember that $f$ is increasing in both arguments, and $N_F$ is fixed.
-% Therefore, an increase in $N_P$ also increases the size of the pie the participants bargain over.
-% This result states that the slice of the pie that the platform gets increases in this case, too.
-% It does not mean, however, that the \emph{relative share} of the pie that the platform gets is also bigger -- increase is only guaranteed in absolute terms.
-% For example, it is possible that for the new, higher value of $N_P$, the complementarities between the fringe firms become stronger, and the platform's bargaining power decreases.\footnote{
-%     In fact, one can show that this is the case if the cross-derivatives of $f$ are negative.
-% }
-% As this result shows, this decrease cannot be large enough to decrease the platform's profits in absolute terms.
-% \cref{fig:increase_N_P_platform} shows an example of this situation.
-
-% \begin{figure}[ht]
-%     \centering
-%     \begin{subfigure}[b]{0.45\textwidth}
-%         \centering
-%         \begin{tikzpicture}[scale=0.8]
-%             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-%                 xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
-%                 \addplot[name path=f, black, thick] {ln(1+x)};
-%                 % \addplot[name path=tildef, dashed, black] {x};
-%                 \node[anchor=north west] at (axis cs: .5, .4) {$N_C f(N_P, sN_F)$};
-%                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
-%                 \draw[name path=top] (axis cs:0,0.693) -- (axis cs:1,0.693);
-%                 \draw[name path=right] (axis cs:1,0) -- (axis cs:1,0.693);
-
-%                 \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
-%                 \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
-
-%                 \node[anchor=north west] at (axis cs: .05, .65) {Fringe ($F$)};
-%                 \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
-%             \end{axis}
-%         \end{tikzpicture}
-%         \caption{Profit shares with $N_P$}
-%     \end{subfigure}
-%     \begin{subfigure}[b]{0.45\textwidth}
-%         \centering
-%         \begin{tikzpicture}[scale=0.8]
-%             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-%                 xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
-%                 \addplot[name path=f, dashed, black] {ln(1+x)};
-%                 \addplot[name path=tildef, black, thick] {x};
-%                 \node[anchor=south east] at (axis cs: 0.6, 0.6) {$N_C f(N_P', sN_F)$};
-%                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
-%                 \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
-%                 \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);
-
-%                 \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
-%                 \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];
-
-%                 \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
-%                 \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
-%             \end{axis}
-%         \end{tikzpicture}
-%         \caption{Profit shares with $N_P'$}
-%     \end{subfigure}
-%     \caption{Illustration of \cref{prop:share_of_platform} in the one-sided bargaining case.
-The right hand side figure shows a world with larger platform product variety ($N_P < N_P'$).
-Even though the platform's share of the total profits is smaller in relative terms in that case, it is still larger in absolute terms.}
-%     \label{fig:increase_N_P_platform}
-% \end{figure}
-
-% Next, let us look at an analogous result for the fringe firms.
-% As the next proposition demonstrates, in this case, the direction of the change depends on the complementarities between the fringe firms.
-% \begin{proposition}
-%     \label{prop:share_of_fringe}
-%     Assume that $f, w$ are twice continuously differentiable.
-%     Let $N_F > 0$.
-%     Then $\pi_F$ is also differentiable.
-%     \begin{align*}
-%         &\text{If } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} < 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} < 0, \\
-%         &\text{if } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} > 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} > 0
-%     \end{align*}
-%     for all $N_P \geq 0$.
-% \end{proposition}
-% In summary, when they are mostly substitutes (the cross-derivatives of $f$ are negative), the fringe's profits decrease as a result of an increase in $N_F$.
-% The intuition is that, even though the total size of the pie increases, the bargaining power of the fringe deteriorates so much that its share decreases not only in relative, but also in absolute terms (as illustrated in \cref{fig:increase_N_P_fringe}).
-% On the other hand, when the fringe firms are mostly complements the fringe's profits increase.
-
-% \begin{figure}[ht]
-%     \centering
-%     \begin{subfigure}[b]{0.45\textwidth}
-%         \centering
-%         \begin{tikzpicture}[scale=0.8]
-%             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.225, samples at={0, 0.02, ..., 0.98, 1},
-%                 xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
-%                 \addplot[name path=f, black, thick] {sqrt(x)};
-%                 % \addplot[name path=tildef, dashed, black] {sqrt(0.5+x)};
-%                 \node[anchor=north west] at (axis cs: .6, 0.77) {$N_C f(0, sN_F)$};
-%                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
-%                 \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
-%                 \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);
-
-%                 \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
-%                 \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
-
-%                 \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
-%                 \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
-%             \end{axis}
-%         \end{tikzpicture}
-%         \caption{Profit shares with $N_P = 0$}
-%     \end{subfigure}
-%     \begin{subfigure}[b]{0.45\textwidth}
-%         \centering
-%         \begin{tikzpicture}[scale=0.8]
-%             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.225, samples at={0, 0.02, ..., 0.98, 1},
-%                 xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
-%                 \addplot[name path=f, dashed, black] {sqrt(x)};
-%                 \addplot[name path=tildef, black, thick] {sqrt(0.5+x)};
-%                 \node[anchor=north west] at (axis cs: 0.05, 0.75) {$N_C f(N_P', sN_F)$};
-%                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
-%                 \draw[name path=top] (axis cs:0,1.225) -- (axis cs:1,1.225);
-%                 \draw[name path=top_old, dashed] (axis cs:0,1) -- (axis cs:1,1);
-%                 \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1.225);
-
-%                 \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
-%                 \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];
-
-%                 \node[anchor=north west] at (axis cs: .05, 1.17) {Fringe ($F$)};
-%                 \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
-%             \end{axis}
-%         \end{tikzpicture}
-%         \caption{Profit shares with $N_P = 0.5$}
-%     \end{subfigure}
-%     \caption{Illustration of \cref{prop:share_of_fringe} when fringe and platforrm products are substitutes.
-An increase in the platform's product variety increases total profits, yet, the fringe's share decreases in absolute terms.}
-%     \label{fig:increase_N_P_fringe}
-% \end{figure}
-
-% Now let us turn to equilibrium entry as a function of the platform's product variety.
-% The previous proposition implies an almost immediate corollary regarding the equilibrium number of fringe entrants.
-% \begin{corollary}
-%     \label{cor:fringe_entry}
-%     Assume that $f, w$ are twice continuously differentiable.
-%     Let $N_F^*$ denote the equilibrium number of fringe firms.
-%     Let us also assume that $N_F^* > 0$.
-%     Furthermore, let us assume that
-%     \begin{align*}
-%         \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} < 0 \quad \forall n_F \leq N_F \\
-%         \frac{\partial^2 f(n_P, n_F)}{\partial n_F^2} < 0 \quad \forall n_F \leq N_F.
-%     \end{align*}
-%     Then the equilibrium number of fringe firms is also differentiable and
-%     \begin{align*}
-%         \frac{\partial N_F^*}{\partial N_P} < 0.
-%     \end{align*}
-% \end{corollary}
-% That is, the equilibrium number of entrants increases as a response to an increase in $N_P$ if the fringe firms are mostly complements, and decreases if they are mostly substitutes.
-% The underlyong reason is again the concave or hump-shaped fringe profit function.
-% If $N_F^*$ is an equilibrium, then fringe profits minus entry costs are strictly positive for all $N_F \leq N_F^*$ and strictly negative for all $N_F > N_F^*$.
-% Therefore, if an increase in $N_P$ decreases the fringe's profits for every $N_F \geq 0$, equilibrium can be restored by decreasing the number of fringe entrants, and vice versa for the other case (\cref{fig:comparative_N_F}).
-
-% \begin{figure}[ht]
-%     \centering
-%     \begin{tikzpicture}[xscale=2,yscale=2,samples=200]
-%         \draw[->] (0,0) -- (0,2);
-%         \draw[->] (0,0) -- (5.5,0) node[below] {$N_F$};
-
-%         \draw[name path=piF,domain=0.01:5.5,variable=\x,black, thick] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
-%         \draw[name path=piF2,domain=0.01:5.5,variable=\x,black, thick] plot ({\x},{6*((\x)/(0.3+\x))-6*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
-%         \draw[name path=IF,domain=0.01:5.5,variable=\x,black,dashed,thick] plot ({\x},{(\x)/3});
-
-%         \node[anchor=south] at (5,1) {$\pi_F(N_P, N_F, N_C)$};
-%         \node[anchor=north] at (5,0.6) {$\pi_F(N_P', N_F, N_C)$};
-%         \node[anchor=south east] at (5,5/3) {$I_F(N_F)$};
-
-%         \fill [name intersections={of=piF and IF, name=i, total=\t}]
-%             [black] (i-2) circle (1pt);
-%         \draw[dashed] (i-2) -- (i-2 |- 0,0) node[below] {$N_F^*$};
-%         \fill [name intersections={of=piF2 and IF, name=i2, total=\t}]
-%             [black] (i2-2) circle (1pt);
-%         \draw[dashed] (i2-2) -- (i2-2 |- 0,0) node[below] {${N_F^*}'$};
-
-%         \draw[->] (i-2 |- 0,0.5) -- (i2-2 |- 0,0.5);
-%     \end{tikzpicture}
-%     \caption{Illustration of comparative statics for equilibrium entry.
-If the change in $N_P$ decreases the fringe's profits for every $N_F \geq 0$, equilibrium can be restored by decreasing the number of fringe entrants, and vice versa for the other case.}
-%     \label{fig:comparative_N_F}
-% \end{figure}
-
-% Finally, let us conclude this section by establishing a stronger result for a more restrictive class of profit functions.
-% In the following, I assume that the profit function has a specific, additive form.
-% Intuitively, this means that -- in terms of total profits generated -- the platform's and the fringe firms' products are substitutable to each other according to some constant ratio.
-% \begin{proposition}
-%     \label{prop:aggregate_size_additive}
-%     Let $f$ have the following, additive form:
-%     \begin{align*}
-%         f(N_P, N_F) = g(\alpha N_P + \beta N_F)
-%     \end{align*}
-%     where $\alpha, \beta > 0$.
-%     Also assume that $g$ is twice differentiable and that $g'' < 0$.
-%     Then
-%     \begin{align*}
-%         \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}.
-%     \end{align*}
-%     Furthermore,
-%     \begin{align*}
-%         \frac{\partial \Pi(N_P, N_F^*(N_P), N_C)}{\partial N_P} < 0.
-%     \end{align*}
-% \end{proposition}
-
-% The first part of this proposition is a stronger version of \cref{cor:fringe_entry}.
-% It states that, not only does the equilibrium number of fringe firms decrease as a response to an increase in $N_P$, but it establishes a lower bound for this decrease.
-% And, as the second part shows, this bound is sufficient to guarantee that the total size of the pie ($\Pi(N_P, N_F, N_C)$) also decreases in equilibrium.
-
-% This result has particularly strong implications in models where total profits (or total product variety) has a monotone relationship with consumer welfare, such as those in \textcite{anderson2020aggregative}.
-% \Cref{sec:example} also presents a demand system which satisfies this property.
-
-% \section{Logit demand}
-% \label{sec:example}
-
-% Let us now add more structure to the model, place the function $\Pi$ on more solid microfoundations.
-% The modeling strategy is heavily inspired by the logit-like demand structure and hybrid platform setting of \textcite{anderson2021hybrid}.
-% The setting can be thought of as a (possibly hybrid) platform market with monopolistically competing fringe firms.
-
-% In the main model, I consider the case when the total profit function only includes the sales of the platform's and fringe firms' products.
-% That is, the platform does not charge any entry fees to the consumers.
-% Here, I consider two variants of the model: a benchmark where the platform can unilaterally commit to any entry fee, and a bargaining model where the platform and the fringe firms negotiate over the distribution of profits.
-% Furthermore, I focus on a particular set of weight functions $w_P$ and $w_F$, which correspont to the Shapley-values of the players in the case of one-sided bargaining.
-
-% As an extension, in \cref{sec:lower_bargaining_power} I also examine what happens when the platform and the fringe firms have unequal bargaining weights, while still retaining more structure than the very general bargaining rule from \cref{ass:profit_sharing}.
-% In particular, I look at the case of bargaining outcomes being described by weighted values, with all fringe players sharing the same weight.
-% Furthermore, in \cref{sec:two_sided}, I also consider the case of two-sided bargaining, where the consumers also participate in the negotiation over the value produced.
-% Finally, \cref{sec:total_welfare_one_sided} explores the case of the platform being able to extract all of the consumer surplus from consumers.
-
-% Throughout the analysis, I treat the product variety of the platform and the number of consumers as exogenous, and focus on the equilibrium number of fringe firms.
-% Nevertheless, the results regarding equilibrium platform profits and consumer surplus are indicative of the potential general equilibrium behavior of the former two, as well.
-
-% \subsection{Setup}
-
-% \subsubsection{Demand}
-
-% Imagine that there is a unit mass of consumers, looking to buy one product each.
-% They choose from a continuum of products, indexed by $i$.
-% Customer $j$ derives the following utility from buying product $i$:
-% \begin{align*}
-%     u^F_{ij} = v^F_i - p^F_i + \mu\epsilon^F_{ij},
-% \end{align*}
-% where $v^F_i$ is the value of product $i$, $p^F_i$ is its price, and $\epsilon^F_{ij}$ is an idiosyncratic taste shock.
-% Throughout this section I assume that the value of each product is the same: $v^F_i = v^F$.
-% This is to simplify the analysis, but is not crucial for the results.
-
-% Additionally, customers can also choose from a unit mass of outside options, yielding utility $u^0_ij = \mu\epsilon^0_{ij}$.
-$\epsilon^F_{ij}$ and $\epsilon^0_{ij}$ are assumed to be independent and identically distributed (i.i.d.) across consumers and products, and follow a standardized Type I Extreme Value distribution.
-This distributional assumption, along with the fact that each consumer consumes only one product, will lead to a tractable, logit-form demand function.
-
-% \subsubsection{Production}
-
-% Each (horizontally differentiated) product is produced by a single, monopolistically competitive (fringe) seller.
-% The production entails a constant marginal cost $c^F_i$.
-% As with the value, I assume that the marginal cost is the same for all products: $c^F_i = c^F$.
-% Facing the demand described in the previous paragraphs, the sellers choose their price $p^F_i$ to maximize profits.
-
-% Additionally, the platform itself can also offer mass $N_P$ of its own products.
-% The value and marginal cost of these products are denoted by $v^P$ and $c^P$, respectively.
-% Furthermore, consumers have the same i.i.d. taste shocks ($\epsilon^P_{ij}$) for platform products as for the products offered by the other sellers.
-% Finally, I assume that the platform prices its products as if they were produced by separate, monopolistically competitive sellers.
-% That is, it does not take into account the fact that it can affect a non-zero measure of the prices, and therefore the aggregate demand.
-% This is to simplify the example, but I expect that it does not affect the main results qualitatively
-
-% \subsubsection{Intermediation}
-
-% The overall structure of the model comes from \cref{sec:model}: assume that the sellers and the consumers can only interact through an intermediary platform, denoted by $P$.
-% Without the platform, the fringe firms are not able to sell their products, and thus make no profits.
-% For this service, the platform can charge a lump-sum entry fee $F_F$ to each fringe firm.\footnote{
-%     This is a critical difference from \textcite[]{anderson2021hybrid}, where the platform charges a per-unit royalty.
-%     % TODO: elaborate on this
-% }
-% In the baseline model, I assume that entry is free for the consumers, and they are always present on the platform, no matter the other players' entry and pricing decisions.\footnote{
-%     This essentially means that I assume a one-sided platform, without the usual network effects.
-% }
-% Later on, I look at the case of the platform appropriating consumer surplus, and also the case of consumers participating in the bargaining over the total surplus.
-
-% As mentioned above, instead of operating as a pure marketplace, the platform may also produce and offer its own products.
-% Therefore, there are three potential modes of operation.
-% First, it can offer no product on its own ($N_P = 0$), and operate as a pure marketplace.
-% Second, it can offer a selection of products alongside with a number of competing fringe firms also being present on the platform ($N_P, N_F > 0$).
-% In this case, it is a hybrid platform.
-% Finally, it can operate as a pure retailer, offering its own products, but no products from other sellers ($N_P > 0, N_F = 0$).
-
-% \subsubsection{Entry and timing}
-
 \section{Results}
@@
 
+\section{More general results}
+\label{sec:more_general_results}
+
+While the main text examines bargaining between the platform and the entrants in the context of a specific, logit-like demand system, many of the results are more general.
+This section presents those and the necessary assumptions.
+The proofs for many of the propositions in the main text also rely on these more general results.
+
+\subsection{Production}
+\label{sec:more_general_production}
+
+Let us assume the following reduced-form, but rather general total profit (or, where applicable, surplus) function:
+\begin{assumption}
+    \label{ass:identical_fringe}
+    The total profits of the platform and the fringe are described by 
+    \begin{align*}
+        \Pi(N_P, N_F, N_C) = N_C f(N_P, N_F),
+    \end{align*}
+    where $f: \mathbb{R}^+_0 \times \mathbb{R}^+_0 \to \mathbb{R}^+_0$.
+\end{assumption}
+It can be justified for markets with the following features: (1) all fringe firms are identical, thus only their number matters in terms of total profit, and (2) consumers are also identical (bar their idiosyncratic taste shocks).
+
+I will assume that, in addition to being increasing in the number of consumers, total profits are also increasing in both the number of fringe firms and the platform' products.
+\begin{assumption}
+    \label{ass:monotone_profits}
+    $f(n_P, n_F)$ is increasing in both $n_P$ and $n_F$.
+\end{assumption}
+Such profit functions arise in settings in which the profit reduction from increased competition is dominated by extra sales due to increased product variety.
+One such example is \textcite{anderson2020aggregative}, where the demand exhibits love for variety, while consumers have access to an outside option.
+Alternatively, indirect network effects, such as those in two-sided markets, can also result in such increasing profits.
+Finally, if we assume that the platform can extract consumer surplus through entry fees or some similar mechanism, then this assumption will be true for any demand system in which total surplus is increasing in product variety.
+
+\subsection{Profit sharing}
+\label{sec:more_general_profit_sharing}
+Next, assume that the platform and the fringe share profits according to the following rule:
+\begin{assumption}
+    \label{ass:profit_sharing}
+    Let $w_P, w_F: \mathbb{R}^+_0 \to \mathbb{R}^+_0$ be non-negative functions such that the following condition holds: $\pi_P(N_P, N_F, N_C) + \pi_F(N_P, N_F, N_C) \leq \Pi(N_P, N_F, N_C)$.
+    %TODO: can I make this condition nicer?
+    Then, the platform's profit ($\pi_P(N_P, N_F, N_C)$) and the fringe's profit ($\pi_F(N_P, N_F, N_C)$) are given by:
+    \begin{align*}
+        \pi_P(N_P, N_F, N_C) &= N_C \int_0^1 w_P(s) f(N_P, s N_F) \ds, \\
+        \pi_F(N_P, N_F, N_C) &= N_C \int_0^1 w_F(s) N_F \partial_2 f(N_P, s N_F) \ds.
+    \end{align*}
+\end{assumption}
+It covers the cases in the main text (namely the Shapley value and the weighted value, and three-way bargaining), but is also more general than those.
+In particular, in the platform game, any random order value \parencite{weber1988probabilistic} can be described by such a rule.
+
+Apart from the cooperative foundations, one major justification for this profit allocation rule is its intuitive behavior in terms of comparative statistics.
+To illustrate this, let us examine what happens when one varies the substitutability between the fringe firms.
+As it turns out, the platform's share increases if the fringe firms are more substitutable.
+The following observation demonstrates this idea.
+\begin{proposition}
+    \label{prop:outcome_based_bargaining_power}
+    Fix some $N_P, N_C \geq 0$.
+Let $f, \tilde{f}: \mathbb{R}^+_0 \times \mathbb{R}^+_0 \to \mathbb{R}^+_0$ two different profit functions such that $f(N_P, N_F) = \tilde{f}(N_P, N_F)$ for some $N_P, N_F$ and $f(N_P, n_F) \leq \tilde{f}(N_P, n_F)$ for all $n_F < N_F$.
+    Furthermore, let us denote the corresponding platform profit shares by $\pi_P$ and $\tilde{\pi}_P$.
+
+    Then, $\pi_P \leq \tilde{\pi}_P$.
+\end{proposition}
+
+In words, \cref{prop:outcome_based_bargaining_power} describes two alternative worlds, in which $N_F$ fringe firms (assuming a platform with $N_P$ product variety and $N_C$ consumers) are able to achieve the same total profit level.
+However, in one of these cases, the fringe firms are more substitutable to each other in the sense that fewer of them are needed to achieve a given level of profit (see \cref{fig:outcome_based_bargaining_power}).
+The observation is that, in this situation, the platform's share is indeed higher when the fringe firms are more substitutable.
+This coincides with the intuitive idea that the platform's bargaining power is higher when it does not really mind loosing a few fringe sellers.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \begin{tikzpicture}[scale=0.8]
+            \centering
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
+                    xtick={0, 1}, ytick=\empty, xlabel={$s$}]
+                \addplot[name path=f, black, thick] {x^2};
+                \node[anchor= east] at (axis cs: .5, .5^2) {$N_C f(N_P, sN_F)$};
+                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);
+
+                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
+
+                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
+                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Fringe firms are complements}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
+                xtick={0, 1}, ytick=\empty, xlabel={$s$}]
+                \addplot[name path=f, black, thick] {x^0.5};
+                \node[anchor=north west] at (axis cs: .5, .5^0.5) {$N_C \tilde{f}(N_P, sN_F)$};
+                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);
+
+                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
+
+                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
+                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Fringe firms are substitutes}
+    \end{subfigure}
+    \caption{Distribution of value between the platform and the fringe.
+Profit shares correspond to the shaded areas.
+The platform's profit share is higher when the fringe firms are more substitutable.}
+    \label{fig:outcome_based_bargaining_power}
+\end{figure}
+
+\subsection{Equilibrium}
+\label{sec:more_general_equilibrium}
+
+Let us now turn to the determination of the equilibrium number of fringe firms.
+Assume that total investment cost for the fringe is given by some increasing, weakly convex function $I_F(N_F)$.
+Note, that it includes the linear (per-firm constant) investment cost used throughout the main text.
+\begin{assumption}
+    Assume that $I_F(N_F)$ is a strictly increasing, convex, twice differentiable function:
+    \begin{align*}
+        \frac{\partial I_F(N_F)}{\partial N_F} > 0, \quad \frac{\partial^2 I_F(N_F)}{\partial N_F^2} \geq 0.
+    \end{align*}
+\end{assumption}
+
+The equilibrium number of entrants is determined by a free entry condition: in the end, the fringe firms' total profits should be equal to the aggregated investment cost.
+\begin{assumption}
+    \label{ass:free_entry}
+    Let us define a free entry equilibrium by the following conditions: Entrants make zero profits after accounting for entry costs: 
+    \begin{align*}
+        \pi_F(N_P, N_F) = I_F(N_F).
+    \end{align*}
+\end{assumption}
+
+Finally, in order to guarantee a unique equilibrium, let us make the following, an additional assumption about the profit function.
+\begin{assumption}
+    \label{ass:single_crossing}
+    Let $f$ be such that the following holds for all $N_F, N_P, N_C \geq 0$:
+    \begin{align*}
+        \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_F} < 0 \text{ or } \frac{\partial^2 \pi_F(N_P, N_F, N_C)}{\partial N_F^2} < 0
+    \end{align*}
+\end{assumption}
+This assumption essentially guarantees that the profit of the fringe (as a function of the number of entrants) has at most a single crossing with total entry cost (apart from the obvious $N_F=0$ intersection).
+Again, the profit functions presented in the main text satisfy this assumption.
+
+\subsection{Results}
+\label{sec:more_general_results}
+
+This section presents a number of results that can be derived even in this rather abstract setting.
+Let us start with a technical, but very useful result.
+\begin{proposition}
+    \label{prop:unique_equilibrium}
+    Under the conditions in \cref{ass:single_crossing}, the equilibrium is unique if it exists.
+\end{proposition}
+The intuition behind this result is that \cref{ass:single_crossing} ensures that the total profits achieved by the fringe is either concave or hump-shaped.
+Consequently, it has at most one crossing with the -- convex and increasing -- total entry cost function (for $n_F > 0$).
+This particular shape (concave or hump-shaped) is also the main driver for the later results about the comparative statics of equilibrium profits and entry.
+
+The following two propositions are partial equilibrium results: consider the number of fringe entrants $N_F$ as fixed.
+The first statement claims that the platform's profits are increasing in its own product variety.
+\begin{proposition}
+    \label{prop:share_of_platform}
+    Assume that $f$ is continuously differentiable with respect to $N_P$ and also twice differentiable.
+    Let $N_F \geq 0$.
+    Then $\pi_P$ is also differentiable and
+    \begin{align*}
+        \frac{\partial \pi_P(N_P, N_F)}{\partial N_P} > 0.
+    \end{align*}
+\end{proposition}
+While it might seem obvious, let us still examine what this result does and does not mean.
+First, remember that $f$ is increasing in both arguments, and $N_F$ is fixed.
+Therefore, an increase in $N_P$ also increases the size of the pie the participants bargain over.
+This result states that the slice of the pie that the platform gets increases in this case, too.
+It does not mean, however, that the \emph{relative share} of the pie that the platform gets is also bigger -- increase is only guaranteed in absolute terms.
+For example, it is possible that for the new, higher value of $N_P$, the complementarities between the fringe firms become stronger, and the platform's bargaining power decreases.\footnote{
+    In fact, one can show that this is the case if the cross-derivatives of $f$ are negative.
+}
+\cref{fig:increase_N_P_platform} shows an example of this situation.
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
+                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
+                \addplot[name path=f, black, thick] {ln(1+x)};
+                % \addplot[name path=tildef, dashed, black] {x};
+                \node[anchor=north west] at (axis cs: .5, .4) {$N_C f(N_P, sN_F)$};
+                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+                \draw[name path=top] (axis cs:0,0.693) -- (axis cs:1,0.693);
+                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,0.693);
+
+                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
+
+                \node[anchor=north west] at (axis cs: .05, .65) {Fringe ($F$)};
+                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Profit shares with $N_P$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
+                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
+                \addplot[name path=f, dashed, black] {ln(1+x)};
+                \addplot[name path=tildef, black, thick] {x};
+                \node[anchor=south east] at (axis cs: 0.6, 0.6) {$N_C f(N_P', sN_F)$};
+                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+                \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
+                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);
+
+                \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];
+
+                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
+                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Profit shares with $N_P'$}
+    \end{subfigure}
+    \caption{Illustration of \cref{prop:share_of_platform} in the one-sided bargaining case.
+The right hand side figure shows a world with larger platform product variety ($N_P < N_P'$).
+Even though the platform's share of the total profits is smaller in relative terms in that case, it is still larger in absolute terms.}
+    \label{fig:increase_N_P_platform}
+\end{figure}
+
+Next, let us look at an analogous result for the fringe firms.
+In their case, the direction of the change depends on the complementarities between the fringe firms.
+\begin{proposition}
+    \label{prop:share_of_fringe}
+    Assume that $f, w$ are twice continuously differentiable.
+    Let $N_F > 0$.
+    Then $\pi_F$ is also differentiable.
+    \begin{align*}
+        &\text{If } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} < 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} < 0, \\
+        &\text{if } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} > 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} > 0
+    \end{align*}
+    for all $N_P \geq 0$.
+\end{proposition}
+In summary, when they are mostly substitutes (the cross-derivatives of $f$ are negative), the fringe's profits decrease as a result of an increase in $N_F$.
+The intuition is that, even though the total size of the pie increases, the bargaining power of the fringe deteriorates so much that its share decreases not only in relative, but also in absolute terms (as illustrated in \cref{fig:increase_N_P_fringe}).
+On the other hand, when the fringe firms are mostly complements the fringe's profits increase.
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.225, samples at={0, 0.02, ..., 0.98, 1},
+                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
+                \addplot[name path=f, black, thick] {sqrt(x)};
+                % \addplot[name path=tildef, dashed, black] {sqrt(0.5+x)};
+                \node[anchor=north west] at (axis cs: .6, 0.77) {$N_C f(0, sN_F)$};
+                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+                \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
+                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);
+
+                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
+
+                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
+                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Profit shares with $N_P = 0$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.225, samples at={0, 0.02, ..., 0.98, 1},
+                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
+                \addplot[name path=f, dashed, black] {sqrt(x)};
+                \addplot[name path=tildef, black, thick] {sqrt(0.5+x)};
+                \node[anchor=north west] at (axis cs: 0.05, 0.75) {$N_C f(N_P', sN_F)$};
+                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+                \draw[name path=top] (axis cs:0,1.225) -- (axis cs:1,1.225);
+                \draw[name path=top_old, dashed] (axis cs:0,1) -- (axis cs:1,1);
+                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1.225);
+
+                \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];
+
+                \node[anchor=north west] at (axis cs: .05, 1.17) {Fringe ($F$)};
+                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Profit shares with $N_P = 0.5$}
+    \end{subfigure}
+    \caption{Illustration of \cref{prop:share_of_fringe} when fringe and platforrm products are substitutes.
+An increase in the platform's product variety increases total profits, yet, the fringe's share decreases in absolute terms.}
+    \label{fig:increase_N_P_fringe}
+\end{figure}
+
+Finally, let us turn to equilibrium entry as a function of the platform's product variety.
+The previous proposition implies an almost immediate corollary regarding the equilibrium number of fringe entrants.
+\begin{corollary}
+    \label{cor:fringe_entry}
+    Assume that $f, w$ are twice continuously differentiable.
+    Let $N_F^*$ denote the equilibrium number of fringe firms.
+    Let us also assume that $N_F^* > 0$, and that
+    \begin{align*}
+        \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} < 0 \quad \forall n_F \leq N_F \\
+        \frac{\partial^2 f(n_P, n_F)}{\partial n_F^2} < 0 \quad \forall n_F \leq N_F.
+    \end{align*}
+    Then the equilibrium number of fringe firms is also differentiable and
+    \begin{align*}
+        \frac{\partial N_F^*}{\partial N_P} < 0.
+    \end{align*}
+\end{corollary}
+That is, the equilibrium number of entrants increases as a response to an increase in $N_P$ if the fringe firms are mostly complements, and decreases if they are mostly substitutes.
+The underlying reason is again the concave or hump-shaped fringe profit function.
+If $N_F^*$ is an equilibrium, then fringe profits minus entry costs are strictly positive for all $N_F \leq N_F^*$ and strictly negative for all $N_F > N_F^*$.
+Therefore, if an increase in $N_P$ decreases the fringe's profits for every $N_F \geq 0$, equilibrium can be restored by decreasing the number of fringe entrants, (and vice versa for the other case).
+
+Finally, let us conclude this section by establishing a stronger result for a more restrictive class of profit functions.
+In the following, I assume that the profit function has an additive form.
+Intuitively, this means that -- in terms of total profits generated -- the platform's and the fringe firms' products are substitutable to each other according to some constant ratio.
+\begin{proposition}
+    \label{prop:aggregate_size_additive}
+    Let $f$ have the following, additive form:
+    \begin{align*}
+        f(N_P, N_F) = g(\alpha N_P + \beta N_F)
+    \end{align*}
+    where $\alpha, \beta > 0$.
+    Also assume that $g$ is twice differentiable and that $g'' < 0$.
+    Then
+    \begin{align*}
+        \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}.
+    \end{align*}
+    Furthermore,
+    \begin{align*}
+        \frac{\partial \Pi(N_P, N_F^*(N_P), N_C)}{\partial N_P} < 0.
+    \end{align*}
+\end{proposition}
+
+The first part of this proposition is a stronger version of \cref{cor:fringe_entry}.
+It states that, not only does the equilibrium number of fringe firms decrease as a response to an increase in $N_P$, but it establishes a lower bound for this decrease.
+And, as the second part shows, this bound is sufficient to guarantee that the total size of the pie ($\Pi(N_P, N_F, N_C)$) also decreases in equilibrium.
+
+This result has particularly strong implications in models where total profits (or total product variety) has a monotone relationship with consumer welfare, such as those in \textcite{anderson2020aggregative}.
+The demand system presented in the main text also has this property.
+
 \section{Proofs and additional lemmas}

### 2024-05-09 src/paper/application.tex
Fix references

@@
 \begin{proposition}
-    \label{prop:profit_sharing_two_sided}
+    \label{prop:three_way_shapley_value}
     \begin{align*}
@@
 \section{More general results}
-\label{sec:more_general_results}
+\label{sec:results_more_general}
 
@@
 \begin{proposition}
-    \label{prop:unique_equilibrium}
+    \label{prop:unique_equilibrium_more_general}
     Under the conditions in \cref{ass:single_crossing}, the equilibrium is unique if it exists.
@@
 
-\begin{proof}[Proof of \cref{prop:unique_equilibrium}]
+\begin{proof}[Proof of \cref{prop:unique_equilibrium_more_general}]
     \Cref{lem:slope_at_eq} states that for any positive $N_F^*$ for which $\pi_F(N_P, N_F^*) - N_F I_F$, the partial derivative with respect to the number of fringe firms is negative.
@@
 
-\begin{proof}[Proof of \cref{lem:profit_assumptions_total_surplus}]
-    To show this, I go through the same steps as in the proof of \cref{lem:profit_assumptions}.
-    Consider the function
-    \begin{align*}
-        g(x) = \frac{sx}{1 + sx} + \log(1 + sx).
-    \end{align*}
-    Also, let us define
-    \begin{align*}
-        G(x) &= \int_0^1 s g(sx) \ds \\
-        &= \frac{1}{x + 1}.
-    \end{align*}
-    Clearly, $G$ is a strictly concave function of $x$.
-
-    Now let us consider $h(x) = N_C \mu g(N_P V_P + V_F x).$
-    By \cref{lem:single_crossing_affine_transformation}, $H(x) = \int_0^1 s h'(sx) \ds$ is also strictly concave in $x$.\footnote{
-        Technically, the lemma establishes concavity \emph{or} being monotone decreasing.
-        It does not matter for this application, but it is easy to see that $H$ is indeed strictly concave.
-    }
-    Finally, notice that $H(x)$ is exactly the profit function of the fringe:
-    \begin{align*}
-        \pi_F(N_P, N_F, N_C) = \int_0^1 N_F h'(s N_F) \ds,
-    \end{align*}
-    and thus the lemma is proven.
-\end{proof}
-
 \end{document}

### 2024-05-09 src/paper/application.tex
Fix proof of unique equilibrium

@@
 
-\begin{proof}[Proof of \cref{lem:profit_assumptions}]
+\begin{proof}[Proof of \cref{prop:unique_equilibrium}]
     First, consider the function
@@
     \begin{align*}
-        \pi_F(N_P, N_F, N_C) = \int_0^1 N_F h'(s N_F) \ds,
-    \end{align*}
-    and thus the lemma is proven.
+        \pi_F(N_P, N_F) = \int_0^1 N_F h'(s N_F) \ds,
+    \end{align*}
+    thus \cref{ass:single_crossing} is satisfied, and in turn \cref{prop:unique_equilibrium_more_general} implies that the equilibrium number of fringe entrants is unique.
 \end{proof}

### 2024-05-09 src/paper/application.tex
Microsoft bought actiblizzard

@@
 Various pieces of legislation have been proposed to regulate, or even ban e-commerce platforms from selling their own products \parencite[][]{phartiyal_2019,reynolds_2022,eu-2022}.
-Furthermore, one of the most prominent ongoing antitrust cases, Microsoft attempting to acquire the video game publisher Activision/Blizzard for a sum of 69 billion USD, is also a case of a platform becoming increasingly hybrid.
-This merger would not only increase market concentration on the software side of the video game industry, but might also have further implications for the competition between Microsoft as a platform owner and the other game developers.
-The deal is currently under investigation by multiple antitrust authorities, including the US Federal Trade Commission, the European Commission, and the UK Competition and Markets Authority \parencite{livni_merced_2023}.
+Furthermore, one of the most prominent recent antitrust cases, Microsoft acquiring the video game publisher Activision/Blizzard for a sum of 69 billion USD, is also a case of a platform becoming increasingly hybrid.
+This merger not only increased market concentration on the software side of the video game industry, but might also have further implications for the competition between Microsoft as a platform owner and the other game developers.
+The deal was under investigation by multiple antitrust authorities, including the US Federal Trade Commission, the European Commission, and the UK Competition and Markets Authority \parencite{livni_merced_2023}.
 

### 2024-05-09 src/paper/application.tex
Rewrite intro so it fits the new structure

@@
 This paper aims to contribute to this discussion by examining an important, but so far underexplored aspect of platforms: the bargaining power disparity between them and the other market participants, and how this disparity is affected by the platforms' hybrid operation.
-In particular, I propose an analytically tractable framework which captures many important aspects of bargaining between one large and a continuum of small players, and apply it to the setting of a hybrid platform facing a continuum of potential entrants.
-The framework is quite general: it does not depend on a specific demand structure and investment cost assumptions, and there is even some flexibility to the assumptions about bargaining outcomes.
-Nevertheless, even in this stylized setting, I can highlight certain factors which might cause a platform's hybrid operation to potentially have negative effects. 
-In particular, when the platform's and the potential entrants' products are substitutes, increasing the platform's product variety will lead to a decrease in the number of entrants.
-Under slightly more restrictive assumptions about the functional form of the profit functions, I show that this decrease in entry is so large as to cause a decrease in total profits, as well.
-Due to the generality of this model, these results are applicable not only to hybrid platform, but to other similar settings, such as upstream producers having their own downstream outlets, or retailers with private labels, as well.
-
-As a more specific example, I also examine this phenomenon in a more fully specified model, too.
-In particular, I provide some sharper results under the assumption of logit-like demand and a specific form of the bargaining rule.
+I propose an analytically tractable model of a which captures many important aspects of bargaining between one large and a continuum of small players: namely a hybrid platform facing a continuum of potential entrants.
 I show that, in the presence of bargaining, hybrid operation can indeed have negative welfare consequences for consumers.
@@
 These observations constitute a so-far overlooked aspect of hybrid platforms that policymakers should be aware of.
-
-The closest model to the second, more applied part of this paper one is the one proposed by \textcite{anderson2021hybrid}.
-The main difference between the two boils down to how the entry fee is decided.
+Due to the relative generality of this model, these results are applicable not only to hybrid platform, but to other similar settings, such as upstream producers having their own downstream outlets, or retailers with private labels, as well.
+
+Many of the results are not tied to the specifics of the model, but are more general instead.
+They do not depend on a specific demand structure and investment cost assumptions, and there is even some flexibility to the assumptions about bargaining outcomes.
+I show that, even in such stylized setting, some interesting observations can be made about the effects of hybrid operation. 
+In particular, when the platform's and the potential entrants' products are substitutes, increasing the platform's product variety will lead to a decrease in the number of entrants.
+I also give sufficient conditions for this decrease in entry being so large as to cause a decrease in total profits, as well.
+
+The closest model to the one proposed in this paper is \textcite{anderson2021hybrid}.
+The key difference between the two boils down to how the entry fee is decided.
 In \textcite{anderson2021hybrid}, the platform sets a percentage entry fee, and the entrants decide whether to enter or not.
@@
 
-The first set of results in this paper go beyond the aforementioned studies in the sense that they illuminate the effects of hybridness as a more abstract phenomenon, and thus also highlight the similarities between the hybrid platform literature and adjacent ones.
+The set of more general results in this paper go beyond the aforementioned studies in the sense that they illuminate the effects of hybridness as a more abstract phenomenon, and thus also highlight the similarities between the hybrid platform literature and adjacent ones.
 Certain structures, such as vertical relationships, or even traditional retail stores share a number of features with platforms (notably, the presence of a dominant, indispensable entity), and can be modeled in much the same way.
@@
 In \cref{sec:model}, I introduce a general version of the model.
-After that, \cref{sec:results} demonstrates results about bargaining outcomes one can derive even in this rather abstract setting.
+After that, \cref{sec:results}\footnote{
+    \Cref{sec:more_general} explores the generalizability of these results, and highlights some common themes in settings with hybrid behavior.
+} demonstrates results about bargaining outcomes one can derive even in this rather abstract setting.
 \Cref{sec:example} concretizes the model by assuming a specific demand system, and also presents a corresponding benchmark model without bargaining.
@@
 \section{Results}
+\label{sec:results}
 
@@
 
-\section{The platform game and the (weighted) Shapley value}
-\label{sec:cooperative_game}
-
-In this section, I describe how the profit sharing rule from \cref{ass:profit_sharing} can be derived from various cooperative games.
-In each of the following subsections, I formally define a cooperative game that models the platform setting, and derive the (weighted) Shapley values of the various players.
-I show that they correspond to the formulas given in \cref{ass:profit_sharing}, with a specific choice of weight functions $w_P$ and $w_F$ for each case.
-
-I start with the simplest case: one-sided bargaining and the usual Shapley value \parencite{shapley1953additive}.
-Then, I look at weighted values \parencite{weber1988probabilistic} in the same cooperative game.
-Finally, I consider the case when the consumers also participate in the bargaining process, and derive the corresponding Shapley values.
-
-\subsection{One-sided case}
-\label{sec:cooperative_game_one_sided}
-
-In the first setting, the platform and the fringe firms bargain over the total profits they generate together, and the consumers are not included in the negotiations.
-The following cooperative game describes this case.
-
-Consider the game $\mathcal{G} = (\mathcal{N}, v)$, characterized by the set of players $\mathcal{N}$ and its characteristic function $v$.
-The set of players consists of the platform plus the fringe firms: $\mathcal{N} = \{P, F_i\}, i \in [0, N_F]$.
-Because the platform is indispensible, the value of a coalition $S$ is zero without the platform, and depends on the number of fringe firms otherwise:
-\begin{align*}
-    v(S) = \begin{cases}
-        0 & \text{if } P \notin S \\
-        N_C f(N_P, n_F(S)) & \text{if } P \in S
-    \end{cases},
-\end{align*}
-where $n_F(S)$ is the measure of fringe firms in $S$.
-
-The following proposition describes the Shapley value of the platform ($\varphi_P(\mathcal{G})$) and the fringe firms ($\varphi_F(\mathcal{G})$) in this game.
-
-\begin{proposition}
-    \label{prop:profit_sharing_one_sided}
-    Consider the cooperative game above.
-    Then, the Shapley values of the platform and the fringe firms are given by
-    \begin{align*}
-        \varphi_P(\mathcal{G}) &= N_C \int_0^1 f(N_P, s N_F) \ds, \\
-        \varphi_P(\mathcal{F}) &= N_C \int_0^1 s N_F \partial_2 f(N_P, s N_F) \ds.
-    \end{align*}
-\end{proposition}
-
-\begin{proof}[proof of \cref{prop:profit_sharing_one_sided}]
-    This result is a direct application of Proposition 3 and Corollary 2 in \textcite{stancsics2023value}.
-\end{proof}
-
-As an immediate consequence, if bargaining outcomes are described by the Shapley value, then the resulting allocations satisfy \cref{ass:profit_sharing} with $w_P(s) \equiv 1$ and $w_F(s) = s$.
-
-\subsection{Weighted value}
-\label{sec:cooperative_game_weighted}
-
-Now let us generalize the previous result, and assume instead that players' shares are described by their weighted values,
-As before, let us start by formally describing the cooperative game.
-The set of players and the characteristic function are the same as in \cref{sec:cooperative_game_one_sided}, but now the game is additionally endowed with a weight system $\mathbf{\lambda} = \{\lambda_P, \lambda_{F}(i)\}$.
-Let us assume that all fringe players have the same weight $\lambda_{F}(i) \equiv 1$.
-
-Then, the weighted values of the players are described by the following proposition.
-
-\begin{proposition}
-    \label{prop:profit_sharing_weighted}
-    Consider the cooperative game above.
-    Then, the weighted values of the platform and the fringe firms are given by
-    \begin{align*}
-        \varphi_P(\mathcal{G}) &= N_C \int_0^1 \lambda_P s ^ {\lambda_P - 1} f(N_P, s N_F) \ds, \\
-        \varphi_F(\mathcal{G}) &= N_C \int_0^1 s ^ {\lambda_P} N_F \partial_2 f(N_P, s N_F) \ds.
-    \end{align*}
-\end{proposition}
-
-\begin{proof}[proof of \cref{prop:profit_sharing_weighted}]
-    This result is a direct application of Proposition 4 in \textcite{stancsics2023value}.
-\end{proof}
-
-As before, the resulting allocations satisfy \cref{ass:profit_sharing} with $w_P(s) \equiv \lambda_P s ^ {\lambda_P - 1}$ and $w_F(s) = s ^ {\lambda_P}$.
-
-\subsection{Two-sided case}
-\label{sec:cooperative_game_two_sided}
-
-Finally, in certain settings, it might be appropriate to assume that the consumers (or, more generally, the entities on the other side of the market) also engage in the bargaining process.
-The cooperative game describing can be formalized as follows.
-
-The set of players consists of the platform plus the fringe firms: $\mathcal{N} = \{P, F_i, C_j\}, i \in [0, N_F], j \in [0, N_C]$.
-The value of a coalition $S$ is zero without the platform, and depends on the number of fringe firms otherwise:
-\begin{align*}
-    v(S) = \begin{cases}
-        0 & \text{if } P \notin S \\
-        n_C(S) f(N_P, n_F(S)) & \text{if } P \in S
-    \end{cases},
-\end{align*}
-where $n_F(S)$ and $n_C(S)$ is the measure of fringe firms and consumers, respectively, in $S$.
-
-As in the one-sided case, simple expressions exist for the Shapley value of the platform ($\varphi_P(\mathcal{G})$), fringe firms ($\varphi_F(\mathcal{G})$) and consumers ($\varphi_C(\mathcal{G})$).
-
-\begin{proposition}
-    \label{prop:profit_sharing_two_sided}
-    Consider the case when only the platform and the fringe firms participate in the bargaining process.
-    Then, the resulting profit shares are given by
-    \begin{align*}
-        \varphi_P(\mathcal{G}) &= N_C \int_0^1 s f(N_P, s N_F) \ds, \\
-        \varphi_F(\mathcal{G}) &= N_C \int_0^1 s^2 N_F \partial_2 f(N_P, s N_F) \ds \\
-        \varphi_C(\mathcal{G}) &= N_C \int_0^1 s f(N_P, s N_F) \ds.
-    \end{align*}
-\end{proposition}
-\begin{proof}[proof of \cref{prop:profit_sharing_two_sided}]
-    This result is a direct application of Proposition 11 in \textcite{stancsics2023value}.
-\end{proof}
-
-One thing to note is that the platform's and fringe firms' shares are lower than in the one-sided case.
-This is due to the fact of needing to share the pie with the consumers, too.
-Additionally, the platform's share is identical to the consumers' (aggregated) share.\footnote{
-    This stems from the linearity of the profit function in the number of consumers.
-}
-This foreshadows the idea that -- even though it might not be welfare-maximizing -- what's good for the platform might also good for the consumers in the two-sided case.
-Finally, as in both examples before, these values satisfy \cref{ass:profit_sharing} with $w_P(s) = s$ and $w_F(s) = s^2$.
-
 \section{More general results}
-\label{sec:results_more_general}
+\label{sec:more_general}
 
@@
 
+\section{The platform game and the (weighted) Shapley value}
+\label{sec:cooperative_game}
+
+In this section, I describe how the profit sharing rule from \cref{ass:profit_sharing} can be derived from various cooperative games.
+In each of the following subsections, I formally define a cooperative game that models the platform setting, and derive the (weighted) Shapley values of the various players.
+I show that they correspond to the formulas given in \cref{ass:profit_sharing}, with a specific choice of weight functions $w_P$ and $w_F$ for each case.
+
+I start with the simplest case: one-sided bargaining and the usual Shapley value \parencite{shapley1953additive}.
+Then, I look at weighted values \parencite{weber1988probabilistic} in the same cooperative game.
+Finally, I consider the case when the consumers also participate in the bargaining process, and derive the corresponding Shapley values.
+
+\subsection{One-sided case}
+\label{sec:cooperative_game_one_sided}
+
+In the first setting, the platform and the fringe firms bargain over the total profits they generate together, and the consumers are not included in the negotiations.
+The following cooperative game describes this case.
+
+Consider the game $\mathcal{G} = (\mathcal{N}, v)$, characterized by the set of players $\mathcal{N}$ and its characteristic function $v$.
+The set of players consists of the platform plus the fringe firms: $\mathcal{N} = \{P, F_i\}, i \in [0, N_F]$.
+Because the platform is indispensible, the value of a coalition $S$ is zero without the platform, and depends on the number of fringe firms otherwise:
+\begin{align*}
+    v(S) = \begin{cases}
+        0 & \text{if } P \notin S \\
+        N_C f(N_P, n_F(S)) & \text{if } P \in S
+    \end{cases},
+\end{align*}
+where $n_F(S)$ is the measure of fringe firms in $S$.
+
+The following proposition describes the Shapley value of the platform ($\varphi_P(\mathcal{G})$) and the fringe firms ($\varphi_F(\mathcal{G})$) in this game.
+
+\begin{proposition}
+    \label{prop:profit_sharing_one_sided}
+    Consider the cooperative game above.
+    Then, the Shapley values of the platform and the fringe firms are given by
+    \begin{align*}
+        \varphi_P(\mathcal{G}) &= N_C \int_0^1 f(N_P, s N_F) \ds, \\
+        \varphi_P(\mathcal{F}) &= N_C \int_0^1 s N_F \partial_2 f(N_P, s N_F) \ds.
+    \end{align*}
+\end{proposition}
+
+\begin{proof}[proof of \cref{prop:profit_sharing_one_sided}]
+    This result is a direct application of Proposition 3 and Corollary 2 in \textcite{stancsics2023value}.
+\end{proof}
+
+As an immediate consequence, if bargaining outcomes are described by the Shapley value, then the resulting allocations satisfy \cref{ass:profit_sharing} with $w_P(s) \equiv 1$ and $w_F(s) = s$.
+
+\subsection{Weighted value}
+\label{sec:cooperative_game_weighted}
+
+Now let us generalize the previous result, and assume instead that players' shares are described by their weighted values,
+As before, let us start by formally describing the cooperative game.
+The set of players and the characteristic function are the same as in \cref{sec:cooperative_game_one_sided}, but now the game is additionally endowed with a weight system $\mathbf{\lambda} = \{\lambda_P, \lambda_{F}(i)\}$.
+Let us assume that all fringe players have the same weight $\lambda_{F}(i) \equiv 1$.
+
+Then, the weighted values of the players are described by the following proposition.
+
+\begin{proposition}
+    \label{prop:profit_sharing_weighted}
+    Consider the cooperative game above.
+    Then, the weighted values of the platform and the fringe firms are given by
+    \begin{align*}
+        \varphi_P(\mathcal{G}) &= N_C \int_0^1 \lambda_P s ^ {\lambda_P - 1} f(N_P, s N_F) \ds, \\
+        \varphi_F(\mathcal{G}) &= N_C \int_0^1 s ^ {\lambda_P} N_F \partial_2 f(N_P, s N_F) \ds.
+    \end{align*}
+\end{proposition}
+
+\begin{proof}[proof of \cref{prop:profit_sharing_weighted}]
+    This result is a direct application of Proposition 4 in \textcite{stancsics2023value}.
+\end{proof}
+
+As before, the resulting allocations satisfy \cref{ass:profit_sharing} with $w_P(s) \equiv \lambda_P s ^ {\lambda_P - 1}$ and $w_F(s) = s ^ {\lambda_P}$.
+
+\subsection{Two-sided case}
+\label{sec:cooperative_game_two_sided}
+
+Finally, in certain settings, it might be appropriate to assume that the consumers (or, more generally, the entities on the other side of the market) also engage in the bargaining process.
+The cooperative game describing can be formalized as follows.
+
+The set of players consists of the platform plus the fringe firms: $\mathcal{N} = \{P, F_i, C_j\}, i \in [0, N_F], j \in [0, N_C]$.
+The value of a coalition $S$ is zero without the platform, and depends on the number of fringe firms otherwise:
+\begin{align*}
+    v(S) = \begin{cases}
+        0 & \text{if } P \notin S \\
+        n_C(S) f(N_P, n_F(S)) & \text{if } P \in S
+    \end{cases},
+\end{align*}
+where $n_F(S)$ and $n_C(S)$ is the measure of fringe firms and consumers, respectively, in $S$.
+
+As in the one-sided case, simple expressions exist for the Shapley value of the platform ($\varphi_P(\mathcal{G})$), fringe firms ($\varphi_F(\mathcal{G})$) and consumers ($\varphi_C(\mathcal{G})$).
+
+\begin{proposition}
+    \label{prop:profit_sharing_two_sided}
+    Consider the case when only the platform and the fringe firms participate in the bargaining process.
+    Then, the resulting profit shares are given by
+    \begin{align*}
+        \varphi_P(\mathcal{G}) &= N_C \int_0^1 s f(N_P, s N_F) \ds, \\
+        \varphi_F(\mathcal{G}) &= N_C \int_0^1 s^2 N_F \partial_2 f(N_P, s N_F) \ds \\
+        \varphi_C(\mathcal{G}) &= N_C \int_0^1 s f(N_P, s N_F) \ds.
+    \end{align*}
+\end{proposition}
+\begin{proof}[proof of \cref{prop:profit_sharing_two_sided}]
+    This result is a direct application of Proposition 11 in \textcite{stancsics2023value}.
+\end{proof}
+
+One thing to note is that the platform's and fringe firms' shares are lower than in the one-sided case.
+This is due to the fact of needing to share the pie with the consumers, too.
+Additionally, the platform's share is identical to the consumers' (aggregated) share.\footnote{
+    This stems from the linearity of the profit function in the number of consumers.
+}
+This foreshadows the idea that -- even though it might not be welfare-maximizing -- what's good for the platform might also good for the consumers in the two-sided case.
+Finally, as in both examples before, these values satisfy \cref{ass:profit_sharing} with $w_P(s) = s$ and $w_F(s) = s^2$.
+
 \section{Proofs and additional lemmas}

### 2024-05-09 src/paper/application.tex
Add proofs for main text

@@
 \begin{proposition}
-    \label{prop:equilibrium_aggregate}
+    \label{prop:equilibrium_aggregate_benchmark}
     If entry costs $I_F$ and $F_F$ are low enough, the equilibrium size of the aggregate is
@@
 The latter is essentially a function of the aggregate, minus the investment costs of the fringe firms.
-As I have shown in \cref{prop:equilibrium_aggregate}, the aggregate is independent of the platform's product variety in the hybrid regime, and therefore the optimal entry fee is also independent of it.
+As I have shown in \cref{prop:equilibrium_aggregate_benchmark}, the aggregate is independent of the platform's product variety in the hybrid regime, and therefore the optimal entry fee is also independent of it.
 
@@
 \begin{corollary}
+    \label{prop:consumer_surplus_benchmark}
     \begin{align*}
@@
 \begin{proposition}
+    \label{prop:N_F_comparative_equilibrium}
     Assume that the platform is operating in the hybrid regime.
@@
 \begin{corollary}
+    \label{prop:aggregate_comparative_hybrid}
     Assume that the platform is operating in the hybrid regime. Then the equilibrium aggregate and consumer surplus is decreasing in the number of the platform's products.
@@
 \begin{proposition}
+    \label{prop:aggregate_comparative_retail}
     Assume that the platform is operating in the pure retail regime. Then the equilibrium aggregate and consumer surplus is increasing in the number of the platform's products.
@@
 \begin{theorem}
+    \label{prop:benchmark_results}
     In the benchmark model with unilateral price setting, in a hybrid regime equilibrium (with $N_F > 0$), the following results hold:
     \begin{itemize}
-        \item The equilibrium number of fringe firms decreases in the number of the platform's products: $\frac{\partial N_F}{\partial N_P} = -\frac{V_P}{V_F} 0$.
+        \item The equilibrium number of fringe firms decreases in the number of the platform's products: $\frac{\partial N_F}{\partial N_P} = -\frac{V_P}{V_F} < 0$.
         \item The aggregate is independent of the platform's product variety: $\frac{\partial A}{\partial N_P} = 0$.
@@
 \begin{theorem}
+    \label{prop:bargaining_results}
     In the bargaining model, in a hybrid regime equilibrium (with $N_F > 0$), the following results hold:
@@
 Intuitively, this means that -- in terms of total profits generated -- the platform's and the fringe firms' products are substitutable to each other according to some constant ratio.
+\begin{assumption}
+    \label{ass:additive_profit}
+    Assume that $f$ has the following, additive form in $N_P$ and $N_F$:
+    \begin{align*}
+        f(N_P, N_F) = g(\alpha N_P + \beta N_F)
+    \end{align*}
+    where $\alpha, \beta > 0$, and $g$ is twice differentiable and that $g'' < 0$.
+\end{assumption}
+
 \begin{proposition}
     \label{prop:aggregate_size_additive}
-    Let $f$ have the following, additive form:
-    \begin{align*}
-        f(N_P, N_F) = g(\alpha N_P + \beta N_F)
-    \end{align*}
-    where $\alpha, \beta > 0$.
-    Also assume that $g$ is twice differentiable and that $g'' < 0$.
+    Let $f$ have the additive form from \cref{ass:additive_profit}.
     Then
@@
 
-\begin{proof}[Proof of \cref{prop:equilibrium_aggregate}]
+\begin{proof}[Proof of \cref{prop:equilibrium_aggregate_benchmark}]
     From \cref{prop:optimal_profit}, the variable profit of each fringe firm is $\pi_{F_i}^{v*} = \mu V_F / A$.
@@
 
-\begin{proof}[Proof of \cref{prop:unique_equilibrium}]
+\begin{proof}[Proof of \cref{lem:shape_of_fringe_profit}]
     First, consider the function
@@
     \end{align*}
-    thus \cref{ass:single_crossing} is satisfied, and in turn \cref{prop:unique_equilibrium_more_general} implies that the equilibrium number of fringe entrants is unique.
+    thus proving the lemma.
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:unique_equilibrium}]
+    \Cref{lem:shape_of_fringe_profit} demonstrates that the fringe total profit function is either concave or decreasing in the number of fringe firms.
+    Thus, \cref{ass:single_crossing} is satisfied, and \cref{prop:unique_equilibrium_more_general} implies that the equilibrium number of fringe entrants is unique.
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:fringe_profits_partial}]
+    $\pi^t_F(N_P ,N_F)$ adheres to the \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing}.
+    Furthermore, 
+    \begin{align*}
+        \frac{\partial^2 \pi^t_F(N_P ,N_F)}{\partial N_P \partial N_F} < 0 \quad \forall\, N_P, N_F \geq 0.
+    \end{align*}
+    Therefore, by \cref{prop:share_of_fringe},
+    \begin{align*}
+        \frac{\partial \pi^t_F(N_P, N_F)}{\partial N_P} < 0 \quad \forall\, N_P, N_F \geq 0.
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:N_F_comparative_equilibrium}]
+    $\pi^t_F(N_P ,N_F)$ adheres to the \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:additive_profit}.
+    Therefore, by \cref{prop:aggregate_size_additive}
+    \begin{align*}
+        N_F > 0 \implies \frac{\partial N_F}{\partial N_P} < -\frac{V_P}{V_F}
+    \end{align*}
+    immediately follows.
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:aggregate_comparative_hybrid}]
+    The first statement follows immediately from
+    \begin{align*}
+        A = N_P V_P + N_F V_F + 1
+    \end{align*}
+    and
+    \begin{align*}
+        \frac{\partial N_F}{\partial N_P} < -\frac{V_P}{V_F}
+    \end{align*}
+    from \cref{prop:N_F_comparative_equilibrium}.
+    The second part is a consequence of
+    \begin{align*}
+        CS \propto \log(A).
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:aggregate_comparative_retail}]
+    The first statement trivially follows from
+    \begin{align*}
+        A = N_P V_P + 1.
+    \end{align*}
+    The second part is a consequence of
+    \begin{align*}
+        CS \propto \log(A).
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:benchmark_results}]
+    The respective results are stated in \cref{prop:equilibrium_aggregate_benchmark} and \cref{prop:consumer_surplus_benchmark}.
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:bargaining}]
+    The respective results are stated in \cref{prop:N_F_comparative_equilibrium} and \cref{prop:aggregate_comparative_hybrid}.
 \end{proof}

### 2024-05-09 src/paper/application.tex
Finish rewriting intro

@@
 The rest of the paper is organized as follows.
-In \cref{sec:model}, I introduce a general version of the model.
+In \cref{sec:model}, I introduce two model of hybrid platforms: a benchmark with the platform setting an entry fee unilaterally, and the main model, where the platform and the fringe firms engage in bargaining.
 After that, \cref{sec:results}\footnote{
     \Cref{sec:more_general} explores the generalizability of these results, and highlights some common themes in settings with hybrid behavior.
-} demonstrates results about bargaining outcomes one can derive even in this rather abstract setting.
-\Cref{sec:example} concretizes the model by assuming a specific demand system, and also presents a corresponding benchmark model without bargaining.
+} demonstrates that the two have very different implications for consumer welfare.
 \Cref{sec:extensions} then examines the effect of different assumptions about the bargaining process.

### 2024-05-11 src/paper/application.tex
Start writing microfouncations for the bargaining outcomes

@@
 \usetikzlibrary{positioning}
+\usetikzlibrary{fit}
+\usetikzlibrary{arrows}
 \pgfplotsset{compat=1.17}
@@
 
+\section{Non-cooperative microfoundations for the bargaining outcome}
+\label{sec:bargaining_microfoundation}
+
+As part of the Nash program\footnote{
+    The research agenda aiming to find links between cooperative and non-cooperative game theory, started by nash1953two
+}, there have been a number of papers proposing microfoundations for the Shapley value in terms of non-cooperative, bargaining-related games \parencite[e.g.][]{gul1989bargaining,winter1994demand,hart1996bargaining,stole1996intra}.
+The cooperative platform game described in \cref{sec:cooperative_game} satisfies the assumption for a number of these models, and thus any of those could be used to build microfoundations for the platform game.
+Among those, I will focus on \textcite{stole1996intra} for the reason that it specifically pertains to a setting with one indispensable player and many small players, just like the current paper.
+
+The model in \textcite{stole1996intra} is phrased in terms of intra-firm bargaining between the workers and the firm itself.
+The workers are assumed to have a fixed outside option, and the firm is the indispensable player.
+This translates directly to the platform game, with the platform being the indispensable player, and fringe firms having a zero outside option.
+Furthermore, in \textcite{stole1996intra}, the bargaining outcome is interpreted as the wage for the workers.
+In the current setting, this would translate to bargaining over profit shares.
+However, it is equivalent to saying that the players negotiate over entry fees, as entry fees combined with equilibrium behavior later on determine the profit shares.
+To keep the model as similar to the benchmark case as possible, I use the latter interpretation.
+
+\begin{figure}
+    \centering
+    \begin{tikzpicture}[node distance=2cm, auto]
+        \node[align=center] (entry_decision) {Potential entrants decide to invest \\ at cost $I_F$ \\ $[N_F]$};
+        \node[align=center, draw, dashed] (entry_fee) [below of=entry_decision] {Entry fees are negotiated \\ between platform \\ and $N_F$ fringe firms \\ $[F_F]$};
+        \node[align=center] (sales) [below of=entry_fee] {Platform and fringe \\ sell products \\ $[\pi_{Fi}^v, \pi_P^v]$};
+        \node[align=center] (final) [below of=sales] {Final profits are realized \\ $[\pi_{Fi}^t, \pi_P^t]$};
+        \draw[->] (entry_decision) -- (entry_fee);
+        \draw[->] (entry_fee) -- (sales);
+        \draw[->] (sales) -- (final);
+
+        \node[align=center, right=of entry_decision, distance=3cm] (arrange_fringe) {Arrange fringe firms in some fixed order};
+        \node[align=center, below of=arrange_fringe] (foreach) {For each (remaining) fringe firm $F_i$:};
+        \node[align=center] (choose_proposer) [below=1cm of foreach] {$F_i$ or $P$ is choosen randomly};
+        \node[align=center] (proposal) [below of=choose_proposer] {Proposer proposes entry fee $F_{F_i}$};
+        \node[align=center] (accept) [below left=2cm and -2cm of proposal] {Responder accepts $F_{F_i}$};
+        \node[align=center] (reject) [below right=2cm and -2cm of proposal] {Responder rejects $F_{F_i}$};
+        \node[align=center] (next_player) [below of=accept] {Move on to next \\ fringe firm $F_{F_{i+1}}$};
+        \node[align=center] (eliminate) [below of=reject] {Eliminate $F_i$};
+
+        \draw[->] (arrange_fringe) -- (foreach);
+        \draw[->] (foreach) -- (choose_proposer);
+        \draw[->] (choose_proposer) -- (proposal);
+        \draw[->] (proposal) -- (accept.north);
+        \draw[->] (proposal) -- (reject.north);
+        \draw[->] (accept) -- (next_player);
+        \draw[->] (reject) -- (eliminate) node[midway,right] {$\rho$};
+
+        \draw[->] (reject.north) to [out=45, in=-45] node[midway,right] {$1 - \rho$} (choose_proposer.east);
+        \draw[->] (eliminate.east) to [out=45, in=-40] (foreach.east);
+
+        \node [draw, dashed, fit=(arrange_fringe)(foreach)(proposal)(accept)(reject)(next_player)(eliminate), inner sep=1em] (expanded_game) {};
+        \draw[-, dashed] (entry_fee.north east) -- (expanded_game.north west);
+        \draw[-, dashed] (entry_fee.south east) -- (expanded_game.south west);
+    \end{tikzpicture}
+    \caption{Timing of the model with extensive-form bargaining. The panel on the right hand side details the bargaining procedure for determining the entry fees.}
+    \label{fig:bargaining_microfoundations}
+\end{figure}
+
 \section{Proofs and additional lemmas}
+\label{sec:proofs}
 
@@
 
-\begin{proof}[Proof of \cref{prop:bargaining}]
+\begin{proof}[Proof of \cref{prop:bargaining_results}]
     The respective results are stated in \cref{prop:N_F_comparative_equilibrium} and \cref{prop:aggregate_comparative_hybrid}.

### 2024-05-11 src/paper/application.tex
Finish microfoundations for bargaining outcome section

@@
 \subsection{Demand and producer profits}
+\label{sec:results_demand}
 
@@
 In the current setting, this would translate to bargaining over profit shares.
-However, it is equivalent to saying that the players negotiate over entry fees, as entry fees combined with equilibrium behavior later on determine the profit shares.
-To keep the model as similar to the benchmark case as possible, I use the latter interpretation.
+However, as I argue later on, it is equivalent to bargaining over entry fees.
+Finally, this section focuses on the main model, with two-sided bargaining, and the Shapley value as the equilibrium concept.
+However, the same logic can be applied to the extensions presented in \cref{sec:extensions}, based on sections 3.1 and 3.2 of \textcite{stole1996intra}.
 
@@
         \node[align=center, below of=arrange_fringe] (foreach) {For each (remaining) fringe firm $F_i$:};
-        \node[align=center] (choose_proposer) [below=1cm of foreach] {$F_i$ or $P$ is choosen randomly};
+        \node[align=center] (choose_proposer) [below=1cm of foreach] {$F_i$ or $P$ is choosen as the proposer};
         \node[align=center] (proposal) [below of=choose_proposer] {Proposer proposes entry fee $F_{F_i}$};
@@
         \node[align=center] (reject) [below right=2cm and -2cm of proposal] {Responder rejects $F_{F_i}$};
-        \node[align=center] (next_player) [below of=accept] {Move on to next \\ fringe firm $F_{F_{i+1}}$};
+        \node[align=center] (next_player) [below of=accept] {Move on to the \\ next fringe firm};
         \node[align=center] (eliminate) [below of=reject] {Eliminate $F_i$};
@@
         \draw[->] (choose_proposer) -- (proposal);
-        \draw[->] (proposal) -- (accept.north);
-        \draw[->] (proposal) -- (reject.north);
+        \draw[->] (proposal) -- (accept);
+        \draw[->] (proposal) -- (reject);
         \draw[->] (accept) -- (next_player);
@@
     \end{tikzpicture}
-    \caption{Timing of the model with extensive-form bargaining. The panel on the right hand side details the bargaining procedure for determining the entry fees.}
+    \caption{Timing of the model with extensive-form bargaining. The panel on the right-hand side details the negotiation procedure for determining the entry fees.}
     \label{fig:bargaining_microfoundations}
 \end{figure}
+
+Let us now describe the bargaining process in the platform game.
+First, a random order is determined for the fringe firms.
+This order will remain fixed throughout the bargaining phase
+
+Then, for each fringe firm (following the order determined earlier), the platform and the fringe firm negotiate over the entry fee.
+This bilateral negotiation follows the alternating offer procedure described in \textcite{binmore1986nash}.
+One of the two players is chosen as a proposer, and can propose an entry fee for the given firm: $F_{F_i}$.
+The other player can either accept or reject the proposal.
+
+If the proposal is accepted, the negotiation moves on to the next fringe firm.
+If it is rejected, with probability $1-\rho$, the other player becomes the proposer, and the negotiation continues.
+Finally, with probability $\rho$, the negotiations break down, and the fringe firm is eliminated from the rest of the game.
+Crucially, after a breakdown occurs, all of the previous offers are voided, and the platform and the remaining fringe firms start the negotiation process from the beginning (following the same, pre-determined order, but skipping the eliminated firms).
+
+This bargaining process is repeated until all fringe firms have either accepted an offer or been eliminated.
+\Cref{fig:bargaining_microfoundations} provides an illustration of the bargaining process, and how it fits into the broader game.
+Theorem 2 in \textcite{stole1996intra} shows that regardless of the ordering of the fringe firms, the unique subgame perfect equilibrium of this game is the Shapley value of the cooperative game.
+Note, that this result is not only true in expectation: conditioning on any ordering of the fringe firms, the result still holds.
+
+The final piece that is needed to establish the interpretation in terms of entry fees is that for any given configuration of firms emerging from the bargaining process, and, crucially, regardless of the agreed upon entry fees, the unique equilibrium of the subsequent game is the one described in \cref{sec:results_demand}.
+According to the previous theorem, players want to agree on a contract such that their final, total profits $\pi^t_{F_i}$ are equal to their Shapley value ($\varphi_{F_i}$).
+Given any equilibrium sales profits ($\pi^v_{F_i}$), they can achieve it by setting the entry fees to $F_{F_i} = \varphi_{F_i} - \pi^v_{F_i}$.
+Finally, \cref{sec:cooperative_game} and \cref{sec:results_demand} establish that both the Shapley value and the equilibrium sales profits are identical for each fringe firms, and thus a single, common entry fee $F_F$ will be agreed upon.
 

### 2024-05-12 src/paper/application.tex
Change notation (F_F -> K_F)

@@
 There is an infinite measure of fringe firms, who are deciding whether to enter the market.
-Entering has two, separate costs: an exogenous investment cost $I_F$, and the lump-sum platform entry fee $F_F$.
+Entering has two, separate costs: an exogenous investment cost $I_F$, and the lump-sum platform entry fee $K_F$.
 One can conceptualize the first as usual fixed costs, such as the cost of setting up production, or designing a product.
@@
 
-In the benchmark model, the game starts by the platform announcing and committing to an entry fee $F_F$.\footnote{
+In the benchmark model, the game starts by the platform announcing and committing to an entry fee $K_F$.\footnote{
     With no commitment power, but the ability to set any prices after fringe firms make their investment decisions, the platform would charge an entry fee that would make the fringe profits zero \emph{sans the investment cost}.
@@
 
-The main difference between the benchmark and the bargaining model is in determining the entry fee $F_F$.
+The main difference between the benchmark and the bargaining model is in determining the entry fee $K_F$.
 In the former, the platform unilaterally sets the fee, and the fringe treats it as a take it or leave it offer.
@@
         \begin{tikzpicture}[node distance=2cm, auto]
-            \node[align=center] (entry_fee) {Platform unilaterally sets the entry fee \\ $[F_F]$};
-            \node[align=center] (entry_decision) [below of=entry_fee] {Potential entrants decide to enter \\ at cost $I_F + F_F$ \\ $[N_F]$};
+            \node[align=center] (entry_fee) {Platform unilaterally sets the entry fee \\ $[K_F]$};
+            \node[align=center] (entry_decision) [below of=entry_fee] {Potential entrants decide to enter \\ at cost $I_F + K_F$ \\ $[N_F]$};
             \node[align=center] (sales) [below of=entry_decision] {Platform and fringe sell products \\ $[\pi_{Fi}^v, \pi_P^v]$};
@@
             \node[align=center] (entry_decision) {Potential entrants decide to invest \\ at cost $I_F$ \\ $[N_F]$};
-            \node[align=center] (entry_fee) [below of=entry_decision] {Entry fees are negotiated \\ between platform and $N_F$ fringe firms \\ $[F_F]$};
+            \node[align=center] (entry_fee) [below of=entry_decision] {Entry fees are negotiated \\ between platform and $N_F$ fringe firms \\ $[K_F]$};
             \node[align=center] (sales) [below of=entry_fee] {Platform and fringe sell products \\ $[\pi_{Fi}^v, \pi_P^v]$};
@@
 If they decide not to, they make zero profits and do not participate in the later stages of the game.
-Furthermore, these firms can only sell their products through the platform, for which the platform can charge a lump-sum entry fee $F_F$.
-The timing of these decisions is as follows: (1) the platform sets and commits to an entry fee $F_F$, (2) the fringe firms decide whether to enter the market, and (3) the firms that have entered pay the entry fee to the platform.
+Furthermore, these firms can only sell their products through the platform, for which the platform can charge a lump-sum entry fee $K_F$.
+The timing of these decisions is as follows: (1) the platform sets and commits to an entry fee $K_F$, (2) the fringe firms decide whether to enter the market, and (3) the firms that have entered pay the entry fee to the platform.
 
@@
 In order to keep the model tractable I model the negotiation process in a reduced form manner.
-In particular, I assume that the platform and the entrants agree on an entry fee $F_F$, which makes the total profits net entry fees equal to the Shapley value of the players.\footnote{
+In particular, I assume that the platform and the entrants agree on an entry fee $K_F$, which makes the total profits net entry fees equal to the Shapley value of the players.\footnote{
     One simple extension would be to use the more general concept of random order values \parencite{weber1988probabilistic}.
@@
     \label{prop:equilibrium_aggregate_benchmark}
-    If entry costs $I_F$ and $F_F$ are low enough, the equilibrium size of the aggregate is
+    If entry costs $I_F$ and $K_F$ are low enough, the equilibrium size of the aggregate is
     \begin{align}
-        A = \mu \frac{V_F}{F_F + I_F}.
+        A = \mu \frac{V_F}{K_F + I_F}.
         \label{eq:aggregate_eq}
@@
     \begin{align*}
-        N_F = \frac{\mu}{F_F + I_F} - N_P \frac{V_P}{V_F} - \frac{1}{V_F}.
+        N_F = \frac{\mu}{K_F + I_F} - N_P \frac{V_P}{V_F} - \frac{1}{V_F}.
     \end{align*}
@@
     \begin{align*}
-        F_F^* = \sqrt{\mu I_F V_F} - I_F.
+        K_F^* = \sqrt{\mu I_F V_F} - I_F.
     \end{align*}
@@
 Notice that the optimal entry fee does not depend on either the platform's product value or product variety (\cref{fig:entry_fee}).
-This is because due to the lump-sum nature of the entry fee, the platform can extract all the surplus from the fringe firms, and thus chooses $F_F$ to maximize total industry profits.
+This is because due to the lump-sum nature of the entry fee, the platform can extract all the surplus from the fringe firms, and thus chooses $K_F$ to maximize total industry profits.
 The latter is essentially a function of the aggregate, minus the investment costs of the fringe firms.
@@
 \begin{align*}
-    F_F^{\text{impl}} = \pi_F^v - \pi_F^t.
+    K_F^{\text{impl}} = \pi_F^v - \pi_F^t.
 \end{align*}
 As shown before, as the platform's product variety grows, its bargaining power also increases.
-This can be thought of as an increase in (implied) entry fees $F_F^{\text{impl}}$, which in turn discourages fringe entry.
+This can be thought of as an increase in (implied) entry fees $K_F^{\text{impl}}$, which in turn discourages fringe entry.
 This is not happening in the benchmark model, as the optimal entry fee does not depend on the platform's product variety.
@@
                     xlabel={$N_P$},
-                    ylabel={$F_F$},
+                    ylabel={$K_F$},
                     xmin=0, xmax=1.5, % adjust these values as needed
@@
                 ]
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=F_F_opt]{\equilibrium};
-                \addplot[color=myred,mark=none,thick] table[x=N_P,y=F_F_implied]{\equilibrium};
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=K_F_opt]{\equilibrium};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y=K_F_implied]{\equilibrium};
                 \legend{Benchmark, Bargaining (implied)}
@@
         \end{tikzpicture}
-        \caption{Optimal/implied entry fee ($F_F$)}
+        \caption{Optimal/implied entry fee ($K_F$)}
         \label{fig:entry_fee}
@@
                 ]
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=F_F_opt]{\equilibrium};
-                \addplot[color=myred,mark=none,thick] table[x=N_P,y=F_F_implied]{\equilibrium};
-                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=F_F_implied]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=K_F_opt]{\equilibrium};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y=K_F_implied]{\equilibrium};
+                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=K_F_implied]{\equilibriumProfitOneSidedLowLambda};
 
@@
         \node[align=center] (entry_decision) {Potential entrants decide to invest \\ at cost $I_F$ \\ $[N_F]$};
-        \node[align=center, draw, dashed] (entry_fee) [below of=entry_decision] {Entry fees are negotiated \\ between platform \\ and $N_F$ fringe firms \\ $[F_F]$};
+        \node[align=center, draw, dashed] (entry_fee) [below of=entry_decision] {Entry fees are negotiated \\ between platform \\ and $N_F$ fringe firms \\ $[K_F]$};
         \node[align=center] (sales) [below of=entry_fee] {Platform and fringe \\ sell products \\ $[\pi_{Fi}^v, \pi_P^v]$};
@@
         \node[align=center] (choose_proposer) [below=1cm of foreach] {$F_i$ or $P$ is choosen as the proposer};
-        \node[align=center] (proposal) [below of=choose_proposer] {Proposer proposes entry fee $F_{F_i}$};
-        \node[align=center] (accept) [below left=2cm and -2cm of proposal] {Responder accepts $F_{F_i}$};
-        \node[align=center] (reject) [below right=2cm and -2cm of proposal] {Responder rejects $F_{F_i}$};
+        \node[align=center] (proposal) [below of=choose_proposer] {Proposer proposes entry fee $K_{F_i}$};
+        \node[align=center] (accept) [below left=2cm and -2cm of proposal] {Responder accepts $K_{F_i}$};
+        \node[align=center] (reject) [below right=2cm and -2cm of proposal] {Responder rejects $K_{F_i}$};
         \node[align=center] (next_player) [below of=accept] {Move on to the \\ next fringe firm};
@@
 This bilateral negotiation follows the alternating offer procedure described in \textcite{binmore1986nash}.
-One of the two players is chosen as a proposer, and can propose an entry fee for the given firm: $F_{F_i}$.
+One of the two players is chosen as a proposer, and can propose an entry fee for the given firm: $K_{F_i}$.
 The other player can either accept or reject the proposal.
@@
 According to the previous theorem, players want to agree on a contract such that their final, total profits $\pi^t_{F_i}$ are equal to their Shapley value ($\varphi_{F_i}$).
-Given any equilibrium sales profits ($\pi^v_{F_i}$), they can achieve it by setting the entry fees to $F_{F_i} = \varphi_{F_i} - \pi^v_{F_i}$.
-Finally, \cref{sec:cooperative_game} and \cref{sec:results_demand} establish that both the Shapley value and the equilibrium sales profits are identical for each fringe firms, and thus a single, common entry fee $F_F$ will be agreed upon.
+Given any equilibrium sales profits ($\pi^v_{F_i}$), they can achieve it by setting the entry fees to $K_{F_i} = \varphi_{F_i} - \pi^v_{F_i}$.
+Finally, \cref{sec:cooperative_game} and \cref{sec:results_demand} establish that both the Shapley value and the equilibrium sales profits are identical for each fringe firms, and thus a single, common entry fee $K_F$ will be agreed upon.
+
+\section{The platform's product pricing assumption}
+\label{sec:separate_pricing}
+
+TODO: discuss the assumptioin of pricing products separately
 
@@
     From \cref{prop:optimal_profit}, the variable profit of each fringe firm is $\pi_{F_i}^{v*} = \mu V_F / A$.
-    Total profit after entry fees and investment costs is therefore $\pi_{F_i}^{t*} = \mu V_F / A - I_F - F_F$.
+    Total profit after entry fees and investment costs is therefore $\pi_{F_i}^{t*} = \mu V_F / A - I_F - K_F$.
     Under free entry, total profits are zero:
     \begin{align*}
-        0 = \pi_{F_i}^{t*} = \mu V_F / A - F_F - I_F.
+        0 = \pi_{F_i}^{t*} = \mu V_F / A - K_F - I_F.
     \end{align*}
@@
     \begin{align*}
-        A = \mu \frac{V_F}{F_F + I_F},
+        A = \mu \frac{V_F}{K_F + I_F},
     \end{align*}
@@
     \begin{align*}
-        \pi_P^t &= \pi_P^v + F_F N_F \\
-        &= \mu \frac{N_P V_P}{F_F + I_F} + F_F \left[ \frac{\mu}{F_F + I_F} - N_P \frac{V_P}{V_F} - \frac{1}{V_F} \right].
-    \end{align*}
-    The function is strictly concave in $F_F$, so the first order condition is sufficient for optimality in the case of an interior solution.
+        \pi_P^t &= \pi_P^v + K_F N_F \\
+        &= \mu \frac{N_P V_P}{K_F + I_F} + K_F \left[ \frac{\mu}{K_F + I_F} - N_P \frac{V_P}{V_F} - \frac{1}{V_F} \right].
+    \end{align*}
+    The function is strictly concave in $K_F$, so the first order condition is sufficient for optimality in the case of an interior solution.
     Assume that that the optimum is indeed interior.
@@
     \begin{align*}
-        \frac{\mu I_F V_F - (F_F + I_F)^2}{V_F (F_F + I_F)^2} = 0.
+        \frac{\mu I_F V_F - (K_F + I_F)^2}{V_F (K_F + I_F)^2} = 0.
     \end{align*}
@@
     \begin{align*}
-        F_F^* = \sqrt{\mu I_F V_F} - I_F,
+        K_F^* = \sqrt{\mu I_F V_F} - I_F,
     \end{align*}
@@
     i.e., the profit that the platform could achieve by excluding the fringe completely.
-    Therefore, the optimum is indeed interior whenever $F_F$ is low enough
-
-    Now consider the case when $F_F^*$ is so large that it would lead to no fringe entry.
+    Therefore, the optimum is indeed interior whenever $K_F$ is low enough
+
+    Now consider the case when $K_F^*$ is so large that it would lead to no fringe entry.
     In that case, the platform's only source of profit is selling its own products, and thus

### 2024-05-12 src/figures/equilibrium_baseline.py

@@ -35,12 +35,12 @@ def create_plot_data(
         else:
             return fsolve(lambda N_F: pi_F_t(N_P, N_F), 1)[0]
         
-    def F_F_opt():
+    def K_F_opt():
         return np.sqrt(mu * I_F * V_F) - I_F
         
     def N_F_opt_bench(N_P):
-        F_F = F_F_opt()
-        N_F_candidate = mu / (F_F + I_F) - N_P * V_P / V_F - 1 / V_F
+        K_F = K_F_opt()
+        N_F_candidate = mu / (K_F + I_F) - N_P * V_P / V_F - 1 / V_F
         return np.maximum(N_F_candidate, 0)
 
     N_P_vec = np.linspace(N_P_range[0], N_P_range[1], num_obs)
@@ -58,19 +58,19 @@ def create_plot_data(
     N_F_bench = N_F_opt_bench(N_P_vec)
     A_bench = N_P_vec * V_P + N_F_bench * V_F + 1
     CS_bench = np.log(A_bench)
-    pi_P_bench = F_F_opt() * N_F_bench + mu * N_P_vec * V_P / A_bench
+    pi_P_bench = K_F_opt() * N_F_bench + mu * N_P_vec * V_P / A_bench
 
     A_noF = N_P_vec * V_P + 1
     CS_noF = np.log(A_noF)
     pi_P_noF = mu * N_P_vec * V_P / A_noF
 
     pi_P_var_vec = mu * N_P_vec * V_P / A_vec
-    F_F_opt_vec = np.where(
+    K_F_opt_vec = np.where(
         N_F_bench > 1e-5,
-        F_F_opt(),
+        K_F_opt(),
         np.nan
     )
-    F_F_implied = np.where(
+    K_F_implied = np.where(
         N_F_vec > 1e-5,
         (pi_P_vec - pi_P_var_vec) / N_F_vec,
         np.nan
@@ -107,8 +107,8 @@ def create_plot_data(
             "A_noF": A_noF,
             "CS_noF": CS_noF,
             "pi_P_noF": pi_P_noF,
-            "F_F_implied": F_F_implied,
-            "F_F_opt": F_F_opt_vec,
+            "K_F_implied": K_F_implied,
+            "K_F_opt": K_F_opt_vec,
         }
     )
 

### 2024-05-12 src/figures/equilibrium_symbolic.py

@@ -58,12 +58,12 @@ def create_plot_data(
         else:
             return fsolve(lambda N_F: pi_F_t(N_P, N_F), 3)[0]
         
-    def F_F_opt():
+    def K_F_opt():
         return np.sqrt(mu * I_F * V_F) - I_F
     
     def N_F_opt_bench(N_P):
-        F_F = F_F_opt()
-        N_F_candidate = mu / (F_F + I_F) - N_P * V_P / V_F - 1 / V_F
+        K_F = K_F_opt()
+        N_F_candidate = mu / (K_F + I_F) - N_P * V_P / V_F - 1 / V_F
         return np.maximum(N_F_candidate, 0)
 
     N_P_vec = np.linspace(N_P_range[0], N_P_range[1], num_obs)
@@ -88,10 +88,10 @@ def create_plot_data(
         N_F_bench = N_F_opt_bench(N_P_vec)
         A_bench = N_P_vec * V_P + N_F_bench * V_F + 1   
         CS_bench = np.log(A_bench)
-        pi_P_bench = F_F_opt() * N_F_bench + mu * N_P_vec * V_P / A_bench
-        F_F_opt_vec = np.where(
+        pi_P_bench = K_F_opt() * N_F_bench + mu * N_P_vec * V_P / A_bench
+        K_F_opt_vec = np.where(
             N_F_bench > 1e-5,
-            F_F_opt(),
+            K_F_opt(),
             np.nan
         )
         hybrid_mode_bench = np.where(
@@ -104,10 +104,10 @@ def create_plot_data(
         A_bench = np.ones_like(N_P_vec, dtype=float) * np.nan
         CS_bench = np.ones_like(N_P_vec, dtype=float) * np.nan
         pi_P_bench = np.ones_like(N_P_vec, dtype=float) * np.nan
-        F_F_opt_vec = np.ones_like(N_P_vec, dtype=float) * np.nan
+        K_F_opt_vec = np.ones_like(N_P_vec, dtype=float) * np.nan
         hybrid_mode_bench = np.ones_like(N_P_vec, dtype=float) * np.nan
 
-    F_F_implied = np.where(
+    K_F_implied = np.where(
         N_F_vec > 1e-5,
         (pi_P_vec - pi_P_var_vec) / N_F_vec,
         np.nan
@@ -137,8 +137,8 @@ def create_plot_data(
             "A_noF": A_noF,
             "CS_noF": CS_noF,
             "pi_P_noF": pi_P_noF,
[…]

### 2024-05-12 src/sympy/benchmark_case.py

@@ -9,22 +9,22 @@ V_F = Symbol('V_F')
 V_P = Symbol('V_P')
 
 I_F = Symbol('I_F')
-F_F = Symbol('F_F')
+K_F = Symbol('K_F')
 
 N_F = Symbol('N_F')
 N_P = Symbol('N_P')
 n = Symbol('n')
 
-A_eq = mu * V_F / (F_F + I_F)
+A_eq = mu * V_F / (K_F + I_F)
 A_def = N_F * V_F + N_P * V_P + 1
 
 N_F_eq = simplify(solve(Eq(A_eq, A_def), N_F)[0])
 
-pi_P = simplify(F_F * N_F_eq + N_P * mu * V_P / A_eq)
+pi_P = simplify(K_F * N_F_eq + N_P * mu * V_P / A_eq)
 
-F_F_opt = simplify(solve(Eq(pi_P.diff(F_F), 0), F_F)[1])
+K_F_opt = simplify(solve(Eq(pi_P.diff(K_F), 0), K_F)[1])
 
-pi_P_opt = simplify(pi_P.subs(F_F, F_F_opt))
+pi_P_opt = simplify(pi_P.subs(K_F, K_F_opt))
 pi_P_ret = mu * (N_P * V_P) / (N_P * V_P + 1)
 
 N_P_bar = (sqrt(mu * V_F / I_F) - 1) / V_P

### 2024-05-12 src/figures/equilibrium_symbolic.py
Fix default arg

@@ -18,7 +18,7 @@ def create_plot_data(
     num_obs: int = 500,
     lambda_P: float = 1,
     value_function: str = "profit",
-    bargaining: str = "one-sided",
+    bargaining: str = "onesided",
 ):
     
     N_P_sp, N_F_sp = Symbol("N_P"), Symbol("N_F")

### 2024-05-12 src/paper/application.tex
Fix axis limits

@@
                     xmin=0, xmax=1.5, % adjust these values as needed
-                    ymin=0, ymax=3, % adjust these values as needed
+                    ymin=0, ymax=1.1, % adjust these values as needed
                     width=\linewidth, % adjust the width of the plot

### 2024-05-12 src/paper/application.tex
Better parametrization

--- 2024-05-12 src/paper/application.tex
@@
 
-In the example parametrization, the implied entry fee is higher than what the platform would prefer to set for any $N_P \geq 0$.
-If it could, it would commit to a lower entry fee to incentivize more fringe entry, and thus increase total profits.
+In the example parametrization, the implied entry fee is lower than what the platform would prefer to set for low values of $N_P$, and higher afterwards.
+There is an optimal platform product variety $N_P^*$ for which the implied entry fee is the same as the optimal entry fee in the benchmark model, and therefore the results of the two models are the same.
+For $N_P > N_P^*$, the platform would like to commit to a lower entry fee to incentivize more fringe entry.
 This is an example that bargaining instead of unilateral pricing does not necessarily lead to lower platform shares, or better welfare outcomes: it can be a lose-lose situation for both the platform and the consumers.
-\Cref{sec:lower_bargaining_power} explores an alternative model where the platform has less bargaining power, and thus -- for sufficiently low values of $N_P$ -- the implied entry fee it achieves in the bargaining model is lower than what it would set unilaterally.
 
@@
 On the other hand, with bargaining, it is increasing in $N_P$ (\cref{fig:entry_fee}).
-Therefore, if the entry fee is already higher than optimal for a given $N_P$, an additional increase will lead to an even more suboptimal (implied) entry fee, and thus a lower increase in platform profits than it would otherwise.
-This is the case in the example parametrization displayed on the figures for every $N_P \geq 0$.
+Therefore, if the entry fee is lower than optimal, then the increase in $N_P$ will bring it closer to the optimal level, and the increase in platform profits will be higher than in the benchmark model.
+On the other hand, when the entry fee is already higher than optimal for a given $N_P$, an additional increase will lead to an even more suboptimal (implied) entry fee, and thus a lower increase in platform profits.
 
@@
                     xlabel={$N_P$},
-                    xmin=0, xmax=1.5, % adjust these values as needed
-                    ymin=0, ymax=1.4, % adjust these values as needed
+                    xmin=0, xmax=4.5, % adjust these values as needed
+                    ymin=0, ymax=4.4, % adjust these values as needed
                     width=\linewidth, % adjust the width of the plot
                     axis lines=left,
-                    xtick={0, 1.5},
+                    xtick={0, 4.5},
                 ]
@@
                     ylabel={$K_F$},
-                    xmin=0, xmax=1.5, % adjust these values as needed
-                    ymin=0, ymax=0.65, % adjust these values as needed
+                    xmin=0, xmax=4.5, % adjust these values as needed
+                    ymin=0, ymax=0.35, % adjust these values as needed
                     width=\linewidth, % adjust the width of the plot
                     axis lines=left,
-                    xtick={0, 1.5},
-                    legend pos=north east
+                    xtick={0, 4.5},
+                    legend pos=south east
                 ]
@@
     \end{subfigure}
-    \caption{Equilibrium number of fringe entrants and (implied) entry fees ($\mu = 1, N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$).
+    \caption{Equilibrium number of fringe entrants and (implied) entry fees ($\mu = 1, N_C = 1, V_P = 1, V_F = 1, I_F = 0.05$).
 In the benchmark model, the entry fee does not depend on the platform's product variety, and an increase in $N_P$ leads to a proportional reduction in $N_F$.
@@
     \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
         \begin{tikzpicture}
@@
                     xlabel={$N_P$},
-                    xmin=0, xmax=1.5, % adjust these values as needed
-                    ymin=0, ymax=0.65, % adjust these values as needed
-                    width=0.5\linewidth, % adjust the width of the plot
+                        xmin=0, xmax=4.5, % adjust these values as needed
+                        ymin=0, ymax=0.9, % adjust these values as needed
+                        width=\linewidth, % adjust the width of the plot
                         axis lines=left,
-                    xtick={0, 1.5},
+                        xtick={0, 4.5},
                         legend pos=south east
@@
         \end{tikzpicture}
-    \caption{Platform profits in equilibrium ($\mu = 1, N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$).
+        \caption{}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                        xmin=0, xmax=1, % adjust these values as needed
+                        ymin=0.58, ymax=0.67, % adjust these values as needed
+                        width=\linewidth, % adjust the width of the plot
+                        axis lines=left,
+                        xtick={0, 1},
+                        legend pos=south east
+                    ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=pi_P_bench]{\equilibrium};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y=pi_P]{\equilibrium};
+                \legend{Benchmark, Bargaining}
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibrium};
+                \addplot[draw=none,name path=hybrid_bench] table[x=N_P,y=hybrid_bench]{\equilibrium};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid_bench and bottom];
+            \end{axis}
+        \end{tikzpicture}
+        \caption{}
+    \end{subfigure}
+    \caption{Platform profits in equilibrium ($\mu = 1, N_C = 1, V_P = 1, V_F = 1, I_F = 0.05$).
 In both cases, platform profits are increasing in $N_P$.
-However, in the case of the hybrid regime under bargaining, this increase is lower, due to the fact that prices deviate further from optimal.
+In the case of the hybrid regime under bargaining, this increase is higher than in the benchmark case as long as the implied the entry fee is lower than optimal, and lower afterwards.
+The right-hand side graph zooms on the relevant section to highlight this observation.
 Dark shaded area represents hybrid mode under the bargaining assumption, while light shaded area represents additional hybrid mode under the benchmark assumption.}
@@
                     xlabel={$N_P$},
-                    xmin=0, xmax=1.5, % adjust these values as needed
-                    ymin=0, ymax=3, % adjust these values as needed
+                    xmin=0, xmax=4.5, % adjust these values as needed
+                    ymin=0, ymax=5.5, % adjust these values as needed
                     width=\linewidth, % adjust the width of the plot
                     axis lines=left,
-                    xtick={0, 1.5},
+                    xtick={0, 4.5},
                     legend pos=south east
@@
                     xlabel={$N_P$},
-                    xmin=0, xmax=1.5, % adjust these values as needed
-                    ymin=0, ymax=1.5, % adjust these values as needed
+                    xmin=0, xmax=4.5, % adjust these values as needed
+                    ymin=0, ymax=1.8, % adjust these values as needed
                     width=\linewidth, % adjust the width of the plot
                     axis lines=left,
-                    xtick={0, 1.5},
+                    xtick={0, 4.5},
                     legend pos=south east
@@
     \end{subfigure}
-    \caption{Size of the aggregate and consumer surplus in equilibrium ($\mu = 1, N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$).
+    \caption{Size of the aggregate and consumer surplus in equilibrium ($\mu = 1, N_C = 1, V_P = 1, V_F = 1, I_F = 0.05$).
 In the benchmark model, an increase in platform product variety has no effect in the hybrid regime.
@@
                     xlabel={$N_P$},
-                    xmin=0, xmax=1.5, % adjust these values as needed
+                    xmin=0, xmax=4.5, % adjust these values as needed
                     ymin=0, ymax=1.8, % adjust these values as needed
@@
                     axis lines=left,
-                    xtick={0, 1.5},
+                    xtick={0, 4.5},
                 ]
@@
                     xlabel={$N_P$},
-                    xmin=0, xmax=1.5, % adjust these values as needed
-                    ymin=0, ymax=3, % adjust these values as needed
+                    xmin=0, xmax=4.5, % adjust these values as needed
+                    ymin=0, ymax=1.1, % adjust these values as needed
                     width=\linewidth, % adjust the width of the plot
                     axis lines=left,
-                    xtick={0, 1.5},
+                    xtick={0, 4.5},
                     legend pos=south east,
@@
                     ylabel={},
-                    xmin=0, xmax=1.5, % adjust these values as needed
+                    xmin=0, xmax=4.5, % adjust these values as needed
                     ymin=0, ymax=0.65, % adjust these values as needed
                     axis lines=left,
-                    xtick={0, 1.5},
+                    xtick={0, 4.5},
                     legend pos=south east,
@@
                     ylabel={},
-                    xmin=0, xmax=1.5, % adjust these values as needed
+                    xmin=0, xmax=4.5, % adjust these values as needed
                     ymin=0, ymax=0.5, % adjust these values as needed
                     axis lines=left,
-                    xtick={0, 1.5},
+                    xtick={0, 4.5},
                     legend pos=south east,
@@
                     ylabel={},
-                    xmin=0, xmax=1.5, % adjust these values as needed
+                    xmin=0, xmax=4.5, % adjust these values as needed
                     ymin=0.2, ymax=0.35, % adjust these values as needed
                     axis lines=left,
-                    xtick={0, 1.5},
+                    xtick={0, 4.5},
                     legend pos=north west,
@@
                     ylabel={},
-                    xmin=0, xmax=1.5, % adjust these values as needed
+                    xmin=0, xmax=4.5, % adjust these values as needed
                     ymin=0.2, ymax=0.35, % adjust these values as needed
                     axis lines=left,
-                    xtick={0, 1.5},
+                    xtick={0, 4.5},
                     legend pos=south west,
@@
 In the case of lower $\lambda_P$ (right), choosing the hybrid mode can be optimal depending on $I_P$.
-The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode ($\mu = 1, N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$).}
+The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode ($\mu = 1, N_C = 1, V_P = 1, V_F = 1, I_F = 0.05$).}
     \label{fig:equilibrium_low_lambda_entry_fees}
@@
                     ylabel={},
-                    xmin=0, xmax=1.5, % adjust these values as needed
+                    xmin=0, xmax=4.5, % adjust these values as needed
                     ymin=0, ymax=3.1, % adjust these values as needed
                     axis lines=left,
-                    xtick={0, 1.5},
+                    xtick={0, 4.5},
                     legend pos=south east,
@@
                     ylabel={},
-                    xmin=0, xmax=1.5, % adjust these values as needed
+                    xmin=0, xmax=4.5, % adjust these values as needed
                     ymin=0, ymax=1.2, % adjust these values as needed

### 2024-05-12 src/paper/application.tex
Update extensions for new parametrization

@@
 \pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_twosided_scale-0.6_lambda-1.csv}\equilibriumFullSurplusTwoSided
-\pgfplotstableread[col sep=comma]{out/figures/equilibrium_profit_onesided_scale-1_lambda-0.5.csv}\equilibriumProfitOneSidedLowLambda
+\pgfplotstableread[col sep=comma]{out/figures/equilibrium_profit_onesided_scale-1_lambda-2.csv}\equilibriumProfitOneSidedHighLambda
 
@@
                     xmin=0, xmax=4.5, % adjust these values as needed
-                    ymin=0, ymax=5.5, % adjust these values as needed
+                    ymin=0, ymax=5.8, % adjust these values as needed
                     width=\linewidth, % adjust the width of the plot
@@
                     xmin=0, xmax=4.5, % adjust these values as needed
-                    ymin=0, ymax=1.8, % adjust these values as needed
+                    ymin=0, ymax=2, % adjust these values as needed
                     width=\linewidth, % adjust the width of the plot
@@
 
-\subsection{Playrs have different innate bargaining power}
+\subsection{Players have different innate bargaining power}
 \label{sec:lower_bargaining_power}
@@
 
-The example parametrizatrion is the same as in the main model, with the only difference that the platform has a lower innate bargaining power ($\lambda_P = 0.5$).
+The example parametrizatrion is the same as in the main model, with the only difference that the platform has a higher innate bargaining power ($\lambda_P = 2$).
 The main result, namely that the platform's product variety has a negative effect on consumer welfare in the hybrid regime, still holds.
-That is, as shown on \cref{fig:fringe_entry_eq_low_lambda}, total aggregate is decreasing in $N_P$ throughout the hybrid regime, due to the platform's products displacing more fringe products than their total number.
-
-The main difference is that, for low enough $N_P$, the implied entry fee (\cref{fig:platform_profits_low_lambda}) is lower than the benchmark, unilaterally set one,  due to the lower bargaining power of the platform.
-As a consequence, total aggregate, and thus consumer surplus, is also above the benchmark outcome in that case.
-Furthermore, there exists some $\bar{N}_P$ for which the unilateral price setting and bargaining outcomes coincide in terms of all variables, due to the implied entry fee being the same.
+That is, as shown on \cref{fig:fringe_entry_eq_high_lambda}, total aggregate is decreasing in $N_P$ throughout the hybrid regime, due to the platform's products displacing more fringe products than their total number.
+
+The main difference is that, for any $N_P\geq 0$, the implied entry fee (\cref{fig:platform_profits_high_lambda}) is higher than the benchmark, unilaterally set one,  due to the higher bargaining power of the platform.
+That is, for any $N_P$, the platform would prefer to set a lower entry fee, but it is unable to do so due to its high bargaining power.
+Total aggregate, and thus consumer surplus, is also below the main model's outcome in this case.
 
 Another major difference pertains to the total profits of the platform as a function of $N_P$.
-It is still true that they are increasing in the number of the platform's products, but now this increase is even more pronounced for low values of $N_P$.
-The reason is that for low $N_P$, the implied entry fee is lower than the optimal one.
-Furthermore, it is increasing in $N_P$ as a result of the platform's increased bargaining power.
-Therefore, the platform's profits are increasing in $N_P$ even more than in the benchmark case or the main model, up to the point where the implied entry fee is equal to the optimal one.
-After that, the same effect as in the main model kicks in, and the increase in profits is lower than in the benchmark case.
-
-\Cref{fig:equilibrium_low_lambda_entry_fees} demonstrates an important consequence of this phenomenon.
+It is still true that they are increasing in the number of the platform's products, but now this increase is even slower in the hybrid regime.
+The reason is that the implied entry fee is always higher than the optimal one, therefore an increase the positive effect of an increase in $N_P$ is somewhat counterbalanced by the entry fee becoming even more suboptimal.
+
+\Cref{fig:equilibrium_high_lambda_entry_fees} demonstrates an important consequence of this phenomenon.
 Imagine that the platform can decide on the number of its products at time 0, at an investment cost of $I_P$ per product.
-In the example for the main model, due to the implied entry fee being higher than optimal even for $N_P = 0$, hybrid operation is never optimal.
-The platform would always prefer either pure retail or pure marketplace operation.
-In contrast, when the platform has lower bargaining power, there exists a range of values for $I_P$ (most notably, $I_P = I_F = 0.2$) for which the platform would prefer to operate in hybrid mode.
-Furthermore, if hybrid operation is not allowed, the platform might switch to become a pure marketplace, thereby increasing consumer surplus.
+In the example for the main model, due to the implied entry fee being higher than optimal even for $N_P = 0$, hybrid operation may be optimal for certain values of $I_P$ (most notably, $I_P = I_F = 0.05$).
+In contrast, in the example with the platform having higher bargaining power, it would always prefer either pure retail or pure marketplace operation.
 
@@
                     xmin=0, xmax=4.5, % adjust these values as needed
-                    ymin=0, ymax=1.8, % adjust these values as needed
+                    ymin=0, ymax=4.4, % adjust these values as needed
                     width=\linewidth, % adjust the width of the plot
@@
                 \addplot[color=myred,mark=none,thick] table[x=N_P,y=N_F]{\equilibrium};
-                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=N_F]{\equilibriumProfitOneSidedLowLambda};
-                \legend{Benchmark, Bargaining ($\lambda = 1$), Bargaining ($\lambda = 0.5$)}
+                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=N_F]{\equilibriumProfitOneSidedHighLambda};
+                \legend{Benchmark, Bargaining ($\lambda = 1$), Bargaining ($\lambda = 2$)}
 
                 \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibrium};
-                \addplot[draw=none,name path=hybrid_alt] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[draw=none,name path=hybrid_alt] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedHighLambda};
                 \addplot[draw=none,name path=bottom] {0};
@@
         \caption{Equilibrium number of fringe firms ($N_F$)}
-        \label{fig:fringe_entry_eq_low_lambda}
+        \label{fig:fringe_entry_eq_high_lambda}
     \end{subfigure}
@@
                     xmin=0, xmax=4.5, % adjust these values as needed
-                    ymin=0, ymax=1.1, % adjust these values as needed
+                    ymin=0, ymax=2, % adjust these values as needed
                     width=\linewidth, % adjust the width of the plot
@@
                 \addplot[color=myred,mark=none,thick] table[x=N_P,y=CS]{\equilibrium};
-                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=CS]{\equilibriumProfitOneSidedLowLambda};
-                \legend{Benchmark, Bargaining ($\lambda = 1$), Bargaining ($\lambda = 0.5$)}
+                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=CS]{\equilibriumProfitOneSidedHighLambda};
+                \legend{Benchmark, Bargaining ($\lambda = 1$), Bargaining ($\lambda = 2$)}
 
                 \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibrium};
-                \addplot[draw=none,name path=hybrid_alt] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[draw=none,name path=hybrid_alt] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedHighLambda};
                 \addplot[draw=none,name path=bottom] {0};
@@
     \end{subfigure}
-    \caption{Equilibrium outcomes in the case when the platform has lower innate bargaining power ($N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$).
-As in every other case, the platform's profits are increasing in $N_P$, while the fringe's profits are decreasing.
-Furthermore, consumer surplus is also decreasing as a result in a decrease in total product variety.
-The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode.}
-    \label{fig:equilibrium_low_lambda}
+    \caption{Equilibrium outcomes in the case when the platform has higher innate bargaining power ($N_C = 1, V_P = 1, V_F = 1, I_F = 0.05$).
+As before, consumer surplus is decreasing in $N_P$ as a result in a decrease in total product variety.
+Dark shaded area represents hybrid mode under $\lambda=2$, while light shaded area represents additional hybrid mode under $\lambda=1$.}
+    \label{fig:equilibrium_high_lambda}
 \end{figure}
@@
                     xmin=0, xmax=4.5, % adjust these values as needed
-                    ymin=0, ymax=0.65, % adjust these values as needed
+                    ymin=0, ymax=0.9, % adjust these values as needed
                     axis lines=left,
@@
                 \addplot[color=myred,mark=none,thick] table[x=N_P,y=pi_P]{\equilibrium};
-                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=pi_P]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=pi_P]{\equilibriumProfitOneSidedHighLambda};
                 \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=pi_P_noF]{\equilibrium};
 
-                \legend{Benchmark, Bargaining ($\lambda = 1$), Bargaining ($\lambda = 0.5$)}
-
-                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
+                \legend{Benchmark, Bargaining ($\lambda = 1$), Bargaining ($\lambda = 2$)}
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedHighLambda};
                 \addplot[draw=none,name path=hybrid_orig] table[x=N_P,y=hybrid]{\equilibrium};
@@
         \caption{Platform profits}
-        \label{fig:platform_profits_low_lambda}
+        \label{fig:platform_profits_high_lambda}
     \end{subfigure}
@@
                     xmin=0, xmax=4.5, % adjust these values as needed
-                    ymin=0, ymax=0.5, % adjust these values as needed
+                    ymin=0, ymax=0.4, % adjust these values as needed
                     axis lines=left,
@@
                 \addplot[color=myred,mark=none,thick] table[x=N_P,y=K_F_implied]{\equilibrium};
-                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=K_F_implied]{\equilibriumProfitOneSidedLowLambda};
-
-                \legend{Benchmark, Bargaining ($\lambda = 1$), Bargaining ($\lambda = 0.5$)}
-
-                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y=K_F_implied]{\equilibriumProfitOneSidedHighLambda};
+
+                \legend{Benchmark, Bargaining ($\lambda = 1$), Bargaining ($\lambda = 2$)}
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedHighLambda};
                 \addplot[draw=none,name path=hybrid_orig] table[x=N_P,y=hybrid]{\equilibrium};
@@
         \caption{Optimal/implied entry fee}
-        \label{fig:entry_fee_low_lambda}
+        \label{fig:entry_fee_high_lambda}
     \end{subfigure}
-    \caption{Platform profits and (implied) entry fees ($\mu = 0.2, N_C = 1, V_P = 1, V_F = 1, I_F = 0.2$).
+    \caption{Platform profits and (implied) entry fees ($\mu = 0.2, N_C = 1, V_P = 1, V_F = 1, I_F = 0.05$).
 Regardless of lambda, platform profits and entry fees are increasing in $N_P$.
@@
 When $\lambda$ is lower, the entry fees are below optimal for low $N_P$, therefore increasing $N_P$ has a larger positive effect on profits.
-Dark shaded area represents hybrid mode under $\lambda=1$, while light shaded area represents additional hybrid mode under $\lambda=0.5$.}
-    \label{fig:profits_and_entry_fees_low_lambda}
+Dark shaded area represents hybrid mode under $\lambda=2$, while light shaded area represents additional hybrid mode under $\lambda=1$.}
+    \label{fig:profits_and_entry_fees_high_lambda}
 \end{figure}
@@
                     xmin=0, xmax=4.5, % adjust these values as needed
-                    ymin=0.2, ymax=0.35, % adjust these values as needed
+                    ymin=0.2, ymax=0.7, % adjust these values as needed
                     axis lines=left,
                     xtick={0, 4.5},
-                    legend pos=north west,
+                    legend pos=south west,
                     width=\linewidth,
                 ]
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.18]{\equilibrium};
-                \addplot[color=myred,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.2]{\equilibrium};
-                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.22]{\equilibrium};
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.04]{\equilibrium};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.05]{\equilibrium};
+                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.06]{\equilibrium};
 
@@
 
-                \legend{$I_P = 0.18$, $I_P = 0.2$, $I_P = 0.22$}
+                \legend{$I_P = 0.04$, $I_P = 0.05$, $I_P = 0.05$}
             \end{axis}
@@
                     xmin=0, xmax=4.5, % adjust these values as needed
-                    ymin=0.2, ymax=0.35, % adjust these values as needed
+                    ymin=0.2, ymax=0.7, % adjust these values as needed
                     axis lines=left,
@@
                 ]
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.18]{\equilibriumProfitOneSidedLowLambda};
-                \addplot[color=myred,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.2]{\equilibriumProfitOneSidedLowLambda};
-                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.22]{\equilibriumProfitOneSidedLowLambda};
-
-                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedLowLambda};
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.04]{\equilibriumProfitOneSidedHighLambda};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.05]{\equilibriumProfitOneSidedHighLambda};
+                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.06]{\equilibriumProfitOneSidedHighLambda};
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedHighLambda};
                 \addplot[draw=none,name path=bottom] {0};
@@
     \caption{Total platform profits if the platform incurs an investment cost for creating its own products ($\pi_P(N_P) - I_P N_P$).
-In the high bargaining power case (left), the platform never chooses to operate in hybrid mode.
+In the high bargaining power case (right), the platform never chooses to operate in hybrid mode.
 It either becomes a pure marketplace or a pure retailer.
-In the case of lower $\lambda_P$ (right), choosing the hybrid mode can be optimal depending on $I_P$.
+In the case of lower $\lambda_P$ (left), choosing the hybrid mode can be optimal depending on $I_P$.
 The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode ($\mu = 1, N_C = 1, V_P = 1, V_F = 1, I_F = 0.05$).}
-    \label{fig:equilibrium_low_lambda_entry_fees}
+    \label{fig:equilibrium_high_lambda_entry_fees}
 \end{figure}
@@
                     xmin=0, xmax=4.5, % adjust these values as needed
-                    ymin=0, ymax=3.1, % adjust these values as needed
+                    ymin=0, ymax=7.5, % adjust these values as needed
                     axis lines=left,
@@
     \end{subfigure}
-    \caption{Equilibrium outcomes in the case when the whole surplus is bargained over ($N_C = 0.6, V_P = 1, V_F = 1, I_F = 0.2$), and both consumers and fringe firms participate in the bargaining.
+    \caption{Equilibrium outcomes in the case when the whole surplus is bargained over ($N_C = 0.6, V_P = 1, V_F = 1, I_F = 0.05$), and both consumers and fringe firms participate in the bargaining.
 As before, the platform's profits are increasing in $N_P$, while the fringe's profits are decreasing.

### 2024-05-23 src/figures/equilibrium_baseline.py
Clean up python scripts

@@ -1,119 +1,0 @@
-import pandas as pd
-import numpy as np
-from scipy.optimize import fsolve
-from collections.abc import Iterable
-import typer
-
-
-def create_plot_data(
-    out_path: str,
-    mu: float = 1,
-    V_P: float = 1,
-    V_F: float = 1,
-    I_F: float = 0.2,
-    N_P_range: tuple[float, float] = (0, 1),
-    num_obs: int = 500,
-):
-    def f(N_P, N_F):
-        return mu * (N_F * V_F + N_P * V_P) / (N_F * V_F + N_P * V_P + 1)
-
-    def pi_P(N_P, N_F):
-        inner_part = np.log(1 + (N_F * V_F) / (N_P * V_P + 1)) / (N_F * V_F)
-        return mu * (1 - inner_part)
-
-    def pi_F(N_P, N_F):
-        first_part = np.log(1 + (N_F * V_F) / (N_P * V_P + 1)) / (N_F * V_F)
-        second_part = 1 / (N_P * V_P + N_F * V_F + 1)
-        return mu * (first_part - second_part)
-
-    def pi_F_t(N_P, N_F):
-        return pi_F(N_P, N_F) - I_F * N_F
-
-    def N_F_opt(N_P):
-        if isinstance(N_P, Iterable):
-            return np.array([N_F_opt(n) for n in N_P])
-        else:
-            return fsolve(lambda N_F: pi_F_t(N_P, N_F), 1)[0]
-        
-    def K_F_opt():
-        return np.sqrt(mu * I_F * V_F) - I_F
-        
-    def N_F_opt_bench(N_P):
-        K_F = K_F_opt()
-        N_F_candidate = mu / (K_F + I_F) - N_P * V_P / V_F - 1 / V_F
-        return np.maximum(N_F_candidate, 0)
-
-    N_P_vec = np.linspace(N_P_range[0], N_P_range[1], num_obs)
-    N_F_vec = N_F_opt(N_P_vec)
-
-    pi_F_vec = pi_F(N_P_vec, N_F_vec)
-    pi_P_vec = pi_P(N_P_vec, N_F_vec)
-    A_vec = N_P_vec * V_P + N_F_vec * V_F + 1
-    CS_vec = np.log(A_vec)
-
-    N_F_cf = np.maximum(N_F_vec[0] * V_F - N_P_vec * V_P, 0)
-    A_cf = N_P_vec * V_P + N_F_cf * V_F + 1
-    CS_cf = np.log(A_cf)
-
[…]

### 2024-05-23 src/figures/equilibrium_nf.py

@@ -1,5 +1,5 @@
 import numpy as np
-import matplotlib. pyplot as plt
+import matplotlib.pyplot as plt
 import typer
 
 
@@ -16,24 +16,41 @@ def plot_equilibrium_nf(N_P_list, mu, V_P, V_F, I_F, N_F_range, num_obs=500):
         lhs_list.append(lhs)
 
     fig, ax = plt.subplots()
-    ax.plot(N_F, rhs, label=r'$N_F$', color='black')
+    ax.plot(N_F, rhs, label=r"$N_F$", color="black")
     for lhs, N_P in zip(lhs_list, N_P_list):
-        ax.plot(N_F, lhs, label=r'$\phi_F(N_F) \mid N_P = {}$'.format(N_P))
+        ax.plot(N_F, lhs, label=r"$\phi_F(N_F) \mid N_P = {}$".format(N_P))
 
-    ax.set_xlabel(r'$\bar N_F$')
+    ax.set_xlabel(r"$\bar N_F$")
     ax.legend()
 
     return fig, ax
 
 
-def create_plot(out_path: str, mu: float = 1, V_P: float = 1, V_F: float = 1, I_F: float = 0.2,
-                N_P: list[float] = [], N_F_range: tuple[float, float] = (0, 1),
-                num_obs: int = 500, width: float = 5, height: float = 3.5, dpi: int = 300):
-
+def create_plot(
+    out_path: str,
+    mu: float = 1,
+    V_P: float = 1,
+    V_F: float = 1,
+    I_F: float = 0.2,
+    N_P: list[float] = [],
+    N_F_range: tuple[float, float] = (0, 1),
+    num_obs: int = 500,
+    width: float = 5,
+    height: float = 3.5,
+    dpi: int = 300,
+):
     if not N_P:
         raise typer.BadParameter("At least one value for N_P must be provided")
 
-    fig, ax = plot_equilibrium_nf(N_P_list=N_P, mu=mu, V_P=V_P, V_F=V_F, I_F=I_F, N_F_range=N_F_range, num_obs=num_obs)
+    fig, ax = plot_equilibrium_nf(
+        N_P_list=N_P,
+        mu=mu,
+        V_P=V_P,
+        V_F=V_F,
+        I_F=I_F,
+        N_F_range=N_F_range,
+        num_obs=num_obs,
+    )
 
     fig.set_size_inches(width, height)
     fig.set_facecolor("white")

### 2024-05-23 src/figures/equilibrium_symbolic.py

@@ -1,10 +1,11 @@
-import pandas as pd
+from collections.abc import Iterable
+
 import numpy as np
+import pandas as pd
+import typer
 from scipy.integrate import quad
 from scipy.optimize import fsolve
-from collections.abc import Iterable
-import typer
-from sympy import Symbol, integrate, simplify, log, lambdify
+from sympy import Symbol, lambdify, log  # type: ignore
 
 
 def create_plot_data(
@@ -20,12 +21,16 @@ def create_plot_data(
     value_function: str = "profit",
     bargaining: str = "onesided",
 ):
-    
     N_P_sp, N_F_sp = Symbol("N_P"), Symbol("N_F")
     s = Symbol("s")
 
-    f_profit = N_C * mu * (s * N_F_sp * V_F + N_P_sp * V_P) / (s * N_F_sp * V_F + N_P_sp * V_P + 1)
-    f_surplus = N_C * mu * log(s * N_F_sp * V_F + N_P_sp * V_P + 1)
+    f_profit = (
+        N_C
+        * mu
+        * (s * N_F_sp * V_F + N_P_sp * V_P)  # type: ignore
+        / (s * N_F_sp * V_F + N_P_sp * V_P + 1)  # type: ignore
+    )
+    f_surplus = N_C * mu * log(s * N_F_sp * V_F + N_P_sp * V_P + 1)  # type: ignore
 
     if value_function == "profit":
         f = f_profit
@@ -33,19 +38,23 @@ def create_plot_data(
         f = f_profit + f_surplus
     else:
         raise typer.BadParameter(f"Unknown value function: {value_function}")
-    
+
     f_num = lambdify((N_P_sp, N_F_sp, s), f)
     f_diff_num = lambdify((N_P_sp, N_F_sp, s), f.diff(s))
 
     if bargaining == "onesided":
-        pi_P_scalar = lambda N_P, N_F: quad(lambda s: f_num(N_P, N_F, s) * lambda_P * s  ** (lambda_P - 1), 0, 1)[0]
-        pi_F_scalar = lambda N_P, N_F: quad(lambda s: f_diff_num(N_P, N_F, s) * s ** lambda_P, 0, 1)[0]
+        def pi_P_scalar(N_P, N_F):
+            return quad(lambda s: f_num(N_P, N_F, s) * lambda_P * s ** (lambda_P - 1), 0, 1)[0]
[…]

### 2024-05-23 src/manim_figures/comparative_equilibrium_entry.py

@@ -1,21 +1,40 @@
-from manim import *
+from manim import (
+    BLACK,
+    BLUE_D,
+    DOWN,
+    RED_D,
+    UP,
+    WHITE,
+    Axes,
+    Brace,
+    BraceBetweenPoints,
+    Create,
+    Line,
+    MathTex,
+    ParametricFunction,
+    Scene,
+    Tex,
+    Text,
+    Transform,
+    Write,
+)
 from numpy import log
 from scipy.optimize import fsolve
 
 
 def pi_F(N_P, N_F):
-    numerator = N_F * (N_F + N_P) - (N_F + N_P + 1) * (N_F + log(N_P + 1) - log(N_F + N_P + 1))
+    numerator = N_F * (N_F + N_P) - (N_F + N_P + 1) * (
+        N_F + log(N_P + 1) - log(N_F + N_P + 1)
+    )
     denominator = N_F * (N_F + N_P + 1)
     return numerator / denominator
 
 
 class Baseline(Scene):
-
     def construct(self):
-
         self.next_section("draw_graph")
 
-        self.camera.background_color = WHITE
+        self.camera.background_color = WHITE  # type: ignore
         Text.set_default(color=BLACK)
         Line.set_default(color=BLACK)
         Tex.set_default(color=BLACK)
@@ -30,7 +49,7 @@ class Baseline(Scene):
             x_length=12,
             y_length=8,
             x_axis_config={"include_ticks": False},
-            y_axis_config={"include_ticks": False}
+            y_axis_config={"include_ticks": False},
         )
         ax_label = ax.get_x_axis_label(r"t")
 
@@ -49,8 +68,12 @@ class Baseline(Scene):
         # Destinations
         pi_F_orig = ax.plot(lambda x: pi_F(N_P_0, x), color=BLUE_D)
         pi_F_alt = ax.plot(lambda x: pi_F(N_P_1, x), color=RED_D)
-        pi_F_orig_label = ax.get_graph_label(pi_F_orig, r"\pi_F(N_P, N_F)", direction=UP)
-        pi_F_alt_label = ax.get_graph_label(pi_F_alt, r"\pi_F(N_P', N_F)", direction=DOWN)
+        pi_F_orig_label = ax.get_graph_label(
+            pi_F_orig, r"\pi_F(N_P, N_F)", direction=UP  # type: ignore
+        )
+        pi_F_alt_label = ax.get_graph_label(
+            pi_F_alt, r"\pi_F(N_P', N_F)", direction=DOWN  # type: ignore
[…]

### 2024-05-23 src/manim_figures/comparative_n_p_on_shares.py

@@ -1,14 +1,32 @@
-from manim import *
-from numpy import sqrt, log1p, exp
+from manim import (
+    BLACK,
+    BLUE,
+    RED,
+    UP,
+    WHITE,
+    Axes,
+    Brace,
+    Create,
+    DashedVMobject,
+    FadeIn,
+    FadeOut,
+    Line,
+    MathTex,
+    ParametricFunction,
+    Scene,
+    Tex,
+    Text,
+    Transform,
+    Write,
+)
+from numpy import exp, log1p
 
 
 class Baseline(Scene):
-
     def construct(self):
-
         self.next_section("draw_graph")
 
-        self.camera.background_color = WHITE
+        self.camera.background_color = WHITE  # type: ignore
         Text.set_default(color=BLACK)
         Line.set_default(color=BLACK)
         Tex.set_default(color=BLACK)
@@ -18,10 +36,7 @@ class Baseline(Scene):
 
         # Create plane
         ax = Axes(
-            x_range=[0, 1, 0.05],
-            y_range=[0, 1.1, 0.05],
-            x_length=10,
-            y_length=10
+            x_range=[0, 1, 0.05], y_range=[0, 1.1, 0.05], x_length=10, y_length=10
         )
         ax_label = ax.get_x_axis_label(r"s")
 
@@ -30,31 +45,48 @@ class Baseline(Scene):
         f_positive = ax.plot(lambda x: x)
         f_negative = ax.plot(lambda x: log1p(exp(1) - 2 + x))
 
-        f_orig_label = ax.get_graph_label(f_orig, "f(N_P, sN_F)", direction=UP)
-        f_positive_label = ax.get_graph_label(f_positive, "f(N_P', sN_F)", direction=UP)
-        f_negative_label = ax.get_graph_label(f_negative, "f(N_P', sN_F)", direction=UP)
+        f_orig_label = ax.get_graph_label(f_orig, "f(N_P, sN_F)", direction=UP)  # type: ignore
+        f_positive_label = ax.get_graph_label(f_positive, "f(N_P', sN_F)", direction=UP)  # type: ignore
+        f_negative_label = ax.get_graph_label(f_negative, "f(N_P', sN_F)", direction=UP)  # type: ignore
 
         top_orig = ax.plot(lambda x: log1p(1))
         top_alt = ax.plot(lambda x: 1)
 
[…]

### 2024-05-23 src/manim_figures/corollary_comparative.py

@@ -1,14 +1,31 @@
-from manim import *
+from manim import (
+    BLACK,
+    BLUE,
+    DOWN,
+    RED,
+    RIGHT,
+    WHITE,
+    Axes,
+    Brace,
+    Create,
+    FadeIn,
+    Line,
+    MathTex,
+    ParametricFunction,
+    ReplacementTransform,
+    Scene,
+    Tex,
+    Text,
+    Write,
+)
 from numpy import sqrt
 
 
 class Baseline(Scene):
-
     def construct(self):
-
         self.next_section("draw_graph")
 
-        self.camera.background_color = WHITE
+        self.camera.background_color = WHITE  # type: ignore
         Text.set_default(color=BLACK)
         Line.set_default(color=BLACK)
         Tex.set_default(color=BLACK)
@@ -17,24 +34,19 @@ class Baseline(Scene):
         ParametricFunction.set_default(color=BLACK)
 
         # Create plane
-        ax = Axes(
-            x_range=[0, 1, 0.05],
-            y_range=[0, 1, 0.05],
-            x_length=10,
-            y_length=10
-        )
+        ax = Axes(x_range=[0, 1, 0.05], y_range=[0, 1, 0.05], x_length=10, y_length=10)
         ax_label = ax.get_x_axis_label(r"t")
 
         self.play(Create(ax), Write(ax_label))
 
         f = ax.plot(lambda x: x**2)
-        f_label = ax.get_graph_label(f, "f(t)", direction=RIGHT)
+        f_label = ax.get_graph_label(f, "f(t)", direction=RIGHT)  # type: ignore
         self.play(Create(f), Create(f_label))
         self.wait(0.5)
 
-        area = ax.get_area(f, (0, 1), opacity=0.5, color=BLUE)
+        area = ax.get_area(f, (0, 1), opacity=0.5, color=BLUE)  # type: ignore
         top = ax.plot(lambda x: 1)
-        area_fringe = ax.get_area(f, (0, 1), bounded_graph=top, opacity=0.5, color=RED)
+        area_fringe = ax.get_area(f, (0, 1), bounded_graph=top, opacity=0.5, color=RED)  # type: ignore
 
         self.play(Create(top))
 
@@ -44,48 +56,63 @@ class Baseline(Scene):
         self.next_section("complements")
 
         f2 = ax.plot(lambda x: sqrt(x))
-        f2_label = ax.get_graph_label(f2, "f(t)", direction=RIGHT)
[…]

### 2024-05-23 src/manim_figures/equilibrium_entry.py

@@ -1,7 +1,31 @@
-from manim import *
+from manim import (
+    BLACK,
+    BLUE_D,
+    DOWN,
+    LEFT,
+    RED_D,
+    RIGHT,
+    UP,
+    WHITE,
+    YELLOW_D,
+    Axes,
+    Brace,
+    BraceBetweenPoints,
+    Create,
+    Dot,
+    FadeIn,
+    FadeOut,
+    Line,
+    MathTex,
+    ParametricFunction,
+    ReplacementTransform,
+    Scene,
+    Tex,
+    Text,
+    Write,
+)
 from numpy import log
 from scipy.optimize import root_scalar
-
 
 B = 1
 C = 0.2
@@ -19,14 +43,11 @@ def phi_F(N_F, N_P):
     return v(N_F, N_P) - phi_P(N_F, N_P)
 
 
-
 class Equilibrium(Scene):
-
     def construct(self):
-
         self.next_section("draw_axes")
 
-        self.camera.background_color = WHITE
+        self.camera.background_color = WHITE  # type: ignore
         Text.set_default(color=BLACK)
         Line.set_default(color=BLACK)
         Tex.set_default(color=BLACK)
@@ -36,10 +57,7 @@ class Equilibrium(Scene):
 
         # Create plane
         ax = Axes(
-            x_range=[0, 1.2, 0.05],
-            y_range=[0, 0.7, 0.05],
-            x_length=11,
-            y_length=6
+            x_range=[0, 1.2, 0.05], y_range=[0, 0.7, 0.05], x_length=11, y_length=6
         )
         ax.shift(UP * 0.5)
         ax_label = MathTex("N_f", color=BLACK)
@@ -53,7 +71,7 @@ class Equilibrium(Scene):
 
         self.next_section("char_func")
         v_fun = ax.plot(lambda N_f: v(N_f, N_P_val), color=BLUE_D)
-        v_label = ax.get_graph_label(v_fun, "v(t)", direction=DOWN)
+        v_label = ax.get_graph_label(v_fun, "v(t)", direction=DOWN)  # type: ignore
         self.play(Create(v_fun), Write(v_label))
 
         # Profit shares
@@ -69,8 +87,14 @@ class Equilibrium(Scene):
         self.next_section("P_profit_share")
         top_line = ax.get_horizontal_line(pie_to_share, color=BLACK)
         top_graph = ax.plot(lambda x: v(N_F_bar_val, N_P_val))
[…]

### 2024-05-23 src/manim_figures/equilibrium_outcomes.py

@@ -1,16 +1,32 @@
-from manim import *
 import pandas as pd
+from manim import (
+    BLACK,
+    BLUE_D,
+    DOWN,
+    RED_D,
+    RIGHT,
+    WHITE,
+    Axes,
+    Brace,
+    Create,
+    Line,
+    MathTex,
+    ParametricFunction,
+    Scene,
+    Tex,
+    Text,
+    Transform,
+    Write,
+)
 
 
 class Baseline(Scene):
-
     def construct(self):
-
         data = pd.read_csv("out/figures/equilibrium.csv")
 
         self.next_section("draw_graph")
 
-        self.camera.background_color = WHITE
+        self.camera.background_color = WHITE  # type: ignore
         Text.set_default(color=BLACK)
         Line.set_default(color=BLACK)
         Tex.set_default(color=BLACK)
@@ -26,35 +42,48 @@ class Baseline(Scene):
             y_length=7,
             x_axis_config={"include_ticks": False},
             y_axis_config={"include_ticks": False},
-
         )
-        x_ax_label, y_ax_label = ax.get_axis_labels(x_label=r"N_P", y_label=r"CS^*(N_P)")
+        x_ax_label, y_ax_label = ax.get_axis_labels(
+            x_label=r"N_P", y_label=r"CS^*(N_P)"
+        )
 
         # Destiniations
-        A_noF =  (ax.plot_line_graph(
-            x_values=data["N_P"], y_values=data["CS_noF"],
-            line_color=BLACK, add_vertex_dots=False
-        ))
+        A_noF = ax.plot_line_graph(
+            x_values=data["N_P"],
+            y_values=data["CS_noF"],
+            line_color=BLACK,  # type: ignore
+            add_vertex_dots=False,
+        )
         A_bench = ax.plot_line_graph(
-            data["N_P"], data["CS_bench"],
-            line_color=BLUE_D, add_vertex_dots=False
+            data["N_P"],
+            data["CS_bench"],
+            line_color=BLUE_D,  # type: ignore
+            add_vertex_dots=False,
         )
         A_barg = ax.plot_line_graph(
-            data["N_P"], data["CS"],
-            line_color=RED_D, add_vertex_dots=False
+            data["N_P"],
+            data["CS"],
+            line_color=RED_D,  # type: ignore
[…]

### 2024-05-23 src/manim_figures/market_structure.py

@@ -1,38 +1,71 @@
-from manim import *
-
+from manim import (
+    BLACK,
+    BLUE_D,
+    DOWN,
+    GREEN,
+    LEFT,
+    RED,
+    RIGHT,
+    UP,
+    WHITE,
+    Brace,
+    Create,
+    FadeIn,
+    Line,
+    MathTex,
+    Rectangle,
+    ReplacementTransform,
+    Scene,
+    Tex,
+    VGroup,
+    Write,
+)
 
 NUM_FIRMS = 4
 
 
 class MarketStructure(Scene):
-
     def construct(self):
-
-        self.camera.background_color = WHITE
+        self.camera.background_color = WHITE  # type: ignore
 
         self.next_section("draw_objects")
 
         firms = []
         for i in range(NUM_FIRMS):
             firm_text = Tex(f"$A_{i + 1}$", color=BLACK, font_size=80)
-            firm_text.bg = Rectangle(height=1.5, width=1.5, color=RED, fill_opacity=0.25)
+            firm_text.bg = Rectangle(  # type: ignore
+                height=1.5,
+                width=1.5,
+                color=RED,  # type: ignore
+                fill_opacity=0.25,
+            )
             firm = VGroup(firm_text, firm_text.bg)
             firms.append(firm)
 
         platform_text = Tex("$P$", color=BLACK, font_size=80)
-        platform_text.bg = Rectangle(height=2.5, width=2.5, color=BLUE_D, fill_opacity=0.25)
+        platform_text.bg = Rectangle(  # type: ignore
+            height=2.5,
+            width=2.5,
+            color=BLUE_D,  # type: ignore
+            fill_opacity=0.25,
+        )
         platform = VGroup(platform_text, platform_text.bg)
 
         consumers = Tex("Consumers", color=BLACK, font_size=80)
-        consumers.bg = Rectangle(height=1.5, width=5, color=GREEN, fill_opacity=0.25)
+        consumers.bg = Rectangle(  # type: ignore
+            height=1.5,
+            width=5,
+            color=GREEN,  # type: ignore
+            fill_opacity=0.25,
+        )
         consumers = VGroup(consumers, consumers.bg)
 
         firms_group = VGroup(*firms)
 
         all_players = VGroup(firms_group, platform, consumers)
 
-        firms_group.arrange(RIGHT, buff=2)
-        all_players.arrange(DOWN, buff=2)
+        firms_group.arrange(RIGHT, buff=2)  # type: ignore
[…]

### 2024-05-23 src/manim_figures/market_structure_benchmark.py

@@ -1,38 +1,71 @@
-from manim import *
-
+from manim import (
+    BLACK,
+    BLUE_D,
+    DOWN,
+    GREEN,
+    LEFT,
+    RED,
+    RIGHT,
+    UP,
+    WHITE,
+    Brace,
+    Create,
+    FadeIn,
+    Line,
+    MathTex,
+    Rectangle,
+    ReplacementTransform,
+    Scene,
+    Tex,
+    VGroup,
+    Write,
+)
 
 NUM_FIRMS = 4
 
 
 class MarketStructure(Scene):
-
     def construct(self):
-
-        self.camera.background_color = WHITE
+        self.camera.background_color = WHITE  # type: ignore
 
         self.next_section("draw_objects")
 
         firms = []
         for i in range(NUM_FIRMS):
             firm_text = Tex(f"$A_{i + 1}$", color=BLACK, font_size=80)
-            firm_text.bg = Rectangle(height=1.5, width=1.5, color=RED, fill_opacity=0.25)
+            firm_text.bg = Rectangle(  # type: ignore
+                height=1.5,
+                width=1.5,
+                color=RED,  # type: ignore
+                fill_opacity=0.25,
+            )
             firm = VGroup(firm_text, firm_text.bg)
             firms.append(firm)
 
         platform_text = Tex("$P$", color=BLACK, font_size=80)
-        platform_text.bg = Rectangle(height=2.5, width=2.5, color=BLUE_D, fill_opacity=0.25)
+        platform_text.bg = Rectangle(  # type: ignore
+            height=2.5,
+            width=2.5,
+            color=BLUE_D,  # type: ignore
+            fill_opacity=0.25,
+        )
         platform = VGroup(platform_text, platform_text.bg)
 
         consumers = Tex("Consumers", color=BLACK, font_size=80)
-        consumers.bg = Rectangle(height=1.5, width=5, color=GREEN, fill_opacity=0.25)
+        consumers.bg = Rectangle(  # type: ignore
+            height=1.5,
+            width=5,
+            color=GREEN,  # type: ignore
+            fill_opacity=0.25,
+        )
         consumers = VGroup(consumers, consumers.bg)
 
         firms_group = VGroup(*firms)
 
         all_players = VGroup(firms_group, platform, consumers)
 
-        firms_group.arrange(RIGHT, buff=2)
-        all_players.arrange(DOWN, buff=2)
+        firms_group.arrange(RIGHT, buff=2)  # type: ignore
[…]

### 2024-05-23 src/manim_figures/proposition_main.py

@@ -1,14 +1,33 @@
-from manim import *
+from manim import (
+    BLACK,
+    BLUE,
+    DOWN,
+    RED,
+    RIGHT,
+    WHITE,
+    Axes,
+    Brace,
+    BraceBetweenPoints,
+    Create,
+    DrawBorderThenFill,
+    FadeIn,
+    FadeOut,
+    Line,
+    ParametricFunction,
+    ReplacementTransform,
+    Scene,
+    Tex,
+    Text,
+    Write,
+)
 from numpy import sqrt
 
 
 class Baseline(Scene):
-
     def construct(self):
-
         self.next_section("draw_bars")
 
-        self.camera.background_color = WHITE
+        self.camera.background_color = WHITE  # type: ignore
         Text.set_default(color=BLACK)
         Line.set_default(color=BLACK)
         Tex.set_default(color=BLACK)
@@ -16,21 +35,18 @@ class Baseline(Scene):
         ParametricFunction.set_default(color=BLACK)
 
         # Create plane
-        ax = Axes(
-            x_range=[0, 1, 0.05],
-            y_range=[0, 1, 0.05],
-            x_length=10,
-            y_length=10
-        )
+        ax = Axes(x_range=[0, 1, 0.05], y_range=[0, 1, 0.05], x_length=10, y_length=10)
         ax_label = ax.get_axis_labels(x_label=r"t")
 
         self.play(Create(ax), Write(ax_label))
 
         f = ax.plot(lambda x: sqrt(x))
-        area = ax.get_area(f, (0, 1), opacity=0.5, color=BLUE)
+        area = ax.get_area(f, (0, 1), opacity=0.5, color=BLUE)  # type: ignore
 
         # Discrete number of firms
-        rects = ax.get_riemann_rectangles(f, (0.2, 1), dx=0.2, input_sample_type="right")
+        rects = ax.get_riemann_rectangles(
+            f, (0.2, 1), dx=0.2, input_sample_type="right"
+        )
         self.play(DrawBorderThenFill(rects))
 
         self.next_section("add_brace")
@@ -44,7 +60,9 @@ class Baseline(Scene):
         self.next_section("more_firms")
 
         # More firms
-        rects2 = ax.get_riemann_rectangles(f, (0.05, 1), dx=0.05, input_sample_type="right")
+        rects2 = ax.get_riemann_rectangles(
+            f, (0.05, 1), dx=0.05, input_sample_type="right"
+        )
 
         # Brace again
[…]

### 2024-05-23 src/manim_figures/shapley_value_demo.py

@@ -1,16 +1,36 @@
-from manim import *
+from manim import (
+    BLACK,
+    BLUE_D,
+    DOWN,
+    LEFT,
+    RED,
+    RIGHT,
+    UP,
+    WHITE,
+    Brace,
+    BraceBetweenPoints,
+    FadeIn,
+    Line,
+    MoveToTarget,
+    Rectangle,
+    ReplacementTransform,
+    Scene,
+    Tex,
+    Text,
+    Transform,
+    VGroup,
+    Write,
+)
 
 
 class ShapleyDemo(Scene):
-
     def construct(self):
-
         box_size = 2
         label_size = 150
         horiz_space = 7
         up_shift = 3
 
-        self.camera.background_color = WHITE
+        self.camera.background_color = WHITE  # type: ignore
 
         Text.set_default(color=BLACK)
         Line.set_default(color=BLACK)
@@ -20,15 +40,30 @@ class ShapleyDemo(Scene):
         self.next_section("draw_objects")
 
         P_text = Tex("$P$", color=BLACK, font_size=label_size)
-        P_text.bg = Rectangle(height=box_size, width=box_size, color=BLUE_D, fill_opacity=0.25)
+        P_text.bg = Rectangle(  # type: ignore
+            height=box_size,
+            width=box_size,
+            color=BLUE_D,  # type: ignore
+            fill_opacity=0.25,
+        )
         P = VGroup(P_text, P_text.bg)
 
         A1_text = Tex("$A_1$", color=BLACK, font_size=label_size)
-        A1_text.bg = Rectangle(height=box_size, width=box_size, color=RED, fill_opacity=0.25)
+        A1_text.bg = Rectangle(  # type: ignore
+            height=box_size,
+            width=box_size,
+            color=RED,  # type: ignore
+            fill_opacity=0.25,
+        )
         A1 = VGroup(A1_text, A1_text.bg)
 
         A2_text = Tex("$A_2$", color=BLACK, font_size=label_size)
-        A2_text.bg = Rectangle(height=box_size, width=box_size, color=RED, fill_opacity=0.25)
+        A2_text.bg = Rectangle(  # type: ignore
+            height=box_size,
+            width=box_size,
+            color=RED,  # type: ignore
+            fill_opacity=0.25,
+        )
         A2 = VGroup(A2_text, A2_text.bg)
 
         P.next_to(A1, horiz_space * LEFT)
@@ -39,9 +74,16 @@ class ShapleyDemo(Scene):
[…]

### 2024-05-23 src/sympy/bargaining_case.py

@@ -1,16 +1,23 @@
-from sympy import Symbol, integrate, init_printing, simplify, expand, factor, solve, log, plot
+from sympy import (
+    Symbol,
+    init_printing,
+    integrate,
+    log,  # type: ignore
+    plot,
+    simplify,
+)
 
 init_printing()
 
-mu = Symbol('mu')
-V_F = Symbol('V_F')
-V_P = Symbol('V_P')
+mu = Symbol("mu")
+V_F = Symbol("V_F")
+V_P = Symbol("V_P")
 
-I_F = Symbol('I_F')
+I_F = Symbol("I_F")
 
-N_F = Symbol('N_F')
-N_P = Symbol('N_P')
-n = Symbol('n')
+N_F = Symbol("N_F")
+N_P = Symbol("N_P")
+n = Symbol("n")
 
 v = mu * (n * V_F + N_P * V_P) / (n * V_F + N_P * V_P + 1)
 
@@ -28,9 +35,7 @@ pi_F_alt = mu * (
     - 1 / (N_P * V_P + N_F * V_F + 1)
 )
 pi_F_t_alt = pi_F_alt - I_F * N_F
-d_N_F_N_P = simplify(
-    pi_F_t_alt.diff(N_F) / pi_F_t_alt.diff(N_P)
-)
+d_N_F_N_P = simplify(pi_F_t_alt.diff(N_F) / pi_F_t_alt.diff(N_P))
 
 simplify((pi_F_alt).diff(N_F))
 simplify((pi_F_alt).diff(N_F).diff(N_F))
@@ -38,12 +43,7 @@ simplify((pi_F_alt).diff(N_F).diff(N_F).diff(N_F))
 
 (2 * log((N_F * V_F) / (N_P * V_P + 1) + 1)).diff(N_F)  # type: ignore
 
-plot_params = {
-    V_F: 1,
-    N_P: 0.5,
-    V_P: 1,
-    mu: 1
-}
+plot_params = {V_F: 1, N_P: 0.5, V_P: 1, mu: 1}
 plot(
     pi_F_alt.subs(plot_params),
     (N_F, 0, 10),
@@ -56,12 +56,25 @@ plot(
 
 # unfortunately the result of this has an ambiguous sign:
 simplify(
-    simplify((pi_F_alt).diff(N_F).diff(N_F) * N_F**3 * V_F * (N_F * V_F + N_P * V_P + 1) ** 3)
[…]

### 2024-05-23 src/sympy/benchmark_case.py

@@ -1,19 +1,25 @@
-from sympy import Symbol, init_printing, simplify, solve, Eq
-from sympy import sqrt
 import sympy.plotting as sp
+from sympy import (
+    Eq,
+    Symbol,
+    init_printing,
+    simplify,
+    solve,
+    sqrt,  # type: ignore
+)
 
 init_printing()
 
-mu = Symbol('mu')
-V_F = Symbol('V_F')
-V_P = Symbol('V_P')
+mu = Symbol("mu")
+V_F = Symbol("V_F")
+V_P = Symbol("V_P")
 
-I_F = Symbol('I_F')
-K_F = Symbol('K_F')
+I_F = Symbol("I_F")
+K_F = Symbol("K_F")
 
-N_F = Symbol('N_F')
-N_P = Symbol('N_P')
-n = Symbol('n')
+N_F = Symbol("N_F")
+N_P = Symbol("N_P")
+n = Symbol("n")
 
 A_eq = mu * V_F / (K_F + I_F)
 A_def = N_F * V_F + N_P * V_P + 1
@@ -48,11 +54,9 @@ plot_single = sp.plot(
     pi_P_ret.subs(params_1),
     (N_P, 0, 5),
     ylim=(0, 4),
-    show=False
+    show=False,
 )
-plot_single.append(
-    sp.plot_implicit(Eq(N_P, N_P_bar.subs(params_1)), show=False)[0]
-)
+plot_single.append(sp.plot_implicit(Eq(N_P, N_P_bar.subs(params_1)), show=False)[0])
 plot_single.show()
 
 plot_multi = sp.plot(
@@ -62,13 +66,8 @@ plot_multi = sp.plot(
     pi_P_ret.subs(params_2),
     (N_P, 0, 5),
     ylim=(0, 4),
-    show=False
+    show=False,
 )
-plot_multi.append(
-    sp.plot_implicit(Eq(N_P, N_P_bar.subs(params_1)), show=False)[0]
-)
-plot_multi.append(
-    sp.plot_implicit(Eq(N_P, N_P_bar.subs(params_2)), show=False)[0]
-)
+plot_multi.append(sp.plot_implicit(Eq(N_P, N_P_bar.subs(params_1)), show=False)[0])
+plot_multi.append(sp.plot_implicit(Eq(N_P, N_P_bar.subs(params_2)), show=False)[0])
 plot_multi.show()
-

### 2024-05-23 src/sympy/integrals.py

@@ -1,12 +1,13 @@
-from sympy import Symbol, integrate, init_printing, simplify, solve, Eq
+from sympy import Eq, Symbol, init_printing, integrate, simplify, solve
+
 init_printing()
 
-mu = Symbol('mu')
-B = Symbol('B')
-C = Symbol('C')
-Nf = Symbol('N_f')
-Np = Symbol('N_P')
-Nfbar = Symbol('\\bar N_f')
+mu = Symbol("mu")
+B = Symbol("B")
+C = Symbol("C")
+Nf = Symbol("N_f")
+Np = Symbol("N_P")
+Nfbar = Symbol("\\bar N_f")
 
 v = (Np * B + Nf * B) / (Np * B + Nf * B + 1)
 

### 2024-05-23 src/sympy/proof_of_lemma.py

@@ -1,15 +1,19 @@
-from sympy import Symbol, integrate, solve, Eq, init_printing, log, plot
+from sympy import Eq, Symbol, init_printing, integrate, log, plot, solve
 
 init_printing()
 
-x = Symbol('x')
-N_F = Symbol('N_F')
+x = Symbol("x")
+N_F = Symbol("N_F")
 f = x / (x + 1)
 
 int_f_sN = integrate(f, (x, 0, N_F)) / N_F
 
 int_1st = f.subs({x: N_F}) / N_F - int_f_sN / N_F
-int_2nd = f.diff(x).subs({x: N_F}) / N_F - 2 * f.subs({x: N_F}) / N_F**2 + 2 * int_f_sN / N_F**2
+int_2nd = (
+    f.diff(x).subs({x: N_F}) / N_F
+    - 2 * f.subs({x: N_F}) / N_F**2
+    + 2 * int_f_sN / N_F**2
+)
 
 eq_1 = Eq(f.diff(x).subs({x: N_F}), int_1st)
 eq_2 = Eq(f.diff(x, 2).subs({x: N_F}), int_2nd)
@@ -21,5 +25,4 @@ plot(eq_2.lhs, eq_2.rhs, (N_F, 2, 5))
 sol_1 = solve(eq_1, log(1 + N_F))
 sol_2 = solve(eq_2, log(1 + N_F))
 
-plot(sol_1[0], sol_2[0], log(1+N_F), (N_F, 0, 5))
-
+plot(sol_1[0], sol_2[0], log(1 + N_F), (N_F, 0, 5))

### 2024-05-23 src/paper/theory.tex
Add pre-commit hooks

@@
 My aim with this paper is both somewhat more general and much more specific in certain aspects.
-For one, I focus on the asymptotic approach, and withing that, a specific way of approximating the infinite game of interest.
+For one, I focus on the asymptotic approach, and within that, a specific way of approximating the infinite game of interest.
 This is motivated by the fact that I am not interested in the oceanic game per se, but rather in its ability to approximate finite-player games.
@@
 The first two of these paper also provides microfoundations for using the Shapley value and the weighted value in an intra-firm bargaining setting.
-The present paper contributes to this literature by generalizing some of its results, and an examinating some general properties of the various values in the context of such games.
-In particular, in addition to the aformentioned papers, the proposed model includes two new features: (1) results about the distribution of the value between the various types of fringe players, and (2) using random order values instead of the less general Shapley value or weighted value.
+The present paper contributes to this literature by generalizing some of its results, and an examination of some general properties of the various values in the context of such games.
+In particular, in addition to the aforementioned papers, the proposed model includes two new features: (1) results about the distribution of the value between the various types of fringe players, and (2) using random order values instead of the less general Shapley value or weighted value.
 Furthermore, I also provide results for the intersection of two important extensions in \textcite{stole1996intra}: the case of weighted values in the case of multiple types of fringe players.

### 2024-05-23 src/presentation/io_day.qmd
Add pre-commit hooks

@@
    - Without the platform, no value can be created
-   - Might have its own products (hybrid mdoe)
+   - Might have its own products (hybrid mode)
 :::
@@
 ::: {.fragment}
- - Assume that the platform prices its products as if they were made by seperate, competitive sellers
+ - Assume that the platform prices its products as if they were made by separate, competitive sellers
    - Possible interpretation: profit-maximizing subsidiaries

### 2024-05-23 src/figures/equilibrium_nf.py

@@ -1,5 +1,5 @@
-import numpy as np
 import matplotlib.pyplot as plt
+import numpy as np
 import typer
 
 

### 2024-05-23 src/figures/equilibrium_symbolic.py

@@ -43,15 +43,23 @@ def create_plot_data(
     f_diff_num = lambdify((N_P_sp, N_F_sp, s), f.diff(s))
 
     if bargaining == "onesided":
+
         def pi_P_scalar(N_P, N_F):
-            return quad(lambda s: f_num(N_P, N_F, s) * lambda_P * s ** (lambda_P - 1), 0, 1)[0]
+            return quad(
+                lambda s: f_num(N_P, N_F, s) * lambda_P * s ** (lambda_P - 1), 0, 1
+            )[0]
+
         def pi_F_scalar(N_P, N_F):
-            return quad(lambda s: f_diff_num(N_P, N_F, s) * s ** lambda_P, 0, 1)[0]
+            return quad(lambda s: f_diff_num(N_P, N_F, s) * s**lambda_P, 0, 1)[0]
     elif bargaining == "twosided":
+
         def pi_P_scalar(N_P, N_F):
-            return quad(lambda s: f_num(N_P, N_F, s) * lambda_P * s ** lambda_P, 0, 1)[0]
+            return quad(lambda s: f_num(N_P, N_F, s) * lambda_P * s**lambda_P, 0, 1)[0]
+
         def pi_F_scalar(N_P, N_F):
-            return quad(lambda s: f_diff_num(N_P, N_F, s) * s ** (lambda_P + 1), 0, 1)[0]
+            return quad(lambda s: f_diff_num(N_P, N_F, s) * s ** (lambda_P + 1), 0, 1)[
+                0
+            ]
     else:
         raise typer.BadParameter(f"Unknown bargaining mode: {bargaining}")
 

### 2024-05-23 src/manim_figures/comparative_equilibrium_entry.py

@@ -69,10 +69,14 @@ class Baseline(Scene):
         pi_F_orig = ax.plot(lambda x: pi_F(N_P_0, x), color=BLUE_D)
         pi_F_alt = ax.plot(lambda x: pi_F(N_P_1, x), color=RED_D)
         pi_F_orig_label = ax.get_graph_label(
-            pi_F_orig, r"\pi_F(N_P, N_F)", direction=UP  # type: ignore
+            pi_F_orig,
+            r"\pi_F(N_P, N_F)",
+            direction=UP,  # type: ignore
         )
         pi_F_alt_label = ax.get_graph_label(
-            pi_F_alt, r"\pi_F(N_P', N_F)", direction=DOWN  # type: ignore
+            pi_F_alt,
+            r"\pi_F(N_P', N_F)",
+            direction=DOWN,  # type: ignore
         )
 
         N_F_opt_0_bar = ax.get_vertical_line(N_F_opt_point_0, color=BLACK)
@@ -84,10 +88,13 @@ class Baseline(Scene):
 
         investment_cost = ax.plot(lambda x: I_F * x)
         investment_cost_label = ax.get_graph_label(
-            investment_cost, r"I_F N_F", direction=UP  # type: ignore
+            investment_cost,
+            r"I_F N_F",
+            direction=UP,  # type: ignore
         )
         brace_loss = BraceBetweenPoints(
-            N_F_opt_1_bar.get_bottom(), N_F_opt_0_bar.get_bottom()  # type: ignore
+            N_F_opt_1_bar.get_bottom(),  # type: ignore
+            N_F_opt_0_bar.get_bottom(),  # type: ignore
         )
         brace_label = MathTex(r"> N_P' - N_P", color=BLACK)
         brace_label.next_to(brace_loss, DOWN)

### 2024-05-23 src/utils/makeutils.py

@@ -1,15 +1,17 @@
-import re
-import os
-import json
 import glob
-import typer
+import json
+import os
+import re
 
+import typer
 
 app = typer.Typer()
 
 
 @app.command()
-def find_input_files(tex_file: str, remove_prefix: str = "", print_console: bool = False):
+def find_input_files(
+    tex_file: str, remove_prefix: str = "", print_console: bool = False
+):
     """Find all of the files that are included, inputted or includegraphics'
     in a tex file.
     Args:
@@ -21,7 +23,7 @@ def find_input_files(tex_file: str, remove_prefix: str = "", print_console: bool
         List[str]: the list of included files
     """
 
-    with open(tex_file, 'r') as file:
+    with open(tex_file, "r") as file:
         tex_contents = file.read()
 
     patterns = [
@@ -45,7 +47,7 @@ def find_input_files(tex_file: str, remove_prefix: str = "", print_console: bool
 
 @app.command()
 def find_manim_sections(manim_file: str, print_console: bool = False):
-    """Find all of the section names in a manim scirpt.
+    """Find all of the section names in a manim script.
     Args:
         tex_file: The path of the tex file.
         print_console: Whether to print the paths of the manim sections
@@ -53,7 +55,7 @@ def find_manim_sections(manim_file: str, print_console: bool = False):
         List[str]: the list of manim sections
     """
 
-    with open(manim_file, 'r') as file:
+    with open(manim_file, "r") as file:
         manim_contents = file.read()
 
     patterns = [
@@ -81,7 +83,7 @@ def rename_manim_sections(section_dir: str):
     os.chdir(section_dir)
     section_json = glob.glob("*.json")[0]
 
-    with open(section_json, 'r') as file:
+    with open(section_json, "r") as file:
         section_contents = json.load(file)
 
     for section in section_contents:
@@ -98,7 +100,7 @@ def find_videos(qmd_file: str, remove_prefix: str = "", print_console: bool = Fa
         List[str]: the list of video paths
     """
 
-    with open(qmd_file, 'r') as file:
+    with open(qmd_file, "r") as file:
         qmd_contents = file.read()
 
     patterns = [

### 2024-05-23 src/paper/application.tex
Spelling

@@
 Nevertheless, there is an important distinction compared to the previous results.
-While this does lead to a decrease in total surplus, in contrast to the two-sided bargaining case, this does not imply a decrese in consumer surplus.
+While this does lead to a decrease in total surplus, in contrast to the two-sided bargaining case, this does not imply a decrease in consumer surplus.
 As mentioned before, the consumers' share of total surplus is equal to the platform's profits, and thus it is increasing in $N_P$ if and only if platform profits (\cref{fig:profits_full_surplus_two_sided}) are.
@@
 The observation is that, in this situation, the platform's share is indeed higher when the fringe firms are more substitutable.
-This coincides with the intuitive idea that the platform's bargaining power is higher when it does not really mind loosing a few fringe sellers.
+This coincides with the intuitive idea that the platform's bargaining power is higher when it does not really mind losing a few fringe sellers.
 
@@
 The set of players consists of the platform plus the fringe firms: $\mathcal{N} = \{P, F_i\}, i \in [0, N_F]$.
-Because the platform is indispensible, the value of a coalition $S$ is zero without the platform, and depends on the number of fringe firms otherwise:
+Because the platform is indispensable, the value of a coalition $S$ is zero without the platform, and depends on the number of fringe firms otherwise:
 \begin{align*}
@@
         \node[align=center, below of=arrange_fringe] (foreach) {For each (remaining) fringe firm $F_i$:};
-        \node[align=center] (choose_proposer) [below=1cm of foreach] {$F_i$ or $P$ is choosen as the proposer};
+        \node[align=center] (choose_proposer) [below=1cm of foreach] {$F_i$ or $P$ is chosen as the proposer};
         \node[align=center] (proposal) [below of=choose_proposer] {Proposer proposes entry fee $K_{F_i}$};
@@
 
-\section{The platform's product pricing assumption}
-\label{sec:separate_pricing}
-
-TODO: discuss the assumptioin of pricing products separately
+% \section{The platform's product pricing assumption}
+% \label{sec:separate_pricing}
+
+% This section explores the consequences of relaxing the assumption that the platform prices its own products as if they were priced by separate entities.
+% So let us now assume, that when pricing product $P_i$, the platform does consider its effect on the sales of its other products.
+
+% For the fringe firms, the problem is the same as before: they choose their prices to maximize their profits, while not having an effect on total aggregate.
+% Thus, the price they set is the same as before: $p_{F_i} = c_{F_i} + \mu$.
+
+% The same is not the case with the platform.
+% When pricing its products, the platform must consider the effect of its prices on the sales of its other products, through its effects on the aggregate.
+% The end result is that the platform will set higher prices than under the separate pricing assumption, because it internalizes the effect of one product's price on the demand for the other products.
+% In particular, it can be shown that the optimal price for the platform's product is
+% \begin{align*}
+%     p_P^* = c_P + \mu + W_0\left( \frac{N_P V_P}{N_F V_F + 1} \right),
+% \end{align*}
+% where $W_0$ is the principal branch of the Lambert $W$ function.
+
+% Given an aggregate of size $A$, the platform's profits are
+% \begin{align*}
+%     \dots
+% \end{align*}
 

### 2024-05-23 src/paper/theory.tex
Spelling

@@
 For practical applications, the case of one indispensable player and a large number of small ones is particularly important in a number of settings.
-Examples include intra-firm ownership strutures \parencite{hart1990property}, wage bargaining \parencite{stole1996intra,stole1996organizational,levy1997individual}, collusion and mergers \parencite{segal2003collusion} and upstream-downstream supply chains \parencite{inderst2003bargaining,montez2007downstream}.
+Examples include intra-firm ownership structures \parencite{hart1990property}, wage bargaining \parencite{stole1996intra,stole1996organizational,levy1997individual}, collusion and mergers \parencite{segal2003collusion} and upstream-downstream supply chains \parencite{inderst2003bargaining,montez2007downstream}.
 The study of multi-sided markets (or platforms) is also a good fit for this modeling approach, as the platform is often assumed to be indispensable for the various sides to interact.\footnote{

### 2024-05-24 src/utils/makeutils.py
Yet another try at CI publishing

@@ -119,5 +119,88 @@ def find_videos(qmd_file: str, remove_prefix: str = "", print_console: bool = Fa
     return paths
 
 
+@app.command()
+def collect_latex_packages(
+    dep_files: list[str],
+    output_file: str = "tl_packages.txt",
+    add_biber: bool = False,
+    add_latexmk: bool = False,
+    add_manim_deps: bool = False,
+    print_console: bool = False,
+) -> set[str]:
+    """Collect all of the latex packages from the dependency files.
+    Args:
+        dep_files: The list of dependency files.
+        output_file: The path of the output file.
+    Returns:
+        List[str]: the list of latex packages
+    """
+
+    packages = set()
+
+    for dep_file in dep_files:
+        with open(dep_file, "r") as file:
+            dep_contents = file.read()
+
+        pattern = re.compile(r"\*\{package\}\{(.*?)\}")
+
+        packages.update(pattern.findall(dep_contents))
+
+    if add_biber:
+        packages.add("biber")
+
+    if add_latexmk:
+        packages.add("latexmk")
+
+    if add_manim_deps:
+        packages.update(
+            [
+                "collection-basic",
+                "amsmath",
+                "babel-english",
+                "cbfonts-fd",
+                "cm-super",
+                "ctex",
+                "doublestroke",
+                "dvisvgm",
+                "everysel",
+                "fontspec",
+                "frcursive",
+                "fundus-calligra",
+                "gnu-freefont",
+                "jknapltx",
+                "latex-bin",
+                "mathastext",
+                "microtype",
+                "ms",
+                "physics",
+                "preview",
+                "ragged2e",
+                "relsize",
+                "rsfs",
+                "setspace",
+                "standalone",
+                "tipa",
+                "wasy",
+                "wasysym",
+                "xcolor",
+                "xetex",
+                "xkeyval",
+            ]
+        )
+
+    if print_console:
+        print(f"Found {len(packages)} dependencies:")
+        for package in packages:
+            print(f" > {package}")
+
+    if output_file:
+        with open(output_file, "w") as file:
+            for package in packages:
+                file.write(package + "\n")
+
+    return packages
+
+
 if __name__ == "__main__":
     app()

### 2024-05-24 src/utils/makeutils.py
Only install latex packages that tlmgr knows about

@@ -2,6 +2,7 @@ import glob
 import json
 import os
 import re
+import subprocess
 
 import typer
 
@@ -126,6 +127,7 @@ def collect_latex_packages(
     add_biber: bool = False,
     add_latexmk: bool = False,
     add_manim_deps: bool = False,
+    check_against_tl: bool = False,
     print_console: bool = False,
 ) -> set[str]:
     """Collect all of the latex packages from the dependency files.
@@ -188,6 +190,14 @@ def collect_latex_packages(
                 "xkeyval",
             ]
         )
+
+    if check_against_tl:
+        tl_packages = set(
+            subprocess.getoutput("tlmgr --verify-repo=none info --data=name").split(
+                "\n"
+            )
+        )
+        packages &= tl_packages
 
     if print_console:
         print(f"Found {len(packages)} dependencies:")

### 2024-05-24 src/utils/makeutils.py
Maybe handle tex dependencies properly now?

@@ -4,6 +4,7 @@ import os
 import re
 import subprocess
 
+import requests
 import typer
 
 app = typer.Typer()
@@ -129,7 +130,7 @@ def collect_latex_packages(
     add_manim_deps: bool = False,
     check_against_tl: bool = False,
     print_console: bool = False,
-) -> set[str]:
+) -> list[str]:
     """Collect all of the latex packages from the dependency files.
     Args:
         dep_files: The list of dependency files.
@@ -138,7 +139,7 @@ def collect_latex_packages(
         List[str]: the list of latex packages
     """
 
-    packages = set()
+    deps = set()
 
     for dep_file in dep_files:
         with open(dep_file, "r") as file:
@@ -146,16 +147,16 @@ def collect_latex_packages(
 
         pattern = re.compile(r"\*\{package\}\{(.*?)\}")
 
-        packages.update(pattern.findall(dep_contents))
+        deps.update(pattern.findall(dep_contents))
 
     if add_biber:
-        packages.add("biber")
+        deps.add("biber")
 
     if add_latexmk:
-        packages.add("latexmk")
+        deps.add("latexmk")
 
     if add_manim_deps:
-        packages.update(
+        deps.update(
             [
                 "collection-basic",
                 "amsmath",
@@ -191,6 +192,18 @@ def collect_latex_packages(
             ]
         )
 
+    packages = set()
+    for dep in deps:
+        req = requests.get(f"https://www.ctan.org/json/2.0/pkg/{dep}")
+        if req.status_code == 200:
+            package_data = json.loads(req.text)
+            if "texlive" in package_data:
+                packages.add(package_data["texlive"])
+            else:
+                print(f"No texlive package found for package {dep}")
+        else:
+            print(f"Package {dep} not found on CTAN")
+
     if check_against_tl:
         tl_packages = set(
             subprocess.getoutput("tlmgr --verify-repo=none info --data=name").split(
@@ -199,17 +212,19 @@ def collect_latex_packages(
         )
         packages &= tl_packages
 
+    package_list = sorted(list(packages))
+
     if print_console:
-        print(f"Found {len(packages)} dependencies:")
-        for package in packages:
+        print(f"Found {len(package_list)} dependencies:")
+        for package in package_list:
             print(f" > {package}")
 
     if output_file:
         with open(output_file, "w") as file:
-            for package in packages:
+            for package in package_list:
                 file.write(package + "\n")
 
-    return packages
+    return package_list
 
 
 if __name__ == "__main__":

### 2024-05-24 src/manim_figures/equilibrium_outcomes.py
Fix manim figure

@@ -22,7 +22,9 @@ from manim import (
 
 class Baseline(Scene):
     def construct(self):
-        data = pd.read_csv("out/figures/equilibrium.csv")
+        data = pd.read_csv(
+            "out/figures/equilibrium_profit_onesided_scale-1_lambda-1.csv"
+        )
 
         self.next_section("draw_graph")
 
@@ -36,8 +38,8 @@ class Baseline(Scene):
 
         # Create plane
         ax = Axes(
-            x_range=[0, 1.5, 0.015],
-            y_range=[0, 2.5, 0.02],
+            x_range=[0, 5.3, 0.05],
+            y_range=[0, 4.1, 0.05],
             x_length=11,
             y_length=7,
             x_axis_config={"include_ticks": False},
@@ -50,19 +52,19 @@ class Baseline(Scene):
         # Destiniations
         A_noF = ax.plot_line_graph(
             x_values=data["N_P"],
-            y_values=data["CS_noF"],
+            y_values=data["CS_noF"] * 2,
             line_color=BLACK,  # type: ignore
             add_vertex_dots=False,
         )
         A_bench = ax.plot_line_graph(
             data["N_P"],
-            data["CS_bench"],
+            data["CS_bench"] * 2,
             line_color=BLUE_D,  # type: ignore
             add_vertex_dots=False,
         )
         A_barg = ax.plot_line_graph(
             data["N_P"],
-            data["CS"],
+            data["CS"] * 2,
             line_color=RED_D,  # type: ignore
             add_vertex_dots=False,
         )
@@ -99,9 +101,9 @@ class Baseline(Scene):
         legend_bench = MathTex(r"\text{Benchmark}", color=BLUE_D)  # type: ignore
         legend_barg = MathTex(r"\text{Bargaining}", color=RED_D)  # type: ignore
 
-        legend_noF.next_to(ax.c2p(1, 2.5), RIGHT + DOWN)  # type: ignore
-        legend_bench.next_to(ax.c2p(1, 2.3), RIGHT + DOWN)  # type: ignore
-        legend_barg.next_to(ax.c2p(1, 2.1), RIGHT + DOWN)  # type: ignore
+        legend_noF.next_to(ax.c2p(3.5, 4), RIGHT + DOWN)  # type: ignore
+        legend_bench.next_to(ax.c2p(3.5, 3.7), RIGHT + DOWN)  # type: ignore
[…]

### 2024-05-25 src/paper/application.tex
Switch to pixi and tectonic
Yet another try at CI publishing
Integrate the timing graph better

@@
 \usepackage{setspace}
+\usepackage{snapshot}
 \usepackage[backend=biber,style=authoryear,maxbibnames=99,hyperref=true]{biblatex}
@@
 
-In the benchmark model, the game starts by the platform announcing and committing to an entry fee $K_F$.\footnote{
+The timing of the two models is illustrated in \cref{fig:timing}.
+In the benchmark model (\cref{fig:timing_benchmark}), the game starts by the platform announcing and committing to an entry fee $K_F$ ($\mathbf{T_1}$).\footnote{
     With no commitment power, but the ability to set any prices after fringe firms make their investment decisions, the platform would charge an entry fee that would make the fringe profits zero \emph{sans the investment cost}.
@@
 }
-In the bargaining case, the platform cannot commit to entry fees at this point.
-Next, each fringe firm decides whether to create a product at cost $I_F$ and enter the market.
-In the bargaining model, the entry fee is decided at this point as a result of some negotiation\footnote{
+Next, each fringe firm decides whether to create a product at cost $I_F$ and enter the market. ($\mathbf{T_2}$)
+After that, the platform and the fringe firms simultaneously choose the prices for their products, engaging in monopolistic competition ($\mathbf{T_3}$).
+Finally, consumers make their purchase decisions, and profits are realized ($\mathbf{T_3}$).
+
+The bargaining model has a slightly different timing, as shown in \cref{fig:timing_bargaining}.
+The platform cannot commit to an entry fee at the beginning, so the game starts with the fringe firms deciding whether to invest in creating a product at cost $I_F$ ($\mathbf{T_1}$).
+After that, the entry fee is decided as a result of some negotiation\footnote{
     The negotiation process, or rather its outcome is described in detail in \cref{sec:cooperative_game}.
-} between the platform and the firms that have made the investment.
-After this, the firms that made the investment pay the platform entry fees, too.
-
-From this point on, the game proceeds in the same way in both models.
-The platform and the fringe firms simultaneously choose the prices for their products, engaging in monopolistic competition.
-Finally, consumers make their purchase decisions, and profits are realized.
-
-In the model with bargaining, the platform and the fringe distribute total profits according to their Shapley values.
-One can also think of the latter as agreeing on an entry fee that makes final profits net entry fees equal to the Shapley value of the various players.
+} between the platform and the firms that have made the investment ($\mathbf{T_2}$).
+Then, the firms that made the investment pay the platform entry fees, too.
+From this point on, the game proceeds in the same way as in the benchmark model: the platform and the fringe firms set their prices ($\mathbf{T_3}$), and consumers make their purchase decisions ($\mathbf{T_4}$).
 
@@
 On the other hand, in the bargaining model, I assume that the entry fee is the result of a negotiation between the parties.
-\Cref{fig:timing} illustrates this difference.
+More precisely, in the latter case, I assume that the platform's and the fringe's total profits at the end of the game correspond to their Shapley values.
+This in turn uniquely determines the entry fee, and thus the negotiation at time ($\mathbf{T_2}$) can be equivalently conceptualized as bargaining over the final profit as well as the entry fee.
 
@@
         \begin{tikzpicture}[node distance=2cm, auto]
-            \node[align=center] (entry_fee) {Platform unilaterally sets the entry fee \\ $[K_F]$};
-            \node[align=center] (entry_decision) [below of=entry_fee] {Potential entrants decide to enter \\ at cost $I_F + K_F$ \\ $[N_F]$};
-            \node[align=center] (sales) [below of=entry_decision] {Platform and fringe sell products \\ $[\pi_{Fi}^v, \pi_P^v]$};
-            \node[align=center] (final) [below of=sales] {Final profits are realized \\ $[\pi_{Fi}^t, \pi_P^t]$};
+            \node[align=center] (entry_fee) {($\mathbf{T_1}$) Platform unilaterally \\ sets the entry fee \\ $[K_F]$};
+            \node[align=center] (entry_decision) [below of=entry_fee] {($\mathbf{T_2}$) Potential entrants decide to \\ enter at cost $I_F + K_F$ \\ $[N_F]$};
+            \node[align=center] (sales) [below of=entry_decision] {($\mathbf{T_3}$) Platform and fringe sell products \\ $[\pi_{Fi}^v, \pi_P^v]$};
+            \node[align=center] (final) [below of=sales] {($\mathbf{T_4}$) Final profits are realized \\ $[\pi_{Fi}^t, \pi_P^t]$};
             \draw[->] (entry_fee) -- (entry_decision);
@@
         \caption{Benchmark model (platform sets the entry fee unilaterally)}
+        \label{fig:timing_benchmark}
     \end{subfigure}
@@
         \begin{tikzpicture}[node distance=2cm, auto]
-            \node[align=center] (entry_decision) {Potential entrants decide to invest \\ at cost $I_F$ \\ $[N_F]$};
-            \node[align=center] (entry_fee) [below of=entry_decision] {Entry fees are negotiated \\ between platform and $N_F$ fringe firms \\ $[K_F]$};
-            \node[align=center] (sales) [below of=entry_fee] {Platform and fringe sell products \\ $[\pi_{Fi}^v, \pi_P^v]$};
-            \node[align=center] (final) [below of=sales] {Final profits are realized \\ $[\pi_{Fi}^t, \pi_P^t]$};
+            \node[align=center] (entry_decision) {($\mathbf{T_1}$) Potential entrants decide to invest \\ at cost $I_F$ \\ $[N_F]$};
+            \node[align=center] (entry_fee) [below of=entry_decision] {($\mathbf{T_2}$) Entry fees are negotiated \\ between platform and $N_F$ fringe firms \\ $[K_F]$};
+            \node[align=center] (sales) [below of=entry_fee] {($\mathbf{T_3}$) Platform and fringe sell products \\ $[\pi_{Fi}^v, \pi_P^v]$};
+            \node[align=center] (final) [below of=sales] {($\mathbf{T_4}$) Final profits are realized \\ $[\pi_{Fi}^t, \pi_P^t]$};
             \draw[->] (entry_decision) -- (entry_fee);
@@
         \caption{Bargaining model (platform and fringe negotiate over the entry fee)}
+        \label{fig:timing_bargaining}
     \end{subfigure}
@@
     The function is strictly concave in $K_F$, so the first order condition is sufficient for optimality in the case of an interior solution.
-    Assume that that the optimum is indeed interior.
+    Assume that the optimum is indeed interior.
     Then the FOC is

### 2024-05-25 src/paper/application.tex
Make clear what is endogeneous

@@
 The timing of the two models is illustrated in \cref{fig:timing}.
+The square brackets indicate the endogenous variables decided at that stage of the game.
 In the benchmark model (\cref{fig:timing_benchmark}), the game starts by the platform announcing and committing to an entry fee $K_F$ ($\mathbf{T_1}$).\footnote{
@@
             \node[align=center] (entry_decision) [below of=entry_fee] {($\mathbf{T_2}$) Potential entrants decide to \\ enter at cost $I_F + K_F$ \\ $[N_F]$};
-            \node[align=center] (sales) [below of=entry_decision] {($\mathbf{T_3}$) Platform and fringe sell products \\ $[\pi_{Fi}^v, \pi_P^v]$};
-            \node[align=center] (final) [below of=sales] {($\mathbf{T_4}$) Final profits are realized \\ $[\pi_{Fi}^t, \pi_P^t]$};
+            \node[align=center] (sales) [below of=entry_decision] {($\mathbf{T_3}$) Platform and fringe set product prices \\ $[p_{P_i}, p_{F_i}]$};
+            \node[align=center] (final) [below of=sales] {($\mathbf{T_4}$) Consumers make consumption decisions \\ $[x_{P_i}, x_{F_i}]$};
             \draw[->] (entry_fee) -- (entry_decision);
@@
             \node[align=center] (entry_fee) [below of=entry_decision] {($\mathbf{T_2}$) Entry fees are negotiated \\ between platform and $N_F$ fringe firms \\ $[K_F]$};
-            \node[align=center] (sales) [below of=entry_fee] {($\mathbf{T_3}$) Platform and fringe sell products \\ $[\pi_{Fi}^v, \pi_P^v]$};
-            \node[align=center] (final) [below of=sales] {($\mathbf{T_4}$) Final profits are realized \\ $[\pi_{Fi}^t, \pi_P^t]$};
+            \node[align=center] (sales) [below of=entry_fee] {($\mathbf{T_3}$) Platform and fringe set product prices \\ $[\pi_{Fi}^v, \pi_P^v]$};
+            \node[align=center] (final) [below of=sales] {($\mathbf{T_4}$) Consumers make consumption decisions \\ $[\pi_{Fi}^t, \pi_P^t]$};
             \draw[->] (entry_decision) -- (entry_fee);
@@
 \end{figure}
+
+The (subgame perfect) equilibrium of this game is defined as follows.
+\begin{definition}
+    \label{def:equilibrium}
+    An equilibrium of the game is a tuple $(N_F, K_F, p_{P_i}, p_{F_i}, x_{P_i}, x_{F_i})$ such that:
+    \begin{enumerate}
+        \item The fringe entrants make zero total profits (including the investment cost $I_F$ and the entry fee $K_F$).
+        \item The platform's entry fee $K_F$ is such that
+        \begin{description}
+            \item[benchmark case:] they maximize total platform profits;
+            \item[bargaining case:] total platform profits are equal to the Shapley value of the platform.
+        \end{description}
+        \item Product prices $p_{F_i}$ and $p_{P_i}$ are such that they maximize per-product profits, given the products on the market ($P_i, i \in [0, N_P]$ and $F_i, i \in [0, N_F]$).
+        \item $x_{F_i}$ and $x_{P_i}$ are the outcome of consumers maximizing their utility, given the prices.
+    \end{enumerate}
+\end{definition}
 
@@
         \node[align=center, draw, dashed] (entry_fee) [below of=entry_decision] {Entry fees are negotiated \\ between platform \\ and $N_F$ fringe firms \\ $[K_F]$};
-        \node[align=center] (sales) [below of=entry_fee] {Platform and fringe \\ sell products \\ $[\pi_{Fi}^v, \pi_P^v]$};
-        \node[align=center] (final) [below of=sales] {Final profits are realized \\ $[\pi_{Fi}^t, \pi_P^t]$};
+        \node[align=center] (sales) [below of=entry_fee] {Platform and fringe \\ set product prices \\ $[p_{P_i}, p_{F_i}]$};
+        \node[align=center] (final) [below of=sales] {Consumers make \\ consumption decisions \\ $[x_{P_i}, x_{F_i}]$};
         \draw[->] (entry_decision) -- (entry_fee);

### 2024-05-26 src/paper/application.tex
Separate assumptions and discussion

@@
 
-Assume that there are two types of players in the market: a platform $P$, a continuum of fringe sellers $F_i$ ($i \in [0, N_F$]) and a continuum of consumers $C_j$ ($j \in [0, 1]$).
+Assume that there are two types of players in the market: a platform $P$, a continuum of fringe sellers $F_i$ ($i \in \mathbb{R}^+$) and a continuum of consumers $C_j$ ($j \in [0, 1]$).
 The fringe firms have one product each, which they can only sell through the platform.
@@
 
-\subsection{Overview}
-
-There is an infinite measure of fringe firms, who are deciding whether to enter the market.
-Entering has two, separate costs: an exogenous investment cost $I_F$, and the lump-sum platform entry fee $K_F$.
-One can conceptualize the first as usual fixed costs, such as the cost of setting up production, or designing a product.
-Meanwhile, the second is a payment to the platform for using its services.
-While percentage fees are more common both in the literature and in practice, I assume a lump-sum fee for a few reasons.
-First, and most importantly, revenue-based fees enter the entrants' pricing decision, and thus create a channel through which platforms distort competition.
-I want to show that even in the absence such distortions, hybrid platforms can have a significant impact on competition.
-Furthermore, due to this distortion, the resulting game could not be represented as a transferable utility game, and the proposed solution concept would not be applicable.
-Finally, lump-sum fees do make sense in settings when individual negotiation takes place and contracts are not standardized.
-
-The timing of the two models is illustrated in \cref{fig:timing}.
+The rest of this section is structured as follows.
+\Cref{sec:model_overview} provides an overview of the model's stages, the timing of the game, as well as the qeuilibrium concept used in this paper.
+Then, \cref{sec:model_details} describes each stage of the game formally.
+Finally, \cref{sec:model_discussion} discusses some of the assumptions made in the model, and their implications.
+
+\subsection{Overview and timing}
+\label{sec:model_overview}
+
+I consider two versions of the model: a benchmark case with the platform setting the entry fee unilaterally, and a bargaining model where the platform and the fringe firms negotiate over the entry fee.
+Each version has four main stages corresponding to determining four sets of endogenous variables: (1) the platform (and the fringe) setting (negotiating) the entry fee, (2) the fringe firms deciding whether to enter the market, (3) the platform and the fringe setting the prices of their products, and (4) consumers making their purchase decisions.
+The main difference between them lies in how the entry fee is determined, and, correspondingly, the order of the first two stages.
+
+The timing of both models is illustrated in \cref{fig:timing}.
 The square brackets indicate the endogenous variables decided at that stage of the game.
@@
         \begin{tikzpicture}[node distance=2cm, auto]
-            \node[align=center] (entry_fee) {($\mathbf{T_1}$) Platform unilaterally \\ sets the entry fee \\ $[K_F]$};
+            \node[align=center] (entry_fee) {($\mathbf{T_1}$) Platform unilaterally sets \\ the entry fee \\ $[K_F]$};
             \node[align=center] (entry_decision) [below of=entry_fee] {($\mathbf{T_2}$) Potential entrants decide to \\ enter at cost $I_F + K_F$ \\ $[N_F]$};
@@
 
-The (subgame perfect) equilibrium of this game is defined as follows.
+For both models, this structure corresponds to a perfect-information extensive-form game.
+As a consequence, the solution concept I use is the subgame perfect equilibrium.
+As the platform's product variety ($N_P$) is assumed to be exogenous, the only strategic variables are (1) the fringe players' entry decisions, (2) the platform's entry fee (only in the benchmark model), (3) the prices of the products and (4) the consumers' purchase decisions.
+
+In these two specific games, the subgame perfect can be charactrerized as follows.
 \begin{definition}
@@
 
-In the rest of this section, I describe each step in detail, starting from the end of the game and working my way back to the beginning.
-
-\subsection{Demand}
+\subsection{Details}
+\label{sec:model_details}
+
+Let us now describe each stage of the game in more detail.
+I start with the final two subgames, as they are identical in both models.
+Then I describe how entry fees and fringe entry is determined first in the benchmark model, and then highlight the differences in the bargaining model.
+
+\subsubsection{Demand}
 \label{sec:demand}
@@
 The price of the outside option is normalized to zero.
+
+\subsubsection{Fringe entry and platform fees}
+
+\paragraph{Benchmark case}
+
+I assume that there is a continuum of potential fringe entrants, indexed by $i \in \mathbb{R}^+_0$.
+Each of them can create a product at an exogenous investment cost $I_F$.
+If they decide not to, they make zero profits and do not participate in the later stages of the game.
+Furthermore, these firms can only sell their products through the platform, for which the platform can charge a lump-sum entry fee $K_F$.
+The timing of these decisions is as follows: (1) the platform sets and commits to an entry fee $K_F$, (2) the fringe firms decide whether to enter the market, and (3) the firms that have entered pay the entry fee to the platform.
+
+\paragraph{Bargaining case}
+\label{sec:model_bargaining}
+
+In contrast to the benchmark model, in this case, the platform cannot commit to an entry fee: it is decided as a result of a negotiation between the platform and the fringe firms.
+In order to keep the model tractable, I model this in a reduced-form manner: I assume that the platform and the entrants agree on an entry fee $K_F$, which makes the total profits net entry fees equal to the Shapley value of the players.
+Due to this assumption, the timing of the model is also slightly different.
+First, the fringe firms decide whether to invest in creating a product at cost $I_F$.
+After this, the platform and the firms that have made the investment negotiate the entry fee.
+Finally, the firms that have entered pay the entry fee to the platform.
+
+In practice, the resulting entry fees look as follows.
+Assume that $N_F$ fringe firms choose to invest in creating a product in the first stage of the game.
+Now, for every $s N_F$ ($s \in [0, 1]$), calculate the total profits that would be realized if the platform and $n_f$ fringe firms were the only players in the market, and they engaged in monopolistic competition as described in the previous paragraph.
+Let us denote these profits by $\pi^v_{F}(N_P,s N_F)$ and $\pi^v_{P}(N_P,s N_F)$, and the corresponding industry-wide total profits by $\Pi$ and $\Pi(N_P,s N_F, N_C)$.
+
+\begin{proposition}
+    \label{prop:shapley_value}
+    The Shapley value of the platform and the fringe firms, and thus final total profits, are given by:
+    \begin{align*}
+        \pi^t_P(N_P, N_F) &= N_C \int_0^1 \Pi(N_P,s N_F) \ds, \\
+        \pi^t_F(N_P, N_F) &= N_C \int_0^1 \partial_2 N_F \Pi(N_P,s N_F) \ds.
+    \end{align*}
+\end{proposition}
+
+\subsection{Discussion}
+\label{sec:model_discussion}
+
+Let us now discuss some of the non-standard assumptions made in the model, and their implications.
+I look at four main categories in this section: the timing of the game, the costs of entry for fringe firms, the way the monopolistic competition is modeled, and the way the bargaining process is modeled.
+
+\subsubsection{Costs of entry}
+
+For each potential fringe entrant $F_i$, entering the marker has two, separate costs: an exogenous investment cost $I_F$, and the lump-sum platform entry fee $K_F$.
+One can conceptualize the first one, $I_F$, as usual fixed costs, such as the cost of setting up production, or designing a product.
+Without it, fringe firms would always make positive profits in the bargaining model, and therefore the free entry equilibrium would not exist.
+Furthermore, it is a quite reasonable assumption in most settings, as some of the costs of entering the market are sunk, and not paid to the platform.
+
+Meanwhile, the second cost, $K_F$, is a payment to the platform for using its services.
+While percentage fees are more common both in the literature and in practice, I assume a lump-sum fee for a few reasons.
+First, and most importantly, revenue-based fees enter the entrants' pricing decision, and thus create a channel through which platforms distort competition.
+I want to show that even in the absence such distortions, hybrid platforms can have a significant impact on competition.
+Furthermore, due to this distortion, the resulting game could not be represented as a transferable utility game, and the proposed solution concept would not be applicable.
+Finally, lump-sum fees do make sense in settings when individual negotiation takes place and contracts are not standardized.
+
+\subsubsection{Timing of the game}
+
+% TODO
+
+\subsubsection{Product pricing}
 
@@
 Therefore, this assumption can be seen as a best-case scenario for consumers, and the results can be interpreted as a lower bound on the negative effects of hybrid operation.
-For a more thorough discussion of this assumption, see \cref{sec:separate_pricing}.
+For a more thorough discussion of this assumption, see.
 
@@
 
-\subsection{Fringe entry and platform fees}
-
-\subsubsection{Benchmark case}
-
-I assume that there is a continuum of potential fringe entrants, indexed by $i \in \mathbb{R}^+_0$.
-Each of them can create a product at an exogenous investment cost $I_F$.
-If they decide not to, they make zero profits and do not participate in the later stages of the game.
-Furthermore, these firms can only sell their products through the platform, for which the platform can charge a lump-sum entry fee $K_F$.
-The timing of these decisions is as follows: (1) the platform sets and commits to an entry fee $K_F$, (2) the fringe firms decide whether to enter the market, and (3) the firms that have entered pay the entry fee to the platform.
-
-\subsubsection{Bargaining case}
-\label{sec:model_bargaining}
-
-In contrast to the benchmark model, in this case, the platform cannot commit to an entry fee: it is decided as a result of a negotiation between the platform and the fringe firms.
-For this reason, the timing of the model is also different.
-First, the fringe firms decide whether to invest in creating a product at cost $I_F$.
-After this, the platform and the firms that have made the investment negotiate the entry fee.
-Finally, the firms that have entered pay the entry fee to the platform.
-
-In order to keep the model tractable I model the negotiation process in a reduced form manner.
-In particular, I assume that the platform and the entrants agree on an entry fee $K_F$, which makes the total profits net entry fees equal to the Shapley value of the players.\footnote{
-    One simple extension would be to use the more general concept of random order values \parencite{weber1988probabilistic}.
+\subsubsection{Bargaining over the platform entry fee}
+
+Although the main reason for utilizing cooperative game theory in this model is tractability, it is by no means the only one.
+This way of modelling bargaining outcomes has many precedents in the industrial organization literature \parencite[e.g.][]{montez2007downstream,hart1990property,levy1997individual,inderst2003bargaining,brugemann2019intra}
+Furthermore, it has a number of appealing properties.
+For example, it is closely related to the marginal contributions of the players to the total value, and, as shown in \cref{sec:more_general_results}, it is also quite intuitive in terms of comparative statistics.
+Furthermore, and perhaps more importantly, there are a number of ways to place it on non-cooperative microfoundations by setting up non-cooperative games for which the Shapley value is a subgame perfect equilibrium \parencite[e.g.][]{gul1989bargaining,hart1996bargaining,stole1996organizational}.
+\Cref{sec:bargaining_microfoundation} provides an example on how this specific model can be placed on such microfoundations.
+The subgame perfect equilibrium of the fully non-cooperative model described in that section coincides with the equilibrium of the bargaining model in the main text.
+Therefore, if one is uncomfortable with the cooperative elements in the model, they can simply think of it as a more tractable representation of the one from \cref{sec:bargaining_microfoundation}.
+
+Let us also discuss the specifics of the cooperative game of which the Shapley value is calculated.
+For the Shapley value (or any other cooperative solution concept) to be well-defined, the corresponding coalitional game must be precisely specified, as well.
+\Cref{sec:cooperative_game} describes it in detail. 
+In short, the idea is the following: given any subset of the players (coalition), players can predict total, industry-wide profits, as the pricing subgame has a unique subgame perfect equilibrium for any subset of the players.
+This total profit is taken as the value of that coalition, thus defining a characteristic function.
+Then, according to the definition of the Shappley value, every firm (including the platform) will get their average marginal contribution this industry-wide profit (with the average taken over all possible orderings of the firms).
+
+One simple extension of this bargaining process would be to use the more general concept of random order values \parencite{weber1988probabilistic}.
+\textcite{stancsics2023bargaining} examines this solution concept for a similar game, but in a more more abstract setting.
 \Cref{sec:cooperative_game_weighted} takes a step in this direction by introducing bargaining weights and utilizing the weighted value.
-}
-This way of modelling bargaining outcomes has many precedents in the industrial organization literature \parencite[e.g.][]{montez2007downstream,hart1990property,levy1997individual,inderst2003bargaining,brugemann2019intra} and has a number of appealing properties.
-For example, it is closely related to the marginal contributions of the players to the total value, and, as it will be shown, it is also quite intuitive in terms of comparative statistics.
-Furthermore, and perhaps more importantly, there are a number of ways to place it on non-cooperative microfoundations by setting up non-cooperative games for which the Shapley value is a subgame perfect equilibrium \parencite[e.g.][]{gul1989bargaining,hart1996bargaining,stole1996organizational}.\footnote{
-    For a possible microfoundation of this specific model, see \cref{sec:bargaining_microfoundation}.
-}
-
-For the Shapley value (or any other cooperative solution concept) to be well-defined, the corresponding coalitional game must be specified.
-\Cref{sec:cooperative_game} describes it in detail, but in short, the idea is the following: given any subset of the players (coalition), players can predict total, industry-wide profits assuming the monopolistic competition described previously.
-This is taken as the value of that coalition, thus defining a characteristic function.
-Then, every firm (including the platform) will get their average marginal contribution this industry-wide profit (with the average taken over all possible orderings of the firms).
-
-In practice, it looks like the following.
-Assume that $N_F$ fringe firms choose to invest in creating a product in the first stage of the game.
-Now, for every $s N_F$ ($s \in [0, 1]$), calculate the total profits that would be realized if the platform and $n_f$ fringe firms were the only players in the market, and they engaged in monopolistic competition as described in the previous paragraph.
-Let us denote these profits by $\pi^v_{F}(N_P,s N_F)$ and $\pi^v_{P}(N_P,s N_F)$, and the corresponding industry-wide total profits by $\Pi$ and $\Pi(N_P,s N_F, N_C)$.
-
-\begin{proposition}
-    \label{prop:shapley_value}
-    The Shapley value of the platform and the fringe firms, and thus final total profits, are given by:
-    \begin{align*}
-        \pi^t_P(N_P, N_F) &= N_C \int_0^1 \Pi(N_P,s N_F) \ds, \\
-        \pi^t_F(N_P, N_F) &= N_C \int_0^1 \partial_2 N_F \Pi(N_P,s N_F) \ds.
-    \end{align*}
-\end{proposition}
-
-\subsection{Equilibrium}
-
-For both models, the previous sections describe a perfect-information extensive-form game.
-As a consequence, the solution concept I use is the subgame perfect equilibrium.
-As the platform's product variety ($N_P$) is assumed to be exogenous, the only strategic variables are (1) the fringe players' entry decisions, (2) the platform's entry fee (only in the benchmark model), and (3) the prices of the products.
-
-Furthermore, the game can be solved via straightforward backward induction.
-In both models, the final subgame is simply a game of monopolistic competition with horizontally differentiated products.
-In the benchmark model, it is preceded by the platform setting the entry fee, while in the bargaining model the entry fee is set according to the previously described rule (which in turn can be motivated by an extensive form game).
-Finally, the first stage of the game is the fringe firms' investment decision.
-Due to the outside option being normalized to zero, the fringe firms will enter the market if and only if the expected profits from doing so are positive, leading to the usual free entry condition.
 

### 2024-05-26 src/paper/application.tex
Add simple homepage
Add discussion of timing

@@
 The square brackets indicate the endogenous variables decided at that stage of the game.
-In the benchmark model (\cref{fig:timing_benchmark}), the game starts by the platform announcing and committing to an entry fee $K_F$ ($\mathbf{T_1}$).\footnote{
-    With no commitment power, but the ability to set any prices after fringe firms make their investment decisions, the platform would charge an entry fee that would make the fringe profits zero \emph{sans the investment cost}.
-    This would lead to a trivial equilibrium, where no firm enters.
-}
+In the benchmark model (\cref{fig:timing_benchmark}), the game starts by the platform announcing and committing to an entry fee $K_F$ ($\mathbf{T_1}$).
 Next, each fringe firm decides whether to create a product at cost $I_F$ and enter the market. ($\mathbf{T_2}$)
@@
 
-% TODO
+The timing of the two models are intended to be as similar as possible.
+The only difference is in the order of the first two stages, which is necessary due to the nature of the two different entry fee setting mechanisms.
+
+In the case of the benchmark model, if the platform set entry fees after fringe firms make their investment decisions, the platform would charge an entry fee that would make the fringe profits zero \emph{sans the investment cost}.
+This would lead to negative fringe profits, and thus to a trivial equilibrium, where no firm enters.
+Therefore, entry fee setting must come before the fringe firms' investment decisions.
+
+Contrary to this, in the bargaining model, the opposite order is necessary.
+This is because the entry fee is the result of a negotiation, so by the time the negotiation takes place, it must already be clear which firms are engaging in it.
+Otherwise, the bargaining process (either in its cooperative, reduced-form version, or in the non-cooperative, extensive form one) would not be well defined.
+Therefore, the fringe firm's entry decisions\footnote{
+    With respect to creating a product.
+    Entering the platform and paying the entry fee is a separate decision, which takes place during the negotiation.
+} must come before the determination of the entry fee.
 
@@
 
-The statements of these theorems are illustrated in \cref{fig:comparative_N_F} and \cref{fig:welfare_aggregate} and \cref{fig:platform_profits}.
+The statements of these theorems are illustrated in \cref{fig:comparative_N_F,fig:welfare_aggregate,fig:platform_profits}.
 The intuition behind these results can be demonstrated by looking at entry fees.

### 2024-05-26 src/paper/application.tex
Extra justification for pricing assumption

@@
 
-Finally, this assumption is not as unrealistic as it might seem at first.
+A number of other papers using the same demand system \parencite[e.g.][]{anderson2020aggregative,anderson2021hybrid} achieve essentially the same outcome by relying on the timing of the model.
+Specifically, if the platform sets product prices before the fringe firms make their entry decisions, the aggregate demand will not depend on the platform's product prices\footnote{
+    At least in the hybrid regime.
+    The optimum in the pure retailer regime is somewhat different.
+}.
+This in turn means that the platform will optimally price its products as if they were produced by separate sellers.
+In the current paper, such a timing would be problematic, because the aim is to keep the benchmark and bargaining models as similar as possible.
+It would be unrealistic to assume that the platform can commit to prices before the fringe firms make their investment decisions, while at the same time it cannot commit to an entry fee in the latter model.
+
+Finally, even taken at face value, this assumption about the platform's pricing is not as unrealistic as it might seem at first.
 For example, the platform might be producing its products through a number of subsidiaries, which are legally separate entities, thus having no control over operational decisions, but still getting the profits from the sales.

### 2024-05-26 src/paper/application.tex
Explain notation better

@@
 They choose from a continuum of products, which are either produced by the fringe (indexed by $F_i$), by the platform ($P_i$) and a unit mass of outside options ($0_i$).
-Customer $j$ derives the following utility from buying product $T_i$:
+Customer $j$ derives the following utility from buying product $T_i$\footnote{
+    To avoid duplication, I denote the different types of products by $T_i$, where $T \in \{F, P, 0\}$ (fringe products, platform profucts, and outside options, respectively).
+    This notation is used throughout the paper for other variables having fringe and platform counterparts, as well.
+}:
 \begin{align*}
@@
 Now, for every $s N_F$ ($s \in [0, 1]$), calculate the total profits that would be realized if the platform and $n_f$ fringe firms were the only players in the market, and they engaged in monopolistic competition as described in the previous paragraph.
-Let us denote these profits by $\pi^v_{F}(N_P,s N_F)$ and $\pi^v_{P}(N_P,s N_F)$, and the corresponding industry-wide total profits by $\Pi$ and $\Pi(N_P,s N_F, N_C)$.
+Let us denote these profits by $\pi^v_{F}(N_P,s N_F)$ and $\pi^v_{P}(N_P,s N_F)$, and the corresponding industry-wide total profits by $\Pi$ and $\Pi(N_P,s N_F, N_C)$.\footnote{
+    Throughout this paper, I use the notation $\pi_T$ to denote the profits realized by player(s) $T$, and $\Pi$ to denote the total industry profits.
+    Furthermore, $\pi^v_T$ denotes profits from sales (i.e., profits not including investment costs and entry fees), whereas $\pi^t_T$ stands for total profits.
+}
 

### 2024-05-27 src/paper/application.tex
Remove stale todos
Talk more about marginal contributions

@@
 This total profit is taken as the value of that coalition, thus defining a characteristic function.
-Then, according to the definition of the Shappley value, every firm (including the platform) will get their average marginal contribution this industry-wide profit (with the average taken over all possible orderings of the firms).
+Then, according to the definition of the Shapley value, every firm (including the platform) will get their average marginal contribution this industry-wide profit (with the average taken over all possible orderings of the firms).
 
@@
 That is, these limits correspond to the platform either receiving or making take-it or leave-it offers.
-
-\textcolor{red}{TODO: can I show a result analogous to \cref{lem:shape_of_fringe_profit} still holds for any $\lambda_P$? If not, focus on a specific case, such as the one on the graphs.}
 
@@
     Let $w_P, w_F: \mathbb{R}^+_0 \to \mathbb{R}^+_0$ be non-negative functions such that the following condition holds: $\pi_P(N_P, N_F, N_C) + \pi_F(N_P, N_F, N_C) \leq \Pi(N_P, N_F, N_C)$.
-    %TODO: can I make this condition nicer?
     Then, the platform's profit ($\pi_P(N_P, N_F, N_C)$) and the fringe's profit ($\pi_F(N_P, N_F, N_C)$) are given by:
@@
 In words, \cref{prop:outcome_based_bargaining_power} describes two alternative worlds, in which $N_F$ fringe firms (assuming a platform with $N_P$ product variety and $N_C$ consumers) are able to achieve the same total profit level.
-However, in one of these cases, the fringe firms are more substitutable to each other in the sense that fewer of them are needed to achieve a given level of profit (see \cref{fig:outcome_based_bargaining_power}).
+However, in the case with $\tilde{f}$, the fringe firms are more substitutable to each other in the sense that fewer of them are needed to achieve a given level of profit (see \cref{fig:outcome_based_bargaining_power}).
 The observation is that, in this situation, the platform's share is indeed higher when the fringe firms are more substitutable.
@@
 This assumption essentially guarantees that the profit of the fringe (as a function of the number of entrants) has at most a single crossing with total entry cost (apart from the obvious $N_F=0$ intersection).
-Again, the profit functions presented in the main text satisfy this assumption.
+The profit functions presented in the main text satisfy this assumption.
 
@@
 Next, let us look at an analogous result for the fringe firms.
-In their case, the direction of the change depends on the complementarities between the fringe firms.
+In their case, the direction of the change depends on the complementarities between the platform and the fringe firms.
 \begin{proposition}
@@
 On the other hand, when the fringe firms are mostly complements the fringe's profits increase.
+
+As the Shapley value of each player is their average marginal contribution to the total value, this result can best be understood through the lens of marginal contributions.
+When the cross derivative is positive, an increase in the platform's product variety increases the marginal contribution of the fringe firms to the total value for any given number of fringe firms.
+Therefore, the share of the fringe also increases.
+On the other hand, when the cross derivative is negative, the marginal contribution of the fringe firms decreases, and so does their share.
 
@@
 \end{corollary}
-That is, the equilibrium number of entrants increases as a response to an increase in $N_P$ if the fringe firms are mostly complements, and decreases if they are mostly substitutes.
+That is, the equilibrium number of entrants increases as a response to an increase in $N_P$ if the platform and the fringe firms are complements, and decreases if they are substitutes.
 The underlying reason is again the concave or hump-shaped fringe profit function.
@@
 Therefore, if an increase in $N_P$ decreases the fringe's profits for every $N_F \geq 0$, equilibrium can be restored by decreasing the number of fringe entrants, (and vice versa for the other case).
+This is also related to the concept of strategic complementary and substitutability, which also depends on the cross-derivatives (i.e. the supermodularity or submodularity) of the profit function.
 
@@
     \begin{align*}
-        \partial_F \pi_F(N_P^*, N_F^*, N_C^*) \coloneqq \left. \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_F} \right|_{N_P = N_P*, N_F = N_F^*, N_C = N_C^*}.
+        \partial_F \pi_F(N_P^*, N_F^*, N_C^*) \coloneqq \left. \frac{\partial \pi_F(N_P, N_F,  )}{\partial N_F} \right|_{N_P = N_P*, N_F = N_F^*, N_C = N_C^*}.
     \end{align*}

### 2024-06-07 src/paper/application.tex
Address some of armin's comments

@@
 
-Let us now describe each stage of the game in more detail.
-I start with the final two subgames, as they are identical in both models.
-Then I describe how entry fees and fringe entry is determined first in the benchmark model, and then highlight the differences in the bargaining model.
-
 \subsubsection{Demand}
@@
 
+Let us now describe each stage of the game in more detail, starting with the final two subgames, as they are identical in both models.
+This part of the model is based on \textcite[]{anderson2021hybrid}, who utilize the exact same utility structure as th one described here.
 Imagine that there is a unit mass of consumers, looking to buy one product each.
@@
 where $v_{T_i}$ is the value of product $T_i$, $p_{T_i}$ is its price, and $\epsilon_{T_i}^j$ is an idiosyncratic taste shock.
-Throughout this section I assume that the value of each product within its category is the same.
+Throughout this section I assume that the value of each fringe product is the same, and the same goes for the platform products.
 I.e., $v_{T_i} = v_T \, \forall\,i$.
@@
 This distributional assumption, along with the fact that each consumer consumes only one product, will lead to a tractable, logit-form demand function.
+The demand for product $T_i$ is that arises from the consumers maximizing their utility is denoted by $x_{T_i}$.
 
@@
 
+Now let us turn to stage 1 and 2 of the game: the determination of the entry fee and the fringe firms' entry decision.
+I start with the benchmark model, where the platform sets the entry fee unilaterally.
+Then, I compare and contrast this with the bargaining model, where the entry fee is the result of a negotiation between the platform and the fringe firms.
+
 \paragraph{Benchmark case}
@@
 Furthermore, these firms can only sell their products through the platform, for which the platform can charge a lump-sum entry fee $K_F$.
-The timing of these decisions is as follows: (1) the platform sets and commits to an entry fee $K_F$, (2) the fringe firms decide whether to enter the market, and (3) the firms that have entered pay the entry fee to the platform.
+The timing of these decisions is as follows: (1) the platform sets and commits to an entry fee $K_F$, (2) the fringe firms decide whether to enter the market and pay investment cost $I_F$ and entry fee $K_F$.
 
@@
 In order to keep the model tractable, I model this in a reduced-form manner: I assume that the platform and the entrants agree on an entry fee $K_F$, which makes the total profits net entry fees equal to the Shapley value of the players.
-Due to this assumption, the timing of the model is also slightly different.
+Due to this assumption, the timing of the model is also different.
 First, the fringe firms decide whether to invest in creating a product at cost $I_F$.
@@
 
-In practice, the resulting entry fees look as follows.
+More specifically, the resulting entry fees look as follows.
 Assume that $N_F$ fringe firms choose to invest in creating a product in the first stage of the game.
 Now, for every $s N_F$ ($s \in [0, 1]$), calculate the total profits that would be realized if the platform and $n_f$ fringe firms were the only players in the market, and they engaged in monopolistic competition as described in the previous paragraph.
-Let us denote these profits by $\pi^v_{F}(N_P,s N_F)$ and $\pi^v_{P}(N_P,s N_F)$, and the corresponding industry-wide total profits by $\Pi$ and $\Pi(N_P,s N_F, N_C)$.\footnote{
+Let us denote these profits by $\pi^v_{F}(N_P,s N_F)$ and $\pi^v_{P}(N_P,s N_F)$, and the corresponding industry-wide total profits by $\Pi$ and $\Pi(N_P,s N_F)$.\footnote{
     Throughout this paper, I use the notation $\pi_T$ to denote the profits realized by player(s) $T$, and $\Pi$ to denote the total industry profits.
@@
     \begin{align*}
-        \pi^t_P(N_P, N_F) &= N_C \int_0^1 \Pi(N_P,s N_F) \ds, \\
-        \pi^t_F(N_P, N_F) &= N_C \int_0^1 \partial_2 N_F \Pi(N_P,s N_F) \ds.
+        \pi^t_P(N_P, N_F) &= \int_0^1 \Pi(N_P,s N_F) \ds, \\
+        \pi^t_F(N_P, N_F) &= \int_0^1 \partial_2 N_F \Pi(N_P,s N_F) \ds.
     \end{align*}
@@
 
-The timing of the two models are intended to be as similar as possible.
+The two models are designed to be as similar as possible, also with respect to the timing of the game.
 The only difference is in the order of the first two stages, which is necessary due to the nature of the two different entry fee setting mechanisms.
 
-In the case of the benchmark model, if the platform set entry fees after fringe firms make their investment decisions, the platform would charge an entry fee that would make the fringe profits zero \emph{sans the investment cost}.
+In the case of the benchmark model, if the platform set entry fees after fringe firms make their investment decisions, the platform would charge an entry fee that would make the fringe profits zero without taking into account the investment cost $I_F$.
 This would lead to negative fringe profits, and thus to a trivial equilibrium, where no firm enters.
@@
 I do this for a number of reasons.
-For one, it simplifies the analysis without affecting the main results qualitatively.
+For one, it simplifies the analysis without affecting the main results qualitatively.  % TODO: refer to results if I can
 More importantly, it lets me focus on the main question of this paper: how the platform's hybrid operation affects the bargaining power.
-If the platform priced its products strategically, there would be a quite mechanical effect that an increase in the number of products would lead to an increase in optimal prices, which would in fact decrease consumer surplus.
-This hard to disentangle the effects of hybrid operation from the effects of strategic pricing.
-Therefore, this assumption can be seen as a best-case scenario for consumers, and the results can be interpreted as a lower bound on the negative effects of hybrid operation.
-For a more thorough discussion of this assumption, see.
+If the platform priced its products strategically, there would be an additional channel through which its product variety could affect the outcomes: in contrast to the fringe firms, it takes into account the effect of its prices on the aggregate demand.
+This would make it harder to disentangle the effects of hybrid operation from the effects of strategic pricing.
+This assumption can be seen as a best-case scenario for consumers and the fringe, where as little market power as possible is given to the platform.
 
@@
 
-Finally, even taken at face value, this assumption about the platform's pricing is not as unrealistic as it might seem at first.
+Finally, even taken at face value, this assumption about the platform's pricing is quite reasonable in a number of settings.
 For example, the platform might be producing its products through a number of subsidiaries, which are legally separate entities, thus having no control over operational decisions, but still getting the profits from the sales.
@@
 Although the main reason for utilizing cooperative game theory in this model is tractability, it is by no means the only one.
-This way of modelling bargaining outcomes has many precedents in the industrial organization literature \parencite[e.g.][]{montez2007downstream,hart1990property,levy1997individual,inderst2003bargaining,brugemann2019intra}
+This way of modelling bargaining outcomes, while uncommon, has been used to great effect in a number of other papers in the industrial organization literature \parencite[e.g.][]{montez2007downstream,hart1990property,levy1997individual,inderst2003bargaining,brugemann2019intra}.
 Furthermore, it has a number of appealing properties.
@@
 The subgame perfect equilibrium of the fully non-cooperative model described in that section coincides with the equilibrium of the bargaining model in the main text.
-Therefore, if one is uncomfortable with the cooperative elements in the model, they can simply think of it as a more tractable representation of the one from \cref{sec:bargaining_microfoundation}.
+Therefore, one can think of the cooperative game as a more tractable representation of the one from \cref{sec:bargaining_microfoundation}.
 
@@
 Discrete choice models with type I Extreme Value errors give rise to a logit-type demand function \parencite[e.g.][]{small1981applied}.
-More specifically, \textcite[]{anderson2021hybrid} utilize the exact same utility structure as in \cref{sec:model}, and show that it gives rise to the following demand function.
+More specifically, \textcite[]{anderson2021hybrid} show that it gives rise to the following demand function.
 \begin{proposition}
@@
 $V_T$ can be thought of as the value of the product, also accounting for marginal costs and taste heterogeneity.
-In this logit demand system, the value of the product is the only parameter that matters for market shares and profits.
+In this logit demand system, the primitive parameters $v_T$ and $c_T$ only affect the outcomes through this value.
 In fact, equilibrium per-product demand and variable profit can simply be expressed as $V_T/ A$ and $\mu V_T/ A$, respectively, where
@@
 denotes the total aggregate.
+Therefore, to simplify the notation, I will use $V_T$ and $A$ in the rest of the paper, instead of the more cumbersome expressions.
 
@@
 \end{corollary}
-This result is a direct consequence of the facts that the aggregate is independent of the platform's product variety in the hybrid regime, and that consumer surplus is a monotone increasing function of the aggregate.
+This result is a direct consequence of the facts that the aggregate is independent of the platform's product variety in the hybrid regime, and that consumer surplus only depends on the aggregate.
 
@@
     \end{subfigure}
-    \caption{Equilibrium number of fringe entrants and (implied) entry fees ($\mu = 1, N_C = 1, V_P = 1, V_F = 1, I_F = 0.05$).
+    \caption{Equilibrium number of fringe entrants and (implied) entry fees ($\mu = 1, V_P = 1, V_F = 1, I_F = 0.05$).
 In the benchmark model, the entry fee does not depend on the platform's product variety, and an increase in $N_P$ leads to a proportional reduction in $N_F$.
@@
     \end{subfigure}
-    \caption{Platform profits in equilibrium ($\mu = 1, N_C = 1, V_P = 1, V_F = 1, I_F = 0.05$).
+    \caption{Platform profits in equilibrium ($\mu = 1, V_P = 1, V_F = 1, I_F = 0.05$).
 In both cases, platform profits are increasing in $N_P$.
@@
     \end{subfigure}
-    \caption{Size of the aggregate and consumer surplus in equilibrium ($\mu = 1, N_C = 1, V_P = 1, V_F = 1, I_F = 0.05$).
+    \caption{Size of the aggregate and consumer surplus in equilibrium ($\mu = 1, V_P = 1, V_F = 1, I_F = 0.05$).
 In the benchmark model, an increase in platform product variety has no effect in the hybrid regime.
@@
     \begin{align*}
-        \pi^t_P(N_P, N_F) &= N_C \int_0^1 \lambda_P s ^ {\lambda_P - 1} \Pi(N_P,s N_F) \ds, \\
-        \pi^t_F(N_P, N_F) &= N_C \int_0^1 s ^ {\lambda_P} \partial_2 N_F \Pi(N_P,s N_F) \ds.
+        \pi^t_P(N_P, N_F) &= \int_0^1 \lambda_P s ^ {\lambda_P - 1} \Pi(N_P,s N_F) \ds, \\
+        \pi^t_F(N_P, N_F) &= \int_0^1 s ^ {\lambda_P} \partial_2 N_F \Pi(N_P,s N_F) \ds.
     \end{align*}
@@
     \end{subfigure}
-    \caption{Equilibrium outcomes in the case when the platform has higher innate bargaining power ($N_C = 1, V_P = 1, V_F = 1, I_F = 0.05$).
+    \caption{Equilibrium outcomes in the case when the platform has higher innate bargaining power ($V_P = 1, V_F = 1, I_F = 0.05$).
 As before, consumer surplus is decreasing in $N_P$ as a result in a decrease in total product variety.
@@
     \end{subfigure}
-    \caption{Platform profits and (implied) entry fees ($\mu = 0.2, N_C = 1, V_P = 1, V_F = 1, I_F = 0.05$).
+    \caption{Platform profits and (implied) entry fees ($\mu = 0.2, V_P = 1, V_F = 1, I_F = 0.05$).
 Regardless of lambda, platform profits and entry fees are increasing in $N_P$.
@@
 In the case of lower $\lambda_P$ (left), choosing the hybrid mode can be optimal depending on $I_P$.
-The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode ($\mu = 1, N_C = 1, V_P = 1, V_F = 1, I_F = 0.05$).}
+The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode ($\mu = 1, V_P = 1, V_F = 1, I_F = 0.05$).}
     \label{fig:equilibrium_high_lambda_entry_fees}
@@
 
-\subsection{Consumers also participate in bargaining}
+\subsection{Three sided bargaining }
 \label{sec:two_sided}
 
-In the second extension, I consider the case when the consumers also participate in the bargaining process.
-This entails two changes compared to the main model.
+In the second extension, I consider the case when the other side also participate in the bargaining process.
+This is more plausible in business to business settings, therefore I use the term customers instead of consumers in this section.
+Nevertheless, I use the same demand structure as in the main model.
+
+This extension entails two changes compared to the main model.
 First, the players bargain over the total surplus generated on all sides of the market, not just total profits.
@@
 
-Let us start by deriving total surplus as a function of $N_P, N_F$ and $N_C$.
+Let us start by deriving total surplus as a function of $N_P, N_F$ and $N_C$ (the number of customers).
 Under the logit-like demand structure described in \cref{sec:demand}, the total surplus is given by
@@
 There are a number of things to note here.
-First, and most importantly, the consumers' share from total surplus is equal to the platform's.\footnote{
-    This is a consequence of the fact that the total surplus function is linear in the number of consumers.
+First, and most importantly, the customers' share from total surplus is equal to the platform's.\footnote{
+    This is a consequence of the fact that customers are ex ante identical, and each of them buy one product, therefore demand, and in turn total surplus is linear in $N_C$.
 }
-As a consequence, what's good for the platform is also optimal for the consumers.
-Therefore, if the platform can choose its mode of operation to maximize its profits, it maximizes consumer welfare, as well (but not necessarily total surplus).
+As a consequence, what's good for the platform is also optimal for the customers.
+Therefore, if the platform can choose its mode of operation to maximize its profits, it maximizes the customers' surplus, as well (but not necessarily total surplus).
 
@@
 Nevertheless, there is an important distinction compared to the previous results.
-While this does lead to a decrease in total surplus, in contrast to the two-sided bargaining case, this does not imply a decrease in consumer surplus.
-As mentioned before, the consumers' share of total surplus is equal to the platform's profits, and thus it is increasing in $N_P$ if and only if platform profits (\cref{fig:profits_full_surplus_two_sided}) are.
-Therefore, consumers might prefer hybrid operation to the platform being a pure marketplace.
+While this does lead to a decrease in total surplus, in contrast to the two-sided bargaining case, this does not imply a decrease in the customers' surplus.
+Their share of total surplus is equal to the platform's profits, and thus it is increasing in $N_P$ if and only if platform profits (\cref{fig:profits_full_surplus_two_sided}) are.
+Therefore, customers might prefer hybrid operation to the platform being a pure marketplace.
 
@@
     \end{subfigure}
-    \caption{Illustration of \cref{prop:share_of_fringe} when fringe and platforrm products are substitutes.
+    \caption{Illustration of \cref{prop:share_of_fringe} when fringe and platform products are substitutes.
 An increase in the platform's product variety increases total profits, yet, the fringe's share decreases in absolute terms.}
@@
         0 & \text{if } P \notin S \\
-        N_C f(N_P, n_F(S)) & \text{if } P \in S
+        f(N_P, n_F(S)) & \text{if } P \in S
     \end{cases},
@@
     \begin{align*}
-        \varphi_P(\mathcal{G}) &= N_C \int_0^1 f(N_P, s N_F) \ds, \\
-        \varphi_P(\mathcal{F}) &= N_C \int_0^1 s N_F \partial_2 f(N_P, s N_F) \ds.
+        \varphi_P(\mathcal{G}) &= \int_0^1 f(N_P, s N_F) \ds, \\
+        \varphi_P(\mathcal{F}) &= \int_0^1 s N_F \partial_2 f(N_P, s N_F) \ds.
     \end{align*}
@@
 
-\begin{proof}[proof of \cref{prop:profit_sharing_one_sided}]
+\begin{proof}[Proof of \cref{prop:profit_sharing_one_sided}]
     This result is a direct application of Proposition 3 and Corollary 2 in \textcite{stancsics2023value}.
@@
     \begin{align*}
-        \varphi_P(\mathcal{G}) &= N_C \int_0^1 \lambda_P s ^ {\lambda_P - 1} f(N_P, s N_F) \ds, \\
-        \varphi_F(\mathcal{G}) &= N_C \int_0^1 s ^ {\lambda_P} N_F \partial_2 f(N_P, s N_F) \ds.
+        \varphi_P(\mathcal{G}) &= \int_0^1 \lambda_P s ^ {\lambda_P - 1} f(N_P, s N_F) \ds, \\
+        \varphi_F(\mathcal{G}) &= \int_0^1 s ^ {\lambda_P} N_F \partial_2 f(N_P, s N_F) \ds.
     \end{align*}
@@
 
-\begin{proof}[proof of \cref{prop:profit_sharing_weighted}]
+\begin{proof}[Proof of \cref{prop:profit_sharing_weighted}]
     This result is a direct application of Proposition 4 in \textcite{stancsics2023value}.

### 2024-06-09 src/paper/application.tex
Add section about endogenizing N_P

@@
 
+\newcommand{\dd}{\mathrm{d}}
 \newcommand{\dt}{\mathrm{d}t}
@@
 \begin{corollary}
+    \label{prop:platform_profits_comparative_benchmark}
     \begin{align*}
@@
 The intuition behind these results can be demonstrated by looking at entry fees.
-First, define the implied entry fee in the bargaining case as the difference between the variable profit and the final, total profit of the fringe firms (bar the investment cost):
-\begin{align*}
-    K_F^{\text{impl}} = \pi_F^v - \pi_F^t.
+First, define the implied entry fee in the bargaining case as the difference between the variable profit and the final, total profit of the fringe firms (bar the investment cost)\footnote{
+    Or, in light of \cref{sec:bargaining_microfoundation}, it can also directly be interpreted as the entry fee that the parties agree on after negotiating.
+}:
+\begin{align*}
+    K_F^i = \frac{\pi_F^v - \pi_F^t}{N_F} - I_F.
 \end{align*}
 As shown before, as the platform's product variety grows, its bargaining power also increases.
-This can be thought of as an increase in (implied) entry fees $K_F^{\text{impl}}$, which in turn discourages fringe entry.
+This can be thought of as an increase in (implied) entry fees $K_F^i$, which in turn discourages fringe entry.
+\begin{proposition}
+    \label{prop:implied_entry_fee_comparative}
+    In the hybrid regime, the implied entry fee is increasing in the number of the platform's products:
+    \begin{align*}
+        N_F(N_P) > 0 \implies \frac{\partial K_F^i(N_P)}{\partial N_P} > 0.
+    \end{align*}
+\end{proposition}
 This is not happening in the benchmark model, as the optimal entry fee does not depend on the platform's product variety.
-\Cref{fig:entry_fee} demonstrates this effect.
+\Cref{fig:entry_fee} demonstrates this difference graphically.
 
@@
 On the other hand, when the entry fee is already higher than optimal for a given $N_P$, an additional increase will lead to an even more suboptimal (implied) entry fee, and thus a lower increase in platform profits.
-
-% This means that, if the platform had to create its product variety at a per-unit investment cost of $I_P$, it would make different (inefficient) choices compared to the benchmark model.
-% In particular, it might invest in some products even if it has a product disadvantage, and it might not invest in some products even if it has a product disadvantage.
-% This phenomenon is more pronounced when the implied entry fee for $N_P = 0$ is lower than optimal, and is explored in more detail in \cref{sec:lower_bargaining_power}.
+\Cref{sec:endogenizing_n_p} explores this phenomenon in more detail.
 
@@
 
+\subsection{Platform's mode of operation}
+\label{sec:endogenizing_n_p}
+
+While completely endogenizing the platform's mode of operation (i.e., the determination of $N_P$) is outside the scope of this paper, some insights can be gained by building on the previous results.
+Let us start by examining whether the platform would prefer to switch to the pure retail regime and exclude the fringe firms.
+
+Assume that $N_P$ is still fixed, but at time 0, the platform can decide whether to exclude the fringe.
+As the next proposition shows, the platform never has an incentive to do so, if otherwise the equilibrium is in the hybrid regime.
+\begin{proposition}
+    \label{prop:hybrid_vs_retail}
+    In both the benchmark and bargaining models, the platform never has an incentive to switch from the hybrid to the pure retail regime:
+    \begin{align*}
+        \pi_P^t(N_P, N_F(N_P)) \geq \pi_P^t(N_P, 0) \forall\, N_P.
+    \end{align*}
+    The inequality is strict whenever $N_F(N_P) > 0$.
+\end{proposition}
+In the case of the benchmark model, this result is rather straightforward: if the platform would find it optimal to exclude the fringe, it could do so by setting the entry fee to a sufficiently high level.
+In the bargaining case, the reasoning is less obvious, as it is not immediately clear that the share of profits that the platform can negotiate for itself is higher than what it could achieve by itself.
+However, it turns out that it is indeed the case.
+The intuition is that the platform's profit is just the average of total profits, with the average taken over the number of fringe firms.
+As total profits are increasing in the number of the fringe entrants, this average is also increasing in $N_F$.
+
+A related, but different question is whether the platform how the platform would decide between operating in pure retail and pure marketplace modes, if hybrid regime is not an option.
+It is particularly relevant from a policy perspective, as it can help understand what happens if hybrid operation is banned.
+The answer to this is less clear-cut, and depends on the parameters of the model.
+For low enough values of $V_P$ and $N_P$, the platform would clearly choose the pure marketplace mode, as with pure retail, its profits can be arbitrarily low.
+The opposite is true for high enough values of $V_P$ and $N_P$.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                    ylabel={},
+                    xmin=0, xmax=4.5, % adjust these values as needed
+                    ymin=0.55, ymax=0.65, % adjust these values as needed
+                    axis lines=left,
+                    xtick={0, 4.5},
+                    legend pos=south west,
+                    width=\linewidth,
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P_bench} - \thisrow{N_P} * 0.045]{\equilibrium};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P_bench} - \thisrow{N_P} * 0.05]{\equilibrium};
+                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P_bench} - \thisrow{N_P} * 0.055]{\equilibrium};
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid_bench]{\equilibrium};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+
+                \legend{$I_P = 0.045$, $I_P = 0.05$, $I_P = 0.055$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Benchmark case}
+        \label{fig:optimal_n_p_benchmark}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                    xlabel={$N_P$},
+                    ylabel={},
+                    xmin=0, xmax=4.5, % adjust these values as needed
+                    ymin=0.55, ymax=0.65, % adjust these values as needed
+                    axis lines=left,
+                    xtick={0, 4.5},
+                    legend pos=north west,
+                    width=\linewidth,
+                ]
+                \addplot[color=myblue,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.045]{\equilibrium};
+                \addplot[color=myred,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.05]{\equilibrium};
+                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.055]{\equilibrium};
+
+                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibrium};
+                \addplot[draw=none,name path=bottom] {0};
+                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
+
+                \legend{$I_P = 0.045$, $I_P = 0.05$, $I_P = 0.055$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Bargaining case}
+        \label{fig:optimal_n_p_bargaining}
+    \end{subfigure}
+    \caption{Total platform profits if the platform incurs an investment cost for creating its own products.
+In the benchmark case, hybrid mode operation can only be optimal in the knife-edge case when neither the platform's nor the fringe's product has an advantage.
+In the bargaining model, hybrid operation may be optimal even if the platform has a product disadvantage.
+The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode ($\mu = 1, V_P = 1, V_F = 1, I_F = 0.05$).}
+    \label{fig:optimal_n_p}
+\end{figure}
+
+Finally, let us look at the more general case, where the platform can choose its number of products at the beginning of the game.
+Similarly to the fringe, assume that it faces an investment cost of $I_P$ per product.
+As before, things are straightforward in the benchmark model: the platform invests in own products only if $\frac{V_P}{I_P} \geq \frac{V_F}{I_F}$.
+The following proposition characterizes the platform's optimal investment more precisely.
+\begin{proposition}
+    \label{prop:optimal_n_p_benchmark}
+    Let $N_P^*$ be the platform's optimal number of products.
+    Then, in the benchmark model, the following holds:
+    \begin{align*}
+        \frac{V_P}{I_P} < \frac{V_F}{I_F} &\implies N_P^* 0, \\
+        \frac{V_P}{I_P} > \frac{V_F}{I_F} &\implies N_P^* > 0, N_F(N_P^*) = 0, \\
+        \frac{V_P}{I_P} = \frac{V_F}{I_F} &\implies N_P^* \in [0, \bar{N}_P] \text{ for some } \bar{N}_P > 0.
+    \end{align*}
+\end{proposition}
+
+The intuition behind this result is that the platform can extract all profits from the fringe firms through the lump-sum entry fee, end thus it invests in its own products only if it has a product advantage (either in terms of less costly investment or more valuable product).
+A consequence of this proposition is that, apart from the knife-edge case of $\frac{V_P}{I_P} = \frac{V_F}{I_F}$, the platform never finds it optimal to operate in hybrid mode: it either creates so many products that it excludes the fringe, or it creates none at all.
+\Cref{fig:optimal_n_p_benchmark} illustrates this result.
+
+As before, the situation is more complicated in the bargaining model.
+Instead of characterizing the platform's optimal investment directly, let us look at it through the lens of implied entry fees.
+Remember, that in the bargaining model, the implied entry fee is increasing in the number of the platform's products.
+Together with the concavity of platform profits as a function of $N_P$, and the statement of \cref{prop:platform_profits_comparative_benchmark}, this implies the following result:
+\begin{proposition}
+    \label{prop:comparative_n_p_bargaining}
+    In the bargaining model, the platform invests in its own products only if it has a product advantage, and the optimal number of products is increasing in the size of this advantage.
+    \begin{align*}
+        K_F^i(N_P) < K_F^{opt} &\implies \frac{\dd \pi_P^t}{\dd N_P} > \frac{V_P}{V_F} I_F \\
+        K_F^i(N_P) > K_F^{opt} &\implies \frac{\dd \pi_P^t}{\dd N_P} < \frac{V_P}{V_F} I_F.
+    \end{align*}
+\end{proposition}
+The intuition is that if, for a certain $N_P$, the implied entry fee is lower than optimal, then the platform investing in more products will bring it closer to the optimal level, and the increase in platform profits will be higher than in the benchmark model.
+Conversely, if the entry fee is already higher than optimal for a given $N_P$, an additional increase will lead to an even more suboptimal (implied) entry fee, and thus a lower increase in platform profits.
+
+The consequence of this result is that in the bargaining model, hybrid operation can be optimal, and not only for knife-edge cases.
+Furthermore, and even more strikingly, the platform may find it optimal to invest in its own products even if it has a product disadvantage, if it helps it to negotiate a more optimal entry fee.
+\Cref{fig:optimal_n_p_bargaining} displays such an example.
+
+\subsection{Discussion}
+TODO: which assumptions are crucial for the results?
+
 \section{Extensions}
@@
 The reason is that the implied entry fee is always higher than the optimal one, therefore an increase the positive effect of an increase in $N_P$ is somewhat counterbalanced by the entry fee becoming even more suboptimal.
-
-\Cref{fig:equilibrium_high_lambda_entry_fees} demonstrates an important consequence of this phenomenon.
-Imagine that the platform can decide on the number of its products at time 0, at an investment cost of $I_P$ per product.
-In the example for the main model, due to the implied entry fee being higher than optimal even for $N_P = 0$, hybrid operation may be optimal for certain values of $I_P$ (most notably, $I_P = I_F = 0.05$).
-In contrast, in the example with the platform having higher bargaining power, it would always prefer either pure retail or pure marketplace operation.
 
@@
 
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}
-            \begin{axis}[
-                    xlabel={$N_P$},
-                    ylabel={},
-                    xmin=0, xmax=4.5, % adjust these values as needed
-                    ymin=0.2, ymax=0.7, % adjust these values as needed
-                    axis lines=left,
-                    xtick={0, 4.5},
-                    legend pos=south west,
-                    width=\linewidth,
-                ]
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.04]{\equilibrium};
-                \addplot[color=myred,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.05]{\equilibrium};
-                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.06]{\equilibrium};
-
-                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibrium};
-                \addplot[draw=none,name path=bottom] {0};
-                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
-
-                \legend{$I_P = 0.04$, $I_P = 0.05$, $I_P = 0.05$}
-            \end{axis}
-        \end{tikzpicture}
-        \caption{$\lambda = 1$}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}
-            \begin{axis}[
-                    xlabel={$N_P$},
-                    ylabel={},
-                    xmin=0, xmax=4.5, % adjust these values as needed
-                    ymin=0.2, ymax=0.7, % adjust these values as needed
-                    axis lines=left,
-                    xtick={0, 4.5},
-                    legend pos=south west,
-                    width=\linewidth,
-                ]
-                \addplot[color=myblue,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.04]{\equilibriumProfitOneSidedHighLambda};
-                \addplot[color=myred,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.05]{\equilibriumProfitOneSidedHighLambda};
-                \addplot[color=mygreen,mark=none,thick] table[x=N_P,y expr=\thisrow{pi_P} - \thisrow{N_P} * 0.06]{\equilibriumProfitOneSidedHighLambda};
-
-                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumProfitOneSidedHighLambda};
-                \addplot[draw=none,name path=bottom] {0};
-                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];
-
-                \legend{$I_P = 0.04$, $I_P = 0.05$, $I_P = 0.05$}
-            \end{axis}
-        \end{tikzpicture}
-        \caption{$\lambda = 0.5$}
-    \end{subfigure}
-    \caption{Total platform profits if the platform incurs an investment cost for creating its own products ($\pi_P(N_P) - I_P N_P$).
-In the high bargaining power case (right), the platform never chooses to operate in hybrid mode.
-It either becomes a pure marketplace or a pure retailer.
-In the case of lower $\lambda_P$ (left), choosing the hybrid mode can be optimal depending on $I_P$.
-The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode ($\mu = 1, V_P = 1, V_F = 1, I_F = 0.05$).}
-    \label{fig:equilibrium_high_lambda_entry_fees}
-\end{figure}
-
 \subsection{Three sided bargaining }

### 2024-06-10 src/paper/application.tex
Rewrite results

@@
     The optimal entry fee when the platform is operating in the hybrid regime is unique and given by
-    \begin{align*}
-        K_F^* = \sqrt{\mu I_F V_F} - I_F.
-    \end{align*}
+    \begin{align}
+        K_F^{opt} = \sqrt{\mu I_F V_F} - I_F. \label{eq:entry_fee_benchmark}
+    \end{align}
     The platform's total profit in this case is
-    \begin{align*}
-        \pi_P^{t} = \mu - 2\sqrt{\frac{I_F \mu}{V_F}} + \frac{I_F}{V_F} (N_P V_P + 1).
-    \end{align*}
+    \begin{align}
+        \pi_P^{t} = \mu - 2\sqrt{\frac{I_F \mu}{V_F}} + \frac{I_F}{V_F} (N_P V_P + 1). \label{eq:platform_profits_hybrid_benchmark}
+    \end{align}
     When the optimal mode of operation is retail, the platform's profit is
-    \begin{align*}
-        \pi_P^{t} = \pi_P^{v} = \mu \frac{ N_P V_P}{N_P V_P + 1}.
-    \end{align*}
+    \begin{align}
+        \pi_P^{t} = \pi_P^{v} = \mu \frac{ N_P V_P}{N_P V_P + 1}. \label{eq:platform_profits_retail_benchmark}
+    \end{align}
 \end{theorem}
@@
 First, let us look at the case when the platform finds it optimal to operate in the hybrid regime.
-Notice that the optimal entry fee does not depend on either the platform's product value or product variety (\cref{fig:entry_fee}).
+As illustrated by \cref{fig:entry_fee}, the optimal entry fee (\cref{eq:entry_fee_benchmark}) does not depend on either the platform's product value or product variety.
 This is because due to the lump-sum nature of the entry fee, the platform can extract all the surplus from the fringe firms, and thus chooses $K_F$ to maximize total industry profits.
 The latter is essentially a function of the aggregate, minus the investment costs of the fringe firms.
-As I have shown in \cref{prop:equilibrium_aggregate_benchmark}, the aggregate is independent of the platform's product variety in the hybrid regime, and therefore the optimal entry fee is also independent of it.
-
-On the other hand, the platform's profit is increasing in the number of its products (\cref{fig:platform_profits}).
+As I show later in \cref{prop:equilibrium_benchmark}, the aggregate is independent of the platform's product variety in the hybrid regime, and therefore the optimal entry fee is also independent of it.
+
+On the other hand, \cref{fig:platform_profits} shows the platform's profit (\cref{eq:platform_profits_hybrid_benchmark,eq:platform_profits_retail_benchmark}) is increasing in the number of its products.
+\begin{corollary}
+    \label{prop:platform_profits_comparative_benchmark}
+    \begin{align*}
+        N_F > 0 \implies \frac{\partial \pi_P^t}{\partial N_P} = \frac{V_P}{V_F} I_F.
+    \end{align*}
+\end{corollary}
 This is a rather mechanical result: the platform's product variety is exogenous, and therefore possible investment costs are not modeled.
@@
 Consequently, in the hybrid regime, the derivative of optimal profits with respect to the platform's product variety is simply the fringe's investment cost, adjusted for the possible difference in product value.
-\begin{corollary}
-    \label{prop:platform_profits_comparative_benchmark}
-    \begin{align*}
-        N_F > 0 \implies \frac{\partial \pi_P^t}{\partial N_P} = \frac{V_P}{V_F} I_F.
-    \end{align*}
-\end{corollary}
-This results also have implications for what would happen if the platform's product variety was an endogenous choice.
-It would only choose to operate in a hybrid mode if it had some advantage over the fringe firm's products (either in investment cost, production cost, or product value).
-Otherwise, it would simply operate as a pure intermediary, and the number of fringe firms would adjust to the equilibrium aggregate.
-
-Another important corollary of \cref{prop:optimal_entry_fee} is that consumer welfare is also unaffected by the platform's product variety in the hybrid regime.
-\begin{corollary}
-    \label{prop:consumer_surplus_benchmark}
-    \begin{align*}
-        N_F > 0 \implies \frac{\partial CS}{\partial N_P} = 0.
-    \end{align*}
-\end{corollary}
-This result is a direct consequence of the facts that the aggregate is independent of the platform's product variety in the hybrid regime, and that consumer surplus only depends on the aggregate.
-
-Next, let us turn to the case when the platform finds it optimal to operate as a pure retailer.
-In this case, the only products on the market are the platform's own products.
-Therefore, quite mechanically, the aggregate, and thus consumer surplus, are increasing in the number of the platform's products.
-\begin{corollary}
-    \begin{align*}
-        N_F = 0 \implies \frac{\partial CS}{\partial N_P} = \frac{\mu V_P}{(1 + N_P V_P)^2} > 0.
-    \end{align*}
-\end{corollary}
+
+Now let us examine consumer welfare as a function of the platform's product variety\footnote{
+    The comparative statics for the platform's product value, $V_P$, are similar.
+}.
+Under the assumed demand system, consumer surplus is proportional to the logarithm of the aggregate.
+Therefore, one only needs to understand how fringe entry, and thus the aggregate changes with the platform's product variety to understand the effect of the latter on consumer welfare.
+The next theorem establishes results for these three variables in the benchmark model.
+\begin{theorem}
+    \label{prop:equilibrium_benchmark}
+    In the benchmark model, if $N_F(N_P) > 0$ (hybrid regime), then the following hold.
+    \begin{itemize}
+        \item The equilibrium number of fringe firms is decreasing in the platform's product variety: $\frac{\dd N_F}{\dd N_P} = -\frac{V_P}{V_F} < -0$.
+        \item The equilibrium size of the aggregate and consumer surplus are independent of the platform's product variety: $\frac{\dd A}{\dd N_P} = \frac{\dd CS}{\dd N_P} = 0$.
+    \end{itemize}
+    If $N_F(N_P) = 0$ (pure retailer regime), then both the aggregate and consumer surplus are increasing in the platform's product variety:
+    \begin{itemize}
+        \item $\frac{\dd A}{\dd N_P} = V_P > 0$,
+        \item $\frac{\dd CS}{\dd N_P} = \frac{\mu V_P}{(1 + N_P V_P)^2} > 0$.
+    \end{itemize}
+\end{theorem}
+
+The most important, and perhaps surprising, results of this theorem is that the platform's product variety has no effect on consumer welfare in the hybrid regime.
+This is due to the fact that the optimal entry fee, which is independent of $N_P$, pins down the aggregate.
+As shown in \cref{fig:fig:fringe_entry_eq}, an increase in the platform's product variety will simply replace fringe firms in a constant ratio, such that the aggregate remains constant (\cref{fig:welfare_aggregate}).
+This, in turn, implies that consumer surplus is also unaffected by the platform's product variety in the hybrid regime, as demonstrated in \cref{fig:welfare_consumer}.
+
+When the platform finds it optimal to operate as a pure retailer, the only products on the market are the platform's own products.
+Therefore, quite mechanically, the aggregate, and thus consumer surplus, are increasing in the number of the platform's products (unshaded parts of \cref{fig:welfare}).
 
@@
 Therefore, for a given $N_P$, the platform prefers to operate in hybrid mode, and does not want to exclude fringe firms from the market.
-This fact, together with the previous corollaries, implies that the platform's product variety always has a weakly positive effect on consumer welfare.\footnote{
+This fact, together with the \cref{prop:equilibrium_benchmark}, implies that the platform's product variety always has a weakly positive effect on consumer welfare.\footnote{
     This is in contrast to \textcite{anderson2021hybrid}, where a platform operating in hybrid mode sets higher royalties to create a price advantage for its own products.
@@
 }
-\begin{corollary}
-    \begin{align*}
-        \frac{\partial CS}{\partial N_P} \geq 0.
-    \end{align*}
-\end{corollary}
-It either has no effect (hybrid operation), or it increases the aggregate (pure retailer), and thus consumer surplus.
-\Cref{fig:fringe_entry_eq} illustrates this effect.
-
-Finally, these results also suggest that if the platform's product variety (and thus also the pure marketplace/ hybrid mode decision) was endogenous, an improvement in the platform's product (either higher value or lower cost) would also have a weakly positive effect on consumer welfare.
-Therefore, it suggests that platform's having their own products are always weakly beneficial for consumers.
-This surprising result depends on a number of -- admittedly unrealistic -- assumptions.
-Namely, the lump-sum nature of the entry fee, no entry fee for consumers, and the platform pricing its products as if they were produced by separate sellers.
-Therefore, one should not take this result as a conclusion applicable to the real world, but as a best-case benchmark.
-On the other hand, these assumptions are also why this model is so useful as a benchmark: as I show in the next subsection, even with these assumptions in place, the platform's product can have a negative effect on consumer welfare if the entry fee is set through bargaining.
 
@@
 
-As described in \cref{sec:model_bargaining}, the participants negotiate over the aggregate profits that they expect to obtain in the subsequent period (assuming the same non-collusive, monopolistic pricing, as before).
+As described in \cref{sec:model_bargaining}, participants negotiate over the aggregate profits that they expect to obtain in the subsequent period (assuming the same non-collusive, monopolistic pricing, as before).
 From \cref{eq:optimal_profit}, the total profit achieved by the platform and $N_F$ fringe firms is given by
@@
 Bargaining outcomes are determined according to Shapley values, given by \cref{prop:shapley_value}.
-Based on these, one can even obtain closed-form expressions for platform and fringe profit shares for this class of demand systems.
+Based on these, one can obtain closed-form expressions for platform and fringe profit shares for this class of demand systems.
 \begin{proposition}
@@
 \end{lemma}
-This lemma states that the fringe profit function is hump-shaped in the sense that it starts with an increasing, concave part, after which it may turn into a decreasing (but not necessarily concave or convex) function of $N_F$.
+This lemma states that the fringe profit function is hump-shaped in the sense that it starts with an increasing\footnote{
+    More precisely, while the lemma does not explicitly state that the function is increasing for low values of $N_F$, the fact that $\pi_F^t(N_P, 0) = 0$ and $\pi_F^t(N_P, N_F) > 0 \forall\, N_F > 0$ implies it.
+}, concave part, after which it may turn into a decreasing (but not necessarily concave or convex) function of $N_F$.
 \Cref{fig:equilibrium} illustrates this property.
 
-While this lemma's main purpose is to help establish the other, more interpretable results in this chapter, it is also interesting in its own right.
-It shows that the number of fringe firms have a non-monotonic effect on the total profits of the fringe.
+While this lemma's main purpose is to help establish the results about fringe entry and consumer surplusfor the bargaining case, it is also interesting in its own right.
+It shows that the number of fringe firms do not necessarily have a monotonic effect on the total profits of the fringe.
 That is, even though industry-wide profits are increasing in $N_F$, the share that the fringe can obtain may decrease after a certain point, not only in relative terms, but also in absolute terms.
-The underlying reason is that as the number of fringe firms increases, due to their substitutability with each other, their bargaining power decreases.
+The underlying reason is that as the number of fringe firms increases, their bargaining power decreases due to their substitutability with each other.
 This decrease can be large enough to offset the total pie getting larger.
@@
 Let us denote this point as $N_F^*$.
-Furthermore, if there exists such a crossing, then it must be that $\pi_F^t(N_F) > I_F N_F \forall\, N_F \in [0, N_F^*)$, and $\pi_F^t(N_F) < I_F N_F \forall\, N_F \in (N_F^*, \infty)$ (see \cref{fig:equilibrium}).
+Furthermore, if such a crossing exists, then it must be that $\pi_F^t(N_F) > I_F N_F \;\forall\, N_F < N_F^*$, and $\pi_F^t(N_F) < I_F N_F \;\forall\, N_F > N_F^*$ (see \cref{fig:equilibrium} for an illustration of this idea).
 Therefore, $N_F^*$ must be the unique number of equilibrium entrants.
-The following proposition formalizes this idea.
+The following proposition formalizes this observation.
 \begin{proposition}
@@
 
-Together with the hump-shaped fringe profit function, this implies that an increase in the platform's product variety leads to a reduction in the number of fringe firms.
-\Cref{fig:comparative_N_F} illustrates this idea.
-What is not immediately clear is how this affects the total size of the aggregate, and consumer welfare.
-In the benchmark case, the decrease in the number of fringe firms was exactly offset by an increase in the platform's product variety, and the aggregate remained constant.
-The following results shows that this is not the case in the bargaining model: as long as the platform is in the hybrid regime, the aggregate decreases in the number of the platform's products.\footnote{
-    Similar results hold for an increase in the platform's product value $V_P$.
-}
-
-\begin{proposition}
-    \label{prop:N_F_comparative_equilibrium}
-    Assume that the platform is operating in the hybrid regime.
-Then, the equilibrium number of fringe firms is decreasing in the number of the platform's products.
-Furthermore, this decrease is more than proportional to the increase in the platform's product variety (also taking into account product value).
-    \begin{align*}
-        N_F > 0 \implies \frac{\partial N_F}{\partial N_P} < -\frac{V_P}{V_F} < 0.
-    \end{align*}
-\end{proposition}
-
-\begin{corollary}
-    \label{prop:aggregate_comparative_hybrid}
-    Assume that the platform is operating in the hybrid regime. Then the equilibrium aggregate and consumer surplus is decreasing in the number of the platform's products.
-    \begin{align*}
-        N_F > 0 \implies \frac{\partial A}{\partial N_P}, \frac{\partial CS}{\partial N_P} < 0.
-    \end{align*}
-\end{corollary}
-
 \begin{figure}[ht]
@@
 
-When the fringe is not viable, the platform's product variety has the same, mechanical effect on total aggregate and consumer surplus as in the benchmark model.
-\begin{proposition}
-    \label{prop:aggregate_comparative_retail}
-    Assume that the platform is operating in the pure retail regime. Then the equilibrium aggregate and consumer surplus is increasing in the number of the platform's products.
-    \begin{align*}
-        N_F = 0 \implies \frac{\partial A}{\partial N_P}, \frac{\partial CS}{\partial N_P} > 0.
-    \end{align*}
-\end{proposition}
+As illustrated in \cref{fig:comparative_N_F}, together with the hump-shaped fringe profit function, this implies that an increase in the platform's product variety leads to a reduction in the number of fringe firms.
+What is not immediately clear is how this affects the total size of the aggregate, and consumer welfare.
+In the benchmark case, the decrease in the number of fringe firms was exactly offset by an increase in the platform's product variety, and the aggregate remained constant.
+The following results shows that this is not the case in the bargaining model: as long as the platform is in the hybrid regime, the aggregate decreases in the number of the platform's products.\footnote{
+    As before, similar results hold for an increase in the platform's product value $V_P$.
+}
+
+\begin{theorem}
+    \label{prop:equilibrium_bargaining}
+    In the bargaining model, if $N_F(N_P) > 0$ (hybrid regime), then the following hold.
+    \begin{itemize}
+        \item The equilibrium number of fringe firms is decreasing in the platform's product variety.
+Furthermore, this decrease is more than proportional to the increase in the platform's product variety: $\frac{\dd N_F}{\dd N_P} < -\frac{V_P}{V_F} < -0$.
+        \item The equilibrium size of the aggregate and consumer surplus are strictly decreasing in the platform's product variety: $\frac{\dd A}{\dd N_P}, \frac{\dd CS}{\dd N_P} < 0$.
+    \end{itemize}
+    If $N_F(N_P) = 0$ (pure retailer regime), then both the aggregate and consumer surplus are increasing in the platform's product variety:
+    \begin{itemize}
+        \item $\frac{\dd A}{\dd N_P} = V_P > 0$,
+        \item $\frac{\dd CS}{\dd N_P} = \frac{\mu V_P}{(1 + N_P V_P)^2} > 0$.
+    \end{itemize}
+\end{theorem}
+
+The main takeaway from this theorem is that the increasing the platform's product variety can actually decrease consumer welfare in the bargaining model.
+The underlying reason is illustrated in \cref{fig:fringe_entry_eq}: the decrease in the number of fringe entrants is large enough to not only to offset the increase in the platform's product variety, but also to decrease the aggregate (\cref{fig:welfare_aggregate}).
+This in turn leads to a decrease in consumer surplus (\cref{fig:welfare_consumer}).
+
 This set of results is in stark contrast to the benchmark model.
@@
 
-This conclusion is in line with many of the findings in the literature on hybrid platforms, such as \textcite{hagiu2022should} or \textcite{anderson2021hybrid}.
-The channel through which this happens, and thus the potential policy implications, are quite different, however.
-In \textcite{hagiu2022should}, the negative consequences are due to its incentives to engage in anti-competitive behavior, such as self-preferencing or imitation.
-In their model, in the absence of such behavior, hybrid platforms can actually increase consumer welfare.
-\textcite{anderson2021hybrid}, on the other hand, shows that even in the absence of such behavior, hybrid platforms can harm consumers, as platforms are inclined to set higher than optimal royalties to create a price advantage for their own products.
-This model goes one step further.
-Due to the lump-sum nature of the entry fee and platforms pricing their products as if they were produced by separate sellers, this inventive is no more present (as demonstrated by the benchmark model).
-However, the fact that the platform having its own products improves its bargaining position leads to a different distortion: the platform sets higher entry fees than it would if it had no products on its own.
-
-\subsection{Example and comparison}
-
-In this section, I look a specific example to illustrate the main results and compare the benchmark and bargaining models.
-But first, let us collect and state the most important results from the previous sections in one theorem each for both models.
-
-In the benchmark model, the platform having its own product variety has a weakly positive effect.
-As long as the market is in the hybrid regime, and there is a non-zero number of fringe firms, it has no effect on the aggregate or consumer surplus.
-When the fringe is no longer feasible, and the platform is in the pure retail regime, the platform's product variety mechanically increases both.
-\begin{theorem}
-    \label{prop:benchmark_results}
-    In the benchmark model with unilateral price setting, in a hybrid regime equilibrium (with $N_F > 0$), the following results hold:
-    \begin{itemize}
-        \item The equilibrium number of fringe firms decreases in the number of the platform's products: $\frac{\partial N_F}{\partial N_P} = -\frac{V_P}{V_F} < 0$.
-        \item The aggregate is independent of the platform's product variety: $\frac{\partial A}{\partial N_P} = 0$.
-        \item Consumer surplus is independent of the platform's product variety: $\frac{\partial CS}{\partial N_P} = 0$.
-        % \item The platform's profit is increasing in the number of its products: $\frac{\partial \pi_P^t}{\partial N_P} = \frac{V_P}{V_F} I_F$.
-    \end{itemize}
-\end{theorem}
-
-In contrast, in the bargaining model, increasing the platform's product variety can have a negative effect on consumer welfare.
-The reason for this is that the platform's product variety increases its bargaining power, and thus decreases the share that the fringe firms obtain.
-This in turn leads to a decrease in the number of fringe firms, and this decrease is large enough to offset the increase in the platform's product variety.
-\begin{theorem}
-    \label{prop:bargaining_results}
-    In the bargaining model, in a hybrid regime equilibrium (with $N_F > 0$), the following results hold:
-    \begin{itemize}
-        \item The equilibrium number of fringe firms decreases in the number of the platform's products more than in the benchmark case: $\frac{\partial N_F}{\partial N_P} < -\frac{V_P}{V_F} 0$.
-        \item The aggregate decreases in the platform's product variety: $\frac{\partial A}{\partial N_P} < 0$.
-        \item Consumer surplus decreases in the platform's product variety: $\frac{\partial CS}{\partial N_P} < 0$.
-    \end{itemize}
-\end{theorem}
-
-The statements of these theorems are illustrated in \cref{fig:comparative_N_F,fig:welfare_aggregate,fig:platform_profits}.
-The intuition behind these results can be demonstrated by looking at entry fees.
+The intuition behind these results can be understood by looking at entry fees.
 First, define the implied entry fee in the bargaining case as the difference between the variable profit and the final, total profit of the fringe firms (bar the investment cost)\footnote{
@@
 \begin{align*}
-    K_F^i = \frac{\pi_F^v - \pi_F^t}{N_F} - I_F.
+    K_F^{impl} = \frac{\pi_F^v - \pi_F^t}{N_F} - I_F.
 \end{align*}
 As shown before, as the platform's product variety grows, its bargaining power also increases.
-This can be thought of as an increase in (implied) entry fees $K_F^i$, which in turn discourages fringe entry.
+This can be thought of as an increase in (implied) entry fees $K_F^{impl}$, which in turn discourages fringe entry.
 \begin{proposition}
@@
     \begin{align*}
-        N_F(N_P) > 0 \implies \frac{\partial K_F^i(N_P)}{\partial N_P} > 0.
+        N_F(N_P) > 0 \implies \frac{\partial K_F^{impl}(N_P)}{\partial N_P} > 0.
     \end{align*}
 \end{proposition}
-This is not happening in the benchmark model, as the optimal entry fee does not depend on the platform's product variety.
-\Cref{fig:entry_fee} demonstrates this difference graphically.
-
-In the example parametrization, the implied entry fee is lower than what the platform would prefer to set for low values of $N_P$, and higher afterwards.
-There is an optimal platform product variety $N_P^*$ for which the implied entry fee is the same as the optimal entry fee in the benchmark model, and therefore the results of the two models are the same.
-For $N_P > N_P^*$, the platform would like to commit to a lower entry fee to incentivize more fringe entry.
-This is an example that bargaining instead of unilateral pricing does not necessarily lead to lower platform shares, or better welfare outcomes: it can be a lose-lose situation for both the platform and the consumers.
-
-Finally, let us look at the platform's profits in equilibrium.
-As in the benchmark model, they are increasing in the number platform's product variety $N_P$ (\cref{fig:platform_profits}). % TODO: can I make it a proper proposition?
-However, in contrast to that case, there is an important difference in the hybrid regime.
-In the benchmark model, the entry fee was independent of the platform's product variety.
-On the other hand, with bargaining, it is increasing in $N_P$ (\cref{fig:entry_fee}).
-Therefore, if the entry fee is lower than optimal, then the increase in $N_P$ will bring it closer to the optimal level, and the increase in platform profits will be higher than in the benchmark model.
-On the other hand, when the entry fee is already higher than optimal for a given $N_P$, an additional increase will lead to an even more suboptimal (implied) entry fee, and thus a lower increase in platform profits.
-\Cref{sec:endogenizing_n_p} explores this phenomenon in more detail.
+This is not happening in the benchmark model, because, as stated in \cref{prop:optimal_entry_fee}, the optimal entry fee does not depend on the platform's product variety.
+\Cref{fig:entry_fee} demonstrates this difference between the two models.
 
@@
     \begin{align*}
-        K_F^i(N_P) < K_F^{opt} &\implies \frac{\dd \pi_P^t}{\dd N_P} > \frac{V_P}{V_F} I_F \\
-        K_F^i(N_P) > K_F^{opt} &\implies \frac{\dd \pi_P^t}{\dd N_P} < \frac{V_P}{V_F} I_F.
+        K_F^{impl}(N_P) < K_F^{opt} &\implies \frac{\dd \pi_P^t}{\dd N_P} > \frac{V_P}{V_F} I_F \\
+        K_F^{impl}(N_P) > K_F^{opt} &\implies \frac{\dd \pi_P^t}{\dd N_P} < \frac{V_P}{V_F} I_F.
     \end{align*}
@@
 \subsection{Discussion}
-TODO: which assumptions are crucial for the results?
+\label{sec:results_discussion}
+
+\paragraph{Generality of the figures}
+While \cref{fig:entry_and_fees,fig:platform_profits,fig:welfare} illustrate the main results of this paper under a specific parametrization, many of the insights are more general.
+In particular, the higher-than-proportional decrease in the number of fringe firms as the platform's product variety increases, and the resulting negative effect on consumer welfare, have corresponding theorems that hold for any parametrization (\cref{prop:equilibrium_benchmark,prop:equilibrium_bargaining}).
+Similarly, the implied entry fee being increasing in the number of the platform's products is a general result (\cref{prop:implied_entry_fee_comparative}).
+
+One aspect that is not general is the fact that the optimal and implied entry fees, in the benchmark and bargaining models, respectively, coincide for some value of $N_P$.
+In the example parametrization, the implied entry fee is lower than what the platform would prefer to set for low values of $N_P$, and higher afterwards.
+There is an optimal platform product variety $N_P^*$ for which the implied entry fee is the same as the optimal entry fee in the benchmark model, and therefore the results of the two models are the same.
+It is possible, however, that even for arbitrarily low values of $N_P$, the implied entry fee is higher than optimal.
+In such a case, the platform would like to commit to a lower entry fee to incentivize more fringe entry, but it cannot do so.
+\Cref{sec:higher_bargaining_power} presents an example where this is the case.
+In such a setting, bargaining does not improve consumer welfare compared to unilateral price-setting, even if the platform is a pure marketplace: it can be a lose-lose situation for both the platform and the consumers.
+
+\paragraph{Consequences of the assumptions}
+The results from the benchmark model suggest that the platform's product variety is always weakly beneficial for consumers.
+Furthermore, if the platform's product variety (and thus also the pure marketplace/ hybrid mode decision) was endogenous, an improvement in the platform's product (either higher value or lower cost) would also have a positive effect on consumer welfare.
+This surprising result depends on a number of -- admittedly unrealistic -- assumptions.
+Namely, the lump-sum nature of the entry fee, no entry fee for consumers, and the platform pricing its products as if they were produced by separate sellers.
+Therefore, one should not take this result as a conclusion applicable to the real world, but as a best-case benchmark.
+On the other hand, these assumptions are also why this model is so useful as a benchmark: as I show in the case of the bargaining model, even with these assumptions in place, the platform's product can have negative welfare consequences if the entry fee is set through bargaining.
+
+Nevertheless, the results of the bargaining model do not hinge on the majority of these assumptions.
+For example, the number of consumers could be endogenous, with the platform setting an entry fee for them.
+Similarly, the platform could take into account the fact that its product prices affect the demand for its other products.
+These changes would translate into a different, possibly less tractable total profit function, but its main properties (i.e.
+being increasing in the number of platform products and fringe firms) would still hold.
+As long as \cref{lem:shape_of_fringe_profit} holds, the main results of the bargaining model would also be valid.
+
+Furthermore, the logit-like nature of the demand function is also not necessary.
+It does simplify the analysis, especially in terms of consumer welfare, but the main results would also hold for a larger class of demand functions\footnote{
+    In particular, demand functions for which the implied profit functions satisfy the assumptions in \cref{sec:more_general}.
+}.
+It is however important that the demand function is such that total profits are increasing in the number of fringe firms.
+Without this, the corresponding cooperative game is not monotone, and the bargaining microfoundations do not apply.
+%TODO: more on this assumption
+
+The other assumption that is crucial for the results is the lump-sum nature of the entry fee.
+Without it, the corresponding cooperative game would not have transferable utility, and the Shapley value would not be a meaningful solution concept.
+One alternative solution concept for that case would be the consistent Shapley value from \textcite{maschler1992consistent}, which can also be interpreted as a bargaining solution \parencite{hart1996bargaining}.
+
+\paragraph{Relation to the literature}
+Similarly to the existing literature on hybrid platforms, the latter conclusion highlights the possibly problematic aspects of hybrid operation, albeit through a novel channel.
+In \textcite{hagiu2022should}, the negative consequences are due to its incentives to engage in anti-competitive behavior, such as self-preferencing or imitation, but in lieu of those, they argue that hybrid platforms can actually be beneficial.
+\textcite{anderson2021hybrid}, on the other hand, shows that even in the absence of such behavior, hybrid platforms can harm consumers, as platforms are inclined to set higher than optimal royalties to create a price advantage for their own products.
+The distortion in their model comes from the percentage-based nature of the entry fee (royalty), incentivizing the platform to set it higher than in the pure intermediary case, to advantage its own products.
+This paper goes one step further.
+Due to the lump-sum nature of the entry fee and platforms pricing their products as if they were produced by separate sellers, the incentive is no more present (as demonstrated by the benchmark model).
+However, I demonstrate that there is another source of distortion when the entry fee is negotiated: a hybrid platform is in a better bargaining than it would be if it had no products on its own.
+This in turn leads to a higher entry fee, and thus lower consumer welfare.
 
@@
 \subsection{Players have different innate bargaining power}
-\label{sec:lower_bargaining_power}
+\label{sec:higher_bargaining_power}
 
@@
     \begin{align*}
-        K_F^* = \sqrt{\mu I_F V_F} - I_F,
+        K_F^{opt} = \sqrt{\mu I_F V_F} - I_F,
     \end{align*}
@@
 
-    Now consider the case when $K_F^*$ is so large that it would lead to no fringe entry.
+    Now consider the case when $K_F^{opt}$ is so large that it would lead to no fringe entry.
     In that case, the platform's only source of profit is selling its own products, and thus

### 2024-06-10 src/paper/application.tex
Move extensions to appendix
Fix some references

@@
 This is due to the fact that the optimal entry fee, which is independent of $N_P$, pins down the aggregate.
-As shown in \cref{fig:fig:fringe_entry_eq}, an increase in the platform's product variety will simply replace fringe firms in a constant ratio, such that the aggregate remains constant (\cref{fig:welfare_aggregate}).
-This, in turn, implies that consumer surplus is also unaffected by the platform's product variety in the hybrid regime, as demonstrated in \cref{fig:welfare_consumer}.
+As shown in \cref{fig:fringe_entry_eq}, an increase in the platform's product variety will simply replace fringe firms in a constant ratio, such that the aggregate remains constant (\cref{fig:welfare_aggregate}).
+This, in turn, implies that consumer surplus is also unaffected by the platform's product variety in the hybrid regime, as demonstrated in \cref{fig:welfare_consumer_surplus}.
 
@@
 This in turn leads to a higher entry fee, and thus lower consumer welfare.
+
+\section{Conclusion and future work}
+\label{sec:conclusion}
+
+This paper introduces a new model of hybrid platforms in which bargaining between the platform and the entrant firms plays a key role.
+It highlights the importance of a so far overlooked aspect of platforms having their own products: the fact that it increases their bargaining power compared to other players'.
+As a result, even in the absence of other frictions, hybrid platforms might have detrimental effects on fringe entry.
+This, in certain situations, such as the one described in this paper, this can lead to fewer fringe reduced product variety, and ultimately, lower consumer welfare.
+
+The contributions of this paper can be broken down into two categories.
+First, a simple, but quite general model of bargaining between one indispensable player and a continuum of potential market entrants is introduced.
+This model is applicable beyond the platform setting, and can describe other markets, such as upstream-downstream relations, or franchising, as well.
+The quite general results obtained from this model also highlight the similarities between those markets.
+Furthermore, many of the results from this paper can be applied in a plug-and-play fashion to other models of large-player-small-player interactions.
+
+The second set of contributions pertains to applying the aforementioned model to a setting with a hybrid platform.
+The demand structure is similar to the one in \textcite{anderson2021hybrid}, and the results convey the same general message: hybrid platforms can have detrimental welfare effects.
+However, the mechanism behind this result is quite different.
+This paper relies on the change in bargaing power, and shows that even in the case of lump-sum entry fees, hybrid platforms can be problematic from a welfare perspective.
+An extension of the main model also highlight the importance of the assumptions on who is participating in the bargaining process.
+
+There is a number of avenues for future research in this direction.
+First, although the results provide some suggestions about what endogenizing the number of the platform's products might entail, a more formal analysis is needed for a more complete picture.
+Second, applying the same bargaining framework, but using a different demand structure (e.g.
+CES utility) for microfounding the profit functions would have important implications for the robustness of the results.
+Finally, I believe this approach for modeling bargaining is a rather good compromise between assuming that one party has all the bargaining power, and modeling the bargaining process in detail, and some of the main ideas in this paper might be a good fit for different settings and and more applied models.
+
+\appendix
+
+\printbibliography
 
@@
 
-\section{Conclusion and future work}
-\label{sec:conclusion}
-
-This paper introduces a new model of hybrid platforms in which bargaining between the platform and the entrant firms plays a key role.
-It highlights the importance of a so far overlooked aspect of platforms having their own products: the fact that it increases their bargaining power compared to other players'.
-As a result, even in the absence of other frictions, hybrid platforms might have detrimental effects on fringe entry.
-This, in certain situations, such as the one described in this paper, this can lead to fewer fringe reduced product variety, and ultimately, lower consumer welfare.
-
-The contributions of this paper can be broken down into two categories.
-First, a simple, but quite general model of bargaining between one indispensable player and a continuum of potential market entrants is introduced.
-This model is applicable beyond the platform setting, and can describe other markets, such as upstream-downstream relations, or franchising, as well.
-The quite general results obtained from this model also highlight the similarities between those markets.
-Furthermore, many of the results from this paper can be applied in a plug-and-play fashion to other models of large-player-small-player interactions.
-
-The second set of contributions pertains to applying the aforementioned model to a setting with a hybrid platform.
-The demand structure is similar to the one in \textcite{anderson2021hybrid}, and the results convey the same general message: hybrid platforms can have detrimental welfare effects.
-However, the mechanism behind this result is quite different.
-This paper relies on the change in bargaing power, and shows that even in the case of lump-sum entry fees, hybrid platforms can be problematic from a welfare perspective.
-An extension of the main model also highlight the importance of the assumptions on who is participating in the bargaining process.
-
-There is a number of avenues for future research in this direction.
-First, although the results provide some suggestions about what endogenizing the number of the platform's products might entail, a more formal analysis is needed for a more complete picture.
-Second, applying the same bargaining framework, but using a different demand structure (e.g.
-CES utility) for microfounding the profit functions would have important implications for the robustness of the results.
-Finally, I believe this approach for modeling bargaining is a rather good compromise between assuming that one party has all the bargaining power, and modeling the bargaining process in detail, and some of the main ideas in this paper might be a good fit for different settings and and more applied models.
-
-\appendix
-
-\printbibliography
-
 \section{More general results}

### 2024-06-10 src/paper/application.tex
Define dX/dN_P notation

@@
 
-On the other hand, \cref{fig:platform_profits} shows the platform's profit (\cref{eq:platform_profits_hybrid_benchmark,eq:platform_profits_retail_benchmark}) is increasing in the number of its products.
+On the other hand, \cref{fig:platform_profits}\footnote{
+    $\frac{\dd X}{\dd N_P}$ denotes equilibrium comparative statics.
+    I.e., if the variable $X$ is a function of $N_P$ and $N_F$, then $$\frac{\dd X}{\dd N_P} = \frac{\partial X(N_P, N_F(N_P))}{\partial N_P}$$.
+} shows the platform's profit (\cref{eq:platform_profits_hybrid_benchmark,eq:platform_profits_retail_benchmark}) is increasing in the number of its products.
 \begin{corollary}
@@
     \begin{align*}
-        N_F > 0 \implies \frac{\partial \pi_P^t}{\partial N_P} = \frac{V_P}{V_F} I_F.
+        N_F(N_P) > 0 \implies \frac{\dd \pi_P^t}{\dd N_P} = \frac{V_P}{V_F} I_F.
     \end{align*}
@@
     \begin{align*}
-        \frac{\pi_F^t(N_P, N_F)}{\partial N_F} < 0 \text{ or } \frac{\partial^2 \pi_F^t(N_P, N_F)}{\partial N_F^2} < 0 \quad \forall\, N_P, N_F \geq 0.
+        \frac{\partial \pi_F^t(N_P, N_F)}{\partial N_F} < 0 \text{ or } \frac{\partial^2 \pi_F^t(N_P, N_F)}{\partial N_F^2} < 0 \quad \forall\, N_P, N_F \geq 0.
     \end{align*}

### 2024-06-19 src/paper/application.tex
Switch to constant investment cost

@@
 Let us now turn to the determination of the equilibrium number of fringe firms.
-Assume that total investment cost for the fringe is given by some increasing, weakly convex function $I_F(N_F)$.
-Note, that it includes the linear (per-firm constant) investment cost used throughout the main text.
-\begin{assumption}
-    Assume that $I_F(N_F)$ is a strictly increasing, convex, twice differentiable function:
-    \begin{align*}
-        \frac{\partial I_F(N_F)}{\partial N_F} > 0, \quad \frac{\partial^2 I_F(N_F)}{\partial N_F^2} \geq 0.
-    \end{align*}
-\end{assumption}
-
+Assume that each firm faces a lump-sum investment cost of $I_F$ to enter the market.\footnote{
+    The results would also hold if the investment cost was non-constant, as long as the marginal cost of investment is weakly increasing.
+}
+Thus, total investment cost for the fringe is given by $I_F N_F$.
 The equilibrium number of entrants is determined by a free entry condition: in the end, the fringe firms' total profits should be equal to the aggregated investment cost.
@@
     \begin{align*}
-        \pi_F(N_P, N_F) = I_F(N_F).
+        \pi_F(N_P, N_F) = I_F N_F.
     \end{align*}
@@
     Let the conditions in \cref{ass:single_crossing} hold.
-Then for any $N_F^* > 0$ for which $\pi_F(N_P, N_F^*, N_C) = I_F(N_F)$, the partial derivative of fringe profits with respect to the number of fringe firms is smaller than the marginal investment cost:
-    \begin{align*}
-        \left. \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_F} \right|_{N_F = N_F^*} < I_F'(N_F).
+Then for any $N_F^* > 0$ for which $\pi_F(N_P, N_F^*, N_C) = I_F N_F$, the partial derivative of fringe profits with respect to the number of fringe firms is smaller than the marginal investment cost $I_F$:
+    \begin{align*}
+        \left. \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_F} \right|_{N_F = N_F^*} < I_F.
     \end{align*}
@@
 
-    Next, observe that if $\partial_F \pi_F(N_P, 0, N_C) < I_F'(0)$, then there is no equilibrium with $N_F > 0$.
-    To show this, assume by contradiction that $\exists N_F^* > 0$ such that $\pi_F(N_P, N_F^*, N_C) = I_F(N_F^*)$.
-    Then the mean value theorem implies that there is a $\bar{N}_F \in (0, N_F^*)$ such that $\partial_F \pi_F(N_P, \bar{N}_F, N_C) = I_F'(\bar{N_F}) \geq I_F'(0)$.
-    However, this clearly cannot be the case as $\partial_F \pi_F(N_P, N_F, N_C) < I_F'(0)$ or $\pi_F(N_P, N_F, N_C) \leq 0$ for all $N_F > 0$.
-
-    Now let $N_F^*$ be a positive number for which $f(N_P, N_F^*, N_C) = I_F(N_F^*)$.
-    It is easy to see that $\partial \pi(N_P, N_F^*, N_C) < I_F'(N_F^*)$.
-    The reason is that if it exists, then $\partial_F \pi_F(N_P, 0, N_C) > I_F'(0)$.
-    Now if $\partial_F \pi_F(N_P, N_F, N_C) \geq I_F'(N_F) \forall N_F > 0$, then $f(N_P, N_F, N_F) > I_F(N_F)$, and the two functions do not intersect.
-    Therefore, there must exist some $\bar{N}_F > 0$ for which $\partial_F \pi_F(N_P, \bar{N}_F, N_C) < I_F'(\bar{N}_F)$.
-    This in turn implies that $\partial_F \pi_F(N_P, N_F, N_C) \leq \partial_F \pi_F(N_P, \bar{N}_F, N_C) < I_F'(\bar{N}_F) \leq I_F'(N_F)$ for all $N_F > \bar{N}_F$.
+    Next, observe that if $\partial_F \pi_F(N_P, 0, N_C) < I_F$, then there is no equilibrium with $N_F > 0$.
+    To show this, assume by contradiction that $\exists N_F^* > 0$ such that $\pi_F(N_P, N_F^*, N_C) = I_F N_F^*$.
+    Then the mean value theorem implies that there is a $\bar{N}_F \in (0, N_F^*)$ such that $\partial_F \pi_F(N_P, \bar{N}_F, N_C) = I_F$.
+    However, this clearly cannot be the case as $\partial_F \pi_F(N_P, N_F, N_C) < I_F$ or $\pi_F(N_P, N_F, N_C) \leq 0$ for all $N_F > 0$.
+
+    Now let $N_F^*$ be a positive number for which $f(N_P, N_F^*, N_C) = I_F N_F^*$.
+    It is easy to see that $\partial \pi(N_P, N_F^*, N_C) < I_F$.
+    The reason is that if it exists, then $\partial_F \pi_F(N_P, 0, N_C) > I_F$.
+    Now if $\partial_F \pi_F(N_P, N_F, N_C) \geq I_F \forall N_F > 0$, then $f(N_P, N_F, N_F) > I_F N_F$, and the two functions do not intersect.
+    Therefore, there must exist some $\bar{N}_F > 0$ for which $\partial_F \pi_F(N_P, \bar{N}_F, N_C) < I_F$.
+    This in turn implies that $\partial_F \pi_F(N_P, N_F, N_C) \leq \partial_F \pi_F(N_P, \bar{N}_F, N_C) < I_F$ for all $N_F > \bar{N}_F$.
 \end{proof}
@@
     \begin{align*}
-        \frac{\partial N_F}{\partial N_P} = \frac{\frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P}}{I_F'(N_F) - \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F}}
+        \frac{\partial N_F}{\partial N_P} = \frac{\frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P}}{I_F - \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F}}
     \end{align*}
@@
     \begin{align*}
-        \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} < I_F'(N_F),
+        \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} < I_F,
     \end{align*}
@@
     \begin{align*}
-        \frac{\partial N_F}{\partial N_P} = \frac{\frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P}}{I_F'(N_F) - \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F}}.
-    \end{align*}
-    Remember, that from \cref{lem:slope_at_eq}, and the assumption on the investment cost function we have that $\frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} < I_F'(N_F)$.
+        \frac{\partial N_F}{\partial N_P} = \frac{\frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P}}{I_F - \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F}}.
+    \end{align*}
+    Remember, that from \cref{lem:slope_at_eq}, and the assumption on the investment cost function we have that $\frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} < I_F$.
     Then, substitute $f(N_P, N_F) = g(\alpha N_P + \beta N_P)$ into $\pi_F$ to get the following fringe profit function:
@@
     First, let us show that (1) is non-negative, and, coupled with the fact that (2) is positive, omitting it increases the denominator in absolute value, thus making the whole expression larger.
-    To see this, observe that the second part of (1) is just the per-unit fringe profit, i.e.
-    \begin{align*}
-        (1) = I_F'(N_F) - \pi_F(N_P, N_F, N_C) / N_F \geq 0 \Leftrightarrow N_F I_F'(N_F) - \pi_F(N_P, N_F, N_C) \leq 0.
-    \end{align*}
-    Next, use the convexity of $I_F$ and the definition of the equilibrium to obtain
-    \begin{align*}
-        N_F I_F'(N_F) - \pi_F(N_P, N_F, N_C) \leq I_F(N_F) - \pi_F(N_P, N_F, N_C) = 0,
-    \end{align*}
-    thus proving that (1) is non-negative.
+    To see this, observe that the second part of (1) is just the per-unit fringe profit.
+    Therefore, in equilibrium, (1) must be zero:
+    \begin{align*}
+        N_F (1) = N_F I_F - \pi_F(N_P, N_F, N_C) = 0.
+    \end{align*}
 

### 2024-06-19 src/paper/application.tex
Reshuffle appendices

@@
 Furthermore, it has a number of appealing properties.
-For example, it is closely related to the marginal contributions of the players to the total value, and, as shown in \cref{sec:more_general_results}, it is also quite intuitive in terms of comparative statistics.
+For example, it is closely related to the marginal contributions of the players to the total value, and, as shown in \cref{sec:more_general_results}, it is also quite intuitive in terms of comparative statics.
 Furthermore, and perhaps more importantly, there are a number of ways to place it on non-cooperative microfoundations by setting up non-cooperative games for which the Shapley value is a subgame perfect equilibrium \parencite[e.g.][]{gul1989bargaining,hart1996bargaining,stole1996organizational}.
@@
 \end{proposition}
+\begin{proof}[Proof of \cref{prop:demand_function}]
+    See Theorem 1 in \textcite{anderson2021hybrid}.
+\end{proof}
 
@@
 
-\subsection{Three sided bargaining }
+\subsection{Three sided bargaining}
 \label{sec:two_sided}
@@
 
-\section{More general results}
+\section{Generalization and proofs}
 \label{sec:more_general}
@@
 This section presents those and the necessary assumptions.
-The proofs for many of the propositions in the main text also rely on these more general results.
+As the results on the main text are not proven directly, but rather derived from the general results, the proofs are also included here.
 
@@
 
-Apart from the cooperative foundations, one major justification for this profit allocation rule is its intuitive behavior in terms of comparative statistics.
+Apart from the cooperative foundations, one major justification for this profit allocation rule is its intuitive behavior in terms of comparative statics.
 To illustrate this, let us examine what happens when one varies the substitutability between the fringe firms.
@@
     \label{prop:outcome_based_bargaining_power}
+    Assume that \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing} hold.
     Fix some $N_P, N_C \geq 0$.
@@
 \end{proposition}
+\begin{proof}[Proof of \cref{prop:outcome_based_bargaining_power}]
+    Immediately follows from the monotonicity of the integral.
+\end{proof}
 
@@
     \label{prop:unique_equilibrium_more_general}
-    Under the conditions in \cref{ass:single_crossing}, the equilibrium is unique if it exists.
+    Under the conditions in \cref{ass:free_entry,ass:single_crossing}, the equilibrium is unique if it exists.
 \end{proposition}
+\begin{proof}[Proof of \cref{prop:unique_equilibrium_more_general}]
+    \Cref{lem:slope_at_eq} states that for any positive $N_F^*$ for which $\pi_F(N_P, N_F^*) - N_F I_F$, the partial derivative with respect to the number of fringe firms is negative.
+    Now assume by contradiction that $\exists 0 < N_F^* < N_F^{**}$ such that $\pi_F(N_P, N_F^*) = I_F N_F^*$ and $\pi_F(N_P, N_F^{**}) = I_F N_F^{**}$.
+    But then the mean value theorem implies that there is a $\bar{N}_F \in (N_F^*, N_F^{**})$ such that $\partial_F \pi_F(N_P, \bar{N}_F) = I_F$.
+    This is a contradiction, as $\partial_F \pi_F(N_P, N_F) < I_F$ for all $N_F^* < N_F$.
+\end{proof}
+
 The intuition behind this result is that \cref{ass:single_crossing} ensures that the total profits achieved by the fringe is either concave or hump-shaped.
@@
     \label{prop:share_of_platform}
-    Assume that $f$ is continuously differentiable with respect to $N_P$ and also twice differentiable.
+    Let \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing} hold.
+    Further assume that $f$ is continuously differentiable with respect to $N_P$ and also twice differentiable.
     Let $N_F \geq 0$.
@@
 \end{proposition}
+\begin{proof}[Proof of \cref{prop:share_of_platform}]
+    $f(N_P, N_F)$ is continuously differentiable in $N_P$, therefore the Leibniz rule can be applied to obtain
+    \begin{align*}
+        \frac{\partial \pi_P(N_P, N_F, N_C)}{\partial N_P} &= N_C \frac{\partial}{\partial N_P} \int_0^1 w_P(s) f(N_P, N_F) \ds \\
+        &= \int_0^1 w_P(s) \underbrace{\frac{\partial f(N_P, sN_F)}{\partial N_P}}_{> 0} \ds > 0
+    \end{align*}
+    for any non-negative, continuous $w_P(s)$.
+\end{proof}
 While it might seem obvious, let us still examine what this result does and does not mean.
@@
     \label{prop:share_of_fringe}
-    Assume that $f, w$ are twice continuously differentiable.
+    Let \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing} hold.
+    Furthermore, assume that $f, w$ are twice continuously differentiable.
     Let $N_F > 0$.
@@
 \end{proposition}
+\begin{proof}[Proof of \cref{prop:share_of_fringe}]
+    Remember that
+    \begin{align*}
+        \pi_F(N_P, N_F, N_C) = N_C \int_0^1 w_F(s) N_F \partial_2 f(N_P, s N_F) \ds,
+    \end{align*}
+    By assumption, $f$ is twice continuously differentiable, therefore $\partial_2$ is also continuously differentiable in $N_P$.
+    Thus, the Leibniz rule can be applied to obtain
+    \begin{align*}
+        \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P} &= \frac{\partial}{\partial N_P} N_C \int_0^1 w_F(s) N_F \partial_2 f(N_P, s N_F) \ds \\
+        &= N_C \int_0^1 w_F(s) N_F \frac{\partial}{\partial N_P} \partial_2 f(N_P, s N_F) \ds \\
+        &= N_C \int_0^1 w_F(s) N_F \partial^2_{12} f(N_P, s N_F) \ds.
+    \end{align*}
+
+    As $w_F(s) \geq 0$ for $s > 0$, if $\partial_2 f(N_P, s N_F)$ has the same sign over $[0, N_F]$, then the integral also has the same sign.
+    Formally,
+    \begin{align*}
+        \forall n_F \in [0, N_F] \enspace \frac{\partial^2 f(N_P, n_F)}{\partial N_P \partial n_F} < 0 &\implies \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P} < 0 \\
+        \forall n_F \in [0, N_F] \enspace \frac{\partial^2 f(N_P, n_F)}{\partial N_P \partial n_F} > 0 &\implies \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P} > 0
+    \end{align*}
+\end{proof}
 In summary, when they are mostly substitutes (the cross-derivatives of $f$ are negative), the fringe's profits decrease as a result of an increase in $N_F$.
@@
     \label{cor:fringe_entry}
-    Assume that $f, w$ are twice continuously differentiable.
+    Let \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:free_entrya,ass:single_crossing} hold.
+    Furthermore, assume that $f, w$ are twice continuously differentiable.
     Let $N_F^*$ denote the equilibrium number of fringe firms.
@@
 \end{corollary}
+\begin{proof}[Proof of \cref{cor:fringe_entry}]
+    \Cref{prop:unique_equilibrium} establishes that if an equilibrium with $N_F > 0$ exists, it is unique.
+    Use the implicit function theorem on the equation from \cref{ass:free_entry} to obtain
+    \begin{align*}
+        \frac{\partial N_F}{\partial N_P} = \frac{\frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P}}{I_F - \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F}}
+    \end{align*}
+    The derivative exists if the above expression is well-defined, i.e. $\frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} \neq I_F$.
+    Remember from \cref{prop:share_of_fringe} that the numerator of this expression is negative under the condition $\frac{\partial^2 f(N_P, N_F, N_C)}{\partial N_P \partial N_F}$.
+    Now all we need to show to conclude the proof is that
+    \begin{align*}
+        \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} < I_F,
+    \end{align*}
+    which is the statement of \cref{lem:slope_at_eq}.
+\end{proof}
+
 That is, the equilibrium number of entrants increases as a response to an increase in $N_P$ if the platform and the fringe firms are complements, and decreases if they are substitutes.
@@
     \label{prop:aggregate_size_additive}
-    Let $f$ have the additive form from \cref{ass:additive_profit}.
+    Let \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:free_entrya,ass:single_crossing,ass:additive_profit} hold.
     Then
@@
 \end{proposition}
+\begin{proof}[Proof of \cref{prop:aggregate_size_additive}]
+    Use the implicit function theorem to get the equilibrium number of fringe firms as a function of the platform's product variety:
+    \begin{align*}
+        \frac{\partial N_F}{\partial N_P} = \frac{\frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P}}{I_F - \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F}}.
+    \end{align*}
+    Remember, that from \cref{lem:slope_at_eq}, and the assumption on the investment cost function we have that $\frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} < I_F$.
+    Then, substitute $f(N_P, N_F) = g(\alpha N_P + \beta N_P)$ into $\pi_F$ to get the following fringe profit function:
+    \begin{align*}
+        \pi_F(N_P, N_F, N_C) = \beta N_C N_F \int_0^1 w_F(s) g'(\alpha N_P + s \beta N_F) \ds.
+    \end{align*}
+    Differentiate it with respect to $N_P$ and $N_F$ and substitute into the first expression to obtain
+    \begin{align*}
+        \frac{\partial N_F}{\partial N_P} = \frac{
+            \alpha \beta N_C N_P \int_0^1 w_F(s) g''(\alpha N_P + s \beta N_F) \ds
+        }{
+            \underbracket{I'_F(N_F) - \beta N_C \int_0^1 w_F(s) g'(\alpha N_P + s \beta N_F) \ds}_{(1)} - \underbracket{\beta^2 N_C N_F \int_0^1 w_F(s) s g''(\alpha N_P + s \beta N_F) \ds}_{(2)}.
+        }
+    \end{align*}
+    From \cref{lem:slope_at_eq}, we know that the denominator of this expression is positive.
+    Furthermore, the concavity of $g$ implies that expression (2) is also positive.
+    Finally, from \cref{prop:share_of_fringe}, we have that the whole expression must be negative.
+
+    First, let us show that (1) is non-negative, and, coupled with the fact that (2) is positive, omitting it increases the denominator in absolute value, thus making the whole expression larger.
+    To see this, observe that the second part of (1) is just the per-unit fringe profit.
+    Therefore, in equilibrium, (1) must be zero:
+    \begin{align*}
+        N_F (1) = N_F I_F - \pi_F(N_P, N_F, N_C) = 0.
+    \end{align*}
+
+    Next, observe that we can bound (2) from above using the fact that $0 \leq s \leq 1$:
+    \begin{align*}
+        (2) \leq \beta^2 N_C N_F \int_0^1 w_F(s) g''(\alpha N_P + s \beta N_F) \ds.
+    \end{align*}
+    For the same reason as before, it also bounds the whole expression from above.
+
+    Putting it all together, we have that
+    \begin{align*}
+        \frac{\partial N_F}{\partial N_P} \leq \frac{\alpha \beta N_C N_P \int_0^1 w_F(s) g''(\alpha N_P + s \beta N_F) \ds}{\beta^2 N_C N_F \int_0^1 w_F(s) g''(\alpha N_P + s \beta N_F) \ds} = -\frac{\alpha}{\beta},
+    \end{align*}
+    which is the first statement of the proposition.
+
+    To prove the second part of the proposition, differentiate total profits with respect to $N_P$:
+    \begin{align*}
+        \frac{\partial \Pi(N_P, N_F^*(N_P), N_C)}{\partial N_F} &= \frac{\partial}{\partial N_F} N_C g(\alpha N_P + \beta N_F^*(N_P)) \\
+        &= \underbrace{N_C g'(\alpha N_P + \beta N_F^*(N_P))}_{> 0} \left[ \alpha + \beta \frac{\partial N_F^*(N_P)}{\partial N_P} \right] \\
+        &< N_C g'(\alpha N_P + \beta N_F^*(N_P)) \left[ \alpha + \beta \left( -\frac{\alpha}{\beta} \right) \right] \\
+        &= 0.
+    \end{align*}
+\end{proof}
 
@@
 
-\section{The platform game and the (weighted) Shapley value}
-\label{sec:cooperative_game}
-
-In this section, I describe how the profit sharing rule from \cref{ass:profit_sharing} can be derived from various cooperative games.
-In each of the following subsections, I formally define a cooperative game that models the platform setting, and derive the (weighted) Shapley values of the various players.
-I show that they correspond to the formulas given in \cref{ass:profit_sharing}, with a specific choice of weight functions $w_P$ and $w_F$ for each case.
-
-I start with the simplest case: one-sided bargaining and the usual Shapley value \parencite{shapley1953additive}.
-Then, I look at weighted values \parencite{weber1988probabilistic} in the same cooperative game.
-Finally, I consider the case when the consumers also participate in the bargaining process, and derive the corresponding Shapley values.
-
-\subsection{One-sided case}
-\label{sec:cooperative_game_one_sided}
-
-In the first setting, the platform and the fringe firms bargain over the total profits they generate together, and the consumers are not included in the negotiations.
-The following cooperative game describes this case.
-
-Consider the game $\mathcal{G} = (\mathcal{N}, v)$, characterized by the set of players $\mathcal{N}$ and its characteristic function $v$.
-The set of players consists of the platform plus the fringe firms: $\mathcal{N} = \{P, F_i\}, i \in [0, N_F]$.
-Because the platform is indispensable, the value of a coalition $S$ is zero without the platform, and depends on the number of fringe firms otherwise:
-\begin{align*}
-    v(S) = \begin{cases}
-        0 & \text{if } P \notin S \\
-        f(N_P, n_F(S)) & \text{if } P \in S
-    \end{cases},
-\end{align*}
-where $n_F(S)$ is the measure of fringe firms in $S$.
-
-The following proposition describes the Shapley value of the platform ($\varphi_P(\mathcal{G})$) and the fringe firms ($\varphi_F(\mathcal{G})$) in this game.
-
-\begin{proposition}
-    \label{prop:profit_sharing_one_sided}
-    Consider the cooperative game above.
-    Then, the Shapley values of the platform and the fringe firms are given by
-    \begin{align*}
-        \varphi_P(\mathcal{G}) &= \int_0^1 f(N_P, s N_F) \ds, \\
-        \varphi_P(\mathcal{F}) &= \int_0^1 s N_F \partial_2 f(N_P, s N_F) \ds.
-    \end{align*}
-\end{proposition}
-
-\begin{proof}[Proof of \cref{prop:profit_sharing_one_sided}]
-    This result is a direct application of Proposition 3 and Corollary 2 in \textcite{stancsics2023value}.
+\subsection{Additional lemmas}
+\label{sec:lemmas}
+This subsection contains a couple of lemmas that are, while not very interesting on their own, necessary for the proofs in the previous sections.
+The first lemma is helpful for establishing whether \cref{ass:single_crossing} holds under a certain $f$ function.
+It states that showing that it holds for any affine transformation of $f$ is sufficient.
+\begin{lemma}
+    \label{lem:single_crossing_affine_transformation}
+    Let $g: \mathbb{R}^+ \to \mathbb{R}$ be a twice continuously differentiable function.
+    Define
+    \begin{align*}
+        G(x) = \int_0^1 g(sx) \ds.
+    \end{align*}
+    Assume that for any $x \geq 0$, $G'(x) < 0$ or $G''(x) < 0$.
+
+    Let $h(x) = c g(a + bx)$ for some $a, c > 0$ and $b > 0$.
+    Then the function $H(x) = \int_0^1 h(sx) \ds$ satisfies the same conditions: for any $x \geq 0$, $h'(x) < 0$ or $h''(x) < 0$.
+\end{lemma}
+\begin{proof}[Proof of \cref{lem:single_crossing_affine_transformation}]
+    Differentiating $H$ yields
+    \begin{align*}
+        H'(x) &= \int_0^1 h'(sx) \ds \\
+              &= \int_0^1 c b g'(a + bsx) \ds \\
+              &= c b G'(a + bsx).
+    \end{align*}
+    Similarly, the second derivative is
+    \begin{align*}
+        H''(x) &= \int_0^1 h''(sx) \ds \\
+               &= \int_0^1 c b^2 g''(a + bsx) \ds \\
+               &= c b^2 G''(a + bsx).
+    \end{align*}
+    Now, for any $x \geq 0$, $y = a + bsx \geq 0$, therefore $G'(y) < 0$ or $G''(y) < 0$.
+    As $c, b > 0$, this implies that $H'(x) < 0$ or $H''(x) < 0$.
 \end{proof}
 
-As an immediate consequence, if bargaining outcomes are described by the Shapley value, then the resulting allocations satisfy \cref{ass:profit_sharing} with $w_P(s) \equiv 1$ and $w_F(s) = s$.
-
-\subsection{Weighted value}
-\label{sec:cooperative_game_weighted}
-
-Now let us generalize the previous result, and assume instead that players' shares are described by their weighted values,
-As before, let us start by formally describing the cooperative game.
-The set of players and the characteristic function are the same as in \cref{sec:cooperative_game_one_sided}, but now the game is additionally endowed with a weight system $\mathbf{\lambda} = \{\lambda_P, \lambda_{F}(i)\}$.
-Let us assume that all fringe players have the same weight $\lambda_{F}(i) \equiv 1$.
-
-Then, the weighted values of the players are described by the following proposition.
-
-\begin{proposition}
-    \label{prop:profit_sharing_weighted}
-    Consider the cooperative game above.
-    Then, the weighted values of the platform and the fringe firms are given by
-    \begin{align*}
-        \varphi_P(\mathcal{G}) &= \int_0^1 \lambda_P s ^ {\lambda_P - 1} f(N_P, s N_F) \ds, \\
-        \varphi_F(\mathcal{G}) &= \int_0^1 s ^ {\lambda_P} N_F \partial_2 f(N_P, s N_F) \ds.
-    \end{align*}
-\end{proposition}
-
-\begin{proof}[Proof of \cref{prop:profit_sharing_weighted}]
-    This result is a direct application of Proposition 4 in \textcite{stancsics2023value}.
+The second one is useful for establishing the single crossing property for the fringe profits and investment costs.
+It states that in an equilibrium, the slope of the fringe profit function is smaller than the investment cost.
+\begin{lemma}
+    \label{lem:slope_at_eq}
+    Let the conditions in \cref{ass:single_crossing} hold.
+Then for any $N_F^* > 0$ for which $\pi_F(N_P, N_F^*, N_C) = I_F N_F$, the partial derivative of fringe profits with respect to the number of fringe firms is smaller than the investment cost $I_F$:
+    \begin{align*}
+        \left. \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_F} \right|_{N_F = N_F^*} < I_F.
+    \end{align*}
+\end{lemma}
+\begin{proof}[Proof of \cref{lem:slope_at_eq}]
+    \cref{ass:single_crossing} states that at any $N_F \geq 0$, $\pi_F(N_P, N_F, N_C)$ is either concave or decreasing in $N_F$.
+    In the remainder, let us denote partial derivatives as follows:
+    \begin{align*}
+        \partial_F \pi_F(N_P^*, N_F^*, N_C^*) \coloneqq \left. \frac{\partial \pi_F(N_P, N_F,  )}{\partial N_F} \right|_{N_P = N_P*, N_F = N_F^*, N_C = N_C^*}.
+    \end{align*}
+
+    Notice that the fact that $\pi_F$ is concave or decreasing in $N_F$ implies that if $\partial_F \pi_F(N_P, N_F', N_C)$ for some $N_F' \geq 0$, then $\partial_F \pi_F(N_P, N_F'', N_C) < \partial_F \pi_F(N_P, N_F', N_C)$ for any $\tilde{N_F} < \bar{N_F}$.
+
+    Next, observe that if $\partial_F \pi_F(N_P, 0, N_C) < I_F$, then there is no equilibrium with $N_F > 0$.
+    To show this, assume by contradiction that $\exists N_F^* > 0$ such that $\pi_F(N_P, N_F^*, N_C) = I_F N_F^*$.
+    Then the mean value theorem implies that there is a $\bar{N}_F \in (0, N_F^*)$ such that $\partial_F \pi_F(N_P, \bar{N}_F, N_C) = I_F$.
+    However, this clearly cannot be the case as $\partial_F \pi_F(N_P, N_F, N_C) < I_F$ or $\pi_F(N_P, N_F, N_C) \leq 0$ for all $N_F > 0$.
+
+    Now let $N_F^*$ be a positive number for which $f(N_P, N_F^*, N_C) = I_F N_F^*$.
+    It is easy to see that $\partial \pi(N_P, N_F^*, N_C) < I_F$.
+    The reason is that if it exists, then $\partial_F \pi_F(N_P, 0, N_C) > I_F$.
+    Now if $\partial_F \pi_F(N_P, N_F, N_C) \geq I_F \forall N_F > 0$, then $f(N_P, N_F, N_F) > I_F N_F$, and the two functions do not intersect.
+    Therefore, there must exist some $\bar{N}_F > 0$ for which $\partial_F \pi_F(N_P, \bar{N}_F, N_C) < I_F$.
+    This in turn implies that $\partial_F \pi_F(N_P, N_F, N_C) \leq \partial_F \pi_F(N_P, \bar{N}_F, N_C) < I_F$ for all $N_F > \bar{N}_F$.
 \end{proof}
 
-As before, the resulting allocations satisfy \cref{ass:profit_sharing} with $w_P(s) \equiv \lambda_P s ^ {\lambda_P - 1}$ and $w_F(s) = s ^ {\lambda_P}$.
-
-\subsection{Two-sided case}
-\label{sec:cooperative_game_two_sided}
-
-Finally, in certain settings, it might be appropriate to assume that the consumers (or, more generally, the entities on the other side of the market) also engage in the bargaining process.
-The cooperative game describing can be formalized as follows.
-
-The set of players consists of the platform plus the fringe firms: $\mathcal{N} = \{P, F_i, C_j\}, i \in [0, N_F], j \in [0, N_C]$.
-The value of a coalition $S$ is zero without the platform, and depends on the number of fringe firms otherwise:
-\begin{align*}
-    v(S) = \begin{cases}
-        0 & \text{if } P \notin S \\
-        n_C(S) f(N_P, n_F(S)) & \text{if } P \in S
-    \end{cases},
-\end{align*}
-where $n_F(S)$ and $n_C(S)$ is the measure of fringe firms and consumers, respectively, in $S$.
-
-As in the one-sided case, simple expressions exist for the Shapley value of the platform ($\varphi_P(\mathcal{G})$), fringe firms ($\varphi_F(\mathcal{G})$) and consumers ($\varphi_C(\mathcal{G})$).
-
-\begin{proposition}
-    \label{prop:profit_sharing_two_sided}
-    Consider the case when only the platform and the fringe firms participate in the bargaining process.
-    Then, the resulting profit shares are given by
-    \begin{align*}
-        \varphi_P(\mathcal{G}) &= N_C \int_0^1 s f(N_P, s N_F) \ds, \\
-        \varphi_F(\mathcal{G}) &= N_C \int_0^1 s^2 N_F \partial_2 f(N_P, s N_F) \ds \\
-        \varphi_C(\mathcal{G}) &= N_C \int_0^1 s f(N_P, s N_F) \ds.
-    \end{align*}
-\end{proposition}
-\begin{proof}[proof of \cref{prop:profit_sharing_two_sided}]
-    This result is a direct application of Proposition 11 in \textcite{stancsics2023value}.
+\begin{proof}[Proof of \cref{prop:optimal_profit}]
+    The profit function for product $Ti$ is the following:
+    \begin{align*}
+        \pi^v_{T_i}(p_{T_i}) &= (p_{T_i} - c_T) x_{T_i}(p_{Ti}) \\
+        &= (p_{T_i} - c_T) \frac{\exp\left( \frac{v_T - p_{T_i}}{\mu} \right)}{A}.
+    \end{align*}
+    Note that $A$ is not influenced by changes in $p_{T_i}$, as $A$ is an integral and $p_T$ is only changed on a zero-measure (singleton) set.
+    Therefore, let calculate the first order condition while treating $A$ as a constant:
+    \begin{align}
+        \label{eq:foc_profit}
+        \mu \frac{\exp\left( \frac{v_T - p_{T_i}}{\mu} \right)}{A} \left[ \frac{p_T - c_T}{\mu} - 1 \right] = 0.
+    \end{align}
+    Also note that $\pi_{T_i}(p_{T_i})$ is strictly concave, so the FOC is sufficient for optimality.
+
+    Now simply rearrange \cref{eq:foc_profit} to obtain
+    \begin{align*}
+        p_{T_i}^* = c_T + \mu
+    \end{align*}
+    and substitute it into the profit function to get
+    \begin{align*}
+        \pi_{T_i}^{v*} = \mu \frac{\exp \left( \frac{v_T - c_T - \mu}{\mu} \right)}{A}.
+    \end{align*}
 \end{proof}
 
-One thing to note is that the platform's and fringe firms' shares are lower than in the one-sided case.
-This is due to the fact of needing to share the pie with the consumers, too.
-Additionally, the platform's share is identical to the consumers' (aggregated) share.\footnote{
-    This stems from the linearity of the profit function in the number of consumers.
-}
-This foreshadows the idea that -- even though it might not be welfare-maximizing -- what's good for the platform might also good for the consumers in the two-sided case.
-Finally, as in both examples before, these values satisfy \cref{ass:profit_sharing} with $w_P(s) = s$ and $w_F(s) = s^2$.
-
-\section{Non-cooperative microfoundations for the bargaining outcome}
+\begin{proof}[Proof of \cref{prop:equilibrium_aggregate_benchmark}]
+    From \cref{prop:optimal_profit}, the variable profit of each fringe firm is $\pi_{F_i}^{v*} = \mu V_F / A$.
+    Total profit after entry fees and investment costs is therefore $\pi_{F_i}^{t*} = \mu V_F / A - I_F - K_F$.
+    Under free entry, total profits are zero:
+    \begin{align*}
+        0 = \pi_{F_i}^{t*} = \mu V_F / A - K_F - I_F.
+    \end{align*}
+    Simple rearrangement gives the formula we are looking for,
+    \begin{align*}
+        A = \mu \frac{V_F}{K_F + I_F},
+    \end{align*}
+    and substituting in $A = N_P V_P + N_F V_F + 1$ yields the equilibrium number of fringe firms,
+    \begin{align*}
+        N_F = \frac{\mu}{K_F + I_F} - N_P \frac{V_P}{V_F} - \frac{1}{V_F}.
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:optimal_entry_fee}]
+    The total profit function of the platform is the following:
+    \begin{align*}
+        \pi_P^t &= \pi_P^v + K_F N_F \\
+        &= \mu \frac{N_P V_P}{K_F + I_F} + K_F \left[ \frac{\mu}{K_F + I_F} - N_P \frac{V_P}{V_F} - \frac{1}{V_F} \right].
+    \end{align*}
+    The function is strictly concave in $K_F$, so the first order condition is sufficient for optimality in the case of an interior solution.
+    Assume that the optimum is indeed interior.
+    Then the FOC is
+    \begin{align*}
+        \frac{\mu I_F V_F - (K_F + I_F)^2}{V_F (K_F + I_F)^2} = 0.
+    \end{align*}
+    Rearranging it gives the optimal entry fee
+    \begin{align*}
+        K_F^{opt} = \sqrt{\mu I_F V_F} - I_F,
+    \end{align*}
+    and substituting it into the profit function leads to
+    \begin{align*}
+        \pi_P^{*t} = \mu - 2\sqrt{\frac{I_F \mu}{V_F}} + \frac{I_F}{V_F} (N_P V_P + 1).
+    \end{align*}
+    Finally, note that
+    \begin{align*}
+        \pi_P^{*t} \geq \mu \frac{N_P V_P}{N_P V_P + 1},
+    \end{align*}
+    i.e., the profit that the platform could achieve by excluding the fringe completely.
+    Therefore, the optimum is indeed interior whenever $K_F$ is low enough
+
+    Now consider the case when $K_F^{opt}$ is so large that it would lead to no fringe entry.
+    In that case, the platform's only source of profit is selling its own products, and thus
+    \begin{align*}
+        \pi_P^{t} = \pi_P^{v} = \mu \frac{ N_P V_P}{N_P V_P + 1}.
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:platform_profits_bargaining}]
+    Simply integrate the total industry profit function with respect to the mass of fringe entrants obtain the platform's share of the pie:
+    \begin{align*}
+        \pi^t_P &= \int_0^1 f(N_P, sN_F) \ds \\
+        &= \mu \int_0^1 \frac{N_P V_P + s N_F V_F}{N_P V_P + s N_F V_F + 1} \ds \\
+        &= \mu \left[ 1 - \frac{\log \left(1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} \right].
+    \end{align*}
+    The fringe's share is just the remainder,
+    \begin{align*}
+        f(N_P, N_F) - \int_0^1 f(N_P, sN_F) \ds = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right]
+    \end{align*}
+    Finally, remember that the investment cost of the fringe is fixed at the bargaining stage, and is therefore not included in the bargaining outcome.
+    Therefore, the total profits of the complete fringe are
+    \begin{align*}
+        \pi^t_P = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F N_F.
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of \cref{lem:shape_of_fringe_profit}]
+    First, consider the function
+    \begin{align*}
+        g(x) = \frac{sx}{1 + sx}.
+    \end{align*}
+    Also, let us define
+    \begin{align*}
+        G(x) &= \int_0^1 s g(sx) \ds \\
+        &= \frac{\log(x+1)}{x} + \frac{1}{x(x+1)} - \frac{1}{x}.
+    \end{align*}
+
+    Differentiation with respect to $x$ yields that
+    \begin{align*}
+        G'(x) < 0 \iff \log(x+1) > \frac{x (2x+1)}{(x+1)^2}
+    \end{align*}
+    and
+    \begin{align*}
+        G''(x) < 0 \iff \log(x+1) < \frac{x (5x^2 + 5x + 2)}{2 (x+1)^3}.
+    \end{align*}
+    There exists $\bar{x} > 0$\footnote{
+        $\bar{x} = 3$ is such a number.
+    }, such that the first equality holds for all $x > \bar{x}$, and the second for all $x < \bar{x}$.
+    Therefore, $G$ is either concave or decreasing for all $x > 0$.
+
+    Now let us consider the function $h(x) = N_C \mu g(N_P V_P + V_F x)$.
+    By \cref{lem:single_crossing_affine_transformation}, $H(x) = \int_0^1 s h'(sx) \ds$ is also either concave or decreasing for any $x > 0$.
+    Finally, notice that $H(x)$ is exactly the profit function of the fringe:
+    \begin{align*}
+        \pi_F(N_P, N_F) = \int_0^1 N_F h'(s N_F) \ds,
+    \end{align*}
+    thus proving the lemma.
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:unique_equilibrium}]
+    \Cref{lem:shape_of_fringe_profit} demonstrates that the fringe total profit function is either concave or decreasing in the number of fringe firms.
+    Thus, \cref{ass:single_crossing} is satisfied, and \cref{prop:unique_equilibrium_more_general} implies that the equilibrium number of fringe entrants is unique.
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:fringe_profits_partial}]
+    $\pi^t_F(N_P ,N_F)$ adheres to the \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing}.
+    Furthermore, 
+    \begin{align*}
+        \frac{\partial^2 \pi^t_F(N_P ,N_F)}{\partial N_P \partial N_F} < 0 \quad \forall\, N_P, N_F \geq 0.
+    \end{align*}
+    Therefore, by \cref{prop:share_of_fringe},
+    \begin{align*}
+        \frac{\partial \pi^t_F(N_P, N_F)}{\partial N_P} < 0 \quad \forall\, N_P, N_F \geq 0.
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:N_F_comparative_equilibrium}]
+    $\pi^t_F(N_P ,N_F)$ adheres to the \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:additive_profit}.
+    Therefore, by \cref{prop:aggregate_size_additive}
+    \begin{align*}
+        N_F > 0 \implies \frac{\partial N_F}{\partial N_P} < -\frac{V_P}{V_F}
+    \end{align*}
+    immediately follows.
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:aggregate_comparative_hybrid}]
+    The first statement follows immediately from
+    \begin{align*}
+        A = N_P V_P + N_F V_F + 1
+    \end{align*}
+    and
+    \begin{align*}
+        \frac{\partial N_F}{\partial N_P} < -\frac{V_P}{V_F}
+    \end{align*}
+    from \cref{prop:N_F_comparative_equilibrium}.
+    The second part is a consequence of
+    \begin{align*}
+        CS \propto \log(A).
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:aggregate_comparative_retail}]
+    The first statement trivially follows from
+    \begin{align*}
+        A = N_P V_P + 1.
+    \end{align*}
+    The second part is a consequence of
+    \begin{align*}
+        CS \propto \log(A).
+    \end{align*}
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:benchmark_results}]
+    The respective results are stated in \cref{prop:equilibrium_aggregate_benchmark} and \cref{prop:consumer_surplus_benchmark}.
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:bargaining_results}]
+    The respective results are stated in \cref{prop:N_F_comparative_equilibrium} and \cref{prop:aggregate_comparative_hybrid}.
+\end{proof}
+
+\section{Bargaining microfoundations and the cooperative game}
+This section examines the bargaining assumption from the main text in more detail.
+I proceed in two steps.
+First, I provides non-cooperative microfoundations for using the cooperative approach in the first place.
+Afterwards, I describe the aforementioned cooperative game in full formality, and derive the (weighted) Shapley value of this game.
+
+\subsection{Non-cooperative microfoundations for the bargaining outcome}
 \label{sec:bargaining_microfoundation}
@@
 However, as I argue later on, it is equivalent to bargaining over entry fees.
-Finally, this section focuses on the main model, with two-sided bargaining, and the Shapley value as the equilibrium concept.
+Finally, this section focuses on the main model, with two-sided bargaining, and the Shapley value as the solution concept.
 However, the same logic can be applied to the extensions presented in \cref{sec:extensions}, based on sections 3.1 and 3.2 of \textcite{stole1996intra}.
@@
 
+\subsection{Cooperative game}
+\label{sec:cooperative_game}
+
+Now let us examine how the profit sharing rule from \cref{ass:profit_sharing} can be derived from various cooperative games.
+In each of the following subsections, I formally define a cooperative game that models the platform setting, and derive the (weighted) Shapley values of the various players.
+I show that they correspond to the formulas given in \cref{ass:profit_sharing}, with a specific choice of weight functions $w_P$ and $w_F$ for each case.
+
+I start with the simplest case: one-sided bargaining and the usual Shapley value \parencite{shapley1953additive}.
+Then, I look at weighted values \parencite{weber1988probabilistic} in the same cooperative game.
+Finally, I consider the case when the consumers also participate in the bargaining process, and derive the corresponding Shapley values.
+
+\subsubsection{One-sided case}
+\label{sec:cooperative_game_one_sided}
+
+In the first setting, the platform and the fringe firms bargain over the total profits they generate together, and the consumers are not included in the negotiations.
+This corresponds to the model in the main text.
+The following cooperative game describes this case.
+
+Consider the game $\mathcal{G} = (\mathcal{N}, v)$, characterized by the set of players $\mathcal{N}$ and its characteristic function $v$.
+The set of players consists of the platform plus the fringe firms: $\mathcal{N} = \{P, F_i\}, i \in [0, N_F]$.
+Because the platform is indispensable, the value of a coalition $S$ is zero without the platform, and depends on the number of fringe firms otherwise:
+\begin{align*}
+    v(S) = \begin{cases}
+        0 & \text{if } P \notin S \\
+        f(N_P, n_F(S)) & \text{if } P \in S
+    \end{cases},
+\end{align*}
+where $n_F(S)$ is the measure of fringe firms in $S$.
+
+The following proposition describes the Shapley value of the platform ($\varphi_P(\mathcal{G})$) and the fringe firms ($\varphi_F(\mathcal{G})$) in this game.
+
+\begin{proposition}
+    \label{prop:profit_sharing_one_sided}
+    Consider the cooperative game above.
+    Then, the Shapley values of the platform and the fringe firms are given by
+    \begin{align*}
+        \varphi_P(\mathcal{G}) &= \int_0^1 f(N_P, s N_F) \ds, \\
+        \varphi_P(\mathcal{F}) &= \int_0^1 s N_F \partial_2 f(N_P, s N_F) \ds.
+    \end{align*}
+\end{proposition}
+\begin{proof}[Proof of \cref{prop:profit_sharing_one_sided}]
+    This result is a direct application of Proposition 3 and Corollary 2 in \textcite{stancsics2023value}.
+\end{proof}
+
+As an immediate consequence, if bargaining outcomes are described by the Shapley value, then the resulting allocations satisfy \cref{ass:profit_sharing} with $w_P(s) \equiv 1$ and $w_F(s) = s$.
+
+\subsubsection{Weighted value}
+\label{sec:cooperative_game_weighted}
+
+Now let us generalize the previous result, and assume instead that players' shares are described by their weighted values.
+As before, let us start by formally describing the cooperative game.
+The set of players and the characteristic function are the same as in \cref{sec:cooperative_game_one_sided}, but now the game is additionally endowed with a weight system $\mathbf{\lambda} = \{\lambda_P, \lambda_{F}(i)\}$.
+Let us assume that all fringe players have the same weight $\lambda_{F}(i) \equiv 1$.
+This describes the situation in \cref{sec:higher_bargaining_power}.
+
+Then, the weighted values of the players are described by the following proposition.
+
+\begin{proposition}
+    \label{prop:profit_sharing_weighted}
+    Consider the cooperative game above.
+    Then, the weighted values of the platform and the fringe firms are given by
+    \begin{align*}
+        \varphi_P(\mathcal{G}) &= \int_0^1 \lambda_P s ^ {\lambda_P - 1} f(N_P, s N_F) \ds, \\
+        \varphi_F(\mathcal{G}) &= \int_0^1 s ^ {\lambda_P} N_F \partial_2 f(N_P, s N_F) \ds.
+    \end{align*}
+\end{proposition}
+\begin{proof}[Proof of \cref{prop:profit_sharing_weighted}]
+    This result is a direct application of Proposition 4 in \textcite{stancsics2023value}.
+\end{proof}
+
+As before, the resulting allocations satisfy \cref{ass:profit_sharing} with $w_P(s) \equiv \lambda_P s ^ {\lambda_P - 1}$ and $w_F(s) = s ^ {\lambda_P}$.
+
+\subsubsection{Two-sided case}
+\label{sec:cooperative_game_two_sided}
+
+Finally, in certain settings, it might be appropriate to assume that the consumers (or, more generally, the entities on the other side of the market) also engage in the bargaining process.
+An example for this is \cref{sec:two_sided}
+In such a case, cooperative game describing can be formalized as follows.
+
+The set of players consists of the platform plus the fringe firms: $\mathcal{N} = \{P, F_i, C_j\}, i \in [0, N_F], j \in [0, N_C]$.
+The value of a coalition $S$ is zero without the platform, and depends on the number of fringe firms otherwise:
+\begin{align*}
+    v(S) = \begin{cases}
+        0 & \text{if } P \notin S \\
+        n_C(S) f(N_P, n_F(S)) & \text{if } P \in S
+    \end{cases},
+\end{align*}
+where $n_F(S)$ and $n_C(S)$ is the measure of fringe firms and consumers, respectively, in $S$.
+
+As in the one-sided case, simple expressions exist for the Shapley value of the platform ($\varphi_P(\mathcal{G})$), fringe firms ($\varphi_F(\mathcal{G})$) and consumers ($\varphi_C(\mathcal{G})$).
+
+\begin{proposition}
+    \label{prop:profit_sharing_two_sided}
+    Consider the case when only the platform and the fringe firms participate in the bargaining process.
+    Then, the resulting profit shares are given by
+    \begin{align*}
+        \varphi_P(\mathcal{G}) &= N_C \int_0^1 s f(N_P, s N_F) \ds, \\
+        \varphi_F(\mathcal{G}) &= N_C \int_0^1 s^2 N_F \partial_2 f(N_P, s N_F) \ds \\
+        \varphi_C(\mathcal{G}) &= N_C \int_0^1 s f(N_P, s N_F) \ds.
+    \end{align*}
+\end{proposition}
+\begin{proof}[proof of \cref{prop:profit_sharing_two_sided}]
+    This result is a direct application of Proposition 11 in \textcite{stancsics2023value}.
+\end{proof}
+
+One thing to note is that the platform's and fringe firms' shares are lower than in the one-sided case.
+This is due to the fact of needing to share the pie with the consumers, too.
+Additionally, the platform's share is identical to the consumers' (aggregated) share.\footnote{
+    This stems from the linearity of the profit function in the number of consumers.
+}
+This foreshadows the idea that -- even though it might not be welfare-maximizing -- what's good for the platform might also good for the consumers in the two-sided case.
+Finally, as in both examples before, these values satisfy \cref{ass:profit_sharing} with $w_P(s) = s$ and $w_F(s) = s^2$.
+
 % \section{The platform's product pricing assumption}
@@
 
-\section{Proofs and additional lemmas}
-\label{sec:proofs}
-
-\begin{lemma}
-    \label{lem:single_crossing_affine_transformation}
-    Let $g: \mathbb{R}^+ \to \mathbb{R}$ be a twice continuously differentiable function.
-    Define
-    \begin{align*}
-        G(x) = \int_0^1 g(sx) \ds.
-    \end{align*}
-    Assume that for any $x \geq 0$, $G'(x) < 0$ or $G''(x) < 0$.
-
-    Let $h(x) = c g(a + bx)$ for some $a, c > 0$ and $b > 0$.
-    Then the function $H(x) = \int_0^1 h(sx) \ds$ satisfies the same conditions: for any $x \geq 0$, $h'(x) < 0$ or $h''(x) < 0$.
-\end{lemma}
-\begin{proof}[Proof of \cref{lem:single_crossing_affine_transformation}]
-    Differentiating $H$ yields
-    \begin{align*}
-        H'(x) &= \int_0^1 h'(sx) \ds \\
-              &= \int_0^1 c b g'(a + bsx) \ds \\
-              &= c b G'(a + bsx).
-    \end{align*}
-    Similarly, the second derivative is
-    \begin{align*}
-        H''(x) &= \int_0^1 h''(sx) \ds \\
-               &= \int_0^1 c b^2 g''(a + bsx) \ds \\
-               &= c b^2 G''(a + bsx).
-    \end{align*}
-    Now, for any $x \geq 0$, $y = a + bsx \geq 0$, therefore $G'(y) < 0$ or $G''(y) < 0$.
-    As $c, b > 0$, this implies that $H'(x) < 0$ or $H''(x) < 0$.
-\end{proof}
-
-\begin{lemma}
-    \label{lem:slope_at_eq}
-    Let the conditions in \cref{ass:single_crossing} hold.
-Then for any $N_F^* > 0$ for which $\pi_F(N_P, N_F^*, N_C) = I_F N_F$, the partial derivative of fringe profits with respect to the number of fringe firms is smaller than the marginal investment cost $I_F$:
-    \begin{align*}
-        \left. \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_F} \right|_{N_F = N_F^*} < I_F.
-    \end{align*}
-\end{lemma}
-\begin{proof}[Proof of \cref{lem:slope_at_eq}]
-    \cref{ass:single_crossing} states that at any $N_F \geq 0$, $\pi_F(N_P, N_F, N_C)$ is either concave or decreasing in $N_F$.
-    In the remainder, let us denote partial derivatives as follows:
-    \begin{align*}
-        \partial_F \pi_F(N_P^*, N_F^*, N_C^*) \coloneqq \left. \frac{\partial \pi_F(N_P, N_F,  )}{\partial N_F} \right|_{N_P = N_P*, N_F = N_F^*, N_C = N_C^*}.
-    \end{align*}
-
-    Notice that the fact that $\pi_F$ is concave or decreasing in $N_F$ implies that if $\partial_F \pi_F(N_P, N_F', N_C)$ for some $N_F' \geq 0$, then $\partial_F \pi_F(N_P, N_F'', N_C) < \partial_F \pi_F(N_P, N_F', N_C)$ for any $\tilde{N_F} < \bar{N_F}$.
-
-    Next, observe that if $\partial_F \pi_F(N_P, 0, N_C) < I_F$, then there is no equilibrium with $N_F > 0$.
-    To show this, assume by contradiction that $\exists N_F^* > 0$ such that $\pi_F(N_P, N_F^*, N_C) = I_F N_F^*$.
-    Then the mean value theorem implies that there is a $\bar{N}_F \in (0, N_F^*)$ such that $\partial_F \pi_F(N_P, \bar{N}_F, N_C) = I_F$.
-    However, this clearly cannot be the case as $\partial_F \pi_F(N_P, N_F, N_C) < I_F$ or $\pi_F(N_P, N_F, N_C) \leq 0$ for all $N_F > 0$.
-
-    Now let $N_F^*$ be a positive number for which $f(N_P, N_F^*, N_C) = I_F N_F^*$.
-    It is easy to see that $\partial \pi(N_P, N_F^*, N_C) < I_F$.
-    The reason is that if it exists, then $\partial_F \pi_F(N_P, 0, N_C) > I_F$.
-    Now if $\partial_F \pi_F(N_P, N_F, N_C) \geq I_F \forall N_F > 0$, then $f(N_P, N_F, N_F) > I_F N_F$, and the two functions do not intersect.
-    Therefore, there must exist some $\bar{N}_F > 0$ for which $\partial_F \pi_F(N_P, \bar{N}_F, N_C) < I_F$.
-    This in turn implies that $\partial_F \pi_F(N_P, N_F, N_C) \leq \partial_F \pi_F(N_P, \bar{N}_F, N_C) < I_F$ for all $N_F > \bar{N}_F$.
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:unique_equilibrium_more_general}]
-    \Cref{lem:slope_at_eq} states that for any positive $N_F^*$ for which $\pi_F(N_P, N_F^*) - N_F I_F$, the partial derivative with respect to the number of fringe firms is negative.
-    Now assume by contradiction that $\exists 0 < N_F^* < N_F^{**}$ such that $\pi_F(N_P, N_F^*) = I_F N_F^*$ and $\pi_F(N_P, N_F^{**}) = I_F N_F^{**}$.
-    But then the mean value theorem implies that there is a $\bar{N}_F \in (N_F^*, N_F^{**})$ such that $\partial_F \pi_F(N_P, \bar{N}_F) = I_F$.
-    This is a contradiction, as $\partial_F \pi_F(N_P, N_F) < I_F$ for all $N_F^* < N_F$.
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:share_of_platform}]
-    $f(N_P, N_F)$ is continuously differentiable in $N_P$, therefore the Leibniz rule can be applied to obtain
-    \begin{align*}
-        \frac{\partial \pi_P(N_P, N_F, N_C)}{\partial N_P} &= N_C \frac{\partial}{\partial N_P} \int_0^1 w_P(s) f(N_P, N_F) \ds \\
-        &= \int_0^1 w_P(s) \underbrace{\frac{\partial f(N_P, sN_F)}{\partial N_P}}_{> 0} \ds > 0
-    \end{align*}
-    for any non-negative, continuous $w_P(s)$.
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:share_of_fringe}]
-    Remember that
-    \begin{align*}
-        \pi_F(N_P, N_F, N_C) = N_C \int_0^1 w_F(s) N_F \partial_2 f(N_P, s N_F) \ds,
-    \end{align*}
-    By assumption, $f$ is twice continuously differentiable, therefore $\partial_2$ is also continuously differentiable in $N_P$.
-    Thus, the Leibniz rule can be applied to obtain
-    \begin{align*}
-        \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P} &= \frac{\partial}{\partial N_P} N_C \int_0^1 w_F(s) N_F \partial_2 f(N_P, s N_F) \ds \\
-        &= N_C \int_0^1 w_F(s) N_F \frac{\partial}{\partial N_P} \partial_2 f(N_P, s N_F) \ds \\
-        &= N_C \int_0^1 w_F(s) N_F \partial^2_{12} f(N_P, s N_F) \ds.
-    \end{align*}
-
-    As $w_F(s) \geq 0$ for $s > 0$, if $\partial_2 f(N_P, s N_F)$ has the same sign over $[0, N_F]$, then the integral also has the same sign.
-    Formally,
-    \begin{align*}
-        \forall n_F \in [0, N_F] \enspace \frac{\partial^2 f(N_P, n_F)}{\partial N_P \partial n_F} < 0 &\implies \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P} < 0 \\
-        \forall n_F \in [0, N_F] \enspace \frac{\partial^2 f(N_P, n_F)}{\partial N_P \partial n_F} > 0 &\implies \frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P} > 0
-    \end{align*}
-\end{proof}
-
-\begin{proof}[Proof of \cref{cor:fringe_entry}]
-    \Cref{prop:unique_equilibrium} establishes that if an equilibrium with $N_F > 0$ exists, it is unique.
-    Use the implicit function theorem on the equation from \cref{ass:free_entry} to obtain
-    \begin{align*}
-        \frac{\partial N_F}{\partial N_P} = \frac{\frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P}}{I_F - \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F}}
-    \end{align*}
-    The derivative exists if the above expression is well-defined, i.e. $\frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} \neq I_F$.
-    Remember from \cref{prop:share_of_fringe} that the numerator of this expression is negative under the condition $\frac{\partial^2 f(N_P, N_F, N_C)}{\partial N_P \partial N_F}$.
-    Now all we need to show to conclude the proof is that
-    \begin{align*}
-        \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} < I_F,
-    \end{align*}
-    which is the statement of \cref{lem:slope_at_eq}.
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:aggregate_size_additive}]
-    Use the implicit function theorem to get the equilibrium number of fringe firms as a function of the platform's product variety:
-    \begin{align*}
-        \frac{\partial N_F}{\partial N_P} = \frac{\frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P}}{I_F - \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F}}.
-    \end{align*}
-    Remember, that from \cref{lem:slope_at_eq}, and the assumption on the investment cost function we have that $\frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} < I_F$.
-    Then, substitute $f(N_P, N_F) = g(\alpha N_P + \beta N_P)$ into $\pi_F$ to get the following fringe profit function:
-    \begin{align*}
-        \pi_F(N_P, N_F, N_C) = \beta N_C N_F \int_0^1 w_F(s) g'(\alpha N_P + s \beta N_F) \ds.
-    \end{align*}
-    Differentiate it with respect to $N_P$ and $N_F$ and substitute into the first expression to obtain
-    \begin{align*}
-        \frac{\partial N_F}{\partial N_P} = \frac{
-            \alpha \beta N_C N_P \int_0^1 w_F(s) g''(\alpha N_P + s \beta N_F) \ds
-        }{
-            \underbracket{I'_F(N_F) - \beta N_C \int_0^1 w_F(s) g'(\alpha N_P + s \beta N_F) \ds}_{(1)} - \underbracket{\beta^2 N_C N_F \int_0^1 w_F(s) s g''(\alpha N_P + s \beta N_F) \ds}_{(2)}.
-        }
-    \end{align*}
-    From \cref{lem:slope_at_eq}, we know that the denominator of this expression is positive.
-    Furthermore, the concavity of $g$ implies that expression (2) is also positive.
-    Finally, from \cref{prop:share_of_fringe}, we have that the whole expression must be negative.
-
-    First, let us show that (1) is non-negative, and, coupled with the fact that (2) is positive, omitting it increases the denominator in absolute value, thus making the whole expression larger.
-    To see this, observe that the second part of (1) is just the per-unit fringe profit.
-    Therefore, in equilibrium, (1) must be zero:
-    \begin{align*}
-        N_F (1) = N_F I_F - \pi_F(N_P, N_F, N_C) = 0.
-    \end{align*}
-
-    Next, observe that we can bound (2) from above using the fact that $0 \leq s \leq 1$:
-    \begin{align*}
-        (2) \leq \beta^2 N_C N_F \int_0^1 w_F(s) g''(\alpha N_P + s \beta N_F) \ds.
-    \end{align*}
-    For the same reason as before, it also bounds the whole expression from above.
-
-    Putting it all together, we have that
-    \begin{align*}
-        \frac{\partial N_F}{\partial N_P} \leq \frac{\alpha \beta N_C N_P \int_0^1 w_F(s) g''(\alpha N_P + s \beta N_F) \ds}{\beta^2 N_C N_F \int_0^1 w_F(s) g''(\alpha N_P + s \beta N_F) \ds} = -\frac{\alpha}{\beta},
-    \end{align*}
-    which is the first statement of the proposition.
-
-    To prove the second part of the proposition, differentiate total profits with respect to $N_P$:
-    \begin{align*}
-        \frac{\partial \Pi(N_P, N_F^*(N_P), N_C)}{\partial N_F} &= \frac{\partial}{\partial N_F} N_C g(\alpha N_P + \beta N_F^*(N_P)) \\
-        &= \underbrace{N_C g'(\alpha N_P + \beta N_F^*(N_P))}_{> 0} \left[ \alpha + \beta \frac{\partial N_F^*(N_P)}{\partial N_P} \right] \\
-        &< N_C g'(\alpha N_P + \beta N_F^*(N_P)) \left[ \alpha + \beta \left( -\frac{\alpha}{\beta} \right) \right] \\
-        &= 0.
-    \end{align*}
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:demand_function}]
-    See Theorem 1 in \textcite{anderson2021hybrid}.
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:optimal_profit}]
-    The profit function for product $Ti$ is the following:
-    \begin{align*}
-        \pi^v_{T_i}(p_{T_i}) &= (p_{T_i} - c_T) x_{T_i}(p_{Ti}) \\
-        &= (p_{T_i} - c_T) \frac{\exp\left( \frac{v_T - p_{T_i}}{\mu} \right)}{A}.
-    \end{align*}
-    Note that $A$ is not influenced by changes in $p_{T_i}$, as $A$ is an integral and $p_T$ is only changed on a zero-measure (singleton) set.
-    Therefore, let calculate the first order condition while treating $A$ as a constant:
-    \begin{align}
-        \label{eq:foc_profit}
-        \mu \frac{\exp\left( \frac{v_T - p_{T_i}}{\mu} \right)}{A} \left[ \frac{p_T - c_T}{\mu} - 1 \right] = 0.
-    \end{align}
-    Also note that $\pi_{T_i}(p_{T_i})$ is strictly concave, so the FOC is sufficient for optimality.
-
-    Now simply rearrange \cref{eq:foc_profit} to obtain
-    \begin{align*}
-        p_{T_i}^* = c_T + \mu
-    \end{align*}
-    and substitute it into the profit function to get
-    \begin{align*}
-        \pi_{T_i}^{v*} = \mu \frac{\exp \left( \frac{v_T - c_T - \mu}{\mu} \right)}{A}.
-    \end{align*}
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:equilibrium_aggregate_benchmark}]
-    From \cref{prop:optimal_profit}, the variable profit of each fringe firm is $\pi_{F_i}^{v*} = \mu V_F / A$.
-    Total profit after entry fees and investment costs is therefore $\pi_{F_i}^{t*} = \mu V_F / A - I_F - K_F$.
-    Under free entry, total profits are zero:
-    \begin{align*}
-        0 = \pi_{F_i}^{t*} = \mu V_F / A - K_F - I_F.
-    \end{align*}
-    Simple rearrangement gives the formula we are looking for,
-    \begin{align*}
-        A = \mu \frac{V_F}{K_F + I_F},
-    \end{align*}
-    and substituting in $A = N_P V_P + N_F V_F + 1$ yields the equilibrium number of fringe firms,
-    \begin{align*}
-        N_F = \frac{\mu}{K_F + I_F} - N_P \frac{V_P}{V_F} - \frac{1}{V_F}.
-    \end{align*}
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:optimal_entry_fee}]
-    The total profit function of the platform is the following:
-    \begin{align*}
-        \pi_P^t &= \pi_P^v + K_F N_F \\
-        &= \mu \frac{N_P V_P}{K_F + I_F} + K_F \left[ \frac{\mu}{K_F + I_F} - N_P \frac{V_P}{V_F} - \frac{1}{V_F} \right].
-    \end{align*}
-    The function is strictly concave in $K_F$, so the first order condition is sufficient for optimality in the case of an interior solution.
-    Assume that the optimum is indeed interior.
-    Then the FOC is
-    \begin{align*}
-        \frac{\mu I_F V_F - (K_F + I_F)^2}{V_F (K_F + I_F)^2} = 0.
-    \end{align*}
-    Rearranging it gives the optimal entry fee
-    \begin{align*}
-        K_F^{opt} = \sqrt{\mu I_F V_F} - I_F,
-    \end{align*}
-    and substituting it into the profit function leads to
-    \begin{align*}
-        \pi_P^{*t} = \mu - 2\sqrt{\frac{I_F \mu}{V_F}} + \frac{I_F}{V_F} (N_P V_P + 1).
-    \end{align*}
-    Finally, note that
-    \begin{align*}
-        \pi_P^{*t} \geq \mu \frac{N_P V_P}{N_P V_P + 1},
-    \end{align*}
-    i.e., the profit that the platform could achieve by excluding the fringe completely.
-    Therefore, the optimum is indeed interior whenever $K_F$ is low enough
-
-    Now consider the case when $K_F^{opt}$ is so large that it would lead to no fringe entry.
-    In that case, the platform's only source of profit is selling its own products, and thus
-    \begin{align*}
-        \pi_P^{t} = \pi_P^{v} = \mu \frac{ N_P V_P}{N_P V_P + 1}.
-    \end{align*}
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:platform_profits_bargaining}]
-    Simply integrate the total industry profit function with respect to the mass of fringe entrants obtain the platform's share of the pie:
-    \begin{align*}
-        \pi^t_P &= \int_0^1 f(N_P, sN_F) \ds \\
-        &= \mu \int_0^1 \frac{N_P V_P + s N_F V_F}{N_P V_P + s N_F V_F + 1} \ds \\
-        &= \mu \left[ 1 - \frac{\log \left(1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} \right].
-    \end{align*}
-    The fringe's share is just the remainder,
-    \begin{align*}
-        f(N_P, N_F) - \int_0^1 f(N_P, sN_F) \ds = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right]
-    \end{align*}
-    Finally, remember that the investment cost of the fringe is fixed at the bargaining stage, and is therefore not included in the bargaining outcome.
-    Therefore, the total profits of the complete fringe are
-    \begin{align*}
-        \pi^t_P = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F N_F.
-    \end{align*}
-\end{proof}
-
-\begin{proof}[Proof of \cref{lem:shape_of_fringe_profit}]
-    First, consider the function
-    \begin{align*}
-        g(x) = \frac{sx}{1 + sx}.
-    \end{align*}
-    Also, let us define
-    \begin{align*}
-        G(x) &= \int_0^1 s g(sx) \ds \\
-        &= \frac{\log(x+1)}{x} + \frac{1}{x(x+1)} - \frac{1}{x}.
-    \end{align*}
-
-    Differentiation with respect to $x$ yields that
-    \begin{align*}
-        G'(x) < 0 \iff \log(x+1) > \frac{x (2x+1)}{(x+1)^2}
-    \end{align*}
-    and
-    \begin{align*}
-        G''(x) < 0 \iff \log(x+1) < \frac{x (5x^2 + 5x + 2)}{2 (x+1)^3}.
-    \end{align*}
-    There exists $\bar{x} > 0$\footnote{
-        $\bar{x} = 3$ is such a number.
-    }, such that the first equality holds for all $x > \bar{x}$, and the second for all $x < \bar{x}$.
-    Therefore, $G$ is either concave or decreasing for all $x > 0$.
-
-    Now let us consider the function $h(x) = N_C \mu g(N_P V_P + V_F x)$.
-    By \cref{lem:single_crossing_affine_transformation}, $H(x) = \int_0^1 s h'(sx) \ds$ is also either concave or decreasing for any $x > 0$.
-    Finally, notice that $H(x)$ is exactly the profit function of the fringe:
-    \begin{align*}
-        \pi_F(N_P, N_F) = \int_0^1 N_F h'(s N_F) \ds,
-    \end{align*}
-    thus proving the lemma.
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:unique_equilibrium}]
-    \Cref{lem:shape_of_fringe_profit} demonstrates that the fringe total profit function is either concave or decreasing in the number of fringe firms.
-    Thus, \cref{ass:single_crossing} is satisfied, and \cref{prop:unique_equilibrium_more_general} implies that the equilibrium number of fringe entrants is unique.
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:fringe_profits_partial}]
-    $\pi^t_F(N_P ,N_F)$ adheres to the \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing}.
-    Furthermore, 
-    \begin{align*}
-        \frac{\partial^2 \pi^t_F(N_P ,N_F)}{\partial N_P \partial N_F} < 0 \quad \forall\, N_P, N_F \geq 0.
-    \end{align*}
-    Therefore, by \cref{prop:share_of_fringe},
-    \begin{align*}
-        \frac{\partial \pi^t_F(N_P, N_F)}{\partial N_P} < 0 \quad \forall\, N_P, N_F \geq 0.
-    \end{align*}
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:N_F_comparative_equilibrium}]
-    $\pi^t_F(N_P ,N_F)$ adheres to the \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:additive_profit}.
-    Therefore, by \cref{prop:aggregate_size_additive}
-    \begin{align*}
-        N_F > 0 \implies \frac{\partial N_F}{\partial N_P} < -\frac{V_P}{V_F}
-    \end{align*}
-    immediately follows.
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:aggregate_comparative_hybrid}]
-    The first statement follows immediately from
-    \begin{align*}
-        A = N_P V_P + N_F V_F + 1
-    \end{align*}
-    and
-    \begin{align*}
-        \frac{\partial N_F}{\partial N_P} < -\frac{V_P}{V_F}
-    \end{align*}
-    from \cref{prop:N_F_comparative_equilibrium}.
-    The second part is a consequence of
-    \begin{align*}
-        CS \propto \log(A).
-    \end{align*}
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:aggregate_comparative_retail}]
-    The first statement trivially follows from
-    \begin{align*}
-        A = N_P V_P + 1.
-    \end{align*}
-    The second part is a consequence of
-    \begin{align*}
-        CS \propto \log(A).
-    \end{align*}
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:benchmark_results}]
-    The respective results are stated in \cref{prop:equilibrium_aggregate_benchmark} and \cref{prop:consumer_surplus_benchmark}.
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:bargaining_results}]
-    The respective results are stated in \cref{prop:N_F_comparative_equilibrium} and \cref{prop:aggregate_comparative_hybrid}.
-\end{proof}
-
 \end{document}

### 2024-06-20 src/paper/application.tex
Finish rearranging appendix

@@
 \subsection{Benchmark: platform sets entry fee unilaterally}
+\label{sec:results_benchmark}
 
@@
 
+In the main text, I use a simpler version of this profit sharing rule.
+I assume that $w_P(s) = w_F(s) \equiv 1$.
+As \cref{sec:cooperative_game} demonstrates, this corresponds to players. Getting their Shapley values in the end.
+Together with the assumptions on the demand system, one can even derive a closed form expression for the platform's profit share (\cref{prop:platform_profits_bargaining}).
+The proof if this proposition is given below
+\begin{proof}[Proof of \cref{prop:platform_profits_bargaining}]
+    Simply integrate the total industry profit function with respect to the mass of fringe entrants obtain the platform's share of the pie:
+    \begin{align*}
+        \pi^t_P &= \int_0^1 f(N_P, sN_F) \ds \\
+        &= \mu \int_0^1 \frac{N_P V_P + s N_F V_F}{N_P V_P + s N_F V_F + 1} \ds \\
+        &= \mu \left[ 1 - \frac{\log \left(1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} \right].
+    \end{align*}
+    The fringe's share is just the remainder,
+    \begin{align*}
+        f(N_P, N_F) - \int_0^1 f(N_P, sN_F) \ds = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right]
+    \end{align*}
+    Finally, remember that the investment cost of the fringe is fixed at the bargaining stage, and is therefore not included in the bargaining outcome.
+    Therefore, the total profits of the complete fringe are
+    \begin{align*}
+        \pi^t_P = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F N_F.
+    \end{align*}
+\end{proof}
+
 Apart from the cooperative foundations, one major justification for this profit allocation rule is its intuitive behavior in terms of comparative statics.
@@
 The profit functions presented in the main text satisfy this assumption.
+
+Under the specific demand system and profit sharing rule described in the main text, it can be shown that this assumption is satisfied.
+\begin{proof}[Proof of \cref{lem:shape_of_fringe_profit}]
+    First, consider the function
+    \begin{align*}
+        g(x) = \frac{sx}{1 + sx}.
+    \end{align*}
+    Also, let us define
+    \begin{align*}
+        G(x) &= \int_0^1 s g(sx) \ds \\
+        &= \frac{\log(x+1)}{x} + \frac{1}{x(x+1)} - \frac{1}{x}.
+    \end{align*}
+
+    Differentiation with respect to $x$ yields that
+    \begin{align*}
+        G'(x) < 0 \iff \log(x+1) > \frac{x (2x+1)}{(x+1)^2}
+    \end{align*}
+    and
+    \begin{align*}
+        G''(x) < 0 \iff \log(x+1) < \frac{x (5x^2 + 5x + 2)}{2 (x+1)^3}.
+    \end{align*}
+    There exists $\bar{x} > 0$\footnote{
+        $\bar{x} = 3$ is such a number.
+    }, such that the first equality holds for all $x > \bar{x}$, and the second for all $x < \bar{x}$.
+    Therefore, $G$ is either concave or decreasing for all $x > 0$.
+
+    Now let us consider the function $h(x) = N_C \mu g(N_P V_P + V_F x)$.
+    By \cref{lem:single_crossing_affine_transformation}, $H(x) = \int_0^1 s h'(sx) \ds$ is also either concave or decreasing for any $x > 0$.
+    Finally, notice that $H(x)$ is exactly the profit function of the fringe:
+    \begin{align*}
+        \pi_F(N_P, N_F) = \int_0^1 N_F h'(s N_F) \ds,
+    \end{align*}
+    thus proving the lemma.
+\end{proof}
 
@@
 This particular shape (concave or hump-shaped) is also the main driver for the later results about the comparative statics of equilibrium profits and entry.
+Given that \cref{ass:free_entry,ass:single_crossing} is satisfied in the model presented in the main text, it immediately follows that the equilibrium in that model is also unique.
+\begin{proof}[Proof of \cref{prop:unique_equilibrium}]
+    \Cref{lem:shape_of_fringe_profit} demonstrates that the fringe total profit function is either concave or decreasing in the number of fringe firms.
+    Thus, \cref{ass:single_crossing} is satisfied, and \cref{prop:unique_equilibrium_more_general} implies that the equilibrium number of fringe entrants is unique.
+\end{proof}
 
@@
 
+Based on this general result, the corresponding on in the main text follows immediately.
+\begin{proof}[Proof of \cref{prop:fringe_profits_partial}]
+    $\pi^t_F(N_P ,N_F)$ adheres to the \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing}.
+    Furthermore, 
+    \begin{align*}
+        \frac{\partial^2 \pi^t_F(N_P ,N_F)}{\partial N_P \partial N_F} < 0 \quad \forall\, N_P, N_F \geq 0.
+    \end{align*}
+    Therefore, by \cref{prop:share_of_fringe},
+    \begin{align*}
+        \frac{\partial \pi^t_F(N_P, N_F)}{\partial N_P} < 0 \quad \forall\, N_P, N_F \geq 0.
+    \end{align*}
+\end{proof}
+
 Finally, let us conclude this section by establishing a stronger result for a more restrictive class of profit functions.
@@
 This result has particularly strong implications in models where total profits (or total product variety) has a monotone relationship with consumer welfare, such as those in \textcite{anderson2020aggregative}.
-The demand system presented in the main text also has this property.
-
-\subsection{Additional lemmas}
+The demand system presented in the main text also has this property, and thus the results of this proposition apply to it as well.
+\begin{proof}[Proof of \cref{prop:N_F_comparative_equilibrium}]
+    $\pi^t_F(N_P ,N_F)$ adheres to the \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:additive_profit}.
+    Therefore, by \cref{prop:aggregate_size_additive}
+    \begin{align*}
+        N_F > 0 \implies \frac{\partial N_F}{\partial N_P} < -\frac{V_P}{V_F}
+    \end{align*}
+    immediately follows.
+\end{proof}
+
+\subsection{Additional lemmas and proofs}
 \label{sec:lemmas}
 This subsection contains a couple of lemmas that are, while not very interesting on their own, necessary for the proofs in the previous sections.
+Furthermore, it contains the proofs of the results presented in \cref{sec:results_benchmark}, as they are not related to the bargaining framework, and are thus omitted from the previous sections.
+
 The first lemma is helpful for establishing whether \cref{ass:single_crossing} holds under a certain $f$ function.
@@
 
+The remainder of this section contains the proofs related to optimal product pricing and various results for the benchmark model.
+
 \begin{proof}[Proof of \cref{prop:optimal_profit}]
@@
 
-\begin{proof}[Proof of \cref{prop:platform_profits_bargaining}]
-    Simply integrate the total industry profit function with respect to the mass of fringe entrants obtain the platform's share of the pie:
-    \begin{align*}
-        \pi^t_P &= \int_0^1 f(N_P, sN_F) \ds \\
-        &= \mu \int_0^1 \frac{N_P V_P + s N_F V_F}{N_P V_P + s N_F V_F + 1} \ds \\
-        &= \mu \left[ 1 - \frac{\log \left(1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} \right].
-    \end{align*}
-    The fringe's share is just the remainder,
-    \begin{align*}
-        f(N_P, N_F) - \int_0^1 f(N_P, sN_F) \ds = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right]
-    \end{align*}
-    Finally, remember that the investment cost of the fringe is fixed at the bargaining stage, and is therefore not included in the bargaining outcome.
-    Therefore, the total profits of the complete fringe are
-    \begin{align*}
-        \pi^t_P = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F N_F.
-    \end{align*}
-\end{proof}
-
-\begin{proof}[Proof of \cref{lem:shape_of_fringe_profit}]
-    First, consider the function
-    \begin{align*}
-        g(x) = \frac{sx}{1 + sx}.
-    \end{align*}
-    Also, let us define
-    \begin{align*}
-        G(x) &= \int_0^1 s g(sx) \ds \\
-        &= \frac{\log(x+1)}{x} + \frac{1}{x(x+1)} - \frac{1}{x}.
-    \end{align*}
-
-    Differentiation with respect to $x$ yields that
-    \begin{align*}
-        G'(x) < 0 \iff \log(x+1) > \frac{x (2x+1)}{(x+1)^2}
-    \end{align*}
-    and
-    \begin{align*}
-        G''(x) < 0 \iff \log(x+1) < \frac{x (5x^2 + 5x + 2)}{2 (x+1)^3}.
-    \end{align*}
-    There exists $\bar{x} > 0$\footnote{
-        $\bar{x} = 3$ is such a number.
-    }, such that the first equality holds for all $x > \bar{x}$, and the second for all $x < \bar{x}$.
-    Therefore, $G$ is either concave or decreasing for all $x > 0$.
-
-    Now let us consider the function $h(x) = N_C \mu g(N_P V_P + V_F x)$.
-    By \cref{lem:single_crossing_affine_transformation}, $H(x) = \int_0^1 s h'(sx) \ds$ is also either concave or decreasing for any $x > 0$.
-    Finally, notice that $H(x)$ is exactly the profit function of the fringe:
-    \begin{align*}
-        \pi_F(N_P, N_F) = \int_0^1 N_F h'(s N_F) \ds,
-    \end{align*}
-    thus proving the lemma.
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:unique_equilibrium}]
-    \Cref{lem:shape_of_fringe_profit} demonstrates that the fringe total profit function is either concave or decreasing in the number of fringe firms.
-    Thus, \cref{ass:single_crossing} is satisfied, and \cref{prop:unique_equilibrium_more_general} implies that the equilibrium number of fringe entrants is unique.
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:fringe_profits_partial}]
-    $\pi^t_F(N_P ,N_F)$ adheres to the \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing}.
-    Furthermore, 
-    \begin{align*}
-        \frac{\partial^2 \pi^t_F(N_P ,N_F)}{\partial N_P \partial N_F} < 0 \quad \forall\, N_P, N_F \geq 0.
-    \end{align*}
-    Therefore, by \cref{prop:share_of_fringe},
-    \begin{align*}
-        \frac{\partial \pi^t_F(N_P, N_F)}{\partial N_P} < 0 \quad \forall\, N_P, N_F \geq 0.
-    \end{align*}
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:N_F_comparative_equilibrium}]
-    $\pi^t_F(N_P ,N_F)$ adheres to the \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:additive_profit}.
-    Therefore, by \cref{prop:aggregate_size_additive}
-    \begin{align*}
-        N_F > 0 \implies \frac{\partial N_F}{\partial N_P} < -\frac{V_P}{V_F}
-    \end{align*}
-    immediately follows.
-\end{proof}
-
 \begin{proof}[Proof of \cref{prop:aggregate_comparative_hybrid}]
@@
     \end{align*}
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:benchmark_results}]
-    The respective results are stated in \cref{prop:equilibrium_aggregate_benchmark} and \cref{prop:consumer_surplus_benchmark}.
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:bargaining_results}]
-    The respective results are stated in \cref{prop:N_F_comparative_equilibrium} and \cref{prop:aggregate_comparative_hybrid}.
 \end{proof}

### 2024-06-20 src/paper/application.tex
Add some missing proofs

@@
 \end{proposition}
+\begin{proof}[Proof of \cref{prop:shapley_value}]
+    The cooperative game is describer in detail in \cref{sec:cooperative_game_one_sided}.
+    This result is a direct consequence of \cref{prop:profit_sharing_one_sided}.
+\end{proof}
 
@@
 In fact, equilibrium per-product demand and variable profit can simply be expressed as $V_T/ A$ and $\mu V_T/ A$, respectively, where
-\begin{align*}
+\begin{align}
     A = N_P V_P + N_F V_F + 1
-\end{align*}
+    \label{eq:aggregate_simple}
+\end{align}
 denotes the total aggregate.
@@
     and the equilibrium number of fringe firms is
-    \begin{align*}
+    \begin{align}
         N_F = \frac{\mu}{K_F + I_F} - N_P \frac{V_P}{V_F} - \frac{1}{V_F}.
-    \end{align*}
+        \label{eq:N_F_eq}
+    \end{align}
     Otherwise,  $N_F = 0$ and the equilibrium size of the aggregate is
@@
     \begin{itemize}
-        \item The equilibrium number of fringe firms is decreasing in the platform's product variety: $\frac{\dd N_F}{\dd N_P} = -\frac{V_P}{V_F} < -0$.
+        \item The equilibrium number of fringe firms is decreasing in the platform's product variety: $\frac{\dd N_F}{\dd N_P} = -\frac{V_P}{V_F} < 0$.
         \item The equilibrium size of the aggregate and consumer surplus are independent of the platform's product variety: $\frac{\dd A}{\dd N_P} = \frac{\dd CS}{\dd N_P} = 0$.
@@
 The underlying reason is illustrated in \cref{fig:fringe_entry_eq}: the decrease in the number of fringe entrants is large enough to not only to offset the increase in the platform's product variety, but also to decrease the aggregate (\cref{fig:welfare_aggregate}).
-This in turn leads to a decrease in consumer surplus (\cref{fig:welfare_consumer}).
+This in turn leads to a decrease in consumer surplus (\cref{fig:welfare_consumer_surplus}).
 
@@
     \begin{align*}
-        \pi_P^t(N_P, N_F(N_P)) \geq \pi_P^t(N_P, 0) \forall\, N_P.
+        \pi_P^t(N_P, N_F(N_P)) \geq \pi_P^t(N_P, 0) \;\forall\, N_P.
     \end{align*}
@@
     \begin{align*}
-        \frac{V_P}{I_P} < \frac{V_F}{I_F} &\implies N_P^* 0, \\
+        \frac{V_P}{I_P} < \frac{V_F}{I_F} &\implies N_P^* = 0, \\
         \frac{V_P}{I_P} > \frac{V_F}{I_F} &\implies N_P^* > 0, N_F(N_P^*) = 0, \\
@@
 \end{proposition}
+\begin{proof}[Proof of \cref{prop:weighted_shapley_value}]
+\end{proof}
+This result is a direct consequence of \cref{prop:profit_sharing_weighted}.
 It is similar to the non-weighted value in that it is an average of marginal contributions, but now those averages are weighted, with the weight function depending on platform's bargaining weight.
@@
 \end{proposition}
+\begin{proof}[Proof of \cref{prop:lambda_P_comparative}]
+    For any $\lambda < \lambda'$, $\int_0^s \lambda t^{\lambda - 1} \dt = s^\lambda > s^{\lambda'} = \int_0^s \lambda' t^{\lambda' - 1} \dt \forall s \in [0, 1]$.
+    Therefore, for any (non-constant) function $\Pi$, $\int_0^1 \lambda s^{\lambda - 1} \Pi(s) \ds > \int_0^1 \lambda' s^{\lambda' - 1} \Pi(s) \ds$.
+\end{proof}
 In fact, the limits as $\lambda_P \to 0$ and $\lambda_P \to \infty$ are quite intuitive: in the former case, the platform's profits are zero, while in the latter case it is able to appropriate all profits.
@@
 \end{proposition}
+\begin{proof}[Proof of \cref{prop:three_way_shapley_value}]
+    \Cref{sec:cooperative_game_two_sided} formally describes the cooperative game corresponding to the three-sided bargaining assumption.
+    This result is a direct consequence of \cref{prop:profit_sharing_two_sided}.
+\end{proof}
 
@@
 \begin{proposition}
+    \label{prop:fringe_entry_two_sided}
     In the hybrid regime under three-sided bargaining, the following holds:
     \begin{align*}
-        N_F > 0 \implies \frac{\partial N_F}{\partial N_P} < -\frac{V_P}{V_F}.
+        N_F > 0 \implies \frac{\dd N_F}{\dd N_P} < -\frac{V_P}{V_F}.
     \end{align*}
 \end{proposition}
+\begin{proof}[Proof of \cref{prop:fringe_entry_two_sided}]
+    The proof is analogous to that of \cref{prop:equilibrium_bargaining}.
+    To see that $\frac{\partial \pi_F}{\partial N_F}$ satisfies \cref{ass:single_crossing}, first consider the function
+    \begin{align*}
+        g(x) = \frac{x}{1 + x} + \log(1 + x).
+    \end{align*}
+    Then observe that
+    \begin{align*}
+        G(x) \coloneq \int_0^1 g(sx) \ds = \frac{\frac{x^{2} \left(x + 1\right)}{2} + \left(1 - \log{\left(x + 1 \right)}\right) \left(x + 1\right) - 1}{x^{2} \left(x + 1\right)}
+    \end{align*}
+    is concave, and thus satisfies \cref{ass:single_crossing}.
+    By \cref{lem:single_crossing_affine_transformation}, $\pi_F$ then also satisfies \cref{ass:single_crossing}.
+    Finally, as \cref{ass:additive_profit,ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:single_crossing} are satisfied, it follows from \cref{prop:aggregate_size_additive} that
+    \begin{align*}
+        \frac{\dd N_F}{\dd N_P} < -\frac{V_P}{V_F}
+    \end{align*}
+    in the hybrid regime.
+
+\end{proof}
+
 As a consequence, the aggregate is decreasing in $N_P$ in the hybrid regime (\cref{fig:fringe_entry_eq_full_surplus_two_sided}).
@@
 \end{corollary}
+\begin{proof}
+    This result also follows from the applicability of \cref{prop:aggregate_size_additive}.
+\end{proof}
 
@@
     \label{cor:fringe_entry}
-    Let \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:free_entrya,ass:single_crossing} hold.
+    Let \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:free_entry,ass:single_crossing} hold.
     Furthermore, assume that $f, w$ are twice continuously differentiable.
@@
     \label{prop:aggregate_size_additive}
-    Let \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:free_entrya,ass:single_crossing,ass:additive_profit} hold.
+    Let \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:free_entry,ass:single_crossing,ass:additive_profit} hold.
     Then
@@
 The demand system presented in the main text also has this property, and thus the results of this proposition apply to it as well.
-\begin{proof}[Proof of \cref{prop:N_F_comparative_equilibrium}]
-    $\pi^t_F(N_P ,N_F)$ adheres to the \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:additive_profit}.
+\begin{proof}[Proof of \cref{prop:platform_profits_comparative_benchmark}]
+    Simply differentiate \cref{eq:platform_profits_hybrid_benchmark} with respect to $N_P$.
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:equilibrium_bargaining}]
+    $\pi^t_F(N_P ,N_F)$ adheres to the \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:additive_profit,ass:single_crossing}.
     Therefore, by \cref{prop:aggregate_size_additive}
     \begin{align*}
-        N_F > 0 \implies \frac{\partial N_F}{\partial N_P} < -\frac{V_P}{V_F}
+        N_F > 0 \implies \frac{\dd N_F}{\dd N_P} < -\frac{V_P}{V_F}
     \end{align*}
     immediately follows.
+    The second set of results can be obtained from this, as well as \cref{eq:aggregate_simple}:
+    \begin{align*}
+        \frac{\dd A}{\dd N_P}& = V_P \frac{\dd N_P}{\dd N_P} + V_F \frac{\dd N_F}{\dd N_P} \\
+        &< V_P - V_F \frac{V_P}{V_F} = 0,
+    \end{align*}
+    where the inequality follows from the previous proposition.
+    Finally, $CS$ is also decreasing as
+    \begin{align*}
+        \frac{\dd CS}{\dd N_P} = \frac{\dd \mu \log(A)}{\dd N_P} < 0.
+    \end{align*}
+
+    For the results about the pure retailer regime, use the fact that $A = N_P V_P + 1$ and $CS(A) = \mu\log(A)$.
 \end{proof}
@@
 
-\begin{proof}[Proof of \cref{prop:aggregate_comparative_hybrid}]
-    The first statement follows immediately from
-    \begin{align*}
-        A = N_P V_P + N_F V_F + 1
-    \end{align*}
-    and
-    \begin{align*}
-        \frac{\partial N_F}{\partial N_P} < -\frac{V_P}{V_F}
-    \end{align*}
-    from \cref{prop:N_F_comparative_equilibrium}.
-    The second part is a consequence of
-    \begin{align*}
-        CS \propto \log(A).
-    \end{align*}
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:aggregate_comparative_retail}]
-    The first statement trivially follows from
-    \begin{align*}
-        A = N_P V_P + 1.
-    \end{align*}
-    The second part is a consequence of
-    \begin{align*}
-        CS \propto \log(A).
-    \end{align*}
+\begin{proof}[Proof of \cref{prop:platform_profits_comparative_benchmark}]
+    Simply differentiate \cref{eq:platform_profits_hybrid_benchmark} with respect to $N_P$.
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:equilibrium_benchmark}]
+    The first statement follows from differentiating \cref{eq:N_F_eq} with respect to $N_P$.
+    $\frac{\dd A}{\dd N_P} = 0$ follows from the fact that $A$ does not depend on $N_P$ in \cref{eq:aggregate_eq}.
+    Finally, $\frac{\dd A}{\dd N_P} = 0$ follows from the fact that consumer surplus only depends on $A$.
+
+    For the results about the pure retailer regime, use the fact that $A = N_P V_P + 1$ and $CS(A) = \mu\log(A)$.
 \end{proof}

### 2024-06-20 src/paper/application.tex
Some more appendix rearrangement

@@
 Together with the assumptions on the demand system, one can even derive a closed form expression for the platform's profit share (\cref{prop:platform_profits_bargaining}).
-The proof if this proposition is given below
+The proof if this proposition is given below.
 \begin{proof}[Proof of \cref{prop:platform_profits_bargaining}]
@@
 
-\subsection{Results}
-\label{sec:more_general_results}
-
-This section presents a number of results that can be derived even in this rather abstract setting.
-Let us start with a technical, but very useful result.
+With \cref{ass:single_crossing} in place, uniqueness of the equilibrium can be established.
 \begin{proposition}
@@
 
+\subsection{Comparative statics}
+\label{sec:more_general_results}
+
+This section presents a number of comparative statics that can be derived even in this rather abstract setting.
+It contains three sets of results: (1) participants' profits in a partial equilibrium setting, where the number of fringe firms is taken as fixed, (2) equilibrium entry as a function of the platform's product variety, and (3) the platform's profits in general equlibrium.
+Throughout the paper, I use $\frac{\partial X}{\partial N_P}$ to denote partial equilibrium results, while $\frac{\dd X}{\dd N_P} \coloneq \frac{\partial X(N_P, N_F(N_P))}{\partial N_P}$ indicates general equilibrium results, where fringe entry is endogeneous.
+
+\paragraph{Profits -- partial equilibrium}
 The following two propositions are partial equilibrium results: consider the number of fringe entrants $N_F$ as fixed.
@@
 
-Finally, let us turn to equilibrium entry as a function of the platform's product variety.
+\paragraph{Number of entrants -- general equilibrium}
+Next, let us turn to equilibrium entry as a function of the platform's product variety.
 The previous proposition implies an almost immediate corollary regarding the equilibrium number of fringe entrants.
@@
     \begin{align*}
-        \frac{\partial N_F^*}{\partial N_P} < 0.
+        \dd{\partial N_F}{\dd N_P} < 0.
     \end{align*}
@@
     \begin{align*}
-        \frac{\partial N_F}{\partial N_P} = \frac{\frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P}}{I_F - \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F}}
+        \frac{\dd N_F}{\dd N_P} = \frac{\frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P}}{I_F - \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F}}
     \end{align*}
@@
     \begin{align*}
-        \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}.
+        \frac{\dd N_F}{\dd N_P} < -\frac{\alpha}{\beta}.
     \end{align*}
@@
     \begin{align*}
-        \frac{\partial \Pi(N_P, N_F^*(N_P), N_C)}{\partial N_P} < 0.
+        \frac{\dd \Pi(N_P, N_F, N_C)}{\dd N_P} < 0.
     \end{align*}
@@
     \begin{align*}
-        \frac{\partial N_F}{\partial N_P} = \frac{\frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P}}{I_F - \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F}}.
+        \frac{\dd N_F}{\dd N_P} = \frac{\frac{\partial \pi_F(N_P, N_F, N_C)}{\partial N_P}}{I_F - \frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F}}.
     \end{align*}
@@
     \begin{align*}
-        \frac{\partial N_F}{\partial N_P} = \frac{
+        \frac{\dd N_F}{\dd N_P} = \frac{
             \alpha \beta N_C N_P \int_0^1 w_F(s) g''(\alpha N_P + s \beta N_F) \ds
@@
     \begin{align*}
-        \frac{\partial N_F}{\partial N_P} \leq \frac{\alpha \beta N_C N_P \int_0^1 w_F(s) g''(\alpha N_P + s \beta N_F) \ds}{\beta^2 N_C N_F \int_0^1 w_F(s) g''(\alpha N_P + s \beta N_F) \ds} = -\frac{\alpha}{\beta},
+        \frac{\dd N_F}{\dd N_P} \leq \frac{\alpha \beta N_C N_P \int_0^1 w_F(s) g''(\alpha N_P + s \beta N_F) \ds}{\beta^2 N_C N_F \int_0^1 w_F(s) g''(\alpha N_P + s \beta N_F) \ds} = -\frac{\alpha}{\beta},
     \end{align*}
@@
     \begin{align*}
-        \frac{\partial \Pi(N_P, N_F^*(N_P), N_C)}{\partial N_F} &= \frac{\partial}{\partial N_F} N_C g(\alpha N_P + \beta N_F^*(N_P)) \\
+        \frac{\dd \Pi(N_P, N_F, N_C)}{\dd N_P}{\dd} &= \frac{\partial \Pi(N_P, N_F(N_P), N_C)}{\partial N_P} \\
+         &= \frac{\partial}{\partial N_P} N_C g(\alpha N_P + \beta N_F^*(N_P)) \\
         &= \underbrace{N_C g'(\alpha N_P + \beta N_F^*(N_P))}_{> 0} \left[ \alpha + \beta \frac{\partial N_F^*(N_P)}{\partial N_P} \right] \\
@@
 \end{proof}
+
+\paragraph{Platform profits -- general equilibrium}
+Finally, let us examine how the platform's product variety impacts its total profits, also taking into account its effect on the number of fringe entrants.
 

### 2024-06-20 src/utils/makeutils.py
Use older texlive in ms and add package ms manually...

@@ -12,7 +12,9 @@ app = typer.Typer()
 
 @app.command()
 def find_input_files(
-    tex_file: str, remove_prefix: str = "", print_console: bool = False
+    tex_file: str,
+    remove_prefix: str = "",
+    print_console: bool = False,
 ):
     """Find all of the files that are included, inputted or includegraphics'
     in a tex file.
@@ -129,6 +131,7 @@ def collect_latex_packages(
     add_latexmk: bool = False,
     add_manim_deps: bool = False,
     check_against_tl: bool = False,
+    force_add: list[str] = [],
     print_console: bool = False,
 ) -> list[str]:
     """Collect all of the latex packages from the dependency files.
@@ -211,6 +214,8 @@ def collect_latex_packages(
             )
         )
         packages &= tl_packages
+
+    packages |= set(force_add)
 
     package_list = sorted(list(packages))
 

### 2024-06-20 src/paper/application.tex
Number appendix stuff with A#, B#, etc.
Use latest textlive in ci but update package list
Add some missing proofs

@@
 \usepackage{snapshot}
+\usepackage{apptools}
 \usepackage[backend=biber,style=authoryear,maxbibnames=99,hyperref=true]{biblatex}
@@
 \newtheorem{definition}{Definition}
-\newtheorem{observation}{Observation}
 \newtheorem{proposition}{Proposition}
@@
 \Crefname{assumption}{Assumption}{Assumptions}
-\crefname{observation}{observation}{observations}
-\Crefname{observation}{Observation}{Observations}
+
+\AtAppendix{\counterwithin{definition}{section}}
+\AtAppendix{\counterwithin{proposition}{section}}
+\AtAppendix{\counterwithin{theorem}{section}}
+\AtAppendix{\counterwithin{corollary}{section}}
+\AtAppendix{\counterwithin{lemma}{section}}
+\AtAppendix{\counterwithin{assumption}{section}}
+\AtAppendix{\counterwithin{equation}{section}}
+\AtAppendix{\counterwithin{figure}{section}}
 
@@
 One simple extension of this bargaining process would be to use the more general concept of random order values \parencite{weber1988probabilistic}.
-\textcite{stancsics2023bargaining} examines this solution concept for a similar game, but in a more more abstract setting.
+\textcite{stancsics2023value} examines this solution concept for a similar game, but in a more abstract setting.
 \Cref{sec:cooperative_game_weighted} takes a step in this direction by introducing bargaining weights and utilizing the weighted value.
@@
 
-While this lemma's main purpose is to help establish the results about fringe entry and consumer surplusfor the bargaining case, it is also interesting in its own right.
+While this lemma's main purpose is to help establish the results about fringe entry and consumer surplus for the bargaining case, it is also interesting in its own right.
 It shows that the number of fringe firms do not necessarily have a monotonic effect on the total profits of the fringe.
-That is, even though industry-wide profits are increasing in $N_F$, the share that the fringe can obtain may decrease after a certain point, not only in relative terms, but also in absolute terms.
+That is, even though industry-wide profits are increasing in $N_F$, the amount that the fringe can obtain may decrease after a certain point, not only as a fraction of the total, but also in absolute terms.
 The underlying reason is that as the number of fringe firms increases, their bargaining power decreases due to their substitutability with each other.
@@
 \Cref{sec:cooperative_game_two_sided} formally describes the corresponding cooperative game, and \cref{prop:profit_sharing_two_sided} establishes the resulting profit shares.
-To summarize, the shares of the various players are as follows.
+To summarize, the various players share the total surplus in the following way.
 \begin{proposition}
@@
     \begin{align*}
-        \pi^t_P &= \int_0^1 f(N_P, sN_F) \ds \\
+        \pi^t_P &= \int_0^1 \Pi(N_P, sN_F) \ds \\
         &= \mu \int_0^1 \frac{N_P V_P + s N_F V_F}{N_P V_P + s N_F V_F + 1} \ds \\
@@
     \begin{align*}
-        f(N_P, N_F) - \int_0^1 f(N_P, sN_F) \ds = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right]
+        \Pi(N_P, N_F) - \int_0^1 \Pi(N_P, sN_F) \ds = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right]
     \end{align*}
@@
     Let \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing} hold.
-    Further assume that $f$ is continuously differentiable with respect to $N_P$ and also twice differentiable.
+    Also assume that $f$ is continuously differentiable with respect to $N_P$ and also twice differentiable.
     Let $N_F \geq 0$.
@@
 In summary, when they are mostly substitutes (the cross-derivatives of $f$ are negative), the fringe's profits decrease as a result of an increase in $N_F$.
-The intuition is that, even though the total size of the pie increases, the bargaining power of the fringe deteriorates so much that its share decreases not only in relative, but also in absolute terms (as illustrated in \cref{fig:increase_N_P_fringe}).
+The intuition is that, even though the total size of the pie increases, the bargaining power of the fringe deteriorates so much that its total profits decreases not only in relative, but also in absolute terms (as illustrated in \cref{fig:increase_N_P_fringe}).
 On the other hand, when the fringe firms are mostly complements the fringe's profits increase.
@@
 When the cross derivative is positive, an increase in the platform's product variety increases the marginal contribution of the fringe firms to the total value for any given number of fringe firms.
-Therefore, the share of the fringe also increases.
-On the other hand, when the cross derivative is negative, the marginal contribution of the fringe firms decreases, and so does their share.
+Therefore, the amount that the fringe gets also increases.
+On the other hand, when the cross derivative is negative, the marginal contribution of the fringe firms decreases, and so does the amount they obtain.
 
@@
 
+Finally, \cref{prop:implied_entry_fee_comparative} can be viewed as a corollary of the previous theorem.
+\begin{proof}[Proof of \cref{prop:implied_entry_fee_comparative}]
+    Remember that in the hybrid regime, regardless of $N_P$, the size o the aggregate is pinned down by the entry fee $K_F$ (\cref{eq:aggregate_eq}).
+    Conversely, when given some $A$, there is a unique entry fee that supports it:
+    \begin{align*}
+        K_F^{impl} = \frac{\mu V_F}{A} - I_F.
+    \end{align*}
+    Furthermore, this entry fee is decreasing in $A$.
+    \Cref{prop:equilibrium_bargaining} states that $A$ is decreasing in $N_P$, and thus it follows that
+    \begin{align*}
+        \frac{\dd K_F^{impl}}{\dd N_P} = \underbracket{\frac{\dd K_F^{impl}}{\dd A}}_{<0} \underbracket{\frac{\dd A}{\dd N_P}}_{<0} > 0.
+    \end{align*}
+\end{proof}
+
 \paragraph{Platform profits -- general equilibrium}
-Finally, let us examine how the platform's product variety impacts its total profits, also taking into account its effect on the number of fringe entrants.
+Now let us consider how the platform's product variety impacts its total profits, also taking into account its effect on the number of fringe entrants.
+While \cref{prop:share_of_platform} establishes that the platform's profits increase in its own product variety, it is not a general equilibrium result.
+In particular, we know that increasing the platform's product variety leads to a decrease in the number of fringe entrants, and in total profits.
+It would be conceivable that this decrease in entry is so large that the platform's profits decrease as well.
+
+While I do not have a general result for the platform's profits in equilibrium, an important observation can be made.
+No matter the form of the profit function, the platform's profits are always higher in the hybrid regime than if it exclusively sold its own products.
+The intuition behind it is that the profit sharing rule is such that each player gets at least as much as they would make on their own\footnote{
+    Which is only a positive amount for the platform, as the fringe cannot create any value on its own.
+}.
+The following proposition formalizes this idea.
+\begin{proposition}
+    \label{prop:hybrid_vs_retail_general}
+    Under \cref{ass:additive_profit,ass:monotone_profits,ass:monotone_profits}, for any $N_C, N_P, N_F \geq 0$,
+    \begin{align*}
+        \pi_P(N_P, N_F, N_C) \geq \pi_P(N_P, 0, N_C).
+    \end{align*}
+\end{proposition}
+\begin{proof}[Proof of \cref{prop:hybrid_vs_retail_general}]
+    \begin{align*}
+        \pi_P(N_P, N_F, N_C) &= N_C \int_0^1 w_P(s) f(N_P, s N_F) \ds \\
+        &\geq N_C \int_0^1 w_P(s) f(N_P, 0) \ds \\
+        &= \int_0^1 w_P(s) \ds N_C f(N_P, 0) \\
+        &= \pi_P(N_P, 0, N_C),
+    \end{align*}
+    with the inequality being strict if $N_F > 0$ and $f$ is not constant its second argument on $[0, N_F]$.
+\end{proof}
+
+\Cref{prop:hybrid_vs_retail} is then a special case of this result.
+\begin{proof}[Proof of \cref{hybrid_vs_retail}]
+    $\Pi$ satisfies \cref{ass:additive_profit,ass:monotone_profits,ass:monotone_profits}.
+    By \cref{prop:hybrid_vs_retail_general}, $\pi_P(N_P, N_F) \geq \pi_P(N_P, N_F)$ for any $N_F$, thus also for $N_F(N_P)$.
+    When $N_F(N_P) > 0$, the inequality is strict.
+\end{proof}
 
@@
 However, as I argue later on, it is equivalent to bargaining over entry fees.
-Finally, this section focuses on the main model, with two-sided bargaining, and the Shapley value as the solution concept.
-However, the same logic can be applied to the extensions presented in \cref{sec:extensions}, based on sections 3.1 and 3.2 of \textcite{stole1996intra}.
+While this section focuses on the main model, with two-sided bargaining, and the Shapley value as the solution, the same logic can be applied to the extensions presented in \cref{sec:extensions}, based on sections 3.1 and 3.2 of \textcite{stole1996intra}.
+Finally, the model is defined for a finite number of small players.
+The continuous version in this paper is the limit of this model as the number of fringe firms goes to infinity.
 

### 2024-06-21 src/paper/application.tex
Add final (?) missing proofs

@@
     \label{prop:comparative_n_p_bargaining}
-    In the bargaining model, the platform invests in its own products only if it has a product advantage, and the optimal number of products is increasing in the size of this advantage.
+    In the bargaining model, the dependence of the platform's profits on its number of products depends on what the implied entry fee is compared to the optimal entry fee:
     \begin{align*}
@@
     \label{ass:monotone_profits}
-    $f(n_P, n_F)$ is increasing in both $n_P$ and $n_F$.
+    $f(N_P, n_F)$ is increasing in both $N_P$ and $N_F$.
 \end{assumption}
@@
 
-Finally, \cref{prop:implied_entry_fee_comparative} can be viewed as a corollary of the previous theorem.
+\Cref{prop:implied_entry_fee_comparative} can be viewed as a corollary of the previous theorem.
 \begin{proof}[Proof of \cref{prop:implied_entry_fee_comparative}]
@@
 
-While I do not have a general result for the platform's profits in equilibrium, an important observation can be made.
-No matter the form of the profit function, the platform's profits are always higher in the hybrid regime than if it exclusively sold its own products.
-The intuition behind it is that the profit sharing rule is such that each player gets at least as much as they would make on their own\footnote{
-    Which is only a positive amount for the platform, as the fringe cannot create any value on its own.
-}.
+While I do not have a general result for the platform's profits in equilibrium, useful can be made.
+No matter the form of the profit function, the platform's profits always prefers more fringe firms to fewer in the bargaining model.
 The following proposition formalizes this idea.
@@
     \label{prop:hybrid_vs_retail_general}
-    Under \cref{ass:additive_profit,ass:monotone_profits,ass:monotone_profits}, for any $N_C, N_P, N_F \geq 0$,
-    \begin{align*}
-        \pi_P(N_P, N_F, N_C) \geq \pi_P(N_P, 0, N_C).
+    Under \cref{ass:additive_profit,ass:monotone_profits,ass:monotone_profits}, for any $N_C, N_P\leq 0$ and $0 \geq N_F \leq N_F'$
+    \begin{align*}
+        \pi_P(N_P, N_F, N_C) \leq \pi_P(N_P, N_F', N_C).
     \end{align*}
@@
         \pi_P(N_P, N_F, N_C) &= N_C \int_0^1 w_P(s) f(N_P, s N_F) \ds \\
-        &\geq N_C \int_0^1 w_P(s) f(N_P, 0) \ds \\
-        &= \int_0^1 w_P(s) \ds N_C f(N_P, 0) \\
-        &= \pi_P(N_P, 0, N_C),
-    \end{align*}
-    with the inequality being strict if $N_F > 0$ and $f$ is not constant its second argument on $[0, N_F]$.
+        &\leq  N_C \int_0^1 w_P(s) f(N_P, s N_F') \ds \\
+        &= \pi_P(N_P, N_F', N_C)
+    \end{align*}
+    with the inequality being strict if $N_F < N_F'$ and $f$ is not constant its second argument on $[0, N_F']$.
 \end{proof}
@@
     $\Pi$ satisfies \cref{ass:additive_profit,ass:monotone_profits,ass:monotone_profits}.
-    By \cref{prop:hybrid_vs_retail_general}, $\pi_P(N_P, N_F) \geq \pi_P(N_P, N_F)$ for any $N_F$, thus also for $N_F(N_P)$.
-    When $N_F(N_P) > 0$, the inequality is strict.
+    The result is an immediate corollary of \cref{prop:hybrid_vs_retail_general} with $N_F=0$ and $N'F=N_F(N_P)$.
+\end{proof}
+
+This observation then makes characterizing the profit-maximizing platform product variety in \cref{sec:endogenizing_n_p} easier, as one does not have to worry about comparing the different regimes in the case of the bargaining model.
+If, for a given $N_P$, hybrid mode would be feasible, then it is also optimal compared to being a pure retailer.
+This result allows us to prove an important result from the main text about the platform's profits as a function of its number of products.
+\begin{proof}[Proof of \cref{prop:comparative_n_p_bargaining}]
+    In the bargaining model, \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:additive_profit,ass:single_crossing} are satisfied.
+    From the proof of \cref{eq:platform_profits}, the platform's profits are strictly concave in the entry fee $K_F$.
+    This implies that for a fixed $N_P$,
+    \begin{align*}
+        \frac{\dd \pi_P}{\dd K_F} > 0 \text{ if } K_F < K_F^{opt},
+        \frac{\dd \pi_P}{\dd K_F} < 0 \text{ if } K_F > K_F^{opt}. \label{eq:profit_on_entry_fee}
+    \end{align*}
+    Now let us consider platform profits, but parametrized through $N_P$ and $K_F$ instead of the usual $N_P$ and $N_F$:
+    \begin{align*}
+        \frac{\dd \pi_P}{\dd N_P} &= \frac{\dd \pi_P(N_P, K_F(N_P))}{\dd N_P} \\
+        &= \frac{\pi_P(N_P, K_F)}{\partial N_P} + \frac{\pi_P(N_P, K_F)}{\partial K_F} \frac{\partial K_F}{\partial N_P}.
+    \end{align*}
+    \Cref{prop:platform_profits_comparative_benchmark} establishes that
+    \begin{align*}
+        \frac{\pi_P(N_P, K_F)}{\partial N_P} = \frac{V_P}{V_F} I_F
+    \end{align*}
+    in the hybrid regime, while \cref{prop:implied_entry_fee_comparative} states that
+    \begin{align*}
+        \frac{\partial K_F}{\partial N_P}.
+    \end{align*}
+    Together with \cref{eq:profit_on_entry_fee}, the statement of the proposition follows.
 \end{proof}
@@
     The total profit function of the platform is the following:
-    \begin{align*}
+    \begin{align}
         \pi_P^t &= \pi_P^v + K_F N_F \\
-        &= \mu \frac{N_P V_P}{K_F + I_F} + K_F \left[ \frac{\mu}{K_F + I_F} - N_P \frac{V_P}{V_F} - \frac{1}{V_F} \right].
-    \end{align*}
+        &= \mu \frac{N_P V_P}{K_F + I_F} + K_F \left[ \frac{\mu}{K_F + I_F} - N_P \frac{V_P}{V_F} - \frac{1}{V_F} \right]. \label{eq:platform_profits}
+    \end{align}
     The function is strictly concave in $K_F$, so the first order condition is sufficient for optimality in the case of an interior solution.
@@
     For the results about the pure retailer regime, use the fact that $A = N_P V_P + 1$ and $CS(A) = \mu\log(A)$.
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:optimal_n_p_benchmark}]
+    From \cref{prop:optimal_entry_fee,prop:equilibrium_benchmark} we have that
+    \begin{itemize}
+        \item $\frac{\dd \pi_P}{\dd N_P} = \frac{V_P}{V_F} I_F$ if $N_F(N_P) > 0$,
+        \item $\frac{\dd \pi_P}{\dd N_P} < \frac{V_P}{V_F} I_F$ if $N_F(N_P) = 0$.
+    \end{itemize}
+    It immediately follows that if the platform can invest in $N_P$ at cost $I_P$, then the optimal number of products is the one that maximizes profits:
+    \begin{align*}
+        \frac{V_P}{I_P} < \frac{V_F}{I_F} &\implies N_P^* = 0, \\
+        \frac{V_P}{I_P} > \frac{V_F}{I_F} &\implies N_P^* > 0, N_F(N_P^*) = 0, \\
+        \frac{V_P}{I_P} = \frac{V_F}{I_F} &\implies N_P^* \in [0, \bar{N}_P] \text{ for some } \bar{N}_P > 0.
+    \end{align*}
+    \Cref{fig:optimal_n_p_benchmark} demonstrates this graphically.
 \end{proof}

### 2024-06-21 src/paper/application.tex
Fix compilation error
Ass chen and riordan reference

@@
 In \cref{sec:model}, I introduce two model of hybrid platforms: a benchmark with the platform setting an entry fee unilaterally, and the main model, where the platform and the fringe firms engage in bargaining.
-After that, \cref{sec:results}\footnote{
-    \Cref{sec:more_general} explores the generalizability of these results, and highlights some common themes in settings with hybrid behavior.
-} demonstrates that the two have very different implications for consumer welfare.
+After that, \cref{sec:results} demonstrates that the two have very different implications for consumer welfare.
 \Cref{sec:extensions} then examines the effect of different assumptions about the bargaining process.
@@
 However, the model is quite general, and the results apply to a broader class of settings, such as vertical markets where the upstream firm can sell directly to consumers, or retail stores with their own private labels.
+Furthermore, while the discussion in the main text focuses on a specific demand structure and profit sharing rule, most of the results apply to a broader class of models.
+\Cref{sec:more_general} explores the generalizability of these results, and highlights some common themes in settings with hybrid behavior.
 
@@
 For each subgame, I also demonstrate that the equilibrium exists and is unique, and therefore the complete game also has a unique equilibrium.
+The propositions in this section are generally proven for a more general framework, and those presented here are special cases of those.
+For this reason, the proofs are also presented together with the more general model in \cref{sec:more_general}.
 
@@
 Alternatively, indirect network effects, such as those in two-sided markets, can also result in such increasing profits.
-Finally, if we assume that the platform can extract consumer surplus through entry fees or some similar mechanism, then this assumption will be true for any demand system in which total surplus is increasing in product variety.
+\textcite{chen2008price} demonstrates that under certain circumstances an even more extreme phenomenon might occur: competition may not only increase industry-wide profits, but prices, as well.
+Finally, under the assumption that the platform can extract consumer surplus through entry fees or some similar mechanism, this assumption is be true for any demand system in which total surplus is increasing in product variety.
 
@@
     This implies that for a fixed $N_P$,
-    \begin{align*}
-        \frac{\dd \pi_P}{\dd K_F} > 0 \text{ if } K_F < K_F^{opt},
-        \frac{\dd \pi_P}{\dd K_F} < 0 \text{ if } K_F > K_F^{opt}. \label{eq:profit_on_entry_fee}
-    \end{align*}
+    \begin{align}
+        &\frac{\dd \pi_P}{\dd K_F} > 0 \text{ if } K_F < K_F^{opt}, \nonumber \\
+        &\frac{\dd \pi_P}{\dd K_F} < 0 \text{ if } K_F > K_F^{opt}. \label{eq:profit_on_entry_fee}
+    \end{align}
     Now let us consider platform profits, but parametrized through $N_P$ and $K_F$ instead of the usual $N_P$ and $N_F$:
@@
     \begin{align}
+        \mu \frac{\exp\left( \frac{v_T - p_{T_i}}{\mu} \right)}{A} \left[ \frac{p_T - c_T}{\mu} - 1 \right] = 0.
         \label{eq:foc_profit}
-        \mu \frac{\exp\left( \frac{v_T - p_{T_i}}{\mu} \right)}{A} \left[ \frac{p_T - c_T}{\mu} - 1 \right] = 0.
     \end{align}
@@
     \begin{align}
-        \pi_P^t &= \pi_P^v + K_F N_F \\
+        \pi_P^t &= \pi_P^v + K_F N_F \nonumber \\
         &= \mu \frac{N_P V_P}{K_F + I_F} + K_F \left[ \frac{\mu}{K_F + I_F} - N_P \frac{V_P}{V_F} - \frac{1}{V_F} \right]. \label{eq:platform_profits}

### 2024-06-24 src/paper/application.tex
Change references to uppercase

@@
 
-\crefname{assumption}{assumption}{assumptions}
+\Crefname{assumption}{assumption}{assumptions}
 \Crefname{assumption}{Assumption}{Assumptions}
@@
 The rest of the paper is organized as follows.
-In \cref{sec:model}, I introduce two model of hybrid platforms: a benchmark with the platform setting an entry fee unilaterally, and the main model, where the platform and the fringe firms engage in bargaining.
-After that, \cref{sec:results} demonstrates that the two have very different implications for consumer welfare.
+In \Cref{sec:model}, I introduce two model of hybrid platforms: a benchmark with the platform setting an entry fee unilaterally, and the main model, where the platform and the fringe firms engage in bargaining.
+After that, \Cref{sec:results} demonstrates that the two have very different implications for consumer welfare.
 \Cref{sec:extensions} then examines the effect of different assumptions about the bargaining process.
-Finally, \cref{sec:conclusion} summarizes the results and discusses possible future work.
+Finally, \Cref{sec:conclusion} summarizes the results and discusses possible future work.
 
@@
 \Cref{sec:model_overview} provides an overview of the model's stages, the timing of the game, as well as the qeuilibrium concept used in this paper.
-Then, \cref{sec:model_details} describes each stage of the game formally.
-Finally, \cref{sec:model_discussion} discusses some of the assumptions made in the model, and their implications.
+Then, \Cref{sec:model_details} describes each stage of the game formally.
+Finally, \Cref{sec:model_discussion} discusses some of the assumptions made in the model, and their implications.
 
@@
 
-The timing of both models is illustrated in \cref{fig:timing}.
+The timing of both models is illustrated in \Cref{fig:timing}.
 The square brackets indicate the endogenous variables decided at that stage of the game.
-In the benchmark model (\cref{fig:timing_benchmark}), the game starts by the platform announcing and committing to an entry fee $K_F$ ($\mathbf{T_1}$).
+In the benchmark model (\Cref{fig:timing_benchmark}), the game starts by the platform announcing and committing to an entry fee $K_F$ ($\mathbf{T_1}$).
 Next, each fringe firm decides whether to create a product at cost $I_F$ and enter the market. ($\mathbf{T_2}$)
@@
 
-The bargaining model has a slightly different timing, as shown in \cref{fig:timing_bargaining}.
+The bargaining model has a slightly different timing, as shown in \Cref{fig:timing_bargaining}.
 The platform cannot commit to an entry fee at the beginning, so the game starts with the fringe firms deciding whether to invest in creating a product at cost $I_F$ ($\mathbf{T_1}$).
 After that, the entry fee is decided as a result of some negotiation\footnote{
-    The negotiation process, or rather its outcome is described in detail in \cref{sec:cooperative_game}.
+    The negotiation process, or rather its outcome is described in detail in \Cref{sec:cooperative_game}.
 } between the platform and the firms that have made the investment ($\mathbf{T_2}$).
@@
 \end{proposition}
-\begin{proof}[Proof of \cref{prop:shapley_value}]
-    The cooperative game is describer in detail in \cref{sec:cooperative_game_one_sided}.
-    This result is a direct consequence of \cref{prop:profit_sharing_one_sided}.
+\begin{proof}[Proof of \Cref{prop:shapley_value}]
+    The cooperative game is describer in detail in \Cref{sec:cooperative_game_one_sided}.
+    This result is a direct consequence of \Cref{prop:profit_sharing_one_sided}.
 \end{proof}
@@
 Furthermore, it has a number of appealing properties.
-For example, it is closely related to the marginal contributions of the players to the total value, and, as shown in \cref{sec:more_general_results}, it is also quite intuitive in terms of comparative statics.
+For example, it is closely related to the marginal contributions of the players to the total value, and, as shown in \Cref{sec:more_general_results}, it is also quite intuitive in terms of comparative statics.
 Furthermore, and perhaps more importantly, there are a number of ways to place it on non-cooperative microfoundations by setting up non-cooperative games for which the Shapley value is a subgame perfect equilibrium \parencite[e.g.][]{gul1989bargaining,hart1996bargaining,stole1996organizational}.
@@
 The subgame perfect equilibrium of the fully non-cooperative model described in that section coincides with the equilibrium of the bargaining model in the main text.
-Therefore, one can think of the cooperative game as a more tractable representation of the one from \cref{sec:bargaining_microfoundation}.
+Therefore, one can think of the cooperative game as a more tractable representation of the one from \Cref{sec:bargaining_microfoundation}.
 
@@
 The propositions in this section are generally proven for a more general framework, and those presented here are special cases of those.
-For this reason, the proofs are also presented together with the more general model in \cref{sec:more_general}.
+For this reason, the proofs are also presented together with the more general model in \Cref{sec:more_general}.
 
@@
 \end{proposition}
-\begin{proof}[Proof of \cref{prop:demand_function}]
+\begin{proof}[Proof of \Cref{prop:demand_function}]
     See Theorem 1 in \textcite{anderson2021hybrid}.
@@
 \end{proposition}
-Note that in the first case (\cref{eq:aggregate_eq}), the size of the aggregate does not depend on the platforms' product variety or the platform's product value.
+Note that in the first case (\Cref{eq:aggregate_eq}), the size of the aggregate does not depend on the platforms' product variety or the platform's product value.
 The intuition behind this is that per-firm fringe profits only depend on these factors indirectly, through the size of the aggregate.
@@
 Now let us turn to the optimal entry fee set by the platform, and its total profits (consisting of revenue from its own sales and the collected entry fees).
-The following proposition establishes these both for the hybrid and the pure retail regimes, and \cref{fig:entry_fee,fig:platform_profits} demonstrates them graphically.
+The following proposition establishes these both for the hybrid and the pure retail regimes, and \Cref{fig:entry_fee,fig:platform_profits} demonstrates them graphically.
 
@@
 First, let us look at the case when the platform finds it optimal to operate in the hybrid regime.
-As illustrated by \cref{fig:entry_fee}, the optimal entry fee (\cref{eq:entry_fee_benchmark}) does not depend on either the platform's product value or product variety.
+As illustrated by \Cref{fig:entry_fee}, the optimal entry fee (\Cref{eq:entry_fee_benchmark}) does not depend on either the platform's product value or product variety.
 This is because due to the lump-sum nature of the entry fee, the platform can extract all the surplus from the fringe firms, and thus chooses $K_F$ to maximize total industry profits.
 The latter is essentially a function of the aggregate, minus the investment costs of the fringe firms.
-As I show later in \cref{prop:equilibrium_benchmark}, the aggregate is independent of the platform's product variety in the hybrid regime, and therefore the optimal entry fee is also independent of it.
-
-On the other hand, \cref{fig:platform_profits}\footnote{
+As I show later in \Cref{prop:equilibrium_benchmark}, the aggregate is independent of the platform's product variety in the hybrid regime, and therefore the optimal entry fee is also independent of it.
+
+On the other hand, \Cref{fig:platform_profits}\footnote{
     $\frac{\dd X}{\dd N_P}$ denotes equilibrium comparative statics.
     I.e., if the variable $X$ is a function of $N_P$ and $N_F$, then $$\frac{\dd X}{\dd N_P} = \frac{\partial X(N_P, N_F(N_P))}{\partial N_P}$$.
-} shows the platform's profit (\cref{eq:platform_profits_hybrid_benchmark,eq:platform_profits_retail_benchmark}) is increasing in the number of its products.
+} shows the platform's profit (\Cref{eq:platform_profits_hybrid_benchmark,eq:platform_profits_retail_benchmark}) is increasing in the number of its products.
 \begin{corollary}
@@
 This is due to the fact that the optimal entry fee, which is independent of $N_P$, pins down the aggregate.
-As shown in \cref{fig:fringe_entry_eq}, an increase in the platform's product variety will simply replace fringe firms in a constant ratio, such that the aggregate remains constant (\cref{fig:welfare_aggregate}).
-This, in turn, implies that consumer surplus is also unaffected by the platform's product variety in the hybrid regime, as demonstrated in \cref{fig:welfare_consumer_surplus}.
+As shown in \Cref{fig:fringe_entry_eq}, an increase in the platform's product variety will simply replace fringe firms in a constant ratio, such that the aggregate remains constant (\Cref{fig:welfare_aggregate}).
+This, in turn, implies that consumer surplus is also unaffected by the platform's product variety in the hybrid regime, as demonstrated in \Cref{fig:welfare_consumer_surplus}.
 
 When the platform finds it optimal to operate as a pure retailer, the only products on the market are the platform's own products.
-Therefore, quite mechanically, the aggregate, and thus consumer surplus, are increasing in the number of the platform's products (unshaded parts of \cref{fig:welfare}).
+Therefore, quite mechanically, the aggregate, and thus consumer surplus, are increasing in the number of the platform's products (unshaded parts of \Cref{fig:welfare}).
 
@@
 Therefore, for a given $N_P$, the platform prefers to operate in hybrid mode, and does not want to exclude fringe firms from the market.
-This fact, together with the \cref{prop:equilibrium_benchmark}, implies that the platform's product variety always has a weakly positive effect on consumer welfare.\footnote{
+This fact, together with the \Cref{prop:equilibrium_benchmark}, implies that the platform's product variety always has a weakly positive effect on consumer welfare.\footnote{
     This is in contrast to \textcite{anderson2021hybrid}, where a platform operating in hybrid mode sets higher royalties to create a price advantage for its own products.
@@
 
-As described in \cref{sec:model_bargaining}, participants negotiate over the aggregate profits that they expect to obtain in the subsequent period (assuming the same non-collusive, monopolistic pricing, as before).
-From \cref{eq:optimal_profit}, the total profit achieved by the platform and $N_F$ fringe firms is given by
+As described in \Cref{sec:model_bargaining}, participants negotiate over the aggregate profits that they expect to obtain in the subsequent period (assuming the same non-collusive, monopolistic pricing, as before).
+From \Cref{eq:optimal_profit}, the total profit achieved by the platform and $N_F$ fringe firms is given by
 \begin{align*}
@@
 \end{align*}
-Bargaining outcomes are determined according to Shapley values, given by \cref{prop:shapley_value}.
+Bargaining outcomes are determined according to Shapley values, given by \Cref{prop:shapley_value}.
 Based on these, one can obtain closed-form expressions for platform and fringe profit shares for this class of demand systems.
@@
     These results do not actually rely on the specific logit demand system.
-    As long as the fringe profit function has the property described in \cref{lem:shape_of_fringe_profit}, and the total profit function satisfies some assumptions, the results hold.
+    As long as the fringe profit function has the property described in \Cref{lem:shape_of_fringe_profit}, and the total profit function satisfies some assumptions, the results hold.
     \Cref{sec:more_general_results} provides more detail on the necessary assumptions.
@@
 Let us denote this point as $N_F^*$.
-Furthermore, if such a crossing exists, then it must be that $\pi_F^t(N_F) > I_F N_F \;\forall\, N_F < N_F^*$, and $\pi_F^t(N_F) < I_F N_F \;\forall\, N_F > N_F^*$ (see \cref{fig:equilibrium} for an illustration of this idea).
+Furthermore, if such a crossing exists, then it must be that $\pi_F^t(N_F) > I_F N_F \;\forall\, N_F < N_F^*$, and $\pi_F^t(N_F) < I_F N_F \;\forall\, N_F > N_F^*$ (see \Cref{fig:equilibrium} for an illustration of this idea).
 Therefore, $N_F^*$ must be the unique number of equilibrium entrants.
@@
 
-As illustrated in \cref{fig:comparative_N_F}, together with the hump-shaped fringe profit function, this implies that an increase in the platform's product variety leads to a reduction in the number of fringe firms.
+As illustrated in \Cref{fig:comparative_N_F}, together with the hump-shaped fringe profit function, this implies that an increase in the platform's product variety leads to a reduction in the number of fringe firms.
 What is not immediately clear is how this affects the total size of the aggregate, and consumer welfare.
@@
 The main takeaway from this theorem is that the increasing the platform's product variety can actually decrease consumer welfare in the bargaining model.
-The underlying reason is illustrated in \cref{fig:fringe_entry_eq}: the decrease in the number of fringe entrants is large enough to not only to offset the increase in the platform's product variety, but also to decrease the aggregate (\cref{fig:welfare_aggregate}).
-This in turn leads to a decrease in consumer surplus (\cref{fig:welfare_consumer_surplus}).
+The underlying reason is illustrated in \Cref{fig:fringe_entry_eq}: the decrease in the number of fringe entrants is large enough to not only to offset the increase in the platform's product variety, but also to decrease the aggregate (\Cref{fig:welfare_aggregate}).
+This in turn leads to a decrease in consumer surplus (\Cref{fig:welfare_consumer_surplus}).
 
@@
 First, define the implied entry fee in the bargaining case as the difference between the variable profit and the final, total profit of the fringe firms (bar the investment cost)\footnote{
-    Or, in light of \cref{sec:bargaining_microfoundation}, it can also directly be interpreted as the entry fee that the parties agree on after negotiating.
+    Or, in light of \Cref{sec:bargaining_microfoundation}, it can also directly be interpreted as the entry fee that the parties agree on after negotiating.
 }:
@@
 \end{proposition}
-This is not happening in the benchmark model, because, as stated in \cref{prop:optimal_entry_fee}, the optimal entry fee does not depend on the platform's product variety.
+This is not happening in the benchmark model, because, as stated in \Cref{prop:optimal_entry_fee}, the optimal entry fee does not depend on the platform's product variety.
 \Cref{fig:entry_fee} demonstrates this difference between the two models.
@@
 Remember, that in the bargaining model, the implied entry fee is increasing in the number of the platform's products.
-Together with the concavity of platform profits as a function of $N_P$, and the statement of \cref{prop:platform_profits_comparative_benchmark}, this implies the following result:
+Together with the concavity of platform profits as a function of $N_P$, and the statement of \Cref{prop:platform_profits_comparative_benchmark}, this implies the following result:
 \begin{proposition}
@@
 \paragraph{Generality of the figures}
-While \cref{fig:entry_and_fees,fig:platform_profits,fig:welfare} illustrate the main results of this paper under a specific parametrization, many of the insights are more general.
-In particular, the higher-than-proportional decrease in the number of fringe firms as the platform's product variety increases, and the resulting negative effect on consumer welfare, have corresponding theorems that hold for any parametrization (\cref{prop:equilibrium_benchmark,prop:equilibrium_bargaining}).
-Similarly, the implied entry fee being increasing in the number of the platform's products is a general result (\cref{prop:implied_entry_fee_comparative}).
+While \Cref{fig:entry_and_fees,fig:platform_profits,fig:welfare} illustrate the main results of this paper under a specific parametrization, many of the insights are more general.
+In particular, the higher-than-proportional decrease in the number of fringe firms as the platform's product variety increases, and the resulting negative effect on consumer welfare, have corresponding theorems that hold for any parametrization (\Cref{prop:equilibrium_benchmark,prop:equilibrium_bargaining}).
+Similarly, the implied entry fee being increasing in the number of the platform's products is a general result (\Cref{prop:implied_entry_fee_comparative}).
 
@@
 being increasing in the number of platform products and fringe firms) would still hold.
-As long as \cref{lem:shape_of_fringe_profit} holds, the main results of the bargaining model would also be valid.
+As long as \Cref{lem:shape_of_fringe_profit} holds, the main results of the bargaining model would also be valid.
 
@@
 It does simplify the analysis, especially in terms of consumer welfare, but the main results would also hold for a larger class of demand functions\footnote{
-    In particular, demand functions for which the implied profit functions satisfy the assumptions in \cref{sec:more_general}.
+    In particular, demand functions for which the implied profit functions satisfy the assumptions in \Cref{sec:more_general}.
 }.
@@
 
-As shown in \cref{sec:cooperative_game_weighted}, the weighted Shapley value, and thus final profits in this setting is given by
+As shown in \Cref{sec:cooperative_game_weighted}, the weighted Shapley value, and thus final profits in this setting is given by
 \begin{proposition}
@@
 \end{proposition}
-\begin{proof}[Proof of \cref{prop:weighted_shapley_value}]
-\end{proof}
-This result is a direct consequence of \cref{prop:profit_sharing_weighted}.
+\begin{proof}[Proof of \Cref{prop:weighted_shapley_value}]
+\end{proof}
+This result is a direct consequence of \Cref{prop:profit_sharing_weighted}.
 It is similar to the non-weighted value in that it is an average of marginal contributions, but now those averages are weighted, with the weight function depending on platform's bargaining weight.
@@
 \end{proposition}
-\begin{proof}[Proof of \cref{prop:lambda_P_comparative}]
+\begin{proof}[Proof of \Cref{prop:lambda_P_comparative}]
     For any $\lambda < \lambda'$, $\int_0^s \lambda t^{\lambda - 1} \dt = s^\lambda > s^{\lambda'} = \int_0^s \lambda' t^{\lambda' - 1} \dt \forall s \in [0, 1]$.
@@
 The main result, namely that the platform's product variety has a negative effect on consumer welfare in the hybrid regime, still holds.
-That is, as shown on \cref{fig:fringe_entry_eq_high_lambda}, total aggregate is decreasing in $N_P$ throughout the hybrid regime, due to the platform's products displacing more fringe products than their total number.
-
-The main difference is that, for any $N_P\geq 0$, the implied entry fee (\cref{fig:platform_profits_high_lambda}) is higher than the benchmark, unilaterally set one,  due to the higher bargaining power of the platform.
+That is, as shown on \Cref{fig:fringe_entry_eq_high_lambda}, total aggregate is decreasing in $N_P$ throughout the hybrid regime, due to the platform's products displacing more fringe products than their total number.
+
+The main difference is that, for any $N_P\geq 0$, the implied entry fee (\Cref{fig:platform_profits_high_lambda}) is higher than the benchmark, unilaterally set one,  due to the higher bargaining power of the platform.
 That is, for any $N_P$, the platform would prefer to set a lower entry fee, but it is unable to do so due to its high bargaining power.
@@
 Let us start by deriving total surplus as a function of $N_P, N_F$ and $N_C$ (the number of customers).
-Under the logit-like demand structure described in \cref{sec:demand}, the total surplus is given by
+Under the logit-like demand structure described in \Cref{sec:demand}, the total surplus is given by
 \begin{proposition}
@@
 \end{proposition}
-\begin{proof}[Proof of \cref{prop:profits_total_surplus}]
+\begin{proof}[Proof of \Cref{prop:profits_total_surplus}]
     See \textcite{small1981applied} for a derivation for the discrete case.
@@
 Next, let us consider the bargaining outcomes in this three-sided setting.
-\Cref{sec:cooperative_game_two_sided} formally describes the corresponding cooperative game, and \cref{prop:profit_sharing_two_sided} establishes the resulting profit shares.
+\Cref{sec:cooperative_game_two_sided} formally describes the corresponding cooperative game, and \Cref{prop:profit_sharing_two_sided} establishes the resulting profit shares.
 To summarize, the various players share the total surplus in the following way.
@@
 \end{proposition}
-\begin{proof}[Proof of \cref{prop:three_way_shapley_value}]
+\begin{proof}[Proof of \Cref{prop:three_way_shapley_value}]
     \Cref{sec:cooperative_game_two_sided} formally describes the cooperative game corresponding to the three-sided bargaining assumption.
-    This result is a direct consequence of \cref{prop:profit_sharing_two_sided}.
+    This result is a direct consequence of \Cref{prop:profit_sharing_two_sided}.
 \end{proof}
@@
 \end{proposition}
-\begin{proof}[Proof of \cref{prop:fringe_entry_two_sided}]
-    The proof is analogous to that of \cref{prop:equilibrium_bargaining}.
-    To see that $\frac{\partial \pi_F}{\partial N_F}$ satisfies \cref{ass:single_crossing}, first consider the function
+\begin{proof}[Proof of \Cref{prop:fringe_entry_two_sided}]
+    The proof is analogous to that of \Cref{prop:equilibrium_bargaining}.
+    To see that $\frac{\partial \pi_F}{\partial N_F}$ satisfies \Cref{ass:single_crossing}, first consider the function
     \begin{align*}
@@
     \end{align*}
-    is concave, and thus satisfies \cref{ass:single_crossing}.
-    By \cref{lem:single_crossing_affine_transformation}, $\pi_F$ then also satisfies \cref{ass:single_crossing}.
-    Finally, as \cref{ass:additive_profit,ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:single_crossing} are satisfied, it follows from \cref{prop:aggregate_size_additive} that
+    is concave, and thus satisfies \Cref{ass:single_crossing}.
+    By \Cref{lem:single_crossing_affine_transformation}, $\pi_F$ then also satisfies \Cref{ass:single_crossing}.
+    Finally, as \Cref{ass:additive_profit,ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:single_crossing} are satisfied, it follows from \Cref{prop:aggregate_size_additive} that
     \begin{align*}
@@
 
-As a consequence, the aggregate is decreasing in $N_P$ in the hybrid regime (\cref{fig:fringe_entry_eq_full_surplus_two_sided}).
+As a consequence, the aggregate is decreasing in $N_P$ in the hybrid regime (\Cref{fig:fringe_entry_eq_full_surplus_two_sided}).
 \begin{corollary}
@@
 \begin{proof}
-    This result also follows from the applicability of \cref{prop:aggregate_size_additive}.
+    This result also follows from the applicability of \Cref{prop:aggregate_size_additive}.
 \end{proof}
@@
 While this does lead to a decrease in total surplus, in contrast to the two-sided bargaining case, this does not imply a decrease in the customers' surplus.
-Their share of total surplus is equal to the platform's profits, and thus it is increasing in $N_P$ if and only if platform profits (\cref{fig:profits_full_surplus_two_sided}) are.
+Their share of total surplus is equal to the platform's profits, and thus it is increasing in $N_P$ if and only if platform profits (\Cref{fig:profits_full_surplus_two_sided}) are.
 Therefore, customers might prefer hybrid operation to the platform being a pure marketplace.
@@
 I assume that $w_P(s) = w_F(s) \equiv 1$.
-As \cref{sec:cooperative_game} demonstrates, this corresponds to players. Getting their Shapley values in the end.
-Together with the assumptions on the demand system, one can even derive a closed form expression for the platform's profit share (\cref{prop:platform_profits_bargaining}).
+As \Cref{sec:cooperative_game} demonstrates, this corresponds to players. Getting their Shapley values in the end.
+Together with the assumptions on the demand system, one can even derive a closed form expression for the platform's profit share (\Cref{prop:platform_profits_bargaining}).
 The proof if this proposition is given below.
-\begin{proof}[Proof of \cref{prop:platform_profits_bargaining}]
+\begin{proof}[Proof of \Cref{prop:platform_profits_bargaining}]
     Simply integrate the total industry profit function with respect to the mass of fringe entrants obtain the platform's share of the pie:
@@
     \label{prop:outcome_based_bargaining_power}
-    Assume that \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing} hold.
+    Assume that \Cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing} hold.
     Fix some $N_P, N_C \geq 0$.
@@
 \end{proposition}
-\begin{proof}[Proof of \cref{prop:outcome_based_bargaining_power}]
+\begin{proof}[Proof of \Cref{prop:outcome_based_bargaining_power}]
     Immediately follows from the monotonicity of the integral.
@@
 
-In words, \cref{prop:outcome_based_bargaining_power} describes two alternative worlds, in which $N_F$ fringe firms (assuming a platform with $N_P$ product variety and $N_C$ consumers) are able to achieve the same total profit level.
-However, in the case with $\tilde{f}$, the fringe firms are more substitutable to each other in the sense that fewer of them are needed to achieve a given level of profit (see \cref{fig:outcome_based_bargaining_power}).
+In words, \Cref{prop:outcome_based_bargaining_power} describes two alternative worlds, in which $N_F$ fringe firms (assuming a platform with $N_P$ product variety and $N_C$ consumers) are able to achieve the same total profit level.
+However, in the case with $\tilde{f}$, the fringe firms are more substitutable to each other in the sense that fewer of them are needed to achieve a given level of profit (see \Cref{fig:outcome_based_bargaining_power}).
 The observation is that, in this situation, the platform's share is indeed higher when the fringe firms are more substitutable.
@@
 Under the specific demand system and profit sharing rule described in the main text, it can be shown that this assumption is satisfied.
-\begin{proof}[Proof of \cref{lem:shape_of_fringe_profit}]
+\begin{proof}[Proof of \Cref{lem:shape_of_fringe_profit}]
     First, consider the function
@@
     Now let us consider the function $h(x) = N_C \mu g(N_P V_P + V_F x)$.
-    By \cref{lem:single_crossing_affine_transformation}, $H(x) = \int_0^1 s h'(sx) \ds$ is also either concave or decreasing for any $x > 0$.
+    By \Cref{lem:single_crossing_affine_transformation}, $H(x) = \int_0^1 s h'(sx) \ds$ is also either concave or decreasing for any $x > 0$.
     Finally, notice that $H(x)$ is exactly the profit function of the fringe:
@@
 
-With \cref{ass:single_crossing} in place, uniqueness of the equilibrium can be established.
+With \Cref{ass:single_crossing} in place, uniqueness of the equilibrium can be established.
 \begin{proposition}
     \label{prop:unique_equilibrium_more_general}
-    Under the conditions in \cref{ass:free_entry,ass:single_crossing}, the equilibrium is unique if it exists.
+    Under the conditions in \Cref{ass:free_entry,ass:single_crossing}, the equilibrium is unique if it exists.
 \end{proposition}
-\begin{proof}[Proof of \cref{prop:unique_equilibrium_more_general}]
+\begin{proof}[Proof of \Cref{prop:unique_equilibrium_more_general}]
     \Cref{lem:slope_at_eq} states that for any positive $N_F^*$ for which $\pi_F(N_P, N_F^*) - N_F I_F$, the partial derivative with respect to the number of fringe firms is negative.
@@
 
-The intuition behind this result is that \cref{ass:single_crossing} ensures that the total profits achieved by the fringe is either concave or hump-shaped.
+The intuition behind this result is that \Cref{ass:single_crossing} ensures that the total profits achieved by the fringe is either concave or hump-shaped.
 Consequently, it has at most one crossing with the -- convex and increasing -- total entry cost function (for $n_F > 0$).
 This particular shape (concave or hump-shaped) is also the main driver for the later results about the comparative statics of equilibrium profits and entry.
-Given that \cref{ass:free_entry,ass:single_crossing} is satisfied in the model presented in the main text, it immediately follows that the equilibrium in that model is also unique.
-\begin{proof}[Proof of \cref{prop:unique_equilibrium}]
+Given that \Cref{ass:free_entry,ass:single_crossing} is satisfied in the model presented in the main text, it immediately follows that the equilibrium in that model is also unique.
+\begin{proof}[Proof of \Cref{prop:unique_equilibrium}]
     \Cref{lem:shape_of_fringe_profit} demonstrates that the fringe total profit function is either concave or decreasing in the number of fringe firms.
-    Thus, \cref{ass:single_crossing} is satisfied, and \cref{prop:unique_equilibrium_more_general} implies that the equilibrium number of fringe entrants is unique.
+    Thus, \Cref{ass:single_crossing} is satisfied, and \Cref{prop:unique_equilibrium_more_general} implies that the equilibrium number of fringe entrants is unique.
 \end{proof}
@@
     \label{prop:share_of_platform}
-    Let \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing} hold.
+    Let \Cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing} hold.
     Also assume that $f$ is continuously differentiable with respect to $N_P$ and also twice differentiable.
@@
 \end{proposition}
-\begin{proof}[Proof of \cref{prop:share_of_platform}]
+\begin{proof}[Proof of \Cref{prop:share_of_platform}]
     $f(N_P, N_F)$ is continuously differentiable in $N_P$, therefore the Leibniz rule can be applied to obtain
@@
 }
-\cref{fig:increase_N_P_platform} shows an example of this situation.
+\Cref{fig:increase_N_P_platform} shows an example of this situation.
 
@@
     \end{subfigure}
-    \caption{Illustration of \cref{prop:share_of_platform} in the one-sided bargaining case.
+    \caption{Illustration of \Cref{prop:share_of_platform} in the one-sided bargaining case.
 The right hand side figure shows a world with larger platform product variety ($N_P < N_P'$).
@@
     \label{prop:share_of_fringe}
-    Let \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing} hold.
+    Let \Cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing} hold.
     Furthermore, assume that $f, w$ are twice continuously differentiable.
@@
 \end{proposition}
-\begin{proof}[Proof of \cref{prop:share_of_fringe}]
+\begin{proof}[Proof of \Cref{prop:share_of_fringe}]
     Remember that
@@
 In summary, when they are mostly substitutes (the cross-derivatives of $f$ are negative), the fringe's profits decrease as a result of an increase in $N_F$.
-The intuition is that, even though the total size of the pie increases, the bargaining power of the fringe deteriorates so much that its total profits decreases not only in relative, but also in absolute terms (as illustrated in \cref{fig:increase_N_P_fringe}).
+The intuition is that, even though the total size of the pie increases, the bargaining power of the fringe deteriorates so much that its total profits decreases not only in relative, but also in absolute terms (as illustrated in \Cref{fig:increase_N_P_fringe}).
 On the other hand, when the fringe firms are mostly complements the fringe's profits increase.
@@
     \end{subfigure}
-    \caption{Illustration of \cref{prop:share_of_fringe} when fringe and platform products are substitutes.
+    \caption{Illustration of \Cref{prop:share_of_fringe} when fringe and platform products are substitutes.
 An increase in the platform's product variety increases total profits, yet, the fringe's share decreases in absolute terms.}
@@
     \label{cor:fringe_entry}
-    Let \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:free_entry,ass:single_crossing} hold.
+    Let \Cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:free_entry,ass:single_crossing} hold.
     Furthermore, assume that $f, w$ are twice continuously differentiable.
@@
 \end{corollary}
-\begin{proof}[Proof of \cref{cor:fringe_entry}]
+\begin{proof}[Proof of \Cref{cor:fringe_entry}]
     \Cref{prop:unique_equilibrium} establishes that if an equilibrium with $N_F > 0$ exists, it is unique.
-    Use the implicit function theorem on the equation from \cref{ass:free_entry} to obtain
+    Use the implicit function theorem on the equation from \Cref{ass:free_entry} to obtain
     \begin{align*}
@@
     The derivative exists if the above expression is well-defined, i.e. $\frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} \neq I_F$.
-    Remember from \cref{prop:share_of_fringe} that the numerator of this expression is negative under the condition $\frac{\partial^2 f(N_P, N_F, N_C)}{\partial N_P \partial N_F}$.
+    Remember from \Cref{prop:share_of_fringe} that the numerator of this expression is negative under the condition $\frac{\partial^2 f(N_P, N_F, N_C)}{\partial N_P \partial N_F}$.
     Now all we need to show to conclude the proof is that
@@
     \end{align*}
-    which is the statement of \cref{lem:slope_at_eq}.
+    which is the statement of \Cref{lem:slope_at_eq}.
 \end{proof}
@@
 Based on this general result, the corresponding on in the main text follows immediately.
-\begin{proof}[Proof of \cref{prop:fringe_profits_partial}]
-    $\pi^t_F(N_P ,N_F)$ adheres to the \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing}.
+\begin{proof}[Proof of \Cref{prop:fringe_profits_partial}]
+    $\pi^t_F(N_P ,N_F)$ adheres to the \Cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing}.
     Furthermore, 
@@
     \end{align*}
-    Therefore, by \cref{prop:share_of_fringe},
+    Therefore, by \Cref{prop:share_of_fringe},
     \begin{align*}
@@
     \label{prop:aggregate_size_additive}
-    Let \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:free_entry,ass:single_crossing,ass:additive_profit} hold.
+    Let \Cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:free_entry,ass:single_crossing,ass:additive_profit} hold.
     Then
@@
 \end{proposition}
-\begin{proof}[Proof of \cref{prop:aggregate_size_additive}]
+\begin{proof}[Proof of \Cref{prop:aggregate_size_additive}]
     Use the implicit function theorem to get the equilibrium number of fringe firms as a function of the platform's product variety:
@@
     \end{align*}
-    Remember, that from \cref{lem:slope_at_eq}, and the assumption on the investment cost function we have that $\frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} < I_F$.
+    Remember, that from \Cref{lem:slope_at_eq}, and the assumption on the investment cost function we have that $\frac{\partial \pi_F (N_P, N_F, N_C)}{\partial N_F} < I_F$.
     Then, substitute $f(N_P, N_F) = g(\alpha N_P + \beta N_P)$ into $\pi_F$ to get the following fringe profit function:
@@
     \end{align*}
-    From \cref{lem:slope_at_eq}, we know that the denominator of this expression is positive.
+    From \Cref{lem:slope_at_eq}, we know that the denominator of this expression is positive.
     Furthermore, the concavity of $g$ implies that expression (2) is also positive.
-    Finally, from \cref{prop:share_of_fringe}, we have that the whole expression must be negative.
+    Finally, from \Cref{prop:share_of_fringe}, we have that the whole expression must be negative.
 
@@
 
-The first part of this proposition is a stronger version of \cref{cor:fringe_entry}.
+The first part of this proposition is a stronger version of \Cref{cor:fringe_entry}.
 It states that, not only does the equilibrium number of fringe firms decrease as a response to an increase in $N_P$, but it establishes a lower bound for this decrease.
@@
 The demand system presented in the main text also has this property, and thus the results of this proposition apply to it as well.
-\begin{proof}[Proof of \cref{prop:platform_profits_comparative_benchmark}]
-    Simply differentiate \cref{eq:platform_profits_hybrid_benchmark} with respect to $N_P$.
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:equilibrium_bargaining}]
-    $\pi^t_F(N_P ,N_F)$ adheres to the \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:additive_profit,ass:single_crossing}.
-    Therefore, by \cref{prop:aggregate_size_additive}
+\begin{proof}[Proof of \Cref{prop:platform_profits_comparative_benchmark}]
+    Simply differentiate \Cref{eq:platform_profits_hybrid_benchmark} with respect to $N_P$.
+\end{proof}
+
+\begin{proof}[Proof of \Cref{prop:equilibrium_bargaining}]
+    $\pi^t_F(N_P ,N_F)$ adheres to the \Cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:additive_profit,ass:single_crossing}.
+    Therefore, by \Cref{prop:aggregate_size_additive}
     \begin{align*}
@@
     immediately follows.
-    The second set of results can be obtained from this, as well as \cref{eq:aggregate_simple}:
+    The second set of results can be obtained from this, as well as \Cref{eq:aggregate_simple}:
     \begin{align*}
@@
 \Cref{prop:implied_entry_fee_comparative} can be viewed as a corollary of the previous theorem.
-\begin{proof}[Proof of \cref{prop:implied_entry_fee_comparative}]
-    Remember that in the hybrid regime, regardless of $N_P$, the size o the aggregate is pinned down by the entry fee $K_F$ (\cref{eq:aggregate_eq}).
+\begin{proof}[Proof of \Cref{prop:implied_entry_fee_comparative}]
+    Remember that in the hybrid regime, regardless of $N_P$, the size o the aggregate is pinned down by the entry fee $K_F$ (\Cref{eq:aggregate_eq}).
     Conversely, when given some $A$, there is a unique entry fee that supports it:
@@
 Now let us consider how the platform's product variety impacts its total profits, also taking into account its effect on the number of fringe entrants.
-While \cref{prop:share_of_platform} establishes that the platform's profits increase in its own product variety, it is not a general equilibrium result.
+While \Cref{prop:share_of_platform} establishes that the platform's profits increase in its own product variety, it is not a general equilibrium result.
 In particular, we know that increasing the platform's product variety leads to a decrease in the number of fringe entrants, and in total profits.
@@
     \label{prop:hybrid_vs_retail_general}
-    Under \cref{ass:additive_profit,ass:monotone_profits,ass:monotone_profits}, for any $N_C, N_P\leq 0$ and $0 \geq N_F \leq N_F'$
+    Under \Cref{ass:additive_profit,ass:monotone_profits,ass:monotone_profits}, for any $N_C, N_P\leq 0$ and $0 \geq N_F \leq N_F'$
     \begin{align*}
@@
 \end{proposition}
-\begin{proof}[Proof of \cref{prop:hybrid_vs_retail_general}]
+\begin{proof}[Proof of \Cref{prop:hybrid_vs_retail_general}]
     \begin{align*}
@@
 \Cref{prop:hybrid_vs_retail} is then a special case of this result.
-\begin{proof}[Proof of \cref{hybrid_vs_retail}]
-    $\Pi$ satisfies \cref{ass:additive_profit,ass:monotone_profits,ass:monotone_profits}.
-    The result is an immediate corollary of \cref{prop:hybrid_vs_retail_general} with $N_F=0$ and $N'F=N_F(N_P)$.
-\end{proof}
-
-This observation then makes characterizing the profit-maximizing platform product variety in \cref{sec:endogenizing_n_p} easier, as one does not have to worry about comparing the different regimes in the case of the bargaining model.
+\begin{proof}[Proof of \Cref{hybrid_vs_retail}]
+    $\Pi$ satisfies \Cref{ass:additive_profit,ass:monotone_profits,ass:monotone_profits}.
+    The result is an immediate corollary of \Cref{prop:hybrid_vs_retail_general} with $N_F=0$ and $N'F=N_F(N_P)$.
+\end{proof}
+
+This observation then makes characterizing the profit-maximizing platform product variety in \Cref{sec:endogenizing_n_p} easier, as one does not have to worry about comparing the different regimes in the case of the bargaining model.
 If, for a given $N_P$, hybrid mode would be feasible, then it is also optimal compared to being a pure retailer.
 This result allows us to prove an important result from the main text about the platform's profits as a function of its number of products.
-\begin{proof}[Proof of \cref{prop:comparative_n_p_bargaining}]
-    In the bargaining model, \cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:additive_profit,ass:single_crossing} are satisfied.
-    From the proof of \cref{eq:platform_profits}, the platform's profits are strictly concave in the entry fee $K_F$.
+\begin{proof}[Proof of \Cref{prop:comparative_n_p_bargaining}]
+    In the bargaining model, \Cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:additive_profit,ass:single_crossing} are satisfied.
+    From the proof of \Cref{eq:platform_profits}, the platform's profits are strictly concave in the entry fee $K_F$.
     This implies that for a fixed $N_P$,
@@
     \end{align*}
-    in the hybrid regime, while \cref{prop:implied_entry_fee_comparative} states that
+    in the hybrid regime, while \Cref{prop:implied_entry_fee_comparative} states that
     \begin{align*}
@@
     \end{align*}
-    Together with \cref{eq:profit_on_entry_fee}, the statement of the proposition follows.
+    Together with \Cref{eq:profit_on_entry_fee}, the statement of the proposition follows.
 \end{proof}
@@
 This subsection contains a couple of lemmas that are, while not very interesting on their own, necessary for the proofs in the previous sections.
-Furthermore, it contains the proofs of the results presented in \cref{sec:results_benchmark}, as they are not related to the bargaining framework, and are thus omitted from the previous sections.
-
-The first lemma is helpful for establishing whether \cref{ass:single_crossing} holds under a certain $f$ function.
+Furthermore, it contains the proofs of the results presented in \Cref{sec:results_benchmark}, as they are not related to the bargaining framework, and are thus omitted from the previous sections.
+
+The first lemma is helpful for establishing whether \Cref{ass:single_crossing} holds under a certain $f$ function.
 It states that showing that it holds for any affine transformation of $f$ is sufficient.
@@
 \end{lemma}
-\begin{proof}[Proof of \cref{lem:single_crossing_affine_transformation}]
+\begin{proof}[Proof of \Cref{lem:single_crossing_affine_transformation}]
     Differentiating $H$ yields
@@
     \label{lem:slope_at_eq}
-    Let the conditions in \cref{ass:single_crossing} hold.
+    Let the conditions in \Cref{ass:single_crossing} hold.
 Then for any $N_F^* > 0$ for which $\pi_F(N_P, N_F^*, N_C) = I_F N_F$, the partial derivative of fringe profits with respect to the number of fringe firms is smaller than the investment cost $I_F$:
@@
 \end{lemma}
-\begin{proof}[Proof of \cref{lem:slope_at_eq}]
-    \cref{ass:single_crossing} states that at any $N_F \geq 0$, $\pi_F(N_P, N_F, N_C)$ is either concave or decreasing in $N_F$.
+\begin{proof}[Proof of \Cref{lem:slope_at_eq}]
+    \Cref{ass:single_crossing} states that at any $N_F \geq 0$, $\pi_F(N_P, N_F, N_C)$ is either concave or decreasing in $N_F$.
     In the remainder, let us denote partial derivatives as follows:
@@
 
-\begin{proof}[Proof of \cref{prop:optimal_profit}]
+\begin{proof}[Proof of \Cref{prop:optimal_profit}]
     The profit function for product $Ti$ is the following:
@@
 
-    Now simply rearrange \cref{eq:foc_profit} to obtain
+    Now simply rearrange \Cref{eq:foc_profit} to obtain
     \begin{align*}
@@
 
-\begin{proof}[Proof of \cref{prop:equilibrium_aggregate_benchmark}]
-    From \cref{prop:optimal_profit}, the variable profit of each fringe firm is $\pi_{F_i}^{v*} = \mu V_F / A$.
+\begin{proof}[Proof of \Cref{prop:equilibrium_aggregate_benchmark}]
+    From \Cref{prop:optimal_profit}, the variable profit of each fringe firm is $\pi_{F_i}^{v*} = \mu V_F / A$.
     Total profit after entry fees and investment costs is therefore $\pi_{F_i}^{t*} = \mu V_F / A - I_F - K_F$.
@@
 
-\begin{proof}[Proof of \cref{prop:optimal_entry_fee}]
+\begin{proof}[Proof of \Cref{prop:optimal_entry_fee}]
     The total profit function of the platform is the following:
@@
 
-\begin{proof}[Proof of \cref{prop:platform_profits_comparative_benchmark}]
-    Simply differentiate \cref{eq:platform_profits_hybrid_benchmark} with respect to $N_P$.
-\end{proof}
-
-\begin{proof}[Proof of \cref{prop:equilibrium_benchmark}]
-    The first statement follows from differentiating \cref{eq:N_F_eq} with respect to $N_P$.
-    $\frac{\dd A}{\dd N_P} = 0$ follows from the fact that $A$ does not depend on $N_P$ in \cref{eq:aggregate_eq}.
+\begin{proof}[Proof of \Cref{prop:platform_profits_comparative_benchmark}]
+    Simply differentiate \Cref{eq:platform_profits_hybrid_benchmark} with respect to $N_P$.
+\end{proof}
+
+\begin{proof}[Proof of \Cref{prop:equilibrium_benchmark}]
+    The first statement follows from differentiating \Cref{eq:N_F_eq} with respect to $N_P$.
+    $\frac{\dd A}{\dd N_P} = 0$ follows from the fact that $A$ does not depend on $N_P$ in \Cref{eq:aggregate_eq}.
     Finally, $\frac{\dd A}{\dd N_P} = 0$ follows from the fact that consumer surplus only depends on $A$.
@@
 
-\begin{proof}[Proof of \cref{prop:optimal_n_p_benchmark}]
-    From \cref{prop:optimal_entry_fee,prop:equilibrium_benchmark} we have that
+\begin{proof}[Proof of \Cref{prop:optimal_n_p_benchmark}]
+    From \Cref{prop:optimal_entry_fee,prop:equilibrium_benchmark} we have that
     \begin{itemize}
@@
 }, there have been a number of papers proposing microfoundations for the Shapley value in terms of non-cooperative, bargaining-related games \parencite[e.g.][]{gul1989bargaining,winter1994demand,hart1996bargaining,stole1996intra}.
-The cooperative platform game described in \cref{sec:cooperative_game} satisfies the assumption for a number of these models, and thus any of those could be used to build microfoundations for the platform game.
+The cooperative platform game described in \Cref{sec:cooperative_game} satisfies the assumption for a number of these models, and thus any of those could be used to build microfoundations for the platform game.
 Among those, I will focus on \textcite{stole1996intra} for the reason that it specifically pertains to a setting with one indispensable player and many small players, just like the current paper.
@@
 However, as I argue later on, it is equivalent to bargaining over entry fees.
-While this section focuses on the main model, with two-sided bargaining, and the Shapley value as the solution, the same logic can be applied to the extensions presented in \cref{sec:extensions}, based on sections 3.1 and 3.2 of \textcite{stole1996intra}.
+While this section focuses on the main model, with two-sided bargaining, and the Shapley value as the solution, the same logic can be applied to the extensions presented in \Cref{sec:extensions}, based on sections 3.1 and 3.2 of \textcite{stole1996intra}.
 Finally, the model is defined for a finite number of small players.
@@
 
-The final piece that is needed to establish the interpretation in terms of entry fees is that for any given configuration of firms emerging from the bargaining process, and, crucially, regardless of the agreed upon entry fees, the unique equilibrium of the subsequent game is the one described in \cref{sec:results_demand}.
+The final piece that is needed to establish the interpretation in terms of entry fees is that for any given configuration of firms emerging from the bargaining process, and, crucially, regardless of the agreed upon entry fees, the unique equilibrium of the subsequent game is the one described in \Cref{sec:results_demand}.
 According to the previous theorem, players want to agree on a contract such that their final, total profits $\pi^t_{F_i}$ are equal to their Shapley value ($\varphi_{F_i}$).
 Given any equilibrium sales profits ($\pi^v_{F_i}$), they can achieve it by setting the entry fees to $K_{F_i} = \varphi_{F_i} - \pi^v_{F_i}$.
-Finally, \cref{sec:cooperative_game} and \cref{sec:results_demand} establish that both the Shapley value and the equilibrium sales profits are identical for each fringe firms, and thus a single, common entry fee $K_F$ will be agreed upon.
+Finally, \Cref{sec:cooperative_game} and \Cref{sec:results_demand} establish that both the Shapley value and the equilibrium sales profits are identical for each fringe firms, and thus a single, common entry fee $K_F$ will be agreed upon.
 
@@
 
-Now let us examine how the profit sharing rule from \cref{ass:profit_sharing} can be derived from various cooperative games.
+Now let us examine how the profit sharing rule from \Cref{ass:profit_sharing} can be derived from various cooperative games.
 In each of the following subsections, I formally define a cooperative game that models the platform setting, and derive the (weighted) Shapley values of the various players.
-I show that they correspond to the formulas given in \cref{ass:profit_sharing}, with a specific choice of weight functions $w_P$ and $w_F$ for each case.
+I show that they correspond to the formulas given in \Cref{ass:profit_sharing}, with a specific choice of weight functions $w_P$ and $w_F$ for each case.
 
@@
 \end{proposition}
-\begin{proof}[Proof of \cref{prop:profit_sharing_one_sided}]
+\begin{proof}[Proof of \Cref{prop:profit_sharing_one_sided}]
     This result is a direct application of Proposition 3 and Corollary 2 in \textcite{stancsics2023value}.
@@
 
-As an immediate consequence, if bargaining outcomes are described by the Shapley value, then the resulting allocations satisfy \cref{ass:profit_sharing} with $w_P(s) \equiv 1$ and $w_F(s) = s$.
+As an immediate consequence, if bargaining outcomes are described by the Shapley value, then the resulting allocations satisfy \Cref{ass:profit_sharing} with $w_P(s) \equiv 1$ and $w_F(s) = s$.
 
@@
 As before, let us start by formally describing the cooperative game.
-The set of players and the characteristic function are the same as in \cref{sec:cooperative_game_one_sided}, but now the game is additionally endowed with a weight system $\mathbf{\lambda} = \{\lambda_P, \lambda_{F}(i)\}$.
+The set of players and the characteristic function are the same as in \Cref{sec:cooperative_game_one_sided}, but now the game is additionally endowed with a weight system $\mathbf{\lambda} = \{\lambda_P, \lambda_{F}(i)\}$.
 Let us assume that all fringe players have the same weight $\lambda_{F}(i) \equiv 1$.
-This describes the situation in \cref{sec:higher_bargaining_power}.
+This describes the situation in \Cref{sec:higher_bargaining_power}.
 
@@
 \end{proposition}
-\begin{proof}[Proof of \cref{prop:profit_sharing_weighted}]
+\begin{proof}[Proof of \Cref{prop:profit_sharing_weighted}]
     This result is a direct application of Proposition 4 in \textcite{stancsics2023value}.
@@
 
-As before, the resulting allocations satisfy \cref{ass:profit_sharing} with $w_P(s) \equiv \lambda_P s ^ {\lambda_P - 1}$ and $w_F(s) = s ^ {\lambda_P}$.
+As before, the resulting allocations satisfy \Cref{ass:profit_sharing} with $w_P(s) \equiv \lambda_P s ^ {\lambda_P - 1}$ and $w_F(s) = s ^ {\lambda_P}$.
 
@@
 Finally, in certain settings, it might be appropriate to assume that the consumers (or, more generally, the entities on the other side of the market) also engage in the bargaining process.
-An example for this is \cref{sec:two_sided}
+An example for this is \Cref{sec:two_sided}
 In such a case, cooperative game describing can be formalized as follows.
@@
 \end{proposition}
-\begin{proof}[proof of \cref{prop:profit_sharing_two_sided}]
+\begin{proof}[proof of \Cref{prop:profit_sharing_two_sided}]
     This result is a direct application of Proposition 11 in \textcite{stancsics2023value}.
@@
 This foreshadows the idea that -- even though it might not be welfare-maximizing -- what's good for the platform might also good for the consumers in the two-sided case.
-Finally, as in both examples before, these values satisfy \cref{ass:profit_sharing} with $w_P(s) = s$ and $w_F(s) = s^2$.
+Finally, as in both examples before, these values satisfy \Cref{ass:profit_sharing} with $w_P(s) = s$ and $w_F(s) = s^2$.
 

### 2024-06-24 src/paper/theory.tex
Yet another try at CI publishing
Change references to uppercase

@@
 \usepackage{setspace}
+\usepackage{snapshot}
+\usepackage{apptools}
 \usepackage[backend=biber,style=authoryear,maxbibnames=99,hyperref=true]{biblatex}
@@
 \newtheorem{assumption}{Assumption}
+
+\AtAppendix{\counterwithin{proposition}{section}}
+\AtAppendix{\counterwithin{theorem}{section}}
+\AtAppendix{\counterwithin{corollary}{section}}
+\AtAppendix{\counterwithin{lemma}{section}}
+\AtAppendix{\counterwithin{assumption}{section}}
+\AtAppendix{\counterwithin{equation}{section}}
+\AtAppendix{\counterwithin{figure}{section}}
 
@@
 The paper is organized as follows.
-In \cref{sec:one_sided}, I present the main results for the case of one indispensable player and a continuum of identical fringe players.
+In \Cref{sec:one_sided}, I present the main results for the case of one indispensable player and a continuum of identical fringe players.
 \Cref{sec:many_sided} extends these results to the case of multiple types of fringe players.
@@
 \Cref{sec:application} provides an example application of the results to a simple model of a two-sided market.
-Finally, \cref{sec:conclusions} concludes the paper.
+Finally, \Cref{sec:conclusions} concludes the paper.
 
@@
 }.
-This result could also be used to prove \cref{prop:one_sided} instead of the direct proof provided in \cref{sec:proofs}.
+This result could also be used to prove \Cref{prop:one_sided} instead of the direct proof provided in \Cref{sec:proofs}.
 
@@
 
-Because the Shapley value is a special case of the random order value, these results are quite straightforward consequences of \cref{prop:one_sided_general} and \cref{cor:fringe_value_general}.
+Because the Shapley value is a special case of the random order value, these results are quite straightforward consequences of \Cref{prop:one_sided_general} and \Cref{cor:fringe_value_general}.
 One only has to notice that each permutation having an equal probability implies that the number of firms coming before $P$ is uniformly distributed on $1, \dots, n$, and thus the share of firms before $P$ converges in distribution to the uniform distribution on $[0, 1]$.
-Alternatively, a more direct proof is provided in \cref{sec:proofs}, or a probabilistic justification can be found in \textcite{levy1997individual}.
-
-The resulting Shapley values also have a nice geometric interpretation shown on \cref{fig:one_sided}.
+Alternatively, a more direct proof is provided in \Cref{sec:proofs}, or a probabilistic justification can be found in \textcite{levy1997individual}.
+
+The resulting Shapley values also have a nice geometric interpretation shown on \Cref{fig:one_sided}.
 Consider a rectangle with sides of length 1 and $f(1)$, respectively.
@@
 In words, regardless of the value of $\bar{n}$, the two types of players share the total value in the same proportion.
-This proportion depends on the parameter $\alpha$ (\cref{fig:power_function_example}), which can be interpreted as the degree of substitutability between the fringe players.
+This proportion depends on the parameter $\alpha$ (\Cref{fig:power_function_example}), which can be interpreted as the degree of substitutability between the fringe players.
 More specifically, the higher $\alpha$ is, the more complementary the fringe players are to each other, and the larger the share they obtain.
@@
 For my main result, I make use of an alternative, computational characterization of the weighted values. 
-\textcite{kalai1987weighted} demonstratesd that weighted values can be calculated by weighting the permutations by the probabilities arising from the following sequential ordering procedure.
+\textcite{kalai1987weighted} demonstrated that weighted values can be calculated by weighting the permutations by the probabilities arising from the following sequential ordering procedure.
 Start with the set of all players.
@@
 Now we have everything we need to derive the weighted value of both types of players.
-Having \cref{eq:entry_distr_discrete} and \cref{lem:entry_distr} allows us to invoke \cref{prop:one_sided_general} to obtain the following proposition.\footnote{
+Having \Cref{eq:entry_distr_discrete} and \Cref{lem:entry_distr} allows us to invoke \Cref{prop:one_sided_general} to obtain the following proposition.\footnote{
     \textcite{stole1996intra} also derive essentially the same expression for the equilibrium outcome of their bargaining game with unequal profit distribution, and assert that it is equal to the weighted value.
@@
 Depending on the shape of this distribution, regions corresponding to different masses of fringe firms can be over or underweighted in this integral, leading to different values.
-Contrary to \cref{prop:one_sided_general}, the probability distribution has a specific functional form, and is characterized by a single parameter, $\lambda$.
+Contrary to \Cref{prop:one_sided_general}, the probability distribution has a specific functional form, and is characterized by a single parameter, $\lambda$.
 \Cref{fig:weigh_function} illustrates the weighting function for various values of $\lambda$.
@@
 First, let us examine the most general case: the random order value.
-Let us start by establishing the analog of \cref{prop:one_sided_general} for the many-sided case to obtain the limit of the value of the big player.
+Let us start by establishing the analog of \Cref{prop:one_sided_general} for the many-sided case to obtain the limit of the value of the big player.
 \begin{proposition}
@@
 \end{proposition}
-The proposition above is almost identical to \cref{prop:one_sided_general}, with the only difference being that the integral is now over the $L$-dimensional unit hypercube, due to $f$ being a function of $L$ variables.
+The proposition above is almost identical to \Cref{prop:one_sided_general}, with the only difference being that the integral is now over the $L$-dimensional unit hypercube, due to $f$ being a function of $L$ variables.
 
@@
 } 
-Therefore, the integral is not taken with respect to the uniform distribution, but rather one resembling that of \cref{prop:one_sided_weighted}.
+Therefore, the integral is not taken with respect to the uniform distribution, but rather one resembling that of \Cref{prop:one_sided_weighted}.
 The result is the following: when the big player has a higher weight, its chances of being relatively late in the ordering are higher, and thus -- due to $f$ being monotone increasing -- its value is higher.
@@
 \end{corollary}
-This result is analogous to \cref{cor:platform_value_weighted}, and demonstrates that a higher weight for player $P$ corresponds to a higher value in this game as well.
+This result is analogous to \Cref{cor:platform_value_weighted}, and demonstrates that a higher weight for player $P$ corresponds to a higher value in this game as well.
 
@@
     Such assumptions are usually justified by some idiosyncratic cost of entry, the distribution of which determines the function $\phi$.
-    For simplicity, I refrain from explicitly modeling this cost in the main text, but \cref{sec:explicit_entry_costs} provides a discussion of how one can incorporate it into the model, its impact on bargaining outcomes.
+    For simplicity, I refrain from explicitly modeling this cost in the main text, but \Cref{sec:explicit_entry_costs} provides a discussion of how one can incorporate it into the model, its impact on bargaining outcomes.
 }
@@
 
-The characteristic function of the game takes a similar form to that in \cref{sec:many_sided}.
+The characteristic function of the game takes a similar form to that in \Cref{sec:many_sided}.
 If the platform is not a member of a coalition, then the value that coalition can generate is zero.
@@
 
-The share received by each type of player is then easily established using \cref{prop:many_sided_weighted}.
+The share received by each type of player is then easily established using \Cref{prop:many_sided_weighted}.
 \begin{proposition}
@@
     This is due to the characteristic function being a polynomial of the number of entrants.
-    Just like in \cref{sec:power_function_example}, each constituent of the polynomial are divided in a constant proportion.
+    Just like in \Cref{sec:power_function_example}, each constituent of the polynomial are divided in a constant proportion.
 }
@@
 Due to the former retaining many of the attractive properties of its more specialized counterparts, it might be a good candidate for modeling bargaining outcomes flexibly and in a tractable manner.
-Furthermore, as shown in \cref{sec:extensions}, the results can also be generalized to cases with not completely indispensable big players, while retaining the essential structure of the results.
+Furthermore, as shown in \Cref{sec:extensions}, the results can also be generalized to cases with not completely indispensable big players, while retaining the essential structure of the results.
 
@@
 Notably, as in the case of the weighted value, the share of player $P$ can again be expressed as an integral of $f$ and some weighting\footnote{
-    Weighting is not a completely precise term, as $h(t)$ does not integrate to one, and is therefore not a probability distribution in this case (\cref{fig:multiple_platforms}).
+    Weighting is not a completely precise term, as $h(t)$ does not integrate to one, and is therefore not a probability distribution in this case (\Cref{fig:multiple_platforms}).
 } function $h(t)$, with the latter depending only on the number of big players.
@@
 where $g(t) = m (1-t) ^ {m-1}$.
-Notice that $g(t)$ now integrates to one, and is thus a probability distribution (\cref{fig:multiple_platforms_total}).
+Notice that $g(t)$ now integrates to one, and is thus a probability distribution (\Cref{fig:multiple_platforms_total}).
 Therefore, the Shapley value in the case of multiple, substitutable big players can be interpreted as a random order value with a single big player.
@@
 Now let us look at how the value of the big players and the fringe changes as a function of the number of the big players.
-Proposition \cref{cor:multiple_platforms_2} again confirms our intuition: more players means that they become more substitutable, and thus their bargaining power decreases.
+Proposition \Cref{cor:multiple_platforms_2} again confirms our intuition: more players means that they become more substitutable, and thus their bargaining power decreases.
 This not only means that the value of each individual big player decreases, but also that their total value goes down.
@@
 
-It is clear that the value of the big player is decreasing in $f_0$ (\cref{fig:non_indispensable}).
+It is clear that the value of the big player is decreasing in $f_0$ (\Cref{fig:non_indispensable}).
 Consequently, the value of the fringe is increasing in $f_0$, which is essentially its outside option (what it can achieve without the big player).
@@
 \end{align*}
-One can obtain the weighted values of all sides using \cref{prop:many_sided_weighted}.
+One can obtain the weighted values of all sides using \Cref{prop:many_sided_weighted}.
 \begin{proposition}
@@
 \end{lemma}
-\begin{proof}[Proof of \cref{lemma:log_convergence}]
+\begin{proof}[Proof of \Cref{lemma:log_convergence}]
     First, note that $\Delta_n$ and $\Delta$ are all continuous functions.
@@
 \end{lemma}
-\begin{proof}[Proof of \cref{lemma:integral_convergence}]
+\begin{proof}[Proof of \Cref{lemma:integral_convergence}]
     \begin{align*}
@@
 
-\begin{proof}[Proof of \cref{lem:convergence_to_manifold}]
+\begin{proof}[Proof of \Cref{lem:convergence_to_manifold}]
     We have to show that
@@
 
-\begin{proof}[Proof of \cref{prop:monotone}]
+\begin{proof}[Proof of \Cref{prop:monotone}]
     Monotonicity is evident.
@@
 
-\begin{proof}[Proof of \cref{prop:one_sided_general}]
+\begin{proof}[Proof of \Cref{prop:one_sided_general}]
     First, observe that $f$ is continuous on the compact set $[0, 1]$, and is therefore also bounded.
@@
 
-\begin{proof}[Proof of \cref{prop:one_sided}]
+\begin{proof}[Proof of \Cref{prop:one_sided}]
     Let $R$ denote a permutation of the set of players ($N$).
@@
 
-\begin{proof}[Proof of \cref{lem:entry_distr}] %\textcolor{red}{(Might have to fix sum indices)} \\
+\begin{proof}[Proof of \Cref{lem:entry_distr}] %\textcolor{red}{(Might have to fix sum indices)} \\
     The probability of $P$ having at most fraction $t$ of the other players before itself is
@@
 
-\begin{proof}[Proof of \cref{prop:one_sided_weighted}]
+\begin{proof}[Proof of \Cref{prop:one_sided_weighted}]
     The weighted value of player $P$ is its expected contribution across all permutations, with each permutation weighted by its probability of occurring.
@@
 
-\begin{proof}[Proof of \cref{prop:multiple_platforms}]
+\begin{proof}[Proof of \Cref{prop:multiple_platforms}]
     \label{prop:one_sided_multiple}
@@
 
-\begin{proof}[Proof of \cref{prop:many_sided_general}]
-    The proof mirrors that of \cref{prop:one_sided_general}.
+\begin{proof}[Proof of \Cref{prop:many_sided_general}]
+    The proof mirrors that of \Cref{prop:one_sided_general}.
     First, note that the random order value can be expressed as follows:
@@
 
-\begin{proof}[Proof of \cref{lem:many_sided_manifold}]
-    Just like in the proof of \cref{prop:many_sided_general}, the random order value can be expressed as follows:
+\begin{proof}[Proof of \Cref{lem:many_sided_manifold}]
+    Just like in the proof of \Cref{prop:many_sided_general}, the random order value can be expressed as follows:
     \begin{align*}
@@
 
-\begin{proof}[Proof of \cref{prop:many_sided_shapley}]
+\begin{proof}[Proof of \Cref{prop:many_sided_shapley}]
     Let us show than $X_n$ converges in distribution to the degenerate random variable $X = (U, \dots, U)$, where $U$ is uniformly distributed on $[0, 1]$.
@@
 
-    Now we can use \cref{lem:convergence_to_manifold} to conclude that $X_n \xrightarrow[]{d} (U, \dots, U)$.
-    Finally, by \cref{lem:many_sided_manifold}, the Shapley-value is
+    Now we can use \Cref{lem:convergence_to_manifold} to conclude that $X_n \xrightarrow[]{d} (U, \dots, U)$.
+    Finally, by \Cref{lem:many_sided_manifold}, the Shapley-value is
     \begin{align*}
@@
 
-\begin{proof}[Proof of \cref{prop:many_sided_weighted}]
-    The proof uses the same approach as that of \cref{prop:many_sided_shapley}.
-    I will show that $X_n \xrightarrow[]{d} h(S)$, where $h(s) = (s^{\lambda_1}, \dots, s^{\lambda_L})$, and $S$ is a random variable with cdf $G(s) = s^{\lambda_P}$, and then rely on \cref{lem:many_sided_manifold}.
+\begin{proof}[Proof of \Cref{prop:many_sided_weighted}]
+    The proof uses the same approach as that of \Cref{prop:many_sided_shapley}.
+    I will show that $X_n \xrightarrow[]{d} h(S)$, where $h(s) = (s^{\lambda_1}, \dots, s^{\lambda_L})$, and $S$ is a random variable with cdf $G(s) = s^{\lambda_P}$, and then rely on \Cref{lem:many_sided_manifold}.
 
@@
     First, as shown by \textcite{kalai1987weighted}, the probability of a permutation can be described by successively selecting the players with probabilities proportional to the weights of the players that have not been selected yet, and then reversing this ordering.\footnote{
-        For more details, see \cref{sec:weighted_one_sided}.
+        For more details, see \Cref{sec:weighted_one_sided}.
     }
@@
     \end{align*}
-    Then we can rely on \cref{lem:convergence_to_manifold} to conclude that $X_n \xrightarrow[]{d} (V_P^{\lambda_1}, \dots, V_P^{\lambda_L})$.
-
-    Finally, by \cref{lem:many_sided_manifold}, the weighted value of player $P$ is
+    Then we can rely on \Cref{lem:convergence_to_manifold} to conclude that $X_n \xrightarrow[]{d} (V_P^{\lambda_1}, \dots, V_P^{\lambda_L})$.
+
+    Finally, by \Cref{lem:many_sided_manifold}, the weighted value of player $P$ is
     \begin{align*}
@@
 
-\begin{proof}[Proof of \cref{prop:welfare_max_entry_fees}]
+\begin{proof}[Proof of \Cref{prop:welfare_max_entry_fees}]
     The (marginal) cost of serving an entrant on side $i$ is $F_i$.
@@
 
-\begin{proof}[Proof of \cref{prop:unilateral_entry_fees}]
+\begin{proof}[Proof of \Cref{prop:unilateral_entry_fees}]
     By assumption, $\pi_P(u_1, u_2)$ is concave in $u_1$ and $u_2$, therefore the first-order conditions are necessary and sufficient for a maximum.
@@
 
-\begin{proof}[Proof of \cref{prop:bargaining_entry_fees}]
-    From \cref{prop:many_sided_weighted}, the value of player $P$ is
+\begin{proof}[Proof of \Cref{prop:bargaining_entry_fees}]
+    From \Cref{prop:many_sided_weighted}, the value of player $P$ is
     \begin{align*}
@@
 
-\begin{proof}[Proof of \cref{prop:all_entry_fees}]
-    See the proof of \cref{prop:welfare_max_entry_fees,prop:unilateral_entry_fees,prop:bargaining_entry_fees}.
+\begin{proof}[Proof of \Cref{prop:all_entry_fees}]
+    See the proof of \Cref{prop:welfare_max_entry_fees,prop:unilateral_entry_fees,prop:bargaining_entry_fees}.
 \end{proof}

### 2024-07-21 src/paper/application.tex
Mention that proofs are through more general results in the appendix

@@
 The propositions in this section are generally proven for a more general framework, and those presented here are special cases of those.
+The reason for presenting the more special case in the main text is twofold.
+First, it the more concrete model is better for expositional purposes, and is a good fit for the setting.
+Second, the link between consumer surplus and the number of products is straightforward under the logit assumption, making it possible to state welfare results, as well.
+
 For this reason, the proofs are also presented together with the more general model in \Cref{sec:more_general}.
+Most of the results only rely on \Cref{ass:additive_profit,ass:free_entry,ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:single_crossing}, and do not require the specific, logit-like demand function described previously.
+Therefore, I proceed to prove those results in two steps.
+First, I demonstrate that the model satisfied the aforementioned assumptions.
+Second, in \Cref{sec:more_general}, I prove the corresponding results for the more general case.
 

### 2024-07-21 src/paper/application.tex
Refer to partial equilibrium results in main text

@@
 From \Cref{eq:optimal_profit}, the total profit achieved by the platform and $N_F$ fringe firms is given by
-\begin{align*}
-    \Pi(N_P, N_F) = \mu \frac{n V_F + N_P V_P}{n V_F + N_P V_P + 1}.
-\end{align*}
+\begin{align}
+    \Pi(N_P, N_F) = \mu \frac{N_F V_F + N_P V_P}{N_F V_F + N_P V_P + 1}.  \label{eq:total_profits}
+\end{align}
 Bargaining outcomes are determined according to Shapley values, given by \Cref{prop:shapley_value}.
@@
 
-Now let us turn to how the platform's dual mode operation affects product variety and consumer welfare.
-I start by showing that the equilibrium is unique in this case, as well.
-This, and a few other results in this section\footnote{
-    These results do not actually rely on the specific logit demand system.
-    As long as the fringe profit function has the property described in \Cref{lem:shape_of_fringe_profit}, and the total profit function satisfies some assumptions, the results hold.
-    \Cref{sec:more_general_results} provides more detail on the necessary assumptions.
-}, rely on the following lemma.
+Let us establish a couple of partial equilibrium results about the profir shares before moving on to the main results.
+Consider the number of fringe firms $N_F$ fixed.
+Then, total profits, as given by \Cref{eq:total_profits}, are clearly increasing in the number of platform products.
+The next proposition shows that the platform's profits are also increasing in $N_P$, while the fringe's profits are decreasing.
+\begin{proposition}
+    \label{prop:profits_partial_bargaining}
+    For any $N_F > 0$, the platform's profits are increasing in the number of its products, while the fringe's profits are decreasing:
+    \begin{align*}
+        \frac{\partial \pi_P^t}{\partial N_P} &> 0, \quad \frac{\partial \pi_F^t}{\partial N_P} < 0.
+    \end{align*}
+\end{proposition}
+This is actually a rather striking results.
+Even though the total size of the pie increases, the slice that the fringe can obtain decreases.
+This is due to the substitutability of the fringe and the platform's own products\footnote{
+    \Cref{prop:share_of_fringe} demonstrates that the direction of the change depends on the cross derivative of the total profit function.
+}: as the latter increases its product variety, the marginal benefit of adding each fringe firm decreases, leading to a detoriation in the fringe's bargaining position.
+
+Let us now endogeneize $N_F$, and turn to the main results of this section: how the platform's dual mode operation affects product variety and consumer welfare.
+I start by showing that, like in the benchmark model, the equilibrium is unique in this case, as well.
+This, and many other results in this section, rely on the following lemma.
 \begin{lemma}
@@
 
+\Cref{prop:profits_partial_bargaining} is a direct corollary of the two previous results.
+\begin{proof}[Proof of \Cref{prop:profits_partial_bargaining}]
+    The model presented in the main text adheres to \Cref{ass:identical_fringe,ass:monotone_profits,ass:profit_sharing}. Thus, by \Cref{prop:share_of_platform},
+    \begin{align*}
+        \frac{\partial \pi_P(N_P, N_F)}{\partial N_P} > 0.
+    \end{align*}
+    Furthermore,
+    \begin{align*}
+        \frac{\partial^2 f(N_P, N_F)}{\partial N_P \partial N_F} = \frac{\partial^2}{\partial N_P \partial N_F} \mu \frac{N_F V_F + N_P V_P}{N_F V_F + N_P V_P + 1} < 0,
+    \end{align*}
+    therefore, by \Cref{prop:share_of_platform},
+    \begin{align*}
+        \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} < 0.
+    \end{align*}    
+\end{proof}
+
 \paragraph{Number of entrants -- general equilibrium}

### 2024-08-09 src/paper/theory.tex
Reorganize paper
Generalize multiple big players case

@@
 \newcommand{\dG}{\mathrm{d}G}
+\newcommand{\dH}{\mathrm{d}H}
 \newcommand{\E}{\mathbb{E}}
@@
 
-\section{One-sided case}
+\section{Identical fringe players}
 \label{sec:one_sided}
@@
 Furthermore, let us denote the random variable $\frac{|\mathcal{P}_P|}{n}$ as $X_n$.
-Assume that $X_n \xrightarrow[]{d} X$ with cdf $G_X(t)$ and (if exists) pdf $g(t)$.
+Assume that $X_n \xrightarrow[]{d} X$ with cdf $G(t)$ and (if exists) pdf $g(t)$.
     Then
@@
 
-\subsection{Shapley value}
+\subsection{Special cases}
+\subsubsection{Shapley value}
 
@@
 
-\subsection{Weighted values}
+\subsubsection{Weighted values}
 \label{sec:weighted_one_sided}
@@
 
-\section{Many-sided case}
+\subsection{Non-indispensable big player(s)}
+\label{sec:extensions}
+
+This section relaxes the assumption that the big player is indispensable.
+I demonstrate two ways in which the model can be extended to include non-indispensable big players, while retaining the essential structure and the tractability of the results.
+In the first case, there are a finite number of big players, which are perfect substitutes of each other.
+In the second case, there is a single big player, but the fringe is able to generate some value on its own.
+In both cases, the value function is still a random order value, and thus results from the main text can be applied. % TODO: elaborate on this
+
+\subsubsection{Shapley value with multiple big players}
+
+Imagine that, instead of just one, there are $m$ players of type $P$, and they are perfect substitutes of each other.
+That is, any coalition still needs at least one of them to create any value, but it does not matter which and how many of them are present.\footnote{
+    The relaxtion of this assumption, while conceptually straightforward, is not as simple to analyze.
+    Instead of having to deal with the minimum of $m$ independent random variables, one needs to consider all order statistics.
+}
+Formally, the value function for coalition $S$ becomes the following:
+\begin{align*}
+    v(S) = \begin{cases}
+        0                              & \text{if } n_P(S) = 0 \\
+        f\left(\frac{n_A(S)}{n}\right) & \text{otherwise}.
+    \end{cases}
+\end{align*}
+
+Let us start by establishing monotonicity for this version of the model, too.
+\begin{proposition}
+    The game is monotone if $f$ is increasing and $f(0) \geq 0$.
+\end{proposition}
+On the other hand, superadditivity is not as simple in this case, as before.
+For example, when $f$ is concave, then $m$ coalitions with one platform each and the fringe divided equally amongst them clearly achieve a higher total payoff than the grand coalition.
+Therefore, the results of this section are most applicable to settings when multiple coalitions cannot be formed at the same time for some reason.
+For example, \textcite{hart1996bargaining} propose an interpretation when there is a single, indivisible, non-replicable resource or technology (not captured in the value function) necessary to produce any value.
+
+For simplicity, let us restrict our attention to probability distributions over the permutations that are symmetric with respect to the big players.
+That is, the probability of having $k_F$ fringe players and $k_P$ big players before player $P_j$ is the same for all $i$.\footnote{
+    This assumption can easily be relaxed, but it would complicate the results without adding much insight.
+}
+As before, I assume that, as the number of fringe players goes to infinity, the distribution of the number of fringe players before player $P_j$ to a continuous distribution.
+
+Let us first establish the sum of the shares of all big players.
+Then, the value of individual big players can be obtained by relying on the symmetry assumption.
+The following proposition provides an expression for the limit of this total value.
+\begin{proposition}
+    \label{prop:multiple_platforms_total}
+    Let $f$ be continuous on [0, 1].
+    Let us denote the number of fringe players in any coalition $S$ as $n_F(S)$.
+    Furthermore, let us denote the random variable $\frac{n_F(\mathcal{P}_{P_j})}{n}$ as $X_n$.
+    Assume that $X_n \xrightarrow[]{d} X$ with cdf $G(t)$ and (if exists) pdf $g(t)$.
+
+    Let $H(t) = 1 - [1 - G(t)]^m$, i.e. the cdf of the minimum of the $m$ independent random variables distributed according to $G$.
+    Then
+    \begin{align*}
+        \varphi_P^\infty = \lim_{n \to \infty} \sum_{j=1}^m \varphi_{P_j}^n = \int_0^1 f(t) \dH(t) = \int_0^1 h(t) f(t) \dt,
+    \end{align*}
+    with the last equality holding if $X$ is a continuous random variable.
+\end{proposition}
+% TODO: needs proof
+
+Notably, value in the case of multiple, substitutable big players can be interpreted as a random order value with a single big player.
+The probability distribution for the corresponding random order value has a specific form, and depends on the number of big players.
+Consequently, all the results from the previous section apply to this case as well.
+
+As with proposition \ref{prop:one_sided}, this result also has a probabilistic interpretation.
+Let the location of the $m$ atoms be $t_1, \dots, t_m$, distributed independently and uniformly on the unit interval.
+The expected marginal contribution of $t_i$ is only positive whenever it is the first amongst the major players.
+Therefore, the total value of the big players is the random order value with corresponding probability distribution being the minimum of $m$ independent random variables describing the number of fringe players before each big player.
+
+Due to the symmetry of the big players in terms of the permutation probabilities, the value of each individual big player is the same.
+\begin{corollary}
+    \label{prop:multiple_platforms_individual}
+    The limit of the value (as $n \to \infty$) of each player of type $P$ is
+    \begin{align*}
+        \varphi_{P_i}^{\infty, m} = \frac{1}{m} \varphi_P^\infty = \int_0^1 \frac{h(t)}{m} f(t) \dt
+    \end{align*}
+    where $H(t) = 1 - [1 - G(t)]^m$, and $h(t) = H'(t)$ whenever $G$ is differentiable.
+\end{corollary}
+Furthermore, the value of the fringe has a similar, marginal contribution-based interpretation as in the case of a single big player.
+\begin{corollary}
+    \label{cor:multiple_platforms}
+    The per-unit Shapley-value of the fringe is
+    \begin{align*}
+        \varphi_A^{\infty, m} = 1 - \int_0^1 f(t) \dH(t) = \int_0^1 H(t) f'(t) \dt,
+    \end{align*}
+    where $H(t) = 1 - [1 - G(t)]^m$.
+\end{corollary}
+
+Finally, let us look at how the value of the big players and the fringe changes as a function of the number of the big players.
+Proposition \Cref{cor:multiple_platforms_2} again confirms our intuition: more players means that they become more substitutable, and thus their bargaining power decreases.
+This not only means that the value of each individual big player decreases, but also that their total value goes down.
+\begin{corollary}
+    \label{cor:multiple_platforms_2}
+    Let $\varphi_{P}^{\infty, m}$ denote the aggregated values of players of type $P$.
+$\varphi_{P}^{\infty, m}$ is decreasing in $m$ and $\varphi_{A}^{\infty, m}$ is increasing in $m$ unless $f$ is constant.
+\end{corollary}
+% TODO: adjust proof
+
+\paragraph{Example: Shapley value.}
+
+I illustrate the effect of the number of big players on the weight function $h(t)$ by looking at the simplest random order value, the Shapley value.
+As shown in \Cref{prop:one_sided}, the limit of the Shapley value in the case of a single big player is just $\int_0^1 f(t) \dt$.
+Therefore, using the notation from \Cref{prop:one_sided_general}, $G(t) = t$.
+Conseqently, by \Cref{prop:multiple_platforms_total}, the sum of the shares of the big players corresponds to the random order value characterized by the cumulative distribution function
+\begin{align} 
+    H(t) = 1 - (1 - t)^m.  \label{eq:weight_function_shapley}
+\end{align}
+That is, the value of the sum of the big players' values is given by
+\begin{align*}
+    \varphi_P^{\infty, m} = \underbracket{m (1-t) ^ {m-1}}_{h(t)} f(t) \dt,
+\end{align*}
+while the value that each individual big player obtains is
+\begin{align*}
+    \varphi_{P_j}^{\infty, m} = \underbracket{(1-t) ^ {m-1}}_{h_j(t)} f(t) \dt.
+\end{align*}
+
+\Cref{fig:multiple_platforms,fig:multiple_platforms_total} illustrate how $h_t$ and $h_j(t)$ depend on the number of big firms, $m$.
+In particular, it is apparent that a $H(t)$ with lower $m$ first order stochastically dominates one with a higher number of big firms.
+This is the underlying reason of the big players' share decreasing in their number, i.e. \Cref{cor:multiple_platforms_2}.
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.1, samples at={0, 0.02, 0.04, ..., 0.98, 1},
+                xtick={0, 1}, ytick={0, 1}, axis lines=left, xlabel={$t$}, legend pos=north west]
+                \addplot[thick] {1};
+                \addplot[thick, dashed] {1-x};
+                \addplot[thick, dotted] {(1-x)^2};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{$h_i(t)$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.1, samples at={0, 0.02, ..., 0.98, 1},
+                xtick={0, 1}, ytick={0, 1}, axis lines=left, xlabel={$t$}, legend pos=north west]
+                \addplot[thick] {x};
+                \addplot[thick, dashed] {x - x^2/2};
+                \addplot[thick, dotted] {x - x^2 + x^3/3};
+                \legend{$m = 1$, $m = 2$, $m = 3$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{$\int_0^t h_i(s) \ds$}
+    \end{subfigure}
+    \caption{Illustration of the weighting function for various values of $m$ in the multiple big player case -- individual big players.}
+    \label{fig:multiple_platforms}
+\end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=3.1, samples at={0, 0.02, 0.04, ..., 0.98, 1},
+                xtick={0, 1}, ytick={0, 1, 2, 3}, axis lines=left, xlabel={$t$}, legend pos=north west]
+                \addplot[thick] {1};
+                \addplot[thick, dashed] {2 * (1-x)};
+                \addplot[thick, dotted] {3 * ((1-x)^2)};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{$h(t)$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.1, samples at={0, 0.02, ..., 0.98, 1},
+                xtick={0, 1}, ytick={0, 1}, axis lines=left, xlabel={$t$}, legend pos=north west]
+                \addplot[thick] {x};
+                \addplot[thick, dashed] {2 * (x - x^2/2)};
+                \addplot[thick, dotted] {3 * (x - x^2 + x^3/3)};
+                \legend{$m = 1$, $m = 2$, $m = 3$}
+            \end{axis}
+        \end{tikzpicture}
+        \caption{$H(t) = \int_0^t h(s) \ds$}
+    \end{subfigure}
+    \caption{Illustration of the weighting function for various values of $m$ in the multiple big player case -- total of big players.}
+    \label{fig:multiple_platforms_total}
+\end{figure}
+
+Now let us look at how the value of the big players and the fringe changes as a function of the number of the big players.
+Proposition \Cref{cor:multiple_platforms_2} again confirms our intuition: more players means that they become more substitutable, and thus their bargaining power decreases.
+This not only means that the value of each individual big player decreases, but also that their total value goes down.
+
+\begin{corollary}
+    \label{cor:multiple_platforms_2}
+    Let $\varphi_{P}^{\infty, m} = m\varphi_{P_i}^{\infty, m}$ denote the aggregated values of players of type $P$.
+$\varphi_{P}^{\infty, m}$ is decreasing in $m$ and $\varphi_{A}^{\infty, m}$ is increasing in $m$ unless $f$ is constant.
+\end{corollary}
+
+Finally, let us show that the value of the fringe has a similar, marginal contribution-based interpretation as in the case of a single big player.
+
+\begin{corollary}
+    \label{cor:multiple_platforms}
+    The per-unit Shapley-value of the fringe is
+    \begin{align*}
+        \varphi_A^{\infty, m} = 1 - \int_0^1 f(t) \dG(t) = \int_0^1 G(t) f'(t) \dt ,
+    \end{align*}
+    where $G(t) = 1 - (1-t)^m$.
+\end{corollary}
+
+\subsubsection{Small players can generate some value on their own}
+
+Another way of relaxing the indispensability of the big player is assuming that the small players can generate some value on their own.
+Suppose that the big player still provides some value to any coalition, but a coalition of fringe players can achieve a positive value even without it.
+Formally, the value function is now the following:
+\begin{align*}
+    v(S) = \begin{cases}
+        f_0\left(\frac{n_A(S)}{n}\right) & P \notin S \\
+        f\left(\frac{n_A(S)}{n}\right)   & \text{otherwise}.
+    \end{cases}
+\end{align*}
+
+As in the case of multiple big players, monotonicity is straightforward to establish.
+\begin{proposition}
+    The game is monotone if $f$ is increasing and $f(t) \geq f_0(t) \geq 0 \forall t$.
+\end{proposition}
+Also similarly, conditions for superadditivity are not as simple.
+Therefore, the simultaneous formation of multiple coalitions must be excluded in this setting as well.
+
+On the other hand, the random order values and their limits are very straightforward to characterize.
+The value of the big player is still its average marginal contribution.
+The only difference is that this marginal contribution (conditional on $s$ share of the fringe coming before $P$) is not $f(s)$, but rather $f(s) - f_0(s)$.
+This is because the big player is not indispensable, as $s$ mass of fringe firms can achieve $f_0(s)$ even without it.
+
+\begin{proposition}
+    \label{prop:one_sided_non_indispensable}
+    Let $f$ be continuous on [0, 1].
+Furthermore, let us denote the random variable $\frac{|\mathcal{P}_P|}{n}$ as $X_n$.
+Assume that $X_n \xrightarrow[]{d} X$ with cdf $G_X(t)$ and (if exists) pdf $g(t)$.
+    Then
+    \begin{align*}
+        \varphi_P^\infty = \lim_{n \to \infty} \varphi_P^n = \int_0^1 f(t) \dG(t) = \int_0^1 g(t) [f(t) - f_0(t)] \dt,
+    \end{align*}
+    with the last equality holding if $X$ is a continuous random variable.
+\end{proposition}
+
+The value of the fringe is also similar to the baseline case, except now fringe players have a non-zero marginal contribution even when $P$ is not present.
+Therefore, there is an additional term in the integral, corresponding to the marginal value of the fringe when $P$ is not present.
+
+\begin{corollary}
+    \label{cor:fringe_value_non_indispensable}
+    The aggregated value of the fringe is
+    \begin{align*}
+        \varphi_A^\infty = f(1) - \int_0^1 f(t) - f_0(t) \dG(t).
+    \end{align*}
+    Furthermore, if $f$ and $f_0$ are differentiable on $[0, 1]$, then the value of the fringe can also be expressed as
+    \begin{align*}
+        \varphi_A^\infty = \int_0^1 G(t) f'(t) + (1 - G(t)) f'_0(t) \dt.
+    \end{align*}
+\end{corollary}
+
+It is clear that the value of the big player is decreasing in $f_0$ (\Cref{fig:non_indispensable}).
+Consequently, the value of the fringe is increasing in $f_0$, which is essentially its outside option (what it can achieve without the big player).
+This is a natural result, and again, it is in line with what one would expect from bargaining theory.
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
+                    xtick={0, 1}, ytick={0}, xlabel={$s$}]
+                \addplot[name path=f, thick] {x^0.5};
+                \addplot[name path=f0, thick] {0.3 * x^0.5};
+                \node[anchor=north west] at (axis cs: .8, .8^0.5) {$f$};
+                \node[anchor=south west] at (axis cs: .8, .3*.8^0.5) {$f_0$};
+                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);
+
+                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and f0];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=f0 and bottom];
+
+                \node[anchor=north west, align=left] at (axis cs: .05, .95) {$\varphi_A^\infty$};
+                \node[anchor=south east, align=left] at (axis cs: .95, .05) {$\varphi_A^\infty$};
+                \node[anchor=north west, align=right] at (axis cs: .5, .5) {$\varphi_P^\infty$};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Fringe can achieve relatively little without $P$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \begin{tikzpicture}[scale=0.8]
+            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
+                    xtick={0, 1}, ytick={0}, xlabel={$s$}]
+                \addplot[name path=f, thick] {x^0.5};
+                \addplot[name path=f0, thick] {0.7 * x^0.5};
+                \node[anchor=north west] at (axis cs: .8, .8^0.5) {$f$};
+                \node[anchor=north west] at (axis cs: .8, .7*.8^0.5) {$f_0$};
+                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
+                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);
+
+                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and f0];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
+                \addplot [fill=red, fill opacity=0.05] fill between [of=f0 and bottom];
+
+                \node[anchor=north west, align=left] at (axis cs: .05, .95) {$\varphi_A^\infty$};
+                \node[anchor=south east, align=left] at (axis cs: .95, .05) {$\varphi_A^\infty$};
+                \node[anchor=north west, align=right] at (axis cs: .5, .7) {$\varphi_P^\infty$};
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Fringe can achieve relatively more without $P$}
+    \end{subfigure}
+    \caption{Distribution of value between player $P$ (blue) and the fringe (red)}
+    \label{fig:non_indispensable}
+\end{figure}
+
+\section{Heterogeneous fringe}
 \label{sec:many_sided}
@@
 
-\subsection{Shapley-value}
+\subsection{Special cases}
+\subsubsection{Shapley-value}
 
@@
 
-\subsection{Weighted value}
+\subsubsection{Weighted value}
 
@@
 
-\section{Non-indispensable big player(s)}
-\label{sec:extensions}
-
-This section demonstrates two ways in which the model can be extended to include non-indispensable big players, while retaining the essential structure and the tractability of the results.
-In the first case, there are a number of big players, which are perfect substitutes of each other.
-In the second case, there is a single big player, the fringe is able to generate some value on its own, and the big player is only needed to generate the rest.
-In both cases, the value function is still a random order value, and thus results from the main text can be applied.
-
-\subsection{Shapley value with multiple big players}
-
-Now imagine that, instead of just one, there are $m$ players of type $P$, and they are perfect substitutes of each other.
-That is, the fringe players still need one at least of them to achieve any value, but it does not matter which and how many of them are present.
-Formally, the value function for coalition $S$ becomes the following:
-\begin{align*}
-    v(S) = \begin{cases}
-        0                              & \text{if } n_P(S) = 0 \\
-        f\left(\frac{n_A(S)}{n}\right) & \text{otherwise}.
-    \end{cases}
-\end{align*}
-
-Let us start by establishing monotonicity for this version of the model, too.
-\begin{proposition}
-    The game is monotone if $f$ is increasing and $f(0) \geq 0$.
-\end{proposition}
-On the other hand, superadditivity is not as simple in this case, as before.
-For example, when $f$ is concave, then $m$ coalitions with one platform each and the fringe divided equally amongst them clearly achieve a higher total payoff than the grand coalition.
-Therefore, the results of this section are most applicable to settings when multiple coalitions cannot be formed at the same time for some reason.
-For example, \textcite{hart1996bargaining} propose an interpretation when there is a single, indivisible, non-replicable resource or technology (not captured in the value function) necessary to produce any value.
-
-As before, the main proposition in this section provides us with an expression of the limit of the value for this variant of the game.
-Notably, as in the case of the weighted value, the share of player $P$ can again be expressed as an integral of $f$ and some weighting\footnote{
-    Weighting is not a completely precise term, as $h(t)$ does not integrate to one, and is therefore not a probability distribution in this case (\Cref{fig:multiple_platforms}).
-} function $h(t)$, with the latter depending only on the number of big players.
-\begin{proposition}
-    \label{prop:multiple_platforms}
-    The limit of the Shapley-value (as $n \to \infty$) of each player of type $P$ is
-    \begin{align*}
-        \varphi_{P_i}^{\infty, m} = \int_0^1 h(t) f(t) \dt,
-    \end{align*}
-    where $h(t) = (1-t) ^ {m-1}$.
-\end{proposition}
-
-As with proposition \ref{prop:one_sided}, this result also has a probabilistic interpretation.
-Let the location of the $m$ atoms be $t_1, \dots, t_m$, distributed independently and uniformly on the unit interval.
-The expected marginal contribution of $t_i$ is only positive whenever it is the first amongst the major players.
-That is, for any $t_i$, the probability if $P_i$ being the first is related to the cdf of the first order statistic from $n-1$ independent uniform distributions: $1 - (1-t)^{m-1}$.
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.8]
-            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.1, samples at={0, 0.02, 0.04, ..., 0.98, 1},
-                xtick={0, 1}, ytick={0, 1}, axis lines=left, xlabel={$t$}, legend pos=north west]
-                \addplot[thick] {1};
-                \addplot[thick, dashed] {1-x};
-                \addplot[thick, dotted] {(1-x)^2};
-            \end{axis}
-        \end{tikzpicture}
-        \caption{$h(t)$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.8]
-            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.1, samples at={0, 0.02, ..., 0.98, 1},
-                xtick={0, 1}, ytick={0, 1}, axis lines=left, xlabel={$t$}, legend pos=north west]
-                \addplot[thick] {x};
-                \addplot[thick, dashed] {x - x^2/2};
-                \addplot[thick, dotted] {x - x^2 + x^3/3};
-                \legend{$m = 1$, $m = 2$, $m = 3$}
-            \end{axis}
-        \end{tikzpicture}
-        \caption{$\int_0^t h(s) \ds$}
-    \end{subfigure}
-    \caption{Illustration of the weighting function for various values of $m$ in the multiple big player case -- individual big player.}
-    \label{fig:multiple_platforms}
-\end{figure}
-
-Let us examine the total value of all the big players.
-Denote the aggregated value of players of type $P$ as $\varphi_{P}^{\infty, m} \coloneqq \sum_{j=1}^m\varphi_{P_j}^{\infty, m} = m\varphi_{P_i}^{\infty, m}$.
-It immediately follows from the previous proposition that
-\begin{align*}
-    \varphi_{P}^{\infty, m} = \int_0^1 g(t) f(t) \dt,
-\end{align*}
-where $g(t) = m (1-t) ^ {m-1}$.
-Notice that $g(t)$ now integrates to one, and is thus a probability distribution (\Cref{fig:multiple_platforms_total}).
-Therefore, the Shapley value in the case of multiple, substitutable big players can be interpreted as a random order value with a single big player.
-The probability distribution for the corresponding random order value has a specific form, and its only parameter is the number of big players.
-Thus, all the results from the previous section apply to this case as well.
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.8]
-            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=3.1, samples at={0, 0.02, 0.04, ..., 0.98, 1},
-                xtick={0, 1}, ytick={0, 1, 2, 3}, axis lines=left, xlabel={$t$}, legend pos=north west]
-                \addplot[thick] {1};
-                \addplot[thick, dashed] {2 * (1-x)};
-                \addplot[thick, dotted] {3 * ((1-x)^2)};
-            \end{axis}
-        \end{tikzpicture}
-        \caption{$g(t)$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.8]
-            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.1, samples at={0, 0.02, ..., 0.98, 1},
-                xtick={0, 1}, ytick={0, 1}, axis lines=left, xlabel={$t$}, legend pos=north west]
-                \addplot[thick] {x};
-                \addplot[thick, dashed] {2 * (x - x^2/2)};
-                \addplot[thick, dotted] {3 * (x - x^2 + x^3/3)};
-                \legend{$m = 1$, $m = 2$, $m = 3$}
-            \end{axis}
-        \end{tikzpicture}
-        \caption{$\int_0^t g(s) \ds$}
-    \end{subfigure}
-    \caption{Illustration of the weighting function for various values of $m$ in the multiple big player case -- total of big players.}
-    \label{fig:multiple_platforms_total}
-\end{figure}
-
-Now let us look at how the value of the big players and the fringe changes as a function of the number of the big players.
-Proposition \Cref{cor:multiple_platforms_2} again confirms our intuition: more players means that they become more substitutable, and thus their bargaining power decreases.
-This not only means that the value of each individual big player decreases, but also that their total value goes down.
-
-\begin{corollary}
-    \label{cor:multiple_platforms_2}
-    Let $\varphi_{P}^{\infty, m} = m\varphi_{P_i}^{\infty, m}$ denote the aggregated values of players of type $P$.
-$\varphi_{P}^{\infty, m}$ is decreasing in $m$ and $\varphi_{A}^{\infty, m}$ is increasing in $m$ unless $f$ is constant.
-\end{corollary}
-
-Finally, let us show that the value of the fringe has a similar, marginal contribution-based interpretation as in the case of a single big player.
-
-\begin{corollary}
-    \label{cor:multiple_platforms}
-    The per-unit Shapley-value of the fringe is
-    \begin{align*}
-        \varphi_A^{\infty, m} = 1 - \int_0^1 f(t) \dG(t) = \int_0^1 G(t) f'(t) \dt ,
-    \end{align*}
-    where $G(t) = 1 - (1-t)^m$.
-\end{corollary}
-
-\subsection{Small players can generate some value on their own}
-
-As a final extension for the one-sided case, let us examine what happens when the small players can generate some value on their own.
-Assume that the big player still provides some value to any coalition, but a coalition of fringe players can achieve a positive value even without it.
-Formally, the value function is the following:
-\begin{align*}
-    v(S) = \begin{cases}
-        f_0\left(\frac{n_A(S)}{n}\right) & P \notin S \\
-        f\left(\frac{n_A(S)}{n}\right)   & \text{otherwise}.
-    \end{cases}
-\end{align*}
-
-As in the case of multiple big players, monotonicity is straightforward to establish.
-\begin{proposition}
-    The game is monotone if $f$ is increasing and $f(t) \geq f_0(t) \geq 0 \forall t$.
-\end{proposition}
-Also similarly, superadditivity is not straightforward in general.
-Therefore, the simultaneous formation of multiple coalitions must be excluded in this setting as well.
-
-On the other hand, the random order values and their limits are very straightforward to characterize.
-The value of the big player is still its average marginal contribution.
-The only difference is that this marginal contribution (conditional on $s$ share of the fringe coming before $P$) is not simply $f(s)$, but rather $f(s) - f_0(s)$.
-This is because the big player is not indispensable, and thus the fringe can achieve some value without it.
-
-\begin{proposition}
-    \label{prop:one_sided_non_indispensable}
-    Let $f$ be continuous on [0, 1].
-Furthermore, let us denote the random variable $\frac{|\mathcal{P}_P|}{n}$ as $X_n$.
-Assume that $X_n \xrightarrow[]{d} X$ with cdf $G_X(t)$ and (if exists) pdf $g(t)$.
-    Then
-    \begin{align*}
-        \varphi_P^\infty = \lim_{n \to \infty} \varphi_P^n = \int_0^1 f(t) \dG(t) = \int_0^1 g(t) [f(t) - f_0(t)] \dt,
-    \end{align*}
-    with the last equality holding if $X$ is a continuous random variable.
-\end{proposition}
-
-The value of the fringe is also similar to the baseline case, except now fringe players have a non-zero marginal contribution even when $P$ is not present.
-Therefore, there is an additional term in the integral, corresponding to the marginal value of the fringe when $P$ is not present.
-
-\begin{corollary}
-    \label{cor:fringe_value_non_indispensable}
-    The aggregated value of the fringe is
-    \begin{align*}
-        \varphi_A^\infty = f(1) - \int_0^1 f(t) - f_0(t) \dG(t).
-    \end{align*}
-    Furthermore, if $f$ and $f_0$ are differentiable on $[0, 1]$, then the value of the fringe can also be expressed as
-    \begin{align*}
-        \varphi_A^\infty = \int_0^1 G(t) f'(t) + (1 - G(t)) f'_0(t) \dt.
-    \end{align*}
-\end{corollary}
-
-It is clear that the value of the big player is decreasing in $f_0$ (\Cref{fig:non_indispensable}).
-Consequently, the value of the fringe is increasing in $f_0$, which is essentially its outside option (what it can achieve without the big player).
-This is a natural result, and again, it is in line with what one would expect from bargaining theory.
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.8]
-            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-                    xtick={0, 1}, ytick={0}, xlabel={$s$}]
-                \addplot[name path=f, thick] {x^0.5};
-                \addplot[name path=f0, thick] {0.3 * x^0.5};
-                \node[anchor=north west] at (axis cs: .8, .8^0.5) {$f$};
-                \node[anchor=south west] at (axis cs: .8, .3*.8^0.5) {$f_0$};
-                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
-                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);
-
-                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and f0];
-                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
-                \addplot [fill=red, fill opacity=0.05] fill between [of=f0 and bottom];
-
-                \node[anchor=north west, align=left] at (axis cs: .05, .95) {$\varphi_A^\infty$};
-                \node[anchor=south east, align=left] at (axis cs: .95, .05) {$\varphi_A^\infty$};
-                \node[anchor=north west, align=right] at (axis cs: .5, .5) {$\varphi_P^\infty$};
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Fringe can achieve relatively little without $P$}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \begin{tikzpicture}[scale=0.8]
-            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
-                    xtick={0, 1}, ytick={0}, xlabel={$s$}]
-                \addplot[name path=f, thick] {x^0.5};
-                \addplot[name path=f0, thick] {0.7 * x^0.5};
-                \node[anchor=north west] at (axis cs: .8, .8^0.5) {$f$};
-                \node[anchor=north west] at (axis cs: .8, .7*.8^0.5) {$f_0$};
-                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
-                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);
-
-                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and f0];
-                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];
-                \addplot [fill=red, fill opacity=0.05] fill between [of=f0 and bottom];
-
-                \node[anchor=north west, align=left] at (axis cs: .05, .95) {$\varphi_A^\infty$};
-                \node[anchor=south east, align=left] at (axis cs: .95, .05) {$\varphi_A^\infty$};
-                \node[anchor=north west, align=right] at (axis cs: .5, .7) {$\varphi_P^\infty$};
-            \end{axis}
-        \end{tikzpicture}
-        \caption{Fringe can achieve relatively more without $P$}
-    \end{subfigure}
-    \caption{Distribution of value between player $P$ (blue) and the fringe (red)}
-    \label{fig:non_indispensable}
-\end{figure}
-
 \section{Idiosyncratic entry costs are modeled explicitly}

### 2024-08-11 src/paper/theory.tex
Add proofs for more general multiple platforms case.

@@
     Let $f$ be continuous on [0, 1].
-    Let us denote the number of fringe players in any coalition $S$ as $n_F(S)$.
-    Furthermore, let us denote the random variable $\frac{n_F(\mathcal{P}_{P_j})}{n}$ as $X_n$.
-    Assume that $X_n \xrightarrow[]{d} X$ with cdf $G(t)$ and (if exists) pdf $g(t)$.
+    Let us denote the number of fringe players in any coalition $S$ as $n_A(S)$.
+    Furthermore, let us denote the random variable $\frac{n_A(\mathcal{P}_{P_j})}{n}$ as $X_n^j$.
+    Assume that $X_n^j$ and $X_n^k$ are independent for all $j \neq k$.
+    Furthermore, supppose that $X_n^j \xrightarrow[]{d} X^j$ with cdf $G(t)$ and (if exists) pdf $g(t)$ for every $j = 1, \dots, m$.
 
@@
 \end{proposition}
-% TODO: needs proof
 
@@
     Let $\varphi_{P}^{\infty, m}$ denote the aggregated values of players of type $P$.
-$\varphi_{P}^{\infty, m}$ is decreasing in $m$ and $\varphi_{A}^{\infty, m}$ is increasing in $m$ unless $f$ is constant.
+$\varphi_{P}^{\infty, m}$ is decreasing in $m$ and $\varphi_{A}^{\infty, m}$ is increasing in $m$ unless $f$ is constant or $X$ is degenerate.
 \end{corollary}
@@
 
-Now let us look at how the value of the big players and the fringe changes as a function of the number of the big players.
-Proposition \Cref{cor:multiple_platforms_2} again confirms our intuition: more players means that they become more substitutable, and thus their bargaining power decreases.
-This not only means that the value of each individual big player decreases, but also that their total value goes down.
-
-\begin{corollary}
-    \label{cor:multiple_platforms_2}
-    Let $\varphi_{P}^{\infty, m} = m\varphi_{P_i}^{\infty, m}$ denote the aggregated values of players of type $P$.
-$\varphi_{P}^{\infty, m}$ is decreasing in $m$ and $\varphi_{A}^{\infty, m}$ is increasing in $m$ unless $f$ is constant.
-\end{corollary}
-
-Finally, let us show that the value of the fringe has a similar, marginal contribution-based interpretation as in the case of a single big player.
-
-\begin{corollary}
-    \label{cor:multiple_platforms}
-    The per-unit Shapley-value of the fringe is
-    \begin{align*}
-        \varphi_A^{\infty, m} = 1 - \int_0^1 f(t) \dG(t) = \int_0^1 G(t) f'(t) \dt ,
-    \end{align*}
-    where $G(t) = 1 - (1-t)^m$.
-\end{corollary}
-
 \subsubsection{Small players can generate some value on their own}
@@
 
+\begin{proof}[Proof of \Cref{prop:multiple_platforms_total}]
+    Observe that, in any order, only the first big player has a positive marginal contribution.
+    Therefore, given $n$ fringe firms, the total value generated by the big players is
+    \begin{align*}
+        \varphi^{n, m}_P &= \sum_{j=1}^m \sum_R \Pr(R) [ v(\mathcal{P}^R_{P_j} \cup \{i\}) - v(\mathcal{P}^R_{P_j}) ] \\
+        &= \sum_{j=1}^m \sum_{k=0}^n \Pr(n_A(\mathcal{P}^R_{P_j}) = k \land n_P(\mathcal{P}^R_{P_j}) = 0) f(k/n),
+    \end{align*}
+    where $n_A(S)$ and $n_P(S)$ denote the number of fringe players and big players in coalition $S$, respectively.
+    This can be further rewritten as
+    \begin{align*}
+        \varphi^{n, m}_P &= \sum_{j=1}^m \sum_{k=0}^n \Pr(n_A(\mathcal{P}^R_{P_j}) = k \mid n_P(\mathcal{P}^R_{P_j}) = 0) \Pr(n_P(\mathcal{P}^R_{P_j}) = 0) f(k/n) \\
+        &= \sum_{k=0}^n \Pr(n_A(\mathcal{P}^R_{P_j}) = k \mid n_P(\mathcal{P}^R_{P_j}) = 0) f(k/n),
+    \end{align*}
+    where the last equality follows from the fact that the big players are identical in terms of permutation probabilities.
+
+    Remember that the share of fringe players before player $j$ is described by the random variable $X_n^j = n_A(\mathcal{P}^R_{P_j}) / n$.
+    Observe that
+    \begin{align*}
+        \Pr(X_n^j = k/n \mid n_P(\mathcal{P}^R_{P_j}) = 0) &= \Pr(X_n^j = k/n \mid X_n^j = \min\{X_n^1, \dots, X_n^m\} \land n_P(\mathcal{P}^R_{P_j}) = 0) \\
+        &= \Pr(\min\{X_n^1, \dots, X_n^m\} = k/n \mid n_P(\mathcal{P}^R_{P_j}) = 0) \\
+        &= \Pr(\min\{X_n^1, \dots, X_n^m\} = k/n).
+    \end{align*}
+
+    All that remains to show is that
+    \begin{align*}
+        \min\{X_n^1, \dots, X_n^m\} \xrightarrow[]{d} \min\{X^1, \dots, X^m\}.
+    \end{align*}
+    First, note that $(X_n^1, \dots, X_n^m) \xrightarrow[]{d} (X^1, \dots, X^m)$ due to the convergence of the marginal distributions and the fact that $X_n^j$ are independent.
+    Furthermore, the mapping $x \mapsto \min\{x_1, \dots, x_m\}$ is continuous, and thus the continuous mapping theorem applies.
+
+    Putting it all together, we have that
+    \begin{align*}
+        \varphi^{n, m}_P &= \sum_{k=0}^n \Pr(n_A(\mathcal{P}^R_{P_j}) \mid n_P(\mathcal{P}^R_{P_j}) = 0) f(k/n) \\
+        &\xrightarrow[d]{} \sum_{k=0}^n \Pr(\min\{X_n^1, \dots, X_n^m\} = k/n) f(k/n) \\
+        &= \E[\min\{X_n^1, \dots, X_n^m\}] \\
+        &\to \E[\min\{X^1, \dots, X^m\}].
+    \end{align*}
+    If the cdf of $X^j$ is $G(t)$, then the cdf of $\min\{X^1, \dots, X^m\}$ is $1 - (1 - G(t))^m$, which concludes the proof.
+\end{proof}
+
 \begin{proof}[Proof of \Cref{prop:multiple_platforms}]
@@
 \begin{proof}[Proof of Corollary \ref{cor:multiple_platforms_2}] (Assuming $f$ is continuously differentiable) %\textcolor{red}{(Assuming $f$ is continuously differentiable -- will have to relax this)}
-    $f'(t)$ is non-negative, so $[1 - (1-t)^m] f'(t)$ is increasing in $m$ $\forall t \in [0, 1]$.
-    As a consequence, $\varphi_A^{n, \infty}$ is also increasing in $m$ if $f'(t)$ is positive on some interval or, $f(t)$ is not constant.
-    Conversely, $\varphi_{P}^{\infty, m} = 1 - \varphi_{A}^{\infty, m}$ is decreasing in $m$.
+    For any cdf $G$, the function $H(t) = 1 - [1 - G(t)]^m$ is increasing in $m$ for any $t$ unless $G(t) \equiv 0$ or $G(t) \equiv 1$.
+    Therefore, the random variable with cdf $G$ first-order stochastically dominates the one with cdf $H$.
+    As a result, the expected value of any monotonically increasing function is higher for the former than for the latter, unless the function is constant almost everywhere.
 \end{proof}

### 2024-08-12 src/paper/theory.tex
Rewrite introduction

@@
 \begin{abstract}
-    This paper investigates the idea of using random order values, a concept from cooperative game theory, to model bargaining outcomes in games with one indispensable player and a continuum of fringe players.
+    This paper investigates the idea of using random order values, a concept from cooperative game theory, to model bargaining outcomes in games with a small number of central players and a continuum of fringe players.
     Two important special cases of random order values are discussed in detail: the Shapley value and the weighted value.
@@
 This is in part motivated by the appealing properties of the resulting gain distributions and their tractability.
-Furthermore, this practice also has solid theoretical justifications thanks to the long line of studies showing that various cooperative solution concepts are related to certain dynamic, non-cooperative bargaining games.
-For example, \textcite{gul1989bargaining,winter1994demand,hart1996bargaining,inderst2003bargaining,} or, perhaps most relevant to this paper, \textcite{stole1996intra} all propose various extensive-form bargaining games in which the equilibrium corresponds to players' Shapley-values.
-
-For practical applications, the case of one indispensable player and a large number of small ones is particularly important in a number of settings.
+Furthermore, this practice also has solid theoretical justifications thanks to the long line of studies showing that various cooperative solution concepts are related to certain dynamic, non-cooperative bargaining games.\footnote{
+    For example, \textcite{gul1989bargaining,winter1994demand,hart1996bargaining,inderst2003bargaining} propose various extensive-form bargaining games in which the equilibrium corresponds to players' Shapley-values.
+    For results specifically for games bargaining with one indispensable player, see \textcite{stole1996intra}.
+}
+
+For practical applications, the case of a small number of central players and a large number of fringe ones is particularly important in a number of settings.
 Examples include intra-firm ownership structures \parencite{hart1990property}, wage bargaining \parencite{stole1996intra,stole1996organizational,levy1997individual}, collusion and mergers \parencite{segal2003collusion} and upstream-downstream supply chains \parencite{inderst2003bargaining,montez2007downstream}.
-The study of multi-sided markets (or platforms) is also a good fit for this modeling approach, as the platform is often assumed to be indispensable for the various sides to interact.\footnote{
+The study of multi-sided markets (or platforms) is also a good fit for this modeling approach, as the platforms are often assumed to be indispensable for the various sides to interact.\footnote{
     \textcite{huang2022shapley} is amongst the very few examples of using cooperative game theory in this setting.
@@
 
-A common feature of most of the aforementioned papers is that they assume a finite number of players.
-This paper explores the idea of using an infinite-player version of these models, where fringe players are represented as a continuum.
-As is often the case in economics, this infinite-player approximation turns out to be more tractable than the original, finite-player model, while retaining the main features of the latter.
+This paper provides a general framework for modeling bargaining outcomes in this setting.
+By relying on the rather concept of random order values, I highlight the common themes between various results found in more applied papers.
+I demonstrate that these values are described by tractable expressions and have geometric interpretations.
+Just as importantly, I show that the outcomes are in line with one's intuitive expectations of bargaining power in such situations.
+
+Apart from the general framework, this paper also extends the results of the related literature in a number of ways.
+Most importantly, I relax the usual assumption that there is only one indispensable player, and show how the results can be generalized when (1) there are multiple central players, and (2) when the central player is not completely indispensable.
+Further contributions include new results for the case of heterogeneous fringe players.
+In particular, I provide results for weighted values in the case of heterogeneous fringe players, which is a novel contribution to the literature.
+Furthermore, I highlight how the value of the fringe players can be expressed in terms of their marginal contributions, i.e. the partial derivatives of the value function.
+
+I rely on an infinite-player (oceanic game) version of these models, where fringe players are represented as a continuum.
+As is often the case in economics, this infinite-player approximation turns out to be more tractable than the  finite-player model, while retaining the desirable features of the latter.
 For example, the resulting profit shares depend on the production function similarly to the finite-player case, while becoming continuous and differentiable functions of the size of the fringe.
@@
 
-The main contribution of this paper is to provide a general framework for modeling bargaining outcomes in games with one indispensable player and a continuum of fringe players.
-I propose an oceanic game with the main feature that the large player is indispensable for creating value\footnote{
-    This assumption will be somewhat relaxed throughout some of the generalizations.
-}, and examine the (Shapley, weighted and random order) values of the players in this game.
-I demonstrate that these values are described by very tractable expressions and have illuminating geometric interpretations.
-Just as importantly, I show that the outcomes are in line with one's intuitive expectations of bargaining power in such situations.
-
-On one hand, this paper provides a taxonomy of the various results found in some applied papers.
-Furthermore, it introduces some new results pertaining to the case of multiple types of fringe players.
-In particular, I highlight how the value of the fringe players can be expressed in terms of their marginal contributions, and how players' bargaining weights affect outcomes through changing the probability weights of orderings from which those marginal contributions are calculated.
-Finally, to showcase the utility of this approach, I also build a simple model of two-sided markets.
-My hope is that the results in this paper can be used as a tool-kit for embedding bargaining outcomes into more complex models.
+The results presented in this paper can be used as a tool-kit for embedding bargaining outcomes into more complex models.
+To showcase the utility of this approach, I present simple model of two-sided markets.
+\textcite{stancsics2023hybrid} provides a more full-fledged example of such an application, where the results of this paper are used to model the bargaining outcomes in a market with a hybrid platform.
 
@@
 Cooperative games with a finite number of atomic players and a continuum of non-atomic ones are called mixed or oceanic games \parencite{milnor1978values}, and have been studied in the cooperative game theory literature.
-Most papers in this line of research focus on rather fundamental questions, such as for which games does the Shapley-value exist, when is it unique \parencite{hart1973values}, and whether the various ways of defining it\footnote{
+Generally, papers in this line of research focus on fundamental questions, such as existence and uniqueness of the value \parencite{hart1973values}, and whether the various ways of defining it\footnote{
     One can characterize the value of the oceanic game directly, relying on a set of axioms (axiomatic approach).
@@
 }
-My aim with this paper is both somewhat more general and much more specific in certain aspects.
+My aim with this paper is both more general and more specific in certain aspects.
 For one, I focus on the asymptotic approach, and within that, a specific way of approximating the infinite game of interest.
 This is motivated by the fact that I am not interested in the oceanic game per se, but rather in its ability to approximate finite-player games.
-Furthermore, I restrict my attention to a specific, but economically important subset of games: those with one indispensable player, and a continuum of fringe players consisting of a finite number of types.
+Furthermore, I restrict my attention to a specific, but economically important subset of games: those with one, or a small number of central players, and a continuum of fringe players consisting of a finite number of types.
 These two restrictions in turn allow me to go beyond the Shapley value, and obtain results for a more general set of solution concepts: random order values.
@@
 Despite the theoretical appeal and tractability of oceanic games, they, in general, saw remarkably little use in the industrial organization, and, more generally, applied economics.
-Nevertheless, there are a few prominent exceptions, such as \textcite{stole1996intra, stole1996organizational} and \textcite{levy1997individual}, which use the Shapley value to model wage bargaining under the assumption of divisible labor (continuum of workers).
-The first two of these paper also provides microfoundations for using the Shapley value and the weighted value in an intra-firm bargaining setting.
-The present paper contributes to this literature by generalizing some of its results, and an examination of some general properties of the various values in the context of such games.
-In particular, in addition to the aforementioned papers, the proposed model includes two new features: (1) results about the distribution of the value between the various types of fringe players, and (2) using random order values instead of the less general Shapley value or weighted value.
-Furthermore, I also provide results for the intersection of two important extensions in \textcite{stole1996intra}: the case of weighted values in the case of multiple types of fringe players.
-
-Finally, en example application is presented to demonstrate the usefulness of the proposed approach.
-This model is based on the seminal work of \textcite{armstrong2006competition} on multi-sided markets.
-Thus, although the present paper is mainly theoretical, it also has some minor contributions towards better understanding the functioning of multi-sided markets.
+Examples of this include \textcite{stole1996intra, stole1996organizational}\footnote{
+    \textcite{stole1996intra} also provides microfoundations for using the Shapley value and the weighted value in a bargaining setting with one indispensable player.
+} and \textcite{levy1997individual}, which use the Shapley value to model wage bargaining under the assumption of divisible labor (continuum of workers).
+
+The present paper contributes to this literature by generalizing its results, and highlighting certain general properties of the various values in the context of such games.
+The latter is achieved by relying on the concept of random order values, which includes the Shapley value and the weighted value as special cases.
+The generalizations include relaxing the assumption on the indispensability of the central player, providing results for the distribution of the value between the various types of fringe players, and going beyond the Shapley value in the heterogeneous fringe player case.
+
+Finally, the example application presented to demonstrate the usefulness of the proposed approach is based on the seminal work of \textcite{armstrong2006competition} on multi-sided markets.
+Thus, despite the main results being presented in an abstract setting, this paper also has some minor contributions towards better understanding the functioning of multi-sided markets.
 
 The paper is organized as follows.
-In \Cref{sec:one_sided}, I present the main results for the case of one indispensable player and a continuum of identical fringe players.
-\Cref{sec:many_sided} extends these results to the case of multiple types of fringe players.
-This is where the most novel results of the paper are presented.
+In \Cref{sec:one_sided}, I present the main results for the case of identical fringe players.
+It includes the generalizations for the case of not completely indispensable big players.
+\Cref{sec:many_sided} extends some of those results to the case of heterogeneous fringe players.
 \Cref{sec:application} provides an example application of the results to a simple model of a two-sided market.
@@
 
-\begin{proof}[Proof of \Cref{prop:multiple_platforms}]
-    \label{prop:one_sided_multiple}
-    First, let us rewrite the expected marginal contribution of player $P_i$ in the following way:
-    \begin{align*}
-        \varphi_{P_i}^{n, m} &= \frac{1}{(n+m)!} \sum_R v(\mathcal{P}_{P_i}^R \cup \{i\}) - v(\mathcal{P}_{P_i}^R) \\
-        &= \frac{1}{(n+m)!} \left[ \sum_{\{R | n_P(\mathcal{P}_{P_i}^R = 0)\}} \left[v(\mathcal{P}_{P_i}^R \cup \{i\}) - v(\mathcal{P}_{P_i}^R)\right] + \sum_{\{R | n_P(\mathcal{P}_{P_i}^R > 0)\}} \left[v(\mathcal{P}_{P_i}^R \cup \{i\}) - v(\mathcal{P}_{P_i}^R)\right] \right]
-    \end{align*}
-    Next, make use of the fact that the marginal contribution of a platform is zero if another platform is already present, and only depends on the number of fringe firms otherwise.
-    \begin{align*}
-        \varphi_{P_i}^{n, m} &= \frac{1}{(n+m)!} \sum_{\{R | n_P(\mathcal{P}_{P_i}^R = 0)\}} f (\mathcal{P}_{A}^R / n) \\
-        &= \frac{1}{(n+m)!} \sum_{k=0}^n |\{R | n_A(\mathcal{P}^R_{P_i} = k) \text{ and } n_P(\mathcal{P}^R_{P_i} = 0)\}| f(k/n)
-    \end{align*}
-    Finally, notice that, while the permutations with $k$ fringe agents before $P_i$ does not depend on $k$, amongst those, the number of permutations with no platform before $P_i$ does depend on it.
-    In particular,
-    \begin{align*}
-        |\{R | n_A(\mathcal{P}^R_{P_i} = k) \text{ and } n_P(\mathcal{P}^R_{P_i} = 0)\}| &= \frac{n!(n+m-k-1)!}{(n-k)!}
-    \end{align*}
-    and
-    \begin{align*}
-        \varphi_{P_i}^{n, m} &= \sum_{k=0}^n \frac{n!(n+m-k-1)!}{(n+m)!(n-k)!} f(k/n) \\
-        &= \sum_{k=0}^n \frac{(n-k+1)(n-k+2) \dots (n-k+m-1)}{(n+1)(n+2) \dots (n+m)} f(k/n) \\
-        &= \frac{1}{n+1}\sum_{k=0}^n \underbrace{\frac{(n(1-k/n)+1)(n(1-k/n)+2) \dots (n(1-k/n)+m-1)}{(n+2) \dots (n+m)} f(k/n)}_{S_n}
-    \end{align*}
-    For any $t = k/n \in [0, 1]$, 
-    \begin{align*}
-        S_n(t) \to (1-t)^{m-1}f(t) \equiv S(t).
-    \end{align*}
-    Furthermore, it is simple to verify that this convergence is uniform, and that $S_n$ and $S$ are all continuous functions.
-    By Dini's theorem, the former properties imply that $S_n \xrightarrow[]{\mathrm{u}} S$ uniformly on $[0, 1]$.
-
-    The conclusion of the proof is similar to that of proposition \ref{prop:one_sided}:
-    \begin{align*}
-        \lim_{n \to \infty} \varphi_{P_i}^{n, m} &= \lim_{n \to \infty} \underbrace{\frac{n}{n+1}}_{\to 1} \sum_{k=0}^{n-1} S_k(k/n) + \underbrace{\frac{1}{1+n}S(1)}_{\to 0} \\
-        &= \lim_{n \to \infty} \sum_{k=0}^{n-1} S_k(k/n) \\
-        &= \int_0^1 (1-t)^{m-1} f(t) \dt
-    \end{align*}
-    with the last equality supported by lemma \ref{lemma:integral_convergence}.
-\end{proof}
-
 \begin{proof}[Proof of Corollary \ref{cor:multiple_platforms}]

### 2024-08-12 src/paper/theory.tex
Improve conclusions

@@
 
-In this paper, I examine the problem of bargaining between one indispensable player and a continuum of fringe players.
+In this paper, I examine the problem of bargaining between a small number of central players and a continuum of fringe players.
 I model this setting relying on the concept of random order values from cooperative game theory.
-I demonstrate that random-order-value-based outcomes have some desirable properties, and coincide with intuitive expectations in terms of comparative statics.
+I demonstrate that the latter's predictions have some desirable properties, and coincide with intuitive expectations in terms of comparative statics.
 Furthermore, the results are analytically tractable, and have neat interpretations both from a geometric perspective, and in terms of players' marginal contributions.
@@
 Due to the former retaining many of the attractive properties of its more specialized counterparts, it might be a good candidate for modeling bargaining outcomes flexibly and in a tractable manner.
+This also applies to weighted value in the case of multiple types of fringe players, providing a rather flexible model (one more general than the Shapley value) for modeling multi-sided markets.
 Furthermore, as shown in \Cref{sec:extensions}, the results can also be generalized to cases with not completely indispensable big players, while retaining the essential structure of the results.
-
-Another contribution of this paper is the derivation of the weighted value in the case of multiple types of fringe players.
-This provides a rather flexible model (one more general than the Shapley value) for modeling multi-sided markets.
-The proof of the corresponding theorem is also instructive in that it highlights how bargaining weights affect player's values through determining the probabilities of player orderings.
 
@@
 
-There is a variety of ways in which this paper could be expanded or built upon.
+There are a variety of ways in which this paper could be expanded or built upon.
 One obvious direction is to consider other solution concepts from cooperative game theory, such as the nuclelous\footnote{
@@
 }.
-Another is to consider either a wider, or different class of games, and see if the various values can be derived in a similar manner.
+Another is to generalize these results to a wider class of games.
+An example of this would be the value of the coalition increasing also in the number of central players in the coalition.
 A further direction is to consider is building non-cooperative microfoundations for the proposed random-order-value-based bargaining outcomes.
-Many such results exist for the Shapley value, and there are also a couple for the the weighted value, but motivating the more general random order value in a similar manner could be a significant step forward for bargaining theory.
-
-Besides these more theoretical directions, the practical applications are no less interesting.
+Many such results exist for the Shapley value, and there are some for the the weighted value, but motivating the more general random order value in a similar manner could be a significant step towards achieving the goal of the Nash program.
+
+The practical applications are no less interesting.
 The proposed profit sharing framework could be embedded in more applied and detailed models describing various settings.

### 2024-08-12 src/paper/theory.tex
Improve sections in the one sided case

@@
 \newcommand{\Var}{\mathrm{Var}}
+\newcommand{\precede}{\mathrm{prec}}
 
@@
 In this section I examine the case of identical fringe players.
-Many of these results are known in the literature, but I include them here for three reasons.
-First, to provide build intuition for the more general case later on.
-Second, to highlight the similarities to the multi-sided case, and to provide a bridge between the two.
-Finally, I also express the fringe's value in terms of its weighted marginal contributions, which is a useful result in its own right.
-In the main text, I only consider the most straightforward case (one large completely indispensable player), but in \ref{sec:extensions} I will somewhat relax these assumptions.
-
+I start with the case of one, indispensable big player, and relax this assumption in \Cref{sec:extensions}.
 Let us start by defining the cooperative game that describes this situation.
-Consider a game with two types of players: a major player $P$ and $n$ smaller players $A_i$, $1 \leq i \leq n$.
+
+Consider a game with two types of players: a central (or big) player $P$ and $n$ smaller players $A_i$, $1 \leq i \leq n$.
 Formally, let us denote the set of all players as $N = \{P, A_1, \dots, A_n\}$.
@@
 \end{align*}
-Such a game can represent, for example, a (one-sided) platform and a number of potential entrants, where the entrants can only reach their prospective consumers through the platform, or as a vertical supply chain with one upstream producer and a number of downstream sellers.
-
-Before delving into the various values, let us characterize the conditions under which this game is monotone and superadditive.
+Such a game can represent, for example, a (one-sided) platform and a number of potential entrants, where the entrants can only reach their prospective consumers through the platform, or a vertical supply chain with one upstream producer and a number of downstream sellers.
+
+Before delving into solution concepts, let us find conditions under which this game is monotone\footnote{
     Monotonicity requires that the value of any coalition is weakly higher than the value of any of its subsets.
-Superadditivity on the other hand requires that the value of the union of two disjoint coalitions is weakly higher than the sum of their values.
+} and superadditive\footnote{
+    Superadditivity requires that the value of the union of two disjoint coalitions is weakly higher than the sum of their values.
+}.
 The latter is a key property of cooperative games, as it ensures that it always pays off to form the grand coalition (i.e., the coalition that includes all players).
@@
 }
-In this specific setting, characterizing monotonicity and superadditivity is extremely straightforward.
+
+As the next proposition shows, characterizing monotonicity and superadditivity is extremely straightforward in this setting.
 \begin{proposition}
@@
 }.
-This result could also be used to prove \Cref{prop:one_sided} instead of the direct proof provided in \Cref{sec:proofs}.
+This result could also be used to prove the main proposition for the Shapley value (\Cref{prop:one_sided}) instead of the direct proof provided in \Cref{sec:proofs}.
 
@@
 Random order values are a class of cooperative solution concepts characterized by efficiency, monotonicity, linearity and the null-player axiom \parencite{weber1988probabilistic}.
-That is, they are a generalization of the Shapley value, where the axiom of symmetry is relaxed.
-Another way to think about them is that they are the average marginal contribution of a player to all possible coalitions, where the average is taken according to some probability distribution over the permutations of the players.
+That is, they are a generalization of the Shapley value, with the axiom of symmetry being relaxed.
+Another way to think about them is that for they can be defined as the average marginal contribution of player to all possible coalitions, where the average is taken according to some probability distribution over the permutations of the players.
 
@@
 First, take all permutations of the players, and assign a probability to each permutation.
-Then, the random order value of player $P$ is the expected marginal contribution of $P$ to the value of the coalition preceding it, where the expectation is taken according to said probability distribution.
+Then, the corresponding random order value of player $P$ is the expected marginal contribution of $P$ to the value of the coalition preceding it, where the expectation is taken according to said probability distribution.
+
+Random order values are of interest for a number of reasons.
+First, they are a natural extension of the Shapley value and the weighted value.
+Furthermore, they provide a convenient framework, of which all subsequent results (Shapley value, weighted value, multiple central players) are special cases of.
 
@@
 Then, formally,
-\begin{align*}
-    \varphi_P^n = \frac{1}{(n+1)!} \sum_{R} \Pr(R) [ v(\mathcal{P}_P^R \cup \{i\}) - v(\mathcal{P}_P^R) ]
-\end{align*}
-where $R$ is a permutation of all players, and $\mathcal{P}_P^R$ is the set of players before $P$ in the permutation $R$. \footnote{
-    For example, if $R = \{A_1, P, A_2\}$, then $\mathcal{P}_P^R = \{A_1\}$.
-}
-
-Random order values are of interest for a number of reasons.
-First, they are a natural extension to the Shapley value and the weighted value.
-Furthermore, they provide a convenient framework, of which all subsequent results (Shapley value, weighted value, multiple big players) are special cases.
+\begin{align}
+    \varphi_P^n = \frac{1}{(n+1)!} \sum_{R} \Pr(R) [ v(\precede_P^R \cup \{i\}) - v(\precede_P^R) ]  \label{eq:one_sided_general}
+\end{align}
+where $R$ is a permutation of all players, and $\precede_P^R$ denotes the set of players before $P$ in the permutation $R$. \footnote{
+    For example, if $R = \{A_1, P, A_2\}$, then $\precede_P^R = \{A_1\}$.
+}
 
@@
 \begin{align*}
-    \varphi_P^n = \frac{1}{n+1} \sum_{k=0}^n \Pr(|\mathcal{P}_P| = k) f(k/n),
-\end{align*}
-where $\Pr(|\mathcal{P}_P| = k)$ is determined by the probability distribution over the permutations.
+    \varphi_P^n = \frac{1}{n+1} \sum_{k=0}^n \Pr(|\precede_P| = k) f(k/n),
+\end{align*}
+where $\Pr(|\precede_P| = k)$ is determined by the probability distribution over the permutations.
 
 Now let us look at the asymptotic limit of this expression, as the number of fringe players goes to infinity.
-The following proposition demonstrates the main idea of this paper: even as the number of fringe players goes to infinity, the value of the big player does not converge to the worth of the grand coalition, $f(1)$.
+The following proposition demonstrates the main idea of this paper: even as the number of fringe players goes to infinity, the value of the big player does not converge to the total worth of the grand coalition, $f(1)$.
 Or, in other words, the fringe, even when its members are infinitesimally small, still retains some bargaining power.
-As a corollary, the continuous fringe model can be thought of as a more tractable approximation of bargaining between a finite number of fringe players, as it retains the latter's main features.
+As a consequence, the continuous fringe model can be thought of as a more tractable approximation of bargaining between a finite number of fringe players.
 
@@
     \label{prop:one_sided_general}
-    Let $f$ be continuous on [0, 1].
-Furthermore, let us denote the random variable $\frac{|\mathcal{P}_P|}{n}$ as $X_n$.
-Assume that $X_n \xrightarrow[]{d} X$ with cdf $G(t)$ and (if exists) pdf $g(t)$.
+    Let $f$ be continuous on [0, 1]. Furthermore, let us denote the random variable $\frac{|\precede_P|}{n}$ as $X_n$. Assume that $X_n \xrightarrow[]{d} X$ with cdf $G(t)$ and (if exists) pdf $g(t)$.
     Then
@@
 \end{proposition}
+
+% TODO: explain relation to marginal contribution
 
@@
 The only difference from the big player's value is that we have to multiply these marginal contributions by the probability of the big player appearing before the fringe firm in question, as otherwise they would be zero.
-The latter interpretation will be particularly useful when thinking about the value of the fringe in the multi-sided setting.
+The latter interpretation is particularly useful when thinking about the value of the fringe in the setting with heterogeneous fringe firms.
 
 It also follows immediately from the previous proposition that (for a fixed total pie size $f(1)$) player $P$ gets a larger share when $f(t)$ is larger for every $t$.
-That is, when only a relatively small fraction of the fringe is needed to create a large part of the total potential surplus (e.g.
-fringe players' products are substitutes of each other), then player $P$ is able to appropriate a larger share of the total value.
-This result aligns with our natural intuition that player $P$ has a better bargaining position in this case, than if only coalitions with most of the fringe firms on board could obtain high values.
-In contrast, when fringe players are more complementary to each other, the big player can only obtain a smaller share, as its bargaining power is more limited.
+That is, when only a relatively small fraction of the fringe is needed to create a large part of the total potential surplus, then player $P$ is able to appropriate a larger share of the total value.
+This result aligns with the intuition that player $P$ has a better bargaining position in this case, than if only coalitions with most of the fringe firms on board were able to obtain high values.
+
+% TODO: relation to substitutability
+% In contrast, when fringe players are more complementary to each other, the big player can only obtain a smaller share, as its bargaining power is more limited.
 
 \subsection{Special cases}
+
+This section discusses the two most important special cases of random order values: the Shapley value and the somewhat more general weighted value.
+While most of these results are known in the literature, I include them here for two reasons: to provide build intuition for the more general and to highlight the similarities to the multi-sided case.
+
 \subsubsection{Shapley value}
 
-Now let us turn our attention to an important special case of random order values: the Shapley value.
-It can be characterized by being the random order value that additionally also satisfies the axiom of symmetry.
-This axiom requires that if two players are identical in terms of the characteristic function, then they should receive the same value.
-Equivalently, it is the same as requiring that all permutations have an equal probability.
-
-The following proposition and corollary derives the limit of the Shapley value for the big player and the fringe, respectively.
+Let us start with one of the most popular cooperative solution concepts, the Shapley value.
+It can be characterized as the random order value that additionally also satisfies the axiom of symmetry.
+This axiom requires that if two players are identical in terms of the characteristic function, then they should have the same value.
+Equivalently, it is the same as imposing that all permutations have an equal probability in \Cref{eq:one_sided_general}.
+
+The following proposition and corollary derives the limit of the Shapley value for both types of players as the number of fringe players goes to infinity.
 
@@
 
-Because the Shapley value is a special case of the random order value, these results are quite straightforward consequences of \Cref{prop:one_sided_general} and \Cref{cor:fringe_value_general}.
+Because the Shapley value is a special case of the random order values, these results are quite straightforward consequences of \Cref{prop:one_sided_general} and \Cref{cor:fringe_value_general}.
 One only has to notice that each permutation having an equal probability implies that the number of firms coming before $P$ is uniformly distributed on $1, \dots, n$, and thus the share of firms before $P$ converges in distribution to the uniform distribution on $[0, 1]$.
@@
 
-The resulting Shapley values also have a nice geometric interpretation shown on \Cref{fig:one_sided}.
-Consider a rectangle with sides of length 1 and $f(1)$, respectively.
-The grand coalition achieves the value $f(1)$, which is also the area of the rectangle.\footnote{
-    Due to superadditivity, the grand coalition can be expected to form, and the main question is how the value is distributed between the big player and the fringe.
-}
+The resulting Shapley values also have an instructive geometric interpretation shown on \Cref{fig:one_sided}.
+Consider a rectangle with sides of length 1 and $f(1)$.
+The grand coalition achieves the value $f(1)$, which is also the area of the rectangle.
 The value of the big player is then $\int_0^1 f(t) \dt$, which is simply the part of the rectangle below the graph of $f$, while the fringe gets the rest.
@@
         \end{tikzpicture}
-        \caption{Fringe players are each other's substitutes}
+        \caption{Fringe players have lower bargaining power}
     \end{subfigure}
@@
         \end{tikzpicture}
-        \caption{Fringe players are each other's complements}
+        \caption{Fringe players have higher bargaining power}
     \end{subfigure}
@@
 
-\Cref{prop:many_sided_shapley} shows that the value of player $P$ in this case is
+\Cref{prop:one_sided} implies that the value of player $P$ in this case is
 \begin{align*}
@@
 In the limit, when $\alpha \to \infty$, the fringe obtains all the value, as essentially all players become indispensable, and share the total value equally.
-On the other hand, when $\alpha \to 0$, the big players can appropriate all the value.
+On the other hand, when $\alpha \to 0$, the big player can appropriate all the value.
 
@@
     Let us denote the number of fringe players in any coalition $S$ as $n_A(S)$.
-    Furthermore, let us denote the random variable $\frac{n_A(\mathcal{P}_{P_j})}{n}$ as $X_n^j$.
+    Furthermore, let us denote the random variable $\frac{n_A(\precede_{P_j})}{n}$ as $X_n^j$.
     Assume that $X_n^j$ and $X_n^k$ are independent for all $j \neq k$.
@@
     Let $f$ be continuous on [0, 1].
-Furthermore, let us denote the random variable $\frac{|\mathcal{P}_P|}{n}$ as $X_n$.
+Furthermore, let us denote the random variable $\frac{|\precede_P|}{n}$ as $X_n$.
 Assume that $X_n \xrightarrow[]{d} X$ with cdf $G_X(t)$ and (if exists) pdf $g(t)$.
@@
     \begin{align*}
-        X_n = \left( \frac{n_{A_1}(\mathcal{P}_P)}{n}, \dots, \frac{n_{A_L}(\mathcal{P}_P)}{n} \right).
+        X_n = \left( \frac{n_{A_1}(\precede_P)}{n}, \dots, \frac{n_{A_L}(\precede_P)}{n} \right).
     \end{align*}
@@
     \begin{align*}
-        \varphi_P^n = \frac{1}{n+1} \sum_{k=0}^n \Pr(|\mathcal{P}_P| / n = k) f(k/n) = \E[X_n].
+        \varphi_P^n = \frac{1}{n+1} \sum_{k=0}^n \Pr(|\precede_P| / n = k) f(k/n) = \E[X_n].
     \end{align*}
@@
     \begin{align*}
-        \lim_{n \to \infty} \varphi_P^n &= \frac{1}{n+1} \sum_{k=0}^n \Pr(|\mathcal{P}_P| / n = k) f(k/n) \\
+        \lim_{n \to \infty} \varphi_P^n &= \frac{1}{n+1} \sum_{k=0}^n \Pr(|\precede_P| / n = k) f(k/n) \\
         &= \lim_{n \to \infty} \E[X_n] \\
@@
     Let $R$ denote a permutation of the set of players ($N$).
-    Additionally, let us denote the players preceding $i$ by $\mathcal{P}_i^R$.
+    Additionally, let us denote the players preceding $i$ by $\precede_i^R$.
     The value of player $P$ is their expected marginal contribution averaged over all permutations of $N$:
     \begin{align*}
-        \varphi_P^n = \frac{1}{(n+1)!} \sum_R v(\mathcal{P}_P^R \cup \{i\}) - v(\mathcal{P}_P^R)
-    \end{align*}
-    First, note that $v(\mathcal{P}_P^R) = 0$ for any permutation, as no coalition can achieve a positive value without player $P$.
-    Furthermore, using the fact that all agents of type $A$ are identical implies that $v(\mathcal{P}_P^R \cup \{i\})$ only depends on the number of agents in the coalition.
+        \varphi_P^n = \frac{1}{(n+1)!} \sum_R v(\precede_P^R \cup \{i\}) - v(\precede_P^R)
+    \end{align*}
+    First, note that $v(\precede_P^R) = 0$ for any permutation, as no coalition can achieve a positive value without player $P$.
+    Furthermore, using the fact that all agents of type $A$ are identical implies that $v(\precede_P^R \cup \{i\})$ only depends on the number of agents in the coalition.
     More precisely, 
     \begin{align*}
-        v(\mathcal{P}_P^R \cup \{i\}) = f(n_A(\mathcal{P}_P^R \cup \{i\}) / n) = f(|\mathcal{P}_P^R| / n).
+        v(\precede_P^R \cup \{i\}) = f(n_A(\precede_P^R \cup \{i\}) / n) = f(|\precede_P^R| / n).
     \end{align*}
@@
     \begin{align*}
-        \{R \mid |\mathcal{P}_P^R| = k\} = n! \quad \forall\, k.
+        \{R \mid |\precede_P^R| = k\} = n! \quad \forall\, k.
     \end{align*}
@@
     \begin{align*}
-        \varphi_P^{n, \lambda} = \sum_R \Pr(R) [v(\mathcal{P}_P^R \cup \{i\}) - v(\mathcal{P}_P^R)]
+        \varphi_P^{n, \lambda} = \sum_R \Pr(R) [v(\precede_P^R \cup \{i\}) - v(\precede_P^R)]
     \end{align*}
@@
     \begin{align*}
-        \varphi^{n, m}_P &= \sum_{j=1}^m \sum_R \Pr(R) [ v(\mathcal{P}^R_{P_j} \cup \{i\}) - v(\mathcal{P}^R_{P_j}) ] \\
-        &= \sum_{j=1}^m \sum_{k=0}^n \Pr(n_A(\mathcal{P}^R_{P_j}) = k \land n_P(\mathcal{P}^R_{P_j}) = 0) f(k/n),
+        \varphi^{n, m}_P &= \sum_{j=1}^m \sum_R \Pr(R) [ v(\precede^R_{P_j} \cup \{i\}) - v(\precede^R_{P_j}) ] \\
+        &= \sum_{j=1}^m \sum_{k=0}^n \Pr(n_A(\precede^R_{P_j}) = k \land n_P(\precede^R_{P_j}) = 0) f(k/n),
     \end{align*}
@@
     \begin{align*}
-        \varphi^{n, m}_P &= \sum_{j=1}^m \sum_{k=0}^n \Pr(n_A(\mathcal{P}^R_{P_j}) = k \mid n_P(\mathcal{P}^R_{P_j}) = 0) \Pr(n_P(\mathcal{P}^R_{P_j}) = 0) f(k/n) \\
-        &= \sum_{k=0}^n \Pr(n_A(\mathcal{P}^R_{P_j}) = k \mid n_P(\mathcal{P}^R_{P_j}) = 0) f(k/n),
+        \varphi^{n, m}_P &= \sum_{j=1}^m \sum_{k=0}^n \Pr(n_A(\precede^R_{P_j}) = k \mid n_P(\precede^R_{P_j}) = 0) \Pr(n_P(\precede^R_{P_j}) = 0) f(k/n) \\
+        &= \sum_{k=0}^n \Pr(n_A(\precede^R_{P_j}) = k \mid n_P(\precede^R_{P_j}) = 0) f(k/n),
     \end{align*}
@@
 
-    Remember that the share of fringe players before player $j$ is described by the random variable $X_n^j = n_A(\mathcal{P}^R_{P_j}) / n$.
+    Remember that the share of fringe players before player $j$ is described by the random variable $X_n^j = n_A(\precede^R_{P_j}) / n$.
     Observe that
     \begin{align*}
-        \Pr(X_n^j = k/n \mid n_P(\mathcal{P}^R_{P_j}) = 0) &= \Pr(X_n^j = k/n \mid X_n^j = \min\{X_n^1, \dots, X_n^m\} \land n_P(\mathcal{P}^R_{P_j}) = 0) \\
-        &= \Pr(\min\{X_n^1, \dots, X_n^m\} = k/n \mid n_P(\mathcal{P}^R_{P_j}) = 0) \\
+        \Pr(X_n^j = k/n \mid n_P(\precede^R_{P_j}) = 0) &= \Pr(X_n^j = k/n \mid X_n^j = \min\{X_n^1, \dots, X_n^m\} \land n_P(\precede^R_{P_j}) = 0) \\
+        &= \Pr(\min\{X_n^1, \dots, X_n^m\} = k/n \mid n_P(\precede^R_{P_j}) = 0) \\
         &= \Pr(\min\{X_n^1, \dots, X_n^m\} = k/n).
@@
     \begin{align*}
-        \varphi^{n, m}_P &= \sum_{k=0}^n \Pr(n_A(\mathcal{P}^R_{P_j}) \mid n_P(\mathcal{P}^R_{P_j}) = 0) f(k/n) \\
+        \varphi^{n, m}_P &= \sum_{k=0}^n \Pr(n_A(\precede^R_{P_j}) \mid n_P(\precede^R_{P_j}) = 0) f(k/n) \\
         &\xrightarrow[d]{} \sum_{k=0}^n \Pr(\min\{X_n^1, \dots, X_n^m\} = k/n) f(k/n) \\
@@
     \begin{align*}
-        \varphi_P^n &= \sum_{k_1=0}^n \dots \sum_{k_L=0}^n \Pr(n_{A_1}(\mathcal{P}_P) = k_1, \dots, n_{A_L}(\mathcal{P}_P) = k_L) f\left(\frac{k_1}{n}, \dots, \frac{k_L}{n}\right) \\
+        \varphi_P^n &= \sum_{k_1=0}^n \dots \sum_{k_L=0}^n \Pr(n_{A_1}(\precede_P) = k_1, \dots, n_{A_L}(\precede_P) = k_L) f\left(\frac{k_1}{n}, \dots, \frac{k_L}{n}\right) \\
         &= \sum_{k_1=0}^n \dots \sum_{k_L=0}^n \Pr(n X_n = (k_1, \dots, k_L)) f\left(\frac{k_1}{n}, \dots, \frac{k_L}{n}\right) \\

### 2024-08-13 src/paper/theory.tex
Improve special cases section

@@
 
-In this section I examine the case of identical fringe players.
+In this section, I examine the case of identical fringe players.
 I start with the case of one, indispensable big player, and relax this assumption in \Cref{sec:extensions}.
@@
 
-This section investigates the case of players having different levels of innate bargaining power.
-One way to model this is by using weighted values \parencite{shapley1953additive}, which are a generalization of the Shapley value.
-They are also a non-symmetric generalization of the Shapley value, albeit with more structure than random order values.
-The idea behind them is that, in addition to the set of players and the characteristic function, the game is also endowed with a weight system, which is a vector of non-negative numbers, one for each player.
+The other important special case of random order values is the weighted value \parencite{shapley1953additive}.
+It relaxes the symmetry axiom of the Shapley value, and allows for players having different levels of innate bargaining power.
+On the other hand, weighted values still have more structure than random order values, as they are characterized by a weight system (a vector of non-negative numbers for each player).
 These weights determine how the value of a coalition is distributed amongst its members in the case when they are all equally important for the coalition.
@@
 
-These weights can be thought of as the measure of some innate bargaining power, not reflected in the value function.\footnote{
+The weights can be thought of as the measure of some innate bargaining power, not reflected in the value function.\footnote{
     Although, this interpretation is not always appropriate.
@@
 }
-Additionally, \textcite{stole1996intra} provides an alternative microfoundation for the weighted value in the case of non-binding contracts.
-
-For my purposes, it is sufficient to deal with the case of simple weights.
-I.e., assume that there is at most one player with zero weight.
-For my main result, I make use of an alternative, computational characterization of the weighted values. 
-\textcite{kalai1987weighted} demonstrated that weighted values can be calculated by weighting the permutations by the probabilities arising from the following sequential ordering procedure.
+Additionally, \textcite{stole1996intra} provides alternative microfoundations for the weighted value in the case of one indispensable and a continuum of fringe players.
+
+For the purposes of the current players, it is sufficient to deal with the case of simple weights\footnote{
+    In general, weighted values allow for more complex weight systems with each player having a vector of weights applied in a lexicographic manner.
+}
+as I assume that there is at most one player with zero weight.
+For my main result, I make use the following characterization of the weighted values: \textcite{kalai1987weighted} demonstrated that weighted values can be calculated by weighting the permutations by the probabilities arising from the following sequential ordering procedure.
 Start with the set of all players.
@@
 This yields a well-defined probability for each permutation of players.
+The weighted value is then the same as the random order value with this probability distribution over the permutations.
 
 Now let us turn to deriving the weighted value and its limit for the big player and the fringe in this specific game.
-First, I propose a lemma that characterizes the distribution of the number of players before $P$ in the limit, and then use it to derive the weighted value of the big player and the fringe.
+First, I prove a lemma that characterizes the distribution of the number of players before $P$ in the limit, and then use it to derive the weighted value of the big player and the fringe.
 Consider the game described in the previous section, and let the weights of players of type $A$ and $P$ be 1 and $\lambda$, respectively.
@@
 
-Now we have everything we need to derive the weighted value of both types of players.
+With this in hand, deriving the weighted value of both types of players is straightforward.
 Having \Cref{eq:entry_distr_discrete} and \Cref{lem:entry_distr} allows us to invoke \Cref{prop:one_sided_general} to obtain the following proposition.\footnote{
@@
 
-As before, the value of the big player can still be expressed as an integral of the value function, while the value of the fringe can be expressed as an integral of the marginal contributions of the fringe players.
-The only difference is that, as in the case of the general random order value, the integrands are weighted by some probability distribution.
+As before, the value of the big player can be expressed as an integral of the value function, while the value of the fringe can be expressed as an integral of the marginal contributions of the fringe players.
+The only difference is that, as in the case of the general random order value, the integrands are weighted by a specific probability distribution.
 Depending on the shape of this distribution, regions corresponding to different masses of fringe firms can be over or underweighted in this integral, leading to different values.
@@
 Now, let us examine how these weights impact the shares of the various players.
+It turns out, that a higher weight corresponds to a higher value in this game.\footnote{
+    This would not necessarily have to be the case, as demonstrated by \textcite{owen1968communications}.
+},
+supporting their interpretation as some kind of innate bargaining power.
 \begin{corollary}
@@
 \end{corollary}
-It turns out, that a higher weight corresponds to a higher Shapley-value in this game.\footnote{
-    This would not necessarily have to be the case, as demonstrated by \textcite{owen1968communications}.
-},
-supporting their interpretation as some kind of innate bargaining power.
-
-Furthermore, the next corollary shows that the limit of the weighted value of $P$, as their weight goes to zero (infinity) is precisely the payoffs $P$ would achieve if $P$ were making (facing) take-it-or-leave-it offers.
+
+Furthermore, the next corollary shows that the limit of the weighted value of $P$, as their weight goes to zero (infinity) is precisely the payoff $P$ that they would achieve if they were making (facing) take-it-or-leave-it offers.
 \begin{corollary}
     \label{cor:paltform_value_weighted_2}
-    If the weight of player $P$ goes to infinity (zero), its weighted Shapley value converges to $f(1)$ ($f(0)$).
+    If the weight of player $P$ goes to infinity (zero), their weighted Shapley value converges to $f(1)$ ($f(0)$).
 \end{corollary}
-This set of results highlights that utilizing (weighted) Shapley values to model bargaining outcomes provides an intermediate solution between inscribing all the bargaining power to one or the other player, and thus a generalization of take-it-or-leave-it offers.
+This set of results highlights that utilizing (weighted) Shapley values to model bargaining outcomes provides an intermediate solution between inscribing all the bargaining power to one or the other player, and thus a generalization of take-it-or-leave-it offers, with the distribution of bargaining power being adjustable by a single parameter.
 
@@
 \end{corollary}
-% TODO: adjust proof
 
 \paragraph{Example: Shapley value.}
-
-I illustrate the effect of the number of big players on the weight function $h(t)$ by looking at the simplest random order value, the Shapley value.
+I illustrate the effect of the number of big players on the weight function $h(t)$ by looking at the simplest of the random order values, the Shapley value.
 As shown in \Cref{prop:one_sided}, the limit of the Shapley value in the case of a single big player is just $\int_0^1 f(t) \dt$.

### 2024-08-13 src/paper/theory.tex
Improve heterogeneous fringe part

@@
 This section discusses the two most important special cases of random order values: the Shapley value and the somewhat more general weighted value.
-While most of these results are known in the literature, I include them here for two reasons: to provide build intuition for the more general and to highlight the similarities to the multi-sided case.
+While most of these results are known in the literature, I include them here for two reasons: to provide build intuition for the more general and to highlight the similarities to the case of heterogeneous fringe players.
 
@@
 Up until this point, we have only considered games with a single type of small player.
-Now imagine that, in addition to player $P$, there are $L$ different varieties of smaller players: $\{A^l_1, \dots, A^l_n\}$ where $1 \leq l \leq L$.
+Now imagine that, in addition to player $P$, there are $L$ different varieties of players: $\{A^l_1, \dots, A^l_n\}$ where $1 \leq l \leq L$.
 The idea is the same as before: I assume that $P$ is necessary for any coalition to have a positive value, and the small players are identical to each other \emph{within their types}.
@@
 
-Let us now turn to the formal definition of the game.
-For a finite number of fringe players, the coalitional form of the game $(N, v)$ is the following.
+Let us now turn to the formal definition of the setting.
+For a finite number of fringe players, the coalitional form, $(N, v)$, of the game is the following.
 The set of players is $N = \{P, A^1_1, \dots, A^1_n, \dots, A^L_1, \dots, A^L_n\}$, which in total contains $nL + 1$ players.\footnote{
@@
     However, this is not as restrictive as it might seem.
-    In the limit, each type of player will become infinitesimally small, and the exact number of players of each type will not matter.
+    In the limit, each type of player will become infinitesimally small, and the exact number of players of each type does not matter.
 }
@@
 \end{align*}
-where $f$ is now a multivariate function from $[0, 1]^L$ to $\mathbb{R}$.
+where $f$ is now a multivariate function from $[0, 1]^L$ to $\mathbb{R}$ and $n_{A^l}(S)$ denotes the number of players of type $A^l$ in coalition $S$.
 
@@
 }
-More than two types of fringe players can be used to model a platform with more than two sides, such as a platform with both buyers and sellers, and a set of advertisers, or, following \textcite{stole1996intra}, bargaining between a firm and multiple types of input suppliers.
-
-For the subseuent discussion, let us follow the structure of the previous section.
+More than two types of fringe players can be used to model a platform with more than two sides, such as a platform with buyers, sellers and a set of advertisers, or, following \textcite{stole1996intra}, bargaining between a firm and multiple types of input suppliers.
+
+The subsequent discussion follows the structure of \Cref{sec:one_sided}.
 I start by characterizing conditions for monotonicity and superadditivity to support the bargaining interpretation and the formation of the grand coalition.
@@
 
-In the next subsections, I will first examine random order values, and then two important special cases: the Shapley value and the weighted value.
-Many of the results will be similar to the one-sided case, including the marginal contribution interpretation of the value of the fringe, and the geometric interpretation of the Shapley value.
+In the next subsections, I will first examine random order values, and then the two important special cases: the Shapley value and the weighted value.
+Many of the results are be similar to the one-sided case, including the marginal contribution interpretation of the value of the fringe, and the geometric interpretation of the Shapley value.
 Furthermore, it turns out that even though the number of fringe players is a multi-dimensional object in this case, for the limit of the Shapley and weighted values, one only has to integrate over a one-dimensional manifold within the unit hypercube, which makes the results more tractable.
@@
 
-First, let us examine the most general case: the random order value.
-Let us start by establishing the analog of \Cref{prop:one_sided_general} for the many-sided case to obtain the limit of the value of the big player.
+I start with the most general case: the random order value.
+Let us establish the analog of \Cref{prop:one_sided_general} for the case of heterogeneous fringe to obtain the limit of the value of the big player.
 \begin{proposition}
@@
 While the above proposition is very general in terms of permutation probabilities, it is not very tractable in practice, as one has to integrate over the entire, $L$-dimensional domain of $f$.
-It would be much more convenient, if one only had to be concerned with a one-dimensional manifold within the hypercube instead.
-It turns out, that for a number of important cases (namely, the Shapley value and the weighted value) it is indeed the case.
-
-Let us start by establishing a general result, after which I will show that the Shapley value and the weighted value are special cases of it.
-The following lemma provides sufficient conditions, under which the limit of the value of the big player can be expressed as an integral over a one-dimensional path, even though the value for any finite number of players depends on the whole domain of $f$.
+It would be much more convenient, if one only had to be concerned with a one-dimensional manifold within this hypercube instead.
+It turns out that, for a number of important cases (namely, the Shapley value and the weighted value), it is indeed the case.
+
+The following lemma states a general result about this idea: it provides sufficient conditions, under which the limit of the value of the big player can be expressed as an integral over a one-dimensional path, even though the value for any finite number of players depends on the whole domain of $f$.
+Later on, I show that it applies to both the Shapley value and the weighted value.
 \begin{lemma}
@@
 
-The lemma states, that if the permutation probabilities are such that the number of fringe players before $P$ converges to a degenerate distribution, then one only has to be concerned with just a tiny fraction of the production function $f$.
+The lemma states, that if the permutation probabilities are such that the number of fringe players before $P$ converges to a degenerate distribution, then one only has to be concerned with just a tiny part of the production function $f$.
 Namely, we only need to know how the function behaves on the set $\{(a_1(t), \dots, a_L(t)) : t \in [0, 1]\} \subset [0, 1]^L$.\footnote{
     For the fringe players, we also need the partial derivatives.
-    Therefore, technically, the behavior of $f$ on some arbitrarily small neighborhood of the set also matters.
+    Therefore, technically, the behavior of $f$ on some arbitrarily small neighborhood of this set also matters.
 }
@@
 The intuition, however, is the same law-of-large-numbers-type argument: if the number of fringe players is large, then it is very unlikely that, after a random ordering, their proportion is very different from its expected value.
-The main difference is that, in this case, this conditional expectations are not linear, but rather given by the $a_l$ functions.
-
-In the remainder of this section, I will show that the Shapley value and the weighted value satisfy the assumptions of the above lemma, and thus the limit of those values can be expressed as an integral over a well-defined one-dimensional path.
+The main difference is that, in this case, these conditional expectations are not linear, but rather given by the $a_l$ functions.
+
+In the remainder of this section, I will show that the Shapley value and the weighted value satisfy the assumptions of the above lemma, and thus the limit of those values can be expressed as an integral over a well-defined, one-dimensional path.\footnote{
+    I do not extend the heterogeneous agent model to the case of non-indispensable big players.
+    It would be conceptually straightforward to do so for cases when \Cref{lem:many_sided_manifold} applies, albeit somewhat more cumbersome.
+}
 
@@
 That is, in the case of the Shapley value, one has to integrate over the diagonal of the unit hypercube to obtain the limit of the value of the big player.\footnote{
-    \textcite{stole1996intra} also obtain the expression for the big player's value for the limiting case of their bargaining game.
+    \textcite{stole1996intra} also obtain this expression for the big player's value for the limiting case of their bargaining game.
     The proof of this proposition demonstrates a way to obtain it as a limit of the Shapley value of the finite games.
@@
 
-The final part of this section is dedicated to the weighted value in the many-sided case.
+The final part of this section is dedicated to the weighted value in the heterogeneous fringe case.
 The set of players and the characteristic function are the same as in the previous section, but, as before, each player has a weight attached to them.
-I will assume that fringe players are identical to each other within their types also with respect to their weights.
+I assume that fringe players are identical to each other within their types also with respect to their weights.
 That is, the weight system for the game is the following: player $P$ has weight $\lambda_P$, while players $A^l_i$ have weight $\lambda_l$.
 
-I will show, that as with non-weighted Shapley value, the limit of the weighted value can be expressed as an integral over a one-dimensional path in the weighted case as well.
-However, now this path is not the diagonal of the unit hypercube, but a function of the fringe players' weights.
+I will show that, as with non-weighted Shapley value, the limit of the weighted value can be expressed as an integral over a one-dimensional path in the weighted case as well.
+However, this path is not the diagonal of the unit hypercube anymore, but a function of the fringe players' weights.
 The reason for this is that not all permutations have the same probability of occurring: those with players having higher weights ordered later are more likely to occur.
@@
 The following statement is the central theorem of this paper.
-In fact, most of the propositions in the previous sections can be considered as special cases of it.
+In fact, many of the propositions with one indispensable player can be considered as special cases of it.
 \begin{theorem}
@@
 \end{theorem}
-The intuition is the following.
+The intuition for this is the following.
 A higher weight for a player means that it has a higher chance of being relatively late in a random permutation.
@@
 \Cref{fig:many_sided_weighted} illustrates this phenomenon in the case of two types of fringe players.
-Fringe players of type $A^2$ have a higher weight than those of type $A^1$, and thus the path the integral is taken over contains more of the latter than the former.
-
-Finally, player $P$'s probability of coming after $s$ proportion of the fringe is also not uniform, but rather influenced by the relationship between its own and the fringe players' weights.\footnote{
+Players of type $A^2$ have a higher weight than those of type $A^1$, and thus the path the integral is taken over contains more of the latter than the former.
+
+Finally, player $P$'s probability of coming after $s$ proportion of the fringe is also not uniform, but rather influenced by the relationship between its own weight and the fringe players' weights.\footnote{
     This is the same mechanism as in the case of the one-sided weighted value.
 } 
-Therefore, the integral is not taken with respect to the uniform distribution, but rather one resembling that of \Cref{prop:one_sided_weighted}.
-The result is the following: when the big player has a higher weight, its chances of being relatively late in the ordering are higher, and thus -- due to $f$ being monotone increasing -- its value is higher.
+Therefore, the integral is not taken with respect to the uniform distribution, but rather one resembling that in \Cref{prop:one_sided_weighted}.
+It results are the same: when the big player has a higher weight, its chances of being relatively late in the ordering are higher, and thus -- due to $f$ being monotone increasing -- its value is higher.
 The following, simple corollary formalizes this idea.
@@
 \end{corollary}
-This result is analogous to \Cref{cor:platform_value_weighted}, and demonstrates that a higher weight for player $P$ corresponds to a higher value in this game as well.
+This result is analogous to \Cref{cor:platform_value_weighted}, and demonstrates that a higher weight for player $P$ corresponds to a higher value in this game, as well.
 

### 2024-08-13 src/paper/theory.tex
Improve example application

@@
 In this section, I apply the ideas from the previous sections to a simple model of two-sided platforms.
-I follow the modelling approach of \textcite{armstrong2006competition}, focusing on the monopoly platform case.
-The model presented in this section expands on the original model in two main ways.
-First, instead of assuming that each player's utility is linear in the number of the other side's players, I allow for more general non-linear network effects. 
-This extension lets me capture and vary the substitutability of the two sides.
-Second, and most importantly, I add bargaining between the platform and the two sides.
+I follow the modelling approach of \textcite{armstrong2006competition}, focusing on the monopolist platform case.
+The model presented in this section expands on the original in two main ways.
+First, and most importantly, I add bargaining between the platform and the two sides.
 That is, besides the welfare-maximizing and unilateral price setting cases presented in \textcite{armstrong2006competition}, I also consider a case where the platform and the two sides bargain over the entry fees.
 I assume that the outcomes of this bargaining process are described by the weighted value.
+Second, instead of assuming that each player's utility is linear in the number of the other side's size, I allow for more general non-linear network effects. 
+This extension lets me capture and vary the substitutability of the players on each sides.
 
@@
 
-Imagine a two-sided market with a continuum of players on both sides and a single platform connecting those two sides.
-Furthermore, assume that the utility that a player on side $i$ derives from participating in the market is an increasing function\footnote{
-    \textcite{armstrong2006competition} -- along with much of the early literature on two-sided markets \parencite[e.g.][]{rochet2003platform,hagiu2006pricing} -- assume that the utility of a player is linear in the number of players on the other side.
-    Using a more general function allows me to model different degrees of network effects.
+Consider a two-sided market with a continuum of players on both sides, and a single platform connecting those two sides.
+Furthermore, assume that the utility that a player on side $i$ derives from participating in this market is an increasing function\footnote{
+    \textcite{armstrong2006competition} -- along with much of the early literature on two-sided markets \parencite[e.g.][]{rochet2003platform,hagiu2006pricing} -- assume that the utility of each player is linear in the number of players on the other side.
+    Using a more general function allows me to model different more kinds of network effects.
 } of the number of players on the other side ($n_j$), minus the entry fee charged by the platform ($p_i$):
@@
 
-Following \textcite{armstrong2006competition}, let us model player entry also in a reduced form manner.
+Following \textcite{armstrong2006competition}, I model player entry also in a reduced form manner.
 Assume that there is a continuum of potential entrants on both sides of the market.
-The number of actual entrants depends on the utility they would derive from participating in the market.\footnote{
-    Such assumptions are usually justified by some idiosyncratic cost of entry, the distribution of which determines the function $\phi$.
-    For simplicity, I refrain from explicitly modeling this cost in the main text, but \Cref{sec:explicit_entry_costs} provides a discussion of how one can incorporate it into the model, its impact on bargaining outcomes.
-}
-Let us denote this relationship as $\phi_i(u_i)$, where $\phi_i$ is a strictly increasing, differentiable function.
+The number of actual entrants depends on the utility they would derive from participating if they entered.
+Let us denote this relationship as $\phi_i(u_i)$, where $\phi_i$ is a strictly increasing, differentiable function.\footnote{
+    Such assumptions are usually justified by having idiosyncratic cost entry costs, the distribution of which determines the function $\phi$.
+    For simplicity, I refrain from explicitly modeling this cost in the main text, but \Cref{sec:explicit_entry_costs} discusses how one can incorporate it into the model, and its impact on bargaining outcomes.
+}
 Then,
@@
 Finally, let us assume that the platform can charge lump-sum entry fees to both sides.
-These fees can also be negative, in which case they are interpreted as subsidies.
+These fees are allowed to be negative, in which case they are interpreted as subsidies.
 The platform's profit is the sum of entry fees, minus the cost of serving the entrants ($F_i$ for each entrant):
@@
 
-I consider two cases as to the determination of the entry fees, as well as a welfare-maximizing benchmark.
-By the latter, I mean the entry fees that maximize social welfare, i.e. the sum of the utilities of the two sides plus the platform's profit.
-After that, I first consider a model analogous to that in \textcite{armstrong2006competition}, where the platform can unilaterally commit to any entry fees it wishes.
-Finally, I examine and contrast the case where the entry fees the result of a bargaining process in such a way that the resulting utilities and profits correspond to the various players' (weighted) values.
+I consider two cases as to the determination of the entry fees, as well as a welfare-maximizing benchmark\footnote{}.
+In the benchmark case, I derive the entry fees that maximize social welfare, i.e. the sum of the utilities of the two sides plus the platform's profit.
+After that, I consider a model analogous to that in \textcite{armstrong2006competition}, where the platform can unilaterally commit to any entry fees it wishes.
+Finally, I examine and contrast the case where the entry fees the result of a bargaining process in such a way that the resulting utilities and profits correspond to the players' (weighted) values.
 
@@
 Let us first consider what the entry fees would be if they were set to maximize social welfare.
-Instead of approaching this problem directly, I rely on the following observation: if entry fees correspond to the externality that a player's entry imposes on the other players, then the resulting entry decisions are welfare-maximizing.
-
-In this specific case, there are two externalities to consider.
-First, it costs the platform $F_i$ to serve an additional player on side $i$.
-Second, the entry of a player on side $i$ increases the utility on side $j$ due to the presence of network effects.
+Instead of approaching this problem directly, I rely on the following observation: if entry fees correspond to the externality that a player's entry imposes on others, then the resulting entry decisions are welfare-maximizing.
+
+In this specific case, there are two externalities to consider: (1) it costs the platform $F_i$ to serve an additional player on side $i$, and (2) the entry of a player on side $i$ increases the utility on side $j$ due to the presence of network effects.
 Welfare is maximized when the price reflects the balance of these two factors.
@@
 
-As in \textcite{armstrong2006competition}, for any $\alpha_j > 0$ welfare-maximizing $F_i$ is below the platform's cost of serving player $i$.
-Thus, the platform's profit would necessarily be negative.
-Therefore, while this case is useful as a benchmark, it is not particularly realistic when the platform has a say in determining entry fees, or even the possibility to exit the market.
-
-As an immediate corollary, utilities in this case are given by
+Similarly to \textcite{armstrong2006competition}, for any $\alpha_j > 0$, the welfare-maximizing entry fee $F_i$ is below the platform's cost of serving player $i$.
+As a consequence, the platform makes negative profits.
+Therefore, while this case is useful as a benchmark, it is not particularly realistic when the platform has a say in determining entry fees, or has the possibility to exit the market altogether.
+
+As an immediate corollary to \Cref{prop:welfare_max_entry_fees}, utilities in this case are given by
 \begin{align*}
@@
 for each individual player on side $i$.
-Consequently, the total welfare on side $i$, as it is simply the number of entrants times the non-idiosyncratic utility of its players, plus the sum (integral) of the idiosyncratic utilities.
+The total welfare on side $i$ is in turn given by
 \begin{align}
@@
 
-That is, players on side $i$ obtain the total generated by themselves, plus $\gamma_j$ times the total utility generated by the other side, net of the cost of serving them.
+That is, players on side $i$ obtain the total generated by themselves, plus $\gamma_j$ times the total utility generated by the other side, minus the cost of serving them.
 The utility of side $i$ depends positively on both $\alpha_i$ (mechanically) and $\alpha_j$ (a stronger positive externality on the other players implies a lower entry fee and thus higher utility).
-Furthermore, it is increasing in the number of entrants on the other side through two channels: (1) entrants on the other side generate utility for side $i$ through network effects, and (2) players on side $i$ are compensated for the positive externality they impose on the other side.
+Furthermore, it is increasing in the number of entrants on the other side through two channels: (1) entrants on the other side generate utility for side $i$ through network effects, and (2) players on side $i$ are compensated for the positive externality they impose on each player on the other side.
 
@@
 
-Now let us examine what happens when the platform sets the entry fees unilaterally.
-First, rewrite the platform's profit as a function of utilities, rather than the number of entrants:
+Now let us examine what happens when the platform can set the entry fees unilaterally.
+First, let us rewrite the platform's profit as a function of utilities, rather than the number of entrants:
 \begin{align*}
@@
 \end{align*}
-If the platform can set entry fees unilaterally, then it's problem is to choose $u_1$ and $u_2$ to maximize this expression.
-
+If the platform can set entry fees unilaterally, then it's problem can be viewed as choosing $u_1$ and $u_2$ to maximize this expression.
+The next proposition characterizes the solution of this maximization problem.
 \begin{proposition}
@@
 In addition to the comparative statics of the welfare-maximizing case, the unilaterally chosen also depend on the elasticity of entry.
-When this elasticity is low, the can set high entry fees, as the reduction in the number of entrants is not relatively minor.
-
-For ease of comparison with the bargaining case, let us also derive the utilities and welfare on side $i$ in this case, too:
+When this elasticity is low, the platform can set high entry fees, as the resulting reduction in the number of entrants is relatively minor.
+
+For ease of comparison with the bargaining case, let us also derive the individual utilities and total welfare on each side, too:
 \begin{align*}
@@
 \end{align*}
-Clearly, equilibrium utilities must be smaller than in the welfare-maximizing case.
+As expected, equilibrium utilities are smaller than in the welfare-maximizing case.
 Due to $\phi_i$ being increasing, the number of entrants is also lower.
@@
 
-\section{Conclusions}
+\section{Conclusion}
 \label{sec:conclusions}

### 2024-08-14 src/paper/theory.tex
Improve example application

@@
     The welfare-maximizing entry fees for side $i$ are characterized by
-    \begin{align*}
-        p_i^* = F_i - \alpha_j \gamma_j n_j n_i^{\gamma_j - 1}.
-    \end{align*}
+    \begin{align}
+        p_i^* = F_i - \alpha_j \gamma_j n_j n_i^{\gamma_j - 1}.  \label{eq:welfare_max_entry_fees}
+    \end{align}
 \end{proposition}
@@
     Then, the profit-maximizing entry fees for side $i$ are characterized by
-    \begin{align*}
-        p_i^u &= F_i - \alpha_j \gamma_j n_j n_i^{\gamma_j - 1} + \frac{\phi_1(u_1)}{\phi'_1(u_1)} \\
-              &= p_i^* + \frac{\phi_1(u_1)}{\phi'_1(u_1)}.
-    \end{align*}
+    \begin{align}
+        p_i^u &= F_i - \alpha_j \gamma_j n_j n_i^{\gamma_j - 1} + \frac{\phi_1(u_1)}{\phi'_1(u_1)}  \label{eq:unilateral_entry_fees} \\
+              &= p_i^* + \frac{\phi_1(u_1)}{\phi'_1(u_1)}.  \nonumber
+    \end{align}
 \end{proposition}
@@
 Finally, let us consider the case when the platform and the entrants bargain over the value they generate.
-Assume that $n_1$ and $n_2$ players have decided to enter on sides $1$ and $2$, respectively.
+Suppose that $n_1$ and $n_2$ players have decided to enter on sides $1$ and $2$, respectively.
 Furthermore, assume that players' bargaining weights are $\lambda_1, \lambda_2$ and $\lambda_P$.
@@
 The characteristic function of the game takes a similar form to that in \Cref{sec:many_sided}.
-If the platform is not a member of a coalition, then the value that coalition can generate is zero.
-Otherwise, it is simply the sum of the utilities of the two sides minus the cost of serving them.\footnote{
-    Entry fees paid to the platform do not matter, as they are within-coalition transfers, and thus do not affect the total value.
-}
-This value, as a function of the number of entrants, is
+If the platform is not a member of a coalition, then that coalition can generate no value.
+Otherwise, the value of the coalition is the sum of the utilities of the two sides minus the cost of serving them:\footnote{
+    Entry fees paid to the platform do not matter as they are within-coalition transfers, and thus do not affect the total value.
+}
 \begin{align*}
@@
 
-The share received by each type of player is then easily established using \Cref{prop:many_sided_weighted}.
+The share received by each type of player can then be established using \Cref{prop:many_sided_weighted}.
 \begin{proposition}
@@
 
-Total welfare $w(n_1, n_2)$ can be divided into four parts: utility generated by side $1$ and $2$, and the costs of serving side $1$ and $2$.
+Total welfare $w(n_1, n_2)$ can be divided into four parts: utility generated by sides $1$ and $2$, and the costs of serving sides $1$ and $2$.
 Each side's share of these parts is given by $S_i^{b_1}, S_i^{b_2}, S_i^{c_1}$ and $S_i^{c_2}$, respectively.
@@
     This is due to the characteristic function being a polynomial of the number of entrants.
-    Just like in \Cref{sec:power_function_example}, each constituent of the polynomial are divided in a constant proportion.
+    Just like in \Cref{sec:power_function_example}, each constituent of the polynomial is divided in a constant proportion.
 }
@@
 Finally, and perhaps most interestingly, the share of side $i$ from the value generated on side $j$ is also increasing in $\gamma_j$.
-This means that if players on side $i$ are less substitutable (or, equivalently, more complementary) in terms of contributing to the utility of the other side, then they will receive a larger share of the value generated there.
-
-These utilities are remarkably similar in structure to those obtained in the welfare maximizing case.
-The main difference is that each part (both costs and positive utilities) is reweighted, and side $i$ only receives a fraction of it.
+This means that if players on side $i$ are less substitutable (or, equivalently, more complementary) in terms of contributing to the utility of the other side, then they will receive a larger portion of the value generated there.
+
+These expressions for welfare are remarkably similar in structure to those obtained in the welfare maximizing case.
+The main difference is that each part (both costs and positive utilities) is reweighted, and either side only receives a fraction of it.
 It is also worth noting that $W_i^b(n_1, n_2) < W_i^*(n_1, n_2)$, and, as a consequence, entry is lower than what would be socially optimal.\footnote{
-    The easiest way to see it is that in the welfare-maximizing case the platform's profit is negative, while in the bargaining case it is positive.
+    The easiest way to see it is this in the welfare-maximizing case the platform's profit is negative, while in the bargaining case it must be non-negative.
     Therefore, fringe utilities must be lower in the latter case.
@@
 These similarities and differences are examined in more detail in the next subsection.
-
-For better comparison, let us also derive implied entry fees and utilities.\footnote{
+%TODO: check if it is true for both sides
+
+For making comparisons easier, let us also derive implied entry fees and utilities.\footnote{
     If one wished to close the model, the number of entrants in equilibrium could be obtained by solving the system of equations $n_i = \phi_i(u_i(n_1, n_2)), n \in \{1, 2\}$, just like in the other cases.
 }
-The latter is simply average welfare, i.e.:
+The latter is simply average welfare, i.e.
 \begin{align*}
@@
 \end{align*}
-Finally, the implied entry fees can be calculated from the equation $u_i = \alpha_i n_j^{\gamma_i} - p_i$, giving
-\begin{align*}
+Implied entry fees on the other hand can be calculated from the equation $u_i = \alpha_i n_j^{\gamma_i} - p_i$, giving
+\begin{align}
     p_i^b(n_1, n_2) &= \frac{\lambda_i}{\lambda_P + \lambda_i} F_i - \frac{\lambda_i \gamma_j}{\lambda_P + \lambda_j + \lambda_i\gamma_j} \alpha_j n_j n_i^{\gamma_j - 1} + \frac{\lambda_P + \lambda_j\gamma_i}{\lambda_P + \lambda_i + \lambda_j\gamma_i} \alpha_i n_j^{\gamma_i}.
-\end{align*}
+\label{eq:bargaining_entry_fees}
+\end{align}
 
@@
 
-Let us now compare the outcomes of the three cases described in the previous subsections.
-To highlight the similarity to \textcite{armstrong2006competition}, I will first consider the case of linear network effects.
+Let us now compare the outcomes of the three cases described in the previous sections.
+To highlight the similarity to \textcite{armstrong2006competition}, I first consider the case of linear network effects.
 Furthermore, for simplicity of exposition, I start by examining the non-weighted Shapley value before moving on to the weighted value.
 
-Assume that network effects are linear, i.e. $\gamma_i = 1$ for $i \in \{1, 2\}$.
-Also, focus on non-weighted Shapley values ($\lambda_P = \lambda_1 = \lambda_2 = 1$).
-From the previous results, the entry fees for side $i$ are
+Therefore, first assume that network effects are linear, i.e. $\gamma_i = 1$ for $i \in \{1, 2\}$ and that all players have equal weights ($\lambda_P = \lambda_1 = \lambda_2 = 1$).
+From \Cref{eq:welfare_max_entry_fees,eq:unilateral_entry_fees,eq:bargaining_entry_fees}, the entry fees for side $i$ are
 \begin{align*}
@@
 
-All of these expressions bear some similarities to each other in that the price is somehow related to the externalities that an entrant imposes on the other players.
+All of these expressions bear some similarities to each other in that the price is related to the externalities that an entrant imposes on the other players.
 In fact, the welfare-maximizing price is just that: the cost of serving one additional player (1) and the positive externality imposed on the other side (2).
-The unilateral pricing case also includes these two factors in full, but also adds a third factor, related to the elasticity of entry (3).
+The unilateral pricing case also includes these two factors in, as well as a third factor, which related to the elasticity of entry (3).
 Namely, the platform extracts some of the surplus generated by the entrants, and the surplus it wants to extract depends on the elasticity of entry, $\phi'_i(u_i)$.
@@
 
-The bargaining case also includes the first two factors, albeit they are somewhat different.
-As opposed to the first two cases, the price only contains some fraction of the externalities, while the rest is shared with the platform and the other side.\footnote{
+The bargaining case also includes factors (1) and (2), albeit they appear somewhat differently.
+As opposed to the first two cases, the price only contains some fraction of these externalities, with the rest being shared with the platform and the other side.\footnote{
     Due to the linearity of the model and the symmetry of the Shapley value, each part of the value is shared equally between players who participate in producing them.
-    This is the reason why, for example, the platform and the firms share the cost of serving the entrants (1) equally, or why all three types of players share the value generated on a given side (2) equally.
-}
-Furthermore, some part of the welfare generated on side $i$ is also shared with the other players, and thus appears in the price (4).
-This is in contrast to both the welfare-maximizing and unilateral pricing cases, where the entry fee did not depend on the actual utility that was materialized on the given side.
+    This is the reason why, for example, the platform and the firms share the cost of serving the entrants (1) equally, and why all three types of players share the value generated on a given side (2) equally.
+}
+Furthermore, a part of the welfare generated on side $i$ (4) is also shared with the other players, and thus appears in the price.
+This is in contrast to both the welfare-maximizing and unilateral pricing cases, where the entry fee for a given side does not depend on the actual utility that was materialized on that side.
 Therefore, bargaining introduces some interesting departures from both the welfare-maximizing and unilateral pricing cases.
 
-Now let us consider non-linear network effects.
+Now let us consider more general, non-linear network effects.
 The welfare-maximizing, unilateral pricing and bargaining entry fees are as follows:
@@
 In fact, in the welfare-maximizing and unilateral pricing cases, nothing changes apart from the marginal externality imposed on the other side (2) being slightly different.
-On the other hand, there is one important difference in the bargaining case.
-In the linear case, the terms related to the value generated on each side were shared between the players in a constant proportion, independent of the model parameters.
-In this non-linear case, however, these shares depend on the shape of the network effects.
-In particular, when side $i$'s network externality on side $j$ is more convex (e.g. firms on side $i$ are less substitutable), then it receives a larger share of the value generated on the other side.
-This is signified by the fact that the coefficient of side $i$'s network externality, $\frac{\gamma_j}{2 + \gamma_j}$, is increasing in $\gamma_j$.
-This result demonstrates that bargaining outcomes are not just a split of the value, but also take into account the shape of the network effects.
+On the contrary, there is an important difference in the bargaining case.
+Under linear network effects, the terms related to the value generated on each side were shared between the players in a constant proportion, independent of the model parameters.
+In this non-linear case, however, these shares do depend on the shape of the network effects.
+In particular, when side $i$'s network externality on side $j$ is more convex, the former receives a larger share of the value generated on the other side.\footnote{
+    The corresponding coefficient, $\frac{\gamma_j}{2 + \gamma_j}$, is increasing in $\gamma_j$.
+}
+This demonstrates that bargaining outcomes are not just a fixed split of the value, but also take into account the shape of the network effects.
 
@@
 
-In the case of the cost of serving one additional player (1), the addition of bargaining weights simply leads to players sharing the cost in a constant proportion, according to their weights.\footnote{
+For the cost of serving the players (1), the addition of bargaining weights simply leads to players sharing that cost in a constant proportion, according to their weights.\footnote{
     This is because this term is linear in the number of entrants.
@@
 The higher the weight, the larger the share for any given player.
-While the latter observation is true for non-linear terms, as well, the influence of the weights is more complex for those.
+While the latter observation is true for non-linear terms, as well, the influence of the weights is more complex in their case.
 Namely, it also depends on the shape of value function.
 For example, in term (2), $\lambda_i$ interacts with the parameter determining the shape of the network effects, $\gamma_j$
-Therefore, the weighted value is more than just a simple reweighting of the non-weighted value, and its effects can be quite complex depending on the assumptions on the value function.
-
-Whether bargaining leads to a higher or lower total welfare depends on the parameters of the model.
-For example, if $\lambda_P$ is very high, then $p_i^b > p_i^u > p_i^*$, leading to fewer firms entering and lower total surplus not only than the welfare-maximizing case, but also than the unilateral pricing case.
-That is, it can happen that everybody looses from bargaining.\footnote{
+Therefore, the weighted value is more than just a simple reweighting of the non-weighted value, and its effects can be quite complex depending on the shape of the value function.
+
+Whether bargaining leads to a higher or lower total welfare in comparison to unilateral price setting depends on the parameters of the model.
+For example, if $\lambda_P$ is high enough, then $p_i^b > p_i^u > p_i^*$, leading to fewer firms entering and lower total surplus not only than the welfare-maximizing case, but also than the unilateral pricing case.
+In other words, it can happen that everybody looses from bargaining.\footnote{
     In such a case, the platform would like to set lower entry fees than what it can achieve via bargaining.
-    While in some settings it makes sense to assume that it can do that, in others, commitment issues might prevent it from doing so.
-}
-On the other hand, if $\lambda_P$ is sufficiently low, then one can find weights $\lambda_1, \lambda_2$, such that $p_i^u > p_i^b > p_i^*$.
-In such a case, the platform would like to set higher entry fees than what it can achieve via bargaining for both sides.
-Furthermore, the total welfare under bargaining is between the welfare-maximizing and unilateral pricing cases.
+    This might be a realistic constraint in settings with commitment issues.
+}
+On the other hand, if $\lambda_P$ is sufficiently low, then one can always find weights $\lambda_1, \lambda_2$, such that $p_i^u > p_i^b > p_i^*$.
+In such a case, the platform would like to set higher entry fees than what it can achieve via bargaining for both sides of the market.
+As a consequence, the total welfare under bargaining is between the welfare-maximizing and unilateral pricing cases.
 Therefore, whether bargaining leads to higher or lower welfare than unilateral pricing depends on model parameters.
-The platform, however, always achieves a (weakly) lower profit than if it could set the entry fees unilaterally.
+The platform, however, always achieves a (weakly) lower profit than if it could chose the entry fees itself.
 
@@
 Therefore, while bargaining can be welfare-improving compared to unilateral price setting, it can not achieve the highest possible total utility.\footnote{
-    One could argue that the welfare maximizing case is not a realistic benchmark anyway, as it assumes that the platform is making a loss.
+    One could argue that the welfare maximizing case is not a realistic benchmark anyway, as the platform is operating at a loss.
 }
@@
 Similarly, the value generated on each side also factors into the entry fee, contrary to the benchmark cases where it does not directly matter.
-This suggests, in situations where bargaining between players is plausible, certain effects might be overrepresented or missed if one assumes unilateral price-setting.
+This suggests, in situations where bargaining between players is plausible, certain effects might be overrepresented or missed if one assumes unilateral price setting.
 

### 2024-08-18 src/paper/application.tex
Do todos

@@
 This section introduces the model used throughout the paper.
-% TODO: better motivation
 I use the terms ``platform'' and ``fringe sellers'', and present my ideas in the context of an intermediated market, such as an online marketplace or an application store.
@@
 I do this for a number of reasons.
-For one, it simplifies the analysis without affecting the main results qualitatively.  % TODO: refer to results if I can
+For one, it simplifies the analysis without affecting the main results qualitatively.
 More importantly, it lets me focus on the main question of this paper: how the platform's hybrid operation affects the bargaining power.
@@
 
-Assume that $N_P$ is still fixed, but at time 0, the platform can decide whether to exclude the fringe.
-As the next proposition shows, the platform never has an incentive to do so, if otherwise the equilibrium is in the hybrid regime.
+Assume that $N_P$ is still fixed, but now at time 0, the platform can decide whether to exclude the fringe.
+As the next proposition shows, the platform never has an incentive to do so.\footnote{
+    Note, that it is possible that the optimal or negotiated entry fee is such that zero fringe firms enter the market.
+    This proposition's main statements is about the platform's decision to exclude the fringe, when the entry fee would be such that the fringe would enter.
+}
 \begin{proposition}
@@
 Similarly to the fringe, assume that it faces an investment cost of $I_P$ per product.
+\Cref{fig:optimal_n_p} illustrates the platform's final profits as a function of its product variety.
+
 As before, things are straightforward in the benchmark model: the platform invests in own products only if $\frac{V_P}{I_P} \geq \frac{V_F}{I_F}$.
@@
 A consequence of this proposition is that, apart from the knife-edge case of $\frac{V_P}{I_P} = \frac{V_F}{I_F}$, the platform never finds it optimal to operate in hybrid mode: it either creates so many products that it excludes the fringe, or it creates none at all.
-\Cref{fig:optimal_n_p_benchmark} illustrates this result.
+\Cref{fig:optimal_n_p_benchmark} displays this result: for low values of $I_P$, the equilibrium is a corner solution with $N_P = 0$, and for high values, the maximum is reached in the pure retail regime.
 
@@
     \label{prop:comparative_n_p_bargaining}
-    In the bargaining model, the dependence of the platform's profits on its number of products depends on what the implied entry fee is compared to the optimal entry fee:
+    In the bargaining model, the dependence of the platform's profits on its number of products is conditional on whether, for a given $N_P$,  the implied entry fee is higher or lower than the optimal entry fee:
     \begin{align*}
@@
 Furthermore, and even more strikingly, the platform may find it optimal to invest in its own products even if it has a product disadvantage, if it helps it to negotiate a more optimal entry fee.
-\Cref{fig:optimal_n_p_bargaining} displays such an example.
+\Cref{fig:optimal_n_p_bargaining} showcases such an example.
+When the platform has a not too large product disadvantage ($I_P = 0.55$ case), the maximum of its profits is reached in the hybrid regime.
+This is doubly unfortunate from a welfare perspective: not only does the platform make an investment that the fringe could have made more efficiently, but it also decreases consumer welfare by reducing the total product variety.
 
@@
 It is however important that the demand function is such that total profits are increasing in the number of fringe firms.
-Without this, the corresponding cooperative game is not monotone, and the bargaining microfoundations do not apply.
-%TODO: more on this assumption
+Without this, the corresponding cooperative game is not monotone, and the bargaining interpretation is less applicable.
+In the model presented in the main text, monotonicity arises due to consumers' taste for variety preferences.
+This assumption might also be justified in settingswith network effects \parencite{rochet2003platform}, or when the platform can extract consumer surplus through entry fees or some other mechanism.\footnote{
+    \textcite{chen2008price} demonstrates that under certain circumstances an even more extreme phenomenon might occur: competition may not only increase industry-wide profits, but prices, as well.
+}
 
@@
 Such profit functions arise in settings in which the profit reduction from increased competition is dominated by extra sales due to increased product variety.
-One such example is \textcite{anderson2020aggregative}, where the demand exhibits love for variety, while consumers have access to an outside option.
-Alternatively, indirect network effects, such as those in two-sided markets, can also result in such increasing profits.
-\textcite{chen2008price} demonstrates that under certain circumstances an even more extreme phenomenon might occur: competition may not only increase industry-wide profits, but prices, as well.
-Finally, under the assumption that the platform can extract consumer surplus through entry fees or some similar mechanism, this assumption is be true for any demand system in which total surplus is increasing in product variety.
+\Cref{sec:results_discussion} discusses this assumption in more detail.
 

### 2024-08-18 src/paper/theory.tex
Do todos

@@
 In particular, I provide results for weighted values in the case of heterogeneous fringe players, which is a novel contribution to the literature.
-Furthermore, I highlight how the value of the fringe players can be expressed in terms of their marginal contributions, i.e. the partial derivatives of the value function.
+Furthermore, I highlight how the value of the fringe players can be expressed in terms of their marginal contributions, i.e. the partial derivatives of the production function.
 
@@
 I start with the case of one, indispensable big player, and relax this assumption in \Cref{sec:extensions}.
+Such a game can represent, for example, a (one-sided) platform and a number of potential entrants, where the entrants can only reach their prospective consumers through the platform, or a vertical supply chain with one upstream producer and a number of downstream sellers.
 Let us start by defining the cooperative game that describes this situation.
@@
 \end{align*}
-Such a game can represent, for example, a (one-sided) platform and a number of potential entrants, where the entrants can only reach their prospective consumers through the platform, or a vertical supply chain with one upstream producer and a number of downstream sellers.
+The function $f$ (henecforth also referred to as the production function) then characterizes this game, and determines the distribution of the value between the big player and the fringe.
 
@@
 
-% TODO: explain relation to marginal contribution
+This result has an immediate interpretation in terms of marginal contributions.
+Remember, that player $P$ is indispensable for creating value.
+Therefore, for any coalition of fringe players, the marginal contribution of player $P$ is the total value that the coalition can generate $P$ included.
+Player $P$'s then is its average marginal contribution, which boils down to the expected value that a coalition can generate conditional on player $P$ being in it.
 
@@
 Alternatively, as the second part of the corollary demonstrates, it is also related to the marginal contributions of the fringe agents.
-The only difference from the big player's value is that we have to multiply these marginal contributions by the probability of the big player appearing before the fringe firm in question, as otherwise they would be zero.
-The latter interpretation is particularly useful when thinking about the value of the fringe in the setting with heterogeneous fringe firms.
+This marginal contribution is the derivative of the production function with respect to the mass of fringe players (i.e., the effect of adding an infinitesimally small player to the coalition), multiplied by the probability of the central player appearing before the fringe player (otherwise the marginal contribution is zero, as the central player is indispensable).
+The second interpretation is particularly useful when thinking about the value of the fringe in the setting with heterogeneous fringe firms.
 
@@
 
-% TODO: relation to substitutability
-% In contrast, when fringe players are more complementary to each other, the big player can only obtain a smaller share, as its bargaining power is more limited.
+In certain settings, this can also be interpreted as the degree of complementarity or substitutability between the fringe players.
+For example, imagine that the fringe consists of a set of firms producing one product each, and the central player is necessary for this product to be sold or created.\footnote{
+    For example, the central player could be a platform that connects the fringe firms with consumers, or a provider of a key input.
+}
+When the fringe firms are substitutes, then additional ones add less value to the total pie.
+Therefore, relatively few of them are needed to create most of the value, and the central player can appropriate a larger share.
+Conversely, when the fringe firms are complements, the fringe firms are in a better bargaining position, and can obtain a larger share of the total value.
 
@@
         \caption{Fringe players have lower bargaining power}
+        \label{fig:one_sided_substitute}
     \end{subfigure}
@@
         \caption{Fringe players have higher bargaining power}
+        \label{fig:one_sided_complement}
     \end{subfigure}
@@
 
-The weights can be thought of as the measure of some innate bargaining power, not reflected in the value function.\footnote{
+The weights can be thought of as the measure of some innate bargaining power, not reflected in the production function.\footnote{
     Although, this interpretation is not always appropriate.
@@
 
-As before, the value of the big player can be expressed as an integral of the value function, while the value of the fringe can be expressed as an integral of the marginal contributions of the fringe players.
+As before, the value of the big player can be expressed as an integral of the production function, while the value of the fringe can be expressed as an integral of the marginal contributions of the fringe players.
 The only difference is that, as in the case of the general random order value, the integrands are weighted by a specific probability distribution.
@@
 In the second case, there is a single big player, but the fringe is able to generate some value on its own.
-In both cases, the value function is still a random order value, and thus results from the main text can be applied. % TODO: elaborate on this
+In both cases, the player's shares are still random order values\footnote{
+    The case of multiple big players is equivalent to the case of a single big player with the same production function, but a different probability distribution over the permutations.
+    Conversely, in the setting when the fringe can generate some value on its own, the production function changes, but the probability distribution is the same.
+}, and thus many of the earlier results apply.
 
@@
 \begin{lemma}
-    % TODO: check notation!
     \label{lem:many_sided_manifold}
@@
     \begin{align*}
-        \varphi_{A^l}^\infty & = \int_0^1 t^{\lambda_P} \lambda_l t^{\lambda_l - 1} \partial_l f(t^{\lambda_1}, \dots, t^{\_L}) \dt.
+        \varphi_{A^l}^\infty & = \int_0^1 t^{\lambda_P} \lambda_l t^{\lambda_l - 1} \partial_l f(t^{\lambda_1}, \dots, t^{\lambda_L}) \dt.
     \end{align*}
@@
 The main difference is that each part (both costs and positive utilities) is reweighted, and either side only receives a fraction of it.
-It is also worth noting that $W_i^b(n_1, n_2) < W_i^*(n_1, n_2)$, and, as a consequence, entry is lower than what would be socially optimal.\footnote{
-    The easiest way to see it is this in the welfare-maximizing case the platform's profit is negative, while in the bargaining case it must be non-negative.
-    Therefore, fringe utilities must be lower in the latter case.
-}
-These similarities and differences are examined in more detail in the next subsection.
-%TODO: check if it is true for both sides
+These similarities and differences are examined in more detail in \Cref{sec:application_comparison}.
 
@@
 \subsection{Comparison}
+\label{sec:application_comparison}
 
@@
 While the latter observation is true for non-linear terms, as well, the influence of the weights is more complex in their case.
-Namely, it also depends on the shape of value function.
+Namely, it also depends on the shape of function.
 For example, in term (2), $\lambda_i$ interacts with the parameter determining the shape of the network effects, $\gamma_j$
-Therefore, the weighted value is more than just a simple reweighting of the non-weighted value, and its effects can be quite complex depending on the shape of the value function.
+Therefore, the weighted value is more than just a simple reweighting of the non-weighted value, and its effects can be quite complex depending on the shape of the total welfare function.
 
@@
 
-Finally, it is always true that $p_1^b < p_1^*$ or $p_2^b < p_2^*$.
+Finally, it is always true that $p_1^b > p_1^*$ or $p_2^b > p_2^*$.
 The reason is that the platform's profit is always non-negative in the bargaining case, while it is negative in the welfare-maximizing case.
@@
 Random order values offer a comprehensive framework for modeling bargaining outcomes, and also include important and well-known special cases, such as the Shapley value or the weighted value.
-Due to the former retaining many of the attractive properties of its more specialized counterparts, it might be a good candidate for modeling bargaining outcomes flexibly and in a tractable manner.
-This also applies to weighted value in the case of multiple types of fringe players, providing a rather flexible model (one more general than the Shapley value) for modeling multi-sided markets.
+Due to the random order values retaining many of the attractive properties of their more specialized counterparts, they are a good candidate for modeling bargaining outcomes flexibly and in a tractable manner.
+This also applies to the weighted value in the case of multiple types of fringe players, which provides a rather flexible model for multi-sided markets.
 Furthermore, as shown in \Cref{sec:extensions}, the results can also be generalized to cases with not completely indispensable big players, while retaining the essential structure of the results.
 
-Finally, I demonstrate how the proposed framework can be applied in practice by
-examining the two-sided platform model based on \textcite{armstrong2006competition}.
+Finally, I demonstrate how the proposed framework can be applied in practice by embedding it in a model of two-sided platforms based on \textcite{armstrong2006competition}.
 I show that the resulting entry fees have some similarities to the welfare-maximizing and unilateral price setting benchmarks, but also differ in some important ways.
-In particular, the externalities that players entrants impose on the platform (cost of serving) and the other side (network externalities) are not fully incorporated into the entry fees, but shared across the affected players.
-Similarly, the value generated on each side also factors into the entry fee, contrary to the benchmark cases where it does not directly matter.
-This suggests, in situations where bargaining between players is plausible, certain effects might be overrepresented or missed if one assumes unilateral price setting.
-
-There are a variety of ways in which this paper could be expanded or built upon.
-One obvious direction is to consider other solution concepts from cooperative game theory, such as the nuclelous\footnote{
+In particular, the externalities that players entrants impose on the platform (cost of serving entrants) and the other side (network externalities) are not fully incorporated into the entry fees, but are instead shared across the affected players.
+Similarly, contrary to the benchmark cases, the value generated on each side also factors into the entry fee for that side.
+This suggests that, in situations where bargaining between players is plausible, certain effects might be over- or underrepresented if one assumes unilateral price setting.
+
+There are a variety of ways in which this paper can be expanded or built upon.
+One possible direction is to consider other solution concepts from cooperative game theory, such as the nuclelous\footnote{
     It retains many of the desirable properties of the weighted values, such as existence and uniquenes while having a more immediate connection to non-cooperative bargaining theory.
 }.
-Another is to generalize these results to a wider class of games.
-An example of this would be the value of the coalition increasing also in the number of central players in the coalition.
-A further direction is to consider is building non-cooperative microfoundations for the proposed random-order-value-based bargaining outcomes.
+Another option is to generalize these results to a wider class of games.
+An example of this would be the assuming that the value of a coalition is increasing in the number of central players, thereby relaxing the assumption that they are complete substitutes of each other.
+A further direction is building non-cooperative microfoundations for the proposed random-order-value-based bargaining outcomes.
 Many such results exist for the Shapley value, and there are some for the the weighted value, but motivating the more general random order value in a similar manner could be a significant step towards achieving the goal of the Nash program.
@@
 The practical applications are no less interesting.
-The proposed profit sharing framework could be embedded in more applied and detailed models describing various settings.
-The example application in this paper is a streamlined example of this, while \textcite{stancsics2023hybrid} is a further step in this direction, applying these ideas to a model of hybrid platforms.
+The proposed profit sharing framework could be embedded in more applied and detailed models describing various economically relevant settings.
+The example application in this paper is a streamlined attempt of this, while \textcite{stancsics2023hybrid}, which apply these ideas to a model of hybrid platforms, is a further step in this direction.
 Due to the simplicity of the results, this approach might be a viable, almost drop-in replacement for unilateral price setting in cases where one does not wish to ascribe all the bargaining power to one player.
@@
 
-I approach this problem by breaking it down into two parts: the bargaining over the idisyncratic and non-idiosyncratic parts of the value generated.
+I approach this problem by breaking it down into two parts: bargaining over the idisyncratic and non-idiosyncratic parts of the value generated.
 Due to the linearity property of the Shapley value, the bargaining outcomes over the whole value are simply the sum of the bargaining outcomes over these two parts.
-Furthermore, the non-idiosyncratic part is simply the value function from the main text, and thus the resulting weighted values are the same as before.
+Furthermore, the non-idiosyncratic part is the same as in the main text, and thus the weighted values arising from it are also identical.
 
@@
     Similarly, the value of side $i \in \{1, 2\}$ is
-    % TODO: improve formalism in the first line of formula below?
-    \begin{align*}
-        W_i &= \int_0^1 t^{\lambda_P} \lambda_i t^{\lambda_i - 1} \partial_i w(t^{\lambda_1} n_1, t^{\lambda_2} n_2) \dt \\
+    \begin{align*}
+        W_i &= \int_0^1 t^{\lambda_P} \lambda_i t^{\lambda_i - 1} \partial_i n_i w(t^{\lambda_1} n_1, t^{\lambda_2} n_2) \dt \\
         &= \int_0^1 t^{\lambda_P} \lambda_i t^{\lambda_i - 1} \left[ \alpha_i n_i t^{\lambda_j \gamma_i} n_j^{\gamma_i} + \alpha_j \lambda_i \gamma_j t^{\lambda_j} n_j t^{\lambda_i (\gamma_j - 1)} n_i^{\gamma_j} - n_i F_i \right] \dt \\

### 2024-08-18 src/paper/theory.tex
Theoremize propositions and vice versa

@@
 
-\begin{proposition}
+\begin{theorem}
     \label{prop:one_sided_general}
@@
     with the last equality holding if $X$ is a continuous random variable.
-\end{proposition}
+\end{theorem}
 
@@
 The following proposition provides an expression for the limit of this total value.
-\begin{proposition}
+\begin{theorem}
     \label{prop:multiple_platforms_total}
@@
     \label{cor:multiple_platforms}
-    The per-unit Shapley-value of the fringe is
+    The per-unit value of the fringe is
     \begin{align*}
@@
 
-\begin{proposition}
+\begin{theorem}
     \label{prop:one_sided_non_indispensable}
@@
 Let us establish the analog of \Cref{prop:one_sided_general} for the case of heterogeneous fringe to obtain the limit of the value of the big player.
-\begin{proposition}
+\begin{theorem}
     \label{prop:many_sided_general}
@@
     with the last equality holding if $X$ is a continuous random variable.
-\end{proposition}
+\end{theorem}
 The proposition above is almost identical to \Cref{prop:one_sided_general}, with the only difference being that the integral is now over the $L$-dimensional unit hypercube, due to $f$ being a function of $L$ variables.
@@
 In fact, many of the propositions with one indispensable player can be considered as special cases of it.
-\begin{theorem}
+\begin{proposition}
     \label{prop:many_sided_weighted}
@@
     \end{align*}
-\end{theorem}
+\end{proposition}
 The intuition for this is the following.

### 2024-08-19 src/paper/application.tex
Fix reference
Rename motivation to introduction
Grammarly intro

@@
 
-\section{Motivation}
-
-Although market structures resembling various aspects of what we call platforms have existed for some time, the term has only gained widespread usage in the 2000s, with the advent of digitization, and a number of behemoth technology companies playing matchmakers on the internet.
-Since then, platforms have become a buzzword in the business world, the subject of increasing regulatory scrutiny, and also a topic of intense academic interest.
-Platforms have a number of unique features that make them different from more traditional market structures.
+\section{Introduction}
+
+Although market structures resembling various aspects of what we call platforms have existed for some time, the term gained widespread usage only in the 2000s, with the advent of digitization and a number of behemoth technology companies playing matchmakers on the Internet.
+Since then, the concept of a platform has become prominent in the business world, drawn increasing regulatory attention, and become a topic of intense academic interest.
+Platforms have several unique features that differentiate them from more traditional market structures.
 The most prominent of those are multi-sidedness and network effects, which most of the early literature \parencite[for an overview, see][]{rochet2006two} and policy debate \parencite[e.g.][]{fletcher2021consumer,calvano2021market} has focused on.
-However, in the more recent years, another important and potentially concerning aspect has been getting more attention: the hybrid operation of certain platforms.
-Essentially, this means that platforms act as an intermediary (deciding the rules) and a market participant (competing with other entrants) at the same time.
-
-While hybrid platforms are not a completely new phenomenon, they are becoming more and more common in various industries.
-Perhaps the most prominent example is Amazon, which, on the one hand sells its own products, and at the same time hosts ax large number of third-party sellers.
+However, in recent years, another important and potentially concerning aspect has been getting more attention: the hybrid operation of certain platforms.
+Such platforms act as intermediaries (deciding the rules) and market participants (competing with other entrants) at the same time.
+
+While hybrid platforms are not an entirely new phenomenon, they are becoming increasingly common in various industries.
+Perhaps the most prominent example is Amazon, which sells its own products while simultaneously hosting a large number of third-party sellers.
 However, examples abound in other industries, as well.
-For example, each of the largest digital distribution platforms for computer and smartphone applications (Google Play, Apple App Store and Microsoft Store) sell their own applications besides their third party offerings.
-In the video game industry, platform owners studios and publishing games under their own brand is the standard.
+For example, each of the largest digital distribution platforms for computer and smartphone applications (Google Play, Apple App Store, and Microsoft Store) sells its own applications in addition to third-party offerings.
+In the video game industry, platforms owning studios and publishing games under their own brand is the standard.
 Many video streaming services (e.g. Netflix, Amazon Prime Video, Hulu) offer a mix of their own and licensed content.
-One can also find examples of similar behavior outside the platform setting, too.
-For example, a number of car manufacturers are planning to sell directly to consumers in addition to selling through their dealership networks.
-
-As deciding the rules of the game and competing in it at the same time gives rise to some obvious concerns, policymakers have been paying increasingly close attention to these platforms in the recent years.
-Various pieces of legislation have been proposed to regulate, or even ban e-commerce platforms from selling their own products \parencite[][]{phartiyal_2019,reynolds_2022,eu-2022}.
-Furthermore, one of the most prominent recent antitrust cases, Microsoft acquiring the video game publisher Activision/Blizzard for a sum of 69 billion USD, is also a case of a platform becoming increasingly hybrid.
-This merger not only increased market concentration on the software side of the video game industry, but might also have further implications for the competition between Microsoft as a platform owner and the other game developers.
+One can find examples of similar behavior outside the platform setting, too.
+For example, several car manufacturers are planning to sell directly to consumers in addition to selling through their dealership networks.
+
+As deciding the rules of the game and competing in it at the same time gives rise to some obvious concerns, policymakers have been paying increasingly close attention to these platforms in recent years.
+Various pieces of legislation have been proposed to regulate or even ban e-commerce platforms from selling their own products \parencite[][]{phartiyal_2019,reynolds_2022,eu-2022}.
+Furthermore, one of the most prominent recent antitrust cases, Microsoft acquiring the video game publisher Activision/Blizzard for 69 billion USD, is also a case of a platform becoming increasingly hybrid.
+This merger not only increased market concentration on the publishing side of the video game industry, but also had implications for the competition between Microsoft as a platform owner and the other game publishers.
 The deal was under investigation by multiple antitrust authorities, including the US Federal Trade Commission, the European Commission, and the UK Competition and Markets Authority \parencite{livni_merced_2023}.
 
-In parallel to the increasing regulatory interest, the academic literature on the topic of hybrid platforms has also been steadily growing.
-\textcite{hagiu2022should} investigate how practices, such as self-preferencing and steering can distort competition on hybrid platforms.
-They argue that -- while such practices are problematic and can have negative welfare effects -- with proper regulation the platform selling its own products can be beneficial for consumers.
-In contrast to this positive result, \textcite[]{anderson2021hybrid} find that even in the absence of such behavior, allowing hybrid operation might have negative consequences due to platforms having an incentive to exclude competitors from the market.
-\textcite[]{gutierrez2021welfare} shows that general conclusions are hard to draw, and welfare effects are platform and product specific.
-For example, using a mechanism design approach, \textcite{kang2022contracting} demonstrate that welfare consequences greatly depend on whether the platform faces competition in the upstream market.
-
-This paper aims to contribute to this discussion by examining an important, but so far underexplored aspect of platforms: the bargaining power disparity between them and the other market participants, and how this disparity is affected by the platforms' hybrid operation.
-I propose an analytically tractable model of a which captures many important aspects of bargaining between one large and a continuum of small players: namely a hybrid platform facing a continuum of potential entrants.
-I show that, in the presence of bargaining, hybrid operation can indeed have negative welfare consequences for consumers.
+Parallel to the increasing regulatory interest, the academic literature on hybrid platforms has also been steadily growing.
+\textcite{hagiu2022should} investigate how practices, such as self-preferencing and steering, can distort competition on hybrid platforms.
+They argue that, while such practices are problematic and can have negative welfare effects, with proper regulation the platform selling its own products can be beneficial for consumers.
+In contrast to this positive result, \textcite[]{anderson2021hybrid} find that even in the absence of such behavior, allowing hybrid operation might have negative consequences due to platforms' incentive to exclude competitors from the market.
+\textcite[]{gutierrez2021welfare} shows that general conclusions are hard to draw, and welfare effects are platform and product-specific.
+For example, using a mechanism design approach, \textcite{kang2022contracting} demonstrates that welfare consequences greatly depend on whether the platform faces competition in the upstream market.
+
+This paper aims to contribute to this discussion by examining an important but underexplored aspect of platforms: the bargaining power disparity between the latter and the other market participants, and how this disparity is affected by the platforms' hybrid operation.
+I propose an analytically tractable that captures many important aspects of bargaining between one large and a continuum of small players: namely, a hybrid platform facing a continuum of potential entrants.
+I show that hybrid operation can indeed have negative welfare consequences for consumers in the presence of bargaining.
 This result is particularly striking in this otherwise distortion-free\footnote{
-    In the benchmark model without bargaining, the platform's hybrid operation does not affect consumer welfare.
+    The platform's hybrid operation does not affect consumer welfare in the benchmark model without bargaining.
 } setting. 
 The intuition is that hybrid operation increases the platform's bargaining power against the entrant sellers.
-This in turn leads to a higher entry fee, fewer entrants, then results in lower consumer surplus.
-These observations constitute a so-far overlooked aspect of hybrid platforms that policymakers should be aware of.
-Due to the relative generality of this model, these results are applicable not only to hybrid platform, but to other similar settings, such as upstream producers having their own downstream outlets, or retailers with private labels, as well.
-
-Many of the results are not tied to the specifics of the model, but are more general instead.
-They do not depend on a specific demand structure and investment cost assumptions, and there is even some flexibility to the assumptions about bargaining outcomes.
-I show that, even in such stylized setting, some interesting observations can be made about the effects of hybrid operation. 
+This, in turn, leads to a higher entry fee and fewer entrants, resulting in lower consumer surplus.
+These observations constitute a so far overlooked aspect of hybrid platforms that policymakers should be aware of.
+Due to this model's generality, these results are applicable not only to hybrid platforms, but also to many other settings, such as upstream producers having their own downstream outlets or retailers with private labels.
+
+Many of the results are not tied to the specifics of the model but are more general.
+They do not depend on a specific demand structure, and there is even some flexibility with regard to the assumptions about bargaining outcomes.
+I show that, even in such a stylized setting, some interesting observations can be made about the effects of the hybrid operation. 
 In particular, when the platform's and the potential entrants' products are substitutes, increasing the platform's product variety will lead to a decrease in the number of entrants.
-I also give sufficient conditions for this decrease in entry being so large as to cause a decrease in total profits, as well.
+I also give sufficient conditions for this decrease in entry being so large as to cause a decrease in total profits.
 
 The closest model to the one proposed in this paper is \textcite{anderson2021hybrid}.
-The key difference between the two boils down to how the entry fee is decided.
-In \textcite{anderson2021hybrid}, the platform sets a percentage entry fee, and the entrants decide whether to enter or not.
+The key difference between the two boils down to how the entry fee is determined.
+In \textcite{anderson2021hybrid}, the platform sets a percentage entry fee, and the entrants decide whether or not to enter.
 In contrast to this, I assume that (1) platforms charge a lump-sum entry fee and that (2) this entry fee is the result of a negotiation process\footnote{
-    The bargaining process is modeled using a solution concept from cooperative game theory, namely the Shapley-value.
-    This allows for a tractable analysis while at the same time capturing many of the important features of bargaining.
+    The bargaining process is modeled using a solution concept from cooperative game theory, namely the Shapley value.
+    This allows for a tractable analysis while at the same time capturing many of the essential features of bargaining.
     Examples of this approach in the industrial organization literature include \textcite{montez2007downstream}, as well as \textcite{hart1990property}, \textcite{levy1997individual}, \textcite{inderst2003bargaining} and \textcite{brugemann2019intra} among others.
@@
 
-The set of more general results in this paper go beyond the aforementioned studies in the sense that they illuminate the effects of hybridness as a more abstract phenomenon, and thus also highlight the similarities between the hybrid platform literature and adjacent ones.
-Certain structures, such as vertical relationships, or even traditional retail stores share a number of features with platforms (notably, the presence of a dominant, indispensable entity), and can be modeled in much the same way.
+The set of more general results in this paper goes beyond the aforementioned studies in the sense that they illuminate the effects of hybrid operation as a more abstract phenomenon, and thus also highlight the similarities between the hybrid platform literature and adjacent ones.
+Certain structures, such as vertical relationships or even traditional retail stores, share several features with platforms (notably, the presence of a dominant, indispensable entity) and can be modeled in much the same way.
 Therefore, the methodology and results in this paper are also of interest to researchers studying questions such as retailers having their own private labels \parencite{steiner2004nature} or vertical integration in upstream-downstream markets \parencite{hart1990vertical,aghion2006vertical}.
-\textcite{de2005vertical} and \textcite{montez2007downstream}, in which bargaining between the upstream and downstream firms take the center stage, are particularly closely related.
+\textcite{de2005vertical} and \textcite{montez2007downstream}, in which bargaining between the upstream and downstream firms take center stage, are particularly closely related.
 Among empirical studies in related settings, \textcite{ho2017insurer} looks at the effect of insurer competition on health care prices, while \textcite{crawford2018welfare} explores the effects of vertical integration on television markets.
@@
 
-Finally, this paper also belongs to the not too large set of models using concepts from cooperative game theory in an industrial organization setting.
+Finally, this paper also belongs to the relatively small set of models that use concepts from cooperative game theory in an industrial organization setting.
 Such examples include the aforementioned \textcite{montez2007downstream}, as well as \textcite{hart1990property}, \textcite{levy1997individual}, \textcite{inderst2003bargaining} and \textcite{brugemann2019intra}, among others.
-In contrast to the majority of those, which focus on games with a finite number of players, I utilize an oceanic game (a continuum of small players instead of a finite number), and demonstrate that this can considerably simplify the analysis in certain cases.
-Therefore, the modeling approach presented in this paper may be of use in other settings as well.
+In contrast to the majority of those, which focus on games with a finite number of players, I utilize an oceanic game (a continuum of small players instead of a finite number), demonstrating that this can considerably simplify the analysis in certain cases.
+Therefore, the modeling approach presented in this paper may also be useful in other settings.
 
@@
 \Cref{prop:hybrid_vs_retail} is then a special case of this result.
-\begin{proof}[Proof of \Cref{hybrid_vs_retail}]
+\begin{proof}[Proof of \Cref{prop:hybrid_vs_retail}]
     $\Pi$ satisfies \Cref{ass:additive_profit,ass:monotone_profits,ass:monotone_profits}.

### 2024-08-19 src/paper/application.tex
Improve conclusion

@@
 This paper introduces a new model of hybrid platforms in which bargaining between the platform and the entrant firms plays a key role.
-It highlights the importance of a so far overlooked aspect of platforms having their own products: the fact that it increases their bargaining power compared to other players'.
+It highlights the importance of a so-far overlooked aspect of platforms having their own products: the fact that it increases their bargaining power compared to other players.
+In certain situations, such as the one described in this paper, this can lead to fewer fringe reduced product variety and, ultimately, lower consumer welfare.
 As a result, even in the absence of other frictions, hybrid platforms might have detrimental effects on fringe entry.
-This, in certain situations, such as the one described in this paper, this can lead to fewer fringe reduced product variety, and ultimately, lower consumer welfare.
-
-The contributions of this paper can be broken down into two categories.
-First, a simple, but quite general model of bargaining between one indispensable player and a continuum of potential market entrants is introduced.
-This model is applicable beyond the platform setting, and can describe other markets, such as upstream-downstream relations, or franchising, as well.
-The quite general results obtained from this model also highlight the similarities between those markets.
-Furthermore, many of the results from this paper can be applied in a plug-and-play fashion to other models of large-player-small-player interactions.
-
-The second set of contributions pertains to applying the aforementioned model to a setting with a hybrid platform.
+
 The demand structure is similar to the one in \textcite{anderson2021hybrid}, and the results convey the same general message: hybrid platforms can have detrimental welfare effects.
 However, the mechanism behind this result is quite different.
-This paper relies on the change in bargaing power, and shows that even in the case of lump-sum entry fees, hybrid platforms can be problematic from a welfare perspective.
-An extension of the main model also highlight the importance of the assumptions on who is participating in the bargaining process.
-
-There is a number of avenues for future research in this direction.
+This paper showcases the channel of changes in bargaining power and shows that even in the case of lump-sum entry fees, hybrid platforms can be problematic from a welfare perspective.
+An extension of the main model also highlights the importance of the assumptions on who is participating in the bargaining process.
+
+As shown in the appendix, the model can be generalized beyond the hybrid platform setting, and can describe other markets, such as upstream-downstream relations or franchising, as well.
+The generality of the results obtained also highlights the similarities between such markets.
+Furthermore, many of those results from can be applied in a plug-and-play fashion to other models of large-player-small-player bargaining.
+
+There are several avenues for future research in this direction.
 First, although the results provide some suggestions about what endogenizing the number of the platform's products might entail, a more formal analysis is needed for a more complete picture.
-Second, applying the same bargaining framework, but using a different demand structure (e.g.
-CES utility) for microfounding the profit functions would have important implications for the robustness of the results.
-Finally, I believe this approach for modeling bargaining is a rather good compromise between assuming that one party has all the bargaining power, and modeling the bargaining process in detail, and some of the main ideas in this paper might be a good fit for different settings and and more applied models.
+Second, applying the same bargaining framework but using a different demand structure (e.g., CES utility) for microfounding the profit functions would have important implications for the robustness of the results.
+Finally, I believe this approach for modeling bargaining is a rather good compromise between assuming that one party has all the bargaining power and modeling the bargaining process in detail.
+Therefore, certain ideas in this paper might be a good fit for modeling different settings involving bargaining power disparities.
 

### 2024-08-19 src/paper/application.tex
Improve wording

@@
 This section introduces the model used throughout the paper.
-I use the terms ``platform'' and ``fringe sellers'', and present my ideas in the context of an intermediated market, such as an online marketplace or an application store.
-However, the model is quite general, and the results apply to a broader class of settings, such as vertical markets where the upstream firm can sell directly to consumers, or retail stores with their own private labels.
+I use the terms ``platform'' and ``fringe sellers'' and present my ideas in the context of an intermediated market, such as an online marketplace or an application store.
+However, the model is quite general, and the results apply to a broader class of settings, such as vertical markets where the upstream firm can sell directly to consumers or retail stores with their own private labels.
 Furthermore, while the discussion in the main text focuses on a specific demand structure and profit sharing rule, most of the results apply to a broader class of models.
-\Cref{sec:more_general} explores the generalizability of these results, and highlights some common themes in settings with hybrid behavior.
-
-Assume that there are two types of players in the market: a platform $P$, a continuum of fringe sellers $F_i$ ($i \in \mathbb{R}^+$) and a continuum of consumers $C_j$ ($j \in [0, 1]$).
+\Cref{sec:more_general} explores the generalizability of these results, highlighting some common themes in settings with hybrid behavior.
+
+Assume that there are two types of players in the market: a platform $P$, a continuum of fringe sellers $F_i$ ($i \in \mathbb{R}^+$), and a continuum of consumers $C_j$ ($j \in [0, 1]$).
 The fringe firms have one product each, which they can only sell through the platform.
@@
 
-The main distinguishing feature of this model is that, instead of assuming that entry fees or royalties are set by the platform and the fringe treat it as take it or leave it offers, I assume that the platform and the fringe engage in some kind of bargaining over their total profits.
-The bargaining rule, as well as other details of the model, are described in the rest of this section.
-
-The rest of this section is structured as follows.
-\Cref{sec:model_overview} provides an overview of the model's stages, the timing of the game, as well as the qeuilibrium concept used in this paper.
-Then, \Cref{sec:model_details} describes each stage of the game formally.
+The main distinguishing feature of this model is that instead of assuming that entry fees or royalties are set by the platform and that the fringe treats them as take-it-or-leave-it offers, I assume that the platform and the fringe engage in some kind of bargaining over their total profits.
+The rest of this section describes the bargaining rule and other details of the model and is structured as follows.
+\Cref{sec:model_overview} provides an overview of the model's stages, the timing of the game, as well as the equilibrium concept used in this paper.
+Then, \Cref{sec:model_details} formally describes each stage of the game.
 Finally, \Cref{sec:model_discussion} discusses some of the assumptions made in the model, and their implications.
@@
 Each version has four main stages corresponding to determining four sets of endogenous variables: (1) the platform (and the fringe) setting (negotiating) the entry fee, (2) the fringe firms deciding whether to enter the market, (3) the platform and the fringe setting the prices of their products, and (4) consumers making their purchase decisions.
-The main difference between them lies in how the entry fee is determined, and, correspondingly, the order of the first two stages.
+The main difference between them lies in how the entry fee is determined and, correspondingly, the order of the first two stages.
 
@@
 The square brackets indicate the endogenous variables decided at that stage of the game.
-In the benchmark model (\Cref{fig:timing_benchmark}), the game starts by the platform announcing and committing to an entry fee $K_F$ ($\mathbf{T_1}$).
+In the benchmark model (\Cref{fig:timing_benchmark}), the game starts with the platform announcing and committing to an entry fee $K_F$ ($\mathbf{T_1}$).
 Next, each fringe firm decides whether to create a product at cost $I_F$ and enter the market. ($\mathbf{T_2}$)
 After that, the platform and the fringe firms simultaneously choose the prices for their products, engaging in monopolistic competition ($\mathbf{T_3}$).
-Finally, consumers make their purchase decisions, and profits are realized ($\mathbf{T_3}$).
-
-The bargaining model has a slightly different timing, as shown in \Cref{fig:timing_bargaining}.
+Finally, consumers make their purchase decisions and profits are realized ($\mathbf{T_3}$).
+
+The bargaining model has slightly different timing, as shown in \Cref{fig:timing_bargaining}.
 The platform cannot commit to an entry fee at the beginning, so the game starts with the fringe firms deciding whether to invest in creating a product at cost $I_F$ ($\mathbf{T_1}$).
 After that, the entry fee is decided as a result of some negotiation\footnote{
-    The negotiation process, or rather its outcome is described in detail in \Cref{sec:cooperative_game}.
+    The negotiation process, or rather its outcome, is described in detail in \Cref{sec:cooperative_game}.
 } between the platform and the firms that have made the investment ($\mathbf{T_2}$).
-Then, the firms that made the investment pay the platform entry fees, too.
+Then, the firms that invested pay the platform entry fees, too.
 From this point on, the game proceeds in the same way as in the benchmark model: the platform and the fringe firms set their prices ($\mathbf{T_3}$), and consumers make their purchase decisions ($\mathbf{T_4}$).
 
-The main difference between the benchmark and the bargaining model is in determining the entry fee $K_F$.
-In the former, the platform unilaterally sets the fee, and the fringe treats it as a take it or leave it offer.
-On the other hand, in the bargaining model, I assume that the entry fee is the result of a negotiation between the parties.
+The main difference between the benchmark and the bargaining model lies in determining the entry fee $K_F$.
+In the former, the platform unilaterally sets the fee, and the fringe treats it as a take-it-or-leave-it offer.
+On the other hand, in the bargaining model, I assume that the entry fee results from negotiation between the parties.
 More precisely, in the latter case, I assume that the platform's and the fringe's total profits at the end of the game correspond to their Shapley values.
-This in turn uniquely determines the entry fee, and thus the negotiation at time ($\mathbf{T_2}$) can be equivalently conceptualized as bargaining over the final profit as well as the entry fee.
+This, in turn, uniquely determines the entry fee.
+Thus, the negotiation at time ($\mathbf{T_2}$) can equivalently be conceptualized as bargaining over the final profits, as well.
 
@@
 For both models, this structure corresponds to a perfect-information extensive-form game.
-As a consequence, the solution concept I use is the subgame perfect equilibrium.
+Consequently, the solution concept I use is the subgame perfect equilibrium.
 As the platform's product variety ($N_P$) is assumed to be exogenous, the only strategic variables are (1) the fringe players' entry decisions, (2) the platform's entry fee (only in the benchmark model), (3) the prices of the products and (4) the consumers' purchase decisions.
 
-In these two specific games, the subgame perfect can be charactrerized as follows.
+The subgame perfect can be characterized in these two specific games as follows.
 \begin{definition}
@@
 Let us now describe each stage of the game in more detail, starting with the final two subgames, as they are identical in both models.
-This part of the model is based on \textcite[]{anderson2021hybrid}, who utilize the exact same utility structure as th one described here.
-Imagine that there is a unit mass of consumers, looking to buy one product each.
-They choose from a continuum of products, which are either produced by the fringe (indexed by $F_i$), by the platform ($P_i$) and a unit mass of outside options ($0_i$).
+This part of the model is based on \textcite[]{anderson2021hybrid}, who utilize the exact same utility structure as the one described here.
+Imagine that there is a unit mass of consumers looking to buy one product each.
+They choose from a continuum of products, which are either produced by the fringe (indexed by $F_i$), by the platform ($P_i$) or are amongst a unit mass of outside options ($0_i$).
 Customer $j$ derives the following utility from buying product $T_i$\footnote{
-    To avoid duplication, I denote the different types of products by $T_i$, where $T \in \{F, P, 0\}$ (fringe products, platform profucts, and outside options, respectively).
+ To avoid duplication, I denote the different types of products by $T_i$, where $T \in \{F, P, 0\}$ (fringe products, platform products, and outside options, respectively).
  This notation is used throughout the paper for other variables having fringe and platform counterparts, as well.
@@
 where $v_{T_i}$ is the value of product $T_i$, $p_{T_i}$ is its price, and $\epsilon_{T_i}^j$ is an idiosyncratic taste shock.
-Throughout this section I assume that the value of each fringe product is the same, and the same goes for the platform products.
+Throughout this section, I assume that the value of each fringe product is the same, and the same goes for the platform products.
 I.e., $v_{T_i} = v_T \, \forall\,i$.
-This is to simplify the analysis, but is not crucial for the results.
-
-$\epsilon_{T_i}^j$ is assumed to be independent and identically distributed (i.i.d.) across consumers and products, and follow a standardized Type I Extreme Value distribution.
+This is to simplify the analysis but is not crucial for the results.
+
+$\epsilon_{T_i}^j$ is assumed to be independent and identically distributed (i.i.d.) across consumers and products and follow a standardized Type I Extreme Value distribution.
 This distributional assumption, along with the fact that each consumer consumes only one product, will lead to a tractable, logit-form demand function.
-The demand for product $T_i$ is that arises from the consumers maximizing their utility is denoted by $x_{T_i}$.
+The demand for product $T_i$, which arises from consumers maximizing their utility, is denoted by $x_{T_i}$.
 
@@
 
-Now let us turn to stage 1 and 2 of the game: the determination of the entry fee and the fringe firms' entry decision.
+Now, let us turn to stages 1 and 2 of the game: the determination of the entry fee and the fringe firms' entry decision.
 I start with the benchmark model, where the platform sets the entry fee unilaterally.
-Then, I compare and contrast this with the bargaining model, where the entry fee is the result of a negotiation between the platform and the fringe firms.
+Then, I compare and contrast this with the bargaining model, where the entry fee results from a negotiation between the platform and the fringe firms.
 
@@
 I assume that there is a continuum of potential fringe entrants, indexed by $i \in \mathbb{R}^+_0$.
-Each of them can create a product at an exogenous investment cost $I_F$.
-If they decide not to, they make zero profits and do not participate in the later stages of the game.
+Each can create a product at an exogenous investment cost $I_F$.
+If they decide not to, they make zero profits and do not participate in the game's later stages.
 Furthermore, these firms can only sell their products through the platform, for which the platform can charge a lump-sum entry fee $K_F$.
@@
 After this, the platform and the firms that have made the investment negotiate the entry fee.
-Finally, the firms that have entered pay the entry fee to the platform.
+Finally, the firms that entered pay the entry fee to the platform.
 
@@
 
-Let us now discuss some of the non-standard assumptions made in the model, and their implications.
+Let us now discuss some of the non-standard assumptions made in the model and their implications.
 I look at four main categories in this section: the timing of the game, the costs of entry for fringe firms, the way the monopolistic competition is modeled, and the way the bargaining process is modeled.
@@
 
-For each potential fringe entrant $F_i$, entering the marker has two, separate costs: an exogenous investment cost $I_F$, and the lump-sum platform entry fee $K_F$.
-One can conceptualize the first one, $I_F$, as usual fixed costs, such as the cost of setting up production, or designing a product.
-Without it, fringe firms would always make positive profits in the bargaining model, and therefore the free entry equilibrium would not exist.
-Furthermore, it is a quite reasonable assumption in most settings, as some of the costs of entering the market are sunk, and not paid to the platform.
+For each potential fringe entrant $F_i$, entering the market has two separate costs: an exogenous investment cost $I_F$ and the lump-sum platform entry fee $K_F$.
+The first one, $I_F$, can be conceptualized as usual fixed costs, such as the cost of setting up production or designing a product.
+Without it, fringe firms would always make positive profits in the bargaining model, and therefore, the free-entry equilibrium would not exist.
+Furthermore, it is quite a reasonable assumption in most settings, as some of the costs of entering the market are sunk and not paid to the platform.
 
@@
 While percentage fees are more common both in the literature and in practice, I assume a lump-sum fee for a few reasons.
-First, and most importantly, revenue-based fees enter the entrants' pricing decision, and thus create a channel through which platforms distort competition.
-I want to show that even in the absence such distortions, hybrid platforms can have a significant impact on competition.
+First, and most importantly, revenue-based fees enter the entrants' pricing decisions, and thus create a channel through which platforms distort competition.
+I want to show that hybrid platforms can significantly impact competition even in the absence of such distortions.
 Furthermore, due to this distortion, the resulting game could not be represented as a transferable utility game, and the proposed solution concept would not be applicable.
@@
 The two models are designed to be as similar as possible, also with respect to the timing of the game.
-The only difference is in the order of the first two stages, which is necessary due to the nature of the two different entry fee setting mechanisms.
+The only difference is in the order of the first two stages, which is necessary due to the nature of the two different entry fee-setting mechanisms.
 
 In the case of the benchmark model, if the platform set entry fees after fringe firms make their investment decisions, the platform would charge an entry fee that would make the fringe profits zero without taking into account the investment cost $I_F$.
-This would lead to negative fringe profits, and thus to a trivial equilibrium, where no firm enters.
-Therefore, entry fee setting must come before the fringe firms' investment decisions.
+This would lead to negative fringe profits and, thus, to a trivial equilibrium where no firm enters.
+Therefore, the entry fee setting must come before the investment decisions of the fringe firms.
 
 Contrary to this, in the bargaining model, the opposite order is necessary.
-This is because the entry fee is the result of a negotiation, so by the time the negotiation takes place, it must already be clear which firms are engaging in it.
-Otherwise, the bargaining process (either in its cooperative, reduced-form version, or in the non-cooperative, extensive form one) would not be well defined.
+This is because the entry fee is the result of a negotiation, and by the time the negotiation takes place, it must already be clear which firms are engaging in it.
+Otherwise, the bargaining process (either in its cooperative, reduced-form version or in the non-cooperative, extensive form one) would not be well defined.
 Therefore, the fringe firm's entry decisions\footnote{
     With respect to creating a product.
-    Entering the platform and paying the entry fee is a separate decision, which takes place during the negotiation.
+    Entering the platform and paying the entry fee are separate decisions, which take place during the negotiation.
 } must come before the determination of the entry fee.
@@
 
-The pricing decision of the fringe sellers is rather straightforward, due to their infinitesimal market share: they do not have to take into account the effect of their prices on the aggregate demand.
-This normally is not the case for the platform, as it can affect a non-zero measure of the prices.
+Due to their infinitesimal market share, the fringe sellers' pricing decisions are rather straightforward: they do not have to take into account the effect of their prices on the aggregate demand.
+This is typically not the case for the platform, as it can affect a non-zero measure of the prices.
 Therefore, when setting the price for product $P_i$, it would optimally like to take into account how it affects demand on its other products $P_j$ $(j \neq i)$.
@@
 For one, it simplifies the analysis without affecting the main results qualitatively.
-More importantly, it lets me focus on the main question of this paper: how the platform's hybrid operation affects the bargaining power.
-If the platform priced its products strategically, there would be an additional channel through which its product variety could affect the outcomes: in contrast to the fringe firms, it takes into account the effect of its prices on the aggregate demand.
+More importantly, it lets me focus on the main question of this paper: how the platform's hybrid operation affects bargaining power.
+If the platform priced its products strategically, there would be an additional channel through which its product variety could affect the outcomes, as, in contrast to the fringe firms, it takes into account the effect of its prices on the aggregate demand.
 This would make it harder to disentangle the effects of hybrid operation from the effects of strategic pricing.
-This assumption can be seen as a best-case scenario for consumers and the fringe, where as little market power as possible is given to the platform.
+This assumption can then be seen as a best-case scenario for consumers and the fringe, in which the platform is given as little market power as possible.
 
@@
 }.
-This in turn means that the platform will optimally price its products as if they were produced by separate sellers.
-In the current paper, such a timing would be problematic, because the aim is to keep the benchmark and bargaining models as similar as possible.
-It would be unrealistic to assume that the platform can commit to prices before the fringe firms make their investment decisions, while at the same time it cannot commit to an entry fee in the latter model.
-
-Finally, even taken at face value, this assumption about the platform's pricing is quite reasonable in a number of settings.
-For example, the platform might be producing its products through a number of subsidiaries, which are legally separate entities, thus having no control over operational decisions, but still getting the profits from the sales.
-Alternatively, there might be some kind of internal competition between the different product teams, which would lead to a similar outcome.
+This, in turn, means that the platform will optimally price its products as if they were produced by separate sellers.
+Such timing would be problematic in the current paper because the aim is to keep the benchmark and bargaining models as similar as possible.
+It would be unrealistic to assume that the platform can commit to prices before the fringe firms make their investment decisions, while at the same time, it cannot commit to an entry fee in the latter model.
+
+Finally, even taken at face value, this assumption about the platform's pricing is quite reasonable in certain settings.
+For example, the platform might produce its products through many legally separate subsidiaries, thus having no control over operational decisions but still earning profits from their sales.
+Alternatively, even within a single firm, there might be some internal competition between the different product teams, leading to a similar outcome.
 
@@
 Although the main reason for utilizing cooperative game theory in this model is tractability, it is by no means the only one.
-This way of modelling bargaining outcomes, while uncommon, has been used to great effect in a number of other papers in the industrial organization literature \parencite[e.g.][]{montez2007downstream,hart1990property,levy1997individual,inderst2003bargaining,brugemann2019intra}.
+This way of modeling bargaining outcomes, while uncommon, has been used to great effect in several other papers in the industrial organization literature \parencite[e.g.][]{montez2007downstream,hart1990property,levy1997individual,inderst2003bargaining,brugemann2019intra}.
 Furthermore, it has a number of appealing properties.
 For example, it is closely related to the marginal contributions of the players to the total value, and, as shown in \Cref{sec:more_general_results}, it is also quite intuitive in terms of comparative statics.
-Furthermore, and perhaps more importantly, there are a number of ways to place it on non-cooperative microfoundations by setting up non-cooperative games for which the Shapley value is a subgame perfect equilibrium \parencite[e.g.][]{gul1989bargaining,hart1996bargaining,stole1996organizational}.
-\Cref{sec:bargaining_microfoundation} provides an example on how this specific model can be placed on such microfoundations.
+Furthermore, and perhaps more importantly, there are many ways to place it on non-cooperative microfoundations by setting up non-cooperative games for which the Shapley value is a subgame perfect equilibrium \parencite[e.g.][]{gul1989bargaining,hart1996bargaining,stole1996organizational}.
+\Cref{sec:bargaining_microfoundation} provides an example of how this specific model can be placed on such microfoundations.
 The subgame perfect equilibrium of the fully non-cooperative model described in that section coincides with the equilibrium of the bargaining model in the main text.
@@
 
-Let us also discuss the specifics of the cooperative game of which the Shapley value is calculated.
-For the Shapley value (or any other cooperative solution concept) to be well-defined, the corresponding coalitional game must be precisely specified, as well.
-\Cref{sec:cooperative_game} describes it in detail. 
+Let us also discuss the specifics of the cooperative game in which the Shapley value is calculated.
+For the Shapley value (or any other cooperative solution concept) to be well-defined, the corresponding coalitional game must also be precisely specified.
+\Cref{sec:cooperative_game} describes the latter in detail. 
 In short, the idea is the following: given any subset of the players (coalition), players can predict total, industry-wide profits, as the pricing subgame has a unique subgame perfect equilibrium for any subset of the players.
 This total profit is taken as the value of that coalition, thus defining a characteristic function.
-Then, according to the definition of the Shapley value, every firm (including the platform) will get their average marginal contribution this industry-wide profit (with the average taken over all possible orderings of the firms).
-
-One simple extension of this bargaining process would be to use the more general concept of random order values \parencite{weber1988probabilistic}.
-\textcite{stancsics2023value} examines this solution concept for a similar game, but in a more abstract setting.
-\Cref{sec:cooperative_game_weighted} takes a step in this direction by introducing bargaining weights and utilizing the weighted value.
-
+Then, according to the definition of the Shapley value, every firm (including the platform) will get their average marginal contribution to this industry-wide profit (with the average taken over all possible orderings of the firms).
+
+A straightforward extension of this bargaining process would be to use the more general concept of random order values \parencite{weber1988probabilistic}.
+\textcite{stancsics2023value} examines this solution concept for a similar game but in a more abstract setting.
+\Cref{sec:cooperative_game_weighted} also takes a step in this direction by introducing bargaining weights and utilizing the weighted value.
 \section{Results}

### 2024-08-20 src/paper/application.tex
Improve wording and fix mistakes

@@
 
-I will now present the main results of the model, again, starting from the final subgame and working backwards.
-For each subgame, I also demonstrate that the equilibrium exists and is unique, and therefore the complete game also has a unique equilibrium.
-The propositions in this section are generally proven for a more general framework, and those presented here are special cases of those.
-The reason for presenting the more special case in the main text is twofold.
-First, it the more concrete model is better for expositional purposes, and is a good fit for the setting.
-Second, the link between consumer surplus and the number of products is straightforward under the logit assumption, making it possible to state welfare results, as well.
-
-For this reason, the proofs are also presented together with the more general model in \Cref{sec:more_general}.
+I will now present the model's main results, starting from the final subgame and working backward.
+I also demonstrate that the equilibrium exists and is unique in each subgame, and therefore, the complete game also has a unique equilibrium.
+The propositions in this section are generally proven within a more general framework, and those presented here are special cases.
+The reason for emphasizing the more special case is twofold.
+First, the more concrete model is better for expositional purposes and is a good fit for the context of platforms.
+Second, the link between consumer surplus and the number of products is straightforward under the logit assumption, making obtaining welfare results possible.
+
+For this reason, the proofs are presented together with the more general model in \Cref{sec:more_general}.
 Most of the results only rely on \Cref{ass:additive_profit,ass:free_entry,ass:identical_fringe,ass:monotone_profits,ass:profit_sharing,ass:single_crossing}, and do not require the specific, logit-like demand function described previously.
 Therefore, I proceed to prove those results in two steps.
-First, I demonstrate that the model satisfied the aforementioned assumptions.
+First, I demonstrate that the model satisfied these assumptions.
 Second, in \Cref{sec:more_general}, I prove the corresponding results for the more general case.
@@
 Discrete choice models with type I Extreme Value errors give rise to a logit-type demand function \parencite[e.g.][]{small1981applied}.
-More specifically, \textcite[]{anderson2021hybrid} show that it gives rise to the following demand function.
+More specifically, \textcite[]{anderson2021hybrid} shows that it gives rise to the following demand function.
 \begin{proposition}
@@
 Let us call $v_T - p_{Ti}$ the net value of product $i$.
-As one would expect, demand is increasing in this net value, and decreasing in the competitors' net values.
+As one would expect, demand is increasing in this net value and decreasing in the competitors' net values.
 Furthermore, demand for each product is increasing in $\mu$, which describes the degree of product differentiation or the importance of taste shocks.
-Finally, notice that, as each producer is infinitesimal, its pricing decision does not affect the aggregate $A$.
+Finally, as each producer is infinitesimal, its pricing decision does not affect the aggregate $A$.
 This last property makes the optimal prices and profits of the producers very simple, as shown in the next proposition.
@@
 denotes the total aggregate.
-Therefore, to simplify the notation, I will use $V_T$ and $A$ in the rest of the paper, instead of the more cumbersome expressions.
-
-Finally, another important feature of this demand system is that, assuming optimal pricing, consumer welfare only depends on the size of the aggregate \parencite{anderson2020aggregative}.
-In particular, consumer surplus is proportional to the logarithm of the aggregate: $CS = \mu \log(A)$. This fact makes welfare analysis rather simple in this setting.
+Therefore, to simplify the notation, I will use $V_T$ and $A$ instead of the more cumbersome expressions in the rest of the paper.
+
+Finally, another key feature of this demand system is that under optimal pricing, consumer welfare only depends on the size of the aggregate \parencite{anderson2020aggregative}.
+In particular, consumer surplus is proportional to the logarithm of the aggregate: $CS = \mu \log(A)$. This fact makes welfare analysis relatively simple in this setting.
 
@@
 
-Let us now examine entry fees and fringe entry decisions in the benchmark model.
+Now, let us examine entry fees and fringe entry decisions in the benchmark model.
 Recall that there is an infinity of potential fringe entrants looking to enter the market.
@@
 Therefore, the zero profit condition for the fringe firms pins down the aggregate in equilibrium (as long as the fringe is feasible).
-That is, an increase in $N_P$ will simply replace some fringe entrants, but the free entry condition will pin down the same aggregate regardless of the number of platform products.
-
-Now let us turn to the optimal entry fee set by the platform, and its total profits (consisting of revenue from its own sales and the collected entry fees).
+That is, an increase in $N_P$ will replace some fringe entrants, but the free entry condition will pin down the same aggregate regardless of the number of platform products.
+
+Now, let us turn to the optimal entry fee set by the platform and its total profits (consisting of revenue from its own sales and the collected entry fees).
 The following proposition establishes these both for the hybrid and the pure retail regimes, and \Cref{fig:entry_fee,fig:platform_profits} demonstrates them graphically.
@@
 
-First, let us look at the case when the platform finds it optimal to operate in the hybrid regime.
+First, let us look at the case of the platform finding it optimal to operate in the hybrid regime.
 As illustrated by \Cref{fig:entry_fee}, the optimal entry fee (\Cref{eq:entry_fee_benchmark}) does not depend on either the platform's product value or product variety.
 This is because due to the lump-sum nature of the entry fee, the platform can extract all the surplus from the fringe firms, and thus chooses $K_F$ to maximize total industry profits.
-The latter is essentially a function of the aggregate, minus the investment costs of the fringe firms.
-As I show later in \Cref{prop:equilibrium_benchmark}, the aggregate is independent of the platform's product variety in the hybrid regime, and therefore the optimal entry fee is also independent of it.
+The latter is a function of the aggregate minus the investment costs of the fringe firms.
+As I show later in \Cref{prop:equilibrium_benchmark}, the aggregate is independent of the platform's product variety in the hybrid regime.
+Therefore, the optimal entry fee is also independent of it.
 
@@
 \end{corollary}
-This is a rather mechanical result: the platform's product variety is exogenous, and therefore possible investment costs are not modeled.
-If the platform is operating in the hybrid regime, less fringe firms are needed to achieve the (fixed) equilibrium aggregate, therefore there is less expenditure on (essentially wasted) investment costs.
+This is a rather mechanical result: the platform's product variety is exogenous, and possible investment costs are not modeled.
+If the platform is operating in the hybrid regime, fewer fringe firms are needed to achieve the (fixed) equilibrium aggregate, so less is spent on (essentially wasted) investment costs.
 Consequently, in the hybrid regime, the derivative of optimal profits with respect to the platform's product variety is simply the fringe's investment cost, adjusted for the possible difference in product value.
@@
 Under the assumed demand system, consumer surplus is proportional to the logarithm of the aggregate.
-Therefore, one only needs to understand how fringe entry, and thus the aggregate changes with the platform's product variety to understand the effect of the latter on consumer welfare.
-The next theorem establishes results for these three variables in the benchmark model.
+Therefore, one only needs to understand how fringe entry, and thus the aggregate, changes with the platform's product variety to understand the latter's effect on consumer welfare.
+The following theorem establishes results for these three variables in the benchmark model.
 \begin{theorem}
@@
 
-The most important, and perhaps surprising, results of this theorem is that the platform's product variety has no effect on consumer welfare in the hybrid regime.
-This is due to the fact that the optimal entry fee, which is independent of $N_P$, pins down the aggregate.
+The most important, and perhaps surprising, result of this theorem is that the platform's product variety does not affect consumer welfare in the hybrid regime.
+This is because the optimal entry fee, which is independent of $N_P$, pins down the aggregate.
 As shown in \Cref{fig:fringe_entry_eq}, an increase in the platform's product variety will simply replace fringe firms in a constant ratio, such that the aggregate remains constant (\Cref{fig:welfare_aggregate}).
@@
 
-When the platform finds it optimal to operate as a pure retailer, the only products on the market are the platform's own products.
+When the platform finds it optimal to operate as a pure retailer, its own products are the only products on the market.
 Therefore, quite mechanically, the aggregate, and thus consumer surplus, are increasing in the number of the platform's products (unshaded parts of \Cref{fig:welfare}).
 
-Finally, note that the profit of the platform under the hybrid regime is higher than under the retail regime, whenever the former is feasible.
-Therefore, for a given $N_P$, the platform prefers to operate in hybrid mode, and does not want to exclude fringe firms from the market.
+Finally, note that the platform's profit under the hybrid regime is higher than under the retail regime whenever the former is feasible.
+Therefore, for a given $N_P$, the platform prefers to operate in hybrid mode and does not want to exclude fringe firms from the market.
 This fact, together with the \Cref{prop:equilibrium_benchmark}, implies that the platform's product variety always has a weakly positive effect on consumer welfare.\footnote{
@@
     The reason for this difference lies in the type of entry fee: they assume a revenue-based, proportional fee, which distorts prices.
-    In contrast, in this paper, I assume a non-distortive, lump sum fee.
+    In contrast, I assume a non-distortive lump sum fee in this paper.
 }
@@
 As the platform cannot choose and commit to an entry fee, the first two periods are switched compared to the benchmark model.
-The game starts by fringe firms' investment decisions, after which, in the second period, bargaining takes place between the platform and the entrants to determine the entry fee.
-
-As described in \Cref{sec:model_bargaining}, participants negotiate over the aggregate profits that they expect to obtain in the subsequent period (assuming the same non-collusive, monopolistic pricing, as before).
+The game starts with fringe firms' investment decisions, after which, in the second period, bargaining takes place between the platform and the entrants to determine the entry fee.
+
+As described in \Cref{sec:model_bargaining}, participants negotiate over the aggregate profits that they expect to obtain in the subsequent period (assuming the same non-collusive, monopolistic pricing as before).
 From \Cref{eq:optimal_profit}, the total profit achieved by the platform and $N_F$ fringe firms is given by
@@
 Bargaining outcomes are determined according to Shapley values, given by \Cref{prop:shapley_value}.
-Based on these, one can obtain closed-form expressions for platform and fringe profit shares for this class of demand systems.
+Based on these, closed-form expressions for platform and fringe profit shares for this class of demand systems can be obtained.
 \begin{proposition}
@@
 
-Let us establish a couple of partial equilibrium results about the profir shares before moving on to the main results.
-Consider the number of fringe firms $N_F$ fixed.
+Let us establish a couple of partial equilibrium results about the profit shares before moving on to the main results.
+Consider the number of fringe firms $N_F$ as fixed.
 Then, total profits, as given by \Cref{eq:total_profits}, are clearly increasing in the number of platform products.
@@
 \end{proposition}
-This is actually a rather striking results.
+This is a rather striking result.
 Even though the total size of the pie increases, the slice that the fringe can obtain decreases.
-This is due to the substitutability of the fringe and the platform's own products\footnote{
+This happens because of the substitutability of the fringe's and the platform's products\footnote{
     \Cref{prop:share_of_fringe} demonstrates that the direction of the change depends on the cross derivative of the total profit function.
-}: as the latter increases its product variety, the marginal benefit of adding each fringe firm decreases, leading to a detoriation in the fringe's bargaining position.
-
-Let us now endogeneize $N_F$, and turn to the main results of this section: how the platform's dual mode operation affects product variety and consumer welfare.
+}: as the latter increases its product variety, the marginal benefit of adding each fringe firm decreases, leading to a deterioration in the fringe's bargaining position.
+
+Let us now endogenize $N_F$ and turn to this section's main results: how the platform's dual-mode operation affects product variety and consumer welfare.
 I start by showing that, like in the benchmark model, the equilibrium is unique in this case, as well.
@@
 
-While this lemma's main purpose is to help establish the results about fringe entry and consumer surplus for the bargaining case, it is also interesting in its own right.
-It shows that the number of fringe firms do not necessarily have a monotonic effect on the total profits of the fringe.
-That is, even though industry-wide profits are increasing in $N_F$, the amount that the fringe can obtain may decrease after a certain point, not only as a fraction of the total, but also in absolute terms.
+While this lemma's primary purpose is to help establish the results about fringe entry and consumer surplus for the bargaining case, it is also interesting in its own right.
+It shows that the number of fringe firms does not necessarily have a monotonic effect on the total profits of the fringe.
+That is, even though industry-wide profits are increasing in $N_F$, the amount that the fringe can obtain may decrease after a certain point, not only as a fraction of the total but also in absolute terms.
 The underlying reason is that as the number of fringe firms increases, their bargaining power decreases due to their substitutability with each other.
-This decrease can be large enough to offset the total pie getting larger.
+This decrease can be large enough to offset the increase in the size of the total pie.
 
@@
 
-An almost immediate corollary is that such a function must have (apart from the trivial $N_F=0$ case) at most one crossing with total investment costs, which is a linear function of $N_F$.
+An almost immediate corollary is that such a function must have (apart from the trivial $N_F=0$ case) at most one crossing with total investment costs, a linear function of $N_F$.
 Let us denote this point as $N_F^*$.
@@
     \label{prop:unique_equilibrium}
-    The equilibrium number of entrants $N_F^*$ is unique in the bargaining case.
+    The equilibrium number of entrants, $N_F^*$, is unique in the bargaining case.
 \end{proposition}
 
-Now let us examine how the platform's product variety affects fringe profits and the equilibrium number of fringe firms.
+Now, let us examine how the platform's product variety affects fringe profits and the equilibrium number of fringe firms.
 First, let us establish that fringe profits are decreasing in the number of the platform's products.
-Note, that this is a partial equilibrium result: $N_F$ is assumed to be fixed, and the platform's product variety is increased.
-Later on, 
+Note that this is a partial equilibrium result: $N_F$ is assumed to be fixed, while the platform's product variety is increased.
 \begin{proposition}
@@
 
-As illustrated in \Cref{fig:comparative_N_F}, together with the hump-shaped fringe profit function, this implies that an increase in the platform's product variety leads to a reduction in the number of fringe firms.
-What is not immediately clear is how this affects the total size of the aggregate, and consumer welfare.
+As illustrated in \Cref{fig:comparative_N_F}, together with the hump-shaped fringe profit function, \Cref{prop:fringe_profits_partial} implies that an increase in the platform's product variety leads to a reduction in the number of fringe firms.
+What is not immediately apparent is how this affects the total size of the aggregate and consumer welfare.
 In the benchmark case, the decrease in the number of fringe firms was exactly offset by an increase in the platform's product variety, and the aggregate remained constant.
-The following results shows that this is not the case in the bargaining model: as long as the platform is in the hybrid regime, the aggregate decreases in the number of the platform's products.\footnote{
+The following results show that this is not the case in the bargaining model: as long as the platform is in the hybrid regime, the aggregate decreases in the number of the platform's products.\footnote{
     As before, similar results hold for an increase in the platform's product value $V_P$.
@@
 
-The main takeaway from this theorem is that the increasing the platform's product variety can actually decrease consumer welfare in the bargaining model.
+The main takeaway from this theorem is that increasing the platform's product variety can decrease consumer welfare in the bargaining model.
 The underlying reason is illustrated in \Cref{fig:fringe_entry_eq}: the decrease in the number of fringe entrants is large enough to not only to offset the increase in the platform's product variety, but also to decrease the aggregate (\Cref{fig:welfare_aggregate}).
-This in turn leads to a decrease in consumer surplus (\Cref{fig:welfare_consumer_surplus}).
+This, in turn, leads to a decrease in consumer surplus (\Cref{fig:welfare_consumer_surplus}).
 
 This set of results is in stark contrast to the benchmark model.
-Instead of increased product variety weakly increasing consumer welfare, when entry fees are negotiated, it can actually decrease it if the platform stays in the hybrid regime.
-
-The intuition behind these results can be understood by looking at entry fees.
+Instead of the increased product variety weakly increasing consumer welfare, when entry fees are negotiated, it has the opposite effect if the platform stays in the hybrid regime.
+
+The intuition behind these results can be understood by examining entry fees.
 First, define the implied entry fee in the bargaining case as the difference between the variable profit and the final, total profit of the fringe firms (bar the investment cost)\footnote{
@@
 \end{align*}
-As shown before, as the platform's product variety grows, its bargaining power also increases.
+As shown before, as the platform's product variety grows, its bargaining power increases.
 This can be thought of as an increase in (implied) entry fees $K_F^{impl}$, which in turn discourages fringe entry.
@@
 \end{proposition}
-This is not happening in the benchmark model, because, as stated in \Cref{prop:optimal_entry_fee}, the optimal entry fee does not depend on the platform's product variety.
+This does not happen in the benchmark model because, as stated in \Cref{prop:optimal_entry_fee}, the optimal entry fee does not depend on the platform's product variety.
 \Cref{fig:entry_fee} demonstrates this difference between the two models.
@@
 
-Assume that $N_P$ is still fixed, but now at time 0, the platform can decide whether to exclude the fringe.
+Assume that $N_P$ is still fixed, but now, at time 0, the platform can decide whether to exclude the fringe.
 As the next proposition shows, the platform never has an incentive to do so.\footnote{
-    Note, that it is possible that the optimal or negotiated entry fee is such that zero fringe firms enter the market.
-    This proposition's main statements is about the platform's decision to exclude the fringe, when the entry fee would be such that the fringe would enter.
+    Note that it is still possible that the optimal or negotiated entry fee is such that zero fringe firms enter the market.
+    The proposition's main statement concerns the platform's decision to exclude the fringe when the entry fee would be such that the fringe would enter.
 }
@@
 \end{proposition}
-In the case of the benchmark model, this result is rather straightforward: if the platform would find it optimal to exclude the fringe, it could do so by setting the entry fee to a sufficiently high level.
-In the bargaining case, the reasoning is less obvious, as it is not immediately clear that the share of profits that the platform can negotiate for itself is higher than what it could achieve by itself.
-However, it turns out that it is indeed the case.
-The intuition is that the platform's profit is just the average of total profits, with the average taken over the number of fringe firms.
+This result is straightforward in the case of the benchmark model: if the platform finds it optimal to exclude the fringe, it can always do so by setting the entry fee to a sufficiently high level.
+In the bargaining case, the reason is less obvious, as it is not immediately clear that the share of profits the platform can negotiate for itself is higher than what it could achieve alone.
+However, it turns out that this is indeed the case.
+The intuition is that the platform's profit is the average of total profits, with the average taken over the number of fringe firms.
 As total profits are increasing in the number of the fringe entrants, this average is also increasing in $N_F$.
 
-A related, but different question is whether the platform how the platform would decide between operating in pure retail and pure marketplace modes, if hybrid regime is not an option.
+A related, but different question is how the platform would decide between operating in pure retail and pure marketplace modes, if hybrid regime was not an option.
 It is particularly relevant from a policy perspective, as it can help understand what happens if hybrid operation is banned.
 The answer to this is less clear-cut, and depends on the parameters of the model.
-For low enough values of $V_P$ and $N_P$, the platform would clearly choose the pure marketplace mode, as with pure retail, its profits can be arbitrarily low.
+For low enough values of $V_P$ and $N_P$, the platform chooses the pure marketplace mode, as with pure retail, its profits can be arbitrarily low.
 The opposite is true for high enough values of $V_P$ and $N_P$.
@@
 Finally, let us look at the more general case, where the platform can choose its number of products at the beginning of the game.
-Similarly to the fringe, assume that it faces an investment cost of $I_P$ per product.
+Similarly to the fringe, assume that the platform faces an investment cost of $I_P$ per product.
 \Cref{fig:optimal_n_p} illustrates the platform's final profits as a function of its product variety.
 
-As before, things are straightforward in the benchmark model: the platform invests in own products only if $\frac{V_P}{I_P} \geq \frac{V_F}{I_F}$.
+As before, things are straightforward in the benchmark model: the platform invests in its own products only if $\frac{V_P}{I_P} \geq \frac{V_F}{I_F}$.
 The following proposition characterizes the platform's optimal investment more precisely.
@@
 
-The intuition behind this result is that the platform can extract all profits from the fringe firms through the lump-sum entry fee, end thus it invests in its own products only if it has a product advantage (either in terms of less costly investment or more valuable product).
-A consequence of this proposition is that, apart from the knife-edge case of $\frac{V_P}{I_P} = \frac{V_F}{I_F}$, the platform never finds it optimal to operate in hybrid mode: it either creates so many products that it excludes the fringe, or it creates none at all.
+The intuition behind this result is that the platform can extract all profits from the fringe firms through the lump-sum entry fee.
+Thus, it invests in its own products only if it has a product advantage (either a less costly investment or a more valuable product).
+A consequence of this proposition is that, apart from the knife-edge case of $\frac{V_P}{I_P} = \frac{V_F}{I_F}$, the platform never finds it optimal to operate in hybrid mode: either it creates so many products that the fringe is not viable, or it creates none at all.
 \Cref{fig:optimal_n_p_benchmark} displays this result: for low values of $I_P$, the equilibrium is a corner solution with $N_P = 0$, and for high values, the maximum is reached in the pure retail regime.
@@
 Instead of characterizing the platform's optimal investment directly, let us look at it through the lens of implied entry fees.
-Remember, that in the bargaining model, the implied entry fee is increasing in the number of the platform's products.
+Remember that in the bargaining model, the implied entry fee increases with the number of the platform's products.
 Together with the concavity of platform profits as a function of $N_P$, and the statement of \Cref{prop:platform_profits_comparative_benchmark}, this implies the following result:
@@
 \end{proposition}
-The intuition is that if, for a certain $N_P$, the implied entry fee is lower than optimal, then the platform investing in more products will bring it closer to the optimal level, and the increase in platform profits will be higher than in the benchmark model.
-Conversely, if the entry fee is already higher than optimal for a given $N_P$, an additional increase will lead to an even more suboptimal (implied) entry fee, and thus a lower increase in platform profits.
-
-The consequence of this result is that in the bargaining model, hybrid operation can be optimal, and not only for knife-edge cases.
-Furthermore, and even more strikingly, the platform may find it optimal to invest in its own products even if it has a product disadvantage, if it helps it to negotiate a more optimal entry fee.
+The intuition is that if, for some $N_P$, the implied entry fee is lower than optimal, then the platform investing in more products will bring it closer to the optimal level, and the increase in platform profits will be higher than the increase in the benchmark model.
+Conversely, if the entry fee is already higher than optimal for a given $N_P$, an additional increase will lead to an even more suboptimal (implied) entry fee and, thus, a lower increase in platform profits.
+
+This result implies that in the bargaining model, hybrid operations can be optimal, and not only for knife-edge cases.
+Furthermore, and even more strikingly, the platform may find it optimal to invest in its own products even if it has a product disadvantage, when this investment helps it to negotiate a more optimal entry fee.
 \Cref{fig:optimal_n_p_bargaining} showcases such an example.
-When the platform has a not too large product disadvantage ($I_P = 0.55$ case), the maximum of its profits is reached in the hybrid regime.
-This is doubly unfortunate from a welfare perspective: not only does the platform make an investment that the fringe could have made more efficiently, but it also decreases consumer welfare by reducing the total product variety.
+When the platform has a not-too-large product disadvantage ($I_P = 0.55$ case), its profits are maximized by operating in the hybrid regime.
+This result is doubly unfortunate from a welfare perspective: not only does the platform make an investment that the fringe could have made more efficiently, but it also decreases consumer welfare by reducing the total product variety.
 
@@
 While \Cref{fig:entry_and_fees,fig:platform_profits,fig:welfare} illustrate the main results of this paper under a specific parametrization, many of the insights are more general.
-In particular, the higher-than-proportional decrease in the number of fringe firms as the platform's product variety increases, and the resulting negative effect on consumer welfare, have corresponding theorems that hold for any parametrization (\Cref{prop:equilibrium_benchmark,prop:equilibrium_bargaining}).
-Similarly, the implied entry fee being increasing in the number of the platform's products is a general result (\Cref{prop:implied_entry_fee_comparative}).
+In particular, the higher-than-proportional decrease in the number of fringe firms and the resulting negative effect on consumer welfare have corresponding theorems that hold for any parametrization (\Cref{prop:equilibrium_benchmark,prop:equilibrium_bargaining}).
+Similarly, the implied entry fee increasing in the number of the platform's products is also a general result (\Cref{prop:implied_entry_fee_comparative}).
 
 One aspect that is not general is the fact that the optimal and implied entry fees, in the benchmark and bargaining models, respectively, coincide for some value of $N_P$.
-In the example parametrization, the implied entry fee is lower than what the platform would prefer to set for low values of $N_P$, and higher afterwards.
-There is an optimal platform product variety $N_P^*$ for which the implied entry fee is the same as the optimal entry fee in the benchmark model, and therefore the results of the two models are the same.
-It is possible, however, that even for arbitrarily low values of $N_P$, the implied entry fee is higher than optimal.
+In the example parametrization, the implied entry fee is lower than what the platform would prefer to set for low values of $N_P$ and higher afterward.
+Therefore, there is an optimal platform product variety $N_P^*$ for which the implied entry fee is the same as the optimal entry fee in the benchmark model, and the results of the two models are the same.
+However, it is possible that even for arbitrarily low values of $N_P$, the implied entry fee is higher than optimal.
 In such a case, the platform would like to commit to a lower entry fee to incentivize more fringe entry, but it cannot do so.
@@
 \paragraph{Consequences of the assumptions}
-The results from the benchmark model suggest that the platform's product variety is always weakly beneficial for consumers.
+The results from the benchmark model suggest that the platform having its own products is always weakly beneficial for consumers.
 Furthermore, if the platform's product variety (and thus also the pure marketplace/ hybrid mode decision) was endogenous, an improvement in the platform's product (either higher value or lower cost) would also have a positive effect on consumer welfare.
 This surprising result depends on a number of -- admittedly unrealistic -- assumptions.
-Namely, the lump-sum nature of the entry fee, no entry fee for consumers, and the platform pricing its products as if they were produced by separate sellers.
-Therefore, one should not take this result as a conclusion applicable to the real world, but as a best-case benchmark.
-On the other hand, these assumptions are also why this model is so useful as a benchmark: as I show in the case of the bargaining model, even with these assumptions in place, the platform's product can have negative welfare consequences if the entry fee is set through bargaining.
-
-Nevertheless, the results of the bargaining model do not hinge on the majority of these assumptions.
-For example, the number of consumers could be endogenous, with the platform setting an entry fee for them.
+Namely, the lump-sum nature of the entry fee, no entry fee for consumers, and the platform pricing its products as if separate sellers produced them.
+Therefore, this result should not be taken as a conclusion applicable to the real world but as a best-case benchmark.
+On the other hand, these assumptions are also why this model is so useful as a benchmark: as I show in the case of the bargaining model, even with these assumptions in place, the platform selling its own products can have negative welfare consequences when the entry fee is set through bargaining.
+
+Nonetheless, the results of the bargaining model do not hinge on the majority of these assumptions.
+For example, the number of consumers could be endogenized, with the platform setting an entry fee for them.
 Similarly, the platform could take into account the fact that its product prices affect the demand for its other products.
-These changes would translate into a different, possibly less tractable total profit function, but its main properties (i.e.
-being increasing in the number of platform products and fringe firms) would still hold.
+These changes would translate into a different, possibly less tractable total profit function, but its main properties (notably, being increasing in the number of platform products and fringe firms) would still be the same.
 As long as \Cref{lem:shape_of_fringe_profit} holds, the main results of the bargaining model would also be valid.
@@
 }.
-It is however important that the demand function is such that total profits are increasing in the number of fringe firms.
-Without this, the corresponding cooperative game is not monotone, and the bargaining interpretation is less applicable.
+It is, however, important that the demand function is such that total profits are increasing in the number of fringe firms.
+Without this, the corresponding cooperative game would not be monotone, and the bargaining interpretation would be less applicable.
 In the model presented in the main text, monotonicity arises due to consumers' taste for variety preferences.
-This assumption might also be justified in settingswith network effects \parencite{rochet2003platform}, or when the platform can extract consumer surplus through entry fees or some other mechanism.\footnote{
-    \textcite{chen2008price} demonstrates that under certain circumstances an even more extreme phenomenon might occur: competition may not only increase industry-wide profits, but prices, as well.
+This assumption might also be justified in settings with network effects \parencite{rochet2003platform}, or when the platform can extract consumer surplus through entry fees or some other mechanism.\footnote{
+    \textcite{chen2008price} demonstrates that under certain circumstances, an even more extreme phenomenon might occur: competition may increase not only industry-wide profits but prices, as well.
 }
 
-The other assumption that is crucial for the results is the lump-sum nature of the entry fee.
+The other assumption crucial for the results is the lump-sum nature of the entry fee.
 Without it, the corresponding cooperative game would not have transferable utility, and the Shapley value would not be a meaningful solution concept.
@@
 \paragraph{Relation to the literature}
-Similarly to the existing literature on hybrid platforms, the latter conclusion highlights the possibly problematic aspects of hybrid operation, albeit through a novel channel.
-In \textcite{hagiu2022should}, the negative consequences are due to its incentives to engage in anti-competitive behavior, such as self-preferencing or imitation, but in lieu of those, they argue that hybrid platforms can actually be beneficial.
+Similar to the existing literature on hybrid platforms, this paper highlights the problematic aspects of hybrid operation, albeit through a novel channel.
+In \textcite{hagiu2022should}, the negative consequences are due to its incentives to engage in anti-competitive behavior, such as self-preferencing or imitation.
+However, in lieu of those, they argue that hybrid platforms can be beneficial.
 \textcite{anderson2021hybrid}, on the other hand, shows that even in the absence of such behavior, hybrid platforms can harm consumers, as platforms are inclined to set higher than optimal royalties to create a price advantage for their own products.
-The distortion in their model comes from the percentage-based nature of the entry fee (royalty), incentivizing the platform to set it higher than in the pure intermediary case, to advantage its own products.
+The distortion in their model comes from the percentage-based nature of the entry fee (royalty), which incentivizes the platform to set it higher than in the pure intermediary case to give an advantage to its own products.
 This paper goes one step further.
-Due to the lump-sum nature of the entry fee and platforms pricing their products as if they were produced by separate sellers, the incentive is no more present (as demonstrated by the benchmark model).
-However, I demonstrate that there is another source of distortion when the entry fee is negotiated: a hybrid platform is in a better bargaining than it would be if it had no products on its own.
-This in turn leads to a higher entry fee, and thus lower consumer welfare.
+Due to the lump-sum nature of the entry fee and platforms pricing their products as if they were produced by separate sellers, the latter incentive is no longer present (as demonstrated by the benchmark model).
+However, I demonstrate that there is another source of distortion when the entry fee is negotiated: a hybrid platform is in a better bargaining position than it would be if it had no products on its own.
+This, in turn, leads to a higher entry fee and, thus, lower consumer welfare.
 

### 2024-08-20 src/paper/application.tex
Reword appendix

@@
 In the previous sections, I assumed that the platform and the fringe firms split total profits according to their Shapley values.
-Because of the symmetry property of the Shapley value, this excludes the possibility of players having some kind of innate bargaining power, which is not related to their profit functions.
-In this extension, I will relax this assumption, and assume instead that profits are shared according to \emph{weighed} values.
-These are a generalization of the Shapley value, where each player has a weight $w_i$ that can, in certain settings, be thought of as a parameter describing bargaining power.\footnote{
+The symmetry property of the Shapley value excludes the possibility of players having some innate bargaining power which is not related to their profit functions.
+In this extension, I will relax this assumption and assume instead that profits are shared according to \emph{weighed} values.
+These are a generalization of the Shapley value, where each player has a weight $w_i$ that can, in certain settings, be considered a parameter describing bargaining power.\footnote{
     \textcite{hart1996bargaining} and \textcite{stole1996intra} provide foundations for this interpretation.
@@
 
-As shown in \Cref{sec:cooperative_game_weighted}, the weighted Shapley value, and thus final profits in this setting is given by
+As shown in \Cref{sec:cooperative_game_weighted}, the weighted Shapley value, and thus final profits in this setting, is given by
 \begin{proposition}
@@
 This result is a direct consequence of \Cref{prop:profit_sharing_weighted}.
-It is similar to the non-weighted value in that it is an average of marginal contributions, but now those averages are weighted, with the weight function depending on platform's bargaining weight.
+It is similar to the non-weighted value in that it is an average of marginal contributions.However, now those averages are weighted, with the weight function depending on the platform's bargaining weight.
 
@@
 \end{proof}
-In fact, the limits as $\lambda_P \to 0$ and $\lambda_P \to \infty$ are quite intuitive: in the former case, the platform's profits are zero, while in the latter case it is able to appropriate all profits.
+In fact, the limits as $\lambda_P \to 0$ and $\lambda_P \to \infty$ are quite intuitive: in the former case, the platform's profits are zero, while in the latter case, it can appropriate all of the profits.
 That is, these limits correspond to the platform either receiving or making take-it or leave-it offers.
 
-The example parametrizatrion is the same as in the main model, with the only difference that the platform has a higher innate bargaining power ($\lambda_P = 2$).
-The main result, namely that the platform's product variety has a negative effect on consumer welfare in the hybrid regime, still holds.
-That is, as shown on \Cref{fig:fringe_entry_eq_high_lambda}, total aggregate is decreasing in $N_P$ throughout the hybrid regime, due to the platform's products displacing more fringe products than their total number.
+The example parametrization is the same as in the main model, with the only difference being that the platform has a higher innate bargaining power ($\lambda_P = 2$).
+The main result, namely that increasing the platform's product variety has a negative effect on consumer welfare in the hybrid regime, still holds.
+That is, as shown on \Cref{fig:fringe_entry_eq_high_lambda}, the total aggregate is decreasing in $N_P$ throughout the hybrid regime due to the platform's products displacing more fringe products than their total number.
 
@@
 
-Another major difference pertains to the total profits of the platform as a function of $N_P$.
-It is still true that they are increasing in the number of the platform's products, but now this increase is even slower in the hybrid regime.
-The reason is that the implied entry fee is always higher than the optimal one, therefore an increase the positive effect of an increase in $N_P$ is somewhat counterbalanced by the entry fee becoming even more suboptimal.
+Another significant difference pertains to the total profits of the platform as a function of $N_P$.
+It is still true that they are increasing in the number of the platform's products, but now this increase is slower in the hybrid regime.
+The reason is that the implied entry fee is always higher than the optimal one, therefore the positive effect of an increase in $N_P$ is somewhat counterbalanced by the entry fee becoming even more suboptimal.
 
@@
 
-In the second extension, I consider the case when the other side also participate in the bargaining process.
-This is more plausible in business to business settings, therefore I use the term customers instead of consumers in this section.
+In the second extension, I consider the case when the other side also participates in the bargaining process.
+This is more plausible in business-to-business settings, so I use the term customers instead of consumers in this section.
 Nevertheless, I use the same demand structure as in the main model.
@@
 This extension entails two changes compared to the main model.
-First, the players bargain over the total surplus generated on all sides of the market, not just total profits.
+First, the players bargain over the total surplus generated on all sides of the market, not just the total profits from selling the products.
 Second, the outcomes are assumed to be described by a cooperative game with three types of players: the platform, the fringe firms, and the consumers.
 
-Let us start by deriving total surplus as a function of $N_P, N_F$ and $N_C$ (the number of customers).
+Let us start by deriving total surplus as a function of $N_P, N_F$, and $N_C$ (the number of customers).
 Under the logit-like demand structure described in \Cref{sec:demand}, the total surplus is given by
@@
 \end{proof}
-Note, that this expression is of the form $\Pi(N_P, N_P, N_C) = N_C f(N_P, N_F)$.
+Note that this expression is of the form $\Pi(N_P, N_P, N_C) = N_C f(N_P, N_F)$.
 Furthermore, $f(N_P, N_F) = g(V_P N_P + V_F N_F)$ for an increasing, strictly concave $g$.
@@
 }
-As a consequence, what's good for the platform is also optimal for the customers.
-Therefore, if the platform can choose its mode of operation to maximize its profits, it maximizes the customers' surplus, as well (but not necessarily total surplus).
+As a consequence, what is good for the platform is also beneficial for the customers.
+Therefore, if the platform can choose its mode of operation to maximize its profits, it also maximizes the customers' surplus (but not necessarily total surplus).
 
@@
 Nevertheless, there is an important distinction compared to the previous results.
-While this does lead to a decrease in total surplus, in contrast to the two-sided bargaining case, this does not imply a decrease in the customers' surplus.
-Their share of total surplus is equal to the platform's profits, and thus it is increasing in $N_P$ if and only if platform profits (\Cref{fig:profits_full_surplus_two_sided}) are.
+While this does decrease total surplus, in contrast to the two-sided bargaining case, it does not imply a decrease in the customers' surplus.
+Their share of the total surplus is equal to the platform's profits, and thus, it is increasing in $N_P$ if and only if platform profits (\Cref{fig:profits_full_surplus_two_sided}) are.
 Therefore, customers might prefer hybrid operation to the platform being a pure marketplace.
@@
 This section presents those and the necessary assumptions.
-As the results on the main text are not proven directly, but rather derived from the general results, the proofs are also included here.
+As the results in the main text are not proven directly, but rather derived from the general results, the proofs are also included here.
 
@@
 \end{assumption}
-It can be justified for markets with the following features: (1) all fringe firms are identical, thus only their number matters in terms of total profit, and (2) consumers are also identical (bar their idiosyncratic taste shocks).
+It can be justified for markets with the following features: (1) all fringe firms are identical, so only their number matters in terms of total profit, and (2) consumers are also identical (bar their idiosyncratic taste shocks).
 
@@
 \end{assumption}
-Such profit functions arise in settings in which the profit reduction from increased competition is dominated by extra sales due to increased product variety.
+Such profit functions arise in settings where the profit reduction from increased competition is dominated by extra sales due to increased product variety.
 \Cref{sec:results_discussion} discusses this assumption in more detail.
@@
 \end{assumption}
-It covers the cases in the main text (namely the Shapley value and the weighted value, and three-way bargaining), but is also more general than those.
-In particular, in the platform game, any random order value \parencite{weber1988probabilistic} can be described by such a rule.
+It covers the cases in the main text and the extensions (namely, the Shapley value, the weighted value, and three-way bargaining) but is also more general than those.
+In particular, in the platform game, such a rule can describe any random order value \parencite{weber1988probabilistic}.
 
@@
 I assume that $w_P(s) = w_F(s) \equiv 1$.
-As \Cref{sec:cooperative_game} demonstrates, this corresponds to players. Getting their Shapley values in the end.
-Together with the assumptions on the demand system, one can even derive a closed form expression for the platform's profit share (\Cref{prop:platform_profits_bargaining}).
-The proof if this proposition is given below.
+As \Cref{sec:cooperative_game} demonstrates, this corresponds to players getting their Shapley values.
+Together with the assumptions on the demand system, one can even derive a closed-form expression for the platform's profit share (\Cref{prop:platform_profits_bargaining}).
+The proof of this proposition is given below.
 \begin{proof}[Proof of \Cref{prop:platform_profits_bargaining}]
@@
 
-Apart from the cooperative foundations, one major justification for this profit allocation rule is its intuitive behavior in terms of comparative statics.
+Apart from the cooperative foundations, one primary justification for this profit allocation rule is its intuitive behavior in terms of comparative statics.
 To illustrate this, let us examine what happens when one varies the substitutability between the fringe firms.
-As it turns out, the platform's share increases if the fringe firms are more substitutable.
+As it turns out, the platform's share increases when the fringe firms are more substitutable.
 The following observation demonstrates this idea.
@@
 
-In words, \Cref{prop:outcome_based_bargaining_power} describes two alternative worlds, in which $N_F$ fringe firms (assuming a platform with $N_P$ product variety and $N_C$ consumers) are able to achieve the same total profit level.
+In words, \Cref{prop:outcome_based_bargaining_power} describes two alternative worlds in which $N_F$ fringe firms and a platform with $N_P$ product variety can achieve the same total profit level.
 However, in the case with $\tilde{f}$, the fringe firms are more substitutable to each other in the sense that fewer of them are needed to achieve a given level of profit (see \Cref{fig:outcome_based_bargaining_power}).
 The observation is that, in this situation, the platform's share is indeed higher when the fringe firms are more substitutable.
-This coincides with the intuitive idea that the platform's bargaining power is higher when it does not really mind losing a few fringe sellers.
+This coincides with the intuitive idea that the platform's bargaining power is higher when it does not mind losing a few fringe sellers.
 
@@
 
-Let us now turn to the determination of the equilibrium number of fringe firms.
+Let us now turn to determining the equilibrium number of fringe firms.
 Assume that each firm faces a lump-sum investment cost of $I_F$ to enter the market.\footnote{
-    The results would also hold if the investment cost was non-constant, as long as the marginal cost of investment is weakly increasing.
+    The results would also hold if the investment costs were non-constant, as long as the marginal cost of investment is weakly increasing.
 }
-Thus, total investment cost for the fringe is given by $I_F N_F$.
+Thus, the total investment cost for the fringe is given by $I_F N_F$.
 The equilibrium number of entrants is determined by a free entry condition: in the end, the fringe firms' total profits should be equal to the aggregated investment cost.
@@
 
-Finally, in order to guarantee a unique equilibrium, let us make the following, an additional assumption about the profit function.
-\begin{assumption}
+\begin{assumption}Finally, in order to guarantee a unique equilibrium, let us make the following additional assumption about the profit function.
     \label{ass:single_crossing}
@@
 \end{assumption}
-This assumption essentially guarantees that the profit of the fringe (as a function of the number of entrants) has at most a single crossing with total entry cost (apart from the obvious $N_F=0$ intersection).
-The profit functions presented in the main text satisfy this assumption.
-
-Under the specific demand system and profit sharing rule described in the main text, it can be shown that this assumption is satisfied.
+This assumption essentially guarantees that the profit of the fringe (as a function of the number of entrants) has at most one single crossing with total entry cost (apart from the obvious $N_F=0$ intersection).
+This assumption is satisfied under the specific demand system and profit-sharing rule described in the main text.
 \begin{proof}[Proof of \Cref{lem:shape_of_fringe_profit}]
@@
 
-With \Cref{ass:single_crossing} in place, uniqueness of the equilibrium can be established.
+With \Cref{ass:single_crossing} in place, the uniqueness of the equilibrium can be established.
 \begin{proposition}
@@
 
-The intuition behind this result is that \Cref{ass:single_crossing} ensures that the total profits achieved by the fringe is either concave or hump-shaped.
+The intuition behind this result is that \Cref{ass:single_crossing} ensures that the total profits achieved by the fringe are either concave or hump-shaped.
 Consequently, it has at most one crossing with the -- convex and increasing -- total entry cost function (for $n_F > 0$).
-This particular shape (concave or hump-shaped) is also the main driver for the later results about the comparative statics of equilibrium profits and entry.
+This particular shape (concave or hump-shaped) is also the main driver for the later comparative statics results of equilibrium profits and number of entrants.
 Given that \Cref{ass:free_entry,ass:single_crossing} is satisfied in the model presented in the main text, it immediately follows that the equilibrium in that model is also unique.
@@
 
-This section presents a number of comparative statics that can be derived even in this rather abstract setting.
+This section presents a number of comparative statics results that can be obtained even in this rather abstract setting.
 It contains three sets of results: (1) participants' profits in a partial equilibrium setting, where the number of fringe firms is taken as fixed, (2) equilibrium entry as a function of the platform's product variety, and (3) the platform's profits in general equlibrium.
-Throughout the paper, I use $\frac{\partial X}{\partial N_P}$ to denote partial equilibrium results, while $\frac{\dd X}{\dd N_P} \coloneq \frac{\partial X(N_P, N_F(N_P))}{\partial N_P}$ indicates general equilibrium results, where fringe entry is endogeneous.
+Throughout the paper, I use $\frac{\partial X}{\partial N_P}$ to denote partial equilibrium results, while $\frac{\dd X}{\dd N_P} \coloneq \frac{\partial X(N_P, N_F(N_P))}{\partial N_P}$ indicates general equilibrium results, where fringe entry is endogenous.
 
@@
 \end{proof}
-While it might seem obvious, let us still examine what this result does and does not mean.
-First, remember that $f$ is increasing in both arguments, and $N_F$ is fixed.
+Let us examine what this result does and does not mean.
+First, remember that $f$ is increasing in both arguments, and $N_F$ is assumed to be fixed for the moment.
 Therefore, an increase in $N_P$ also increases the size of the pie the participants bargain over.
-This result states that the slice of the pie that the platform gets increases in this case, too.
-It does not mean, however, that the \emph{relative share} of the pie that the platform gets is also bigger -- increase is only guaranteed in absolute terms.
+This result states that the slice of the pie the platform gets increases in this case, too.
+It does not mean, however, that the \emph{relative share} of the pie that the platform gets is also bigger -- the increase guaranteed only in absolute terms.
 For example, it is possible that for the new, higher value of $N_P$, the complementarities between the fringe firms become stronger, and the platform's bargaining power decreases.\footnote{
@@
 \end{proof}
-In summary, when they are mostly substitutes (the cross-derivatives of $f$ are negative), the fringe's profits decrease as a result of an increase in $N_F$.
-The intuition is that, even though the total size of the pie increases, the bargaining power of the fringe deteriorates so much that its total profits decreases not only in relative, but also in absolute terms (as illustrated in \Cref{fig:increase_N_P_fringe}).
+In summary, when they are primarily substitutes (the cross-derivatives of $f$ are negative), the fringe's profits decrease as a result of an increase in $N_F$.
+The intuition is that, even though the total size of the pie increases, the bargaining power of the fringe deteriorates so much that its total profits decrease not only in relative but also in absolute terms (as illustrated in \Cref{fig:increase_N_P_fringe}).
 On the other hand, when the fringe firms are mostly complements the fringe's profits increase.
 
-As the Shapley value of each player is their average marginal contribution to the total value, this result can best be understood through the lens of marginal contributions.
+As each player's Shapley value is their average marginal contribution to the total value, this result can best be understood through the lens of marginal contributions.
 When the cross derivative is positive, an increase in the platform's product variety increases the marginal contribution of the fringe firms to the total value for any given number of fringe firms.
@@
 
-That is, the equilibrium number of entrants increases as a response to an increase in $N_P$ if the platform and the fringe firms are complements, and decreases if they are substitutes.
+That is, the equilibrium number of entrants increases as a response to an increase in $N_P$ if the platform and the fringe firms are complements and decreases if they are substitutes.
 The underlying reason is again the concave or hump-shaped fringe profit function.
 If $N_F^*$ is an equilibrium, then fringe profits minus entry costs are strictly positive for all $N_F \leq N_F^*$ and strictly negative for all $N_F > N_F^*$.
-Therefore, if an increase in $N_P$ decreases the fringe's profits for every $N_F \geq 0$, equilibrium can be restored by decreasing the number of fringe entrants, (and vice versa for the other case).
-This is also related to the concept of strategic complementary and substitutability, which also depends on the cross-derivatives (i.e. the supermodularity or submodularity) of the profit function.
-
-Based on this general result, the corresponding on in the main text follows immediately.
+Therefore, if an increase in $N_P$ decreases the fringe's profits for every $N_F \geq 0$, equilibrium can be restored by decreasing the number of fringe entrants (and vice versa for the other case).
+This result is related to the concept of strategic complementary and substitutability, which also depends on the profit function's cross-derivatives (i.e., supermodularity or submodularity).
+
+Based on this general result, the corresponding one in the main text follows immediately.
 \begin{proof}[Proof of \Cref{prop:fringe_profits_partial}]
@@
 In the following, I assume that the profit function has an additive form.
-Intuitively, this means that -- in terms of total profits generated -- the platform's and the fringe firms' products are substitutable to each other according to some constant ratio.
+Intuitively, this means that, in terms of total profits generated, the platform's and the fringe firms' products are substitutable according to some constant ratio.
 \begin{assumption}
@@
 The first part of this proposition is a stronger version of \Cref{cor:fringe_entry}.
-It states that, not only does the equilibrium number of fringe firms decrease as a response to an increase in $N_P$, but it establishes a lower bound for this decrease.
-And, as the second part shows, this bound is sufficient to guarantee that the total size of the pie ($\Pi(N_P, N_F, N_C)$) also decreases in equilibrium.
-
-This result has particularly strong implications in models where total profits (or total product variety) has a monotone relationship with consumer welfare, such as those in \textcite{anderson2020aggregative}.
-The demand system presented in the main text also has this property, and thus the results of this proposition apply to it as well.
+It states that, not only does the equilibrium number of fringe firms decrease as a response to an increase in $N_P$, but there is a lower bound for this decrease.
+Moreover, as the second part shows, this bound is sufficient to guarantee that the total size of the pie ($\Pi(N_P, N_F, N_C)$) also decreases in equilibrium.
+
+This result has powerful implications in models where total profits (or total product variety) have a monotone relationship with consumer welfare, such as those in \textcite{anderson2020aggregative}.
+The demand system presented in the main text also has this property, and thus, the results of this proposition apply to it, as well.
 \begin{proof}[Proof of \Cref{prop:platform_profits_comparative_benchmark}]
@@
 \paragraph{Platform profits -- general equilibrium}
-Now let us consider how the platform's product variety impacts its total profits, also taking into account its effect on the number of fringe entrants.
+Now, let us consider how the platform's product variety impacts its total profits, while also taking into account its effect on the number of fringe entrants.
 While \Cref{prop:share_of_platform} establishes that the platform's profits increase in its own product variety, it is not a general equilibrium result.
-In particular, we know that increasing the platform's product variety leads to a decrease in the number of fringe entrants, and in total profits.
+In particular, we know that increasing the platform's product variety decreases the number of fringe entrants and total profits.
 It would be conceivable that this decrease in entry is so large that the platform's profits decrease as well.
 
-While I do not have a general result for the platform's profits in equilibrium, useful can be made.
-No matter the form of the profit function, the platform's profits always prefers more fringe firms to fewer in the bargaining model.
+While I do not have a general result for the platform's profits in equilibrium, useful observations can be made.
+No matter the form of the profit function, the platform always prefers having more fringe firms to fewer in the bargaining model.
 The following proposition formalizes this idea.
@@
 This observation then makes characterizing the profit-maximizing platform product variety in \Cref{sec:endogenizing_n_p} easier, as one does not have to worry about comparing the different regimes in the case of the bargaining model.
-If, for a given $N_P$, hybrid mode would be feasible, then it is also optimal compared to being a pure retailer.
+If hybrid mode is be feasible for a given $N_P$, then it is also optimal compared to being a pure retailer.
 This result allows us to prove an important result from the main text about the platform's profits as a function of its number of products.
@@
 \label{sec:lemmas}
-This subsection contains a couple of lemmas that are, while not very interesting on their own, necessary for the proofs in the previous sections.
-Furthermore, it contains the proofs of the results presented in \Cref{sec:results_benchmark}, as they are not related to the bargaining framework, and are thus omitted from the previous sections.
-
-The first lemma is helpful for establishing whether \Cref{ass:single_crossing} holds under a certain $f$ function.
-It states that showing that it holds for any affine transformation of $f$ is sufficient.
+This subsection contains a couple of lemmas that, while not very interesting on their own, are necessary for the proofs in the previous sections.
+Furthermore, it contains the proofs of the results presented in \Cref{sec:results_benchmark}, as they are unrelated to the bargaining framework and are thus omitted from the previous section.
+
+The first lemma helps establish whether \Cref{ass:single_crossing} holds under a specific function $f$.
+It states that it is sufficient to show that it holds for some affine transformation of $f$.
 \begin{lemma}
@@
 I proceed in two steps.
-First, I provides non-cooperative microfoundations for using the cooperative approach in the first place.
-Afterwards, I describe the aforementioned cooperative game in full formality, and derive the (weighted) Shapley value of this game.
+First, I provide non-cooperative microfoundations for using the cooperative approach as a reduced-form way of describing bargaining outcomes.
+Afterwards, I describe the cooperative game in full formality and derive the (weighted) Shapley value of this game.
 
@@
     The research agenda aiming to find links between cooperative and non-cooperative game theory, started by nash1953two
-}, there have been a number of papers proposing microfoundations for the Shapley value in terms of non-cooperative, bargaining-related games \parencite[e.g.][]{gul1989bargaining,winter1994demand,hart1996bargaining,stole1996intra}.
-The cooperative platform game described in \Cref{sec:cooperative_game} satisfies the assumption for a number of these models, and thus any of those could be used to build microfoundations for the platform game.
-Among those, I will focus on \textcite{stole1996intra} for the reason that it specifically pertains to a setting with one indispensable player and many small players, just like the current paper.
+}, there have been several papers proposing microfoundations for the Shapley value in terms of non-cooperative, bargaining-related games \parencite[e.g.][]{gul1989bargaining,winter1994demand,hart1996bargaining,stole1996intra}.
+The cooperative platform game described in \Cref{sec:cooperative_game} satisfies the assumption for many of those models.
+Any one of those could be used to build microfoundations for the platform game.
+I will focus on \textcite{stole1996intra} because it specifically pertains to a setting with one indispensable player and many small players, just like the current paper.
 
 The model in \textcite{stole1996intra} is phrased in terms of intra-firm bargaining between the workers and the firm itself.
-The workers are assumed to have a fixed outside option, and the firm is the indispensable player.
-This translates directly to the platform game, with the platform being the indispensable player, and fringe firms having a zero outside option.
-Furthermore, in \textcite{stole1996intra}, the bargaining outcome is interpreted as the wage for the workers.
-In the current setting, this would translate to bargaining over profit shares.
-However, as I argue later on, it is equivalent to bargaining over entry fees.
-While this section focuses on the main model, with two-sided bargaining, and the Shapley value as the solution, the same logic can be applied to the extensions presented in \Cref{sec:extensions}, based on sections 3.1 and 3.2 of \textcite{stole1996intra}.
+The workers are assumed to have a fixed outside option, and the firm is an indispensable player.
+This translates directly to the platform game, with the platform being the indispensable player and fringe the firms' outside option having zero value.
+Furthermore, in \textcite{stole1996intra}, the bargaining outcome is interpreted as workers' wages.
+In the current setting, this translates to bargaining over profit shares.
+However, as I argue later, it is equivalent to bargaining over entry fees.
+While this section focuses on the main model with two-sided bargaining and the Shapley value as the solution, the same logic can be applied to the extensions presented in \Cref{sec:extensions}, based on sections 3.1 and 3.2 of \textcite{stole1996intra}.
 Finally, the model is defined for a finite number of small players.
@@
 First, a random order is determined for the fringe firms.
-This order will remain fixed throughout the bargaining phase
+This order will remain fixed throughout the bargaining phase.
 
@@
 This bilateral negotiation follows the alternating offer procedure described in \textcite{binmore1986nash}.
-One of the two players is chosen as a proposer, and can propose an entry fee for the given firm: $K_{F_i}$.
+One of the two players is chosen as the proposer and can propose an entry fee for the given firm: $K_{F_i}$.
 The other player can either accept or reject the proposal.
@@
 If the proposal is accepted, the negotiation moves on to the next fringe firm.
-If it is rejected, with probability $1-\rho$, the other player becomes the proposer, and the negotiation continues.
+If it is rejected, then with probability $1-\rho$, the other player becomes the proposer, and the negotiation continues.
 Finally, with probability $\rho$, the negotiations break down, and the fringe firm is eliminated from the rest of the game.
-Crucially, after a breakdown occurs, all of the previous offers are voided, and the platform and the remaining fringe firms start the negotiation process from the beginning (following the same, pre-determined order, but skipping the eliminated firms).
-
-This bargaining process is repeated until all fringe firms have either accepted an offer or been eliminated.
-\Cref{fig:bargaining_microfoundations} provides an illustration of the bargaining process, and how it fits into the broader game.
+Crucially, after a breakdown occurs, all previous agreements are void, and the platform and the remaining fringe firms start the negotiation process from the beginning (following the same pre-determined order, but skipping the eliminated firms).
+
+This bargaining process is repeated until all fringe firms either accept an offer or are eliminated.
+\Cref{fig:bargaining_microfoundations} illustrates the bargaining process and how it fits into the broader game.
 Theorem 2 in \textcite{stole1996intra} shows that regardless of the ordering of the fringe firms, the unique subgame perfect equilibrium of this game is the Shapley value of the cooperative game.
-Note, that this result is not only true in expectation: conditioning on any ordering of the fringe firms, the result still holds.
-
-The final piece that is needed to establish the interpretation in terms of entry fees is that for any given configuration of firms emerging from the bargaining process, and, crucially, regardless of the agreed upon entry fees, the unique equilibrium of the subsequent game is the one described in \Cref{sec:results_demand}.
-According to the previous theorem, players want to agree on a contract such that their final, total profits $\pi^t_{F_i}$ are equal to their Shapley value ($\varphi_{F_i}$).
+Note that this result is not only true in expectation: conditioning on any ordering of the fringe firms, the result still holds.
+
+The final piece that is needed to establish the interpretation in terms of entry fees is that for any given configuration of firms emerging from the bargaining process, and, crucially, regardless of the agreed-upon entry fees, the unique equilibrium of the subsequent game is the one described in \Cref{sec:results_demand}.
+According to the previous theorem, players want to agree on a contract such that their final total profits $\pi^t_{F_i}$ are equal to their Shapley value ($\varphi_{F_i}$).
 Given any equilibrium sales profits ($\pi^v_{F_i}$), they can achieve it by setting the entry fees to $K_{F_i} = \varphi_{F_i} - \pi^v_{F_i}$.
-Finally, \Cref{sec:cooperative_game} and \Cref{sec:results_demand} establish that both the Shapley value and the equilibrium sales profits are identical for each fringe firms, and thus a single, common entry fee $K_F$ will be agreed upon.
+Finally, \Cref{sec:cooperative_game} and \Cref{sec:results_demand} establish that both the Shapley value and the equilibrium sales profits are identical for each fringe firm, and thus a single common entry fee $K_F$ will be agreed upon.
 
@@
 
-Now let us examine how the profit sharing rule from \Cref{ass:profit_sharing} can be derived from various cooperative games.
-In each of the following subsections, I formally define a cooperative game that models the platform setting, and derive the (weighted) Shapley values of the various players.
+Now let us examine how the profit sharing rule from \Cref{ass:profit_sharing} can be derived from the random order values of cooperative games.
+In each of the following subsections, I formally define a cooperative game that models the platform setting and derive the (weighted) Shapley values of the various players.
 I show that they correspond to the formulas given in \Cref{ass:profit_sharing}, with a specific choice of weight functions $w_P$ and $w_F$ for each case.
@@
 Finally, I consider the case when the consumers also participate in the bargaining process, and derive the corresponding Shapley values.
-
-\subsubsection{One-sided case}
-\label{sec:cooperative_game_one_sided}
-
-In the first setting, the platform and the fringe firms bargain over the total profits they generate together, and the consumers are not included in the negotiations.
-This corresponds to the model in the main text.
-The following cooperative game describes this case.
-
-Consider the game $\mathcal{G} = (\mathcal{N}, v)$, characterized by the set of players $\mathcal{N}$ and its characteristic function $v$.
-The set of players consists of the platform plus the fringe firms: $\mathcal{N} = \{P, F_i\}, i \in [0, N_F]$.
-Because the platform is indispensable, the value of a coalition $S$ is zero without the platform, and depends on the number of fringe firms otherwise:
+Now let us examine how the profit sharing rule from \Cref{ass:profit_sharing} can be derived from the random order values of cooperative games.
+In each of the following subsections, I formally define a cooperative game that models the platform setting, and derive the (weighted) Shapley values of the various players.
+I show that they correspond to the formulas given in \Cref{ass:profit_sharing}, with a specific choice of weight functions $w_P$ and $w_F$ for each case.
+
+I start with the simplest case: one-sided bargaining and the usual Shapley value \parencite{shapley1953additive}.
+Then, I look at weighted values \parencite{weber1988probabilistic} in the same cooperative game.
+Finally, I consider the case when the consumers also participate in the bargaining process and derive the corresponding Shapley values.
 \begin{align*}
@@
 
-Now let us generalize the previous result, and assume instead that players' shares are described by their weighted values.
-As before, let us start by formally describing the cooperative game.
+Now, let us generalize the previous result by assuming that players' shares are described by their weighted values.
+As before, I start by formally describing the cooperative game.
 The set of players and the characteristic function are the same as in \Cref{sec:cooperative_game_one_sided}, but now the game is additionally endowed with a weight system $\mathbf{\lambda} = \{\lambda_P, \lambda_{F}(i)\}$.
@@
 An example for this is \Cref{sec:two_sided}
-In such a case, cooperative game describing can be formalized as follows.
+In such a case, the underlying cooperative game can be formalized as follows.
 
 The set of players consists of the platform plus the fringe firms: $\mathcal{N} = \{P, F_i, C_j\}, i \in [0, N_F], j \in [0, N_C]$.
-The value of a coalition $S$ is zero without the platform, and depends on the number of fringe firms otherwise:
+The value of a coalition $S$ is zero without the platform and depends on the number of fringe firms otherwise:
 \begin{align*}
@@
 }
-This foreshadows the idea that -- even though it might not be welfare-maximizing -- what's good for the platform might also good for the consumers in the two-sided case.
+This foreshadows the idea that, even though it might not be welfare-maximizing, what is good for the platform might also benefit the consumers in the two-sided case.
 Finally, as in both examples before, these values satisfy \Cref{ass:profit_sharing} with $w_P(s) = s$ and $w_F(s) = s^2$.
 
-% \section{The platform's product pricing assumption}
-% \label{sec:separate_pricing}
-
-% This section explores the consequences of relaxing the assumption that the platform prices its own products as if they were priced by separate entities.
-% So let us now assume, that when pricing product $P_i$, the platform does consider its effect on the sales of its other products.
-
-% For the fringe firms, the problem is the same as before: they choose their prices to maximize their profits, while not having an effect on total aggregate.
-% Thus, the price they set is the same as before: $p_{F_i} = c_{F_i} + \mu$.
-
-% The same is not the case with the platform.
-% When pricing its products, the platform must consider the effect of its prices on the sales of its other products, through its effects on the aggregate.
-% The end result is that the platform will set higher prices than under the separate pricing assumption, because it internalizes the effect of one product's price on the demand for the other products.
-% In particular, it can be shown that the optimal price for the platform's product is
-% \begin{align*}
-%     p_P^* = c_P + \mu + W_0\left( \frac{N_P V_P}{N_F V_F + 1} \right),
-% \end{align*}
-% where $W_0$ is the principal branch of the Lambert $W$ function.
-
-% Given an aggregate of size $A$, the platform's profits are
-% \begin{align*}
-%     \dots
-% \end{align*}
-
 \end{document}

### 2024-08-20 src/paper/theory.tex
Improve wording and other minor corrections

@@
 \begin{abstract}
-    This paper investigates the idea of using random order values, a concept from cooperative game theory, to model bargaining outcomes in games with a small number of central players and a continuum of fringe players.
+    This paper investigates using random order values, a concept from cooperative game theory, to model bargaining outcomes in games with a small number of central players and a continuum of fringe players.
     Two important special cases of random order values are discussed in detail: the Shapley value and the weighted value.
-    I show that this approach proves to be very tractable, and leads to results that are in line with one's intuitive expectations about bargaining outcomes.
-    Thus, it can be a useful tool in modelling situations where one does not want to attribute all the bargaining power to one side of the market, and at the same time would like to avoid having to deal with an explicit multi-stage bargaining game.
+    This approach proves to be very tractable and leads to results that are in line with one's intuitive expectations about bargaining outcomes.
+    Thus, it can be a valuable tool in modelling situations where one does not wish to attribute all the bargaining power to one side of the market and, at the same time, would like to avoid having to deal with an explicit multi-stage bargaining game.
     The utility of this approach is demonstrated via a simple model of a two-sided market.
@@
 
-Using cooperative game theory to model bargaining outcomes has quite a few precedents in the industrial organization literature.
-This is in part motivated by the appealing properties of the resulting gain distributions and their tractability.
+Using cooperative game theory to model bargaining outcomes has quite a few precedents in the economics literature.
+This is, in part, motivated by the appealing properties of the resulting gain distributions and their tractability.
 Furthermore, this practice also has solid theoretical justifications thanks to the long line of studies showing that various cooperative solution concepts are related to certain dynamic, non-cooperative bargaining games.\footnote{
-    For example, \textcite{gul1989bargaining,winter1994demand,hart1996bargaining,inderst2003bargaining} propose various extensive-form bargaining games in which the equilibrium corresponds to players' Shapley-values.
+    For example, \textcite{gul1989bargaining,winter1994demand,hart1996bargaining,inderst2003bargaining} propose various extensive-form bargaining games in which the equilibrium corresponds to players' Shapley values.
     For results specifically for games bargaining with one indispensable player, see \textcite{stole1996intra}.
@@
 
-For practical applications, the case of a small number of central players and a large number of fringe ones is particularly important in a number of settings.
+The case of a small number of central players and a large number of fringe ones is particularly important in several settings.
 Examples include intra-firm ownership structures \parencite{hart1990property}, wage bargaining \parencite{stole1996intra,stole1996organizational,levy1997individual}, collusion and mergers \parencite{segal2003collusion} and upstream-downstream supply chains \parencite{inderst2003bargaining,montez2007downstream}.
-The study of multi-sided markets (or platforms) is also a good fit for this modeling approach, as the platforms are often assumed to be indispensable for the various sides to interact.\footnote{
+The study of multi-sided markets (or platforms) is also a good fit for this modeling approach, as platforms are often assumed to be indispensable for the various sides' interaction.\footnote{
     \textcite{huang2022shapley} is amongst the very few examples of using cooperative game theory in this setting.
@@
 This paper provides a general framework for modeling bargaining outcomes in this setting.
-By relying on the rather concept of random order values, I highlight the common themes between various results found in more applied papers.
+By relying on the general concept of random order values, I highlight the common themes between various results found in more applied papers.
 I demonstrate that these values are described by tractable expressions and have geometric interpretations.
-Just as importantly, I show that the outcomes are in line with one's intuitive expectations of bargaining power in such situations.
-
-Apart from the general framework, this paper also extends the results of the related literature in a number of ways.
-Most importantly, I relax the usual assumption that there is only one indispensable player, and show how the results can be generalized when (1) there are multiple central players, and (2) when the central player is not completely indispensable.
+Just as importantly, I show that the outcomes align with one's intuitive expectations of bargaining power in such situations.
+
+Apart from the general framework, this paper extends the results of the related literature in several ways.
+Most importantly, I relax the usual assumption that there is only one indispensable player, and show how the results can be generalized when (1) there are multiple central players and (2) when the central player is not completely indispensable.
 Further contributions include new results for the case of heterogeneous fringe players.
 In particular, I provide results for weighted values in the case of heterogeneous fringe players, which is a novel contribution to the literature.
-Furthermore, I highlight how the value of the fringe players can be expressed in terms of their marginal contributions, i.e. the partial derivatives of the production function.
+Furthermore, I highlight how the value of the fringe players can be expressed in terms of their marginal contributions (i.e. the partial derivatives of the production function).
 
 I rely on an infinite-player (oceanic game) version of these models, where fringe players are represented as a continuum.
-As is often the case in economics, this infinite-player approximation turns out to be more tractable than the  finite-player model, while retaining the desirable features of the latter.
-For example, the resulting profit shares depend on the production function similarly to the finite-player case, while becoming continuous and differentiable functions of the size of the fringe.
-This can be useful when embedding these results into more complex models.
-
-The results presented in this paper can be used as a tool-kit for embedding bargaining outcomes into more complex models.
-To showcase the utility of this approach, I present simple model of two-sided markets.
-\textcite{stancsics2023hybrid} provides a more full-fledged example of such an application, where the results of this paper are used to model the bargaining outcomes in a market with a hybrid platform.
+As is often the case in economics, this infinite-player approximation is more tractable than the finite-player model while retaining the latter's desirable features.
+For example, the resulting profit shares depend on the production function, similar to how they do in the finite player case.
+At the same time, they are continuous and differentiable functions of the size of the fringe.
+The latter can be useful when embedding these results into more complex models.
+
+The results presented in this paper can be used as a toolkit for embedding bargaining outcomes into more complex models.
+To showcase the utility of this approach, I present a simple model of two-sided markets.
+\textcite{stancsics2023hybrid} provides a more full-fledged example of such an application, which relies on the results of the current paper to model bargaining outcomes in a market with a hybrid platform.
 
@@
 Cooperative games with a finite number of atomic players and a continuum of non-atomic ones are called mixed or oceanic games \parencite{milnor1978values}, and have been studied in the cooperative game theory literature.
-Generally, papers in this line of research focus on fundamental questions, such as existence and uniqueness of the value \parencite{hart1973values}, and whether the various ways of defining it\footnote{
+Generally, papers in this line of research focus on fundamental questions, such as the existence and uniqueness of the value \parencite{hart1973values}, and whether the various ways of defining it\footnote{
     One can characterize the value of the oceanic game directly, relying on a set of axioms (axiomatic approach).
-Alternatively the value of an infinite-player game can also be defined as the limit of the value of a series of finite-player games (asymptotic approach).
+Alternatively, the value of an infinite-player game can also be defined as the limit of the value of a series of finite-player games (asymptotic approach).
 } lead to the same result \parencite{fogelman1980asymptotic}.\footnote{
-    \textcite{hart1973values} shows that in the case of mixed games, the usual axioms do not in general characterize a unique value.
-    However, \textcite{fogelman1980asymptotic} demonstrates that, for a quite large subset of games, the asymptotic approach leads to one specific element from the set characterized by the axiomatic approach.
+    \textcite{hart1973values} shows that in the case of mixed games, the usual axioms do not, in general, characterize a unique value.
+    However, \textcite{fogelman1980asymptotic} demonstrates that, for a large subset of games, the asymptotic approach leads to one specific element from the set characterized by the axiomatic approach.
 }
 My aim with this paper is both more general and more specific in certain aspects.
-For one, I focus on the asymptotic approach, and within that, a specific way of approximating the infinite game of interest.
-This is motivated by the fact that I am not interested in the oceanic game per se, but rather in its ability to approximate finite-player games.
-Furthermore, I restrict my attention to a specific, but economically important subset of games: those with one, or a small number of central players, and a continuum of fringe players consisting of a finite number of types.
-These two restrictions in turn allow me to go beyond the Shapley value, and obtain results for a more general set of solution concepts: random order values.
+For one, I focus on the asymptotic approach and, within that, a specific way of approximating the game of interest.
+This is motivated by the fact that I am not interested in the oceanic game per se but rather in its ability to approximate finite-player games.
+Furthermore, I restrict my attention to a specific but economically significant subset of games: those with one (or a small number of) central player(s) and a continuum of fringe ones.
+These two restrictions allow me to go beyond the Shapley value and obtain results for a more general set of solution concepts: random order values.
 Additionally, instead of looking at general results, such as existence, I can provide and interpret explicit expressions for the values of the various players.
 
-The other strand of research that is closely related to this paper belongs to the industrial organization literature.
-Despite the theoretical appeal and tractability of oceanic games, they, in general, saw remarkably little use in the industrial organization, and, more generally, applied economics.
-Examples of this include \textcite{stole1996intra, stole1996organizational}\footnote{
+The other strand of research closely related to this paper belongs to the industrial organization literature.
+Despite their theoretical appeal and tractability, oceanic games saw remarkably little use in industrial organization and, more generally, applied economics.
+Rare examples of such applications include \textcite{stole1996intra, stole1996organizational}\footnote{
     \textcite{stole1996intra} also provides microfoundations for using the Shapley value and the weighted value in a bargaining setting with one indispensable player.
-} and \textcite{levy1997individual}, which use the Shapley value to model wage bargaining under the assumption of divisible labor (continuum of workers).
-
-The present paper contributes to this literature by generalizing its results, and highlighting certain general properties of the various values in the context of such games.
+} and \textcite{levy1997individual}, which use the Shapley value to model wage bargaining under a divisible labor assumption (continuum of workers).
+
+The present paper contributes to this literature by generalizing its results and highlighting some general properties of the various values in the context of such games.
 The latter is achieved by relying on the concept of random order values, which includes the Shapley value and the weighted value as special cases.
@@
 Finally, the example application presented to demonstrate the usefulness of the proposed approach is based on the seminal work of \textcite{armstrong2006competition} on multi-sided markets.
-Thus, despite the main results being presented in an abstract setting, this paper also has some minor contributions towards better understanding the functioning of multi-sided markets.
+Thus, despite the main results being presented in an abstract setting, this paper also has some minor contributions towards better understanding the functioning of platform economies.
 
@@
 In \Cref{sec:one_sided}, I present the main results for the case of identical fringe players.
-It includes the generalizations for the case of not completely indispensable big players.
-\Cref{sec:many_sided} extends some of those results to the case of heterogeneous fringe players.
+It includes generalizations that relax the assumption about the indispensability of the central player.
+\Cref{sec:many_sided} then extends many of those results to the case of heterogeneous fringe players.
 \Cref{sec:application} provides an example application of the results to a simple model of a two-sided market.
@@
 In this section, I examine the case of identical fringe players.
-I start with the case of one, indispensable big player, and relax this assumption in \Cref{sec:extensions}.
-Such a game can represent, for example, a (one-sided) platform and a number of potential entrants, where the entrants can only reach their prospective consumers through the platform, or a vertical supply chain with one upstream producer and a number of downstream sellers.
+I start with the case of one indispensable big player and then relax this assumption in \Cref{sec:extensions}.
+Such a game can represent, for example, a (one-sided) platform and several potential entrants, where the entrants can only reach their prospective consumers through the platform, or a vertical supply chain with one upstream producer and many downstream sellers.
 Let us start by defining the cooperative game that describes this situation.
@@
 \end{align*}
-The function $f$ (henecforth also referred to as the production function) then characterizes this game, and determines the distribution of the value between the big player and the fringe.
+The function $f$ (henceforth the production function) then characterizes this game and determines the distribution of the value between the big player and the fringe.
 
@@
 The latter is a key property of cooperative games, as it ensures that it always pays off to form the grand coalition (i.e., the coalition that includes all players).
-Furthermore, in the context of bargaining, these properties provide some theoretical support for using the Shapley-value or the weighted value to represent bargaining outcomes, as many results creating a link between non-cooperative bargaining games and the values of cooperative games often rely on these assumptions.\footnote{
+Furthermore, in the context of bargaining, these properties provide theoretical support for using the Shapley value or the weighted value to represent bargaining outcomes, as many results that create a link between non-cooperative bargaining games and the values of cooperative games rely on these assumptions.\footnote{
     For example, the results in \textcite{gul1989bargaining} rely on superadditivity, while monotonicity suffices for \textcite[]{hart1996bargaining}.
@@
 
-As the next proposition shows, characterizing monotonicity and superadditivity is extremely straightforward in this setting.
+As the following proposition shows, characterizing monotonicity and superadditivity is straightforward in this setting.
 \begin{proposition}
@@
 \end{proposition}
-The intuition behind this result is quite straightforward.
+The intuition behind this result is relatively straightforward.
 As player $P$ is necessary to create any value, no two disjoint coalitions can both achieve a positive value.
@@
     This assumption is not entirely innocuous.
-    For example, having more small firms could in theory lead to stronger competition, decreasing total profits.
+    For example, having more small firms could, in theory, lead to stronger competition, decreasing total profits.
     However, it often holds in models with network effects \parencite{rochet2003platform} or with consumers having taste for variety \parencite{anderson2020aggregative}.
@@
 As a side note, it also ensures that the game is of bounded variation, and thus the main theorem in \textcite{fogelman1980asymptotic} applies.
-Namely, the asymptotic and the axiomatic approach of characterizing the Shapley-value of the game both lead to the same result\footnote{
+Namely, the asymptotic and the axiomatic approach of characterizing the Shapley value of the game both lead to the same result\footnote{
     More precisely, the asymptotic value coincides with the axiomatic one derived using the uniform distribution.
@@
 }.
-This result could also be used to prove the main proposition for the Shapley value (\Cref{prop:one_sided}) instead of the direct proof provided in \Cref{sec:proofs}.
+This result observation can also be used to prove the main proposition about the Shapley value (\Cref{prop:one_sided}) instead of the direct proof provided in \Cref{sec:proofs}.
 
@@
 
-Random order values are a class of cooperative solution concepts characterized by efficiency, monotonicity, linearity and the null-player axiom \parencite{weber1988probabilistic}.
+Random order values are a class of cooperative solution concepts characterized by efficiency, monotonicity, linearity, and the null-player axiom \parencite{weber1988probabilistic}.
 That is, they are a generalization of the Shapley value, with the axiom of symmetry being relaxed.
-Another way to think about them is that for they can be defined as the average marginal contribution of player to all possible coalitions, where the average is taken according to some probability distribution over the permutations of the players.
+Another way to think about them is that they can be defined as the average marginal contribution of a player to all possible coalitions, where the average is taken according to some probability distribution over the players' permutations.
 
@@
 
-Random order values are of interest for a number of reasons.
+Random order values are of interest for several reasons.
 First, they are a natural extension of the Shapley value and the weighted value.
-Furthermore, they provide a convenient framework, of which all subsequent results (Shapley value, weighted value, multiple central players) are special cases of.
-
-For the remainder of the paper, let us use the following notation: $\varphi_P^n$ denotes the (depending on section, Shapley, weighted or random order) value of player $P$ in the game with players $N = \{P, A_1, \dots, A_n\}$.
+Furthermore, they provide a convenient framework, of which all subsequent results (Shapley value, weighted value, multiple central players) are special cases.
+
+For the remainder of the paper, let us use the following notation: $\varphi_P^n$ denotes the (depending on the section, Shapley, weighted or random order) value of player $P$ in the game with players $N = \{P, A_1, \dots, A_n\}$.
 Then, formally,
@@
 
-Now let us look at the asymptotic limit of this expression, as the number of fringe players goes to infinity.
+Now, let us look at the asymptotic limit of this expression as the number of fringe players goes to infinity.
 The following proposition demonstrates the main idea of this paper: even as the number of fringe players goes to infinity, the value of the big player does not converge to the total worth of the grand coalition, $f(1)$.
 Or, in other words, the fringe, even when its members are infinitesimally small, still retains some bargaining power.
-As a consequence, the continuous fringe model can be thought of as a more tractable approximation of bargaining between a finite number of fringe players.
+As a consequence, the continuous fringe model can be considered a more tractable approximation of bargaining between a finite number of fringe players.
 
@@
 This result has an immediate interpretation in terms of marginal contributions.
-Remember, that player $P$ is indispensable for creating value.
-Therefore, for any coalition of fringe players, the marginal contribution of player $P$ is the total value that the coalition can generate $P$ included.
-Player $P$'s then is its average marginal contribution, which boils down to the expected value that a coalition can generate conditional on player $P$ being in it.
-
-Now let us turn to the value of the fringe.
+Remember that player $P$ is indispensable for creating value.
+Therefore, for any coalition of fringe players, the marginal contribution of player $P$ is the total value that the coalition can generate with $P$ included in it.
+Player $P$'s average marginal contributionthen boils down to the expected value that a coalition can generate conditional on player $P$ being in it.
+
+Now, let us turn to the value of the fringe.
 The following corollary shows that the aggregated value of the fringe remains positive even in the limit.
-In other words, even though the fringe players become smaller and more numerous, they do not lose all of their bargaining power, and still end up with a positive payoff in the end.
+In other words, even though the fringe players become smaller and more numerous, they do not lose all their bargaining power and still end up with a positive payoff.
 \begin{corollary}
@@
 
-It also provides us with two ways of thinking about the value of the fringe.
-First, due to random order values being efficient, it can be thought of as the leftover from the total value after subtracting the value of the big player.
+This corollary also provides two ways of thinking about the value of the fringe.
+First, because random order values are efficient, the fringe's share can be thought of as the leftover from the total value after subtracting the value of the big player.
 Alternatively, as the second part of the corollary demonstrates, it is also related to the marginal contributions of the fringe agents.
-This marginal contribution is the derivative of the production function with respect to the mass of fringe players (i.e., the effect of adding an infinitesimally small player to the coalition), multiplied by the probability of the central player appearing before the fringe player (otherwise the marginal contribution is zero, as the central player is indispensable).
-The second interpretation is particularly useful when thinking about the value of the fringe in the setting with heterogeneous fringe firms.
+This marginal contribution is the derivative of the production function (i.e., the effect of adding an infinitesimally small player to the coalition) multiplied by the probability of the central player appearing before a given fringe player (otherwise, the marginal contribution would be zero, as the central player is indispensable).
+The second interpretation is particularly useful when thinking about the value of the fringe in a setting with heterogeneous fringe firms.
 
 It also follows immediately from the previous proposition that (for a fixed total pie size $f(1)$) player $P$ gets a larger share when $f(t)$ is larger for every $t$.
-That is, when only a relatively small fraction of the fringe is needed to create a large part of the total potential surplus, then player $P$ is able to appropriate a larger share of the total value.
-This result aligns with the intuition that player $P$ has a better bargaining position in this case, than if only coalitions with most of the fringe firms on board were able to obtain high values.
-
-In certain settings, this can also be interpreted as the degree of complementarity or substitutability between the fringe players.
+That is, when only a relatively small fraction of the fringe is needed to create a large part of the total potential surplus, player $P$ can appropriate a larger share of the total value.
+This result aligns with the intuition that player $P$ has a better bargaining position in this case than if only coalitions with most of the fringe firms on board could create considerable value.
+
+In specific settings, this property of the production function can also be interpreted as the degree of complementarity or substitutability between the fringe players.
 For example, imagine that the fringe consists of a set of firms producing one product each, and the central player is necessary for this product to be sold or created.\footnote{
-    For example, the central player could be a platform that connects the fringe firms with consumers, or a provider of a key input.
-}
-When the fringe firms are substitutes, then additional ones add less value to the total pie.
-Therefore, relatively few of them are needed to create most of the value, and the central player can appropriate a larger share.
+    For example, the central player can be a platform that connects the fringe firms with consumers, or the provider of a key input.
+}
+When the fringe firms are substitutes, each additional one adds less value to the total pie.
+Therefore, relatively few are needed to create most of the value, and the central player can appropriate a larger share.
 Conversely, when the fringe firms are complements, the fringe firms are in a better bargaining position, and can obtain a larger share of the total value.
@@
 This section discusses the two most important special cases of random order values: the Shapley value and the somewhat more general weighted value.
-While most of these results are known in the literature, I include them here for two reasons: to provide build intuition for the more general and to highlight the similarities to the case of heterogeneous fringe players.
+While most of these results are known in the literature, I include them here for two reasons: to build intuition for the more general case and to highlight the similarities to the model with heterogeneous fringe players.
 
@@
 Let us start with one of the most popular cooperative solution concepts, the Shapley value.
-It can be characterized as the random order value that additionally also satisfies the axiom of symmetry.
+It can be characterized as the random order value that also satisfies the axiom of symmetry.
 This axiom requires that if two players are identical in terms of the characteristic function, then they should have the same value.
@@
 
-The following proposition and corollary derives the limit of the Shapley value for both types of players as the number of fringe players goes to infinity.
+The following proposition and corollary derive the limit of the Shapley value for both types of players as the number of fringe players goes to infinity.
 
@@
     \label{cor:fringe_value}
-    The aggregated Shapley-value of the fringe is
+    The aggregated Shapley value of the fringe is
     \begin{align*}
@@
 
-Because the Shapley value is a special case of the random order values, these results are quite straightforward consequences of \Cref{prop:one_sided_general} and \Cref{cor:fringe_value_general}.
+Because the Shapley value is a special case of the random order values, these results are straightforward consequences of \Cref{prop:one_sided_general} and \Cref{cor:fringe_value_general}.
 One only has to notice that each permutation having an equal probability implies that the number of firms coming before $P$ is uniformly distributed on $1, \dots, n$, and thus the share of firms before $P$ converges in distribution to the uniform distribution on $[0, 1]$.
@@
 
-Finally, the following corollary highlights that, even though the individual share of each $A_i$ vanishes as their number goes to infinity, their total value still remains positive.
+Finally, the following corollary highlights that even though the individual share of each $A_i$ vanishes as their number goes to infinity, their total value remains positive.
 \begin{corollary}
@@
 Consider the case when $f(n) = n^\alpha$, for some $\alpha > 0$.
-Assume that the bargaining takes place between player $P$ and a measure $\bar{n}$ of fringe players.
+Assume that the bargaining occurs between player $P$ and a measure $\bar{n}$ of fringe players.
 Thus, the value that the grand coalition can achieve is $\bar{n}^\alpha$.
@@
 
-In words, regardless of the value of $\bar{n}$, the two types of players share the total value in the same proportion.
+In other words, regardless of the value of $\bar{n}$, the two types of players share the total value in the same proportion.
 This proportion depends on the parameter $\alpha$ (\Cref{fig:power_function_example}), which can be interpreted as the degree of substitutability between the fringe players.
-More specifically, the higher $\alpha$ is, the more complementary the fringe players are to each other, and the larger the share they obtain.
-In the limit, when $\alpha \to \infty$, the fringe obtains all the value, as essentially all players become indispensable, and share the total value equally.
-On the other hand, when $\alpha \to 0$, the big player can appropriate all the value.
+More specifically, the higher $\alpha$ is, the more complementary the fringe players are to each other and the larger the share they obtain.
+In the limit, when $\alpha \to \infty$, the fringe obtains all the value, as essentially all players become indispensable and share the total value equally.
+On the other hand, when $\alpha \to 0$, the big player can appropriate all of the value.
 
@@
 The other important special case of random order values is the weighted value \parencite{shapley1953additive}.
-It relaxes the symmetry axiom of the Shapley value, and allows for players having different levels of innate bargaining power.
-On the other hand, weighted values still have more structure than random order values, as they are characterized by a weight system (a vector of non-negative numbers for each player).
-These weights determine how the value of a coalition is distributed amongst its members in the case when they are all equally important for the coalition.
-Then, relying on the linearity of the value, this distribution can be extended to the case when the players are not equally important.
-
-The weights can be thought of as the measure of some innate bargaining power, not reflected in the production function.\footnote{
-    Although, this interpretation is not always appropriate.
+It relaxes the symmetry axiom of the Shapley value and allows players to have different levels of innate bargaining power.
+On the other hand, weighted values still have more structure than random order values, as they are characterized by a weight system that is more restrictive than assigning arbitrary probabilities to each permutation of players.
+These weights determine how a coalition's value is distributed amongst its members when they are all equally important to the coalition.
+Then, relying on the linearity of the value, this can be extended to the case when the players are not equally important.
+
+The weights can be thought of as a measure of some innate bargaining power, which is not reflected in the production function.\footnote{
+    However, this interpretation is not always appropriate.
     As \textcite{owen1968communications} demonstrates, there are games where the weighted value is not monotone increasing in a player's weight.
 }
-Further support for this interpretation in certain games can be found in \textcite{hart1996bargaining}, demonstrating that in a certain alternating offer bargaining game, weights are related to the probability of each player making the offer.\footnote{
-    For example, only one player having a positive value corresponds to them making take it or leave it offers.
+Further support for this interpretation in certain games can be found in \textcite{hart1996bargaining}, demonstrating that weights in a certain alternating offer bargaining game are related to the probability of each player making the offer.\footnote{
+    For example, only one player having a positive weight corresponds to that player making take it or leave it offers.
 }
@@
 For the purposes of the current players, it is sufficient to deal with the case of simple weights\footnote{
-    In general, weighted values allow for more complex weight systems with each player having a vector of weights applied in a lexicographic manner.
+    In general, weighted values allow for more complex weight systems, with each player having a vector of weights applied in a lexicographic manner.
 }
 as I assume that there is at most one player with zero weight.
-For my main result, I make use the following characterization of the weighted values: \textcite{kalai1987weighted} demonstrated that weighted values can be calculated by weighting the permutations by the probabilities arising from the following sequential ordering procedure.
+For the main result in this section, I make use of the following characterization of the weighted values: \textcite{kalai1987weighted} demonstrated that weighted values can be calculated by weighting the permutations by the probabilities arising from the following sequential ordering procedure.
 Start with the set of all players.
@@
 
-Now let us turn to deriving the weighted value and its limit for the big player and the fringe in this specific game.
-First, I prove a lemma that characterizes the distribution of the number of players before $P$ in the limit, and then use it to derive the weighted value of the big player and the fringe.
+Now, let us derive the weighted value and its limit for the big player and the fringe in this specific game.
+I start by proving a lemma that characterizes the distribution of the number of players before $P$ in the limit.
+Then, I use it to derive the weighted values of the players.
+
 Consider the game described in the previous section, and let the weights of players of type $A$ and $P$ be 1 and $\lambda$, respectively.
@@
 Having \Cref{eq:entry_distr_discrete} and \Cref{lem:entry_distr} allows us to invoke \Cref{prop:one_sided_general} to obtain the following proposition.\footnote{
-    \textcite{stole1996intra} also derive essentially the same expression for the equilibrium outcome of their bargaining game with unequal profit distribution, and assert that it is equal to the weighted value.
+    \textcite{stole1996intra} also derive essentially the same expression for the equilibrium outcome of their bargaining game with unequal profit distribution and assert that it is equal to the weighted value.
 }
@@
 Depending on the shape of this distribution, regions corresponding to different masses of fringe firms can be over or underweighted in this integral, leading to different values.
-Contrary to \Cref{prop:one_sided_general}, the probability distribution has a specific functional form, and is characterized by a single parameter, $\lambda$.
+Contrary to \Cref{prop:one_sided_general}, the probability distribution has a specific functional form and is characterized by a single parameter, $\lambda$.
 \Cref{fig:weigh_function} illustrates the weighting function for various values of $\lambda$.
@@
     \end{subfigure}
-    \caption{Illustration of the weighting function for various values of $\lambda$ in the weighted Shapley-value.}
+    \caption{Illustration of the weighting function for various values of $\lambda$ in the weighted Shapley value.}
     \label{fig:weigh_function}
@@
 Now, let us examine how these weights impact the shares of the various players.
-It turns out, that a higher weight corresponds to a higher value in this game.\footnote{
+It turns out that a higher weight corresponds to a higher value in this game.\footnote{
     This would not necessarily have to be the case, as demonstrated by \textcite{owen1968communications}.
@@
 
-Furthermore, the next corollary shows that the limit of the weighted value of $P$, as their weight goes to zero (infinity) is precisely the payoff $P$ that they would achieve if they were making (facing) take-it-or-leave-it offers.
+Furthermore, the following corollary shows that the limit of the weighted value of $P$, as their weight goes to zero (infinity), is precisely the payoff $P$ that they would achieve if they were making (facing) take-it-or-leave-it offers.
 \begin{corollary}
@@
 \end{corollary}
-This set of results highlights that utilizing (weighted) Shapley values to model bargaining outcomes provides an intermediate solution between inscribing all the bargaining power to one or the other player, and thus a generalization of take-it-or-leave-it offers, with the distribution of bargaining power being adjustable by a single parameter.
+This set of results highlights that utilizing (weighted) Shapley values to model bargaining outcomes provides an intermediate solution between inscribing all the bargaining power to one type of player and, thus, ait is a generalization of take-it-or-leave-it offers, with the distribution of bargaining power being adjustable by a single parameter.
 
@@
 
-This section relaxes the assumption that the big player is indispensable.
-I demonstrate two ways in which the model can be extended to include non-indispensable big players, while retaining the essential structure and the tractability of the results.
-In the first case, there are a finite number of big players, which are perfect substitutes of each other.
+This section relaxes the assumption that the central player is indispensable.
+I demonstrate two ways in which the model can be extended to include non-indispensable big players while retaining the essential structure and the tractability of the results.
+In the first case, there is a finite number of big players who are perfect substitutes for each other.
 In the second case, there is a single big player, but the fringe is able to generate some value on its own.
 In both cases, the player's shares are still random order values\footnote{
-    The case of multiple big players is equivalent to the case of a single big player with the same production function, but a different probability distribution over the permutations.
+    The case of multiple big players is equivalent to that of a single big player with the same production function but a different probability distribution over the permutations.
     Conversely, in the setting when the fringe can generate some value on its own, the production function changes, but the probability distribution is the same.
-}, and thus many of the earlier results apply.
-
-\subsubsection{Shapley value with multiple big players}
-
-Imagine that, instead of just one, there are $m$ players of type $P$, and they are perfect substitutes of each other.
+}, and thus, many of the earlier results apply.
+
+\subsubsection{Multiple central players}
+
+Imagine that, instead of just one, there are $m$ players of type $P$, and they are perfect substitutes for each other.
 That is, any coalition still needs at least one of them to create any value, but it does not matter which and how many of them are present.\footnote{
-    The relaxtion of this assumption, while conceptually straightforward, is not as simple to analyze.
+    The relaxation of this assumption, while conceptually straightforward, is more complex to analyze.
     Instead of having to deal with the minimum of $m$ independent random variables, one needs to consider all order statistics.
@@
 \end{proposition}
-On the other hand, superadditivity is not as simple in this case, as before.
-For example, when $f$ is concave, then $m$ coalitions with one platform each and the fringe divided equally amongst them clearly achieve a higher total payoff than the grand coalition.
-Therefore, the results of this section are most applicable to settings when multiple coalitions cannot be formed at the same time for some reason.
-For example, \textcite{hart1996bargaining} propose an interpretation when there is a single, indivisible, non-replicable resource or technology (not captured in the value function) necessary to produce any value.
-
-For simplicity, let us restrict our attention to probability distributions over the permutations that are symmetric with respect to the big players.
+On the other hand, superadditivity is more complex in this case than before.
+For example, when $f$ is concave, then $m$ coalitions with one platform each and the fringe divided equally amongst them achieve a higher total payoff than the grand coalition.
+Therefore, the results of this section are most applicable to settings when multiple coalitions cannot be formed simultaneously.
+For example, \textcite{hart1996bargaining} proposes that it might be due to a single, indivisible, non-replicable resource or technology (not captured in the value function) necessary to produce any value.
+
+For simplicity, let us restrict our attention to probability distributions over the permutations which are symmetric with respect to the big players.
 That is, the probability of having $k_F$ fringe players and $k_P$ big players before player $P_j$ is the same for all $i$.\footnote{
@@
 }
-As before, I assume that, as the number of fringe players goes to infinity, the distribution of the number of fringe players before player $P_j$ to a continuous distribution.
+As before, I assume that, as the number of fringe players goes to infinity, the distribution of the number of fringe players before player $P_j$ converges to a continuous distribution.
 
 Let us first establish the sum of the shares of all big players.
-Then, the value of individual big players can be obtained by relying on the symmetry assumption.
+Then, the value of individual big players can be obtained by relying on the assumption of symmetry.
 The following proposition provides an expression for the limit of this total value.
@@
 
-    Let $H(t) = 1 - [1 - G(t)]^m$, i.e. the cdf of the minimum of the $m$ independent random variables distributed according to $G$.
+    Let $H(t) = 1 - [1 - G(t)]^m$, i.e., the cdf of the minimum of the $m$ independent random variables distributed according to $G$.
     Then
@@
 
-Notably, value in the case of multiple, substitutable big players can be interpreted as a random order value with a single big player.
+Notably, value in the case of multiple, substitutable big players can reformulated as a random order value with a single big player.
 The probability distribution for the corresponding random order value has a specific form, and depends on the number of big players.
-Consequently, all the results from the previous section apply to this case as well.
+Consequently, all the results from the previous section also apply to this case.
 
@@
 Let the location of the $m$ atoms be $t_1, \dots, t_m$, distributed independently and uniformly on the unit interval.
-The expected marginal contribution of $t_i$ is only positive whenever it is the first amongst the major players.
-Therefore, the total value of the big players is the random order value with corresponding probability distribution being the minimum of $m$ independent random variables describing the number of fringe players before each big player.
+The expected marginal contribution of $t_i$ is only positive whenever it is the first amongst the central players.
+Therefore, the total value of the big players is the random order value, with the corresponding probability distribution being the minimum of $m$ independent random variables describing the number of fringe players before each big player.
 
@@
 Proposition \Cref{cor:multiple_platforms_2} again confirms our intuition: more players means that they become more substitutable, and thus their bargaining power decreases.
-This not only means that the value of each individual big player decreases, but also that their total value goes down.
+This not only means that the value of each individual big player decreases but also that the sum of their values is reduced.
 \begin{corollary}
@@
 \paragraph{Example: Shapley value.}
-I illustrate the effect of the number of big players on the weight function $h(t)$ by looking at the simplest of the random order values, the Shapley value.
+I illustrate the effect of the number of central players on the weight function $h(t)$ by looking at the simplest of the random order values, the Shapley value.
 As shown in \Cref{prop:one_sided}, the limit of the Shapley value in the case of a single big player is just $\int_0^1 f(t) \dt$.
 Therefore, using the notation from \Cref{prop:one_sided_general}, $G(t) = t$.
-Conseqently, by \Cref{prop:multiple_platforms_total}, the sum of the shares of the big players corresponds to the random order value characterized by the cumulative distribution function
+Consequently, by \Cref{prop:multiple_platforms_total}, the sum of the shares of the big players corresponds to the random order value characterized by the cumulative distribution function
 \begin{align} 
@@
 
-\Cref{fig:multiple_platforms,fig:multiple_platforms_total} illustrate how $h_t$ and $h_j(t)$ depend on the number of big firms, $m$.
-In particular, it is apparent that a $H(t)$ with lower $m$ first order stochastically dominates one with a higher number of big firms.
-This is the underlying reason of the big players' share decreasing in their number, i.e. \Cref{cor:multiple_platforms_2}.
+\Cref{fig:multiple_platforms,fig:multiple_platforms_total} illustrate how $h_t$ and $h_j(t)$ depend on the number of central players, $m$.
+In particular, it is apparent that a $H(t)$ with lower $m$ first order stochastically dominates one with a higher number of players of type $P$.
+This is the underlying reason for the big players' share decreasing in their number, i.e., \Cref{cor:multiple_platforms_2}.
 
@@
 
-Another way of relaxing the indispensability of the big player is assuming that the small players can generate some value on their own.
-Suppose that the big player still provides some value to any coalition, but a coalition of fringe players can achieve a positive value even without it.
+Another way of relaxing the central player's indispensability is to assume that the fringe players can generate some value on their own.
+Suppose the big player still provides some value to any coalition, but a coalition of fringe players can achieve a positive value even without it.
 Formally, the value function is now the following:
@@
 
-As in the case of multiple big players, monotonicity is straightforward to establish.
+As with multiple central players, monotonicity is straightforward to establish.
 \begin{proposition}
@@
 Also similarly, conditions for superadditivity are not as simple.
-Therefore, the simultaneous formation of multiple coalitions must be excluded in this setting as well.
+Therefore, the simultaneous formation of multiple coalitions must be assumed away in this setting, too.
 
@@
 The value of the big player is still its average marginal contribution.
-The only difference is that this marginal contribution (conditional on $s$ share of the fringe coming before $P$) is not $f(s)$, but rather $f(s) - f_0(s)$.
-This is because the big player is not indispensable, as $s$ mass of fringe firms can achieve $f_0(s)$ even without it.
+The only difference is that this marginal contribution (conditional on $s$ share of the fringe coming before $P$) is not $f(s)$, but instead $f(s) - f_0(s)$.
+This is because the big player is not indispensable, as $s$ mass of fringe firms can achieve $f_0(s)$ without it.
 
@@
 
-The value of the fringe is also similar to the baseline case, except now fringe players have a non-zero marginal contribution even when $P$ is not present.
-Therefore, there is an additional term in the integral, corresponding to the marginal value of the fringe when $P$ is not present.
+The value of the fringe is also similar to the baseline case, except now fringe players have a non-zero marginal contribution  to coalitions not containing player $P$.
+Therefore, there is an additional term in the integral corresponding to the marginal value of fringe players when $P$ is not present.
 
@@
 
-It is clear that the value of the big player is decreasing in $f_0$ (\Cref{fig:non_indispensable}).
-Consequently, the value of the fringe is increasing in $f_0$, which is essentially its outside option (what it can achieve without the big player).
-This is a natural result, and again, it is in line with what one would expect from bargaining theory.
+Clearly, the value of the big player is decreasing in $f_0$ (\Cref{fig:non_indispensable}).
+Consequently, the value of the fringe is increasing in $f_0$, which is essentially its outside option.
+This is a natural result, and again, it aligns with what one would expect from bargaining theory.
 \begin{figure}
@@
 \subsection{Special cases}
-\subsubsection{Shapley-value}
+\subsubsection{Shapley value}
 
@@
 \begin{proof}[Proof of Corollary \ref{cor:fringe_value}]
-    The first equality comes from the efficiency of the Shapley-value.
+    The first equality comes from the efficiency of the Shapley value.
     The values of all players sum up to $f(1)$ for all $n \in \mathbb{N}$, therefore
@@
     Now we can use \Cref{lem:convergence_to_manifold} to conclude that $X_n \xrightarrow[]{d} (U, \dots, U)$.
-    Finally, by \Cref{lem:many_sided_manifold}, the Shapley-value is
+    Finally, by \Cref{lem:many_sided_manifold}, the Shapley value is
     \begin{align*}

### 2024-08-21 src/paper/theory.tex
Improve wording in main text

@@
 
-Up until this point, we have only considered games with a single type of small player.
+Until now, we have only considered games with a single type of small player.
 Now imagine that, in addition to player $P$, there are $L$ different varieties of players: $\{A^l_1, \dots, A^l_n\}$ where $1 \leq l \leq L$.
 The idea is the same as before: I assume that $P$ is necessary for any coalition to have a positive value, and the small players are identical to each other \emph{within their types}.
-The substitutability of the different types of small players will be captured by the -- now multivariate -- function $f$.
+The -- now multivariate-- function $ f$ captures the substitutability of the different types of small players.
 
 Let us now turn to the formal definition of the setting.
-For a finite number of fringe players, the coalitional form, $(N, v)$, of the game is the following.
+For a finite number of fringe players, the game's coalitional form, $(N, v)$, is the following.
 The set of players is $N = \{P, A^1_1, \dots, A^1_n, \dots, A^L_1, \dots, A^L_n\}$, which in total contains $nL + 1$ players.\footnote{
@@
 For example, it also captures the situation of a single upstream producer, a large number of downstream firms, and a similarly large number of customers, as long as both the customers and the downstream firms can participate in the bargaining process.\footnote{
-    A setting where these assumptions might be plausible is, for example, the new car market with a car producer, a number of independent dealerships, and customers who might engage in some form of negotiation.
-}
-More than two types of fringe players can be used to model a platform with more than two sides, such as a platform with buyers, sellers and a set of advertisers, or, following \textcite{stole1996intra}, bargaining between a firm and multiple types of input suppliers.
+    A setting where these assumptions might be plausible is, for example, the new car market, which has a car producer, several independent dealerships, and customers who might engage in some form of negotiation.
+}
+Models with more than two types of fringe players can represent, for example, a platform with more than two sides (such as buyers, sellers, and a set of advertisers) or, following \textcite{stole1996intra}, bargaining between a firm and multiple types of input providers.
 
 The subsequent discussion follows the structure of \Cref{sec:one_sided}.
-I start by characterizing conditions for monotonicity and superadditivity to support the bargaining interpretation and the formation of the grand coalition.
-It turns out that necessary and sufficient conditions for these properties are the straightforward analogues of those from the one-sided case.
+I start by characterizing conditions for monotonicity and superadditivity to support the bargaining interpretation of the results and the formation of the grand coalition.
+It turns out that the necessary and sufficient conditions for these properties are straightforward analogs of those from the one-sided case.
 \begin{proposition}
@@
 
-In the next subsections, I will first examine random order values, and then the two important special cases: the Shapley value and the weighted value.
-Many of the results are be similar to the one-sided case, including the marginal contribution interpretation of the value of the fringe, and the geometric interpretation of the Shapley value.
-Furthermore, it turns out that even though the number of fringe players is a multi-dimensional object in this case, for the limit of the Shapley and weighted values, one only has to integrate over a one-dimensional manifold within the unit hypercube, which makes the results more tractable.
+In the following subsections, I first examine random order values and then the two most important special cases: the Shapley value and the weighted value.
+Many of the results are similar to the one-sided case, including the marginal contribution interpretation of the fringe's value and the geometric interpretation of the Shapley value.
+Furthermore, even though the number of fringe players is a multi-dimensional object in this case, for the limit of the Shapley and weighted values, one only has to integrate over a one-dimensional manifold within the unit hypercube, making the results more tractable.
 
@@
 \end{theorem}
-The proposition above is almost identical to \Cref{prop:one_sided_general}, with the only difference being that the integral is now over the $L$-dimensional unit hypercube, due to $f$ being a function of $L$ variables.
-
-While the above proposition is very general in terms of permutation probabilities, it is not very tractable in practice, as one has to integrate over the entire, $L$-dimensional domain of $f$.
-It would be much more convenient, if one only had to be concerned with a one-dimensional manifold within this hypercube instead.
-It turns out that, for a number of important cases (namely, the Shapley value and the weighted value), it is indeed the case.
-
-The following lemma states a general result about this idea: it provides sufficient conditions, under which the limit of the value of the big player can be expressed as an integral over a one-dimensional path, even though the value for any finite number of players depends on the whole domain of $f$.
-Later on, I show that it applies to both the Shapley value and the weighted value.
+The proposition above is almost identical to \Cref{prop:one_sided_general}, with the only difference being that the integral is now over the $L$-dimensional unit hypercube due to $f$ being a function of $L$ variables.
+
+While the above proposition is very general in terms of permutation probabilities, its tractability in practice is hampered by the fact that one has to integrate over the entire $L$-dimensional domain of $f$.
+It would be much more convenient if one only had to be concerned with some smaller, one-dimensional manifold within this hypercube.
+It turns out that this is indeed the case for a number of important cases (namely, the Shapley value and the weighted value).
+
+The following lemma states a general result about this idea: it provides sufficient conditions under which the limit of the value of the big player can be expressed as an integral over a one-dimensional path, even though the value for any finite number of players depends on the whole domain of $f$.
+Later on I show that it applies to both the Shapley value and the weighted value.
 \begin{lemma}
@@
 
-The lemma states, that if the permutation probabilities are such that the number of fringe players before $P$ converges to a degenerate distribution, then one only has to be concerned with just a tiny part of the production function $f$.
+The lemma states that if the permutation probabilities are such that the number of fringe players before $P$ converges to a degenerate distribution, then one only has to be concerned with just a tiny part of the production function $f$.
 Namely, we only need to know how the function behaves on the set $\{(a_1(t), \dots, a_L(t)) : t \in [0, 1]\} \subset [0, 1]^L$.\footnote{
@@
 }
-This result is essentially a generalization of the diagonal formula from \textcite{aumann2015values} or \textcite{stole1996intra} to the case where permutation probabilities are not uniform.
-The intuition, however, is the same law-of-large-numbers-type argument: if the number of fringe players is large, then it is very unlikely that, after a random ordering, their proportion is very different from its expected value.
-The main difference is that, in this case, these conditional expectations are not linear, but rather given by the $a_l$ functions.
-
-In the remainder of this section, I will show that the Shapley value and the weighted value satisfy the assumptions of the above lemma, and thus the limit of those values can be expressed as an integral over a well-defined, one-dimensional path.\footnote{
+This result essentially generalizes the diagonal formula from \textcite{aumann2015values} or \textcite{stole1996intra} to the case where permutation probabilities are not uniform.
+The intuition, however, is the same law-of-large-numbers-type argument: if the number of fringe players is large, then it is very improbable that, after a random ordering, their proportion in some subset of players is very different from its (conditional) expected value.
+The main difference is that, in this case, these conditional expectations are not necessarily linear but rather given by the $a_l$ functions.
+
+In the remainder of this section, I show that the Shapley value and the weighted value satisfy the assumptions of the above lemma
+Thus, the limit of those values can be expressed as an integral over a well-defined, one-dimensional path.\footnote{
     I do not extend the heterogeneous agent model to the case of non-indispensable big players.
-    It would be conceptually straightforward to do so for cases when \Cref{lem:many_sided_manifold} applies, albeit somewhat more cumbersome.
+    It would be conceptually straightforward to do so for cases when \Cref{lem:many_sided_manifold} applies, albeit more cumbersome.
 }
@@
 
-Let us now turn our attention to the Shapley value.
-As hinted before, due to the uniformity of the permutation probabilities, we get a diagonal formula in this case.
+Now, let us turn our attention to the Shapley value.
+As hinted at earlier, due to the uniformity of the permutation probabilities, we obtain a diagonal formula in this case.
 \Cref{prop:many_sided_shapley} establishes this result formally.
@@
 The set of players and the characteristic function are the same as in the previous section, but, as before, each player has a weight attached to them.
-I assume that fringe players are identical to each other within their types also with respect to their weights.
+I assume that fringe players of the same type have identical weights.
 That is, the weight system for the game is the following: player $P$ has weight $\lambda_P$, while players $A^l_i$ have weight $\lambda_l$.
 
-I will show that, as with non-weighted Shapley value, the limit of the weighted value can be expressed as an integral over a one-dimensional path in the weighted case as well.
-However, this path is not the diagonal of the unit hypercube anymore, but a function of the fringe players' weights.
-The reason for this is that not all permutations have the same probability of occurring: those with players having higher weights ordered later are more likely to occur.
+I will show that, as with the non-weighted Shapley value, the limit of the weighted value can also be expressed as an integral over a one-dimensional path in the weighted case.
+However, this path is no longer the diagonal of the unit hypercube but a function of the fringe players' weights.
+This is because not all permutations have the same probability of occurring: those with players having higher weights ordered later are more likely to occur.
 
 The following statement is the central theorem of this paper.
-In fact, many of the propositions with one indispensable player can be considered as special cases of it.
+Many of the propositions with one indispensable player can be considered as special cases of it.
 \begin{proposition}
@@
 \Cref{fig:many_sided_weighted} illustrates this phenomenon in the case of two types of fringe players.
-Players of type $A^2$ have a higher weight than those of type $A^1$, and thus the path the integral is taken over contains more of the latter than the former.
-
-Finally, player $P$'s probability of coming after $s$ proportion of the fringe is also not uniform, but rather influenced by the relationship between its own weight and the fringe players' weights.\footnote{
+Players of type $A^2$ have a higher weight than those of type $A^1$, and thus, the path the integral is taken over contains more of the latter than the former.
+
+Finally, player $P$'s probability of coming after $s$ proportion of the fringe is also not uniform but rather influenced by the relationship between its own and the fringe players' weights.\footnote{
     This is the same mechanism as in the case of the one-sided weighted value.
@@
 Therefore, the integral is not taken with respect to the uniform distribution, but rather one resembling that in \Cref{prop:one_sided_weighted}.
-It results are the same: when the big player has a higher weight, its chances of being relatively late in the ordering are higher, and thus -- due to $f$ being monotone increasing -- its value is higher.
-The following, simple corollary formalizes this idea.
+Its effect is also the same: when the big player has a higher weight, its chances of being relatively late in the ordering are higher, and thus -- due to $f$ being monotone increasing -- its value is higher.
+The following simple corollary formalizes this idea.
 
@@
 \end{corollary}
-This result is analogous to \Cref{cor:platform_value_weighted}, and demonstrates that a higher weight for player $P$ corresponds to a higher value in this game, as well.
+This result is analogous to \Cref{cor:platform_value_weighted} and demonstrates that a higher weight for player $P$ corresponds to a higher value in this game, as well.
 
@@
 In this section, I apply the ideas from the previous sections to a simple model of two-sided platforms.
-I follow the modelling approach of \textcite{armstrong2006competition}, focusing on the monopolist platform case.
+I follow the modeling approach of \textcite{armstrong2006competition}, focusing on the monopolist platform case.
 The model presented in this section expands on the original in two main ways.
 First, and most importantly, I add bargaining between the platform and the two sides.
-That is, besides the welfare-maximizing and unilateral price setting cases presented in \textcite{armstrong2006competition}, I also consider a case where the platform and the two sides bargain over the entry fees.
+That is, besides the welfare-maximizing and unilateral price-setting cases presented in \textcite{armstrong2006competition}, I also consider a case where the platform and the two sides bargain over the entry fees.
 I assume that the outcomes of this bargaining process are described by the weighted value.
 Second, instead of assuming that each player's utility is linear in the number of the other side's size, I allow for more general non-linear network effects. 
-This extension lets me capture and vary the substitutability of the players on each sides.
+This extension lets me capture and vary the substitutability of the players on each side.
 
@@
     \textcite{armstrong2006competition} -- along with much of the early literature on two-sided markets \parencite[e.g.][]{rochet2003platform,hagiu2006pricing} -- assume that the utility of each player is linear in the number of players on the other side.
-    Using a more general function allows me to model different more kinds of network effects.
+    Using a more general function allows for modeling different kinds of network effects.
 } of the number of players on the other side ($n_j$), minus the entry fee charged by the platform ($p_i$):
@@
 
-Following \textcite{armstrong2006competition}, I model player entry also in a reduced form manner.
+Following \textcite{armstrong2006competition}, I also model player entry in a reduced form manner.
 Assume that there is a continuum of potential entrants on both sides of the market.
@@
     Such assumptions are usually justified by having idiosyncratic cost entry costs, the distribution of which determines the function $\phi$.
-    For simplicity, I refrain from explicitly modeling this cost in the main text, but \Cref{sec:explicit_entry_costs} discusses how one can incorporate it into the model, and its impact on bargaining outcomes.
+    For simplicity, I refrain from explicitly modeling this cost in the main text, but \Cref{sec:explicit_entry_costs} discusses how one can incorporate it into the model and how it impacts bargaining outcomes.
 }
@@
 Finally, let us assume that the platform can charge lump-sum entry fees to both sides.
-These fees are allowed to be negative, in which case they are interpreted as subsidies.
-The platform's profit is the sum of entry fees, minus the cost of serving the entrants ($F_i$ for each entrant):
+These fees are allowed to be negative, in which case they can be interpreted as subsidies.
+The platform's profit is the sum of entry fees minus the cost of serving the entrants ($F_i$ for each entrant):
 \begin{align*}
@@
 
-I consider two cases as to the determination of the entry fees, as well as a welfare-maximizing benchmark\footnote{}.
-In the benchmark case, I derive the entry fees that maximize social welfare, i.e. the sum of the utilities of the two sides plus the platform's profit.
-After that, I consider a model analogous to that in \textcite{armstrong2006competition}, where the platform can unilaterally commit to any entry fees it wishes.
-Finally, I examine and contrast the case where the entry fees the result of a bargaining process in such a way that the resulting utilities and profits correspond to the players' (weighted) values.
+I consider two cases as to the determination of the entry fees, as well as a welfare-maximizing benchmark.
+In the benchmark case, I derive the entry fees that maximize social welfare (i.e., the sum of the utilities of the two sides plus the platform's profit).
+After that, I consider a model analogous to that in \textcite{armstrong2006competition}, where the platform can unilaterally commit to any entry fees.
+Finally, I examine and contrast the case where the entry fees result from a bargaining process such that the resulting utilities and profits correspond to the players' (weighted) values.
 
@@
 for each individual player on side $i$.
-The total welfare on side $i$ is in turn given by
+The total welfare on side $i$ is, in turn, given by
 \begin{align}
@@
 
-The effects of $\gamma_j$ are somewhat more complex, and are best understood through the dependence of the utility on side $i$ on $n_i$.
-Total welfare on side $i$ is always increasing in $n_i$, but individual utilities are not.
-If $\gamma_j > 1$ (i.e., network effects are convex), then $u_i$ is indeed increasing in $n_i$, as the positive externality each individual player imposes on the other side is increasing in the number of entrants.
+The effects of $\gamma_j$ are somewhat more complex and are best understood through the dependence of the utility of side $i$ on $n_i$.
+Total welfare on side $i$ is always increasing in $n_i$, but individual utilities do not have to be.
+If $\gamma_j > 1$ (i.e., network effects are convex), then $u_i$ is indeed increasing in $n_i$, as the positive externality each player imposes on the other side is increasing in the number of entrants.
 Conversely, when $\gamma_j < 1$, the positive externality of the whole side is still increasing in their number (therefore, $W_i$ is increasing in $n_i$), but the positive externality each individual player imposes is now a decreasing function of it (thus, $u_i$ is decreasing in $n_i$).
@@
 
-Now let us examine what happens when the platform can set the entry fees unilaterally.
-First, let us rewrite the platform's profit as a function of utilities, rather than the number of entrants:
+Now, let us examine what happens when the platform can set the entry fees unilaterally.
+First, let us rewrite the platform's profit as a function of utilities instead of number of entrants:
 \begin{align*}
@@
 \end{align*}
-If the platform can set entry fees unilaterally, then it's problem can be viewed as choosing $u_1$ and $u_2$ to maximize this expression.
-The next proposition characterizes the solution of this maximization problem.
+If the platform can set entry fees unilaterally, then its problem can be viewed as choosing $u_1$ and $u_2$ to maximize this expression.
+The following proposition characterizes the solution of this maximization problem.
 \begin{proposition}
@@
 As one would expect, profit-maximizing entry fees are higher than welfare-maximizing ones.
-In addition to the comparative statics of the welfare-maximizing case, the unilaterally chosen also depend on the elasticity of entry.
+In addition to the comparative statics of the welfare-maximizing case, unilaterally chosen entry fees also depend on the elasticity of entry.
 When this elasticity is low, the platform can set high entry fees, as the resulting reduction in the number of entrants is relatively minor.
 
-For ease of comparison with the bargaining case, let us also derive the individual utilities and total welfare on each side, too:
+For ease of comparison with the bargaining case, let us  also derive the individual utilities and total welfare on each side:
 \begin{align*}
@@
 Suppose that $n_1$ and $n_2$ players have decided to enter on sides $1$ and $2$, respectively.
-Furthermore, assume that players' bargaining weights are $\lambda_1, \lambda_2$ and $\lambda_P$.
+Furthermore, assume that players' bargaining weights are $\lambda_1, \lambda_2$, and $\lambda_P$.
 
@@
 }
-Furthermore, all of these shares are increasing in one's own bargaining weight, and decreasing in the others' weights.
+Furthermore, all of these shares are increasing in one's own bargaining weight and decreasing in the others' weights.
 Finally, and perhaps most interestingly, the share of side $i$ from the value generated on side $j$ is also increasing in $\gamma_j$.
@@
 
-For making comparisons easier, let us also derive implied entry fees and utilities.\footnote{
+To make comparisons easier, let us also derive implied entry fees and utilities.\footnote{
     If one wished to close the model, the number of entrants in equilibrium could be obtained by solving the system of equations $n_i = \phi_i(u_i(n_1, n_2)), n \in \{1, 2\}$, just like in the other cases.
@@
 \end{align*}
-Implied entry fees on the other hand can be calculated from the equation $u_i = \alpha_i n_j^{\gamma_i} - p_i$, giving
+Implied entry fees, on the other hand, can be calculated from the equation $u_i = \alpha_i n_j^{\gamma_i} - p_i$, yielding
 \begin{align}
@@
 
-Therefore, first assume that network effects are linear, i.e. $\gamma_i = 1$ for $i \in \{1, 2\}$ and that all players have equal weights ($\lambda_P = \lambda_1 = \lambda_2 = 1$).
+Therefore, first assume that network effects are linear, i.e., $\gamma_i = 1$ for $i \in \{1, 2\}$ and that all players have equal weights ($\lambda_P = \lambda_1 = \lambda_2 = 1$).
 From \Cref{eq:welfare_max_entry_fees,eq:unilateral_entry_fees,eq:bargaining_entry_fees}, the entry fees for side $i$ are
@@
 \end{align*}
-for the welfare-maximizing, unilateral price setting and bargaining cases, respectively.
-
-All of these expressions bear some similarities to each other in that the price is related to the externalities that an entrant imposes on the other players.
+for the welfare-maximizing, unilateral price setting, and bargaining cases, respectively.
+
+All of these expressions are similar in that the price is related to the externalities that an entrant imposes on the other players.
 In fact, the welfare-maximizing price is just that: the cost of serving one additional player (1) and the positive externality imposed on the other side (2).
-The unilateral pricing case also includes these two factors in, as well as a third factor, which related to the elasticity of entry (3).
+The unilateral pricing case also includes these two factors , as well as a third factor related to the elasticity of entry (3).
 Namely, the platform extracts some of the surplus generated by the entrants, and the surplus it wants to extract depends on the elasticity of entry, $\phi'_i(u_i)$.
-It is the same mechanism that leads to markups in a simple monopolistic pricing model.
+It is the same mechanism that leads to markups in monopolistic pricing models.
 
 The bargaining case also includes factors (1) and (2), albeit they appear somewhat differently.
-As opposed to the first two cases, the price only contains some fraction of these externalities, with the rest being shared with the platform and the other side.\footnote{
-    Due to the linearity of the model and the symmetry of the Shapley value, each part of the value is shared equally between players who participate in producing them.
-    This is the reason why, for example, the platform and the firms share the cost of serving the entrants (1) equally, and why all three types of players share the value generated on a given side (2) equally.
-}
-Furthermore, a part of the welfare generated on side $i$ (4) is also shared with the other players, and thus appears in the price.
-This is in contrast to both the welfare-maximizing and unilateral pricing cases, where the entry fee for a given side does not depend on the actual utility that was materialized on that side.
+Unlike the first two cases, the price only contains some fraction of these externalities, with the rest being shared with the platform and the other side.\footnote{
+    Due to the linearity of the model and the symmetry of the Shapley value, each part of the value is shared equally between players who participate in creating it.
+    This is the reason why, for example, the platform and the firms share the cost of serving the entrants (1) equally and why all three types of players share the value generated on a given side (2) equally.
+}
+Furthermore, a part of the welfare generated on side $i$ (4) is also shared with the other players and thus appears in the price.
+This is in contrast to the welfare-maximizing and unilateral pricing cases, where the entry fee for a given side does not depend on the actual utility that is materialized on that side.
 Therefore, bargaining introduces some interesting departures from both the welfare-maximizing and unilateral pricing cases.
 
-Now let us consider more general, non-linear network effects.
-The welfare-maximizing, unilateral pricing and bargaining entry fees are as follows:
+Now, let us consider more general, non-linear network effects.
+The welfare-maximizing, unilateral pricing, and bargaining entry fees are as follows:
 \begin{align*}
@@
 }
-This demonstrates that bargaining outcomes are not just a fixed split of the value, but also take into account the shape of the network effects.
+This demonstrates that predicted bargaining outcomes are not just a fixed split of the value but also take into account the shape of the network effects.
 
@@
 
-For the cost of serving the players (1), the addition of bargaining weights simply leads to players sharing that cost in a constant proportion, according to their weights.\footnote{
+For the cost of serving the players (1), adding bargaining weights simply leads to players sharing that cost in a constant, but not necessarily equal, proportion.\footnote{
     This is because this term is linear in the number of entrants.
@@
 The higher the weight, the larger the share for any given player.
-While the latter observation is true for non-linear terms, as well, the influence of the weights is more complex in their case.
-Namely, it also depends on the shape of function.
+While the latter observation is also true for non-linear terms, the influence of the weights is more complex in their case.
+Namely, it also depends on the shape of the function.
 For example, in term (2), $\lambda_i$ interacts with the parameter determining the shape of the network effects, $\gamma_j$
@@
 Whether bargaining leads to a higher or lower total welfare in comparison to unilateral price setting depends on the parameters of the model.
-For example, if $\lambda_P$ is high enough, then $p_i^b > p_i^u > p_i^*$, leading to fewer firms entering and lower total surplus not only than the welfare-maximizing case, but also than the unilateral pricing case.
-In other words, it can happen that everybody looses from bargaining.\footnote{
-    In such a case, the platform would like to set lower entry fees than what it can achieve via bargaining.
-    This might be a realistic constraint in settings with commitment issues.
-}
+For example, if $\lambda_P$ is high enough, then $p_i^b > p_i^u > p_i^*$, leading to fewer firms entering and lower total surplus not only than the welfare-maximizing case but also than the unilateral pricing case.
+In other words, it can happen that everybody looses from bargaining.
 On the other hand, if $\lambda_P$ is sufficiently low, then one can always find weights $\lambda_1, \lambda_2$, such that $p_i^u > p_i^b > p_i^*$.
-In such a case, the platform would like to set higher entry fees than what it can achieve via bargaining for both sides of the market.
-As a consequence, the total welfare under bargaining is between the welfare-maximizing and unilateral pricing cases.
+In such a case, the platform would like to set higher entry fees than what it can achieve via bargaining for both sides of the market.\footnote{
+    This might be realistic in settings with commitment issues.
+}
+Consequently, the total welfare under bargaining is between the welfare-maximizing and unilateral pricing cases.
 Therefore, whether bargaining leads to higher or lower welfare than unilateral pricing depends on model parameters.
@@
 This also implies that the total welfare is strictly lower under bargaining than in the welfare maximizing benchmark.
-Therefore, while bargaining can be welfare-improving compared to unilateral price setting, it can not achieve the highest possible total utility.\footnote{
+Therefore, while bargaining can be welfare-improving compared to unilateral price setting, it can not lead to the first-best solution.\footnote{
     One could argue that the welfare maximizing case is not a realistic benchmark anyway, as the platform is operating at a loss.
@@
 
-In this paper, I examine the problem of bargaining between a small number of central players and a continuum of fringe players.
+In this paper, I explore the problem of bargaining between a small number of central players and a continuum of fringe ones.
 I model this setting relying on the concept of random order values from cooperative game theory.
-I demonstrate that the latter's predictions have some desirable properties, and coincide with intuitive expectations in terms of comparative statics.
-Furthermore, the results are analytically tractable, and have neat interpretations both from a geometric perspective, and in terms of players' marginal contributions.
-
-Random order values offer a comprehensive framework for modeling bargaining outcomes, and also include important and well-known special cases, such as the Shapley value or the weighted value.
-Due to the random order values retaining many of the attractive properties of their more specialized counterparts, they are a good candidate for modeling bargaining outcomes flexibly and in a tractable manner.
-This also applies to the weighted value in the case of multiple types of fringe players, which provides a rather flexible model for multi-sided markets.
-Furthermore, as shown in \Cref{sec:extensions}, the results can also be generalized to cases with not completely indispensable big players, while retaining the essential structure of the results.
+I demonstrate that the latter's predictions possess desirable properties and coincide with intuitive expectations in terms of comparative statics.
+Furthermore, the results are analytically tractable and have neat interpretations both from a geometric perspective and in terms of players' marginal contributions.
+
+Random order values offer a comprehensive framework for modeling bargaining outcomes.
+They also encompass important and well-known special cases, such as the Shapley value or the weighted value.
+Because random order values retain many of the attractive properties of their more specialized counterparts, they are a good candidate for modeling bargaining outcomes in a flexible and tractable manner.
+This also applies to the weighted value in the case of multiple types of fringe players, which provides a relatively versatile model for multi-sided markets.
+Furthermore, as shown in \Cref{sec:extensions}, the results can also be generalized to cases with not completely indispensable central players while retaining the essential structure of the results.
 
 Finally, I demonstrate how the proposed framework can be applied in practice by embedding it in a model of two-sided platforms based on \textcite{armstrong2006competition}.
-I show that the resulting entry fees have some similarities to the welfare-maximizing and unilateral price setting benchmarks, but also differ in some important ways.
-In particular, the externalities that players entrants impose on the platform (cost of serving entrants) and the other side (network externalities) are not fully incorporated into the entry fees, but are instead shared across the affected players.
-Similarly, contrary to the benchmark cases, the value generated on each side also factors into the entry fee for that side.
+I show that the resulting entry fees have some similarities to the welfare-maximizing and unilateral price-setting benchmarks, but they also differ in important ways.
+In particular, the externalities that entrants impose on the platform (the cost of serving entrants) and the other side (network externalities) are not fully incorporated into the entry fees but are instead shared among the affected players.
+Similarly, contrary to the benchmark cases, the value generated on each side also factors into that side's entry fee.
 This suggests that, in situations where bargaining between players is plausible, certain effects might be over- or underrepresented if one assumes unilateral price setting.
@@
 One possible direction is to consider other solution concepts from cooperative game theory, such as the nuclelous\footnote{
-    It retains many of the desirable properties of the weighted values, such as existence and uniquenes while having a more immediate connection to non-cooperative bargaining theory.
+    It retains many desirable properties of the weighted values, such as existence and uniqueness, while having a more immediate connection to non-cooperative bargaining theory.
 }.
-Another option is to generalize these results to a wider class of games.
-An example of this would be the assuming that the value of a coalition is increasing in the number of central players, thereby relaxing the assumption that they are complete substitutes of each other.
+Another option is to generalize these results to a broader class of games.
+An example of this would be assuming that the value of a coalition increases with the number of central players, thereby relaxing the assumption that they are complete substitutes for each other.
 A further direction is building non-cooperative microfoundations for the proposed random-order-value-based bargaining outcomes.
-Many such results exist for the Shapley value, and there are some for the the weighted value, but motivating the more general random order value in a similar manner could be a significant step towards achieving the goal of the Nash program.
+Such results exist for the Shapley value and the weighted value, but motivating the more general random order values in a similar manner could be a significant step towards achieving the goal of the Nash program.
 
 The practical applications are no less interesting.
-The proposed profit sharing framework could be embedded in more applied and detailed models describing various economically relevant settings.
-The example application in this paper is a streamlined attempt of this, while \textcite{stancsics2023hybrid}, which apply these ideas to a model of hybrid platforms, is a further step in this direction.
-Due to the simplicity of the results, this approach might be a viable, almost drop-in replacement for unilateral price setting in cases where one does not wish to ascribe all the bargaining power to one player.
+The proposed profit-sharing framework could be embedded in more detailed and realistic models describing various economically relevant settings.
+The example application in this paper is a streamlined attempt at this, while \textcite{stancsics2023hybrid}, which applies these ideas to a model of hybrid platforms, is a further step in this direction.
+Due to the simplicity of the results, the approach presented here might be a viable, almost drop-in replacement for unilateral price setting in cases where one does not wish to ascribe all the bargaining power to one player.
 

### 2024-08-21 src/paper/theory.tex
Improve wording in appendix

@@
 Entry is given by the usual assumption that a player enters if and only if the total utility of entering is non-negative.
-Due to the properties of $\kappa_i$, this implies that there is a well-defined, finite number of entrants on each side.
+Due to the properties of $\kappa_i$, this implies a well-defined, finite number of entrants on each side.
 Let us denote the number of entrants as a function of their non-idiosyncratic utility as $\phi_i(u_i)$.
@@
 This microfoundation does not change the results of the welfare-maximizing and unilateral pricing cases in any fundamental way.
-Total welfare must be adjusted to include this idosyncratic cost, but entry fees do not change at all.
-The reason is that, in the welfare-maximizing case, optimal prices only depend on externalities, while in the unilateral pricing case, the only additional factor is the elasticity of entry\footnote{
-    With this microfoundation in mind, one also relate this entry elasticity as the marginal cost of entry.
-}.
+Total welfare must be adjusted to include this idiosyncratic cost, but entry fees do not change at all.
+The reason is that, in the welfare-maximizing case, optimal prices only depend on externalities, while in the unilateral pricing case, the only additional factor is the elasticity of entry.
 On the other hand, the bargaining case is more interesting.
-The reason is that this idiosyncratic cost becomes a part of the value that the players bargain over, and thus it affects the characteristic function and the resulting bargaining outcomes.
-
-I approach this problem by breaking it down into two parts: bargaining over the idisyncratic and non-idiosyncratic parts of the value generated.
+The reason is that this idiosyncratic cost becomes a part of the value the players bargain over, and thus, it affects the characteristic function and the resulting bargaining outcomes.
+
+I approach this problem by splitting it into two parts: bargaining over the idiosyncratic and non-idiosyncratic parts of the value generated.
 Due to the linearity property of the Shapley value, the bargaining outcomes over the whole value are simply the sum of the bargaining outcomes over these two parts.
-Furthermore, the non-idiosyncratic part is the same as in the main text, and thus the weighted values arising from it are also identical.
+Furthermore, the non-idiosyncratic part is the same as in the main text.
+Thus, the weighted values arising from it are also identical.
 
 Let us continue by examining the idiosyncratic part of the value.
-Assume that, even though entrants with different costs have different contribution to the total value, there can be no discrimination between them in terms of the bargaining outcomes.
-That is, they each must share the same fraction of the total idiosyncratic cost (e.g. have the same value).
+Assume that, even though entrants with different costs have different contribution to the total value, there can be no discrimination between them in terms of the bargaining outcomes.\footnote{
+    In other words, the entry fee must be the same for each player on the same side.
+}
+That is, they must each share the same fraction of the total idiosyncratic cost.
 
 Let us denote the total idiosyncratic cost incurred by all players on both sides as $K(n_1, n_2)$.
-Also, suppose that if $n_i$ players enter on side $i$, then they are the ones with the lowest idiosyncratic cost.
+Also, suppose that if $n_i$ players enter on side $i$, then they are the ones with the lowest idiosyncratic cost amongst all possible entrants.
 Then, the total idiosyncratic cost is simply the sum of the idiosyncratic costs of the entrants on both sides:
@@
 
-That is, each side only has to bear some part of the total idiosyncratic cost, and the rest is shared with the platform.
+That is, each side only has to bear some part of their idiosyncratic entry cost, with the rest being shared with the platform.
 As with the rest of the value, the share of the idiosyncratic cost is increasing in one's own bargaining weight.
 This might seem counterintuitive at first, as one may expect that a player with a higher bargaining weight would be able to shift more of the cost to the other side.
-However, in the case of random order values, this intuition is only correct for monotonic games, which it is not.
-One has to keep in mind though that this is just part of the final payoffs, and the other parts are increasing in one's own bargaining weight.
-Therefore, as long as the game over the total value is monotonic, the final payoffs will be increasing in one's own bargaining weight.
+However,  this intuition is only correct for monotonic games, which it is not.
+One has to remember that this is just part of the final payoffs, and the other parts are increasing in one's own bargaining weight.
+Therefore, as long as the game over the total value is monotonic, the final payoffs will be increasing in one's own bargaining weight, too.
 
@@
 As with the other components of the value, the idiosyncratic entry cost is also shared between the platform and the entrants.
-Part of it $(*)$ is incurred on the side of the entrants, while the other part $(**)$ paid by the platform as a reduction of entry fees.
-How this cost is divided is not straightforward, though.
-As in the case of non-linear network effects, it depends on the bargaining weights and the shape of the idiosyncratic cost function, with the two also interacting in a non-trivial way.
+Part of it, $(*)$, is incurred on the side of the entrants, while the other part, $(**)$, is paid by the platform as a reduction of entry fees.
+However, how this cost is divided is quite intricate.
+As in the case of non-linear network effects, it depends on the bargaining weights and the shape of the idiosyncratic cost function, with the two also interacting in a complex way.
 

### 2024-08-21 src/paper/application.tex
Highlight diff-in-diff idea

@@
 I propose an analytically tractable that captures many important aspects of bargaining between one large and a continuum of small players: namely, a hybrid platform facing a continuum of potential entrants.
-I show that hybrid operation can indeed have negative welfare consequences for consumers in the presence of bargaining.
-This result is particularly striking in this otherwise distortion-free\footnote{
-    The platform's hybrid operation does not affect consumer welfare in the benchmark model without bargaining.
-} setting. 
+In this paper's distortion-free setting with lump-sum entry fees, hybrid platforms are not detrimental to consumer welfare under the usual assumption of the platform setting the entry fee unilaterally.
+I show that, in contrast, in the presence of bargaining, hybrid operation can reduce consumer welfare.
 The intuition is that hybrid operation increases the platform's bargaining power against the entrant sellers.

### 2024-08-21 src/paper/theory.tex
Armin's comments

@@
 
-This paper provides a general framework for modeling bargaining outcomes in this setting.
-By relying on the general concept of random order values, I highlight the common themes between various results found in more applied papers.
+I focus on how the central and fringe players split the total value that they can create.
+By relying on a generalization of the Shapley value, namely, random order values\footnote{
+    Similarly to the Shapley-value, random order values are also based on players' average marginal contributions to coalitions' values.
+    Contrary to the Shapley value, this average can be taken with respect to any probability distribution.
+}, this paper provides a general framework for modeling bargaining outcomes in this setting.
+This also highlights the common themes between various results found in more applied papers.
 I demonstrate that these values are described by tractable expressions and have geometric interpretations.
@@
 
-The other strand of research closely related to this paper belongs to the industrial organization literature.
+The other strand of research closely related to this paper belongs to the industrial organization literature, and, more specifically, to the literature on intermediation, multi-sided markets and vertical integration.
 Despite their theoretical appeal and tractability, oceanic games saw remarkably little use in industrial organization and, more generally, applied economics.
@@
 
-The present paper contributes to this literature by generalizing its results and highlighting some general properties of the various values in the context of such games.
+The present paper contributes to this literature by providing a general framework for modeling bargaining outcomes in such settings, and highlighting some general properties of the various bargaining rules used in these papers.
 The latter is achieved by relying on the concept of random order values, which includes the Shapley value and the weighted value as special cases.
-The generalizations include relaxing the assumption on the indispensability of the central player, providing results for the distribution of the value between the various types of fringe players, and going beyond the Shapley value in the heterogeneous fringe player case.
+The generalizations include relaxing the assumption on the indispensability of the central player, which is especially relevant in the context of competing platforms.
+Additionally, I provide results on how the total value is distributed between the various players in the case of heterogeneous fringe when using weighted values.
 
@@
 Thus, despite the main results being presented in an abstract setting, this paper also has some minor contributions towards better understanding the functioning of platform economies.
+In particular, it highlights that, in contrast to the unilateral price-setting case, under bargaining, entry fees for each side of the market do depend on the surplus realized on that side.\footnote{
+    In the benchmark, unilateral price-setting model, the entry fee only depends on the externalities that the entrants impose and the elasticity of entry as a function of the entry fee.
+}
 

### 2024-08-21 src/paper/application.tex
Fix typo

@@
 This section presents a number of comparative statics results that can be obtained even in this rather abstract setting.
-It contains three sets of results: (1) participants' profits in a partial equilibrium setting, where the number of fringe firms is taken as fixed, (2) equilibrium entry as a function of the platform's product variety, and (3) the platform's profits in general equlibrium.
+It contains three sets of results: (1) participants' profits in a partial equilibrium setting, where the number of fringe firms is taken as fixed, (2) equilibrium entry as a function of the platform's product variety, and (3) the platform's profits in general equilibrium.
 Throughout the paper, I use $\frac{\partial X}{\partial N_P}$ to denote partial equilibrium results, while $\frac{\dd X}{\dd N_P} \coloneq \frac{\partial X(N_P, N_F(N_P))}{\partial N_P}$ indicates general equilibrium results, where fringe entry is endogenous.

### 2024-08-22 src/paper/theory.tex
Fix typo
Improve proof

@@
     Assume that $X_n^j$ and $X_n^k$ are independent for all $j \neq k$.
-    Furthermore, supppose that $X_n^j \xrightarrow[]{d} X^j$ with cdf $G(t)$ and (if exists) pdf $g(t)$ for every $j = 1, \dots, m$.
+    Furthermore, suppose that $X_n^j \xrightarrow[]{d} X^j$ with cdf $G(t)$ and (if exists) pdf $g(t)$ for every $j = 1, \dots, m$.
 
@@
     First, fix some fringe player $A_{li}$.
-    Let $Y_n$ be the random variable describing the share of each type of fringe player that precede player $A_{li}$.
+    Let $Y_n = (Y_n^1, \dots, Y_n^L)$ be the random variable describing the share of each type of fringe player that precede player $A_{li}$.
     Also, let $Q_n$ be the random variable describing whether player $P$ precedes player $A_{li}$.
@@
     \begin{align*}
-        \varphi_{A_{l}}^n = n \varphi_{A_{li}}^n = \E \bigg[ \underbrace{\mathbf{1}[Q_n = 1] \frac{f(Y_1, \dots, Y_l + 1/n, \dots, Y_L) - f(Y_1, \dots, Y_l, \dots, Y_L)}{1/n}}_{\coloneqq \Delta_n} \bigg].
-    \end{align*}
-
-    Now notice that, because the number of fringe players goes to infinity,
-    \begin{align*}
-        X_n \xrightarrow[]{d} (a_1(\xi), \dots, a_L(\xi)) &\implies Y_n \xrightarrow[]{d} (a_1(\xi), \dots, a_L(\xi)) \\
-        &\implies (Y_1, \dots, Y_n) | Y_l = a_l(s) \xrightarrow[]{d} (a_1(s), \dots, a_l(s)) .
+        \varphi_{A_{l}}^n = n \varphi_{A_{li}}^n &= \E \bigg[ \mathbf{1}[Q_n = 1] \underbrace{\frac{f(Y_n^1, \dots, Y_n^l + 1/n, \dots, Y_n^L) - f(Y_n^1, \dots, Y_n^l, \dots, Y_n^L)}{1/n}}_{\coloneqq \Delta_n} \bigg] \\
+        &= \E_{Y_n^L} \Bigg[ \E \bigg[ \mathbf{1}[Q_n = 1] \underbrace{\frac{f(Y_n^1, \dots, Y_n^l + 1/n, \dots, Y_n^l) - f(Y_n^1, \dots, Y_n^l, \dots, Y_n^L)}{1/n}}_{\coloneqq \Delta_n} \bigg| Y_n^l \bigg] \Bigg].
+    \end{align*}
+
+    Now, notice that, because the number of fringe players goes to infinity,
+    \begin{align*}
+        X_n \xrightarrow[]{d} (a_1(\xi), \dots, a_L(\xi)) &\implies Y_n \mid Y_n^l = y \xrightarrow[]{d} (a_1(a_l^{-1}(y)), \dots, a_L(a_l^{-1}(y))).
     \end{align*}
@@
     \begin{align*}
-        \Pr(Q_n = 1 | [Y_n]_l = a_l(s)) \to H(s).
+        \Pr(Q_n = 1 | Y_n^l = y) \to H(a_l^{-1}(y)).
     \end{align*}
@@
     \begin{align*}
-        \lim_{n \to \infty} \varphi_{A_{l}}^n &= \lim_{n \to \infty} \E[\Delta_n (Y_n)] \\
+        \lim_{n \to \infty} \varphi_{A_{l}}^n &= \lim_{n \to \infty} \E[\mathbf{1}[Q_n = 1] \Delta_n (Y_n)] \\
         &= \E[ H(s) \partial_l f(Y_1, \dots, Y_L) ] \\
-        &= \int_0^1 H(s) \partial_l f(a_1(s), \dots, a_L(s)) \mathrm{d} a_l(s) \\
+        &= \int_0^1 H(a_l^{-1}(y)) \partial_l f(a_1(a_l^{-1}(y)), \dots, a_L(a_l^{-1}(y))) \mathrm{d}y \\
         &= \int_0^1 H(s) a_l'(s) \partial_l f(a_1(s), \dots, a_L(s)) \ds.

### 2024-08-26 src/paper/application.tex
Archive repo and point to new one.

@@
 \newcommand*{\firstdraft}{\normalsize{First draft: 27 March 2023}} 
-\newcommand*{\latestversion}{\normalsize{Latest version: \href{https://stanmart.github.io/ValueOfIntermediation/application.pdf}{stanmart.github.io/ValueOfIntermediation/application.pdf}}}
+\newcommand*{\latestversion}{\normalsize{Latest version: \href{https://stanmart.github.io/phd-thesis/application.pdf}{stanmart.github.io/phd-thesis/application.pdf}}}
 

### 2024-08-26 src/paper/theory.tex
Archive repo and point to new one.

@@
 \newcommand*{\firstdraft}{\normalsize{First draft: 2 August 2022}} 
-\newcommand*{\latestversion}{\normalsize{Latest version: \href{https://stanmart.github.io/ValueOfIntermediation/theory.pdf}{stanmart.github.io/ValueOfIntermediation/theory.pdf}}}
+\newcommand*{\latestversion}{\normalsize{Latest version: \href{https://stanmart.github.io/phd-thesis/theory.pdf}{stanmart.github.io/phd-thesis/theory.pdf}}}
 
